### 2018-05-15 pilot_manuscript.Rmd
here's the papaja

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
```

# Method

## Participants

## Material

## Procedure

```{r scraping, eval=FALSE, include=FALSE}

```

## Data analysis

```{r data-cleanup, eval=FALSE, include=FALSE}

```

# Results

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2018-06-19 pilot_manuscript.Rmd
started the markdown and wrote some stuff

@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "Moral Foundations of U.S. Political News Organizations"
+shorttitle        : "MORAL FOUNDATIONS OF U.S. NEWS"
 
 author: 
-  - name          : "First Author"
+  - name          : "William E. Padfield"
     affiliation   : "1"
@@
     address       : "Postal address"
-    email         : "my@email.com"
-  - name          : "Ernst-August Doelle"
+    email         : "Padfield94@live.missouristate.edu"
+  - name          : "Erin M. Buchanan, PhD."
     affiliation   : "1,2"
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Missouri State University"
   - id            : "2"
@@
 ## Participants
+Political articles were scraped from the websites of four (*N* = 4) notable U.S.
+news sources.
+The sources were *The New York Times*, National Public Radio (NPR), *Fox News*, and *Breitbart*.
+They were selected for their widespread recognition and the fact they are easily categorized (by the general public) according to perceived political lean.
+In general, *The New York Times* and *NPR* are perceived by many to have a liberal bias or lean.
+In contrast, Fox News and Breitbart are believed to have a conservative bias or lean.
+Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
+For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
+Identification of the sources' poltical URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
+While in the multi-week process of scraping articles, we noticed word counts for NPR and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
+Upon investigation, we found another, more robust URL for polticial content from NPR: their poltics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
+Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
+We later ran a process in order to exclude any duplicate articles.
+*Fox News* presented a similar issue.
+We discovered *Fox News* utilized six URLs in addition to the regular politics page.
+These URLs led to pages containing content pertaining the U.S.
+Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
+Once again, duplicates were subsequently eliminated from any analyses.
 
@@
 ```{r scraping, eval=FALSE, include=FALSE}
+library(rvest)
+####NY Times####
+#Specifying the url for desired website to be scrapped
+url <- 'https://www.nytimes.com/section/politics'
+
+#Reading the HTML code from the website - headlines
+webpage <- read_html(url)
+headline_data = html_nodes(webpage,'.story-link a, .story-body a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep("http", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.story-content')
+
+  ##pull the text
+  text_data = html_text(headline_data)
+
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+    } ##end for loop
+
+####NPR original front page####
+url2 = 'https://www.npr.org/sections/politics/'
+webpage2 = read_html(url2)
+headline_data2 = html_nodes(webpage2,'.title a')
+
+#URLs
+attr_data2 = html_attrs(headline_data2) 
+attr_data2
+
+urlslist2 = unlist(attr_data2)
+urlslist2 = urlslist2[grep("http", urlslist2)]
+urlslist2
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 1:length(urlslist2)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist2[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'#storytext > p')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  NPRDF$Source[i] = "NPR"
+  NPRDF$Url[i] = urlslist2[i]
+  NPRDF$Text[i] = paste(text_data2, collapse = "")
+} ##end for loop
+
+####Fox News####
+url3 = 'http://www.foxnews.com/politics.html'
+url3.1 = 'http://www.foxnews.com/category/politics/executive.html'
+url3.2 = 'http://www.foxnews.com/category/politics/senate.htm.html'
+url3.3 = 'http://www.foxnews.com/category/politics/house-representatives.html'
+url3.4 = 'http://www.foxnews.com/category/politics/judiciary.html'
+url3.5 = 'http://www.foxnews.com/category/politics/foreign-policy.html'
+url3.6 = 'http://www.foxnews.com/category/politics/elections.html'
+webpage3 = read_html(url3)
+webpage3.1 = read_html(url3.1)
+webpage3.2 = read_html(url3.2)
+webpage3.3 = read_html(url3.3)
+webpage3.4 = read_html(url3.4)
+webpage3.5 = read_html(url3.5)
+webpage3.6 = read_html(url3.6)
+
+headline_data3 = html_nodes(webpage3, '.story- a , .article-list .title a')
+headline_data3.1 = html_nodes(webpage3.1, '.story- a , .article-list .title a')
+headline_data3.2 = html_nodes(webpage3.2, '.story- a , .article-list .title a')
+headline_data3.3 = html_nodes(webpage3.3, '.story- a , .article-list .title a')
+headline_data3.4 = html_nodes(webpage3.4, '.story- a , .article-list .title a')
+headline_data3.5 = html_nodes(webpage3.5, '.story- a , .article-list .title a')
+headline_data3.6 = html_nodes(webpage3.6, '.story- a , .article-list .title a')
+
+#headline_data = html_text(headline_data)
+head(headline_data3)
+
+attr_data3 = html_attrs(headline_data3) 
+attr_data3.1 = html_attrs(headline_data3.1) 
+attr_data3.2 = html_attrs(headline_data3.2) 
+attr_data3.3 = html_attrs(headline_data3.3) 
+attr_data3.4 = html_attrs(headline_data3.4) 
+attr_data3.5 = html_attrs(headline_data3.5) 
+attr_data3.6 = html_attrs(headline_data3.6)
+
+attr_data3
+
+urlslist3 = c(unlist(attr_data3), unlist(attr_data3.1), 
+              unlist(attr_data3.2), unlist(attr_data3.3), 
+              unlist(attr_data3.4), unlist(attr_data3.5, attr_data3.6))
+##find all that are href
+urlslist3 = urlslist3[grep("http|.html", urlslist3)]
+##fix the ones without the leading foxnews.com
+urlslist3F = paste("http://www.foxnews.com", urlslist3[grep("^http", urlslist3, invert = T)], sep = "")
+urlslist3N = urlslist3[grep("^http", urlslist3)]
+urlslist3 = c(urlslist3N, urlslist3F)
+urlslist3 = unique(urlslist3)
+urlslist3
+
+##start a data frame
+FoxDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(FoxDF) = c("Source", "Url", "Text")
+FoxDF = as.data.frame(FoxDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage3 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data3 = html_nodes(webpage3,'p+ p , .fn-video+ p , .twitter+ p , .speakable')
+
+  ##pull the text
+  text_data3 = html_text(headline_data3)
+
+  ##save the data
+  FoxDF$Source[i] = "Fox News"
+  FoxDF$Url[i] = urlslist3[i]
+  FoxDF$Text[i] = paste(text_data3, collapse = "")
+} ##end for loop
+
+####Breitbart####
+url4 = 'http://www.breitbart.com/big-government/'
+webpage4 = read_html(url4)
+headline_data4 = html_nodes(webpage4, '.title a , #grid-block-0 span , #BBTrendUL a , #disqus-popularUL a , font')
+#headline_data4 = html_text(headline_data4)
+head(headline_data4)
+
+attr_data4 = html_attrs(headline_data4) 
+attr_data4
+
+urlslist4 = unlist(attr_data4)
+##find all that are href
+urlslist4 = urlslist4[grep("http|/big-government", urlslist4)]
+##fix the ones without the leading bb
+urlslist4F = paste("http://www.breitbart.com", urlslist4[grep("^http", urlslist4, invert = T)], sep = "")
+urlslist4N = urlslist4[grep("^http", urlslist4)]
+urlslist4 = c(urlslist4N, urlslist4F)
+urlslist4 = unique(urlslist4)
+urlslist4
+
+##start a data frame
+BreitbartDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
+colnames(BreitbartDF) = c("Source", "Url", "Text")
+BreitbartDF = as.data.frame(BreitbartDF)
+
+##for loops
+for (i in 1:length(urlslist4)){
+
+  ##read in the URL
+  webpage4 <- read_html(urlslist4[i])
+
+  ##pull the specific nodes
+  headline_data4 = html_nodes(webpage4,'.entry-content p , h2')
+
+  ##pull the text
+  text_data4 = html_text(headline_data4)
+
+  ##save the data
+  BreitbartDF$Source[i] = "Breitbart"
+  BreitbartDF$Url[i] = urlslist4[i]
+  BreitbartDF$Text[i] = paste(text_data4, collapse = "")
+} ##end for loop
+
+####NPR Archive####
+url5 = 'https://www.npr.org/sections/politics/archive'
+webpage5 = read_html(url5)
+headline_data5 = html_nodes(webpage5,'.title a')
+#headline_data = html_text(headline_data)
+#head(headline_data)
+
+#URLs
+attr_data5 = html_attrs(headline_data5) 
+attr_data5
+
+urlslist5 = unlist(attr_data5)
+urlslist5 = urlslist5[grep("http", urlslist5)]
+urlslist5
+
+##start a data frame
+NPRArchiveDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
+colnames(NPRArchiveDF) = c("Source", "Url", "Text")
+NPRArchiveDF = as.data.frame(NPRArchiveDF)
+
+##for loops
+for (i in 1:length(urlslist5)){
+
+  ##read in the URL
+  webpage5 <- read_html(urlslist5[i])
+
+  ##pull the specific nodes
+  headline_data5 = html_nodes(webpage5,'#storytext > p')
+
+  ##pull the text
+  text_data5 = html_text(headline_data5)
+
+  ##save the data
+  NPRArchiveDF$Source[i] = "NPR"
+  NPRArchiveDF$Url[i] = urlslist5[i]
+  NPRArchiveDF$Text[i] = paste(text_data5, collapse = "")
+} ##end for loop
+
+####put together####
+##set your working directory
+setwd("~/OneDrive - Missouri State University/RESEARCH/2 projects/Will-Pilot")
+
+##import the overalldata 
+overalldata = read.csv("overalldata.csv")
+
+##combine with new data (add the other DF names in here...)
+newdata = rbind(overalldata, NYtimesDF, NPRDF, FoxDF, BreitbartDF, NPRArchiveDF)
+
+#temp NPR updates
+#newdata = newdata[ , -4]
+#newdata = rbind(newdata, NPRArchiveDF)
+
+#change politics archive to NPR, so we can eliminate dupes
+#newdata$Source[newdata$Source == "NPR Politics Archive"] = "NPR"
+#newdata$Source = droplevels(newdata$Source)
+
+##make the newdata unique in case of overlap across days
+newdata = unique(newdata)
+
+##write it back out
+write.csv(newdata, "overalldata.csv", row.names = F)
+
+##number of articles
+table(newdata$Source)
+
+##number of words
+library(ngram)
+newdata$Text = as.character(newdata$Text)
+for (i in 1:nrow(newdata)) {
+
+  #newdata$writing[i] = preprocess(newdata$Text[i], case="lower", remove.punct=TRUE)
+  newdata$wordcount[i] = string.summary(newdata$Text[i])$words
+
+}
+
+tapply(newdata$wordcount, newdata$Source, mean)
+tapply(newdata$wordcount, newdata$Source, sum)
 
@@
 ```{r data-cleanup, eval=FALSE, include=FALSE}
+##pull in the data
+master = read.csv("overalldata.csv", stringsAsFactors = F)
 
+##get rid of the blank stuff
+library(ngram)
+
+for (i in 1:nrow(master)) {
+  master$wordcount[i] = wordcount(master$Text[i])
+}
+
+nozero = subset(master, wordcount > 0)
+tapply(nozero$wordcount, nozero$Source, mean)
+tapply(nozero$wordcount, nozero$Source, sum)
+
+##take out the disqus ones
+nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
+
+##figure out the duplicates
+nodis$URLS = duplicated(nodis$Url)
+
+##all data
+final = subset(nodis, URLS == FALSE)
+
+tapply(final$wordcount, final$Source, mean)
+tapply(final$wordcount, final$Source, sum)
+
+#write.csv(final, "finaldata.csv")
+
+####start here####
+final = read.csv("finaldata.csv", stringsAsFactors = F)
+final = na.omit(final) #one weird NA line
+
+```
+
+```{r fix MFD, eval=FALSE, include=FALSE}
+##figure out the percent of MFD words
+
+##the amount of time people used the original MFD words
+original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
+
+##adding forms/conjugations of words to original_mfd
+#harm/care
+original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
+                             "sympathetic","sympathies","damaged",
+                             "damaging","attacked","attacking","attacker",
+                             "attacks","attackers", "benefits", "benefitted",
+                             "benefitting", "cares", "cared", "caring", "crushes",
+                             "crushing", "crushed", "dangerous", "defends", "defending",
+                             "defended", "detroys", "destroyed", "destroying",
+                             "fights", "fought", "fighting", "guards", "guarded",
+                             "guarding", "harms", "harmed", "harming", "hurts",
+                             "hurting", "kills", "killed", "killing", "preserves",
+                             "preserved", "preserving", "protects", "protected",
+                             "protecting", "protection", "ruins", "ruined", "ruining",
+                             "safely", "safer", "shelters", "sheltered", "sheltering",
+                             "spurns", "spurned", "spurning", "stomps", "stomped",
+                             "stomping", "suffers", "suffered", "suffering",
+                             "violence", "warring")
+
+#fairness/reciprocity
+original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
+                             "biases", "discriminates", "discriminated",
+                             "discriminating", "discrimination", "equals",
+                             "equaled", "equaling", "equates", "equated",
+                             "equating", "evens", "evened", "evening",
+                             "excludes", "excluded", "excluding", "fairness",
+                             "favors", "favored", "favoring", "honesty",
+                             "impariality", "justice", "justifies", "justified",
+                             "justifying", "prefers", "preferred", "preferring",
+                             "prejudices", "prejudiced", "prejudicing", "reasons",
+                             "reasoned", "reasoning", "rights", "tolerates",
+                             "tolerated", "tolerating", "toleration")
+
+#ingroup/loyalty
+original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
+                             "communities", "deceives", "deceived", "deceiving",
+                             "deception", "deceptions", "deserts", "deserted",
+                             "deserting", "desertion", "families", "fellows",
+                             "foreigners", "groups", "grouped", "grouping",
+                             "indviduals", "indvidualize", "individualized",
+                             "individualizing", "members", "nations", "sides",
+                             "togetherness", "traits", "unites", "united", "uniting")
+
+#authority/respect
+original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
+                              "classes", "classed", "classing", "command",
+                              "commanded", "commanding", "controls", "controlled",
+                              "controlling", "defects", "defected", "defecting",
+                              "defers", "deferred", "deferring", "deference",
+                              "defies", "defied", "defying", "defiance", "deserts",
+                              "deserted", "deserting", "desertion", "duties",
+                              "faiths", "fathers", "fathered", "fathering",
+                              "honors", "honored", "honoring", "laws", "leads",
+                              "leading", "mothers", "mothered", "mothering",
+                              "obeys", "obeyed", "obeying", "opposes", "opposed",
+                              "opposing", "orders", "ordered", "ordering", "permits",
+                              "permitted", "permitting", "positions", "positioned",
+                              "positioning", "preserves", "preserved", "preserving",
+                              "preservation", "protests", "protested", "protesting",
+                              "refuses", "refused", "refusing", "refusal", "respects",
+                              "respected", "respecting", "respectful", "reveres",
+                              "revered", "revering", "reverence", "serves", "served",
+                              "serving", "traditions", "traditional", "traits")
+
+#purity/sanctity
+original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
+                             "adulteries", "adulterous", "adulterer", "adulterers",
+                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
+                             "cleanliness", "dirty", "diseases", "diseased", 
+                             "disgusts", "disgusted", "disgusting", "grossness",
+                             "innocence", "modesty", "preserves", "preserved",
+                             "preserving", "preservation", "promiscuity",
+                             "promiscuities", "purity", "rights", "ruins", "ruined",
+                             "ruining", "sacredness", "sickness", "sicknesses",
+                             "sins", "wholeness", "wholesome")
+
+##separate them into h low, h high until you have ten categories 
+#harm/care
+original_mfd$h2hi[35:112] = NA 
+original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
+                      "protect", "safe", "shelter", "sympathetic",
+                      "sympathies", "benefits", "benefitted",
+                      "benefitting", "cares", "cared", "caring","defends", 
+                      "defending","defended", "guards", "guarded",
+                      "guarding","preserves",
+                      "preserved", "preserving", "protects", "protected",
+                      "protecting", "protection",  
+                      "safely", "safer", "shelters", 
+                      "sheltered", "sheltering")
+original_mfd$h2lo[61:112] = NA
+original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
+                      "damage", "danger", "destroy", "fight", "harm",
+                      "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
+                      "violent", "war","abusive",
+                      "abuser","abused","abusing","damaged",
+                      "damaging","attacked","attacking","attacker",
+                      "attacks","attackers","crushes",
+                      "crushing", "crushed", "dangerous","detroys", 
+                      "destroyed", "destroying",
+                      "fights", "fought", "fighting","harms", 
+                      "harmed", "harming", "hurts",
+                      "hurting", "kills", "killed", "killing",
+                      "ruins", "ruined", "ruining", "spurns", 
+                      "spurned", "spurning", "stomps", "stomped",
+                      "stomping", "suffers", "suffered", "suffering",
+                      "violence", "warring")
+
+#fairness/reciprocity
+original_mfd$f2hi[41:112] = NA
+original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
+                      "fair", "honest", "just", "justify", "reason",
+                      "right", "tolerate", "impartial", "balances", 
+                      "balanced", "balancing",
+                      "equals", "equaled", "equaling", "equates", "equated",
+                      "equating", "evens", "evened", "evening","fairness",
+                      "honesty", "impartiality", "justice", "justifies", 
+                      "justified", "justifying", "reasons",
+                      "reasoned", "reasoning", "rights", "tolerates",
+                      "tolerated", "tolerating", "toleration")
+original_mfd$f2lo[25:112] = NA
+original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
+                      "prefer", "prejudice", "biased", "biases", "discriminates", 
+                      "discriminated", "discriminating", "discrimination",
+                      "excludes", "excluded", "excluding", 
+                      "favors", "favored", "favoring", "prefers", "preferred", "preferring",
+                      "prejudices", "prejudiced", "prejudicing")
+
+#ingroup/loyalty
+original_mfd$i2hi[30:112] = NA
+original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
+                      "group", "member", "nation", "side", "together",
+                      "trait", "unite", "collects", 
+                      "collected", "collecting", "collective",
+                      "communities", "families", "fellows",
+                      "groups", "grouped", "grouping",
+                      "members", "nations", "sides",
+                      "togetherness", "traits", "unites", 
+                      "united", "uniting")
+original_mfd$i2lo[19:112] = NA 
+original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
+                      "deceives", "deceived", "deceiving",
+                      "deception", "deceptions", "deserts", "deserted",
+                      "deserting", "desertion", "foreigners",
+                      "indviduals", "indvidualize", "individualized",
+                      "individualizing")
+
+#authority/respect
+original_mfd$a2hi[86:112] = NA
+original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
+                      "control", "defer", "duty", "faith", "father", "honor",
+                      "law", "lead", "legal", "mother", "obey", 
+                      "order", "permit", "position", "preserve",
+                      "respect", "revere", "serve", "tradtition", "trait",
+                      "abides", "abided", "abiding", "authorities",
+                      "classes", "classed", "classing", "command",
+                      "commanded", "commanding", "controls", "controlled",
+                      "controlling","defers", "deferred", "deferring", "deference",
+                      "duties","faiths", "fathers", "fathered", "fathering",
+                      "honors", "honored", "honoring", "laws", "leads",
+                      "leading", "mothers", "mothered", "mothering",
+                      "obeys", "obeyed", "obeying", "orders", 
+                      "ordered", "ordering", "permits",
+                      "permitted", "permitting", "positions", "positioned",
+                      "positioning", "preserves", "preserved", "preserving",
+                      "preservation", "respects",
+                      "respected", "respecting", "respectful", "reveres",
+                      "revered", "revering", "reverence", "serves", "served",
+                      "serving", "traditions", "traditional", "traits")
+original_mfd$a2lo[28:112] = NA
+original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
+                      "protest", "refuse", "defects", "defected", 
+                      "defecting","defies", "defied", "defying", "defiance", "deserts",
+                      "deserted", "deserting", "desertion", "opposes", "opposed",
+                      "opposing", "protests", "protested", "protesting",
+                      "refuses", "refused", "refusing", "refusal")
+
+#purity/sanctity
+original_mfd$p2hi[32:112] = NA
+original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
+                      "preserve", "pure", "right", "sacred", "whole",
+                      "abstains", "abstained", "abstaining", "abstinence",
+                      "churches", "cleans", "cleaned", "cleaning", "cleanse",
+                      "cleanliness", "innocence", "modesty", "preserves", "preserved",
+                      "preserving", "preservation", "purity", "rights", 
+                      "sacredness", "wholeness", "wholesome")
+original_mfd$p2lo[30:112] = NA
+original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
+                      "promiscuous", "ruin", "sick", "sin", "trash",
+                      "adulteries", "adulterous", "adulterer", "adulterers",
+                      "dirty", "diseases", "diseased", "disgusts", 
+                      "disgusted", "disgusting", "grossness", "promiscuity",
+                      "promiscuities", "ruins", "ruined","ruining", 
+                      "sickness", "sicknesses", "sins")
+```
+
+```{r process text, eval=FALSE, include=FALSE}
+##load libraries
+library(tm)
+library(ngram)
+
+#process the Text column (write a loop) - save processed text as a separate column
+for(i in 1:nrow(final)) {
+
+  final$edited[i] = preprocess(final$Text[i], #one value at a time
+           case = "lower", 
+           remove.punct = TRUE,
+           remove.numbers = FALSE, 
+           fix.spacing = TRUE)
+
+##stem the words - do this second in the loop
+  final$stemmed[i] = stemDocument(final$edited[i], language = "english")
+}
+
+##stem the original MFD stuff - separate loop on only the mfd data frame
+for(i in 1:nrow(original_mfd)) {
+  original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
+  original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
+  original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
+  original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
+  original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
+  original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
+  original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
+  original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
+  original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
+  original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
+}
+
+final$hhisum = NA
+final$hlosum = NA
+final$fhisum = NA
+final$flosum = NA
+final$ihisum = NA
+final$ilosum = NA
+final$ahisum = NA
+final$alosum = NA
+final$phisum = NA
+final$plosum = NA
+
+for (i in 1:nrow(final)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
+##find the rows that match the mfd list and sum and save
+final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
+final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])
+
+final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
+final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])
+
+final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
+final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])
+
+final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
+final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])
+
+final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
+final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
+}
+
+final$hperhi = final$hsumhi / final$wordcount * 100
+final$hperlo = final$hsumlo / final$wordcount * 100
+final$fperhi = final$fsumhi / final$wordcount * 100
+final$fperlo = final$fsumlo / final$wordcount * 100
+final$iperhi = final$isumhi / final$wordcount * 100
+final$iperlo = final$isumlo / final$wordcount * 100
+final$aperhi = final$asumhi / final$wordcount * 100
+final$aperlo = final$asumlo / final$wordcount * 100
+final$pperhi = final$psumhi / final$wordcount * 100
+final$pperlo = final$psumlo / final$wordcount * 100
+
+#let's look at the means
+tapply(final$hperhi, final$Source, mean)
+tapply(final$hperlo, final$Source, mean)
+tapply(final$fperhi, final$Source, mean)
+tapply(final$fperlo, final$Source, mean)
+tapply(final$iperhi, final$Source, mean)
+tapply(final$iperlo, final$Source, mean)
+tapply(final$aperhi, final$Source, mean)
+tapply(final$aperlo, final$Source, mean)
+tapply(final$pperhi, final$Source, mean)
+tapply(final$pperlo, final$Source, mean)
+```
+
+```{r mlm, eval=FALSE, include=FALSE}
+##Attempt at MLM
+mlm_data = final[ , -c(3:28) ]
+library(reshape)
+long_mlm = melt(mlm_data,
+                id = c("X", "Source"))
+colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
+long_mlm$lean = factor(long_mlm$Source,
+                       levels = names(table(long_mlm$Source)),
+                       labels = c("Conservative1", "Conservative",
+                                  "Liberal1", "Liberal"))
+long_mlm$lean = gsub("1", "", long_mlm$lean)
+
+##set up the analysis
+library(nlme)
+#####intercept only model####
+##gls = generalized least squares
+##ML = maximum likelihood
+model1 = gls(percent ~ 1, #DV ~ IV (which is only the intercept; is y-average diff than 0?)
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit")
+summary(model1)
+
+####random intercept only model####
+##note we switched to LME function
+model2 = lme(percent ~ 1, 
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|partno) #sets random intercept for each participant
+summary(model2) #note changed Value in output; also, 
+#Random effects tells how much intercept varies among Pps
+anova(model1, model2) #tests if necessary to nest; Yes, we need to do MLM
+
+####predictor model####
+model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|partno)
+summary(model3)
+anova(model1, model2, model3)
+
+model3.1 = lme(percent ~ lean + moraltype, #now we want to switch the 1 for IV of interest
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|partno)
+summary(model3.1)
+
+model3.2 = lme(percent ~ lean * moraltype, #now we want to switch the 1 for IV of interest
+               data = long_mlm, 
+               method = "ML", 
+               na.action = "na.omit",
+               random = ~1|partno)
+summary(model3.2)
+
+##model 3 on each moral foundation separately
+#h_hi
+model3h_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|partno)
+summary(model3h_hi)
+tapply(long_mlm[long_mlm$moraltype == "hperhi", ]$percent,
+       long_mlm[long_mlm$moraltype == "hperhi", ]$lean, mean)
+#h_lo
+model3h_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "hperlo", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3h_lo)
+tapply(long_mlm[long_mlm$moraltype == "hperlo", ]$percent,
+       long_mlm[long_mlm$moraltype == "hperlo", ]$lean, mean)
+#f_hi
+model3f_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "fperhi", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3f_hi)
+tapply(long_mlm[long_mlm$moraltype == "fperhi", ]$percent,
+       long_mlm[long_mlm$moraltype == "fperhi", ]$lean, mean)
+#f_lo
+model3f_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "fperlo", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3f_lo)
+tapply(long_mlm[long_mlm$moraltype == "fperlo", ]$percent,
+       long_mlm[long_mlm$moraltype == "fperlo", ]$lean, mean)
+#i_hi
+model3i_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "iperhi", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3i_hi)
+tapply(long_mlm[long_mlm$moraltype == "iperhi", ]$percent,
+       long_mlm[long_mlm$moraltype == "iperhi", ]$lean, mean)
+#i_lo
+model3i_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "iperlo", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3i_lo)
+tapply(long_mlm[long_mlm$moraltype == "iperlo", ]$percent,
+       long_mlm[long_mlm$moraltype == "iperlo", ]$lean, mean)
+#a_hi
+model3a_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "aperhi", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3a_hi)
+tapply(long_mlm[long_mlm$moraltype == "aperhi", ]$percent,
+       long_mlm[long_mlm$moraltype == "aperhi", ]$lean, mean)
+#a_lo
+model3a_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "aperlo", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3a_lo)
+tapply(long_mlm[long_mlm$moraltype == "aperlo", ]$percent,
+       long_mlm[long_mlm$moraltype == "aperlo", ]$lean, mean)
+#p_hi
+model3p_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "pperhi", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3p_hi)
+tapply(long_mlm[long_mlm$moraltype == "pperhi", ]$percent,
+       long_mlm[long_mlm$moraltype == "pperhi", ]$lean, mean)
+#p_lo
+model3p_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
+                 data = long_mlm[long_mlm$moraltype == "pperlo", ], 
+                 method = "ML", 
+                 na.action = "na.omit",
+                 random = ~1|partno)
+summary(model3p_lo)
+tapply(long_mlm[long_mlm$moraltype == "pperlo", ]$percent,
+       long_mlm[long_mlm$moraltype == "pperlo", ]$lean, mean)
 ```

### 2018-06-19 pilot_manuscript.Rmd
small updates for you

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
+    address       : "901 S. National Ave, Springfield, MO, 65897"
     email         : "Padfield94@live.missouristate.edu"
   - name          : "Erin M. Buchanan, PhD."
-    affiliation   : "1,2"
+    affiliation   : "1"
 
@@
     institution   : "Missouri State University"
-  - id            : "2"
-    institution   : "Konstanz Business School"
 
@@
 
-bibliography      : ["r-references.bib"]
+#bibliography      : ["r-references.bib"] #turn this off right now so it knits
 
@@
 
-## Participants
-Political articles were scraped from the websites of four (*N* = 4) notable U.S.
+## Sources
+
+Political articles were scraped from the websites of four notable U.S.
 news sources.
-The sources were *The New York Times*, National Public Radio (NPR), *Fox News*, and *Breitbart*.
+The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
 They were selected for their widespread recognition and the fact they are easily categorized (by the general public) according to perceived political lean.
@@
 For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
+
 Identification of the sources' poltical URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for NPR and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
+While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
 Upon investigation, we found another, more robust URL for polticial content from NPR: their poltics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
@@
 
-```{r fix MFD, eval=FALSE, include=FALSE}
+```{r fix-MFD, eval=FALSE, include=FALSE}
 ##figure out the percent of MFD words
@@
 
-```{r process text, eval=FALSE, include=FALSE}
+```{r process-text, eval=FALSE, include=FALSE}
 ##load libraries

### 2018-06-25 pilot_manuscript.Rmd
wrote stuff in the Method section

@@
 ## Procedure
+Using the 'rvest' library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset.
+Using this dataset, we identified word count and average word count per source.
+This process was run once daily starting on *DATE* until *DATE.* Starting on *DATE,* the process was run twice daily - once inthe morning and again in the evening.
+Data collection was terminated once 250,000 words per source was collected on *DATE.*
 
@@
 
+Once data collection ended, the text was scanned using the ngram package in *R*.
+This was done in order to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
+At this point, duplicate articles were discarded.
 ```{r data-cleanup, eval=FALSE, include=FALSE}
@@
 ```
-
+In order to fully capture the evaluative power of the Moral Foundations Dictionary (MFD; *CITE*), forms and conjugations of words were added to the original MFD.
+For example, *abuse* was supplemented with *abusive*, *abuser*, *abused*, and *abusing.* Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e.
+*abide* as a postive authority/respect word and *defect* as a negative authority/respect word).
 ```{r fix-MFD, eval=FALSE, include=FALSE}
@@
 ```
-
+Once the MFD was separated along lines of positive and negative, the article text was processed using the "tm" and "ngram" packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues.
+The individual words were then reduced to their stems (i.e.
+*abused* was stemmed to *abus*).
+The same was done to the MFD words.
+The article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a sum and percentage of their occurence.
 ```{r process-text, eval=FALSE, include=FALSE}
@@
 ```
-
+Usung the "nlme" library in *R*, a 2 X 5 multillevel model with news source as a random intercept was run. *IMMA NEED SOME HELP WITH HOW TO STRUCTURE THIS PART :)*
 ```{r mlm, eval=FALSE, include=FALSE}

### 2018-07-02 pilot_manuscript.Rmd
Wrote more and (very basically) outlined some other sections

@@
 ```
-
+# Introduction
+Talk about MFT, MFQ, MFD
+Talk about political discourse, nature of news media in 2018/Trump era
+This project brings the two together in holy matrimony.
 # Method
@@
 
-Once data collection ended, the text was scanned using the ngram package in *R*.
+Once data collection ended, the text was scanned using the "ngram" package in *R*.
 This was done in order to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
@@
 ```
-Usung the "nlme" library in *R*, a 2 X 5 multillevel model with news source as a random intercept was run. *IMMA NEED SOME HELP WITH HOW TO STRUCTURE THIS PART :)*
+Usung the "nlme" library in *R*, a 2 X 5 multillevel model with news source as a random intercept was run.
+First, an intercept-only model was run, followed by a random intercept model.
+Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e.
+"harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run.
+Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
 ```{r mlm, eval=FALSE, include=FALSE}
@@
 # Results
-
+NUMBERS!!!
 # Discussion
+How it turned out
+What to do for future project
+Argue: why is still a good thing to study??
 

### 2018-07-03 pilot_manuscript.Rmd
made a few small edits
Mostly want to ask you about the MLMs we did and figure out the best approach for the results section.

--- 2018-06-19 pilot_manuscript.Rmd
@@
 ## Procedure
+Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@CITE_rvest].
+Using this dataset, we identified word count and average word count per source.
+This process was run once daily starting on *DATE* until *DATE.* Starting on *DATE,* the process was run twice daily - once in the morning and again in the evening.
+Data collection was terminated once 250,000 words per source was collected on *DATE.*
 
@@
 
+Once data collection ended, the text was scanned using the *ngram* package in *R* [@CITE_ngram].
+This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
+At this point, duplicate articles were discarded.
+
 ```{r data-cleanup, eval=FALSE, include=FALSE}
@@
 ```
+
+In order to fully capture the evaluative power of the Moral Foundations Dictionary (MFD; *CITE*), forms and conjugations of words were added to the original MFD.
+For example, *abuse* was supplemented with *abusive*, *abuser*, *abused*, and *abusing*.
+Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a postive authority/respect word and *defect* as a negative authority/respect word).
 
@@
 
+Once the MFD was separated along lines of positive and negative, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
+The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
+The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function.
+The article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a sum and percentage of their occurence.
+
 ```{r process-text, eval=FALSE, include=FALSE}
@@
 ```
+
+Using the *nlme* library in *R*, a 2 (Political Lean) by 5 (MFD area) multillevel model with news source as a random intercept was analyzed to control for correlated error between articles published in the same news source.
+An intercept-only model was compared to a random intercept model with the news sources as the random factor, and ...SAY HERE WHAT HAPPENED?
+PROB A TABLE OF THE MODEL #S.
+
+#stopped here to ask questions
+
+Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e.
+"harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run.
+Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
 

### 2018-07-03 pilot_manuscript.Rmd
small updates with mumin

@@
 library("papaja")
+library(MuMIn)
 ```
@@
 anova(model1, model2, model3)
+r.squaredGLMM(model3) #gives you two, report both
 

### 2018-07-10 pilot_manuscript.Rmd
updates and first try at Results

@@
 
-```{r data-cleanup, eval=FALSE, include=FALSE}
+```{r data-cleanup, eval=TRUE, include=FALSE}
 ##pull in the data
@@
 
-```{r fix-MFD, eval=FALSE, include=FALSE}
+```{r fix-MFD, eval=TRUE, include=FALSE}
 ##figure out the percent of MFD words
@@
 
-```{r process-text, eval=FALSE, include=FALSE}
+```{r process-text, eval=TRUE, include=FALSE}
 ##load libraries
@@
 anova(model1, model2) #tests if necessary to nest; Yes, we need to do MLM
-
+r.squaredGLMM(model2)
 ####predictor model####
@@
 summary(model3.1)
-
+r.squaredGLMM(model3.1)
 model3.2 = lme(percent ~ lean * moraltype, #now we want to switch the 1 for IV of interest
@@
 summary(model3.2)
-
+r.squaredGLMM(model3.2)
 ##model 3 on each moral foundation separately
@@
 
+```{r mlm table}
+##three models
+table = matrix(NA, nrow = 5, ncol = 10)
+colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
+                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")
+
+##stick in the information you need
+table[1, ] = c("Model 1", 2, 43610.91, 
+               43627.55, -21803.46, "", "",
+               "", "", "")
+
+table[2, ] = c("Model 2", 3, 43611.04, 
+               43636.01, -21802.52, 0.000, 0.004,
+               "Model 1 vs Model 2", 1.871644, 0.173)
+
+table[3, ] = c("Model 3", 4, 43604.33, 
+               43637.62, -21798.17, 0.0003, 0.0037,
+               "Model 2 vs. Model 3", 8.703020, 0.0032)
+
+table[4, ] = c("Model 3.1", 13, 37913.11, 
+               38021.30, -18943.55, 0.17, 0.19,
+               "Model 3 vs. Model 3.1", 5709.23, "< .001")
+
+table[5, ] = c("Model 3.2", 22, 37904.00, 
+              38087.09, -18930.00, 0.17, 0.19,
+               "Model 3.1 vs. Model 3.2", 27.11, 0.001)
+
+##print that sucker out
+library(knitr)
+kable(table)
+```
+
 # Results
-NUMBERS!!!
+Anymore screening/data prep here?
+
+Political lean of the news organization was used to predict the percent of words matching the Moral Foundations Dictionary.
+According to an analysis of variance (ANOVA) between the intercept-only model (Model 1) and the random intercept-only model (Model 2, *R2m* = 0.00, *R2c* = 0.004), there were no statistically significant differences (*F* = *?*, *p* = 0.17).
+There was a signficant difference between the random intercept-only model and the predictor model (Model 3, *R2m* = 0.0003, *R2c* = 0.0037), *F* = *?*, *p* = .003).
+We found a significant difference between the two political leans (*b* = -0.018, *SE* = 0.006, *t*(3039) = -2.95, *p* = 0.003).
+Next, we added Moral Foundation Type as a predictor of percent to the third model (Model 3.1, *R2m* = 0.17, *R2c* = 0.19).
+The ANOVA revealed a significant difference between Models 3 and 3.1, *F* = *?*, *p* < .001)
+
+#Significance for, like, all of the little moral types. Put in table?
+
+Finally, we analyzed the interaction between political lean and Moral Foundation type as a preditor of percent (Model 3.2, *R2m* = 0.17, *R2c* = 0.19).
+Using ANOVA, we found a significant difference between Models 3.1 and 3.2, *F* = *?*, *p* = .001).
+
+#Again, lots of stuff here. Needs to be reported? Put in table?
+
+Comparisons between the models can be found in Table 1. 
 # Discussion

### 2018-07-16 pilot_manuscript.Rmd
Some things added here and there

@@
 ```{r load_packages, include = FALSE}
-library("papaja")
+library("papaja") #R says this package doesn't exist in current version :/
 library(MuMIn)
@@
 # Introduction
-Talk about MFT, MFQ, MFD
+Talk about MFT, MFQ, MFD (primer on moral psychology?)
+
+(Brief) primer on political research?
+
 Talk about political discourse, nature of news media in 2018/Trump era
+
 This project brings the two together in holy matrimony.
@@
 table = matrix(NA, nrow = 5, ncol = 10)
+
+##ARE ALL OF THESE COLUMNS NEEDED?? ALSO, ORDER?
 colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
@@
 # Results
-Anymore screening/data prep here?
+Any more screening/data prep here?
 
@@
 How it turned out
-What to do for future project
-Argue: why is still a good thing to study??
+
+Limitations of this one (no rationale behind choosing sources except "people say NPR's liberal??")
+
+What to do for future project (focus on one MF? Different sources? More sources?)
+
+Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, "alternative facts," subjective reality - philosophical stuff)
 

### 2018-07-19 pilot_manuscript.Rmd
updated some of the results

@@
     email         : "Padfield94@live.missouristate.edu"
-  - name          : "Erin M. Buchanan, PhD."
+  - name          : "Erin M. Buchanan, Ph.D."
     affiliation   : "1"
@@
 library(MuMIn)
+knitr::opts_chunk$set(cache = TRUE)
 ```
@@
 For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
+All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
 
-Identification of the sources' poltical URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
+Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
 While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
-Upon investigation, we found another, more robust URL for polticial content from NPR: their poltics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
+Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
 Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
@@
 
-## Material
+## Materials
 
-## Procedure
 Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@CITE_rvest].
@@
 For example, *abuse* was supplemented with *abusive*, *abuser*, *abused*, and *abusing*.
-Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a postive authority/respect word and *defect* as a negative authority/respect word).
+Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a positive authority/respect word and *defect* as a negative authority/respect word).
 
@@
 
-Once the MFD was separated along lines of positive and negative, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
+Once the MFD was separated along lines of positive and negative dimensions for each of the foundations, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
 The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
 The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function.
-The article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a sum and percentage of their occurence.
+The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence.
+Therefore, for each article, the percentage of the number of *harm* (low end) and *care* (high end) related words were calculated and this process was repeated for each of the foundations.
+This procedure created ten percentages that were included as the dependent variable for the following analyses.
 
@@
 
-Using the *nlme* library in *R*, a 2 (Political Lean) by 5 (MFD area) multillevel model with news source as a random intercept was analyzed to control for correlated error between articles published in the same news source.
-An intercept-only model was compared to a random intercept model with the news sources as the random factor, and ...SAY HERE WHAT HAPPENED?
-PROB A TABLE OF THE MODEL #S.
-
-#stopped here to ask questions
-
-Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e.
-"harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run.
-Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
-
-```{r mlm, eval=FALSE, include=FALSE}
+```{r mlm-analyses, include = FALSE}
 ##Attempt at MLM
@@
 library(nlme)
+
 #####intercept only model####
@@
 summary(model1)
+
+```
+
+```{r model-table, results='asis', include=FALSE}
+tableprint = matrix(NA, nrow = 10, ncol = 10)
+
+##stuff you had before
+##three models
+table = matrix(NA, nrow = 5, ncol = 10)
+
+##ARE ALL OF THESE COLUMNS NEEDED?? ALSO, ORDER?
+colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
+                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")
+
+##stick in the information you need
+table[1, ] = c("Model 1", 2, 43610.91, 
+               43627.55, -21803.46, "", "",
+               "", "", "")
+
+table[2, ] = c("Model 2", 3, 43611.04, 
+               43636.01, -21802.52, 0.000, 0.004,
+               "Model 1 vs Model 2", 1.871644, 0.173)
+
+table[3, ] = c("Model 3", 4, 43604.33, 
+               43637.62, -21798.17, 0.0003, 0.0037,
+               "Model 2 vs. Model 3", 8.703020, 0.0032)
+
+table[4, ] = c("Model 3.1", 13, 37913.11, 
+               38021.30, -18943.55, 0.17, 0.19,
+               "Model 3 vs. Model 3.1", 5709.23, "< .001")
+
+table[5, ] = c("Model 3.2", 22, 37904.00, 
+              38087.09, -18930.00, 0.17, 0.19,
+               "Model 3.1 vs. Model 3.2", 27.11, 0.001)
+
+```
+
+# Results
+
+To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
+MLM is a regression technique that allows one to control for the repeated measurement and nest structured of the data, which creates correlated error [@CITE_gelman].
+First, an intercept only model was created using percent text overall as the dependent variable.
+Using the *nlme* library in *R* [@CITE_nlme], a model with the news source as the random intercept was analyzed to determine if it was necessary to control for correlated error.
+Table @\ref(tab:model-table) includes the model statistics for all models.
+
+#stopped here to ask questions
+
+Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e.
+"harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run.
+Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
+
+```{r mlm, eval=FALSE, include=FALSE}
 
@@
 
-```{r mlm table}
-##three models
-table = matrix(NA, nrow = 5, ncol = 10)
-
-##ARE ALL OF THESE COLUMNS NEEDED?? ALSO, ORDER?
-colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
-                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")
-
-##stick in the information you need
-table[1, ] = c("Model 1", 2, 43610.91, 
-               43627.55, -21803.46, "", "",
-               "", "", "")
-
-table[2, ] = c("Model 2", 3, 43611.04, 
-               43636.01, -21802.52, 0.000, 0.004,
-               "Model 1 vs Model 2", 1.871644, 0.173)
-
-table[3, ] = c("Model 3", 4, 43604.33, 
-               43637.62, -21798.17, 0.0003, 0.0037,
-               "Model 2 vs. Model 3", 8.703020, 0.0032)
-
-table[4, ] = c("Model 3.1", 13, 37913.11, 
-               38021.30, -18943.55, 0.17, 0.19,
-               "Model 3 vs. Model 3.1", 5709.23, "< .001")
-
-table[5, ] = c("Model 3.2", 22, 37904.00, 
-              38087.09, -18930.00, 0.17, 0.19,
-               "Model 3.1 vs. Model 3.2", 27.11, 0.001)
-
-##print that sucker out
-library(knitr)
-kable(table)
-```
-
-# Results
 Any more screening/data prep here?
@@
 According to an analysis of variance (ANOVA) between the intercept-only model (Model 1) and the random intercept-only model (Model 2, *R2m* = 0.00, *R2c* = 0.004), there were no statistically significant differences (*F* = *?*, *p* = 0.17).
-There was a signficant difference between the random intercept-only model and the predictor model (Model 3, *R2m* = 0.0003, *R2c* = 0.0037), *F* = *?*, *p* = .003).
+There was a significant difference between the random intercept-only model and the predictor model (Model 3, *R2m* = 0.0003, *R2c* = 0.0037), *F* = *?*, *p* = .003).
 We found a significant difference between the two political leans (*b* = -0.018, *SE* = 0.006, *t*(3039) = -2.95, *p* = 0.003).
@@
 
-Finally, we analyzed the interaction between political lean and Moral Foundation type as a preditor of percent (Model 3.2, *R2m* = 0.17, *R2c* = 0.19).
+Finally, we analyzed the interaction between political lean and Moral Foundation type as a predictor of percent (Model 3.2, *R2m* = 0.17, *R2c* = 0.19).
 Using ANOVA, we found a significant difference between Models 3.1 and 3.2, *F* = *?*, *p* = .001).

### 2018-07-24 pilot_manuscript.Rmd
Added new models

@@
 ```{r load_packages, include = FALSE}
-library("papaja") #R says this package doesn't exist in current version :/
+library(papaja) #R says this package doesn't exist in current version :/
 library(MuMIn)
@@
        long_mlm[long_mlm$moraltype == "pperlo", ]$lean, mean)
+
+####NEW MODELS####
+
+##overall percent - no random intercept
+model4 = lme(percent ~ 1,
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|partno) #How to get rid of intercept??
+summary(model4)
+r.squaredGLMM(model4)
+
+##overall percent - random intercept by source
+model4.1 = lme(percent ~ 1,
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.1)
+r.squaredGLMM(model4.1)
+
+##MFD category ~ lean 
+model5.1 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.1)
+r.squaredGLMM(model5.1)
+
+model5.2 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "hperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.2)
+r.squaredGLMM(model5.2)
+
+model5.3 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "fperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.3)
+r.squaredGLMM(model5.3)
+
+model5.4 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "fperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.4)
+r.squaredGLMM(model5.4)
+
+model5.5 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "iperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.5)
+r.squaredGLMM(model5.5)
+
+model5.6 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "iperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.6)
+r.squaredGLMM(model5.6)
+
+model5.7 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "aperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.7)
+r.squaredGLMM(model5.7)
+
+model5.8 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "aperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.8)
+r.squaredGLMM(model5.8)
+
+model5.9 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "pperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.9)
+r.squaredGLMM(model5.9)
+
+model5.10 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "pperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model5.10)
+r.squaredGLMM(model5.10)
+
 ```

### 2018-07-31 pilot_manuscript.Rmd
added the example mlm write up and table

--- 2018-07-19 pilot_manuscript.Rmd
@@
 ```{r load_packages, include = FALSE}
-library("papaja") #R says this package doesn't exist in current version :/
+library(papaja) 
 library(MuMIn)
+library(reshape)
+library(nlme)
+library(ggplot2)
+
 knitr::opts_chunk$set(cache = TRUE)
@@
 
-```{r mlm-analyses, include = FALSE}
+```{r mlm-analyses, echo=FALSE, warning=FALSE, include = FALSE}
 ##Attempt at MLM
 mlm_data = final[ , -c(3:28) ]
-library(reshape)
 long_mlm = melt(mlm_data,
@@
 
-##set up the analysis
-library(nlme)
-
 #####intercept only model####
@@
 ##ML = maximum likelihood
-model1 = gls(percent ~ 1, #DV ~ IV (which is only the intercept; is y-average diff than 0?)
+model1 = gls(percent ~ 1, 
              data = long_mlm, 
@@
 
+####overall percent - random intercept by source####
+model3 = lme(percent ~ 1,
+             data = long_mlm, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model3)
+r.squaredGLMM(model3)
+
+####separate models by type####
+##MFD category ~ lean 
+model4.1 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.1)
+r.squaredGLMM(model4.1)
+
+model4.2 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "hperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.2)
+r.squaredGLMM(model4.2)
+
+model4.3 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "fperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.3)
+r.squaredGLMM(model4.3)
+
+model4.4 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "fperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.4)
+r.squaredGLMM(model4.4)
+
+model4.5 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "iperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.5)
+r.squaredGLMM(model4.5)
+
+model4.6 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "iperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.6)
+r.squaredGLMM(model4.6)
+
+model4.7 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "aperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.7)
+r.squaredGLMM(model4.7)
+
+model4.8 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "aperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.8)
+r.squaredGLMM(model4.8)
+
+model4.9 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "pperhi", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.9)
+r.squaredGLMM(model4.9)
+
+model4.10 = lme(percent ~ lean,
+             data = long_mlm[long_mlm$moraltype == "pperlo", ], 
+             method = "ML", 
+             na.action = "na.omit",
+             random = ~1|Source)
+summary(model4.10)
+r.squaredGLMM(model4.10)
+
 ```
 
-```{r model-table, results='asis', include=FALSE}
-tableprint = matrix(NA, nrow = 10, ncol = 10)
+```{r model-table, results='asis', echo=FALSE}
+tableprint = matrix(NA, nrow = 12, ncol = 7)
 
-##stuff you had before
-##three models
-table = matrix(NA, nrow = 5, ncol = 10)
+colnames(tableprint) = c("Model", "AIC", "BIC", "$\\chi^2$", "$df$",
+                         "$R^2_m", "$R^2_c")
 
-##ARE ALL OF THESE COLUMNS NEEDED?? ALSO, ORDER?
-colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
-                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")
+#put in each model set information
+#temp store model summary
+temp = summary(model1)
 
-##stick in the information you need
-table[1, ] = c("Model 1", 2, 43610.91, 
-               43627.55, -21803.46, "", "",
-               "", "", "")
+#put in the information
+#entered a raw number here, as a reminder
+tableprint[1 , ] = c("Non-Random Intercept", temp$AIC, temp$BIC,
+                     temp$logLik, 30409, "-", "-")
 
-table[2, ] = c("Model 2", 3, 43611.04, 
-               43636.01, -21802.52, 0.000, 0.004,
-               "Model 1 vs Model 2", 1.871644, 0.173)
+temp = summary(model3)
+tableprint[2 , ] = c("Random Intercept", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms, r.squaredGLMM(model3))
 
-table[3, ] = c("Model 3", 4, 43604.33, 
-               43637.62, -21798.17, 0.0003, 0.0037,
-               "Model 2 vs. Model 3", 8.703020, 0.0032)
+temp = summary(model4.1)
+tableprint[3 , ] = c("Harm High", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.1))
 
-table[4, ] = c("Model 3.1", 13, 37913.11, 
-               38021.30, -18943.55, 0.17, 0.19,
-               "Model 3 vs. Model 3.1", 5709.23, "< .001")
+temp = summary(model4.2)
+tableprint[4 , ] = c("Harm Low", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.2))
 
-table[5, ] = c("Model 3.2", 22, 37904.00, 
-              38087.09, -18930.00, 0.17, 0.19,
-               "Model 3.1 vs. Model 3.2", 27.11, 0.001)
+temp = summary(model4.3)
+tableprint[5 , ] = c("Fairness High", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.3))
 
+temp = summary(model4.4)
+tableprint[6 , ] = c("Fairness Low", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.4))
+
+temp = summary(model4.5)
+tableprint[7 , ] = c("Ingroup High", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.5))
+
+temp = summary(model4.6)
+tableprint[8 , ] = c("Ingroup Low", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.6))
+
+temp = summary(model4.7)
+tableprint[9 , ] = c("Authority High", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.7))
+
+temp = summary(model4.8)
+tableprint[10 , ] = c("Authority Low", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.8))
+
+temp = summary(model4.9)
+tableprint[11 , ] = c("Purity High", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.9))
+
+temp = summary(model4.10)
+tableprint[12 , ] = c("Purity Low", temp$AIC, temp$BIC,
+                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.10))
+#keep going
+
+#round and clean up
+tableprint[ , 2:4] = printnum(as.numeric(tableprint[ , 2:4]))
+tableprint[-1 , 6] = printp(as.numeric(tableprint[-1 , 6]))
+tableprint[-1 , 7] = printp(as.numeric(tableprint[-1 , 7]))
+
+apa_table.latex(as.data.frame(tableprint),
+          align = c("l", rep("c", 6)), 
+          caption = "MLM Model Statistics",
+          note = "Degrees of freedom indicate residual $df$ for each model.",
+          escape = FALSE
+ )
 ```
@@
 Table @\ref(tab:model-table) includes the model statistics for all models.
+While the $\Delta\chi^2$(1) = `r printnum(anova(model1,model3)[,8][2]))`, *p* = `r printp(anova(model1,model3)[,9][2])` was not significant, all models were still structured with a random intercept by source to control for even a small amount of correlated error.
 
-#stopped here to ask questions
+Next, predictor models with political lean predicting percent of MFD words was analyzed for each of the MFD categories separately (i.e., "harm-positive", "harm-negative", etc.).
+Coefficient values indicate the mean differences between conservative and liberal sources, and to help illustrate these differences, the overall means were plotted in Figure \@ref(fig:graph-means).
+For harm words, there was not a significant difference in the words indicating harm-negative *b* = `r printnum(summary(model4.1)$tTable[2,1])`, *t*(`r summary(model4.1)$tTable[2,3]`) = `r printnum(summary(model4.1)$tTable[2,4])`, *p* = `r printp(summary(model4.1)$tTable[2,5])` or harm-positive *b* = `r printnum(summary(model4.2)$tTable[2,1])`, *t*(`r summary(model4.2)$tTable[2,3]`) = `r printnum(summary(model4.2)$tTable[2,4])`, *p* = `r printp(summary(model4.2)$tTable[2,5])`.
 
-Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e.
-"harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run.
-Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
+```{r graph-means, echo=FALSE}
+#make a ggplot here! :) 
+#put the categories on the bottom X
+#put the lean as the group
+#y is the percent
+#use the long_mlm dataset
+#i will make low and high happen as different panels
 
-```{r mlm, eval=FALSE, include=FALSE}
-
-####random intercept only model####
-##note we switched to LME function
-model2 = lme(percent ~ 1, 
-             data = long_mlm, 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|partno) #sets random intercept for each participant
-summary(model2) #note changed Value in output; also, 
-#Random effects tells how much intercept varies among Pps
-anova(model1, model2) #tests if necessary to nest; Yes, we need to do MLM
-r.squaredGLMM(model2)
-####predictor model####
-model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-             data = long_mlm, 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|partno)
-summary(model3)
-anova(model1, model2, model3)
-r.squaredGLMM(model3) #gives you two, report both
-
-model3.1 = lme(percent ~ lean + moraltype, #now we want to switch the 1 for IV of interest
-             data = long_mlm, 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|partno)
-summary(model3.1)
-r.squaredGLMM(model3.1)
-model3.2 = lme(percent ~ lean * moraltype, #now we want to switch the 1 for IV of interest
-               data = long_mlm, 
-               method = "ML", 
-               na.action = "na.omit",
-               random = ~1|partno)
-summary(model3.2)
-r.squaredGLMM(model3.2)
-##model 3 on each moral foundation separately
-#h_hi
-model3h_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|partno)
-summary(model3h_hi)
-tapply(long_mlm[long_mlm$moraltype == "hperhi", ]$percent,
-       long_mlm[long_mlm$moraltype == "hperhi", ]$lean, mean)
-#h_lo
-model3h_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "hperlo", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3h_lo)
-tapply(long_mlm[long_mlm$moraltype == "hperlo", ]$percent,
-       long_mlm[long_mlm$moraltype == "hperlo", ]$lean, mean)
-#f_hi
-model3f_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "fperhi", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3f_hi)
-tapply(long_mlm[long_mlm$moraltype == "fperhi", ]$percent,
-       long_mlm[long_mlm$moraltype == "fperhi", ]$lean, mean)
-#f_lo
-model3f_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "fperlo", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3f_lo)
-tapply(long_mlm[long_mlm$moraltype == "fperlo", ]$percent,
-       long_mlm[long_mlm$moraltype == "fperlo", ]$lean, mean)
-#i_hi
-model3i_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "iperhi", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3i_hi)
-tapply(long_mlm[long_mlm$moraltype == "iperhi", ]$percent,
-       long_mlm[long_mlm$moraltype == "iperhi", ]$lean, mean)
-#i_lo
-model3i_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "iperlo", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3i_lo)
-tapply(long_mlm[long_mlm$moraltype == "iperlo", ]$percent,
-       long_mlm[long_mlm$moraltype == "iperlo", ]$lean, mean)
-#a_hi
-model3a_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "aperhi", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3a_hi)
-tapply(long_mlm[long_mlm$moraltype == "aperhi", ]$percent,
-       long_mlm[long_mlm$moraltype == "aperhi", ]$lean, mean)
-#a_lo
-model3a_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "aperlo", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3a_lo)
-tapply(long_mlm[long_mlm$moraltype == "aperlo", ]$percent,
-       long_mlm[long_mlm$moraltype == "aperlo", ]$lean, mean)
-#p_hi
-model3p_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "pperhi", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3p_hi)
-tapply(long_mlm[long_mlm$moraltype == "pperhi", ]$percent,
-       long_mlm[long_mlm$moraltype == "pperhi", ]$lean, mean)
-#p_lo
-model3p_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
-                 data = long_mlm[long_mlm$moraltype == "pperlo", ], 
-                 method = "ML", 
-                 na.action = "na.omit",
-                 random = ~1|partno)
-summary(model3p_lo)
-tapply(long_mlm[long_mlm$moraltype == "pperlo", ]$percent,
-       long_mlm[long_mlm$moraltype == "pperlo", ]$lean, mean)
 ```
 
-Any more screening/data prep here?
-
-Political lean of the news organization was used to predict the percent of words matching the Moral Foundations Dictionary.
-According to an analysis of variance (ANOVA) between the intercept-only model (Model 1) and the random intercept-only model (Model 2, *R2m* = 0.00, *R2c* = 0.004), there were no statistically significant differences (*F* = *?*, *p* = 0.17).
-There was a significant difference between the random intercept-only model and the predictor model (Model 3, *R2m* = 0.0003, *R2c* = 0.0037), *F* = *?*, *p* = .003).
-We found a significant difference between the two political leans (*b* = -0.018, *SE* = 0.006, *t*(3039) = -2.95, *p* = 0.003).
-Next, we added Moral Foundation Type as a predictor of percent to the third model (Model 3.1, *R2m* = 0.17, *R2c* = 0.19).
-The ANOVA revealed a significant difference between Models 3 and 3.1, *F* = *?*, *p* < .001)
-
-#Significance for, like, all of the little moral types. Put in table?
-
-Finally, we analyzed the interaction between political lean and Moral Foundation type as a predictor of percent (Model 3.2, *R2m* = 0.17, *R2c* = 0.19).
-Using ANOVA, we found a significant difference between Models 3.1 and 3.2, *F* = *?*, *p* = .001).
-
-#Again, lots of stuff here. Needs to be reported? Put in table?
-
-Comparisons between the models can be found in Table 1. 
 # Discussion

### 2018-08-14 pilot_manuscript.Rmd
Wrote the results stuff and made a Graph!
but what labels should we use for the x-axis??

@@
 For harm words, there was not a significant difference in the words indicating harm-negative *b* = `r printnum(summary(model4.1)$tTable[2,1])`, *t*(`r summary(model4.1)$tTable[2,3]`) = `r printnum(summary(model4.1)$tTable[2,4])`, *p* = `r printp(summary(model4.1)$tTable[2,5])` or harm-positive *b* = `r printnum(summary(model4.2)$tTable[2,1])`, *t*(`r summary(model4.2)$tTable[2,3]`) = `r printnum(summary(model4.2)$tTable[2,4])`, *p* = `r printp(summary(model4.2)$tTable[2,5])`.
+For fair words, there was no signfificant difference in the words indicating fair-negative *b* = `r printnum(summary(model4.3)$tTable[2,1])`, *t*(`r summary(model4.3)$tTable[2,3]`) = `r printnum(summary(model4.3)$tTable[2,4])`, *p* = `r printp(summary(model4.3)$tTable[2,5])` or fair-positive *b* = `r printnum(summary(model4.4)$tTable[2,1])`, *t*(`r summary(model4.4)$tTable[2,3]`) = `r printnum(summary(model4.4)$tTable[2,4])`, *p* = `r printp(summary(model4.4)$tTable[2,5])`.
+For ingroup words, there was no signfificant difference in the words indicating ingroup-negative *b* = `r printnum(summary(model4.5)$tTable[2,1])`, *t*(`r summary(model4.5)$tTable[2,3]`) = `r printnum(summary(model4.5)$tTable[2,4])`, *p* = `r printp(summary(model4.5)$tTable[2,5])` or ingroup-positive *b* = `r printnum(summary(model4.6)$tTable[2,1])`, *t*(`r summary(model4.6)$tTable[2,3]`) = `r printnum(summary(model4.6)$tTable[2,4])`, *p* = `r printp(summary(model4.6)$tTable[2,5])`.
+For authority words, there was not a signfificant difference in the words indicating authority-negative *b* = `r printnum(summary(model4.7)$tTable[2,1])`, *t*(`r summary(model4.7)$tTable[2,3]`) = `r printnum(summary(model4.7)$tTable[2,4])`, *p* = `r printp(summary(model4.7)$tTable[2,5])` or authority-positive *b* = `r printnum(summary(model4.8)$tTable[2,1])`, *t*(`r summary(model4.8)$tTable[2,3]`) = `r printnum(summary(model4.8)$tTable[2,4])`, *p* = `r printp(summary(model4.8)$tTable[2,5])`.
+For purity words, there was a signfificant difference in the words indicating purity-negative *b* = `r printnum(summary(model4.9)$tTable[2,1])`, *t*(`r summary(model4.9)$tTable[2,3]`) = `r printnum(summary(model4.9)$tTable[2,4])`, *p* = `r printp(summary(model4.9)$tTable[2,5])`.
+There was no significant difference for purity-positive *b* = `r printnum(summary(model4.10)$tTable[2,1])`, *t*(`r summary(model4.10)$tTable[2,3]`) = `r printnum(summary(model4.10)$tTable[2,4])`, *p* = `r printp(summary(model4.10)$tTable[2,5])`.
 
@@
 #i will make low and high happen as different panels
+
+long_mlm$moraltype = factor(long_mlm$moraltype, 
+                  levels=c("hperhi", "hperlo", "fperhi", "fperlo",
+                           "iperhi", "iperlo", "aperhi", "aperlo", "pperhi", "pperlo"),
+                  labels = c("Harm-positive", "Harm-negative", "Fair-positive",
+                             "Fair-negative", "Ingroup-positive", "Ingroup-negative",
+                             "Authority-positive", "Authority-negative", 
+                             "Purity-positive", "Purity-negative")) 
+cleanup = theme(panel.grid.major = element_blank(), 
+                panel.grid.minor = element_blank(), 
+                panel.background = element_blank(), 
+                axis.line.x = element_line(color = "black"),
+                axis.line.y = element_line(color = "black"),
+                legend.key = element_rect(fill = "white"),
+                text = element_text(size = 15))
+overallgraph = ggplot(long_mlm, aes(moraltype, percent, fill = lean))
+overallgraph +
+  stat_summary(fun.y = mean,
+               geom = "bar",
+               position = "dodge") +
+  stat_summary(fun.data = mean_cl_normal,
+               geom = "errorbar", 
+               position = position_dodge(width = 0.90),
+               width = .2) +
+  xlab("Moral Category") +
+  ylab("Percent") + 
+  cleanup +
+  scale_fill_manual(name = "Political Lean", 
+                    labels = c("Liberal", "Conservative"),
+                    values = c("Light Gray", "Dark Gray"))
 

### 2018-08-21 pilot_manuscript.Rmd
fixed the graph

@@
                 text = element_text(size = 15))
-overallgraph = ggplot(long_mlm, aes(moraltype, percent, fill = lean))
+
+long_mlm$moral_foundation = long_mlm$moraltype
+long_mlm$moral_foundation = gsub("-positive", "", long_mlm$moral_foundation)
+long_mlm$moral_foundation = gsub("-negative", "", long_mlm$moral_foundation)
+
+long_mlm$valence = long_mlm$moraltype
+long_mlm$valence = gsub("Harm-positive", "Positive", long_mlm$valence)
+long_mlm$valence = gsub("Harm-negative", "Negative", long_mlm$valence)
+long_mlm$valence = gsub("Authority-positive", "Positive", long_mlm$valence)
+long_mlm$valence = gsub("Authority-negative", "Negative", long_mlm$valence)
+long_mlm$valence = gsub("Fair-positive", "Positive", long_mlm$valence)
+long_mlm$valence = gsub("Fair-negative", "Negative", long_mlm$valence)
+long_mlm$valence = gsub("Purity-positive", "Positive", long_mlm$valence)
+long_mlm$valence = gsub("Purity-negative", "Negative", long_mlm$valence)
+long_mlm$valence = gsub("Ingroup-positive", "Positive", long_mlm$valence)
+long_mlm$valence = gsub("Ingroup-negative", "Negative", long_mlm$valence)
+
+overallgraph = ggplot(long_mlm, aes(moral_foundation, percent, fill = lean))
 overallgraph +
@@
                     labels = c("Liberal", "Conservative"),
-                    values = c("Light Gray", "Dark Gray"))
+                    values = c("Light Gray", "Dark Gray")) +
+  facet_grid(~valence) + 
+  NULL
 

### 2018-08-28 pilot_manuscript.Rmd
updates for pilot study

@@
 
-##stem the original MFD stuff - separate loop on only the mfd data frame
-for(i in 1:nrow(original_mfd)) {
-  original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
-  original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
-  original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
-  original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
-  original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
-  original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
-  original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
-  original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
-  original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
-  original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
-}
+# ##stem the original MFD stuff - separate loop on only the mfd data frame
+# for(i in 1:nrow(original_mfd)) {
+#   original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
+#   original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
+#   original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
+#   original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
+#   original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
+#   original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
+#   original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
+#   original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
+#   original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
+#   original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
+# }
+# 
+# final$hhisum = NA
+# final$hlosum = NA
+# final$fhisum = NA
+# final$flosum = NA
+# final$ihisum = NA
+# final$ilosum = NA
+# final$ahisum = NA
+# final$alosum = NA
+# final$phisum = NA
+# final$plosum = NA
+# 
+# for (i in 1:nrow(final)) {
+# ##first make a table of a response, unlisting everything
+# temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
+# ##find the rows that match the mfd list and sum and save
+# final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
+# final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])
+# 
+# final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
+# final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])
+# 
+# final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
+# final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])
+# 
+# final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
+# final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])
+# 
+# final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
+# final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
+# }
+# 
+# final$hperhi = final$hsumhi / final$wordcount * 100
+# final$hperlo = final$hsumlo / final$wordcount * 100
+# final$fperhi = final$fsumhi / final$wordcount * 100
+# final$fperlo = final$fsumlo / final$wordcount * 100
+# final$iperhi = final$isumhi / final$wordcount * 100
+# final$iperlo = final$isumlo / final$wordcount * 100
+# final$aperhi = final$asumhi / final$wordcount * 100
+# final$aperlo = final$asumlo / final$wordcount * 100
+# final$pperhi = final$psumhi / final$wordcount * 100
+# final$pperlo = final$psumlo / final$wordcount * 100
+# 
+# #let's look at the means
+# tapply(final$hperhi, final$Source, mean)
+# tapply(final$hperlo, final$Source, mean)
+# tapply(final$fperhi, final$Source, mean)
+# tapply(final$fperlo, final$Source, mean)
+# tapply(final$iperhi, final$Source, mean)
+# tapply(final$iperlo, final$Source, mean)
+# tapply(final$aperhi, final$Source, mean)
+# tapply(final$aperlo, final$Source, mean)
+# tapply(final$pperhi, final$Source, mean)
+# tapply(final$pperlo, final$Source, mean)
+```
 
-final$hhisum = NA
-final$hlosum = NA
-final$fhisum = NA
-final$flosum = NA
-final$ihisum = NA
-final$ilosum = NA
-final$ahisum = NA
-final$alosum = NA
-final$phisum = NA
-final$plosum = NA
+```{r new_data, include = FALSE}
+#take final$stemmed column loop over this
+
+harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
 
@@
 temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-##find the rows that match the mfd list and sum and save
-final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
-final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])
 
-final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
-final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(harmstuffthing$words[harmstuffthing$words != "" & harmstuffthing$words != "NA"])]
 
-final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
-final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])
+#add to the dataset
+temp2$URL = final$Url[i]
+temp2$Source = final$Source[i]
+temp2$wordcount = final$wordcount[i]
 
-final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
-final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])
-
-final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
-final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
+#bind with original
+harm_final_data = rbind(harm_final_data, temp2)
 }
 
-final$hperhi = final$hsumhi / final$wordcount * 100
-final$hperlo = final$hsumlo / final$wordcount * 100
-final$fperhi = final$fsumhi / final$wordcount * 100
-final$fperlo = final$fsumlo / final$wordcount * 100
-final$iperhi = final$isumhi / final$wordcount * 100
-final$iperlo = final$isumlo / final$wordcount * 100
-final$aperhi = final$asumhi / final$wordcount * 100
-final$aperlo = final$asumlo / final$wordcount * 100
-final$pperhi = final$psumhi / final$wordcount * 100
-final$pperlo = final$psumlo / final$wordcount * 100
-
-#let's look at the means
-tapply(final$hperhi, final$Source, mean)
-tapply(final$hperlo, final$Source, mean)
-tapply(final$fperhi, final$Source, mean)
-tapply(final$fperlo, final$Source, mean)
-tapply(final$iperhi, final$Source, mean)
-tapply(final$iperlo, final$Source, mean)
-tapply(final$aperhi, final$Source, mean)
-tapply(final$aperlo, final$Source, mean)
-tapply(final$pperhi, final$Source, mean)
-tapply(final$pperlo, final$Source, mean)
 ```

### 2018-08-28 Untitled.R

@@ -1,0 +1,12 @@
+
+
+##you will run this for each foundation AFTER running the MTMM project 
+##through MTMM set up
+harmstuffthing = data.frame("words" = c(original_mfd$h2, harm_words, harm_words_reduce, harm_words_reduce_exp2))
+harmstuffthing$dataset = c(rep("orig", length(original_mfd$h2)),
+                           rep("all_exp1", length(harm_words)),
+                           rep("reduce_exp1", length(harm_words_reduce)),
+                           rep("reduce_exp2", length(harm_words_reduce_exp2)))
+write.csv(harmstuffthing, "harm_words_total.csv", row.names = F)
+
+

### 2018-09-01 pilot_manuscript.Rmd
New MFD datasets!

@@
 #take final$stemmed column loop over this
-
+#Harm
 harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
@@
 #only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harmstuffthing$words[harmstuffthing$words != "" & harmstuffthing$words != "NA"])]
+temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA"])]
 
@@
 harm_final_data = rbind(harm_final_data, temp2)
+}
+
+#Fair
+fair_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA"])]
+
+#add to the dataset
+temp2$URL = final$Url[i]
+temp2$Source = final$Source[i]
+temp2$wordcount = final$wordcount[i]
+
+#bind with original
+fair_final_data = rbind(fair_final_data, temp2)
+}
+
+#Ingroup
+ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA"])]
+
+#add to the dataset
+temp2$URL = final$Url[i]
+temp2$Source = final$Source[i]
+temp2$wordcount = final$wordcount[i]
+
+#bind with original
+ingroup_final_data = rbind(ingroup_final_data, temp2)
+}
+
+#Authority
+authority_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA"])]
+
+#add to the dataset
+temp2$URL = final$Url[i]
+temp2$Source = final$Source[i]
+temp2$wordcount = final$wordcount[i]
+
+#bind with original
+authority_final_data = rbind(authority_final_data, temp2)
+}
+
+#Purity
+purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA"])]
+
+#add to the dataset
+temp2$URL = final$Url[i]
+temp2$Source = final$Source[i]
+temp2$wordcount = final$wordcount[i]
+
+#bind with original
+purity_final_data = rbind(purity_final_data, temp2)
 }

### 2018-09-01 Untitled.R

@@ -2,11 +2,47 @@
 
 ##you will run this for each foundation AFTER running the MTMM project 
 ##through MTMM set up
-harmstuffthing = data.frame("words" = c(original_mfd$h2, harm_words, harm_words_reduce, harm_words_reduce_exp2))
-harmstuffthing$dataset = c(rep("orig", length(original_mfd$h2)),
+#Harm
+harm_all = data.frame("words" = c(original_mfd$h2, harm_words, harm_words_reduce, 
+                                  harm_words_reduce_exp2))
+harm_all$dataset = c(rep("orig", length(original_mfd$h2)),
                            rep("all_exp1", length(harm_words)),
                            rep("reduce_exp1", length(harm_words_reduce)),
                            rep("reduce_exp2", length(harm_words_reduce_exp2)))
-write.csv(harmstuffthing, "harm_words_total.csv", row.names = F)
+write.csv(harm_all, "harm_words_total.csv", row.names = F)
 
+#Fair
+fair_all = data.frame("words" = c(original_mfd$f2, fair_words, fair_words_reduce, 
+                                  fair_words_reduce_exp2))
+fair_all$dataset = c(rep("orig", length(original_mfd$f2)),
+                     rep("all_exp1", length(fair_words)),
+                     rep("reduce_exp1", length(fair_words_reduce)),
+                     rep("reduce_exp2", length(fair_words_reduce_exp2)))
+write.csv(fair_all, "fair_words_total.csv", row.names = F)
 
+#Ingroup
+ingroup_all = data.frame("words" = c(original_mfd$i2, ingroup_words, ingroup_words_reduce, 
+                                     ingroup_words_reduce_exp2))
+ingroup_all$dataset = c(rep("orig", length(original_mfd$i2)),
+                     rep("all_exp1", length(ingroup_words)),
+                     rep("reduce_exp1", length(ingroup_words_reduce)),
+                     rep("reduce_exp2", length(ingroup_words_reduce_exp2)))
+write.csv(ingroup_all, "ingroup_words_total.csv", row.names = F)
+
+#Authority
+authority_all = data.frame("words" = c(original_mfd$a2, authority_words, authority_words_reduce, 
+                                     authority_words_reduce_exp2))
+authority_all$dataset = c(rep("orig", length(original_mfd$a2)),
+                        rep("all_exp1", length(authority_words)),
+                        rep("reduce_exp1", length(authority_words_reduce)),
[…]

### 2018-09-04 pilot_manuscript.Rmd
working on paper

@@
 ##write it back out
-write.csv(newdata, "overalldata.csv", row.names = F)
+#write.csv(newdata, "overalldata.csv", row.names = F)
 
@@
 
-##separate them into h low, h high until you have ten categories 
-#harm/care
-original_mfd$h2hi[35:112] = NA 
-original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
-                      "protect", "safe", "shelter", "sympathetic",
-                      "sympathies", "benefits", "benefitted",
-                      "benefitting", "cares", "cared", "caring","defends", 
-                      "defending","defended", "guards", "guarded",
-                      "guarding","preserves",
-                      "preserved", "preserving", "protects", "protected",
-                      "protecting", "protection",  
-                      "safely", "safer", "shelters", 
-                      "sheltered", "sheltering")
-original_mfd$h2lo[61:112] = NA
-original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
-                      "damage", "danger", "destroy", "fight", "harm",
-                      "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
-                      "violent", "war","abusive",
-                      "abuser","abused","abusing","damaged",
-                      "damaging","attacked","attacking","attacker",
-                      "attacks","attackers","crushes",
-                      "crushing", "crushed", "dangerous","detroys", 
-                      "destroyed", "destroying",
-                      "fights", "fought", "fighting","harms", 
-                      "harmed", "harming", "hurts",
-                      "hurting", "kills", "killed", "killing",
-                      "ruins", "ruined", "ruining", "spurns", 
-                      "spurned", "spurning", "stomps", "stomped",
-                      "stomping", "suffers", "suffered", "suffering",
-                      "violence", "warring")
-
-#fairness/reciprocity
-original_mfd$f2hi[41:112] = NA
-original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
-                      "fair", "honest", "just", "justify", "reason",
-                      "right", "tolerate", "impartial", "balances", 
-                      "balanced", "balancing",
-                      "equals", "equaled", "equaling", "equates", "equated",
-                      "equating", "evens", "evened", "evening","fairness",
-                      "honesty", "impartiality", "justice", "justifies", 
-                      "justified", "justifying", "reasons",
-                      "reasoned", "reasoning", "rights", "tolerates",
-                      "tolerated", "tolerating", "toleration")
-original_mfd$f2lo[25:112] = NA
-original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
-                      "prefer", "prejudice", "biased", "biases", "discriminates", 
-                      "discriminated", "discriminating", "discrimination",
-                      "excludes", "excluded", "excluding", 
-                      "favors", "favored", "favoring", "prefers", "preferred", "preferring",
-                      "prejudices", "prejudiced", "prejudicing")
-
-#ingroup/loyalty
-original_mfd$i2hi[30:112] = NA
-original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
-                      "group", "member", "nation", "side", "together",
-                      "trait", "unite", "collects", 
-                      "collected", "collecting", "collective",
-                      "communities", "families", "fellows",
-                      "groups", "grouped", "grouping",
-                      "members", "nations", "sides",
-                      "togetherness", "traits", "unites", 
-                      "united", "uniting")
-original_mfd$i2lo[19:112] = NA 
-original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
-                      "deceives", "deceived", "deceiving",
-                      "deception", "deceptions", "deserts", "deserted",
-                      "deserting", "desertion", "foreigners",
-                      "indviduals", "indvidualize", "individualized",
-                      "individualizing")
-
-#authority/respect
-original_mfd$a2hi[86:112] = NA
-original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
-                      "control", "defer", "duty", "faith", "father", "honor",
-                      "law", "lead", "legal", "mother", "obey", 
-                      "order", "permit", "position", "preserve",
-                      "respect", "revere", "serve", "tradtition", "trait",
-                      "abides", "abided", "abiding", "authorities",
-                      "classes", "classed", "classing", "command",
-                      "commanded", "commanding", "controls", "controlled",
-                      "controlling","defers", "deferred", "deferring", "deference",
-                      "duties","faiths", "fathers", "fathered", "fathering",
-                      "honors", "honored", "honoring", "laws", "leads",
-                      "leading", "mothers", "mothered", "mothering",
-                      "obeys", "obeyed", "obeying", "orders", 
-                      "ordered", "ordering", "permits",
-                      "permitted", "permitting", "positions", "positioned",
-                      "positioning", "preserves", "preserved", "preserving",
-                      "preservation", "respects",
-                      "respected", "respecting", "respectful", "reveres",
-                      "revered", "revering", "reverence", "serves", "served",
-                      "serving", "traditions", "traditional", "traits")
-original_mfd$a2lo[28:112] = NA
-original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
-                      "protest", "refuse", "defects", "defected", 
-                      "defecting","defies", "defied", "defying", "defiance", "deserts",
-                      "deserted", "deserting", "desertion", "opposes", "opposed",
-                      "opposing", "protests", "protested", "protesting",
-                      "refuses", "refused", "refusing", "refusal")
-
-#purity/sanctity
-original_mfd$p2hi[32:112] = NA
-original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
-                      "preserve", "pure", "right", "sacred", "whole",
-                      "abstains", "abstained", "abstaining", "abstinence",
-                      "churches", "cleans", "cleaned", "cleaning", "cleanse",
-                      "cleanliness", "innocence", "modesty", "preserves", "preserved",
-                      "preserving", "preservation", "purity", "rights", 
-                      "sacredness", "wholeness", "wholesome")
-original_mfd$p2lo[30:112] = NA
-original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
-                      "promiscuous", "ruin", "sick", "sin", "trash",
-                      "adulteries", "adulterous", "adulterer", "adulterers",
-                      "dirty", "diseases", "diseased", "disgusts", 
-                      "disgusted", "disgusting", "grossness", "promiscuity",
-                      "promiscuities", "ruins", "ruined","ruining", 
-                      "sickness", "sicknesses", "sins")
+# ##separate them into h low, h high until you have ten categories 
+# #harm/care
+# original_mfd$h2hi[35:112] = NA 
+# original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
+#                       "protect", "safe", "shelter", "sympathetic",
+#                       "sympathies", "benefits", "benefitted",
+#                       "benefitting", "cares", "cared", "caring","defends", 
+#                       "defending","defended", "guards", "guarded",
+#                       "guarding","preserves",
+#                       "preserved", "preserving", "protects", "protected",
+#                       "protecting", "protection",  
+#                       "safely", "safer", "shelters", 
+#                       "sheltered", "sheltering")
+# original_mfd$h2lo[61:112] = NA
+# original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
+#                       "damage", "danger", "destroy", "fight", "harm",
+#                       "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
+#                       "violent", "war","abusive",
+#                       "abuser","abused","abusing","damaged",
+#                       "damaging","attacked","attacking","attacker",
+#                       "attacks","attackers","crushes",
+#                       "crushing", "crushed", "dangerous","detroys", 
+#                       "destroyed", "destroying",
+#                       "fights", "fought", "fighting","harms", 
+#                       "harmed", "harming", "hurts",
+#                       "hurting", "kills", "killed", "killing",
+#                       "ruins", "ruined", "ruining", "spurns", 
+#                       "spurned", "spurning", "stomps", "stomped",
+#                       "stomping", "suffers", "suffered", "suffering",
+#                       "violence", "warring")
+# 
+# #fairness/reciprocity
+# original_mfd$f2hi[41:112] = NA
+# original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
+#                       "fair", "honest", "just", "justify", "reason",
+#                       "right", "tolerate", "impartial", "balances", 
+#                       "balanced", "balancing",
+#                       "equals", "equaled", "equaling", "equates", "equated",
+#                       "equating", "evens", "evened", "evening","fairness",
+#                       "honesty", "impartiality", "justice", "justifies", 
+#                       "justified", "justifying", "reasons",
+#                       "reasoned", "reasoning", "rights", "tolerates",
+#                       "tolerated", "tolerating", "toleration")
+# original_mfd$f2lo[25:112] = NA
+# original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
+#                       "prefer", "prejudice", "biased", "biases", "discriminates", 
+#                       "discriminated", "discriminating", "discrimination",
+#                       "excludes", "excluded", "excluding", 
+#                       "favors", "favored", "favoring", "prefers", "preferred", "preferring",
+#                       "prejudices", "prejudiced", "prejudicing")
+# 
+# #ingroup/loyalty
+# original_mfd$i2hi[30:112] = NA
+# original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
+#                       "group", "member", "nation", "side", "together",
+#                       "trait", "unite", "collects", 
+#                       "collected", "collecting", "collective",
+#                       "communities", "families", "fellows",
+#                       "groups", "grouped", "grouping",
+#                       "members", "nations", "sides",
+#                       "togetherness", "traits", "unites", 
+#                       "united", "uniting")
+# original_mfd$i2lo[19:112] = NA 
+# original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
+#                       "deceives", "deceived", "deceiving",
+#                       "deception", "deceptions", "deserts", "deserted",
+#                       "deserting", "desertion", "foreigners",
+#                       "indviduals", "indvidualize", "individualized",
+#                       "individualizing")
+# 
+# #authority/respect
+# original_mfd$a2hi[86:112] = NA
+# original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
+#                       "control", "defer", "duty", "faith", "father", "honor",
+#                       "law", "lead", "legal", "mother", "obey", 
+#                       "order", "permit", "position", "preserve",
+#                       "respect", "revere", "serve", "tradtition", "trait",
+#                       "abides", "abided", "abiding", "authorities",
+#                       "classes", "classed", "classing", "command",
+#                       "commanded", "commanding", "controls", "controlled",
+#                       "controlling","defers", "deferred", "deferring", "deference",
+#                       "duties","faiths", "fathers", "fathered", "fathering",
+#                       "honors", "honored", "honoring", "laws", "leads",
+#                       "leading", "mothers", "mothered", "mothering",
+#                       "obeys", "obeyed", "obeying", "orders", 
+#                       "ordered", "ordering", "permits",
+#                       "permitted", "permitting", "positions", "positioned",
+#                       "positioning", "preserves", "preserved", "preserving",
+#                       "preservation", "respects",
+#                       "respected", "respecting", "respectful", "reveres",
+#                       "revered", "revering", "reverence", "serves", "served",
+#                       "serving", "traditions", "traditional", "traits")
+# original_mfd$a2lo[28:112] = NA
+# original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
+#                       "protest", "refuse", "defects", "defected", 
+#                       "defecting","defies", "defied", "defying", "defiance", "deserts",
+#                       "deserted", "deserting", "desertion", "opposes", "opposed",
+#                       "opposing", "protests", "protested", "protesting",
+#                       "refuses", "refused", "refusing", "refusal")
+# 
+# #purity/sanctity
+# original_mfd$p2hi[32:112] = NA
+# original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
+#                       "preserve", "pure", "right", "sacred", "whole",
+#                       "abstains", "abstained", "abstaining", "abstinence",
+#                       "churches", "cleans", "cleaned", "cleaning", "cleanse",
+#                       "cleanliness", "innocence", "modesty", "preserves", "preserved",
+#                       "preserving", "preservation", "purity", "rights", 
+#                       "sacredness", "wholeness", "wholesome")
+# original_mfd$p2lo[30:112] = NA
+# original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
+#                       "promiscuous", "ruin", "sick", "sin", "trash",
+#                       "adulteries", "adulterous", "adulterer", "adulterers",
+#                       "dirty", "diseases", "diseased", "disgusts", 
+#                       "disgusted", "disgusting", "grossness", "promiscuity",
+#                       "promiscuities", "ruins", "ruined","ruining", 
+#                       "sickness", "sicknesses", "sins")
 ```
@@
 ```{r new_data, include = FALSE}
-#take final$stemmed column loop over this
-#Harm
-harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+
+###harm
+#read in the harm total words from the mtmm project
+harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)
+
+harm_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
 
@@
 #only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA"])]
+temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA" & !is.na(harm_all$words)]), ]
 

### 2018-09-04 pilot_manuscript.Rmd
still working on the paper

@@
 ```{r scraping, eval=FALSE, include=FALSE}
+
 library(rvest)

### 2018-09-04 SAGE/script for sage.R

@@ -1,0 +1,477 @@
+
+# Web Scraping Code -------------------------------------------------------
+
+#we ran this part daily until the bottom numbers were past 250K words for each one
+
+library(rvest)
+####NY Times####
+#Specifying the url for desired website to be scrapped
+url <- 'https://www.nytimes.com/section/politics'
+
+#Reading the HTML code from the website - headlines
+webpage <- read_html(url)
+headline_data = html_nodes(webpage,'.story-link a, .story-body a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep("http", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+  
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+  
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.story-content') 
+  
+  ##pull the text
+  text_data = html_text(headline_data)
+  
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+} ##end for loop
+
+####NPR original front page####
+url2 = 'https://www.npr.org/sections/politics/'
+webpage2 = read_html(url2)
+headline_data2 = html_nodes(webpage2,'.title a')
+
+#URLs
+attr_data2 = html_attrs(headline_data2) 
+attr_data2
+
+urlslist2 = unlist(attr_data2)
+urlslist2 = urlslist2[grep("http", urlslist2)]
+urlslist2
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 1:length(urlslist2)){
+  
+  ##read in the URL
+  webpage2 <- read_html(urlslist2[i])
+  
+  ##pull the specific nodes
[…]

### 2018-09-06 SAGE/script for sage.R
updated text
needs the data exemplar, questions, references

@@ -474,4 +474,5 @@ overallgraph +
   ylab("Percent") + 
   cleanup +
   facet_grid(~MoralFoundation) + 
+  scale_fill_manual(values = c("grey20", "grey40", "grey60", "grey80")) +
   NULL

### 2018-09-08 pilot_manuscript.Rmd
Fixed comma issues, etc.

@@
 #Fair
-fair_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)
+
+fair_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
 
@@
 #only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA"])]
+temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA" & !is.na(fair_all$words)]), ]
 
@@
 #Ingroup
-ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+ingroup_all = read.csv("ingroup_words_total.csv", stringsAsFactors = F)
+
+ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
 
@@
 #only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA"])]
+temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & !is.na(ingroup_all$words)]), ]
 
@@
 #Authority
-authority_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+authority_all = read.csv("authority_words_total.csv", stringsAsFactors = F)
+
+authority_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
 
@@
 #only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA"])]
+temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA" & !is.na(authority_all$words)]), ]
 
@@
 #Purity
+purity_all = read.csv("purity_words_total.csv", stringsAsFactors = F)
+
 purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
@@
 #only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA"])]
+temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA" & !is.na(purity_all$words)]), ]
 

### 2018-09-11 pilot_manuscript.Rmd
updated sage and thesis stuff

@@
 ```{r new_data, include = FALSE}
+##open the Warriner data for later
+warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+
+for(i in 1:nrow(warriner)) {
+  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
+}
 
@@
 temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA" & !is.na(harm_all$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
 
@@
 
+#pull in the data from Warriner 
+library(expss)
+harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
+#fought, safer, spurn
+
 #Fair
@@
 temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA" & !is.na(fair_all$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
 
@@
 
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
 #add to the dataset
@@
 
+```
+
+```{r descriptives, include = FALSE}
+#summarize the dataset so that you have the total and percent for each foundation
+
+#report descriptive statistics of the foundations
+
+#note that a big problem is the valence of the words 
 ```

### 2018-10-08 pilot_manuscript.Rmd
updated thesis stuff
Did some Introduction work
Obviously, more needs to be done

@@
 # Introduction
-Talk about MFT, MFQ, MFD (primer on moral psychology?)
+
+Something clever to start
+
+##Moral Foundations Theory
+
+Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain.
+The researchers argued older theories of moral psychology were focused primarly on issues of justice, fairness, and caring - indvidually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
+In other words, moral psychology ignored the valid moral foundations of conservatives.
+Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
+
+The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@GILLIGAN1991].
+*LET'S CHECK THIS CITATION IN MENDELEY*!.The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
+*Harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm.
+*Fairness/reciprocity* represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
+The other three foundations (*ingroup/loyalty*, *authority/respct*, and *purity/sanctity*) are the "binding" foundations, owing to their focus on group-related concerns, rather than those of individuals.
+*Ingroup/loyalty* represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
+*Authority/respect* represents an endorsement of social hierarchies and traditions while denigrating disobedience.
+Finally, *purity/sanctity* represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony [@Haidt2007].
+Liberals tend to endorse the individualizing foundations more than conservatives.
+Endorsements for the three binding foundations, however, are lower than conservatives.
+Conservatives, on the other hand, tend to endorse all five foundations equally, implying they base judments (at least partially) on each foundation [@Graham2009].
+
+##Moral Foundations Dictionary
+
+In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
+The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
+The researchers created a preliminary list of words that they believed would be associated with the five foundations.
+Then, using the Linguistic Inquiry and Word Count (LIWC; @Pennebaker2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
+The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
+Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
+Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers.
+However, conservative ministers did not use *ingroup/loyalty* words more than liberals.
+Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].
 
@@
 
+#figure out stupid words
+#table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
+#fought, safer, spurn
+
 #Ingroup

### 2018-10-09 pilot_manuscript.Rmd
fixed the warriner words

@@
 ```
-# Introduction
 
@@
 This project brings the two together in holy matrimony.
+
 # Method
@@
 
-###harm
+####harm####
+
 #read in the harm total words from the mtmm project
@@
 #figure out stupid words
-#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
+table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
 #fought, safer, spurn
-
-#Fair
+harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
+harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
+#no spurn avaliable
+
+####Fair####
 fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)
@@
 
+fair_final_data$valence = vlookup(fair_final_data$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
 #figure out stupid words
-#table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
-#fought, safer, spurn
+table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
+#just plagiar safer
+fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
+#nothing for just or plagiarism
 
@@
 
+ingroup_final_data$valence = vlookup(ingroup_final_data$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
+#backstabb  benedict      best      fals   indvidu      juda    knight      true
+ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
+ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
+ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
+
 #Authority
@@
 
+authority_final_data$valence = vlookup(authority_final_data$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
+#  abov behind   gase higher  older  taken 
+authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
+authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
+authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
+authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
+
 #Purity
@@
 
-purity_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)
+purity_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
 
@@
 
+purity_final_data$valence = vlookup(purity_final_data$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(purity_final_data$Var1[is.na(purity_final_data$valence) & purity_final_data$Freq > 0])
+#befor christian     jesus      mari      none    sacred    someon      true     women 
+purity_final_data$valence[purity_final_data$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
+purity_final_data$valence[purity_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
+purity_final_data$valence[purity_final_data$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
 ```

### 2018-10-20 pilot_manuscript.Rmd
wrote more of the Intro

@@
 
-(Brief) primer on political research?
-
-Talk about political discourse, nature of news media in 2018/Trump era
+## News Media and Politics
+
+Research into politics, language, and media has illuminated the complex relationships between all three.
+Any politically-oriented discussion of language use as an implication of moral or poltical position assumes that langauge and ideology are intrisincally linked.
+Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through langauge, thus implying a connection between ideology and language.
+She goes on to criticize the notion that language is either the "pre-existing raw material" used to shape ideologies or the "post-hoc vehicle" for their propogation.
+Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies [@Cameron2006].
+
+The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S.
+For example, Druckman, Jacobs, and Ostermeier (-@Druckman2004) investigated issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
+In their research, the authors consider "issue" as that which attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
+"Image" priming, on the other hand, describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].
+The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
+They linked the Nixon adminstration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
+Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].
+
+Druckman, Jacobs, and Ostermeier (-@Druckman2004) also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy.
+This implies news media may affect perception of politicians based on where the media places emphasis.
+Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014].
+Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their districts.
+As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014].
+The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
+
+Talk about political discourse, nature of news media in 2018/Trump era/Kavanaugh
 

### 2018-10-23 pilot_manuscript.Rmd
erin tests

@@
 The researchers created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count (LIWC; @Pennebaker2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
+Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
 The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
@@
 
-Druckman, Jacobs, and Ostermeier (-@Druckman2004) also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy.
+@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy.
 This implies news media may affect perception of politicians based on where the media places emphasis.
@@
 
+```{r update-mlm, include = FALSE}
+
+#harm_final_data clean up
+harm_final_data$percent = harm_final_data$Freq / harm_final_data$wordcount *100
+harm_final_data$lean = factor(harm_final_data$Source, 
+                              levels = names(table(harm_final_data$Source)),
+                              labels = c("Conservative1", "Conservative",
+                                  "Liberal1", "Liberal"))
+harm_final_data$lean = gsub("1", "", harm_final_data$lean)
+
+harm_final_data$weighted = harm_final_data$percent*harm_final_data$valence
+
+#boring models first
+
+#final model
+modelfinal = lme(percent ~ valence*lean,
+                 data = harm_final_data,
+                 method = "ML", 
+                 na.action = "na.omit", 
+                 random = list(~1|Var1, ~1|Source))
+summary(modelfinal)
+
+with(harm_final_data, tapply(percent, list(lean), mean))
+with(harm_final_data, tapply(valence, list(lean), mean, na.rm = T))
+with(harm_final_data, tapply(weighted, list(lean), mean, na.rm = T))
+
+modelfinal = lme(weighted ~ lean,
+                 data = harm_final_data,
+                 method = "ML", 
+                 na.action = "na.omit", 
+                 random = list(~1|Var1, ~1|Source))
+summary(modelfinal)
+
+```
+
 ```{r mlm-analyses, echo=FALSE, warning=FALSE, include = FALSE}

### 2018-10-27 pilot_manuscript.Rmd
wrote some intro stuff

@@
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
+
+#Kavanaugh Supreme Court Hearing
+In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
+Kavanaugh was previously on the U.S.
+Court of Appeals for the District of Columbia.
+The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD].
+Following allegations of sexual assault by high school classmate Dr.
+Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
+
+On September 27, the committee questioned Dr.
+Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD].
+During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
+According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television.
+This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
+On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
+Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
+The investigation concluded with no significant findings.
+The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].
 

### 2018-10-29 pilot_manuscript.Rmd
wrote a little more

@@
 Research into politics, language, and media has illuminated the complex relationships between all three.
-Any politically-oriented discussion of language use as an implication of moral or poltical position assumes that langauge and ideology are intrisincally linked.
+Any politically-oriented discussion of word occurence as an implication of moral or poltical position assumes that langauge and ideology are intrisincally linked.
 Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through langauge, thus implying a connection between ideology and language.
@@
 For example, Druckman, Jacobs, and Ostermeier (-@Druckman2004) investigated issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
-In their research, the authors consider "issue" as that which attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
+In their research, the authors consider "issues" as communication that attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
 "Image" priming, on the other hand, describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].
@@
 Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014].
-Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their districts.
+Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
 As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014].
@@
 The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].
+
+The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
+On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime oppurtunity to bring morality back into interpretation of the Constitution.
+Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
+Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
+On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Additionally, the moral duty of the Senate as the upper chamber in the U.S.
+legislature has been scrutinized in public discourse with respect to its handling of the assualt allegations vis-a-vis Kavanaugh's confirmation.
 

### 2018-10-30 pilot_manuscript.Rmd
Some formatting edits to manuscript

@@
 
-#Kavanaugh Supreme Court Hearing
+##Kavanaugh Supreme Court Hearing
 In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
@@
 
-# Method
+# Method - Experiment 1
 
@@
 
-# Results
+# Experiment 1 results
 
@@
 
+# Method - Experiment 2
+
+## Sources
+Experiment 2 largely followed the same method as Experiment 1. Political articles specifically referring to Brett Kavanaugh and his Supreme Court confirmation hearing were scraped
+
+## Materials
+
+## Data analysis
+
+# Experiment 2 results
+
 # Discussion
+
+## Experiment 1
+
+## Experiment 2
+
+## General discussion
 How it turned out

### 2018-10-30 pilot_manuscript.Rmd
updated analyses

@@
 warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
 
@@
 ```{r update-mlm, include = FALSE}
-
 #harm_final_data clean up
-harm_final_data$percent = harm_final_data$Freq / harm_final_data$wordcount *100
-harm_final_data$lean = factor(harm_final_data$Source, 
-                              levels = names(table(harm_final_data$Source)),
-                              labels = c("Conservative1", "Conservative",
-                                  "Liberal1", "Liberal"))
-harm_final_data$lean = gsub("1", "", harm_final_data$lean)
-
-harm_final_data$weighted = harm_final_data$percent*harm_final_data$valence
+#multiply by frequency and create percentage
+harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100
+
+#flatten down to sum by article 
+harm_final_temp = aggregate(harm_final_data$weight, 
+          by = list(harm_final_data$URL),
+          FUN = sum, na.rm = T)
+colnames(harm_final_temp) = c("URL", "MFDweight")
+
+harm_final_temp$lean[grepl("nytimes.com", harm_final_temp$URL) |
+                       grepl("npr.org", harm_final_temp$URL)] = "Liberal"
+harm_final_temp$lean[grepl("breitbart.com", harm_final_temp$URL) |
+                       grepl("foxnews.com", harm_final_temp$URL)] = "Conservative"
+
+harm_final_temp$Source[grepl("nytimes.com", harm_final_temp$URL)] = "NY Times"
+harm_final_temp$Source[grepl("npr.org", harm_final_temp$URL)] = "NPR"
+harm_final_temp$Source[grepl("foxnews.com", harm_final_temp$URL)] = "Fox"
+harm_final_temp$Source[grepl("breitbart.com", harm_final_temp$URL)] = "Breitbart"
+
+harm_model = lme(MFDweight ~ lean, 
+                 data = harm_final_temp, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 

### 2018-11-04 pilot_manuscript.Rmd
takin a Brain Break!

@@
 Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].
+
+To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurence of words from the foundation's respective word list.
+As such, most analyses assume that zero percent occurence is indicative of no endorsement, while any non-zero percent occurence indicates endorsement of the foundation.
+This may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
+A quick glance at the MFD words for *harm/care* reveals the presence of words that are more closely associated with universally accepted conceptions of *harm* over *care* and vice-versa [@Graham2009].
+For example, the word "cruel" has relatively negative connotations compared to "benefit." For the *harm/care* foundation, it is conceivable that use of the word "cruel" might indicate a greater attentional focus of the idea of *harm* rather than *care*.
+
+For *harm/care*, the definition of the foundation as well as its name clearly distinguishes between two somewhat opposite sides of an attentional continuum, with *harm* on the negative end and *care* on the positive side.
+In other words, the entries in the MFD for *harm/care* have somewhat clear positive and negative valences.
+The same pattern can be seen in the MFD entries for the other four foundations.
+*Purity/sanctity* features words that likely have a negative valence to most observers, including "disease"" and "trash," along with more positive words, including "right" and "sacred" [@Graham2009].
+This, however, brings up other questions regarding the definition and names of the other four foundations apart from *harm/care*: *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*.
+The latter four foudnations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of *fairness/reciprocity*.
+
+When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
+How can raw percentage of MFD word occurence capture the valence and focus of the writer or speaker?
+If 2% of a politician's speech features positive words (i.e.
+"benefit" and "defend") from the MFD *harm/care* list, how can researchers be sure the level and nature of the speaker's "endorsement" of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the *harm/care* list?
+They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the *harm/care* spectrum.
+
+This issue is compounded by the fact the Moral Foundations Questionnaire and its subscales assume endorsement lies on a continuum.
+
+##Valence
 

### 2018-11-06 pilot_manuscript.Rmd
little more - hoping to start valence section in the morning

@@
 
-This issue is compounded by the fact the Moral Foundations Questionnaire and its subscales assume endorsement lies on a continuum.
+This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
+One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@GILLIGAN1991].
+The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning "strongly disagree" at 1 to "strongly agree" at 6.
+While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
+When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@GILLIGAN1991].
+This specificity is not present in most analyses involving the MFD and percent occurence, unless they also take into account the valence of the words used in the text or speech of interest.
 

### 2018-11-06 pilot_manuscript.Rmd
i don't know what i did

@@
 ##Kavanaugh Supreme Court Hearing
+
 In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.

### 2018-11-24 pilot_manuscript.Rmd
I thnk I got this updated correctly

@@
 title             : "Moral Foundations of U.S. Political News Organizations"
-shorttitle        : "MORAL FOUNDATIONS OF U.S. NEWS"
+shorttitle        : "MORAL NEWS"
 
@@
 library(ggplot2)
+library(expss)
 
@@
 
-```{r data-cleanup, eval=TRUE, include=FALSE}
+```{r data-cleanup, eval=FALSE, include=FALSE}
 ##pull in the data
@@
 
-#write.csv(final, "finaldata.csv")
-
-####start here####
-final = read.csv("finaldata.csv", stringsAsFactors = F)
-final = na.omit(final) #one weird NA line
+write.csv(final, "finaldata.csv")
 
@@
 Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a positive authority/respect word and *defect* as a negative authority/respect word).
-
-```{r fix-MFD, eval=TRUE, include=FALSE}
-##figure out the percent of MFD words
-
-##the amount of time people used the original MFD words
-original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
-
-##adding forms/conjugations of words to original_mfd
-#harm/care
-original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
-                             "sympathetic","sympathies","damaged",
-                             "damaging","attacked","attacking","attacker",
-                             "attacks","attackers", "benefits", "benefitted",
-                             "benefitting", "cares", "cared", "caring", "crushes",
-                             "crushing", "crushed", "dangerous", "defends", "defending",
-                             "defended", "detroys", "destroyed", "destroying",
-                             "fights", "fought", "fighting", "guards", "guarded",
-                             "guarding", "harms", "harmed", "harming", "hurts",
-                             "hurting", "kills", "killed", "killing", "preserves",
-                             "preserved", "preserving", "protects", "protected",
-                             "protecting", "protection", "ruins", "ruined", "ruining",
-                             "safely", "safer", "shelters", "sheltered", "sheltering",
-                             "spurns", "spurned", "spurning", "stomps", "stomped",
-                             "stomping", "suffers", "suffered", "suffering",
-                             "violence", "warring")
-
-#fairness/reciprocity
-original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
-                             "biases", "discriminates", "discriminated",
-                             "discriminating", "discrimination", "equals",
-                             "equaled", "equaling", "equates", "equated",
-                             "equating", "evens", "evened", "evening",
-                             "excludes", "excluded", "excluding", "fairness",
-                             "favors", "favored", "favoring", "honesty",
-                             "impariality", "justice", "justifies", "justified",
-                             "justifying", "prefers", "preferred", "preferring",
-                             "prejudices", "prejudiced", "prejudicing", "reasons",
-                             "reasoned", "reasoning", "rights", "tolerates",
-                             "tolerated", "tolerating", "toleration")
-
-#ingroup/loyalty
-original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
-                             "communities", "deceives", "deceived", "deceiving",
-                             "deception", "deceptions", "deserts", "deserted",
-                             "deserting", "desertion", "families", "fellows",
-                             "foreigners", "groups", "grouped", "grouping",
-                             "indviduals", "indvidualize", "individualized",
-                             "individualizing", "members", "nations", "sides",
-                             "togetherness", "traits", "unites", "united", "uniting")
-
-#authority/respect
-original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
-                              "classes", "classed", "classing", "command",
-                              "commanded", "commanding", "controls", "controlled",
-                              "controlling", "defects", "defected", "defecting",
-                              "defers", "deferred", "deferring", "deference",
-                              "defies", "defied", "defying", "defiance", "deserts",
-                              "deserted", "deserting", "desertion", "duties",
-                              "faiths", "fathers", "fathered", "fathering",
-                              "honors", "honored", "honoring", "laws", "leads",
-                              "leading", "mothers", "mothered", "mothering",
-                              "obeys", "obeyed", "obeying", "opposes", "opposed",
-                              "opposing", "orders", "ordered", "ordering", "permits",
-                              "permitted", "permitting", "positions", "positioned",
-                              "positioning", "preserves", "preserved", "preserving",
-                              "preservation", "protests", "protested", "protesting",
-                              "refuses", "refused", "refusing", "refusal", "respects",
-                              "respected", "respecting", "respectful", "reveres",
-                              "revered", "revering", "reverence", "serves", "served",
-                              "serving", "traditions", "traditional", "traits")
-
-#purity/sanctity
-original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
-                             "adulteries", "adulterous", "adulterer", "adulterers",
-                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
-                             "cleanliness", "dirty", "diseases", "diseased", 
-                             "disgusts", "disgusted", "disgusting", "grossness",
-                             "innocence", "modesty", "preserves", "preserved",
-                             "preserving", "preservation", "promiscuity",
-                             "promiscuities", "purity", "rights", "ruins", "ruined",
-                             "ruining", "sacredness", "sickness", "sicknesses",
-                             "sins", "wholeness", "wholesome")
-
-# ##separate them into h low, h high until you have ten categories 
-# #harm/care
-# original_mfd$h2hi[35:112] = NA 
-# original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
-#                       "protect", "safe", "shelter", "sympathetic",
-#                       "sympathies", "benefits", "benefitted",
-#                       "benefitting", "cares", "cared", "caring","defends", 
-#                       "defending","defended", "guards", "guarded",
-#                       "guarding","preserves",
-#                       "preserved", "preserving", "protects", "protected",
-#                       "protecting", "protection",  
-#                       "safely", "safer", "shelters", 
-#                       "sheltered", "sheltering")
-# original_mfd$h2lo[61:112] = NA
-# original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
-#                       "damage", "danger", "destroy", "fight", "harm",
-#                       "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
-#                       "violent", "war","abusive",
-#                       "abuser","abused","abusing","damaged",
-#                       "damaging","attacked","attacking","attacker",
-#                       "attacks","attackers","crushes",
-#                       "crushing", "crushed", "dangerous","detroys", 
-#                       "destroyed", "destroying",
-#                       "fights", "fought", "fighting","harms", 
-#                       "harmed", "harming", "hurts",
-#                       "hurting", "kills", "killed", "killing",
-#                       "ruins", "ruined", "ruining", "spurns", 
-#                       "spurned", "spurning", "stomps", "stomped",
-#                       "stomping", "suffers", "suffered", "suffering",
-#                       "violence", "warring")
-# 
-# #fairness/reciprocity
-# original_mfd$f2hi[41:112] = NA
-# original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
-#                       "fair", "honest", "just", "justify", "reason",
-#                       "right", "tolerate", "impartial", "balances", 
-#                       "balanced", "balancing",
-#                       "equals", "equaled", "equaling", "equates", "equated",
-#                       "equating", "evens", "evened", "evening","fairness",
-#                       "honesty", "impartiality", "justice", "justifies", 
-#                       "justified", "justifying", "reasons",
-#                       "reasoned", "reasoning", "rights", "tolerates",
-#                       "tolerated", "tolerating", "toleration")
-# original_mfd$f2lo[25:112] = NA
-# original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
-#                       "prefer", "prejudice", "biased", "biases", "discriminates", 
-#                       "discriminated", "discriminating", "discrimination",
-#                       "excludes", "excluded", "excluding", 
-#                       "favors", "favored", "favoring", "prefers", "preferred", "preferring",
-#                       "prejudices", "prejudiced", "prejudicing")
-# 
-# #ingroup/loyalty
-# original_mfd$i2hi[30:112] = NA
-# original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
-#                       "group", "member", "nation", "side", "together",
-#                       "trait", "unite", "collects", 
-#                       "collected", "collecting", "collective",
-#                       "communities", "families", "fellows",
-#                       "groups", "grouped", "grouping",
-#                       "members", "nations", "sides",
-#                       "togetherness", "traits", "unites", 
-#                       "united", "uniting")
-# original_mfd$i2lo[19:112] = NA 
-# original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
-#                       "deceives", "deceived", "deceiving",
-#                       "deception", "deceptions", "deserts", "deserted",
-#                       "deserting", "desertion", "foreigners",
-#                       "indviduals", "indvidualize", "individualized",
-#                       "individualizing")
-# 
-# #authority/respect
-# original_mfd$a2hi[86:112] = NA
-# original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
-#                       "control", "defer", "duty", "faith", "father", "honor",
-#                       "law", "lead", "legal", "mother", "obey", 
-#                       "order", "permit", "position", "preserve",
-#                       "respect", "revere", "serve", "tradtition", "trait",
-#                       "abides", "abided", "abiding", "authorities",
-#                       "classes", "classed", "classing", "command",
-#                       "commanded", "commanding", "controls", "controlled",
-#                       "controlling","defers", "deferred", "deferring", "deference",
-#                       "duties","faiths", "fathers", "fathered", "fathering",
-#                       "honors", "honored", "honoring", "laws", "leads",
-#                       "leading", "mothers", "mothered", "mothering",
-#                       "obeys", "obeyed", "obeying", "orders", 
-#                       "ordered", "ordering", "permits",
-#                       "permitted", "permitting", "positions", "positioned",
-#                       "positioning", "preserves", "preserved", "preserving",
-#                       "preservation", "respects",
-#                       "respected", "respecting", "respectful", "reveres",
-#                       "revered", "revering", "reverence", "serves", "served",
-#                       "serving", "traditions", "traditional", "traits")
-# original_mfd$a2lo[28:112] = NA
-# original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
-#                       "protest", "refuse", "defects", "defected", 
-#                       "defecting","defies", "defied", "defying", "defiance", "deserts",
-#                       "deserted", "deserting", "desertion", "opposes", "opposed",
-#                       "opposing", "protests", "protested", "protesting",
-#                       "refuses", "refused", "refusing", "refusal")
-# 
-# #purity/sanctity
-# original_mfd$p2hi[32:112] = NA
-# original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
-#                       "preserve", "pure", "right", "sacred", "whole",
-#                       "abstains", "abstained", "abstaining", "abstinence",
-#                       "churches", "cleans", "cleaned", "cleaning", "cleanse",
-#                       "cleanliness", "innocence", "modesty", "preserves", "preserved",
-#                       "preserving", "preservation", "purity", "rights", 
-#                       "sacredness", "wholeness", "wholesome")
-# original_mfd$p2lo[30:112] = NA
-# original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
-#                       "promiscuous", "ruin", "sick", "sin", "trash",
-#                       "adulteries", "adulterous", "adulterer", "adulterers",
-#                       "dirty", "diseases", "diseased", "disgusts", 
-#                       "disgusted", "disgusting", "grossness", "promiscuity",
-#                       "promiscuities", "ruins", "ruined","ruining", 
-#                       "sickness", "sicknesses", "sins")
-```
 
@@
 
-```{r process-text, eval=TRUE, include=FALSE}
+```{r stem_text, eval=TRUE, include=FALSE}
+
+final = read.csv("finaldata.csv", stringsAsFactors = F)
+final = na.omit(final) #one weird NA line
+
 ##load libraries
@@
 
-# ##stem the original MFD stuff - separate loop on only the mfd data frame
-# for(i in 1:nrow(original_mfd)) {
-#   original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
-#   original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
-#   original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
-#   original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
-#   original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
-#   original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
-#   original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
-#   original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
-#   original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
-#   original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
-# }
-# 
-# final$hhisum = NA
-# final$hlosum = NA
-# final$fhisum = NA
-# final$flosum = NA
-# final$ihisum = NA
-# final$ilosum = NA
-# final$ahisum = NA
-# final$alosum = NA
-# final$phisum = NA
-# final$plosum = NA
-# 
-# for (i in 1:nrow(final)) {
-# ##first make a table of a response, unlisting everything
-# temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-# ##find the rows that match the mfd list and sum and save
-# final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
-# final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])
-# 
-# final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
-# final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])
-# 
-# final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
-# final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])
-# 
-# final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
-# final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])
-# 
-# final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
-# final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
-# }
-# 
-# final$hperhi = final$hsumhi / final$wordcount * 100
-# final$hperlo = final$hsumlo / final$wordcount * 100
-# final$fperhi = final$fsumhi / final$wordcount * 100
-# final$fperlo = final$fsumlo / final$wordcount * 100
-# final$iperhi = final$isumhi / final$wordcount * 100
-# final$iperlo = final$isumlo / final$wordcount * 100
-# final$aperhi = final$asumhi / final$wordcount * 100
-# final$aperlo = final$asumlo / final$wordcount * 100
-# final$pperhi = final$psumhi / final$wordcount * 100
-# final$pperlo = final$psumlo / final$wordcount * 100
-# 
-# #let's look at the means
-# tapply(final$hperhi, final$Source, mean)
-# tapply(final$hperlo, final$Source, mean)
-# tapply(final$fperhi, final$Source, mean)
-# tapply(final$fperlo, final$Source, mean)
-# tapply(final$iperhi, final$Source, mean)
-# tapply(final$iperlo, final$Source, mean)
-# tapply(final$aperhi, final$Source, mean)
-# tapply(final$aperlo, final$Source, mean)
-# tapply(final$pperhi, final$Source, mean)
-# tapply(final$pperlo, final$Source, mean)
-```
-
-```{r new_data, include = FALSE}
+```
+
+```{r stem_warriner, include = FALSE}
 ##open the Warriner data for later
@@
 } 
-
-####harm####
-
+```
+
+```{r create_datasets_harm, include=FALSE}
 #read in the harm total words from the mtmm project
@@
 #pull in the data from Warriner 
-library(expss)
 harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
@@
 #no spurn avaliable
-
-####Fair####
+```
+
+```{r create_datasets_fair, include=FALSE}
 fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)
@@
 #nothing for just or plagiarism
-
-#Ingroup
+```
+
+```{r create_datasets_ingroup, include=FALSE}
 ingroup_all = read.csv("ingroup_words_total.csv", stringsAsFactors = F)
@@
 ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-
-#Authority
+```
+
+```{r create_datasets_authority, include=FALSE}
 authority_all = read.csv("authority_words_total.csv", stringsAsFactors = F)
@@
 authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-
-#Purity
+```
+
+```{r create_datasets_purity, include=FALSE}
 purity_all = read.csv("purity_words_total.csv", stringsAsFactors = F)
@@
 
-```{r update-mlm, include = FALSE}
-#harm_final_data clean up
+```{r analysis_harm, include = FALSE}
+#final_data clean up
 #multiply by frequency and create percentage
@@
                  random = list(~1|Source))
-
-#boring models first
-
-#final model
-modelfinal = lme(percent ~ valence*lean,
-                 data = harm_final_data,
+summary(harm_model)
+```
+
+```{r analysis_fair, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+fair_final_data$weight = fair_final_data$Freq * fair_final_data$valence / fair_final_data$wordcount * 100
+
+#flatten down to sum by article 
+fair_final_temp = aggregate(fair_final_data$weight, 
+          by = list(fair_final_data$URL),
+          FUN = sum, na.rm = T)
+colnames(fair_final_temp) = c("URL", "MFDweight")
+
+fair_final_temp$lean[grepl("nytimes.com", fair_final_temp$URL) |
+                       grepl("npr.org", fair_final_temp$URL)] = "Liberal"
+fair_final_temp$lean[grepl("breitbart.com", fair_final_temp$URL) |
+                       grepl("foxnews.com", fair_final_temp$URL)] = "Conservative"
+
+fair_final_temp$Source[grepl("nytimes.com", fair_final_temp$URL)] = "NY Times"
+fair_final_temp$Source[grepl("npr.org", fair_final_temp$URL)] = "NPR"
+fair_final_temp$Source[grepl("foxnews.com", fair_final_temp$URL)] = "Fox"
+fair_final_temp$Source[grepl("breitbart.com", fair_final_temp$URL)] = "Breitbart"
+
+fair_model = lme(MFDweight ~ lean, 
+                 data = fair_final_temp, 
                  method = "ML",
                  na.action = "na.omit",
-                 random = list(~1|Var1, ~1|Source))
-summary(modelfinal)
-
-with(harm_final_data, tapply(percent, list(lean), mean))
-with(harm_final_data, tapply(valence, list(lean), mean, na.rm = T))
-with(harm_final_data, tapply(weighted, list(lean), mean, na.rm = T))
-
-modelfinal = lme(weighted ~ lean,
-                 data = harm_final_data,
+                 random = list(~1|Source))
+summary(fair_model)
+```
+
+```{r analysis_ingroup, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+ingroup_final_data$weight = ingroup_final_data$Freq * ingroup_final_data$valence / ingroup_final_data$wordcount * 100
+
+#flatten down to sum by article 
+ingroup_final_temp = aggregate(ingroup_final_data$weight, 
+          by = list(ingroup_final_data$URL),
+          FUN = sum, na.rm = T)
+colnames(ingroup_final_temp) = c("URL", "MFDweight")
+
+ingroup_final_temp$lean[grepl("nytimes.com", ingroup_final_temp$URL) |
+                       grepl("npr.org", ingroup_final_temp$URL)] = "Liberal"
+ingroup_final_temp$lean[grepl("breitbart.com", ingroup_final_temp$URL) |
+                       grepl("foxnews.com", ingroup_final_temp$URL)] = "Conservative"
+
+ingroup_final_temp$Source[grepl("nytimes.com", ingroup_final_temp$URL)] = "NY Times"
+ingroup_final_temp$Source[grepl("npr.org", ingroup_final_temp$URL)] = "NPR"
+ingroup_final_temp$Source[grepl("foxnews.com", ingroup_final_temp$URL)] = "Fox"
+ingroup_final_temp$Source[grepl("breitbart.com", ingroup_final_temp$URL)] = "Breitbart"
+
+ingroup_model = lme(MFDweight ~ lean, 
+                 data = ingroup_final_temp, 
                  method = "ML",
                  na.action = "na.omit",
-                 random = list(~1|Var1, ~1|Source))
-summary(modelfinal)
-
-```
-
-```{r mlm-analyses, echo=FALSE, warning=FALSE, include = FALSE}
-##Attempt at MLM
-mlm_data = final[ , -c(3:28) ]
-long_mlm = melt(mlm_data,
-                id = c("X", "Source"))
-colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
-long_mlm$lean = factor(long_mlm$Source,
-                       levels = names(table(long_mlm$Source)),
-                       labels = c("Conservative1", "Conservative",
-                                  "Liberal1", "Liberal"))
-long_mlm$lean = gsub("1", "", long_mlm$lean)
-
-#####intercept only model####
-##gls = generalized least squares
-##ML = maximum likelihood
-model1 = gls(percent ~ 1, 
-             data = long_mlm, 
-             method = "ML", 
-             na.action = "na.omit")
-summary(model1)
-
-####overall percent - random intercept by source####
-model3 = lme(percent ~ 1,
-             data = long_mlm, 
+                 random = list(~1|Source))
+summary(ingroup_model)
+```
+
+```{r analysis_authority, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+authority_final_data$weight = authority_final_data$Freq * authority_final_data$valence / authority_final_data$wordcount * 100
+
+#flatten down to sum by article 
+authority_final_temp = aggregate(authority_final_data$weight, 
+          by = list(authority_final_data$URL),
+          FUN = sum, na.rm = T)
+colnames(authority_final_temp) = c("URL", "MFDweight")
+
+authority_final_temp$lean[grepl("nytimes.com", authority_final_temp$URL) |
+                       grepl("npr.org", authority_final_temp$URL)] = "Liberal"
+authority_final_temp$lean[grepl("breitbart.com", authority_final_temp$URL) |
+                       grepl("foxnews.com", authority_final_temp$URL)] = "Conservative"
+
+authority_final_temp$Source[grepl("nytimes.com", authority_final_temp$URL)] = "NY Times"
+authority_final_temp$Source[grepl("npr.org", authority_final_temp$URL)] = "NPR"
+authority_final_temp$Source[grepl("foxnews.com", authority_final_temp$URL)] = "Fox"
+authority_final_temp$Source[grepl("breitbart.com", authority_final_temp$URL)] = "Breitbart"
+
+authority_model = lme(MFDweight ~ lean, 
+                 data = authority_final_temp, 
                  method = "ML",
                  na.action = "na.omit",
-             random = ~1|Source)
-summary(model3)
-r.squaredGLMM(model3)
-
-####separate models by type####
-##MFD category ~ lean 
-model4.1 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
+                 random = list(~1|Source))
+summary(authority_model)
+```
+
+```{r analysis_purity, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+purity_final_data$weight = purity_final_data$Freq * purity_final_data$valence / purity_final_data$wordcount * 100
+
+#flatten down to sum by article 
+purity_final_temp = aggregate(purity_final_data$weight, 
+          by = list(purity_final_data$URL),
+          FUN = sum, na.rm = T)
+colnames(purity_final_temp) = c("URL", "MFDweight")
+
+purity_final_temp$lean[grepl("nytimes.com", purity_final_temp$URL) |
+                       grepl("npr.org", purity_final_temp$URL)] = "Liberal"
+purity_final_temp$lean[grepl("breitbart.com", purity_final_temp$URL) |
+                       grepl("foxnews.com", purity_final_temp$URL)] = "Conservative"
+
+purity_final_temp$Source[grepl("nytimes.com", purity_final_temp$URL)] = "NY Times"
+purity_final_temp$Source[grepl("npr.org", purity_final_temp$URL)] = "NPR"
+purity_final_temp$Source[grepl("foxnews.com", purity_final_temp$URL)] = "Fox"
+purity_final_temp$Source[grepl("breitbart.com", purity_final_temp$URL)] = "Breitbart"
+
+purity_model = lme(MFDweight ~ lean, 
+                 data = purity_final_temp, 
                  method = "ML",
                  na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.1)
-r.squaredGLMM(model4.1)
-
-model4.2 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "hperlo", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.2)
-r.squaredGLMM(model4.2)
-
-model4.3 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "fperhi", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.3)
-r.squaredGLMM(model4.3)
-
-model4.4 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "fperlo", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.4)
-r.squaredGLMM(model4.4)
-
-model4.5 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "iperhi", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.5)
-r.squaredGLMM(model4.5)
-
-model4.6 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "iperlo", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.6)
-r.squaredGLMM(model4.6)
-
-model4.7 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "aperhi", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.7)
-r.squaredGLMM(model4.7)
-
-model4.8 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "aperlo", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.8)
-r.squaredGLMM(model4.8)
-
-model4.9 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "pperhi", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.9)
-r.squaredGLMM(model4.9)
-
-model4.10 = lme(percent ~ lean,
-             data = long_mlm[long_mlm$moraltype == "pperlo", ], 
-             method = "ML", 
-             na.action = "na.omit",
-             random = ~1|Source)
-summary(model4.10)
-r.squaredGLMM(model4.10)
-
-```
-
-```{r model-table, results='asis', echo=FALSE}
-tableprint = matrix(NA, nrow = 12, ncol = 7)
-
-colnames(tableprint) = c("Model", "AIC", "BIC", "$\\chi^2$", "$df$",
-                         "$R^2_m", "$R^2_c")
-
-#put in each model set information
-#temp store model summary
-temp = summary(model1)
-
-#put in the information
-#entered a raw number here, as a reminder
-tableprint[1 , ] = c("Non-Random Intercept", temp$AIC, temp$BIC,
-                     temp$logLik, 30409, "-", "-")
-
-temp = summary(model3)
-tableprint[2 , ] = c("Random Intercept", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms, r.squaredGLMM(model3))
-
-temp = summary(model4.1)
-tableprint[3 , ] = c("Harm High", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.1))
-
-temp = summary(model4.2)
-tableprint[4 , ] = c("Harm Low", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.2))
-
-temp = summary(model4.3)
-tableprint[5 , ] = c("Fairness High", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.3))
-
-temp = summary(model4.4)
-tableprint[6 , ] = c("Fairness Low", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.4))
-
-temp = summary(model4.5)
-tableprint[7 , ] = c("Ingroup High", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.5))
-
-temp = summary(model4.6)
-tableprint[8 , ] = c("Ingroup Low", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.6))
-
-temp = summary(model4.7)
-tableprint[9 , ] = c("Authority High", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.7))
-
-temp = summary(model4.8)
-tableprint[10 , ] = c("Authority Low", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.8))
-
-temp = summary(model4.9)
-tableprint[11 , ] = c("Purity High", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.9))
-
-temp = summary(model4.10)
-tableprint[12 , ] = c("Purity Low", temp$AIC, temp$BIC,
-                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.10))
-#keep going
-
-#round and clean up
-tableprint[ , 2:4] = printnum(as.numeric(tableprint[ , 2:4]))
-tableprint[-1 , 6] = printp(as.numeric(tableprint[-1 , 6]))
-tableprint[-1 , 7] = printp(as.numeric(tableprint[-1 , 7]))
-
-apa_table.latex(as.data.frame(tableprint),
-          align = c("l", rep("c", 6)), 
-          caption = "MLM Model Statistics",
-          note = "Degrees of freedom indicate residual $df$ for each model.",
-          escape = FALSE
- )
+                 random = list(~1|Source))
+summary(purity_model)
 ```
@@
 To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nest structured of the data, which creates correlated error [@CITE_gelman].
-First, an intercept only model was created using percent text overall as the dependent variable.
-Using the *nlme* library in *R* [@CITE_nlme], a model with the news source as the random intercept was analyzed to determine if it was necessary to control for correlated error.
-Table @\ref(tab:model-table) includes the model statistics for all models.
-While the $\Delta\chi^2$(1) = `r printnum(anova(model1,model3)[,8][2]))`, *p* = `r printp(anova(model1,model3)[,9][2])` was not significant, all models were still structured with a random intercept by source to control for even a small amount of correlated error.
-
-Next, predictor models with political lean predicting percent of MFD words was analyzed for each of the MFD categories separately (i.e., "harm-positive", "harm-negative", etc.).
-Coefficient values indicate the mean differences between conservative and liberal sources, and to help illustrate these differences, the overall means were plotted in Figure \@ref(fig:graph-means).
-For harm words, there was not a significant difference in the words indicating harm-negative *b* = `r printnum(summary(model4.1)$tTable[2,1])`, *t*(`r summary(model4.1)$tTable[2,3]`) = `r printnum(summary(model4.1)$tTable[2,4])`, *p* = `r printp(summary(model4.1)$tTable[2,5])` or harm-positive *b* = `r printnum(summary(model4.2)$tTable[2,1])`, *t*(`r summary(model4.2)$tTable[2,3]`) = `r printnum(summary(model4.2)$tTable[2,4])`, *p* = `r printp(summary(model4.2)$tTable[2,5])`.
-For fair words, there was no signfificant difference in the words indicating fair-negative *b* = `r printnum(summary(model4.3)$tTable[2,1])`, *t*(`r summary(model4.3)$tTable[2,3]`) = `r printnum(summary(model4.3)$tTable[2,4])`, *p* = `r printp(summary(model4.3)$tTable[2,5])` or fair-positive *b* = `r printnum(summary(model4.4)$tTable[2,1])`, *t*(`r summary(model4.4)$tTable[2,3]`) = `r printnum(summary(model4.4)$tTable[2,4])`, *p* = `r printp(summary(model4.4)$tTable[2,5])`.
-For ingroup words, there was no signfificant difference in the words indicating ingroup-negative *b* = `r printnum(summary(model4.5)$tTable[2,1])`, *t*(`r summary(model4.5)$tTable[2,3]`) = `r printnum(summary(model4.5)$tTable[2,4])`, *p* = `r printp(summary(model4.5)$tTable[2,5])` or ingroup-positive *b* = `r printnum(summary(model4.6)$tTable[2,1])`, *t*(`r summary(model4.6)$tTable[2,3]`) = `r printnum(summary(model4.6)$tTable[2,4])`, *p* = `r printp(summary(model4.6)$tTable[2,5])`.
-For authority words, there was not a signfificant difference in the words indicating authority-negative *b* = `r printnum(summary(model4.7)$tTable[2,1])`, *t*(`r summary(model4.7)$tTable[2,3]`) = `r printnum(summary(model4.7)$tTable[2,4])`, *p* = `r printp(summary(model4.7)$tTable[2,5])` or authority-positive *b* = `r printnum(summary(model4.8)$tTable[2,1])`, *t*(`r summary(model4.8)$tTable[2,3]`) = `r printnum(summary(model4.8)$tTable[2,4])`, *p* = `r printp(summary(model4.8)$tTable[2,5])`.
-For purity words, there was a signfificant difference in the words indicating purity-negative *b* = `r printnum(summary(model4.9)$tTable[2,1])`, *t*(`r summary(model4.9)$tTable[2,3]`) = `r printnum(summary(model4.9)$tTable[2,4])`, *p* = `r printp(summary(model4.9)$tTable[2,5])`.
-There was no significant difference for purity-positive *b* = `r printnum(summary(model4.10)$tTable[2,1])`, *t*(`r summary(model4.10)$tTable[2,3]`) = `r printnum(summary(model4.10)$tTable[2,4])`, *p* = `r printp(summary(model4.10)$tTable[2,5])`.
-
-```{r graph-means, echo=FALSE}
-#make a ggplot here! :) 
-#put the categories on the bottom X
-#put the lean as the group
-#y is the percent
-#use the long_mlm dataset
-#i will make low and high happen as different panels
-
-long_mlm$moraltype = factor(long_mlm$moraltype, 
-                  levels=c("hperhi", "hperlo", "fperhi", "fperlo",
-                           "iperhi", "iperlo", "aperhi", "aperlo", "pperhi", "pperlo"),
-                  labels = c("Harm-positive", "Harm-negative", "Fair-positive",
-                             "Fair-negative", "Ingroup-positive", "Ingroup-negative",
-                             "Authority-positive", "Authority-negative", 
-                             "Purity-positive", "Purity-negative")) 
-cleanup = theme(panel.grid.major = element_blank(), 
-                panel.grid.minor = element_blank(), 
-                panel.background = element_blank(), 
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 15))
-
-long_mlm$moral_foundation = long_mlm$moraltype
-long_mlm$moral_foundation = gsub("-positive", "", long_mlm$moral_foundation)
-long_mlm$moral_foundation = gsub("-negative", "", long_mlm$moral_foundation)
-
-long_mlm$valence = long_mlm$moraltype
-long_mlm$valence = gsub("Harm-positive", "Positive", long_mlm$valence)
-long_mlm$valence = gsub("Harm-negative", "Negative", long_mlm$valence)
-long_mlm$valence = gsub("Authority-positive", "Positive", long_mlm$valence)
-long_mlm$valence = gsub("Authority-negative", "Negative", long_mlm$valence)
-long_mlm$valence = gsub("Fair-positive", "Positive", long_mlm$valence)
-long_mlm$valence = gsub("Fair-negative", "Negative", long_mlm$valence)
-long_mlm$valence = gsub("Purity-positive", "Positive", long_mlm$valence)
-long_mlm$valence = gsub("Purity-negative", "Negative", long_mlm$valence)
-long_mlm$valence = gsub("Ingroup-positive", "Positive", long_mlm$valence)
-long_mlm$valence = gsub("Ingroup-negative", "Negative", long_mlm$valence)
-
-overallgraph = ggplot(long_mlm, aes(moral_foundation, percent, fill = lean))
-overallgraph +
-  stat_summary(fun.y = mean,
-               geom = "bar",
-               position = "dodge") +
-  stat_summary(fun.data = mean_cl_normal,
-               geom = "errorbar", 
-               position = position_dodge(width = 0.90),
-               width = .2) +
-  xlab("Moral Category") +
-  ylab("Percent") + 
-  cleanup +
-  scale_fill_manual(name = "Political Lean", 
-                    labels = c("Liberal", "Conservative"),
-                    values = c("Light Gray", "Dark Gray")) +
-  facet_grid(~valence) + 
-  NULL
-
-```
+MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@CITE_gelman].
+Using the *nlme* library in *R* [@CITE_nlme], each foundation's weighted percentage was predicated by the political lean of the news soource, using the individual news sources as a random intercept to control for the structure of the data.
 

### 2018-11-25 pilot_manuscript.Rmd
Wrote things about valence

@@
 ##Valence
+
+Borrowing from Osgood's work in the 1950s, @Bradley1999 recognized valence as one of three related dimensions comprising emotion when developing their Affective Norms for English Words (ANEW).
+As mentioned before, "valence," the first dimension, denotes the pleasantness of a given word.
+"Arousal," the second dimension, describes the stimulating nature of a word.
+Lastly, "dominance" or "control" describes the extent to which a word makes one feel in or out of control [@Bradley1999].
+The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Mannikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
+
+Participants saw the stimulus word and responded on each scale.
+The valence scale featured a smiling figure at one end (representing pleasantness) and a frowning figure at the other end (for unpleasantness).
+The arousal scale had a "wide-eyed" figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
+Finally, the control scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end [@Bradley1999].
+The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words [@Bradley1999].
+ANEW represented an important first step in establishing affective norms for large numbers of English words.
+However, later researchers found the 1,040-word list to be limiting for a language consisting of thousands of words.
+
+@Warriner2013 exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e.
+"watch" rather than "watched" and "watching").
+The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory [@Warriner2013].
+They argue the list of words included in ANEW is sufficient for small-scale factorial research designs, but the list is "prohibitively small" for larger-scale "megastudies" that are common in psycholinguistic research today [@Warriner2013].
+
+In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert as well as the content lemmas from the SUBTLEX-US corpus consisiting of subtitles from various forms of visual media [@Warriner2013].
+This resulted in the final list of 13,915 lemmas.
+Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
+Particpants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
+The researchers used a nine-point scale similar to the one used by @Bradley1999 when collecting ratings for ANEW [@Warriner2013].
+
+The researchers noted several points of interest upon observing ratings.
+First, they found that valence and dominance ratings had a negative skew, indicating more words elicited feelings of happiness and control than their respective opposites.
+Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
+This indicates words with high degrees of positivity and negativity elicited higher arousal [@Warriner2013].
+These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
+
+@Warriner2014 *WE NEED THIS IN MENDELEY* utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in langauge.
+The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
+Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with postive valence were also used more frequently [@Warriner2014].
+While the researchers concede the possiblility of an acquiensence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.
+
+One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
+@Kuperman2014 *WE NEED THIS IN MENDELEY* sought to use the @Warriner2013 norms to fill in the knowledge gaps regarding variance in word recognition.
+The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
+First, @Kuperman2014 found higher response latencies in negative-valence words, lower response latencies in neutral words, and even lower response latencies in words with positive valence.
+The researchers also concluded that words causing higher arousal tend to have higher response latencies than less-arousing words.
+They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
+They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
+Finally, @Kuperman2014 found a greater effect for lexical decision tasks than for naming tasks.
+This research serves as further evidence that the @Warriner2014 list can be used for research inquiries both within and without the field of psycholinguistics.
+
+In the present studies, the researchers used the 2013 Warriner list in order to denote the valence of the words appearing in the news articles scraped from the internet.
+Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
+The valence was used as a means to determine whether individiual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
+Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
 

### 2018-11-27 pilot_manuscript.Rmd
updated pilot stuff

@@
 library(expss)
+library(MOTE)
 
@@
 
-@Warriner2014 *WE NEED THIS IN MENDELEY* utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in langauge.
+@Warriner2014 utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in langauge.
 The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
@@
 One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-@Kuperman2014 *WE NEED THIS IN MENDELEY* sought to use the @Warriner2013 norms to fill in the knowledge gaps regarding variance in word recognition.
+@Kuperman2014 sought to use the @Warriner2013 norms to fill in the knowledge gaps regarding variance in word recognition.
 The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
@@
 
-# Method - Experiment 1
+# Experiment 1
+
+# Method
 
@@
 This procedure created ten percentages that were included as the dependent variable for the following analyses.
-
 ```{r stem_text, eval=TRUE, include=FALSE}
@@
 
-# Experiment 1 results
+# Results
 
@@
 
-# Method - Experiment 2
+```{r exp1-table, results = 'asis', echo = F}
+#MFD, mean, sd, mean, sd, t, p, d
+tableprint = matrix(NA, ncol = 8, nrow = 5)
+colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+
+#calculate d
+harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
+                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
+                 a = .05)
+
+#put in the numbers
+tableprint[1, ] = c("Harm", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
+                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
+                    harm_d$d)
+
+tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
+tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
+```
+# Discussion
+
+# Experiment 2
+
+Kav stuff here
+
+# Method
 
@@
 
+Expected material stuff
+- we are going to pick liberal and conservative sources from that thing document linked stuff
+- list those here:
+
+- pick a specific date range we want to pull articles from 
+- list that here: here's when the stuff was happening and so picked two weeks before and after
+
 ## Data analysis
 
+How you would run the data analysis
+
 # Experiment 2 results
@@
 
-## Experiment 1
-
-## Experiment 2
-
-## General discussion
+# Conclusions
+
 How it turned out

### 2018-12-01 pilot_manuscript.Rmd
Edited some Method and found info for Exp 2

@@
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
-
-##Kavanaugh Supreme Court Hearing
-
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD].
-Following allegations of sexual assault by high school classmate Dr.
-Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
-
-On September 27, the committee questioned Dr.
-Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD].
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television.
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].
-
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime oppurtunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assualt allegations vis-a-vis Kavanaugh's confirmation.
 
@@
 
-In order to fully capture the evaluative power of the Moral Foundations Dictionary (MFD; *CITE*), forms and conjugations of words were added to the original MFD.
-For example, *abuse* was supplemented with *abusive*, *abuser*, *abused*, and *abusing*.
-Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a positive authority/respect word and *defect* as a negative authority/respect word).
-
-Once the MFD was separated along lines of positive and negative dimensions for each of the foundations, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
+Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value.
+Once the MFD words' valences were added to the dataset, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
 The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
-The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function.
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence.
-Therefore, for each article, the percentage of the number of *harm* (low end) and *care* (high end) related words were calculated and this process was repeated for each of the foundations.
-This procedure created ten percentages that were included as the dependent variable for the following analyses.
+The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
+
+DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with reduncies removed at the end.
+
+The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence and their valence.
+Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated and this process was repeated for each of the foundations.
+This procedure created five percentages that were included as the dependent variable for the following analyses.
 ```{r stem_text, eval=TRUE, include=FALSE}
@@
 
-Kav stuff here
+##Kavanaugh Supreme Court Hearing
+
+In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
+Kavanaugh was previously on the U.S.
+Court of Appeals for the District of Columbia.
+The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD].
+Following allegations of sexual assault by high school classmate Dr.
+Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
+
+On September 27, the committee questioned Dr.
+Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD].
+During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
+According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television.
+This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
+On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
+Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
+The investigation concluded with no significant findings.
+The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].
+
+The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
+On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime oppurtunity to bring morality back into interpretation of the Constitution.
+Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
+Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
+On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Additionally, the moral duty of the Senate as the upper chamber in the U.S.
+legislature has been scrutinized in public discourse with respect to its handling of the assualt allegations vis-a-vis Kavanaugh's confirmation.
 
@@
 - list those here:
+  Sources used by LIBERALS (according to the document thing):
+  The New Yorker
+  Slate
+  The Daily Show (is it wise to use satirical news for this??)
+  The Guardian
+  Al Jazeera America
+  NPR
+  New York Times
+  Buzzfeed
+  PBS
+  BBC
+  Huffington Post
+  Washington Post
+  The Economist
+  Politico
+  MSNBC
+  CNN
+  NBC News
+  CBS News
+  Google News
+  Bloomberg
+  ABC News
+  USA TODAY
+
+  Sources used by CONSERVATIVES:
+  Fox News
+  Drudge Report
+  Breitbart
+  Rush Limbaugh Show
+  The Blaze
+  Sean Hannity
+  Glenn Beck (does he still report "news"??)
 
 - pick a specific date range we want to pull articles from 
-- list that here: here's when the stuff was happening and so picked two weeks before and after
+- list that here:
+
+START DATE: September 13, 2018
+
+(September 27, 2018: Ford and Kavanaugh testimony before Senate Judiciary Committee)
+
+END DATE: October 11, 2018
+
+here's when the stuff was happening and so picked two weeks before and after
 

### 2018-12-01 pilot_manuscript.Rmd
added the apa table elements

@@
 
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence and their valence.
-Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated and this process was repeated for each of the foundations.
+The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
+Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations.
 This procedure created five percentages that were included as the dependent variable for the following analyses.
@@
 #summarize the dataset so that you have the total and percent for each foundation
-
+summary(harm_final_data)
+summary(fair_final_data)
+summary(ingroup_final_data)
+summary(authority_final_data)
+summary(purity_final_data)
 #report descriptive statistics of the foundations
-
+mean(harm_final_data$valence)
+sd(harm_final_data$valence)
+mean(fair_final_data$valence)
+sd(fair_final_data$valence)
+mean(ingroup_final_data$valence)
+sd(ingroup_final_data$valence)
+mean(authority_final_data$valence)
+sd(authority_final_data$valence)
+mean(purity_final_data$valence)
+sd(purity_final_data$valence)
 #note that a big problem is the valence of the words 
@@
 #calculate d
+#harm
 harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
@@
 
+#fair
+fair_d = d.ind.t(m1 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"]),
+                 n2 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"]),
+                 a = .05)
+
+#ingroup
+ingroup_d = d.ind.t(m1 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"]),
+                 n2 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"]),
+                 a = .05)
+
+#authority
+authority_d = d.ind.t(m1 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"]),
+                 n2 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"]),
+                 a = .05)
+
+#purity
+purity_d = d.ind.t(m1 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"]),
+                 n2 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"]),
+                 a = .05)
+
 #put in the numbers
-tableprint[1, ] = c("Harm", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
+tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                     summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                     harm_d$d)
+tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
+                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
+                    fair_d$d)
+tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
+                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
+                    ingroup_d$d)
+tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
+                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
+                    authority_d$d)
+tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
+                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
+                    purity_d$d)
 
@@
 During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television.
+According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@CITE_NIELSEN].
 This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.

### 2018-12-04 pilot_manuscript.tex
update and comments

\documentclass[,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Moral Foundations of U.S. Political News Organizations},
            pdfauthor={William E. Padfield~\& Erin M. Buchanan, Ph.D.},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Moral Foundations of U.S. Political News Organizations}
    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan,
Ph.D.\textsuperscript{1}}
    \date{}

\shorttitle{MORAL NEWS}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Missouri State University}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to William E.
Padfield, 901 S. National Ave, Springfield, MO, 65897. E-mail:
\href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}

\abstract{
Enter abstract here. Each new line herein must be indented, like this
line.

}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

Something clever to start

\#\#Moral Foundations Theory

Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a
method by which to capture the entirety of humans' moral domain. The
researchers argued older theories of moral psychology were focused
primarly on issues of justice, fairness, and caring - indvidually
focused foundations of morality that align with the beliefs of political
liberals ({\textbf{???}}). In other words, moral psychology ignored the
valid moral foundations of conservatives. Moral Foundations Theory (MFT)
holds that people's moral domain can be mapped by quantifying their
endorsement of five moral foundations: \emph{harm/care},
\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
\emph{authority/respect}, and \emph{purity/sanctity} ({\textbf{???}}).

The researchers settled on these specific foundations after the
completion of a literature survey of research in anthropology and
evolutionary psychology ({\textbf{???}}). \emph{LET'S CHECK THIS
CITATION IN MENDELEY}!.The first two foundations (\emph{harm/care} and
\emph{fairness/reciprocity}) are termed the \enquote{individualizing
foundations,} as they are centered on the concerns of individuals rather
than groups. \emph{Harm/care} represents an endorsement of compassion
and kindness, while opposing cruelty and harm.
\emph{Fairness/reciprocity} represents concerns centered on guaranteeing
individual rights as well as justice and equality among all people. The
other three foundations (\emph{ingroup/loyalty},
\emph{authority/respct}, and \emph{purity/sanctity}) are the
\enquote{binding} foundations, owing to their focus on group-related
concerns, rather than those of individuals. \emph{Ingroup/loyalty}
represents endorsements of patriotism and heroism and discourages
nonconformity and dissent. \emph{Authority/respect} represents an
endorsement of social hierarchies and traditions while denigrating
disobedience. Finally, \emph{purity/sanctity} represents concerns
regarding chastity and piety, while discouraging vices and indulgences,
including lust, avarice, and gluttony ({\textbf{???}}). Liberals tend to
endorse the individualizing foundations more than conservatives.
Endorsements for the three binding foundations, however, are lower than
conservatives. Conservatives, on the other hand, tend to endorse all
five foundations equally, implying they base judments (at least
partially) on each foundation ({\textbf{???}}).

\#\#Moral Foundations Dictionary

In order to capture language's role in moral and political reasoning,
({\textbf{???}}) formulated the Moral Foundations Dictionary (MFD) in
order to capture moral reasoning and justification as used in speech and
text. The MFD is composed of 259 words, with around 50 words assigned to
each of the five foundations. The researchers created a preliminary list
of words that they believed would be associated with the five
foundations. Then, using the Linguistic Inquiry and Word Count (LIWC;
{\textbf{???}}) computer program, they analyzed transcripts of liberal
and conservative Christian sermons in order to obtain frequencies of the
occurrence of words from the researchers' initial list. The researchers
manually checked the results from LIWC in order to make sure the results
make sense given the contexts and rhetorical devices used in the
sermons. Similar to previous research on Moral Foundations Theory,
liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup}
words more often than conservative ministers. Conversely, conservative
ministers used \emph{authority} and \emph{purity} words more often than
liberal ministers. However, conservative ministers did not use
\emph{ingroup/loyalty} words more than liberals. Rather, liberal
ministers used words pertaining to \emph{ingroup/loyalty}, but in
contexts that promote rebellion and independence - causes
\emph{opposite} to positive endorsements of that foundation
({\textbf{???}}).

To this point, most text analysis utilizing the Moral Foundations
Dictionary operationalizes endorsement of any one of the foundations as
percent occurence of words from the foundation's respective word list.
As such, most analyses assume that zero percent occurence is indicative
of no endorsement, while any non-zero percent occurence indicates
endorsement of the foundation. This may not be sufficient in describing
the true nature of the writer or speaker's endorsement of one of the
sets of moral intuitions. A quick glance at the MFD words for
\emph{harm/care} reveals the presence of words that are more closely
associated with universally accepted conceptions of \emph{harm} over
\emph{care} and vice-versa ({\textbf{???}}). For example, the word
\enquote{cruel} has relatively negative connotations compared to
\enquote{benefit.} For the \emph{harm/care} foundation, it is
conceivable that use of the word \enquote{cruel} might indicate a
greater attentional focus of the idea of \emph{harm} rather than
\emph{care}.

For \emph{harm/care}, the definition of the foundation as well as its
name clearly distinguishes between two somewhat opposite sides of an
attentional continuum, with \emph{harm} on the negative end and
\emph{care} on the positive side. In other words, the entries in the MFD
for \emph{harm/care} have somewhat clear positive and negative valences.
The same pattern can be seen in the MFD entries for the other four
foundations. \emph{Purity/sanctity} features words that likely have a
negative valence to most observers, including \enquote{disease}" and
\enquote{trash,} along with more positive words, including
\enquote{right} and \enquote{sacred} ({\textbf{???}}). This, however,
brings up other questions regarding the definition and names of the
other four foundations apart from \emph{harm/care}:
\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
\emph{authority/respect}, and \emph{purity/sanctity}. The latter four
foudnations have names that are harder to understand as a valence
continuum, as the concepts in the names are more similar, even to the
point of being virtually synonymous in the case of
\emph{fairness/reciprocity}.

When considering the issue of positive versus negative valence in MFD
words, the question of how texts are analyzed vis-a-vis the MFD remains.
How can raw percentage of MFD word occurence capture the valence and
focus of the writer or speaker? If 2\% of a politician's speech features
positive words (i.e. \enquote{benefit} and \enquote{defend}) from the
MFD \emph{harm/care} list, how can researchers be sure the level and
nature of the speaker's \enquote{endorsement} of the foundation equals
that of another politician whose speech contained negatively connoted
MFD words from the \emph{harm/care} list? They would have equal
endorsements as far as the numbers are concerned, but the words used and
focus given are on opposite sides of the \emph{harm/care} spectrum.

This issue is compounded by the fact the Moral Foundations Questionnaire
(MFQ) and its subscales assume endorsement lies on a continuum. One item
under the \emph{fairness/reciprocity} judgment subscale reads,
\enquote{Justice is the most important requirement for a society}
({\textbf{???}}). The survey respondent must select a number on a scale
from 1 to 6 indicating responses spanning \enquote{strongly disagree} at
1 to \enquote{strongly agree} at 6. While the scales in the MFQ do not
represent true valence as it pertains to individual words, it does allow
for a greater degree of specificity in terms of an individual's
endorsement of a particular moral foundation. When a respondent selects
a 4 for the aforementioned MFQ statement, they clearly are indicating
they \enquote{slightly agree} with the statement ({\textbf{???}}). This
specificity is not present in most analyses involving the MFD and
percent occurence, unless they also take into account the valence of the
words used in the text or speech of interest.

\#\#Valence

Borrowing from Osgood's work in the 1950s, ({\textbf{???}}) recognized
valence as one of three related dimensions comprising emotion when
developing their Affective Norms for English Words (ANEW). As mentioned
before, \enquote{valence,} the first dimension, denotes the pleasantness
of a given word. \enquote{Arousal,} the second dimension, describes the
stimulating nature of a word. Lastly, \enquote{dominance} or
\enquote{control} describes the extent to which a word makes one feel in
or out of control ({\textbf{???}}). The researchers developed ANEW by
presenting participants with a list of 100-150 words and asking for them
to rate the word on all three dimensions using the Self-Assessment
Mannikin (SAM), which allows ratings along either a nine-point scale
when using traditional paper instruments or a twenty-point scale when
using a computerized version.

Participants saw the stimulus word and responded on each scale. The
valence scale featured a smiling figure at one end (representing
pleasantness) and a frowning figure at the other end (for
unpleasantness). The arousal scale had a \enquote{wide-eyed} figure at
one end with a sleepy figure at the other, representing stimulating and
unstimulating respectively. Finally, the control scale featured a large
figure, indicating the highest degree of control, at one end and a small
figure, indicating a lack of control, at the other end ({\textbf{???}}).
The end result of this procedure yielded affective norms along the three
dimensions for 1,040 English words ({\textbf{???}}). ANEW represented an
important first step in establishing affective norms for large numbers
of English words. However, later researchers found the 1,040-word list
to be limiting for a language consisting of thousands of words.

({\textbf{???}}) exponentially lengthened the list of words with
affective norms to 13,915 English lemmas, the base forms of words
without inflection (i.e. \enquote{watch} rather than \enquote{watched}
and \enquote{watching}). The researchers recognized the importance of
affective norms in several areas of study, including emotion, language
processing, and memory ({\textbf{???}}). They argue the list of words
included in ANEW is sufficient for small-scale factorial research
designs, but the list is \enquote{prohibitively small} for larger-scale
\enquote{megastudies} that are common in psycholinguistic research today
({\textbf{???}}).

In order to source a large number of lemmas for affective ratings, the
researchers drew from several validated sources. These include the
30,000 lemmas with age-of-acquisition (average age at which a particular
word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and
Brysbaert as well as the content lemmas from the SUBTLEX-US corpus
consisiting of subtitles from various forms of visual media
({\textbf{???}}). This resulted in the final list of 13,915 lemmas.
Lists of 346-350 words were presented to participants recruited through
the Amazon Mechanical Turk subject pool. Particpants rated the words
along one of the three dimensions, unlike the ANEW project in which
participants rated each word along all three dimensions at once. The
researchers used a nine-point scale similar to the one used by
({\textbf{???}}) when collecting ratings for ANEW ({\textbf{???}}).

The researchers noted several points of interest upon observing ratings.
First, they found that valence and dominance ratings had a negative
skew, indicating more words elicited feelings of happiness and control
than their respective opposites. Also, when examining the relationship
between valence and arousal ratings, the researchers found a U-shaped
relationship. This indicates words with high degrees of positivity and
negativity elicited higher arousal ({\textbf{???}}). These observations
along with the now-greatly expanded list of affective norms has been
applied to several lines of inquiry in psycholinguistics.

({\textbf{???}}) utilized the new affective norms list in order to
investigate the validity of the Pollyanna hypothesis, or the prevalence
of a generally optimistic outlook in humans as reflected in langauge.
The researchers were able to conclude the existence of a greater number
of positive-valence English words in the list of 13,915 lemmas.
Additionally, after observing token frequency in a number of text
corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers
found that words with postive valence were also used more frequently
({\textbf{???}}). While the researchers concede the possiblility of an
acquiensence bias in ratings as a possible explanation for the observed
positivity bias, this investigation represents one application of the
({\textbf{???}}) list in emotional studies.

One cognition-based study investigates the relationship between emotion
and response latencies in word recognition. ({\textbf{???}}) sought to
use the ({\textbf{???}}) norms to fill in the knowledge gaps regarding
variance in word recognition. The researchers drew several conclusions
regarding emotion and word recognition (specifically in naming and
lexical decision tasks). First, ({\textbf{???}}) found higher response
latencies in negative-valence words, lower response latencies in neutral
words, and even lower response latencies in words with positive valence.
The researchers also concluded that words causing higher arousal tend to
have higher response latencies than less-arousing words. They found
valence had a stronger effect on recognition than arousal (both effects
were independent, not interactive). They found an interaction between
emotion and word frequency such that valence and arousal are more
effective on lower frequency words than high frequency words. Finally,
({\textbf{???}}) found a greater effect for lexical decision tasks than
for naming tasks. This research serves as further evidence that the
({\textbf{???}}) list can be used for research inquiries both within and
without the field of psycholinguistics.

In the present studies, the researchers used the 2013 Warriner list in
order to denote the valence of the words appearing in the news articles
scraped from the internet. Valence was considered as another independent
variable and its relationship with the words comprising the Moral
Foundations Dictionary were of chief interest to the researchers. The
valence was used as a means to determine whether individiual words in
the MFD represented more positive aspects of their respective foundation
or if they denoted a more negative aspect of the foundation.
Incorporating word valence into a study involving the MFD is meant to
alleviate some of the issues regarding the aforementioned ambiguity
regarding the words in the Moral Foundations Dictionary.

\hypertarget{news-media-and-politics}{%
\subsection{News Media and Politics}\label{news-media-and-politics}}

Research into politics, language, and media has illuminated the complex
relationships between all three. Any politically-oriented discussion of
word occurence as an implication of moral or poltical position assumes
that langauge and ideology are intrisincally linked. Deborah Cameron
({\textbf{???}}) points out the expressive nature of ideological beliefs
and how that expression is conveyed through langauge, thus implying a
connection between ideology and language. She goes on to criticize the
notion that language is either the \enquote{pre-existing raw material}
used to shape ideologies or the \enquote{post-hoc vehicle} for their
propogation. Rather, the structure of language itself is shaped by
ideology and social processes even when it is used to explain or express
ideologies ({\textbf{???}}).

The use of language both to express and further an ideological goal has
been documented in the techniques employed by candidates for political
office in the U.S. For example, Druckman, Jacobs, and Ostermeier
(({\textbf{???}})) investigated issue and image priming on the part of
candidates as implied by the disproportionate attention candidates paid
to particular issues over others. In their research, the authors
consider \enquote{issues} as communication that attmepts to persuade
constituents to vote for the candidates based on their strengths in
matters of public policy. \enquote{Image} priming, on the other hand,
describes techniques deployed in order to sway votes based on favorable
aspects of the candidate's behavior and personality ({\textbf{???}}).
The researchers found numerous examples of issue and image priming
during the 1972 re-election campaign of Richard Nixon. They linked the
Nixon adminstration's awareness of the issues for which the president
had public support to the issues he should emphasize (and prime) during
the campaign. Likewise the researchers found evidence that Nixon's team
was aware of negative evaluations of his warmth and trustworthiness, and
thus took steps to prime his purportedly positive qualities, including
strength and competence ({\textbf{???}}).

({\textbf{???}}) also cited research from Iyengar and Kinder (1987)
suggesting the news media affected perceptions of President Jimmy
Carter's competence by emphasizing (read: priming) issues related to
energy, defense, and the economy. This implies news media may affect
perception of politicians based on where the media places emphasis.
Other research into news media suggests certain media outlets, at least
indirectly, may have an effect on the voting records of representatives
in Congress ({\textbf{???}}). Specifically, the researchers identified a
pattern of declining support for President Bill Clinton's policies
chiefly among Republicans in the House of Representatives after the Fox
News Channel began broadcasting on cable and satellite systems in their
respective districts. As Fox News was, at the time of its launch in
1996, the only outwardly ideological national news network, the
reserachers were able to track its spread across the country and observe
voting records of members of Congress both before and after Fox News'
arrival ({\textbf{???}}). The researchers concluded that members of
Congress, excluding those newly elected at the time of Fox News
Channel's emergence, attempted to anticipate resultant
conservative-leaning shifts among their constituents by bolstering their
conservative voting record before the next election ({\textbf{???}}).

Talk about political discourse, nature of news media in 2018/Trump
era/Kavanaugh

This project brings the two together in holy matrimony.

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{sources}{%
\subsection{Sources}\label{sources}}

Political articles were scraped from the websites of four notable U.S.
news sources. The sources were \emph{The New York Times}, \emph{National
Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}. They were
selected for their widespread recognition and the fact they are easily
categorized (by the general public) according to perceived political
lean. In general, \emph{The New York Times} and \emph{NPR} are perceived
by many to have a liberal bias or lean. In contrast, Fox News and
Breitbart are believed to have a conservative bias or lean. Political
articles in particular were identified and subsequently scraped by
including the specific URL directing to each source's political content
in the \emph{R} script. For example, rather than scrape from
nytimes.com, which would return undesired results (non-political
features, reviews, etc.), we instead included
nytimes.com/section/politics so that more or less exclusively political
content was obtained. All code for this manuscript can be found at OSF
LINK, and the scripts are provided inline with this manuscript written
with the \emph{papaja} library ({\textbf{???}}).

Identification of the sources' political URLs presented a problem for
two of the sources owing to complications with how their particular
sites were structured. While in the multi-week process of scraping
articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were
not growing at a similar pace as those from \emph{The New York Times}
and \emph{Breitbart}. Upon investigation, we found another, more robust
URL for political content from NPR: their politics content
\enquote{archive.} The page structure on NPR's website was such that
only a limited selection of articles is displayed to the user at a given
time. Scraping both the archive and the normal politics page ensured we
were obtaining most (if not all) new articles as they were published. We
later ran a process in order to exclude any duplicate articles.
\emph{Fox News} presented a similar issue. We discovered \emph{Fox News}
utilized six URLs in addition to the regular politics page. These URLs
led to pages containing content pertaining the U.S. Executive Branch,
Senate, House of Representatives, Judicial Branch, foreign policy, and
elections. Once again, duplicates were subsequently eliminated from any
analyses.

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

Using the \emph{rvest} library in the statistical package \emph{R}, we
pulled body text for individual articles from each of the aforementioned
sources (identified using CSS language) and compiled them into a dataset
({\textbf{???}}). Using this dataset, we identified word count and
average word count per source. This process was run once daily starting
on \emph{DATE} until \emph{DATE.} Starting on \emph{DATE,} the process
was run twice daily - once in the morning and again in the evening. Data
collection was terminated once 250,000 words per source was collected on
\emph{DATE.}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

Once data collection ended, the text was scanned using the \emph{ngram}
package in \emph{R} ({\textbf{???}}). This package includes a word count
function, which was used to remove articles that came through as blank
text, as well as to eliminate text picked up from the Disqus commenting
system used by certain websites. At this point, duplicate articles were
discarded.

Using the ({\textbf{???}}) dictionary, the words making up each of the
five foundations in the MFD were assigned their respective valence
value. Once the MFD words' valences were added to the dataset, the
article text was processed using the \emph{tm} and \emph{ngram} packages
in \emph{R} in order to render the text in lowercase, remove
punctuation, and fix spacing issues ({\textbf{???}}). The individual
words were then reduced to their stems (i.e., \emph{abused} was stemmed
to \emph{abus}). The same procedure was applied to the MFD words and the
words in the ({\textbf{???}}) dataset.

DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that
project were imported and added to each foundation, with reduncies
removed at the end.

The source article words were compiled into a dataset where they were
matched up with their counterparts in the MFD along with their valence
and a percentage of their occurrence. Therefore, for each article, the
percentage of the number of \emph{harm/care} words occurring in the
articles were calculated, and this process was repeated for each of the
foundations. This procedure created five percentages that were included
as the dependent variable for the following analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

To analyze if news sources adhered to differences in word use based on
their target audience, we utilized a multilevel model (MLM) to analyze
the data. MLM is a regression technique that allows one to control for
the repeated measurement and nested structured of the data, which
creates correlated error ({\textbf{???}}). Using the \emph{nlme} library
in \emph{R} ({\textbf{???}}), each foundation's weighted percentage was
predicated by the political lean of the news soource, using the
individual news sources as a random intercept to control for the
structure of the data.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

\#\#Kavanaugh Supreme Court Hearing

In the wake of Justice Anthony Kennedy's retirement from the Supreme
Court of the United States, President Donald Trump nominated Brett
Kavanaugh as the new Associate Justice. Kavanaugh was previously on the
U.S. Court of Appeals for the District of Columbia. The Senate Judiciary
Committee began his confirmation hearing on September 4, 2018
({\textbf{???}}). Following allegations of sexual assault by high school
classmate Dr.~Christine Blasey Ford, the committee postponed its vote on
whether or not to open the confirmation to the entire Senate.

On September 27, the committee questioned Dr.~Ford before commencing a
second round of questioning for Judge Kavanaugh ({\textbf{???}}). During
the intervening weeks between hearings, two more women came forward with
two separate allegations of sexual assault on the part of Kavanaugh.
According to Nielsen reports, more than 20 million people watched the
September 27 proceedings on television ({\textbf{???}}). This figure
does not take into account viewers who watched online, nor does it
account for viewers outside the United States. On September 28, the
Senate Judiciary Committee voted to send the nomination to the Senate
floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long
FBI investigation on Kavanaugh and the allegations facing him, which the
committee, and later the President, approved. The investigation
concluded with no significant findings. The Senate voted 50-48 to
approve Kavanaugh's appointment on October 6, 2018 ({\textbf{???}}).

The Kavanaugh nomination, confirmation hearing, and eventual
swearing-in, as well as the news media's coverage of all three events,
feature many moral dimensions that likely differ depending on one's
morals. On one side of the debate, Kavanaugh's Supreme Court tenure
presents a prime oppurtunity to bring morality back into interpretation
of the Constitution. Kavanaugh's confirmation creates a conservative
stronghold among the justices on the court. Commentators have noted this
might help advance a judicial agenda that backpedals certain rights
previously upheld by the Supreme Court, including abortion and gay
marriage - social issues challenged by their opponents at least
partially on moral grounds. On the other side of the debate, the assault
allegations have energized Kavanaugh's opponents to advocate for his
rejection from the court owing to misdeeds resulting from Kavanaugh's
own alleged lack of morals. Additionally, the moral duty of the Senate
as the upper chamber in the U.S. legislature has been scrutinized in
public discourse with respect to its handling of the assualt allegations
vis-a-vis Kavanaugh's confirmation.

\hypertarget{method-1}{%
\section{Method}\label{method-1}}

\hypertarget{sources-1}{%
\subsection{Sources}\label{sources-1}}

Experiment 2 largely followed the same method as Experiment 1. Political
articles specifically referring to Brett Kavanaugh and his Supreme Court
confirmation hearing were scraped

\hypertarget{materials-1}{%
\subsection{Materials}\label{materials-1}}

Expected material stuff - we are going to pick liberal and conservative
sources from that thing document linked stuff - list those here: Sources
used by LIBERALS (according to the document thing): The New Yorker Slate
The Daily Show (is it wise to use satirical news for this??) The
Guardian Al Jazeera America NPR New York Times Buzzfeed PBS BBC
Huffington Post Washington Post The Economist Politico MSNBC CNN NBC
News CBS News Google News Bloomberg ABC News USA TODAY

Sources used by CONSERVATIVES: Fox News Drudge Report Breitbart Rush
Limbaugh Show The Blaze Sean Hannity Glenn Beck (does he still report
\enquote{news}??)

\begin{itemize}
\tightlist
\item
  pick a specific date range we want to pull articles from
\item
  list that here:
\end{itemize}

START DATE: September 13, 2018

(September 27, 2018: Ford and Kavanaugh testimony before Senate
Judiciary Committee)

END DATE: October 11, 2018

here's when the stuff was happening and so picked two weeks before and
after

\hypertarget{data-analysis-1}{%
\subsection{Data analysis}\label{data-analysis-1}}

How you would run the data analysis

\hypertarget{experiment-2-results}{%
\section{Experiment 2 results}\label{experiment-2-results}}

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

How it turned out

Limitations of this one (no rationale behind choosing sources except
\enquote{people say NPR's liberal??})

What to do for future project (focus on one MF? Different sources? More
sources?)

Argue: why is still a good thing to study?? (probably something about
current state of discourse, information, truth, \enquote{alternative
facts,} subjective reality - philosophical stuff)

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}

\endgroup

\end{document}

### 2018-12-04 pilot_manuscript.Rmd
update and comments
updated the reference

@@
 
-##Moral Foundations Theory
+## Moral Foundations Theory
 
@@
 
-The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@GILLIGAN1991].
-*LET'S CHECK THIS CITATION IN MENDELEY*!.The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
+The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
 *Harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm.
@@
 
-##Moral Foundations Dictionary
+## Moral Foundations Dictionary
 
@@
 
-##Valence
+## Valence
 
@@
 
-##Kavanaugh Supreme Court Hearing
+## Kavanaugh Supreme Court Hearing
 

### 2018-12-04 pilot_manuscript.Rmd
i don't know what i did

@@
 This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@GILLIGAN1991].
+One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@Graham2011].
 The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning "strongly disagree" at 1 to "strongly agree" at 6.
 While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
-When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@GILLIGAN1991].
+When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@Graham2011].
 This specificity is not present in most analyses involving the MFD and percent occurence, unless they also take into account the valence of the words used in the text or speech of interest.
@@
 This procedure created five percentages that were included as the dependent variable for the following analyses.
+
 ```{r stem_text, eval=TRUE, include=FALSE}
@@
 tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
+
+apa_table(tableprint,
+          note = "something useful here",
+          caption = "stuff at the top", 
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 7))
+          )
 ```

### 2018-12-04 pilot_manuscript.tex
i don't know what i did

@@
 
-\#\#Moral Foundations Theory
+\hypertarget{moral-foundations-theory}{%
+\subsection{Moral Foundations Theory}\label{moral-foundations-theory}}
 
@@
 completion of a literature survey of research in anthropology and
-evolutionary psychology ({\textbf{???}}). \emph{LET'S CHECK THIS
-CITATION IN MENDELEY}!.The first two foundations (\emph{harm/care} and
-\emph{fairness/reciprocity}) are termed the \enquote{individualizing
-foundations,} as they are centered on the concerns of individuals rather
-than groups. \emph{Harm/care} represents an endorsement of compassion
-and kindness, while opposing cruelty and harm.
-\emph{Fairness/reciprocity} represents concerns centered on guaranteeing
-individual rights as well as justice and equality among all people. The
-other three foundations (\emph{ingroup/loyalty},
+evolutionary psychology ({\textbf{???}}).The first two foundations
+(\emph{harm/care} and \emph{fairness/reciprocity}) are termed the
+\enquote{individualizing foundations,} as they are centered on the
+concerns of individuals rather than groups. \emph{Harm/care} represents
+an endorsement of compassion and kindness, while opposing cruelty and
+harm. \emph{Fairness/reciprocity} represents concerns centered on
+guaranteeing individual rights as well as justice and equality among all
+people. The other three foundations (\emph{ingroup/loyalty},
 \emph{authority/respct}, and \emph{purity/sanctity}) are the
@@
 
-\#\#Moral Foundations Dictionary
+\hypertarget{moral-foundations-dictionary}{%
+\subsection{Moral Foundations
+Dictionary}\label{moral-foundations-dictionary}}
 
@@
 
-\#\#Valence
+\hypertarget{valence}{%
+\subsection{Valence}\label{valence}}
 
@@
 
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp1-table}stuff at the top}
+\begin{tabular}{lccccccc}
+\toprule
+Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+\midrule
+Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .850 & 0.01\\
+Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .715 & 0.02\\
+Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .789 & -0.04\\
+Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.17 & .087 & -0.20\\
+Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.37 & .141 & -0.09\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} something useful here}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
 \hypertarget{discussion}{%
@@
 
-\#\#Kavanaugh Supreme Court Hearing
+\hypertarget{kavanaugh-supreme-court-hearing}{%
+\subsection{Kavanaugh Supreme Court
+Hearing}\label{kavanaugh-supreme-court-hearing}}
 

### 2018-12-17 pilot_manuscript.Rmd
Upadated intro text to reflect comments

@@
 
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain.
+Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007].
 The researchers argued older theories of moral psychology were focused primarly on issues of justice, fairness, and caring - indvidually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
@@
 
-The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
+The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].
+The researchers attempted to locate virtues and morals corresponding to "evolutionary thinking." For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the *fairness/reciprocity* foundation.
+Additionally, evolutionary literature on disgust and its correlation to human behavior regarding food and sex informed the *purity/sanctity* foundation [@Graham2011].
+The researchers identified the five "top candidates" for the foundations of human cultures' morality [@Graham2011].
+
+The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
 *Harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm.
@@
 Liberals tend to endorse the individualizing foundations more than conservatives.
-Endorsements for the three binding foundations, however, are lower than conservatives.
-Conservatives, on the other hand, tend to endorse all five foundations equally, implying they base judments (at least partially) on each foundation [@Graham2009].
+Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
+It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judments on all foundations [@Graham2009].
 
@@
 The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
+The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguious statements requiring human verification: "Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus" [@Graham2009].
+This sentence added to the *authority/respect* total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
+The researchers eliminated this sentence from the *authority/respect* raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions [@Graham2009].
+
 Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
@@
 
-To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurence of words from the foundation's respective word list.
+To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurence of words in a given text from the foundation's respective word list.
 As such, most analyses assume that zero percent occurence is indicative of no endorsement, while any non-zero percent occurence indicates endorsement of the foundation.
-This may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
+This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
 A quick glance at the MFD words for *harm/care* reveals the presence of words that are more closely associated with universally accepted conceptions of *harm* over *care* and vice-versa [@Graham2009].
@@
 
-For *harm/care*, the definition of the foundation as well as its name clearly distinguishes between two somewhat opposite sides of an attentional continuum, with *harm* on the negative end and *care* on the positive side.
+For *harm/care*, the definition of the foundation, as well as its name, clearly distinguishes between two somewhat opposite sides of an attentional continuum, with *harm* on the negative end and *care* on the positive side.
 In other words, the entries in the MFD for *harm/care* have somewhat clear positive and negative valences.
@@
 *Purity/sanctity* features words that likely have a negative valence to most observers, including "disease"" and "trash," along with more positive words, including "right" and "sacred" [@Graham2009].
-This, however, brings up other questions regarding the definition and names of the other four foundations apart from *harm/care*: *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*.
+These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from *harm/care*: *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*.
 The latter four foudnations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of *fairness/reciprocity*.
@@
 This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
+The Moral Foundations Questionnaire (MFQ) measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
+The quesionnaire is made up of judgment items and relevance items.
+Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
+An example of such a statement reads: “It can never be right to kill another human being” [@Graham2011].
+Relevance items gauge the respondent's opinion regarding the importance of foundation-related concerns.
+For example, the respondent is directed to rate how important the following situation is to their sense of morals: "whether or not someone did something disgusting." This example measures the relevance of the *purity/sanctity* foundations.
+Each foundation has a judgment and relevance subscale, totalling 10 subscales for the MFQ [@Graham2011].
+
+The aforementioned ambiguity of the Moral Foundations Dictionary as an instrument becomes clearer upon closer examination of the items in the Moral Foundations Questionnaire.
 One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@Graham2011].
@@
 In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert as well as the content lemmas from the SUBTLEX-US corpus consisiting of subtitles from various forms of visual media [@Warriner2013].
-This resulted in the final list of 13,915 lemmas.
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by @Kuperman2012 as well as the content lemmas from the SUBTLEX-US corpus consisiting of subtitles from various forms of visual media [@Warriner2013].
+This data collection resulted in the final list of 13,915 lemmas.
 Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
@@
 
+In addition to applications in emotion research, the Warriner norms [-@Warriner2013] have been utilized in cognitive research as well.
 One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
@@
 The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
-First, @Kuperman2014 found higher response latencies in negative-valence words, lower response latencies in neutral words, and even lower response latencies in words with positive valence.
-The researchers also concluded that words causing higher arousal tend to have higher response latencies than less-arousing words.
+First, @Kuperman2014 found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
+The researchers also concluded that words causing higher arousal tend to have slower decision times than less-arousing words.
 They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
 They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
-Finally, @Kuperman2014 found a greater effect for lexical decision tasks than for naming tasks.
+Finally, @Kuperman2014 found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks [@Kuperman2014].
 This research serves as further evidence that the @Warriner2014 list can be used for research inquiries both within and without the field of psycholinguistics.
 
-In the present studies, the researchers used the 2013 Warriner list in order to denote the valence of the words appearing in the news articles scraped from the internet.
+In the present studies, the researchers used the @Warriner2013 list in order to denote the valence of the words appearing in the news articles scraped from the internet.
 Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
@@
 Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies [@Cameron2006].
+Owing to the fact the Moral Foundations Dictionary was developed in order to assess the moral, which includes the ideological, orientation of discourse, its purported ability to assess parts of the structure of language (vocabulary) for ideological lean is of chief interest to the researchers in the present study.
 
 The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S.
-For example, Druckman, Jacobs, and Ostermeier (-@Druckman2004) investigated issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
-In their research, the authors consider "issues" as communication that attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-"Image" priming, on the other hand, describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].
+Druckman, Jacobs, and Ostermeier (-@Druckman2004) considered political "issues" as communication that attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
+According to the researhcers, "image" priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
 The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
@@
 
-@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy.
-This implies news media may affect perception of politicians based on where the media places emphasis.
+@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.
+priming) issues related to energy, defense, and the economy.
+This focus implies news media may affect perception of politicians based on where the media places emphasis.
 Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014].
@@
 legislature has been scrutinized in public discourse with respect to its handling of the assualt allegations vis-a-vis Kavanaugh's confirmation.
+
+For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on the Kavanaugh confirmation hearing.
+News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
 

### 2018-12-22 pilot_manuscript.Rmd
Added moral psych overview to intro

@@
 
-Something clever to start
+Morality is prevalent/important
+
+Domain of philosophers
+
+Then psychologists (more on that later)
+
+Btw, it's intrinsically linked with politics
+
+Lots of partisan media choices today = different appeals to audience's moral concerns?
 
 ## Moral Foundations Theory
+
+As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg [@Haidt2007].
+Kohlberg's research popularized his theory of the devlopment of moral reasoning.
+This theory establishes the steps of moral reasoning through which humans proceed as they mature.
+Kohlberg borrwowed from Jean Piaget's stages of cognitive devlopment in which children progress from the sensorimotor through to the formal operations stage [@Haidt2007].
+Similarly, Kohlberg found people typcially start with a "pre-conventional" understanding of morality during infancy and progress through several steps until they reach a "post-conventional" ethics [@Haidt2007].
+People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice.
+From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality [@Haidt2007].
+This view persisted until it encountered criticism in the early 1980s.
+
+Kohlberg's conception of morality faced major scrutiny from psycholgist Carol Gilligan.
+In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women [@Haidt2007].
+She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
+Gilligan thus asserted morality was built upon an alternative moral foundation: caring [@Haidt2007].
+This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring [@Haidt2007].
+While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
+
+In their brief overview of the history of moral psychology, @Graham2009 explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
+Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
+Such a system, they argued, did not account for moral concerns outside of the western world [@Graham2009].
+Individually focused concerns can be grouped under an overarching "ethic of autonomy," which was thought to be one of three ethics upon which humans base moral decisions.
+The other two ethics were the "ethic of community" (comprising one's duty to their family, tribe, etc.) and the "ethic of divinity"" - representing one's duty not to defile their God-given body and soul [@Graham2009].
+In the 2000s, @Haidt2007 took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
 
@@
 This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The Moral Foundations Questionnaire (MFQ) measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
+The Moral Foundations Questionnaire (MFQ), which was developed subsequent to the MFD, measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
 The quesionnaire is made up of judgment items and relevance items.

### 2018-12-23 pilot_manuscript.Rmd
more intro before i got tired :/

@@
 
-Morality is prevalent/important
+In the United States, today's media landscape affords consumers a multitude of options for obtaining political news.
+Since the advent of cable news networks and the World Wide Web in the last decades of the twentieth century, consumers have gained access to an ever-expanding menagerie of news sources, many of which can be called up via a simple click, touch, or swipe.
+Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
+For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant respectively.
+These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
+In a media environment where consumers are fed news content that algorithms predict they will like (based on user-generated data) in addition to cable news, there exists the possibility consumers only see news content that comports to their worldview.
+
+Btw, morality is intrinsically linked with politics; i.e. Morality is prevalent/important
 
@@
 Then psychologists (more on that later)
-
-Btw, it's intrinsically linked with politics
-
-Lots of partisan media choices today = different appeals to audience's moral concerns?
 

### 2018-12-28 pilot_manuscript.Rmd
intro and responded to comments

@@
 These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
-In a media environment where consumers are fed news content that algorithms predict they will like (based on user-generated data) in addition to cable news, there exists the possibility consumers only see news content that comports to their worldview.
-
-Btw, morality is intrinsically linked with politics; i.e. Morality is prevalent/important
-
-Domain of philosophers
-
-Then psychologists (more on that later)
+Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
+Specifically, the use of differing moral language in political articales might be an indicator of political bias in news media.
+
+Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
+Starting in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
+Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
+As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." This remains an issue in the field during the twenty-first century as researchers begin to infer moral and political leanings from text and speech.
 
@@
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
-
-Talk about political discourse, nature of news media in 2018/Trump era/Kavanaugh
-
-This project brings the two together in holy matrimony.
 
@@
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
+The reasearchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks Kavanaugh's confirmation was prominent in the news.
+The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
 

### 2019-01-01 pilot_manuscript.Rmd
More in Exp1 Method and chose sources!

@@
 # Method
+For Experiment 1, the researchers approached the methodology with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework.
+The researchers hypothesized the news sources genrally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
+Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
 
@@
 In general, *The New York Times* and *NPR* are perceived by many to have a liberal bias or lean.
-In contrast, Fox News and Breitbart are believed to have a conservative bias or lean.
+In contrast, Fox News and Breitbart are believed to have a conservative bias or lean [@Mitchell2014].
 Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
@@
 
-Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value.
-Once the MFD words' valences were added to the dataset, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
+The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
 The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
 The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
+Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value.
 
@@
 This procedure created five percentages that were included as the dependent variable for the following analyses.
+It should be noted the valence scores for the MFD words were *z*-scored, so negative valence scores are possible.
 
@@
 
+In contrast to Experiment 1, the reserachers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scaped text as well as for any inferences drawn from the analyses.
 For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on the Kavanaugh confirmation hearing.
@@
 - list those here:
-  Sources used by LIBERALS (according to the document thing):
-  The New Yorker
+  Sources used by LIBERALS:
+  MSNBC
   Slate
-  The Daily Show (is it wise to use satirical news for this??)
-  The Guardian
-  Al Jazeera America
+  Huffington Post
   NPR
   New York Times
+  Politico
+
+  Sources used by CONSERVATIVES:
+  Fox News
+  Drudge Report
+  Breitbart
+  Rush Limbaugh Show
+  The Blaze
+  Sean Hannity
+
+  DROPPED:
+  Glenn Beck (does he still report "news"??)
+  The Daily Show (is it wise to use satirical news for this??) - Answer = Nope
+  The Guardian (not American)
+  The New Yorker
+  Al Jazeera America
   Buzzfeed
@@
   BBC
-  Huffington Post
   Washington Post
   The Economist
-  Politico
-  MSNBC
   CNN
@@
 
-  Sources used by CONSERVATIVES:
-  Fox News
-  Drudge Report
-  Breitbart
-  Rush Limbaugh Show
-  The Blaze
-  Sean Hannity
-  Glenn Beck (does he still report "news"??)
-
-- pick a specific date range we want to pull articles from 
-- list that here:
-
 START DATE: September 13, 2018

### 2019-01-03 pilot_manuscript.Rmd
Exp1 Results expansion; outline Exp1 discussion

@@
 
+The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
+The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
+Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 1.
+
 ```{r exp1-table, results = 'asis', echo = F}
@@
 # Discussion 
+What we found - nothing really, even some disconfirming evidence, but it wasn't sig and eff size was small.
+
+Why it might not have worked (focus too broad??)
+
+Well, this was exploratory anyway, so lets firm up the method and try another way.
+How about a polarizing and morally-focused singular issue??
+Which leads us to Experiment 2, in which we hope to confirm the method!!
 

### 2019-01-05 pilot_manuscript.Rmd
wrote actual words for Exp1 Discussion

--- 2019-01-01 pilot_manuscript.Rmd
@@
 # Discussion
+
+The results obtained in Experiment 1 did not confirm the hypothesis.
+The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
+The strongest effect found was for the *authority/respect* foundation owing to the fact its Cohen's *d* value was greater than the other four foundations.
+However, the effect was in the opposite direction of that which was hypothesized.
+Specifically, the results indicated that liberal leaning sources demonstrated higher endorsement of that foundation than convservatives.
+This is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
+It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
+
+Upon speculation, the researchers identified one possible reason for why the resuls were unable to confirm the hypothesis.
+The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
+Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language let alone words from the Moral Foundations Dictionary.
+In short, the range of topics covered in Experiment 1 was likely too broad.
+The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
+
+Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
+The researchers identified two primary changes in methodology that were subsequently employed in Experiment 2.
+First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
+Second, the reserachers chose to focus their data collection efforts exclusively on one event in U.S.
+politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
+Supreme Court.
+In Experiment 2, the reserachers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
 

### 2019-01-06 pilot_manuscript.Rmd
Sources and Materials for Exp 2

@@
 ## Sources
-Experiment 2 largely followed the same method as Experiment 1. Political articles specifically referring to Brett Kavanaugh and his Supreme Court confirmation hearing were scraped
+Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
+news sources.
+These sources were selected woting to their favorability among political partisans according to @Mitchell2014.
+The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
+The sources favored by conservatives included *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
+Political articles referencing Brett Kavanaugh's nominatino process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
+All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
 
 ## Materials
+
+Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, *Politico*, *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
+We compiled the articles into a dataset [@CITE_rvest].
+Using this dataset, we identified word count and average word count per source.
+This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
+This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
 
@@
   Fox News
-  Drudge Report
+  Drudge Report *HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK?*
   Breitbart

### 2019-01-12 pilot_manuscript.Rmd
basic data analysis process for Exp2

@@
 
-How you would run the data analysis
+As in Experiment 1, the text was scanned using the *ngram* package in *R* at the conclusion of data collection [@CITE_ngram].
+Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system.
+Duplicate articles were subsequently discarded.
+
+Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@CITE_tm].
+Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).
+Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
+Using the @Warriner2013 dictionary, the words in the MFD were assigned their valence value.
+
+DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
+
+Words from the source article words were then compiled into a dataset where they were paired up with the MFD words (where applicable) as wel as their percent occurrence and valence.
+At the end of this process, the percentage of the number of words from each moral foundation appearing in the articles was computed.
+This procedure created five percentages serving as the dependent variable for the multilevel model.
+Valence scores for the MFD words were *z*-scored, allowing for the possibility of negative valence scores.
 

### 2019-01-12 pilot_manuscript.Rmd
tiny edit :)

@@
 Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
-Starting in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
+Starting chiefly in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
 Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." This remains an issue in the field during the twenty-first century as researchers begin to infer moral and political leanings from text and speech.
+As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." This remains an issue in the field in the twenty-first century as researchers begin to infer moral and political leanings from text and speech.
 

### 2019-01-13 pilot_manuscript.Rmd
changed literally one word

@@
 Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." This remains an issue in the field in the twenty-first century as researchers begin to infer moral and political leanings from text and speech.
+As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." This remains an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
 

### 2019-01-14 pilot_manuscript.Rmd
small updates
just some small things i noticed in our meeting

@@
 ```
+
 # Discussion
@@
 ## Sources
+
 Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.

### 2019-01-17 pilot_manuscript.Rmd
Fixed citations
Not sure what to do for Congressional Record - it's weird

@@
 
-Once data collection ended, the text was scanned using the *ngram* package in *R* [@CITE_ngram].
+Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017].
 This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
@@
 To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@CITE_gelman].
-Using the *nlme* library in *R* [@CITE_nlme], each foundation's weighted percentage was predicated by the political lean of the news soource, using the individual news sources as a random intercept to control for the structure of the data.
+MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
+Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated by the political lean of the news soource, using the individual news sources as a random intercept to control for the structure of the data.
 
@@
 During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@CITE_NIELSEN].
+According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018].
 This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
@@
 Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, *Politico*, *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-We compiled the articles into a dataset [@CITE_rvest].
+We compiled the articles into a dataset [@Wickham2018].
 Using this dataset, we identified word count and average word count per source.
@@
   Sources used by LIBERALS:
-  MSNBC
   Slate
@@
   Fox News
-  Drudge Report *HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK?*
   Breitbart
@@
   USA TODAY
+  Drudge Report *HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK? The answer is NOPE*
+  MSNBC *CLOSEST TO POLITICAL CENTER; buh-bye!*
 
@@
 
-As in Experiment 1, the text was scanned using the *ngram* package in *R* at the conclusion of data collection [@CITE_ngram].
+As in Experiment 1, the text was scanned using the *ngram* package in *R* at the conclusion of data collection [@Schmidt2017].
 Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system.
@@
 
-Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@CITE_tm].
+Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@Feinerer2017].
 Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).

### 2019-01-21 pilot_manuscript.Rmd
updated thesis

@@
   - name          : "Erin M. Buchanan, Ph.D."
-    affiliation   : "1"
+    affiliation   : "2"
 
@@
     institution   : "Missouri State University"
+  - id            : "2"
+    instituation  : "Harrisburg University of Science and Technology"
 
@@
 
-keywords          : "keywords"
-wordcount         : "X"
-
-#bibliography      : ["r-references.bib"] #turn this off right now so it knits
+keywords          : "politics, morality, psycholinguistics"
+
+bibliography      : ["will_thesis.bib"] #turn this off right now so it knits
 
@@
 Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
-Specifically, the use of differing moral language in political articales might be an indicator of political bias in news media.
+Specifically, the use of differing moral language in political articles might be an indicator of political bias in news media.
 
@@
 As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg [@Haidt2007].
-Kohlberg's research popularized his theory of the devlopment of moral reasoning.
+Kohlberg's research popularized his theory of the development of moral reasoning.
 This theory establishes the steps of moral reasoning through which humans proceed as they mature.
-Kohlberg borrwowed from Jean Piaget's stages of cognitive devlopment in which children progress from the sensorimotor through to the formal operations stage [@Haidt2007].
-Similarly, Kohlberg found people typcially start with a "pre-conventional" understanding of morality during infancy and progress through several steps until they reach a "post-conventional" ethics [@Haidt2007].
+Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage [@Haidt2007].
+Similarly, Kohlberg found people typically start with a "pre-conventional" understanding of morality during infancy and progress through several steps until they reach a "post-conventional" ethics [@Haidt2007].
 People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice.
@@
 
-Kohlberg's conception of morality faced major scrutiny from psycholgist Carol Gilligan.
+Kohlberg's conception of morality faced major scrutiny from psychologist Carol Gilligan.
 In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women [@Haidt2007].
@@
 Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007].
-The researchers argued older theories of moral psychology were focused primarly on issues of justice, fairness, and caring - indvidually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
+The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
 In other words, moral psychology ignored the valid moral foundations of conservatives.
@@
 *Fairness/reciprocity* represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
-The other three foundations (*ingroup/loyalty*, *authority/respct*, and *purity/sanctity*) are the "binding" foundations, owing to their focus on group-related concerns, rather than those of individuals.
+The other three foundations (*ingroup/loyalty*, *authority/respect*, and *purity/sanctity*) are the "binding" foundations, owing to their focus on group-related concerns, rather than those of individuals.
 *Ingroup/loyalty* represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
@@
 Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
-It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judments on all foundations [@Graham2009].
+It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations [@Graham2009].
 
@@
 The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
-The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguious statements requiring human verification: "Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus" [@Graham2009].
+The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: "Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus" [@Graham2009].
 This sentence added to the *authority/respect* total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
@@
 
-To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurence of words in a given text from the foundation's respective word list.
-As such, most analyses assume that zero percent occurence is indicative of no endorsement, while any non-zero percent occurence indicates endorsement of the foundation.
+To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurrence of words in a given text from the foundation's respective word list.
+As such, most analyses assume that zero percent occurrence is indicative of no endorsement, while any non-zero percent occurrence indicates endorsement of the foundation.
 This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
@@
 These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from *harm/care*: *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*.
-The latter four foudnations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of *fairness/reciprocity*.
+The latter four foundations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of *fairness/reciprocity*.
 
 When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
-How can raw percentage of MFD word occurence capture the valence and focus of the writer or speaker?
-If 2% of a politician's speech features positive words (i.e.
-"benefit" and "defend") from the MFD *harm/care* list, how can researchers be sure the level and nature of the speaker's "endorsement" of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the *harm/care* list?
+How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
+If 2% of a politician's speech features positive words (i.e., "benefit" and "defend") from the MFD *harm/care* list, how can researchers be sure the level and nature of the speaker's "endorsement" of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the *harm/care* list?
 They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the *harm/care* spectrum.
@@
 The Moral Foundations Questionnaire (MFQ), which was developed subsequent to the MFD, measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
-The quesionnaire is made up of judgment items and relevance items.
+The questionnaire is made up of judgment items and relevance items.
 Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
@@
 For example, the respondent is directed to rate how important the following situation is to their sense of morals: "whether or not someone did something disgusting." This example measures the relevance of the *purity/sanctity* foundations.
-Each foundation has a judgment and relevance subscale, totalling 10 subscales for the MFQ [@Graham2011].
+Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ [@Graham2011].
 
@@
 When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@Graham2011].
-This specificity is not present in most analyses involving the MFD and percent occurence, unless they also take into account the valence of the words used in the text or speech of interest.
+This specificity is not present in most analyses involving the MFD and percent occurrence, unless they also take into account the valence of the words used in the text or speech of interest.
 
@@
 
-@Warriner2013 exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e.
-"watch" rather than "watched" and "watching").
+@Warriner2013 exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e., "watch" rather than "watched" and "watching").
 The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory [@Warriner2013].
@@
 In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by @Kuperman2012 as well as the content lemmas from the SUBTLEX-US corpus consisiting of subtitles from various forms of visual media [@Warriner2013].
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by @Kuperman2012 as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media [@Warriner2013].
 This data collection resulted in the final list of 13,915 lemmas.
 Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
-Particpants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
+Participants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
 The researchers used a nine-point scale similar to the one used by @Bradley1999 when collecting ratings for ANEW [@Warriner2013].
@@
 
-@Warriner2014 utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in langauge.
+@Warriner2015 utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in language.
 The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with postive valence were also used more frequently [@Warriner2014].
-While the researchers concede the possiblility of an acquiensence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.
+Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with positive valence were also used more frequently [@Warriner2015].
+While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.
 
@@
 Finally, @Kuperman2014 found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks [@Kuperman2014].
-This research serves as further evidence that the @Warriner2014 list can be used for research inquiries both within and without the field of psycholinguistics.
+This research serves as further evidence that the @Warriner2013 list can be used for research inquiries both within and without the field of psycholinguistics.
 
@@
 Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
-The valence was used as a means to determine whether individiual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
+The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
 Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
@@
 Research into politics, language, and media has illuminated the complex relationships between all three.
-Any politically-oriented discussion of word occurence as an implication of moral or poltical position assumes that langauge and ideology are intrisincally linked.
-Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through langauge, thus implying a connection between ideology and language.
-She goes on to criticize the notion that language is either the "pre-existing raw material" used to shape ideologies or the "post-hoc vehicle" for their propogation.
+Any politically-oriented discussion of word occurrence as an implication of moral or political position assumes that language and ideology are intrinsically linked.
+Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through language, thus implying a connection between ideology and language.
+She goes on to criticize the notion that language is either the "pre-existing raw material" used to shape ideologies or the "post-hoc vehicle" for their propagation.
 Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies [@Cameron2006].
@@
 
-The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S.
-Druckman, Jacobs, and Ostermeier (-@Druckman2004) considered political "issues" as communication that attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-According to the researhcers, "image" priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
+The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S., @Druckman2004 considered political "issues" as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
+According to the researchers, "image" priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].
+The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
 The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
-They linked the Nixon adminstration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
+They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
 Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].
@@
 Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014].
+As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014].
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
@@
 For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
+All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
 
@@
 
-DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with reduncies removed at the end.
+DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
 
@@
 MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
-Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated by the political lean of the news soource, using the individual news sources as a random intercept to control for the structure of the data.
+Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
 
@@
 However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher endorsement of that foundation than convservatives.
+Specifically, the results indicated that liberal leaning sources demonstrated higher endorsement of that foundation than conservatives.
 This is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
@@
 
-Upon speculation, the researchers identified one possible reason for why the resuls were unable to confirm the hypothesis.
+Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
 The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
@@
 First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the reserachers chose to focus their data collection efforts exclusively on one event in U.S.
+Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
 politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
 Supreme Court.
-In Experiment 2, the reserachers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
+In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
 
@@
 The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime oppurtunity to bring morality back into interpretation of the Constitution.
+On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
 Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
@@
 Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assualt allegations vis-a-vis Kavanaugh's confirmation.
-
-In contrast to Experiment 1, the reserachers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scaped text as well as for any inferences drawn from the analyses.
+legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
+
+In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
 For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on the Kavanaugh confirmation hearing.
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
-The reasearchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks Kavanaugh's confirmation was prominent in the news.
+The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks Kavanaugh's confirmation was prominent in the news.
 The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
@@
 news sources.
-These sources were selected woting to their favorability among political partisans according to @Mitchell2014.
+These sources were selected owing to their favorability among political partisans according to @Mitchell2014.
 The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
 The sources favored by conservatives included *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-Political articles referencing Brett Kavanaugh's nominatino process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
-All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
+Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
+All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
 
@@
 
-Words from the source article words were then compiled into a dataset where they were paired up with the MFD words (where applicable) as wel as their percent occurrence and valence.
+Words from the source article words were then compiled into a dataset where they were paired up with the MFD words (where applicable) as well as their percent occurrence and valence.
 At the end of this process, the percentage of the number of words from each moral foundation appearing in the articles was computed.

### 2019-01-21 pilot_manuscript.tex
updated thesis

@@
             pdfauthor={William E. Padfield~\& Erin M. Buchanan, Ph.D.},
-            pdfkeywords={keywords},
+            pdfkeywords={politics, morality, psycholinguistics},
             pdfborder={0 0 0},
@@
   \title{Moral Foundations of U.S. Political News Organizations}
-    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan,
-Ph.D.\textsuperscript{1}}
+    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan, Ph.D.\textsuperscript{1}}
     \date{}
@@
 \textsuperscript{1} Missouri State University}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{politics, morality, psycholinguistics}
 \usepackage{csquotes}
@@
 
-\authornote{Add complete departmental affiliations for each
-author here. Each new line herein must be indented, like this line.
+\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 
@@
 Correspondence concerning this article should be addressed to William E.
-Padfield, 901 S. National Ave, Springfield, MO, 65897. E-mail:
-\href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
+Padfield, 901 S.
+National Ave, Springfield, MO, 65897.
+E-mail: \href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
 
 \abstract{
-Enter abstract here. Each new line herein must be indented, like this
-line.
+Enter abstract here. Each new line herein must be indented, like this line.
 
@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-Something clever to start
+In the United States, today's media landscape affords consumers a multitude of options for obtaining political news.
+Since the advent of cable news networks and the World Wide Web in the last decades of the twentieth century, consumers have gained access to an ever-expanding menagerie of news sources, many of which can be called up via a simple click, touch, or swipe.
+Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
+For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant respectively.
+These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
+Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
+Specifically, the use of differing moral language in political articles might be an indicator of political bias in news media.
+
+Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
+Starting chiefly in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
+Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
+As the field developed, however, considerable debate has taken place regarding operational definitions of \enquote{morality.} This remains an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
 
@@
 
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a
-method by which to capture the entirety of humans' moral domain. The
-researchers argued older theories of moral psychology were focused
-primarly on issues of justice, fairness, and caring - indvidually
-focused foundations of morality that align with the beliefs of political
-liberals ({\textbf{???}}). In other words, moral psychology ignored the
-valid moral foundations of conservatives. Moral Foundations Theory (MFT)
-holds that people's moral domain can be mapped by quantifying their
-endorsement of five moral foundations: \emph{harm/care},
-\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
-\emph{authority/respect}, and \emph{purity/sanctity} ({\textbf{???}}).
+As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg (Haidt \& Graham, 2007).
+Kohlberg's research popularized his theory of the development of moral reasoning.
+This theory establishes the steps of moral reasoning through which humans proceed as they mature.
+Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage (Haidt \& Graham, 2007).
+Similarly, Kohlberg found people typically start with a \enquote{pre-conventional} understanding of morality during infancy and progress through several steps until they reach a \enquote{post-conventional} ethics (Haidt \& Graham, 2007).
+People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice.
+From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality (Haidt \& Graham, 2007).
+This view persisted until it encountered criticism in the early 1980s.
 
-The researchers settled on these specific foundations after the
-completion of a literature survey of research in anthropology and
-evolutionary psychology ({\textbf{???}}).The first two foundations
-(\emph{harm/care} and \emph{fairness/reciprocity}) are termed the
-\enquote{individualizing foundations,} as they are centered on the
-concerns of individuals rather than groups. \emph{Harm/care} represents
-an endorsement of compassion and kindness, while opposing cruelty and
-harm. \emph{Fairness/reciprocity} represents concerns centered on
-guaranteeing individual rights as well as justice and equality among all
-people. The other three foundations (\emph{ingroup/loyalty},
-\emph{authority/respct}, and \emph{purity/sanctity}) are the
-\enquote{binding} foundations, owing to their focus on group-related
-concerns, rather than those of individuals. \emph{Ingroup/loyalty}
-represents endorsements of patriotism and heroism and discourages
-nonconformity and dissent. \emph{Authority/respect} represents an
-endorsement of social hierarchies and traditions while denigrating
-disobedience. Finally, \emph{purity/sanctity} represents concerns
-regarding chastity and piety, while discouraging vices and indulgences,
-including lust, avarice, and gluttony ({\textbf{???}}). Liberals tend to
-endorse the individualizing foundations more than conservatives.
-Endorsements for the three binding foundations, however, are lower than
-conservatives. Conservatives, on the other hand, tend to endorse all
-five foundations equally, implying they base judments (at least
-partially) on each foundation ({\textbf{???}}).
+Kohlberg's conception of morality faced major scrutiny from psychologist Carol Gilligan.
+In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women (Haidt \& Graham, 2007).
+She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
+Gilligan thus asserted morality was built upon an alternative moral foundation: caring (Haidt \& Graham, 2007).
+This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring (Haidt \& Graham, 2007).
+While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
+
+In their brief overview of the history of moral psychology, Graham, Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
+Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
+Such a system, they argued, did not account for moral concerns outside of the western world (Graham et al., 2009).
+Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
+The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.) and the \enquote{ethic of divinity}" - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
+In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
+
+Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain (Haidt \& Graham, 2007).
+The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals (Haidt \& Graham, 2007).
+In other words, moral psychology ignored the valid moral foundations of conservatives.
+Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007).
+
+The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology (Graham et al., 2011).
+The researchers attempted to locate virtues and morals corresponding to \enquote{evolutionary thinking.} For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the \emph{fairness/reciprocity} foundation.
+Additionally, evolutionary literature on disgust and its correlation to human behavior regarding food and sex informed the \emph{purity/sanctity} foundation (Graham et al., 2011).
+The researchers identified the five \enquote{top candidates} for the foundations of human cultures' morality (Graham et al., 2011).
+
+The first two foundations (\emph{harm/care} and \emph{fairness/reciprocity}) are termed the \enquote{individualizing foundations,} as they are centered on the concerns of individuals rather than groups.
+\emph{Harm/care} represents an endorsement of compassion and kindness, while opposing cruelty and harm.
+\emph{Fairness/reciprocity} represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
+The other three foundations (\emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}) are the \enquote{binding} foundations, owing to their focus on group-related concerns, rather than those of individuals.
+\emph{Ingroup/loyalty} represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
+\emph{Authority/respect} represents an endorsement of social hierarchies and traditions while denigrating disobedience.
+Finally, \emph{purity/sanctity} represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony (Haidt \& Graham, 2007).
+Liberals tend to endorse the individualizing foundations more than conservatives.
+Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
+It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations (Graham et al., 2009).
 
 \hypertarget{moral-foundations-dictionary}{%
-\subsection{Moral Foundations
-Dictionary}\label{moral-foundations-dictionary}}
+\subsection{Moral Foundations Dictionary}\label{moral-foundations-dictionary}}
 
-In order to capture language's role in moral and political reasoning,
-({\textbf{???}}) formulated the Moral Foundations Dictionary (MFD) in
-order to capture moral reasoning and justification as used in speech and
-text. The MFD is composed of 259 words, with around 50 words assigned to
-each of the five foundations. The researchers created a preliminary list
-of words that they believed would be associated with the five
-foundations. Then, using the Linguistic Inquiry and Word Count (LIWC;
-{\textbf{???}}) computer program, they analyzed transcripts of liberal
-and conservative Christian sermons in order to obtain frequencies of the
-occurrence of words from the researchers' initial list. The researchers
-manually checked the results from LIWC in order to make sure the results
-make sense given the contexts and rhetorical devices used in the
-sermons. Similar to previous research on Moral Foundations Theory,
-liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup}
-words more often than conservative ministers. Conversely, conservative
-ministers used \emph{authority} and \emph{purity} words more often than
-liberal ministers. However, conservative ministers did not use
-\emph{ingroup/loyalty} words more than liberals. Rather, liberal
-ministers used words pertaining to \emph{ingroup/loyalty}, but in
-contexts that promote rebellion and independence - causes
-\emph{opposite} to positive endorsements of that foundation
-({\textbf{???}}).
+In order to capture language's role in moral and political reasoning, Graham et al.
+(2009) formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
+The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
+The researchers created a preliminary list of words that they believed would be associated with the five foundations.
+Then, using the Linguistic Inquiry and Word Count (LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
+The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
+The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: \enquote{Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus} (Graham et al., 2009).
+This sentence added to the \emph{authority/respect} total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
+The researchers eliminated this sentence from the \emph{authority/respect} raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions (Graham et al., 2009).
 
-To this point, most text analysis utilizing the Moral Foundations
-Dictionary operationalizes endorsement of any one of the foundations as
-percent occurence of words from the foundation's respective word list.
-As such, most analyses assume that zero percent occurence is indicative
-of no endorsement, while any non-zero percent occurence indicates
-endorsement of the foundation. This may not be sufficient in describing
-the true nature of the writer or speaker's endorsement of one of the
-sets of moral intuitions. A quick glance at the MFD words for
-\emph{harm/care} reveals the presence of words that are more closely
-associated with universally accepted conceptions of \emph{harm} over
-\emph{care} and vice-versa ({\textbf{???}}). For example, the word
-\enquote{cruel} has relatively negative connotations compared to
-\enquote{benefit.} For the \emph{harm/care} foundation, it is
-conceivable that use of the word \enquote{cruel} might indicate a
-greater attentional focus of the idea of \emph{harm} rather than
-\emph{care}.
+Similar to previous research on Moral Foundations Theory, liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than conservative ministers.
+Conversely, conservative ministers used \emph{authority} and \emph{purity} words more often than liberal ministers.
+However, conservative ministers did not use \emph{ingroup/loyalty} words more than liberals.
+Rather, liberal ministers used words pertaining to \emph{ingroup/loyalty}, but in contexts that promote rebellion and independence - causes \emph{opposite} to positive endorsements of that foundation (Graham et al., 2009).
 
-For \emph{harm/care}, the definition of the foundation as well as its
-name clearly distinguishes between two somewhat opposite sides of an
-attentional continuum, with \emph{harm} on the negative end and
-\emph{care} on the positive side. In other words, the entries in the MFD
-for \emph{harm/care} have somewhat clear positive and negative valences.
-The same pattern can be seen in the MFD entries for the other four
-foundations. \emph{Purity/sanctity} features words that likely have a
-negative valence to most observers, including \enquote{disease}" and
-\enquote{trash,} along with more positive words, including
-\enquote{right} and \enquote{sacred} ({\textbf{???}}). This, however,
-brings up other questions regarding the definition and names of the
-other four foundations apart from \emph{harm/care}:
-\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
-\emph{authority/respect}, and \emph{purity/sanctity}. The latter four
-foudnations have names that are harder to understand as a valence
-continuum, as the concepts in the names are more similar, even to the
-point of being virtually synonymous in the case of
-\emph{fairness/reciprocity}.
+To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurrence of words in a given text from the foundation's respective word list.
+As such, most analyses assume that zero percent occurrence is indicative of no endorsement, while any non-zero percent occurrence indicates endorsement of the foundation.
+This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
+A quick glance at the MFD words for \emph{harm/care} reveals the presence of words that are more closely associated with universally accepted conceptions of \emph{harm} over \emph{care} and vice-versa (Graham et al., 2009).
+For example, the word \enquote{cruel} has relatively negative connotations compared to \enquote{benefit.} For the \emph{harm/care} foundation, it is conceivable that use of the word \enquote{cruel} might indicate a greater attentional focus of the idea of \emph{harm} rather than \emph{care}.
 
-When considering the issue of positive versus negative valence in MFD
-words, the question of how texts are analyzed vis-a-vis the MFD remains.
-How can raw percentage of MFD word occurence capture the valence and
-focus of the writer or speaker? If 2\% of a politician's speech features
-positive words (i.e. \enquote{benefit} and \enquote{defend}) from the
-MFD \emph{harm/care} list, how can researchers be sure the level and
-nature of the speaker's \enquote{endorsement} of the foundation equals
-that of another politician whose speech contained negatively connoted
-MFD words from the \emph{harm/care} list? They would have equal
-endorsements as far as the numbers are concerned, but the words used and
-focus given are on opposite sides of the \emph{harm/care} spectrum.
+For \emph{harm/care}, the definition of the foundation, as well as its name, clearly distinguishes between two somewhat opposite sides of an attentional continuum, with \emph{harm} on the negative end and \emph{care} on the positive side.
+In other words, the entries in the MFD for \emph{harm/care} have somewhat clear positive and negative valences.
+The same pattern can be seen in the MFD entries for the other four foundations.
+\emph{Purity/sanctity} features words that likely have a negative valence to most observers, including \enquote{disease}" and \enquote{trash,} along with more positive words, including \enquote{right} and \enquote{sacred} (Graham et al., 2009).
+These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from \emph{harm/care}: \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}.
+The latter four foundations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of \emph{fairness/reciprocity}.
 
-This issue is compounded by the fact the Moral Foundations Questionnaire
-(MFQ) and its subscales assume endorsement lies on a continuum. One item
-under the \emph{fairness/reciprocity} judgment subscale reads,
-\enquote{Justice is the most important requirement for a society}
-({\textbf{???}}). The survey respondent must select a number on a scale
-from 1 to 6 indicating responses spanning \enquote{strongly disagree} at
-1 to \enquote{strongly agree} at 6. While the scales in the MFQ do not
-represent true valence as it pertains to individual words, it does allow
-for a greater degree of specificity in terms of an individual's
-endorsement of a particular moral foundation. When a respondent selects
-a 4 for the aforementioned MFQ statement, they clearly are indicating
-they \enquote{slightly agree} with the statement ({\textbf{???}}). This
-specificity is not present in most analyses involving the MFD and
-percent occurence, unless they also take into account the valence of the
-words used in the text or speech of interest.
+When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
+How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
+If 2\% of a politician's speech features positive words (i.e.
+\enquote{benefit} and \enquote{defend}) from the MFD \emph{harm/care} list, how can researchers be sure the level and nature of the speaker's \enquote{endorsement} of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the \emph{harm/care} list?
+They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the \emph{harm/care} spectrum.
+
+This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
+The Moral Foundations Questionnaire (MFQ), which was developed subsequent to the MFD, measures individuals' endorsements of each of the foundations using a six-point scale (Graham et al., 2011).
+The questionnaire is made up of judgment items and relevance items.
+Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
+An example of such a statement reads: \enquote{It can never be right to kill another human being} (Graham et al., 2011).
+Relevance items gauge the respondent's opinion regarding the importance of foundation-related concerns.
+For example, the respondent is directed to rate how important the following situation is to their sense of morals: \enquote{whether or not someone did something disgusting.} This example measures the relevance of the \emph{purity/sanctity} foundations.
+Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ (Graham et al., 2011).
+
+The aforementioned ambiguity of the Moral Foundations Dictionary as an instrument becomes clearer upon closer examination of the items in the Moral Foundations Questionnaire.
+One item under the \emph{fairness/reciprocity} judgment subscale reads, \enquote{Justice is the most important requirement for a society} (Graham et al., 2011).
+The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning \enquote{strongly disagree} at 1 to \enquote{strongly agree} at 6.
+While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
+When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they \enquote{slightly agree} with the statement (Graham et al., 2011).
+This specificity is not present in most analyses involving the MFD and percent occurrence, unless they also take into account the valence of the words used in the text or speech of interest.
 
@@
 
-Borrowing from Osgood's work in the 1950s, ({\textbf{???}}) recognized
-valence as one of three related dimensions comprising emotion when
-developing their Affective Norms for English Words (ANEW). As mentioned
-before, \enquote{valence,} the first dimension, denotes the pleasantness
-of a given word. \enquote{Arousal,} the second dimension, describes the
-stimulating nature of a word. Lastly, \enquote{dominance} or
-\enquote{control} describes the extent to which a word makes one feel in
-or out of control ({\textbf{???}}). The researchers developed ANEW by
-presenting participants with a list of 100-150 words and asking for them
-to rate the word on all three dimensions using the Self-Assessment
-Mannikin (SAM), which allows ratings along either a nine-point scale
-when using traditional paper instruments or a twenty-point scale when
-using a computerized version.
+Borrowing from Osgood's work in the 1950s, Bradley and Lang (1999) recognized valence as one of three related dimensions comprising emotion when developing their Affective Norms for English Words (ANEW).
+As mentioned before, \enquote{valence,} the first dimension, denotes the pleasantness of a given word.
+\enquote{Arousal,} the second dimension, describes the stimulating nature of a word.
+Lastly, \enquote{dominance} or \enquote{control} describes the extent to which a word makes one feel in or out of control (Bradley \& Lang, 1999).
+The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Mannikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
 
-Participants saw the stimulus word and responded on each scale. The
-valence scale featured a smiling figure at one end (representing
-pleasantness) and a frowning figure at the other end (for
-unpleasantness). The arousal scale had a \enquote{wide-eyed} figure at
-one end with a sleepy figure at the other, representing stimulating and
-unstimulating respectively. Finally, the control scale featured a large
-figure, indicating the highest degree of control, at one end and a small
-figure, indicating a lack of control, at the other end ({\textbf{???}}).
-The end result of this procedure yielded affective norms along the three
-dimensions for 1,040 English words ({\textbf{???}}). ANEW represented an
-important first step in establishing affective norms for large numbers
-of English words. However, later researchers found the 1,040-word list
-to be limiting for a language consisting of thousands of words.
+Participants saw the stimulus word and responded on each scale.
+The valence scale featured a smiling figure at one end (representing pleasantness) and a frowning figure at the other end (for unpleasantness).
+The arousal scale had a \enquote{wide-eyed} figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
+Finally, the control scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end (Bradley \& Lang, 1999).
+The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words (Bradley \& Lang, 1999).
+ANEW represented an important first step in establishing affective norms for large numbers of English words.
+However, later researchers found the 1,040-word list to be limiting for a language consisting of thousands of words.
 
-({\textbf{???}}) exponentially lengthened the list of words with
-affective norms to 13,915 English lemmas, the base forms of words
-without inflection (i.e. \enquote{watch} rather than \enquote{watched}
-and \enquote{watching}). The researchers recognized the importance of
-affective norms in several areas of study, including emotion, language
-processing, and memory ({\textbf{???}}). They argue the list of words
-included in ANEW is sufficient for small-scale factorial research
-designs, but the list is \enquote{prohibitively small} for larger-scale
-\enquote{megastudies} that are common in psycholinguistic research today
-({\textbf{???}}).
+Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e.
+\enquote{watch} rather than \enquote{watched} and \enquote{watching}).
+The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory (Warriner et al., 2013).
+They argue the list of words included in ANEW is sufficient for small-scale factorial research designs, but the list is \enquote{prohibitively small} for larger-scale \enquote{megastudies} that are common in psycholinguistic research today (Warriner et al., 2013).
 
-In order to source a large number of lemmas for affective ratings, the
-researchers drew from several validated sources. These include the
-30,000 lemmas with age-of-acquisition (average age at which a particular
-word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and
-Brysbaert as well as the content lemmas from the SUBTLEX-US corpus
-consisiting of subtitles from various forms of visual media
-({\textbf{???}}). This resulted in the final list of 13,915 lemmas.
-Lists of 346-350 words were presented to participants recruited through
-the Amazon Mechanical Turk subject pool. Particpants rated the words
-along one of the three dimensions, unlike the ANEW project in which
-participants rated each word along all three dimensions at once. The
-researchers used a nine-point scale similar to the one used by
-({\textbf{???}}) when collecting ratings for ANEW ({\textbf{???}}).
+In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media (Warriner et al., 2013).
+This data collection resulted in the final list of 13,915 lemmas.
+Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
+Participants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
+The researchers used a nine-point scale similar to the one used by Bradley and Lang (1999) when collecting ratings for ANEW (Warriner et al., 2013).
 
 The researchers noted several points of interest upon observing ratings.
-First, they found that valence and dominance ratings had a negative
-skew, indicating more words elicited feelings of happiness and control
-than their respective opposites. Also, when examining the relationship
-between valence and arousal ratings, the researchers found a U-shaped
-relationship. This indicates words with high degrees of positivity and
-negativity elicited higher arousal ({\textbf{???}}). These observations
-along with the now-greatly expanded list of affective norms has been
-applied to several lines of inquiry in psycholinguistics.
+First, they found that valence and dominance ratings had a negative skew, indicating more words elicited feelings of happiness and control than their respective opposites.
+Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
+This indicates words with high degrees of positivity and negativity elicited higher arousal (Warriner et al., 2013).
+These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
 
-({\textbf{???}}) utilized the new affective norms list in order to
-investigate the validity of the Pollyanna hypothesis, or the prevalence
-of a generally optimistic outlook in humans as reflected in langauge.
-The researchers were able to conclude the existence of a greater number
-of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text
-corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers
-found that words with postive valence were also used more frequently
-({\textbf{???}}). While the researchers concede the possiblility of an
-acquiensence bias in ratings as a possible explanation for the observed
-positivity bias, this investigation represents one application of the
-({\textbf{???}}) list in emotional studies.
+Warriner and Kuperman (2015) utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in language.
+The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
+Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with postie valence were also used more frequently (Warriner \& Kuperman, 2015).
+While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the Warriner et al.
+(2013) list in emotional studies.
 
-One cognition-based study investigates the relationship between emotion
-and response latencies in word recognition. ({\textbf{???}}) sought to
-use the ({\textbf{???}}) norms to fill in the knowledge gaps regarding
-variance in word recognition. The researchers drew several conclusions
-regarding emotion and word recognition (specifically in naming and
-lexical decision tasks). First, ({\textbf{???}}) found higher response
-latencies in negative-valence words, lower response latencies in neutral
-words, and even lower response latencies in words with positive valence.
-The researchers also concluded that words causing higher arousal tend to
-have higher response latencies than less-arousing words. They found
-valence had a stronger effect on recognition than arousal (both effects
-were independent, not interactive). They found an interaction between
-emotion and word frequency such that valence and arousal are more
-effective on lower frequency words than high frequency words. Finally,
-({\textbf{???}}) found a greater effect for lexical decision tasks than
-for naming tasks. This research serves as further evidence that the
-({\textbf{???}}) list can be used for research inquiries both within and
-without the field of psycholinguistics.
+In addition to applications in emotion research, the Warriner norms (2013) have been utilized in cognitive research as well.
+One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
+Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use the Warriner et al.
+(2013) norms to fill in the knowledge gaps regarding variance in word recognition.
+The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
+First, Kuperman et al.
+(2014) found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
+The researchers also concluded that words causing higher arousal tend to have slower decision times than less-arousing words.
+They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
+They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
+Finally, Kuperman et al.
+(2014) found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks (Kuperman et al., 2014).
+This research serves as further evidence that the Warriner and Kuperman (2015) list can be used for research inquiries both within and without the field of psycholinguistics.
 
-In the present studies, the researchers used the 2013 Warriner list in
-order to denote the valence of the words appearing in the news articles
-scraped from the internet. Valence was considered as another independent
-variable and its relationship with the words comprising the Moral
-Foundations Dictionary were of chief interest to the researchers. The
-valence was used as a means to determine whether individiual words in
-the MFD represented more positive aspects of their respective foundation
-or if they denoted a more negative aspect of the foundation.
-Incorporating word valence into a study involving the MFD is meant to
-alleviate some of the issues regarding the aforementioned ambiguity
-regarding the words in the Moral Foundations Dictionary.
+In the present studies, the researchers used the Warriner et al.
+(2013) list in order to denote the valence of the words appearing in the news articles scraped from the internet.
+Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
+The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
+Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
 
@@
 
-Research into politics, language, and media has illuminated the complex
-relationships between all three. Any politically-oriented discussion of
-word occurence as an implication of moral or poltical position assumes
-that langauge and ideology are intrisincally linked. Deborah Cameron
-({\textbf{???}}) points out the expressive nature of ideological beliefs
-and how that expression is conveyed through langauge, thus implying a
-connection between ideology and language. She goes on to criticize the
-notion that language is either the \enquote{pre-existing raw material}
-used to shape ideologies or the \enquote{post-hoc vehicle} for their
-propogation. Rather, the structure of language itself is shaped by
-ideology and social processes even when it is used to explain or express
-ideologies ({\textbf{???}}).
+Research into politics, language, and media has illuminated the complex relationships between all three.
+Any politically-oriented discussion of word occurrence as an implication of moral or political position assumes that language and ideology are intrinsically linked.
+Deborah Cameron (2006) points out the expressive nature of ideological beliefs and how that expression is conveyed through language, thus implying a connection between ideology and language.
+She goes on to criticize the notion that language is either the \enquote{pre-existing raw material} used to shape ideologies or the \enquote{post-hoc vehicle} for their propagation.
+Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies (Cameron, 2006).
+Owing to the fact the Moral Foundations Dictionary was developed in order to assess the moral, which includes the ideological, orientation of discourse, its purported ability to assess parts of the structure of language (vocabulary) for ideological lean is of chief interest to the researchers in the present study.
 
-The use of language both to express and further an ideological goal has
-been documented in the techniques employed by candidates for political
-office in the U.S. For example, Druckman, Jacobs, and Ostermeier
-(({\textbf{???}})) investigated issue and image priming on the part of
-candidates as implied by the disproportionate attention candidates paid
-to particular issues over others. In their research, the authors
-consider \enquote{issues} as communication that attmepts to persuade
-constituents to vote for the candidates based on their strengths in
-matters of public policy. \enquote{Image} priming, on the other hand,
-describes techniques deployed in order to sway votes based on favorable
-aspects of the candidate's behavior and personality ({\textbf{???}}).
-The researchers found numerous examples of issue and image priming
-during the 1972 re-election campaign of Richard Nixon. They linked the
-Nixon adminstration's awareness of the issues for which the president
-had public support to the issues he should emphasize (and prime) during
-the campaign. Likewise the researchers found evidence that Nixon's team
-was aware of negative evaluations of his warmth and trustworthiness, and
-thus took steps to prime his purportedly positive qualities, including
-strength and competence ({\textbf{???}}).
+The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S.
+Druckman, Jacobs, and Ostermeier ((2004)) considered political \enquote{issues} as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
+According to the researchers, \enquote{image} priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality (Druckman et al., 2004).The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
+The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
+They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
+Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence (Druckman et al., 2004).
 
-({\textbf{???}}) also cited research from Iyengar and Kinder (1987)
-suggesting the news media affected perceptions of President Jimmy
-Carter's competence by emphasizing (read: priming) issues related to
-energy, defense, and the economy. This implies news media may affect
-perception of politicians based on where the media places emphasis.
-Other research into news media suggests certain media outlets, at least
-indirectly, may have an effect on the voting records of representatives
-in Congress ({\textbf{???}}). Specifically, the researchers identified a
-pattern of declining support for President Bill Clinton's policies
-chiefly among Republicans in the House of Representatives after the Fox
-News Channel began broadcasting on cable and satellite systems in their
-respective districts. As Fox News was, at the time of its launch in
-1996, the only outwardly ideological national news network, the
-reserachers were able to track its spread across the country and observe
-voting records of members of Congress both before and after Fox News'
-arrival ({\textbf{???}}). The researchers concluded that members of
-Congress, excluding those newly elected at the time of Fox News
-Channel's emergence, attempted to anticipate resultant
-conservative-leaning shifts among their constituents by bolstering their
-conservative voting record before the next election ({\textbf{???}}).
-
-Talk about political discourse, nature of news media in 2018/Trump
-era/Kavanaugh
-
-This project brings the two together in holy matrimony.
+Druckman et al.
+(2004) also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.~priming) issues related to energy, defense, and the economy.
+This focus implies news media may affect perception of politicians based on where the media places emphasis.
+Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress (Clinton \& Enamorado, 2014).
+Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
+As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival (Clinton \& Enamorado, 2014).
+The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election (Clinton \& Enamorado, 2014).
 
@@
 
+For Experiment 1, the researchers approached the methodology with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework.
+The researchers hypothesized the news sources genrally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
+Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
+
 \hypertarget{sources}{%
@@
 Political articles were scraped from the websites of four notable U.S.
-news sources. The sources were \emph{The New York Times}, \emph{National
-Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}. They were
-selected for their widespread recognition and the fact they are easily
-categorized (by the general public) according to perceived political
-lean. In general, \emph{The New York Times} and \emph{NPR} are perceived
-by many to have a liberal bias or lean. In contrast, Fox News and
-Breitbart are believed to have a conservative bias or lean. Political
-articles in particular were identified and subsequently scraped by
-including the specific URL directing to each source's political content
-in the \emph{R} script. For example, rather than scrape from
-nytimes.com, which would return undesired results (non-political
-features, reviews, etc.), we instead included
-nytimes.com/section/politics so that more or less exclusively political
-content was obtained. All code for this manuscript can be found at OSF
-LINK, and the scripts are provided inline with this manuscript written
-with the \emph{papaja} library ({\textbf{???}}).
+news sources.
+The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
+They were selected for their widespread recognition and the fact they are easily categorized (by the general public) according to perceived political lean.
+In general, \emph{The New York Times} and \emph{NPR} are perceived by many to have a liberal bias or lean.
+In contrast, Fox News and Breitbart are believed to have a conservative bias or lean (Mitchell, Matsa, Gottfried, \& Kiley, 2014).
+Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the \emph{R} script.
+For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
+All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
 
-Identification of the sources' political URLs presented a problem for
-two of the sources owing to complications with how their particular
-sites were structured. While in the multi-week process of scraping
-articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were
-not growing at a similar pace as those from \emph{The New York Times}
-and \emph{Breitbart}. Upon investigation, we found another, more robust
-URL for political content from NPR: their politics content
-\enquote{archive.} The page structure on NPR's website was such that
-only a limited selection of articles is displayed to the user at a given
-time. Scraping both the archive and the normal politics page ensured we
-were obtaining most (if not all) new articles as they were published. We
-later ran a process in order to exclude any duplicate articles.
-\emph{Fox News} presented a similar issue. We discovered \emph{Fox News}
-utilized six URLs in addition to the regular politics page. These URLs
-led to pages containing content pertaining the U.S. Executive Branch,
-Senate, House of Representatives, Judicial Branch, foreign policy, and
-elections. Once again, duplicates were subsequently eliminated from any
-analyses.
+Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
+While in the multi-week process of scraping articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not growing at a similar pace as those from \emph{The New York Times} and \emph{Breitbart}.
+Upon investigation, we found another, more robust URL for political content from NPR: their politics content \enquote{archive.} The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
+Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
+We later ran a process in order to exclude any duplicate articles.
+\emph{Fox News} presented a similar issue.
+We discovered \emph{Fox News} utilized six URLs in addition to the regular politics page.
+These URLs led to pages containing content pertaining the U.S.
+Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
+Once again, duplicates were subsequently eliminated from any analyses.
 
@@
 
-Using the \emph{rvest} library in the statistical package \emph{R}, we
-pulled body text for individual articles from each of the aforementioned
-sources (identified using CSS language) and compiled them into a dataset
-({\textbf{???}}). Using this dataset, we identified word count and
-average word count per source. This process was run once daily starting
-on \emph{DATE} until \emph{DATE.} Starting on \emph{DATE,} the process
-was run twice daily - once in the morning and again in the evening. Data
-collection was terminated once 250,000 words per source was collected on
-\emph{DATE.}
+Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset ({\textbf{???}}).
+Using this dataset, we identified word count and average word count per source.
+This process was run once daily starting on \emph{DATE} until \emph{DATE.} Starting on \emph{DATE,} the process was run twice daily - once in the morning and again in the evening.
+Data collection was terminated once 250,000 words per source was collected on \emph{DATE.}
 
@@
 
-Once data collection ended, the text was scanned using the \emph{ngram}
-package in \emph{R} ({\textbf{???}}). This package includes a word count
-function, which was used to remove articles that came through as blank
-text, as well as to eliminate text picked up from the Disqus commenting
-system used by certain websites. At this point, duplicate articles were
-discarded.
+Once data collection ended, the text was scanned using the \emph{ngram} package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017).
+This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
+At this point, duplicate articles were discarded.
 
-Using the ({\textbf{???}}) dictionary, the words making up each of the
-five foundations in the MFD were assigned their respective valence
-value. Once the MFD words' valences were added to the dataset, the
-article text was processed using the \emph{tm} and \emph{ngram} packages
-in \emph{R} in order to render the text in lowercase, remove
-punctuation, and fix spacing issues ({\textbf{???}}). The individual
-words were then reduced to their stems (i.e., \emph{abused} was stemmed
-to \emph{abus}). The same procedure was applied to the MFD words and the
-words in the ({\textbf{???}}) dataset.
+The article text was processed using the \emph{tm} and \emph{ngram} packages in \emph{R} in order to render the text in lowercase, remove punctuation, and fix spacing issues ({\textbf{???}}).
+The individual words were then reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}).
+The same procedure was applied to the MFD words and the words in the Warriner et al.
+(2013) dataset.
+Using the Warriner et al.
+(2013) dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value.
 
-DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that
-project were imported and added to each foundation, with reduncies
-removed at the end.
+DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
 
-The source article words were compiled into a dataset where they were
-matched up with their counterparts in the MFD along with their valence
-and a percentage of their occurrence. Therefore, for each article, the
-percentage of the number of \emph{harm/care} words occurring in the
-articles were calculated, and this process was repeated for each of the
-foundations. This procedure created five percentages that were included
-as the dependent variable for the following analyses.
+The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
+Therefore, for each article, the percentage of the number of \emph{harm/care} words occurring in the articles were calculated, and this process was repeated for each of the foundations.
+This procedure created five percentages that were included as the dependent variable for the following analyses.
+It should be noted the valence scores for the MFD words were \emph{z}-scored, so negative valence scores are possible.
 
@@
 
-To analyze if news sources adhered to differences in word use based on
-their target audience, we utilized a multilevel model (MLM) to analyze
-the data. MLM is a regression technique that allows one to control for
-the repeated measurement and nested structured of the data, which
-creates correlated error ({\textbf{???}}). Using the \emph{nlme} library
-in \emph{R} ({\textbf{???}}), each foundation's weighted percentage was
-predicated by the political lean of the news soource, using the
-individual news sources as a random intercept to control for the
-structure of the data.
+To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
+MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error (Gelman, 2006).
+Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
+
+The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
+The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
+Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 1.
 
@@
 
+The results obtained in Experiment 1 did not confirm the hypothesis.
+The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
+The strongest effect found was for the \emph{authority/respect} foundation owing to the fact its Cohen's \emph{d} value was greater than the other four foundations.
+However, the effect was in the opposite direction of that which was hypothesized.
+Specifically, the results indicated that liberal leaning sources demonstrated higher endorsement of that foundation than conservatives.
+This is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
+It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
+
+Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
+The selection of the broad and amorphous topic of \enquote{political news} may have led to the scraping of large numbers of articles with little to no moral-centric content.
+Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language let alone words from the Moral Foundations Dictionary.
+In short, the range of topics covered in Experiment 1 was likely too broad.
+The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
+
+Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
+The researchers identified two primary changes in methodology that were subsequently employed in Experiment 2.
+First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
+Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
+politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
+Supreme Court.
+In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
+
 \hypertarget{experiment-2}{%
@@
 \hypertarget{kavanaugh-supreme-court-hearing}{%
-\subsection{Kavanaugh Supreme Court
-Hearing}\label{kavanaugh-supreme-court-hearing}}
+\subsection{Kavanaugh Supreme Court Hearing}\label{kavanaugh-supreme-court-hearing}}
 
-In the wake of Justice Anthony Kennedy's retirement from the Supreme
-Court of the United States, President Donald Trump nominated Brett
-Kavanaugh as the new Associate Justice. Kavanaugh was previously on the
-U.S. Court of Appeals for the District of Columbia. The Senate Judiciary
-Committee began his confirmation hearing on September 4, 2018
-({\textbf{???}}). Following allegations of sexual assault by high school
-classmate Dr.~Christine Blasey Ford, the committee postponed its vote on
-whether or not to open the confirmation to the entire Senate.
+In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
+Kavanaugh was previously on the U.S.
+Court of Appeals for the District of Columbia.
+The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 ({\textbf{???}}).
+Following allegations of sexual assault by high school classmate Dr.~Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
 
-On September 27, the committee questioned Dr.~Ford before commencing a
-second round of questioning for Judge Kavanaugh ({\textbf{???}}). During
-the intervening weeks between hearings, two more women came forward with
-two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the
-September 27 proceedings on television ({\textbf{???}}). This figure
-does not take into account viewers who watched online, nor does it
-account for viewers outside the United States. On September 28, the
-Senate Judiciary Committee voted to send the nomination to the Senate
-floor. Senator Jeff Flake of Arizona, however, lobbied for a week-long
-FBI investigation on Kavanaugh and the allegations facing him, which the
-committee, and later the President, approved. The investigation
-concluded with no significant findings. The Senate voted 50-48 to
-approve Kavanaugh's appointment on October 6, 2018 ({\textbf{???}}).
+On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh ({\textbf{???}}).
+During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
+According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television (O'Connell, 2018).
+This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
+On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
+Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
+The investigation concluded with no significant findings.
+The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 ({\textbf{???}}).
 
-The Kavanaugh nomination, confirmation hearing, and eventual
-swearing-in, as well as the news media's coverage of all three events,
-feature many moral dimensions that likely differ depending on one's
-morals. On one side of the debate, Kavanaugh's Supreme Court tenure
-presents a prime oppurtunity to bring morality back into interpretation
-of the Constitution. Kavanaugh's confirmation creates a conservative
-stronghold among the justices on the court. Commentators have noted this
-might help advance a judicial agenda that backpedals certain rights
-previously upheld by the Supreme Court, including abortion and gay
-marriage - social issues challenged by their opponents at least
-partially on moral grounds. On the other side of the debate, the assault
-allegations have energized Kavanaugh's opponents to advocate for his
-rejection from the court owing to misdeeds resulting from Kavanaugh's
-own alleged lack of morals. Additionally, the moral duty of the Senate
-as the upper chamber in the U.S. legislature has been scrutinized in
-public discourse with respect to its handling of the assualt allegations
-vis-a-vis Kavanaugh's confirmation.
+The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
+On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
+Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
+Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
+On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Additionally, the moral duty of the Senate as the upper chamber in the U.S.
+legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
+
+In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on the Kavanaugh confirmation hearing.
+News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
+The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks Kavanaugh's confirmation was prominent in the news.
+The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
 
@@
 
-Experiment 2 largely followed the same method as Experiment 1. Political
-articles specifically referring to Brett Kavanaugh and his Supreme Court
-confirmation hearing were scraped
+Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
+news sources.
+These sources were selected owing to their favorability among political partisans according to Mitchell et al.
+(2014).
+The sources favored by liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{MSNBC}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
+The sources favored by conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Drudge Report}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
+Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
+All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
 
@@
 
-Expected material stuff - we are going to pick liberal and conservative
-sources from that thing document linked stuff - list those here: Sources
-used by LIBERALS (according to the document thing): The New Yorker Slate
-The Daily Show (is it wise to use satirical news for this??) The
-Guardian Al Jazeera America NPR New York Times Buzzfeed PBS BBC
-Huffington Post Washington Post The Economist Politico MSNBC CNN NBC
-News CBS News Google News Bloomberg ABC News USA TODAY
+Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{MSNBC}, \emph{Slate}, \emph{Huffington Post}, \emph{Politico}, \emph{Fox News}, \emph{Breitbart}, \emph{The Drudge Report}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
+We compiled the articles into a dataset ({\textbf{???}}).
+Using this dataset, we identified word count and average word count per source.
+This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
+This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
 
-Sources used by CONSERVATIVES: Fox News Drudge Report Breitbart Rush
-Limbaugh Show The Blaze Sean Hannity Glenn Beck (does he still report
-\enquote{news}??)
+Expected material stuff
+- we are going to pick liberal and conservative sources from that thing document linked stuff
+- list those here:
+Sources used by LIBERALS:
+Slate
+Huffington Post
+NPR
+New York Times
+Politico
 
-\begin{itemize}
-\tightlist
-\item
-  pick a specific date range we want to pull articles from
-\item
-  list that here:
-\end{itemize}
+Sources used by CONSERVATIVES:
+Fox News
+Breitbart
+Rush Limbaugh Show
+The Blaze
+Sean Hannity
+
+DROPPED:
+Glenn Beck (does he still report \enquote{news}??)
+The Daily Show (is it wise to use satirical news for this??) - Answer = Nope
+The Guardian (not American)
+The New Yorker
+Al Jazeera America
+Buzzfeed
+PBS
+BBC
+Washington Post
+The Economist
+CNN
+NBC News
+CBS News
+Google News
+Bloomberg
+ABC News
+USA TODAY
+Drudge Report \emph{HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK? The answer is NOPE}
+MSNBC \emph{CLOSEST TO POLITICAL CENTER; buh-bye!}
 
@@
 
-(September 27, 2018: Ford and Kavanaugh testimony before Senate
-Judiciary Committee)
+(September 27, 2018: Ford and Kavanaugh testimony before Senate Judiciary Committee)
 
@@
 
-here's when the stuff was happening and so picked two weeks before and
-after
+here's when the stuff was happening and so picked two weeks before and after
 
@@
 
-How you would run the data analysis
+As in Experiment 1, the text was scanned using the \emph{ngram} package in \emph{R} at the conclusion of data collection (Schmidt et al., 2017).
+Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system.
+Duplicate articles were subsequently discarded.
+
+Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
+Each individual word was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}).
+Once again, the same procedure was applied to the MFD words and the words in the Warriner et al.
+(2013) dataset.
+Using the Warriner et al.
+(2013) dictionary, the words in the MFD were assigned their valence value.
+
+DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
+
+Words from the source article words were then compiled into a dataset where they were paired up with the MFD words (where applicable) as well as their percent occurrence and valence.
+At the end of this process, the percentage of the number of words from each moral foundation appearing in the articles was computed.
+This procedure created five percentages serving as the dependent variable for the multilevel model.
+Valence scores for the MFD words were \emph{z}-scored, allowing for the possibility of negative valence scores.
 
@@
 
-Limitations of this one (no rationale behind choosing sources except
-\enquote{people say NPR's liberal??})
+Limitations of this one (no rationale behind choosing sources except \enquote{people say NPR's liberal??})
 
-What to do for future project (focus on one MF? Different sources? More
-sources?)
+What to do for future project (focus on one MF? Different sources? More sources?)
 
-Argue: why is still a good thing to study?? (probably something about
-current state of discourse, information, truth, \enquote{alternative
-facts,} subjective reality - philosophical stuff)
+Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, \enquote{alternative facts,} subjective reality - philosophical stuff)
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Aust2017}{}%
+Aust, F., \& Barth, M. (2017). papaja: Create APA manuscripts with R Markdown. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Bradley1999}{}%
+Bradley, M.
+M., \& Lang, P.
+J.
+(1999).
+\emph{Affective Norms for English Words (ANEW): Instruction Manual and Affective Ratings} (No.
+C-1).
+The Center for Research in Psychophysiology, University of Florida.
+
+\leavevmode\hypertarget{ref-Cameron2006}{}%
+Cameron, D. (2006). Ideology and language. \emph{Journal of Political Ideologies}, \emph{11}(2), 141--152. doi:\href{https://doi.org/10.1080/13569310600687916}{10.1080/13569310600687916}
+
+\leavevmode\hypertarget{ref-Clinton2014}{}%
+Clinton, J.
+D., \& Enamorado, T.
+(2014).
+The National News Media's Effect on Congress: How Fox News Affected Elites in Congress.
+\emph{The Journal of Politics}, \emph{76}(4), 928--943.
+doi:\href{https://doi.org/10.1017/S0022381614000425}{10.1017/S0022381614000425}
+
+\leavevmode\hypertarget{ref-Druckman2004}{}%
+Druckman, J.
+N., Jacobs, L.
+R., \& Ostermeier, E.
+(2004).
+Candidate Strategies to Prime Issues and Image.
+\emph{The Journal of Politics}, \emph{66}(4), 1180--1202.
+doi:\href{https://doi.org/10.1111/j.0022-3816.2004.00295.x}{10.1111/j.0022-3816.2004.00295.x}
+
+\leavevmode\hypertarget{ref-Feinerer2017}{}%
+Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from \url{http://tm.r-forge.r-project.org/}
+
+\leavevmode\hypertarget{ref-Gelman2006}{}%
+Gelman, A.
+(2006).
+Multilevel (hierarchical) modeling: What it can and cannot do.
+\emph{Technometrics}, \emph{48}(3), 432--435.
+doi:\href{https://doi.org/10.1198/004017005000000661}{10.1198/004017005000000661}
+
+\leavevmode\hypertarget{ref-Graham2009}{}%
+Graham, J., Haidt, J., \& Nosek, B.
+A.
+(2009).
+Liberals and conservatives rely on different sets of moral foundations.
+\emph{Journal of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
+doi:\href{https://doi.org/10.1037/a0015141}{10.1037/a0015141}
+
+\leavevmode\hypertarget{ref-Graham2011}{}%
+Graham, J., Nosek, B.
+A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
+H.
+(2011).
+Mapping the moral domain.
+\emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
+doi:\href{https://doi.org/10.1037/a0021847}{10.1037/a0021847}
+
+\leavevmode\hypertarget{ref-Haidt2007}{}%
+Haidt, J., \& Graham, J.
+(2007).
+When Morality Opposes Justice: Conservatives Have Moral Intuitions that Liberals may not Recognize.
+\emph{Social Justice Research}, \emph{20}(1), 98--116.
+doi:\href{https://doi.org/10.1007/s11211-007-0034-z}{10.1007/s11211-007-0034-z}
+
+\leavevmode\hypertarget{ref-Kuperman2014}{}%
+Kuperman, V., Estes, Z., Brysbaert, M., \& Warriner, A.
+B.
+(2014).
+Emotion and language: Valence and arousal affect word recognition.
+\emph{Journal of Experimental Psychology: General}, \emph{143}(3), 1065--1081.
+doi:\href{https://doi.org/10.1037/a0035669}{10.1037/a0035669}
+
+\leavevmode\hypertarget{ref-Kuperman2012}{}%
+Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M.
+(2012).
+Age-of-acquisition ratings for 30,000 English words.
+\emph{Behavior Research Methods}, \emph{44}(4), 978--990.
+doi:\href{https://doi.org/10.3758/s13428-012-0210-4}{10.3758/s13428-012-0210-4}
+
+\leavevmode\hypertarget{ref-Mitchell2014}{}%
+Mitchell, A., Matsa, K.
+E., Gottfried, J., \& Kiley, J.
+(2014).
+Political Polarization \& Media Habits \textbar{} Pew Research Center.
+Retrieved from \url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
+
+\leavevmode\hypertarget{ref-OConnell2018}{}%
+O'Connell, M.
+(2018).
+Ford-Kavanaugh Ratings: Hearing Brings 20 Million Viewers to Cable and Broadcast \textbar{} Hollywood Reporter.
+Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
+
+\leavevmode\hypertarget{ref-Pennebaker2007}{}%
+Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). Liwc2007: Linguistic inquiry and word count. Austin, TX.
+
+\leavevmode\hypertarget{ref-Pinheiro2017}{}%
+Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). nlme: Linear and nonlinear mixed effects models. Retrieved from \url{https://cran.r-project.org/package=nlme}
+
+\leavevmode\hypertarget{ref-Schmidt2017}{}%
+Schmidt, M.
+F., Gonzalez-Cabrera, I., \& Tomasello, M.
+(2017).
+Children's developing metaethical judgments.
+\emph{Journal of Experimental Child Psychology}, \emph{164}, 163--177.
+doi:\href{https://doi.org/10.1016/j.jecp.2017.07.008}{10.1016/j.jecp.2017.07.008}
+
+\leavevmode\hypertarget{ref-Warriner2015}{}%
+Warriner, A.
+B., \& Kuperman, V.
+(2015).
+Affective biases in English are bi-dimensional.
+\emph{Cognition and Emotion}, \emph{29}(7), 1147--1167.
+doi:\href{https://doi.org/10.1080/02699931.2014.968098}{10.1080/02699931.2014.968098}
+
+\leavevmode\hypertarget{ref-Warriner2013}{}%
+Warriner, A. B., Kuperman, V., \& Brysbaert, M. (2013). Norms of Valence, Arousal, and Dominance for 13,915 English Lemmas. \emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
 

### 2019-01-21 pilot_manuscript.Rmd
editing from EMB2 pdf comments

@@
 
-  Enter author note here.
+  William Padfield is a master's degree candidate in psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
 
@@
 Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." This remains an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
+As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." Concerns regarding operationalization remain an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
 
@@
 Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage [@Haidt2007].
-Similarly, Kohlberg found people typically start with a "pre-conventional" understanding of morality during infancy and progress through several steps until they reach a "post-conventional" ethics [@Haidt2007].
+Similarly, Kohlberg found people typically start with a "pre-conventional" understanding of morality during infancy and progress through several steps until they reach a "post-conventional" ethics.
 People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice.
@@
 
+Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007].
+The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
+In other words, moral psychology ignored the valid moral foundations of conservatives.
+Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
+
 In their brief overview of the history of moral psychology, @Graham2009 explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
@@
 Individually focused concerns can be grouped under an overarching "ethic of autonomy," which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the "ethic of community" (comprising one's duty to their family, tribe, etc.) and the "ethic of divinity"" - representing one's duty not to defile their God-given body and soul [@Graham2009].
+The other two ethics were the "ethic of community" (comprising one's duty to their family, tribe, etc.), and the "ethic of divinity"" - representing one's duty not to defile their God-given body and soul [@Graham2009].
 In the 2000s, @Haidt2007 took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
 
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007].
-The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
-
-The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].
+Haidt and Graham settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].
 The researchers attempted to locate virtues and morals corresponding to "evolutionary thinking." For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the *fairness/reciprocity* foundation.
@@
 Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
+The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
 The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: "Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus" [@Graham2009].
@@
 The arousal scale had a "wide-eyed" figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
-Finally, the control scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end [@Bradley1999].
+Finally, the dominance scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end [@Bradley1999].
 The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words [@Bradley1999].
@@
 In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by @Kuperman2012 as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media [@Warriner2013].
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by @Kuperman2012 as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media [@New2007].
 This data collection resulted in the final list of 13,915 lemmas.
@@
 Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
-This indicates words with high degrees of positivity and negativity elicited higher arousal [@Warriner2013].
+This U-shape indicates words with high degrees of positivity and negativity elicited higher arousal [@Warriner2013].
 These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
@@
 
-In addition to applications in emotion research, the Warriner norms [-@Warriner2013] have been utilized in cognitive research as well.
+In addition to applications in emotion research, the @Warriner2013 norms have been utilized in cognitive research as well.
 One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-@Kuperman2014 sought to use the @Warriner2013 norms to fill in the knowledge gaps regarding variance in word recognition.
+@Kuperman2014 sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
 The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
@@
 The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
+Specifically, valences were used to weight the MFD words by their relative degree of positivity or negativity.
 Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
@@
 Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014].
+As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival.
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
@@
 # Method
-For Experiment 1, the researchers approached the methodology with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework.
+For Experiment 1, the researchers approached the study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
 The researchers hypothesized the news sources genrally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
@@
 
-Political articles were scraped from the websites of four notable U.S.
-news sources.
+Political articles were collected from the websites of four notable U.S.
+news sources, a process known as web scraping.
 The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
@@
 
-The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm].
+The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@Feinerer2017].
 The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
 The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value.
+Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
 
@@
 Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-This procedure created five percentages that were included as the dependent variable for the following analyses.
-It should be noted the valence scores for the MFD words were *z*-scored, so negative valence scores are possible.
+Words' percent occurence were multiplied by their *z*-scored valence.
+Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence.
+Positive values indicate positive valence, and negative values indicate negative valence.
+Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
 
@@
 MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
-Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
+Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
 
@@
 Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 1.
+Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
+Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
 
@@
 apa_table(tableprint,
-          note = "something useful here",
-          caption = "stuff at the top", 
+          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
+          caption = "Experiment 1 Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
 However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher endorsement of that foundation than conservatives.
-This is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
+Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
+This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
 It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
@@
 The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language let alone words from the Moral Foundations Dictionary.
+Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
 In short, the range of topics covered in Experiment 1 was likely too broad.
@@
 Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-The researchers identified two primary changes in methodology that were subsequently employed in Experiment 2.
+Generally speaking, the researchers believe their methodology to be sound.
+Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
+Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
+The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
+Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurence.
+
+While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
+The researchers identified two such changes that were subsequently employed in Experiment 2.
 First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
@@
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks Kavanaugh's confirmation was prominent in the news.
+The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks before and two weeks after Kavanaugh's confirmation, owing to its prominence in the news.
 The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
@@
 These sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
-The sources favored by conservatives included *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
+The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
+The sources favored by conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
+All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts, again written with the *papaja* library in *R*, are provided inline with this manuscript [@Aust2017].
 
@@
 
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): *The New York Times*, *National Public Radio (NPR)*, *MSNBC*, *Slate*, *Huffington Post*, *Politico*, *Fox News*, *Breitbart*, *The Drudge Report*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-We compiled the articles into a dataset [@Wickham2018].
+Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
+We compiled the articles into a dataset [@Wickham2016].
 Using this dataset, we identified word count and average word count per source.
@@
 
-Expected material stuff
-- we are going to pick liberal and conservative sources from that thing document linked stuff
-- list those here:
-  Sources used by LIBERALS:
-  Slate
-  Huffington Post
-  NPR
-  New York Times
-  Politico
-
-  Sources used by CONSERVATIVES:
-  Fox News
-  Breitbart
-  Rush Limbaugh Show
-  The Blaze
-  Sean Hannity
-
-  DROPPED:
-  Glenn Beck (does he still report "news"??)
-  The Daily Show (is it wise to use satirical news for this??) - Answer = Nope
-  The Guardian (not American)
-  The New Yorker
-  Al Jazeera America
-  Buzzfeed
-  PBS
-  BBC
-  Washington Post
-  The Economist
-  CNN
-  NBC News
-  CBS News
-  Google News
-  Bloomberg
-  ABC News
-  USA TODAY
-  Drudge Report *HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK? The answer is NOPE*
-  MSNBC *CLOSEST TO POLITICAL CENTER; buh-bye!*
-
-START DATE: September 13, 2018
-
-(September 27, 2018: Ford and Kavanaugh testimony before Senate Judiciary Committee)
-
-END DATE: October 11, 2018
-
-here's when the stuff was happening and so picked two weeks before and after
-
 ## Data analysis
 
-As in Experiment 1, the text was scanned using the *ngram* package in *R* at the conclusion of data collection [@Schmidt2017].
-Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system.
-Duplicate articles were subsequently discarded.
+As in Experiment 1, the text was scanned with *ngram*.
+Again, blank articles, text from the Disqus system, and duplicate articles were removed [@Schmidt2017].
+The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017].
+Words were subsequently matched with their valences from @Warriner2013.
 
@@
 Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words in the MFD were assigned their valence value.
-
-DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
-
-Words from the source article words were then compiled into a dataset where they were paired up with the MFD words (where applicable) as well as their percent occurrence and valence.
-At the end of this process, the percentage of the number of words from each moral foundation appearing in the articles was computed.
-This procedure created five percentages serving as the dependent variable for the multilevel model.
-Valence scores for the MFD words were *z*-scored, allowing for the possibility of negative valence scores.
+Using the @Warriner2013 dictionary, the words in the MFD were assigned their respective valence.
+The researchers obtained the words' percent occurence in the text.
+Once again, percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
 

### 2019-01-26 pilot_manuscript.Rmd
new Kohlberg and Gilligan stuff
based on their words

@@
 Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as they mature.
-Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage [@Haidt2007].
-Similarly, Kohlberg found people typically start with a "pre-conventional" understanding of morality during infancy and progress through several steps until they reach a "post-conventional" ethics.
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice.
+This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance [@Kohlberg1977].
+Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
+Similarly, Kohlberg found people typically start with a "pre-conventional" understanding of morality during infancy in which children understand "right" and "wrong" purely in terms of how they interact with resultant experiences of rewards and punishment.
+Typically, people progress through several steps until they reach a "post-conventional" ethics.
+People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their "self-chosen ethical principles" [@Kohlberg1977].
 From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality [@Haidt2007].
@@
 In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women [@Haidt2007].
+Gilligan drew attention to purported differences in the ways men and women are taught to relate to self and others.
 She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring [@Haidt2007].
+She pushes back against Kohlberg's assumption that moral development replaces "rule of brute force," as enforced by men, with the justice-based "rule of law." According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law [@Gilligan1982].
+Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
+Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
+Gilligan thus asserted morality was built upon an alternative moral foundation: caring [@Gilligan1982].
 This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring [@Haidt2007].

### 2019-01-27 pilot_manuscript.Rmd
I rant about how social priming studies dont replicate!

@@
 The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
+
 They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
 Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].
-
-@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.
+The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.
 priming) issues related to energy, defense, and the economy.
-This focus implies news media may affect perception of politicians based on where the media places emphasis.
+This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
+
+There is a potential caveat regarding the validity of @Druckman2004's findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
+@Pashler2012 point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
+Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
+Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
+@Pashler2012 point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
+Studies investigating perceptual priming have been "directly replicated in hundreds of labs" [@Pashler2012].
+This does not appear to be the case for social priming, as argued by @Pashler2012.
+
+@Pashler2012 noticed the unusually large effect size values (Cohen's *d*) reported by researchers studying social priming effects.
+The researchers reproduced two studies from @Williams2008 The first study attempted to prime participants by having them plot points on a Cartesian grid.
+The independent variable was priming condition and contained three levels: short, middle, and long distance.
+Those instructed to plot points further apart were hypothesized to express a higher degree of psychological distance regarding their family.
+The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
+@Pashler2012 concluded those two studies from @Williams2008 held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
+
+While these concerns regarding the replication of social priming studies are valid and deserve further investigation, @Druckman2004 does not purport to demonstrate a widespread effect of social priming on the American electorate.
+In other words, this reseach makes no claim to empirically supported priming effects.
+Rather, @Druckman2004 chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
+These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
+As such, @Druckman2004's research on Nixon serves as an example of language's potential utility in the propogation of desirable political opinions.
+The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
+The idea that even 1970s news media could contain political biases is of particular interest to the current study, which investigates similar phenomena in contemporary news media.
+
 Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014].

### 2019-02-02 pilot_manuscript.Rmd
added blip regarding MTMM project

@@
 
-DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
+Concurrent research by Jordan, Buchanan & Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using one sample.
+The instruments will be analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
+The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity.
+Additionally, the researchers are investigating whether or not a reduced set of MFD words may likewise bolster the validity of the MFD.
+Depending on the results of that research, either an augmented or reduced Moral Foundations Dictionary may be utilized in this analysis rather than the original version.
 
@@
 Words were subsequently matched with their valences from @Warriner2013.
+Depending on the results of Jordan, Buchanan & Padfield's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
 

### 2019-02-02 pilot_manuscript.Rmd
finally fixed Congressional Record citation

@@
 Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD].
+The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@USGovernment2018b].
 Following allegations of sexual assault by high school classmate Dr.
@@
 On September 27, the committee questioned Dr.
-Ford before commencing a second round of questioning for Judge Kavanaugh [@CITE_CONGRESSIONAL_RECORD].
+Ford before commencing a second round of questioning for Judge Kavanaugh [@USGovernment2018].
 During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
@@
 The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@CITE_CONGRESSIONAL_RECORD].
+The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@USGovernment2018a].
 

### 2019-02-04 pilot_manuscript.Rmd
updated the text a bit.

@@
 Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
-For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant respectively.
+For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant, respectively.
 These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
@@
 The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with positive valence were also used more frequently [@Warriner2015].
+Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, the Corpus for Contemporary American English (COCA), the British National Corpus (BNC), Touchstone Applied Science Associates, Inc.
+Corpus (TASA), and the corpus used for the Hyperspace Analogue to Language model (HAL), the researchers found that words with positive valence were also used more frequently [@Warriner2015].
 While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.
@@
 @Kuperman2014 sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
-The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
+The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks - two cognitive processing tasks wherein a participant has to read aloud or judge a word for its lexicality).
 First, @Kuperman2014 found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
@@
 Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].
-The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.
-priming) issues related to energy, defense, and the economy.
+The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g., priming) issues related to energy, defense, and the economy.
 This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
@@
 Studies investigating perceptual priming have been "directly replicated in hundreds of labs" [@Pashler2012].
-This does not appear to be the case for social priming, as argued by @Pashler2012.
+This replication rate does not appear to be the case for social priming, as argued by @Pashler2012.
 
@@
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
+
+Therefore, the current study sought to combine both methods related questions and extension/replication of previous moral foundation results found for liberal and conservative sources.
+First, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
+Second, these weighted percentages were examined for their differences in across liberal and conservative news sources.
 
@@
 
-Concurrent research by Jordan, Buchanan & Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using one sample.
-The instruments will be analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity.
-Additionally, the researchers are investigating whether or not a reduced set of MFD words may likewise bolster the validity of the MFD.
-Depending on the results of that research, either an augmented or reduced Moral Foundations Dictionary may be utilized in this analysis rather than the original version.
+Concurrent research by Jordan, Buchanan, and Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
+The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
+The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
+Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
 
@@
 Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 1.
+To interpret the weighted scores, one can examine the mean and standard deviations for each.
+A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
+Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
+Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
 Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.

### 2019-02-04 pilot_manuscript.tex
updated the text a bit.

@@
   \title{Moral Foundations of U.S. Political News Organizations}
-    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan, Ph.D.\textsuperscript{1}}
+    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan, Ph.D.\textsuperscript{2}}
     \date{}
@@
 \vspace{0.5cm}
-\textsuperscript{1} Missouri State University}
+\textsuperscript{1} Missouri State University\\\textsuperscript{2} }
 \keywords{politics, morality, psycholinguistics}
@@
 
-Enter author note here.
+William Padfield is a master's degree candidate in psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
 
@@
 Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of \enquote{morality.} This remains an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
+As the field developed, however, considerable debate has taken place regarding operational definitions of \enquote{morality.} Concerns regarding operationalization remain an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
 
@@
 Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as they mature.
-Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage (Haidt \& Graham, 2007).
-Similarly, Kohlberg found people typically start with a \enquote{pre-conventional} understanding of morality during infancy and progress through several steps until they reach a \enquote{post-conventional} ethics (Haidt \& Graham, 2007).
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice.
+This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance ({\textbf{???}}).
+Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
+Similarly, Kohlberg found people typically start with a \enquote{pre-conventional} understanding of morality during infancy in which children understand \enquote{right} and \enquote{wrong} purely in terms of how they interact with resultant experiences of rewards and punishment.
+Typically, people progress through several steps until they reach a \enquote{post-conventional} ethics.
+People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their \enquote{self-chosen ethical principles} ({\textbf{???}}).
 From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality (Haidt \& Graham, 2007).
@@
 In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women (Haidt \& Graham, 2007).
+Gilligan drew attention to purported differences in the ways men and women are taught to relate to self and others.
 She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring (Haidt \& Graham, 2007).
+She pushes back against Kohlberg's assumption that moral development replaces \enquote{rule of brute force,} as enforced by men, with the justice-based \enquote{rule of law.} According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law ({\textbf{???}}).
+Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
+Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
+Gilligan thus asserted morality was built upon an alternative moral foundation: caring ({\textbf{???}}).
 This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring (Haidt \& Graham, 2007).
 While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
-
-In their brief overview of the history of moral psychology, Graham, Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
-Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
-Such a system, they argued, did not account for moral concerns outside of the western world (Graham et al., 2009).
-Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.) and the \enquote{ethic of divinity}" - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
-In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
 
@@
 
-The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology (Graham et al., 2011).
+In their brief overview of the history of moral psychology, Graham, Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
+Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
+Such a system, they argued, did not account for moral concerns outside of the western world (Graham et al., 2009).
+Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
+The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.), and the \enquote{ethic of divinity}" - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
+In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
+
+Haidt and Graham settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology (Graham et al., 2011).
 The researchers attempted to locate virtues and morals corresponding to \enquote{evolutionary thinking.} For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the \emph{fairness/reciprocity} foundation.
@@
 Then, using the Linguistic Inquiry and Word Count (LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons.
+The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
 The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: \enquote{Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus} (Graham et al., 2009).
@@
 How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
-If 2\% of a politician's speech features positive words (i.e.
-\enquote{benefit} and \enquote{defend}) from the MFD \emph{harm/care} list, how can researchers be sure the level and nature of the speaker's \enquote{endorsement} of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the \emph{harm/care} list?
+If 2\% of a politician's speech features positive words (i.e., \enquote{benefit} and \enquote{defend}) from the MFD \emph{harm/care} list, how can researchers be sure the level and nature of the speaker's \enquote{endorsement} of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the \emph{harm/care} list?
 They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the \emph{harm/care} spectrum.
@@
 The arousal scale had a \enquote{wide-eyed} figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
-Finally, the control scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end (Bradley \& Lang, 1999).
+Finally, the dominance scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end (Bradley \& Lang, 1999).
 The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words (Bradley \& Lang, 1999).
@@
 
-Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e.
-\enquote{watch} rather than \enquote{watched} and \enquote{watching}).
+Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e., \enquote{watch} rather than \enquote{watched} and \enquote{watching}).
 The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory (Warriner et al., 2013).
@@
 In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media (Warriner et al., 2013).
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media ({\textbf{???}}).
 This data collection resulted in the final list of 13,915 lemmas.
@@
 Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
-This indicates words with high degrees of positivity and negativity elicited higher arousal (Warriner et al., 2013).
+This U-shape indicates words with high degrees of positivity and negativity elicited higher arousal (Warriner et al., 2013).
 These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
@@
 The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with postie valence were also used more frequently (Warriner \& Kuperman, 2015).
+Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with positive valence were also used more frequently (Warriner \& Kuperman, 2015).
 While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the Warriner et al.
@@
 
-In addition to applications in emotion research, the Warriner norms (2013) have been utilized in cognitive research as well.
+In addition to applications in emotion research, the Warriner et al.
+(2013) norms have been utilized in cognitive research as well.
 One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use the Warriner et al.
-(2013) norms to fill in the knowledge gaps regarding variance in word recognition.
+Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
 The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
@@
 (2014) found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks (Kuperman et al., 2014).
-This research serves as further evidence that the Warriner and Kuperman (2015) list can be used for research inquiries both within and without the field of psycholinguistics.
+This research serves as further evidence that the Warriner et al.
+(2013) list can be used for research inquiries both within and without the field of psycholinguistics.
 
@@
 
-The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S.
-Druckman, Jacobs, and Ostermeier ((2004)) considered political \enquote{issues} as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-According to the researchers, \enquote{image} priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality (Druckman et al., 2004).The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
+The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S., Druckman, Jacobs, and Ostermeier (2004) considered political \enquote{issues} as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
+According to the researchers, \enquote{image} priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality (Druckman et al., 2004).
+The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
 The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
+
 They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
 Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence (Druckman et al., 2004).
+The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.~priming) issues related to energy, defense, and the economy.
+This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
 
-Druckman et al.
-(2004) also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.~priming) issues related to energy, defense, and the economy.
-This focus implies news media may affect perception of politicians based on where the media places emphasis.
+There is a potential caveat regarding the validity of Druckman et al.
+(2004)'s findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
+({\textbf{???}}) point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
+Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
+Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
+({\textbf{???}}) point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
+Studies investigating perceptual priming have been \enquote{directly replicated in hundreds of labs} ({\textbf{???}}).
+This does not appear to be the case for social priming, as argued by ({\textbf{???}}).
+
+({\textbf{???}}) noticed the unusually large effect size values (Cohen's \emph{d}) reported by researchers studying social priming effects.
+The researchers reproduced two studies from ({\textbf{???}}) The first study attempted to prime participants by having them plot points on a Cartesian grid.
+The independent variable was priming condition and contained three levels: short, middle, and long distance.
+Those instructed to plot points further apart were hypothesized to express a higher degree of psychological distance regarding their family.
+The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
+({\textbf{???}}) concluded those two studies from ({\textbf{???}}) held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
+
+While these concerns regarding the replication of social priming studies are valid and deserve further investigation, Druckman et al.
+(2004) does not purport to demonstrate a widespread effect of social priming on the American electorate.
+In other words, this reseach makes no claim to empirically supported priming effects.
+Rather, Druckman et al.
+(2004) chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
+These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
+As such, Druckman et al.
+(2004)'s research on Nixon serves as an example of language's potential utility in the propogation of desirable political opinions.
+The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
+The idea that even 1970s news media could contain political biases is of particular interest to the current study, which investigates similar phenomena in contemporary news media.
+
 Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress (Clinton \& Enamorado, 2014).
 Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival (Clinton \& Enamorado, 2014).
+As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival.
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election (Clinton \& Enamorado, 2014).
@@
 
-For Experiment 1, the researchers approached the methodology with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework.
+For Experiment 1, the researchers approached the study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
 The researchers hypothesized the news sources genrally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
@@
 
-Political articles were scraped from the websites of four notable U.S.
-news sources.
+Political articles were collected from the websites of four notable U.S.
+news sources, a process known as web scraping.
 The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
@@
 For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
+All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
 
@@
 
-The article text was processed using the \emph{tm} and \emph{ngram} packages in \emph{R} in order to render the text in lowercase, remove punctuation, and fix spacing issues ({\textbf{???}}).
+The article text was processed using the \emph{tm} and \emph{ngram} packages in \emph{R} in order to render the text in lowercase, remove punctuation, and fix spacing issues (Feinerer \& Hornik, 2017).
 The individual words were then reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}).
@@
 Using the Warriner et al.
-(2013) dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value.
+(2013) dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
 
-DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
+Concurrent research by Jordan, Buchanan \& Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using one sample.
+The instruments will be analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
+The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity.
+Additionally, the researchers are investigating whether or not a reduced set of MFD words may likewise bolster the validity of the MFD.
+Depending on the results of that research, either an augmented or reduced Moral Foundations Dictionary may be utilized in this analysis rather than the original version.
 
@@
 Therefore, for each article, the percentage of the number of \emph{harm/care} words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-This procedure created five percentages that were included as the dependent variable for the following analyses.
-It should be noted the valence scores for the MFD words were \emph{z}-scored, so negative valence scores are possible.
+Words' percent occurence were multiplied by their \emph{z}-scored valence.
+Valences were \emph{z}-scored in order to eliminate any ambiguity regarding the direction of the valence.
+Positive values indicate positive valence, and negative values indicate negative valence.
+Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
 
@@
 MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error (Gelman, 2006).
-Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
+Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
 
@@
 Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 1.
+Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
+Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
 
@@
 \begin{threeparttable}
-\caption{\label{tab:exp1-table}stuff at the top}
+\caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
 \begin{tabular}{lccccccc}
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} something useful here}
+\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
 \end{tablenotes}
@@
 The selection of the broad and amorphous topic of \enquote{political news} may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language let alone words from the Moral Foundations Dictionary.
+Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
 In short, the range of topics covered in Experiment 1 was likely too broad.
@@
 (2014).
-The sources favored by liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{MSNBC}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
-The sources favored by conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Drudge Report}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
+The sources favored by liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
+The sources favored by conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
-All code for this manuscript can be found at OSF LINK, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
+All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts, again written with the \emph{papaja} library in \emph{R}, are provided inline with this manuscript (Aust \& Barth, 2017).
 
@@
 
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the following 12 sources (identified using CSS language): \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{MSNBC}, \emph{Slate}, \emph{Huffington Post}, \emph{Politico}, \emph{Fox News}, \emph{Breitbart}, \emph{The Drudge Report}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
+Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
 We compiled the articles into a dataset ({\textbf{???}}).
@@
 
-Expected material stuff
-- we are going to pick liberal and conservative sources from that thing document linked stuff
-- list those here:
-Sources used by LIBERALS:
-Slate
-Huffington Post
-NPR
-New York Times
-Politico
-
-Sources used by CONSERVATIVES:
-Fox News
-Breitbart
-Rush Limbaugh Show
-The Blaze
-Sean Hannity
-
-DROPPED:
-Glenn Beck (does he still report \enquote{news}??)
-The Daily Show (is it wise to use satirical news for this??) - Answer = Nope
-The Guardian (not American)
-The New Yorker
-Al Jazeera America
-Buzzfeed
-PBS
-BBC
-Washington Post
-The Economist
-CNN
-NBC News
-CBS News
-Google News
-Bloomberg
-ABC News
-USA TODAY
-Drudge Report \emph{HEY! THIS IS MOSTLY AN AGGREGATOR!!! IS IT STILL OK? The answer is NOPE}
-MSNBC \emph{CLOSEST TO POLITICAL CENTER; buh-bye!}
-
-START DATE: September 13, 2018
-
-(September 27, 2018: Ford and Kavanaugh testimony before Senate Judiciary Committee)
-
-END DATE: October 11, 2018
-
-here's when the stuff was happening and so picked two weeks before and after
-
 \hypertarget{data-analysis-1}{%
@@
 
-As in Experiment 1, the text was scanned using the \emph{ngram} package in \emph{R} at the conclusion of data collection (Schmidt et al., 2017).
-Using the package's word count function, articles that came through as blank text were removed, as well as text scraped from the Disqus commenting system.
-Duplicate articles were subsequently discarded.
+As in Experiment 1, the text was scanned with \emph{ngram}.
+Again, blank articles, text from the Disqus system, and duplicate articles were removed (Schmidt et al., 2017).
+The text was processed and stemmed in order to convert to a usable form for further analysis (Feinerer \& Hornik, 2017).
+Words were subsequently matched with their valences from Warriner et al.
+(2013).
+Depending on the results of Jordan, Buchanan \& Padfield's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
 
@@
 Using the Warriner et al.
-(2013) dictionary, the words in the MFD were assigned their valence value.
-
-DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with redundancies removed at the end.
-
-Words from the source article words were then compiled into a dataset where they were paired up with the MFD words (where applicable) as well as their percent occurrence and valence.
-At the end of this process, the percentage of the number of words from each moral foundation appearing in the articles was computed.
-This procedure created five percentages serving as the dependent variable for the multilevel model.
-Valence scores for the MFD words were \emph{z}-scored, allowing for the possibility of negative valence scores.
+(2013) dictionary, the words in the MFD were assigned their respective valence.
+The researchers obtained the words' percent occurence in the text.
+Once again, percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
 

### 2019-02-09 pilot_manuscript.Rmd
updated small tweaks
fixed citations and updated .bib file

@@
 # Method
+
 For Experiment 1, the researchers approached the study with the intention to answer a method question.
@@
 
-Concurrent research by Jordan, Buchanan, and Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
+Concurrent research by @Jordan2019 is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
 The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
@@
 Words were subsequently matched with their valences from @Warriner2013.
-Depending on the results of Jordan, Buchanan & Padfield's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
+Depending on the results of @Jordan2019's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
 
@@
 
-# Experiment 2 results
+# Experiment 2
+
+## Results
 
@@
 # Conclusions
-
-How it turned out
-
-Limitations of this one (no rationale behind choosing sources except "people say NPR's liberal??")
-
-What to do for future project (focus on one MF? Different sources? More sources?)
-
-Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, "alternative facts," subjective reality - philosophical stuff)
 

### 2019-02-09 pilot_manuscript.Rmd
wrote abstract and fixed scrape dates for Exp1

@@
 abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
+
+  The media ecosystem has grown, and political opinions have diverged such that there are competing conceptions of objective truth.
+Commentators often point to political biases in news coverage as a catalyst for this political divide.
+The Moral Foundations Dictionary (MFD) facilitates identification of ideological leanings in text through frequency of the occurrence of certain words.
+Through web scraping, the researchers extracted articles from popular news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
+In Experiment 1, the researchers gathered poltical articles from four sources.
+They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
+In Experiment 2, the researchers will expand their number of sources to 10 and will analyze articles that pertain to the 2018 confirmation hearings of U.S.
+Supreme Court Justice Brett Kavanaugh.
+This topic was selected due to the moral disputes associated with his nomination.
 
@@
 Using this dataset, we identified word count and average word count per source.
-This process was run once daily starting on *DATE* until *DATE.* Starting on *DATE,* the process was run twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected on *DATE.*
+This process was run once daily starting in February 2018 until March 2018.
+Starting in mid-March 2018, the process was run twice daily - once in the morning and again in the evening.
+Data collection was terminated once 250,000 words per source was collected in April 2018.
 

### 2019-02-09 pilot_manuscript.Rmd
idk i reinstalled papaja??? also, small update to citations

@@
 author_note: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 
@@
 
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@CITE_rvest].
+Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016].
 Using this dataset, we identified word count and average word count per source.

### 2019-02-09 pilot_manuscript.tex
idk i reinstalled papaja??? also, small update to citations

@@
   \title{Moral Foundations of U.S. Political News Organizations}
-    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan, Ph.D.\textsuperscript{2}}
+    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan,
+Ph.D.\textsuperscript{2}}
     \date{}
@@
 
-\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-William Padfield is a master's degree candidate in psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
+\authornote{ William Padfield is a master's degree candidate
+in psychology at Missouri State University. This thesis partially
+fulfills the requirements for the Master of Science degree in
+Psychology.
 
 Correspondence concerning this article should be addressed to William E.
-Padfield, 901 S.
-National Ave, Springfield, MO, 65897.
-E-mail: \href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
+Padfield, 901 S. National Ave, Springfield, MO, 65897. E-mail:
+\href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
 
 \abstract{
-Enter abstract here. Each new line herein must be indented, like this line.
+The media ecosystem has grown, and political opinions have diverged such
+that there are competing conceptions of objective truth. Commentators
+often point to political biases in news coverage as a catalyst for this
+political divide. The Moral Foundations Dictionary (MFD) facilitates
+identification of ideological leanings in text through frequency of the
+occurrence of certain words. Through web scraping, the researchers
+extracted articles from popular news sources' websites, calculated MFD
+word frequencies, and identified words' respective valences. This
+process attempts to uncover news outlets' positive or negative
+endorsements of certain moral dimensions concomitant with a particular
+ideology. In Experiment 1, the researchers gathered poltical articles
+from four sources. They were unable to reveal significant differences in
+moral or political endorsements, but they solidified the method to be
+employed in further research. In Experiment 2, the researchers will
+expand their number of sources to 10 and will analyze articles that
+pertain to the 2018 confirmation hearings of U.S. Supreme Court Justice
+Brett Kavanaugh. This topic was selected due to the moral disputes
+associated with his nomination.
 
@@
 
-In the United States, today's media landscape affords consumers a multitude of options for obtaining political news.
-Since the advent of cable news networks and the World Wide Web in the last decades of the twentieth century, consumers have gained access to an ever-expanding menagerie of news sources, many of which can be called up via a simple click, touch, or swipe.
-Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
-For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant respectively.
-These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
-Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
-Specifically, the use of differing moral language in political articles might be an indicator of political bias in news media.
+In the United States, today's media landscape affords consumers a
+multitude of options for obtaining political news. Since the advent of
+cable news networks and the World Wide Web in the last decades of the
+twentieth century, consumers have gained access to an ever-expanding
+menagerie of news sources, many of which can be called up via a simple
+click, touch, or swipe. Concurrent with this growth in available news
+sources, concerns regarding political bias in news reporting have
+entered public consciousness. For example, commentators argue that
+networks including Fox News Channel and MSNBC communicate political news
+from a conservative and liberal slant, respectively. These purported
+biases have been a cause for concern given the potential for incomplete
+or inaccurate news reporting potentially resulting from these biases.
+Given the inherently moral nature of many political arguments and
+positions, bias in news reporting might manifest as differing moral
+appeals. Specifically, the use of differing moral language in political
+articles might be an indicator of political bias in news media.
 
-Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
-Starting chiefly in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
-Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of \enquote{morality.} Concerns regarding operationalization remain an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
+Morality and ethics have been of interest to thinkers, academics, and
+philosophers since antiquity. Starting chiefly in the twentieth century,
+a scientific approach to humans' understanding of morality emerged under
+the domain of psychology. Theories attempting to explain the development
+and application of people's moral intuitions built the foundation for
+the subfield of moral psychology. As the field developed, however,
+considerable debate has taken place regarding operational definitions of
+\enquote{morality.} Concerns regarding operationalization remain an
+issue in the field in the twenty-first century as researchers attempt to
+infer moral and political leanings from text and speech.
 
-\hypertarget{moral-foundations-theory}{%
-\subsection{Moral Foundations Theory}\label{moral-foundations-theory}}
+\subsection{Moral Foundations Theory}\label{moral-foundations-theory}
 
-As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg (Haidt \& Graham, 2007).
-Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance ({\textbf{???}}).
-Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
-Similarly, Kohlberg found people typically start with a \enquote{pre-conventional} understanding of morality during infancy in which children understand \enquote{right} and \enquote{wrong} purely in terms of how they interact with resultant experiences of rewards and punishment.
-Typically, people progress through several steps until they reach a \enquote{post-conventional} ethics.
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their \enquote{self-chosen ethical principles} ({\textbf{???}}).
-From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality (Haidt \& Graham, 2007).
+As a discipline, modern moral psychology started in the late 1960s with
+Lawrence Kohlberg (Haidt \& Graham, 2007). Kohlberg's research
+popularized his theory of the development of moral reasoning. This
+theory establishes the steps of moral reasoning through which humans
+proceed as their cognitive structures assume higher levels of
+sophistication and nuance (Kohlberg \& Hersh, 1977). Kohlberg borrowed
+from Jean Piaget's stages of cognitive development in which children
+progress from the sensorimotor through to the formal operations stage.
+Similarly, Kohlberg found people typically start with a
+\enquote{pre-conventional} understanding of morality during infancy in
+which children understand \enquote{right} and \enquote{wrong} purely in
+terms of how they interact with resultant experiences of rewards and
+punishment. Typically, people progress through several steps until they
+reach a \enquote{post-conventional} ethics. People who have reached the
+post-conventional stage are said to be able to weigh competing
+abstractions and reason their way to a conclusion that promotes justice
+based upon their \enquote{self-chosen ethical principles} (Kohlberg \&
+Hersh, 1977). From Kohlberg's perspective, issues of justice and
+fairness comprise the foundation of morality (Haidt \& Graham, 2007).
 This view persisted until it encountered criticism in the early 1980s.
 
-Kohlberg's conception of morality faced major scrutiny from psychologist Carol Gilligan.
-In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women (Haidt \& Graham, 2007).
-Gilligan drew attention to purported differences in the ways men and women are taught to relate to self and others.
-She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-She pushes back against Kohlberg's assumption that moral development replaces \enquote{rule of brute force,} as enforced by men, with the justice-based \enquote{rule of law.} According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law ({\textbf{???}}).
-Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
-Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring ({\textbf{???}}).
-This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring (Haidt \& Graham, 2007).
-While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
+Kohlberg's conception of morality faced major scrutiny from psychologist
+Carol Gilligan. In 1982, Gilligan criticized Kohlberg's theory on the
+grounds that it focused solely on the moral concerns of men, and that it
+ignored those of women (Haidt \& Graham, 2007). Gilligan drew attention
+to purported differences in the ways men and women are taught to relate
+to self and others. She offered a historic argument contending women
+have traditionally filled roles related to caring and nurturing. She
+pushes back against Kohlberg's assumption that moral development
+replaces \enquote{rule of brute force,} as enforced by men, with the
+justice-based \enquote{rule of law.} According to Gilligan, this
+assumption implies women are less morally developed, owing to their
+absence both in masculine displays of violence as well as in enforcement
+of the law (Gilligan, 1982). Gilligan argues for the existence of a
+distinct, but equal development process that women and girls must
+undergo in order to develop their moral selves. Stark differences in the
+ways women are traditionally taught to interact with their social world
+cause them to develop ethical systems based upon their non-aggressive
+relationships with others. Gilligan thus asserted morality was built
+upon an alternative moral foundation: caring (Gilligan, 1982). This
+debate between competing conceptions of morality did not resolve until
+Gilligan and Kohlberg conceded the existence of two moral foundations:
+justice and caring (Haidt \& Graham, 2007). While this new direction in
+moral psychology appeared to represent a more inclusive outlook on the
+construct, these novel ideas would soon be challenged on the grounds of
+its apparent western-centric outlook.
 
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain (Haidt \& Graham, 2007).
-The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals (Haidt \& Graham, 2007).
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007).
+Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a
+method by which to capture the entirety of humans' moral domain (Haidt
+\& Graham, 2007). The researchers argued older theories of moral
+psychology were focused primarily on issues of justice, fairness, and
+caring - individually focused foundations of morality that align with
+the beliefs of political liberals (Haidt \& Graham, 2007). In other
+words, moral psychology ignored the valid moral foundations of
+conservatives. Moral Foundations Theory (MFT) holds that people's moral
+domain can be mapped by quantifying their endorsement of five moral
+foundations: \emph{harm/care}, \emph{fairness/reciprocity},
+\emph{ingroup/loyalty}, \emph{authority/respect}, and
+\emph{purity/sanctity} (Haidt \& Graham, 2007).
 
-In their brief overview of the history of moral psychology, Graham, Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
-Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
-Such a system, they argued, did not account for moral concerns outside of the western world (Graham et al., 2009).
-Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.), and the \enquote{ethic of divinity}" - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
-In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
+In their brief overview of the history of moral psychology, Graham,
+Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's
+objections to moral psychology as it stood in the late 1980s. Their
+criticism centered on the fact moral psychology concerned itself with
+issues regarding justice and individuals' rights. Such a system, they
+argued, did not account for moral concerns outside of the western world
+(Graham et al., 2009). Individually focused concerns can be grouped
+under an overarching \enquote{ethic of autonomy,} which was thought to
+be one of three ethics upon which humans base moral decisions. The other
+two ethics were the \enquote{ethic of community} (comprising one's duty
+to their family, tribe, etc.), and the \enquote{ethic of divinity}" -
+representing one's duty not to defile their God-given body and soul
+(Graham et al., 2009). In the 2000s, Haidt and Graham (2007) took this
+line of reasoning further in their assertion that moral psychology
+favored certain political ideologies over others.
 
-Haidt and Graham settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology (Graham et al., 2011).
-The researchers attempted to locate virtues and morals corresponding to \enquote{evolutionary thinking.} For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the \emph{fairness/reciprocity} foundation.
-Additionally, evolutionary literature on disgust and its correlation to human behavior regarding food and sex informed the \emph{purity/sanctity} foundation (Graham et al., 2011).
-The researchers identified the five \enquote{top candidates} for the foundations of human cultures' morality (Graham et al., 2011).
+Haidt and Graham settled on these specific foundations after the
+completion of a literature survey of research in anthropology and
+evolutionary psychology (Graham et al., 2011). The researchers attempted
+to locate virtues and morals corresponding to \enquote{evolutionary
+thinking.} For instance, the researchers cited Mauss' work on reciprocal
+gift-giving, which informed the establishment of the
+\emph{fairness/reciprocity} foundation. Additionally, evolutionary
+literature on disgust and its correlation to human behavior regarding
+food and sex informed the \emph{purity/sanctity} foundation (Graham et
+al., 2011). The researchers identified the five \enquote{top candidates}
+for the foundations of human cultures' morality (Graham et al., 2011).
 
-The first two foundations (\emph{harm/care} and \emph{fairness/reciprocity}) are termed the \enquote{individualizing foundations,} as they are centered on the concerns of individuals rather than groups.
-\emph{Harm/care} represents an endorsement of compassion and kindness, while opposing cruelty and harm.
-\emph{Fairness/reciprocity} represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
-The other three foundations (\emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}) are the \enquote{binding} foundations, owing to their focus on group-related concerns, rather than those of individuals.
-\emph{Ingroup/loyalty} represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
-\emph{Authority/respect} represents an endorsement of social hierarchies and traditions while denigrating disobedience.
-Finally, \emph{purity/sanctity} represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony (Haidt \& Graham, 2007).
-Liberals tend to endorse the individualizing foundations more than conservatives.
-Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
-It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations (Graham et al., 2009).
+The first two foundations (\emph{harm/care} and
+\emph{fairness/reciprocity}) are termed the \enquote{individualizing
+foundations,} as they are centered on the concerns of individuals rather
+than groups. \emph{Harm/care} represents an endorsement of compassion
+and kindness, while opposing cruelty and harm.
+\emph{Fairness/reciprocity} represents concerns centered on guaranteeing
+individual rights as well as justice and equality among all people. The
+other three foundations (\emph{ingroup/loyalty},
+\emph{authority/respect}, and \emph{purity/sanctity}) are the
+\enquote{binding} foundations, owing to their focus on group-related
+concerns, rather than those of individuals. \emph{Ingroup/loyalty}
+represents endorsements of patriotism and heroism and discourages
+nonconformity and dissent. \emph{Authority/respect} represents an
+endorsement of social hierarchies and traditions while denigrating
+disobedience. Finally, \emph{purity/sanctity} represents concerns
+regarding chastity and piety, while discouraging vices and indulgences,
+including lust, avarice, and gluttony (Haidt \& Graham, 2007). Liberals
+tend to endorse the individualizing foundations more than conservatives.
+Conservatives, on the other hand, tend to endorse the binding
+foundations more than liberals. It should be noted, however,
+conservatives also tend to endorse all five foundations equally,
+implying they base moral judgments on all foundations (Graham et al.,
+2009).
 
-\hypertarget{moral-foundations-dictionary}{%
-\subsection{Moral Foundations Dictionary}\label{moral-foundations-dictionary}}
+\subsection{Moral Foundations
+Dictionary}\label{moral-foundations-dictionary}
 
-In order to capture language's role in moral and political reasoning, Graham et al.
-(2009) formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
-The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-The researchers created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count (LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
-The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: \enquote{Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus} (Graham et al., 2009).
-This sentence added to the \emph{authority/respect} total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
-The researchers eliminated this sentence from the \emph{authority/respect} raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions (Graham et al., 2009).
+In order to capture language's role in moral and political reasoning,
+Graham et al. (2009) formulated the Moral Foundations Dictionary (MFD)
+in order to capture moral reasoning and justification as used in speech
+and text. The MFD is composed of 259 words, with around 50 words
+assigned to each of the five foundations. The researchers created a
+preliminary list of words that they believed would be associated with
+the five foundations. Then, using the Linguistic Inquiry and Word Count
+(LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they
+analyzed transcripts of liberal and conservative Christian sermons in
+order to obtain frequencies of the occurrence of words from the
+researchers' initial list. The researchers manually checked the results
+from LIWC in order to make sure the results make sense given the
+contexts and rhetorical devices used in the sermons, as word frequency
+analysis ignores sentence context. The researchers offered the following
+example from a Unitarian sermon as a demonstration of ambiguous
+statements requiring human verification: \enquote{Don't let some
+self-interested ecclesiastical or government authority tell you what to
+believe, but read the Bible with your own eyes and open your heart
+directly to Jesus} (Graham et al., 2009). This sentence added to the
+\emph{authority/respect} total in LIWC's analysis, but it appears to
+suggest that one should reject authority in this context. The
+researchers eliminated this sentence from the \emph{authority/respect}
+raw count on account of this discrepancy between the use of
+authority-related words and the speaker's clear intentions (Graham et
+al., 2009).
 
-Similar to previous research on Moral Foundations Theory, liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than conservative ministers.
-Conversely, conservative ministers used \emph{authority} and \emph{purity} words more often than liberal ministers.
-However, conservative ministers did not use \emph{ingroup/loyalty} words more than liberals.
-Rather, liberal ministers used words pertaining to \emph{ingroup/loyalty}, but in contexts that promote rebellion and independence - causes \emph{opposite} to positive endorsements of that foundation (Graham et al., 2009).
+Similar to previous research on Moral Foundations Theory, liberal
+ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words
+more often than conservative ministers. Conversely, conservative
+ministers used \emph{authority} and \emph{purity} words more often than
+liberal ministers. However, conservative ministers did not use
+\emph{ingroup/loyalty} words more than liberals. Rather, liberal
+ministers used words pertaining to \emph{ingroup/loyalty}, but in
+contexts that promote rebellion and independence - causes
+\emph{opposite} to positive endorsements of that foundation (Graham et
+al., 2009).
 
-To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurrence of words in a given text from the foundation's respective word list.
-As such, most analyses assume that zero percent occurrence is indicative of no endorsement, while any non-zero percent occurrence indicates endorsement of the foundation.
-This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
-A quick glance at the MFD words for \emph{harm/care} reveals the presence of words that are more closely associated with universally accepted conceptions of \emph{harm} over \emph{care} and vice-versa (Graham et al., 2009).
-For example, the word \enquote{cruel} has relatively negative connotations compared to \enquote{benefit.} For the \emph{harm/care} foundation, it is conceivable that use of the word \enquote{cruel} might indicate a greater attentional focus of the idea of \emph{harm} rather than \emph{care}.
+To this point, most text analysis utilizing the Moral Foundations
+Dictionary operationalizes endorsement of any one of the foundations as
+percent occurrence of words in a given text from the foundation's
+respective word list. As such, most analyses assume that zero percent
+occurrence is indicative of no endorsement, while any non-zero percent
+occurrence indicates endorsement of the foundation. This operational
+definition may not be sufficient in describing the true nature of the
+writer or speaker's endorsement of one of the sets of moral intuitions.
+A quick glance at the MFD words for \emph{harm/care} reveals the
+presence of words that are more closely associated with universally
+accepted conceptions of \emph{harm} over \emph{care} and vice-versa
+(Graham et al., 2009). For example, the word \enquote{cruel} has
+relatively negative connotations compared to \enquote{benefit.} For the
+\emph{harm/care} foundation, it is conceivable that use of the word
+\enquote{cruel} might indicate a greater attentional focus of the idea
+of \emph{harm} rather than \emph{care}.
 
-For \emph{harm/care}, the definition of the foundation, as well as its name, clearly distinguishes between two somewhat opposite sides of an attentional continuum, with \emph{harm} on the negative end and \emph{care} on the positive side.
-In other words, the entries in the MFD for \emph{harm/care} have somewhat clear positive and negative valences.
-The same pattern can be seen in the MFD entries for the other four foundations.
-\emph{Purity/sanctity} features words that likely have a negative valence to most observers, including \enquote{disease}" and \enquote{trash,} along with more positive words, including \enquote{right} and \enquote{sacred} (Graham et al., 2009).
-These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from \emph{harm/care}: \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}.
-The latter four foundations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of \emph{fairness/reciprocity}.
+For \emph{harm/care}, the definition of the foundation, as well as its
+name, clearly distinguishes between two somewhat opposite sides of an
+attentional continuum, with \emph{harm} on the negative end and
+\emph{care} on the positive side. In other words, the entries in the MFD
+for \emph{harm/care} have somewhat clear positive and negative valences.
+The same pattern can be seen in the MFD entries for the other four
+foundations. \emph{Purity/sanctity} features words that likely have a
+negative valence to most observers, including \enquote{disease}" and
+\enquote{trash,} along with more positive words, including
+\enquote{right} and \enquote{sacred} (Graham et al., 2009). These
+dichotomies, however, bring up other questions regarding the definition
+and names of the other four foundations apart from \emph{harm/care}:
+\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
+\emph{authority/respect}, and \emph{purity/sanctity}. The latter four
+foundations have names that are harder to understand as a valence
+continuum, as the concepts in the names are more similar, even to the
+point of being virtually synonymous in the case of
+\emph{fairness/reciprocity}.
 
-When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
-How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
-If 2\% of a politician's speech features positive words (i.e., \enquote{benefit} and \enquote{defend}) from the MFD \emph{harm/care} list, how can researchers be sure the level and nature of the speaker's \enquote{endorsement} of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the \emph{harm/care} list?
-They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the \emph{harm/care} spectrum.
+When considering the issue of positive versus negative valence in MFD
+words, the question of how texts are analyzed vis-a-vis the MFD remains.
+How can raw percentage of MFD word occurrence capture the valence and
+focus of the writer or speaker? If 2\% of a politician's speech features
+positive words (i.e., \enquote{benefit} and \enquote{defend}) from the
+MFD \emph{harm/care} list, how can researchers be sure the level and
+nature of the speaker's \enquote{endorsement} of the foundation equals
+that of another politician whose speech contained negatively connoted
+MFD words from the \emph{harm/care} list? They would have equal
+endorsements as far as the numbers are concerned, but the words used and
+focus given are on opposite sides of the \emph{harm/care} spectrum.
 
-This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The Moral Foundations Questionnaire (MFQ), which was developed subsequent to the MFD, measures individuals' endorsements of each of the foundations using a six-point scale (Graham et al., 2011).
-The questionnaire is made up of judgment items and relevance items.
-Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
-An example of such a statement reads: \enquote{It can never be right to kill another human being} (Graham et al., 2011).
-Relevance items gauge the respondent's opinion regarding the importance of foundation-related concerns.
-For example, the respondent is directed to rate how important the following situation is to their sense of morals: \enquote{whether or not someone did something disgusting.} This example measures the relevance of the \emph{purity/sanctity} foundations.
-Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ (Graham et al., 2011).
+This issue is compounded by the fact the Moral Foundations Questionnaire
+(MFQ) and its subscales assume endorsement lies on a continuum. The
+Moral Foundations Questionnaire (MFQ), which was developed subsequent to
+the MFD, measures individuals' endorsements of each of the foundations
+using a six-point scale (Graham et al., 2011). The questionnaire is made
+up of judgment items and relevance items. Judgment items are phrased
+such that the respondent signals their agreement or disagreement with
+straightforward statements. An example of such a statement reads:
+\enquote{It can never be right to kill another human being} (Graham et
+al., 2011). Relevance items gauge the respondent's opinion regarding the
+importance of foundation-related concerns. For example, the respondent
+is directed to rate how important the following situation is to their
+sense of morals: \enquote{whether or not someone did something
+disgusting.} This example measures the relevance of the
+\emph{purity/sanctity} foundations. Each foundation has a judgment and
+relevance subscale, totaling 10 subscales for the MFQ (Graham et al.,
+2011).
 
-The aforementioned ambiguity of the Moral Foundations Dictionary as an instrument becomes clearer upon closer examination of the items in the Moral Foundations Questionnaire.
-One item under the \emph{fairness/reciprocity} judgment subscale reads, \enquote{Justice is the most important requirement for a society} (Graham et al., 2011).
-The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning \enquote{strongly disagree} at 1 to \enquote{strongly agree} at 6.
-While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
-When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they \enquote{slightly agree} with the statement (Graham et al., 2011).
-This specificity is not present in most analyses involving the MFD and percent occurrence, unless they also take into account the valence of the words used in the text or speech of interest.
+The aforementioned ambiguity of the Moral Foundations Dictionary as an
+instrument becomes clearer upon closer examination of the items in the
+Moral Foundations Questionnaire. One item under the
+\emph{fairness/reciprocity} judgment subscale reads, \enquote{Justice is
+the most important requirement for a society} (Graham et al., 2011). The
+survey respondent must select a number on a scale from 1 to 6 indicating
+responses spanning \enquote{strongly disagree} at 1 to \enquote{strongly
+agree} at 6. While the scales in the MFQ do not represent true valence
+as it pertains to individual words, it does allow for a greater degree
+of specificity in terms of an individual's endorsement of a particular
+moral foundation. When a respondent selects a 4 for the aforementioned
+MFQ statement, they clearly are indicating they \enquote{slightly agree}
+with the statement (Graham et al., 2011). This specificity is not
+present in most analyses involving the MFD and percent occurrence,
+unless they also take into account the valence of the words used in the
+text or speech of interest.
 
-\hypertarget{valence}{%
-\subsection{Valence}\label{valence}}
+\subsection{Valence}\label{valence}
 
-Borrowing from Osgood's work in the 1950s, Bradley and Lang (1999) recognized valence as one of three related dimensions comprising emotion when developing their Affective Norms for English Words (ANEW).
-As mentioned before, \enquote{valence,} the first dimension, denotes the pleasantness of a given word.
-\enquote{Arousal,} the second dimension, describes the stimulating nature of a word.
-Lastly, \enquote{dominance} or \enquote{control} describes the extent to which a word makes one feel in or out of control (Bradley \& Lang, 1999).
-The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Mannikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
+Borrowing from Osgood's work in the 1950s, Bradley and Lang (1999)
+recognized valence as one of three related dimensions comprising emotion
+when developing their Affective Norms for English Words (ANEW). As
+mentioned before, \enquote{valence,} the first dimension, denotes the
+pleasantness of a given word. \enquote{Arousal,} the second dimension,
+describes the stimulating nature of a word. Lastly, \enquote{dominance}
+or \enquote{control} describes the extent to which a word makes one feel
+in or out of control (Bradley \& Lang, 1999). The researchers developed
+ANEW by presenting participants with a list of 100-150 words and asking
+for them to rate the word on all three dimensions using the
+Self-Assessment Mannikin (SAM), which allows ratings along either a
+nine-point scale when using traditional paper instruments or a
+twenty-point scale when using a computerized version.
 
-Participants saw the stimulus word and responded on each scale.
-The valence scale featured a smiling figure at one end (representing pleasantness) and a frowning figure at the other end (for unpleasantness).
-The arousal scale had a \enquote{wide-eyed} figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
-Finally, the dominance scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end (Bradley \& Lang, 1999).
-The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words (Bradley \& Lang, 1999).
-ANEW represented an important first step in establishing affective norms for large numbers of English words.
-However, later researchers found the 1,040-word list to be limiting for a language consisting of thousands of words.
+Participants saw the stimulus word and responded on each scale. The
+valence scale featured a smiling figure at one end (representing
+pleasantness) and a frowning figure at the other end (for
+unpleasantness). The arousal scale had a \enquote{wide-eyed} figure at
+one end with a sleepy figure at the other, representing stimulating and
+unstimulating respectively. Finally, the dominance scale featured a
+large figure, indicating the highest degree of control, at one end and a
+small figure, indicating a lack of control, at the other end (Bradley \&
+Lang, 1999). The end result of this procedure yielded affective norms
+along the three dimensions for 1,040 English words (Bradley \& Lang,
+1999). ANEW represented an important first step in establishing
+affective norms for large numbers of English words. However, later
+researchers found the 1,040-word list to be limiting for a language
+consisting of thousands of words.
 
-Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e., \enquote{watch} rather than \enquote{watched} and \enquote{watching}).
-The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory (Warriner et al., 2013).
-They argue the list of words included in ANEW is sufficient for small-scale factorial research designs, but the list is \enquote{prohibitively small} for larger-scale \enquote{megastudies} that are common in psycholinguistic research today (Warriner et al., 2013).
+Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the
+list of words with affective norms to 13,915 English lemmas, the base
+forms of words without inflection (i.e., \enquote{watch} rather than
+\enquote{watched} and \enquote{watching}). The researchers recognized
+the importance of affective norms in several areas of study, including
+emotion, language processing, and memory (Warriner et al., 2013). They
+argue the list of words included in ANEW is sufficient for small-scale
+factorial research designs, but the list is \enquote{prohibitively
+small} for larger-scale \enquote{megastudies} that are common in
+psycholinguistic research today (Warriner et al., 2013).
 
-In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media ({\textbf{???}}).
-This data collection resulted in the final list of 13,915 lemmas.
-Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
-Participants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
-The researchers used a nine-point scale similar to the one used by Bradley and Lang (1999) when collecting ratings for ANEW (Warriner et al., 2013).
+In order to source a large number of lemmas for affective ratings, the
+researchers drew from several validated sources. These include the
+30,000 lemmas with age-of-acquisition (average age at which a particular
+word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and
+Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US
+corpus consisting of subtitles from various forms of visual media (New,
+Brysbaert, Veronis, \& Pallier, 2007). This data collection resulted in
+the final list of 13,915 lemmas. Lists of 346-350 words were presented
+to participants recruited through the Amazon Mechanical Turk subject
+pool. Participants rated the words along one of the three dimensions,
+unlike the ANEW project in which participants rated each word along all
+three dimensions at once. The researchers used a nine-point scale
+similar to the one used by Bradley and Lang (1999) when collecting
+ratings for ANEW (Warriner et al., 2013).
 
 The researchers noted several points of interest upon observing ratings.
-First, they found that valence and dominance ratings had a negative skew, indicating more words elicited feelings of happiness and control than their respective opposites.
-Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
-This U-shape indicates words with high degrees of positivity and negativity elicited higher arousal (Warriner et al., 2013).
-These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
+First, they found that valence and dominance ratings had a negative
+skew, indicating more words elicited feelings of happiness and control
+than their respective opposites. Also, when examining the relationship
+between valence and arousal ratings, the researchers found a U-shaped
+relationship. This U-shape indicates words with high degrees of
+positivity and negativity elicited higher arousal (Warriner et al.,
+2013). These observations along with the now-greatly expanded list of
+affective norms has been applied to several lines of inquiry in
+psycholinguistics.
 
-Warriner and Kuperman (2015) utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in language.
-The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with positive valence were also used more frequently (Warriner \& Kuperman, 2015).
-While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the Warriner et al.
-(2013) list in emotional studies.
+Warriner and Kuperman (2015) utilized the new affective norms list in
+order to investigate the validity of the Pollyanna hypothesis, or the
+prevalence of a generally optimistic outlook in humans as reflected in
+language. The researchers were able to conclude the existence of a
+greater number of positive-valence English words in the list of 13,915
+lemmas. Additionally, after observing token frequency in a number of
+text corpora, including SUBTLEX-US, the Corpus for Contemporary American
+English (COCA), the British National Corpus (BNC), Touchstone Applied
+Science Associates, Inc. Corpus (TASA), and the corpus used for the
+Hyperspace Analogue to Language model (HAL), the researchers found that
+words with positive valence were also used more frequently (Warriner \&
+Kuperman, 2015). While the researchers concede the possibility of an
+acquiescence bias in ratings as a possible explanation for the observed
+positivity bias, this investigation represents one application of the
+Warriner et al. (2013) list in emotional studies.
 
 In addition to applications in emotion research, the Warriner et al.
-(2013) norms have been utilized in cognitive research as well.
-One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
-The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
-First, Kuperman et al.
-(2014) found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
-The researchers also concluded that words causing higher arousal tend to have slower decision times than less-arousing words.
-They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
-They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
-Finally, Kuperman et al.
-(2014) found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks (Kuperman et al., 2014).
-This research serves as further evidence that the Warriner et al.
-(2013) list can be used for research inquiries both within and without the field of psycholinguistics.
+(2013) norms have been utilized in cognitive research as well. One
+cognition-based study investigates the relationship between emotion and
+response latencies in word recognition. Kuperman, Estes, Brysbaert, and
+Warriner (2014) sought to use these new norms to fill in the knowledge
+gaps regarding variance in word recognition. The researchers drew
+several conclusions regarding emotion and word recognition (specifically
+in naming and lexical decision tasks - two cognitive processing tasks
+wherein a participant has to read aloud or judge a word for its
+lexicality). First, Kuperman et al. (2014) found slower decision-making
+and reading times in negative-valence words, faster times in neutral
+words, and even faster times in words with positive valence. The
+researchers also concluded that words causing higher arousal tend to
+have slower decision times than less-arousing words. They found valence
+had a stronger effect on recognition than arousal (both effects were
+independent, not interactive). They found an interaction between emotion
+and word frequency such that valence and arousal are more effective on
+lower frequency words than high frequency words. Finally, Kuperman et
+al. (2014) found a greater effect of valence and arousal on response
+latency for lexical decision tasks than for naming tasks (Kuperman et
+al., 2014). This research serves as further evidence that the Warriner
+et al. (2013) list can be used for research inquiries both within and
+without the field of psycholinguistics.
 
-In the present studies, the researchers used the Warriner et al.
-(2013) list in order to denote the valence of the words appearing in the news articles scraped from the internet.
-Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
-The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
-Specifically, valences were used to weight the MFD words by their relative degree of positivity or negativity.
-Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
+In the present studies, the researchers used the Warriner et al. (2013)
+list in order to denote the valence of the words appearing in the news
+articles scraped from the internet. Valence was considered as another
+independent variable and its relationship with the words comprising the
+Moral Foundations Dictionary were of chief interest to the researchers.
+The valence was used as a means to determine whether individual words in
+the MFD represented more positive aspects of their respective foundation
+or if they denoted a more negative aspect of the foundation.
+Specifically, valences were used to weight the MFD words by their
+relative degree of positivity or negativity. Incorporating word valence
+into a study involving the MFD is meant to alleviate some of the issues
+regarding the aforementioned ambiguity regarding the words in the Moral
+Foundations Dictionary.
 
-\hypertarget{news-media-and-politics}{%
-\subsection{News Media and Politics}\label{news-media-and-politics}}
+\subsection{News Media and Politics}\label{news-media-and-politics}
 
-Research into politics, language, and media has illuminated the complex relationships between all three.
-Any politically-oriented discussion of word occurrence as an implication of moral or political position assumes that language and ideology are intrinsically linked.
-Deborah Cameron (2006) points out the expressive nature of ideological beliefs and how that expression is conveyed through language, thus implying a connection between ideology and language.
-She goes on to criticize the notion that language is either the \enquote{pre-existing raw material} used to shape ideologies or the \enquote{post-hoc vehicle} for their propagation.
-Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies (Cameron, 2006).
-Owing to the fact the Moral Foundations Dictionary was developed in order to assess the moral, which includes the ideological, orientation of discourse, its purported ability to assess parts of the structure of language (vocabulary) for ideological lean is of chief interest to the researchers in the present study.
+Research into politics, language, and media has illuminated the complex
+relationships between all three. Any politically-oriented discussion of
+word occurrence as an implication of moral or political position assumes
+that language and ideology are intrinsically linked. Deborah Cameron
+(2006) points out the expressive nature of ideological beliefs and how
+that expression is conveyed through language, thus implying a connection
+between ideology and language. She goes on to criticize the notion that
+language is either the \enquote{pre-existing raw material} used to shape
+ideologies or the \enquote{post-hoc vehicle} for their propagation.
+Rather, the structure of language itself is shaped by ideology and
+social processes even when it is used to explain or express ideologies
+(Cameron, 2006). Owing to the fact the Moral Foundations Dictionary was
+developed in order to assess the moral, which includes the ideological,
+orientation of discourse, its purported ability to assess parts of the
+structure of language (vocabulary) for ideological lean is of chief
+interest to the researchers in the present study.
 
-The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S., Druckman, Jacobs, and Ostermeier (2004) considered political \enquote{issues} as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-According to the researchers, \enquote{image} priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality (Druckman et al., 2004).
-The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
-The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
+The use of language both to express and further an ideological goal has
+been documented in the techniques employed by candidates for political
+office in the U.S., Druckman, Jacobs, and Ostermeier (2004) considered
+political \enquote{issues} as communication that attempts to persuade
+constituents to vote for the candidates based on their strengths in
+matters of public policy. According to the researchers, \enquote{image}
+priming describes techniques deployed in order to sway votes based on
+favorable aspects of the candidate's behavior and personality (Druckman
+et al., 2004). The researchers investigated political issue and image
+priming on the part of candidates as implied by the disproportionate
+attention candidates paid to particular issues over others. The
+researchers found numerous examples of issue and image priming during
+the 1972 re-election campaign of Richard Nixon.
 
-They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
-Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence (Druckman et al., 2004).
-The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.~priming) issues related to energy, defense, and the economy.
-This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
+They linked the Nixon administration's awareness of the issues for which
+the president had public support to the issues he should emphasize (and
+prime) during the campaign. Likewise the researchers found evidence that
+Nixon's team was aware of negative evaluations of his warmth and
+trustworthiness, and thus took steps to prime his purportedly positive
+qualities, including strength and competence (Druckman et al., 2004).
+The researchers also cited research from Iyengar and Kinder (1987)
+suggesting the news media affected perceptions of President Jimmy
+Carter's competence by emphasizing (e.g., priming) issues related to
+energy, defense, and the economy. This focus implies news media may
+contribute to Americans' perception of politicians based on where the
+media places emphasis.
 
 There is a potential caveat regarding the validity of Druckman et al.
-(2004)'s findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
-({\textbf{???}}) point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
-Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
-Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
-({\textbf{???}}) point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
-Studies investigating perceptual priming have been \enquote{directly replicated in hundreds of labs} ({\textbf{???}}).
-This does not appear to be the case for social priming, as argued by ({\textbf{???}}).
+(2004)'s findings: reproductions of several studies purporting to
+demonstrate social priming effects have failed to replicate the original
+results. Pashler, Coburn, and Harris (2012) point out the distinction
+between perceptual and social (or goal) priming both in their
+operational definitions as well as their replicability. Perceptual
+priming often works through the inducement of a certain response from a
+related prime, as in, for example, semantic priming. Social (or goal)
+priming encompasses phenomena by which people exhibit complex behavioral
+changes subsequent to exposure to a prime. Pashler et al. (2012) point
+out well-known studies investigating social priming, including the use
+of elderly-related primes to induce slower walking speeds in
+participants. Studies investigating perceptual priming have been
+\enquote{directly replicated in hundreds of labs} (Pashler et al.,
+2012). This replication rate does not appear to be the case for social
+priming, as argued by Pashler et al. (2012).
 
-({\textbf{???}}) noticed the unusually large effect size values (Cohen's \emph{d}) reported by researchers studying social priming effects.
-The researchers reproduced two studies from ({\textbf{???}}) The first study attempted to prime participants by having them plot points on a Cartesian grid.
-The independent variable was priming condition and contained three levels: short, middle, and long distance.
-Those instructed to plot points further apart were hypothesized to express a higher degree of psychological distance regarding their family.
-The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
-({\textbf{???}}) concluded those two studies from ({\textbf{???}}) held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
+Pashler et al. (2012) noticed the unusually large effect size values
+(Cohen's \emph{d}) reported by researchers studying social priming
+effects. The researchers reproduced two studies from Williams and Bargh
+(2008) The first study attempted to prime participants by having them
+plot points on a Cartesian grid. The independent variable was priming
+condition and contained three levels: short, middle, and long distance.
+Those instructed to plot points further apart were hypothesized to
+express a higher degree of psychological distance regarding their
+family. The second study used the same priming conditions, but
+hypothesized that greater distance between points would prime
+participants to estimate fewer calories in unhealthy foods than those
+who were primed with shorter distances between points. Pashler et al.
+(2012) concluded those two studies from Williams and Bargh (2008) held
+little validity while also casting doubt on the prevalence of social
+priming effects themselves, based on the inability of other researchers
+to replicate previously reported effects in this area.
 
-While these concerns regarding the replication of social priming studies are valid and deserve further investigation, Druckman et al.
-(2004) does not purport to demonstrate a widespread effect of social priming on the American electorate.
-In other words, this reseach makes no claim to empirically supported priming effects.
-Rather, Druckman et al.
-(2004) chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
-These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
-As such, Druckman et al.
-(2004)'s research on Nixon serves as an example of language's potential utility in the propogation of desirable political opinions.
-The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
-The idea that even 1970s news media could contain political biases is of particular interest to the current study, which investigates similar phenomena in contemporary news media.
+While these concerns regarding the replication of social priming studies
+are valid and deserve further investigation, Druckman et al. (2004) does
+not purport to demonstrate a widespread effect of social priming on the
+American electorate. In other words, this reseach makes no claim to
+empirically supported priming effects. Rather, Druckman et al. (2004)
+chronicle the efforts on the part of the Nixon Administration to prop up
+the president's supposed strengths while downplaying his weaknesses.
+These tactics were deployed through the careful use of language in order
+to achieve the administration's political goals. As such, Druckman et
+al. (2004)'s research on Nixon serves as an example of language's
+potential utility in the propogation of desirable political opinions.
+The researcher's investigation of news media's focus on specific issues
+during the Carter Administration likewise provide an example of language
+as a potential conduit for the transfer of politically biased
+information. The idea that even 1970s news media could contain political
+biases is of particular interest to the current study, which
+investigates similar phenomena in contemporary news media.
 
-Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress (Clinton \& Enamorado, 2014).
-Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival.
-The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election (Clinton \& Enamorado, 2014).
+Other research into news media suggests certain media outlets, at least
+indirectly, may have an effect on the voting records of representatives
+in Congress (Clinton \& Enamorado, 2014). Specifically, the researchers
+identified a pattern of declining support for President Bill Clinton's
+policies chiefly among Republicans in the House of Representatives after
+the Fox News Channel began broadcasting on cable and satellite systems
+in their respective districts. As Fox News was, at the time of its
+launch in 1996, the only outwardly ideological national news network,
+the researchers were able to track its spread across the country and
+observe voting records of members of Congress both before and after Fox
+News' arrival. The researchers concluded that members of Congress,
+excluding those newly elected at the time of Fox News Channel's
+emergence, attempted to anticipate resultant conservative-leaning shifts
+among their constituents by bolstering their conservative voting record
+before the next election (Clinton \& Enamorado, 2014).
 
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
+Therefore, the current study sought to combine both methods related
+questions and extension/replication of previous moral foundation results
+found for liberal and conservative sources. First, the MFD was combined
+with previous research by the current authors (see below) and weighted
+by valence to create weighted percentages to better specify endorsement.
+Second, these weighted percentages were examined for their differences
+in across liberal and conservative news sources.
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\section{Experiment 1}\label{experiment-1}
 
-For Experiment 1, the researchers approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources genrally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
-Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
+\section{Method}\label{method}
 
-\hypertarget{sources}{%
-\subsection{Sources}\label{sources}}
+For Experiment 1, the researchers approached the study with the
+intention to answer a method question. That is, this portion of the
+current research was conducted in order to solidify the best method by
+which to analyze political news text under the Moral Foundations Theory
+framework while also alleviating some of the aforementioned valence
+problem observed in the Moral Foundations Dictionary. The researchers
+hypothesized the news sources genrally perceived as liberal leaning
+(\emph{NPR} and \emph{The New York Times}) would contain MFD words and
+valences indicating endorsements of the individualizing moral
+foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
+Additionally, the researchers hypothesized the two sources generally
+perceived to be conservative leaning (\emph{Fox News} and
+\emph{Breitbart}) would feature MFD words and valences indicating equal
+endorsement of all five foundations.
+
+\subsection{Sources}\label{sources}
 
 Political articles were collected from the websites of four notable U.S.
-news sources, a process known as web scraping.
-The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
-They were selected for their widespread recognition and the fact they are easily categorized (by the general public) according to perceived political lean.
-In general, \emph{The New York Times} and \emph{NPR} are perceived by many to have a liberal bias or lean.
-In contrast, Fox News and Breitbart are believed to have a conservative bias or lean (Mitchell, Matsa, Gottfried, \& Kiley, 2014).
-Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the \emph{R} script.
-For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
+news sources, a process known as web scraping. The sources were
+\emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox
+News}, and \emph{Breitbart}. They were selected for their widespread
+recognition and the fact they are easily categorized (by the general
+public) according to perceived political lean. In general, \emph{The New
+York Times} and \emph{NPR} are perceived by many to have a liberal bias
+or lean. In contrast, Fox News and Breitbart are believed to have a
+conservative bias or lean (Mitchell, Matsa, Gottfried, \& Kiley, 2014).
+Political articles in particular were identified and subsequently
+scraped by including the specific URL directing to each source's
+political content in the \emph{R} script. For example, rather than
+scrape from nytimes.com, which would return undesired results
+(non-political features, reviews, etc.), we instead included
+nytimes.com/section/politics so that more or less exclusively political
+content was obtained. All code for this manuscript can be found at
+\url{https://osf.io/5kpj7/}, and the scripts are provided inline with
+this manuscript written with the \emph{papaja} library (Aust \& Barth,
+2017).
 
-Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not growing at a similar pace as those from \emph{The New York Times} and \emph{Breitbart}.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content \enquote{archive.} The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
-Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
-We later ran a process in order to exclude any duplicate articles.
-\emph{Fox News} presented a similar issue.
-We discovered \emph{Fox News} utilized six URLs in addition to the regular politics page.
-These URLs led to pages containing content pertaining the U.S.
-Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
-Once again, duplicates were subsequently eliminated from any analyses.
+Identification of the sources' political URLs presented a problem for
+two of the sources owing to complications with how their particular
+sites were structured. While in the multi-week process of scraping
+articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were
+not growing at a similar pace as those from \emph{The New York Times}
+and \emph{Breitbart}. Upon investigation, we found another, more robust
+URL for political content from NPR: their politics content
+\enquote{archive.} The page structure on NPR's website was such that
+only a limited selection of articles is displayed to the user at a given
+time. Scraping both the archive and the normal politics page ensured we
+were obtaining most (if not all) new articles as they were published. We
+later ran a process in order to exclude any duplicate articles.
+\emph{Fox News} presented a similar issue. We discovered \emph{Fox News}
+utilized six URLs in addition to the regular politics page. These URLs
+led to pages containing content pertaining the U.S. Executive Branch,
+Senate, House of Representatives, Judicial Branch, foreign policy, and
+elections. Once again, duplicates were subsequently eliminated from any
+analyses.
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\subsection{Materials}\label{materials}
 
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset ({\textbf{???}}).
-Using this dataset, we identified word count and average word count per source.
-This process was run once daily starting on \emph{DATE} until \emph{DATE.} Starting on \emph{DATE,} the process was run twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected on \emph{DATE.}
+Using the \emph{rvest} library in the statistical package \emph{R}, we
+pulled body text for individual articles from each of the aforementioned
+sources (identified using CSS language) and compiled them into a dataset
+(Wickham, 2016). Using this dataset, we identified word count and
+average word count per source. This process was run once daily starting
+in February 2018 until March 2018. Starting in mid-March 2018, the
+process was run twice daily - once in the morning and again in the
+evening. Data collection was terminated once 250,000 words per source
+was collected in April 2018.
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsection{Data analysis}\label{data-analysis}
 
-Once data collection ended, the text was scanned using the \emph{ngram} package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017).
-This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
-At this point, duplicate articles were discarded.
+Once data collection ended, the text was scanned using the \emph{ngram}
+package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017).
+This package includes a word count function, which was used to remove
+articles that came through as blank text, as well as to eliminate text
+picked up from the Disqus commenting system used by certain websites. At
+this point, duplicate articles were discarded.
 
-The article text was processed using the \emph{tm} and \emph{ngram} packages in \emph{R} in order to render the text in lowercase, remove punctuation, and fix spacing issues (Feinerer \& Hornik, 2017).
-The individual words were then reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}).
-The same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
+The article text was processed using the \emph{tm} and \emph{ngram}
+packages in \emph{R} in order to render the text in lowercase, remove
+punctuation, and fix spacing issues (Feinerer \& Hornik, 2017). The
+individual words were then reduced to their stems (i.e., \emph{abused}
+was stemmed to \emph{abus}). The same procedure was applied to the MFD
+words and the words in the Warriner et al. (2013) dataset. Using the
+Warriner et al. (2013) dictionary, the words making up each of the five
+foundations in the MFD were matched to their respective valence value.
 
-Concurrent research by Jordan, Buchanan \& Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using one sample.
-The instruments will be analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity.
-Additionally, the researchers are investigating whether or not a reduced set of MFD words may likewise bolster the validity of the MFD.
-Depending on the results of that research, either an augmented or reduced Moral Foundations Dictionary may be utilized in this analysis rather than the original version.
+Concurrent research by Jordan, Buchanan, and Padfield (2019) is
+assessing the validity of both the Moral Foundations Questionnaire and
+the Moral Foundations Dictionary through a multi-trait multi-method
+analysis of the two instruments using multiple samples. The instruments
+and foundation areas are being analyzed against one another, in order to
+test reliability, as well as against the Congressional Record in order
+to test predictive validity for political orientation. The researchers
+were able to identify a number of potential new words that, if added to
+the MFD, could comprise a dictionary with greater validity, and less
+likelihood of zero percent texts, as this often occurs with the current
+MFD. Those results have informed this analysis, and their updated
+findings may change the underlying dictionary used in this analysis
+(albeit, we do not expect any changes in the results presented below).
 
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
-Therefore, for each article, the percentage of the number of \emph{harm/care} words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurence were multiplied by their \emph{z}-scored valence.
-Valences were \emph{z}-scored in order to eliminate any ambiguity regarding the direction of the valence.
-Positive values indicate positive valence, and negative values indicate negative valence.
-Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
+The source article words were compiled into a dataset where they were
+matched up with their counterparts in the MFD along with their valence
+and a percentage of their occurrence. Therefore, for each article, the
+percentage of the number of \emph{harm/care} words occurring in the
+articles were calculated, and this process was repeated for each of the
+foundations. Words' percent occurence were multiplied by their
+\emph{z}-scored valence. Valences were \emph{z}-scored in order to
+eliminate any ambiguity regarding the direction of the valence. Positive
+values indicate positive valence, and negative values indicate negative
+valence. Words were categorized in accordance to their MFD affiliation,
+creating a weighted sum for each moral foundation.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error (Gelman, 2006).
-Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
+To analyze if news sources adhered to differences in word use based on
+their target audience, we utilized a multilevel model (MLM) to analyze
+the data. MLM is a regression technique that allows one to control for
+the repeated measurement and nested structured of the data, which
+creates correlated error (Gelman, 2006). Using the \emph{nlme} library
+in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each
+foundation's weighted percentage was predicated here by the political
+lean of the news source, using the individual news sources as a random
+intercept to control for the structure of the data.
 
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 1.
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
+The multilevel model did not indicate the presence of any significant or
+practical effect of political lean for any of the five moral
+foundations. The strongest effect size was observed for the
+\emph{authority/respect} foundation, but the effect was in the opposite
+direction from what was originally hypothesized - liberal sources tended
+to use more \emph{authority/respect} words than did conservative
+sources. Descriptive and test statistics, \emph{p}-values and effect
+sizes (Cohen's \emph{d}) can be found in Table 1. To interpret the
+weighted scores, one can examine the mean and standard deviations for
+each. A zero score for the mean, with a non-zero standard deviation,
+would indicate a perfect balance of positive and negative words in each
+category, likely representing a neutral tone when all words are
+considered. Negative percentages would indicate more representation of
+the negative words in the MFD area, while positive percentages indicate
+an endorsement of the positive words in a MFD. Therefore, we suggest
+using the sign of the mean score to determine the directionality of the
+endorsement for the MFD (positive, neutral, negative), and the standard
+deviation to ensure that a zero score is not zero endorsement (i.e., a
+SD of zero indicates no words were used). Based on the weighted percent
+values for the five foundations, the researchers observed that MFD words
+seem to make up a small portion of the article text. Furthermore, the
+observed percentages and means appear to indicate a generally positive
+endorsement of all five foundations across both liberal and conservative
+sources.
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
-The results obtained in Experiment 1 did not confirm the hypothesis.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The strongest effect found was for the \emph{authority/respect} foundation owing to the fact its Cohen's \emph{d} value was greater than the other four foundations.
-However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
-This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
-It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
+The results obtained in Experiment 1 did not confirm the hypothesis. The
+researchers found little compelling evidence of an effect of partisan
+lean on MFD endorsement. The strongest effect found was for the
+\emph{authority/respect} foundation owing to the fact its Cohen's
+\emph{d} value was greater than the other four foundations. However, the
+effect was in the opposite direction of that which was hypothesized.
+Specifically, the results indicated that liberal leaning sources
+demonstrated higher positivity regarding that foundation than
+conservatives. This result is contrary not only to the research
+hypothesis for Experiment 1 but also to previous findings in Moral
+Foundations Theory research. It should be noted, however, the effect
+size was small and the relationship was not found to be statistically
+significant.
 
-Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
-The selection of the broad and amorphous topic of \enquote{political news} may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
-In short, the range of topics covered in Experiment 1 was likely too broad.
-The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
+Upon speculation, the researchers identified one possible reason for why
+the results were unable to confirm the hypothesis. The selection of the
+broad and amorphous topic of \enquote{political news} may have led to
+the scraping of large numbers of articles with little to no
+moral-centric content. Rather, many articles may have been, for example,
+simple reporting on congressional procedures that would leave little
+room for the use of moral language here, let alone words from the Moral
+Foundations Dictionary. In short, the range of topics covered in
+Experiment 1 was likely too broad. The possibility exists that a tighter
+focus on one political issue or event, especially one that (on the
+surface) has a stronger relationship with morality might be more
+illuminating for research in moral language in news media.
 
-Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-Generally speaking, the researchers believe their methodology to be sound.
-Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
-Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
-The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurence.
+Owing to the exploratory nature of Experiment 1, the researchers were
+afforded the opportunity to consider changes to the method to be
+utilized in Experiment 2. Generally speaking, the researchers believe
+their methodology to be sound. Web scraping methods and text processing
+remain viable methods for collecting large amounts of text and
+subsequently rendering that text in a form suitable for data analysis.
+Experiment 1 also demonstrated a method by which to address inherent
+problems in the Moral Foundations Dictionary relating to valence. The
+solution provided in Experiment 1 appears to provide insights into the
+MFD words where none previously existed. Finally, calculating weighted
+percentages and sums for each moral foundation provides an easily
+interpreted summary of MFD word positivity and occurence.
 
-While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
-The researchers identified two such changes that were subsequently employed in Experiment 2.
-First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
-politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court.
-In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
+While the methodology used in Experiment 1 features many strengths,
+there are aspects which could be strengthened for future studies. The
+researchers identified two such changes that were subsequently employed
+in Experiment 2. First, the researchers elected to include more news
+sources for web scraping and analysis in addition to the four used in
+Experiment 1. Second, the researchers chose to focus their data
+collection efforts exclusively on one event in U.S. politics: the
+nomination and confirmation of Justice Brett Kavanaugh to the U.S.
+Supreme Court. In Experiment 2, the researchers sought to confirm the
+usefulness and validity of the method as well as test a similar
+hypothesis as Experiment 1.
 
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
+\section{Experiment 2}\label{experiment-2}
 
-\hypertarget{kavanaugh-supreme-court-hearing}{%
-\subsection{Kavanaugh Supreme Court Hearing}\label{kavanaugh-supreme-court-hearing}}
+\subsection{Kavanaugh Supreme Court
+Hearing}\label{kavanaugh-supreme-court-hearing}
 
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 ({\textbf{???}}).
-Following allegations of sexual assault by high school classmate Dr.~Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
+In the wake of Justice Anthony Kennedy's retirement from the Supreme
+Court of the United States, President Donald Trump nominated Brett
+Kavanaugh as the new Associate Justice. Kavanaugh was previously on the
+U.S. Court of Appeals for the District of Columbia. The Senate Judiciary
+Committee began his confirmation hearing on September 4, 2018 (US
+Government, 2018a). Following allegations of sexual assault by high
+school classmate Dr.~Christine Blasey Ford, the committee postponed its
+vote on whether or not to open the confirmation to the entire Senate.
 
-On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh ({\textbf{???}}).
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television (O'Connell, 2018).
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 ({\textbf{???}}).
+On September 27, the committee questioned Dr.~Ford before commencing a
+second round of questioning for Judge Kavanaugh (US Government, 2018b).
+During the intervening weeks between hearings, two more women came
+forward with two separate allegations of sexual assault on the part of
+Kavanaugh. According to Nielsen reports, more than 20 million people
+watched the September 27 proceedings on television (O'Connell, 2018).
+This figure does not take into account viewers who watched online, nor
+does it account for viewers outside the United States. On September 28,
+the Senate Judiciary Committee voted to send the nomination to the
+Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a
+week-long FBI investigation on Kavanaugh and the allegations facing him,
+which the committee, and later the President, approved. The
+investigation concluded with no significant findings. The Senate voted
+50-48 to approve Kavanaugh's appointment on October 6, 2018 (US
+Government, 2018c).
 
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
+The Kavanaugh nomination, confirmation hearing, and eventual
+swearing-in, as well as the news media's coverage of all three events,
+feature many moral dimensions that likely differ depending on one's
+morals. On one side of the debate, Kavanaugh's Supreme Court tenure
+presents a prime opportunity to bring morality back into interpretation
+of the Constitution. Kavanaugh's confirmation creates a conservative
+stronghold among the justices on the court. Commentators have noted this
+might help advance a judicial agenda that backpedals certain rights
+previously upheld by the Supreme Court, including abortion and gay
+marriage - social issues challenged by their opponents at least
+partially on moral grounds. On the other side of the debate, the assault
+allegations have energized Kavanaugh's opponents to advocate for his
+rejection from the court owing to misdeeds resulting from Kavanaugh's
+own alleged lack of morals. Additionally, the moral duty of the Senate
+as the upper chamber in the U.S. legislature has been scrutinized in
+public discourse with respect to its handling of the assault allegations
+vis-a-vis Kavanaugh's confirmation.
 
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on the Kavanaugh confirmation hearing.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks before and two weeks after Kavanaugh's confirmation, owing to its prominence in the news.
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
+In contrast to Experiment 1, the researchers approached Experiment 2
+with the intention to confirm the method employed was valid for the
+analysis of the scraped text as well as for any inferences drawn from
+the analyses. For Experiment 2, the researchers hypothesized that news
+sources perceived as liberal will exhibit positive endorsements of the
+individualizing moral foundations (\emph{harm/care} and
+\emph{fairness/reciprocity}) in their articles reporting on the
+Kavanaugh confirmation hearing. News sources perceived as conservative
+are hypothesized to positively endorse all five foundations equally in
+their coverage of the Kavanaugh hearing. The researchers tested the
+hypothesis by analyzing the content scraped from news sources' web pages
+during the two weeks before and two weeks after Kavanaugh's
+confirmation, owing to its prominence in the news. The content will be
+analyzed for valence and moral alignment under Moral Foundations Theory.
 
-\hypertarget{method-1}{%
-\section{Method}\label{method-1}}
+\section{Method}\label{method-1}
 
-\hypertarget{sources-1}{%
-\subsection{Sources}\label{sources-1}}
+\subsection{Sources}\label{sources-1}
 
-Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
-news sources.
-These sources were selected owing to their favorability among political partisans according to Mitchell et al.
-(2014).
-The sources favored by liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
-The sources favored by conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts, again written with the \emph{papaja} library in \emph{R}, are provided inline with this manuscript (Aust \& Barth, 2017).
+Articles pertaining to the Brett Kavanaugh Supreme Court nomination and
+confirmation were scraped from the websites of 12 U.S. news sources.
+These sources were selected owing to their favorability among political
+partisans according to Mitchell et al. (2014). The sources favored by
+liberals were \emph{The New York Times}, \emph{National Public Radio
+(NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico}
+(Mitchell et al., 2014). The sources favored by conservatives included
+\emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show},
+\emph{The Blaze}, and \emph{Sean Hannity}. Political articles
+referencing Brett Kavanaugh's nomination process were identified and
+subsequently scraped by including the URL for each source's coverage of
+the nomination in the \emph{R} script. All code for this manuscript can
+be found at \url{https://osf.io/5kpj7/}, and the scripts, again written
+with the \emph{papaja} library in \emph{R}, are provided inline with
+this manuscript (Aust \& Barth, 2017).
 
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
+\subsection{Materials}\label{materials-1}
 
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset ({\textbf{???}}).
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
+Using the \emph{rvest} library in the statistical package \emph{R}, we
+pulled body text for individual articles from each of the aforementioned
+10 news sources (identified using CSS language). We compiled the
+articles into a dataset (Wickham, 2016). Using this dataset, we
+identified word count and average word count per source. This process
+was run for articles pertaining to Kavanaugh's nomination that were
+published between September 13, 2018 and October 11, 2018 inclusive.
+This date range was selected in reference to the widely-publicized and
+viewed nomination hearing on September 27, 2018. We set the start date
+at September 13 (two weeks before the hearing) and the end date at
+October 11 (two weeks after the hearing) so that we could capture a
+large amount of data (roughly one month) during which Kavanaugh's
+nomination was at its peak saturation in news coverage.
 
-\hypertarget{data-analysis-1}{%
-\subsection{Data analysis}\label{data-analysis-1}}
+\subsection{Data analysis}\label{data-analysis-1}
 
-As in Experiment 1, the text was scanned with \emph{ngram}.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed (Schmidt et al., 2017).
-The text was processed and stemmed in order to convert to a usable form for further analysis (Feinerer \& Hornik, 2017).
-Words were subsequently matched with their valences from Warriner et al.
-(2013).
-Depending on the results of Jordan, Buchanan \& Padfield's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
+As in Experiment 1, the text was scanned with \emph{ngram}. Again, blank
+articles, text from the Disqus system, and duplicate articles were
+removed (Schmidt et al., 2017). The text was processed and stemmed in
+order to convert to a usable form for further analysis (Feinerer \&
+Hornik, 2017). Words were subsequently matched with their valences from
+Warriner et al. (2013). Depending on the results of Jordan et al.
+(2019)'s research, alternative forms of the Moral Foudnations Dictionary
+may be imported instead of the original dictionary.
 
-Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
-Each individual word was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}).
-Once again, the same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurence in the text.
-Once again, percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
+Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the
+researchers processed the text in order to convert it to lowercase, fix
+spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
+Each individual word was reduced to its stem (i.e., \emph{diseased} was
+stemmed to \emph{diseas}). Once again, the same procedure was applied to
+the MFD words and the words in the Warriner et al. (2013) dataset. Using
+the Warriner et al. (2013) dictionary, the words in the MFD were
+assigned their respective valence. The researchers obtained the words'
+percent occurence in the text. Once again, percents were multiplied by
+\emph{z}-scored valence and categorized into their proper MFD category.
 
-\hypertarget{experiment-2-results}{%
-\section{Experiment 2 results}\label{experiment-2-results}}
+\section{Experiment 2}\label{experiment-2-1}
 
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
+\subsection{Results}\label{results-1}
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\section{Discussion}\label{discussion-1}
 
-How it turned out
-
-Limitations of this one (no rationale behind choosing sources except \enquote{people say NPR's liberal??})
-
-What to do for future project (focus on one MF? Different sources? More sources?)
-
-Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, \enquote{alternative facts,} subjective reality - philosophical stuff)
+\section{Conclusions}\label{conclusions}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
 \begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Aust2017}{}%
-Aust, F., \& Barth, M. (2017). papaja: Create APA manuscripts with R Markdown. Retrieved from \url{https://github.com/crsh/papaja}
+\hypertarget{ref-Aust2017}{}
+Aust, F., \& Barth, M. (2017). papaja: Create APA manuscripts with R
+Markdown. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-Bradley1999}{}%
-Bradley, M.
-M., \& Lang, P.
-J.
-(1999).
-\emph{Affective Norms for English Words (ANEW): Instruction Manual and Affective Ratings} (No.
-C-1).
-The Center for Research in Psychophysiology, University of Florida.
+\hypertarget{ref-Bradley1999}{}
+Bradley, M. M., \& Lang, P. J. (1999). \emph{Affective Norms for English
+Words (ANEW): Instruction Manual and Affective Ratings} (No. C-1). The
+Center for Research in Psychophysiology, University of Florida.
 
-\leavevmode\hypertarget{ref-Cameron2006}{}%
-Cameron, D. (2006). Ideology and language. \emph{Journal of Political Ideologies}, \emph{11}(2), 141--152. doi:\href{https://doi.org/10.1080/13569310600687916}{10.1080/13569310600687916}
+\hypertarget{ref-Cameron2006}{}
+Cameron, D. (2006). Ideology and language. \emph{Journal of Political
+Ideologies}, \emph{11}(2), 141--152.
+doi:\href{https://doi.org/10.1080/13569310600687916}{10.1080/13569310600687916}
 
-\leavevmode\hypertarget{ref-Clinton2014}{}%
-Clinton, J.
-D., \& Enamorado, T.
-(2014).
-The National News Media's Effect on Congress: How Fox News Affected Elites in Congress.
-\emph{The Journal of Politics}, \emph{76}(4), 928--943.
+\hypertarget{ref-Clinton2014}{}
+Clinton, J. D., \& Enamorado, T. (2014). The National News Media's
+Effect on Congress: How Fox News Affected Elites in Congress. \emph{The
+Journal of Politics}, \emph{76}(4), 928--943.
 doi:\href{https://doi.org/10.1017/S0022381614000425}{10.1017/S0022381614000425}
 
-\leavevmode\hypertarget{ref-Druckman2004}{}%
-Druckman, J.
-N., Jacobs, L.
-R., \& Ostermeier, E.
-(2004).
-Candidate Strategies to Prime Issues and Image.
-\emph{The Journal of Politics}, \emph{66}(4), 1180--1202.
+\hypertarget{ref-Druckman2004}{}
+Druckman, J. N., Jacobs, L. R., \& Ostermeier, E. (2004). Candidate
+Strategies to Prime Issues and Image. \emph{The Journal of Politics},
+\emph{66}(4), 1180--1202.
 doi:\href{https://doi.org/10.1111/j.0022-3816.2004.00295.x}{10.1111/j.0022-3816.2004.00295.x}
 
-\leavevmode\hypertarget{ref-Feinerer2017}{}%
-Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from \url{http://tm.r-forge.r-project.org/}
+\hypertarget{ref-Feinerer2017}{}
+Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from
+\url{http://tm.r-forge.r-project.org/}
 
-\leavevmode\hypertarget{ref-Gelman2006}{}%
-Gelman, A.
-(2006).
-Multilevel (hierarchical) modeling: What it can and cannot do.
-\emph{Technometrics}, \emph{48}(3), 432--435.
+\hypertarget{ref-Gelman2006}{}
+Gelman, A. (2006). Multilevel (hierarchical) modeling: What it can and
+cannot do. \emph{Technometrics}, \emph{48}(3), 432--435.
 doi:\href{https://doi.org/10.1198/004017005000000661}{10.1198/004017005000000661}
 
-\leavevmode\hypertarget{ref-Graham2009}{}%
-Graham, J., Haidt, J., \& Nosek, B.
-A.
-(2009).
-Liberals and conservatives rely on different sets of moral foundations.
-\emph{Journal of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
+\hypertarget{ref-Gilligan1982}{}
+Gilligan, C. (1982). New maps of development: New visions of maturity.
+\emph{American Journal of Orthopsychiatry}, \emph{52}(2), 199--212.
+doi:\href{https://doi.org/10.1111/j.1939-0025.1982.tb02682.x}{10.1111/j.1939-0025.1982.tb02682.x}
+
+\hypertarget{ref-Graham2009}{}
+Graham, J., Haidt, J., \& Nosek, B. A. (2009). Liberals and
+conservatives rely on different sets of moral foundations. \emph{Journal
+of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
 doi:\href{https://doi.org/10.1037/a0015141}{10.1037/a0015141}
 
-\leavevmode\hypertarget{ref-Graham2011}{}%
-Graham, J., Nosek, B.
-A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
-H.
-(2011).
-Mapping the moral domain.
-\emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
+\hypertarget{ref-Graham2011}{}
+Graham, J., Nosek, B. A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
+H. (2011). Mapping the moral domain. \emph{Journal of Personality and
+Social Psychology}, \emph{101}(2), 366--385.
 doi:\href{https://doi.org/10.1037/a0021847}{10.1037/a0021847}
 
-\leavevmode\hypertarget{ref-Haidt2007}{}%
-Haidt, J., \& Graham, J.
-(2007).
-When Morality Opposes Justice: Conservatives Have Moral Intuitions that Liberals may not Recognize.
+\hypertarget{ref-Haidt2007}{}
+Haidt, J., \& Graham, J. (2007). When Morality Opposes Justice:
+Conservatives Have Moral Intuitions that Liberals may not Recognize.
 \emph{Social Justice Research}, \emph{20}(1), 98--116.
@@
 
-\leavevmode\hypertarget{ref-Kuperman2014}{}%
-Kuperman, V., Estes, Z., Brysbaert, M., \& Warriner, A.
-B.
-(2014).
+\hypertarget{ref-Jordan2019}{}
+Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{A
+Validation of the Moral Foundations Questionnaire and Dictionary}.
+Retrieved from \url{https://osf.io/kt9yf/}
+
+\hypertarget{ref-Kohlberg1977}{}
+Kohlberg, L., \& Hersh, R. H. (1977). Moral development: A review of the
+theory. \emph{Theory into Practice}, \emph{16}(2), 53--59.
+doi:\href{https://doi.org/10.1080/00405847709542675}{10.1080/00405847709542675}
+
+\hypertarget{ref-Kuperman2014}{}
+Kuperman, V., Estes, Z., Brysbaert, M., \& Warriner, A. B. (2014).
 Emotion and language: Valence and arousal affect word recognition.
-\emph{Journal of Experimental Psychology: General}, \emph{143}(3), 1065--1081.
+\emph{Journal of Experimental Psychology: General}, \emph{143}(3),
+1065--1081.
 doi:\href{https://doi.org/10.1037/a0035669}{10.1037/a0035669}
 
-\leavevmode\hypertarget{ref-Kuperman2012}{}%
-Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M.
-(2012).
-Age-of-acquisition ratings for 30,000 English words.
-\emph{Behavior Research Methods}, \emph{44}(4), 978--990.
+\hypertarget{ref-Kuperman2012}{}
+Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M. (2012).
+Age-of-acquisition ratings for 30,000 English words. \emph{Behavior
+Research Methods}, \emph{44}(4), 978--990.
 doi:\href{https://doi.org/10.3758/s13428-012-0210-4}{10.3758/s13428-012-0210-4}
 
-\leavevmode\hypertarget{ref-Mitchell2014}{}%
-Mitchell, A., Matsa, K.
-E., Gottfried, J., \& Kiley, J.
-(2014).
+\hypertarget{ref-Mitchell2014}{}
+Mitchell, A., Matsa, K. E., Gottfried, J., \& Kiley, J. (2014).
 Political Polarization \& Media Habits \textbar{} Pew Research Center.
-Retrieved from \url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
+Retrieved from
+\url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
 
-\leavevmode\hypertarget{ref-OConnell2018}{}%
-O'Connell, M.
-(2018).
-Ford-Kavanaugh Ratings: Hearing Brings 20 Million Viewers to Cable and Broadcast \textbar{} Hollywood Reporter.
-Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
+\hypertarget{ref-New2007}{}
+New, B., Brysbaert, M., Veronis, J., \& Pallier, C. (2007). The use of
+film subtitles to estimate word frequencies. \emph{Applied
+Psycholinguistics}, \emph{28}(4), 661--677.
+doi:\href{https://doi.org/10.1017/S014271640707035X}{10.1017/S014271640707035X}
 
-\leavevmode\hypertarget{ref-Pennebaker2007}{}%
-Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). Liwc2007: Linguistic inquiry and word count. Austin, TX.
+\hypertarget{ref-OConnell2018}{}
+O'Connell, M. (2018). Ford-Kavanaugh Ratings: Hearing Brings 20 Million
+Viewers to Cable and Broadcast \textbar{} Hollywood Reporter. Retrieved
+from
+\url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
 
-\leavevmode\hypertarget{ref-Pinheiro2017}{}%
-Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). nlme: Linear and nonlinear mixed effects models. Retrieved from \url{https://cran.r-project.org/package=nlme}
+\hypertarget{ref-Pashler2012}{}
+Pashler, H., Coburn, N., \& Harris, C. R. (2012). Priming of Social
+Distance? Failure to Replicate Effects on Social and Food Judgments.
+\emph{PLoS ONE}, \emph{7}(8).
+doi:\href{https://doi.org/10.1371/journal.pone.0042510}{10.1371/journal.pone.0042510}
 
-\leavevmode\hypertarget{ref-Schmidt2017}{}%
-Schmidt, M.
-F., Gonzalez-Cabrera, I., \& Tomasello, M.
-(2017).
-Children's developing metaethical judgments.
-\emph{Journal of Experimental Child Psychology}, \emph{164}, 163--177.
+\hypertarget{ref-Pennebaker2007}{}
+Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). Liwc2007:
+Linguistic inquiry and word count. Austin, TX.
+
+\hypertarget{ref-Pinheiro2017}{}
+Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017).
+nlme: Linear and nonlinear mixed effects models. Retrieved from
+\url{https://cran.r-project.org/package=nlme}
+
+\hypertarget{ref-Schmidt2017}{}
+Schmidt, M. F., Gonzalez-Cabrera, I., \& Tomasello, M. (2017).
+Children's developing metaethical judgments. \emph{Journal of
+Experimental Child Psychology}, \emph{164}, 163--177.
 doi:\href{https://doi.org/10.1016/j.jecp.2017.07.008}{10.1016/j.jecp.2017.07.008}
 
-\leavevmode\hypertarget{ref-Warriner2015}{}%
-Warriner, A.
-B., \& Kuperman, V.
-(2015).
-Affective biases in English are bi-dimensional.
-\emph{Cognition and Emotion}, \emph{29}(7), 1147--1167.
+\hypertarget{ref-USGovernment2018b}{}
+US Government. (2018a). Congressional Record. \emph{Congressional
+Record}, \emph{164}(146), 46.
+doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\hypertarget{ref-USGovernment2018}{}
+US Government. (2018b). Congressional Record. \emph{Congressional
+Record}, \emph{164}(160), 93.
+doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\hypertarget{ref-USGovernment2018a}{}
+US Government. (2018c). Congressional Record. \emph{Congressional
+Record}, \emph{164}(167), 14.
+doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\hypertarget{ref-Warriner2015}{}
+Warriner, A. B., \& Kuperman, V. (2015). Affective biases in English are
+bi-dimensional. \emph{Cognition and Emotion}, \emph{29}(7), 1147--1167.
 doi:\href{https://doi.org/10.1080/02699931.2014.968098}{10.1080/02699931.2014.968098}
 
-\leavevmode\hypertarget{ref-Warriner2013}{}%
-Warriner, A. B., Kuperman, V., \& Brysbaert, M. (2013). Norms of Valence, Arousal, and Dominance for 13,915 English Lemmas. \emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
+\hypertarget{ref-Warriner2013}{}
+Warriner, A. B., Kuperman, V., \& Brysbaert, M. (2013). Norms of
+valence, arousal, and dominance for 13,915 English lemmas.
+\emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
+doi:\href{https://doi.org/10.3758/s13428-012-0314-x}{10.3758/s13428-012-0314-x}
+
+\hypertarget{ref-Wickham2016}{}
+Wickham, H. (2016). Package ` rvest '.
+
+\hypertarget{ref-Williams2008}{}
+Williams, L. E., \& Bargh, J. a. (2008). Keeping One ' s Distance.
+\emph{Psychological Science}, \emph{19}(3), 302--308.
+doi:\href{https://doi.org/10.1111/j.1467-9280.2008.02084.x}{10.1111/j.1467-9280.2008.02084.x}
 

### 2019-02-11 pilot_manuscript.Rmd
just changed a few little typos

@@
   - id            : "2"
-    instituation  : "Harrisburg University of Science and Technology"
+    institution  : "Harrisburg University of Science and Technology"
 
@@
 
-  William Padfield is a master's degree candidate in psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
+  William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
 

### 2019-02-11 pilot_manuscript.tex
just changed a few little typos

--- 2019-02-04 pilot_manuscript.tex
@@
 \vspace{0.5cm}
-\textsuperscript{1} Missouri State University\\\textsuperscript{2} }
+\textsuperscript{1} Missouri State University\\\textsuperscript{2} Harrisburg University of Science and Technology}
 \keywords{politics, morality, psycholinguistics}
@@
 
-\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-William Padfield is a master's degree candidate in psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
+\authornote{
+William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
 
@@
 \abstract{
-Enter abstract here. Each new line herein must be indented, like this line.
+The media ecosystem has grown, and political opinions have diverged such that there are competing conceptions of objective truth.
+Commentators often point to political biases in news coverage as a catalyst for this political divide.
+The Moral Foundations Dictionary (MFD) facilitates identification of ideological leanings in text through frequency of the occurrence of certain words.
+Through web scraping, the researchers extracted articles from popular news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
+In Experiment 1, the researchers gathered poltical articles from four sources.
+They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
+In Experiment 2, the researchers will expand their number of sources to 10 and will analyze articles that pertain to the 2018 confirmation hearings of U.S.
+Supreme Court Justice Brett Kavanaugh.
+This topic was selected due to the moral disputes associated with his nomination.
 
@@
 Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance ({\textbf{???}}).
+This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance (Kohlberg \& Hersh, 1977).
 Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
@@
 Typically, people progress through several steps until they reach a \enquote{post-conventional} ethics.
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their \enquote{self-chosen ethical principles} ({\textbf{???}}).
+People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their \enquote{self-chosen ethical principles} (Kohlberg \& Hersh, 1977).
 From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality (Haidt \& Graham, 2007).
@@
 She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-She pushes back against Kohlberg's assumption that moral development replaces \enquote{rule of brute force,} as enforced by men, with the justice-based \enquote{rule of law.} According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law ({\textbf{???}}).
+She pushes back against Kohlberg's assumption that moral development replaces \enquote{rule of brute force,} as enforced by men, with the justice-based \enquote{rule of law.} According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law (Gilligan, 1982).
 Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
 Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring ({\textbf{???}}).
+Gilligan thus asserted morality was built upon an alternative moral foundation: caring (Gilligan, 1982).
 This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring (Haidt \& Graham, 2007).
@@
 In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media ({\textbf{???}}).
+These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media (New, Brysbaert, Veronis, \& Pallier, 2007).
 This data collection resulted in the final list of 13,915 lemmas.
@@
 The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, COCA, BNC, TASA, and HAL, the researchers found that words with positive valence were also used more frequently (Warriner \& Kuperman, 2015).
+Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, the Corpus for Contemporary American English (COCA), the British National Corpus (BNC), Touchstone Applied Science Associates, Inc.~Corpus (TASA), and the corpus used for the Hyperspace Analogue to Language model (HAL), the researchers found that words with positive valence were also used more frequently (Warriner \& Kuperman, 2015).
 While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the Warriner et al.
@@
 Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
-The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks).
+The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks - two cognitive processing tasks wherein a participant has to read aloud or judge a word for its lexicality).
 First, Kuperman et al.
@@
 Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence (Druckman et al., 2004).
-The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g.~priming) issues related to energy, defense, and the economy.
+The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g., priming) issues related to energy, defense, and the economy.
 This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
@@
 (2004)'s findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
-({\textbf{???}}) point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
+Pashler, Coburn, and Harris (2012) point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
 Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
 Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
-({\textbf{???}}) point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
-Studies investigating perceptual priming have been \enquote{directly replicated in hundreds of labs} ({\textbf{???}}).
-This does not appear to be the case for social priming, as argued by ({\textbf{???}}).
+Pashler et al.
+(2012) point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
+Studies investigating perceptual priming have been \enquote{directly replicated in hundreds of labs} (Pashler et al., 2012).
+This replication rate does not appear to be the case for social priming, as argued by Pashler et al.
+(2012).
 
-({\textbf{???}}) noticed the unusually large effect size values (Cohen's \emph{d}) reported by researchers studying social priming effects.
-The researchers reproduced two studies from ({\textbf{???}}) The first study attempted to prime participants by having them plot points on a Cartesian grid.
+Pashler et al.
+(2012) noticed the unusually large effect size values (Cohen's \emph{d}) reported by researchers studying social priming effects.
+The researchers reproduced two studies from Williams and Bargh (2008) The first study attempted to prime participants by having them plot points on a Cartesian grid.
 The independent variable was priming condition and contained three levels: short, middle, and long distance.
@@
 The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
-({\textbf{???}}) concluded those two studies from ({\textbf{???}}) held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
+Pashler et al.
+(2012) concluded those two studies from Williams and Bargh (2008) held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
 
@@
 The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election (Clinton \& Enamorado, 2014).
+
+Therefore, the current study sought to combine both methods related questions and extension/replication of previous moral foundation results found for liberal and conservative sources.
+First, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
+Second, these weighted percentages were examined for their differences in across liberal and conservative news sources.
 
@@
 
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset ({\textbf{???}}).
+Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset (Wickham, 2016).
 Using this dataset, we identified word count and average word count per source.
-This process was run once daily starting on \emph{DATE} until \emph{DATE.} Starting on \emph{DATE,} the process was run twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected on \emph{DATE.}
+This process was run once daily starting in February 2018 until March 2018.
+Starting in mid-March 2018, the process was run twice daily - once in the morning and again in the evening.
+Data collection was terminated once 250,000 words per source was collected in April 2018.
 
@@
 
-Concurrent research by Jordan, Buchanan \& Padfield is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using one sample.
-The instruments will be analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity.
-Additionally, the researchers are investigating whether or not a reduced set of MFD words may likewise bolster the validity of the MFD.
-Depending on the results of that research, either an augmented or reduced Moral Foundations Dictionary may be utilized in this analysis rather than the original version.
+Concurrent research by Jordan, Buchanan, and Padfield (2019) is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
+The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
+The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
+Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
 
@@
 Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 1.
+To interpret the weighted scores, one can examine the mean and standard deviations for each.
+A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
+Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
+Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
 Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
@@
 Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 ({\textbf{???}}).
+The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 (US Government, 2018a).
 Following allegations of sexual assault by high school classmate Dr.~Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
 
-On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh ({\textbf{???}}).
+On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh (US Government, 2018b).
 During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
@@
 The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 ({\textbf{???}}).
+The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 (US Government, 2018c).
 
@@
 Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset ({\textbf{???}}).
+We compiled the articles into a dataset (Wickham, 2016).
 Using this dataset, we identified word count and average word count per source.
@@
 (2013).
-Depending on the results of Jordan, Buchanan \& Padfield's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
+Depending on the results of Jordan et al.
+(2019)'s research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
 
@@
 
-\hypertarget{experiment-2-results}{%
-\section{Experiment 2 results}\label{experiment-2-results}}
+\hypertarget{experiment-2-1}{%
+\section{Experiment 2}\label{experiment-2-1}}
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 \section{Conclusions}\label{conclusions}}
-
-How it turned out
-
-Limitations of this one (no rationale behind choosing sources except \enquote{people say NPR's liberal??})
-
-What to do for future project (focus on one MF? Different sources? More sources?)
-
-Argue: why is still a good thing to study?? (probably something about current state of discourse, information, truth, \enquote{alternative facts,} subjective reality - philosophical stuff)
 
@@
 (1999).
-\emph{Affective Norms for English Words (ANEW): Instruction Manual and Affective Ratings} (No.
+\emph{Affective Norms for English Words (ANEW): Instruction manual and affective ratings} (No.
 C-1).
@@
 (2014).
-The National News Media's Effect on Congress: How Fox News Affected Elites in Congress.
+The national news media's effect on Congress: How Fox News affected elites in Congress.
 \emph{The Journal of Politics}, \emph{76}(4), 928--943.
@@
 (2004).
-Candidate Strategies to Prime Issues and Image.
+Candidate strategies to prime issues and image.
 \emph{The Journal of Politics}, \emph{66}(4), 1180--1202.
@@
 doi:\href{https://doi.org/10.1198/004017005000000661}{10.1198/004017005000000661}
+
+\leavevmode\hypertarget{ref-Gilligan1982}{}%
+Gilligan, C.
+(1982).
+New maps of development: New visions of maturity.
+\emph{American Journal of Orthopsychiatry}, \emph{52}(2), 199--212.
+doi:\href{https://doi.org/10.1111/j.1939-0025.1982.tb02682.x}{10.1111/j.1939-0025.1982.tb02682.x}
 
@@
 (2007).
-When Morality Opposes Justice: Conservatives Have Moral Intuitions that Liberals may not Recognize.
+When morality opposes justice: Conservatives have moral intuitions that Liberals may not recognize.
 \emph{Social Justice Research}, \emph{20}(1), 98--116.
 doi:\href{https://doi.org/10.1007/s11211-007-0034-z}{10.1007/s11211-007-0034-z}
+
+\leavevmode\hypertarget{ref-Jordan2019}{}%
+Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{A validation of the Moral Foundations Questionnaire and Dictionary}. Retrieved from \url{https://osf.io/kt9yf/}
+
+\leavevmode\hypertarget{ref-Kohlberg1977}{}%
+Kohlberg, L., \& Hersh, R.
+H.
+(1977).
+Moral development: A review of the theory.
+\emph{Theory into Practice}, \emph{16}(2), 53--59.
+doi:\href{https://doi.org/10.1080/00405847709542675}{10.1080/00405847709542675}
 
@@
 (2014).
-Political Polarization \& Media Habits \textbar{} Pew Research Center.
+Political polarization \& media habits \textbar{} Pew Research Center.
 Retrieved from \url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
+
+\leavevmode\hypertarget{ref-New2007}{}%
+New, B., Brysbaert, M., Veronis, J., \& Pallier, C.
+(2007).
+The use of film subtitles to estimate word frequencies.
+\emph{Applied Psycholinguistics}, \emph{28}(4), 661--677.
+doi:\href{https://doi.org/10.1017/S014271640707035X}{10.1017/S014271640707035X}
 
@@
 (2018).
-Ford-Kavanaugh Ratings: Hearing Brings 20 Million Viewers to Cable and Broadcast \textbar{} Hollywood Reporter.
+Ford-Kavanaugh Ratings: Hearing Brings 20 Million viewers to cable and broadcast \textbar{} Hollywood Reporter.
 Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
+
+\leavevmode\hypertarget{ref-Pashler2012}{}%
+Pashler, H., Coburn, N., \& Harris, C.
+R.
+(2012).
+Priming of Social Distance?
+Failure to Replicate Effects on Social and Food Judgments.
+\emph{PLoS ONE}, \emph{7}(8).
+doi:\href{https://doi.org/10.1371/journal.pone.0042510}{10.1371/journal.pone.0042510}
 
@@
 
+\leavevmode\hypertarget{ref-USGovernment2018b}{}%
+US Government. (2018a). Congressional Record. \emph{Congressional Record}, \emph{164}(146), 46. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\leavevmode\hypertarget{ref-USGovernment2018}{}%
+US Government. (2018b). Congressional Record. \emph{Congressional Record}, \emph{164}(160), 93. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\leavevmode\hypertarget{ref-USGovernment2018a}{}%
+US Government. (2018c). Congressional Record. \emph{Congressional Record}, \emph{164}(167), 14. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
 \leavevmode\hypertarget{ref-Warriner2015}{}%
@@
 \leavevmode\hypertarget{ref-Warriner2013}{}%
-Warriner, A. B., Kuperman, V., \& Brysbaert, M. (2013). Norms of Valence, Arousal, and Dominance for 13,915 English Lemmas. \emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
+Warriner, A.
+B., Kuperman, V., \& Brysbaert, M.
+(2013).
+Norms of valence, arousal, and dominance for 13,915 English lemmas.
+\emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
+doi:\href{https://doi.org/10.3758/s13428-012-0314-x}{10.3758/s13428-012-0314-x}
+
+\leavevmode\hypertarget{ref-Wickham2016}{}%
+Wickham, H. (2016). Package ` rvest '. Retrieved from \url{https://cran.r-project.org/package=rvest}
+
+\leavevmode\hypertarget{ref-Williams2008}{}%
+Williams, L.
+E., \& Bargh, J.
+A.
+(2008).
+Keeping one's distance.
+\emph{Psychological Science}, \emph{19}(3), 302--308.
+doi:\href{https://doi.org/10.1111/j.1467-9280.2008.02084.x}{10.1111/j.1467-9280.2008.02084.x}
 

### 2019-02-25 pilot_manuscript.Rmd
added bit to search NYtimes

@@
 
+```{r NYTimes, eval = F, include = F}
+
+library(rvest)
+####NY Times####
+#Specifying the url for desired website to be scrapped
+url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
+
+#Reading the HTML code from the website - headlines
+webpage <- read_html(url)
+headline_data = html_nodes(webpage,'a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep(".html", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+#paste NY on front
+urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
+
+  ##pull the text
+  text_data = html_text(headline_data)
+
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+    } ##end for loop
+
+```
+
 ## Sources

### 2019-03-02 pilot_manuscript.Rmd
set up some scraping stuff. Will resume tomorrow

@@
 ####NY Times####
-#Specifying the url for desired website to be scrapped
+#Specifying the url for desired website to be scraped
 url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
@@
 
+```
+
+````{r NPR, eval = F, include = F}
+url2 = 'https://www.npr.org/search?query=kavanaugh&page=1'
+webpage2 = read_html(url2)
+headline_data2 = html_nodes(webpage2,'.title .ais-Highlight-nonHighlighted')
+
+#URLs
+attr_data2 = html_attrs(headline_data2) 
+attr_data2
+
+urlslist2 = unlist(attr_data2)
+urlslist2 = urlslist2[grep("http", urlslist2)]
+urlslist2
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 1:length(urlslist2)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist2[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'#storytext > p')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  NPRDF$Source[i] = "NPR"
+  NPRDF$Url[i] = urlslist2[i]
+  NPRDF$Text[i] = paste(text_data2, collapse = "")
+} ##end for loop
+```
+
+````{r Slate, eval = F, include = F}
+url3 = 'https://slate.com/search?q=kavanaugh&via=homepage_nav_search'
+webpage3 = read_html(url3)
+headline_data3 = html_nodes(webpage3,'.gs-title')
+
+#URLs
+attr_data3 = html_attrs(headline_data3) 
+attr_data3
+
+urlslist3 = unlist(attr_data3)
+urlslist3 = urlslist3[grep("http", urlslist3)]
+urlslist3
+
+##start a data frame
+SlateDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(SlateDF) = c("Source", "Url", "Text")
+SlateDF = as.data.frame(SlateDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage3 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data3 = html_nodes(webpage3,'.slate-paragraph')
+
+  ##pull the text
+  text_data3 = html_text(headline_data3)
+
+  ##save the data
+  SlateDF$Source[i] = "Slate"
+  SlateDF$Url[i] = urlslist3[i]
+  SlateDF$Text[i] = paste(text_data3, collapse = "")
+} ##end for loop
+```
+
+````{r HuffPo, eval = F, include = F}
+url4 = 'https://search.huffingtonpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s'
+webpage4 = read_html(url4)
+headline_data4 = html_nodes(webpage4,'.fw-b')
+
+#URLs
+attr_data4 = html_attrs(headline_data4) 
+attr_data4
+
+urlslist4 = unlist(attr_data4)
+urlslist4 = urlslist4[grep("http", urlslist4)]
+urlslist4
+
+##start a data frame
+HuffpoDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
+colnames(HuffpoDF) = c("Source", "Url", "Text")
+HuffpoDF = as.data.frame(HuffpoDF)
+
+##for loops
+for (i in 1:length(urlslist4)){
+
+  ##read in the URL
+  webpage4 <- read_html(urlslist4[i])
+
+  ##pull the specific nodes
+  headline_data4 = html_nodes(webpage4,'p')
+
+  ##pull the text
+  text_data4 = html_text(headline_data4)
+
+  ##save the data
+  HuffPoDF$Source[i] = "Huffington Post"
+  HuffpoDF$Url[i] = urlslist4[i]
+  HuffpoDF$Text[i] = paste(text_data4, collapse = "")
+} ##end for loop
+```
+
+````{r Politico, eval = F, include = F}
+url5 = 'https://www.politico.com/search?q=kavanaugh&s=newest'
+webpage5 = read_html(url5)
+headline_data5 = html_nodes(webpage5,'.summary a')
+
+#URLs
+attr_data5 = html_attrs(headline_data5) 
+attr_data5
+
+urlslist5 = unlist(attr_data5)
+urlslist5 = urlslist5[grep("http", urlslist5)]
+urlslist5
+
+##start a data frame
+PoliticoDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
+colnames(PoliticoDF) = c("Source", "Url", "Text")
+PoliticoDF = as.data.frame(PoliticoDF)
+
+##for loops
+for (i in 1:length(urlslist5)){
+
+  ##read in the URL
+  webpage5 <- read_html(urlslist5[i])
+
+  ##pull the specific nodes
+  headline_data5 = html_nodes(webpage5,'.story-text > p')
+
+  ##pull the text
+  text_data5 = html_text(headline_data5)
+
+  ##save the data
+  PoliticoDF$Source[i] = "Politico"
+  PoliticoDF$Url[i] = urlslist5[i]
+  PoliticoDF$Text[i] = paste(text_data5, collapse = "")
+} ##end for loop
+```
+
+````{r Fox News, eval = F, include = F}
+url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&sort=latest&start=0'
+webpage6 = read_html(url6)
+headline_data6 = html_nodes(webpage6, 'h3 .ng-binding')
+
+attr_data6 = html_attrs(headline_data6) 
+attr_data6
+
+urlslist6 = unlist(attr_data6)
+urlslist6 = urlslist6[grep("http|.html", urlslist6)]
+
+##start a data frame
+FoxDF = matrix(NA, nrow = length(urlslist6), ncol = 3)
+colnames(FoxDF) = c("Source", "Url", "Text")
+FoxDF = as.data.frame(FoxDF)
+
+##for loops
+for (i in 1:length(urlslist6)){
+
+  ##read in the URL
+  webpage6 <- read_html(urlslist6[i])
+
+  ##pull the specific nodes
+  headline_data6 = html_nodes(webpage6,'p+ p , .fn-video+ p , .twitter+ p , .speakable')
+
+  ##pull the text
+  text_data6 = html_text(headline_data6)
+
+  ##save the data
+  FoxDF$Source[i] = "Fox News"
+  FoxDF$Url[i] = urlslist6[i]
+  FoxDF$Text[i] = paste(text_data6, collapse = "")
+} ##end for loop
+```
+
+````{r Breitbart, eval = F, include = F}
+url7 = 'http://www.breitbart.com/big-government/'
+webpage7 = read_html(url7)
+headline_data7 = html_nodes(webpage7, '.gs-title')
+
+attr_data7 = html_attrs(headline_data7) 
+attr_data7
+
+urlslist7 = unlist(attr_data7)
+urlslist7 = urlslist4[grep(urlslist7)]
+
+##start a data frame
+BreitbartDF = matrix(NA, nrow = length(urlslist7), ncol = 3)
+colnames(BreitbartDF) = c("Source", "Url", "Text")
+BreitbartDF = as.data.frame(BreitbartDF)
+
+##for loops
+for (i in 1:length(urlslist7)){
+
+  ##read in the URL
+  webpage7 <- read_html(urlslist7[i])
+
+  ##pull the specific nodes
+  headline_data7 = html_nodes(webpage7,'p , h2')
+
+  ##pull the text
+  text_data7 = html_text(headline_data7)
+
+  ##save the data
+  BreitbartDF$Source[i] = "Breitbart"
+  BreitbartDF$Url[i] = urlslist7[i]
+  BreitbartDF$Text[i] = paste(text_data7, collapse = "")
+} ##end for loop
+```
+
+````{r Rush Limbaugh, eval = F, include = F}
+url8 = 'https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1'
+webpage8 = read_html(url8)
+headline_data8 = html_nodes(webpage8, '.ais-hits--content a')
+
+attr_data8 = html_attrs(headline_data8) 
+attr_data8
+
+urlslist8 = unlist(attr_data8)
+urlslist8 = urlslist8[grep(urlslist8)]
+
+##start a data frame
+RushDF = matrix(NA, nrow = length(urlslist8), ncol = 3)
+colnames(RushDF) = c("Source", "Url", "Text")
+RushDF = as.data.frame(RushDF)
+
+##for loops
+for (i in 1:length(urlslist8)){
+
+  ##read in the URL
+  webpage8 <- read_html(urlslist8[i])
+
+  ##pull the specific nodes
+  headline_data8 = html_nodes(webpage8,'p')
+
+  ##pull the text
+  text_data8 = html_text(headline_data8)
+
+  ##save the data
+  RushDF$Source[i] = "Rush Limbaugh"
+  RushDF$Url[i] = urlslist8[i]
+  RushDF$Text[i] = paste(text_data8, collapse = "")
+} ##end for loop
+```
+
+````{r Blaze, eval = F, include = F}
+url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
+webpage9 = read_html(url9)
+headline_data9 = html_nodes(webpage9, '.widget__headline-text')
+
+attr_data9 = html_attrs(headline_data9) 
+attr_data9
+
+urlslist9 = unlist(attr_data9)
+urlslist9 = urlslist9[grep(urlslist9)]
+
+##start a data frame
+BlazeDF = matrix(NA, nrow = length(urlslist9), ncol = 3)
+colnames(BlazeDF) = c("Source", "Url", "Text")
+BlazeDF = as.data.frame(BlazeDF)
+
+##for loops
+for (i in 1:length(urlslist9)){
+
+  ##read in the URL
+  webpage9 <- read_html(urlslist9[i])
+
+  ##pull the specific nodes
+  headline_data9 = html_nodes(webpage9,'p')
+
+  ##pull the text
+  text_data9 = html_text(headline_data9)
+
+  ##save the data
+  BlazeDF$Source[i] = "The Blaze"
+  BlazeDF$Url[i] = urlslist9[i]
+  BlazeDF$Text[i] = paste(text_data9, collapse = "")
+} ##end for loop
+```
+
+````{r Sean Hannity, eval = F, include = F}
+url10 = 'https://www.theblaze.com/search/?q=kavanaugh'
+webpage10 = read_html(url10)
+headline_data10 = html_nodes(webpage10, '.gs-title')
+
+attr_data10 = html_attrs(headline_data10) 
+attr_data10
+
+urlslist10 = unlist(attr_data10)
+urlslist10 = urlslist10[grep(urlslist10)]
+
+##start a data frame
+SeanDF = matrix(NA, nrow = length(urlslist10), ncol = 3)
+colnames(SeanDF) = c("Source", "Url", "Text")
+SeanDF = as.data.frame(SeanDF)
+
+##for loops
+for (i in 1:length(urlslist10)){
+
+  ##read in the URL
+  webpage10 <- read_html(urlslist10[i])
+
+  ##pull the specific nodes
+  headline_data10 = html_nodes(webpage10,'p')
+
+  ##pull the text
+  text_data10 = html_text(headline_data10)
+
+  ##save the data
+  SeanDF$Source[i] = "Sean Hannity"
+  SeanDF$Url[i] = urlslist10[i]
+  SeanDF$Text[i] = paste(text_data10, collapse = "")
+} ##end for loop
 ```

### 2019-03-04 selenium example.R
PUMP THE JAM

@@ -1,0 +1,83 @@
+library(rvest)
+library(RSelenium)
+
+##go here
+##http://selenium-release.storage.googleapis.com/3.9/selenium-server-standalone-3.9.1.jar
+
+##an example to show you what's happening
+rD <- rsDriver()
+remDr <- rD[["client"]]
+remDr$navigate("http://www.google.com/ncr")
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+##end example
+
+
+##fox example
+rD <- rsDriver()
+remDr <- rD[["client"]]
+
+#page for NYTIMES
+url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
+
+#navigate to it
+remDr$navigate(url)
+
+#click the button 
+webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
+
+#with 752 results at 10 per page we need
+#752 - 10 original = 742 / 10 per click = 75 clicks
+
+for (i in 1:5) { #change this to 75 later
+webElem$clickElement()
+  Sys.sleep(runif(1, 1, 5))
+}
+
+webpage <-remDr$getPageSource()
+
+#Reading the HTML code from the website - headlines
+webpage2 <- read_html(unlist(webpage))
+
+headline_data = html_nodes(webpage2,'a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep(".html", urlslist)]
+urlslist = urlslist[grep("/2018", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+#paste NY on front
+urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+  
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+  
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn') 
+  
+  ##pull the text
+  text_data = html_text(headline_data)
+  
+  ##save the data
[…]

### 2019-03-04 pilot_manuscript.Rmd
updates

@@
 ````{r NPR, eval = F, include = F}
-url2 = 'https://www.npr.org/search?query=kavanaugh&page=1'
+urlslist_final = c()
+
+##loop through the page number at the end until done with ~1000 / 20 = 50
+for (i in 1:2){ ##change this to 50
+  url2 = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
   webpage2 = read_html(url2)
-headline_data2 = html_nodes(webpage2,'.title .ais-Highlight-nonHighlighted')
+  headline_data2 = html_nodes(webpage2,'.title')
 
@@
   attr_data2 = html_attrs(headline_data2) 
-attr_data2
-
   urlslist2 = unlist(attr_data2)
   urlslist2 = urlslist2[grep("http", urlslist2)]
-urlslist2
+
+  #add them to an overall
+  urlslist_final = c(urlslist_final, urlslist2)
+
+  Sys.sleep(runif(1, 1, 5))
+}
 
 ##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
+NPRDF = matrix(NA, nrow = length(urlslist_final), ncol = 3)
 colnames(NPRDF) = c("Source", "Url", "Text")
@@
   NPRDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 5))
 } ##end for loop

### 2019-03-04 selenium example.R

@@ -1,9 +1,6 @@
 library(rvest)
 library(RSelenium)
 
-##go here
-##http://selenium-release.storage.googleapis.com/3.9/selenium-server-standalone-3.9.1.jar
-
 ##an example to show you what's happening
 rD <- rsDriver()
 remDr <- rD[["client"]]
@@ -13,8 +10,7 @@ remDr$close()
 rD[["server"]]$stop()
 ##end example
 
-
-##fox example
+##NY times example
 rD <- rsDriver()
 remDr <- rD[["client"]]
 
@@ -25,13 +21,15 @@ url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=bes
 remDr$navigate(url)
 
 #click the button 
+#don't change class name
+#right click --> inspect element 
 webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
 
 #with 752 results at 10 per page we need
 #752 - 10 original = 742 / 10 per click = 75 clicks
 
 for (i in 1:5) { #change this to 75 later
-webElem$clickElement()
+  webElem$clickElement()
   Sys.sleep(runif(1, 1, 5))
 }
 

### 2019-03-10 pilot_manuscript.Rmd
filled in progress issues; minor changes to thesis script

@@
   ##save the data
-  HuffPoDF$Source[i] = "Huffington Post"
+  HuffpoDF$Source[i] = "Huffington Post"
   HuffpoDF$Url[i] = urlslist4[i]
@@
 ````{r Fox News, eval = F, include = F}
-url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&sort=latest&start=0'
+url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=0'
 webpage6 = read_html(url6)
@@
 ````{r Breitbart, eval = F, include = F}
-url7 = 'http://www.breitbart.com/big-government/'
+url7 = 'https://www.breitbart.com/search/?s=kavanaugh#gsc.tab=0&gsc.q=kavanaugh&gsc.page=1'
 webpage7 = read_html(url7)
@@
 urlslist7 = unlist(attr_data7)
-urlslist7 = urlslist4[grep(urlslist7)]
+urlslist7 = urlslist7[grep(urlslist7)]
 
@@
 webpage8 = read_html(url8)
+#headline_data8 = html_nodes(webpage8, 'a')    trying something different
 headline_data8 = html_nodes(webpage8, '.ais-hits--content a')
@@
 ````{r Sean Hannity, eval = F, include = F}
-url10 = 'https://www.theblaze.com/search/?q=kavanaugh'
+url10 = 'https://www.hannity.com/'
 webpage10 = read_html(url10)

### 2019-03-17 pilot_manuscript.Rmd
wrote about MFT criticisms and validation of MFQ

@@
 
+Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
+@Suhler2011 list several potential weaknesses of MFT that they argue might threaten the theory's validity.
+First, the authors challenge @Haidt2007's claims the moral intuitions represented by MFT are innate and modular.
+@Suhler2011 claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
+Rather, behaviors likely result from interactions between genetics and experience [@Suhler2011].
+According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
+Similarly, @Haidt2007 rely on evidence authored by evolutionary psychologists to make a "strong modularity claim" [@Suhler2011].
+However, as with innateness, there is little neurobiological evidence to support modularity.
+
+@Suhler2011 also criticized the content and taxonomy of the five foundations.
+The authors criticize @Haidt2007's omissions of additional foundations, including *industry* and *modesty*, claiming these concepts are moralized in many societies worldwide.
+Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
+For example, @Suhler2011 posit that *ingroup/loyalty* is merely a group-focused version of *harm/care*.
+Work by @Graham2011 might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
+Finally, @Suhler2011 point out that particular concepts related to a foundation, including "anger" in *fairness/reciprocity* and "deception" in *ingroup/loyalty*, could be ascribed to any of the other foundations as well.
+In other words, it becomes difficult to recognize a particular concept as indidcative of any one foundation when, in theory, they could be applied to all five [@Haidt2007; @Suhler2011].
+
+These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
+The current authors argue these criticisms are especially valid when considered alongside questions regarding the Moral Foundations Dictionary they state herein.
+However, there exists compelling evidence regarding the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
+This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Fondations Dictionary.
+
 ## Moral Foundations Dictionary
@@
 Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ [@Graham2011].
+
+The Moral Foundations Questionnaire has been validated by multiple researchers.
+Likewise, its five-factor structure has been demonstrated to fit data in multiple countries [@Graham2011; @Davies2014].
+In their article introducing the 30-item MFQ, @Graham2011 conducted an exploratory factor analysis (EFA) and found that a five-factor model fit better than a one, two, or three-factor model.
+@Davies2014 conducted a confirmatory factor analysis (CFA) of the MFQ with a sample from New Zealand and likewise found the five-factor model provided the best fit.
+While @Davies2014 concede the US and New Zealand share many similarities as Western nations, which could raise questions regarding the validity of the MFQ in non-Western nations.
+However, there are striking differences between the two countries, including the lack of a two-party political system in New Zealand, that provide grounds for claiming the MFQ generalizes beyond the United States.
+Furthermore, @Graham2011 claim to find a "reasonable" degree of generalizability for the MFQ across participants from many different regions in the world.
+These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by @Shuler2011 should still be taken into account in studies involving the theory.
 

### 2019-03-18 pilot_manuscript.Rmd
updating your folder

@@
 ##import the overalldata 
-overalldata = read.csv("overalldata.csv")
+overalldata = read.csv("exp1_data/overalldata.csv")
 
@@
 ##pull in the data
-master = read.csv("overalldata.csv", stringsAsFactors = F)
+master = read.csv("exp1_data/overalldata.csv", stringsAsFactors = F)
 
@@
 
-final = read.csv("finaldata.csv", stringsAsFactors = F)
+final = read.csv("exp1_data/finaldata.csv", stringsAsFactors = F)
 final = na.omit(final) #one weird NA line
@@
 ##open the Warriner data for later
-warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+warriner = read.csv("exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
 warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
@@
 #read in the harm total words from the mtmm project
-harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)
+harm_all = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)
+fair_all = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all = read.csv("iexp1_data/ngroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("authority_words_total.csv", stringsAsFactors = F)
+authority_all = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("purity_words_total.csv", stringsAsFactors = F)
+purity_all = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 library(rvest)
-####NY Times####
-#Specifying the url for desired website to be scraped
+library(RSelenium)
+
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#page for NYTIMES
 url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
 
+#navigate to it
+remDr$navigate(url)
+
+#click the button 
+#don't change class name
+#right click --> inspect element 
+webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
+
+#with 752 results at 10 per page we need
+#752 - 10 original = 742 / 10 per click = 75 clicks
+
+for (i in 1:75) { #change this to 75 later
+  webElem$clickElement()
+  Sys.sleep(runif(1, 1, 5))
+}
+
+webpage <-remDr$getPageSource()
+
 #Reading the HTML code from the website - headlines
-webpage <- read_html(url)
-headline_data = html_nodes(webpage,'a')
+webpage2 <- read_html(unlist(webpage))
+
+headline_data = html_nodes(webpage2,'a')
 
@@
 urlslist = urlslist[grep(".html", urlslist)]
+urlslist = urlslist[grep("/2018", urlslist)]
 urlslist = unique(urlslist)
@@
   NYtimesDF$Text[i] = paste(text_data, collapse = "")
+  Sys.sleep(runif(1, 1, 10)) #don't make them angry
 } ##end for loop
+
+write.csv(NYtimesDF, "NYtimes_kav.csv", row.names = F)
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
 

### 2019-03-18 Analysis.R

@@ -1,491 +1,0 @@
-##set working directory
-setwd("~/OneDrive - Missouri State University/RESEARCH/2 projects/Will-Pilot")
-
-##pull in the data
-master = read.csv("overalldata.csv", stringsAsFactors = F)
-
-##get rid of the blank stuff
-library(ngram)
-
-for (i in 1:nrow(master)) {
-  master$wordcount[i] = wordcount(master$Text[i])
-}
-
-nozero = subset(master, wordcount > 0)
-tapply(nozero$wordcount, nozero$Source, mean)
-tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones
-nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##figure out the duplicates
-nodis$URLS = duplicated(nodis$Url)
-
-##all data
-final = subset(nodis, URLS == FALSE)
-
-tapply(final$wordcount, final$Source, mean)
-tapply(final$wordcount, final$Source, sum)
-
-#write.csv(final, "finaldata.csv")
-
-####start here####
-final = read.csv("finaldata.csv", stringsAsFactors = F)
-final = na.omit(final) #one weird NA line
-
-##figure out the percent of MFD words
-
-##the amount of time people used the original MFD words
-original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
-
-##adding forms/conjugations of words to original_mfd
-#harm/care
-original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
-                             "sympathetic","sympathies","damaged",
-                             "damaging","attacked","attacking","attacker",
-                             "attacks","attackers", "benefits", "benefitted",
-                             "benefitting", "cares", "cared", "caring", "crushes",
-                             "crushing", "crushed", "dangerous", "defends", "defending",
-                             "defended", "detroys", "destroyed", "destroying",
-                             "fights", "fought", "fighting", "guards", "guarded",
-                             "guarding", "harms", "harmed", "harming", "hurts",
-                             "hurting", "kills", "killed", "killing", "preserves",
-                             "preserved", "preserving", "protects", "protected",
-                             "protecting", "protection", "ruins", "ruined", "ruining",
-                             "safely", "safer", "shelters", "sheltered", "sheltering",
-                             "spurns", "spurned", "spurning", "stomps", "stomped",
-                             "stomping", "suffers", "suffered", "suffering",
-                             "violence", "warring")
-                             
-#fairness/reciprocity
[…]

### 2019-03-18 Scraping News Sites.R

@@ -1,273 +1,0 @@
-library(rvest)
-####NY Times####
-#Specifying the url for desired website to be scrapped
-url <- 'https://www.nytimes.com/section/politics'
-
-#Reading the HTML code from the website - headlines
-webpage <- read_html(url)
-headline_data = html_nodes(webpage,'.story-link a, .story-body a')
-#headline_data = html_text(headline_data) #convert to readable text
-#head(headline_data) #hmmm, I think it could work
-
-#okay, so I can get the urls this way, but idk how to get rid of the other crap
-attr_data = html_attrs(headline_data) 
-attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep("http", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-  
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-  
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.story-content') 
-  
-  ##pull the text
-  text_data = html_text(headline_data)
-  
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-    } ##end for loop
-
-####NPR original front page####
-url2 = 'https://www.npr.org/sections/politics/'
-webpage2 = read_html(url2)
-headline_data2 = html_nodes(webpage2,'.title a')
-#headline_data = html_text(headline_data)
-#head(headline_data) #Very nice. NPR Politics does not show a huge list on its front page
-
-#Los Localizadores Uniformes de Recursos (URLs)
-attr_data2 = html_attrs(headline_data2) 
-attr_data2
-
-urlslist2 = unlist(attr_data2)
-urlslist2 = urlslist2[grep("http", urlslist2)]
-urlslist2
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
[…]

### 2019-03-18 Scraping practice.R

@@ -1,143 +1,0 @@
-library(rvest)
-#Specifying the url for desired website to be scrapped
-url <- 'http://www.imdb.com/search/title?count=100&release_date=2017,2017&title_type=feature'
-
-#Reading the HTML code from the website
-webpage <- read_html(url)
-
-#Using CSS selectors to scrap the rankings section
-rank_data_html <- html_nodes(webpage,'.text-primary')
-
-#Converting the ranking data to text
-rank_data <- html_text(rank_data_html)
-
-#Let's have a look at the rankings
-head(rank_data)
-
-#Data-Preprocessing: Converting rankings to numerical
-rank_data<-as.numeric(rank_data)
-
-#Let's have another look at the rankings
-head(rank_data)
-
-#Using CSS selectors to scrap the title section
-title_data_html <- html_nodes(webpage,'.lister-item-header a')
-
-#Converting the title data to text
-title_data <- html_text(title_data_html)
-
-#Let's have a look at the title
-head(title_data)
-
-#Using CSS selectors to scrap the description section
-description_data_html <- html_nodes(webpage,'.ratings-bar+ .text-muted')
-
-#Converting the description data to text
-description_data <- html_text(description_data_html)
-
-#Let's have a look at the description data
-head(description_data)
-
-#Data-Preprocessing: removing '\n'
-description_data<-gsub("\n","",description_data)
-
-#Let's have another look at the description data 
-head(description_data)
-
-#Using CSS selectors to scrap the Movie runtime section
-runtime_data_html <- html_nodes(webpage,'.text-muted .runtime')
-
-#Converting the runtime data to text
-runtime_data <- html_text(runtime_data_html)
-
-#Let's have a look at the runtime
-head(runtime_data)
-
-#Data-Preprocessing: removing mins and converting it to numerical
-
-runtime_data<-gsub(" min","",runtime_data)
-runtime_data<-as.numeric(runtime_data)
-
-#Let's have another look at the runtime data
-head(rank_data)
-
-#Using CSS selectors to scrap the Movie genre section
-genre_data_html <- html_nodes(webpage,'.genre')
-
-#Converting the genre data to text
-genre_data <- html_text(genre_data_html)
-
-#Let's have a look at the genre
-head(genre_data)
-
-#Data-Preprocessing: removing \n
-genre_data<-gsub("\n","",genre_data)
-
-#Data-Preprocessing: removing excess spaces
-genre_data<-gsub(" ","",genre_data)
-
[…]

### 2019-03-18 Untitled.R

@@ -1,48 +1,0 @@
-
-
-##you will run this for each foundation AFTER running the MTMM project 
-##through MTMM set up
-#Harm
-harm_all = data.frame("words" = c(original_mfd$h2, harm_words, harm_words_reduce, 
-                                  harm_words_reduce_exp2))
-harm_all$dataset = c(rep("orig", length(original_mfd$h2)),
-                           rep("all_exp1", length(harm_words)),
-                           rep("reduce_exp1", length(harm_words_reduce)),
-                           rep("reduce_exp2", length(harm_words_reduce_exp2)))
-write.csv(harm_all, "harm_words_total.csv", row.names = F)
-
-#Fair
-fair_all = data.frame("words" = c(original_mfd$f2, fair_words, fair_words_reduce, 
-                                  fair_words_reduce_exp2))
-fair_all$dataset = c(rep("orig", length(original_mfd$f2)),
-                     rep("all_exp1", length(fair_words)),
-                     rep("reduce_exp1", length(fair_words_reduce)),
-                     rep("reduce_exp2", length(fair_words_reduce_exp2)))
-write.csv(fair_all, "fair_words_total.csv", row.names = F)
-
-#Ingroup
-ingroup_all = data.frame("words" = c(original_mfd$i2, ingroup_words, ingroup_words_reduce, 
-                                     ingroup_words_reduce_exp2))
-ingroup_all$dataset = c(rep("orig", length(original_mfd$i2)),
-                     rep("all_exp1", length(ingroup_words)),
-                     rep("reduce_exp1", length(ingroup_words_reduce)),
-                     rep("reduce_exp2", length(ingroup_words_reduce_exp2)))
-write.csv(ingroup_all, "ingroup_words_total.csv", row.names = F)
-
-#Authority
-authority_all = data.frame("words" = c(original_mfd$a2, authority_words, authority_words_reduce, 
-                                     authority_words_reduce_exp2))
-authority_all$dataset = c(rep("orig", length(original_mfd$a2)),
-                        rep("all_exp1", length(authority_words)),
-                        rep("reduce_exp1", length(authority_words_reduce)),
-                        rep("reduce_exp2", length(authority_words_reduce_exp2)))
-write.csv(authority_all, "authority_words_total.csv", row.names = F)
-
-#Purity
-purity_all = data.frame("words" = c(original_mfd$p2, purity_words, purity_words_reduce, 
-                                       purity_words_reduce_exp2))
[…]

### 2019-03-18 scripts/Analysis.R

@@ -1,0 +1,491 @@
+##set working directory
+setwd("~/OneDrive - Missouri State University/RESEARCH/2 projects/Will-Pilot")
+
+##pull in the data
+master = read.csv("overalldata.csv", stringsAsFactors = F)
+
+##get rid of the blank stuff
+library(ngram)
+
+for (i in 1:nrow(master)) {
+  master$wordcount[i] = wordcount(master$Text[i])
+}
+
+nozero = subset(master, wordcount > 0)
+tapply(nozero$wordcount, nozero$Source, mean)
+tapply(nozero$wordcount, nozero$Source, sum)
+
+##take out the disqus ones
+nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
+
+##figure out the duplicates
+nodis$URLS = duplicated(nodis$Url)
+
+##all data
+final = subset(nodis, URLS == FALSE)
+
+tapply(final$wordcount, final$Source, mean)
+tapply(final$wordcount, final$Source, sum)
+
+#write.csv(final, "finaldata.csv")
+
+####start here####
+final = read.csv("finaldata.csv", stringsAsFactors = F)
+final = na.omit(final) #one weird NA line
+
+##figure out the percent of MFD words
+
+##the amount of time people used the original MFD words
+original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
+
+##adding forms/conjugations of words to original_mfd
+#harm/care
+original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
+                             "sympathetic","sympathies","damaged",
+                             "damaging","attacked","attacking","attacker",
+                             "attacks","attackers", "benefits", "benefitted",
+                             "benefitting", "cares", "cared", "caring", "crushes",
+                             "crushing", "crushed", "dangerous", "defends", "defending",
+                             "defended", "detroys", "destroyed", "destroying",
+                             "fights", "fought", "fighting", "guards", "guarded",
+                             "guarding", "harms", "harmed", "harming", "hurts",
+                             "hurting", "kills", "killed", "killing", "preserves",
+                             "preserved", "preserving", "protects", "protected",
+                             "protecting", "protection", "ruins", "ruined", "ruining",
+                             "safely", "safer", "shelters", "sheltered", "sheltering",
+                             "spurns", "spurned", "spurning", "stomps", "stomped",
+                             "stomping", "suffers", "suffered", "suffering",
+                             "violence", "warring")
+                             
+#fairness/reciprocity
[…]

### 2019-03-18 scripts/Scraping News Sites.R

@@ -1,0 +1,273 @@
+library(rvest)
+####NY Times####
+#Specifying the url for desired website to be scrapped
+url <- 'https://www.nytimes.com/section/politics'
+
+#Reading the HTML code from the website - headlines
+webpage <- read_html(url)
+headline_data = html_nodes(webpage,'.story-link a, .story-body a')
+#headline_data = html_text(headline_data) #convert to readable text
+#head(headline_data) #hmmm, I think it could work
+
+#okay, so I can get the urls this way, but idk how to get rid of the other crap
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep("http", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+  
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+  
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.story-content') 
+  
+  ##pull the text
+  text_data = html_text(headline_data)
+  
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+    } ##end for loop
+
+####NPR original front page####
+url2 = 'https://www.npr.org/sections/politics/'
+webpage2 = read_html(url2)
+headline_data2 = html_nodes(webpage2,'.title a')
+#headline_data = html_text(headline_data)
+#head(headline_data) #Very nice. NPR Politics does not show a huge list on its front page
+
+#Los Localizadores Uniformes de Recursos (URLs)
+attr_data2 = html_attrs(headline_data2) 
+attr_data2
+
+urlslist2 = unlist(attr_data2)
+urlslist2 = urlslist2[grep("http", urlslist2)]
+urlslist2
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
[…]

### 2019-03-18 scripts/Scraping practice.R

@@ -1,0 +1,143 @@
+library(rvest)
+#Specifying the url for desired website to be scrapped
+url <- 'http://www.imdb.com/search/title?count=100&release_date=2017,2017&title_type=feature'
+
+#Reading the HTML code from the website
+webpage <- read_html(url)
+
+#Using CSS selectors to scrap the rankings section
+rank_data_html <- html_nodes(webpage,'.text-primary')
+
+#Converting the ranking data to text
+rank_data <- html_text(rank_data_html)
+
+#Let's have a look at the rankings
+head(rank_data)
+
+#Data-Preprocessing: Converting rankings to numerical
+rank_data<-as.numeric(rank_data)
+
+#Let's have another look at the rankings
+head(rank_data)
+
+#Using CSS selectors to scrap the title section
+title_data_html <- html_nodes(webpage,'.lister-item-header a')
+
+#Converting the title data to text
+title_data <- html_text(title_data_html)
+
+#Let's have a look at the title
+head(title_data)
+
+#Using CSS selectors to scrap the description section
+description_data_html <- html_nodes(webpage,'.ratings-bar+ .text-muted')
+
+#Converting the description data to text
+description_data <- html_text(description_data_html)
+
+#Let's have a look at the description data
+head(description_data)
+
+#Data-Preprocessing: removing '\n'
+description_data<-gsub("\n","",description_data)
+
+#Let's have another look at the description data 
+head(description_data)
+
+#Using CSS selectors to scrap the Movie runtime section
+runtime_data_html <- html_nodes(webpage,'.text-muted .runtime')
+
+#Converting the runtime data to text
+runtime_data <- html_text(runtime_data_html)
+
+#Let's have a look at the runtime
+head(runtime_data)
+
+#Data-Preprocessing: removing mins and converting it to numerical
+
+runtime_data<-gsub(" min","",runtime_data)
+runtime_data<-as.numeric(runtime_data)
+
+#Let's have another look at the runtime data
+head(rank_data)
+
+#Using CSS selectors to scrap the Movie genre section
+genre_data_html <- html_nodes(webpage,'.genre')
+
+#Converting the genre data to text
+genre_data <- html_text(genre_data_html)
+
+#Let's have a look at the genre
+head(genre_data)
+
+#Data-Preprocessing: removing \n
+genre_data<-gsub("\n","",genre_data)
+
+#Data-Preprocessing: removing excess spaces
+genre_data<-gsub(" ","",genre_data)
+
[…]

### 2019-03-18 scripts/Untitled.R

@@ -1,0 +1,48 @@
+
+
+##you will run this for each foundation AFTER running the MTMM project 
+##through MTMM set up
+#Harm
+harm_all = data.frame("words" = c(original_mfd$h2, harm_words, harm_words_reduce, 
+                                  harm_words_reduce_exp2))
+harm_all$dataset = c(rep("orig", length(original_mfd$h2)),
+                           rep("all_exp1", length(harm_words)),
+                           rep("reduce_exp1", length(harm_words_reduce)),
+                           rep("reduce_exp2", length(harm_words_reduce_exp2)))
+write.csv(harm_all, "harm_words_total.csv", row.names = F)
+
+#Fair
+fair_all = data.frame("words" = c(original_mfd$f2, fair_words, fair_words_reduce, 
+                                  fair_words_reduce_exp2))
+fair_all$dataset = c(rep("orig", length(original_mfd$f2)),
+                     rep("all_exp1", length(fair_words)),
+                     rep("reduce_exp1", length(fair_words_reduce)),
+                     rep("reduce_exp2", length(fair_words_reduce_exp2)))
+write.csv(fair_all, "fair_words_total.csv", row.names = F)
+
+#Ingroup
+ingroup_all = data.frame("words" = c(original_mfd$i2, ingroup_words, ingroup_words_reduce, 
+                                     ingroup_words_reduce_exp2))
+ingroup_all$dataset = c(rep("orig", length(original_mfd$i2)),
+                     rep("all_exp1", length(ingroup_words)),
+                     rep("reduce_exp1", length(ingroup_words_reduce)),
+                     rep("reduce_exp2", length(ingroup_words_reduce_exp2)))
+write.csv(ingroup_all, "ingroup_words_total.csv", row.names = F)
+
+#Authority
+authority_all = data.frame("words" = c(original_mfd$a2, authority_words, authority_words_reduce, 
+                                     authority_words_reduce_exp2))
+authority_all$dataset = c(rep("orig", length(original_mfd$a2)),
+                        rep("all_exp1", length(authority_words)),
+                        rep("reduce_exp1", length(authority_words_reduce)),
+                        rep("reduce_exp2", length(authority_words_reduce_exp2)))
+write.csv(authority_all, "authority_words_total.csv", row.names = F)
+
+#Purity
+purity_all = data.frame("words" = c(original_mfd$p2, purity_words, purity_words_reduce, 
+                                       purity_words_reduce_exp2))
[…]

### 2019-03-18 scripts/selenium example.R

@@ -1,0 +1,81 @@
+library(rvest)
+library(RSelenium)
+
+##an example to show you what's happening
+rD <- rsDriver()
+remDr <- rD[["client"]]
+remDr$navigate("http://www.google.com/ncr")
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+##end example
+
+##NY times example
+rD <- rsDriver()
+remDr <- rD[["client"]]
+
+#page for NYTIMES
+url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
+
+#navigate to it
+remDr$navigate(url)
+
+#click the button 
+#don't change class name
+#right click --> inspect element 
+webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
+
+#with 752 results at 10 per page we need
+#752 - 10 original = 742 / 10 per click = 75 clicks
+
+for (i in 1:5) { #change this to 75 later
+  webElem$clickElement()
+  Sys.sleep(runif(1, 1, 5))
+}
+
+webpage <-remDr$getPageSource()
+
+#Reading the HTML code from the website - headlines
+webpage2 <- read_html(unlist(webpage))
+
+headline_data = html_nodes(webpage2,'a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep(".html", urlslist)]
+urlslist = urlslist[grep("/2018", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+#paste NY on front
+urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+  
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+  
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn') 
+  
+  ##pull the text
+  text_data = html_text(headline_data)
+  
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
[…]

### 2019-03-18 selenium example.R

@@ -1,81 +1,0 @@
-library(rvest)
-library(RSelenium)
-
-##an example to show you what's happening
-rD <- rsDriver()
-remDr <- rD[["client"]]
-remDr$navigate("http://www.google.com/ncr")
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-##end example
-
-##NY times example
-rD <- rsDriver()
-remDr <- rD[["client"]]
-
-#page for NYTIMES
-url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
-
-#navigate to it
-remDr$navigate(url)
-
-#click the button 
-#don't change class name
-#right click --> inspect element 
-webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
-
-#with 752 results at 10 per page we need
-#752 - 10 original = 742 / 10 per click = 75 clicks
-
-for (i in 1:5) { #change this to 75 later
-  webElem$clickElement()
-  Sys.sleep(runif(1, 1, 5))
-}
-
-webpage <-remDr$getPageSource()
-
-#Reading the HTML code from the website - headlines
-webpage2 <- read_html(unlist(webpage))
-
-headline_data = html_nodes(webpage2,'a')
-
-attr_data = html_attrs(headline_data) 
-attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep(".html", urlslist)]
-urlslist = urlslist[grep("/2018", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-#paste NY on front
-urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-  
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-  
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn') 
-  
-  ##pull the text
-  text_data = html_text(headline_data)
-  
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
[…]

### 2019-03-19 pilot_manuscript.Rmd
new descriptive stats section
adding NYtimes GS

@@
 
+## Descriptive Statistics
+
+overall valence for each source
+
+types/tokens ratios, etc. for each source also number of articles
+
+table - columns are types (unique words), tokens (total words), readability statistics, number of articles, total number of words, valence
+
+## Inferential Statistics
+
 To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
@@
 
-```{r NYTimes, eval = F, include = F}
+```{r NYTimes_kav, eval = F, include = F}
 
@@
 
+```
+
+```{r NYTimes_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#page for NYTIMES
+url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'
+
+#navigate to it
+remDr$navigate(url)
+
+#click the button 
+#don't change class name
+#right click --> inspect element 
+webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
+
+#with 803 results at 10 per page we need
+#803 - 10 original / 10 per click is 80 clicks
+
+for (i in 1:80) {
+  webElem$clickElement()
+  Sys.sleep(runif(1, 1, 5))
+}
+
+webpage <-remDr$getPageSource()
+
+#Reading the HTML code from the website - headlines
+webpage2 <- read_html(unlist(webpage))
+
+headline_data = html_nodes(webpage2,'a')
+
+attr_data = html_attrs(headline_data) 
+#attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep(".html", urlslist)]
+urlslist = urlslist[grep("/201", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+#paste NY on front
+urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
+
+  ##pull the text
+  text_data = html_text(headline_data)
+
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+  Sys.sleep(runif(1, 1, 10)) #don't make them angry
+} ##end for loop
+
+write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
+beep(sound = 5)
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
 ```

### 2019-03-19 pilot_manuscript.Rmd
not sure what this thing is doing
making some progress

@@
 ````{r NPR, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
 urlslist_final = c()
@@
 for (i in 1:2){ ##change this to 50
-  url2 = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
-  webpage2 = read_html(url2)
-  headline_data2 = html_nodes(webpage2,'.title')
-
-  #URLs
-  attr_data2 = html_attrs(headline_data2) 
-  urlslist2 = unlist(attr_data2)
-  urlslist2 = urlslist2[grep("http", urlslist2)]
-
-  #add them to an overall
-  urlslist_final = c(urlslist_final, urlslist2)
-
+
+  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
+
+  #navigate to it
+  remDr$navigate(url)
+
+  #get the page source
+  webpage <-remDr$getPageSource()
+
+  #Reading the HTML code from the website - headlines
+  webpage2 <- read_html(unlist(webpage))
+
+  #pull the links
+  headline_data = html_nodes(webpage2,'a')
+  attr_data = html_attrs(headline_data)
+
+  #deal with the links
+  urlslist = unlist(attr_data)
+  urlslist = urlslist[grep("^/201", urlslist)]
+  urlslist = unique(urlslist)
+
+  #combine into one list
+  urlslist_final = c(urlslist, urlslist_final)
+
+  #don't go too fast
   Sys.sleep(runif(1, 1, 5))
-}
+
+} #close the loop
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
 
@@
 } ##end for loop
+
 ```

### 2019-03-19 pilot_manuscript.Rmd
trying to figure out NPR

@@
 
-````{r NPR, eval = F, include = F}
+````{r NPR_kav, eval = F, include = F}
 library(rvest)
@@
 #create a blank space to put the links
-urlslist_final = c()
+urlslist_final = list()
 
 ##loop through the page number at the end until done with ~1000 / 20 = 50
-for (i in 1:2){ ##change this to 50
+for (i in 1:2) { ##change this to 50
 
@@
 
-  #get the page source
-  webpage <-remDr$getPageSource()
-
-  #Reading the HTML code from the website - headlines
-  webpage2 <- read_html(unlist(webpage))
-
-  #pull the links
-  headline_data = html_nodes(webpage2,'a')
-  attr_data = html_attrs(headline_data)
-
-  #deal with the links
-  urlslist = unlist(attr_data)
-  urlslist = urlslist[grep("^/201", urlslist)]
-  urlslist = unique(urlslist)
-
-  #combine into one list
-  urlslist_final = c(urlslist, urlslist_final)
+  #get the links
+  webElems <- remDr$findElements(using = "css", "[href]")
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
 

### 2019-03-22 pilot_manuscript.Rmd
gotten through slate

@@
 ##loop through the page number at the end until done with ~1000 / 20 = 50
-for (i in 1:2) { ##change this to 50
+for (i in 1:50) { ##change this to 50
 
@@
   remDr$navigate(url)
+
+  #scroll on the page
+  webscroll <- remDr$findElement("css", "body")
+  webscroll$sendKeysToElement(list(key = "end"))
 
@@
 
+beep(sound = 3)
+
+urlslist = unlist(urlslist_final)
+#find all the ones with /2018/
+urlslist2 = urlslist[grep("/2018", urlslist)]
+urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
+urlslist2 = unique(urlslist2)
+temp = strsplit(urlslist2, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#deal with the ones with extra parts
+temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
+
+#pull only the right dates
+rows = rownames(temp2[ temp2$`4` == 2018 & #must be 2018 and 
+                         (temp2$`5` == "09" & as.numeric(temp2$`6`)>=13 | 
+                            temp2$`5` == "10" & as.numeric(temp2$`6`)<=11), #Must be 9 or 10 
+                ])
+
+urlslist3 = urlslist2[as.numeric(rows)]
+
 ##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist_final), ncol = 3)
+NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
 colnames(NPRDF) = c("Source", "Url", "Text")
@@
 ##for loops
-for (i in 1:length(urlslist2)){
+for (i in 1:length(urlslist3)){
 
   ##read in the URL
-  webpage2 <- read_html(urlslist2[i])
+  webpage2 <- read_html(urlslist3[i])
 
@@
   NPRDF$Source[i] = "NPR"
-  NPRDF$Url[i] = urlslist2[i]
+  NPRDF$Url[i] = urlslist3[i]
   NPRDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
+} ##end for loop
+
+beep(sound = 3)
+
+write.csv(NPRDF, "NPR_kav.csv", row.names = F)
+
+```
+
+```{r NPR_shut, eval = F, include = F}
+
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+##loop through the page number at the end until done with ~3316 / 20 = 166
+for (i in 1:166) {
+
+  url = paste0('https://www.npr.org/search?query=government%20shutodwn&page=', i)
+
+  #navigate to it
+  remDr$navigate(url)
+
+  #scroll on the page
+  webscroll <- remDr$findElement("css", "body")
+  webscroll$sendKeysToElement(list(key = "end"))
+
+  #get the links
+  webElems <- remDr$findElements(using = "css", "[href]")
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
   Sys.sleep(runif(1, 1, 5))
+
+} #close the loop
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+urlslist = unlist(urlslist_final)
+#find all the ones with /2018/
+urlslist2 = urlslist[grep("/201", urlslist)]
+urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
+urlslist2 = unique(urlslist2)
+temp = strsplit(urlslist2, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#deal with the ones with extra parts
+temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
+
+#pull only the right dates
+rows = rownames(temp2[ (temp2$`4` == 2018 | temp2$`4` == 2019) & #must be 2018/19 and  
+                         (
+                           (temp2$`5` == "12" & as.numeric(temp2$`6`)>8 & temp2$`4` == 2018) | #after dec 12
+                            (temp2$`5`== "01" & temp2$`4` == 2019) | #all of jan
+                            (temp2$`5` == "02" & as.numeric(temp2$`6`)<8 & temp2$`4` == 2019)
+                           ), #before feb 8
+                ])
+
+urlslist3 = urlslist2[as.numeric(rows)]
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 315:length(urlslist3)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'#storytext > p')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  NPRDF$Source[i] = "NPR"
+  NPRDF$Url[i] = urlslist3[i]
+  NPRDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
 } ##end for loop
 
-```
-
-````{r Slate, eval = F, include = F}
-url3 = 'https://slate.com/search?q=kavanaugh&via=homepage_nav_search'
-webpage3 = read_html(url3)
-headline_data3 = html_nodes(webpage3,'.gs-title')
-
-#URLs
-attr_data3 = html_attrs(headline_data3) 
-attr_data3
-
-urlslist3 = unlist(attr_data3)
-urlslist3 = urlslist3[grep("http", urlslist3)]
-urlslist3
+beep(sound = 3)
+
+write.csv(NPRDF, "NPR_gs.csv", row.names = F)
+```
+
+````{r Slate_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://slate.com/search?q=kavanaugh&via=homepage_nav_search"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#appear to be 10 pages
+for (i in 1:10){
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
+
+  #don't go too fast for the page to load
+  Sys.sleep(runif(1, 1, 5))
+
+  #click on the page number
+  webClick[[i]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones with /2018/
+urlslist2 = urlslist[grep("/2018/10|/2018/09", urlslist)]
+urlslist2 = unique(urlslist2)
+
+#71 articles seems suspiciously low, so also scraped this page
+#https://slate.com/tag/brett-kavanaugh/
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#337 / 20 = 17 pages
+for (i in 1:17){
+
+  url = paste0("https://slate.com/tag/brett-kavanaugh/", i)
+
+  remDr$navigate(url)
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones with /2018/
+urlslist2.1 = urlslist[grep("/2018/10|/2018/09", urlslist)]
+urlslist2.1 = unique(urlslist2.1)
+
+urlslist3 = unique(c(urlslist2, urlslist2.1))
 
 ##start a data frame
-SlateDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(SlateDF) = c("Source", "Url", "Text")
-SlateDF = as.data.frame(SlateDF)
+SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(SLATEDF) = c("Source", "Url", "Text")
+SLATEDF = as.data.frame(SLATEDF)
 
@@
   ##read in the URL
-  webpage3 <- read_html(urlslist3[i])
+  webpage2 <- read_html(urlslist3[i])
 
   ##pull the specific nodes
-  headline_data3 = html_nodes(webpage3,'.slate-paragraph')
+  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
 
   ##pull the text
-  text_data3 = html_text(headline_data3)
+  text_data2 = html_text(headline_data2)
 
   ##save the data
-  SlateDF$Source[i] = "Slate"
-  SlateDF$Url[i] = urlslist3[i]
-  SlateDF$Text[i] = paste(text_data3, collapse = "")
+  SLATEDF$Source[i] = "SLATE"
+  SLATEDF$Url[i] = urlslist3[i]
+  SLATEDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
 } ##end for loop
+
+beep(sound = 3)
+
+write.csv(SLATEDF, "SLATE_kav.csv", row.names = F)
+
+```
+
+```{r SLATE_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://slate.com/search?q=government+shutdown"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#appear to be 10 pages
+for (i in 1:10){
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
+
+  #don't go too fast for the page to load
+  Sys.sleep(runif(1, 1, 5))
+
+  #click on the page number
+  webClick[[i]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones from 12 2018 to 02 2019
+urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
+urlslist2 = unique(urlslist2)
+
+#60 something articles seems suspiciously low, so also scraped this page
+#https://slate.com/tag/governtment-shutdown
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#354 / 20 = 18 pages
+for (i in 1:18){
+
+  url = paste0("https://slate.com/tag/government-shutdown/", i)
+
+  remDr$navigate(url)
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones with /2018/
+urlslist2.1 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
+urlslist2.1 = unique(urlslist2.1)
+
+urlslist3 = unique(c(urlslist2, urlslist2.1))
+
+##start a data frame
+SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(SLATEDF) = c("Source", "Url", "Text")
+SLATEDF = as.data.frame(SLATEDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  SLATEDF$Source[i] = "SLATE"
+  SLATEDF$Url[i] = urlslist3[i]
+  SLATEDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
+} ##end for loop
+
+#beep(sound = 3)
+
+write.csv(SLATEDF, "SLATE_gs.csv", row.names = F)
 ```

### 2019-03-22 temp.R

@@ -1,0 +1,128 @@
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://slate.com/search?q=government+shutdown"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#appear to be 10 pages
+for (i in 1:10){
+  
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
+  
+  #don't go too fast for the page to load
+  Sys.sleep(runif(1, 1, 5))
+  
+  #click on the page number
+  webClick[[i]]$clickElement()
+  
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+  
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+  
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+  
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones from 12 2018 to 02 2019
+urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
+urlslist2 = unique(urlslist2)
+
+#60 something articles seems suspiciously low, so also scraped this page
+#https://slate.com/tag/governtment-shutdown
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#354 / 20 = 18 pages
+for (i in 1:18){
+  
+  url = paste0("https://slate.com/tag/government-shutdown/", i)
+  
+  remDr$navigate(url)
+  
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+  
+  #find the urls for page X
[…]

### 2019-03-23 pilot_manuscript.Rmd
added more to Exp2 intro, including shutdown

@@
 The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
-They were selected for their widespread recognition and the fact they are easily categorized (by the general public) according to perceived political lean.
-In general, *The New York Times* and *NPR* are perceived by many to have a liberal bias or lean.
-In contrast, Fox News and Breitbart are believed to have a conservative bias or lean [@Mitchell2014].
+They were selected for their widespread recognition and the fact politcial partisans have strong preferences for some sources over others.
+The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported idealogical consistency represented by the consumers of several news sources.
+In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean.
+In contrast, Fox News and Breitbart are believed to have a conservative bias or lean.
+@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
+
 Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
@@
 
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
+The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals.
+The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns.
 On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
@@
 Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
+Concerns around abortion might be related either to *harm/care* or *purity/sanctity*.
 On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Likewise, arguments could be made that relate concerns regarding sexual violence to *harm/care* or *fairness/reciprocity*.
 Additionally, the moral duty of the Senate as the upper chamber in the U.S.
@@
 
+##U.S. Government Shutdown of 2018-2019
+
+The U.S.
+Federal Government partially shut down on December 22, 2018.
+The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019].
+The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border waLL.
+President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019].
+Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].
+
+The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
+President Trump signed the bill, ending the longest govenrment shutdown in U.S.
+history [@Axelrod2019].
+Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole [@Kheel2019].
+Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed [@Peoples2019].
+While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
+
+As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
+Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
+As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns [@Martin2019].
+Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
+Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people [@Martin2019].
+This example potentially ties into the five moral foundations.
+Theological concerns regarding the border wall might invoke *authority/respect* as well as *purity/sanctity*.
+
+Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
+In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
+
+# Method
+
 In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on the Kavanaugh confirmation hearing.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks before and two weeks after Kavanaugh's confirmation, owing to its prominence in the news.
+For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
+The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
 The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-
-# Method
 
@@
 news sources.
-These sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
-The sources favored by conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
+As in Experiment 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
+The sources favored by the highest proportion of consistent liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
+The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.

### 2019-03-24 pilot_manuscript.Rmd
first try at valence for sorces' articles
will do more later

@@
 
+```{r exp1 source descriptives, results = 'asis', echo = FALSE}
+#Get the final dataset split into the 4 sources
+final$Source = as.factor(final$Source)
+NYtimesDesc1 = subset(final, Source == "NY Times") #number of obs. = number of articles for that source; NYT = 406
+NPRDesc1 = subset(final, Source == "NPR") #NPR = 695 articles
+FoxDesc1 = subset(final, Source == "Fox News") #Fox = 503 articles
+BreitbartDesc1 = subset(final, Source == "Breitbart") #Breitbart = 1,437 articles
+
+##Add valence
+#NY Times
+NYTimes_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
+
+for (i in 1:nrow(NYtimesDesc1)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(NYtimesDesc1$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = NYtimesDesc1$Url[i]
+temp2$Source = NYtimesDesc1$Source[i]
+temp2$wordcount = NYtimesDesc1$wordcount[i]
+temp2$Text = NYtimesDesc1$Text[i]
+
+#bind with original
+NYTimes_final_desc = rbind(NYTimes_final_desc, temp2)
+}
+
+NYTimes_final_desc$valence = vlookup(NYTimes_final_desc$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#NPR
+NPR_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
+
+for (i in 1:nrow(NPRDesc1)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(NPRDesc1$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = NPRDesc1$Url[i]
+temp2$Source = NPRDesc1$Source[i]
+temp2$wordcount = NPRDesc1$wordcount[i]
+temp2$Text = NPRDesc1$Text[i]
+
+#bind with original
+NPR_final_desc = rbind(NPR_final_desc, temp2)
+}
+
+NPR_final_desc$valence = vlookup(NPR_final_desc$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#Fox News
+Fox_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
+
+for (i in 1:nrow(FoxDesc1)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(FoxDesc1$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = FoxDesc1$Url[i]
+temp2$Source = FoxDesc1$Source[i]
+temp2$wordcount = FoxDesc1$wordcount[i]
+temp2$Text = FoxDesc1$Text[i]
+
+#bind with original
+Fox_final_desc = rbind(Fox_final_desc, temp2)
+}
+
+Fox_final_desc$valence = vlookup(Fox_final_desc$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#Breitbart
+Breitbart_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
+
+for (i in 1:nrow(BreitbartDesc1)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(BreitbartDesc1$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = BreitbartDesc1$Url[i]
+temp2$Source = BreitbartDesc1$Source[i]
+temp2$wordcount = BreitbartDesc1$wordcount[i]
+temp2$Text = BreitbartDesc1$Text[i]
+
+#bind with original
+Breitbart_final_desc = rbind(Breitbart_final_desc, temp2)
+}
+
+Breitbart_final_desc$valence = vlookup(Breitbart_final_desc$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+##Eliminate NAs
+NYTimes_final_desc = na.omit(NYTimes_final_desc)
+NPR_final_desc = na.omit(NPR_final_desc)
+Fox_final_desc = na.omit(Fox_final_desc)
+Breitbart_final_desc = na.omit(Breitbart_final_desc)
+
+#Calculate mean valence by source
+NYTimes_valence_mean = mean(NYTimes_final_desc$valence)
+NPR_valence_mean = mean(NPR_final_desc$valence)
+Fox_valence_mean = mean(Fox_final_desc$valence)
+Breitbart_valence_mean = mean(Breitbart_final_desc$valence)
+
+```
 overall valence for each source

### 2019-03-25 pilot_manuscript.Rmd
almost done with breitbart

--- 2019-03-22 pilot_manuscript.Rmd
@@
 
-````{r HuffPo, eval = F, include = F}
-url4 = 'https://search.huffingtonpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s'
-webpage4 = read_html(url4)
-headline_data4 = html_nodes(webpage4,'.fw-b')
-
-#URLs
-attr_data4 = html_attrs(headline_data4) 
-attr_data4
-
-urlslist4 = unlist(attr_data4)
-urlslist4 = urlslist4[grep("http", urlslist4)]
-urlslist4
+````{r HuffPo_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#943 results with 10 per page 94 clicks
+for (i in 1:94){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "class name", "fz-20")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "class name", "next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
 
 ##start a data frame
-HuffpoDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
-colnames(HuffpoDF) = c("Source", "Url", "Text")
-HuffpoDF = as.data.frame(HuffpoDF)
-
-##for loops
-for (i in 1:length(urlslist4)){
-
-  ##read in the URL
-  webpage4 <- read_html(urlslist4[i])
-
-  ##pull the specific nodes
-  headline_data4 = html_nodes(webpage4,'p')
-
-  ##pull the text
-  text_data4 = html_text(headline_data4)
+HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HUFFPODF) = c("Source", "Url", "Text")
+HUFFPODF = as.data.frame(HUFFPODF)
+int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
+
+for (i in 937:length(urlslist)){
+
+  #convert the url
+  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
+  temp = gsub("%3a", ":", temp)
+  temp = gsub("%2f", "/", temp)
+
+  webpage = read_html(temp)
+  #figure out the date
+  headline_data = html_nodes(webpage, '.timestamp__date--published')
+  text_data = html_text(headline_data)
+  time = unlist(strsplit(text_data, split = "\n| "))[2]
+  time = as.Date(time, format = "%m/%d/%Y")
+
+  if (time %within% int) {
+    ##pull out the text
+    headline_data2 = html_nodes(webpage,'p') 
+    text_data2 = html_text(headline_data2)
 
     ##save the data
-  HuffpoDF$Source[i] = "Huffington Post"
-  HuffpoDF$Url[i] = urlslist4[i]
-  HuffpoDF$Text[i] = paste(text_data4, collapse = "")
-} ##end for loop
-```
-
-````{r Politico, eval = F, include = F}
-url5 = 'https://www.politico.com/search?q=kavanaugh&s=newest'
-webpage5 = read_html(url5)
-headline_data5 = html_nodes(webpage5,'.summary a')
-
-#URLs
-attr_data5 = html_attrs(headline_data5) 
-attr_data5
-
-urlslist5 = unlist(attr_data5)
-urlslist5 = urlslist5[grep("http", urlslist5)]
-urlslist5
+    HUFFPODF$Source[i] = "HUFFPO"
+    HUFFPODF$Url[i] = urlslist[i]
+    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 3)
+
+write.csv(HUFFPODF, "HUFFPO_kav.csv", row.names = F)
+```
+
+```{r HuffPo_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=government+shutdown&fr=huffpost_desktop"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#942 results with 10 per page 94 clicks
+for (i in 1:94){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "class name", "fz-20")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "class name", "next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 2)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
 
 ##start a data frame
-PoliticoDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
-colnames(PoliticoDF) = c("Source", "Url", "Text")
-PoliticoDF = as.data.frame(PoliticoDF)
-
-##for loops
-for (i in 1:length(urlslist5)){
-
-  ##read in the URL
-  webpage5 <- read_html(urlslist5[i])
-
-  ##pull the specific nodes
-  headline_data5 = html_nodes(webpage5,'.story-text > p')
-
-  ##pull the text
-  text_data5 = html_text(headline_data5)
+HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HUFFPODF) = c("Source", "Url", "Text")
+HUFFPODF = as.data.frame(HUFFPODF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
+
+for (i in 1:length(urlslist)){
+
+  #convert the url
+  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
+  temp = gsub("%3a", ":", temp)
+  temp = gsub("%2f", "/", temp)
+
+  webpage = read_html(temp)
+  #figure out the date
+  headline_data = html_nodes(webpage, '.timestamp__date--published')
+  text_data = html_text(headline_data)
+  time = unlist(strsplit(text_data, split = "\n| "))[2]
+  time = as.Date(time, format = "%m/%d/%Y")
+
+  if (time %within% int) {
+    ##pull out the text
+    headline_data2 = html_nodes(webpage,'p') 
+    text_data2 = html_text(headline_data2)
 
     ##save the data
-  PoliticoDF$Source[i] = "Politico"
-  PoliticoDF$Url[i] = urlslist5[i]
-  PoliticoDF$Text[i] = paste(text_data5, collapse = "")
-} ##end for loop
-```
-
-````{r Fox News, eval = F, include = F}
-url6 = 'https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=0'
-webpage6 = read_html(url6)
-headline_data6 = html_nodes(webpage6, 'h3 .ng-binding')
-
-attr_data6 = html_attrs(headline_data6) 
-attr_data6
-
-urlslist6 = unlist(attr_data6)
-urlslist6 = urlslist6[grep("http|.html", urlslist6)]
+    HUFFPODF$Source[i] = "HUFFPO"
+    HUFFPODF$Url[i] = urlslist[i]
+    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 2)
+
+write.csv(HUFFPODF, "HUFFPO_gs.csv", row.names = F)
+```
+
+````{r Politico_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=kavanaugh&pv=&c=&r=&start=09%2F13%2F2018&start_submit=09%2F13%2F2018&end=10%2F11%2F2018&end_submit=10%2F11%2F2018"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#749 with 20 per page with 37 clicks
+
+for (i in 1:37){
+
+  if (i > 1){
+    #navigate to the next page
+    url = paste0("https://www.politico.com/search/", i, 
+                 "?s=newest&q=kavanaugh&adv=true&start=09/13/2018&end=10/11/2018")
+    remDr$navigate(url)
+  }
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 7)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[grep("/2018/", urlslist)]
+urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
 
 ##start a data frame
-FoxDF = matrix(NA, nrow = length(urlslist6), ncol = 3)
-colnames(FoxDF) = c("Source", "Url", "Text")
-FoxDF = as.data.frame(FoxDF)
-
-##for loops
-for (i in 1:length(urlslist6)){
-
-  ##read in the URL
-  webpage6 <- read_html(urlslist6[i])
-
-  ##pull the specific nodes
-  headline_data6 = html_nodes(webpage6,'p+ p , .fn-video+ p , .twitter+ p , .speakable')
-
-  ##pull the text
-  text_data6 = html_text(headline_data6)
+POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(POLITICODF) = c("Source", "Url", "Text")
+POLITICODF = as.data.frame(POLITICODF)
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
 
   ##save the data
-  FoxDF$Source[i] = "Fox News"
-  FoxDF$Url[i] = urlslist6[i]
-  FoxDF$Text[i] = paste(text_data6, collapse = "")
-} ##end for loop
-```
-
-````{r Breitbart, eval = F, include = F}
-url7 = 'https://www.breitbart.com/search/?s=kavanaugh#gsc.tab=0&gsc.q=kavanaugh&gsc.page=1'
-webpage7 = read_html(url7)
-headline_data7 = html_nodes(webpage7, '.gs-title')
-
-attr_data7 = html_attrs(headline_data7) 
-attr_data7
-
-urlslist7 = unlist(attr_data7)
-urlslist7 = urlslist7[grep(urlslist7)]
+  POLITICODF$Source[i] = "POLITICO"
+  POLITICODF$Url[i] = urlslist[i]
+  POLITICODF$Text[i] = paste(text_data2, collapse = "")
+
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+beep(sound = 7)
+
+write.csv(POLITICODF, "POLITICO_kav.csv", row.names = F)
+#easiest one yet
+```
+
+```{r Politico_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=government+shutdown&pv=&c=&r=&start=12%2F08%2F2018&start_submit=12%2F08%2F2018&end=02%2F08%2F2019&end_submit=02%2F08%2F2019"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#1329 with 20 per page with 66 clicks
+
+for (i in 1:66){
+
+  if (i > 1){
+    #navigate to the next page
+    url = paste0("https://www.politico.com/search/", i, 
+                 "?s=newest&q=government shutdown&adv=true&start=12/08/2018&end=02/08/2019")
+    remDr$navigate(url)
+  }
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 7)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[grep("/2018/", urlslist)]
+urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
 
 ##start a data frame
-BreitbartDF = matrix(NA, nrow = length(urlslist7), ncol = 3)
-colnames(BreitbartDF) = c("Source", "Url", "Text")
-BreitbartDF = as.data.frame(BreitbartDF)
-
-##for loops
-for (i in 1:length(urlslist7)){
-
-  ##read in the URL
-  webpage7 <- read_html(urlslist7[i])
-
-  ##pull the specific nodes
-  headline_data7 = html_nodes(webpage7,'p , h2')
-
-  ##pull the text
-  text_data7 = html_text(headline_data7)
+POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(POLITICODF) = c("Source", "Url", "Text")
+POLITICODF = as.data.frame(POLITICODF)
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
 
   ##save the data
-  BreitbartDF$Source[i] = "Breitbart"
-  BreitbartDF$Url[i] = urlslist7[i]
-  BreitbartDF$Text[i] = paste(text_data7, collapse = "")
-} ##end for loop
+  POLITICODF$Source[i] = "POLITICO"
+  POLITICODF$Url[i] = urlslist[i]
+  POLITICODF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(POLITICODF, "POLITICO_gs.csv", row.names = F)
+
+```
+
+````{r Fox_kav, eval = F, include = F}
+
+##start a data frame
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#1651 with 10 per page with 165 clicks
+
+for (i in 1:165){
+
+    #navigate to the page
+    url = paste0("https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=",
+                 (i-1)*10)
+    remDr$navigate(url)
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", ".ng-binding")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("video.", urlslist))] #take out videos
+urlslist = urlslist[-c(grep("/search-results", urlslist))] #take out search result fake links
+
+##start a data frame
+FOXDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(FOXDF) = c("Source", "Url", "Text")
+FOXDF = as.data.frame(FOXDF)
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  FOXDF$Source[i] = "FOX"
+  FOXDF$Url[i] = urlslist[i]
+  FOXDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(FOXDF, "FOX_kav.csv", row.names = F)
+```
+
+````{r Breitbart_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.breitbart.com/tag/brett-kavanaugh/"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+for (i in 1:42){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "h2 a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  if (i > 1)
+    {
+  url = paste0("https://www.breitbart.com/tag/brett-kavanaugh/page/",
+               i+1, "/")
+  remDr$navigate(url)
+  }
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
+                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
+                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
+                       ])
+
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(BREITBARTDF) = c("Source", "Url", "Text")
+BREITBARTDF = as.data.frame(BREITBARTDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'h2, p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  BREITBARTDF$Source[i] = "BREITBART"
+  BREITBARTDF$Url[i] = urlslist3[i]
+  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(BREITBARTDF, "BREITBART_kav.csv", row.names = F)
 ```

### 2019-03-25 temp.R

@@ -1,128 +1,91 @@
 library(rvest)
 library(RSelenium)
 library(beepr)
+library(lubridate)
 
 #open the browser
 rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
 remDr <- rD[["client"]]
 
-url = "https://slate.com/search?q=government+shutdown"
-
-remDr$navigate(url)
-
 #create a blank space to put the links
 urlslist_final = list()
 
+url = "https://www.breitbart.com/tag/government-shutdown/"
+
+remDr$navigate(url)
+
 #loop over the results and go through them
-#appear to be 10 pages
-for (i in 1:10){
+for (i in 1:16){
   
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "h2 a")
   
-  #don't go too fast for the page to load
-  Sys.sleep(runif(1, 1, 5))
-  
-  #click on the page number
-  webClick[[i]]$clickElement()
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  if (i > 1)
+    {
+  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
+               i+1, "/")
+  remDr$navigate(url)
+  }
   
   #page reload
   Sys.sleep(runif(1, 1, 5))
   
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-  
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-  
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
 }
 
 remDr$close()
 # stop the selenium server
 rD[["server"]]$stop()
 
-beep(sound = 3)
+beep(sound = 6)
 
 ##deal with the URLS
 urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
 
-#find all the ones from 12 2018 to 02 2019
-urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
-urlslist2 = unique(urlslist2)
[…]

### 2019-03-25 pilot_manuscript.Rmd
rush time

@@
 
-````{r Rush Limbaugh, eval = F, include = F}
-url8 = 'https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1'
-webpage8 = read_html(url8)
-#headline_data8 = html_nodes(webpage8, 'a')    trying something different
-headline_data8 = html_nodes(webpage8, '.ais-hits--content a')
-
-attr_data8 = html_attrs(headline_data8) 
-attr_data8
-
-urlslist8 = unlist(attr_data8)
-urlslist8 = urlslist8[grep(urlslist8)]
+```{r Breitbart_gs, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.breitbart.com/tag/government-shutdown/"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+for (i in 1:16){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "h2 a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  if (i > 1)
+    {
+  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
+               i+1, "/")
+  remDr$navigate(url)
+  }
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
+                         (
+                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
+                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
+                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
+                         ), #before feb 8
+                       ])
+
+urlslist3 = urlslist[as.numeric(rows)]
 
 ##start a data frame
-RushDF = matrix(NA, nrow = length(urlslist8), ncol = 3)
-colnames(RushDF) = c("Source", "Url", "Text")
-RushDF = as.data.frame(RushDF)
-
-##for loops
-for (i in 1:length(urlslist8)){
-
-  ##read in the URL
-  webpage8 <- read_html(urlslist8[i])
-
-  ##pull the specific nodes
-  headline_data8 = html_nodes(webpage8,'p')
-
-  ##pull the text
-  text_data8 = html_text(headline_data8)
+BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(BREITBARTDF) = c("Source", "Url", "Text")
+BREITBARTDF = as.data.frame(BREITBARTDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'h2, p') 
+  text_data2 = html_text(headline_data2)
 
   ##save the data
-  RushDF$Source[i] = "Rush Limbaugh"
-  RushDF$Url[i] = urlslist8[i]
-  RushDF$Text[i] = paste(text_data8, collapse = "")
-} ##end for loop
+  BREITBARTDF$Source[i] = "BREITBART"
+  BREITBARTDF$Url[i] = urlslist3[i]
+  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(BREITBARTDF, "BREITBART_gs.csv", row.names = F)
+```
+
+````{r Rush_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+##18 pages
+for (i in 1:18){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
+
+  #click on the page number
+  webClick[[18]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
+                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
+                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
+                       ])
+
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(RUSHDF) = c("Source", "Url", "Text")
+RUSHDF = as.data.frame(RUSHDF)
+
+for (i in 49:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  RUSHDF$Source[i] = "RUSH"
+  RUSHDF$Url[i] = urlslist3[i]
+  RUSHDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(RUSHDF, "RUSH_kav.csv", row.names = F)
 ```

### 2019-03-25 temp.R

@@ -10,25 +10,25 @@ remDr <- rD[["client"]]
 #create a blank space to put the links
 urlslist_final = list()
 
-url = "https://www.breitbart.com/tag/government-shutdown/"
+url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"
 
 remDr$navigate(url)
 
 #loop over the results and go through them
-for (i in 1:16){
+##18 pages
+for (i in 1:47){
   
   #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "h2 a")
+  webElems <- remDr$findElements(using = "css", "a")
   
   #add the urls to a list
   urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
 
-  if (i > 1)
-    {
-  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
-               i+1, "/")
-  remDr$navigate(url)
-  }
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
+  
+  #click on the page number
+  webClick[[18]]$clickElement()
   
   #page reload
   Sys.sleep(runif(1, 1, 5))
@@ -45,6 +45,7 @@ beep(sound = 6)
 urlslist = unlist(urlslist_final)
 urlslist = unique(urlslist)
 urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
 
 ##find the right dates
 temp = strsplit(urlslist, split = "/")
@@ -59,26 +60,25 @@ rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/1
                              (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
                          ), #before feb 8
                        ])
-
 urlslist3 = urlslist[as.numeric(rows)]
 
 ##start a data frame
-BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(BREITBARTDF) = c("Source", "Url", "Text")
-BREITBARTDF = as.data.frame(BREITBARTDF)
[…]

### 2019-03-25 pilot_manuscript.Rmd
adding more runs

@@
 
+```{r Rush_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+##18 pages
+for (i in 1:47){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
+
+  #click on the page number
+  webClick[[18]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
+                         (
+                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
+                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
+                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
+                         ), #before feb 8
+                       ])
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(RUSHDF) = c("Source", "Url", "Text")
+RUSHDF = as.data.frame(RUSHDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  RUSHDF$Source[i] = "RUSH"
+  RUSHDF$Url[i] = urlslist3[i]
+  RUSHDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(RUSHDF, "RUSH_gs.csv", row.names = F)
+
+```
+
 ````{r Blaze, eval = F, include = F}

### 2019-03-25 temp.R

@@ -68,7 +68,7 @@ colnames(RUSHDF) = c("Source", "Url", "Text")
 RUSHDF = as.data.frame(RUSHDF)
 
 
-for (i in 49:length(urlslist3)){
+for (i in 1:length(urlslist3)){
   
   webpage = read_html(urlslist3[i])
   

### 2019-03-25 temp.R
updating with blaze

@@ -7,45 +7,39 @@ library(lubridate)
 rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
 remDr <- rD[["client"]]
 
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"
+url = "https://www.theblaze.com/search/?q=kavanaugh"
 
 remDr$navigate(url)
 
-#loop over the results and go through them
-##18 pages
-for (i in 1:47){
+webClick <- remDr$findElements(using = "css", ".action-btn")
+
+#click next until done
+while (length(webClick) > 0 ) { 
   
   #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
+  webClick <- remDr$findElements(using = "css", ".action-btn")
   
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
+  webClick[[1]]$clickElement()
   
-  #click on the page number
-  webClick[[18]]$clickElement()
-  
-  #page reload
   Sys.sleep(runif(1, 1, 5))
-  
 }
+
+#find the urls for page X
+webElems <- remDr$findElements(using = "css", "a")
+
+#add the urls to a list
+urlslist_final = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
 
 remDr$close()
 # stop the selenium server
 rD[["server"]]$stop()
 
-beep(sound = 6)
 
 ##deal with the URLS
-urlslist = unlist(urlslist_final)
+urlslist = urlslist_final
 urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
+urlslist = urlslist[-c(grep("video/", urlslist))]
+urlslist = urlslist[grep("/news/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
 
 ##find the right dates
 temp = strsplit(urlslist, split = "/")
[…]

### 2019-03-25 pilot_manuscript.Rmd
stuff
here's the powerpoint

@@
 ```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("iexp1_data/ngroup_words_total.csv", stringsAsFactors = F)
+ingroup_all = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r exp1 source descriptives, results = 'asis', echo = FALSE}
+
+final$uniquewords = NA
+final$valenceavg = NA
+
+for (i in 1:nrow(final)){
+
+  #add unique
+  final$uniquewords[i] = length(unique(unlist(strsplit(final$stemmed[i], " "))))
+
+  #add valence
+  tempwords = as.data.frame(unlist(strsplit(final$stemmed[i], " ")))
+  colnames(tempwords) = "theword"
+  tempwords$tempval = vlookup(tempwords$theword, #index in original data
+                    warriner, #where's the stuff you want to put in
+                    "V.Mean.Sum", #what column is the stuff you want
+                    "Word2") #what's the matching index
+
+}
+
 #Get the final dataset split into the 4 sources
@@
 
-for (i in 49:length(urlslist3)){
+for (i in 1:length(urlslist3)){
 
@@
 #loop over the results and go through them
-##18 pages
+##47 pages
 for (i in 1:47){

### 2019-03-25 pilot_manuscript.Rmd
updated the graph and saved you a picture

@@
 
-```{r exp1 source descriptives, results = 'asis', echo = FALSE}
+```{r exp1 source descriptives, results = 'asis', echo = FALSE, message = F}
 
@@
 
-}
-
-#Get the final dataset split into the 4 sources
-final$Source = as.factor(final$Source)
-NYtimesDesc1 = subset(final, Source == "NY Times") #number of obs. = number of articles for that source; NYT = 406
-NPRDesc1 = subset(final, Source == "NPR") #NPR = 695 articles
-FoxDesc1 = subset(final, Source == "Fox News") #Fox = 503 articles
-BreitbartDesc1 = subset(final, Source == "Breitbart") #Breitbart = 1,437 articles
-
-##Add valence
-#NY Times
-NYTimes_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
-
-for (i in 1:nrow(NYtimesDesc1)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(NYtimesDesc1$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = NYtimesDesc1$Url[i]
-temp2$Source = NYtimesDesc1$Source[i]
-temp2$wordcount = NYtimesDesc1$wordcount[i]
-temp2$Text = NYtimesDesc1$Text[i]
-
-#bind with original
-NYTimes_final_desc = rbind(NYTimes_final_desc, temp2)
-}
-
-NYTimes_final_desc$valence = vlookup(NYTimes_final_desc$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#NPR
-NPR_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
-
-for (i in 1:nrow(NPRDesc1)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(NPRDesc1$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = NPRDesc1$Url[i]
-temp2$Source = NPRDesc1$Source[i]
-temp2$wordcount = NPRDesc1$wordcount[i]
-temp2$Text = NPRDesc1$Text[i]
-
-#bind with original
-NPR_final_desc = rbind(NPR_final_desc, temp2)
-}
-
-NPR_final_desc$valence = vlookup(NPR_final_desc$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#Fox News
-Fox_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
-
-for (i in 1:nrow(FoxDesc1)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(FoxDesc1$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = FoxDesc1$Url[i]
-temp2$Source = FoxDesc1$Source[i]
-temp2$wordcount = FoxDesc1$wordcount[i]
-temp2$Text = FoxDesc1$Text[i]
-
-#bind with original
-Fox_final_desc = rbind(Fox_final_desc, temp2)
-}
-
-Fox_final_desc$valence = vlookup(Fox_final_desc$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#Breitbart
-Breitbart_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)
-
-for (i in 1:nrow(BreitbartDesc1)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(BreitbartDesc1$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = BreitbartDesc1$Url[i]
-temp2$Source = BreitbartDesc1$Source[i]
-temp2$wordcount = BreitbartDesc1$wordcount[i]
-temp2$Text = BreitbartDesc1$Text[i]
-
-#bind with original
-Breitbart_final_desc = rbind(Breitbart_final_desc, temp2)
-}
-
-Breitbart_final_desc$valence = vlookup(Breitbart_final_desc$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-##Eliminate NAs
-NYTimes_final_desc = na.omit(NYTimes_final_desc)
-NPR_final_desc = na.omit(NPR_final_desc)
-Fox_final_desc = na.omit(Fox_final_desc)
-Breitbart_final_desc = na.omit(Breitbart_final_desc)
-
-#Calculate mean valence by source
-NYTimes_valence_mean = mean(NYTimes_final_desc$valence)
-NPR_valence_mean = mean(NPR_final_desc$valence)
-Fox_valence_mean = mean(Fox_final_desc$valence)
-Breitbart_valence_mean = mean(Breitbart_final_desc$valence)
-
-```
+  final$valenceavg[i] = mean(tempwords$tempval, na.rm = T)
+
+}
+
+tapply(final$valenceavg, final$Source, mean)
+tapply(final$valenceavg, final$Source, sd)
+tapply(final$wordcount, final$Source, mean)
+tapply(final$wordcount, final$Source, sd)
+tapply(final$uniquewords, final$Source, mean)
+tapply(final$uniquewords, final$Source, sd)
+tapply(final$Source, final$Source, length)
+tapply(final$wordcount, final$Source, sum)
+
+library(quanteda)
+
+final$FK = NA
+
+for (i in 1:nrow(final)){
+  final$FK[i] = unlist(textstat_readability(final$Text[i], 
+                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
+}
+
+tapply(final$FK, final$Source, mean)
+tapply(final$FK, final$Source, sd)
+
+```
+
 overall valence for each source
@@
 
+```{r conference-pic, eval = F, include = F}
+library(ggplot2)
+library(reshape)
+
+cleanup = theme(panel.grid.major = element_blank(), 
+                panel.grid.minor = element_blank(), 
+                panel.background = element_blank(), 
+                axis.line.x = element_line(color = "black"),
+                axis.line.y = element_line(color = "black"),
+                legend.key = element_rect(fill = "white"),
+                text = element_text(size = 10))
+
+graphdata = as.data.frame(tableprint)
+graphlong = melt(graphdata[ , c(1,2,4)], 
+                 id = "Foundation")
+graphlong2 = melt(graphdata[ , c(1, 3,5)],
+                  id = "Foundation",
+                  measured = c("SD_C", "SD_L"))
+graphlong$sd = graphlong2$value
+graphlong$lower = as.numeric(as.character(graphlong$value)) - 2*as.numeric(as.character(graphlong$sd))
+graphlong$upper = as.numeric(as.character(graphlong$value)) + 2*as.numeric(as.character(graphlong$sd))
+
+graphlong$value = as.numeric(as.character(graphlong$value))
+
+graph_data = ggplot(graphlong, aes(Foundation, value, color = variable)) + 
+  geom_point(position = position_dodge(width = 0.90)) +
+  geom_errorbar(aes(ymin = lower, ymax = upper), 
+                position = position_dodge(width = 0.90),
+                width = .2) + 
+  cleanup +
+  ylab("Mean Weighted Valence") + 
+  scale_color_manual(values = c("red", "blue"),
+                       labels = c("Conservative", "Liberal"),
+                       name = "Party") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
+  geom_hline(yintercept = 0, linetype = 1, color = "black")
+
+tiff(filename = "exp1_graph.tiff", res = 300, width = 4, 
+     height = 3, units = 'in', compression = "lzw")
+plot(graph_data)
+dev.off()
+
+```
+
 # Discussion

### 2019-03-25 temp.R
updated blaze

@@ -7,7 +7,7 @@ library(lubridate)
 rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
 remDr <- rD[["client"]]
 
-url = "https://www.theblaze.com/search/?q=kavanaugh"
+url = "https://www.theblaze.com/search/?q=government+shutdown"
 
 remDr$navigate(url)
 
@@ -39,39 +39,33 @@ rD[["server"]]$stop()
 urlslist = urlslist_final
 urlslist = unique(urlslist)
 urlslist = urlslist[-c(grep("video/", urlslist))]
-urlslist = urlslist[grep("/news/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
-                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
-                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
+urlslist = urlslist[grep("/news/", urlslist)]
+urlslist = urlslist[-c(grep("/201[3-7]", urlslist))]
 
 ##start a data frame
-BLAZEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+BLAZEDF = matrix(NA, nrow = length(urlslist), ncol = 3)
 colnames(BLAZEDF) = c("Source", "Url", "Text")
 BLAZEDF = as.data.frame(BLAZEDF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
 
 
-for (i in 1:length(urlslist3)){
+for (i in 1:length(urlslist)){
   
-  webpage = read_html(urlslist3[i])
+  webpage = read_html(urlslist[i])
   
-  headline_data2 = html_nodes(webpage,'h1, h3, p') 
-  text_data2 = html_text(headline_data2)
+  headline_data = html_nodes(webpage, '.post-date')
+  text_data = html_text(headline_data)
[…]

### 2019-03-26 pilot_manuscript.Rmd
complete!

@@
 
-````{r Blaze, eval = F, include = F}
+````{r Blaze_kav, eval = F, include = F}
 url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
@@
 
-````{r Sean Hannity, eval = F, include = F}
-url10 = 'https://www.hannity.com/'
-webpage10 = read_html(url10)
-headline_data10 = html_nodes(webpage10, '.gs-title')
-
-attr_data10 = html_attrs(headline_data10) 
-attr_data10
-
-urlslist10 = unlist(attr_data10)
-urlslist10 = urlslist10[grep(urlslist10)]
+```{r Blaze_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.theblaze.com/search/?q=government+shutdown"
+
+remDr$navigate(url)
+
+webClick <- remDr$findElements(using = "css", ".action-btn")
+
+#click next until done
+while (length(webClick) > 0 ) {
+
+  #find the urls for page X
+  webClick <- remDr$findElements(using = "css", ".action-btn")
+
+  webClick[[1]]$clickElement()
+
+  Sys.sleep(runif(1, 1, 5))
+}
+
+#find the urls for page X
+webElems <- remDr$findElements(using = "css", "a")
+
+#add the urls to a list
+urlslist_final = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+##deal with the URLS
+urlslist = urlslist_final
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("video/", urlslist))]
+urlslist = urlslist[grep("/news/", urlslist)]
+urlslist = urlslist[-c(grep("/201[3-7]", urlslist))]
 
 ##start a data frame
-SeanDF = matrix(NA, nrow = length(urlslist10), ncol = 3)
-colnames(SeanDF) = c("Source", "Url", "Text")
-SeanDF = as.data.frame(SeanDF)
-
-##for loops
-for (i in 1:length(urlslist10)){
-
-  ##read in the URL
-  webpage10 <- read_html(urlslist10[i])
-
-  ##pull the specific nodes
-  headline_data10 = html_nodes(webpage10,'p')
-
-  ##pull the text
-  text_data10 = html_text(headline_data10)
+BLAZEDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(BLAZEDF) = c("Source", "Url", "Text")
+BLAZEDF = as.data.frame(BLAZEDF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data = html_nodes(webpage, '.post-date')
+  text_data = html_text(headline_data)
+  date = as.Date(text_data, "%B %d, %Y")
+
+  if (date %within% int){
+    headline_data2 = html_nodes(webpage,'h1, h3, p') 
+    text_data2 = html_text(headline_data2)
 
     ##save the data
-  SeanDF$Source[i] = "Sean Hannity"
-  SeanDF$Url[i] = urlslist10[i]
-  SeanDF$Text[i] = paste(text_data10, collapse = "")
-} ##end for loop
+    BLAZEDF$Source[i] = "BLAZE"
+    BLAZEDF$Url[i] = urlslist[i]
+    BLAZEDF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(BLAZEDF, "BLAZE_gs.csv", row.names = F)
+
+```
+
+```{r Hannity_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.hannity.com/trending/brett-kavanaugh/"
+
+remDr$navigate(url)
+
+urlslist_final = list()
+
+for (i in 1:4){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #move on to the next page
+  url = paste0("https://www.hannity.com/trending/brett-kavanaugh/?pg=", i+1)
+
+  remDr$navigate(url)
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+
+#also use google search to see if we can find more
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.google.com/search?q=kavanaugh+site%3Ahannity.com&source=lnt&tbs=cdr%3A1%2Ccd_min%3A9%2F13%2F2018%2Ccd_max%3A10%2F11%2F2018&tbm="
+
+remDr$navigate(url)
+
+urlslist_final2 = list()
+
+for (i in 1:3){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "link text", "Next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+urlslist2 = unlist(urlslist_final2)
+urlslist2 = c(urlslist, urlslist2)
+urlslist2 = unique(urlslist2)
+urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
+urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
+urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
+
+##start a data frame
+HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HANNITYDF) = c("Source", "Url", "Text")
+HANNITYDF = as.data.frame(HANNITYDF)
+int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data = html_nodes(webpage, '.author-info')
+  text_data = html_text(headline_data)
+  text_data = strsplit(text_data, " ")[[1]][7]
+  date = as.Date(text_data, "%m.%d.%y")
+
+  if (date %within% int){
+    headline_data2 = html_nodes(webpage,'h1, p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    HANNITYDF$Source[i] = "HANNITY"
+    HANNITYDF$Url[i] = urlslist3[i]
+    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(HANNITYDF, "HANNITY_kav.csv", row.names = F)
+```
+
+```{r Hannity_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "http://www.hannity.com/trending/shutdown/"
+
+remDr$navigate(url)
+
+urlslist_final = list()
+
+for (i in 1:4){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #move on to the next page
+  url = paste0("http://www.hannity.com/trending/shutdown/?pg=", i+1)
+
+  remDr$navigate(url)
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+
+#also use google search to see if we can find more
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.google.com/search?biw=1366&bih=632&tbs=cdr%3A1%2Ccd_min%3A12%2F8%2F2018%2Ccd_max%3A2%2F8%2F2019&ei=gECaXNe8Aaft_Qb9w7G4BA&q=government+shutdown+site%3Ahannity.com&oq=government+shutdown+site%3Ahannity.com&gs_l=psy-ab.3...0.0..1915...0.0..0.0.0.......0......gws-wiz.aFps0nA33mY"
+
+remDr$navigate(url)
+
+urlslist_final2 = list()
+
+for (i in 1:9){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "link text", "Next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+urlslist2 = unlist(urlslist_final2)
+urlslist2 = c(urlslist, urlslist2)
+urlslist2 = unique(urlslist2)
+urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
+urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
+urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
+
+##start a data frame
+HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HANNITYDF) = c("Source", "Url", "Text")
+HANNITYDF = as.data.frame(HANNITYDF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data = html_nodes(webpage, '.author-info')
+  text_data = html_text(headline_data)
+  text_data = strsplit(text_data, " ")[[1]][7]
+  date = as.Date(text_data, "%m.%d.%y")
+
+  if (date %within% int){
+    headline_data2 = html_nodes(webpage,'h1, p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    HANNITYDF$Source[i] = "HANNITY"
+    HANNITYDF$Url[i] = urlslist3[i]
+    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(HANNITYDF, "HANNITY_gs.csv", row.names = F)
+
 ```

### 2019-03-26 temp.R

@@ -7,28 +7,28 @@ library(lubridate)
 rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
 remDr <- rD[["client"]]
 
-url = "https://www.theblaze.com/search/?q=government+shutdown"
+url = "http://www.hannity.com/trending/shutdown/"
 
 remDr$navigate(url)
 
-webClick <- remDr$findElements(using = "css", ".action-btn")
+urlslist_final = list()
 
-#click next until done
-while (length(webClick) > 0 ) { 
+for (i in 1:4){
   
   #find the urls for page X
-  webClick <- remDr$findElements(using = "css", ".action-btn")
+  webElems <- remDr$findElements(using = "css", "a")
   
-  webClick[[1]]$clickElement()
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
   
-  Sys.sleep(runif(1, 1, 5))
+  #move on to the next page
+  url = paste0("http://www.hannity.com/trending/shutdown/?pg=", i+1)
+  
+  remDr$navigate(url)
+  
+  Sys.sleep(runif(1,1,5))
+  
 }
-
-#find the urls for page X
-webElems <- remDr$findElements(using = "css", "a")
-
-#add the urls to a list
-urlslist_final = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
 
 remDr$close()
 # stop the selenium server
@@ -36,35 +36,74 @@ rD[["server"]]$stop()
 
 
 ##deal with the URLS
-urlslist = urlslist_final
+urlslist = unlist(urlslist_final)
 urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("video/", urlslist))]
-urlslist = urlslist[grep("/news/", urlslist)]
-urlslist = urlslist[-c(grep("/201[3-7]", urlslist))]
+
+#also use google search to see if we can find more
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
[…]

### 2019-03-31 pilot_manuscript.Rmd
Added scripts for Exp2 analysis

@@
 The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
-*Harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm.
+*harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm.
 *Fairness/reciprocity* represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
@@
 
+```{r data_clean_kav, eval = T, echo = F}
+##combine all kav data into one dataset
+#read it in
+NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv")
+NPR_kav = read.csv("exp2_data/NPR_kav.csv")
+SLATE_kav = read.csv("exp2_data/SLATE_kav.csv")
+HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv")
+POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv")
+FOX_kav = read.csv("exp2_data/FOX_kav.csv")
+BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv")
+RUSH_kav = read.csv("exp2_data/RUSH_kav.csv")
+BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv")
+HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv")
+
+#merge it together
+overalldata_kav = rbind(NYtimes_kav, NPR_kav)
+overalldata_kav = rbind(overalldata_kav, SLATE_kav)
+overalldata_kav = rbind(overalldata_kav, HUFFPO_kav)
+overalldata_kav = rbind(overalldata_kav, POLITICO_kav)
+overalldata_kav = rbind(overalldata_kav, FOX_kav)
+overalldata_kav = rbind(overalldata_kav, BREITBART_kav)
+overalldata_kav = rbind(overalldata_kav, RUSH_kav)
+overalldata_kav = rbind(overalldata_kav, BLAZE_kav)
+overalldata_kav = rbind(overalldata_kav, HANNITY_kav)
+
+write.csv(overalldata_kav, "exp2_data/overalldata_kav.csv", row.names = F)
+
+##pull in the data
+master_kav = read.csv("exp2_data/overalldata_kav.csv", stringsAsFactors = F)
+
+##get rid of the blank stuff
+library(ngram)
+
+for (i in 1:nrow(master_kav)) {
+  master_kav$wordcount[i] = wordcount(master_kav$Text[i])
+}
+
+nozero = subset(master_kav, wordcount > 0)
+tapply(nozero$wordcount, nozero$Source, mean)
+tapply(nozero$wordcount, nozero$Source, sum)
+
+##take out the disqus ones
+nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
+
+##figure out the duplicates
+nodis$URLS = duplicated(nodis$Url)
+
+##all data
+final_kav = subset(nodis, URLS == FALSE)
+
+tapply(final_kav$wordcount, final_kav$Source, mean)
+tapply(final_kav$wordcount, final_kav$Source, sum)
+
+write.csv(final_kav, "exp2_data/finaldata_kav.csv")
+```
+
+```{r data_clean_gs, eval = T, echo = F}
+##combine all gs data into one dataset
+#read it in
+NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv")
+NPR_gs = read.csv("exp2_data/NPR_gs.csv")
+SLATE_gs = read.csv("exp2_data/SLATE_gs.csv")
+HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv")
+POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv")
+FOX_gs = read.csv("exp2_data/FOX_gs.csv")
+BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv")
+RUSH_gs = read.csv("exp2_data/RUSH_gs.csv")
+BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv")
+HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv")
+
+#merge it together
+overalldata_gs = rbind(NYtimes_gs, NPR_gs)
+overalldata_gs = rbind(overalldata_gs, SLATE_gs)
+overalldata_gs = rbind(overalldata_gs, HUFFPO_gs)
+overalldata_gs = rbind(overalldata_gs, POLITICO_gs)
+overalldata_gs = rbind(overalldata_gs, FOX_gs)
+overalldata_gs = rbind(overalldata_gs, BREITBART_gs)
+overalldata_gs = rbind(overalldata_gs, RUSH_gs)
+overalldata_gs = rbind(overalldata_gs, BLAZE_gs)
+overalldata_gs = rbind(overalldata_gs, HANNITY_gs)
+
+write.csv(overalldata_gs, "exp2_data/overalldata_gs.csv", row.names = F)
+
+##pull in the data
+master_gs = read.csv("exp2_data/overalldata_gs.csv", stringsAsFactors = F)
+
+##get rid of the blank stuff
+library(ngram)
+
+for (i in 1:nrow(master_gs)) {
+  master_gs$wordcount[i] = wordcount(master_gs$Text[i])
+}
+
+nozero = subset(master_gs, wordcount > 0)
+tapply(nozero$wordcount, nozero$Source, mean)
+tapply(nozero$wordcount, nozero$Source, sum)
+
+##take out the disqus ones
+nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
+
+##figure out the duplicates
+nodis$URLS = duplicated(nodis$Url)
+
+##all data
+final_gs = subset(nodis, URLS == FALSE)
+
+tapply(final_gs$wordcount, final_gs$Source, mean)
+tapply(final_gs$wordcount, final_gs$Source, sum)
+
+write.csv(final_gs, "exp2_data/finaldata_gs.csv")
+```
+
+```{r stem_text_both, eval = T, echo = F}
+##stem Kav text
+final_kav = read.csv("exp2_data/finaldata_kav.csv", stringsAsFactors = F)
+#final = na.omit(final) #one weird NA line
+
+##load libraries
+library(tm)
+library(ngram)
+
+#process the Text column (write a loop) - save processed text as a separate column
+for(i in 1:nrow(final_kav)) {
+
+  final_kav$edited[i] = preprocess(final_kav$Text[i], #one value at a time
+           case = "lower", 
+           remove.punct = TRUE,
+           remove.numbers = FALSE, 
+           fix.spacing = TRUE)
+
+##stem the words - do this second in the loop
+  final_kav$stemmed[i] = stemDocument(final_kav$edited[i], language = "english")
+}
+
+##stem GS text
+final_gs = read.csv("exp1_data/finaldata_gs.csv", stringsAsFactors = F)
+
+#process the Text column (write a loop) - save processed text as a separate column
+for(i in 1:nrow(final_gs)) {
+
+  final_gs$edited[i] = preprocess(fina_gs$Text[i], #one value at a time
+           case = "lower", 
+           remove.punct = TRUE,
+           remove.numbers = FALSE, 
+           fix.spacing = TRUE)
+
+##stem the words - do this second in the loop
+  final_gs$stemmed[i] = stemDocument(final_gs$edited[i], language = "english")
+}
+
+```
+```{r stem_warriner_exp2, eval = T, echo = F}
+##open the Warriner data for later
+warriner = read.csv("exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
+
+for(i in 1:nrow(warriner)) {
+  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
+} 
+```
+
 ## Data analysis
@@
 
+```{r create_datasets_harm_kav, eval = T, echo = F}
+#read in the harm total words from the mtmm project
+harm_all_kav = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
+
+harm_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_kav)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(harm_all_kav$words[harm_all_kav$words != "" & harm_all_kav$words != "NA" & !is.na(harm_all_kav$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_kav$Url[i]
+temp2$Source = final_kav$Source[i]
+temp2$wordcount = final_kav$wordcount[i]
+
+#bind with original
+harm_final_data_kav = rbind(harm_final_data_kav, temp2)
+}
+
+#pull in the data from Warriner 
+harm_final_data_kav$valence = vlookup(harm_final_data_kav$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(harm_final_data_kav$Var1[is.na(harm_final_data_kav$valence) & harm_final_data_kav$Freq > 0])
+#fought, safer, spurn
+harm_final_data_kav$valence[harm_final_data_kav$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
+harm_final_data_kav$valence[harm_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
+#no spurn avaliable
+```
+
+```{r create_datasets_fair_kav, include=FALSE}
+fair_all_kav = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
+
+fair_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_kav)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(fair_all_kav$words[fair_all_kav$words != "" & fair_all_kav$words != "NA" & !is.na(fair_all_kav$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_kav$Url[i]
+temp2$Source = final_kav$Source[i]
+temp2$wordcount = final_kav$wordcount[i]
+
+#bind with original
+fair_final_data_kav = rbind(fair_final_data_kav, temp2)
+}
+
+fair_final_data_kav$valence = vlookup(fair_final_data_kav$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(fair_final_data_kav$Var1[is.na(fair_final_data_kav$valence) & fair_final_data_kav$Freq > 0])
+#just plagiar safer
+fair_final_data_kav$valence[fair_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
+#nothing for just or plagiarism
+```
+
+```{r create_datasets_ingroup_kav, include=FALSE}
+ingroup_all_kav = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+
+ingroup_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_kav)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(ingroup_all_kav$words[ingroup_all_kav$words != "" & ingroup_all_kav$words != "NA" & !is.na(ingroup_all_kav$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_kav$Url[i]
+temp2$Source = final_kav$Source[i]
+temp2$wordcount = final_kav$wordcount[i]
+
+#bind with original
+ingroup_final_data_kav = rbind(ingroup_final_data_kav, temp2)
+}
+
+ingroup_final_data_kav$valence = vlookup(ingroup_final_data_kav$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(ingroup_final_data_kav$Var1[is.na(ingroup_final_data_kav$valence) & ingroup_final_data_kav$Freq > 0])
+#backstabb  benedict      best      fals   indvidu      juda    knight      true
+ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
+ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
+ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
+```
+
+```{r create_datasets_authority_kav, include=FALSE}
+authority_all_kav = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
+
+authority_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_kav)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(authority_all_kav$words[authority_all_kav$words != "" & authority_all_kav$words != "NA" & !is.na(authority_all_kav$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_kav$Url[i]
+temp2$Source = final_kav$Source[i]
+temp2$wordcount = final_kav$wordcount[i]
+
+#bind with original
+authority_final_data_kav = rbind(authority_final_data_kav, temp2)
+}
+
+authority_final_data_kav$valence = vlookup(authority_final_data_kav$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(authority_final_data_kav$Var1[is.na(authority_final_data_kav$valence) & authority_final_data_kav$Freq > 0])
+#  abov behind   gase higher  older  taken 
+authority_final_data_kav$valence[authority_final_data_kav$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
+authority_final_data_kav$valence[authority_final_data_kav$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
+authority_final_data_kav$valence[authority_final_data_kav$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
+authority_final_data_kav$valence[authority_final_data_kav$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
+```
+
+```{r create_datasets_purity_kav, include=FALSE}
+purity_all_kav = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
+
+purity_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_kav)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(purity_all_kav$words[purity_all_kav$words != "" & purity_all_kav$words != "NA" & !is.na(purity_all_kav$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_kav$Url[i]
+temp2$Source = final_kav$Source[i]
+temp2$wordcount = final_kav$wordcount[i]
+
+#bind with original
+purity_final_data_kav = rbind(purity_final_data_kav, temp2)
+}
+
+purity_final_data_kav$valence = vlookup(purity_final_data_kav$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(purity_final_data_kav$Var1[is.na(purity_final_data_kav$valence) & purity_final_data_kav$Freq > 0])
+#befor christian     jesus      mari      none    sacred    someon      true     women 
+purity_final_data_kav$valence[purity_final_data_kav$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
+purity_final_data_kav$valence[purity_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
+purity_final_data_kav$valence[purity_final_data_kav$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
+```
+
+```{r create_datasets_harm_gs, eval = T, echo = F}
+#read in the harm total words from the mtmm project
+harm_all_gs = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
+
+harm_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_gs)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(harm_all_gs$words[harm_all_gs$words != "" & harm_all_gs$words != "NA" & !is.na(harm_all_gs$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_gs$Url[i]
+temp2$Source = final_gs$Source[i]
+temp2$wordcount = final_gs$wordcount[i]
+
+#bind with original
+harm_final_data_gs = rbind(harm_final_data_gs, temp2)
+}
+
+#pull in the data from Warriner 
+harm_final_data_gs$valence = vlookup(harm_final_data_gs$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(harm_final_data_gs$Var1[is.na(harm_final_data_gs$valence) & harm_final_data_gs$Freq > 0])
+#fought, safer, spurn
+harm_final_data_gs$valence[harm_final_data_gs$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
+harm_final_data_gs$valence[harm_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
+#no spurn avaliable
+```
+
+```{r create_datasets_fair_gs, include=FALSE}
+fair_all_gs = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
+
+fair_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_gs)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(fair_all_gs$words[fair_all_gs$words != "" & fair_all_gs$words != "NA" & !is.na(fair_all_gs$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_gs$Url[i]
+temp2$Source = final_gs$Source[i]
+temp2$wordcount = final_gs$wordcount[i]
+
+#bind with original
+fair_final_data_gs = rbind(fair_final_data_gs, temp2)
+}
+
+fair_final_data_gs$valence = vlookup(fair_final_data_gs$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(fair_final_data_gs$Var1[is.na(fair_final_data_gs$valence) & fair_final_data_gs$Freq > 0])
+#just plagiar safer
+fair_final_data_gs$valence[fair_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
+#nothing for just or plagiarism
+```
+
+```{r create_datasets_ingroup_gs, include=FALSE}
+ingroup_all_gs = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+
+ingroup_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_gs)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(ingroup_all_gs$words[ingroup_all_gs$words != "" & ingroup_all_gs$words != "NA" & !is.na(ingroup_all_gs$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_gs$Url[i]
+temp2$Source = final_gs$Source[i]
+temp2$wordcount = final_gs$wordcount[i]
+
+#bind with original
+ingroup_final_data_gs = rbind(ingroup_final_data_gs, temp2)
+}
+
+ingroup_final_data_gs$valence = vlookup(ingroup_final_data_gs$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(ingroup_final_data_gs$Var1[is.na(ingroup_final_data_gs$valence) & ingroup_final_data_gs$Freq > 0])
+#backstabb  benedict      best      fals   indvidu      juda    knight      true
+ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
+ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
+ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
+```
+
+```{r create_datasets_authority_gs, include=FALSE}
+authority_all_gs = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
+
+authority_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_gs)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(authority_all_gs$words[authority_all_gs$words != "" & authority_all_gs$words != "NA" & !is.na(authority_all_gs$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_gs$Url[i]
+temp2$Source = final_gs$Source[i]
+temp2$wordcount = final_gs$wordcount[i]
+
+#bind with original
+authority_final_data_gs = rbind(authority_final_data_gs, temp2)
+}
+
+authority_final_data_gs$valence = vlookup(authority_final_data_gs$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(authority_final_data_gs$Var1[is.na(authority_final_data_gs$valence) & authority_final_data_gs$Freq > 0])
+#  abov behind   gase higher  older  taken 
+authority_final_data_gs$valence[authority_final_data_gs$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
+authority_final_data_gs$valence[authority_final_data_gs$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
+authority_final_data_gs$valence[authority_final_data_gs$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
+authority_final_data_gs$valence[authority_final_data_gs$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
+```
+
+```{r create_datasets_purity_gs, include=FALSE}
+purity_all_gs = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
+
+purity_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
+
+for (i in 1:nrow(final_gs)) {
+##first make a table of a response, unlisting everything
+temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
+
+#only pull the words in the dataset for each foundation
+temp2 = temp[temp$Var1 %in% unique(purity_all_gs$words[purity_all_gs$words != "" & purity_all_gs$words != "NA" & !is.na(purity_all_gs$words)]), ]
+
+#control here for times when no words
+if (nrow(temp2) == 0){
+  temp2 = data.frame("Var1" = 0, "Freq" = 0)
+}
+
+#add to the dataset
+temp2$URL = final_gs$Url[i]
+temp2$Source = final_gs$Source[i]
+temp2$wordcount = final_gs$wordcount[i]
+
+#bind with original
+purity_final_data_gs = rbind(purity_final_data_gs, temp2)
+}
+
+purity_final_data_gs$valence = vlookup(purity_final_data_gs$Var1, #index in original data
+                                  warriner, #where's the stuff you want to put in
+                                  "V.Mean.Sum", #what column is the stuff you want
+                                  "Word2") #what's the matching index
+
+#figure out stupid words
+table(purity_final_data_gs$Var1[is.na(purity_final_data_gs$valence) & purity_final_data_gs$Freq > 0])
+#befor christian     jesus      mari      none    sacred    someon      true     women 
+purity_final_data_gs$valence[purity_final_data_gs$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
+purity_final_data_gs$valence[purity_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
+purity_final_data_gs$valence[purity_final_data_gs$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
+```
+
+```{r descriptives_both, include = FALSE}
+##summarize the dataset so that you have the total and percent for each foundation
+#kav
+summary(harm_final_data_kav)
+summary(fair_final_data_kav)
+summary(ingroup_final_data_kav)
+summary(authority_final_data_kav)
+summary(purity_final_data_kav)
+#gs
+summary(harm_final_data_gs)
+summary(fair_final_data_gs)
+summary(ingroup_final_data_gs)
+summary(authority_final_data_gs)
+summary(purity_final_data_gs)
+##report descriptive statistics of the foundations
+#kav
+mean(harm_final_data_kav$valence)
+sd(harm_final_data_kav$valence)
+mean(fair_final_data_kav$valence)
+sd(fair_final_data_kav$valence)
+mean(ingroup_final_data_kav$valence)
+sd(ingroup_final_data_kav$valence)
+mean(authority_final_data_kav$valence)
+sd(authority_final_data_kav$valence)
+mean(purity_final_data_kav$valence)
+sd(purity_final_data_kav$valence)
+#gs
+mean(harm_final_data_gs$valence)
+sd(harm_final_data_gs$valence)
+mean(fair_final_data_gs$valence)
+sd(fair_final_data_gs$valence)
+mean(ingroup_final_data_gs$valence)
+sd(ingroup_final_data_gs$valence)
+mean(authority_final_data_gs$valence)
+sd(authority_final_data_gs$valence)
+mean(purity_final_data_gs$valence)
+sd(purity_final_data_gs$valence)
+#note that a big problem is the valence of the words 
+```
+
+```{r analysis_harm_kav, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+harm_final_data_kav$weight = harm_final_data_kav$Freq * harm_final_data_kav$valence / harm_final_data_kav$wordcount * 100
+
+#flatten down to sum by article 
+harm_final_temp_kav = aggregate(harm_final_data_kav$weight, 
+          by = list(harm_final_data_kav$URL),
+          FUN = sum, na.rm = T)
+colnames(harm_final_temp_kav) = c("URL", "MFDweight")
+
+harm_final_temp_kav$lean[grepl("nytimes.com", harm_final_temp_kav$URL) |
+                       grepl("npr.org", harm_final_temp_kav$URL) |
+                        grepl("slate.com", harm_final_temp_kav$URL) |
+                        grepl("huffingtonpost.com", harm_final_temp_kav$URL) |
+                        grepl("politico.com", harm_final_temp_kav$URL)] = "Liberal"
+
+harm_final_temp_kav$lean[grepl("breitbart.com", harm_final_temp_kav$URL) |
+                       grepl("foxnews.com", harm_final_temp_kav$URL) |
+                       grepl("rushlimbaugh.com", harm_final_temp_kav$URL) |
+                       grepl("theblaze.com", harm_final_temp_kav$URL) |
+                       grepl("hannity.com", harm_final_temp_kav$URL)] = "Conservative"
+
+harm_final_temp_kav$Source[grepl("nytimes.com", harm_final_temp_kav$URL)] = "NY Times"
+harm_final_temp_kav$Source[grepl("npr.org", harm_final_temp_kav$URL)] = "NPR"
+harm_final_temp_kav$Source[grepl("slate.com", harm_final_temp_kav$URL)] = "Slate"
+harm_final_temp_kav$Source[grepl("huffingtonpost.com", harm_final_temp_kav$URL)] = "Huffington Post"
+harm_final_temp_kav$Source[grepl("politico.com", harm_final_temp_kav$URL)] = "Politico"
+harm_final_temp_kav$Source[grepl("foxnews.com", harm_final_temp_kav$URL)] = "Fox"
+harm_final_temp_kav$Source[grepl("breitbart.com", harm_final_temp_kav$URL)] = "Breitbart"
+harm_final_temp_kav$Source[grepl("rushlimbaugh.com", harm_final_temp_kav$URL)] = "Rush Limbaugh"
+harm_final_temp_kav$Source[grepl("theblaze.com", harm_final_temp_kav$URL)] = "The Blaze"
+harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
+harm_model_kav = lme(MFDweight ~ lean, 
+                 data = harm_final_temp_kav, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(harm_model_kav)
+```
+
+```{r analysis_fair_kav, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+fair_final_data_kav$weight = fair_final_data_kav$Freq * fair_final_data_kav$valence / fair_final_data_kav$wordcount * 100
+
+#flatten down to sum by article 
+fair_final_temp_kav = aggregate(fair_final_data_kav$weight, 
+          by = list(fair_final_data_kav$URL),
+          FUN = sum, na.rm = T)
+colnames(fair_final_temp_kav) = c("URL", "MFDweight")
+
+fair_final_temp_kav$lean[grepl("nytimes.com", fair_final_temp_kav$URL) |
+                       grepl("npr.org", fair_final_temp_kav$URL) |
+                        grepl("slate.com", fair_final_temp_kav$URL) |
+                        grepl("huffingtonpost.com", fair_final_temp_kav$URL) |
+                        grepl("politico.com", fair_final_temp_kav$URL)] = "Liberal"
+
+fair_final_temp_kav$lean[grepl("breitbart.com", fair_final_temp_kav$URL) |
+                       grepl("foxnews.com", fair_final_temp_kav$URL) |
+                       grepl("rushlimbaugh.com", fair_final_temp_kav$URL) |
+                       grepl("theblaze.com", fair_final_temp_kav$URL) |
+                       grepl("hannity.com", fair_final_temp_kav$URL)] = "Conservative"
+
+fair_final_temp_kav$Source[grepl("nytimes.com", fair_final_temp_kav$URL)] = "NY Times"
+fair_final_temp_kav$Source[grepl("npr.org", fair_final_temp_kav$URL)] = "NPR"
+fair_final_temp_kav$Source[grepl("slate.com", fair_final_temp_kav$URL)] = "Slate"
+fair_final_temp_kav$Source[grepl("huffingtonpost.com", fair_final_temp_kav$URL)] = "Huffington Post"
+fair_final_temp_kav$Source[grepl("politico.com", fair_final_temp_kav$URL)] = "Politico"
+fair_final_temp_kav$Source[grepl("foxnews.com", fair_final_temp_kav$URL)] = "Fox"
+fair_final_temp_kav$Source[grepl("breitbart.com", fair_final_temp_kav$URL)] = "Breitbart"
+fair_final_temp_kav$Source[grepl("rushlimbaugh.com", fair_final_temp_kav$URL)] = "Rush Limbaugh"
+fair_final_temp_kav$Source[grepl("theblaze.com", fair_final_temp_kav$URL)] = "The Blaze"
+fair_final_temp_kav$Source[grepl("hannity.com", fair_final_temp_kav$URL)] = "Sean Hannity"
+fair_model_kav = lme(MFDweight ~ lean, 
+                 data = fair_final_temp_kav, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(fair_model_kav)
+```
+
+```{r analysis_ingroup_kav, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+ingroup_final_data_kav$weight = ingroup_final_data_kav$Freq * ingroup_final_data_kav$valence / ingroup_final_data_kav$wordcount * 100
+
+#flatten down to sum by article 
+ingroup_final_temp_kav = aggregate(ingroup_final_data_kav$weight, 
+          by = list(ingroup_final_data_kav$URL),
+          FUN = sum, na.rm = T)
+colnames(ingroup_final_temp_kav) = c("URL", "MFDweight")
+
+ingroup_final_temp_kav$lean[grepl("nytimes.com", ingroup_final_temp_kav$URL) |
+                       grepl("npr.org", ingroup_final_temp_kav$URL) |
+                        grepl("slate.com", ingroup_final_temp_kav$URL) |
+                        grepl("huffingtonpost.com", ingroup_final_temp_kav$URL) |
+                        grepl("politico.com", ingroup_final_temp_kav$URL)] = "Liberal"
+
+ingroup_final_temp_kav$lean[grepl("breitbart.com", ingroup_final_temp_kav$URL) |
+                       grepl("foxnews.com", ingroup_final_temp_kav$URL) |
+                       grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL) |
+                       grepl("theblaze.com", ingroup_final_temp_kav$URL) |
+                       grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Conservative"
+
+ingroup_final_temp_kav$Source[grepl("nytimes.com", ingroup_final_temp_kav$URL)] = "NY Times"
+ingroup_final_temp_kav$Source[grepl("npr.org", ingroup_final_temp_kav$URL)] = "NPR"
+ingroup_final_temp_kav$Source[grepl("slate.com", ingroup_final_temp_kav$URL)] = "Slate"
+ingroup_final_temp_kav$Source[grepl("huffingtonpost.com", ingroup_final_temp_kav$URL)] = "Huffington Post"
+ingroup_final_temp_kav$Source[grepl("politico.com", ingroup_final_temp_kav$URL)] = "Politico"
+ingroup_final_temp_kav$Source[grepl("foxnews.com", ingroup_final_temp_kav$URL)] = "Fox"
+ingroup_final_temp_kav$Source[grepl("breitbart.com", ingroup_final_temp_kav$URL)] = "Breitbart"
+ingroup_final_temp_kav$Source[grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL)] = "Rush Limbaugh"
+ingroup_final_temp_kav$Source[grepl("theblaze.com", ingroup_final_temp_kav$URL)] = "The Blaze"
+ingroup_final_temp_kav$Source[grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Sean Hannity"
+ingroup_model_kav = lme(MFDweight ~ lean, 
+                 data = ingroup_final_temp_kav, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(ingroup_model_kav)
+```
+
+```{r analysis_authority_kav, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+authority_final_data_kav$weight = authority_final_data_kav$Freq * authority_final_data_kav$valence / authority_final_data_kav$wordcount * 100
+
+#flatten down to sum by article 
+authority_final_temp_kav = aggregate(authority_final_data_kav$weight, 
+          by = list(authority_final_data_kav$URL),
+          FUN = sum, na.rm = T)
+colnames(authority_final_temp_kav) = c("URL", "MFDweight")
+
+authority_final_temp_kav$lean[grepl("nytimes.com", authority_final_temp_kav$URL) |
+                       grepl("npr.org", authority_final_temp_kav$URL) |
+                        grepl("slate.com", authority_final_temp_kav$URL) |
+                        grepl("huffingtonpost.com", authority_final_temp_kav$URL) |
+                        grepl("politico.com", authority_final_temp_kav$URL)] = "Liberal"
+
+authority_final_temp_kav$lean[grepl("breitbart.com", authority_final_temp_kav$URL) |
+                       grepl("foxnews.com", authority_final_temp_kav$URL) |
+                       grepl("rushlimbaugh.com", authority_final_temp_kav$URL) |
+                       grepl("theblaze.com", authority_final_temp_kav$URL) |
+                       grepl("hannity.com", authority_final_temp_kav$URL)] = "Conservative"
+
+authority_final_temp_kav$Source[grepl("nytimes.com", authority_final_temp_kav$URL)] = "NY Times"
+authority_final_temp_kav$Source[grepl("npr.org", authority_final_temp_kav$URL)] = "NPR"
+authority_final_temp_kav$Source[grepl("slate.com", authority_final_temp_kav$URL)] = "Slate"
+authority_final_temp_kav$Source[grepl("huffingtonpost.com", authority_final_temp_kav$URL)] = "Huffington Post"
+authority_final_temp_kav$Source[grepl("politico.com", authority_final_temp_kav$URL)] = "Politico"
+authority_final_temp_kav$Source[grepl("foxnews.com", authority_final_temp_kav$URL)] = "Fox"
+authority_final_temp_kav$Source[grepl("breitbart.com", authority_final_temp_kav$URL)] = "Breitbart"
+authority_final_temp_kav$Source[grepl("rushlimbaugh.com", authority_final_temp_kav$URL)] = "Rush Limbaugh"
+authority_final_temp_kav$Source[grepl("theblaze.com", authority_final_temp_kav$URL)] = "The Blaze"
+authority_final_temp_kav$Source[grepl("hannity.com", authority_final_temp_kav$URL)] = "Sean Hannity"
+authority_model_kav = lme(MFDweight ~ lean, 
+                 data = authority_final_temp_kav, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(authority_model_kav)
+```
+
+```{r analysis_purity_kav, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+purity_final_data_kav$weight = purity_final_data_kav$Freq * purity_final_data_kav$valence / purity_final_data_kav$wordcount * 100
+
+#flatten down to sum by article 
+purity_final_temp_kav = aggregate(purity_final_data_kav$weight, 
+          by = list(purity_final_data_kav$URL),
+          FUN = sum, na.rm = T)
+colnames(purity_final_temp_kav) = c("URL", "MFDweight")
+
+purity_final_temp_kav$lean[grepl("nytimes.com", purity_final_temp_kav$URL) |
+                       grepl("npr.org", purity_final_temp_kav$URL) |
+                        grepl("slate.com", purity_final_temp_kav$URL) |
+                        grepl("huffingtonpost.com", purity_final_temp_kav$URL) |
+                        grepl("politico.com", purity_final_temp_kav$URL)] = "Liberal"
+
+purity_final_temp_kav$lean[grepl("breitbart.com", purity_final_temp_kav$URL) |
+                       grepl("foxnews.com", purity_final_temp_kav$URL) |
+                       grepl("rushlimbaugh.com", purity_final_temp_kav$URL) |
+                       grepl("theblaze.com", purity_final_temp_kav$URL) |
+                       grepl("hannity.com", purity_final_temp_kav$URL)] = "Conservative"
+
+purity_final_temp_kav$Source[grepl("nytimes.com", purity_final_temp_kav$URL)] = "NY Times"
+purity_final_temp_kav$Source[grepl("npr.org", purity_final_temp_kav$URL)] = "NPR"
+purity_final_temp_kav$Source[grepl("slate.com", purity_final_temp_kav$URL)] = "Slate"
+purity_final_temp_kav$Source[grepl("huffingtonpost.com", purity_final_temp_kav$URL)] = "Huffington Post"
+purity_final_temp_kav$Source[grepl("politico.com", purity_final_temp_kav$URL)] = "Politico"
+purity_final_temp_kav$Source[grepl("foxnews.com", purity_final_temp_kav$URL)] = "Fox"
+purity_final_temp_kav$Source[grepl("breitbart.com", purity_final_temp_kav$URL)] = "Breitbart"
+purity_final_temp_kav$Source[grepl("rushlimbaugh.com", purity_final_temp_kav$URL)] = "Rush Limbaugh"
+purity_final_temp_kav$Source[grepl("theblaze.com", purity_final_temp_kav$URL)] = "The Blaze"
+purity_final_temp_kav$Source[grepl("hannity.com", purity_final_temp_kav$URL)] = "Sean Hannity"
+purity_model_kav = lme(MFDweight ~ lean, 
+                 data = purity_final_temp_kav, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(purity_model_kav)
+```
+
+```{r analysis_harm_gs, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+harm_final_data_gs$weight = harm_final_data_gs$Freq * harm_final_data_gs$valence / harm_final_data_gs$wordcount * 100
+
+#flatten down to sum by article 
+harm_final_temp_gs = aggregate(harm_final_data_gs$weight, 
+          by = list(harm_final_data_gs$URL),
+          FUN = sum, na.rm = T)
+colnames(harm_final_temp_gs) = c("URL", "MFDweight")
+
+harm_final_temp_gs$lean[grepl("nytimes.com", harm_final_temp_gs$URL) |
+                       grepl("npr.org", harm_final_temp_gs$URL) |
+                        grepl("slate.com", harm_final_temp_gs$URL) |
+                        grepl("huffingtonpost.com", harm_final_temp_gs$URL) |
+                        grepl("politico.com", harm_final_temp_gs$URL)] = "Liberal"
+
+harm_final_temp_gs$lean[grepl("breitbart.com", harm_final_temp_gs$URL) |
+                       grepl("foxnews.com", harm_final_temp_gs$URL) |
+                       grepl("rushlimbaugh.com", harm_final_temp_gs$URL) |
+                       grepl("theblaze.com", harm_final_temp_gs$URL) |
+                       grepl("hannity.com", harm_final_temp_gs$URL)] = "Conservative"
+
+harm_final_temp_gs$Source[grepl("nytimes.com", harm_final_temp_gs$URL)] = "NY Times"
+harm_final_temp_gs$Source[grepl("npr.org", harm_final_temp_gs$URL)] = "NPR"
+harm_final_temp_gs$Source[grepl("slate.com", harm_final_temp_gs$URL)] = "Slate"
+harm_final_temp_gs$Source[grepl("huffingtonpost.com", harm_final_temp_gs$URL)] = "Huffington Post"
+harm_final_temp_gs$Source[grepl("politico.com", harm_final_temp_gs$URL)] = "Politico"
+harm_final_temp_gs$Source[grepl("foxnews.com", harm_final_temp_gs$URL)] = "Fox"
+harm_final_temp_gs$Source[grepl("breitbart.com", harm_final_temp_gs$URL)] = "Breitbart"
+harm_final_temp_gs$Source[grepl("rushlimbaugh.com", harm_final_temp_gs$URL)] = "Rush Limbaugh"
+harm_final_temp_gs$Source[grepl("theblaze.com", harm_final_temp_gs$URL)] = "The Blaze"
+harm_final_temp_gs$Source[grepl("hannity.com", harm_final_temp_gs$URL)] = "Sean Hannity"
+harm_model_gs = lme(MFDweight ~ lean, 
+                 data = harm_final_temp_gs, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(harm_model_gs)
+```
+
+```{r analysis_fair_gs, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+fair_final_data_gs$weight = fair_final_data_gs$Freq * fair_final_data_gs$valence / fair_final_data_gs$wordcount * 100
+
+#flatten down to sum by article 
+fair_final_temp_gs = aggregate(fair_final_data_gs$weight, 
+          by = list(fair_final_data_gs$URL),
+          FUN = sum, na.rm = T)
+colnames(fair_final_temp_gs) = c("URL", "MFDweight")
+
+fair_final_temp_gs$lean[grepl("nytimes.com", fair_final_temp_gs$URL) |
+                       grepl("npr.org", fair_final_temp_gs$URL) |
+                        grepl("slate.com", fair_final_temp_gs$URL) |
+                        grepl("huffingtonpost.com", fair_final_temp_gs$URL) |
+                        grepl("politico.com", fair_final_temp_gs$URL)] = "Liberal"
+
+fair_final_temp_gs$lean[grepl("breitbart.com", fair_final_temp_gs$URL) |
+                       grepl("foxnews.com", fair_final_temp_gs$URL) |
+                       grepl("rushlimbaugh.com", fair_final_temp_gs$URL) |
+                       grepl("theblaze.com", fair_final_temp_gs$URL) |
+                       grepl("hannity.com", fair_final_temp_gs$URL)] = "Conservative"
+
+fair_final_temp_gs$Source[grepl("nytimes.com", fair_final_temp_gs$URL)] = "NY Times"
+fair_final_temp_gs$Source[grepl("npr.org", fair_final_temp_gs$URL)] = "NPR"
+fair_final_temp_gs$Source[grepl("slate.com", fair_final_temp_gs$URL)] = "Slate"
+fair_final_temp_gs$Source[grepl("huffingtonpost.com", fair_final_temp_gs$URL)] = "Huffington Post"
+fair_final_temp_gs$Source[grepl("politico.com", fair_final_temp_gs$URL)] = "Politico"
+fair_final_temp_gs$Source[grepl("foxnews.com", fair_final_temp_gs$URL)] = "Fox"
+fair_final_temp_gs$Source[grepl("breitbart.com", fair_final_temp_gs$URL)] = "Breitbart"
+fair_final_temp_gs$Source[grepl("rushlimbaugh.com", fair_final_temp_gs$URL)] = "Rush Limbaugh"
+fair_final_temp_gs$Source[grepl("theblaze.com", fair_final_temp_gs$URL)] = "The Blaze"
+fair_final_temp_gs$Source[grepl("hannity.com", fair_final_temp_gs$URL)] = "Sean Hannity"
+fair_model_gs = lme(MFDweight ~ lean, 
+                 data = fair_final_temp_gs, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(fair_model_gs)
+```
+
+```{r analysis_ingroup_gs, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+ingroup_final_data_gs$weight = ingroup_final_data_gs$Freq * ingroup_final_data_gs$valence / ingroup_final_data_gs$wordcount * 100
+
+#flatten down to sum by article 
+ingroup_final_temp_gs = aggregate(ingroup_final_data_gs$weight, 
+          by = list(ingroup_final_data_gs$URL),
+          FUN = sum, na.rm = T)
+colnames(ingroup_final_temp_gs) = c("URL", "MFDweight")
+
+ingroup_final_temp_gs$lean[grepl("nytimes.com", ingroup_final_temp_gs$URL) |
+                       grepl("npr.org", ingroup_final_temp_gs$URL) |
+                        grepl("slate.com", ingroup_final_temp_gs$URL) |
+                        grepl("huffingtonpost.com", ingroup_final_temp_gs$URL) |
+                        grepl("politico.com", ingroup_final_temp_gs$URL)] = "Liberal"
+
+ingroup_final_temp_gs$lean[grepl("breitbart.com", ingroup_final_temp_gs$URL) |
+                       grepl("foxnews.com", ingroup_final_temp_gs$URL) |
+                       grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL) |
+                       grepl("theblaze.com", ingroup_final_temp_gs$URL) |
+                       grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Conservative"
+
+ingroup_final_temp_gs$Source[grepl("nytimes.com", ingroup_final_temp_gs$URL)] = "NY Times"
+ingroup_final_temp_gs$Source[grepl("npr.org", ingroup_final_temp_gs$URL)] = "NPR"
+ingroup_final_temp_gs$Source[grepl("slate.com", ingroup_final_temp_gs$URL)] = "Slate"
+ingroup_final_temp_gs$Source[grepl("huffingtonpost.com", ingroup_final_temp_gs$URL)] = "Huffington Post"
+ingroup_final_temp_gs$Source[grepl("politico.com", ingroup_final_temp_gs$URL)] = "Politico"
+ingroup_final_temp_gs$Source[grepl("foxnews.com", ingroup_final_temp_gs$URL)] = "Fox"
+ingroup_final_temp_gs$Source[grepl("breitbart.com", ingroup_final_temp_gs$URL)] = "Breitbart"
+ingroup_final_temp_gs$Source[grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL)] = "Rush Limbaugh"
+ingroup_final_temp_gs$Source[grepl("theblaze.com", ingroup_final_temp_gs$URL)] = "The Blaze"
+ingroup_final_temp_gs$Source[grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Sean Hannity"
+ingroup_model_gs = lme(MFDweight ~ lean, 
+                 data = ingroup_final_temp_gs, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(ingroup_model_gs)
+```
+
+```{r analysis_authority_gs, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+authority_final_data_gs$weight = authority_final_data_gs$Freq * authority_final_data_gs$valence / authority_final_data_gs$wordcount * 100
+
+#flatten down to sum by article 
+authority_final_temp_gs = aggregate(authority_final_data_gs$weight, 
+          by = list(authority_final_data_gs$URL),
+          FUN = sum, na.rm = T)
+colnames(authority_final_temp_gs) = c("URL", "MFDweight")
+
+authority_final_temp_gs$lean[grepl("nytimes.com", authority_final_temp_gs$URL) |
+                       grepl("npr.org", authority_final_temp_gs$URL) |
+                        grepl("slate.com", authority_final_temp_gs$URL) |
+                        grepl("huffingtonpost.com", authority_final_temp_gs$URL) |
+                        grepl("politico.com", authority_final_temp_gs$URL)] = "Liberal"
+
+authority_final_temp_gs$lean[grepl("breitbart.com", authority_final_temp_gs$URL) |
+                       grepl("foxnews.com", authority_final_temp_gs$URL) |
+                       grepl("rushlimbaugh.com", authority_final_temp_gs$URL) |
+                       grepl("theblaze.com", authority_final_temp_gs$URL) |
+                       grepl("hannity.com", authority_final_temp_gs$URL)] = "Conservative"
+
+authority_final_temp_gs$Source[grepl("nytimes.com", authority_final_temp_gs$URL)] = "NY Times"
+authority_final_temp_gs$Source[grepl("npr.org", authority_final_temp_gs$URL)] = "NPR"
+authority_final_temp_gs$Source[grepl("slate.com", authority_final_temp_gs$URL)] = "Slate"
+authority_final_temp_gs$Source[grepl("huffingtonpost.com", authority_final_temp_gs$URL)] = "Huffington Post"
+authority_final_temp_gs$Source[grepl("politico.com", authority_final_temp_gs$URL)] = "Politico"
+authority_final_temp_gs$Source[grepl("foxnews.com", authority_final_temp_gs$URL)] = "Fox"
+authority_final_temp_gs$Source[grepl("breitbart.com", authority_final_temp_gs$URL)] = "Breitbart"
+authority_final_temp_gs$Source[grepl("rushlimbaugh.com", authority_final_temp_gs$URL)] = "Rush Limbaugh"
+authority_final_temp_gs$Source[grepl("theblaze.com", authority_final_temp_gs$URL)] = "The Blaze"
+authority_final_temp_gs$Source[grepl("hannity.com", authority_final_temp_gs$URL)] = "Sean Hannity"
+authority_model_gs = lme(MFDweight ~ lean, 
+                 data = authority_final_temp_gs, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(authority_model_gs)
+```
+
+```{r analysis_purity_gs, include = FALSE}
+#final_data clean up
+#multiply by frequency and create percentage
+purity_final_data_gs$weight = purity_final_data_gs$Freq * purity_final_data_gs$valence / purity_final_data_gs$wordcount * 100
+
+#flatten down to sum by article 
+purity_final_temp_gs = aggregate(purity_final_data_gs$weight, 
+          by = list(purity_final_data_gs$URL),
+          FUN = sum, na.rm = T)
+colnames(purity_final_temp_gs) = c("URL", "MFDweight")
+
+purity_final_temp_gs$lean[grepl("nytimes.com", purity_final_temp_gs$URL) |
+                       grepl("npr.org", purity_final_temp_gs$URL) |
+                        grepl("slate.com", purity_final_temp_gs$URL) |
+                        grepl("huffingtonpost.com", purity_final_temp_gs$URL) |
+                        grepl("politico.com", purity_final_temp_gs$URL)] = "Liberal"
+
+purity_final_temp_gs$lean[grepl("breitbart.com", purity_final_temp_gs$URL) |
+                       grepl("foxnews.com", purity_final_temp_gs$URL) |
+                       grepl("rushlimbaugh.com", purity_final_temp_gs$URL) |
+                       grepl("theblaze.com", purity_final_temp_gs$URL) |
+                       grepl("hannity.com", purity_final_temp_gs$URL)] = "Conservative"
+
+purity_final_temp_gs$Source[grepl("nytimes.com", purity_final_temp_gs$URL)] = "NY Times"
+purity_final_temp_gs$Source[grepl("npr.org", purity_final_temp_gs$URL)] = "NPR"
+purity_final_temp_gs$Source[grepl("slate.com", purity_final_temp_gs$URL)] = "Slate"
+purity_final_temp_gs$Source[grepl("huffingtonpost.com", purity_final_temp_gs$URL)] = "Huffington Post"
+purity_final_temp_gs$Source[grepl("politico.com", purity_final_temp_gs$URL)] = "Politico"
+purity_final_temp_gs$Source[grepl("foxnews.com", purity_final_temp_gs$URL)] = "Fox"
+purity_final_temp_gs$Source[grepl("breitbart.com", purity_final_temp_gs$URL)] = "Breitbart"
+purity_final_temp_gs$Source[grepl("rushlimbaugh.com", purity_final_temp_gs$URL)] = "Rush Limbaugh"
+purity_final_temp_gs$Source[grepl("theblaze.com", purity_final_temp_gs$URL)] = "The Blaze"
+purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
+purity_model_gs = lme(MFDweight ~ lean, 
+                 data = purity_final_temp_gs, 
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+summary(purity_model_gs)
+```
 # Experiment 2
@@
 ## Results
-
+```{r exp2 source descriptives_both, results = 'asis', echo = FALSE, message = F}
+#Kav
+final_kav$uniquewords = NA
+final_kav$valenceavg = NA
+
+for (i in 1:nrow(final_kav)){
+
+  #add unique
+  final_kav$uniquewords[i] = length(unique(unlist(strsplit(final_kav$stemmed[i], " "))))
+
+  #add valence
+  tempwords_kav = as.data.frame(unlist(strsplit(final_kav$stemmed[i], " ")))
+  colnames(tempwords_kav) = "theword"
+  tempwords_kav$tempval = vlookup(tempwords_kav$theword, #index in original data
+                    warriner, #where's the stuff you want to put in
+                    "V.Mean.Sum", #what column is the stuff you want
+                    "Word2") #what's the matching index
+
+  final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
+
+}
+
+tapply(final_kav$valenceavg, final_kav$Source, mean)
+tapply(final_kav$valenceavg, final_kav$Source, sd)
+tapply(final_kav$wordcount, final_kav$Source, mean)
+tapply(final_kav$wordcount, final_kav$Source, sd)
+tapply(final_kav$uniquewords, final_kav$Source, mean)
+tapply(final_kav$uniquewords, final_kav$Source, sd)
+tapply(final_kav$Source, final_kav$Source, length)
+tapply(final_kav$wordcount, final_kav$Source, sum)
+
+library(quanteda)
+
+final_kav$FK = NA
+
+for (i in 1:nrow(final_kav)){
+  final_kav$FK[i] = unlist(textstat_readability(final_kav$Text[i], 
+                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
+}
+
+tapply(final_kav$FK, final_kav$Source, mean)
+tapply(final_kav$FK, final_kav$Source, sd)
+
+#GS
+final_gs$uniquewords = NA
+final_gs$valenceavg = NA
+
+for (i in 1:nrow(final_gs)){
+
+  #add unique
+  final_gs$uniquewords[i] = length(unique(unlist(strsplit(final_gs$stemmed[i], " "))))
+
+  #add valence
+  tempwords_gs = as.data.frame(unlist(strsplit(final_gs$stemmed[i], " ")))
+  colnames(tempwords_gs) = "theword"
+  tempwords_gs$tempval = vlookup(tempwords_gs$theword, #index in original data
+                    warriner, #where's the stuff you want to put in
+                    "V.Mean.Sum", #what column is the stuff you want
+                    "Word2") #what's the matching index
+
+  final_gs$valenceavg[i] = mean(tempwords_gs$tempval, na.rm = T)
+
+}
+
+tapply(final_gs$valenceavg, final_gs$Source, mean)
+tapply(final_gs$valenceavg, final_gs$Source, sd)
+tapply(final_gs$wordcount, final_gs$Source, mean)
+tapply(final_gs$wordcount, final_gs$Source, sd)
+tapply(final_gs$uniquewords, final_gs$Source, mean)
+tapply(final_gs$uniquewords, final_gs$Source, sd)
+tapply(final_gs$Source, final_gs$Source, length)
+tapply(final_gs$wordcount, final_gs$Source, sum)
+
+library(quanteda)
+
+final_gs$FK = NA
+
+for (i in 1:nrow(final_gs)){
+  final_gs$FK[i] = unlist(textstat_readability(final_gs$Text[i], 
+                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
+}
+
+tapply(final_gs$FK, final_gs$Source, mean)
+tapply(final_gs$FK, final_gs$Source, sd)
+```
+
+```{r exp2-table_kav, results = 'asis', echo = F}
+#MFD, mean, sd, mean, sd, t, p, d
+tableprint_kav = matrix(NA, ncol = 8, nrow = 5)
+colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+
+#calculate d
+#harm
+harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
+#fair
+fair_d_kav = d.ind.t(m1 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
+#ingroup
+ingroup_d_kav = d.ind.t(m1 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
+#authority
+authority_d_kav = d.ind.t(m1 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
+#purity
+purity_d_kav = d.ind.t(m1 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
+#put in the numbers
+tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1, 
+                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
+                    harm_d_kav$d)
+tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1, 
+                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
+                    fair_d_kav$d)
+tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1, 
+                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
+                    ingroup_d_kav$d)
+tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1, 
+                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
+                    authority_d_kav$d)
+tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1, 
+                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
+                    purity_d_kav$d)
+
+tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]))
+tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
+
+apa_table(tableprint_kav,
+          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
+          caption = "Kavanaugh Results - Multilevel Model", 
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 7))
+          )
+```
+
+```{r exp2-table_gs, results = 'asis', echo = F}
+#MFD, mean, sd, mean, sd, t, p, d
+tableprint_gs = matrix(NA, ncol = 8, nrow = 5)
+colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+
+#calculate d
+#harm
+harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
+#fair
+fair_d_gs = d.ind.t(m1 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
+#ingroup
+ingroup_d_gs = d.ind.t(m1 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
+#authority
+authority_d_gs = d.ind.t(m1 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
+#purity
+purity_d_gs = d.ind.t(m1 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T), 
+                 m2 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
+#put in the numbers
+tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1, 
+                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
+                    harm_d_gs$d)
+tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1, 
+                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
+                    fair_d_gs$d)
+tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1, 
+                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
+                    ingroup_d_gs$d)
+tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1, 
+                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
+                    authority_d_gs$d)
+tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1, 
+                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
+                    purity_d_gs$d)
+
+tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]))
+tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
+
+apa_table(tableprint_gs,
+          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
+          caption = "Government Shutdown Results - Multilevel Model", 
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 7))
+          )
+```
+
+```{r conference-pic_kav, eval = F, include = F}
+library(ggplot2)
+library(reshape)
+
+cleanup = theme(panel.grid.major = element_blank(), 
+                panel.grid.minor = element_blank(), 
+                panel.background = element_blank(), 
+                axis.line.x = element_line(color = "black"),
+                axis.line.y = element_line(color = "black"),
+                legend.key = element_rect(fill = "white"),
+                text = element_text(size = 10))
+
+graphdata_kav = as.data.frame(tableprint_kav)
+graphlong_kav = melt(graphdata_kav[ , c(1,2,4)], 
+                 id = "Foundation")
+graphlong2_kav = melt(graphdata_kav[ , c(1, 3,5)],
+                  id = "Foundation",
+                  measured = c("SD_C", "SD_L"))
+graphlong_kav$sd = graphlong2_kav$value
+graphlong_kav$lower = as.numeric(as.character(graphlong_kav$value)) - 2*as.numeric(as.character(graphlong_kav$sd))
+graphlong_kav$upper = as.numeric(as.character(graphlong_kav$value)) + 2*as.numeric(as.character(graphlong_kav$sd))
+
+graphlong_kav$value = as.numeric(as.character(graphlong_kav$value))
+
+graph_data_kav = ggplot(graphlong_kav, aes(Foundation, value, color = variable)) + 
+  geom_point(position = position_dodge(width = 0.90)) +
+  geom_errorbar(aes(ymin = lower, ymax = upper), 
+                position = position_dodge(width = 0.90),
+                width = .2) + 
+  cleanup +
+  ylab("Mean Weighted Valence") + 
+  scale_color_manual(values = c("red", "blue"),
+                       labels = c("Conservative", "Liberal"),
+                       name = "Party") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
+  geom_hline(yintercept = 0, linetype = 1, color = "black")
+
+tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
+     height = 3, units = 'in', compression = "lzw")
+plot(graph_data_kav)
+dev.off()
+
+```
+
+```{r conference-pic_gs, eval = F, include = F}
+graphdata_gs = as.data.frame(tableprint_gs)
+graphlong_gs = melt(graphdata_gs[ , c(1,2,4)], 
+                 id = "Foundation")
+graphlong2_gs = melt(graphdata_gs[ , c(1, 3,5)],
+                  id = "Foundation",
+                  measured = c("SD_C", "SD_L"))
+graphlong_gs$sd = graphlong2_gs$value
+graphlong_gs$lower = as.numeric(as.character(graphlong_gs$value)) - 2*as.numeric(as.character(graphlong_gs$sd))
+graphlong_gs$upper = as.numeric(as.character(graphlong_gs$value)) + 2*as.numeric(as.character(graphlong_gs$sd))
+
+graphlong_gs$value = as.numeric(as.character(graphlong_gs$value))
+
+graph_data_gs = ggplot(graphlong_gs, aes(Foundation, value, color = variable)) + 
+  geom_point(position = position_dodge(width = 0.90)) +
+  geom_errorbar(aes(ymin = lower, ymax = upper), 
+                position = position_dodge(width = 0.90),
+                width = .2) + 
+  cleanup +
+  ylab("Mean Weighted Valence") + 
+  scale_color_manual(values = c("red", "blue"),
+                       labels = c("Conservative", "Liberal"),
+                       name = "Party") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
+  geom_hline(yintercept = 0, linetype = 1, color = "black")
+
+tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
+     height = 3, units = 'in', compression = "lzw")
+plot(graph_data_gs)
+dev.off()
+
+```
 # Discussion

### 2019-04-01 pilot_manuscript.Rmd
small changes to the draft

@@
 In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean.
-In contrast, Fox News and Breitbart are believed to have a conservative bias or lean.
+In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean.
 @Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
@@
 
-##U.S. Government Shutdown of 2018-2019
+## U.S. Government Shutdown of 2018-2019
 
@@
 The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019].
-The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border waLL.
+The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
 President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019].
@@
 dev.off()
-
 ```
@@
 dev.off()
-
-```
+=
+```
+
 # Discussion

### 2019-04-01 pilot_manuscript.Rmd
almost there i think

@@
 
-```{r exp1 source descriptives, results = 'asis', echo = FALSE, message = F}
+```{r exp1_source_descriptives, results = 'asis', echo = FALSE, message = F}
 
@@
 
+####build the table here####
+tableprint = matrix(NA, nrow=4, ncol=7)
+colnames(tableprint) = c("Sources", "Unique_Words", "stuff")
+
+tableprint[ , 1] = levels(final$Source)
+tableprint[ , 2] = tapply(final$uniquewords, final$Source, mean)
+
+#change this to match
+apa_table(as.data.frame(tableprint),
+          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
+          caption = "Experiment 1 Results - Multilevel Model", 
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 6))
+          )
+
 ```
@@
 table - columns are types (unique words), tokens (total words), readability statistics, number of articles, total number of words, valence
+
+talk about the table here
 
@@
 #read it in
-NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv")
-NPR_kav = read.csv("exp2_data/NPR_kav.csv")
-SLATE_kav = read.csv("exp2_data/SLATE_kav.csv")
-HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv")
-POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv")
-FOX_kav = read.csv("exp2_data/FOX_kav.csv")
-BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv")
-RUSH_kav = read.csv("exp2_data/RUSH_kav.csv")
-BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv")
-HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv")
+NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
 
 #merge it together
-overalldata_kav = rbind(NYtimes_kav, NPR_kav)
-overalldata_kav = rbind(overalldata_kav, SLATE_kav)
-overalldata_kav = rbind(overalldata_kav, HUFFPO_kav)
-overalldata_kav = rbind(overalldata_kav, POLITICO_kav)
-overalldata_kav = rbind(overalldata_kav, FOX_kav)
-overalldata_kav = rbind(overalldata_kav, BREITBART_kav)
-overalldata_kav = rbind(overalldata_kav, RUSH_kav)
-overalldata_kav = rbind(overalldata_kav, BLAZE_kav)
-overalldata_kav = rbind(overalldata_kav, HANNITY_kav)
-
-write.csv(overalldata_kav, "exp2_data/overalldata_kav.csv", row.names = F)
-
-##pull in the data
-master_kav = read.csv("exp2_data/overalldata_kav.csv", stringsAsFactors = F)
+master_kav = rbind(NYtimes_kav, NPR_kav, SLATE_kav, 
+                        HUFFPO_kav, POLITICO_kav, FOX_kav, 
+                        BREITBART_kav, RUSH_kav, BLAZE_kav, 
+                        HANNITY_kav)
 
@@
 
-##take out the disqus ones
-nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##figure out the duplicates
-nodis$URLS = duplicated(nodis$Url)
+##take out the disqus ones - there are none
+#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
 
 ##all data
-final_kav = subset(nodis, URLS == FALSE)
-
-tapply(final_kav$wordcount, final_kav$Source, mean)
-tapply(final_kav$wordcount, final_kav$Source, sum)
-
-write.csv(final_kav, "exp2_data/finaldata_kav.csv")
+final_kav = nozero
 ```
@@
 #read it in
-NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv")
-NPR_gs = read.csv("exp2_data/NPR_gs.csv")
-SLATE_gs = read.csv("exp2_data/SLATE_gs.csv")
-HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv")
-POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv")
-FOX_gs = read.csv("exp2_data/FOX_gs.csv")
-BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv")
-RUSH_gs = read.csv("exp2_data/RUSH_gs.csv")
-BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv")
-HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv")
+NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F)
+NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F)
+SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F)
+HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F)
+POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F)
+FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F)
+BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F)
+RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F)
+BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F)
+HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F)
 
 #merge it together
-overalldata_gs = rbind(NYtimes_gs, NPR_gs)
-overalldata_gs = rbind(overalldata_gs, SLATE_gs)
-overalldata_gs = rbind(overalldata_gs, HUFFPO_gs)
-overalldata_gs = rbind(overalldata_gs, POLITICO_gs)
-overalldata_gs = rbind(overalldata_gs, FOX_gs)
-overalldata_gs = rbind(overalldata_gs, BREITBART_gs)
-overalldata_gs = rbind(overalldata_gs, RUSH_gs)
-overalldata_gs = rbind(overalldata_gs, BLAZE_gs)
-overalldata_gs = rbind(overalldata_gs, HANNITY_gs)
-
-write.csv(overalldata_gs, "exp2_data/overalldata_gs.csv", row.names = F)
-
-##pull in the data
-master_gs = read.csv("exp2_data/overalldata_gs.csv", stringsAsFactors = F)
-
-##get rid of the blank stuff
-library(ngram)
+master_gs = rbind(NYtimes_gs, NPR_gs, SLATE_gs, 
+                        HUFFPO_gs, POLITICO_gs, FOX_gs, 
+                        BREITBART_gs, RUSH_gs, BLAZE_gs, 
+                        HANNITY_gs)
 
@@
 ##take out the disqus ones
-nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##figure out the duplicates
-nodis$URLS = duplicated(nodis$Url)
+#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
 
 ##all data
-final_gs = subset(nodis, URLS == FALSE)
-
-tapply(final_gs$wordcount, final_gs$Source, mean)
-tapply(final_gs$wordcount, final_gs$Source, sum)
-
-write.csv(final_gs, "exp2_data/finaldata_gs.csv")
+final_gs = nozero
 ```
@@
 ```{r stem_text_both, eval = T, echo = F}
-##stem Kav text
-final_kav = read.csv("exp2_data/finaldata_kav.csv", stringsAsFactors = F)
-#final = na.omit(final) #one weird NA line
-
-##load libraries
-library(tm)
-library(ngram)
-
 #process the Text column (write a loop) - save processed text as a separate column
@@
 
-##stem GS text
-final_gs = read.csv("exp1_data/finaldata_gs.csv", stringsAsFactors = F)
-
 #process the Text column (write a loop) - save processed text as a separate column
@@
 
-  final_gs$edited[i] = preprocess(fina_gs$Text[i], #one value at a time
+  final_gs$edited[i] = preprocess(final_gs$Text[i], #one value at a time
            case = "lower", 
@@
 
-```
-```{r stem_warriner_exp2, eval = T, echo = F}
-##open the Warriner data for later
-warriner = read.csv("exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
-warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
-
-for(i in 1:nrow(warriner)) {
-  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
-} 
 ```

### 2019-04-06 pilot_manuscript.Rmd
reverted some of the files that I think I screwed up

@@
 POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F)
 BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")

### 2019-04-06 pilot_manuscript.Rmd
not really making any progress

@@
 #read it in
-NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F)
-BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #not ok fix
+POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
+FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
+BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
+RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
+BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
+HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
 
@@
 #read it in
-NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F)
-NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F)
-SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F)
-HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F)
-POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F)
-FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F)
-BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F)
-RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F)
-BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F)
-HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F)
+NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
+NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
+SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
+HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
+POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
+FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
+BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
+RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
+BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
+HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
 

### 2019-04-07 pilot_manuscript.Rmd
Built the source descriptive tables and wrote about it in Exp1

@@
 ####build the table here####
-tableprint = matrix(NA, nrow=4, ncol=7)
-colnames(tableprint) = c("Sources", "Unique_Words", "stuff")
-
-tableprint[ , 1] = levels(final$Source)
-tableprint[ , 2] = tapply(final$uniquewords, final$Source, mean)
+tableprint = matrix(NA, nrow=4, ncol=11)
+colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
+
+tableprint[ , 1] = print(unique(final$Source))
+tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
+tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
+tableprint[ , 4] = tapply(final$X, final$Source, length)
+tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
+tableprint[ , 6] = tapply(final$wordcount, final$Source, mean)
+tableprint[ , 7] = tapply(final$wordcount, final$Source, sd)
+tableprint[ , 8] = tapply(final$uniquewords, final$Source, mean)
+tableprint[ , 9] = tapply(final$uniquewords, final$Source, sd)
+tableprint[ , 10] = tapply(final$FK, final$Source, mean)
+tableprint[ , 11] = tapply(final$FK, final$Source, sd)
 
@@
 apa_table(as.data.frame(tableprint),
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Experiment 1 Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
+          caption = "Experiment 1 - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
           format = "latex",
@@
 
-overall valence for each source
-
-types/tokens ratios, etc. for each source also number of articles
-
-table - columns are types (unique words), tokens (total words), readability statistics, number of articles, total number of words, valence
-
-talk about the table here
+The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
+Statistics calculated included *z*-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
+Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula.
+Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
+The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage [@Kincaid1975].
+For example, a text with a readability score of 11 should be easily read by a high school junior.
+
+As seen in Table 1, the sources are similar in some aspects yet different in others.
+Valence appears to be slightly positive across all sources.
+The standard deviations seem to indicate little to no presence of a difference in valence.
+*The New York Times* published the greatest number of articles as well as total words.
+*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
+Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
+Once again the standard deviations call into question any apparent differences between sources.
+Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
+This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
+As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
 
@@
 The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 1.
+Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 2.
 To interpret the weighted scores, one can examine the mean and standard deviations for each.
@@
 
+#Kav Table
+####build the table here####
+tableprint = matrix(NA, nrow=10, ncol=11)
+colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
+
+tableprint[ , 1] = print(unique(final$Source))
+tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean)
+tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd)
+tableprint[ , 4] = tapply(final_kav$X, final$Source, length)
+tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum)
+tableprint[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean)
+tableprint[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
+tableprint[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean)
+tableprint[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd)
+tableprint[ , 10] = tapply(final_kav$FK, final_kav$Source, mean)
+tableprint[ , 11] = tapply(final_kav$FK, final_kav$Source, sd)
+
+#change this to match
+apa_table(as.data.frame(tableprint),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
+          caption = "Kavanaugh - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 6))
+          )
+
 #GS
@@
 tapply(final_gs$FK, final_gs$Source, sd)
+
+#GS Table
+####build the table here####
+tableprint = matrix(NA, nrow=10, ncol=11)
+colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
+
+tableprint[ , 1] = print(unique(final$Source))
+tableprint[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
+tableprint[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
+tableprint[ , 4] = tapply(final_gs$X, final$Source, length)
+tableprint[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
+tableprint[ , 6] = tapply(final_gs$wordcount, final_gs$Source, mean)
+tableprint[ , 7] = tapply(final_gs$wordcount, final_gs$Source, sd)
+tableprint[ , 8] = tapply(final_gs$uniquewords, final_gs$Source, mean)
+tableprint[ , 9] = tapply(final_gs$uniquewords, final_gs$Source, sd)
+tableprint[ , 10] = tapply(final_gs$FK, final_gs$Source, mean)
+tableprint[ , 11] = tapply(final_gs$FK, final_gs$Source, sd)
+
+#change this to match
+apa_table(as.data.frame(tableprint),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
+          caption = "Government Shutdown - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 6))
+          )
 ```

### 2019-04-07 pilot_manuscript.Rmd
addressed a couple of notes from Trello

@@
 Theological concerns regarding the border wall might invoke *authority/respect* as well as *purity/sanctity*.
+In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
+could also elicit moral concerns related to *ingroup/outgroup*.
 
@@
 We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
+
+The same process was followed for scraping articles related to the partical U.S.
+Government shutdown of 2018-2019.
+The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
+Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
 

### 2019-04-07 pilot_manuscript.Rmd
FIXED IT

@@
 SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #not ok fix
+HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
 POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
@@
 
+#fix this issue
+master_kav$Text = gsub("\\.", "\\. ", master_kav$Text)
+
 ##get rid of the blank stuff
@@
 #read it in
-NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
+NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
 NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
@@
                         HANNITY_gs)
+
+#fix this issue
+master_gs$Text = gsub("\\.", "\\. ", master_gs$Text)
 
@@
 ## Results
+
 ```{r exp2 source descriptives_both, results = 'asis', echo = FALSE, message = F}

### 2019-04-07 pilot_manuscript.Rmd
all updates! WOOO

@@
 nozero = subset(master_kav, wordcount > 0)
+nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
 tapply(nozero$wordcount, nozero$Source, mean)
@@
 nozero = subset(master_gs, wordcount > 0)
+nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
+
 tapply(nozero$wordcount, nozero$Source, mean)
@@
 #kav
-mean(harm_final_data_kav$valence)
-sd(harm_final_data_kav$valence)
-mean(fair_final_data_kav$valence)
-sd(fair_final_data_kav$valence)
-mean(ingroup_final_data_kav$valence)
-sd(ingroup_final_data_kav$valence)
-mean(authority_final_data_kav$valence)
-sd(authority_final_data_kav$valence)
-mean(purity_final_data_kav$valence)
-sd(purity_final_data_kav$valence)
+mean(harm_final_data_kav$valence, na.rm = T)
+sd(harm_final_data_kav$valence, na.rm = T)
+mean(fair_final_data_kav$valence, na.rm = T)
+sd(fair_final_data_kav$valence, na.rm = T)
+mean(ingroup_final_data_kav$valence, na.rm = T)
+sd(ingroup_final_data_kav$valence, na.rm = T)
+mean(authority_final_data_kav$valence, na.rm = T)
+sd(authority_final_data_kav$valence, na.rm = T)
+mean(purity_final_data_kav$valence, na.rm = T)
+sd(purity_final_data_kav$valence, na.rm = T)
 #gs
-mean(harm_final_data_gs$valence)
-sd(harm_final_data_gs$valence)
-mean(fair_final_data_gs$valence)
-sd(fair_final_data_gs$valence)
-mean(ingroup_final_data_gs$valence)
-sd(ingroup_final_data_gs$valence)
-mean(authority_final_data_gs$valence)
-sd(authority_final_data_gs$valence)
-mean(purity_final_data_gs$valence)
-sd(purity_final_data_gs$valence)
+mean(harm_final_data_gs$valence, na.rm = T)
+sd(harm_final_data_gs$valence, na.rm = T)
+mean(fair_final_data_gs$valence, na.rm = T)
+sd(fair_final_data_gs$valence, na.rm = T)
+mean(ingroup_final_data_gs$valence, na.rm = T)
+sd(ingroup_final_data_gs$valence, na.rm = T)
+mean(authority_final_data_gs$valence, na.rm = T)
+sd(authority_final_data_gs$valence, na.rm = T)
+mean(purity_final_data_gs$valence, na.rm = T)
+sd(purity_final_data_gs$valence, na.rm = T)
 #note that a big problem is the valence of the words 
@@
 summary(harm_model_kav)
+r.squaredGLMM(harm_model_kav)
 ```
@@
 ```
+
 # Experiment 2
@@
 
-```{r exp2 source descriptives_both, results = 'asis', echo = FALSE, message = F}
+```{r exp2_source_descriptives_kav, results = 'asis', echo = FALSE, message = F}
 #Kav
@@
           )
-
+```
+
+```{r exp2_source_descriptives_gs, results = 'asis', echo = FALSE, message = F}
+#Kav
 #GS
@@
 #harm
-harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
+harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T), 
                  m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
@@
 tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1, 
-                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
+                    summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
                     harm_d_kav$d)
 tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1, 
-                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
+                    summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
                     fair_d_kav$d)
 tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1, 
-                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
+                    summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
                     ingroup_d_kav$d)
 tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1, 
-                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
+                    summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
                     authority_d_kav$d)
 tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1, 
-                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
+                    summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
                     purity_d_kav$d)
@@
 #harm
-harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
+harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T), 
                  m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
@@
 tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1, 
-                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
+                    summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
                     harm_d_gs$d)
 tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1, 
-                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
+                    summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
                     fair_d_gs$d)
 tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1, 
-                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
+                    summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
                     ingroup_d_gs$d)
 tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1, 
-                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
+                    summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
                     authority_d_gs$d)
 tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1, 
-                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
+                    summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
                     purity_d_gs$d)
@@
 
-tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
-     height = 3, units = 'in', compression = "lzw")
-plot(graph_data_kav)
-dev.off()
+#tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
+#     height = 3, units = 'in', compression = "lzw")
+#plot(graph_data_kav)
+#dev.off()
 ```

### 2019-04-13 pilot_manuscript.Rmd
tried to get descriptives, but it ain't work :/

@@
 
+## Descriptive Statistics
+
+The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
+As in Experiment 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
+
+Table 3 displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
+The sources are similar in some aspects yet different in others.
+Valence appears to be slightly positive across all sources.
+The standard deviations seem to indicate little to no presence of a difference in valence.
+*The New York Times* published the greatest number of articles as well as total words.
+*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
+Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
+Once again the standard deviations call into question any apparent differences between sources.
+Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
+This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
+As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
+
+Table 4 displays descriptive statistics for articles about the partial government shutdown.
+
 ```{r exp2_source_descriptives_kav, results = 'asis', echo = FALSE, message = F}
@@
 
-tableprint[ , 1] = print(unique(final$Source))
+tableprint[ , 1] = print(unique(final_kav$Source))
 tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean)
 tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd)
-tableprint[ , 4] = tapply(final_kav$X, final$Source, length)
+tableprint[ , 4] = tapply(final_kav$X, final_kav$Source, length)
 tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum)

### 2019-04-13 pilot_manuscript.Rmd
debugging is zero fun

@@
 author_note: |
-
   William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
@@
 abstract: |
-
   The media ecosystem has grown, and political opinions have diverged such that there are competing conceptions of objective truth.
@@
 lineno            : yes
+lang              : "english"
+class             : "man"
 mask              : no
-
-class             : "man"
 output            : papaja::apa6_pdf
+replace_ampersands: yes
+csl               : apa6.csl
 ---
@@
 knitr::opts_chunk$set(cache = TRUE)
+options(tinytex.verbose = TRUE)
 ```
@@
 Individually focused concerns can be grouped under an overarching "ethic of autonomy," which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the "ethic of community" (comprising one's duty to their family, tribe, etc.), and the "ethic of divinity"" - representing one's duty not to defile their God-given body and soul [@Graham2009].
+The other two ethics were the "ethic of community" (comprising one's duty to their family, tribe, etc.), and the "ethic of divinity" - representing one's duty not to defile their God-given body and soul [@Graham2009].
 In the 2000s, @Haidt2007 took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
@@
 The same pattern can be seen in the MFD entries for the other four foundations.
-*Purity/sanctity* features words that likely have a negative valence to most observers, including "disease"" and "trash," along with more positive words, including "right" and "sacred" [@Graham2009].
+*Purity/sanctity* features words that likely have a negative valence to most observers, including "disease" and "trash," along with more positive words, including "right" and "sacred" [@Graham2009].
 These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from *harm/care*: *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*.
@@
 Furthermore, @Graham2011 claim to find a "reasonable" degree of generalizability for the MFQ across participants from many different regions in the world.
-These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by @Shuler2011 should still be taken into account in studies involving the theory.
+These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by @Suhler2011 should still be taken into account in studies involving the theory.
 
@@
 
-tableprint[ , 1] = print(unique(final$Source))
+tableprint[ , 1] = unique(final$Source)
 tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
@@
           note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          caption = "Experiment 1 - Descriptive Statistics by Source", 
+          #caption = "Experiment 1 - Descriptive Statistics by Source", 
           col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Experiment 1 Results - Multilevel Model", 
+          #caption = "Experiment 1 Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
 As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
-
 Table 4 displays descriptive statistics for articles about the partial government shutdown.
@@
 
-tableprint[ , 1] = print(unique(final_kav$Source))
+tableprint[ , 1] = unique(final_kav$Source)
 tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean)
 tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd)
-tableprint[ , 4] = tapply(final_kav$X, final_kav$Source, length)
+tableprint[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
 tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum)
@@
           note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          caption = "Kavanaugh - Descriptive Statistics by Source", 
+          #caption = "Kavanaugh - Descriptive Statistics by Source", 
           col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
@@
 
-tableprint[ , 1] = print(unique(final$Source))
+tableprint[ , 1] = unique(final_gs$Source)
 tableprint[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
 tableprint[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
-tableprint[ , 4] = tapply(final_gs$X, final$Source, length)
+tableprint[ , 4] = tapply(final_gs$valenceavg, final_gs$Source, length)
 tableprint[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
@@
           note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          caption = "Government Shutdown - Descriptive Statistics by Source", 
+          #caption = "Government Shutdown - Descriptive Statistics by Source", 
           col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Kavanaugh Results - Multilevel Model", 
+          #caption = "Kavanaugh Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Government Shutdown Results - Multilevel Model", 
+          #caption = "Government Shutdown Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
 
-tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
-     height = 3, units = 'in', compression = "lzw")
-plot(graph_data_gs)
-dev.off()
-=
+#tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
+#     height = 3, units = 'in', compression = "lzw")
+#plot(graph_data_gs)
+#dev.off()
 ```

### 2019-04-13 pilot_manuscript.tex
debugging is zero fun

@@
-\documentclass[,man]{apa6}
+\documentclass[english,,man]{apa6}
 \usepackage{lmodern}
@@
 \urlstyle{same}  % don't use monospace font for urls
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
 \usepackage{graphicx,grffile}
@@
 
-\authornote{
-William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
+\authornote{William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
 
@@
 Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.), and the \enquote{ethic of divinity}" - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
+The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.), and the \enquote{ethic of divinity} - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
 In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
@@
 The first two foundations (\emph{harm/care} and \emph{fairness/reciprocity}) are termed the \enquote{individualizing foundations,} as they are centered on the concerns of individuals rather than groups.
-\emph{Harm/care} represents an endorsement of compassion and kindness, while opposing cruelty and harm.
+\emph{harm/care} represents an endorsement of compassion and kindness, while opposing cruelty and harm.
 \emph{Fairness/reciprocity} represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
@@
 It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations (Graham et al., 2009).
+
+Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
+Suhler, Churchland, Joseph, Graham, and Nosek (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
+First, the authors challenge Haidt and Graham (2007)'s claims the moral intuitions represented by MFT are innate and modular.
+Suhler et al.
+(2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
+Rather, behaviors likely result from interactions between genetics and experience (Suhler et al., 2011).
+According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
+Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler et al., 2011).
+However, as with innateness, there is little neurobiological evidence to support modularity.
+
+Suhler et al.
+(2011) also criticized the content and taxonomy of the five foundations.
+The authors criticize Haidt and Graham (2007)'s omissions of additional foundations, including \emph{industry} and \emph{modesty}, claiming these concepts are moralized in many societies worldwide.
+Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
+For example, Suhler et al.
+(2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
+Work by Graham et al.
+(2011) might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
+Finally, Suhler et al.
+(2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
+In other words, it becomes difficult to recognize a particular concept as indidcative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler et al., 2011).
+
+These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
+The current authors argue these criticisms are especially valid when considered alongside questions regarding the Moral Foundations Dictionary they state herein.
+However, there exists compelling evidence regarding the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
+This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Fondations Dictionary.
 
@@
 The same pattern can be seen in the MFD entries for the other four foundations.
-\emph{Purity/sanctity} features words that likely have a negative valence to most observers, including \enquote{disease}" and \enquote{trash,} along with more positive words, including \enquote{right} and \enquote{sacred} (Graham et al., 2009).
+\emph{Purity/sanctity} features words that likely have a negative valence to most observers, including \enquote{disease} and \enquote{trash,} along with more positive words, including \enquote{right} and \enquote{sacred} (Graham et al., 2009).
 These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from \emph{harm/care}: \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}.
@@
 Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ (Graham et al., 2011).
+
+The Moral Foundations Questionnaire has been validated by multiple researchers.
+Likewise, its five-factor structure has been demonstrated to fit data in multiple countries (Davies, Sibley, \& Liu, 2014; Graham et al., 2011).
+In their article introducing the 30-item MFQ, Graham et al.
+(2011) conducted an exploratory factor analysis (EFA) and found that a five-factor model fit better than a one, two, or three-factor model.
+Davies et al.
+(2014) conducted a confirmatory factor analysis (CFA) of the MFQ with a sample from New Zealand and likewise found the five-factor model provided the best fit.
+While Davies et al.
+(2014) concede the US and New Zealand share many similarities as Western nations, which could raise questions regarding the validity of the MFQ in non-Western nations.
+However, there are striking differences between the two countries, including the lack of a two-party political system in New Zealand, that provide grounds for claiming the MFQ generalizes beyond the United States.
+Furthermore, Graham et al.
+(2011) claim to find a \enquote{reasonable} degree of generalizability for the MFQ across participants from many different regions in the world.
+These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler et al.
+(2011) should still be taken into account in studies involving the theory.
 
@@
 The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
-They were selected for their widespread recognition and the fact they are easily categorized (by the general public) according to perceived political lean.
-In general, \emph{The New York Times} and \emph{NPR} are perceived by many to have a liberal bias or lean.
-In contrast, Fox News and Breitbart are believed to have a conservative bias or lean (Mitchell, Matsa, Gottfried, \& Kiley, 2014).
+They were selected for their widespread recognition and the fact politcial partisans have strong preferences for some sources over others.
+The researchers determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported idealogical consistency represented by the consumers of several news sources.
+In general, \emph{The New York Times} and \emph{NPR} are preferred by consumers reporting a liberal bias or lean.
+In contrast, \emph{Fox News} and \emph{Breitbart} are believed to have a conservative bias or lean.
+Mitchell et al.
+(2014)'s article presented political ideology as a scale ranging from \enquote{consistently liberal} to \enquote{consistently conservative.} In between these extremes lie more moderate positions, including \enquote{mostly liberal,} \enquote{mixed,} and \enquote{mostly conservative.} Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either \enquote{liberal} and \enquote{conservative} in order to form a basis for comparison.
+
 Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the \emph{R} script.
@@
 
+\hypertarget{descriptive-statistics}{%
+\subsection{Descriptive Statistics}\label{descriptive-statistics}}
+
+Breitbart Fox News NPR NY Times
+0.2859474 0.2865543 0.2836801 0.3036140
+Breitbart Fox News NPR NY Times
+0.1758739 0.1657591 0.2303375 0.1316283
+Breitbart Fox News NPR NY Times
+502.4509 590.0179 435.9381 1114.7266
+Breitbart Fox News NPR NY Times
+347.9033 528.6040 642.6311 511.8552
+Breitbart Fox News NPR NY Times
+243.3633 283.5666 191.9583 454.2660
+Breitbart Fox News NPR NY Times
+120.7606 188.9969 192.2881 154.5782
+Breitbart Fox News NPR NY Times
+1437 503 695 406
+Breitbart Fox News NPR NY Times
+722022 296779 302977 452579
+Breitbart Fox News NPR NY Times
+18.41894 16.92098 13.80370 16.32188
+Breitbart Fox News NPR NY Times
+8.011796 7.159823 3.928992 3.290628
+
+\textbackslash{}begin\{table\}{[}tbp{]}
+\textbackslash{}begin\{center\}
+\textbackslash{}begin\{threeparttable\}
+
+\caption{\label{tab:exp1_source_descriptives}}
+
+\textbackslash{}begin\{tabular\}\{lcccccclccc\}
+\toprule
+Source \& \$M\_Valence \& \(SD_Valence\) \& Number of Articles \& Total Words \& \(M_Tokens\) \& \(SD_Tokens\) \& \(M_Types\) \& SD\_Types \& \(M_Readability\) \& \(SD_Readability\)\textbackslash{}
+\midrule
+NY Times \& 0.285947446148072 \& 0.175873929325112 \& 1437 \& 722022 \& 502.450939457202 \& 347.903319774803 \& 243.363256784969 \& 120.760589770644 \& 18.4189422361943 \& 8.01179627082686\textbackslash{}
+NPR \& 0.286554347926494 \& 0.165759138672493 \& 503 \& 296779 \& 590.017892644135 \& 528.604003868971 \& 283.566600397614 \& 188.996856562777 \& 16.9209846559293 \& 7.15982285267178\textbackslash{}
+Fox News \& 0.283680149614328 \& 0.230337453667188 \& 695 \& 302977 \& 435.938129496403 \& 642.63105430646 \& 191.958273381295 \& 192.288110075879 \& 13.8036963247 \& 3.92899246122398\textbackslash{}
+Breitbart \& 0.303614030842649 \& 0.131628349251591 \& 406 \& 452579 \& 1114.72660098522 \& 511.855179780783 \& 454.266009852217 \& 154.578209626066 \& 16.3218777264871 \& 3.29062776810359\textbackslash{}
+\bottomrule
+\addlinespace
+\textbackslash{}end\{tabular\}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
+\end{tablenotes}
+
+\textbackslash{}end\{threeparttable\}
+\textbackslash{}end\{center\}
+\textbackslash{}end\{table\}
+
+The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
+Statistics calculated included \emph{z}-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
+Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula.
+Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
+The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage (Kincaid, Fishburne, Robert P., Richard L., \& Brad S., 1975).
+For example, a text with a readability score of 11 should be easily read by a high school junior.
+
+As seen in Table 1, the sources are similar in some aspects yet different in others.
+Valence appears to be slightly positive across all sources.
+The standard deviations seem to indicate little to no presence of a difference in valence.
+\emph{The New York Times} published the greatest number of articles as well as total words.
+\emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
+Per indvidual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
+Once again the standard deviations call into question any apparent differences between sources.
+Finally, \emph{Fox News} appears to be the most readable source on average, while \emph{The New York Times} is the least readable.
+This might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
+As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
+
+\hypertarget{inferential-statistics}{%
+\subsection{Inferential Statistics}\label{inferential-statistics}}
+
 To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
@@
 The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 1.
+Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 2.
 To interpret the weighted scores, one can examine the mean and standard deviations for each.
@@
 \begin{threeparttable}
-\caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
+\caption{\label{tab:exp1-table}}
 \begin{tabular}{lccccccc}
@@
 Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
+Concerns around abortion might be related either to \emph{harm/care} or \emph{purity/sanctity}.
 On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Likewise, arguments could be made that relate concerns regarding sexual violence to \emph{harm/care} or \emph{fairness/reciprocity}.
 Additionally, the moral duty of the Senate as the upper chamber in the U.S.
@@
 
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on the Kavanaugh confirmation hearing.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks before and two weeks after Kavanaugh's confirmation, owing to its prominence in the news.
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
+\hypertarget{u.s.-government-shutdown-of-2018-2019}{%
+\subsection{U.S. Government Shutdown of 2018-2019}\label{u.s.-government-shutdown-of-2018-2019}}
+
+The U.S.
+Federal Government partially shut down on December 22, 2018.
+The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress (Axelrod, 2019).
+The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
+President Trump demanded \$5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget (Peoples \& Swanson, 2019).
+Owing to the lack of funding, the government began a partial shutdown, causing \enquote{around 800,000} federal employees to be either furloughed or compelled to work without pay (Axelrod, 2019).
+
+The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
+President Trump signed the bill, ending the longest govenrment shutdown in U.S.
+history (Axelrod, 2019).
+Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole (Kheel \& Mitchell, 2019).
+Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed (Peoples \& Swanson, 2019).
+While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
+
+As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
+Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
+As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns (Martin, 2019).
+Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
+Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people (Martin, 2019).
+This example potentially ties into the five moral foundations.
+Theological concerns regarding the border wall might invoke \emph{authority/respect} as well as \emph{purity/sanctity}.
+In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
+could also elicit moral concerns related to \emph{ingroup/outgroup}.
+
+Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
+In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
 
@@
 \section{Method}\label{method-1}}
+
+In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
+The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
+The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
 
@@
 news sources.
-These sources were selected owing to their favorability among political partisans according to Mitchell et al.
+As in Experiment 1, these sources were selected owing to their favorability among political partisans according to Mitchell et al.
 (2014).
-The sources favored by liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
-The sources favored by conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
+The sources favored by the highest proportion of consistent liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
+The sources favored by the highest proportion of consistent conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
@@
 We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
+
+The same process was followed for scraping articles related to the partical U.S.
+Government shutdown of 2018-2019.
+The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
+Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
+
+\begin{verbatim}
+##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
+##  462.4440  496.4967 2018.6502  219.4815  650.4457  296.7350 1108.0689 
+##  POLITICO      RUSH     SLATE 
+## 1551.9478 1552.7151  845.2059
+\end{verbatim}
+
+\begin{verbatim}
+##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
+##    128097    375848   1304048      5926    359046    108605    723569 
+##  POLITICO      RUSH     SLATE 
+##   1069292    267067    229896
+\end{verbatim}
+
+\begin{verbatim}
+##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
+##  397.7857  332.9644 2763.2942  163.6667  560.6944  348.1889 1106.7696 
+##  POLITICO      RUSH     SLATE 
+## 1574.3198 1956.7949  728.6667
+\end{verbatim}
+
+\begin{verbatim}
+##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
+##     38983    102886   2799217     10311    242220    151114    831184 
+##  POLITICO      RUSH     SLATE 
+##    349499    152630     85254
+\end{verbatim}
 
@@
 
+\begin{verbatim}
+## 
+## fought  safer  spurn 
+##     87     26      5
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## fought  safer  spurn 
+##    112     80      5
+\end{verbatim}
+
 \hypertarget{experiment-2-1}{%
@@
 \subsection{Results}\label{results-1}}
+
+\hypertarget{descriptive-statistics-1}{%
+\subsection{Descriptive Statistics}\label{descriptive-statistics-1}}
+
+The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
+As in Experiment 1, statistics calculated include \emph{z}-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source (Kincaid et al., 1975).
+
+Table 3 displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
+The sources are similar in some aspects yet different in others.
+Valence appears to be slightly positive across all sources.
+The standard deviations seem to indicate little to no presence of a difference in valence.
+\emph{The New York Times} published the greatest number of articles as well as total words.
+\emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
+Per indvidual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
+Once again the standard deviations call into question any apparent differences between sources.
+Finally, \emph{Fox News} appears to be the most readable source on average, while \emph{The New York Times} is the least readable.
+This might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
+As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
+Table 4 displays descriptive statistics for articles about the partial government shutdown.
+
+\begin{verbatim}
+BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
+\end{verbatim}
+
+0.2485825 0.2969520 0.2882946 0.3134749 0.2749170 0.2177703 0.3278847
+POLITICO RUSH SLATE
+NaN 0.3817549 0.2945150
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+0.1283312 0.1311957 0.1100579 0.1089378 0.1243028 0.2458333 0.1267266
+POLITICO RUSH SLATE
+NA 0.1339493 0.1235115
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+462.4440 496.4967 2018.6502 219.4815 650.4457 296.7350 1108.0689
+POLITICO RUSH SLATE
+1551.9478 1552.7151 845.2059
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+149.6635 609.9120 2709.7690 145.9798 462.2122 499.0987 570.3075
+POLITICO RUSH SLATE
+1045.4670 1258.5090 612.2226
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+210.5199 230.0304 534.4675 121.0370 283.0670 128.1230 461.2649
+POLITICO RUSH SLATE
+614.6647 419.0000 332.4228
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+53.13550 153.61822 404.21137 57.25952 129.23455 172.51298 174.19696
+POLITICO RUSH SLATE
+358.67966 225.79665 168.16852
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+277 757 646 27 552 366 653
+POLITICO RUSH SLATE
+689 172 272
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+128097 375848 1304048 5926 359046 108605 723569
+POLITICO RUSH SLATE
+1069292 267067 229896
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+10.829946 11.011777 9.701136 11.884344 10.791419 12.489576 10.563974
+POLITICO RUSH SLATE
+12.090968 9.415941 12.350359
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+1.871086 2.122317 1.848820 2.372470 1.909656 3.620217 2.099457
+POLITICO RUSH SLATE
+2.602008 9.255734 2.469494
+
+\textbackslash{}begin\{table\}{[}tbp{]}
+\textbackslash{}begin\{center\}
+\textbackslash{}begin\{threeparttable\}
+
+\caption{\label{tab:exp2_source_descriptives_kav}}
+
+\textbackslash{}begin\{tabular\}\{lcccccclccc\}
+\toprule
+Source \& \$M\_Valence \& \(SD_Valence\) \& Number of Articles \& Total Words \& \(M_Tokens\) \& \(SD_Tokens\) \& \(M_Types\) \& SD\_Types \& \(M_Readability\) \& \(SD_Readability\)\textbackslash{}
+\midrule
+NY Times \& 0.248582461954873 \& 0.128331247765861 \& 277 \& 128097 \& 462.4440433213 \& 149.663540314715 \& 210.519855595668 \& 53.135496091658 \& 10.8299460563033 \& 1.87108620272245\textbackslash{}
+NPR \& 0.296952015363949 \& 0.131195722288699 \& 757 \& 375848 \& 496.496697490092 \& 609.911984327776 \& 230.030383091149 \& 153.61822352656 \& 11.0117767439097 \& 2.12231727243672\textbackslash{}
+SLATE \& 0.288294612452221 \& 0.110057878050137 \& 646 \& 1304048 \& 2018.65015479876 \& 2709.7689798081 \& 534.467492260062 \& 404.21136695319 \& 9.70113600527088 \& 1.84882018527607\textbackslash{}
+HUFFPO \& 0.313474919759693 \& 0.108937766427717 \& 27 \& 5926 \& 219.481481481481 \& 145.979811662796 \& 121.037037037037 \& 57.2595181751682 \& 11.8843441276617 \& 2.37246998423358\textbackslash{}
+POLITICO \& 0.274917000644333 \& 0.124302802662318 \& 552 \& 359046 \& 650.445652173913 \& 462.21217142652 \& 283.067028985507 \& 129.234550340392 \& 10.7914191586328 \& 1.90965621447939\textbackslash{}
+FOX \& 0.217770347500186 \& 0.2458332698723 \& 366 \& 108605 \& 296.734972677596 \& 499.098654130005 \& 128.122950819672 \& 172.512977214565 \& 12.4895757587921 \& 3.62021720854147\textbackslash{}
+BREITBART \& 0.327884697009488 \& 0.126726583211477 \& 653 \& 723569 \& 1108.06891271057 \& 570.307523730945 \& 461.264931087289 \& 174.196961926317 \& 10.5639743164815 \& 2.09945747809235\textbackslash{}
+RUSH \& NaN \& NA \& 689 \& 1069292 \& 1551.94775036284 \& 1045.46703853415 \& 614.66473149492 \& 358.679655515179 \& 12.0909683600071 \& 2.60200753688676\textbackslash{}
+BLAZE \& 0.381754930162833 \& 0.133949323543338 \& 172 \& 267067 \& 1552.71511627907 \& 1258.50895031214 \& 419 \& 225.796653329873 \& 9.41594130925692 \& 9.25573422733374\textbackslash{}
+HANNITY \& 0.294514982957241 \& 0.123511487515174 \& 272 \& 229896 \& 845.205882352941 \& 612.222641383098 \& 332.422794117647 \& 168.168519181875 \& 12.3503593297322 \& 2.46949447044547\textbackslash{}
+\bottomrule
+\addlinespace
+\textbackslash{}end\{tabular\}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
+\end{tablenotes}
+
+\textbackslash{}end\{threeparttable\}
+\textbackslash{}end\{center\}
+\textbackslash{}end\{table\}
+
+\begin{verbatim}
+BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
+\end{verbatim}
+
+0.2630738 0.3363861 0.3502582 0.2895833 0.2955373 0.2292974 0.3292069
+POLITICO RUSH SLATE
+0.2948354 0.3669883 0.3033559
+BLAZE BREITBART FOX HANNITY HUFFPO NPR
+0.12830612 0.14962810 0.12655527 0.14435751 0.13263919 0.21714483
+NY Times POLITICO RUSH SLATE
+0.12716701 0.09816753 0.12112741 0.11622436
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+397.7857 332.9644 2763.2942 163.6667 560.6944 348.1889 1106.7696
+POLITICO RUSH SLATE
+1574.3198 1956.7949 728.6667
+BLAZE BREITBART FOX HANNITY HUFFPO NPR
+102.09771 238.70276 3405.43855 33.59387 425.52190 457.33985
+NY Times POLITICO RUSH SLATE
+506.91798 875.62557 1544.14427 464.34307
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+185.66327 168.30744 637.29812 95.12698 258.26620 155.52535 471.80160
+POLITICO RUSH SLATE
+638.31532 482.79487 301.70940
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+41.93489 81.59286 493.99860 16.59041 130.54439 171.29690 174.88347
+POLITICO RUSH SLATE
+313.33750 252.79150 138.73586
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+98 309 1013 63 432 434 751
+POLITICO RUSH SLATE
+222 78 117
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+38983 102886 2799217 10311 242220 151114 831184
+POLITICO RUSH SLATE
+349499 152630 85254
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+10.684144 10.714110 9.337567 13.406829 10.669212 11.192714 11.279935
+POLITICO RUSH SLATE
+11.283515 9.760202 11.858193
+BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
+1.849923 2.046638 1.907440 4.791906 1.826810 3.150647 2.188760
+POLITICO RUSH SLATE
+1.234029 7.600883 2.510134
+
+\textbackslash{}begin\{table\}{[}tbp{]}
+\textbackslash{}begin\{center\}
+\textbackslash{}begin\{threeparttable\}
+
+\caption{\label{tab:exp2_source_descriptives_gs}}
+
+\textbackslash{}begin\{tabular\}\{lcccccclccc\}
+\toprule
+Source \& \$M\_Valence \& \(SD_Valence\) \& Number of Articles \& Total Words \& \(M_Tokens\) \& \(SD_Tokens\) \& \(M_Types\) \& SD\_Types \& \(M_Readability\) \& \(SD_Readability\)\textbackslash{}
+\midrule
+NY Times \& 0.263073762515189 \& 0.128306121930571 \& 98 \& 38983 \& 397.785714285714 \& 102.097714464963 \& 185.663265306122 \& 41.9348891176587 \& 10.6841442081704 \& 1.84992301246728\textbackslash{}
+NPR \& 0.336386116861354 \& 0.149628095737843 \& 309 \& 102886 \& 332.964401294498 \& 238.702761753771 \& 168.307443365696 \& 81.5928638511323 \& 10.7141103107316 \& 2.04663844695781\textbackslash{}
+SLATE \& 0.350258204124201 \& 0.126555273689823 \& 1013 \& 2799217 \& 2763.2941757157 \& 3405.4385462127 \& 637.298124383021 \& 493.998601763112 \& 9.33756681985634 \& 1.90743987105106\textbackslash{}
+HUFFPO \& 0.289583347963234 \& 0.144357514755571 \& 63 \& 10311 \& 163.666666666667 \& 33.5938742495827 \& 95.1269841269841 \& 16.5904092616031 \& 13.4068286179036 \& 4.7919060550463\textbackslash{}
+POLITICO \& 0.295537320180438 \& 0.132639186552305 \& 432 \& 242220 \& 560.694444444444 \& 425.521903288046 \& 258.266203703704 \& 130.544392770929 \& 10.6692121592768 \& 1.82680953279554\textbackslash{}
+FOX \& 0.229297405563287 \& 0.21714483329782 \& 434 \& 151114 \& 348.188940092166 \& 457.339854495746 \& 155.52534562212 \& 171.296902150535 \& 11.1927143814131 \& 3.15064661540684\textbackslash{}
+BREITBART \& 0.329206931218954 \& 0.127167010716965 \& 751 \& 831184 \& 1106.76964047936 \& 506.917980410773 \& 471.801597869507 \& 174.883471443445 \& 11.2799353793112 \& 2.18876019242514\textbackslash{}
+RUSH \& 0.294835377053155 \& 0.0981675318751069 \& 222 \& 349499 \& 1574.31981981982 \& 875.625574158975 \& 638.315315315315 \& 313.33749985304 \& 11.2835154976977 \& 1.23402883439991\textbackslash{}
+BLAZE \& 0.366988255105934 \& 0.121127409825597 \& 78 \& 152630 \& 1956.79487179487 \& 1544.14427492755 \& 482.794871794872 \& 252.791498653617 \& 9.76020159415253 \& 7.60088309094014\textbackslash{}
+HANNITY \& 0.303355863690906 \& 0.116224358322565 \& 117 \& 85254 \& 728.666666666667 \& 464.343065802237 \& 301.709401709402 \& 138.735860405917 \& 11.8581927760125 \& 2.51013431157023\textbackslash{}
+\bottomrule
+\addlinespace
+\textbackslash{}end\{tabular\}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
+\end{tablenotes}
+
+\textbackslash{}end\{threeparttable\}
+\textbackslash{}end\{center\}
+\textbackslash{}end\{table\}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp2-table_kav}}
+\begin{tabular}{lccccccc}
+\toprule
+Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+\midrule
+Harm/Care & 0.39 & 1.35 & 0.66 & 1.35 & 2.89 & .020 & -0.19\\
+Fairness/Reciprocity & 1.26 & 1.27 & 1.06 & 1.27 & -1.58 & .154 & 0.16\\
+Ingroup/Loyalty & 1.15 & 1.22 & 1.06 & 1.22 & -0.63 & .549 & 0.07\\
+Authority/Respect & 0.85 & 0.99 & 0.75 & 0.99 & -0.93 & .380 & 0.10\\
+Purity/Sanctity & 0.90 & 1.28 & 1.06 & 1.28 & 0.88 & .406 & -0.11\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp2-table_gs}}
+\begin{tabular}{lccccccc}
+\toprule
+Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+\midrule
+Harm/Care & 0.91 & 1.27 & 1.01 & 1.27 & 1.68 & .132 & -0.07\\
+Fairness/Reciprocity & 1.22 & 1.05 & 0.91 & 1.05 & -0.76 & .468 & 0.27\\
+Ingroup/Loyalty & 1.38 & 1.16 & 1.11 & 1.16 & -0.48 & .644 & 0.21\\
+Authority/Respect & 0.87 & 1.24 & 0.36 & 1.24 & -1.38 & .203 & 0.37\\
+Purity/Sanctity & 1.29 & 1.13 & 0.99 & 1.13 & 0.03 & .979 & 0.22\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
 
@@
 
+\leavevmode\hypertarget{ref-Axelrod2019}{}%
+Axelrod, T.
+(2019).
+Poll: Majority of Americans hold Trump and Republicans responsible for shutdown \textbar{} TheHill.
+Retrieved from \url{https://thehill.com/homenews/campaign/427007-poll-majority-of-americans-hold-trump-and-republicans-responsible-for}
+
 \leavevmode\hypertarget{ref-Bradley1999}{}%
@@
 doi:\href{https://doi.org/10.1017/S0022381614000425}{10.1017/S0022381614000425}
+
+\leavevmode\hypertarget{ref-Davies2014}{}%
+Davies, C.
+L., Sibley, C.
+G., \& Liu, J.
+H.
+(2014).
+Confirmatory factor analysis of the moral foundations questionnaire independent scale validation in a new zealand sample.
+\emph{Social Psychology}, \emph{45}(6), 431--436.
+doi:\href{https://doi.org/10.1027/1864-9335/a000201}{10.1027/1864-9335/a000201}
 
@@
 
+\leavevmode\hypertarget{ref-Kheel2019}{}%
+Kheel, R., \& Mitchell, E.
+(2019).
+Overnight Defense: Trump agrees to reopen government without wall funding \textbar{} Senate approves stopgap spending \textbar{} Dems ask Armed Services chair to block military funding for wall \textbar{} Coast Guard official assures workers they will receive back pay \textbar{} TheHill.
+Retrieved from \url{https://thehill.com/policy/defense/overnights/427045-overnight-defense-trump-agrees-to-reopen-government-without-wall}
+
+\leavevmode\hypertarget{ref-Kincaid1975}{}%
+Kincaid, J.
+P., Fishburne, J., Robert P., R., Richard L., C., \& Brad S.
+(1975).
+Derivation of New Readability Formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted Personnel.
+doi:\href{https://doi.org/10.21236/ADA006655}{10.21236/ADA006655}
+
 \leavevmode\hypertarget{ref-Kohlberg1977}{}%
@@
 doi:\href{https://doi.org/10.3758/s13428-012-0210-4}{10.3758/s13428-012-0210-4}
+
+\leavevmode\hypertarget{ref-Martin2019}{}%
+Martin, M. (2019). The Moral Question Of Trump's Border Wall : NPR. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
 
@@
 
+\leavevmode\hypertarget{ref-Peoples2019}{}%
+Peoples, S., \& Swanson, E. (2019, January). Trump's approval rating sinks in new poll as he gets most blame for shutdown. Chicago.
+
 \leavevmode\hypertarget{ref-Pinheiro2017}{}%
@@
 doi:\href{https://doi.org/10.1016/j.jecp.2017.07.008}{10.1016/j.jecp.2017.07.008}
+
+\leavevmode\hypertarget{ref-Suhler2011}{}%
+Suhler, C.
+L., Churchland, P., Joseph, C., Graham, J., \& Nosek, B.
+(2011).
+Can Innate , Modular `` Foundations '' Explain Morality ?
+Challenges for Haidt ʼ s Moral Foundations Theory.
+\emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
 

### 2019-04-13 pilot_manuscript.Rmd
so rude

@@
 
-```{r exp1_source_descriptives, results = 'asis', echo = FALSE, message = F}
+```{r exp1sourcedescriptives, results = 'asis', echo = FALSE, message = F}
 
@@
 
-```{r exp2_source_descriptives_kav, results = 'asis', echo = FALSE, message = F}
+```{r exp2sourcedescriptiveskav, results = 'asis', echo = FALSE, message = F}
 #Kav
@@
 
-```{r exp2_source_descriptives_gs, results = 'asis', echo = FALSE, message = F}
+```{r exp2sourcedescriptivesgs, results = 'asis', echo = FALSE, message = F}
 #Kav
@@
 
-```{r exp2-table_kav, results = 'asis', echo = F}
+```{r exp2-tablekav, results = 'asis', echo = F}
 #MFD, mean, sd, mean, sd, t, p, d
@@
 
-```{r exp2-table_gs, results = 'asis', echo = F}
+```{r exp2-tablegs, results = 'asis', echo = F}
 #MFD, mean, sd, mean, sd, t, p, d

### 2019-04-13 pilot_manuscript erin test.Rmd
LOOK AT THIS SHIT

--- 2019-04-13 pilot_manuscript.Rmd
@@
 knitr::opts_chunk$set(cache = TRUE)
-options(tinytex.verbose = TRUE)
 ```
@@
 
-# Results
-
-## Descriptive Statistics
-
-```{r exp1sourcedescriptives, results = 'asis', echo = FALSE, message = F}
+```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}
 
@@
 
-tapply(final$valenceavg, final$Source, mean)
-tapply(final$valenceavg, final$Source, sd)
-tapply(final$wordcount, final$Source, mean)
-tapply(final$wordcount, final$Source, sd)
-tapply(final$uniquewords, final$Source, mean)
-tapply(final$uniquewords, final$Source, sd)
-tapply(final$Source, final$Source, length)
-tapply(final$wordcount, final$Source, sum)
+# tapply(final$valenceavg, final$Source, mean)
+# tapply(final$valenceavg, final$Source, sd)
+# tapply(final$wordcount, final$Source, mean)
+# tapply(final$wordcount, final$Source, sd)
+# tapply(final$uniquewords, final$Source, mean)
+# tapply(final$uniquewords, final$Source, sd)
+# tapply(final$Source, final$Source, length)
+# tapply(final$wordcount, final$Source, sum)
 
@@
 tableprint[ , 11] = tapply(final$FK, final$Source, sd)
-
+```
+
+```{r temp, results = 'asis', eval = T, echo = F}
 #change this to match
+
+tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+
 apa_table(as.data.frame(tableprint),
           note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          #caption = "Experiment 1 - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
+          caption = "Experiment 1 - Descriptive Statistics by Source",
           format = "latex",
+          small = T,
           escape = F,
-          align = c("l", rep("c", 6))
-          )
-
-```
-
-The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included *z*-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula.
-Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage [@Kincaid1975].
-For example, a text with a readability score of 11 should be easily read by a high school junior.
-
-As seen in Table 1, the sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
-*The New York Times* published the greatest number of articles as well as total words.
-*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
-Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
-This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
-
-## Inferential Statistics
-
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
-Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 2.
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
-
-```{r exp1-table, results = 'asis', echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
-
-#calculate d
-#harm
-harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
-                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d = d.ind.t(m1 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"]),
-                 n2 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d = d.ind.t(m1 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d = d.ind.t(m1 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"]),
-                 n2 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d = d.ind.t(m1 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"]),
-                 n2 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
-                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
-                    harm_d$d)
-tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
-                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
-                    fair_d$d)
-tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
-                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
-                    ingroup_d$d)
-tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
-                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
-                    authority_d$d)
-tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
-                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
-                    purity_d$d)
-
-tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
-tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
-
-apa_table(tableprint,
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          #caption = "Experiment 1 Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7))
-          )
-```
-
-```{r conference-pic, eval = F, include = F}
-library(ggplot2)
-library(reshape)
-
-cleanup = theme(panel.grid.major = element_blank(), 
-                panel.grid.minor = element_blank(), 
-                panel.background = element_blank(), 
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 10))
-
-graphdata = as.data.frame(tableprint)
-graphlong = melt(graphdata[ , c(1,2,4)], 
-                 id = "Foundation")
-graphlong2 = melt(graphdata[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong$sd = graphlong2$value
-graphlong$lower = as.numeric(as.character(graphlong$value)) - 2*as.numeric(as.character(graphlong$sd))
-graphlong$upper = as.numeric(as.character(graphlong$value)) + 2*as.numeric(as.character(graphlong$sd))
-
-graphlong$value = as.numeric(as.character(graphlong$value))
-
-graph_data = ggplot(graphlong, aes(Foundation, value, color = variable)) + 
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), 
-                position = position_dodge(width = 0.90),
-                width = .2) + 
-  cleanup +
-  ylab("Mean Weighted Valence") + 
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-tiff(filename = "exp1_graph.tiff", res = 300, width = 4, 
-     height = 3, units = 'in', compression = "lzw")
-plot(graph_data)
-dev.off()
-
-```
-
-# Discussion
-
-The results obtained in Experiment 1 did not confirm the hypothesis.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The strongest effect found was for the *authority/respect* foundation owing to the fact its Cohen's *d* value was greater than the other four foundations.
-However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
-This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
-It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
-
-Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
-The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
-In short, the range of topics covered in Experiment 1 was likely too broad.
-The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
-
-Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-Generally speaking, the researchers believe their methodology to be sound.
-Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
-Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
-The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurence.
-
-While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
-The researchers identified two such changes that were subsequently employed in Experiment 2.
-First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
-politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court.
-In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
-
-# Experiment 2
-
-## Kavanaugh Supreme Court Hearing
-
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@USGovernment2018b].
-Following allegations of sexual assault by high school classmate Dr.
-Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
-
-On September 27, the committee questioned Dr.
-Ford before commencing a second round of questioning for Judge Kavanaugh [@USGovernment2018].
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018].
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@USGovernment2018a].
-
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals.
-The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-Concerns around abortion might be related either to *harm/care* or *purity/sanctity*.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Likewise, arguments could be made that relate concerns regarding sexual violence to *harm/care* or *fairness/reciprocity*.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
-
-## U.S. Government Shutdown of 2018-2019
-
-The U.S.
-Federal Government partially shut down on December 22, 2018.
-The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019].
-The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
-President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019].
-Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].
-
-The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
-President Trump signed the bill, ending the longest govenrment shutdown in U.S.
-history [@Axelrod2019].
-Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole [@Kheel2019].
-Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed [@Peoples2019].
-While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
-
-As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
-Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
-As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns [@Martin2019].
-Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
-Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people [@Martin2019].
-This example potentially ties into the five moral foundations.
-Theological concerns regarding the border wall might invoke *authority/respect* as well as *purity/sanctity*.
-In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
-could also elicit moral concerns related to *ingroup/outgroup*.
-
-Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
-In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
-
-# Method
-
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-
-```{r NYTimes_kav, eval = F, include = F}
-
-library(rvest)
-library(RSelenium)
-
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#page for NYTIMES
-url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
-
-#navigate to it
-remDr$navigate(url)
-
-#click the button 
-#don't change class name
-#right click --> inspect element 
-webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
-
-#with 752 results at 10 per page we need
-#752 - 10 original = 742 / 10 per click = 75 clicks
-
-for (i in 1:75) { #change this to 75 later
-  webElem$clickElement()
-  Sys.sleep(runif(1, 1, 5))
-}
-
-webpage <-remDr$getPageSource()
-
-#Reading the HTML code from the website - headlines
-webpage2 <- read_html(unlist(webpage))
-
-headline_data = html_nodes(webpage2,'a')
-
-attr_data = html_attrs(headline_data) 
-attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep(".html", urlslist)]
-urlslist = urlslist[grep("/2018", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-#paste NY on front
-urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
-
-  ##pull the text
-  text_data = html_text(headline_data)
-
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-  Sys.sleep(runif(1, 1, 10)) #don't make them angry
-} ##end for loop
-
-write.csv(NYtimesDF, "NYtimes_kav.csv", row.names = F)
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-```
-
-```{r NYTimes_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#page for NYTIMES
-url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'
-
-#navigate to it
-remDr$navigate(url)
-
-#click the button 
-#don't change class name
-#right click --> inspect element 
-webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
-
-#with 803 results at 10 per page we need
-#803 - 10 original / 10 per click is 80 clicks
-
-for (i in 1:80) {
-  webElem$clickElement()
-  Sys.sleep(runif(1, 1, 5))
-}
-
-webpage <-remDr$getPageSource()
-
-#Reading the HTML code from the website - headlines
-webpage2 <- read_html(unlist(webpage))
-
-headline_data = html_nodes(webpage2,'a')
-
-attr_data = html_attrs(headline_data) 
-#attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep(".html", urlslist)]
-urlslist = urlslist[grep("/201", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-#paste NY on front
-urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
-
-  ##pull the text
-  text_data = html_text(headline_data)
-
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-  Sys.sleep(runif(1, 1, 10)) #don't make them angry
-} ##end for loop
-
-write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
-beep(sound = 5)
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-```
-
-````{r NPR_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-##loop through the page number at the end until done with ~1000 / 20 = 50
-for (i in 1:50) { ##change this to 50
-
-  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
-
-  #navigate to it
-  remDr$navigate(url)
-
-  #scroll on the page
-  webscroll <- remDr$findElement("css", "body")
-  webscroll$sendKeysToElement(list(key = "end"))
-
-  #get the links
-  webElems <- remDr$findElements(using = "css", "[href]")
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-} #close the loop
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-urlslist = unlist(urlslist_final)
-#find all the ones with /2018/
-urlslist2 = urlslist[grep("/2018", urlslist)]
-urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
-urlslist2 = unique(urlslist2)
-temp = strsplit(urlslist2, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#deal with the ones with extra parts
-temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`4` == 2018 & #must be 2018 and 
-                         (temp2$`5` == "09" & as.numeric(temp2$`6`)>=13 | 
-                            temp2$`5` == "10" & as.numeric(temp2$`6`)<=11), #Must be 9 or 10 
-                ])
-
-urlslist3 = urlslist2[as.numeric(rows)]
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(NPRDF) = c("Source", "Url", "Text")
-NPRDF = as.data.frame(NPRDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'#storytext > p')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  NPRDF$Source[i] = "NPR"
-  NPRDF$Url[i] = urlslist3[i]
-  NPRDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-beep(sound = 3)
-
-write.csv(NPRDF, "NPR_kav.csv", row.names = F)
-
-```
-
-```{r NPR_shut, eval = F, include = F}
-
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-##loop through the page number at the end until done with ~3316 / 20 = 166
-for (i in 1:166) {
-
-  url = paste0('https://www.npr.org/search?query=government%20shutodwn&page=', i)
-
-  #navigate to it
-  remDr$navigate(url)
-
-  #scroll on the page
-  webscroll <- remDr$findElement("css", "body")
-  webscroll$sendKeysToElement(list(key = "end"))
-
-  #get the links
-  webElems <- remDr$findElements(using = "css", "[href]")
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-} #close the loop
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-urlslist = unlist(urlslist_final)
-#find all the ones with /2018/
-urlslist2 = urlslist[grep("/201", urlslist)]
-urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
-urlslist2 = unique(urlslist2)
-temp = strsplit(urlslist2, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#deal with the ones with extra parts
-temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
-
-#pull only the right dates
-rows = rownames(temp2[ (temp2$`4` == 2018 | temp2$`4` == 2019) & #must be 2018/19 and  
-                         (
-                           (temp2$`5` == "12" & as.numeric(temp2$`6`)>8 & temp2$`4` == 2018) | #after dec 12
-                            (temp2$`5`== "01" & temp2$`4` == 2019) | #all of jan
-                            (temp2$`5` == "02" & as.numeric(temp2$`6`)<8 & temp2$`4` == 2019)
-                           ), #before feb 8
-                ])
-
-urlslist3 = urlslist2[as.numeric(rows)]
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(NPRDF) = c("Source", "Url", "Text")
-NPRDF = as.data.frame(NPRDF)
-
-##for loops
-for (i in 315:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'#storytext > p')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  NPRDF$Source[i] = "NPR"
-  NPRDF$Url[i] = urlslist3[i]
-  NPRDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-beep(sound = 3)
-
-write.csv(NPRDF, "NPR_gs.csv", row.names = F)
-```
-
-````{r Slate_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://slate.com/search?q=kavanaugh&via=homepage_nav_search"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#appear to be 10 pages
-for (i in 1:10){
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
-
-  #don't go too fast for the page to load
-  Sys.sleep(runif(1, 1, 5))
-
-  #click on the page number
-  webClick[[i]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones with /2018/
-urlslist2 = urlslist[grep("/2018/10|/2018/09", urlslist)]
-urlslist2 = unique(urlslist2)
-
-#71 articles seems suspiciously low, so also scraped this page
-#https://slate.com/tag/brett-kavanaugh/
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#337 / 20 = 17 pages
-for (i in 1:17){
-
-  url = paste0("https://slate.com/tag/brett-kavanaugh/", i)
-
-  remDr$navigate(url)
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones with /2018/
-urlslist2.1 = urlslist[grep("/2018/10|/2018/09", urlslist)]
-urlslist2.1 = unique(urlslist2.1)
-
-urlslist3 = unique(c(urlslist2, urlslist2.1))
-
-##start a data frame
-SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(SLATEDF) = c("Source", "Url", "Text")
-SLATEDF = as.data.frame(SLATEDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  SLATEDF$Source[i] = "SLATE"
-  SLATEDF$Url[i] = urlslist3[i]
-  SLATEDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-beep(sound = 3)
-
-write.csv(SLATEDF, "SLATE_kav.csv", row.names = F)
-
-```
-
-```{r SLATE_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://slate.com/search?q=government+shutdown"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#appear to be 10 pages
-for (i in 1:10){
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
-
-  #don't go too fast for the page to load
-  Sys.sleep(runif(1, 1, 5))
-
-  #click on the page number
-  webClick[[i]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones from 12 2018 to 02 2019
-urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
-urlslist2 = unique(urlslist2)
-
-#60 something articles seems suspiciously low, so also scraped this page
-#https://slate.com/tag/governtment-shutdown
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#354 / 20 = 18 pages
-for (i in 1:18){
-
-  url = paste0("https://slate.com/tag/government-shutdown/", i)
-
-  remDr$navigate(url)
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones with /2018/
-urlslist2.1 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
-urlslist2.1 = unique(urlslist2.1)
-
-urlslist3 = unique(c(urlslist2, urlslist2.1))
-
-##start a data frame
-SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(SLATEDF) = c("Source", "Url", "Text")
-SLATEDF = as.data.frame(SLATEDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  SLATEDF$Source[i] = "SLATE"
-  SLATEDF$Url[i] = urlslist3[i]
-  SLATEDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-#beep(sound = 3)
-
-write.csv(SLATEDF, "SLATE_gs.csv", row.names = F)
-```
-
-````{r HuffPo_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#943 results with 10 per page 94 clicks
-for (i in 1:94){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "class name", "fz-20")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "class name", "next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-##start a data frame
-HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HUFFPODF) = c("Source", "Url", "Text")
-HUFFPODF = as.data.frame(HUFFPODF)
-int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
-
-for (i in 937:length(urlslist)){
-
-  #convert the url
-  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
-  temp = gsub("%3a", ":", temp)
-  temp = gsub("%2f", "/", temp)
-
-  webpage = read_html(temp)
-  #figure out the date
-  headline_data = html_nodes(webpage, '.timestamp__date--published')
-  text_data = html_text(headline_data)
-  time = unlist(strsplit(text_data, split = "\n| "))[2]
-  time = as.Date(time, format = "%m/%d/%Y")
-
-  if (time %within% int) {
-    ##pull out the text
-    headline_data2 = html_nodes(webpage,'p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HUFFPODF$Source[i] = "HUFFPO"
-    HUFFPODF$Url[i] = urlslist[i]
-    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 3)
-
-write.csv(HUFFPODF, "HUFFPO_kav.csv", row.names = F)
-```
-
-```{r HuffPo_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=government+shutdown&fr=huffpost_desktop"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#942 results with 10 per page 94 clicks
-for (i in 1:94){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "class name", "fz-20")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "class name", "next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 2)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-##start a data frame
-HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HUFFPODF) = c("Source", "Url", "Text")
-HUFFPODF = as.data.frame(HUFFPODF)
-int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
-
-for (i in 1:length(urlslist)){
-
-  #convert the url
-  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
-  temp = gsub("%3a", ":", temp)
-  temp = gsub("%2f", "/", temp)
-
-  webpage = read_html(temp)
-  #figure out the date
-  headline_data = html_nodes(webpage, '.timestamp__date--published')
-  text_data = html_text(headline_data)
-  time = unlist(strsplit(text_data, split = "\n| "))[2]
-  time = as.Date(time, format = "%m/%d/%Y")
-
-  if (time %within% int) {
-    ##pull out the text
-    headline_data2 = html_nodes(webpage,'p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HUFFPODF$Source[i] = "HUFFPO"
-    HUFFPODF$Url[i] = urlslist[i]
-    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 2)
-
-write.csv(HUFFPODF, "HUFFPO_gs.csv", row.names = F)
-```
-
-````{r Politico_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=kavanaugh&pv=&c=&r=&start=09%2F13%2F2018&start_submit=09%2F13%2F2018&end=10%2F11%2F2018&end_submit=10%2F11%2F2018"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#749 with 20 per page with 37 clicks
-
-for (i in 1:37){
-
-  if (i > 1){
-    #navigate to the next page
-    url = paste0("https://www.politico.com/search/", i, 
-                 "?s=newest&q=kavanaugh&adv=true&start=09/13/2018&end=10/11/2018")
-    remDr$navigate(url)
-  }
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 7)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[grep("/2018/", urlslist)]
-urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
-
-##start a data frame
-POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(POLITICODF) = c("Source", "Url", "Text")
-POLITICODF = as.data.frame(POLITICODF)
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  POLITICODF$Source[i] = "POLITICO"
-  POLITICODF$Url[i] = urlslist[i]
-  POLITICODF$Text[i] = paste(text_data2, collapse = "")
-
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-beep(sound = 7)
-
-write.csv(POLITICODF, "POLITICO_kav.csv", row.names = F)
-#easiest one yet
-```
-
-```{r Politico_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=government+shutdown&pv=&c=&r=&start=12%2F08%2F2018&start_submit=12%2F08%2F2018&end=02%2F08%2F2019&end_submit=02%2F08%2F2019"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#1329 with 20 per page with 66 clicks
-
-for (i in 1:66){
-
-  if (i > 1){
-    #navigate to the next page
-    url = paste0("https://www.politico.com/search/", i, 
-                 "?s=newest&q=government shutdown&adv=true&start=12/08/2018&end=02/08/2019")
-    remDr$navigate(url)
-  }
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 7)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[grep("/2018/", urlslist)]
-urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
-
-##start a data frame
-POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(POLITICODF) = c("Source", "Url", "Text")
-POLITICODF = as.data.frame(POLITICODF)
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  POLITICODF$Source[i] = "POLITICO"
-  POLITICODF$Url[i] = urlslist[i]
-  POLITICODF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(POLITICODF, "POLITICO_gs.csv", row.names = F)
-
-```
-
-````{r Fox_kav, eval = F, include = F}
-
-##start a data frame
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#1651 with 10 per page with 165 clicks
-
-for (i in 1:165){
-
-    #navigate to the page
-    url = paste0("https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=",
-                 (i-1)*10)
-    remDr$navigate(url)
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", ".ng-binding")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("video.", urlslist))] #take out videos
-urlslist = urlslist[-c(grep("/search-results", urlslist))] #take out search result fake links
-
-##start a data frame
-FOXDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(FOXDF) = c("Source", "Url", "Text")
-FOXDF = as.data.frame(FOXDF)
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  FOXDF$Source[i] = "FOX"
-  FOXDF$Url[i] = urlslist[i]
-  FOXDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(FOXDF, "FOX_kav.csv", row.names = F)
-```
-
-````{r Breitbart_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.breitbart.com/tag/brett-kavanaugh/"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-for (i in 1:42){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "h2 a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  if (i > 1)
-    {
-  url = paste0("https://www.breitbart.com/tag/brett-kavanaugh/page/",
-               i+1, "/")
-  remDr$navigate(url)
-  }
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
-                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
-                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(BREITBARTDF) = c("Source", "Url", "Text")
-BREITBARTDF = as.data.frame(BREITBARTDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'h2, p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  BREITBARTDF$Source[i] = "BREITBART"
-  BREITBARTDF$Url[i] = urlslist3[i]
-  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(BREITBARTDF, "BREITBART_kav.csv", row.names = F)
-```
-
-```{r Breitbart_gs, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.breitbart.com/tag/government-shutdown/"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-for (i in 1:16){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "h2 a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  if (i > 1)
-    {
-  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
-               i+1, "/")
-  remDr$navigate(url)
-  }
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
-                         (
-                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
-                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
-                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
-                         ), #before feb 8
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(BREITBARTDF) = c("Source", "Url", "Text")
-BREITBARTDF = as.data.frame(BREITBARTDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'h2, p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  BREITBARTDF$Source[i] = "BREITBART"
-  BREITBARTDF$Url[i] = urlslist3[i]
-  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(BREITBARTDF, "BREITBART_gs.csv", row.names = F)
-```
-
-````{r Rush_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-##18 pages
-for (i in 1:18){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
-
-  #click on the page number
-  webClick[[18]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
-                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
-                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(RUSHDF) = c("Source", "Url", "Text")
-RUSHDF = as.data.frame(RUSHDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  RUSHDF$Source[i] = "RUSH"
-  RUSHDF$Url[i] = urlslist3[i]
-  RUSHDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(RUSHDF, "RUSH_kav.csv", row.names = F)
-```
-
-```{r Rush_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-##47 pages
-for (i in 1:47){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
-
-  #click on the page number
-  webClick[[18]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
-                         (
-                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
-                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
-                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
-                         ), #before feb 8
-                       ])
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(RUSHDF) = c("Source", "Url", "Text")
-RUSHDF = as.data.frame(RUSHDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  RUSHDF$Source[i] = "RUSH"
-  RUSHDF$Url[i] = urlslist3[i]
-  RUSHDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(RUSHDF, "RUSH_gs.csv", row.names = F)
-
-```
-
-````{r Blaze_kav, eval = F, include = F}
-url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
-webpage9 = read_html(url9)
-headline_data9 = html_nodes(webpage9, '.widget__headline-text')
-
-attr_data9 = html_attrs(headline_data9) 
-attr_data9
-
-urlslist9 = unlist(attr_data9)
-urlslist9 = urlslist9[grep(urlslist9)]
-
-##start a data frame
-BlazeDF = matrix(NA, nrow = length(urlslist9), ncol = 3)
-colnames(BlazeDF) = c("Source", "Url", "Text")
-BlazeDF = as.data.frame(BlazeDF)
-
-##for loops
-for (i in 1:length(urlslist9)){
-
-  ##read in the URL
-  webpage9 <- read_html(urlslist9[i])
-
-  ##pull the specific nodes
-  headline_data9 = html_nodes(webpage9,'p')
-
-  ##pull the text
-  text_data9 = html_text(headline_data9)
-
-  ##save the data
-  BlazeDF$Source[i] = "The Blaze"
-  BlazeDF$Url[i] = urlslist9[i]
-  BlazeDF$Text[i] = paste(text_data9, collapse = "")
-} ##end for loop
-```
-
-```{r Blaze_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.theblaze.com/search/?q=government+shutdown"
-
-remDr$navigate(url)
-
-webClick <- remDr$findElements(using = "css", ".action-btn")
-
-#click next until done
-while (length(webClick) > 0 ) {
-
-  #find the urls for page X
-  webClick <- remDr$findElements(using = "css", ".action-btn")
-
-  webClick[[1]]$clickElement()
-
-  Sys.sleep(runif(1, 1, 5))
-}
-
-#find the urls for page X
-webElems <- remDr$findElements(using = "css", "a")
-
-#add the urls to a list
-urlslist_final = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-##deal with the URLS
-urlslist = urlslist_final
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("video/", urlslist))]
-urlslist = urlslist[grep("/news/", urlslist)]
-urlslist = urlslist[-c(grep("/201[3-7]", urlslist))]
-
-##start a data frame
-BLAZEDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(BLAZEDF) = c("Source", "Url", "Text")
-BLAZEDF = as.data.frame(BLAZEDF)
-int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data = html_nodes(webpage, '.post-date')
-  text_data = html_text(headline_data)
-  date = as.Date(text_data, "%B %d, %Y")
-
-  if (date %within% int){
-    headline_data2 = html_nodes(webpage,'h1, h3, p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    BLAZEDF$Source[i] = "BLAZE"
-    BLAZEDF$Url[i] = urlslist[i]
-    BLAZEDF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(BLAZEDF, "BLAZE_gs.csv", row.names = F)
-
-```
-
-```{r Hannity_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.hannity.com/trending/brett-kavanaugh/"
-
-remDr$navigate(url)
-
-urlslist_final = list()
-
-for (i in 1:4){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #move on to the next page
-  url = paste0("https://www.hannity.com/trending/brett-kavanaugh/?pg=", i+1)
-
-  remDr$navigate(url)
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-#also use google search to see if we can find more
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.google.com/search?q=kavanaugh+site%3Ahannity.com&source=lnt&tbs=cdr%3A1%2Ccd_min%3A9%2F13%2F2018%2Ccd_max%3A10%2F11%2F2018&tbm="
-
-remDr$navigate(url)
-
-urlslist_final2 = list()
-
-for (i in 1:3){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "link text", "Next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-urlslist2 = unlist(urlslist_final2)
-urlslist2 = c(urlslist, urlslist2)
-urlslist2 = unique(urlslist2)
-urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
-urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
-urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
-
-##start a data frame
-HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HANNITYDF) = c("Source", "Url", "Text")
-HANNITYDF = as.data.frame(HANNITYDF)
-int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data = html_nodes(webpage, '.author-info')
-  text_data = html_text(headline_data)
-  text_data = strsplit(text_data, " ")[[1]][7]
-  date = as.Date(text_data, "%m.%d.%y")
-
-  if (date %within% int){
-    headline_data2 = html_nodes(webpage,'h1, p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HANNITYDF$Source[i] = "HANNITY"
-    HANNITYDF$Url[i] = urlslist3[i]
-    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(HANNITYDF, "HANNITY_kav.csv", row.names = F)
-```
-
-```{r Hannity_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "http://www.hannity.com/trending/shutdown/"
-
-remDr$navigate(url)
-
-urlslist_final = list()
-
-for (i in 1:4){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #move on to the next page
-  url = paste0("http://www.hannity.com/trending/shutdown/?pg=", i+1)
-
-  remDr$navigate(url)
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-#also use google search to see if we can find more
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.google.com/search?biw=1366&bih=632&tbs=cdr%3A1%2Ccd_min%3A12%2F8%2F2018%2Ccd_max%3A2%2F8%2F2019&ei=gECaXNe8Aaft_Qb9w7G4BA&q=government+shutdown+site%3Ahannity.com&oq=government+shutdown+site%3Ahannity.com&gs_l=psy-ab.3...0.0..1915...0.0..0.0.0.......0......gws-wiz.aFps0nA33mY"
-
-remDr$navigate(url)
-
-urlslist_final2 = list()
-
-for (i in 1:9){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "link text", "Next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-urlslist2 = unlist(urlslist_final2)
-urlslist2 = c(urlslist, urlslist2)
-urlslist2 = unique(urlslist2)
-urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
-urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
-urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
-
-##start a data frame
-HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HANNITYDF) = c("Source", "Url", "Text")
-HANNITYDF = as.data.frame(HANNITYDF)
-int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data = html_nodes(webpage, '.author-info')
-  text_data = html_text(headline_data)
-  text_data = strsplit(text_data, " ")[[1]][7]
-  date = as.Date(text_data, "%m.%d.%y")
-
-  if (date %within% int){
-    headline_data2 = html_nodes(webpage,'h1, p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HANNITYDF$Source[i] = "HANNITY"
-    HANNITYDF$Url[i] = urlslist3[i]
-    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(HANNITYDF, "HANNITY_gs.csv", row.names = F)
-
-```
-
-## Sources
-
-Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
-news sources.
-As in Experiment 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by the highest proportion of consistent liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
-The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts, again written with the *papaja* library in *R*, are provided inline with this manuscript [@Aust2017].
-
-## Materials
-
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset [@Wickham2016].
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the partical U.S.
-Government shutdown of 2018-2019.
-The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
-
-```{r data_clean_kav, eval = T, echo = F}
-##combine all kav data into one dataset
-#read it in
-NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
-BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
-RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-
-#merge it together
-master_kav = rbind(NYtimes_kav, NPR_kav, SLATE_kav, 
-                        HUFFPO_kav, POLITICO_kav, FOX_kav, 
-                        BREITBART_kav, RUSH_kav, BLAZE_kav, 
-                        HANNITY_kav)
-
-#fix this issue
-master_kav$Text = gsub("\\.", "\\. ", master_kav$Text)
-
-##get rid of the blank stuff
-library(ngram)
-
-for (i in 1:nrow(master_kav)) {
-  master_kav$wordcount[i] = wordcount(master_kav$Text[i])
-}
-
-nozero = subset(master_kav, wordcount > 0)
-nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-tapply(nozero$wordcount, nozero$Source, mean)
-tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones - there are none
-#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##all data
-final_kav = nozero
-```
-
-```{r data_clean_gs, eval = T, echo = F}
-##combine all gs data into one dataset
-#read it in
-NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
-NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
-SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
-HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
-POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
-FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
-BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
-RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
-BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
-HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
-
-#merge it together
-master_gs = rbind(NYtimes_gs, NPR_gs, SLATE_gs, 
-                        HUFFPO_gs, POLITICO_gs, FOX_gs, 
-                        BREITBART_gs, RUSH_gs, BLAZE_gs, 
-                        HANNITY_gs)
-
-#fix this issue
-master_gs$Text = gsub("\\.", "\\. ", master_gs$Text)
-
-for (i in 1:nrow(master_gs)) {
-  master_gs$wordcount[i] = wordcount(master_gs$Text[i])
-}
-
-nozero = subset(master_gs, wordcount > 0)
-nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-
-tapply(nozero$wordcount, nozero$Source, mean)
-tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones
-#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##all data
-final_gs = nozero
-```
-
-```{r stem_text_both, eval = T, echo = F}
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final_kav)) {
-
-  final_kav$edited[i] = preprocess(final_kav$Text[i], #one value at a time
-           case = "lower", 
-           remove.punct = TRUE,
-           remove.numbers = FALSE, 
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final_kav$stemmed[i] = stemDocument(final_kav$edited[i], language = "english")
-}
-
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final_gs)) {
-
-  final_gs$edited[i] = preprocess(final_gs$Text[i], #one value at a time
-           case = "lower", 
-           remove.punct = TRUE,
-           remove.numbers = FALSE, 
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final_gs$stemmed[i] = stemDocument(final_gs$edited[i], language = "english")
-}
-
-```
-
-## Data analysis
-
-As in Experiment 1, the text was scanned with *ngram*.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed [@Schmidt2017].
-The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017].
-Words were subsequently matched with their valences from @Warriner2013.
-Depending on the results of @Jordan2019's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
-
-Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@Feinerer2017].
-Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).
-Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurence in the text.
-Once again, percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
-
-```{r create_datasets_harm_kav, eval = T, echo = F}
-#read in the harm total words from the mtmm project
-harm_all_kav = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all_kav$words[harm_all_kav$words != "" & harm_all_kav$words != "NA" & !is.na(harm_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-harm_final_data_kav = rbind(harm_final_data_kav, temp2)
-}
-
-#pull in the data from Warriner 
-harm_final_data_kav$valence = vlookup(harm_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(harm_final_data_kav$Var1[is.na(harm_final_data_kav$valence) & harm_final_data_kav$Freq > 0])
-#fought, safer, spurn
-harm_final_data_kav$valence[harm_final_data_kav$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data_kav$valence[harm_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all_kav$words[fair_all_kav$words != "" & fair_all_kav$words != "NA" & !is.na(fair_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-fair_final_data_kav = rbind(fair_final_data_kav, temp2)
-}
-
-fair_final_data_kav$valence = vlookup(fair_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data_kav$Var1[is.na(fair_final_data_kav$valence) & fair_final_data_kav$Freq > 0])
-#just plagiar safer
-fair_final_data_kav$valence[fair_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all_kav$words[ingroup_all_kav$words != "" & ingroup_all_kav$words != "NA" & !is.na(ingroup_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-ingroup_final_data_kav = rbind(ingroup_final_data_kav, temp2)
-}
-
-ingroup_final_data_kav$valence = vlookup(ingroup_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data_kav$Var1[is.na(ingroup_final_data_kav$valence) & ingroup_final_data_kav$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all_kav$words[authority_all_kav$words != "" & authority_all_kav$words != "NA" & !is.na(authority_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-authority_final_data_kav = rbind(authority_final_data_kav, temp2)
-}
-
-authority_final_data_kav$valence = vlookup(authority_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data_kav$Var1[is.na(authority_final_data_kav$valence) & authority_final_data_kav$Freq > 0])
-#  abov behind   gase higher  older  taken 
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all_kav$words[purity_all_kav$words != "" & purity_all_kav$words != "NA" & !is.na(purity_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-purity_final_data_kav = rbind(purity_final_data_kav, temp2)
-}
-
-purity_final_data_kav$valence = vlookup(purity_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data_kav$Var1[is.na(purity_final_data_kav$valence) & purity_final_data_kav$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women 
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r create_datasets_harm_gs, eval = T, echo = F}
-#read in the harm total words from the mtmm project
-harm_all_gs = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all_gs$words[harm_all_gs$words != "" & harm_all_gs$words != "NA" & !is.na(harm_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-harm_final_data_gs = rbind(harm_final_data_gs, temp2)
-}
-
-#pull in the data from Warriner 
-harm_final_data_gs$valence = vlookup(harm_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(harm_final_data_gs$Var1[is.na(harm_final_data_gs$valence) & harm_final_data_gs$Freq > 0])
-#fought, safer, spurn
-harm_final_data_gs$valence[harm_final_data_gs$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data_gs$valence[harm_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair_gs, include=FALSE}
-fair_all_gs = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all_gs$words[fair_all_gs$words != "" & fair_all_gs$words != "NA" & !is.na(fair_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-fair_final_data_gs = rbind(fair_final_data_gs, temp2)
-}
-
-fair_final_data_gs$valence = vlookup(fair_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data_gs$Var1[is.na(fair_final_data_gs$valence) & fair_final_data_gs$Freq > 0])
-#just plagiar safer
-fair_final_data_gs$valence[fair_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup_gs, include=FALSE}
-ingroup_all_gs = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all_gs$words[ingroup_all_gs$words != "" & ingroup_all_gs$words != "NA" & !is.na(ingroup_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-ingroup_final_data_gs = rbind(ingroup_final_data_gs, temp2)
-}
-
-ingroup_final_data_gs$valence = vlookup(ingroup_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data_gs$Var1[is.na(ingroup_final_data_gs$valence) & ingroup_final_data_gs$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority_gs, include=FALSE}
-authority_all_gs = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all_gs$words[authority_all_gs$words != "" & authority_all_gs$words != "NA" & !is.na(authority_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-authority_final_data_gs = rbind(authority_final_data_gs, temp2)
-}
-
-authority_final_data_gs$valence = vlookup(authority_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data_gs$Var1[is.na(authority_final_data_gs$valence) & authority_final_data_gs$Freq > 0])
-#  abov behind   gase higher  older  taken 
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity_gs, include=FALSE}
-purity_all_gs = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all_gs$words[purity_all_gs$words != "" & purity_all_gs$words != "NA" & !is.na(purity_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-purity_final_data_gs = rbind(purity_final_data_gs, temp2)
-}
-
-purity_final_data_gs$valence = vlookup(purity_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data_gs$Var1[is.na(purity_final_data_gs$valence) & purity_final_data_gs$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women 
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r descriptives_both, include = FALSE}
-##summarize the dataset so that you have the total and percent for each foundation
-#kav
-summary(harm_final_data_kav)
-summary(fair_final_data_kav)
-summary(ingroup_final_data_kav)
-summary(authority_final_data_kav)
-summary(purity_final_data_kav)
-#gs
-summary(harm_final_data_gs)
-summary(fair_final_data_gs)
-summary(ingroup_final_data_gs)
-summary(authority_final_data_gs)
-summary(purity_final_data_gs)
-##report descriptive statistics of the foundations
-#kav
-mean(harm_final_data_kav$valence, na.rm = T)
-sd(harm_final_data_kav$valence, na.rm = T)
-mean(fair_final_data_kav$valence, na.rm = T)
-sd(fair_final_data_kav$valence, na.rm = T)
-mean(ingroup_final_data_kav$valence, na.rm = T)
-sd(ingroup_final_data_kav$valence, na.rm = T)
-mean(authority_final_data_kav$valence, na.rm = T)
-sd(authority_final_data_kav$valence, na.rm = T)
-mean(purity_final_data_kav$valence, na.rm = T)
-sd(purity_final_data_kav$valence, na.rm = T)
-#gs
-mean(harm_final_data_gs$valence, na.rm = T)
-sd(harm_final_data_gs$valence, na.rm = T)
-mean(fair_final_data_gs$valence, na.rm = T)
-sd(fair_final_data_gs$valence, na.rm = T)
-mean(ingroup_final_data_gs$valence, na.rm = T)
-sd(ingroup_final_data_gs$valence, na.rm = T)
-mean(authority_final_data_gs$valence, na.rm = T)
-sd(authority_final_data_gs$valence, na.rm = T)
-mean(purity_final_data_gs$valence, na.rm = T)
-sd(purity_final_data_gs$valence, na.rm = T)
-#note that a big problem is the valence of the words 
-```
-
-```{r analysis_harm_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data_kav$weight = harm_final_data_kav$Freq * harm_final_data_kav$valence / harm_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-harm_final_temp_kav = aggregate(harm_final_data_kav$weight, 
-          by = list(harm_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp_kav) = c("URL", "MFDweight")
-
-harm_final_temp_kav$lean[grepl("nytimes.com", harm_final_temp_kav$URL) |
-                       grepl("npr.org", harm_final_temp_kav$URL) |
-                        grepl("slate.com", harm_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", harm_final_temp_kav$URL) |
-                        grepl("politico.com", harm_final_temp_kav$URL)] = "Liberal"
-
-harm_final_temp_kav$lean[grepl("breitbart.com", harm_final_temp_kav$URL) |
-                       grepl("foxnews.com", harm_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", harm_final_temp_kav$URL) |
-                       grepl("theblaze.com", harm_final_temp_kav$URL) |
-                       grepl("hannity.com", harm_final_temp_kav$URL)] = "Conservative"
-
-harm_final_temp_kav$Source[grepl("nytimes.com", harm_final_temp_kav$URL)] = "NY Times"
-harm_final_temp_kav$Source[grepl("npr.org", harm_final_temp_kav$URL)] = "NPR"
-harm_final_temp_kav$Source[grepl("slate.com", harm_final_temp_kav$URL)] = "Slate"
-harm_final_temp_kav$Source[grepl("huffingtonpost.com", harm_final_temp_kav$URL)] = "Huffington Post"
-harm_final_temp_kav$Source[grepl("politico.com", harm_final_temp_kav$URL)] = "Politico"
-harm_final_temp_kav$Source[grepl("foxnews.com", harm_final_temp_kav$URL)] = "Fox"
-harm_final_temp_kav$Source[grepl("breitbart.com", harm_final_temp_kav$URL)] = "Breitbart"
-harm_final_temp_kav$Source[grepl("rushlimbaugh.com", harm_final_temp_kav$URL)] = "Rush Limbaugh"
-harm_final_temp_kav$Source[grepl("theblaze.com", harm_final_temp_kav$URL)] = "The Blaze"
-harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
-harm_model_kav = lme(MFDweight ~ lean, 
-                 data = harm_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model_kav)
-r.squaredGLMM(harm_model_kav)
-```
-
-```{r analysis_fair_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data_kav$weight = fair_final_data_kav$Freq * fair_final_data_kav$valence / fair_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-fair_final_temp_kav = aggregate(fair_final_data_kav$weight, 
-          by = list(fair_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp_kav) = c("URL", "MFDweight")
-
-fair_final_temp_kav$lean[grepl("nytimes.com", fair_final_temp_kav$URL) |
-                       grepl("npr.org", fair_final_temp_kav$URL) |
-                        grepl("slate.com", fair_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", fair_final_temp_kav$URL) |
-                        grepl("politico.com", fair_final_temp_kav$URL)] = "Liberal"
-
-fair_final_temp_kav$lean[grepl("breitbart.com", fair_final_temp_kav$URL) |
-                       grepl("foxnews.com", fair_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", fair_final_temp_kav$URL) |
-                       grepl("theblaze.com", fair_final_temp_kav$URL) |
-                       grepl("hannity.com", fair_final_temp_kav$URL)] = "Conservative"
-
-fair_final_temp_kav$Source[grepl("nytimes.com", fair_final_temp_kav$URL)] = "NY Times"
-fair_final_temp_kav$Source[grepl("npr.org", fair_final_temp_kav$URL)] = "NPR"
-fair_final_temp_kav$Source[grepl("slate.com", fair_final_temp_kav$URL)] = "Slate"
-fair_final_temp_kav$Source[grepl("huffingtonpost.com", fair_final_temp_kav$URL)] = "Huffington Post"
-fair_final_temp_kav$Source[grepl("politico.com", fair_final_temp_kav$URL)] = "Politico"
-fair_final_temp_kav$Source[grepl("foxnews.com", fair_final_temp_kav$URL)] = "Fox"
-fair_final_temp_kav$Source[grepl("breitbart.com", fair_final_temp_kav$URL)] = "Breitbart"
-fair_final_temp_kav$Source[grepl("rushlimbaugh.com", fair_final_temp_kav$URL)] = "Rush Limbaugh"
-fair_final_temp_kav$Source[grepl("theblaze.com", fair_final_temp_kav$URL)] = "The Blaze"
-fair_final_temp_kav$Source[grepl("hannity.com", fair_final_temp_kav$URL)] = "Sean Hannity"
-fair_model_kav = lme(MFDweight ~ lean, 
-                 data = fair_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model_kav)
-```
-
-```{r analysis_ingroup_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data_kav$weight = ingroup_final_data_kav$Freq * ingroup_final_data_kav$valence / ingroup_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-ingroup_final_temp_kav = aggregate(ingroup_final_data_kav$weight, 
-          by = list(ingroup_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp_kav) = c("URL", "MFDweight")
-
-ingroup_final_temp_kav$lean[grepl("nytimes.com", ingroup_final_temp_kav$URL) |
-                       grepl("npr.org", ingroup_final_temp_kav$URL) |
-                        grepl("slate.com", ingroup_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", ingroup_final_temp_kav$URL) |
-                        grepl("politico.com", ingroup_final_temp_kav$URL)] = "Liberal"
-
-ingroup_final_temp_kav$lean[grepl("breitbart.com", ingroup_final_temp_kav$URL) |
-                       grepl("foxnews.com", ingroup_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL) |
-                       grepl("theblaze.com", ingroup_final_temp_kav$URL) |
-                       grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Conservative"
-
-ingroup_final_temp_kav$Source[grepl("nytimes.com", ingroup_final_temp_kav$URL)] = "NY Times"
-ingroup_final_temp_kav$Source[grepl("npr.org", ingroup_final_temp_kav$URL)] = "NPR"
-ingroup_final_temp_kav$Source[grepl("slate.com", ingroup_final_temp_kav$URL)] = "Slate"
-ingroup_final_temp_kav$Source[grepl("huffingtonpost.com", ingroup_final_temp_kav$URL)] = "Huffington Post"
-ingroup_final_temp_kav$Source[grepl("politico.com", ingroup_final_temp_kav$URL)] = "Politico"
-ingroup_final_temp_kav$Source[grepl("foxnews.com", ingroup_final_temp_kav$URL)] = "Fox"
-ingroup_final_temp_kav$Source[grepl("breitbart.com", ingroup_final_temp_kav$URL)] = "Breitbart"
-ingroup_final_temp_kav$Source[grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL)] = "Rush Limbaugh"
-ingroup_final_temp_kav$Source[grepl("theblaze.com", ingroup_final_temp_kav$URL)] = "The Blaze"
-ingroup_final_temp_kav$Source[grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Sean Hannity"
-ingroup_model_kav = lme(MFDweight ~ lean, 
-                 data = ingroup_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model_kav)
-```
-
-```{r analysis_authority_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data_kav$weight = authority_final_data_kav$Freq * authority_final_data_kav$valence / authority_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-authority_final_temp_kav = aggregate(authority_final_data_kav$weight, 
-          by = list(authority_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp_kav) = c("URL", "MFDweight")
-
-authority_final_temp_kav$lean[grepl("nytimes.com", authority_final_temp_kav$URL) |
-                       grepl("npr.org", authority_final_temp_kav$URL) |
-                        grepl("slate.com", authority_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", authority_final_temp_kav$URL) |
-                        grepl("politico.com", authority_final_temp_kav$URL)] = "Liberal"
-
-authority_final_temp_kav$lean[grepl("breitbart.com", authority_final_temp_kav$URL) |
-                       grepl("foxnews.com", authority_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", authority_final_temp_kav$URL) |
-                       grepl("theblaze.com", authority_final_temp_kav$URL) |
-                       grepl("hannity.com", authority_final_temp_kav$URL)] = "Conservative"
-
-authority_final_temp_kav$Source[grepl("nytimes.com", authority_final_temp_kav$URL)] = "NY Times"
-authority_final_temp_kav$Source[grepl("npr.org", authority_final_temp_kav$URL)] = "NPR"
-authority_final_temp_kav$Source[grepl("slate.com", authority_final_temp_kav$URL)] = "Slate"
-authority_final_temp_kav$Source[grepl("huffingtonpost.com", authority_final_temp_kav$URL)] = "Huffington Post"
-authority_final_temp_kav$Source[grepl("politico.com", authority_final_temp_kav$URL)] = "Politico"
-authority_final_temp_kav$Source[grepl("foxnews.com", authority_final_temp_kav$URL)] = "Fox"
-authority_final_temp_kav$Source[grepl("breitbart.com", authority_final_temp_kav$URL)] = "Breitbart"
-authority_final_temp_kav$Source[grepl("rushlimbaugh.com", authority_final_temp_kav$URL)] = "Rush Limbaugh"
-authority_final_temp_kav$Source[grepl("theblaze.com", authority_final_temp_kav$URL)] = "The Blaze"
-authority_final_temp_kav$Source[grepl("hannity.com", authority_final_temp_kav$URL)] = "Sean Hannity"
-authority_model_kav = lme(MFDweight ~ lean, 
-                 data = authority_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model_kav)
-```
-
-```{r analysis_purity_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data_kav$weight = purity_final_data_kav$Freq * purity_final_data_kav$valence / purity_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-purity_final_temp_kav = aggregate(purity_final_data_kav$weight, 
-          by = list(purity_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp_kav) = c("URL", "MFDweight")
-
-purity_final_temp_kav$lean[grepl("nytimes.com", purity_final_temp_kav$URL) |
-                       grepl("npr.org", purity_final_temp_kav$URL) |
-                        grepl("slate.com", purity_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", purity_final_temp_kav$URL) |
-                        grepl("politico.com", purity_final_temp_kav$URL)] = "Liberal"
-
-purity_final_temp_kav$lean[grepl("breitbart.com", purity_final_temp_kav$URL) |
-                       grepl("foxnews.com", purity_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", purity_final_temp_kav$URL) |
-                       grepl("theblaze.com", purity_final_temp_kav$URL) |
-                       grepl("hannity.com", purity_final_temp_kav$URL)] = "Conservative"
-
-purity_final_temp_kav$Source[grepl("nytimes.com", purity_final_temp_kav$URL)] = "NY Times"
-purity_final_temp_kav$Source[grepl("npr.org", purity_final_temp_kav$URL)] = "NPR"
-purity_final_temp_kav$Source[grepl("slate.com", purity_final_temp_kav$URL)] = "Slate"
-purity_final_temp_kav$Source[grepl("huffingtonpost.com", purity_final_temp_kav$URL)] = "Huffington Post"
-purity_final_temp_kav$Source[grepl("politico.com", purity_final_temp_kav$URL)] = "Politico"
-purity_final_temp_kav$Source[grepl("foxnews.com", purity_final_temp_kav$URL)] = "Fox"
-purity_final_temp_kav$Source[grepl("breitbart.com", purity_final_temp_kav$URL)] = "Breitbart"
-purity_final_temp_kav$Source[grepl("rushlimbaugh.com", purity_final_temp_kav$URL)] = "Rush Limbaugh"
-purity_final_temp_kav$Source[grepl("theblaze.com", purity_final_temp_kav$URL)] = "The Blaze"
-purity_final_temp_kav$Source[grepl("hannity.com", purity_final_temp_kav$URL)] = "Sean Hannity"
-purity_model_kav = lme(MFDweight ~ lean, 
-                 data = purity_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model_kav)
-```
-
-```{r analysis_harm_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data_gs$weight = harm_final_data_gs$Freq * harm_final_data_gs$valence / harm_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-harm_final_temp_gs = aggregate(harm_final_data_gs$weight, 
-          by = list(harm_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp_gs) = c("URL", "MFDweight")
-
-harm_final_temp_gs$lean[grepl("nytimes.com", harm_final_temp_gs$URL) |
-                       grepl("npr.org", harm_final_temp_gs$URL) |
-                        grepl("slate.com", harm_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", harm_final_temp_gs$URL) |
-                        grepl("politico.com", harm_final_temp_gs$URL)] = "Liberal"
-
-harm_final_temp_gs$lean[grepl("breitbart.com", harm_final_temp_gs$URL) |
-                       grepl("foxnews.com", harm_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", harm_final_temp_gs$URL) |
-                       grepl("theblaze.com", harm_final_temp_gs$URL) |
-                       grepl("hannity.com", harm_final_temp_gs$URL)] = "Conservative"
-
-harm_final_temp_gs$Source[grepl("nytimes.com", harm_final_temp_gs$URL)] = "NY Times"
-harm_final_temp_gs$Source[grepl("npr.org", harm_final_temp_gs$URL)] = "NPR"
-harm_final_temp_gs$Source[grepl("slate.com", harm_final_temp_gs$URL)] = "Slate"
-harm_final_temp_gs$Source[grepl("huffingtonpost.com", harm_final_temp_gs$URL)] = "Huffington Post"
-harm_final_temp_gs$Source[grepl("politico.com", harm_final_temp_gs$URL)] = "Politico"
-harm_final_temp_gs$Source[grepl("foxnews.com", harm_final_temp_gs$URL)] = "Fox"
-harm_final_temp_gs$Source[grepl("breitbart.com", harm_final_temp_gs$URL)] = "Breitbart"
-harm_final_temp_gs$Source[grepl("rushlimbaugh.com", harm_final_temp_gs$URL)] = "Rush Limbaugh"
-harm_final_temp_gs$Source[grepl("theblaze.com", harm_final_temp_gs$URL)] = "The Blaze"
-harm_final_temp_gs$Source[grepl("hannity.com", harm_final_temp_gs$URL)] = "Sean Hannity"
-harm_model_gs = lme(MFDweight ~ lean, 
-                 data = harm_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model_gs)
-```
-
-```{r analysis_fair_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data_gs$weight = fair_final_data_gs$Freq * fair_final_data_gs$valence / fair_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-fair_final_temp_gs = aggregate(fair_final_data_gs$weight, 
-          by = list(fair_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp_gs) = c("URL", "MFDweight")
-
-fair_final_temp_gs$lean[grepl("nytimes.com", fair_final_temp_gs$URL) |
-                       grepl("npr.org", fair_final_temp_gs$URL) |
-                        grepl("slate.com", fair_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", fair_final_temp_gs$URL) |
-                        grepl("politico.com", fair_final_temp_gs$URL)] = "Liberal"
-
-fair_final_temp_gs$lean[grepl("breitbart.com", fair_final_temp_gs$URL) |
-                       grepl("foxnews.com", fair_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", fair_final_temp_gs$URL) |
-                       grepl("theblaze.com", fair_final_temp_gs$URL) |
-                       grepl("hannity.com", fair_final_temp_gs$URL)] = "Conservative"
-
-fair_final_temp_gs$Source[grepl("nytimes.com", fair_final_temp_gs$URL)] = "NY Times"
-fair_final_temp_gs$Source[grepl("npr.org", fair_final_temp_gs$URL)] = "NPR"
-fair_final_temp_gs$Source[grepl("slate.com", fair_final_temp_gs$URL)] = "Slate"
-fair_final_temp_gs$Source[grepl("huffingtonpost.com", fair_final_temp_gs$URL)] = "Huffington Post"
-fair_final_temp_gs$Source[grepl("politico.com", fair_final_temp_gs$URL)] = "Politico"
-fair_final_temp_gs$Source[grepl("foxnews.com", fair_final_temp_gs$URL)] = "Fox"
-fair_final_temp_gs$Source[grepl("breitbart.com", fair_final_temp_gs$URL)] = "Breitbart"
-fair_final_temp_gs$Source[grepl("rushlimbaugh.com", fair_final_temp_gs$URL)] = "Rush Limbaugh"
-fair_final_temp_gs$Source[grepl("theblaze.com", fair_final_temp_gs$URL)] = "The Blaze"
-fair_final_temp_gs$Source[grepl("hannity.com", fair_final_temp_gs$URL)] = "Sean Hannity"
-fair_model_gs = lme(MFDweight ~ lean, 
-                 data = fair_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model_gs)
-```
-
-```{r analysis_ingroup_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data_gs$weight = ingroup_final_data_gs$Freq * ingroup_final_data_gs$valence / ingroup_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-ingroup_final_temp_gs = aggregate(ingroup_final_data_gs$weight, 
-          by = list(ingroup_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp_gs) = c("URL", "MFDweight")
-
-ingroup_final_temp_gs$lean[grepl("nytimes.com", ingroup_final_temp_gs$URL) |
-                       grepl("npr.org", ingroup_final_temp_gs$URL) |
-                        grepl("slate.com", ingroup_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", ingroup_final_temp_gs$URL) |
-                        grepl("politico.com", ingroup_final_temp_gs$URL)] = "Liberal"
-
-ingroup_final_temp_gs$lean[grepl("breitbart.com", ingroup_final_temp_gs$URL) |
-                       grepl("foxnews.com", ingroup_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL) |
-                       grepl("theblaze.com", ingroup_final_temp_gs$URL) |
-                       grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Conservative"
-
-ingroup_final_temp_gs$Source[grepl("nytimes.com", ingroup_final_temp_gs$URL)] = "NY Times"
-ingroup_final_temp_gs$Source[grepl("npr.org", ingroup_final_temp_gs$URL)] = "NPR"
-ingroup_final_temp_gs$Source[grepl("slate.com", ingroup_final_temp_gs$URL)] = "Slate"
-ingroup_final_temp_gs$Source[grepl("huffingtonpost.com", ingroup_final_temp_gs$URL)] = "Huffington Post"
-ingroup_final_temp_gs$Source[grepl("politico.com", ingroup_final_temp_gs$URL)] = "Politico"
-ingroup_final_temp_gs$Source[grepl("foxnews.com", ingroup_final_temp_gs$URL)] = "Fox"
-ingroup_final_temp_gs$Source[grepl("breitbart.com", ingroup_final_temp_gs$URL)] = "Breitbart"
-ingroup_final_temp_gs$Source[grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL)] = "Rush Limbaugh"
-ingroup_final_temp_gs$Source[grepl("theblaze.com", ingroup_final_temp_gs$URL)] = "The Blaze"
-ingroup_final_temp_gs$Source[grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Sean Hannity"
-ingroup_model_gs = lme(MFDweight ~ lean, 
-                 data = ingroup_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model_gs)
-```
-
-```{r analysis_authority_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data_gs$weight = authority_final_data_gs$Freq * authority_final_data_gs$valence / authority_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-authority_final_temp_gs = aggregate(authority_final_data_gs$weight, 
-          by = list(authority_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp_gs) = c("URL", "MFDweight")
-
-authority_final_temp_gs$lean[grepl("nytimes.com", authority_final_temp_gs$URL) |
-                       grepl("npr.org", authority_final_temp_gs$URL) |
-                        grepl("slate.com", authority_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", authority_final_temp_gs$URL) |
-                        grepl("politico.com", authority_final_temp_gs$URL)] = "Liberal"
-
-authority_final_temp_gs$lean[grepl("breitbart.com", authority_final_temp_gs$URL) |
-                       grepl("foxnews.com", authority_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", authority_final_temp_gs$URL) |
-                       grepl("theblaze.com", authority_final_temp_gs$URL) |
-                       grepl("hannity.com", authority_final_temp_gs$URL)] = "Conservative"
-
-authority_final_temp_gs$Source[grepl("nytimes.com", authority_final_temp_gs$URL)] = "NY Times"
-authority_final_temp_gs$Source[grepl("npr.org", authority_final_temp_gs$URL)] = "NPR"
-authority_final_temp_gs$Source[grepl("slate.com", authority_final_temp_gs$URL)] = "Slate"
-authority_final_temp_gs$Source[grepl("huffingtonpost.com", authority_final_temp_gs$URL)] = "Huffington Post"
-authority_final_temp_gs$Source[grepl("politico.com", authority_final_temp_gs$URL)] = "Politico"
-authority_final_temp_gs$Source[grepl("foxnews.com", authority_final_temp_gs$URL)] = "Fox"
-authority_final_temp_gs$Source[grepl("breitbart.com", authority_final_temp_gs$URL)] = "Breitbart"
-authority_final_temp_gs$Source[grepl("rushlimbaugh.com", authority_final_temp_gs$URL)] = "Rush Limbaugh"
-authority_final_temp_gs$Source[grepl("theblaze.com", authority_final_temp_gs$URL)] = "The Blaze"
-authority_final_temp_gs$Source[grepl("hannity.com", authority_final_temp_gs$URL)] = "Sean Hannity"
-authority_model_gs = lme(MFDweight ~ lean, 
-                 data = authority_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model_gs)
-```
-
-```{r analysis_purity_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data_gs$weight = purity_final_data_gs$Freq * purity_final_data_gs$valence / purity_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-purity_final_temp_gs = aggregate(purity_final_data_gs$weight, 
-          by = list(purity_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp_gs) = c("URL", "MFDweight")
-
-purity_final_temp_gs$lean[grepl("nytimes.com", purity_final_temp_gs$URL) |
-                       grepl("npr.org", purity_final_temp_gs$URL) |
-                        grepl("slate.com", purity_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", purity_final_temp_gs$URL) |
-                        grepl("politico.com", purity_final_temp_gs$URL)] = "Liberal"
-
-purity_final_temp_gs$lean[grepl("breitbart.com", purity_final_temp_gs$URL) |
-                       grepl("foxnews.com", purity_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", purity_final_temp_gs$URL) |
-                       grepl("theblaze.com", purity_final_temp_gs$URL) |
-                       grepl("hannity.com", purity_final_temp_gs$URL)] = "Conservative"
-
-purity_final_temp_gs$Source[grepl("nytimes.com", purity_final_temp_gs$URL)] = "NY Times"
-purity_final_temp_gs$Source[grepl("npr.org", purity_final_temp_gs$URL)] = "NPR"
-purity_final_temp_gs$Source[grepl("slate.com", purity_final_temp_gs$URL)] = "Slate"
-purity_final_temp_gs$Source[grepl("huffingtonpost.com", purity_final_temp_gs$URL)] = "Huffington Post"
-purity_final_temp_gs$Source[grepl("politico.com", purity_final_temp_gs$URL)] = "Politico"
-purity_final_temp_gs$Source[grepl("foxnews.com", purity_final_temp_gs$URL)] = "Fox"
-purity_final_temp_gs$Source[grepl("breitbart.com", purity_final_temp_gs$URL)] = "Breitbart"
-purity_final_temp_gs$Source[grepl("rushlimbaugh.com", purity_final_temp_gs$URL)] = "Rush Limbaugh"
-purity_final_temp_gs$Source[grepl("theblaze.com", purity_final_temp_gs$URL)] = "The Blaze"
-purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
-purity_model_gs = lme(MFDweight ~ lean, 
-                 data = purity_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model_gs)
-```
-
-# Experiment 2
-
-## Results
-
-## Descriptive Statistics
-
-The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Experiment 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
-
-Table 3 displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
-The sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
-*The New York Times* published the greatest number of articles as well as total words.
-*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
-Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
-This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
-Table 4 displays descriptive statistics for articles about the partial government shutdown.
-
-```{r exp2sourcedescriptiveskav, results = 'asis', echo = FALSE, message = F}
-#Kav
-final_kav$uniquewords = NA
-final_kav$valenceavg = NA
-
-for (i in 1:nrow(final_kav)){
-
-  #add unique
-  final_kav$uniquewords[i] = length(unique(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-  #add valence
-  tempwords_kav = as.data.frame(unlist(strsplit(final_kav$stemmed[i], " ")))
-  colnames(tempwords_kav) = "theword"
-  tempwords_kav$tempval = vlookup(tempwords_kav$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
-
-}
-
-tapply(final_kav$valenceavg, final_kav$Source, mean)
-tapply(final_kav$valenceavg, final_kav$Source, sd)
-tapply(final_kav$wordcount, final_kav$Source, mean)
-tapply(final_kav$wordcount, final_kav$Source, sd)
-tapply(final_kav$uniquewords, final_kav$Source, mean)
-tapply(final_kav$uniquewords, final_kav$Source, sd)
-tapply(final_kav$Source, final_kav$Source, length)
-tapply(final_kav$wordcount, final_kav$Source, sum)
-
-library(quanteda)
-
-final_kav$FK = NA
-
-for (i in 1:nrow(final_kav)){
-  final_kav$FK[i] = unlist(textstat_readability(final_kav$Text[i], 
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-tapply(final_kav$FK, final_kav$Source, mean)
-tapply(final_kav$FK, final_kav$Source, sd)
-
-#Kav Table
-####build the table here####
-tableprint = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-tableprint[ , 1] = unique(final_kav$Source)
-tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean)
-tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd)
-tableprint[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
-tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum)
-tableprint[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean)
-tableprint[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
-tableprint[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean)
-tableprint[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd)
-tableprint[ , 10] = tapply(final_kav$FK, final_kav$Source, mean)
-tableprint[ , 11] = tapply(final_kav$FK, final_kav$Source, sd)
-
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          #caption = "Kavanaugh - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 6))
-          )
-```
-
-```{r exp2sourcedescriptivesgs, results = 'asis', echo = FALSE, message = F}
-#Kav
-#GS
-final_gs$uniquewords = NA
-final_gs$valenceavg = NA
-
-for (i in 1:nrow(final_gs)){
-
-  #add unique
-  final_gs$uniquewords[i] = length(unique(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-  #add valence
-  tempwords_gs = as.data.frame(unlist(strsplit(final_gs$stemmed[i], " ")))
-  colnames(tempwords_gs) = "theword"
-  tempwords_gs$tempval = vlookup(tempwords_gs$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final_gs$valenceavg[i] = mean(tempwords_gs$tempval, na.rm = T)
-
-}
-
-tapply(final_gs$valenceavg, final_gs$Source, mean)
-tapply(final_gs$valenceavg, final_gs$Source, sd)
-tapply(final_gs$wordcount, final_gs$Source, mean)
-tapply(final_gs$wordcount, final_gs$Source, sd)
-tapply(final_gs$uniquewords, final_gs$Source, mean)
-tapply(final_gs$uniquewords, final_gs$Source, sd)
-tapply(final_gs$Source, final_gs$Source, length)
-tapply(final_gs$wordcount, final_gs$Source, sum)
-
-library(quanteda)
-
-final_gs$FK = NA
-
-for (i in 1:nrow(final_gs)){
-  final_gs$FK[i] = unlist(textstat_readability(final_gs$Text[i], 
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-tapply(final_gs$FK, final_gs$Source, mean)
-tapply(final_gs$FK, final_gs$Source, sd)
-
-#GS Table
-####build the table here####
-tableprint = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-tableprint[ , 1] = unique(final_gs$Source)
-tableprint[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
-tableprint[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
-tableprint[ , 4] = tapply(final_gs$valenceavg, final_gs$Source, length)
-tableprint[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
-tableprint[ , 6] = tapply(final_gs$wordcount, final_gs$Source, mean)
-tableprint[ , 7] = tapply(final_gs$wordcount, final_gs$Source, sd)
-tableprint[ , 8] = tapply(final_gs$uniquewords, final_gs$Source, mean)
-tableprint[ , 9] = tapply(final_gs$uniquewords, final_gs$Source, sd)
-tableprint[ , 10] = tapply(final_gs$FK, final_gs$Source, mean)
-tableprint[ , 11] = tapply(final_gs$FK, final_gs$Source, sd)
-
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          #caption = "Government Shutdown - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 6))
-          )
-```
-
-```{r exp2-tablekav, results = 'asis', echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint_kav = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
-
-#calculate d
-#harm
-harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d_kav = d.ind.t(m1 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d_kav = d.ind.t(m1 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d_kav = d.ind.t(m1 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d_kav = d.ind.t(m1 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1, 
-                    summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
-                    harm_d_kav$d)
-tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1, 
-                    summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
-                    fair_d_kav$d)
-tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1, 
-                    summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
-                    ingroup_d_kav$d)
-tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1, 
-                    summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
-                    authority_d_kav$d)
-tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1, 
-                    summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
-                    purity_d_kav$d)
-
-tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]))
-tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
-
-apa_table(tableprint_kav,
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          #caption = "Kavanaugh Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7))
-          )
-```
-
-```{r exp2-tablegs, results = 'asis', echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint_gs = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
-
-#calculate d
-#harm
-harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d_gs = d.ind.t(m1 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d_gs = d.ind.t(m1 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d_gs = d.ind.t(m1 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d_gs = d.ind.t(m1 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1, 
-                    summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
-                    harm_d_gs$d)
-tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1, 
-                    summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
-                    fair_d_gs$d)
-tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1, 
-                    summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
-                    ingroup_d_gs$d)
-tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1, 
-                    summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
-                    authority_d_gs$d)
-tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1, 
-                    summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
-                    purity_d_gs$d)
-
-tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]))
-tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
-
-apa_table(tableprint_gs,
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          #caption = "Government Shutdown Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7))
-          )
-```
-
-```{r conference-pic_kav, eval = F, include = F}
-library(ggplot2)
-library(reshape)
-
-cleanup = theme(panel.grid.major = element_blank(), 
-                panel.grid.minor = element_blank(), 
-                panel.background = element_blank(), 
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 10))
-
-graphdata_kav = as.data.frame(tableprint_kav)
-graphlong_kav = melt(graphdata_kav[ , c(1,2,4)], 
-                 id = "Foundation")
-graphlong2_kav = melt(graphdata_kav[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong_kav$sd = graphlong2_kav$value
-graphlong_kav$lower = as.numeric(as.character(graphlong_kav$value)) - 2*as.numeric(as.character(graphlong_kav$sd))
-graphlong_kav$upper = as.numeric(as.character(graphlong_kav$value)) + 2*as.numeric(as.character(graphlong_kav$sd))
-
-graphlong_kav$value = as.numeric(as.character(graphlong_kav$value))
-
-graph_data_kav = ggplot(graphlong_kav, aes(Foundation, value, color = variable)) + 
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), 
-                position = position_dodge(width = 0.90),
-                width = .2) + 
-  cleanup +
-  ylab("Mean Weighted Valence") + 
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-#tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
-#     height = 3, units = 'in', compression = "lzw")
-#plot(graph_data_kav)
-#dev.off()
-```
-
-```{r conference-pic_gs, eval = F, include = F}
-graphdata_gs = as.data.frame(tableprint_gs)
-graphlong_gs = melt(graphdata_gs[ , c(1,2,4)], 
-                 id = "Foundation")
-graphlong2_gs = melt(graphdata_gs[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong_gs$sd = graphlong2_gs$value
-graphlong_gs$lower = as.numeric(as.character(graphlong_gs$value)) - 2*as.numeric(as.character(graphlong_gs$sd))
-graphlong_gs$upper = as.numeric(as.character(graphlong_gs$value)) + 2*as.numeric(as.character(graphlong_gs$sd))
-
-graphlong_gs$value = as.numeric(as.character(graphlong_gs$value))
-
-graph_data_gs = ggplot(graphlong_gs, aes(Foundation, value, color = variable)) + 
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), 
-                position = position_dodge(width = 0.90),
-                width = .2) + 
-  cleanup +
-  ylab("Mean Weighted Valence") + 
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-#tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
-#     height = 3, units = 'in', compression = "lzw")
-#plot(graph_data_gs)
-#dev.off()
-```
+          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"))
+```
+
+# Results
 

### 2019-04-13 pilot_manuscript.Rmd
LOOK AT THIS SHIT

@@
 
-```{r exp1sourcedescriptives, results = 'asis', echo = FALSE, message = F}
+```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}
 
@@
 
+tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+
 #change this to match
 apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          #caption = "Experiment 1 - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
+          caption = "Experiment 1 - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
           format = "latex",
@@
           )
-
 ```
@@
 
-As seen in Table 1, the sources are similar in some aspects yet different in others.
+As seen in Table \@ref(tab:exp1-source-descriptives), the sources are similar in some aspects yet different in others.
 Valence appears to be slightly positive across all sources.
@@
 The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table 2.
+Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp1-table).
 To interpret the weighted scores, one can examine the mean and standard deviations for each.
@@
 
-Table 3 displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
+Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
 The sources are similar in some aspects yet different in others.
@@
 As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
-Table 4 displays descriptive statistics for articles about the partial government shutdown.
-
-```{r exp2sourcedescriptiveskav, results = 'asis', echo = FALSE, message = F}
+Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive statistics for articles about the partial government shutdown.
+
+```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
 #Kav
@@
 
-tapply(final_kav$valenceavg, final_kav$Source, mean)
-tapply(final_kav$valenceavg, final_kav$Source, sd)
-tapply(final_kav$wordcount, final_kav$Source, mean)
-tapply(final_kav$wordcount, final_kav$Source, sd)
-tapply(final_kav$uniquewords, final_kav$Source, mean)
-tapply(final_kav$uniquewords, final_kav$Source, sd)
-tapply(final_kav$Source, final_kav$Source, length)
-tapply(final_kav$wordcount, final_kav$Source, sum)
+# tapply(final_kav$valenceavg, final_kav$Source, mean)
+# tapply(final_kav$valenceavg, final_kav$Source, sd)
+# tapply(final_kav$wordcount, final_kav$Source, mean)
+# tapply(final_kav$wordcount, final_kav$Source, sd)
+# tapply(final_kav$uniquewords, final_kav$Source, mean)
+# tapply(final_kav$uniquewords, final_kav$Source, sd)
+# tapply(final_kav$Source, final_kav$Source, length)
+# tapply(final_kav$wordcount, final_kav$Source, sum)
 
@@
 
+tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+
 #change this to match
 apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          #caption = "Kavanaugh - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
+          caption = "Kavanaugh - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
           format = "latex",
@@
 
-```{r exp2sourcedescriptivesgs, results = 'asis', echo = FALSE, message = F}
+```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
 #Kav
@@
 
-tapply(final_gs$valenceavg, final_gs$Source, mean)
-tapply(final_gs$valenceavg, final_gs$Source, sd)
-tapply(final_gs$wordcount, final_gs$Source, mean)
-tapply(final_gs$wordcount, final_gs$Source, sd)
-tapply(final_gs$uniquewords, final_gs$Source, mean)
-tapply(final_gs$uniquewords, final_gs$Source, sd)
-tapply(final_gs$Source, final_gs$Source, length)
-tapply(final_gs$wordcount, final_gs$Source, sum)
+# tapply(final_gs$valenceavg, final_gs$Source, mean)
+# tapply(final_gs$valenceavg, final_gs$Source, sd)
+# tapply(final_gs$wordcount, final_gs$Source, mean)
+# tapply(final_gs$wordcount, final_gs$Source, sd)
+# tapply(final_gs$uniquewords, final_gs$Source, mean)
+# tapply(final_gs$uniquewords, final_gs$Source, sd)
+# tapply(final_gs$Source, final_gs$Source, length)
+# tapply(final_gs$wordcount, final_gs$Source, sum)
 
@@
 
+tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+
 #change this to match
 apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
-          #caption = "Government Shutdown - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
+          caption = "Government Shutdown - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
           format = "latex",

### 2019-04-13 pilot_manuscript_erin_test.tex
LOOK AT THIS SHIT

--- 2019-02-11 pilot_manuscript.tex
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error (Gelman, 2006).
-Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 1.
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
+Breitbart Fox News NPR NY Times
+18.41894 16.92098 13.80370 16.32188
+Breitbart Fox News NPR NY Times
+8.011796 7.159823 3.928992 3.290628
 
@@
 \begin{threeparttable}
-\caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
-\begin{tabular}{lccccccc}
+\caption{\label{tab:temp}Experiment 1 - Descriptive Statistics by Source}
+\small{
+\begin{tabular}{lllllllllll}
 \toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
 \midrule
-Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .850 & 0.01\\
-Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .715 & 0.02\\
-Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .789 & -0.04\\
-Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.17 & .087 & -0.20\\
-Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.37 & .141 & -0.09\\
+NY Times & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.36 & 120.76 & 18.42 & 8.01\\
+NPR & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.57 & 189.00 & 16.92 & 7.16\\
+Fox News & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.29 & 13.80 & 3.93\\
+Breitbart & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.32 & 3.29\\
 \bottomrule
@@
 \end{tabular}
+}
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
 \end{tablenotes}
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
-
-The results obtained in Experiment 1 did not confirm the hypothesis.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The strongest effect found was for the \emph{authority/respect} foundation owing to the fact its Cohen's \emph{d} value was greater than the other four foundations.
-However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
-This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
-It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
-
-Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
-The selection of the broad and amorphous topic of \enquote{political news} may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
-In short, the range of topics covered in Experiment 1 was likely too broad.
-The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
-
-Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-Generally speaking, the researchers believe their methodology to be sound.
-Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
-Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
-The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurence.
-
-While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
-The researchers identified two such changes that were subsequently employed in Experiment 2.
-First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
-politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court.
-In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
-
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
-
-\hypertarget{kavanaugh-supreme-court-hearing}{%
-\subsection{Kavanaugh Supreme Court Hearing}\label{kavanaugh-supreme-court-hearing}}
-
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 (US Government, 2018a).
-Following allegations of sexual assault by high school classmate Dr.~Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
-
-On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh (US Government, 2018b).
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television (O'Connell, 2018).
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 (US Government, 2018c).
-
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
-
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on the Kavanaugh confirmation hearing.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages during the two weeks before and two weeks after Kavanaugh's confirmation, owing to its prominence in the news.
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-
-\hypertarget{method-1}{%
-\section{Method}\label{method-1}}
-
-\hypertarget{sources-1}{%
-\subsection{Sources}\label{sources-1}}
-
-Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
-news sources.
-These sources were selected owing to their favorability among political partisans according to Mitchell et al.
-(2014).
-The sources favored by liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
-The sources favored by conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts, again written with the \emph{papaja} library in \emph{R}, are provided inline with this manuscript (Aust \& Barth, 2017).
-
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
-
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset (Wickham, 2016).
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-\hypertarget{data-analysis-1}{%
-\subsection{Data analysis}\label{data-analysis-1}}
-
-As in Experiment 1, the text was scanned with \emph{ngram}.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed (Schmidt et al., 2017).
-The text was processed and stemmed in order to convert to a usable form for further analysis (Feinerer \& Hornik, 2017).
-Words were subsequently matched with their valences from Warriner et al.
-(2013).
-Depending on the results of Jordan et al.
-(2019)'s research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
-
-Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
-Each individual word was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}).
-Once again, the same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurence in the text.
-Once again, percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
-
-\hypertarget{experiment-2-1}{%
-\section{Experiment 2}\label{experiment-2-1}}
-
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
 
@@
 
+\leavevmode\hypertarget{ref-Davies2014}{}%
+Davies, C.
+L., Sibley, C.
+G., \& Liu, J.
+H.
+(2014).
+Confirmatory factor analysis of the moral foundations questionnaire independent scale validation in a new zealand sample.
+\emph{Social Psychology}, \emph{45}(6), 431--436.
+doi:\href{https://doi.org/10.1027/1864-9335/a000201}{10.1027/1864-9335/a000201}
+
 \leavevmode\hypertarget{ref-Druckman2004}{}%
@@
 Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from \url{http://tm.r-forge.r-project.org/}
-
-\leavevmode\hypertarget{ref-Gelman2006}{}%
-Gelman, A.
-(2006).
-Multilevel (hierarchical) modeling: What it can and cannot do.
-\emph{Technometrics}, \emph{48}(3), 432--435.
-doi:\href{https://doi.org/10.1198/004017005000000661}{10.1198/004017005000000661}
 
@@
 
-\leavevmode\hypertarget{ref-OConnell2018}{}%
-O'Connell, M.
-(2018).
-Ford-Kavanaugh Ratings: Hearing Brings 20 Million viewers to cable and broadcast \textbar{} Hollywood Reporter.
-Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
-
 \leavevmode\hypertarget{ref-Pashler2012}{}%
@@
 
-\leavevmode\hypertarget{ref-Pinheiro2017}{}%
-Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). nlme: Linear and nonlinear mixed effects models. Retrieved from \url{https://cran.r-project.org/package=nlme}
-
 \leavevmode\hypertarget{ref-Schmidt2017}{}%
@@
 
-\leavevmode\hypertarget{ref-USGovernment2018b}{}%
-US Government. (2018a). Congressional Record. \emph{Congressional Record}, \emph{164}(146), 46. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-USGovernment2018}{}%
-US Government. (2018b). Congressional Record. \emph{Congressional Record}, \emph{164}(160), 93. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-USGovernment2018a}{}%
-US Government. (2018c). Congressional Record. \emph{Congressional Record}, \emph{164}(167), 14. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+\leavevmode\hypertarget{ref-Suhler2011}{}%
+Suhler, C.
+L., Churchland, P., Joseph, C., Graham, J., \& Nosek, B.
+(2011).
+Can Innate , Modular `` Foundations '' Explain Morality ?
+Challenges for Haidt ' s Moral Foundations Theory.
+\emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
 

### 2019-04-14 pilot_manuscript.Rmd
Just started Conclusion. More to come...

@@
 
-Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
-The sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
-*The New York Times* published the greatest number of articles as well as total words.
-*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
-Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
-This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
+Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
+The sources were similar in most basic linguistic aspects, except for number of articles.
+Sources varied on the number of articles published pertaining to this topic.
+For example, *The Huffington Post* appears to have published only 27 aritcles while *NPR* published 757 articles.
+Valence was found to be slightly positive across all sources with the standard deviations precluding any conclusions supporting the presence of differences.
+*Slate* produced the most total words with the most tokens on average.
+*Rush Limbaugh* featured the highest number of types on average.
+*The Blaze* was the most readable source on average by grade level while *Fox News* was the least readable.
+The standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
+
 Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive statistics for articles about the partial government shutdown.
+Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
+Once again, there was variation in the number of articles published by each sorce on this topic.
+*The Hugginton Post* and *The Blaze* published fewer than 100 articles while *Slate* published 1,013 articles.
+*Slate* again featured the most total words and mean tokens.
+*Rush Limbaugh* again had the most types on average.
+For this topic, *Slate* was the most readable while *The Huffington Post* was the least readable.
+For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive, at least on a descriptive level.
 
@@
 ```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
-#Kav
 #GS
@@
 ```
+
+## Inferential Statistics
+
+To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
+Once again, the researchers used the *nlme* library in *R* [@Pinheiro2017].
+Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested ata structure.
+MLMs were constructed from datasets compiled for both topics of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
+
+For the Kavanuagh topic, the multilevel model indicated the presence of a significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
+There were no other significant or practical effect of political lean for any of the other four moral foundations.
+The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than consevative sources.
+Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp2-tablekav).
+
+For news articles about the partial U.S.
+Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations.
+A small-to-medium effect size was observed for *authority/respect*.
+The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
+This is similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
+As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
+Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
+Owing to a lack of matching effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
+
+Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
+A similar pattern was observed for the results in Experiment 1.
+As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
 
@@
 
+The results obtained in Experiment 2 did not completely confirm either of the hypotheses.
+The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
+The only significant effect was found for *harm/care* in the Kavanuagh confirmation hearing dataset.
+While the effect was in the hypothesized direction (higher positive endorsement for liberal sources), the effect size was small.
+While there were no significant effects found for the government shutdown topic, a small-to-medium effect size was calculated for the *authority/respect* foundation.
+Once again, the effect was in the hypothesized direction with conservative sources providing higher postive endorsements of the foundation relative to liberal sources.
+
+Both of these effects are consistent with both the resesarch hypotheses as well as previous findings in Moral Foundations Theory scholarship.
+It should be noted these effects were found in isolation, and similar patterns were not found across the other studies.
+These findings undermine any inferences of political bias stemming from the content of news articles.
+The results obtained for Experiment 2 call into question the Moral Foundations Dictionary's efficacy as a tool for establishing differences between political news sources by partisan lean.
+
 # Conclusions
+
+Within the theoretical framework of Moral Foundations Theory [@Haidt2007], the researchers attempted to devise a method leveraging the Moral Foundations Dictionary [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
+This method was carried out in several parts.
+First, the researchers collected the articles through web scraping techniques in *R* [@Wickham2016].
+Second, the text was processed using *ngram* and *tm* in *R* to render it in a form conducive to computerized statistical analysis [@Feinerer2017].
+Third, percent occurrence of words in the Moral Foundations Dictionary (MFD) was calculated on each source in order to establish how often words indicating endorsement of the five moral foundations appeared.
+Frequency of MFD word occurrence per article was weighted for valence by multiplying the scores by mean *z-scored* valence ratings from @Warriner2013.
+Finally, the researchers constructed multi-level models using *nlme* in *R* [@Pinheiro2017] for each foundation in which weighted percentages were predicted by each source's political lean.
+Individual source was held as a random intercept to control for correlated error.
+This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertianing to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
+Government shutdown from December 2018 to January 2019.
+
+In Experiment 1, the researchers analyzed general political news articles from four prominent U.S.
+news sources: *The New York Times*, *NPR*, *Fox News*, and *Breitbart*.
+They hypothesized *The New York Times* and *NPR* would endorse moral foundations representative of liberal political views and that *Fox News* and *Breitbart* would endorse foundations indicative of conservative views.
+The researchers assigned a political lean (liberal or conservative) to the sources based upon consumer preferences established by @Mitchell2014.
+After collecting the articles through web scraping, processing the article text, calculating percent occurrence of MFD words, and weighting that value by valence, the researchers constructed the MLM.
+The results obtained were not significant in any statistical or practical sense.
+There was a small effect found for the *authority/respect* foundation according to Cohen's *d*, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
+The researchers viewed these results as an opportunity to alter their method for use in Experiment 2.
+
+In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political bias in U.S.
+news sources.
+First, the researchers expanded the number of news sources from which articles were collected.
+They added *Slate*, *Politico*, and *Huffington Post* to the list of liberal sources and *The Blaze*, *Rush Limbaugh*, and *Sean Hannity* to the conservative sources.
+Once again, political bias groups were assigned based on @Mitchell2014's findings.
+Second, they elected to collect articles and compile datasets pertaining to two specific topics in U.S.
+news: the Kavanaugh hearing and the government shutdown.
+These topics were chosen due to their relevance to multiple moral foundations.
+Other than those two alterations, the same method (scraping, processing, weighting, and multi-level modelling) was employed for Experiment 2.
+
+For articles pertaining to the Kavanaugh hearing, there was a statistically significant effect for *harm/care*, but the effect size was modest.
+No other statistically or practically significant effects were found for the Kavanaugh topic.
+Likewise, there were no statistically or pracitically signifcant effects revealed for the government shutdown topic.
+However, there was a small-to-medium effect size for *authority/respect*.
+The fact these patterns do not appear in any of the other studies undertaken herein decreases the researchers' ability to draw any valuable conclusions regarding the MFD's ability to reveal political bias in American news media.
 

### 2019-04-15 pilot_manuscript.Rmd
DONE!!!!!!

@@
 They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
-In Experiment 2, the researchers will expand their number of sources to 10 and will analyze articles that pertain to the 2018 confirmation hearings of U.S.
-Supreme Court Justice Brett Kavanaugh.
-This topic was selected due to the moral disputes associated with his nomination.
+In Experiment 2, the researchers will expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+Supreme Court Justice Brett Kavanaugh and the partial U.S.
+Goverment Shutdown of 2018-2019.
+Once again, no significant differences in moral or political endorsements were found.
 
@@
 Finally, @Suhler2011 point out that particular concepts related to a foundation, including "anger" in *fairness/reciprocity* and "deception" in *ingroup/loyalty*, could be ascribed to any of the other foundations as well.
-In other words, it becomes difficult to recognize a particular concept as indidcative of any one foundation when, in theory, they could be applied to all five [@Haidt2007; @Suhler2011].
+In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five [@Haidt2007; @Suhler2011].
 
@@
 However, there exists compelling evidence regarding the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
-This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Fondations Dictionary.
+This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary.
 
@@
 Likewise, its five-factor structure has been demonstrated to fit data in multiple countries [@Graham2011; @Davies2014].
-In their article introducing the 30-item MFQ, @Graham2011 conducted an exploratory factor analysis (EFA) and found that a five-factor model fit better than a one, two, or three-factor model.
+In their article introducing the 30-item MFQ, @Graham2011 conducted an exploratory factor analysis (EFA) and found that a five-factor model fit the data better than a one, two, or three-factor model.
 @Davies2014 conducted a confirmatory factor analysis (CFA) of the MFQ with a sample from New Zealand and likewise found the five-factor model provided the best fit.
@@
 While these concerns regarding the replication of social priming studies are valid and deserve further investigation, @Druckman2004 does not purport to demonstrate a widespread effect of social priming on the American electorate.
-In other words, this reseach makes no claim to empirically supported priming effects.
+In other words, this research makes no claim to empirically supported priming effects.
 Rather, @Druckman2004 chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
 These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
-As such, @Druckman2004's research on Nixon serves as an example of language's potential utility in the propogation of desirable political opinions.
+As such, @Druckman2004's research on Nixon serves as an example of language's potential utility in the propagation of desirable political opinions.
 The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
@@
 That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources genrally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
+The researchers hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
 Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
+Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
 
@@
 The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
-They were selected for their widespread recognition and the fact politcial partisans have strong preferences for some sources over others.
-The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported idealogical consistency represented by the consumers of several news sources.
+They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
+The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
 In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean.
@@
 Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurence were multiplied by their *z*-scored valence.
+Words' percent occurrence were multiplied by their *z*-scored valence.
 Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence.
@@
 *Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
-Per indvidual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
+Per individual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
 Once again the standard deviations call into question any apparent differences between sources.
@@
 The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurence.
+Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurrence.
 
@@
 The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
-President Trump signed the bill, ending the longest govenrment shutdown in U.S.
+President Trump signed the bill, ending the longest government shutdown in U.S.
 history [@Axelrod2019].
@@
 The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
+Once again, no human participants were needed for this study, so no Institutional Review Board approval was necessary.
 
@@
 
-The same process was followed for scraping articles related to the partical U.S.
+The same process was followed for scraping articles related to the partial U.S.
 Government shutdown of 2018-2019.
@@
 Words were subsequently matched with their valences from @Warriner2013.
-Depending on the results of @Jordan2019's research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
+Depending on the results of @Jordan2019's research, alternative forms of the Moral Foundations Dictionary may be imported instead of the original dictionary.
 
@@
 Using the @Warriner2013 dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurence in the text.
+The researchers obtained the words' percent occurrence in the text.
 Once again, percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
@@
 The sources were similar in most basic linguistic aspects, except for number of articles.
-Sources varied on the number of articles published pertaining to this topic.
-For example, *The Huffington Post* appears to have published only 27 aritcles while *NPR* published 757 articles.
-Valence was found to be slightly positive across all sources with the standard deviations precluding any conclusions supporting the presence of differences.
+For example, *The Huffington Post* appears to have published only 27 articles while *NPR* published 757 articles on this topic.
+Valence was found to be slightly positive across all sources.
 *Slate* produced the most total words with the most tokens on average.
@@
 Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each sorce on this topic.
+Once again, there was variation in the number of articles published by each source on this topic.
 *The Hugginton Post* and *The Blaze* published fewer than 100 articles while *Slate* published 1,013 articles.
@@
 For this topic, *Slate* was the most readable while *The Huffington Post* was the least readable.
-For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive, at least on a descriptive level.
+For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
 
@@
 
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
+To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
 Once again, the researchers used the *nlme* library in *R* [@Pinheiro2017].
-Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested ata structure.
+Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
 MLMs were constructed from datasets compiled for both topics of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
 
-For the Kavanuagh topic, the multilevel model indicated the presence of a significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
+For the Kavanaugh topic, the multilevel model indicated the presence of a significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
 There were no other significant or practical effect of political lean for any of the other four moral foundations.
-The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than consevative sources.
+The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than conservative sources.
 Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp2-tablekav).
@@
 Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of matching effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
+Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
 
@@
 
-The results obtained in Experiment 2 did not completely confirm either of the hypotheses.
+The results obtained in Experiment 2 did not confirm either of the hypotheses.
 The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The only significant effect was found for *harm/care* in the Kavanuagh confirmation hearing dataset.
+The only significant effect was found for *harm/care* in the Kavanaugh confirmation hearing dataset.
 While the effect was in the hypothesized direction (higher positive endorsement for liberal sources), the effect size was small.
 While there were no significant effects found for the government shutdown topic, a small-to-medium effect size was calculated for the *authority/respect* foundation.
-Once again, the effect was in the hypothesized direction with conservative sources providing higher postive endorsements of the foundation relative to liberal sources.
-
-Both of these effects are consistent with both the resesarch hypotheses as well as previous findings in Moral Foundations Theory scholarship.
+Once again, the effect was in the hypothesized direction with conservative sources providing higher positive endorsements of the foundation relative to liberal sources.
+
+Both of these effects are consistent with both the research hypotheses as well as previous findings in Moral Foundations Theory scholarship.
 It should be noted these effects were found in isolation, and similar patterns were not found across the other studies.
@@
 Individual source was held as a random intercept to control for correlated error.
-This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertianing to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
+This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertaining to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
 Government shutdown from December 2018 to January 2019.
@@
 No other statistically or practically significant effects were found for the Kavanaugh topic.
-Likewise, there were no statistically or pracitically signifcant effects revealed for the government shutdown topic.
+Likewise, there were no statistically or practically significant effects revealed for the government shutdown topic.
 However, there was a small-to-medium effect size for *authority/respect*.
 The fact these patterns do not appear in any of the other studies undertaken herein decreases the researchers' ability to draw any valuable conclusions regarding the MFD's ability to reveal political bias in American news media.
+
+The results obtained in both experiments, while not confirmatory, provide several avenues for future investigation.
+Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of political bias in American news under the auspices of Moral Foundations Theory.
+This does not, however, rule out the possibility that news media is biased.
+As @Mitchell2014 has demonstrated, self-reported political partisans are drawn to separate sources, but the present research was unable to offer any content-based explanations of this phenomenon.
+Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
+The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
+
+Despite the fact the results regarding political bias were inconclusive, the researchers still retain confidence in the overall structure of the methodology established in the current study.
+Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
+The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
+Additionally, multi-level models were necessary to control for the nested nature of the data where political lean encompassed several sources, which themselves encompassed numerous articles.
+
+Thus, the researchers' attention turned to the instrument used to detect differences.
+In the present study, the researchers utilized the Moral Foundations Dictionary, a metric developed from Moral Foundations Theory [@Graham2009].
+Based upon the results obtained, it might be necessary to investigate alternative instruments that might better elucidate the differences of interest.
+Likewise, other theoretical perspectives may be better equipped to explain political differences in discourse.
+
+Tools such as these could be developed through the Linguistic Inquiry and Word Count program (LIWC) [@Pennebaker2007].
+As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context [@Graham2009].
+This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
+The authors established sound psychometric properties for the tool, implying its validity in several applications.
+For this reason, the researchers elected to utilize the MFD as their primary instrument.
+
+Other instruments could theoretically be developed through a LIWC analysis, including those that would be useful for analyzing political discourse.
+Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from @Warriner2013.
+The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
+However, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
+Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
+
+There is, however, another theoretical framework that could prove useful when applied to the method established in the present research.
+Relational Frame Theory originates in applied behavior analysis, but there exists recent scholarship that demonstrates its potential usefulness in the political realm.
+Relational Frame Theory (RFT) holds that stimuli, including speech and discourse, elicit responses in terms of relationships to other stimuli, even when the stimuli do not otherwise appear to be related [@Blackledge2014].
+For example, an individual's equivalent fear response to a venomous snake as well as a wooded area said to "contain snakes" represents "mutual entailment." That is, the fear response is an effect of both the snake and environment stimuli, which cause the fear response.
+"Combinatorial entailment" can be represented by a fear response elicited by a novel stimulus whose relationship to a well-known stimulus elicits a certain response [@Blackledge2014].
+In the snake example, if another stimulus (Stimulus A), were said to be "worse than" the snake, the relationship between A and the snake would elicit a more severe fear response to Stimulus A.
+RFT utilizes a set of "families" describing the nature of these relationships.
+Such families include "coordinative," establishing similarities between stimuli, and "distinctive," implying fundamental differences between stimuli [@Belisle2018].
+These families can be used to analyze networks of relational frames in discourse.
+
+@Belisle2018 conducted a text analysis (using a computer algorithm) of several speeches made by four recent U.S.
+presidents under Relational Frame Theory.
+These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
+For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts [@Belisle2018].
+At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
+In any case, this research appears to indicate that RFT might be useful for analyzing political news content similar to the method employed in the current study.
+
+Another apparent strength of RFT is its demonstrated effectiveness in the analysis of political discourse.
+Unlike the development of the Moral Foundations Dictionary, this application of RFT was performed on public facing political discourse that might be more similar to news articles than the Christian sermons upon which the MFD was compiled.
+Additionally, there would likely be greater overlap between the speeches analyzed in @Belisle2018's work and political news, as the media often quotes speeches by the president.
+Furthermore, the types or "families" of relational frames could be used as the individual constructs much like the moral foundations in the present research.
+In order to conform with the method established for this study, their occurrence would need to be scored, probably as a percent.
+This would allow for an intuitive approach to weighting by *z*-scored valence if needed.
+
+While Relational Frame Theory appears to represent a viable option for further research into political news analysis, there are some drawbacks.
+First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
+One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it was a theory designed to investigate not only moral differences but also political differences.
+While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
+
+In order to seriously consider RFT as a viable framework for this type of analysis, the researchers would like to be able to draw on further confirmatory evidence of the theory's utility in political discourse analysis.
+Specifically, analyses of more individuals than the four presidents addressed by @Belisle2018 would be needed to further demonstrate RFT's applicability in this field.
+Also, though presidential speeches may be more similar to news articles than sermons, they are still a distinct form of discourse with different goals and audiences than news outlets.
+RFT's reliability across these forms appears to remain untested as of this writing.
+These potential shortcomings are testable and might be overcome through more research.
+As such, RFT's potential as a useful framework for political discourse analysis should not be discounted.
+
+The researchers aimed to utilize the Moral Foundations Dictionary and valence in the analysis of political news articles to determine whether or not bias was present.
+In Experiment 1, they tested general political news from four U.S.
+news sources - two liberal and two conservative.
+They were unable to find any significant evidence of political bias in that analysis.
+After adjusting the method to include more sources and specific topics for articles, including the Kavanaugh hearing and the government shutdown, the researchers were once again unable to uncover differences in MFD word use between conservative and liberal news sources.
+The results in the current study seem to demonstrate the MFD's weaknesses in applications to political discourse.
+MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
+In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, or through a different theoretical perspective such as Relational Frame Theory.
+Despite the results obtained in the current study, the researchers have reason to believe this line of inquiry warrants further investigation and that the correct method will one day be established.
+
+Never before has news media and discourse represented such fertile ground for psychological research.
+The plethora of options and the potential for misinformation present important challenges for American democracy in the twenty-first century.
+The potential divisions in American society resulting from an abundance of choices for sources of political information, coupled with the notion that public discourse seems to offer competing conceptions of objective truth, underscores the importance of research into the content of political news.
+Democracy functions effectively on the foundation an informed and engaged electorate.
+Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of citizens every day so that insights into the nature and consequences of political discourse can be more completely understood.
 

### 2019-04-16 pilot_manuscript.Rmd
all the updates!

@@
 This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The Moral Foundations Questionnaire (MFQ), which was developed subsequent to the MFD, measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
+The MFQ, which was developed subsequent to the MFD, measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
 The questionnaire is made up of judgment items and relevance items.
@@
 
-```{r create_datasets_harm, include=FALSE}
+```{r create_datasets_harm, echo = F, include=FALSE}
 #read in the harm total words from the mtmm project
@@
 #figure out stupid words
-table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
+#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
 #fought, safer, spurn
@@
 
-```{r descriptives, include = FALSE}
+```{r descriptives, echo = F, include = FALSE}
 #summarize the dataset so that you have the total and percent for each foundation 
-summary(harm_final_data)
-summary(fair_final_data)
-summary(ingroup_final_data)
-summary(authority_final_data)
-summary(purity_final_data)
-#report descriptive statistics of the foundations
-mean(harm_final_data$valence)
-sd(harm_final_data$valence)
-mean(fair_final_data$valence)
-sd(fair_final_data$valence)
-mean(ingroup_final_data$valence)
-sd(ingroup_final_data$valence)
-mean(authority_final_data$valence)
-sd(authority_final_data$valence)
-mean(purity_final_data$valence)
-sd(purity_final_data$valence)
+# summary(harm_final_data)
+# summary(fair_final_data)
+# summary(ingroup_final_data)
+# summary(authority_final_data)
+# summary(purity_final_data)
+# #report descriptive statistics of the foundations
+# mean(harm_final_data$valence)
+# sd(harm_final_data$valence)
+# mean(fair_final_data$valence)
+# sd(fair_final_data$valence)
+# mean(ingroup_final_data$valence)
+# sd(ingroup_final_data$valence)
+# mean(authority_final_data$valence)
+# sd(authority_final_data$valence)
+# mean(purity_final_data$valence)
+# sd(purity_final_data$valence)
 #note that a big problem is the valence of the words 
@@
 
-tapply(final$FK, final$Source, mean)
-tapply(final$FK, final$Source, sd)
+# tapply(final$FK, final$Source, mean)
+# tapply(final$FK, final$Source, sd)
 
@@
 
-tableprint[ , 1] = unique(final$Source)
+#tableprint[ , 1] = unique(final$Source)
+tableprint[ , 1] = c("Breitbart", "Fox News", "NPR", "New York Times")
 tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
 tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
-tableprint[ , 4] = tapply(final$X, final$Source, length)
+tableprint[ , 4] = tapply(final$valenceavg, final$Source, length)
 tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
@@
 tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+
+tableprint = tableprint[c(3, 4, 1, 2) , ]
 
@@
 Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
-This might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
+This result might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
 As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
@@
 nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-tapply(nozero$wordcount, nozero$Source, mean)
-tapply(nozero$wordcount, nozero$Source, sum)
+# tapply(nozero$wordcount, nozero$Source, mean)
+# tapply(nozero$wordcount, nozero$Source, sum)
 
@@
 
-tapply(nozero$wordcount, nozero$Source, mean)
-tapply(nozero$wordcount, nozero$Source, sum)
+# tapply(nozero$wordcount, nozero$Source, mean)
+# tapply(nozero$wordcount, nozero$Source, sum)
 
@@
 
-```{r create_datasets_harm_kav, eval = T, echo = F}
+```{r create_datasets_harm_kav, eval = T, echo = F, include = F}
 #read in the harm total words from the mtmm project
@@
 #figure out stupid words
-table(harm_final_data_kav$Var1[is.na(harm_final_data_kav$valence) & harm_final_data_kav$Freq > 0])
+#table(harm_final_data_kav$Var1[is.na(harm_final_data_kav$valence) & harm_final_data_kav$Freq > 0])
 #fought, safer, spurn
@@
 
-```{r create_datasets_harm_gs, eval = T, echo = F}
+```{r create_datasets_harm_gs, eval = T, echo = F, include = F}
 #read in the harm total words from the mtmm project
@@
 #figure out stupid words
-table(harm_final_data_gs$Var1[is.na(harm_final_data_gs$valence) & harm_final_data_gs$Freq > 0])
+#table(harm_final_data_gs$Var1[is.na(harm_final_data_gs$valence) & harm_final_data_gs$Freq > 0])
 #fought, safer, spurn
@@
 
-```{r create_datasets_fair_gs, include=FALSE}
+```{r create_datasets_fair_gs, echo = F, include=FALSE}
 fair_all_gs = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
@@
 
-```{r create_datasets_ingroup_gs, include=FALSE}
+```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
 ingroup_all_gs = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
@@
 
-```{r create_datasets_authority_gs, include=FALSE}
+```{r create_datasets_authority_gs, echo = F, include=FALSE}
 authority_all_gs = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
@@
 
-```{r create_datasets_purity_gs, include=FALSE}
+```{r create_datasets_purity_gs, echo = F, include=FALSE}
 purity_all_gs = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
@@
 
-```{r descriptives_both, include = FALSE}
+```{r descriptives_both, echo = F, include = FALSE}
 ##summarize the dataset so that you have the total and percent for each foundation
@@
 
-# Experiment 2
-
-## Results
+# Results
 
@@
 
-tapply(final_kav$FK, final_kav$Source, mean)
-tapply(final_kav$FK, final_kav$Source, sd)
+# tapply(final_kav$FK, final_kav$Source, mean)
+# tapply(final_kav$FK, final_kav$Source, sd)
 
@@
 
-tableprint[ , 1] = unique(final_kav$Source)
-tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean)
-tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd)
+#tableprint[ , 1] = unique(final_kav$Source)
+tableprint[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
+                     "Huffington Post", "NPR", "New York Times", "Politico",
+                     "Rush Limbaugh", "Slate")
+tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
+tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
 tableprint[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
-tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum)
-tableprint[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean)
+tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
+tableprint[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
 tableprint[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
-tableprint[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean)
-tableprint[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd)
-tableprint[ , 10] = tapply(final_kav$FK, final_kav$Source, mean)
-tableprint[ , 11] = tapply(final_kav$FK, final_kav$Source, sd)
+tableprint[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
+tableprint[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
+tableprint[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
+tableprint[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
 
 tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+
+tableprint = tableprint[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
 
@@
           escape = F,
+          small = T,
           align = c("l", rep("c", 6))
@@
 
-tapply(final_gs$FK, final_gs$Source, mean)
-tapply(final_gs$FK, final_gs$Source, sd)
+# tapply(final_gs$FK, final_gs$Source, mean)
+# tapply(final_gs$FK, final_gs$Source, sd)
 
@@
 
-tableprint[ , 1] = unique(final_gs$Source)
+#tableprint[ , 1] = unique(final_gs$Source)
+tableprint[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
+                     "Huffington Post", "NPR", "New York Times", "Politico",
+                     "Rush Limbaugh", "Slate")
 tableprint[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
@@
 
+tableprint = tableprint[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
+
 #change this to match
@@
           escape = F,
+          small = T, 
           align = c("l", rep("c", 6))
@@
 The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This is similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
+This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
 As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.

### 2019-04-16 pilot_manuscript.tex
so rude
all the updates!

@@
 Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-Suhler, Churchland, Joseph, Graham, and Nosek (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
+Suhler and Churchland (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
 First, the authors challenge Haidt and Graham (2007)'s claims the moral intuitions represented by MFT are innate and modular.
-Suhler et al.
-(2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
-Rather, behaviors likely result from interactions between genetics and experience (Suhler et al., 2011).
+Suhler and Churchland (2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
+Rather, behaviors likely result from interactions between genetics and experience (Suhler \& Churchland, 2011).
 According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
-Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler et al., 2011).
+Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler \& Churchland, 2011).
 However, as with innateness, there is little neurobiological evidence to support modularity.
 
-Suhler et al.
-(2011) also criticized the content and taxonomy of the five foundations.
+Suhler and Churchland (2011) also criticized the content and taxonomy of the five foundations.
 The authors criticize Haidt and Graham (2007)'s omissions of additional foundations, including \emph{industry} and \emph{modesty}, claiming these concepts are moralized in many societies worldwide.
 Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-For example, Suhler et al.
-(2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
+For example, Suhler and Churchland (2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
 Work by Graham et al.
 (2011) might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
-Finally, Suhler et al.
-(2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
-In other words, it becomes difficult to recognize a particular concept as indidcative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler et al., 2011).
+Finally, Suhler and Churchland (2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
+In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler \& Churchland, 2011).
 
@@
 This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The Moral Foundations Questionnaire (MFQ), which was developed subsequent to the MFD, measures individuals' endorsements of each of the foundations using a six-point scale (Graham et al., 2011).
+The MFQ, which was developed subsequent to the MFD, measures individuals' endorsements of each of the foundations using a six-point scale (Graham et al., 2011).
 The questionnaire is made up of judgment items and relevance items.
@@
 In their article introducing the 30-item MFQ, Graham et al.
-(2011) conducted an exploratory factor analysis (EFA) and found that a five-factor model fit better than a one, two, or three-factor model.
+(2011) conducted an exploratory factor analysis (EFA) and found that a five-factor model fit the data better than a one, two, or three-factor model.
 Davies et al.
@@
 (2011) claim to find a \enquote{reasonable} degree of generalizability for the MFQ across participants from many different regions in the world.
-These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler et al.
-(2011) should still be taken into account in studies involving the theory.
+These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler and Churchland (2011) should still be taken into account in studies involving the theory.
 
@@
 (2004) does not purport to demonstrate a widespread effect of social priming on the American electorate.
-In other words, this reseach makes no claim to empirically supported priming effects.
+In other words, this research makes no claim to empirically supported priming effects.
 Rather, Druckman et al.
@@
 As such, Druckman et al.
-(2004)'s research on Nixon serves as an example of language's potential utility in the propogation of desirable political opinions.
+(2004)'s research on Nixon serves as an example of language's potential utility in the propagation of desirable political opinions.
 The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
@@
 That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources genrally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
+The researchers hypothesized the news sources generally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
 Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
+Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
 
@@
 The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
-They were selected for their widespread recognition and the fact politcial partisans have strong preferences for some sources over others.
-The researchers determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported idealogical consistency represented by the consumers of several news sources.
+They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
+The researchers determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
 In general, \emph{The New York Times} and \emph{NPR} are preferred by consumers reporting a liberal bias or lean.
@@
 Therefore, for each article, the percentage of the number of \emph{harm/care} words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurence were multiplied by their \emph{z}-scored valence.
+Words' percent occurrence were multiplied by their \emph{z}-scored valence.
 Valences were \emph{z}-scored in order to eliminate any ambiguity regarding the direction of the valence.
@@
 
-Breitbart Fox News NPR NY Times
-0.2859474 0.2865543 0.2836801 0.3036140
-Breitbart Fox News NPR NY Times
-0.1758739 0.1657591 0.2303375 0.1316283
-Breitbart Fox News NPR NY Times
-502.4509 590.0179 435.9381 1114.7266
-Breitbart Fox News NPR NY Times
-347.9033 528.6040 642.6311 511.8552
-Breitbart Fox News NPR NY Times
-243.3633 283.5666 191.9583 454.2660
-Breitbart Fox News NPR NY Times
-120.7606 188.9969 192.2881 154.5782
-Breitbart Fox News NPR NY Times
-1437 503 695 406
-Breitbart Fox News NPR NY Times
-722022 296779 302977 452579
-Breitbart Fox News NPR NY Times
-18.41894 16.92098 13.80370 16.32188
-Breitbart Fox News NPR NY Times
-8.011796 7.159823 3.928992 3.290628
-
-\textbackslash{}begin\{table\}{[}tbp{]}
-\textbackslash{}begin\{center\}
-\textbackslash{}begin\{threeparttable\}
-
-\caption{\label{tab:exp1_source_descriptives}}
-
-\textbackslash{}begin\{tabular\}\{lcccccclccc\}
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp1-source-descriptives}Experiment 1 - Descriptive Statistics by Source}
+\begin{tabular}{lcccccclccc}
 \toprule
-Source \& \$M\_Valence \& \(SD_Valence\) \& Number of Articles \& Total Words \& \(M_Tokens\) \& \(SD_Tokens\) \& \(M_Types\) \& SD\_Types \& \(M_Readability\) \& \(SD_Readability\)\textbackslash{}
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
 \midrule
-NY Times \& 0.285947446148072 \& 0.175873929325112 \& 1437 \& 722022 \& 502.450939457202 \& 347.903319774803 \& 243.363256784969 \& 120.760589770644 \& 18.4189422361943 \& 8.01179627082686\textbackslash{}
-NPR \& 0.286554347926494 \& 0.165759138672493 \& 503 \& 296779 \& 590.017892644135 \& 528.604003868971 \& 283.566600397614 \& 188.996856562777 \& 16.9209846559293 \& 7.15982285267178\textbackslash{}
-Fox News \& 0.283680149614328 \& 0.230337453667188 \& 695 \& 302977 \& 435.938129496403 \& 642.63105430646 \& 191.958273381295 \& 192.288110075879 \& 13.8036963247 \& 3.92899246122398\textbackslash{}
-Breitbart \& 0.303614030842649 \& 0.131628349251591 \& 406 \& 452579 \& 1114.72660098522 \& 511.855179780783 \& 454.266009852217 \& 154.578209626066 \& 16.3218777264871 \& 3.29062776810359\textbackslash{}
+NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.29 & 13.80 & 3.93\\
+New York Times & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.32 & 3.29\\
+Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.36 & 120.76 & 18.42 & 8.01\\
+Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.57 & 189.00 & 16.92 & 7.16\\
 \bottomrule
 \addlinespace
-\textbackslash{}end\{tabular\}
-
+\end{tabular}
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
 \end{tablenotes}
-
-\textbackslash{}end\{threeparttable\}
-\textbackslash{}end\{center\}
-\textbackslash{}end\{table\}
+\end{threeparttable}
+\end{center}
+\end{table}
 
@@
 
-As seen in Table 1, the sources are similar in some aspects yet different in others.
+As seen in Table \ref{tab:exp1-source-descriptives}, the sources are similar in some aspects yet different in others.
 Valence appears to be slightly positive across all sources.
@@
 \emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
-Per indvidual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
+Per individual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
 Once again the standard deviations call into question any apparent differences between sources.
 Finally, \emph{Fox News} appears to be the most readable source on average, while \emph{The New York Times} is the least readable.
-This might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
+This result might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
 As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
@@
 The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table 2.
+Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp1-table}.
 To interpret the weighted scores, one can examine the mean and standard deviations for each.
@@
 The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
-President Trump signed the bill, ending the longest govenrment shutdown in U.S.
+President Trump signed the bill, ending the longest government shutdown in U.S.
 history (Axelrod, 2019).
@@
 Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
-
-\begin{verbatim}
-##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
-##  462.4440  496.4967 2018.6502  219.4815  650.4457  296.7350 1108.0689 
-##  POLITICO      RUSH     SLATE 
-## 1551.9478 1552.7151  845.2059
-\end{verbatim}
-
-\begin{verbatim}
-##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
-##    128097    375848   1304048      5926    359046    108605    723569 
-##  POLITICO      RUSH     SLATE 
-##   1069292    267067    229896
-\end{verbatim}
-
-\begin{verbatim}
-##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
-##  397.7857  332.9644 2763.2942  163.6667  560.6944  348.1889 1106.7696 
-##  POLITICO      RUSH     SLATE 
-## 1574.3198 1956.7949  728.6667
-\end{verbatim}
-
-\begin{verbatim}
-##     BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
-##     38983    102886   2799217     10311    242220    151114    831184 
-##  POLITICO      RUSH     SLATE 
-##    349499    152630     85254
-\end{verbatim}
 
@@
 Depending on the results of Jordan et al.
-(2019)'s research, alternative forms of the Moral Foudnations Dictionary may be imported instead of the original dictionary.
+(2019)'s research, alternative forms of the Moral Foundations Dictionary may be imported instead of the original dictionary.
 
@@
 (2013) dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurence in the text.
+The researchers obtained the words' percent occurrence in the text.
 Once again, percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
 
-\begin{verbatim}
-## 
-## fought  safer  spurn 
-##     87     26      5
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## fought  safer  spurn 
-##    112     80      5
-\end{verbatim}
-
-\hypertarget{experiment-2-1}{%
-\section{Experiment 2}\label{experiment-2-1}}
-
 \hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
+\section{Results}\label{results-1}}
 
@@
 
-Table 3 displays the descriptive statistics for sources' writing on the Kavanaugh confirmation.
-The sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
-\emph{The New York Times} published the greatest number of articles as well as total words.
-\emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
-Per indvidual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, \emph{Fox News} appears to be the most readable source on average, while \emph{The New York Times} is the least readable.
-This might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
-Table 4 displays descriptive statistics for articles about the partial government shutdown.
-
-\begin{verbatim}
-BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
-\end{verbatim}
-
-0.2485825 0.2969520 0.2882946 0.3134749 0.2749170 0.2177703 0.3278847
-POLITICO RUSH SLATE
-NaN 0.3817549 0.2945150
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-0.1283312 0.1311957 0.1100579 0.1089378 0.1243028 0.2458333 0.1267266
-POLITICO RUSH SLATE
-NA 0.1339493 0.1235115
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-462.4440 496.4967 2018.6502 219.4815 650.4457 296.7350 1108.0689
-POLITICO RUSH SLATE
-1551.9478 1552.7151 845.2059
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-149.6635 609.9120 2709.7690 145.9798 462.2122 499.0987 570.3075
-POLITICO RUSH SLATE
-1045.4670 1258.5090 612.2226
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-210.5199 230.0304 534.4675 121.0370 283.0670 128.1230 461.2649
-POLITICO RUSH SLATE
-614.6647 419.0000 332.4228
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-53.13550 153.61822 404.21137 57.25952 129.23455 172.51298 174.19696
-POLITICO RUSH SLATE
-358.67966 225.79665 168.16852
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-277 757 646 27 552 366 653
-POLITICO RUSH SLATE
-689 172 272
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-128097 375848 1304048 5926 359046 108605 723569
-POLITICO RUSH SLATE
-1069292 267067 229896
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-10.829946 11.011777 9.701136 11.884344 10.791419 12.489576 10.563974
-POLITICO RUSH SLATE
-12.090968 9.415941 12.350359
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-1.871086 2.122317 1.848820 2.372470 1.909656 3.620217 2.099457
-POLITICO RUSH SLATE
-2.602008 9.255734 2.469494
-
-\textbackslash{}begin\{table\}{[}tbp{]}
-\textbackslash{}begin\{center\}
-\textbackslash{}begin\{threeparttable\}
-
-\caption{\label{tab:exp2_source_descriptives_kav}}
-
-\textbackslash{}begin\{tabular\}\{lcccccclccc\}
-\toprule
-Source \& \$M\_Valence \& \(SD_Valence\) \& Number of Articles \& Total Words \& \(M_Tokens\) \& \(SD_Tokens\) \& \(M_Types\) \& SD\_Types \& \(M_Readability\) \& \(SD_Readability\)\textbackslash{}
-\midrule
-NY Times \& 0.248582461954873 \& 0.128331247765861 \& 277 \& 128097 \& 462.4440433213 \& 149.663540314715 \& 210.519855595668 \& 53.135496091658 \& 10.8299460563033 \& 1.87108620272245\textbackslash{}
-NPR \& 0.296952015363949 \& 0.131195722288699 \& 757 \& 375848 \& 496.496697490092 \& 609.911984327776 \& 230.030383091149 \& 153.61822352656 \& 11.0117767439097 \& 2.12231727243672\textbackslash{}
-SLATE \& 0.288294612452221 \& 0.110057878050137 \& 646 \& 1304048 \& 2018.65015479876 \& 2709.7689798081 \& 534.467492260062 \& 404.21136695319 \& 9.70113600527088 \& 1.84882018527607\textbackslash{}
-HUFFPO \& 0.313474919759693 \& 0.108937766427717 \& 27 \& 5926 \& 219.481481481481 \& 145.979811662796 \& 121.037037037037 \& 57.2595181751682 \& 11.8843441276617 \& 2.37246998423358\textbackslash{}
-POLITICO \& 0.274917000644333 \& 0.124302802662318 \& 552 \& 359046 \& 650.445652173913 \& 462.21217142652 \& 283.067028985507 \& 129.234550340392 \& 10.7914191586328 \& 1.90965621447939\textbackslash{}
-FOX \& 0.217770347500186 \& 0.2458332698723 \& 366 \& 108605 \& 296.734972677596 \& 499.098654130005 \& 128.122950819672 \& 172.512977214565 \& 12.4895757587921 \& 3.62021720854147\textbackslash{}
-BREITBART \& 0.327884697009488 \& 0.126726583211477 \& 653 \& 723569 \& 1108.06891271057 \& 570.307523730945 \& 461.264931087289 \& 174.196961926317 \& 10.5639743164815 \& 2.09945747809235\textbackslash{}
-RUSH \& NaN \& NA \& 689 \& 1069292 \& 1551.94775036284 \& 1045.46703853415 \& 614.66473149492 \& 358.679655515179 \& 12.0909683600071 \& 2.60200753688676\textbackslash{}
-BLAZE \& 0.381754930162833 \& 0.133949323543338 \& 172 \& 267067 \& 1552.71511627907 \& 1258.50895031214 \& 419 \& 225.796653329873 \& 9.41594130925692 \& 9.25573422733374\textbackslash{}
-HANNITY \& 0.294514982957241 \& 0.123511487515174 \& 272 \& 229896 \& 845.205882352941 \& 612.222641383098 \& 332.422794117647 \& 168.168519181875 \& 12.3503593297322 \& 2.46949447044547\textbackslash{}
-\bottomrule
-\addlinespace
-\textbackslash{}end\{tabular\}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
-\end{tablenotes}
-
-\textbackslash{}end\{threeparttable\}
-\textbackslash{}end\{center\}
-\textbackslash{}end\{table\}
-
-\begin{verbatim}
-BLAZE BREITBART       FOX   HANNITY    HUFFPO       NPR  NY Times 
-\end{verbatim}
-
-0.2630738 0.3363861 0.3502582 0.2895833 0.2955373 0.2292974 0.3292069
-POLITICO RUSH SLATE
-0.2948354 0.3669883 0.3033559
-BLAZE BREITBART FOX HANNITY HUFFPO NPR
-0.12830612 0.14962810 0.12655527 0.14435751 0.13263919 0.21714483
-NY Times POLITICO RUSH SLATE
-0.12716701 0.09816753 0.12112741 0.11622436
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-397.7857 332.9644 2763.2942 163.6667 560.6944 348.1889 1106.7696
-POLITICO RUSH SLATE
-1574.3198 1956.7949 728.6667
-BLAZE BREITBART FOX HANNITY HUFFPO NPR
-102.09771 238.70276 3405.43855 33.59387 425.52190 457.33985
-NY Times POLITICO RUSH SLATE
-506.91798 875.62557 1544.14427 464.34307
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-185.66327 168.30744 637.29812 95.12698 258.26620 155.52535 471.80160
-POLITICO RUSH SLATE
-638.31532 482.79487 301.70940
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-41.93489 81.59286 493.99860 16.59041 130.54439 171.29690 174.88347
-POLITICO RUSH SLATE
-313.33750 252.79150 138.73586
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-98 309 1013 63 432 434 751
-POLITICO RUSH SLATE
-222 78 117
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-38983 102886 2799217 10311 242220 151114 831184
-POLITICO RUSH SLATE
-349499 152630 85254
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-10.684144 10.714110 9.337567 13.406829 10.669212 11.192714 11.279935
-POLITICO RUSH SLATE
-11.283515 9.760202 11.858193
-BLAZE BREITBART FOX HANNITY HUFFPO NPR NY Times
-1.849923 2.046638 1.907440 4.791906 1.826810 3.150647 2.188760
-POLITICO RUSH SLATE
-1.234029 7.600883 2.510134
-
-\textbackslash{}begin\{table\}{[}tbp{]}
-\textbackslash{}begin\{center\}
-\textbackslash{}begin\{threeparttable\}
-
-\caption{\label{tab:exp2_source_descriptives_gs}}
-
-\textbackslash{}begin\{tabular\}\{lcccccclccc\}
-\toprule
-Source \& \$M\_Valence \& \(SD_Valence\) \& Number of Articles \& Total Words \& \(M_Tokens\) \& \(SD_Tokens\) \& \(M_Types\) \& SD\_Types \& \(M_Readability\) \& \(SD_Readability\)\textbackslash{}
-\midrule
-NY Times \& 0.263073762515189 \& 0.128306121930571 \& 98 \& 38983 \& 397.785714285714 \& 102.097714464963 \& 185.663265306122 \& 41.9348891176587 \& 10.6841442081704 \& 1.84992301246728\textbackslash{}
-NPR \& 0.336386116861354 \& 0.149628095737843 \& 309 \& 102886 \& 332.964401294498 \& 238.702761753771 \& 168.307443365696 \& 81.5928638511323 \& 10.7141103107316 \& 2.04663844695781\textbackslash{}
-SLATE \& 0.350258204124201 \& 0.126555273689823 \& 1013 \& 2799217 \& 2763.2941757157 \& 3405.4385462127 \& 637.298124383021 \& 493.998601763112 \& 9.33756681985634 \& 1.90743987105106\textbackslash{}
-HUFFPO \& 0.289583347963234 \& 0.144357514755571 \& 63 \& 10311 \& 163.666666666667 \& 33.5938742495827 \& 95.1269841269841 \& 16.5904092616031 \& 13.4068286179036 \& 4.7919060550463\textbackslash{}
-POLITICO \& 0.295537320180438 \& 0.132639186552305 \& 432 \& 242220 \& 560.694444444444 \& 425.521903288046 \& 258.266203703704 \& 130.544392770929 \& 10.6692121592768 \& 1.82680953279554\textbackslash{}
-FOX \& 0.229297405563287 \& 0.21714483329782 \& 434 \& 151114 \& 348.188940092166 \& 457.339854495746 \& 155.52534562212 \& 171.296902150535 \& 11.1927143814131 \& 3.15064661540684\textbackslash{}
-BREITBART \& 0.329206931218954 \& 0.127167010716965 \& 751 \& 831184 \& 1106.76964047936 \& 506.917980410773 \& 471.801597869507 \& 174.883471443445 \& 11.2799353793112 \& 2.18876019242514\textbackslash{}
-RUSH \& 0.294835377053155 \& 0.0981675318751069 \& 222 \& 349499 \& 1574.31981981982 \& 875.625574158975 \& 638.315315315315 \& 313.33749985304 \& 11.2835154976977 \& 1.23402883439991\textbackslash{}
-BLAZE \& 0.366988255105934 \& 0.121127409825597 \& 78 \& 152630 \& 1956.79487179487 \& 1544.14427492755 \& 482.794871794872 \& 252.791498653617 \& 9.76020159415253 \& 7.60088309094014\textbackslash{}
-HANNITY \& 0.303355863690906 \& 0.116224358322565 \& 117 \& 85254 \& 728.666666666667 \& 464.343065802237 \& 301.709401709402 \& 138.735860405917 \& 11.8581927760125 \& 2.51013431157023\textbackslash{}
-\bottomrule
-\addlinespace
-\textbackslash{}end\{tabular\}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.}
-\end{tablenotes}
-
-\textbackslash{}end\{threeparttable\}
-\textbackslash{}end\{center\}
-\textbackslash{}end\{table\}
+Table \ref{tab:exp2-source-descriptives-kav} displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
+The sources were similar in most basic linguistic aspects, except for number of articles.
+For example, \emph{The Huffington Post} appears to have published only 27 articles while \emph{NPR} published 757 articles on this topic.
+Valence was found to be slightly positive across all sources.
+\emph{Slate} produced the most total words with the most tokens on average.
+\emph{Rush Limbaugh} featured the highest number of types on average.
+\emph{The Blaze} was the most readable source on average by grade level while \emph{Fox News} was the least readable.
+The standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
+
+Table \ref{tab:exp2-source-descriptives-gs} displays descriptive statistics for articles about the partial government shutdown.
+Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
+Once again, there was variation in the number of articles published by each source on this topic.
+\emph{The Hugginton Post} and \emph{The Blaze} published fewer than 100 articles while \emph{Slate} published 1,013 articles.
+\emph{Slate} again featured the most total words and mean tokens.
+\emph{Rush Limbaugh} again had the most types on average.
+For this topic, \emph{Slate} was the most readable while \emph{The Huffington Post} was the least readable.
+For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
 
@@
 \begin{threeparttable}
-\caption{\label{tab:exp2-table_kav}}
+\caption{\label{tab:exp2-source-descriptives-kav}Kavanaugh - Descriptive Statistics by Source}
+\small{
+\begin{tabular}{lcccccclccc}
+\toprule
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+\midrule
+Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.79 & 1.91\\
+NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.49 & 3.62\\
+New York Times & 0.33 & 0.13 & 653 & 723569 & 1,108.07 & 570.31 & 461.26 & 174.20 & 10.56 & 2.10\\
+Politico & 0.32 & 0.10 & 689 & 1069292 & 1,551.95 & 1,045.47 & 614.66 & 358.68 & 12.09 & 2.60\\
+Slate & 0.29 & 0.12 & 272 & 229896 & 845.21 & 612.22 & 332.42 & 168.17 & 12.35 & 2.47\\
+The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.83 & 1.87\\
+Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 11.01 & 2.12\\
+Fox News & 0.29 & 0.11 & 646 & 1304048 & 2,018.65 & 2,709.77 & 534.47 & 404.21 & 9.70 & 1.85\\
+Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.88 & 2.37\\
+Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1,552.72 & 1,258.51 & 419.00 & 225.80 & 9.42 & 9.26\\
+\bottomrule
+\addlinespace
+\end{tabular}
+}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp2-source-descriptives-gs}Government Shutdown - Descriptive Statistics by Source}
+\small{
+\begin{tabular}{lcccccclccc}
+\toprule
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+\midrule
+Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.67 & 1.83\\
+NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.19 & 3.15\\
+New York Times & 0.33 & 0.13 & 751 & 831184 & 1,106.77 & 506.92 & 471.80 & 174.88 & 11.28 & 2.19\\
+Politico & 0.29 & 0.10 & 222 & 349499 & 1,574.32 & 875.63 & 638.32 & 313.34 & 11.28 & 1.23\\
+Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.86 & 2.51\\
+The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.68 & 1.85\\
+Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.71 & 2.05\\
+Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2,763.29 & 3,405.44 & 637.30 & 494.00 & 9.34 & 1.91\\
+Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.41 & 4.79\\
+Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1,956.79 & 1,544.14 & 482.79 & 252.79 & 9.76 & 7.60\\
+\bottomrule
+\addlinespace
+\end{tabular}
+}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\hypertarget{inferential-statistics-1}{%
+\subsection{Inferential Statistics}\label{inferential-statistics-1}}
+
+To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
+Once again, the researchers used the \emph{nlme} library in \emph{R} (Pinheiro et al., 2017).
+Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
+MLMs were constructed from datasets compiled for both topics of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
+
+For the Kavanaugh topic, the multilevel model indicated the presence of a significant effect for \emph{harm/care}, but the practical effect denoted by Cohen's \emph{d} was found to be small.
+There were no other significant or practical effect of political lean for any of the other four moral foundations.
+The effect for \emph{harm/care} was in the hypothesized direction with liberal sources tending to use more positively \emph{harm/care} words than conservative sources.
+Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp2-tablekav}.
+
+For news articles about the partial U.S.
+Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations.
+A small-to-medium effect size was observed for \emph{authority/respect}.
+The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
+This effect was similar to Experiment 1 in which the largest effect size was observed for \emph{authority/respect}.
+As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
+Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
+Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
+
+Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
+A similar pattern was observed for the results in Experiment 1.
+As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp2-tablekav}}
 \begin{tabular}{lccccccc}
@@
 \begin{threeparttable}
-\caption{\label{tab:exp2-table_gs}}
+\caption{\label{tab:exp2-tablegs}}
 \begin{tabular}{lccccccc}
@@
 
+The results obtained in Experiment 2 did not confirm either of the hypotheses.
+The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
+The only significant effect was found for \emph{harm/care} in the Kavanaugh confirmation hearing dataset.
+While the effect was in the hypothesized direction (higher positive endorsement for liberal sources), the effect size was small.
+While there were no significant effects found for the government shutdown topic, a small-to-medium effect size was calculated for the \emph{authority/respect} foundation.
+Once again, the effect was in the hypothesized direction with conservative sources providing higher positive endorsements of the foundation relative to liberal sources.
+
+Both of these effects are consistent with both the research hypotheses as well as previous findings in Moral Foundations Theory scholarship.
+It should be noted these effects were found in isolation, and similar patterns were not found across the other studies.
+These findings undermine any inferences of political bias stemming from the content of news articles.
+The results obtained for Experiment 2 call into question the Moral Foundations Dictionary's efficacy as a tool for establishing differences between political news sources by partisan lean.
+
 \hypertarget{conclusions}{%
 \section{Conclusions}\label{conclusions}}
+
+Within the theoretical framework of Moral Foundations Theory (Haidt \& Graham, 2007), the researchers attempted to devise a method leveraging the Moral Foundations Dictionary (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
+This method was carried out in several parts.
+First, the researchers collected the articles through web scraping techniques in \emph{R} (Wickham, 2016).
+Second, the text was processed using \emph{ngram} and \emph{tm} in \emph{R} to render it in a form conducive to computerized statistical analysis (Feinerer \& Hornik, 2017).
+Third, percent occurrence of words in the Moral Foundations Dictionary (MFD) was calculated on each source in order to establish how often words indicating endorsement of the five moral foundations appeared.
+Frequency of MFD word occurrence per article was weighted for valence by multiplying the scores by mean \emph{z-scored} valence ratings from Warriner et al.
+(2013).
+Finally, the researchers constructed multi-level models using \emph{nlme} in \emph{R} (Pinheiro et al., 2017) for each foundation in which weighted percentages were predicted by each source's political lean.
+Individual source was held as a random intercept to control for correlated error.
+This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertaining to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
+Government shutdown from December 2018 to January 2019.
+
+In Experiment 1, the researchers analyzed general political news articles from four prominent U.S.
+news sources: \emph{The New York Times}, \emph{NPR}, \emph{Fox News}, and \emph{Breitbart}.
+They hypothesized \emph{The New York Times} and \emph{NPR} would endorse moral foundations representative of liberal political views and that \emph{Fox News} and \emph{Breitbart} would endorse foundations indicative of conservative views.
+The researchers assigned a political lean (liberal or conservative) to the sources based upon consumer preferences established by Mitchell et al.
+(2014).
+After collecting the articles through web scraping, processing the article text, calculating percent occurrence of MFD words, and weighting that value by valence, the researchers constructed the MLM.
+The results obtained were not significant in any statistical or practical sense.
+There was a small effect found for the \emph{authority/respect} foundation according to Cohen's \emph{d}, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
+The researchers viewed these results as an opportunity to alter their method for use in Experiment 2.
+
+In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political bias in U.S.
+news sources.
+First, the researchers expanded the number of news sources from which articles were collected.
+They added \emph{Slate}, \emph{Politico}, and \emph{Huffington Post} to the list of liberal sources and \emph{The Blaze}, \emph{Rush Limbaugh}, and \emph{Sean Hannity} to the conservative sources.
+Once again, political bias groups were assigned based on Mitchell et al.
+(2014)'s findings.
+Second, they elected to collect articles and compile datasets pertaining to two specific topics in U.S.
+news: the Kavanaugh hearing and the government shutdown.
+These topics were chosen due to their relevance to multiple moral foundations.
+Other than those two alterations, the same method (scraping, processing, weighting, and multi-level modelling) was employed for Experiment 2.
+
+For articles pertaining to the Kavanaugh hearing, there was a statistically significant effect for \emph{harm/care}, but the effect size was modest.
+No other statistically or practically significant effects were found for the Kavanaugh topic.
+Likewise, there were no statistically or practically significant effects revealed for the government shutdown topic.
+However, there was a small-to-medium effect size for \emph{authority/respect}.
+The fact these patterns do not appear in any of the other studies undertaken herein decreases the researchers' ability to draw any valuable conclusions regarding the MFD's ability to reveal political bias in American news media.
+
+The results obtained in both experiments, while not confirmatory, provide several avenues for future investigation.
+Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of political bias in American news under the auspices of Moral Foundations Theory.
+This does not, however, rule out the possibility that news media is biased.
+As Mitchell et al.
+(2014) has demonstrated, self-reported political partisans are drawn to separate sources, but the present research was unable to offer any content-based explanations of this phenomenon.
+Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
+The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
+
+Despite the fact the results regarding political bias were inconclusive, the researchers still retain confidence in the overall structure of the methodology established in the current study.
+Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
+The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
+Additionally, multi-level models were necessary to control for the nested nature of the data where political lean encompassed several sources, which themselves encompassed numerous articles.
+
+Thus, the researchers' attention turned to the instrument used to detect differences.
+In the present study, the researchers utilized the Moral Foundations Dictionary, a metric developed from Moral Foundations Theory (Graham et al., 2009).
+Based upon the results obtained, it might be necessary to investigate alternative instruments that might better elucidate the differences of interest.
+Likewise, other theoretical perspectives may be better equipped to explain political differences in discourse.
+
+Tools such as these could be developed through the Linguistic Inquiry and Word Count program (LIWC) (Pennebaker et al., 2007).
+As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context (Graham et al., 2009).
+This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
+The authors established sound psychometric properties for the tool, implying its validity in several applications.
+For this reason, the researchers elected to utilize the MFD as their primary instrument.
+
+Other instruments could theoretically be developed through a LIWC analysis, including those that would be useful for analyzing political discourse.
+Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from Warriner et al.
+(2013).
+The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
+However, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
+Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
+
+There is, however, another theoretical framework that could prove useful when applied to the method established in the present research.
+Relational Frame Theory originates in applied behavior analysis, but there exists recent scholarship that demonstrates its potential usefulness in the political realm.
+Relational Frame Theory (RFT) holds that stimuli, including speech and discourse, elicit responses in terms of relationships to other stimuli, even when the stimuli do not otherwise appear to be related (Blackledge, 2014).
+For example, an individual's equivalent fear response to a venomous snake as well as a wooded area said to \enquote{contain snakes} represents \enquote{mutual entailment.} That is, the fear response is an effect of both the snake and environment stimuli, which cause the fear response.
+\enquote{Combinatorial entailment} can be represented by a fear response elicited by a novel stimulus whose relationship to a well-known stimulus elicits a certain response (Blackledge, 2014).
+In the snake example, if another stimulus (Stimulus A), were said to be \enquote{worse than} the snake, the relationship between A and the snake would elicit a more severe fear response to Stimulus A.
+RFT utilizes a set of \enquote{families} describing the nature of these relationships.
+Such families include \enquote{coordinative,} establishing similarities between stimuli, and \enquote{distinctive,} implying fundamental differences between stimuli (Belisle, Paliliunas, Dixon, \& Tarbox, 2018).
+These families can be used to analyze networks of relational frames in discourse.
+
+Belisle et al.
+(2018) conducted a text analysis (using a computer algorithm) of several speeches made by four recent U.S.
+presidents under Relational Frame Theory.
+These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
+For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts (Belisle et al., 2018).
+At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
+In any case, this research appears to indicate that RFT might be useful for analyzing political news content similar to the method employed in the current study.
+
+Another apparent strength of RFT is its demonstrated effectiveness in the analysis of political discourse.
+Unlike the development of the Moral Foundations Dictionary, this application of RFT was performed on public facing political discourse that might be more similar to news articles than the Christian sermons upon which the MFD was compiled.
+Additionally, there would likely be greater overlap between the speeches analyzed in Belisle et al.
+(2018)'s work and political news, as the media often quotes speeches by the president.
+Furthermore, the types or \enquote{families} of relational frames could be used as the individual constructs much like the moral foundations in the present research.
+In order to conform with the method established for this study, their occurrence would need to be scored, probably as a percent.
+This would allow for an intuitive approach to weighting by \emph{z}-scored valence if needed.
+
+While Relational Frame Theory appears to represent a viable option for further research into political news analysis, there are some drawbacks.
+First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
+One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it was a theory designed to investigate not only moral differences but also political differences.
+While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
+
+In order to seriously consider RFT as a viable framework for this type of analysis, the researchers would like to be able to draw on further confirmatory evidence of the theory's utility in political discourse analysis.
+Specifically, analyses of more individuals than the four presidents addressed by Belisle et al.
+(2018) would be needed to further demonstrate RFT's applicability in this field.
+Also, though presidential speeches may be more similar to news articles than sermons, they are still a distinct form of discourse with different goals and audiences than news outlets.
+RFT's reliability across these forms appears to remain untested as of this writing.
+These potential shortcomings are testable and might be overcome through more research.
+As such, RFT's potential as a useful framework for political discourse analysis should not be discounted.
+
+The researchers aimed to utilize the Moral Foundations Dictionary and valence in the analysis of political news articles to determine whether or not bias was present.
+In Experiment 1, they tested general political news from four U.S.
+news sources - two liberal and two conservative.
+They were unable to find any significant evidence of political bias in that analysis.
+After adjusting the method to include more sources and specific topics for articles, including the Kavanaugh hearing and the government shutdown, the researchers were once again unable to uncover differences in MFD word use between conservative and liberal news sources.
+The results in the current study seem to demonstrate the MFD's weaknesses in applications to political discourse.
+MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
+In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, or through a different theoretical perspective such as Relational Frame Theory.
+Despite the results obtained in the current study, the researchers have reason to believe this line of inquiry warrants further investigation and that the correct method will one day be established.
+
+Never before has news media and discourse represented such fertile ground for psychological research.
+The plethora of options and the potential for misinformation present important challenges for American democracy in the twenty-first century.
+The potential divisions in American society resulting from an abundance of choices for sources of political information, coupled with the notion that public discourse seems to offer competing conceptions of objective truth, underscores the importance of research into the content of political news.
+Democracy functions effectively on the foundation an informed and engaged electorate.
+Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of citizens every day so that insights into the nature and consequences of political discourse can be more completely understood.
 
@@
 Retrieved from \url{https://thehill.com/homenews/campaign/427007-poll-majority-of-americans-hold-trump-and-republicans-responsible-for}
+
+\leavevmode\hypertarget{ref-Belisle2018}{}%
+Belisle, J., Paliliunas, D., Dixon, M.
+R., \& Tarbox, J.
+(2018).
+Feasibility of contextual behavioral speech analyses of US presidents: Inaugural addresses of Bill Clinton, George W.
+Bush, Barack Obama, and Donald Trump, 1993--2017.
+\emph{Journal of Contextual Behavioral Science}, \emph{10}(July), 14--18.
+doi:\href{https://doi.org/10.1016/j.jcbs.2018.07.002}{10.1016/j.jcbs.2018.07.002}
+
+\leavevmode\hypertarget{ref-Blackledge2014}{}%
+Blackledge, J.
+T.
+(2014).
+An introduction to relational frame theory: Basics and applications.
+\emph{The Behavior Analyst Today}, \emph{3}(4), 421--433.
+doi:\href{https://doi.org/10.1037/h0099997}{10.1037/h0099997}
 
@@
 (1975).
-Derivation of New Readability Formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted Personnel.
+Derivation of new readability formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy enlisted personnel.
 doi:\href{https://doi.org/10.21236/ADA006655}{10.21236/ADA006655}
@@
 \leavevmode\hypertarget{ref-Martin2019}{}%
-Martin, M. (2019). The Moral Question Of Trump's Border Wall : NPR. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
+Martin, M. (2019). The moral question opf Trump's border wall. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
 
@@
 (2018).
-Ford-Kavanaugh Ratings: Hearing Brings 20 Million viewers to cable and broadcast \textbar{} Hollywood Reporter.
+Ford-Kavanaugh Ratings: Hearing brings 20 million viewers to cable and broadcast \textbar{} Hollywood Reporter.
 Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
@@
 Suhler, C.
-L., Churchland, P., Joseph, C., Graham, J., \& Nosek, B.
+L., \& Churchland, P.
 (2011).
-Can Innate , Modular `` Foundations '' Explain Morality ?
-Challenges for Haidt ʼ s Moral Foundations Theory.
+Can innate, modular "foundations" explain morality?
+Challenges for Haidt's Moral Foundations Theory.
 \emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
+doi:\href{https://doi.org/10.1162/jocn.2011.21637}{10.1162/jocn.2011.21637}
 

### 2019-04-16 pilot_manuscript.Rmd
Made all the edits

@@
 They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
-In Experiment 2, the researchers will expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
@@
 The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included *z*-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula.
+Statistics calculated included average *z*-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
+Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula [@Kincaid1975].
 Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
@@
 Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
+The large standard deviations seem to indicate little to no presence of a difference in valence.
 *The New York Times* published the greatest number of articles as well as total words.
@@
 
-Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
+Articles pertaining to the Brett Kavanaugh Supreme Court confirmation hearing and the 2018-2019 U.S.
+Government shutdown were scraped from the websites of 10 U.S.
 news sources.
@@
 Words were subsequently matched with their valences from @Warriner2013.
-Depending on the results of @Jordan2019's research, alternative forms of the Moral Foundations Dictionary may be imported instead of the original dictionary.
+Depending on the results of @Jordan2019's multi-trait multi-method analysis of the MFD and the Moral Foundations Questionnaire, alternative forms of the Moral Foundations Dictionary with additional words may be imported instead of the original dictionary.
 
@@
 The researchers obtained the words' percent occurrence in the text.
-Once again, percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
+Percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
 
@@
 The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, *The Huffington Post* appears to have published only 27 articles while *NPR* published 757 articles on this topic.
+For example, *Sean hannity* appears to have published only 27 articles while *Breitbart* published 757 articles on this topic.
 Valence was found to be slightly positive across all sources.
-*Slate* produced the most total words with the most tokens on average.
-*Rush Limbaugh* featured the highest number of types on average.
-*The Blaze* was the most readable source on average by grade level while *Fox News* was the least readable.
-The standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
+*Fox News* produced the most total words with the most tokens on average.
+*Politico* featured the highest number of types on average.
+*Rush Limbaugh* was the most readable source on average by grade level while *Slate* was the least readable.
+The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
 
@@
 Once again, there was variation in the number of articles published by each source on this topic.
-*The Hugginton Post* and *The Blaze* published fewer than 100 articles while *Slate* published 1,013 articles.
-*Slate* again featured the most total words and mean tokens.
-*Rush Limbaugh* again had the most types on average.
-For this topic, *Slate* was the most readable while *The Huffington Post* was the least readable.
-For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
+*Sean Hannity*, *Rush Limbaugh*, and *The Blaze* published fewer than 100 articles while *Fox News* published 1,013 articles.
+*Fox News* again featured the most total words and mean tokens.
+*Politico* had the most types on average.
+For this topic, *Fox News* was the most readable while *Slate* was the least readable.
+For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
 
@@
 To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
-Once again, the researchers used the *nlme* library in *R* [@Pinheiro2017].
+The researchers used the *nlme* library in *R* [@Pinheiro2017].
 Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-MLMs were constructed from datasets compiled for both topics of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
-There were no other significant or practical effect of political lean for any of the other four moral foundations.
+Two separate MLMs were constructed from datasets compiled for each topic of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
+
+For the Kavanaugh topic, the multilevel model indicated the presence of a statistically significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
+There were no other significant or practical effects of political lean for any of the other four moral foundations.
 The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than conservative sources.
@@
 Within the theoretical framework of Moral Foundations Theory [@Haidt2007], the researchers attempted to devise a method leveraging the Moral Foundations Dictionary [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
-This method was carried out in several parts.
-First, the researchers collected the articles through web scraping techniques in *R* [@Wickham2016].
-Second, the text was processed using *ngram* and *tm* in *R* to render it in a form conducive to computerized statistical analysis [@Feinerer2017].
-Third, percent occurrence of words in the Moral Foundations Dictionary (MFD) was calculated on each source in order to establish how often words indicating endorsement of the five moral foundations appeared.
-Frequency of MFD word occurrence per article was weighted for valence by multiplying the scores by mean *z-scored* valence ratings from @Warriner2013.
-Finally, the researchers constructed multi-level models using *nlme* in *R* [@Pinheiro2017] for each foundation in which weighted percentages were predicted by each source's political lean.
+The researchers downloaded news article text from the web, processed the text, matched it with the Moral Foundations Dictionary words, and calculated average valence for words in each article.
+To analyze the data, the researchers constructed multi-level models for each foundation in which weighted percentages were predicted by each source's political lean.
 Individual source was held as a random intercept to control for correlated error.
@@
 
-In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political bias in U.S.
+In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political leanings in U.S.
 news sources.
@@
 The results obtained in both experiments, while not confirmatory, provide several avenues for future investigation.
-Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of political bias in American news under the auspices of Moral Foundations Theory.
+Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of an effect of political lean on American news writing under the auspices of Moral Foundations Theory.
 This does not, however, rule out the possibility that news media is biased.
@@
 The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-Additionally, multi-level models were necessary to control for the nested nature of the data where political lean encompassed several sources, which themselves encompassed numerous articles.
+This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
 
@@
 This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
-The authors established sound psychometric properties for the tool, implying its validity in several applications.
+The original authors of the MFD established sound psychometric properties for the tool, implying its validity in several applications.
 For this reason, the researchers elected to utilize the MFD as their primary instrument.
@@
 The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
-However, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
+James Pennebaker [-@Pennebaker2007], one of the creators of LIWC, has suggested the program could be applied to analyses of cognitive, social, and emotional states.
+Furthermore, there is some evidence LIWC can be used to detect deception, but the reliability of the program's accuracy in this regard (67%) calls this assertion into question [@Pennebaker2011].
+Despite the promising extent of LIWC's abilities, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
 Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
@@
 First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
+In other words, RFT represents one method by which to analyze political text, but with the caveat that the categories are not known to represent patterns of political ideology.
 One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it was a theory designed to investigate not only moral differences but also political differences.
@@
 In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, or through a different theoretical perspective such as Relational Frame Theory.
-Despite the results obtained in the current study, the researchers have reason to believe this line of inquiry warrants further investigation and that the correct method will one day be established.
 
 Never before has news media and discourse represented such fertile ground for psychological research.
-The plethora of options and the potential for misinformation present important challenges for American democracy in the twenty-first century.
-The potential divisions in American society resulting from an abundance of choices for sources of political information, coupled with the notion that public discourse seems to offer competing conceptions of objective truth, underscores the importance of research into the content of political news.
-Democracy functions effectively on the foundation an informed and engaged electorate.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of citizens every day so that insights into the nature and consequences of political discourse can be more completely understood.
+The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
+Along with this recent increase in the amount of text information, there is now an obligation on the part of researchers to devise proper methods for analyzing that text.
+Solid methodologies must be constructed and periodically improved to keep pace with evolving technologies.
+Likewise, a strong theoretical foundation is paramount to making sense of the current and future media ecosystem.
+Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
 

### 2019-04-16 pilot_manuscript.tex
Knitted the thesis and saved as Padfield Thesis

@@
 
-\authornote{William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
+\authornote{William Padfield is a master's degree candidate in
+Psychology at Missouri State University. This thesis partially fulfills
+the requirements for the Master of Science degree in Psychology.
 
 Correspondence concerning this article should be addressed to William E.
-Padfield, 901 S.
-National Ave, Springfield, MO, 65897.
-E-mail: \href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
+Padfield, 901 S. National Ave, Springfield, MO, 65897. E-mail:
+\href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
 
 \abstract{
-The media ecosystem has grown, and political opinions have diverged such that there are competing conceptions of objective truth.
-Commentators often point to political biases in news coverage as a catalyst for this political divide.
-The Moral Foundations Dictionary (MFD) facilitates identification of ideological leanings in text through frequency of the occurrence of certain words.
-Through web scraping, the researchers extracted articles from popular news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
-This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, the researchers gathered poltical articles from four sources.
-They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
-In Experiment 2, the researchers will expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
-Supreme Court Justice Brett Kavanaugh and the partial U.S.
-Goverment Shutdown of 2018-2019.
-Once again, no significant differences in moral or political endorsements were found.
+The media ecosystem has grown, and political opinions have diverged such
+that there are competing conceptions of objective truth. Commentators
+often point to political biases in news coverage as a catalyst for this
+political divide. The Moral Foundations Dictionary (MFD) facilitates
+identification of ideological leanings in text through frequency of the
+occurrence of certain words. Through web scraping, the researchers
+extracted articles from popular news sources' websites, calculated MFD
+word frequencies, and identified words' respective valences. This
+process attempts to uncover news outlets' positive or negative
+endorsements of certain moral dimensions concomitant with a particular
+ideology. In Experiment 1, the researchers gathered poltical articles
+from four sources. They were unable to reveal significant differences in
+moral or political endorsements, but they solidified the method to be
+employed in further research. In Experiment 2, the researchers expanded
+their number of sources to 10 and analyzed articles that pertain to two
+specific topics: the 2018 confirmation hearings of U.S. Supreme Court
+Justice Brett Kavanaugh and the partial U.S. Goverment Shutdown of
+2018-2019. Once again, no significant differences in moral or political
+endorsements were found.
 
@@
 
-In the United States, today's media landscape affords consumers a multitude of options for obtaining political news.
-Since the advent of cable news networks and the World Wide Web in the last decades of the twentieth century, consumers have gained access to an ever-expanding menagerie of news sources, many of which can be called up via a simple click, touch, or swipe.
-Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
-For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant, respectively.
-These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
-Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
-Specifically, the use of differing moral language in political articles might be an indicator of political bias in news media.
-
-Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
-Starting chiefly in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
-Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of \enquote{morality.} Concerns regarding operationalization remain an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
-
-\hypertarget{moral-foundations-theory}{%
-\subsection{Moral Foundations Theory}\label{moral-foundations-theory}}
-
-As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg (Haidt \& Graham, 2007).
-Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance (Kohlberg \& Hersh, 1977).
-Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
-Similarly, Kohlberg found people typically start with a \enquote{pre-conventional} understanding of morality during infancy in which children understand \enquote{right} and \enquote{wrong} purely in terms of how they interact with resultant experiences of rewards and punishment.
-Typically, people progress through several steps until they reach a \enquote{post-conventional} ethics.
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their \enquote{self-chosen ethical principles} (Kohlberg \& Hersh, 1977).
-From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality (Haidt \& Graham, 2007).
+In the United States, today's media landscape affords consumers a
+multitude of options for obtaining political news. Since the advent of
+cable news networks and the World Wide Web in the last decades of the
+twentieth century, consumers have gained access to an ever-expanding
+menagerie of news sources, many of which can be called up via a simple
+click, touch, or swipe. Concurrent with this growth in available news
+sources, concerns regarding political bias in news reporting have
+entered public consciousness. For example, commentators argue that
+networks including Fox News Channel and MSNBC communicate political news
+from a conservative and liberal slant, respectively. These purported
+biases have been a cause for concern given the potential for incomplete
+or inaccurate news reporting potentially resulting from these biases.
+Given the inherently moral nature of many political arguments and
+positions, bias in news reporting might manifest as differing moral
+appeals. Specifically, the use of differing moral language in political
+articles might be an indicator of political bias in news media.
+
+Morality and ethics have been of interest to thinkers, academics, and
+philosophers since antiquity. Starting chiefly in the twentieth century,
+a scientific approach to humans' understanding of morality emerged under
+the domain of psychology. Theories attempting to explain the development
+and application of people's moral intuitions built the foundation for
+the subfield of moral psychology. As the field developed, however,
+considerable debate has taken place regarding operational definitions of
+\enquote{morality.} Concerns regarding operationalization remain an
+issue in the field in the twenty-first century as researchers attempt to
+infer moral and political leanings from text and speech.
+
+\subsection{Moral Foundations Theory}\label{moral-foundations-theory}
+
+As a discipline, modern moral psychology started in the late 1960s with
+Lawrence Kohlberg (Haidt \& Graham, 2007). Kohlberg's research
+popularized his theory of the development of moral reasoning. This
+theory establishes the steps of moral reasoning through which humans
+proceed as their cognitive structures assume higher levels of
+sophistication and nuance (Kohlberg \& Hersh, 1977). Kohlberg borrowed
+from Jean Piaget's stages of cognitive development in which children
+progress from the sensorimotor through to the formal operations stage.
+Similarly, Kohlberg found people typically start with a
+\enquote{pre-conventional} understanding of morality during infancy in
+which children understand \enquote{right} and \enquote{wrong} purely in
+terms of how they interact with resultant experiences of rewards and
+punishment. Typically, people progress through several steps until they
+reach a \enquote{post-conventional} ethics. People who have reached the
+post-conventional stage are said to be able to weigh competing
+abstractions and reason their way to a conclusion that promotes justice
+based upon their \enquote{self-chosen ethical principles} (Kohlberg \&
+Hersh, 1977). From Kohlberg's perspective, issues of justice and
+fairness comprise the foundation of morality (Haidt \& Graham, 2007).
 This view persisted until it encountered criticism in the early 1980s.
 
-Kohlberg's conception of morality faced major scrutiny from psychologist Carol Gilligan.
-In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women (Haidt \& Graham, 2007).
-Gilligan drew attention to purported differences in the ways men and women are taught to relate to self and others.
-She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-She pushes back against Kohlberg's assumption that moral development replaces \enquote{rule of brute force,} as enforced by men, with the justice-based \enquote{rule of law.} According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law (Gilligan, 1982).
-Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
-Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring (Gilligan, 1982).
-This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring (Haidt \& Graham, 2007).
-While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
-
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain (Haidt \& Graham, 2007).
-The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals (Haidt \& Graham, 2007).
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007).
-
-In their brief overview of the history of moral psychology, Graham, Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
-Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
-Such a system, they argued, did not account for moral concerns outside of the western world (Graham et al., 2009).
-Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.), and the \enquote{ethic of divinity} - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
-In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
-
-Haidt and Graham settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology (Graham et al., 2011).
-The researchers attempted to locate virtues and morals corresponding to \enquote{evolutionary thinking.} For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the \emph{fairness/reciprocity} foundation.
-Additionally, evolutionary literature on disgust and its correlation to human behavior regarding food and sex informed the \emph{purity/sanctity} foundation (Graham et al., 2011).
-The researchers identified the five \enquote{top candidates} for the foundations of human cultures' morality (Graham et al., 2011).
-
-The first two foundations (\emph{harm/care} and \emph{fairness/reciprocity}) are termed the \enquote{individualizing foundations,} as they are centered on the concerns of individuals rather than groups.
-\emph{harm/care} represents an endorsement of compassion and kindness, while opposing cruelty and harm.
-\emph{Fairness/reciprocity} represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
-The other three foundations (\emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}) are the \enquote{binding} foundations, owing to their focus on group-related concerns, rather than those of individuals.
-\emph{Ingroup/loyalty} represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
-\emph{Authority/respect} represents an endorsement of social hierarchies and traditions while denigrating disobedience.
-Finally, \emph{purity/sanctity} represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony (Haidt \& Graham, 2007).
-Liberals tend to endorse the individualizing foundations more than conservatives.
-Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
-It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations (Graham et al., 2009).
-
-Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-Suhler and Churchland (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
-First, the authors challenge Haidt and Graham (2007)'s claims the moral intuitions represented by MFT are innate and modular.
-Suhler and Churchland (2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
-Rather, behaviors likely result from interactions between genetics and experience (Suhler \& Churchland, 2011).
-According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
-Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler \& Churchland, 2011).
-However, as with innateness, there is little neurobiological evidence to support modularity.
-
-Suhler and Churchland (2011) also criticized the content and taxonomy of the five foundations.
-The authors criticize Haidt and Graham (2007)'s omissions of additional foundations, including \emph{industry} and \emph{modesty}, claiming these concepts are moralized in many societies worldwide.
-Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-For example, Suhler and Churchland (2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
-Work by Graham et al.
-(2011) might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
-Finally, Suhler and Churchland (2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
-In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler \& Churchland, 2011).
-
-These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
-The current authors argue these criticisms are especially valid when considered alongside questions regarding the Moral Foundations Dictionary they state herein.
-However, there exists compelling evidence regarding the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
-This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary.
-
-\hypertarget{moral-foundations-dictionary}{%
-\subsection{Moral Foundations Dictionary}\label{moral-foundations-dictionary}}
-
-In order to capture language's role in moral and political reasoning, Graham et al.
-(2009) formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
-The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-The researchers created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count (LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
-The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: \enquote{Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus} (Graham et al., 2009).
-This sentence added to the \emph{authority/respect} total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
-The researchers eliminated this sentence from the \emph{authority/respect} raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions (Graham et al., 2009).
-
-Similar to previous research on Moral Foundations Theory, liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than conservative ministers.
-Conversely, conservative ministers used \emph{authority} and \emph{purity} words more often than liberal ministers.
-However, conservative ministers did not use \emph{ingroup/loyalty} words more than liberals.
-Rather, liberal ministers used words pertaining to \emph{ingroup/loyalty}, but in contexts that promote rebellion and independence - causes \emph{opposite} to positive endorsements of that foundation (Graham et al., 2009).
-
-To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurrence of words in a given text from the foundation's respective word list.
-As such, most analyses assume that zero percent occurrence is indicative of no endorsement, while any non-zero percent occurrence indicates endorsement of the foundation.
-This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
-A quick glance at the MFD words for \emph{harm/care} reveals the presence of words that are more closely associated with universally accepted conceptions of \emph{harm} over \emph{care} and vice-versa (Graham et al., 2009).
-For example, the word \enquote{cruel} has relatively negative connotations compared to \enquote{benefit.} For the \emph{harm/care} foundation, it is conceivable that use of the word \enquote{cruel} might indicate a greater attentional focus of the idea of \emph{harm} rather than \emph{care}.
-
-For \emph{harm/care}, the definition of the foundation, as well as its name, clearly distinguishes between two somewhat opposite sides of an attentional continuum, with \emph{harm} on the negative end and \emph{care} on the positive side.
-In other words, the entries in the MFD for \emph{harm/care} have somewhat clear positive and negative valences.
-The same pattern can be seen in the MFD entries for the other four foundations.
-\emph{Purity/sanctity} features words that likely have a negative valence to most observers, including \enquote{disease} and \enquote{trash,} along with more positive words, including \enquote{right} and \enquote{sacred} (Graham et al., 2009).
-These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from \emph{harm/care}: \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}.
-The latter four foundations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of \emph{fairness/reciprocity}.
-
-When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
-How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
-If 2\% of a politician's speech features positive words (i.e., \enquote{benefit} and \enquote{defend}) from the MFD \emph{harm/care} list, how can researchers be sure the level and nature of the speaker's \enquote{endorsement} of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the \emph{harm/care} list?
-They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the \emph{harm/care} spectrum.
-
-This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The MFQ, which was developed subsequent to the MFD, measures individuals' endorsements of each of the foundations using a six-point scale (Graham et al., 2011).
-The questionnaire is made up of judgment items and relevance items.
-Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
-An example of such a statement reads: \enquote{It can never be right to kill another human being} (Graham et al., 2011).
-Relevance items gauge the respondent's opinion regarding the importance of foundation-related concerns.
-For example, the respondent is directed to rate how important the following situation is to their sense of morals: \enquote{whether or not someone did something disgusting.} This example measures the relevance of the \emph{purity/sanctity} foundations.
-Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ (Graham et al., 2011).
-
-The Moral Foundations Questionnaire has been validated by multiple researchers.
-Likewise, its five-factor structure has been demonstrated to fit data in multiple countries (Davies, Sibley, \& Liu, 2014; Graham et al., 2011).
-In their article introducing the 30-item MFQ, Graham et al.
-(2011) conducted an exploratory factor analysis (EFA) and found that a five-factor model fit the data better than a one, two, or three-factor model.
-Davies et al.
-(2014) conducted a confirmatory factor analysis (CFA) of the MFQ with a sample from New Zealand and likewise found the five-factor model provided the best fit.
-While Davies et al.
-(2014) concede the US and New Zealand share many similarities as Western nations, which could raise questions regarding the validity of the MFQ in non-Western nations.
-However, there are striking differences between the two countries, including the lack of a two-party political system in New Zealand, that provide grounds for claiming the MFQ generalizes beyond the United States.
-Furthermore, Graham et al.
-(2011) claim to find a \enquote{reasonable} degree of generalizability for the MFQ across participants from many different regions in the world.
-These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler and Churchland (2011) should still be taken into account in studies involving the theory.
-
-The aforementioned ambiguity of the Moral Foundations Dictionary as an instrument becomes clearer upon closer examination of the items in the Moral Foundations Questionnaire.
-One item under the \emph{fairness/reciprocity} judgment subscale reads, \enquote{Justice is the most important requirement for a society} (Graham et al., 2011).
-The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning \enquote{strongly disagree} at 1 to \enquote{strongly agree} at 6.
-While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
-When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they \enquote{slightly agree} with the statement (Graham et al., 2011).
-This specificity is not present in most analyses involving the MFD and percent occurrence, unless they also take into account the valence of the words used in the text or speech of interest.
-
-\hypertarget{valence}{%
-\subsection{Valence}\label{valence}}
-
-Borrowing from Osgood's work in the 1950s, Bradley and Lang (1999) recognized valence as one of three related dimensions comprising emotion when developing their Affective Norms for English Words (ANEW).
-As mentioned before, \enquote{valence,} the first dimension, denotes the pleasantness of a given word.
-\enquote{Arousal,} the second dimension, describes the stimulating nature of a word.
-Lastly, \enquote{dominance} or \enquote{control} describes the extent to which a word makes one feel in or out of control (Bradley \& Lang, 1999).
-The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Mannikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
-
-Participants saw the stimulus word and responded on each scale.
-The valence scale featured a smiling figure at one end (representing pleasantness) and a frowning figure at the other end (for unpleasantness).
-The arousal scale had a \enquote{wide-eyed} figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
-Finally, the dominance scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end (Bradley \& Lang, 1999).
-The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words (Bradley \& Lang, 1999).
-ANEW represented an important first step in establishing affective norms for large numbers of English words.
-However, later researchers found the 1,040-word list to be limiting for a language consisting of thousands of words.
-
-Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e., \enquote{watch} rather than \enquote{watched} and \enquote{watching}).
-The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory (Warriner et al., 2013).
-They argue the list of words included in ANEW is sufficient for small-scale factorial research designs, but the list is \enquote{prohibitively small} for larger-scale \enquote{megastudies} that are common in psycholinguistic research today (Warriner et al., 2013).
-
-In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media (New, Brysbaert, Veronis, \& Pallier, 2007).
-This data collection resulted in the final list of 13,915 lemmas.
-Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
-Participants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
-The researchers used a nine-point scale similar to the one used by Bradley and Lang (1999) when collecting ratings for ANEW (Warriner et al., 2013).
+Kohlberg's conception of morality faced major scrutiny from psychologist
+Carol Gilligan. In 1982, Gilligan criticized Kohlberg's theory on the
+grounds that it focused solely on the moral concerns of men, and that it
+ignored those of women (Haidt \& Graham, 2007). Gilligan drew attention
+to purported differences in the ways men and women are taught to relate
+to self and others. She offered a historic argument contending women
+have traditionally filled roles related to caring and nurturing. She
+pushes back against Kohlberg's assumption that moral development
+replaces \enquote{rule of brute force,} as enforced by men, with the
+justice-based \enquote{rule of law.} According to Gilligan, this
+assumption implies women are less morally developed, owing to their
+absence both in masculine displays of violence as well as in enforcement
+of the law (Gilligan, 1982). Gilligan argues for the existence of a
+distinct, but equal development process that women and girls must
+undergo in order to develop their moral selves. Stark differences in the
+ways women are traditionally taught to interact with their social world
+cause them to develop ethical systems based upon their non-aggressive
+relationships with others. Gilligan thus asserted morality was built
+upon an alternative moral foundation: caring (Gilligan, 1982). This
+debate between competing conceptions of morality did not resolve until
+Gilligan and Kohlberg conceded the existence of two moral foundations:
+justice and caring (Haidt \& Graham, 2007). While this new direction in
+moral psychology appeared to represent a more inclusive outlook on the
+construct, these novel ideas would soon be challenged on the grounds of
+its apparent western-centric outlook.
+
+Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a
+method by which to capture the entirety of humans' moral domain (Haidt
+\& Graham, 2007). The researchers argued older theories of moral
+psychology were focused primarily on issues of justice, fairness, and
+caring - individually focused foundations of morality that align with
+the beliefs of political liberals (Haidt \& Graham, 2007). In other
+words, moral psychology ignored the valid moral foundations of
+conservatives. Moral Foundations Theory (MFT) holds that people's moral
+domain can be mapped by quantifying their endorsement of five moral
+foundations: \emph{harm/care}, \emph{fairness/reciprocity},
+\emph{ingroup/loyalty}, \emph{authority/respect}, and
+\emph{purity/sanctity} (Haidt \& Graham, 2007).
+
+In their brief overview of the history of moral psychology, Graham,
+Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's
+objections to moral psychology as it stood in the late 1980s. Their
+criticism centered on the fact moral psychology concerned itself with
+issues regarding justice and individuals' rights. Such a system, they
+argued, did not account for moral concerns outside of the western world
+(Graham et al., 2009). Individually focused concerns can be grouped
+under an overarching \enquote{ethic of autonomy,} which was thought to
+be one of three ethics upon which humans base moral decisions. The other
+two ethics were the \enquote{ethic of community} (comprising one's duty
+to their family, tribe, etc.), and the \enquote{ethic of divinity} -
+representing one's duty not to defile their God-given body and soul
+(Graham et al., 2009). In the 2000s, Haidt and Graham (2007) took this
+line of reasoning further in their assertion that moral psychology
+favored certain political ideologies over others.
+
+Haidt and Graham settled on these specific foundations after the
+completion of a literature survey of research in anthropology and
+evolutionary psychology (Graham et al., 2011). The researchers attempted
+to locate virtues and morals corresponding to \enquote{evolutionary
+thinking.} For instance, the researchers cited Mauss' work on reciprocal
+gift-giving, which informed the establishment of the
+\emph{fairness/reciprocity} foundation. Additionally, evolutionary
+literature on disgust and its correlation to human behavior regarding
+food and sex informed the \emph{purity/sanctity} foundation (Graham et
+al., 2011). The researchers identified the five \enquote{top candidates}
+for the foundations of human cultures' morality (Graham et al., 2011).
+
+The first two foundations (\emph{harm/care} and
+\emph{fairness/reciprocity}) are termed the \enquote{individualizing
+foundations,} as they are centered on the concerns of individuals rather
+than groups. \emph{harm/care} represents an endorsement of compassion
+and kindness, while opposing cruelty and harm.
+\emph{Fairness/reciprocity} represents concerns centered on guaranteeing
+individual rights as well as justice and equality among all people. The
+other three foundations (\emph{ingroup/loyalty},
+\emph{authority/respect}, and \emph{purity/sanctity}) are the
+\enquote{binding} foundations, owing to their focus on group-related
+concerns, rather than those of individuals. \emph{Ingroup/loyalty}
+represents endorsements of patriotism and heroism and discourages
+nonconformity and dissent. \emph{Authority/respect} represents an
+endorsement of social hierarchies and traditions while denigrating
+disobedience. Finally, \emph{purity/sanctity} represents concerns
+regarding chastity and piety, while discouraging vices and indulgences,
+including lust, avarice, and gluttony (Haidt \& Graham, 2007). Liberals
+tend to endorse the individualizing foundations more than conservatives.
+Conservatives, on the other hand, tend to endorse the binding
+foundations more than liberals. It should be noted, however,
+conservatives also tend to endorse all five foundations equally,
+implying they base moral judgments on all foundations (Graham et al.,
+2009).
+
+Moral Foundations Theory has received criticism on the grounds that its
+assumptions regarding moral intuitions have little empirical basis.
+Suhler and Churchland (2011) list several potential weaknesses of MFT
+that they argue might threaten the theory's validity. First, the authors
+challenge Haidt and Graham (2007)'s claims the moral intuitions
+represented by MFT are innate and modular. Suhler and Churchland (2011)
+claim that advances in biological sciences (embryology and microbiology,
+specifically) make it more difficult for researchers to claim any one
+trait is either innate or learned through experience. Rather, behaviors
+likely result from interactions between genetics and experience (Suhler
+\& Churchland, 2011). According to the authors, without solid data
+supporting the innateness of moral foundations, Haidt and Graham have
+little from which to make such a claim. Similarly, Haidt and Graham
+(2007) rely on evidence authored by evolutionary psychologists to make a
+\enquote{strong modularity claim} (Suhler \& Churchland, 2011). However,
+as with innateness, there is little neurobiological evidence to support
+modularity.
+
+Suhler and Churchland (2011) also criticized the content and taxonomy of
+the five foundations. The authors criticize Haidt and Graham (2007)'s
+omissions of additional foundations, including \emph{industry} and
+\emph{modesty}, claiming these concepts are moralized in many societies
+worldwide. Likewise, the authors question whether or not the foundations
+are sufficiently distinct as to stand as their own foundation. For
+example, Suhler and Churchland (2011) posit that \emph{ingroup/loyalty}
+is merely a group-focused version of \emph{harm/care}. Work by Graham et
+al. (2011) might serve to rebut this criticism, as the researchers found
+their original five-factor structure seemed to best fit the data when
+validating the Moral Foundations Questionnaire. Finally, Suhler and
+Churchland (2011) point out that particular concepts related to a
+foundation, including \enquote{anger} in \emph{fairness/reciprocity} and
+\enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any
+of the other foundations as well. In other words, it becomes difficult
+to recognize a particular concept as indicative of any one foundation
+when, in theory, they could be applied to all five (Haidt \& Graham,
+2007; Suhler \& Churchland, 2011).
+
+These criticisms of Moral Foundations Theory are valid and should be
+taken into consideration when conducting research with instruments
+derived from MFT. The current authors argue these criticisms are
+especially valid when considered alongside questions regarding the Moral
+Foundations Dictionary they state herein. However, there exists
+compelling evidence regarding the validity of Moral Foundations Theory,
+albeit regarding its application solely through the Moral Foundations
+Questionnaire. This evidence is discussed within a brief explanation of
+the Moral Foundations Questionnaire and its relationship to the Moral
+Foundations Dictionary.
+
+\subsection{Moral Foundations
+Dictionary}\label{moral-foundations-dictionary}
+
+In order to capture language's role in moral and political reasoning,
+Graham et al. (2009) formulated the Moral Foundations Dictionary (MFD)
+in order to capture moral reasoning and justification as used in speech
+and text. The MFD is composed of 259 words, with around 50 words
+assigned to each of the five foundations. The researchers created a
+preliminary list of words that they believed would be associated with
+the five foundations. Then, using the Linguistic Inquiry and Word Count
+(LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they
+analyzed transcripts of liberal and conservative Christian sermons in
+order to obtain frequencies of the occurrence of words from the
+researchers' initial list. The researchers manually checked the results
+from LIWC in order to make sure the results make sense given the
+contexts and rhetorical devices used in the sermons, as word frequency
+analysis ignores sentence context. The researchers offered the following
+example from a Unitarian sermon as a demonstration of ambiguous
+statements requiring human verification: \enquote{Don't let some
+self-interested ecclesiastical or government authority tell you what to
+believe, but read the Bible with your own eyes and open your heart
+directly to Jesus} (Graham et al., 2009). This sentence added to the
+\emph{authority/respect} total in LIWC's analysis, but it appears to
+suggest that one should reject authority in this context. The
+researchers eliminated this sentence from the \emph{authority/respect}
+raw count on account of this discrepancy between the use of
+authority-related words and the speaker's clear intentions (Graham et
+al., 2009).
+
+Similar to previous research on Moral Foundations Theory, liberal
+ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words
+more often than conservative ministers. Conversely, conservative
+ministers used \emph{authority} and \emph{purity} words more often than
+liberal ministers. However, conservative ministers did not use
+\emph{ingroup/loyalty} words more than liberals. Rather, liberal
+ministers used words pertaining to \emph{ingroup/loyalty}, but in
+contexts that promote rebellion and independence - causes
+\emph{opposite} to positive endorsements of that foundation (Graham et
+al., 2009).
+
+To this point, most text analysis utilizing the Moral Foundations
+Dictionary operationalizes endorsement of any one of the foundations as
+percent occurrence of words in a given text from the foundation's
+respective word list. As such, most analyses assume that zero percent
+occurrence is indicative of no endorsement, while any non-zero percent
+occurrence indicates endorsement of the foundation. This operational
+definition may not be sufficient in describing the true nature of the
+writer or speaker's endorsement of one of the sets of moral intuitions.
+A quick glance at the MFD words for \emph{harm/care} reveals the
+presence of words that are more closely associated with universally
+accepted conceptions of \emph{harm} over \emph{care} and vice-versa
+(Graham et al., 2009). For example, the word \enquote{cruel} has
+relatively negative connotations compared to \enquote{benefit.} For the
+\emph{harm/care} foundation, it is conceivable that use of the word
+\enquote{cruel} might indicate a greater attentional focus of the idea
+of \emph{harm} rather than \emph{care}.
+
+For \emph{harm/care}, the definition of the foundation, as well as its
+name, clearly distinguishes between two somewhat opposite sides of an
+attentional continuum, with \emph{harm} on the negative end and
+\emph{care} on the positive side. In other words, the entries in the MFD
+for \emph{harm/care} have somewhat clear positive and negative valences.
+The same pattern can be seen in the MFD entries for the other four
+foundations. \emph{Purity/sanctity} features words that likely have a
+negative valence to most observers, including \enquote{disease} and
+\enquote{trash,} along with more positive words, including
+\enquote{right} and \enquote{sacred} (Graham et al., 2009). These
+dichotomies, however, bring up other questions regarding the definition
+and names of the other four foundations apart from \emph{harm/care}:
+\emph{fairness/reciprocity}, \emph{ingroup/loyalty},
+\emph{authority/respect}, and \emph{purity/sanctity}. The latter four
+foundations have names that are harder to understand as a valence
+continuum, as the concepts in the names are more similar, even to the
+point of being virtually synonymous in the case of
+\emph{fairness/reciprocity}.
+
+When considering the issue of positive versus negative valence in MFD
+words, the question of how texts are analyzed vis-a-vis the MFD remains.
+How can raw percentage of MFD word occurrence capture the valence and
+focus of the writer or speaker? If 2\% of a politician's speech features
+positive words (i.e., \enquote{benefit} and \enquote{defend}) from the
+MFD \emph{harm/care} list, how can researchers be sure the level and
+nature of the speaker's \enquote{endorsement} of the foundation equals
+that of another politician whose speech contained negatively connoted
+MFD words from the \emph{harm/care} list? They would have equal
+endorsements as far as the numbers are concerned, but the words used and
+focus given are on opposite sides of the \emph{harm/care} spectrum.
+
+This issue is compounded by the fact the Moral Foundations Questionnaire
+(MFQ) and its subscales assume endorsement lies on a continuum. The MFQ,
+which was developed subsequent to the MFD, measures individuals'
+endorsements of each of the foundations using a six-point scale (Graham
+et al., 2011). The questionnaire is made up of judgment items and
+relevance items. Judgment items are phrased such that the respondent
+signals their agreement or disagreement with straightforward statements.
+An example of such a statement reads: \enquote{It can never be right to
+kill another human being} (Graham et al., 2011). Relevance items gauge
+the respondent's opinion regarding the importance of foundation-related
+concerns. For example, the respondent is directed to rate how important
+the following situation is to their sense of morals: \enquote{whether or
+not someone did something disgusting.} This example measures the
+relevance of the \emph{purity/sanctity} foundations. Each foundation has
+a judgment and relevance subscale, totaling 10 subscales for the MFQ
+(Graham et al., 2011).
+
+The Moral Foundations Questionnaire has been validated by multiple
+researchers. Likewise, its five-factor structure has been demonstrated
+to fit data in multiple countries (Davies, Sibley, \& Liu, 2014; Graham
+et al., 2011). In their article introducing the 30-item MFQ, Graham et
+al. (2011) conducted an exploratory factor analysis (EFA) and found that
+a five-factor model fit the data better than a one, two, or three-factor
+model. Davies et al. (2014) conducted a confirmatory factor analysis
+(CFA) of the MFQ with a sample from New Zealand and likewise found the
+five-factor model provided the best fit. While Davies et al. (2014)
+concede the US and New Zealand share many similarities as Western
+nations, which could raise questions regarding the validity of the MFQ
+in non-Western nations. However, there are striking differences between
+the two countries, including the lack of a two-party political system in
+New Zealand, that provide grounds for claiming the MFQ generalizes
+beyond the United States. Furthermore, Graham et al. (2011) claim to
+find a \enquote{reasonable} degree of generalizability for the MFQ
+across participants from many different regions in the world. These two
+bodies of work also provide the best available evidence that the five
+moral foundations are sufficiently distinct from one another, though
+broader criticisms of MFT raised by Suhler and Churchland (2011) should
+still be taken into account in studies involving the theory.
+
+The aforementioned ambiguity of the Moral Foundations Dictionary as an
+instrument becomes clearer upon closer examination of the items in the
+Moral Foundations Questionnaire. One item under the
+\emph{fairness/reciprocity} judgment subscale reads, \enquote{Justice is
+the most important requirement for a society} (Graham et al., 2011). The
+survey respondent must select a number on a scale from 1 to 6 indicating
+responses spanning \enquote{strongly disagree} at 1 to \enquote{strongly
+agree} at 6. While the scales in the MFQ do not represent true valence
+as it pertains to individual words, it does allow for a greater degree
+of specificity in terms of an individual's endorsement of a particular
+moral foundation. When a respondent selects a 4 for the aforementioned
+MFQ statement, they clearly are indicating they \enquote{slightly agree}
+with the statement (Graham et al., 2011). This specificity is not
+present in most analyses involving the MFD and percent occurrence,
+unless they also take into account the valence of the words used in the
+text or speech of interest.
+
+\subsection{Valence}\label{valence}
+
+Borrowing from Osgood's work in the 1950s, Bradley and Lang (1999)
+recognized valence as one of three related dimensions comprising emotion
+when developing their Affective Norms for English Words (ANEW). As
+mentioned before, \enquote{valence,} the first dimension, denotes the
+pleasantness of a given word. \enquote{Arousal,} the second dimension,
+describes the stimulating nature of a word. Lastly, \enquote{dominance}
+or \enquote{control} describes the extent to which a word makes one feel
+in or out of control (Bradley \& Lang, 1999). The researchers developed
+ANEW by presenting participants with a list of 100-150 words and asking
+for them to rate the word on all three dimensions using the
+Self-Assessment Mannikin (SAM), which allows ratings along either a
+nine-point scale when using traditional paper instruments or a
+twenty-point scale when using a computerized version.
+
+Participants saw the stimulus word and responded on each scale. The
+valence scale featured a smiling figure at one end (representing
+pleasantness) and a frowning figure at the other end (for
+unpleasantness). The arousal scale had a \enquote{wide-eyed} figure at
+one end with a sleepy figure at the other, representing stimulating and
+unstimulating respectively. Finally, the dominance scale featured a
+large figure, indicating the highest degree of control, at one end and a
+small figure, indicating a lack of control, at the other end (Bradley \&
+Lang, 1999). The end result of this procedure yielded affective norms
+along the three dimensions for 1,040 English words (Bradley \& Lang,
+1999). ANEW represented an important first step in establishing
+affective norms for large numbers of English words. However, later
+researchers found the 1,040-word list to be limiting for a language
+consisting of thousands of words.
+
+Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the
+list of words with affective norms to 13,915 English lemmas, the base
+forms of words without inflection (i.e., \enquote{watch} rather than
+\enquote{watched} and \enquote{watching}). The researchers recognized
+the importance of affective norms in several areas of study, including
+emotion, language processing, and memory (Warriner et al., 2013). They
+argue the list of words included in ANEW is sufficient for small-scale
+factorial research designs, but the list is \enquote{prohibitively
+small} for larger-scale \enquote{megastudies} that are common in
+psycholinguistic research today (Warriner et al., 2013).
+
+In order to source a large number of lemmas for affective ratings, the
+researchers drew from several validated sources. These include the
+30,000 lemmas with age-of-acquisition (average age at which a particular
+word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and
+Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US
+corpus consisting of subtitles from various forms of visual media (New,
+Brysbaert, Veronis, \& Pallier, 2007). This data collection resulted in
+the final list of 13,915 lemmas. Lists of 346-350 words were presented
+to participants recruited through the Amazon Mechanical Turk subject
+pool. Participants rated the words along one of the three dimensions,
+unlike the ANEW project in which participants rated each word along all
+three dimensions at once. The researchers used a nine-point scale
+similar to the one used by Bradley and Lang (1999) when collecting
+ratings for ANEW (Warriner et al., 2013).
 
 The researchers noted several points of interest upon observing ratings.
-First, they found that valence and dominance ratings had a negative skew, indicating more words elicited feelings of happiness and control than their respective opposites.
-Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
-This U-shape indicates words with high degrees of positivity and negativity elicited higher arousal (Warriner et al., 2013).
-These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
-
-Warriner and Kuperman (2015) utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in language.
-The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, the Corpus for Contemporary American English (COCA), the British National Corpus (BNC), Touchstone Applied Science Associates, Inc.~Corpus (TASA), and the corpus used for the Hyperspace Analogue to Language model (HAL), the researchers found that words with positive valence were also used more frequently (Warriner \& Kuperman, 2015).
-While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the Warriner et al.
-(2013) list in emotional studies.
+First, they found that valence and dominance ratings had a negative
+skew, indicating more words elicited feelings of happiness and control
+than their respective opposites. Also, when examining the relationship
+between valence and arousal ratings, the researchers found a U-shaped
+relationship. This U-shape indicates words with high degrees of
+positivity and negativity elicited higher arousal (Warriner et al.,
+2013). These observations along with the now-greatly expanded list of
+affective norms has been applied to several lines of inquiry in
+psycholinguistics.
+
+Warriner and Kuperman (2015) utilized the new affective norms list in
+order to investigate the validity of the Pollyanna hypothesis, or the
+prevalence of a generally optimistic outlook in humans as reflected in
+language. The researchers were able to conclude the existence of a
+greater number of positive-valence English words in the list of 13,915
+lemmas. Additionally, after observing token frequency in a number of
+text corpora, including SUBTLEX-US, the Corpus for Contemporary American
+English (COCA), the British National Corpus (BNC), Touchstone Applied
+Science Associates, Inc. Corpus (TASA), and the corpus used for the
+Hyperspace Analogue to Language model (HAL), the researchers found that
+words with positive valence were also used more frequently (Warriner \&
+Kuperman, 2015). While the researchers concede the possibility of an
+acquiescence bias in ratings as a possible explanation for the observed
+positivity bias, this investigation represents one application of the
+Warriner et al. (2013) list in emotional studies.
 
 In addition to applications in emotion research, the Warriner et al.
-(2013) norms have been utilized in cognitive research as well.
-One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
-The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks - two cognitive processing tasks wherein a participant has to read aloud or judge a word for its lexicality).
-First, Kuperman et al.
-(2014) found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
-The researchers also concluded that words causing higher arousal tend to have slower decision times than less-arousing words.
-They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
-They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
-Finally, Kuperman et al.
-(2014) found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks (Kuperman et al., 2014).
-This research serves as further evidence that the Warriner et al.
-(2013) list can be used for research inquiries both within and without the field of psycholinguistics.
-
-In the present studies, the researchers used the Warriner et al.
-(2013) list in order to denote the valence of the words appearing in the news articles scraped from the internet.
-Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
-The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
-Specifically, valences were used to weight the MFD words by their relative degree of positivity or negativity.
-Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
-
-\hypertarget{news-media-and-politics}{%
-\subsection{News Media and Politics}\label{news-media-and-politics}}
-
-Research into politics, language, and media has illuminated the complex relationships between all three.
-Any politically-oriented discussion of word occurrence as an implication of moral or political position assumes that language and ideology are intrinsically linked.
-Deborah Cameron (2006) points out the expressive nature of ideological beliefs and how that expression is conveyed through language, thus implying a connection between ideology and language.
-She goes on to criticize the notion that language is either the \enquote{pre-existing raw material} used to shape ideologies or the \enquote{post-hoc vehicle} for their propagation.
-Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies (Cameron, 2006).
-Owing to the fact the Moral Foundations Dictionary was developed in order to assess the moral, which includes the ideological, orientation of discourse, its purported ability to assess parts of the structure of language (vocabulary) for ideological lean is of chief interest to the researchers in the present study.
-
-The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S., Druckman, Jacobs, and Ostermeier (2004) considered political \enquote{issues} as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-According to the researchers, \enquote{image} priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality (Druckman et al., 2004).
-The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
-The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
-
-They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
-Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence (Druckman et al., 2004).
-The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g., priming) issues related to energy, defense, and the economy.
-This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
+(2013) norms have been utilized in cognitive research as well. One
+cognition-based study investigates the relationship between emotion and
+response latencies in word recognition. Kuperman, Estes, Brysbaert, and
+Warriner (2014) sought to use these new norms to fill in the knowledge
+gaps regarding variance in word recognition. The researchers drew
+several conclusions regarding emotion and word recognition (specifically
+in naming and lexical decision tasks - two cognitive processing tasks
+wherein a participant has to read aloud or judge a word for its
+lexicality). First, Kuperman et al. (2014) found slower decision-making
+and reading times in negative-valence words, faster times in neutral
+words, and even faster times in words with positive valence. The
+researchers also concluded that words causing higher arousal tend to
+have slower decision times than less-arousing words. They found valence
+had a stronger effect on recognition than arousal (both effects were
+independent, not interactive). They found an interaction between emotion
+and word frequency such that valence and arousal are more effective on
+lower frequency words than high frequency words. Finally, Kuperman et
+al. (2014) found a greater effect of valence and arousal on response
+latency for lexical decision tasks than for naming tasks (Kuperman et
+al., 2014). This research serves as further evidence that the Warriner
+et al. (2013) list can be used for research inquiries both within and
+without the field of psycholinguistics.
+
+In the present studies, the researchers used the Warriner et al. (2013)
+list in order to denote the valence of the words appearing in the news
+articles scraped from the internet. Valence was considered as another
+independent variable and its relationship with the words comprising the
+Moral Foundations Dictionary were of chief interest to the researchers.
+The valence was used as a means to determine whether individual words in
+the MFD represented more positive aspects of their respective foundation
+or if they denoted a more negative aspect of the foundation.
+Specifically, valences were used to weight the MFD words by their
+relative degree of positivity or negativity. Incorporating word valence
+into a study involving the MFD is meant to alleviate some of the issues
+regarding the aforementioned ambiguity regarding the words in the Moral
+Foundations Dictionary.
+
+\subsection{News Media and Politics}\label{news-media-and-politics}
+
+Research into politics, language, and media has illuminated the complex
+relationships between all three. Any politically-oriented discussion of
+word occurrence as an implication of moral or political position assumes
+that language and ideology are intrinsically linked. Deborah Cameron
+(2006) points out the expressive nature of ideological beliefs and how
+that expression is conveyed through language, thus implying a connection
+between ideology and language. She goes on to criticize the notion that
+language is either the \enquote{pre-existing raw material} used to shape
+ideologies or the \enquote{post-hoc vehicle} for their propagation.
+Rather, the structure of language itself is shaped by ideology and
+social processes even when it is used to explain or express ideologies
+(Cameron, 2006). Owing to the fact the Moral Foundations Dictionary was
+developed in order to assess the moral, which includes the ideological,
+orientation of discourse, its purported ability to assess parts of the
+structure of language (vocabulary) for ideological lean is of chief
+interest to the researchers in the present study.
+
+The use of language both to express and further an ideological goal has
+been documented in the techniques employed by candidates for political
+office in the U.S., Druckman, Jacobs, and Ostermeier (2004) considered
+political \enquote{issues} as communication that attempts to persuade
+constituents to vote for the candidates based on their strengths in
+matters of public policy. According to the researchers, \enquote{image}
+priming describes techniques deployed in order to sway votes based on
+favorable aspects of the candidate's behavior and personality (Druckman
+et al., 2004). The researchers investigated political issue and image
+priming on the part of candidates as implied by the disproportionate
+attention candidates paid to particular issues over others. The
+researchers found numerous examples of issue and image priming during
+the 1972 re-election campaign of Richard Nixon.
+
+They linked the Nixon administration's awareness of the issues for which
+the president had public support to the issues he should emphasize (and
+prime) during the campaign. Likewise the researchers found evidence that
+Nixon's team was aware of negative evaluations of his warmth and
+trustworthiness, and thus took steps to prime his purportedly positive
+qualities, including strength and competence (Druckman et al., 2004).
+The researchers also cited research from Iyengar and Kinder (1987)
+suggesting the news media affected perceptions of President Jimmy
+Carter's competence by emphasizing (e.g., priming) issues related to
+energy, defense, and the economy. This focus implies news media may
+contribute to Americans' perception of politicians based on where the
+media places emphasis.
 
 There is a potential caveat regarding the validity of Druckman et al.
-(2004)'s findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
-Pashler, Coburn, and Harris (2012) point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
-Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
-Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
-Pashler et al.
-(2012) point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
-Studies investigating perceptual priming have been \enquote{directly replicated in hundreds of labs} (Pashler et al., 2012).
-This replication rate does not appear to be the case for social priming, as argued by Pashler et al.
-(2012).
-
-Pashler et al.
-(2012) noticed the unusually large effect size values (Cohen's \emph{d}) reported by researchers studying social priming effects.
-The researchers reproduced two studies from Williams and Bargh (2008) The first study attempted to prime participants by having them plot points on a Cartesian grid.
-The independent variable was priming condition and contained three levels: short, middle, and long distance.
-Those instructed to plot points further apart were hypothesized to express a higher degree of psychological distance regarding their family.
-The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
-Pashler et al.
-(2012) concluded those two studies from Williams and Bargh (2008) held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
-
-While these concerns regarding the replication of social priming studies are valid and deserve further investigation, Druckman et al.
-(2004) does not purport to demonstrate a widespread effect of social priming on the American electorate.
-In other words, this research makes no claim to empirically supported priming effects.
-Rather, Druckman et al.
-(2004) chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
-These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
-As such, Druckman et al.
-(2004)'s research on Nixon serves as an example of language's potential utility in the propagation of desirable political opinions.
-The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
-The idea that even 1970s news media could contain political biases is of particular interest to the current study, which investigates similar phenomena in contemporary news media.
-
-Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress (Clinton \& Enamorado, 2014).
-Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival.
-The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election (Clinton \& Enamorado, 2014).
-
-Therefore, the current study sought to combine both methods related questions and extension/replication of previous moral foundation results found for liberal and conservative sources.
-First, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Second, these weighted percentages were examined for their differences in across liberal and conservative news sources.
-
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
-
-\hypertarget{method}{%
-\section{Method}\label{method}}
-
-For Experiment 1, the researchers approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources generally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
-Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
-Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
-
-\hypertarget{sources}{%
-\subsection{Sources}\label{sources}}
+(2004)'s findings: reproductions of several studies purporting to
+demonstrate social priming effects have failed to replicate the original
+results. Pashler, Coburn, and Harris (2012) point out the distinction
+between perceptual and social (or goal) priming both in their
+operational definitions as well as their replicability. Perceptual
+priming often works through the inducement of a certain response from a
+related prime, as in, for example, semantic priming. Social (or goal)
+priming encompasses phenomena by which people exhibit complex behavioral
+changes subsequent to exposure to a prime. Pashler et al. (2012) point
+out well-known studies investigating social priming, including the use
+of elderly-related primes to induce slower walking speeds in
+participants. Studies investigating perceptual priming have been
+\enquote{directly replicated in hundreds of labs} (Pashler et al.,
+2012). This replication rate does not appear to be the case for social
+priming, as argued by Pashler et al. (2012).
+
+Pashler et al. (2012) noticed the unusually large effect size values
+(Cohen's \emph{d}) reported by researchers studying social priming
+effects. The researchers reproduced two studies from Williams and Bargh
+(2008) The first study attempted to prime participants by having them
+plot points on a Cartesian grid. The independent variable was priming
+condition and contained three levels: short, middle, and long distance.
+Those instructed to plot points further apart were hypothesized to
+express a higher degree of psychological distance regarding their
+family. The second study used the same priming conditions, but
+hypothesized that greater distance between points would prime
+participants to estimate fewer calories in unhealthy foods than those
+who were primed with shorter distances between points. Pashler et al.
+(2012) concluded those two studies from Williams and Bargh (2008) held
+little validity while also casting doubt on the prevalence of social
+priming effects themselves, based on the inability of other researchers
+to replicate previously reported effects in this area.
+
+While these concerns regarding the replication of social priming studies
+are valid and deserve further investigation, Druckman et al. (2004) does
+not purport to demonstrate a widespread effect of social priming on the
+American electorate. In other words, this research makes no claim to
+empirically supported priming effects. Rather, Druckman et al. (2004)
+chronicle the efforts on the part of the Nixon Administration to prop up
+the president's supposed strengths while downplaying his weaknesses.
+These tactics were deployed through the careful use of language in order
+to achieve the administration's political goals. As such, Druckman et
+al. (2004)'s research on Nixon serves as an example of language's
+potential utility in the propagation of desirable political opinions.
+The researcher's investigation of news media's focus on specific issues
+during the Carter Administration likewise provide an example of language
+as a potential conduit for the transfer of politically biased
+information. The idea that even 1970s news media could contain political
+biases is of particular interest to the current study, which
+investigates similar phenomena in contemporary news media.
+
+Other research into news media suggests certain media outlets, at least
+indirectly, may have an effect on the voting records of representatives
+in Congress (Clinton \& Enamorado, 2014). Specifically, the researchers
+identified a pattern of declining support for President Bill Clinton's
+policies chiefly among Republicans in the House of Representatives after
+the Fox News Channel began broadcasting on cable and satellite systems
+in their respective districts. As Fox News was, at the time of its
+launch in 1996, the only outwardly ideological national news network,
+the researchers were able to track its spread across the country and
+observe voting records of members of Congress both before and after Fox
+News' arrival. The researchers concluded that members of Congress,
+excluding those newly elected at the time of Fox News Channel's
+emergence, attempted to anticipate resultant conservative-leaning shifts
+among their constituents by bolstering their conservative voting record
+before the next election (Clinton \& Enamorado, 2014).
+
+Therefore, the current study sought to combine both methods related
+questions and extension/replication of previous moral foundation results
+found for liberal and conservative sources. First, the MFD was combined
+with previous research by the current authors (see below) and weighted
+by valence to create weighted percentages to better specify endorsement.
+Second, these weighted percentages were examined for their differences
+in across liberal and conservative news sources.
+
+\section{Experiment 1}\label{experiment-1}
+
+\section{Method}\label{method}
+
+For Experiment 1, the researchers approached the study with the
+intention to answer a method question. That is, this portion of the
+current research was conducted in order to solidify the best method by
+which to analyze political news text under the Moral Foundations Theory
+framework while also alleviating some of the aforementioned valence
+problem observed in the Moral Foundations Dictionary. The researchers
+hypothesized the news sources generally perceived as liberal leaning
+(\emph{NPR} and \emph{The New York Times}) would contain MFD words and
+valences indicating endorsements of the individualizing moral
+foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
+Additionally, the researchers hypothesized the two sources generally
+perceived to be conservative leaning (\emph{Fox News} and
+\emph{Breitbart}) would feature MFD words and valences indicating equal
+endorsement of all five foundations. Owing to the lack of a need for
+human participants, the researchers did not petition Missouri State
+University's Institutional Review Board, as no such approval was needed
+to conduct this study.
+
+\subsection{Sources}\label{sources}
 
 Political articles were collected from the websites of four notable U.S.
-news sources, a process known as web scraping.
-The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
-They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-The researchers determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, \emph{The New York Times} and \emph{NPR} are preferred by consumers reporting a liberal bias or lean.
-In contrast, \emph{Fox News} and \emph{Breitbart} are believed to have a conservative bias or lean.
-Mitchell et al.
-(2014)'s article presented political ideology as a scale ranging from \enquote{consistently liberal} to \enquote{consistently conservative.} In between these extremes lie more moderate positions, including \enquote{mostly liberal,} \enquote{mixed,} and \enquote{mostly conservative.} Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either \enquote{liberal} and \enquote{conservative} in order to form a basis for comparison.
-
-Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the \emph{R} script.
-For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
-
-Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not growing at a similar pace as those from \emph{The New York Times} and \emph{Breitbart}.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content \enquote{archive.} The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
-Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
-We later ran a process in order to exclude any duplicate articles.
-\emph{Fox News} presented a similar issue.
-We discovered \emph{Fox News} utilized six URLs in addition to the regular politics page.
-These URLs led to pages containing content pertaining the U.S.
-Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
-Once again, duplicates were subsequently eliminated from any analyses.
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset (Wickham, 2016).
-Using this dataset, we identified word count and average word count per source.
-This process was run once daily starting in February 2018 until March 2018.
-Starting in mid-March 2018, the process was run twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected in April 2018.
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-Once data collection ended, the text was scanned using the \emph{ngram} package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017).
-This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
-At this point, duplicate articles were discarded.
-
-The article text was processed using the \emph{tm} and \emph{ngram} packages in \emph{R} in order to render the text in lowercase, remove punctuation, and fix spacing issues (Feinerer \& Hornik, 2017).
-The individual words were then reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}).
-The same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
-
-Concurrent research by Jordan, Buchanan, and Padfield (2019) is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
-The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
-Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
-
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
-Therefore, for each article, the percentage of the number of \emph{harm/care} words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurrence were multiplied by their \emph{z}-scored valence.
-Valences were \emph{z}-scored in order to eliminate any ambiguity regarding the direction of the valence.
-Positive values indicate positive valence, and negative values indicate negative valence.
-Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{descriptive-statistics}{%
-\subsection{Descriptive Statistics}\label{descriptive-statistics}}
+news sources, a process known as web scraping. The sources were
+\emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox
+News}, and \emph{Breitbart}. They were selected for their widespread
+recognition and the fact political partisans have strong preferences for
+some sources over others. The researchers determined the political lean
+of each source by referencing Mitchell, Matsa, Gottfried, and Kiley
+(2014)'s article demonstrating the self-reported ideological consistency
+represented by the consumers of several news sources. In general,
+\emph{The New York Times} and \emph{NPR} are preferred by consumers
+reporting a liberal bias or lean. In contrast, \emph{Fox News} and
+\emph{Breitbart} are believed to have a conservative bias or lean.
+Mitchell et al. (2014)'s article presented political ideology as a scale
+ranging from \enquote{consistently liberal} to \enquote{consistently
+conservative.} In between these extremes lie more moderate positions,
+including \enquote{mostly liberal,} \enquote{mixed,} and \enquote{mostly
+conservative.} Owing to the lower number of sources analyzed herein, the
+researchers elected to categorize the sources as either
+\enquote{liberal} and \enquote{conservative} in order to form a basis
+for comparison.
+
+Political articles in particular were identified and subsequently
+scraped by including the specific URL directing to each source's
+political content in the \emph{R} script. For example, rather than
+scrape from nytimes.com, which would return undesired results
+(non-political features, reviews, etc.), we instead included
+nytimes.com/section/politics so that more or less exclusively political
+content was obtained. All code for this manuscript can be found at
+\url{https://osf.io/5kpj7/}, and the scripts are provided inline with
+this manuscript written with the \emph{papaja} library (Aust \& Barth,
+2017).
+
+Identification of the sources' political URLs presented a problem for
+two of the sources owing to complications with how their particular
+sites were structured. While in the multi-week process of scraping
+articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were
+not growing at a similar pace as those from \emph{The New York Times}
+and \emph{Breitbart}. Upon investigation, we found another, more robust
+URL for political content from NPR: their politics content
+\enquote{archive.} The page structure on NPR's website was such that
+only a limited selection of articles is displayed to the user at a given
+time. Scraping both the archive and the normal politics page ensured we
+were obtaining most (if not all) new articles as they were published. We
+later ran a process in order to exclude any duplicate articles.
+\emph{Fox News} presented a similar issue. We discovered \emph{Fox News}
+utilized six URLs in addition to the regular politics page. These URLs
+led to pages containing content pertaining the U.S. Executive Branch,
+Senate, House of Representatives, Judicial Branch, foreign policy, and
+elections. Once again, duplicates were subsequently eliminated from any
+analyses.
+
+\subsection{Materials}\label{materials}
+
+Using the \emph{rvest} library in the statistical package \emph{R}, we
+pulled body text for individual articles from each of the aforementioned
+sources (identified using CSS language) and compiled them into a dataset
+(Wickham, 2016). Using this dataset, we identified word count and
+average word count per source. This process was run once daily starting
+in February 2018 until March 2018. Starting in mid-March 2018, the
+process was run twice daily - once in the morning and again in the
+evening. Data collection was terminated once 250,000 words per source
+was collected in April 2018.
+
+\subsection{Data analysis}\label{data-analysis}
+
+Once data collection ended, the text was scanned using the \emph{ngram}
+package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017).
+This package includes a word count function, which was used to remove
+articles that came through as blank text, as well as to eliminate text
+picked up from the Disqus commenting system used by certain websites. At
+this point, duplicate articles were discarded.
+
+The article text was processed using the \emph{tm} and \emph{ngram}
+packages in \emph{R} in order to render the text in lowercase, remove
+punctuation, and fix spacing issues (Feinerer \& Hornik, 2017). The
+individual words were then reduced to their stems (i.e., \emph{abused}
+was stemmed to \emph{abus}). The same procedure was applied to the MFD
+words and the words in the Warriner et al. (2013) dataset. Using the
+Warriner et al. (2013) dictionary, the words making up each of the five
+foundations in the MFD were matched to their respective valence value.
+
+Concurrent research by Jordan, Buchanan, and Padfield (2019) is
+assessing the validity of both the Moral Foundations Questionnaire and
+the Moral Foundations Dictionary through a multi-trait multi-method
+analysis of the two instruments using multiple samples. The instruments
+and foundation areas are being analyzed against one another, in order to
+test reliability, as well as against the Congressional Record in order
+to test predictive validity for political orientation. The researchers
+were able to identify a number of potential new words that, if added to
+the MFD, could comprise a dictionary with greater validity, and less
+likelihood of zero percent texts, as this often occurs with the current
+MFD. Those results have informed this analysis, and their updated
+findings may change the underlying dictionary used in this analysis
+(albeit, we do not expect any changes in the results presented below).
+
+The source article words were compiled into a dataset where they were
+matched up with their counterparts in the MFD along with their valence
+and a percentage of their occurrence. Therefore, for each article, the
+percentage of the number of \emph{harm/care} words occurring in the
+articles were calculated, and this process was repeated for each of the
+foundations. Words' percent occurrence were multiplied by their
+\emph{z}-scored valence. Valences were \emph{z}-scored in order to
+eliminate any ambiguity regarding the direction of the valence. Positive
+values indicate positive valence, and negative values indicate negative
+valence. Words were categorized in accordance to their MFD affiliation,
+creating a weighted sum for each moral foundation.
+
+\section{Results}\label{results}
+
+\subsection{Descriptive Statistics}\label{descriptive-statistics}
 
@@
 
-The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included \emph{z}-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula.
-Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage (Kincaid, Fishburne, Robert P., Richard L., \& Brad S., 1975).
-For example, a text with a readability score of 11 should be easily read by a high school junior.
-
-As seen in Table \ref{tab:exp1-source-descriptives}, the sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
-\emph{The New York Times} published the greatest number of articles as well as total words.
-\emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
-Per individual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, \emph{Fox News} appears to be the most readable source on average, while \emph{The New York Times} is the least readable.
-This result might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
-
-\hypertarget{inferential-statistics}{%
-\subsection{Inferential Statistics}\label{inferential-statistics}}
-
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error (Gelman, 2006).
-Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp1-table}.
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
+The researchers calculated descriptive statistics for each news source
+in order to understand any and all fundamental linguistic differences in
+the sources' use of English. Statistics calculated included average
+\emph{z}-scored valence of the unique words per article, number of
+articles per source, total number of words per source, average number of
+tokens (words) per article in each source, average number of types
+(unique words) per article in each source, and mean readability level
+per source. Readability statistics were calculated using the
+Flesch-Kincaid Grade Level Readability formula (Kincaid, Fishburne,
+Robert P., Richard L., \& Brad S., 1975). Readability is calculated
+using a formula where the total number of syllables, words, and
+sentences in a given passage are determinants of its difficulty. The
+obtained value is intended to match up with the grade level at which one
+should be able to comfortably read the passage (Kincaid et al., 1975).
+For example, a text with a readability score of 11 should be easily read
+by a high school junior.
+
+As seen in Table \ref{tab:exp1-source-descriptives}, the sources are
+similar in some aspects yet different in others. Valence appears to be
+slightly positive across all sources. The large standard deviations seem
+to indicate little to no presence of a difference in valence. \emph{The
+New York Times} published the greatest number of articles as well as
+total words. \emph{Breitbart} featured the lowest number of articles,
+and \emph{NPR} the lowest number of total words from all articles. Per
+individual article, however, \emph{Breitbart} appears to feature the
+highest average number of words as well as unique words. Once again the
+standard deviations call into question any apparent differences between
+sources. Finally, \emph{Fox News} appears to be the most readable source
+on average, while \emph{The New York Times} is the least readable. This
+result might be attributable to the greater number of tokens in the
+average \emph{New York Times} article compared to \emph{Fox News}. As
+before, the standard deviations for readability hamper one's ability to
+draw solid conclusions regarding differences in the sources' use of
+language.
+
+\subsection{Inferential Statistics}\label{inferential-statistics}
+
+To analyze if news sources adhered to differences in word use based on
+their target audience, we utilized a multilevel model (MLM) to analyze
+the data. MLM is a regression technique that allows one to control for
+the repeated measurement and nested structured of the data, which
+creates correlated error (Gelman, 2006). Using the \emph{nlme} library
+in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each
+foundation's weighted percentage was predicated here by the political
+lean of the news source, using the individual news sources as a random
+intercept to control for the structure of the data.
+
+The multilevel model did not indicate the presence of any significant or
+practical effect of political lean for any of the five moral
+foundations. The strongest effect size was observed for the
+\emph{authority/respect} foundation, but the effect was in the opposite
+direction from what was originally hypothesized - liberal sources tended
+to use more \emph{authority/respect} words than did conservative
+sources. Descriptive and test statistics, \emph{p}-values and effect
+sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp1-table}. To
+interpret the weighted scores, one can examine the mean and standard
+deviations for each. A zero score for the mean, with a non-zero standard
+deviation, would indicate a perfect balance of positive and negative
+words in each category, likely representing a neutral tone when all
+words are considered. Negative percentages would indicate more
+representation of the negative words in the MFD area, while positive
+percentages indicate an endorsement of the positive words in a MFD.
+Therefore, we suggest using the sign of the mean score to determine the
+directionality of the endorsement for the MFD (positive, neutral,
+negative), and the standard deviation to ensure that a zero score is not
+zero endorsement (i.e., a SD of zero indicates no words were used).
+Based on the weighted percent values for the five foundations, the
+researchers observed that MFD words seem to make up a small portion of
+the article text. Furthermore, the observed percentages and means appear
+to indicate a generally positive endorsement of all five foundations
+across both liberal and conservative sources.
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The results obtained in Experiment 1 did not confirm the hypothesis.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The strongest effect found was for the \emph{authority/respect} foundation owing to the fact its Cohen's \emph{d} value was greater than the other four foundations.
-However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
-This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
-It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
-
-Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
-The selection of the broad and amorphous topic of \enquote{political news} may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
-In short, the range of topics covered in Experiment 1 was likely too broad.
-The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
-
-Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-Generally speaking, the researchers believe their methodology to be sound.
-Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
-Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
-The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurrence.
-
-While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
-The researchers identified two such changes that were subsequently employed in Experiment 2.
-First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
-politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court.
-In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
-
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
-
-\hypertarget{kavanaugh-supreme-court-hearing}{%
-\subsection{Kavanaugh Supreme Court Hearing}\label{kavanaugh-supreme-court-hearing}}
-
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 (US Government, 2018a).
-Following allegations of sexual assault by high school classmate Dr.~Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
-
-On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh (US Government, 2018b).
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television (O'Connell, 2018).
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 (US Government, 2018c).
-
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals.
-The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-Concerns around abortion might be related either to \emph{harm/care} or \emph{purity/sanctity}.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Likewise, arguments could be made that relate concerns regarding sexual violence to \emph{harm/care} or \emph{fairness/reciprocity}.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
-
-\hypertarget{u.s.-government-shutdown-of-2018-2019}{%
-\subsection{U.S. Government Shutdown of 2018-2019}\label{u.s.-government-shutdown-of-2018-2019}}
-
-The U.S.
-Federal Government partially shut down on December 22, 2018.
-The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress (Axelrod, 2019).
-The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
-President Trump demanded \$5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget (Peoples \& Swanson, 2019).
-Owing to the lack of funding, the government began a partial shutdown, causing \enquote{around 800,000} federal employees to be either furloughed or compelled to work without pay (Axelrod, 2019).
-
-The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
-President Trump signed the bill, ending the longest government shutdown in U.S.
-history (Axelrod, 2019).
-Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole (Kheel \& Mitchell, 2019).
-Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed (Peoples \& Swanson, 2019).
-While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
-
-As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
-Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
-As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns (Martin, 2019).
-Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
-Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people (Martin, 2019).
-This example potentially ties into the five moral foundations.
-Theological concerns regarding the border wall might invoke \emph{authority/respect} as well as \emph{purity/sanctity}.
-In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
-could also elicit moral concerns related to \emph{ingroup/outgroup}.
-
-Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
-In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
-
-\hypertarget{method-1}{%
-\section{Method}\label{method-1}}
-
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-Once again, no human participants were needed for this study, so no Institutional Review Board approval was necessary.
-
-\hypertarget{sources-1}{%
-\subsection{Sources}\label{sources-1}}
-
-Articles pertaining to the Brett Kavanaugh Supreme Court nomination and confirmation were scraped from the websites of 12 U.S.
-news sources.
-As in Experiment 1, these sources were selected owing to their favorability among political partisans according to Mitchell et al.
-(2014).
-The sources favored by the highest proportion of consistent liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
-The sources favored by the highest proportion of consistent conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts, again written with the \emph{papaja} library in \emph{R}, are provided inline with this manuscript (Aust \& Barth, 2017).
-
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
-
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset (Wickham, 2016).
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the partial U.S.
-Government shutdown of 2018-2019.
-The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
-
-\hypertarget{data-analysis-1}{%
-\subsection{Data analysis}\label{data-analysis-1}}
-
-As in Experiment 1, the text was scanned with \emph{ngram}.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed (Schmidt et al., 2017).
-The text was processed and stemmed in order to convert to a usable form for further analysis (Feinerer \& Hornik, 2017).
-Words were subsequently matched with their valences from Warriner et al.
-(2013).
-Depending on the results of Jordan et al.
-(2019)'s research, alternative forms of the Moral Foundations Dictionary may be imported instead of the original dictionary.
-
-Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
-Each individual word was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}).
-Once again, the same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurrence in the text.
-Once again, percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
-
-\hypertarget{results-1}{%
-\section{Results}\label{results-1}}
-
-\hypertarget{descriptive-statistics-1}{%
-\subsection{Descriptive Statistics}\label{descriptive-statistics-1}}
-
-The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Experiment 1, statistics calculated include \emph{z}-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source (Kincaid et al., 1975).
-
-Table \ref{tab:exp2-source-descriptives-kav} displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
-The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, \emph{The Huffington Post} appears to have published only 27 articles while \emph{NPR} published 757 articles on this topic.
-Valence was found to be slightly positive across all sources.
-\emph{Slate} produced the most total words with the most tokens on average.
-\emph{Rush Limbaugh} featured the highest number of types on average.
-\emph{The Blaze} was the most readable source on average by grade level while \emph{Fox News} was the least readable.
-The standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
-
-Table \ref{tab:exp2-source-descriptives-gs} displays descriptive statistics for articles about the partial government shutdown.
-Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each source on this topic.
-\emph{The Hugginton Post} and \emph{The Blaze} published fewer than 100 articles while \emph{Slate} published 1,013 articles.
-\emph{Slate} again featured the most total words and mean tokens.
-\emph{Rush Limbaugh} again had the most types on average.
-For this topic, \emph{Slate} was the most readable while \emph{The Huffington Post} was the least readable.
-For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
+\section{Discussion}\label{discussion}
+
+The results obtained in Experiment 1 did not confirm the hypothesis. The
+researchers found little compelling evidence of an effect of partisan
+lean on MFD endorsement. The strongest effect found was for the
+\emph{authority/respect} foundation owing to the fact its Cohen's
+\emph{d} value was greater than the other four foundations. However, the
+effect was in the opposite direction of that which was hypothesized.
+Specifically, the results indicated that liberal leaning sources
+demonstrated higher positivity regarding that foundation than
+conservatives. This result is contrary not only to the research
+hypothesis for Experiment 1 but also to previous findings in Moral
+Foundations Theory research. It should be noted, however, the effect
+size was small and the relationship was not found to be statistically
+significant.
+
+Upon speculation, the researchers identified one possible reason for why
+the results were unable to confirm the hypothesis. The selection of the
+broad and amorphous topic of \enquote{political news} may have led to
+the scraping of large numbers of articles with little to no
+moral-centric content. Rather, many articles may have been, for example,
+simple reporting on congressional procedures that would leave little
+room for the use of moral language here, let alone words from the Moral
+Foundations Dictionary. In short, the range of topics covered in
+Experiment 1 was likely too broad. The possibility exists that a tighter
+focus on one political issue or event, especially one that (on the
+surface) has a stronger relationship with morality might be more
+illuminating for research in moral language in news media.
+
+Owing to the exploratory nature of Experiment 1, the researchers were
+afforded the opportunity to consider changes to the method to be
+utilized in Experiment 2. Generally speaking, the researchers believe
+their methodology to be sound. Web scraping methods and text processing
+remain viable methods for collecting large amounts of text and
+subsequently rendering that text in a form suitable for data analysis.
+Experiment 1 also demonstrated a method by which to address inherent
+problems in the Moral Foundations Dictionary relating to valence. The
+solution provided in Experiment 1 appears to provide insights into the
+MFD words where none previously existed. Finally, calculating weighted
+percentages and sums for each moral foundation provides an easily
+interpreted summary of MFD word positivity and occurrence.
+
+While the methodology used in Experiment 1 features many strengths,
+there are aspects which could be strengthened for future studies. The
+researchers identified two such changes that were subsequently employed
+in Experiment 2. First, the researchers elected to include more news
+sources for web scraping and analysis in addition to the four used in
+Experiment 1. Second, the researchers chose to focus their data
+collection efforts exclusively on one event in U.S. politics: the
+nomination and confirmation of Justice Brett Kavanaugh to the U.S.
+Supreme Court. In Experiment 2, the researchers sought to confirm the
+usefulness and validity of the method as well as test a similar
+hypothesis as Experiment 1.
+
+\section{Experiment 2}\label{experiment-2}
+
+\subsection{Kavanaugh Supreme Court
+Hearing}\label{kavanaugh-supreme-court-hearing}
+
+In the wake of Justice Anthony Kennedy's retirement from the Supreme
+Court of the United States, President Donald Trump nominated Brett
+Kavanaugh as the new Associate Justice. Kavanaugh was previously on the
+U.S. Court of Appeals for the District of Columbia. The Senate Judiciary
+Committee began his confirmation hearing on September 4, 2018 (US
+Government, 2018a). Following allegations of sexual assault by high
+school classmate Dr.~Christine Blasey Ford, the committee postponed its
+vote on whether or not to open the confirmation to the entire Senate.
+
+On September 27, the committee questioned Dr.~Ford before commencing a
+second round of questioning for Judge Kavanaugh (US Government, 2018b).
+During the intervening weeks between hearings, two more women came
+forward with two separate allegations of sexual assault on the part of
+Kavanaugh. According to Nielsen reports, more than 20 million people
+watched the September 27 proceedings on television (O'Connell, 2018).
+This figure does not take into account viewers who watched online, nor
+does it account for viewers outside the United States. On September 28,
+the Senate Judiciary Committee voted to send the nomination to the
+Senate floor. Senator Jeff Flake of Arizona, however, lobbied for a
+week-long FBI investigation on Kavanaugh and the allegations facing him,
+which the committee, and later the President, approved. The
+investigation concluded with no significant findings. The Senate voted
+50-48 to approve Kavanaugh's appointment on October 6, 2018 (US
+Government, 2018c).
+
+The Kavanaugh nomination, confirmation hearing, and eventual
+swearing-in, as well as the news media's coverage of all three events,
+feature many dimensions that likely differ depending on one's morals.
+The issue might be exacerbated given the presence of questionable sexual
+behaviors at the center of many concerns. On one side of the debate,
+Kavanaugh's Supreme Court tenure presents a prime opportunity to bring
+morality back into interpretation of the Constitution. Kavanaugh's
+confirmation creates a conservative stronghold among the justices on the
+court. Commentators have noted this might help advance a judicial agenda
+that backpedals certain rights previously upheld by the Supreme Court,
+including abortion and gay marriage - social issues challenged by their
+opponents at least partially on moral grounds. Concerns around abortion
+might be related either to \emph{harm/care} or \emph{purity/sanctity}.
+On the other side of the debate, the assault allegations have energized
+Kavanaugh's opponents to advocate for his rejection from the court owing
+to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Likewise, arguments could be made that relate concerns regarding sexual
+violence to \emph{harm/care} or \emph{fairness/reciprocity}.
+Additionally, the moral duty of the Senate as the upper chamber in the
+U.S. legislature has been scrutinized in public discourse with respect
+to its handling of the assault allegations vis-a-vis Kavanaugh's
+confirmation.
+
+\subsection{U.S. Government Shutdown of
+2018-2019}\label{u.s.-government-shutdown-of-2018-2019}
+
+The U.S. Federal Government partially shut down on December 22, 2018.
+The government reopened on January 25, 2019 upon the passage of an
+appropriations bill by both houses of Congress (Axelrod, 2019). The
+shutdown stemmed from a disagreement between President Donald Trump and
+Congress over funding for the president's proposed U.S.-Mexico border
+wall. President Trump demanded \$5.7 billion dollars in the new budget
+to be appropriated for the wall, which Congress did not provide in its
+budget (Peoples \& Swanson, 2019). Owing to the lack of funding, the
+government began a partial shutdown, causing \enquote{around 800,000}
+federal employees to be either furloughed or compelled to work without
+pay (Axelrod, 2019).
+
+The government shutdown ended 35 days later when Congress passed a
+continuing resolution to fund the government for three weeks while
+further negotiations regarding the budget would take place. President
+Trump signed the bill, ending the longest government shutdown in U.S.
+history (Axelrod, 2019). Many political commentators cite the mounting
+pressure on Trump and Congress stemming from significant costs both to
+unpaid American workers and the economy as a whole (Kheel \& Mitchell,
+2019). Perhaps owing to the financial pressures experienced by thousands
+of federal employees and their families as a result of a political
+quarrel, President Trump saw his approval rating fall as the shutdown
+progressed (Peoples \& Swanson, 2019). While the shutdown and its
+associated burdens were unpopular, the issues discussed concurrent to
+the shutdown offer the potential for more divergent opinions.
+
+As mentioned before, the shutdown started as a result of an impasse
+regarding funding for the border wall. Since the wall was proposed
+during the 2016 presidential campaign, the issue has taken on a moral
+dimension. As an example, Shaun Casey, the director of Georgetown
+University's Berkely Center for Religion, Peace and World Affairs, cites
+diverging opinions stemming from theological concerns (Martin, 2019).
+Some supporters, citing certain passages from the Bible, believe
+construction of the wall is part of a divinely ordained process handed
+down by God. Opponents, on the other hand, have cited other parts of the
+Bible extolling the significance of exiled peoples, especially the
+Hebrew people (Martin, 2019). This example potentially ties into the
+five moral foundations. Theological concerns regarding the border wall
+might invoke \emph{authority/respect} as well as \emph{purity/sanctity}.
+In addition to these two foundations, the involvement of foreign
+countries and their citizens' migration into the U.S. could also elicit
+moral concerns related to \emph{ingroup/outgroup}.
+
+Owing to the wealth of moral opinions regarding the border wall and its
+association with the 2018-2019 government shutdown, the researchers
+decided to add the government shutdown as a news event to analyze under
+the auspices of Moral Foundations Theory. In addition to articles
+related to the Kavanaugh confirmation hearing, the researchers scraped
+articles related to the government shutdown in order to analyze their
+content for valence and moral alignment.
+
+\section{Method}\label{method-1}
+
+In contrast to Experiment 1, the researchers approached Experiment 2
+with the intention to confirm the method employed was valid for the
+analysis of the scraped text as well as for any inferences drawn from
+the analyses. For Experiment 2, the researchers hypothesized that news
+sources perceived as liberal will exhibit positive endorsements of the
+individualizing moral foundations (\emph{harm/care} and
+\emph{fairness/reciprocity}) in their articles reporting on both the
+Kavanaugh confirmation hearing as well as the 2018-2019 government
+shutdown. News sources perceived as conservative are hypothesized to
+positively endorse all five foundations equally in their coverage of the
+Kavanaugh hearing and the government shutdown. The researchers tested
+the hypothesis by analyzing the content scraped from news sources' web
+pages spanning the two weeks before (September 13, 2018) and two weeks
+after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its
+prominence in the news. Likewise, the researchers analyzed content
+spanning two weeks before the start of the government shutdown (December
+8, 2018) to two weeks following the end of the shutdown (February 8,
+2019). The content will be analyzed for valence and moral alignment
+under Moral Foundations Theory. Once again, no human participants were
+needed for this study, so no Institutional Review Board approval was
+necessary.
+
+\subsection{Sources}\label{sources-1}
+
+Articles pertaining to the Brett Kavanaugh Supreme Court confirmation
+hearing and the 2018-2019 U.S. Government shutdown were scraped from the
+websites of 10 U.S. news sources. As in Experiment 1, these sources were
+selected owing to their favorability among political partisans according
+to Mitchell et al. (2014). The sources favored by the highest proportion
+of consistent liberals were \emph{The New York Times}, \emph{National
+Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and
+\emph{Politico} (Mitchell et al., 2014). The sources favored by the
+highest proportion of consistent conservatives included \emph{Fox News},
+\emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and
+\emph{Sean Hannity}. Political articles referencing Brett Kavanaugh's
+nomination process were identified and subsequently scraped by including
+the URL for each source's coverage of the nomination in the \emph{R}
+script. All code for this manuscript can be found at
+\url{https://osf.io/5kpj7/}, and the scripts, again written with the
+\emph{papaja} library in \emph{R}, are provided inline with this
+manuscript (Aust \& Barth, 2017).
+
+\subsection{Materials}\label{materials-1}
+
+Using the \emph{rvest} library in the statistical package \emph{R}, we
+pulled body text for individual articles from each of the aforementioned
+10 news sources (identified using CSS language). We compiled the
+articles into a dataset (Wickham, 2016). Using this dataset, we
+identified word count and average word count per source. This process
+was run for articles pertaining to Kavanaugh's nomination that were
+published between September 13, 2018 and October 11, 2018 inclusive.
+This date range was selected in reference to the widely-publicized and
+viewed nomination hearing on September 27, 2018. We set the start date
+at September 13 (two weeks before the hearing) and the end date at
+October 11 (two weeks after the hearing) so that we could capture a
+large amount of data (roughly one month) during which Kavanaugh's
+nomination was at its peak saturation in news coverage.
+
+The same process was followed for scraping articles related to the
+partial U.S. Government shutdown of 2018-2019. The articles scraped were
+published between December 8, 2018 and February 8, 2019 inclusive. Once
+again, the researchers elected to scrape articles published two weeks
+before and after the event in question in order to capitalize on the
+shutdown's saturation in American news media.
+
+\subsection{Data analysis}\label{data-analysis-1}
+
+As in Experiment 1, the text was scanned with \emph{ngram}. Again, blank
+articles, text from the Disqus system, and duplicate articles were
+removed (Schmidt et al., 2017). The text was processed and stemmed in
+order to convert to a usable form for further analysis (Feinerer \&
+Hornik, 2017). Words were subsequently matched with their valences from
+Warriner et al. (2013). Depending on the results of Jordan et al.
+(2019)'s multi-trait multi-method analysis of the MFD and the Moral
+Foundations Questionnaire, alternative forms of the Moral Foundations
+Dictionary with additional words may be imported instead of the original
+dictionary.
+
+Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the
+researchers processed the text in order to convert it to lowercase, fix
+spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
+Each individual word was reduced to its stem (i.e., \emph{diseased} was
+stemmed to \emph{diseas}). Once again, the same procedure was applied to
+the MFD words and the words in the Warriner et al. (2013) dataset. Using
+the Warriner et al. (2013) dictionary, the words in the MFD were
+assigned their respective valence. The researchers obtained the words'
+percent occurrence in the text. Percents were multiplied by
+\emph{z}-scored valence and categorized into their proper MFD category.
+
+\section{Results}\label{results-1}
+
+\subsection{Descriptive Statistics}\label{descriptive-statistics-1}
+
+The researchers calculated descriptive statistics for each news source
+per topic in order to reveal the presence (if any) of linguistic
+differences in the sources' use of language. As in Experiment 1,
+statistics calculated include \emph{z}-scored valence, number of
+articles per source, total words per source, mean tokens per article in
+each source, mean types per article in each source, and mean readability
+level (using the Flesch-Kincaid Grade Level Readability formula) per
+source (Kincaid et al., 1975).
+
+Table \ref{tab:exp2-source-descriptives-kav} displays the descriptive
+statistics for sources' writing on the Kavanaugh confirmation hearing.
+The sources were similar in most basic linguistic aspects, except for
+number of articles. For example, \emph{Sean hannity} appears to have
+published only 27 articles while \emph{Breitbart} published 757 articles
+on this topic. Valence was found to be slightly positive across all
+sources. \emph{Fox News} produced the most total words with the most
+tokens on average. \emph{Politico} featured the highest number of types
+on average. \emph{Rush Limbaugh} was the most readable source on average
+by grade level while \emph{Slate} was the least readable. The large
+standard deviations for these statistics, however, preclude conclusions
+regarding differences in the sources' use of language.
+
+Table \ref{tab:exp2-source-descriptives-gs} displays descriptive
+statistics for articles about the partial government shutdown. Like the
+Kavanaugh hearing, the sources were similar in average valence (slightly
+positive). Once again, there was variation in the number of articles
+published by each source on this topic. \emph{Sean Hannity}, \emph{Rush
+Limbaugh}, and \emph{The Blaze} published fewer than 100 articles while
+\emph{Fox News} published 1,013 articles. \emph{Fox News} again featured
+the most total words and mean tokens. \emph{Politico} had the most types
+on average. For this topic, \emph{Fox News} was the most readable while
+\emph{Slate} was the least readable. For each statistic, the excessively
+high standard deviations render any assertions regarding linguistic
+differences inconclusive on a descriptive level.
 
@@
 
-\hypertarget{inferential-statistics-1}{%
-\subsection{Inferential Statistics}\label{inferential-statistics-1}}
-
-To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
-Once again, the researchers used the \emph{nlme} library in \emph{R} (Pinheiro et al., 2017).
-Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-MLMs were constructed from datasets compiled for both topics of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a significant effect for \emph{harm/care}, but the practical effect denoted by Cohen's \emph{d} was found to be small.
-There were no other significant or practical effect of political lean for any of the other four moral foundations.
-The effect for \emph{harm/care} was in the hypothesized direction with liberal sources tending to use more positively \emph{harm/care} words than conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp2-tablekav}.
-
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations.
-A small-to-medium effect size was observed for \emph{authority/respect}.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Experiment 1 in which the largest effect size was observed for \emph{authority/respect}.
-As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Experiment 1.
-As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
+\subsection{Inferential Statistics}\label{inferential-statistics-1}
+
+To analyze if news sources adhered to differences in word use based on
+their target audience, the researchers utilized a multilevel model (MLM)
+to analyze if news sources leveraged different vocabularies based on
+target audience. The researchers used the \emph{nlme} library in
+\emph{R} (Pinheiro et al., 2017). Each foundation's weighted percentage
+was predicted by the source's political lean, using the individual
+source as a random intercept to control for the nested data structure.
+Two separate MLMs were constructed from datasets compiled for each topic
+of interest: the Kavanaugh hearing and the partial government shutdown
+of 2018-2019.
+
+For the Kavanaugh topic, the multilevel model indicated the presence of
+a statistically significant effect for \emph{harm/care}, but the
+practical effect denoted by Cohen's \emph{d} was found to be small.
+There were no other significant or practical effects of political lean
+for any of the other four moral foundations. The effect for
+\emph{harm/care} was in the hypothesized direction with liberal sources
+tending to use more positively \emph{harm/care} words than conservative
+sources. Descriptive and test statistics, \emph{p}-values and effect
+sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp2-tablekav}.
+
+For news articles about the partial U.S. Federal Government Shutdown of
+2018-2019, there were no significant or practical effects of political
+lean for the moral foundations. A small-to-medium effect size was
+observed for \emph{authority/respect}. The effect was in the predicted
+direction as well, as conservative sources tended to offer more positive
+endorsements of the foundation than liberal sources. This effect was
+similar to Experiment 1 in which the largest effect size was observed
+for \emph{authority/respect}. As noted before, the effect found in
+Experiment 1 was in the opposite direction as what was hypothesized.
+Thus, it is difficult to draw comparisons between the two studies
+despite the similar pattern for effect size. Owing to a lack of similar
+effects for either Experiment 1 or the Kavanaugh topic, there is doubt
+as to whether or not a practical or generalized effect exists for
+\emph{authority/respect}.
+
+Based on the weighted percent values for the five foundations applied to
+both topics, MFD words seem to make up little of the article text. A
+similar pattern was observed for the results in Experiment 1. As in
+Experiment 1, the percentages and means seem to indicate a generally
+positive endorsement of all five moral foundations across both political
+leanings.
 
@@
 
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
-
-The results obtained in Experiment 2 did not confirm either of the hypotheses.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The only significant effect was found for \emph{harm/care} in the Kavanaugh confirmation hearing dataset.
-While the effect was in the hypothesized direction (higher positive endorsement for liberal sources), the effect size was small.
-While there were no significant effects found for the government shutdown topic, a small-to-medium effect size was calculated for the \emph{authority/respect} foundation.
-Once again, the effect was in the hypothesized direction with conservative sources providing higher positive endorsements of the foundation relative to liberal sources.
-
-Both of these effects are consistent with both the research hypotheses as well as previous findings in Moral Foundations Theory scholarship.
-It should be noted these effects were found in isolation, and similar patterns were not found across the other studies.
-These findings undermine any inferences of political bias stemming from the content of news articles.
-The results obtained for Experiment 2 call into question the Moral Foundations Dictionary's efficacy as a tool for establishing differences between political news sources by partisan lean.
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-Within the theoretical framework of Moral Foundations Theory (Haidt \& Graham, 2007), the researchers attempted to devise a method leveraging the Moral Foundations Dictionary (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
-This method was carried out in several parts.
-First, the researchers collected the articles through web scraping techniques in \emph{R} (Wickham, 2016).
-Second, the text was processed using \emph{ngram} and \emph{tm} in \emph{R} to render it in a form conducive to computerized statistical analysis (Feinerer \& Hornik, 2017).
-Third, percent occurrence of words in the Moral Foundations Dictionary (MFD) was calculated on each source in order to establish how often words indicating endorsement of the five moral foundations appeared.
-Frequency of MFD word occurrence per article was weighted for valence by multiplying the scores by mean \emph{z-scored} valence ratings from Warriner et al.
-(2013).
-Finally, the researchers constructed multi-level models using \emph{nlme} in \emph{R} (Pinheiro et al., 2017) for each foundation in which weighted percentages were predicted by each source's political lean.
-Individual source was held as a random intercept to control for correlated error.
-This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertaining to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
-Government shutdown from December 2018 to January 2019.
-
-In Experiment 1, the researchers analyzed general political news articles from four prominent U.S.
-news sources: \emph{The New York Times}, \emph{NPR}, \emph{Fox News}, and \emph{Breitbart}.
-They hypothesized \emph{The New York Times} and \emph{NPR} would endorse moral foundations representative of liberal political views and that \emph{Fox News} and \emph{Breitbart} would endorse foundations indicative of conservative views.
-The researchers assigned a political lean (liberal or conservative) to the sources based upon consumer preferences established by Mitchell et al.
-(2014).
-After collecting the articles through web scraping, processing the article text, calculating percent occurrence of MFD words, and weighting that value by valence, the researchers constructed the MLM.
-The results obtained were not significant in any statistical or practical sense.
-There was a small effect found for the \emph{authority/respect} foundation according to Cohen's \emph{d}, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-The researchers viewed these results as an opportunity to alter their method for use in Experiment 2.
-
-In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political bias in U.S.
-news sources.
-First, the researchers expanded the number of news sources from which articles were collected.
-They added \emph{Slate}, \emph{Politico}, and \emph{Huffington Post} to the list of liberal sources and \emph{The Blaze}, \emph{Rush Limbaugh}, and \emph{Sean Hannity} to the conservative sources.
-Once again, political bias groups were assigned based on Mitchell et al.
-(2014)'s findings.
-Second, they elected to collect articles and compile datasets pertaining to two specific topics in U.S.
-news: the Kavanaugh hearing and the government shutdown.
-These topics were chosen due to their relevance to multiple moral foundations.
-Other than those two alterations, the same method (scraping, processing, weighting, and multi-level modelling) was employed for Experiment 2.
-
-For articles pertaining to the Kavanaugh hearing, there was a statistically significant effect for \emph{harm/care}, but the effect size was modest.
-No other statistically or practically significant effects were found for the Kavanaugh topic.
-Likewise, there were no statistically or practically significant effects revealed for the government shutdown topic.
-However, there was a small-to-medium effect size for \emph{authority/respect}.
-The fact these patterns do not appear in any of the other studies undertaken herein decreases the researchers' ability to draw any valuable conclusions regarding the MFD's ability to reveal political bias in American news media.
-
-The results obtained in both experiments, while not confirmatory, provide several avenues for future investigation.
-Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of political bias in American news under the auspices of Moral Foundations Theory.
-This does not, however, rule out the possibility that news media is biased.
-As Mitchell et al.
-(2014) has demonstrated, self-reported political partisans are drawn to separate sources, but the present research was unable to offer any content-based explanations of this phenomenon.
-Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
-The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
-
-Despite the fact the results regarding political bias were inconclusive, the researchers still retain confidence in the overall structure of the methodology established in the current study.
-Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-Additionally, multi-level models were necessary to control for the nested nature of the data where political lean encompassed several sources, which themselves encompassed numerous articles.
-
-Thus, the researchers' attention turned to the instrument used to detect differences.
-In the present study, the researchers utilized the Moral Foundations Dictionary, a metric developed from Moral Foundations Theory (Graham et al., 2009).
-Based upon the results obtained, it might be necessary to investigate alternative instruments that might better elucidate the differences of interest.
-Likewise, other theoretical perspectives may be better equipped to explain political differences in discourse.
-
-Tools such as these could be developed through the Linguistic Inquiry and Word Count program (LIWC) (Pennebaker et al., 2007).
-As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context (Graham et al., 2009).
-This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
-The authors established sound psychometric properties for the tool, implying its validity in several applications.
-For this reason, the researchers elected to utilize the MFD as their primary instrument.
-
-Other instruments could theoretically be developed through a LIWC analysis, including those that would be useful for analyzing political discourse.
-Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from Warriner et al.
-(2013).
-The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
-However, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
-Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
-
-There is, however, another theoretical framework that could prove useful when applied to the method established in the present research.
-Relational Frame Theory originates in applied behavior analysis, but there exists recent scholarship that demonstrates its potential usefulness in the political realm.
-Relational Frame Theory (RFT) holds that stimuli, including speech and discourse, elicit responses in terms of relationships to other stimuli, even when the stimuli do not otherwise appear to be related (Blackledge, 2014).
-For example, an individual's equivalent fear response to a venomous snake as well as a wooded area said to \enquote{contain snakes} represents \enquote{mutual entailment.} That is, the fear response is an effect of both the snake and environment stimuli, which cause the fear response.
-\enquote{Combinatorial entailment} can be represented by a fear response elicited by a novel stimulus whose relationship to a well-known stimulus elicits a certain response (Blackledge, 2014).
-In the snake example, if another stimulus (Stimulus A), were said to be \enquote{worse than} the snake, the relationship between A and the snake would elicit a more severe fear response to Stimulus A.
-RFT utilizes a set of \enquote{families} describing the nature of these relationships.
-Such families include \enquote{coordinative,} establishing similarities between stimuli, and \enquote{distinctive,} implying fundamental differences between stimuli (Belisle, Paliliunas, Dixon, \& Tarbox, 2018).
-These families can be used to analyze networks of relational frames in discourse.
-
-Belisle et al.
-(2018) conducted a text analysis (using a computer algorithm) of several speeches made by four recent U.S.
-presidents under Relational Frame Theory.
-These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
-For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts (Belisle et al., 2018).
-At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
-In any case, this research appears to indicate that RFT might be useful for analyzing political news content similar to the method employed in the current study.
-
-Another apparent strength of RFT is its demonstrated effectiveness in the analysis of political discourse.
-Unlike the development of the Moral Foundations Dictionary, this application of RFT was performed on public facing political discourse that might be more similar to news articles than the Christian sermons upon which the MFD was compiled.
-Additionally, there would likely be greater overlap between the speeches analyzed in Belisle et al.
-(2018)'s work and political news, as the media often quotes speeches by the president.
-Furthermore, the types or \enquote{families} of relational frames could be used as the individual constructs much like the moral foundations in the present research.
-In order to conform with the method established for this study, their occurrence would need to be scored, probably as a percent.
-This would allow for an intuitive approach to weighting by \emph{z}-scored valence if needed.
-
-While Relational Frame Theory appears to represent a viable option for further research into political news analysis, there are some drawbacks.
-First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
-One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it was a theory designed to investigate not only moral differences but also political differences.
-While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
-
-In order to seriously consider RFT as a viable framework for this type of analysis, the researchers would like to be able to draw on further confirmatory evidence of the theory's utility in political discourse analysis.
-Specifically, analyses of more individuals than the four presidents addressed by Belisle et al.
-(2018) would be needed to further demonstrate RFT's applicability in this field.
-Also, though presidential speeches may be more similar to news articles than sermons, they are still a distinct form of discourse with different goals and audiences than news outlets.
-RFT's reliability across these forms appears to remain untested as of this writing.
-These potential shortcomings are testable and might be overcome through more research.
-As such, RFT's potential as a useful framework for political discourse analysis should not be discounted.
-
-The researchers aimed to utilize the Moral Foundations Dictionary and valence in the analysis of political news articles to determine whether or not bias was present.
-In Experiment 1, they tested general political news from four U.S.
-news sources - two liberal and two conservative.
-They were unable to find any significant evidence of political bias in that analysis.
-After adjusting the method to include more sources and specific topics for articles, including the Kavanaugh hearing and the government shutdown, the researchers were once again unable to uncover differences in MFD word use between conservative and liberal news sources.
-The results in the current study seem to demonstrate the MFD's weaknesses in applications to political discourse.
-MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
-In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, or through a different theoretical perspective such as Relational Frame Theory.
-Despite the results obtained in the current study, the researchers have reason to believe this line of inquiry warrants further investigation and that the correct method will one day be established.
-
-Never before has news media and discourse represented such fertile ground for psychological research.
-The plethora of options and the potential for misinformation present important challenges for American democracy in the twenty-first century.
-The potential divisions in American society resulting from an abundance of choices for sources of political information, coupled with the notion that public discourse seems to offer competing conceptions of objective truth, underscores the importance of research into the content of political news.
-Democracy functions effectively on the foundation an informed and engaged electorate.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of citizens every day so that insights into the nature and consequences of political discourse can be more completely understood.
+\section{Discussion}\label{discussion-1}
+
+The results obtained in Experiment 2 did not confirm either of the
+hypotheses. The researchers found little compelling evidence of an
+effect of partisan lean on MFD endorsement. The only significant effect
+was found for \emph{harm/care} in the Kavanaugh confirmation hearing
+dataset. While the effect was in the hypothesized direction (higher
+positive endorsement for liberal sources), the effect size was small.
+While there were no significant effects found for the government
+shutdown topic, a small-to-medium effect size was calculated for the
+\emph{authority/respect} foundation. Once again, the effect was in the
+hypothesized direction with conservative sources providing higher
+positive endorsements of the foundation relative to liberal sources.
+
+Both of these effects are consistent with both the research hypotheses
+as well as previous findings in Moral Foundations Theory scholarship. It
+should be noted these effects were found in isolation, and similar
+patterns were not found across the other studies. These findings
+undermine any inferences of political bias stemming from the content of
+news articles. The results obtained for Experiment 2 call into question
+the Moral Foundations Dictionary's efficacy as a tool for establishing
+differences between political news sources by partisan lean.
+
+\section{Conclusions}\label{conclusions}
+
+Within the theoretical framework of Moral Foundations Theory (Haidt \&
+Graham, 2007), the researchers attempted to devise a method leveraging
+the Moral Foundations Dictionary (Graham et al., 2009) in order to
+quantify political bias stemming from content published by several
+prominent American news sources. The researchers downloaded news article
+text from the web, processed the text, matched it with the Moral
+Foundations Dictionary words, and calculated average valence for words
+in each article. To analyze the data, the researchers constructed
+multi-level models for each foundation in which weighted percentages
+were predicted by each source's political lean. Individual source was
+held as a random intercept to control for correlated error. This process
+was undertaken once in Experiment 1 for general political news and twice
+in Experiment 2 using articles pertaining to two specific topics in
+American news: Brett Kavanaugh's confirmation to the Supreme Court and
+the most recent (as of this writing) partial U.S. Government shutdown
+from December 2018 to January 2019.
+
+In Experiment 1, the researchers analyzed general political news
+articles from four prominent U.S. news sources: \emph{The New York
+Times}, \emph{NPR}, \emph{Fox News}, and \emph{Breitbart}. They
+hypothesized \emph{The New York Times} and \emph{NPR} would endorse
+moral foundations representative of liberal political views and that
+\emph{Fox News} and \emph{Breitbart} would endorse foundations
+indicative of conservative views. The researchers assigned a political
+lean (liberal or conservative) to the sources based upon consumer
+preferences established by Mitchell et al. (2014). After collecting the
+articles through web scraping, processing the article text, calculating
+percent occurrence of MFD words, and weighting that value by valence,
+the researchers constructed the MLM. The results obtained were not
+significant in any statistical or practical sense. There was a small
+effect found for the \emph{authority/respect} foundation according to
+Cohen's \emph{d}, but the effect suggested endorsement for that
+foundation opposite to what was hypothesized. The researchers viewed
+these results as an opportunity to alter their method for use in
+Experiment 2.
+
+In Experiment 2, the researchers adjusted their method in order to
+increase their potential ability to quantify political leanings in U.S.
+news sources. First, the researchers expanded the number of news sources
+from which articles were collected. They added \emph{Slate},
+\emph{Politico}, and \emph{Huffington Post} to the list of liberal
+sources and \emph{The Blaze}, \emph{Rush Limbaugh}, and \emph{Sean
+Hannity} to the conservative sources. Once again, political bias groups
+were assigned based on Mitchell et al. (2014)'s findings. Second, they
+elected to collect articles and compile datasets pertaining to two
+specific topics in U.S. news: the Kavanaugh hearing and the government
+shutdown. These topics were chosen due to their relevance to multiple
+moral foundations. Other than those two alterations, the same method
+(scraping, processing, weighting, and multi-level modelling) was
+employed for Experiment 2.
+
+For articles pertaining to the Kavanaugh hearing, there was a
+statistically significant effect for \emph{harm/care}, but the effect
+size was modest. No other statistically or practically significant
+effects were found for the Kavanaugh topic. Likewise, there were no
+statistically or practically significant effects revealed for the
+government shutdown topic. However, there was a small-to-medium effect
+size for \emph{authority/respect}. The fact these patterns do not appear
+in any of the other studies undertaken herein decreases the researchers'
+ability to draw any valuable conclusions regarding the MFD's ability to
+reveal political bias in American news media.
+
+The results obtained in both experiments, while not confirmatory,
+provide several avenues for future investigation. Twice confronted with
+the failure to uncover differences in news media's political content,
+the researchers were unable to confirm the existence of an effect of
+political lean on American news writing under the auspices of Moral
+Foundations Theory. This does not, however, rule out the possibility
+that news media is biased. As Mitchell et al. (2014) has demonstrated,
+self-reported political partisans are drawn to separate sources, but the
+present research was unable to offer any content-based explanations of
+this phenomenon. Even when attenuating the scraping criteria to collect
+text concerning (what the researchers believed to be) morally resonant
+topics, the method failed to detect differences in MFD word use by
+prominent news sources. The researchers' focus, therefore, turns toward
+the limitations of the method, especially the chosen theoretical
+framework, under which the present research was conducted.
+
+Despite the fact the results regarding political bias were inconclusive,
+the researchers still retain confidence in the overall structure of the
+methodology established in the current study. Specifically, the
+procedure for scraping text from the web, processing, stemming, and
+weighting the scores with valence seems to represent a solid method for
+preparing a high quantity of text passages for data analysis. The
+researchers implemented valence as an indicator of the directionality of
+endorsement due to the inherent ambiguity of simply calculating MFD word
+percent occurrence. This method served both to augment the face validity
+of the MFD by incorporating valence (thus reducing ambiguity) and to
+generate a score that is easy to understand and analyze.
+
+Thus, the researchers' attention turned to the instrument used to detect
+differences. In the present study, the researchers utilized the Moral
+Foundations Dictionary, a metric developed from Moral Foundations Theory
+(Graham et al., 2009). Based upon the results obtained, it might be
+necessary to investigate alternative instruments that might better
+elucidate the differences of interest. Likewise, other theoretical
+perspectives may be better equipped to explain political differences in
+discourse.
+
+Tools such as these could be developed through the Linguistic Inquiry
+and Word Count program (LIWC) (Pennebaker et al., 2007). As stated
+before, the Moral Foundations Dictionary was established through an
+analysis of Christian sermons performed mostly with LIWC as well as some
+human-enforced corrections due to context (Graham et al., 2009). This
+approach was grounded in Moral Foundations Theory, a clear framework
+within which the authors developed the MFD. The original authors of the
+MFD established sound psychometric properties for the tool, implying its
+validity in several applications. For this reason, the researchers
+elected to utilize the MFD as their primary instrument.
+
+Other instruments could theoretically be developed through a LIWC
+analysis, including those that would be useful for analyzing political
+discourse. Researchers could obtain percent occurrence scores for words
+appearing in certain LIWC categories, which could then be weighted with
+valence scores from Warriner et al. (2013). The researchers will
+consider other applications of the LIWC in future studies aiming to
+analyze political content. James Pennebaker (2007), one of the creators
+of LIWC, has suggested the program could be applied to analyses of
+cognitive, social, and emotional states. Furthermore, there is some
+evidence LIWC can be used to detect deception, but the reliability of
+the program's accuracy in this regard (67\%) calls this assertion into
+question (Pennebaker, 2011). Despite the promising extent of LIWC's
+abilities, without a firm theoretical foundation for such analyses, any
+such applications of LIWC would face serious questions as to their
+relevance, validity, and generalizability. Nevertheless, LIWC analyses
+may represent a path to further research into political differences in
+news media as well as theory formation.
+
+There is, however, another theoretical framework that could prove useful
+when applied to the method established in the present research.
+Relational Frame Theory originates in applied behavior analysis, but
+there exists recent scholarship that demonstrates its potential
+usefulness in the political realm. Relational Frame Theory (RFT) holds
+that stimuli, including speech and discourse, elicit responses in terms
+of relationships to other stimuli, even when the stimuli do not
+otherwise appear to be related (Blackledge, 2014). For example, an
+individual's equivalent fear response to a venomous snake as well as a
+wooded area said to \enquote{contain snakes} represents \enquote{mutual
+entailment.} That is, the fear response is an effect of both the snake
+and environment stimuli, which cause the fear response.
+\enquote{Combinatorial entailment} can be represented by a fear response
+elicited by a novel stimulus whose relationship to a well-known stimulus
+elicits a certain response (Blackledge, 2014). In the snake example, if
+another stimulus (Stimulus A), were said to be \enquote{worse than} the
+snake, the relationship between A and the snake would elicit a more
+severe fear response to Stimulus A. RFT utilizes a set of
+\enquote{families} describing the nature of these relationships. Such
+families include \enquote{coordinative,} establishing similarities
+between stimuli, and \enquote{distinctive,} implying fundamental
+differences between stimuli (Belisle, Paliliunas, Dixon, \& Tarbox,
+2018). These families can be used to analyze networks of relational
+frames in discourse.
+
+Belisle et al. (2018) conducted a text analysis (using a computer
+algorithm) of several speeches made by four recent U.S. presidents under
+Relational Frame Theory. These speeches, representing prominent examples
+of political discourse, were found to differ in their use of relational
+frames. For example, speeches by Donald Trump were found to contain more
+distinctive frames than other presidents, while Barack Obama utilized
+more coordinative frames than his counterparts (Belisle et al., 2018).
+At first glance, the differences appear to fall along party lines,
+though other factors may be involved as well. In any case, this research
+appears to indicate that RFT might be useful for analyzing political
+news content similar to the method employed in the current study.
+
+Another apparent strength of RFT is its demonstrated effectiveness in
+the analysis of political discourse. Unlike the development of the Moral
+Foundations Dictionary, this application of RFT was performed on public
+facing political discourse that might be more similar to news articles
+than the Christian sermons upon which the MFD was compiled.
+Additionally, there would likely be greater overlap between the speeches
+analyzed in Belisle et al. (2018)'s work and political news, as the
+media often quotes speeches by the president. Furthermore, the types or
+\enquote{families} of relational frames could be used as the individual
+constructs much like the moral foundations in the present research. In
+order to conform with the method established for this study, their
+occurrence would need to be scored, probably as a percent. This would
+allow for an intuitive approach to weighting by \emph{z}-scored valence
+if needed.
+
+While Relational Frame Theory appears to represent a viable option for
+further research into political news analysis, there are some drawbacks.
+First, RFT by itself does not purport to elucidate political differences
+in discourse, and its applications to political research are not yet
+well established. In other words, RFT represents one method by which to
+analyze political text, but with the caveat that the categories are not
+known to represent patterns of political ideology. One of the main
+strengths of Moral Foundations Theory in the eyes of the researchers was
+that it was a theory designed to investigate not only moral differences
+but also political differences. While the results obtained herein may
+weaken assumptions regarding the MFD's capabilities with political text,
+Moral Foundations Theory has been repeatedly established as a strong
+framework for detecting political differences along moral lines.
+
+In order to seriously consider RFT as a viable framework for this type
+of analysis, the researchers would like to be able to draw on further
+confirmatory evidence of the theory's utility in political discourse
+analysis. Specifically, analyses of more individuals than the four
+presidents addressed by Belisle et al. (2018) would be needed to further
+demonstrate RFT's applicability in this field. Also, though presidential
+speeches may be more similar to news articles than sermons, they are
+still a distinct form of discourse with different goals and audiences
+than news outlets. RFT's reliability across these forms appears to
+remain untested as of this writing. These potential shortcomings are
+testable and might be overcome through more research. As such, RFT's
+potential as a useful framework for political discourse analysis should
+not be discounted.
+
+The researchers aimed to utilize the Moral Foundations Dictionary and
+valence in the analysis of political news articles to determine whether
+or not bias was present. In Experiment 1, they tested general political
+news from four U.S. news sources - two liberal and two conservative.
+They were unable to find any significant evidence of political bias in
+that analysis. After adjusting the method to include more sources and
+specific topics for articles, including the Kavanaugh hearing and the
+government shutdown, the researchers were once again unable to uncover
+differences in MFD word use between conservative and liberal news
+sources. The results in the current study seem to demonstrate the MFD's
+weaknesses in applications to political discourse. MFD words simply
+might not appear often enough in news articles to register as
+endorsement for any particular moral foundation over the others. In
+future research, this weakness could be addressed through further
+alterations to the method, including alternative analyses using computer
+programs including LIWC, or through a different theoretical perspective
+such as Relational Frame Theory.
+
+Never before has news media and discourse represented such fertile
+ground for psychological research. The plethora of options for news
+sources has created not only an abundance of choice but also vast
+quantities of text data. Along with this recent increase in the amount
+of text information, there is now an obligation on the part of
+researchers to devise proper methods for analyzing that text. Solid
+methodologies must be constructed and periodically improved to keep pace
+with evolving technologies. Likewise, a strong theoretical foundation is
+paramount to making sense of the current and future media ecosystem.
+Therefore, it is incumbent upon social scientists to continue
+investigating the information consumed by millions of Americans every
+day so that insights into the nature and consequences of political
+discourse can be more completely understood.
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
 \begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Aust2017}{}%
-Aust, F., \& Barth, M. (2017). papaja: Create APA manuscripts with R Markdown. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-Axelrod2019}{}%
-Axelrod, T.
-(2019).
-Poll: Majority of Americans hold Trump and Republicans responsible for shutdown \textbar{} TheHill.
-Retrieved from \url{https://thehill.com/homenews/campaign/427007-poll-majority-of-americans-hold-trump-and-republicans-responsible-for}
-
-\leavevmode\hypertarget{ref-Belisle2018}{}%
-Belisle, J., Paliliunas, D., Dixon, M.
-R., \& Tarbox, J.
-(2018).
-Feasibility of contextual behavioral speech analyses of US presidents: Inaugural addresses of Bill Clinton, George W.
-Bush, Barack Obama, and Donald Trump, 1993--2017.
-\emph{Journal of Contextual Behavioral Science}, \emph{10}(July), 14--18.
+\hypertarget{ref-Aust2017}{}
+Aust, F., \& Barth, M. (2017). papaja: Create APA manuscripts with R
+Markdown. Retrieved from \url{https://github.com/crsh/papaja}
+
+\hypertarget{ref-Axelrod2019}{}
+Axelrod, T. (2019). Poll: Majority of Americans hold Trump and
+Republicans responsible for shutdown \textbar{} TheHill. Retrieved from
+\url{https://thehill.com/homenews/campaign/427007-poll-majority-of-americans-hold-trump-and-republicans-responsible-for}
+
+\hypertarget{ref-Belisle2018}{}
+Belisle, J., Paliliunas, D., Dixon, M. R., \& Tarbox, J. (2018).
+Feasibility of contextual behavioral speech analyses of US presidents:
+Inaugural addresses of Bill Clinton, George W. Bush, Barack Obama, and
+Donald Trump, 1993--2017. \emph{Journal of Contextual Behavioral
+Science}, \emph{10}(July), 14--18.
 doi:\href{https://doi.org/10.1016/j.jcbs.2018.07.002}{10.1016/j.jcbs.2018.07.002}
 
-\leavevmode\hypertarget{ref-Blackledge2014}{}%
-Blackledge, J.
-T.
-(2014).
-An introduction to relational frame theory: Basics and applications.
-\emph{The Behavior Analyst Today}, \emph{3}(4), 421--433.
-doi:\href{https://doi.org/10.1037/h0099997}{10.1037/h0099997}
-
-\leavevmode\hypertarget{ref-Bradley1999}{}%
-Bradley, M.
-M., \& Lang, P.
-J.
-(1999).
-\emph{Affective Norms for English Words (ANEW): Instruction manual and affective ratings} (No.
-C-1).
-The Center for Research in Psychophysiology, University of Florida.
-
-\leavevmode\hypertarget{ref-Cameron2006}{}%
-Cameron, D. (2006). Ideology and language. \emph{Journal of Political Ideologies}, \emph{11}(2), 141--152. doi:\href{https://doi.org/10.1080/13569310600687916}{10.1080/13569310600687916}
-
-\leavevmode\hypertarget{ref-Clinton2014}{}%
-Clinton, J.
-D., \& Enamorado, T.
-(2014).
-The national news media's effect on Congress: How Fox News affected elites in Congress.
-\emph{The Journal of Politics}, \emph{76}(4), 928--943.
+\hypertarget{ref-Blackledge2014}{}
+Blackledge, J. T. (2014). An introduction to relational frame theory:
+Basics and applications. \emph{The Behavior Analyst Today}, \emph{3}(4),
+421--433. doi:\href{https://doi.org/10.1037/h0099997}{10.1037/h0099997}
+
+\hypertarget{ref-Bradley1999}{}
+Bradley, M. M., \& Lang, P. J. (1999). \emph{Affective Norms for English
+Words (ANEW): Instruction manual and affective ratings} (No. C-1). The
+Center for Research in Psychophysiology, University of Florida.
+
+\hypertarget{ref-Cameron2006}{}
+Cameron, D. (2006). Ideology and language. \emph{Journal of Political
+Ideologies}, \emph{11}(2), 141--152.
+doi:\href{https://doi.org/10.1080/13569310600687916}{10.1080/13569310600687916}
+
+\hypertarget{ref-Clinton2014}{}
+Clinton, J. D., \& Enamorado, T. (2014). The national news media's
+effect on Congress: How Fox News affected elites in Congress. \emph{The
+Journal of Politics}, \emph{76}(4), 928--943.
 doi:\href{https://doi.org/10.1017/S0022381614000425}{10.1017/S0022381614000425}
 
-\leavevmode\hypertarget{ref-Davies2014}{}%
-Davies, C.
-L., Sibley, C.
-G., \& Liu, J.
-H.
-(2014).
-Confirmatory factor analysis of the moral foundations questionnaire independent scale validation in a new zealand sample.
-\emph{Social Psychology}, \emph{45}(6), 431--436.
+\hypertarget{ref-Davies2014}{}
+Davies, C. L., Sibley, C. G., \& Liu, J. H. (2014). Confirmatory factor
+analysis of the moral foundations questionnaire independent scale
+validation in a new zealand sample. \emph{Social Psychology},
+\emph{45}(6), 431--436.
 doi:\href{https://doi.org/10.1027/1864-9335/a000201}{10.1027/1864-9335/a000201}
 
-\leavevmode\hypertarget{ref-Druckman2004}{}%
-Druckman, J.
-N., Jacobs, L.
-R., \& Ostermeier, E.
-(2004).
-Candidate strategies to prime issues and image.
-\emph{The Journal of Politics}, \emph{66}(4), 1180--1202.
+\hypertarget{ref-Druckman2004}{}
+Druckman, J. N., Jacobs, L. R., \& Ostermeier, E. (2004). Candidate
+strategies to prime issues and image. \emph{The Journal of Politics},
+\emph{66}(4), 1180--1202.
 doi:\href{https://doi.org/10.1111/j.0022-3816.2004.00295.x}{10.1111/j.0022-3816.2004.00295.x}
 
-\leavevmode\hypertarget{ref-Feinerer2017}{}%
-Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from \url{http://tm.r-forge.r-project.org/}
-
-\leavevmode\hypertarget{ref-Gelman2006}{}%
-Gelman, A.
-(2006).
-Multilevel (hierarchical) modeling: What it can and cannot do.
-\emph{Technometrics}, \emph{48}(3), 432--435.
+\hypertarget{ref-Feinerer2017}{}
+Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from
+\url{http://tm.r-forge.r-project.org/}
+
+\hypertarget{ref-Gelman2006}{}
+Gelman, A. (2006). Multilevel (hierarchical) modeling: What it can and
+cannot do. \emph{Technometrics}, \emph{48}(3), 432--435.
 doi:\href{https://doi.org/10.1198/004017005000000661}{10.1198/004017005000000661}
 
-\leavevmode\hypertarget{ref-Gilligan1982}{}%
-Gilligan, C.
-(1982).
-New maps of development: New visions of maturity.
+\hypertarget{ref-Gilligan1982}{}
+Gilligan, C. (1982). New maps of development: New visions of maturity.
 \emph{American Journal of Orthopsychiatry}, \emph{52}(2), 199--212.
@@
 
-\leavevmode\hypertarget{ref-Graham2009}{}%
-Graham, J., Haidt, J., \& Nosek, B.
-A.
-(2009).
-Liberals and conservatives rely on different sets of moral foundations.
-\emph{Journal of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
+\hypertarget{ref-Graham2009}{}
+Graham, J., Haidt, J., \& Nosek, B. A. (2009). Liberals and
+conservatives rely on different sets of moral foundations. \emph{Journal
+of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
 doi:\href{https://doi.org/10.1037/a0015141}{10.1037/a0015141}
 
-\leavevmode\hypertarget{ref-Graham2011}{}%
-Graham, J., Nosek, B.
-A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
-H.
-(2011).
-Mapping the moral domain.
-\emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
+\hypertarget{ref-Graham2011}{}
+Graham, J., Nosek, B. A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
+H. (2011). Mapping the moral domain. \emph{Journal of Personality and
+Social Psychology}, \emph{101}(2), 366--385.
 doi:\href{https://doi.org/10.1037/a0021847}{10.1037/a0021847}
 
-\leavevmode\hypertarget{ref-Haidt2007}{}%
-Haidt, J., \& Graham, J.
-(2007).
-When morality opposes justice: Conservatives have moral intuitions that Liberals may not recognize.
+\hypertarget{ref-Haidt2007}{}
+Haidt, J., \& Graham, J. (2007). When morality opposes justice:
+Conservatives have moral intuitions that Liberals may not recognize.
 \emph{Social Justice Research}, \emph{20}(1), 98--116.
@@
 
-\leavevmode\hypertarget{ref-Jordan2019}{}%
-Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{A validation of the Moral Foundations Questionnaire and Dictionary}. Retrieved from \url{https://osf.io/kt9yf/}
-
-\leavevmode\hypertarget{ref-Kheel2019}{}%
-Kheel, R., \& Mitchell, E.
-(2019).
-Overnight Defense: Trump agrees to reopen government without wall funding \textbar{} Senate approves stopgap spending \textbar{} Dems ask Armed Services chair to block military funding for wall \textbar{} Coast Guard official assures workers they will receive back pay \textbar{} TheHill.
-Retrieved from \url{https://thehill.com/policy/defense/overnights/427045-overnight-defense-trump-agrees-to-reopen-government-without-wall}
-
-\leavevmode\hypertarget{ref-Kincaid1975}{}%
-Kincaid, J.
-P., Fishburne, J., Robert P., R., Richard L., C., \& Brad S.
-(1975).
-Derivation of new readability formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy enlisted personnel.
+\hypertarget{ref-Jordan2019}{}
+Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{A
+validation of the Moral Foundations Questionnaire and Dictionary}.
+Retrieved from \url{https://osf.io/kt9yf/}
+
+\hypertarget{ref-Kheel2019}{}
+Kheel, R., \& Mitchell, E. (2019). Overnight Defense: Trump agrees to
+reopen government without wall funding \textbar{} Senate approves
+stopgap spending \textbar{} Dems ask Armed Services chair to block
+military funding for wall \textbar{} Coast Guard official assures
+workers they will receive back pay \textbar{} TheHill. Retrieved from
+\url{https://thehill.com/policy/defense/overnights/427045-overnight-defense-trump-agrees-to-reopen-government-without-wall}
+
+\hypertarget{ref-Kincaid1975}{}
+Kincaid, J. P., Fishburne, J., Robert P., R., Richard L., C., \& Brad S.
+(1975). Derivation of new readability formulas (Automated Readability
+Index, Fog Count and Flesch Reading Ease Formula) for Navy enlisted
+personnel.
 doi:\href{https://doi.org/10.21236/ADA006655}{10.21236/ADA006655}
 
-\leavevmode\hypertarget{ref-Kohlberg1977}{}%
-Kohlberg, L., \& Hersh, R.
-H.
-(1977).
-Moral development: A review of the theory.
-\emph{Theory into Practice}, \emph{16}(2), 53--59.
+\hypertarget{ref-Kohlberg1977}{}
+Kohlberg, L., \& Hersh, R. H. (1977). Moral development: A review of the
+theory. \emph{Theory into Practice}, \emph{16}(2), 53--59.
 doi:\href{https://doi.org/10.1080/00405847709542675}{10.1080/00405847709542675}
 
-\leavevmode\hypertarget{ref-Kuperman2014}{}%
-Kuperman, V., Estes, Z., Brysbaert, M., \& Warriner, A.
-B.
-(2014).
+\hypertarget{ref-Kuperman2014}{}
+Kuperman, V., Estes, Z., Brysbaert, M., \& Warriner, A. B. (2014).
 Emotion and language: Valence and arousal affect word recognition.
-\emph{Journal of Experimental Psychology: General}, \emph{143}(3), 1065--1081.
+\emph{Journal of Experimental Psychology: General}, \emph{143}(3),
+1065--1081.
 doi:\href{https://doi.org/10.1037/a0035669}{10.1037/a0035669}
 
-\leavevmode\hypertarget{ref-Kuperman2012}{}%
-Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M.
-(2012).
-Age-of-acquisition ratings for 30,000 English words.
-\emph{Behavior Research Methods}, \emph{44}(4), 978--990.
+\hypertarget{ref-Kuperman2012}{}
+Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M. (2012).
+Age-of-acquisition ratings for 30,000 English words. \emph{Behavior
+Research Methods}, \emph{44}(4), 978--990.
 doi:\href{https://doi.org/10.3758/s13428-012-0210-4}{10.3758/s13428-012-0210-4}
 
-\leavevmode\hypertarget{ref-Martin2019}{}%
-Martin, M. (2019). The moral question opf Trump's border wall. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
-
-\leavevmode\hypertarget{ref-Mitchell2014}{}%
-Mitchell, A., Matsa, K.
-E., Gottfried, J., \& Kiley, J.
-(2014).
+\hypertarget{ref-Martin2019}{}
+Martin, M. (2019). The moral question opf Trump's border wall. NPR.
+Retrieved from
+\url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
+
+\hypertarget{ref-Mitchell2014}{}
+Mitchell, A., Matsa, K. E., Gottfried, J., \& Kiley, J. (2014).
 Political polarization \& media habits \textbar{} Pew Research Center.
-Retrieved from \url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
-
-\leavevmode\hypertarget{ref-New2007}{}%
-New, B., Brysbaert, M., Veronis, J., \& Pallier, C.
-(2007).
-The use of film subtitles to estimate word frequencies.
-\emph{Applied Psycholinguistics}, \emph{28}(4), 661--677.
+Retrieved from
+\url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
+
+\hypertarget{ref-New2007}{}
+New, B., Brysbaert, M., Veronis, J., \& Pallier, C. (2007). The use of
+film subtitles to estimate word frequencies. \emph{Applied
+Psycholinguistics}, \emph{28}(4), 661--677.
 doi:\href{https://doi.org/10.1017/S014271640707035X}{10.1017/S014271640707035X}
 
-\leavevmode\hypertarget{ref-OConnell2018}{}%
-O'Connell, M.
-(2018).
-Ford-Kavanaugh Ratings: Hearing brings 20 million viewers to cable and broadcast \textbar{} Hollywood Reporter.
-Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
-
-\leavevmode\hypertarget{ref-Pashler2012}{}%
-Pashler, H., Coburn, N., \& Harris, C.
-R.
-(2012).
-Priming of Social Distance?
-Failure to Replicate Effects on Social and Food Judgments.
+\hypertarget{ref-OConnell2018}{}
+O'Connell, M. (2018). Ford-Kavanaugh Ratings: Hearing brings 20 million
+viewers to cable and broadcast \textbar{} Hollywood Reporter. Retrieved
+from
+\url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
+
+\hypertarget{ref-Pashler2012}{}
+Pashler, H., Coburn, N., \& Harris, C. R. (2012). Priming of Social
+Distance? Failure to Replicate Effects on Social and Food Judgments.
 \emph{PLoS ONE}, \emph{7}(8).
@@
 
-\leavevmode\hypertarget{ref-Pennebaker2007}{}%
-Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). Liwc2007: Linguistic inquiry and word count. Austin, TX.
-
-\leavevmode\hypertarget{ref-Peoples2019}{}%
-Peoples, S., \& Swanson, E. (2019, January). Trump's approval rating sinks in new poll as he gets most blame for shutdown. Chicago.
-
-\leavevmode\hypertarget{ref-Pinheiro2017}{}%
-Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). nlme: Linear and nonlinear mixed effects models. Retrieved from \url{https://cran.r-project.org/package=nlme}
-
-\leavevmode\hypertarget{ref-Schmidt2017}{}%
-Schmidt, M.
-F., Gonzalez-Cabrera, I., \& Tomasello, M.
-(2017).
-Children's developing metaethical judgments.
-\emph{Journal of Experimental Child Psychology}, \emph{164}, 163--177.
+\hypertarget{ref-Pennebaker2011}{}
+Pennebaker, J. W. (2011). Using computer analyses to identify language
+style and aggressive intent: The secret life of function words.
+\emph{Dynamics of Asymmetric Conflict}, \emph{4}(2), 92--102.
+doi:\href{https://doi.org/10.1080/17467586.2011.627932}{10.1080/17467586.2011.627932}
+
+\hypertarget{ref-Pennebaker2007}{}
+Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). Liwc2007:
+Linguistic inquiry and word count. Austin, TX.
+
+\hypertarget{ref-Peoples2019}{}
+Peoples, S., \& Swanson, E. (2019, January). Trump's approval rating
+sinks in new poll as he gets most blame for shutdown. Chicago.
+
+\hypertarget{ref-Pinheiro2017}{}
+Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017).
+nlme: Linear and nonlinear mixed effects models. Retrieved from
+\url{https://cran.r-project.org/package=nlme}
+
+\hypertarget{ref-Schmidt2017}{}
+Schmidt, M. F., Gonzalez-Cabrera, I., \& Tomasello, M. (2017).
+Children's developing metaethical judgments. \emph{Journal of
+Experimental Child Psychology}, \emph{164}, 163--177.
 doi:\href{https://doi.org/10.1016/j.jecp.2017.07.008}{10.1016/j.jecp.2017.07.008}
 
-\leavevmode\hypertarget{ref-Suhler2011}{}%
-Suhler, C.
-L., \& Churchland, P.
-(2011).
-Can innate, modular "foundations" explain morality?
-Challenges for Haidt's Moral Foundations Theory.
-\emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
+\hypertarget{ref-Suhler2011}{}
+Suhler, C. L., \& Churchland, P. (2011). Can innate, modular
+``foundations'' explain morality? Challenges for Haidt's Moral
+Foundations Theory. \emph{Journal of Cognitive Neuroscience},
+\emph{23}(9), 2103--2116.
 doi:\href{https://doi.org/10.1162/jocn.2011.21637}{10.1162/jocn.2011.21637}
 
-\leavevmode\hypertarget{ref-USGovernment2018b}{}%
-US Government. (2018a). Congressional Record. \emph{Congressional Record}, \emph{164}(146), 46. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-USGovernment2018}{}%
-US Government. (2018b). Congressional Record. \emph{Congressional Record}, \emph{164}(160), 93. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-USGovernment2018a}{}%
-US Government. (2018c). Congressional Record. \emph{Congressional Record}, \emph{164}(167), 14. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-Warriner2015}{}%
-Warriner, A.
-B., \& Kuperman, V.
-(2015).
-Affective biases in English are bi-dimensional.
-\emph{Cognition and Emotion}, \emph{29}(7), 1147--1167.
+\hypertarget{ref-USGovernment2018b}{}
+US Government. (2018a). Congressional Record. \emph{Congressional
+Record}, \emph{164}(146), 46.
+doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\hypertarget{ref-USGovernment2018}{}
+US Government. (2018b). Congressional Record. \emph{Congressional
+Record}, \emph{164}(160), 93.
+doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\hypertarget{ref-USGovernment2018a}{}
+US Government. (2018c). Congressional Record. \emph{Congressional
+Record}, \emph{164}(167), 14.
+doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
+
+\hypertarget{ref-Warriner2015}{}
+Warriner, A. B., \& Kuperman, V. (2015). Affective biases in English are
+bi-dimensional. \emph{Cognition and Emotion}, \emph{29}(7), 1147--1167.
 doi:\href{https://doi.org/10.1080/02699931.2014.968098}{10.1080/02699931.2014.968098}
 
-\leavevmode\hypertarget{ref-Warriner2013}{}%
-Warriner, A.
-B., Kuperman, V., \& Brysbaert, M.
-(2013).
-Norms of valence, arousal, and dominance for 13,915 English lemmas.
+\hypertarget{ref-Warriner2013}{}
+Warriner, A. B., Kuperman, V., \& Brysbaert, M. (2013). Norms of
+valence, arousal, and dominance for 13,915 English lemmas.
 \emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
@@
 
-\leavevmode\hypertarget{ref-Wickham2016}{}%
-Wickham, H. (2016). Package ` rvest '. Retrieved from \url{https://cran.r-project.org/package=rvest}
-
-\leavevmode\hypertarget{ref-Williams2008}{}%
-Williams, L.
-E., \& Bargh, J.
-A.
-(2008).
-Keeping one's distance.
+\hypertarget{ref-Wickham2016}{}
+Wickham, H. (2016). Package ` rvest '. Retrieved from
+\url{https://cran.r-project.org/package=rvest}
+
+\hypertarget{ref-Williams2008}{}
+Williams, L. E., \& Bargh, J. A. (2008). Keeping one's distance.
 \emph{Psychological Science}, \emph{19}(3), 302--308.

### 2019-04-23 pilot_manuscript.Rmd
Form + Updates from emb2 PDF

@@
 In Experiment 1, the researchers gathered poltical articles from four sources.
-They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
+We were unable to reveal significant differences in moral or political endorsements, but we solidified the method to be employed in further research.
 In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
@@
 These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
-The current authors argue these criticisms are especially valid when considered alongside questions regarding the Moral Foundations Dictionary they state herein.
-However, there exists compelling evidence regarding the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
-This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary.
+Such criticisms are especially valid when considered alongside questions about the Moral Foundations Dictionary in particular.
+Nevertheless, there exists compelling evidence supporting the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
+This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary in the next section.
 
@@
 The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-The researchers created a preliminary list of words that they believed would be associated with the five foundations.
+@Graham2009 created a preliminary list of words that they believed would be associated with the five foundations.
 Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
+@Graham2009 manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
 The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: "Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus" [@Graham2009].
@@
 The researchers eliminated this sentence from the *authority/respect* raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions [@Graham2009].
+The original Moral Foundations Dictionary can be found in the Appendix.
 
@@
 Using this dataset, we identified word count and average word count per source.
-This process was run once daily starting in February 2018 until March 2018.
-Starting in mid-March 2018, the process was run twice daily - once in the morning and again in the evening.
+This process was completed once daily starting in February 2018 until March 2018.
+Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening.
 Data collection was terminated once 250,000 words per source was collected in April 2018.
@@
 Valence appears to be slightly positive across all sources.
-The large standard deviations seem to indicate little to no presence of a difference in valence.
+The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
 *The New York Times* published the greatest number of articles as well as total words.
@@
 Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* appears to be the most readable source on average, while *The New York Times* is the least readable.
+Finally, *Fox News* articles had the lowest reading grade level on average, while *The New York Times* ihad the highest.
 This result might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
+The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
+Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.
 
@@
 The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, *Sean hannity* appears to have published only 27 articles while *Breitbart* published 757 articles on this topic.
+For example, *Sean Hannity* appears to have published only 27 articles while *Breitbart* published 757 articles on this topic.
 Valence was found to be slightly positive across all sources.
 *Fox News* produced the most total words with the most tokens on average.
+This is likely due to the fact *Fox News* transcribes many of their videos and publishes them in article form.
 *Politico* featured the highest number of types on average.
-*Rush Limbaugh* was the most readable source on average by grade level while *Slate* was the least readable.
-The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
+*Rush Limbaugh* featured the lowest readability score on average by grade level while *Slate* featured the highest grade-level readability score.
+The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language, as there is likely a lot of overlap between sources' use of language.
 
@@
 *Sean Hannity*, *Rush Limbaugh*, and *The Blaze* published fewer than 100 articles while *Fox News* published 1,013 articles.
-*Fox News* again featured the most total words and mean tokens.
+*Fox News* again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
 *Politico* had the most types on average.
-For this topic, *Fox News* was the most readable while *Slate* was the least readable.
-For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
+For this topic, *Fox News* featured the lowest reading grade level while *Slate* featured the highest reading grade level.
+For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
 
@@
 
+There remains an aspect of language which this method still cannot address: context.
+Owing to the presence of millions of words in the analyses presented in the current study, the researchers would be unable to check for context and correct endorsement scores accordingly.
+@Graham2009 actually performed a process of human error-checking for context when formulating the MFD.
+While this might have helped that team fix mistakes made by the LIWC program (@Pennebaker2007), manual coding of this nature has the potential to introduce an unnacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and beleif systems.
+
 Thus, the researchers' attention turned to the instrument used to detect differences.
 In the present study, the researchers utilized the Moral Foundations Dictionary, a metric developed from Moral Foundations Theory [@Graham2009].
-Based upon the results obtained, it might be necessary to investigate alternative instruments that might better elucidate the differences of interest.
-Likewise, other theoretical perspectives may be better equipped to explain political differences in discourse.
+Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
+Likewise, other theoretical perspectives may be more equipped to explain political differences in discourse.
 
@@
 The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
-James Pennebaker [-@Pennebaker2007], one of the creators of LIWC, has suggested the program could be applied to analyses of cognitive, social, and emotional states.
+@Pennebaker2007 has suggested the program could be applied to analyses of cognitive, social, and emotional states.
 Furthermore, there is some evidence LIWC can be used to detect deception, but the reliability of the program's accuracy in this regard (67%) calls this assertion into question [@Pennebaker2011].
@@
 First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
-In other words, RFT represents one method by which to analyze political text, but with the caveat that the categories are not known to represent patterns of political ideology.
-One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it was a theory designed to investigate not only moral differences but also political differences.
+In other words, RFT represents one method by which to analyze political text by analyzing occurrence of particular frames.
+However, there exists the caveat that the frame families are not known to represent patterns of political ideology at this time.
+One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it is a theory under which endorsement patterns (direction and relationship) could be predicted based upon political affiliation.
 While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
@@
 As such, RFT's potential as a useful framework for political discourse analysis should not be discounted.
+
+CONTEXT!
 
@@
 \endgroup
+
+\newpage
+
+# Appendix
+
+```{r appendix_mfd, eval = T, include = T}
+orig_mfd = read.csv("exp1_data/original_mfd.csv")
+####build the table here####
+tableprint = matrix(NA, nrow=length(orig_mfd), ncol=5)
+colnames(tableprint) = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity")
+
+#tableprint[ , 1] = unique(final_gs$Source)
+tableprint[ , 1] = orig_mfd[,1]
+tableprint[ , 2] = orig_mfd[,2]
+tableprint[ , 3] = orig_mfd[,3]
+tableprint[ , 4] = orig_mfd[,4]
+tableprint[ , 5] = orig_mfd[,5]
+
+tableprint = tableprint[c(1,2,3,4,5)]
+tableprint = orig_mfd
+#change this to match
+apa_table(as.data.frame(tableprint),
+          note = "Original Moral Foundations Dictionary from Graham et al. (2009)",
+          caption = "Moral Foundations Dictionary", 
+          col.names = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity"),
+          format = "latex",
+          escape = F,
+          small = T, 
+          align = c("l", rep("c", 6))
+          )
+```

### 2019-04-24 pilot_manuscript.Rmd
Fixed more stuff. Almost done!!

@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          #caption = "Experiment 1 Results - Multilevel Model", 
+          caption = "Experiment 1 Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          #caption = "Kavanaugh Results - Multilevel Model", 
+          caption = "Kavanaugh Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          #caption = "Government Shutdown Results - Multilevel Model", 
+          caption = "Government Shutdown Results - Multilevel Model", 
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
 Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
+Given part of the researchers' goal with this study was to answer a method question, they must contemplate whether or not the method or the construct of interest (political lean) are the primary contributor to null results.
+Either the method used to detect lean was insufficent for this purpose, or political lean simply does not exist, indicating the presence of a true negative in the results.
+
+The researchers believe these results represent a false negative rather than a true negative.
+That is, we believe political lean exists, but that we have been unable to detect it at a content level.
+The researchers again turn to @Mitchell2014's work in this area: political partisans prefer certain news outlets over others.
+There must be something about the sources' content that facilitates partisans' repeated usage.
+Otherwise, they might not express such loyalty to any one source (or group of sources) over others.
+Given this aspect of the news economy, the researchers still believe certain news outlets in the U.S.
+contatin a political slant.
 The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
@@
 While this might have helped that team fix mistakes made by the LIWC program (@Pennebaker2007), manual coding of this nature has the potential to introduce an unnacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and beleif systems.
-
-Thus, the researchers' attention turned to the instrument used to detect differences.
-In the present study, the researchers utilized the Moral Foundations Dictionary, a metric developed from Moral Foundations Theory [@Graham2009].
+Additionally, the numerous ways in which context affects meaning make it difficult to interpret MFD word occurrence outside of a narrow operational definition of "endorsement." In fact, political lean may be communicated through methods other than through the use of particular words.
+
+One method through which news organizations might appeal to political partisans is through their content strategy rather than their use of MFD words.
+The results in the current study demonstrate a similar pattern of endorsement across both conservative and liberal sources.
+Specifically, the researchers found slightly positive endorsements for all five foundations no matter the political lean of the source.
+While this may simply be an indication of insufficient MFD word occurrence in news articles, it may also demonstrate truly equal endorsement despite political lean.
+While news organizations may endorse all moral foundations, they may also adopt strategies for doing so that appeal to the political partisans consuming their product.
+As an example, a liberal source might endorse *purity/sanctity* through an appeal to reduce waste or pollution (i.e.
+keeping the earth "clean").
+A conservative source, on the other hand, might endorse *purity/sanctity* through an argument in favor of abstinence or religious commitment (i.e.
+keeping a "clean" soul, mind, or body).
+Both publications would register as positive endorsement of *purity/sanctity* despite appropriating the concept for distinct purposes.
+Through these divergent strategies, liberal and conservative news organizations might be able to appeal to their fans while exhibiting similar levels of moral endorsement.
+This could represent a further weakness of the Moral Foudnations Dictionary as an instrument, as it is unable to identify these potential strategies for communicating certain points of view.
+
+Thus, the researchers' attention turned to the instrument used to detect differences: the Moral Foundations Dictionary.
+As mentioned before, MFD is a measure developed from Moral Foundations Theory [@Graham2009].
 Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
@@
 RFT utilizes a set of "families" describing the nature of these relationships.
-Such families include "coordinative," establishing similarities between stimuli, and "distinctive," implying fundamental differences between stimuli [@Belisle2018].
+Such families include (among others) "coordinative," establishing similarities between stimuli, "distinctive," implying fundamental differences between stimuli, and "hierarchical," implying a relation in terms of differing order or rank [@Belisle2018].
 These families can be used to analyze networks of relational frames in discourse.
@@
 These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
-For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts [@Belisle2018].
+For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts.
+According to @Belisle2018, these observations imply President Obama, who empolyed more coordinative frames, utilized language emphasizing unity and similarity between people.
+Donald Trump, on the other hand emphasized differences and divisions between people through his use of distinctive frames [@Belisle2018].
 At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
@@
 
-CONTEXT!
+MAYBE DO DATA, THEN THEORIZE
 
@@
 MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
-In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, or through a different theoretical perspective such as Relational Frame Theory.
+In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, through a different theoretical perspective such as Relational Frame Theory, or through alternative strategies involving collecting data and drawing conclusions from which future theories may be derived.
 

### 2019-04-24 pilot_manuscript.Rmd
Another update; copy editing is next

@@
 Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
-Likewise, other theoretical perspectives may be more equipped to explain political differences in discourse.
-
-Tools such as these could be developed through the Linguistic Inquiry and Word Count program (LIWC) [@Pennebaker2007].
+Going beyond specific instruments, other theoretical perspectives may be more equipped to explain political differences in discourse.
+Likewise, an atheoretical approach in which large quantities of data are collected from which theories are formulated may be best suited to this area of research.
+
+Alternative instruments could be developed through the Linguistic Inquiry and Word Count program (LIWC) [@Pennebaker2007].
 As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context [@Graham2009].
@@
 
-Other instruments could theoretically be developed through a LIWC analysis, including those that would be useful for analyzing political discourse.
+Instruments that improve upon the Moral Foundations Dictionary could theoretically be developed through a LIWC analysis.
 Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from @Warriner2013.
@@
 
-MAYBE DO DATA, THEN THEORIZE
+Finally, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
+Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
+The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
+Likewise, there are several approaches to analyzing such data, including linear models (like multi-level models) and network-style models such as latent semantic analysis [@Landauer1998].
+Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
 

### 2019-04-24 pilot_manuscript.tex
Fixing shit for the knit (it rhymes)

@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 
@@
 ideology. In Experiment 1, the researchers gathered poltical articles
-from four sources. They were unable to reveal significant differences in
-moral or political endorsements, but they solidified the method to be
+from four sources. We were unable to reveal significant differences in
+moral or political endorsements, but we solidified the method to be
 employed in further research. In Experiment 2, the researchers expanded
@@
 assumptions regarding moral intuitions have little empirical basis.
-Suhler and Churchland (2011) list several potential weaknesses of MFT
-that they argue might threaten the theory's validity. First, the authors
-challenge Haidt and Graham (2007)'s claims the moral intuitions
-represented by MFT are innate and modular. Suhler and Churchland (2011)
-claim that advances in biological sciences (embryology and microbiology,
+Suhler, Churchland, and Joseph (2011) list several potential weaknesses
+of MFT that they argue might threaten the theory's validity. First, the
+authors challenge Haidt and Graham (2007)'s claims the moral intuitions
+represented by MFT are innate and modular. Suhler et al. (2011) claim
+that advances in biological sciences (embryology and microbiology,
 specifically) make it more difficult for researchers to claim any one
@@
 likely result from interactions between genetics and experience (Suhler
-\& Churchland, 2011). According to the authors, without solid data
-supporting the innateness of moral foundations, Haidt and Graham have
-little from which to make such a claim. Similarly, Haidt and Graham
-(2007) rely on evidence authored by evolutionary psychologists to make a
-\enquote{strong modularity claim} (Suhler \& Churchland, 2011). However,
-as with innateness, there is little neurobiological evidence to support
+et al., 2011). According to the authors, without solid data supporting
+the innateness of moral foundations, Haidt and Graham have little from
+which to make such a claim. Similarly, Haidt and Graham (2007) rely on
+evidence authored by evolutionary psychologists to make a
+\enquote{strong modularity claim} (Suhler et al., 2011). However, as
+with innateness, there is little neurobiological evidence to support
 modularity.
 
-Suhler and Churchland (2011) also criticized the content and taxonomy of
-the five foundations. The authors criticize Haidt and Graham (2007)'s
+Suhler et al. (2011) also criticized the content and taxonomy of the
+five foundations. The authors criticize Haidt and Graham (2007)'s
 omissions of additional foundations, including \emph{industry} and
@@
 are sufficiently distinct as to stand as their own foundation. For
-example, Suhler and Churchland (2011) posit that \emph{ingroup/loyalty}
-is merely a group-focused version of \emph{harm/care}. Work by Graham et
+example, Suhler et al. (2011) posit that \emph{ingroup/loyalty} is
+merely a group-focused version of \emph{harm/care}. Work by Graham et
 al. (2011) might serve to rebut this criticism, as the researchers found
 their original five-factor structure seemed to best fit the data when
-validating the Moral Foundations Questionnaire. Finally, Suhler and
-Churchland (2011) point out that particular concepts related to a
-foundation, including \enquote{anger} in \emph{fairness/reciprocity} and
+validating the Moral Foundations Questionnaire. Finally, Suhler et al.
+(2011) point out that particular concepts related to a foundation,
+including \enquote{anger} in \emph{fairness/reciprocity} and
 \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any
@@
 when, in theory, they could be applied to all five (Haidt \& Graham,
-2007; Suhler \& Churchland, 2011).
+2007; Suhler et al., 2011).
 
@@
 taken into consideration when conducting research with instruments
-derived from MFT. The current authors argue these criticisms are
-especially valid when considered alongside questions regarding the Moral
-Foundations Dictionary they state herein. However, there exists
-compelling evidence regarding the validity of Moral Foundations Theory,
-albeit regarding its application solely through the Moral Foundations
-Questionnaire. This evidence is discussed within a brief explanation of
-the Moral Foundations Questionnaire and its relationship to the Moral
-Foundations Dictionary.
+derived from MFT. Such criticisms are especially valid when considered
+alongside questions about the Moral Foundations Dictionary in
+particular. Nevertheless, there exists compelling evidence supporting
+the validity of Moral Foundations Theory, albeit regarding its
+application solely through the Moral Foundations Questionnaire. This
+evidence is discussed within a brief explanation of the Moral
+Foundations Questionnaire and its relationship to the Moral Foundations
+Dictionary in the next section.
 
@@
 and text. The MFD is composed of 259 words, with around 50 words
-assigned to each of the five foundations. The researchers created a
+assigned to each of the five foundations. Graham et al. (2009) created a
 preliminary list of words that they believed would be associated with
@@
 order to obtain frequencies of the occurrence of words from the
-researchers' initial list. The researchers manually checked the results
-from LIWC in order to make sure the results make sense given the
+researchers' initial list. Graham et al. (2009) manually checked the
+results from LIWC in order to make sure the results make sense given the
 contexts and rhetorical devices used in the sermons, as word frequency
@@
 authority-related words and the speaker's clear intentions (Graham et
-al., 2009).
+al., 2009). The original Moral Foundations Dictionary can be found in
+the Appendix.
 
@@
 moral foundations are sufficiently distinct from one another, though
-broader criticisms of MFT raised by Suhler and Churchland (2011) should
-still be taken into account in studies involving the theory.
+broader criticisms of MFT raised by Suhler et al. (2011) should still be
+taken into account in studies involving the theory.
 
@@
 (Wickham, 2016). Using this dataset, we identified word count and
-average word count per source. This process was run once daily starting
-in February 2018 until March 2018. Starting in mid-March 2018, the
-process was run twice daily - once in the morning and again in the
-evening. Data collection was terminated once 250,000 words per source
-was collected in April 2018.
+average word count per source. This process was completed once daily
+starting in February 2018 until March 2018. Starting in mid-March 2018,
+the process was completed twice daily - once in the morning and again in
+the evening. Data collection was terminated once 250,000 words per
+source was collected in April 2018.
 
@@
 slightly positive across all sources. The large standard deviations seem
-to indicate little to no presence of a difference in valence. \emph{The
-New York Times} published the greatest number of articles as well as
-total words. \emph{Breitbart} featured the lowest number of articles,
-and \emph{NPR} the lowest number of total words from all articles. Per
-individual article, however, \emph{Breitbart} appears to feature the
-highest average number of words as well as unique words. Once again the
-standard deviations call into question any apparent differences between
-sources. Finally, \emph{Fox News} appears to be the most readable source
-on average, while \emph{The New York Times} is the least readable. This
-result might be attributable to the greater number of tokens in the
-average \emph{New York Times} article compared to \emph{Fox News}. As
-before, the standard deviations for readability hamper one's ability to
-draw solid conclusions regarding differences in the sources' use of
-language.
+to indicate little to no presence of a difference in valence across
+sources. \emph{The New York Times} published the greatest number of
+articles as well as total words. \emph{Breitbart} featured the lowest
+number of articles, and \emph{NPR} the lowest number of total words from
+all articles. Per individual article, however, \emph{Breitbart} appears
+to feature the highest average number of words as well as unique words.
+Once again the standard deviations call into question any apparent
+differences between sources. Finally, \emph{Fox News} articles had the
+lowest reading grade level on average, while \emph{The New York Times}
+ihad the highest. This result might be attributable to the greater
+number of tokens in the average \emph{New York Times} article compared
+to \emph{Fox News}. The standard deviations for readability suggest the
+presence of a diverse array of articles for each source, ranging from
+low to high reading level. Large standard deviations suggest the sources
+feature a lot of overlap between them in their representation of scores.
 
@@
 \begin{threeparttable}
-\caption{\label{tab:exp1-table}}
+\caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
 \begin{tabular}{lccccccc}
@@
 The sources were similar in most basic linguistic aspects, except for
-number of articles. For example, \emph{Sean hannity} appears to have
+number of articles. For example, \emph{Sean Hannity} appears to have
 published only 27 articles while \emph{Breitbart} published 757 articles
@@
 sources. \emph{Fox News} produced the most total words with the most
-tokens on average. \emph{Politico} featured the highest number of types
-on average. \emph{Rush Limbaugh} was the most readable source on average
-by grade level while \emph{Slate} was the least readable. The large
-standard deviations for these statistics, however, preclude conclusions
-regarding differences in the sources' use of language.
+tokens on average. This is likely due to the fact \emph{Fox News}
+transcribes many of their videos and publishes them in article form.
+\emph{Politico} featured the highest number of types on average.
+\emph{Rush Limbaugh} featured the lowest readability score on average by
+grade level while \emph{Slate} featured the highest grade-level
+readability score. The large standard deviations for these statistics,
+however, preclude conclusions regarding differences in the sources' use
+of language, as there is likely a lot of overlap between sources' use of
+language.
 
@@
 \emph{Fox News} published 1,013 articles. \emph{Fox News} again featured
-the most total words and mean tokens. \emph{Politico} had the most types
-on average. For this topic, \emph{Fox News} was the most readable while
-\emph{Slate} was the least readable. For each statistic, the excessively
-high standard deviations render any assertions regarding linguistic
-differences inconclusive on a descriptive level.
+the most total words and mean tokens, but this is likely due to to the
+presence of a large amount of video transcriptions that the organization
+published as articles. \emph{Politico} had the most types on average.
+For this topic, \emph{Fox News} featured the lowest reading grade level
+while \emph{Slate} featured the highest reading grade level. For each
+statistic, the excessively high standard deviations render any
+assertions regarding linguistic differences inconclusive on a
+descriptive level due to the aforementioned overlap in sources' language
+use.
 
@@
 \begin{threeparttable}
-\caption{\label{tab:exp2-tablekav}}
+\caption{\label{tab:exp2-tablekav}Kavanaugh Results - Multilevel Model}
 \begin{tabular}{lccccccc}
@@
 \begin{threeparttable}
-\caption{\label{tab:exp2-tablegs}}
+\caption{\label{tab:exp2-tablegs}Government Shutdown Results - Multilevel Model}
 \begin{tabular}{lccccccc}
@@
 topics, the method failed to detect differences in MFD word use by
-prominent news sources. The researchers' focus, therefore, turns toward
-the limitations of the method, especially the chosen theoretical
-framework, under which the present research was conducted.
+prominent news sources. Given part of the researchers' goal with this
+study was to answer a method question, they must contemplate whether or
+not the method or the construct of interest (political lean) are the
+primary contributor to null results. Either the method used to detect
+lean was insufficent for this purpose, or political lean simply does not
+exist, indicating the presence of a true negative in the results.
+
+The researchers believe these results represent a false negative rather
+than a true negative. That is, we believe political lean exists, but
+that we have been unable to detect it at a content level. The
+researchers again turn to Mitchell et al. (2014)\enquote{s work in this
+area: political partisans prefer certain news outlets over others. There
+must be something about the sources} content that facilitates partisans'
+repeated usage. Otherwise, they might not express such loyalty to any
+one source (or group of sources) over others. Given this aspect of the
+news economy, the researchers still believe certain news outlets in the
+U.S. contatin a political slant. The researchers' focus, therefore,
+turns toward the limitations of the method, especially the chosen
+theoretical framework, under which the present research was conducted.
 
@@
 
+There remains an aspect of language which this method still cannot
+address: context. Owing to the presence of millions of words in the
+analyses presented in the current study, the researchers would be unable
+to check for context and correct endorsement scores accordingly. Graham
+et al. (2009) actually performed a process of human error-checking for
+context when formulating the MFD. While this might have helped that team
+fix mistakes made by the LIWC program (Pennebaker et al. (2007)), manual
+coding of this nature has the potential to introduce an unnacceptable
+level of bias in the method, as perceptions of context would be
+dependent upon raters' interpretations and beleif systems. Additionally,
+the numerous ways in which context affects meaning make it difficult to
+interpret MFD word occurrence outside of a narrow operational definition
+of \enquote{endorsement.} In fact, political lean may be communicated
+through methods other than through the use of particular words.
+
+One method through which news organizations might appeal to political
+partisans is through their content strategy rather than their use of MFD
+words. The results in the current study demonstrate a similar pattern of
+endorsement across both conservative and liberal sources. Specifically,
+the researchers found slightly positive endorsements for all five
+foundations no matter the political lean of the source. While this may
+simply be an indication of insufficient MFD word occurrence in news
+articles, it may also demonstrate truly equal endorsement despite
+political lean. While news organizations may endorse all moral
+foundations, they may also adopt strategies for doing so that appeal to
+the political partisans consuming their product. As an example, a
+liberal source might endorse \emph{purity/sanctity} through an appeal to
+reduce waste or pollution (i.e.~keeping the earth \enquote{clean}). A
+conservative source, on the other hand, might endorse
+\emph{purity/sanctity} through an argument in favor of abstinence or
+religious commitment (i.e.~keeping a \enquote{clean} soul, mind, or
+body). Both publications would register as positive endorsement of
+\emph{purity/sanctity} despite appropriating the concept for distinct
+purposes. Through these divergent strategies, liberal and conservative
+news organizations might be able to appeal to their fans while
+exhibiting similar levels of moral endorsement. This could represent a
+further weakness of the Moral Foudnations Dictionary as an instrument,
+as it is unable to identify these potential strategies for communicating
+certain points of view.
+
 Thus, the researchers' attention turned to the instrument used to detect
-differences. In the present study, the researchers utilized the Moral
-Foundations Dictionary, a metric developed from Moral Foundations Theory
-(Graham et al., 2009). Based upon the results obtained, it might be
-necessary to investigate alternative instruments that might better
-elucidate the differences of interest. Likewise, other theoretical
-perspectives may be better equipped to explain political differences in
-discourse.
-
-Tools such as these could be developed through the Linguistic Inquiry
-and Word Count program (LIWC) (Pennebaker et al., 2007). As stated
-before, the Moral Foundations Dictionary was established through an
-analysis of Christian sermons performed mostly with LIWC as well as some
-human-enforced corrections due to context (Graham et al., 2009). This
-approach was grounded in Moral Foundations Theory, a clear framework
-within which the authors developed the MFD. The original authors of the
-MFD established sound psychometric properties for the tool, implying its
-validity in several applications. For this reason, the researchers
-elected to utilize the MFD as their primary instrument.
-
-Other instruments could theoretically be developed through a LIWC
-analysis, including those that would be useful for analyzing political
-discourse. Researchers could obtain percent occurrence scores for words
-appearing in certain LIWC categories, which could then be weighted with
-valence scores from Warriner et al. (2013). The researchers will
-consider other applications of the LIWC in future studies aiming to
-analyze political content. James Pennebaker (2007), one of the creators
-of LIWC, has suggested the program could be applied to analyses of
-cognitive, social, and emotional states. Furthermore, there is some
-evidence LIWC can be used to detect deception, but the reliability of
-the program's accuracy in this regard (67\%) calls this assertion into
-question (Pennebaker, 2011). Despite the promising extent of LIWC's
-abilities, without a firm theoretical foundation for such analyses, any
-such applications of LIWC would face serious questions as to their
-relevance, validity, and generalizability. Nevertheless, LIWC analyses
-may represent a path to further research into political differences in
-news media as well as theory formation.
+differences: the Moral Foundations Dictionary. As mentioned before, MFD
+is a measure developed from Moral Foundations Theory (Graham et al.,
+2009). Based upon the results obtained, it might be necessary to
+investigate alternative instruments that could better elucidate the
+differences of interest. Going beyond specific instruments, other
+theoretical perspectives may be more equipped to explain political
+differences in discourse. Likewise, an atheoretical approach in which
+large quantities of data are collected from which theories are
+formulated may be best suited to this area of research.
+
+Alternative instruments could be developed through the Linguistic
+Inquiry and Word Count program (LIWC) (Pennebaker et al., 2007). As
+stated before, the Moral Foundations Dictionary was established through
+an analysis of Christian sermons performed mostly with LIWC as well as
+some human-enforced corrections due to context (Graham et al., 2009).
+This approach was grounded in Moral Foundations Theory, a clear
+framework within which the authors developed the MFD. The original
+authors of the MFD established sound psychometric properties for the
+tool, implying its validity in several applications. For this reason,
+the researchers elected to utilize the MFD as their primary instrument.
+
+Instruments that improve upon the Moral Foundations Dictionary could
+theoretically be developed through a LIWC analysis. Researchers could
+obtain percent occurrence scores for words appearing in certain LIWC
+categories, which could then be weighted with valence scores from
+Warriner et al. (2013). The researchers will consider other applications
+of the LIWC in future studies aiming to analyze political content.
+Pennebaker et al. (2007) has suggested the program could be applied to
+analyses of cognitive, social, and emotional states. Furthermore, there
+is some evidence LIWC can be used to detect deception, but the
+reliability of the program's accuracy in this regard (67\%) calls this
+assertion into question (Pennebaker, 2011). Despite the promising extent
+of LIWC's abilities, without a firm theoretical foundation for such
+analyses, any such applications of LIWC would face serious questions as
+to their relevance, validity, and generalizability. Nevertheless, LIWC
+analyses may represent a path to further research into political
+differences in news media as well as theory formation.
 
@@
 \enquote{families} describing the nature of these relationships. Such
-families include \enquote{coordinative,} establishing similarities
-between stimuli, and \enquote{distinctive,} implying fundamental
-differences between stimuli (Belisle, Paliliunas, Dixon, \& Tarbox,
-2018). These families can be used to analyze networks of relational
-frames in discourse.
+families include (among others) \enquote{coordinative,} establishing
+similarities between stimuli, \enquote{distinctive,} implying
+fundamental differences between stimuli, and \enquote{hierarchical,}
+implying a relation in terms of differing order or rank (Belisle,
+Paliliunas, Dixon, \& Tarbox, 2018). These families can be used to
+analyze networks of relational frames in discourse.
 
@@
 distinctive frames than other presidents, while Barack Obama utilized
-more coordinative frames than his counterparts (Belisle et al., 2018).
-At first glance, the differences appear to fall along party lines,
-though other factors may be involved as well. In any case, this research
-appears to indicate that RFT might be useful for analyzing political
-news content similar to the method employed in the current study.
+more coordinative frames than his counterparts. According to Belisle et
+al. (2018), these observations imply President Obama, who empolyed more
+coordinative frames, utilized language emphasizing unity and similarity
+between people. Donald Trump, on the other hand emphasized differences
+and divisions between people through his use of distinctive frames
+(Belisle et al., 2018). At first glance, the differences appear to fall
+along party lines, though other factors may be involved as well. In any
+case, this research appears to indicate that RFT might be useful for
+analyzing political news content similar to the method employed in the
+current study.
 
@@
 well established. In other words, RFT represents one method by which to
-analyze political text, but with the caveat that the categories are not
-known to represent patterns of political ideology. One of the main
-strengths of Moral Foundations Theory in the eyes of the researchers was
-that it was a theory designed to investigate not only moral differences
-but also political differences. While the results obtained herein may
-weaken assumptions regarding the MFD's capabilities with political text,
-Moral Foundations Theory has been repeatedly established as a strong
-framework for detecting political differences along moral lines.
+analyze political text by analyzing occurrence of particular frames.
+However, there exists the caveat that the frame families are not known
+to represent patterns of political ideology at this time. One of the
+main strengths of Moral Foundations Theory in the eyes of the
+researchers was that it is a theory under which endorsement patterns
+(direction and relationship) could be predicted based upon political
+affiliation. While the results obtained herein may weaken assumptions
+regarding the MFD's capabilities with political text, Moral Foundations
+Theory has been repeatedly established as a strong framework for
+detecting political differences along moral lines.
 
@@
 not be discounted.
+
+Finally, future studies aiming to uncover political lean in discourse
+may benefit from a bottom-up, data-driven approach. Researchers might
+derive substantive insights into political lean through gathering data
+after which they may formulate theories that explain systematic
+observations obtained from that data. The availability of text corpora
+along with methods for extracting large amounts of text from the
+internet (as was demonstrated in the current study) potentially make
+this a feasible option. Likewise, there are several approaches to
+analyzing such data, including linear models (like multi-level models)
+and network-style models such as latent semantic analysis (Landauer,
+1998). Owing to the wealth of representative data as well as the
+sophistication of current analytic tools, there is high potential for
+the explanatory power of new theories involving political discourse.
 
@@
 alterations to the method, including alternative analyses using computer
-programs including LIWC, or through a different theoretical perspective
-such as Relational Frame Theory.
+programs including LIWC, through a different theoretical perspective
+such as Relational Frame Theory, or through alternative strategies
+involving collecting data and drawing conclusions from which future
+theories may be derived.
 
@@
 Kincaid, J. P., Fishburne, J., Robert P., R., Richard L., C., \& Brad S.
-(1975). Derivation of new readability formulas (Automated Readability
-Index, Fog Count and Flesch Reading Ease Formula) for Navy enlisted
-personnel.
+(1975). Derivation of New Readability Formulas (Automated Readability
+Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted
+Personnel.
 doi:\href{https://doi.org/10.21236/ADA006655}{10.21236/ADA006655}
@@
 
+\hypertarget{ref-Landauer1998}{}
+Landauer, T. K. (1998). Learning and Representing Verbal Meaning.
+\emph{Current Directions in Psychological Science}, \emph{7}(5),
+161--164.
+doi:\href{https://doi.org/10.1111/1467-8721.ep10836862}{10.1111/1467-8721.ep10836862}
+
 \hypertarget{ref-Martin2019}{}
-Martin, M. (2019). The moral question opf Trump's border wall. NPR.
+Martin, M. (2019). The Moral Question Of Trump's Border Wall : NPR. NPR.
 Retrieved from
@@
 \hypertarget{ref-OConnell2018}{}
-O'Connell, M. (2018). Ford-Kavanaugh Ratings: Hearing brings 20 million
+O'Connell, M. (2018). Ford-Kavanaugh Ratings: Hearing Brings 20 Million
 viewers to cable and broadcast \textbar{} Hollywood Reporter. Retrieved
@@
 \hypertarget{ref-Suhler2011}{}
-Suhler, C. L., \& Churchland, P. (2011). Can innate, modular
-``foundations'' explain morality? Challenges for Haidt's Moral
-Foundations Theory. \emph{Journal of Cognitive Neuroscience},
+Suhler, C. L., Churchland, P., \& Joseph, C. (2011). Can Innate ,
+Modular `` Foundations '' Explain Morality ? Challenges for Haidt's
+Moral Foundations Theory. \emph{Journal of Cognitive Neuroscience},
 \emph{23}(9), 2103--2116.
-doi:\href{https://doi.org/10.1162/jocn.2011.21637}{10.1162/jocn.2011.21637}
 
@@
 
+\newpage
+
+\section{Appendix}\label{appendix}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:appendix_mfd}Moral Foundations Dictionary}
+\small{
+\begin{tabular}{lcccc}
+\toprule
+Harm/Care & Fairness/Reciprocity & Ingroup/Loyalty & Authority/Respect & Purity/Sanctity\\
+\midrule
+abuse & balance & collect & abide & abstain\\
+attack & bias & community & authority & adultery\\
+benefit & constant & deceive & class & church\\
+care & discriminate & desert & command & clean\\
+cruel & equal & family & control & dirt\\
+crush & equate & fellow & defect & disease\\
+damage & even & foreign & defer & disgust\\
+danger & exclude & group & defy & gross\\
+defend & fair & individual & desert & innocent\\
+destroy & favor & member & duty & modest\\
+fight & honest & nation & faith & preserve\\
+guard & impartial & side & father & promiscuous\\
+harm & just & together & honor & pure\\
+hurt & justify & trait & law & right\\
+kill & prefer & unite & lead & ruin\\
+preserve & prejudice &  & legal & sacred\\
+protect & reason &  & mother & sick\\
+ruin & right &  & obey & sin\\
+safe & tolerate &  & oppose & trash\\
+shelter &  &  & order & whole\\
+spurn &  &  & permit & \\
+stomp &  &  & position & \\
+suffer &  &  & preserve & \\
+sympathy &  &  & protest & \\
+violent &  &  & refuse & \\
+war &  &  & respect & \\
+ &  &  & revere & \\
+ &  &  & serve & \\
+ &  &  & tradition & \\
+ &  &  & trait & \\
+\bottomrule
+\addlinespace
+\end{tabular}
+}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Original Moral Foundations Dictionary from Graham et al. (2009)}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
 \end{document}

### 2020-07-29 manuscript/Partisan Media Manuscript.Rmd
updating

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(rio)
```

# Experiment 1

move the data collection from the original thesis

```{r}
exp1 <- import("finaldata_LIWC.csv")
exp1 <- na.omit(exp1)

library(nlme)

model1 <- gls(Analytic ~ 1,
              data = exp1,
              method = "ML",
              na.action = "na.omit")

model2 <- lme(Analytic ~ 1,
              data = exp1,
              method = "ML",
              random = list(~1|Source), 
              na.action = "na.omit")

model3 <- lme(Analytic ~ PartisanLean,
              data = exp1,
              method = "ML",
              random = list(~1|Source), 
              na.action = "na.omit")
anova(model1,model2,model3)
```

Doing the bootstrapping thing from the language of war paper
- analytic, cognitive processing, authenticity, tone, clout

# Experiment 2

move the data collection from the original thesis
both effect sizes and topics analysis

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-07-29 thesis/pilot_manuscript.Rmd
updating

--- 2019-04-24 pilot_manuscript.Rmd
@@
 footnotelist      : no
-lineno            : yes
+lineno            : no
 lang              : "english"
@@
 
-```{r appendix_mfd, eval = T, include = T}
-orig_mfd = read.csv("exp1_data/original_mfd.csv")
+```{r appendix_mfd, results = 'asis', echo = FALSE, message = F}
+orig_mfd = read.csv("exp1_data/original_mfd.csv", stringsAsFactors = F, fileEncoding="UTF-8")
 ####build the table here####
@@
 #tableprint[ , 1] = unique(final_gs$Source)
-tableprint[ , 1] = orig_mfd[,1]
-tableprint[ , 2] = orig_mfd[,2]
-tableprint[ , 3] = orig_mfd[,3]
-tableprint[ , 4] = orig_mfd[,4]
-tableprint[ , 5] = orig_mfd[,5]
+#tableprint[ , 1] = orig_mfd[,1]
+#tableprint[ , 2] = orig_mfd[,2]
+#tableprint[ , 3] = orig_mfd[,3]
+#tableprint[ , 4] = orig_mfd[,4]
+#tableprint[ , 5] = orig_mfd[,5]
 

### 2020-07-31 manuscript/Partisan Media Manuscript.Rmd
bootstrap function and study 1

@@
 ```{r setup, include = FALSE}
-library("papaja")
+library(papaja)
 library(rio)
+library(forestplot)
+library(boot)
+library(nlme)
+library(MOTE)
+library(tools)
+
+setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
+nsim = 100
+
+####make the table for study 1####
+table1 = matrix(NA, ncol = 12, nrow = 23)
+colnames(table1) = c("DV", "Mconservative", 
+                     "SDconservative", "Mliberal", "SDliberal", 
+                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
+                     "bcilowL", "bcihighL")
+table1 = as.data.frame(table1)
+
+####make the table for study 2: government shutdown####
+table2 = matrix(NA, ncol = 12, nrow = 23)
+colnames(table2) = c("DV", "Mconservative", 
+                     "SDconservative", "Mliberal", "SDliberal", 
+                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
+                     "bcilowL", "bcihighL")
+table2 = as.data.frame(table2)
+
+####make the table for study 2: Kavanaugh Hearings####
+table3 = matrix(NA, ncol = 12, nrow = 23)
+colnames(table3) = c("DV", "Mconservative", 
+                     "SDconservative", "Mliberal", "SDliberal", 
+                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
+                     "bcilowL", "bcihighL")
+table3 = as.data.frame(table3)
+
+```
+
+```{r bootstrap-function, include = FALSE}
+####bootstrap function #####
+bootstrap_values <- function(formula, dataset, nsim){
+
+  store_mean <- rep(NA, nsim)
+  store_sd <- rep(NA, nsim)  
+  attempts <- 0
+  #loop until you have enough
+  while(attempts < nsim){
+    #create a dataset
+    d <- dataset[sample(1:nrow(dataset), 
+                        size = nrow(dataset),
+                        replace = TRUE), ]
+    #test the model
+    tryCatch({
+
+      model1 = lme(formula, 
+             data = d, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = list(~1|Source),
+             control=lmeControl(opt = "nlminb")) 
+      meanvalue = summary(model1)$tTable[1]
+      sdvalue = summary(model1)$tTable[2] * sqrt(nrow(d))
+      attempts <- attempts + 1
+      store_mean[attempts] <- meanvalue
+      store_sd[attempts] <- sdvalue
+      return(store_mean, store_sd, attempts)
+    }, error = function(x){})
+  }
+
+  return(list("mean" = store_mean, "sd" = store_sd))
+}
+
 ```
@@
 
-```{r}
+```{r bootstrap study 1}
 exp1 <- import("finaldata_LIWC.csv")
 exp1 <- na.omit(exp1)
+exp1$PartisanLean = ifelse(exp1$PartisanLean=='Conservative', 0, 1)
+groups = c(0, 1)
+DVs = c('Analytic','Clout','Authentic','Tone','WPS','Sixltr','anger','social','family','female','male','cogproc','affiliation','achieve','power','reward','risk','focuspast','focuspresent','focusfuture','money','relig','death')
+r = 1
+for(DV in DVs){
+  for(group in groups){
+    data = subset(exp1, PartisanLean==group)
+    f = as.formula(paste(DV,'~1', sep=''))
+    bs = bootstrap_values(f,data,nsim)
+    table1[r, 1] = DV
+    if(group==0){
+      table1[r, 2] = mean(bs$mean)
+      table1[r, 3] = mean(bs$sd)
+      ncon = length(na.omit(data[[DV]]))
+      table1[r, 9] = quantile(bs$mean, 0.025)
+      table1[r, 10] = quantile(bs$mean, 0.975)
+    }
+    if(group==1){
+      table1[r, 4] = mean(bs$mean)
+      table1[r, 5] = mean(bs$sd)
+      nlib = length(na.omit(data[[DV]]))
+      table1[r, 11] = quantile(bs$mean, 0.025)
+      table1[r, 12] = quantile(bs$mean, 0.975)
+    }
+  }
+  mdiff = d.ind.t(m1 = table1[r,2], m2 = table1[r,3], 
+                sd1 = table1[r,4], sd2 = table1[r,5],
+                n1 = ncon, 
+                n2 = nlib, 
+                a = .05)
+  table1[r, 6] = mdiff$d
+  table1[r, 7] = mdiff$dlow
+  table1[r, 8] = mdiff$dhigh
+  r = r + 1
+}
 
-library(nlme)
-
-model1 <- gls(Analytic ~ 1,
-              data = exp1,
-              method = "ML",
-              na.action = "na.omit")
-
-model2 <- lme(Analytic ~ 1,
-              data = exp1,
-              method = "ML",
-              random = list(~1|Source), 
-              na.action = "na.omit")
-
-model3 <- lme(Analytic ~ PartisanLean,
-              data = exp1,
-              method = "ML",
-              random = list(~1|Source), 
-              na.action = "na.omit")
-anova(model1,model2,model3)
 ```
@@
 both effect sizes and topics analysis
+
+```{r bootstrap study 2: goverment shutdown}
+exp2 <- import("exp2_merged data_LIWC.csv")
+colnames(exp2)[1:5] = c('Source', 'URL', 'Text', 'Event', 'PartisanLean')
+#subset with Event=='gs'
+```
+
+```{r bootstrap study 2: kavanaugh hearings}
+exp2 <- import("exp2_merged data_LIWC.csv")
+colnames(exp2)[1:5] = c('Source', 'URL', 'Text', 'Event', 'PartisanLean')
+#subset with Event=='kav'
+
+```
 

### 2020-08-03 manuscript/Partisan Media Manuscript.Rmd
updating manuscript

--- 2020-07-29 manuscript/Partisan Media Manuscript.Rmd
@@
 ```{r setup, include = FALSE}
-library("papaja")
+#install.packages(c("devtools", "rio", "forestplot", "nlme", "MOTE", "tools"))
+#devtools::install_github("crsh/papaja")
+library(papaja) 
 library(rio)
+library(forestplot)
+library(nlme)
+library(MOTE)
+library(tools)
+
+#setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
+nsim = 100
+
+####make the table for study 1####
+table1 = matrix(NA, ncol = 12, nrow = 23)
+colnames(table1) = c("DV", "Mconservative", 
+                     "SDconservative", "Mliberal", "SDliberal", 
+                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
+                     "bcilowL", "bcihighL")
+table1 = as.data.frame(table1)
+
+####make the table for study 2: government shutdown####
+table2 = matrix(NA, ncol = 12, nrow = 23)
+colnames(table2) = c("DV", "Mconservative", 
+                     "SDconservative", "Mliberal", "SDliberal", 
+                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
+                     "bcilowL", "bcihighL")
+table2 = as.data.frame(table2)
+
+####make the table for study 2: Kavanaugh Hearings####
+table3 = matrix(NA, ncol = 12, nrow = 23)
+colnames(table3) = c("DV", "Mconservative", 
+                     "SDconservative", "Mliberal", "SDliberal", 
+                     "d", "dlow", "dhigh", "bcilowC", "bcihighC", 
+                     "bcilowL", "bcihighL")
+table3 = as.data.frame(table3)
+```
+
+```{r bootstrap-function, include = FALSE}
+####bootstrap function #####
+bootstrap_values <- function(formula, dataset, nsim){
+
+  store_mean <- rep(NA, nsim)
+  store_sd <- rep(NA, nsim)  
+  attempts <- 0
+  #loop until you have enough
+  while(attempts < nsim){
+    #create a dataset
+    d <- dataset[sample(1:nrow(dataset), 
+                        size = nrow(dataset),
+                        replace = TRUE), ]
+    #test the model
+    tryCatch({
+
+      model1 = lme(formula, 
+             data = d, 
+             method = "ML", 
+             na.action = "na.omit",
+             random = list(~1|Source),
+             control=lmeControl(opt = "nlminb")) 
+      meanvalue = summary(model1)$tTable[1]
+      sdvalue = summary(model1)$tTable[2] * sqrt(nrow(d))
+      attempts <- attempts + 1
+      store_mean[attempts] <- meanvalue
+      store_sd[attempts] <- sdvalue
+      return(store_mean, store_sd, attempts)
+    }, error = function(x){})
+  }
+
+  return(list("mean" = store_mean, "sd" = store_sd))
+}
+
 ```
@@
 
-```{r}
+```{r bootstrap-study-1, include = F}
+# Import the data
 exp1 <- import("finaldata_LIWC.csv")
+
+# Eliminate Duplicates
 exp1 <- na.omit(exp1)
 
-library(nlme)
+# Create group labels
+exp1$PartisanLean = ifelse(exp1$PartisanLean=='Conservative', 0, 1)
 
-model1 <- gls(Analytic ~ 1,
-              data = exp1,
-              method = "ML",
-              na.action = "na.omit")
+# Create IVs and DVs
+groups = c(0, 1)
+DVs = c('Analytic','Clout','Authentic','Tone','WPS','Sixltr','anger','social','family','female','male','cogproc','affiliation','achieve','power','reward','risk','focuspast','focuspresent','focusfuture','money','relig','death')
 
-model2 <- lme(Analytic ~ 1,
-              data = exp1,
-              method = "ML",
-              random = list(~1|Source), 
-              na.action = "na.omit")
-
-model3 <- lme(Analytic ~ PartisanLean,
-              data = exp1,
-              method = "ML",
-              random = list(~1|Source), 
-              na.action = "na.omit")
-anova(model1,model2,model3)
+# Loop over the DVs and create values 
+# This saves the difference between groups
+r = 1
+for(DV in DVs){
+  for(group in groups){
+    data = subset(exp1, PartisanLean==group)
+    f = as.formula(paste(DV,'~1', sep=''))
+    bs = bootstrap_values(f,data,nsim)
+    table1[r, 1] = DV
+    if(group==0){
+      table1[r, 2] = mean(bs$mean)
+      table1[r, 3] = mean(bs$sd)
+      ncon = length(na.omit(data[[DV]]))
+      table1[r, 9] = quantile(bs$mean, 0.025)
+      table1[r, 10] = quantile(bs$mean, 0.975)
+    }
+    if(group==1){
+      table1[r, 4] = mean(bs$mean)
+      table1[r, 5] = mean(bs$sd)
+      nlib = length(na.omit(data[[DV]]))
+      table1[r, 11] = quantile(bs$mean, 0.025)
+      table1[r, 12] = quantile(bs$mean, 0.975)
+    }
+  }
+  mdiff = d.ind.t(m1 = table1[r,2], m2 = table1[r,3], 
+                sd1 = table1[r,4], sd2 = table1[r,5],
+                n1 = ncon, 
+                n2 = nlib, 
+                a = .05)
+  table1[r, 6] = mdiff$d
+  table1[r, 7] = mdiff$dlow
+  table1[r, 8] = mdiff$dhigh
+  r = r + 1
+}
 ```
@@
 both effect sizes and topics analysis
+
+```{r bootstrap-study-2-goverment-shutdown}
+# Import the Data
+exp2 <- import("exp2_merged data_LIWC.csv")
+colnames(exp2)[1:5] = c('Source', 'URL', 'Text', 'Event', 'PartisanLean')
+
+#subset with Event=='gs'
+exp2 <- subset(exp2, Event == "gs")
+```
+
+```{r bootstrap-study-2-kavanaugh-hearings}
+exp2 <- import("exp2_merged data_LIWC.csv")
+colnames(exp2)[1:5] = c('Source', 'URL', 'Text', 'Event', 'PartisanLean')
+
+#subset with Event=='kav'
+
+```
 

### 2020-08-03 manuscript/Partisan Media Manuscript.Rmd
fixed effect sizes

--- 2020-07-31 manuscript/Partisan Media Manuscript.Rmd
@@
   }
-  mdiff = d.ind.t(m1 = table1[r,2], m2 = table1[r,3], 
-                sd1 = table1[r,4], sd2 = table1[r,5],
+  mdiff = d.ind.t(m1 = table1[r,2], m2 = table1[r,4], 
+                sd1 = table1[r,3], sd2 = table1[r,5],
                 n1 = ncon, 

### 2020-08-04 thesis/pilot_manuscript.tex
reran the manuscript, mostly to correct typos and post preprint

--- 2019-04-16 pilot_manuscript.tex
@@
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+%
 \documentclass[english,,man]{apa6}
@@
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
+  \usepackage{unicode-math}
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{hyperref}
-\hypersetup{unicode=true,
+\hypersetup{
             pdftitle={Moral Foundations of U.S. Political News Organizations},
-            pdfauthor={William E. Padfield~\& Erin M. Buchanan, Ph.D.},
+            pdfauthor={William E. Padfield1 \& Erin M. Buchanan, Ph.D.2},
             pdfkeywords={politics, morality, psycholinguistics},
@@
 \urlstyle{same}  % don't use monospace font for urls
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\fi
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-  \title{Moral Foundations of U.S. Political News Organizations}
-    \author{William E. Padfield\textsuperscript{1}~\& Erin M. Buchanan, Ph.D.\textsuperscript{2}}
-    \date{}
-
-\shorttitle{MORAL NEWS}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Missouri State University\\\textsuperscript{2} Harrisburg University of Science and Technology}
-\keywords{politics, morality, psycholinguistics}
-\usepackage{csquotes}
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{MORAL NEWS}
+\keywords{politics, morality, psycholinguistics}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
-
-\authornote{William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
-
-Correspondence concerning this article should be addressed to William E.
-Padfield, 901 S.
-National Ave, Springfield, MO, 65897.
-E-mail: \href{mailto:Padfield94@live.missouristate.edu}{\nolinkurl{Padfield94@live.missouristate.edu}}}
+\usepackage{csquotes}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+
+\title{Moral Foundations of U.S. Political News Organizations}
+\author{William E. Padfield\textsuperscript{1} \& Erin M. Buchanan, Ph.D.\textsuperscript{2}}
+\date{}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Missouri State University\\\textsuperscript{2} Harrisburg University of Science and Technology}
 
@@
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, the researchers gathered poltical articles from four sources.
-They were unable to reveal significant differences in moral or political endorsements, but they solidified the method to be employed in further research.
-In Experiment 2, the researchers will expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Experiment 1, the researchers gathered political articles from four sources.
+We were unable to reveal significant differences in moral or political endorsements, but we solidified the method to be employed in further research.
+In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
-Goverment Shutdown of 2018-2019.
+Government Shutdown of 2018-2019.
 Once again, no significant differences in moral or political endorsements were found.
-
 }
@@
 Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-Suhler and Churchland (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
+Suhler, Churchland, and Joseph (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
 First, the authors challenge Haidt and Graham (2007)'s claims the moral intuitions represented by MFT are innate and modular.
-Suhler and Churchland (2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
-Rather, behaviors likely result from interactions between genetics and experience (Suhler \& Churchland, 2011).
+Suhler et al.
+(2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
+Rather, behaviors likely result from interactions between genetics and experience (Suhler et al., 2011).
 According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
-Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler \& Churchland, 2011).
+Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler et al., 2011).
 However, as with innateness, there is little neurobiological evidence to support modularity.
 
-Suhler and Churchland (2011) also criticized the content and taxonomy of the five foundations.
+Suhler et al.
+(2011) also criticized the content and taxonomy of the five foundations.
 The authors criticize Haidt and Graham (2007)'s omissions of additional foundations, including \emph{industry} and \emph{modesty}, claiming these concepts are moralized in many societies worldwide.
 Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-For example, Suhler and Churchland (2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
+For example, Suhler et al.
+(2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
 Work by Graham et al.
 (2011) might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
-Finally, Suhler and Churchland (2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
-In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler \& Churchland, 2011).
+Finally, Suhler et al.
+(2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
+In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler et al., 2011).
 
 These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
-The current authors argue these criticisms are especially valid when considered alongside questions regarding the Moral Foundations Dictionary they state herein.
-However, there exists compelling evidence regarding the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
-This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary.
+Such criticisms are especially valid when considered alongside questions about the Moral Foundations Dictionary in particular.
+Nevertheless, there exists compelling evidence supporting the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
+This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary in the next section.
 
@@
 The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-The researchers created a preliminary list of words that they believed would be associated with the five foundations.
+Graham et al.
+(2009) created a preliminary list of words that they believed would be associated with the five foundations.
 Then, using the Linguistic Inquiry and Word Count (LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
+Graham et al.
+(2009) manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
 The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: \enquote{Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus} (Graham et al., 2009).
@@
 The researchers eliminated this sentence from the \emph{authority/respect} raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions (Graham et al., 2009).
+The original Moral Foundations Dictionary can be found in the Appendix.
 
@@
 (2011) claim to find a \enquote{reasonable} degree of generalizability for the MFQ across participants from many different regions in the world.
-These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler and Churchland (2011) should still be taken into account in studies involving the theory.
+These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler et al.
+(2011) should still be taken into account in studies involving the theory.
 
@@
 Lastly, \enquote{dominance} or \enquote{control} describes the extent to which a word makes one feel in or out of control (Bradley \& Lang, 1999).
-The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Mannikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
+The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Manikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
 
@@
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:exp1-source-descriptives}Experiment 1 - Descriptive Statistics by Source}
+
 \begin{tabular}{lcccccclccc}
@@
 \midrule
-NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.29 & 13.80 & 3.93\\
-New York Times & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.32 & 3.29\\
-Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.36 & 120.76 & 18.42 & 8.01\\
-Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.57 & 189.00 & 16.92 & 7.16\\
+NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.29 & 13.81 & 3.93\\
+New York Times & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.33 & 3.30\\
+Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.36 & 120.76 & 18.43 & 8.02\\
+Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.57 & 189.00 & 16.93 & 7.17\\
 \bottomrule
@@
 \end{tabular}
+
 \begin{tablenotes}[para]
@@
 \end{tablenotes}
+
 \end{threeparttable}
 \end{center}
+
 \end{table}
@@
 The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included \emph{z}-scored valence, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula.
+Statistics calculated included average \emph{z}-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
+Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula (Kincaid, Fishburne, Robert P., Richard L., \& Brad S., 1975).
 Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage (Kincaid, Fishburne, Robert P., Richard L., \& Brad S., 1975).
+The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage (Kincaid et al., 1975).
 For example, a text with a readability score of 11 should be easily read by a high school junior.
@@
 Valence appears to be slightly positive across all sources.
-The standard deviations seem to indicate little to no presence of a difference in valence.
+The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
 \emph{The New York Times} published the greatest number of articles as well as total words.
@@
 Once again the standard deviations call into question any apparent differences between sources.
-Finally, \emph{Fox News} appears to be the most readable source on average, while \emph{The New York Times} is the least readable.
+Finally, \emph{Fox News} articles had the lowest reading grade level on average, while \emph{The New York Times} had the highest.
 This result might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
-As before, the standard deviations for readability hamper one's ability to draw solid conclusions regarding differences in the sources' use of language.
+The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
+Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.
 
@@
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
-\caption{\label{tab:exp1-table}}
+
+\caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
+
 \begin{tabular}{lccccccc}
@@
 Depending on the results of Jordan et al.
-(2019)'s research, alternative forms of the Moral Foundations Dictionary may be imported instead of the original dictionary.
+(2019)'s multi-trait multi-method analysis of the MFD and the Moral Foundations Questionnaire, alternative forms of the Moral Foundations Dictionary with additional words may be imported instead of the original dictionary.
 
@@
 The researchers obtained the words' percent occurrence in the text.
-Once again, percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
+Percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
 
@@
 The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, \emph{The Huffington Post} appears to have published only 27 articles while \emph{NPR} published 757 articles on this topic.
+For example, \emph{Sean Hannity} appears to have published only 27 articles while \emph{Breitbart} published 757 articles on this topic.
 Valence was found to be slightly positive across all sources.
-\emph{Slate} produced the most total words with the most tokens on average.
-\emph{Rush Limbaugh} featured the highest number of types on average.
-\emph{The Blaze} was the most readable source on average by grade level while \emph{Fox News} was the least readable.
-The standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language.
+\emph{Fox News} produced the most total words with the most tokens on average.
+This is likely due to the fact \emph{Fox News} transcribes many of their videos and publishes them in article form.
+\emph{Politico} featured the highest number of types on average.
+\emph{Rush Limbaugh} featured the lowest readability score on average by grade level while \emph{Slate} featured the highest grade-level readability score.
+The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language, as there is likely a lot of overlap between sources' use of language.
 
@@
 Once again, there was variation in the number of articles published by each source on this topic.
-\emph{The Hugginton Post} and \emph{The Blaze} published fewer than 100 articles while \emph{Slate} published 1,013 articles.
-\emph{Slate} again featured the most total words and mean tokens.
-\emph{Rush Limbaugh} again had the most types on average.
-For this topic, \emph{Slate} was the most readable while \emph{The Huffington Post} was the least readable.
-For each statistic, the standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level.
+\emph{Sean Hannity}, \emph{Rush Limbaugh}, and \emph{The Blaze} published fewer than 100 articles while \emph{Fox News} published 1,013 articles.
+\emph{Fox News} again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
+\emph{Politico} had the most types on average.
+For this topic, \emph{Fox News} featured the lowest reading grade level while \emph{Slate} featured the highest reading grade level.
+For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
 
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:exp2-source-descriptives-kav}Kavanaugh - Descriptive Statistics by Source}
+
 \small{
+
 \begin{tabular}{lcccccclccc}
@@
 \midrule
-Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.79 & 1.91\\
+Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.80 & 1.91\\
 NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.49 & 3.62\\
@@
 The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.83 & 1.87\\
-Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 11.01 & 2.12\\
-Fox News & 0.29 & 0.11 & 646 & 1304048 & 2,018.65 & 2,709.77 & 534.47 & 404.21 & 9.70 & 1.85\\
-Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.88 & 2.37\\
+Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 11.04 & 2.17\\
+Fox News & 0.29 & 0.11 & 646 & 1304048 & 2,018.65 & 2,709.77 & 534.47 & 404.21 & 9.70 & 1.87\\
+Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.89 & 2.37\\
 Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1,552.72 & 1,258.51 & 419.00 & 225.80 & 9.42 & 9.26\\
@@
 \end{tabular}
+
 }
+
 \begin{tablenotes}[para]
@@
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:exp2-source-descriptives-gs}Government Shutdown - Descriptive Statistics by Source}
+
 \small{
+
 \begin{tabular}{lcccccclccc}
@@
 \midrule
-Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.67 & 1.83\\
+Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.69 & 1.84\\
 NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.19 & 3.15\\
 New York Times & 0.33 & 0.13 & 751 & 831184 & 1,106.77 & 506.92 & 471.80 & 174.88 & 11.28 & 2.19\\
-Politico & 0.29 & 0.10 & 222 & 349499 & 1,574.32 & 875.63 & 638.32 & 313.34 & 11.28 & 1.23\\
+Politico & 0.29 & 0.10 & 222 & 349499 & 1,574.32 & 875.63 & 638.32 & 313.34 & 11.29 & 1.24\\
 Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.86 & 2.51\\
-The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.68 & 1.85\\
-Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.71 & 2.05\\
-Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2,763.29 & 3,405.44 & 637.30 & 494.00 & 9.34 & 1.91\\
+The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.69 & 1.85\\
+Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.72 & 2.05\\
+Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2,763.29 & 3,405.44 & 637.30 & 494.00 & 9.37 & 1.94\\
 Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.41 & 4.79\\
-Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1,956.79 & 1,544.14 & 482.79 & 252.79 & 9.76 & 7.60\\
+Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1,956.79 & 1,544.14 & 482.79 & 252.79 & 9.76 & 7.61\\
 \bottomrule
@@
 To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
-Once again, the researchers used the \emph{nlme} library in \emph{R} (Pinheiro et al., 2017).
+The researchers used the \emph{nlme} library in \emph{R} (Pinheiro et al., 2017).
 Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-MLMs were constructed from datasets compiled for both topics of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a significant effect for \emph{harm/care}, but the practical effect denoted by Cohen's \emph{d} was found to be small.
-There were no other significant or practical effect of political lean for any of the other four moral foundations.
+Two separate MLMs were constructed from datasets compiled for each topic of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
+
+For the Kavanaugh topic, the multilevel model indicated the presence of a statistically significant effect for \emph{harm/care}, but the practical effect denoted by Cohen's \emph{d} was found to be small.
+There were no other significant or practical effects of political lean for any of the other four moral foundations.
 The effect for \emph{harm/care} was in the hypothesized direction with liberal sources tending to use more positively \emph{harm/care} words than conservative sources.
@@
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
-\caption{\label{tab:exp2-tablekav}}
+
+\caption{\label{tab:exp2-tablekav}Kavanaugh Results - Multilevel Model}
+
 \begin{tabular}{lccccccc}
@@
 \begin{table}[tbp]
+
 \begin{center}
 \begin{threeparttable}
-\caption{\label{tab:exp2-tablegs}}
+
+\caption{\label{tab:exp2-tablegs}Government Shutdown Results - Multilevel Model}
+
 \begin{tabular}{lccccccc}
@@
 Within the theoretical framework of Moral Foundations Theory (Haidt \& Graham, 2007), the researchers attempted to devise a method leveraging the Moral Foundations Dictionary (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
-This method was carried out in several parts.
-First, the researchers collected the articles through web scraping techniques in \emph{R} (Wickham, 2016).
-Second, the text was processed using \emph{ngram} and \emph{tm} in \emph{R} to render it in a form conducive to computerized statistical analysis (Feinerer \& Hornik, 2017).
-Third, percent occurrence of words in the Moral Foundations Dictionary (MFD) was calculated on each source in order to establish how often words indicating endorsement of the five moral foundations appeared.
-Frequency of MFD word occurrence per article was weighted for valence by multiplying the scores by mean \emph{z-scored} valence ratings from Warriner et al.
-(2013).
-Finally, the researchers constructed multi-level models using \emph{nlme} in \emph{R} (Pinheiro et al., 2017) for each foundation in which weighted percentages were predicted by each source's political lean.
+The researchers downloaded news article text from the web, processed the text, matched it with the Moral Foundations Dictionary words, and calculated average valence for words in each article.
+To analyze the data, the researchers constructed multi-level models for each foundation in which weighted percentages were predicted by each source's political lean.
 Individual source was held as a random intercept to control for correlated error.
@@
 Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
+Given part of the researchers' goal with this study was to answer a method question, they must contemplate whether or not the method or the construct of interest (political lean) are the primary contributor to null results.
+Either the method used to detect lean was insufficient for this purpose, or political lean simply does not exist, indicating the presence of a true negative in the results.
+
+The researchers believe these results represent a false negative rather than a true negative.
+That is, we believe political lean exists, but that we have been unable to detect it at a content level.
+The researchers again turn to Mitchell et al.
+(2014)\enquote{s work in this area: political partisans prefer certain news outlets over others.
+There must be something about the sources} content that facilitates partisans' repeated usage.
+Otherwise, they might not express such loyalty to any one source (or group of sources) over others.
+Given this aspect of the news economy, the researchers still believe certain news outlets in the U.S.
+contain a political slant.
 The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
@@
 The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-Additionally, multi-level models were necessary to control for the nested nature of the data where political lean encompassed several sources, which themselves encompassed numerous articles.
-
-Thus, the researchers' attention turned to the instrument used to detect differences.
-In the present study, the researchers utilized the Moral Foundations Dictionary, a metric developed from Moral Foundations Theory (Graham et al., 2009).
-Based upon the results obtained, it might be necessary to investigate alternative instruments that might better elucidate the differences of interest.
-Likewise, other theoretical perspectives may be better equipped to explain political differences in discourse.
-
-Tools such as these could be developed through the Linguistic Inquiry and Word Count program (LIWC) (Pennebaker et al., 2007).
+This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
+
+There remains an aspect of language which this method still cannot address: context.
+Owing to the presence of millions of words in the analyses presented in the current study, the researchers would be unable to check for context and correct endorsement scores accordingly.
+Graham et al.
+(2009) actually performed a process of human error-checking for context when formulating the MFD.
+While this might have helped that team fix mistakes made by the LIWC program (Pennebaker et al.
+(2007)), manual coding of this nature has the potential to introduce an unacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and belief systems.
+Additionally, the numerous ways in which context affects meaning make it difficult to interpret MFD word occurrence outside of a narrow operational definition of \enquote{endorsement.} In fact, political lean may be communicated through methods other than through the use of particular words.
+
+One method through which news organizations might appeal to political partisans is through their content strategy rather than their use of MFD words.
+The results in the current study demonstrate a similar pattern of endorsement across both conservative and liberal sources.
+Specifically, the researchers found slightly positive endorsements for all five foundations no matter the political lean of the source.
+While this may simply be an indication of insufficient MFD word occurrence in news articles, it may also demonstrate truly equal endorsement despite political lean.
+While news organizations may endorse all moral foundations, they may also adopt strategies for doing so that appeal to the political partisans consuming their product.
+As an example, a liberal source might endorse \emph{purity/sanctity} through an appeal to reduce waste or pollution (i.e.~keeping the earth \enquote{clean}).
+A conservative source, on the other hand, might endorse \emph{purity/sanctity} through an argument in favor of abstinence or religious commitment (i.e.~keeping a \enquote{clean} soul, mind, or body).
+Both publications would register as positive endorsement of \emph{purity/sanctity} despite appropriating the concept for distinct purposes.
+Through these divergent strategies, liberal and conservative news organizations might be able to appeal to their fans while exhibiting similar levels of moral endorsement.
+This could represent a further weakness of the Moral Foundations Dictionary as an instrument, as it is unable to identify these potential strategies for communicating certain points of view.
+
+Thus, the researchers' attention turned to the instrument used to detect differences: the Moral Foundations Dictionary.
+As mentioned before, MFD is a measure developed from Moral Foundations Theory (Graham et al., 2009).
+Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
+Going beyond specific instruments, other theoretical perspectives may be more equipped to explain political differences in discourse.
+Likewise, an atheoretical approach in which large quantities of data are collected from which theories are formulated may be best suited to this area of research.
+
+Alternative instruments could be developed through the Linguistic Inquiry and Word Count program (LIWC) (Pennebaker et al., 2007).
 As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context (Graham et al., 2009).
 This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
-The authors established sound psychometric properties for the tool, implying its validity in several applications.
+The original authors of the MFD established sound psychometric properties for the tool, implying its validity in several applications.
 For this reason, the researchers elected to utilize the MFD as their primary instrument.
 
-Other instruments could theoretically be developed through a LIWC analysis, including those that would be useful for analyzing political discourse.
+Instruments that improve upon the Moral Foundations Dictionary could theoretically be developed through a LIWC analysis.
 Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from Warriner et al.
@@
 The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
-However, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
+Pennebaker et al.
+(2007) has suggested the program could be applied to analyses of cognitive, social, and emotional states.
+Furthermore, there is some evidence LIWC can be used to detect deception, but the reliability of the program's accuracy in this regard (67\%) calls this assertion into question (Pennebaker, 2011).
+Despite the promising extent of LIWC's abilities, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
 Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
@@
 RFT utilizes a set of \enquote{families} describing the nature of these relationships.
-Such families include \enquote{coordinative,} establishing similarities between stimuli, and \enquote{distinctive,} implying fundamental differences between stimuli (Belisle, Paliliunas, Dixon, \& Tarbox, 2018).
+Such families include (among others) \enquote{coordinative,} establishing similarities between stimuli, \enquote{distinctive,} implying fundamental differences between stimuli, and \enquote{hierarchical,} implying a relation in terms of differing order or rank (Belisle, Paliliunas, Dixon, \& Tarbox, 2018).
 These families can be used to analyze networks of relational frames in discourse.
@@
 These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
-For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts (Belisle et al., 2018).
+For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts.
+According to Belisle et al.
+(2018), these observations imply President Obama, who employed more coordinative frames, utilized language emphasizing unity and similarity between people.
+Donald Trump, on the other hand emphasized differences and divisions between people through his use of distinctive frames (Belisle et al., 2018).
 At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
@@
 First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
-One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it was a theory designed to investigate not only moral differences but also political differences.
+In other words, RFT represents one method by which to analyze political text by analyzing occurrence of particular frames.
+However, there exists the caveat that the frame families are not known to represent patterns of political ideology at this time.
+One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it is a theory under which endorsement patterns (direction and relationship) could be predicted based upon political affiliation.
 While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
@@
 
+Finally, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
+Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
+The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
+Likewise, there are several approaches to analyzing such data, including linear models (like multi-level models) and network-style models such as latent semantic analysis (Landauer, 1998).
+Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
+
 The researchers aimed to utilize the Moral Foundations Dictionary and valence in the analysis of political news articles to determine whether or not bias was present.
@@
 MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
-In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, or through a different theoretical perspective such as Relational Frame Theory.
-Despite the results obtained in the current study, the researchers have reason to believe this line of inquiry warrants further investigation and that the correct method will one day be established.
+In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, through a different theoretical perspective such as Relational Frame Theory, or through alternative strategies involving collecting data and drawing conclusions from which future theories may be derived.
 
 Never before has news media and discourse represented such fertile ground for psychological research.
-The plethora of options and the potential for misinformation present important challenges for American democracy in the twenty-first century.
-The potential divisions in American society resulting from an abundance of choices for sources of political information, coupled with the notion that public discourse seems to offer competing conceptions of objective truth, underscores the importance of research into the content of political news.
-Democracy functions effectively on the foundation an informed and engaged electorate.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of citizens every day so that insights into the nature and consequences of political discourse can be more completely understood.
+The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
+Along with this recent increase in the amount of text information, there is now an obligation on the part of researchers to devise proper methods for analyzing that text.
+Solid methodologies must be constructed and periodically improved to keep pace with evolving technologies.
+Likewise, a strong theoretical foundation is paramount to making sense of the current and future media ecosystem.
+Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
 
@@
 (1975).
-Derivation of new readability formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy enlisted personnel.
+Derivation of New Readability Formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted Personnel.
 doi:\href{https://doi.org/10.21236/ADA006655}{10.21236/ADA006655}
@@
 
+\leavevmode\hypertarget{ref-Landauer1998}{}%
+Landauer, T.
+K.
+(1998).
+Learning and Representing Verbal Meaning.
+\emph{Current Directions in Psychological Science}, \emph{7}(5), 161--164.
+doi:\href{https://doi.org/10.1111/1467-8721.ep10836862}{10.1111/1467-8721.ep10836862}
+
 \leavevmode\hypertarget{ref-Martin2019}{}%
-Martin, M. (2019). The moral question opf Trump's border wall. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
+Martin, M. (2019). The Moral Question Of Trump's Border Wall : NPR. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
 
@@
 (2018).
-Ford-Kavanaugh Ratings: Hearing brings 20 million viewers to cable and broadcast \textbar{} Hollywood Reporter.
+Ford-Kavanaugh Ratings: Hearing Brings 20 Million viewers to cable and broadcast \textbar{} Hollywood Reporter.
 Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
@@
 
+\leavevmode\hypertarget{ref-Pennebaker2011}{}%
+Pennebaker, J.
+W.
+(2011).
+Using computer analyses to identify language style and aggressive intent: The secret life of function words.
+\emph{Dynamics of Asymmetric Conflict}, \emph{4}(2), 92--102.
+doi:\href{https://doi.org/10.1080/17467586.2011.627932}{10.1080/17467586.2011.627932}
+
 \leavevmode\hypertarget{ref-Pennebaker2007}{}%
@@
 Suhler, C.
-L., \& Churchland, P.
+L., Churchland, P., \& Joseph, C.
 (2011).
-Can innate, modular "foundations" explain morality?
+Can Innate , Modular `` Foundations '' Explain Morality ?
 Challenges for Haidt's Moral Foundations Theory.
 \emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
-doi:\href{https://doi.org/10.1162/jocn.2011.21637}{10.1162/jocn.2011.21637}
 
@@
 
+\newpage
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:appendix_mfd}Moral Foundations Dictionary}
+
+\small{
+
+\begin{tabular}{lcccc}
+\toprule
+Harm/Care & Fairness/Reciprocity & Ingroup/Loyalty & Authority/Respect & Purity/Sanctity\\
+\midrule
+abuse & balance & collect & abide & abstain\\
+attack & bias & community & authority & adultery\\
+benefit & constant & deceive & class & church\\
+care & discriminate & desert & command & clean\\
+cruel & equal & family & control & dirt\\
+crush & equate & fellow & defect & disease\\
+damage & even & foreign & defer & disgust\\
+danger & exclude & group & defy & gross\\
+defend & fair & individual & desert & innocent\\
+destroy & favor & member & duty & modest\\
+fight & honest & nation & faith & preserve\\
+guard & impartial & side & father & promiscuous\\
+harm & just & together & honor & pure\\
+hurt & justify & trait & law & right\\
+kill & prefer & unite & lead & ruin\\
+preserve & prejudice &  & legal & sacred\\
+protect & reason &  & mother & sick\\
+ruin & right &  & obey & sin\\
+safe & tolerate &  & oppose & trash\\
+shelter &  &  & order & whole\\
+spurn &  &  & permit & \\
+stomp &  &  & position & \\
+suffer &  &  & preserve & \\
+sympathy &  &  & protest & \\
+violent &  &  & refuse & \\
+war &  &  & respect & \\
+ &  &  & revere & \\
+ &  &  & serve & \\
+ &  &  & tradition & \\
+ &  &  & trait & \\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Original Moral Foundations Dictionary from Graham et al. (2009)}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \end{document}

### 2020-08-05 manuscript/Partisan Media Manuscript.Rmd

--- 2020-08-03 manuscript/Partisan Media Manuscript.Rmd
@@
 #setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
-nsim = 100
+nsim = 10
 
@@
 
-# Eliminate Duplicates
+# Eliminate Missing Data
 exp1 <- na.omit(exp1)
@@
   for(group in groups){
-    data = subset(exp1, PartisanLean==group)
+    data = subset(exp1, PartisanLean==group) #data name
     f = as.formula(paste(DV,'~1', sep=''))
@@
     if(group==0){
-      table1[r, 2] = mean(bs$mean)
+      table1[r, 2] = mean(bs$mean) #table name all the way down 
       table1[r, 3] = mean(bs$sd)
@@
 
+- put notes here, I fixed the code
+
 # Experiment 2
@@
 
+# Eliminate Missing Data
+
 #subset with Event=='gs'
-exp2 <- subset(exp2, Event == "gs")
+exp2_gs <- subset(exp2, Event == "gs")
+
 ```
@@
 ```{r bootstrap-study-2-kavanaugh-hearings}
-exp2 <- import("exp2_merged data_LIWC.csv")
-colnames(exp2)[1:5] = c('Source', 'URL', 'Text', 'Event', 'PartisanLean')
 
 #subset with Event=='kav'
-
+exp2_kav ... 
 ```

### 2021-04-14 manuscript/Partisan Media Manuscript.Rmd
kj manuscript suggestions

@@
 
+TO-DO LIST:
+1. Introduction/Lit Review for new direction using LIWC instead of MFD (KJ)
+2. Write Methods by combine data from Will's thesis and bootstrap method from LangofWar (EB)
+
 ```{r setup, include = FALSE}
@@
 
-#setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
-nsim = 10
+setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
+nsim = 100
 
@@
 # Eliminate Missing Data
+exp2 <- na.omit(exp2)
 
@@
 exp2_gs <- subset(exp2, Event == "gs")
+
+# Create group labels
+exp2_gs$PartisanLean = ifelse(exp2_gs$PartisanLean=='Conservative', 0, 1)
+
+# Create IVs and DVs
+groups = c(0, 1)
+DVs = c('Analytic','Clout','Authentic','Tone','WPS','Sixltr','anger','social','family','female','male','cogproc','affiliation','achieve','power','reward','risk','focuspast','focuspresent','focusfuture','money','relig','death')
+
+# Loop over the DVs and create values 
+# This saves the difference between groups
+r = 1
+for(DV in DVs){
+  for(group in groups){
+    data = subset(exp2_gs, PartisanLean==group) #data name
+    f = as.formula(paste(DV,'~1', sep=''))
+    bs = bootstrap_values(f,data,nsim)
+    table2[r, 1] = DV
+    if(group==0){
+      table2[r, 2] = mean(bs$mean) #table name all the way down 
+      table2[r, 3] = mean(bs$sd)
+      ncon = length(na.omit(data[[DV]]))
+      table2[r, 9] = quantile(bs$mean, 0.025)
+      table2[r, 10] = quantile(bs$mean, 0.975)
+    }
+    if(group==1){
+      table2[r, 4] = mean(bs$mean)
+      table2[r, 5] = mean(bs$sd)
+      nlib = length(na.omit(data[[DV]]))
+      table2[r, 11] = quantile(bs$mean, 0.025)
+      table2[r, 12] = quantile(bs$mean, 0.975)
+    }
+  }
+  mdiff = d.ind.t(m1 = table2[r,2], m2 = table2[r,4], 
+                sd1 = table2[r,3], sd2 = table2[r,5],
+                n1 = ncon, 
+                n2 = nlib, 
+                a = .05)
+  table2[r, 6] = mdiff$d
+  table2[r, 7] = mdiff$dlow
+  table2[r, 8] = mdiff$dhigh
+  r = r + 1
+}
 
@@
 #subset with Event=='kav'
-exp2_kav ... 
+exp2_kav  <- subset(exp2, Event == "kav")
+
+# Create group labels
+exp2_kav$PartisanLean = ifelse(exp2_kav$PartisanLean=='Conservative', 0, 1)
+
+# Create IVs and DVs
+groups = c(0, 1)
+DVs = c('Analytic','Clout','Authentic','Tone','WPS','Sixltr','anger','social','family','female','male','cogproc','affiliation','achieve','power','reward','risk','focuspast','focuspresent','focusfuture','money','relig','death')
+
+# Loop over the DVs and create values 
+# This saves the difference between groups
+r = 1
+for(DV in DVs){
+  for(group in groups){
+    data = subset(exp2_kav, PartisanLean==group) #data name
+    f = as.formula(paste(DV,'~1', sep=''))
+    bs = bootstrap_values(f,data,nsim)
+    table3[r, 1] = DV
+    if(group==0){
+      table3[r, 2] = mean(bs$mean) #table name all the way down 
+      table3[r, 3] = mean(bs$sd)
+      ncon = length(na.omit(data[[DV]]))
+      table3[r, 9] = quantile(bs$mean, 0.025)
+      table3[r, 10] = quantile(bs$mean, 0.975)
+    }
+    if(group==1){
+      table3[r, 4] = mean(bs$mean)
+      table3[r, 5] = mean(bs$sd)
+      nlib = length(na.omit(data[[DV]]))
+      table3[r, 11] = quantile(bs$mean, 0.025)
+      table3[r, 12] = quantile(bs$mean, 0.975)
+    }
+  }
+  mdiff = d.ind.t(m1 = table3[r,2], m2 = table3[r,4], 
+                sd1 = table3[r,3], sd2 = table3[r,5],
+                n1 = ncon, 
+                n2 = nlib, 
+                a = .05)
+  table3[r, 6] = mdiff$d
+  table3[r, 7] = mdiff$dlow
+  table3[r, 8] = mdiff$dhigh
+  r = r + 1
+}
 ```

### 2021-04-14 datacleaning_kj.R

@@ -1,0 +1,35 @@
+setwd("C:/Users/kayla/Documents/GitHub/Will-Pilot/exp1_data")
+
+#Merge Exp2 text files and code partisan lean
+library(stringr)
+file.names = dir("C:/Users/kayla/Documents/GitHub/Will-Pilot/exp2_data/", pattern = '.csv')
+first = TRUE
+for(i in 1:length(file.names))
+{
+  df = read.csv(file.names[i], stringsAsFactors = FALSE)
+  colnames(df)[1] = "Source"
+  df$Text = gsub('\n', ' ', df$Text)
+  df$Text = gsub('\t', ' ', df$Text)
+  event = str_extract(file.names[i], '_[a-z]+')
+  event = str_replace(event, "_", '')
+  df$Event = rep(event, nrow(df))
+  if(df$Source=='BLAZE'|df$Source=='BREITBART'|df$Source=='FOX'|df$Source=='HANNITY'|df$Source=='RUSH')
+  {df$PartisanLean = rep('Conservative', nrow(df))}
+  if(df$Source=='HUFFPO'|df$Source=='NPR'|df$Source=='NY Times'|df$Source=='POLITICO'|df$Source=='SLATE')
+  {df$PartisanLean = rep('Liberal', nrow(df))}
+  if(first==TRUE)
+  {
+    df_full = df
+    first = FALSE
+  }
+  df_full = rbind(df_full, df)
+}
+
+write.csv(df_full, "exp2_merged data.csv", row.names = FALSE)
+
+#Code Partisan Lean for Exp1
+dfO = read.csv("finaldata.csv", stringsAsFactors = FALSE)
+df = read.csv("finaldata_LIWC.csv", stringsAsFactors = FALSE)
+colnames(df)[1:6] = colnames(dfO)[1:6]
+df$PartisanLean = ifelse(df$Source=="Breitbart"|df$Source=="Fox News", "Conservative", "Liberal")
+write.csv(df, 'finaldata_LIWC.csv', row.names = FALSE)

### 2021-04-29 manuscript/Partisan Media Manuscript.Rmd
manuscript updates coming your way

@@
 author: 
-  - name          : "First Author"
+  - name          : "Kayla N. Jordan"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
+    address       : "326 Market St., Harrisburg, PA, 17101"
+    email         : "kjordan@harrisburgu.edu"
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
       - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
+      - Formal analysis
+      - Methodology
+      - Software
+  - name          : "William E. Padfield"
+    affiliation   : "2"
     role:
+      - Writing - Original Draft Preparation
+      - Data curation
+      - Formal analysis
+      - Methodology
+      - Investigation
+  - name          : "Erin M. Buchanan"
+    affiliation   : "1"
+    role:
+      - Writing - Original Draft Preparation
       - Writing - Review & Editing 
+      - Data curation
+      - Formal analysis
+      - Methodology
+      - Software
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Harrisburg University of Science and Technology"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Missouri State University"
 
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  Kayla N.
+Jordan is an Assistant Professor of Social Analytics at Harrisburg University of Science and Technology, and Erin M.
+Buchanan is a Professor of Cognitive Analytics.
+William E.
+Padfield completed his Masters Degree at Missouri State University, and this study is a follow up analysis to his previous contribution.
 
@@
 
-setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
 nsim = 100
@@
 
-move the data collection from the original thesis
+# Method
+
+-----EB WILL NEED TO REWORK PART OF THIS AFTER I SEE THE INTRODUCTION-----
+
+For Experiment 1, the researchers approached the study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
+The researchers hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
+Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
+Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
+
+## Sources
+
+Political articles were collected from the websites of four notable U.S.
+news sources, a process known as web scraping.
+The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
+They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
+The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
+In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean.
+In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean.
+@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
+
+Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
+For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
+All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
+
+Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
+While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
+Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
+Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
+We later ran a process in order to exclude any duplicate articles.
+*Fox News* presented a similar issue.
+We discovered *Fox News* utilized six URLs in addition to the regular politics page.
+These URLs led to pages containing content pertaining the U.S.
+Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
+Once again, duplicates were subsequently eliminated from any analyses.
+
+## Materials
+
+Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016].
+Using this dataset, we identified word count and average word count per source.
+This process was completed once daily starting in February 2018 until March 2018.
+Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening.
+Data collection was terminated once 250,000 words per source was collected in April 2018.
+
+```{r scraping, eval=FALSE, include=FALSE}
+
+library(rvest)
+####NY Times####
+#Specifying the url for desired website to be scrapped
+url <- 'https://www.nytimes.com/section/politics'
+
+#Reading the HTML code from the website - headlines
+webpage <- read_html(url)
+headline_data = html_nodes(webpage,'.story-link a, .story-body a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep("http", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.story-content')
+
+  ##pull the text
+  text_data = html_text(headline_data)
+
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+    } ##end for loop
+
+####NPR original front page####
+url2 = 'https://www.npr.org/sections/politics/'
+webpage2 = read_html(url2)
+headline_data2 = html_nodes(webpage2,'.title a')
+
+#URLs
+attr_data2 = html_attrs(headline_data2) 
+attr_data2
+
+urlslist2 = unlist(attr_data2)
+urlslist2 = urlslist2[grep("http", urlslist2)]
+urlslist2
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 1:length(urlslist2)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist2[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'#storytext > p')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  NPRDF$Source[i] = "NPR"
+  NPRDF$Url[i] = urlslist2[i]
+  NPRDF$Text[i] = paste(text_data2, collapse = "")
+} ##end for loop
+
+####Fox News####
+url3 = 'http://www.foxnews.com/politics.html'
+url3.1 = 'http://www.foxnews.com/category/politics/executive.html'
+url3.2 = 'http://www.foxnews.com/category/politics/senate.htm.html'
+url3.3 = 'http://www.foxnews.com/category/politics/house-representatives.html'
+url3.4 = 'http://www.foxnews.com/category/politics/judiciary.html'
+url3.5 = 'http://www.foxnews.com/category/politics/foreign-policy.html'
+url3.6 = 'http://www.foxnews.com/category/politics/elections.html'
+webpage3 = read_html(url3)
+webpage3.1 = read_html(url3.1)
+webpage3.2 = read_html(url3.2)
+webpage3.3 = read_html(url3.3)
+webpage3.4 = read_html(url3.4)
+webpage3.5 = read_html(url3.5)
+webpage3.6 = read_html(url3.6)
+
+headline_data3 = html_nodes(webpage3, '.story- a , .article-list .title a')
+headline_data3.1 = html_nodes(webpage3.1, '.story- a , .article-list .title a')
+headline_data3.2 = html_nodes(webpage3.2, '.story- a , .article-list .title a')
+headline_data3.3 = html_nodes(webpage3.3, '.story- a , .article-list .title a')
+headline_data3.4 = html_nodes(webpage3.4, '.story- a , .article-list .title a')
+headline_data3.5 = html_nodes(webpage3.5, '.story- a , .article-list .title a')
+headline_data3.6 = html_nodes(webpage3.6, '.story- a , .article-list .title a')
+
+#headline_data = html_text(headline_data)
+head(headline_data3)
+
+attr_data3 = html_attrs(headline_data3) 
+attr_data3.1 = html_attrs(headline_data3.1) 
+attr_data3.2 = html_attrs(headline_data3.2) 
+attr_data3.3 = html_attrs(headline_data3.3) 
+attr_data3.4 = html_attrs(headline_data3.4) 
+attr_data3.5 = html_attrs(headline_data3.5) 
+attr_data3.6 = html_attrs(headline_data3.6)
+
+attr_data3
+
+urlslist3 = c(unlist(attr_data3), unlist(attr_data3.1), 
+              unlist(attr_data3.2), unlist(attr_data3.3), 
+              unlist(attr_data3.4), unlist(attr_data3.5, attr_data3.6))
+##find all that are href
+urlslist3 = urlslist3[grep("http|.html", urlslist3)]
+##fix the ones without the leading foxnews.com
+urlslist3F = paste("http://www.foxnews.com", urlslist3[grep("^http", urlslist3, invert = T)], sep = "")
+urlslist3N = urlslist3[grep("^http", urlslist3)]
+urlslist3 = c(urlslist3N, urlslist3F)
+urlslist3 = unique(urlslist3)
+urlslist3
+
+##start a data frame
+FoxDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(FoxDF) = c("Source", "Url", "Text")
+FoxDF = as.data.frame(FoxDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage3 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data3 = html_nodes(webpage3,'p+ p , .fn-video+ p , .twitter+ p , .speakable')
+
+  ##pull the text
+  text_data3 = html_text(headline_data3)
+
+  ##save the data
+  FoxDF$Source[i] = "Fox News"
+  FoxDF$Url[i] = urlslist3[i]
+  FoxDF$Text[i] = paste(text_data3, collapse = "")
+} ##end for loop
+
+####Breitbart####
+url4 = 'http://www.breitbart.com/big-government/'
+webpage4 = read_html(url4)
+headline_data4 = html_nodes(webpage4, '.title a , #grid-block-0 span , #BBTrendUL a , #disqus-popularUL a , font')
+#headline_data4 = html_text(headline_data4)
+head(headline_data4)
+
+attr_data4 = html_attrs(headline_data4) 
+attr_data4
+
+urlslist4 = unlist(attr_data4)
+##find all that are href
+urlslist4 = urlslist4[grep("http|/big-government", urlslist4)]
+##fix the ones without the leading bb
+urlslist4F = paste("http://www.breitbart.com", urlslist4[grep("^http", urlslist4, invert = T)], sep = "")
+urlslist4N = urlslist4[grep("^http", urlslist4)]
+urlslist4 = c(urlslist4N, urlslist4F)
+urlslist4 = unique(urlslist4)
+urlslist4
+
+##start a data frame
+BreitbartDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
+colnames(BreitbartDF) = c("Source", "Url", "Text")
+BreitbartDF = as.data.frame(BreitbartDF)
+
+##for loops
+for (i in 1:length(urlslist4)){
+
+  ##read in the URL
+  webpage4 <- read_html(urlslist4[i])
+
+  ##pull the specific nodes
+  headline_data4 = html_nodes(webpage4,'.entry-content p , h2')
+
+  ##pull the text
+  text_data4 = html_text(headline_data4)
+
+  ##save the data
+  BreitbartDF$Source[i] = "Breitbart"
+  BreitbartDF$Url[i] = urlslist4[i]
+  BreitbartDF$Text[i] = paste(text_data4, collapse = "")
+} ##end for loop
+
+####NPR Archive####
+url5 = 'https://www.npr.org/sections/politics/archive'
+webpage5 = read_html(url5)
+headline_data5 = html_nodes(webpage5,'.title a')
+#headline_data = html_text(headline_data)
+#head(headline_data)
+
+#URLs
+attr_data5 = html_attrs(headline_data5) 
+attr_data5
+
+urlslist5 = unlist(attr_data5)
+urlslist5 = urlslist5[grep("http", urlslist5)]
+urlslist5
+
+##start a data frame
+NPRArchiveDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
+colnames(NPRArchiveDF) = c("Source", "Url", "Text")
+NPRArchiveDF = as.data.frame(NPRArchiveDF)
+
+##for loops
+for (i in 1:length(urlslist5)){
+
+  ##read in the URL
+  webpage5 <- read_html(urlslist5[i])
+
+  ##pull the specific nodes
+  headline_data5 = html_nodes(webpage5,'#storytext > p')
+
+  ##pull the text
+  text_data5 = html_text(headline_data5)
+
+  ##save the data
+  NPRArchiveDF$Source[i] = "NPR"
+  NPRArchiveDF$Url[i] = urlslist5[i]
+  NPRArchiveDF$Text[i] = paste(text_data5, collapse = "")
+} ##end for loop
+
+####put together####
+
+##import the overalldata 
+overalldata = read.csv("../exp1_data/overalldata.csv")
+
+##combine with new data (add the other DF names in here...)
+newdata = rbind(overalldata, NYtimesDF, NPRDF, FoxDF, BreitbartDF, NPRArchiveDF)
+
+##make the newdata unique in case of overlap across days
+newdata = unique(newdata)
+
+##write it back out
+write.csv(newdata, "overalldata.csv", row.names = F)
+```
+
+## Data analysis
+
+Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017].
+This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
+At this point, duplicate articles were discarded.
+
+```{r data-cleanup, eval=FALSE, include=FALSE}
+##pull in the data
+master = read.csv("../exp1_data/overalldata.csv", stringsAsFactors = F)
+
+##get rid of the blank stuff
+library(ngram)
+
+for (i in 1:nrow(master)) {
+  master$wordcount[i] = wordcount(master$Text[i])
+}
+
+nozero = subset(master, wordcount > 0)
+tapply(nozero$wordcount, nozero$Source, mean)
+tapply(nozero$wordcount, nozero$Source, sum)
+
+##take out the disqus ones
+nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
+
+##figure out the duplicates
+nodis$URLS = duplicated(nodis$Url)
+
+##all data
+final = subset(nodis, URLS == FALSE)
+
+tapply(final$wordcount, final$Source, mean)
+tapply(final$wordcount, final$Source, sum)
+
+write.csv(final, "finaldata.csv")
+```
+
+```{r kayla-cleanup, eval = F, echo = F}
+#Code Partisan Lean for Exp1
+dfO = read.csv("finaldata.csv", stringsAsFactors = FALSE)
+df = read.csv("finaldata_LIWC.csv", stringsAsFactors = FALSE)
+colnames(df)[1:6] = colnames(dfO)[1:6]
+df$PartisanLean = ifelse(df$Source=="Breitbart"|df$Source=="Fox News", "Conservative", "Liberal")
+write.csv(df, 'finaldata_LIWC.csv', row.names = FALSE)
+```
+
+----KJ ENTER A PARAGRAPH ABOUT THE LIWC HERE?-----
+
+----NOTE this was rewritten since we published it before, Will's thesis sections were not because it's only a preprint----
+
+This dataset includes multiple instances of each news source across time, thus, repeated measures data within the source.
+Therefore, we analyzed this data with multilevel modeling to control for the correlated error due to source category.
+The *nlme* package was used to calculate the mean and standard deviation of each variable by partisan lean of the source [@Pinheiro2017].
+The source was included as a random intercept factor [@Gelman2006] using the intercept to predict the dependent variable category from the LIWC.
+The standard error of each estimate was multiplied by the square root of sample size (*n*) to create the standard deviation.
+We used bootstrapping to complete this analysis 1000 times, and the normal confidence interval from the *boot* library was calculated [CITE BOOT HERE] separately for each partisan lean.
+The bootstrapped mean and standard deviation are shown in FIGURE ??, and $d_s$ was calculated using the *MOTE* library using pooled standard deviation as the denominator [@Lakens2013; @Buchanan2017].
+$d_s$ represents the standardized mean difference between Conservative and Liberal leaning sources.
+We examined the bootstrapped confidence interval of $d_s$, rather than *p*-values, for determining differences between groups.
+Confidence intervals that included zero, suggested no support for differences in the LIWC category between partisan lean, while confidence intervals that did not include zero indicate support for differences in the dependent variable.
 
@@
 # Experiment 2
+
+-----QUESTION HERE IF WE WANT THIS HERE OR AT THE FRONT, WILL NEED TO TEXT UPDATE----
+
+## Kavanaugh Supreme Court Hearing
+
+In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
+Kavanaugh was previously on the U.S.
+Court of Appeals for the District of Columbia.
+The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@USGovernment2018b].
+Following allegations of sexual assault by high school classmate Dr.
+Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
+
+On September 27, the committee questioned Dr.
+Ford before commencing a second round of questioning for Judge Kavanaugh [@USGovernment2018].
+During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
+According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018].
+This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
+On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
+Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
+The investigation concluded with no significant findings.
+The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@USGovernment2018a].
+
+The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals.
+The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns.
+On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
+Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
+Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
+Concerns around abortion might be related either to *harm/care* or *purity/sanctity*.
+On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
+Likewise, arguments could be made that relate concerns regarding sexual violence to *harm/care* or *fairness/reciprocity*.
+Additionally, the moral duty of the Senate as the upper chamber in the U.S.
+legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
+
+## U.S. Government Shutdown of 2018-2019
+
+The U.S.
+Federal Government partially shut down on December 22, 2018.
+The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019].
+The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
+President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019].
+Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].
+
+The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
+President Trump signed the bill, ending the longest government shutdown in U.S.
+history [@Axelrod2019].
+Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole [@Kheel2019].
+Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed [@Peoples2019].
+While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
+
+As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
+Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
+As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns [@Martin2019].
+Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
+Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people [@Martin2019].
+This example potentially ties into the five moral foundations.
+Theological concerns regarding the border wall might invoke *authority/respect* as well as *purity/sanctity*.
+In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
+could also elicit moral concerns related to *ingroup/outgroup*.
+
+Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
+In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
+
+# Method
+
+In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
+The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
+The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
+Once again, no human participants were needed for this study, so no Institutional Review Board approval was necessary.
+
+```{r NYTimes_kav, eval = F, include = F}
+
+library(rvest)
+library(RSelenium)
+
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#page for NYTIMES
+url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
+
+#navigate to it
+remDr$navigate(url)
+
+#click the button 
+#don't change class name
+#right click --> inspect element 
+webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
+
+#with 752 results at 10 per page we need
+#752 - 10 original = 742 / 10 per click = 75 clicks
+
+for (i in 1:75) { #change this to 75 later
+  webElem$clickElement()
+  Sys.sleep(runif(1, 1, 5))
+}
+
+webpage <-remDr$getPageSource()
+
+#Reading the HTML code from the website - headlines
+webpage2 <- read_html(unlist(webpage))
+
+headline_data = html_nodes(webpage2,'a')
+
+attr_data = html_attrs(headline_data) 
+attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep(".html", urlslist)]
+urlslist = urlslist[grep("/2018", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+#paste NY on front
+urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
+
+  ##pull the text
+  text_data = html_text(headline_data)
+
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+  Sys.sleep(runif(1, 1, 10)) #don't make them angry
+} ##end for loop
+
+write.csv(NYtimesDF, "NYtimes_kav.csv", row.names = F)
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+```
+
+```{r NYTimes_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#page for NYTIMES
+url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'
+
+#navigate to it
+remDr$navigate(url)
+
+#click the button 
+#don't change class name
+#right click --> inspect element 
+webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
+
+#with 803 results at 10 per page we need
+#803 - 10 original / 10 per click is 80 clicks
+
+for (i in 1:80) {
+  webElem$clickElement()
+  Sys.sleep(runif(1, 1, 5))
+}
+
+webpage <-remDr$getPageSource()
+
+#Reading the HTML code from the website - headlines
+webpage2 <- read_html(unlist(webpage))
+
+headline_data = html_nodes(webpage2,'a')
+
+attr_data = html_attrs(headline_data) 
+#attr_data
+
+urlslist = unlist(attr_data)
+urlslist = urlslist[grep(".html", urlslist)]
+urlslist = urlslist[grep("/201", urlslist)]
+urlslist = unique(urlslist)
+urlslist
+
+#paste NY on front
+urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
+
+##start a data frame
+NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(NYtimesDF) = c("Source", "Url", "Text")
+NYtimesDF = as.data.frame(NYtimesDF)
+
+##for loops
+for (i in 1:length(urlslist)){
+
+  ##read in the URL
+  webpage <- read_html(urlslist[i])
+
+  ##pull the specific nodes
+  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
+
+  ##pull the text
+  text_data = html_text(headline_data)
+
+  ##save the data
+  NYtimesDF$Source[i] = "NY Times"
+  NYtimesDF$Url[i] = urlslist[i]
+  NYtimesDF$Text[i] = paste(text_data, collapse = "")
+  Sys.sleep(runif(1, 1, 10)) #don't make them angry
+} ##end for loop
+
+write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
+beep(sound = 5)
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+```
+
+````{r NPR_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+##loop through the page number at the end until done with ~1000 / 20 = 50
+for (i in 1:50) { ##change this to 50
+
+  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
+
+  #navigate to it
+  remDr$navigate(url)
+
+  #scroll on the page
+  webscroll <- remDr$findElement("css", "body")
+  webscroll$sendKeysToElement(list(key = "end"))
+
+  #get the links
+  webElems <- remDr$findElements(using = "css", "[href]")
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+
+} #close the loop
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+urlslist = unlist(urlslist_final)
+#find all the ones with /2018/
+urlslist2 = urlslist[grep("/2018", urlslist)]
+urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
+urlslist2 = unique(urlslist2)
+temp = strsplit(urlslist2, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#deal with the ones with extra parts
+temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
+
+#pull only the right dates
+rows = rownames(temp2[ temp2$`4` == 2018 & #must be 2018 and 
+                         (temp2$`5` == "09" & as.numeric(temp2$`6`)>=13 | 
+                            temp2$`5` == "10" & as.numeric(temp2$`6`)<=11), #Must be 9 or 10 
+                ])
+
+urlslist3 = urlslist2[as.numeric(rows)]
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'#storytext > p')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  NPRDF$Source[i] = "NPR"
+  NPRDF$Url[i] = urlslist3[i]
+  NPRDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
+} ##end for loop
+
+beep(sound = 3)
+
+write.csv(NPRDF, "NPR_kav.csv", row.names = F)
+
+```
+
+```{r NPR_shut, eval = F, include = F}
+
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+##loop through the page number at the end until done with ~3316 / 20 = 166
+for (i in 1:166) {
+
+  url = paste0('https://www.npr.org/search?query=government%20shutodwn&page=', i)
+
+  #navigate to it
+  remDr$navigate(url)
+
+  #scroll on the page
+  webscroll <- remDr$findElement("css", "body")
+  webscroll$sendKeysToElement(list(key = "end"))
+
+  #get the links
+  webElems <- remDr$findElements(using = "css", "[href]")
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+
+} #close the loop
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+urlslist = unlist(urlslist_final)
+#find all the ones with /2018/
+urlslist2 = urlslist[grep("/201", urlslist)]
+urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
+urlslist2 = unique(urlslist2)
+temp = strsplit(urlslist2, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#deal with the ones with extra parts
+temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
+
+#pull only the right dates
+rows = rownames(temp2[ (temp2$`4` == 2018 | temp2$`4` == 2019) & #must be 2018/19 and  
+                         (
+                           (temp2$`5` == "12" & as.numeric(temp2$`6`)>8 & temp2$`4` == 2018) | #after dec 12
+                            (temp2$`5`== "01" & temp2$`4` == 2019) | #all of jan
+                            (temp2$`5` == "02" & as.numeric(temp2$`6`)<8 & temp2$`4` == 2019)
+                           ), #before feb 8
+                ])
+
+urlslist3 = urlslist2[as.numeric(rows)]
+
+##start a data frame
+NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(NPRDF) = c("Source", "Url", "Text")
+NPRDF = as.data.frame(NPRDF)
+
+##for loops
+for (i in 315:length(urlslist3)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'#storytext > p')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  NPRDF$Source[i] = "NPR"
+  NPRDF$Url[i] = urlslist3[i]
+  NPRDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
+} ##end for loop
+
+beep(sound = 3)
+
+write.csv(NPRDF, "NPR_gs.csv", row.names = F)
+```
+
+````{r Slate_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://slate.com/search?q=kavanaugh&via=homepage_nav_search"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#appear to be 10 pages
+for (i in 1:10){
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
+
+  #don't go too fast for the page to load
+  Sys.sleep(runif(1, 1, 5))
+
+  #click on the page number
+  webClick[[i]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones with /2018/
+urlslist2 = urlslist[grep("/2018/10|/2018/09", urlslist)]
+urlslist2 = unique(urlslist2)
+
+#71 articles seems suspiciously low, so also scraped this page
+#https://slate.com/tag/brett-kavanaugh/
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#337 / 20 = 17 pages
+for (i in 1:17){
+
+  url = paste0("https://slate.com/tag/brett-kavanaugh/", i)
+
+  remDr$navigate(url)
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones with /2018/
+urlslist2.1 = urlslist[grep("/2018/10|/2018/09", urlslist)]
+urlslist2.1 = unique(urlslist2.1)
+
+urlslist3 = unique(c(urlslist2, urlslist2.1))
+
+##start a data frame
+SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(SLATEDF) = c("Source", "Url", "Text")
+SLATEDF = as.data.frame(SLATEDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  SLATEDF$Source[i] = "SLATE"
+  SLATEDF$Url[i] = urlslist3[i]
+  SLATEDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
+} ##end for loop
+
+beep(sound = 3)
+
+write.csv(SLATEDF, "SLATE_kav.csv", row.names = F)
+
+```
+
+```{r SLATE_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://slate.com/search?q=government+shutdown"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#appear to be 10 pages
+for (i in 1:10){
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
+
+  #don't go too fast for the page to load
+  Sys.sleep(runif(1, 1, 5))
+
+  #click on the page number
+  webClick[[i]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones from 12 2018 to 02 2019
+urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
+urlslist2 = unique(urlslist2)
+
+#60 something articles seems suspiciously low, so also scraped this page
+#https://slate.com/tag/governtment-shutdown
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#354 / 20 = 18 pages
+for (i in 1:18){
+
+  url = paste0("https://slate.com/tag/government-shutdown/", i)
+
+  remDr$navigate(url)
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #don't go too fast
+  Sys.sleep(runif(1, 1, 5))
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+
+#find all the ones with /2018/
+urlslist2.1 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
+urlslist2.1 = unique(urlslist2.1)
+
+urlslist3 = unique(c(urlslist2, urlslist2.1))
+
+##start a data frame
+SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(SLATEDF) = c("Source", "Url", "Text")
+SLATEDF = as.data.frame(SLATEDF)
+
+##for loops
+for (i in 1:length(urlslist3)){
+
+  ##read in the URL
+  webpage2 <- read_html(urlslist3[i])
+
+  ##pull the specific nodes
+  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
+
+  ##pull the text
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  SLATEDF$Source[i] = "SLATE"
+  SLATEDF$Url[i] = urlslist3[i]
+  SLATEDF$Text[i] = paste(text_data2, collapse = "")
+  Sys.sleep(runif(1, 1, 10))
+} ##end for loop
+
+#beep(sound = 3)
+
+write.csv(SLATEDF, "SLATE_gs.csv", row.names = F)
+```
+
+````{r HuffPo_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#943 results with 10 per page 94 clicks
+for (i in 1:94){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "class name", "fz-20")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "class name", "next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 3)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+
+##start a data frame
+HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HUFFPODF) = c("Source", "Url", "Text")
+HUFFPODF = as.data.frame(HUFFPODF)
+int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
+
+for (i in 937:length(urlslist)){
+
+  #convert the url
+  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
+  temp = gsub("%3a", ":", temp)
+  temp = gsub("%2f", "/", temp)
+
+  webpage = read_html(temp)
+  #figure out the date
+  headline_data = html_nodes(webpage, '.timestamp__date--published')
+  text_data = html_text(headline_data)
+  time = unlist(strsplit(text_data, split = "\n| "))[2]
+  time = as.Date(time, format = "%m/%d/%Y")
+
+  if (time %within% int) {
+    ##pull out the text
+    headline_data2 = html_nodes(webpage,'p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    HUFFPODF$Source[i] = "HUFFPO"
+    HUFFPODF$Url[i] = urlslist[i]
+    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 3)
+
+write.csv(HUFFPODF, "HUFFPO_kav.csv", row.names = F)
+```
+
+```{r HuffPo_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=government+shutdown&fr=huffpost_desktop"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#942 results with 10 per page 94 clicks
+for (i in 1:94){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "class name", "fz-20")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the button to click on 
+  webClick <- remDr$findElements(using = "class name", "next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 2)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+
+##start a data frame
+HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HUFFPODF) = c("Source", "Url", "Text")
+HUFFPODF = as.data.frame(HUFFPODF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
+
+for (i in 1:length(urlslist)){
+
+  #convert the url
+  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
+  temp = gsub("%3a", ":", temp)
+  temp = gsub("%2f", "/", temp)
+
+  webpage = read_html(temp)
+  #figure out the date
+  headline_data = html_nodes(webpage, '.timestamp__date--published')
+  text_data = html_text(headline_data)
+  time = unlist(strsplit(text_data, split = "\n| "))[2]
+  time = as.Date(time, format = "%m/%d/%Y")
+
+  if (time %within% int) {
+    ##pull out the text
+    headline_data2 = html_nodes(webpage,'p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    HUFFPODF$Source[i] = "HUFFPO"
+    HUFFPODF$Url[i] = urlslist[i]
+    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 2)
+
+write.csv(HUFFPODF, "HUFFPO_gs.csv", row.names = F)
+```
+
+````{r Politico_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=kavanaugh&pv=&c=&r=&start=09%2F13%2F2018&start_submit=09%2F13%2F2018&end=10%2F11%2F2018&end_submit=10%2F11%2F2018"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#749 with 20 per page with 37 clicks
+
+for (i in 1:37){
+
+  if (i > 1){
+    #navigate to the next page
+    url = paste0("https://www.politico.com/search/", i, 
+                 "?s=newest&q=kavanaugh&adv=true&start=09/13/2018&end=10/11/2018")
+    remDr$navigate(url)
+  }
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 7)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[grep("/2018/", urlslist)]
+urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
+
+##start a data frame
+POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(POLITICODF) = c("Source", "Url", "Text")
+POLITICODF = as.data.frame(POLITICODF)
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  POLITICODF$Source[i] = "POLITICO"
+  POLITICODF$Url[i] = urlslist[i]
+  POLITICODF$Text[i] = paste(text_data2, collapse = "")
+
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+beep(sound = 7)
+
+write.csv(POLITICODF, "POLITICO_kav.csv", row.names = F)
+#easiest one yet
+```
+
+```{r Politico_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=government+shutdown&pv=&c=&r=&start=12%2F08%2F2018&start_submit=12%2F08%2F2018&end=02%2F08%2F2019&end_submit=02%2F08%2F2019"
+
+remDr$navigate(url)
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#1329 with 20 per page with 66 clicks
+
+for (i in 1:66){
+
+  if (i > 1){
+    #navigate to the next page
+    url = paste0("https://www.politico.com/search/", i, 
+                 "?s=newest&q=government shutdown&adv=true&start=12/08/2018&end=02/08/2019")
+    remDr$navigate(url)
+  }
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "[href]")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 7)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[grep("/2018/", urlslist)]
+urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
+
+##start a data frame
+POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(POLITICODF) = c("Source", "Url", "Text")
+POLITICODF = as.data.frame(POLITICODF)
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  POLITICODF$Source[i] = "POLITICO"
+  POLITICODF$Url[i] = urlslist[i]
+  POLITICODF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(POLITICODF, "POLITICO_gs.csv", row.names = F)
+
+```
+
+````{r Fox_kav, eval = F, include = F}
+
+##start a data frame
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+#loop over the results and go through them
+#1651 with 10 per page with 165 clicks
+
+for (i in 1:165){
+
+    #navigate to the page
+    url = paste0("https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=",
+                 (i-1)*10)
+    remDr$navigate(url)
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", ".ng-binding")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("video.", urlslist))] #take out videos
+urlslist = urlslist[-c(grep("/search-results", urlslist))] #take out search result fake links
+
+##start a data frame
+FOXDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(FOXDF) = c("Source", "Url", "Text")
+FOXDF = as.data.frame(FOXDF)
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  FOXDF$Source[i] = "FOX"
+  FOXDF$Url[i] = urlslist[i]
+  FOXDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(FOXDF, "FOX_kav.csv", row.names = F)
+```
+
+````{r Breitbart_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.breitbart.com/tag/brett-kavanaugh/"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+for (i in 1:42){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "h2 a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  if (i > 1)
+    {
+  url = paste0("https://www.breitbart.com/tag/brett-kavanaugh/page/",
+               i+1, "/")
+  remDr$navigate(url)
+  }
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
+                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
+                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
+                       ])
+
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(BREITBARTDF) = c("Source", "Url", "Text")
+BREITBARTDF = as.data.frame(BREITBARTDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'h2, p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  BREITBARTDF$Source[i] = "BREITBART"
+  BREITBARTDF$Url[i] = urlslist3[i]
+  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(BREITBARTDF, "BREITBART_kav.csv", row.names = F)
+```
+
+```{r Breitbart_gs, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.breitbart.com/tag/government-shutdown/"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+for (i in 1:16){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "h2 a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  if (i > 1)
+    {
+  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
+               i+1, "/")
+  remDr$navigate(url)
+  }
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
+                         (
+                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
+                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
+                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
+                         ), #before feb 8
+                       ])
+
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(BREITBARTDF) = c("Source", "Url", "Text")
+BREITBARTDF = as.data.frame(BREITBARTDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'h2, p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  BREITBARTDF$Source[i] = "BREITBART"
+  BREITBARTDF$Url[i] = urlslist3[i]
+  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(BREITBARTDF, "BREITBART_gs.csv", row.names = F)
+```
+
+````{r Rush_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+##18 pages
+for (i in 1:18){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
+
+  #click on the page number
+  webClick[[18]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
+                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
+                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
+                       ])
+
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(RUSHDF) = c("Source", "Url", "Text")
+RUSHDF = as.data.frame(RUSHDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  RUSHDF$Source[i] = "RUSH"
+  RUSHDF$Url[i] = urlslist3[i]
+  RUSHDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(RUSHDF, "RUSH_kav.csv", row.names = F)
+```
+
+```{r Rush_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+#create a blank space to put the links
+urlslist_final = list()
+
+url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"
+
+remDr$navigate(url)
+
+#loop over the results and go through them
+##47 pages
+for (i in 1:47){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
+
+  #click on the page number
+  webClick[[18]]$clickElement()
+
+  #page reload
+  Sys.sleep(runif(1, 1, 5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+beep(sound = 6)
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("store", urlslist))] #take out store
+urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
+
+##find the right dates
+temp = strsplit(urlslist, split = "/")
+temp2 = plyr::ldply(temp, rbind)
+temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
+
+#pull only the right dates
+rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
+                         (
+                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
+                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
+                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
+                         ), #before feb 8
+                       ])
+urlslist3 = urlslist[as.numeric(rows)]
+
+##start a data frame
+RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
+colnames(RUSHDF) = c("Source", "Url", "Text")
+RUSHDF = as.data.frame(RUSHDF)
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data2 = html_nodes(webpage,'p') 
+  text_data2 = html_text(headline_data2)
+
+  ##save the data
+  RUSHDF$Source[i] = "RUSH"
+  RUSHDF$Url[i] = urlslist3[i]
+  RUSHDF$Text[i] = paste(text_data2, collapse = "")
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(RUSHDF, "RUSH_gs.csv", row.names = F)
+
+```
+
+````{r Blaze_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
+webpage9 = read_html(url9)
+headline_data9 = html_nodes(webpage9, '.widget__headline-text')
+
+attr_data9 = html_attrs(headline_data9) 
+attr_data9
+
+urlslist9 = unlist(attr_data9)
+urlslist9 = urlslist9[grep(urlslist9)]
+
+##start a data frame
+BlazeDF = matrix(NA, nrow = length(urlslist9), ncol = 3)
+colnames(BlazeDF) = c("Source", "Url", "Text")
+BlazeDF = as.data.frame(BlazeDF)
+
+##for loops
+for (i in 1:length(urlslist9)){
+
+  ##read in the URL
+  webpage9 <- read_html(urlslist9[i])
+
+  ##pull the specific nodes
+  headline_data9 = html_nodes(webpage9,'p')
+
+  ##pull the text
+  text_data9 = html_text(headline_data9)
+
+  ##save the data
+  BlazeDF$Source[i] = "The Blaze"
+  BlazeDF$Url[i] = urlslist9[i]
+  BlazeDF$Text[i] = paste(text_data9, collapse = "")
+} ##end for loop
+```
+
+```{r Blaze_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.theblaze.com/search/?q=government+shutdown"
+
+remDr$navigate(url)
+
+webClick <- remDr$findElements(using = "css", ".action-btn")
+
+#click next until done
+while (length(webClick) > 0 ) {
+
+  #find the urls for page X
+  webClick <- remDr$findElements(using = "css", ".action-btn")
+
+  webClick[[1]]$clickElement()
+
+  Sys.sleep(runif(1, 1, 5))
+}
+
+#find the urls for page X
+webElems <- remDr$findElements(using = "css", "a")
+
+#add the urls to a list
+urlslist_final = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+##deal with the URLS
+urlslist = urlslist_final
+urlslist = unique(urlslist)
+urlslist = urlslist[-c(grep("video/", urlslist))]
+urlslist = urlslist[grep("/news/", urlslist)]
+urlslist = urlslist[-c(grep("/201[3-7]", urlslist))]
+
+##start a data frame
+BLAZEDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(BLAZEDF) = c("Source", "Url", "Text")
+BLAZEDF = as.data.frame(BLAZEDF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
+
+for (i in 1:length(urlslist)){
+
+  webpage = read_html(urlslist[i])
+
+  headline_data = html_nodes(webpage, '.post-date')
+  text_data = html_text(headline_data)
+  date = as.Date(text_data, "%B %d, %Y")
+
+  if (date %within% int){
+    headline_data2 = html_nodes(webpage,'h1, h3, p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    BLAZEDF$Source[i] = "BLAZE"
+    BLAZEDF$Url[i] = urlslist[i]
+    BLAZEDF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(BLAZEDF, "BLAZE_gs.csv", row.names = F)
+
+```
+
+```{r Hannity_kav, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.hannity.com/trending/brett-kavanaugh/"
+
+remDr$navigate(url)
+
+urlslist_final = list()
+
+for (i in 1:4){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #move on to the next page
+  url = paste0("https://www.hannity.com/trending/brett-kavanaugh/?pg=", i+1)
+
+  remDr$navigate(url)
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+
+#also use google search to see if we can find more
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.google.com/search?q=kavanaugh+site%3Ahannity.com&source=lnt&tbs=cdr%3A1%2Ccd_min%3A9%2F13%2F2018%2Ccd_max%3A10%2F11%2F2018&tbm="
+
+remDr$navigate(url)
+
+urlslist_final2 = list()
+
+for (i in 1:3){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "link text", "Next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+urlslist2 = unlist(urlslist_final2)
+urlslist2 = c(urlslist, urlslist2)
+urlslist2 = unique(urlslist2)
+urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
+urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
+urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
+
+##start a data frame
+HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HANNITYDF) = c("Source", "Url", "Text")
+HANNITYDF = as.data.frame(HANNITYDF)
+int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data = html_nodes(webpage, '.author-info')
+  text_data = html_text(headline_data)
+  text_data = strsplit(text_data, " ")[[1]][7]
+  date = as.Date(text_data, "%m.%d.%y")
+
+  if (date %within% int){
+    headline_data2 = html_nodes(webpage,'h1, p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    HANNITYDF$Source[i] = "HANNITY"
+    HANNITYDF$Url[i] = urlslist3[i]
+    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(HANNITYDF, "HANNITY_kav.csv", row.names = F)
+```
+
+```{r Hannity_shut, eval = F, include = F}
+library(rvest)
+library(RSelenium)
+library(beepr)
+library(lubridate)
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "http://www.hannity.com/trending/shutdown/"
+
+remDr$navigate(url)
+
+urlslist_final = list()
+
+for (i in 1:4){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #move on to the next page
+  url = paste0("http://www.hannity.com/trending/shutdown/?pg=", i+1)
+
+  remDr$navigate(url)
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+##deal with the URLS
+urlslist = unlist(urlslist_final)
+urlslist = unique(urlslist)
+
+#also use google search to see if we can find more
+
+#open the browser
+rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
+remDr <- rD[["client"]]
+
+url = "https://www.google.com/search?biw=1366&bih=632&tbs=cdr%3A1%2Ccd_min%3A12%2F8%2F2018%2Ccd_max%3A2%2F8%2F2019&ei=gECaXNe8Aaft_Qb9w7G4BA&q=government+shutdown+site%3Ahannity.com&oq=government+shutdown+site%3Ahannity.com&gs_l=psy-ab.3...0.0..1915...0.0..0.0.0.......0......gws-wiz.aFps0nA33mY"
+
+remDr$navigate(url)
+
+urlslist_final2 = list()
+
+for (i in 1:9){
+
+  #find the urls for page X
+  webElems <- remDr$findElements(using = "css", "a")
+
+  #add the urls to a list
+  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
+
+  #find the thing to click on 
+  webClick <- remDr$findElements(using = "link text", "Next")
+
+  #click on the page number
+  webClick[[1]]$clickElement()
+
+  Sys.sleep(runif(1,1,5))
+
+}
+
+remDr$close()
+# stop the selenium server
+rD[["server"]]$stop()
+
+urlslist2 = unlist(urlslist_final2)
+urlslist2 = c(urlslist, urlslist2)
+urlslist2 = unique(urlslist2)
+urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
+urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
+urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
+
+##start a data frame
+HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
+colnames(HANNITYDF) = c("Source", "Url", "Text")
+HANNITYDF = as.data.frame(HANNITYDF)
+int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
+
+for (i in 1:length(urlslist3)){
+
+  webpage = read_html(urlslist3[i])
+
+  headline_data = html_nodes(webpage, '.author-info')
+  text_data = html_text(headline_data)
+  text_data = strsplit(text_data, " ")[[1]][7]
+  date = as.Date(text_data, "%m.%d.%y")
+
+  if (date %within% int){
+    headline_data2 = html_nodes(webpage,'h1, p') 
+    text_data2 = html_text(headline_data2)
+
+    ##save the data
+    HANNITYDF$Source[i] = "HANNITY"
+    HANNITYDF$Url[i] = urlslist3[i]
+    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
+  }
+
+  Sys.sleep(runif(1,1,10))
+
+  }
+
+beep(sound = 7)
+
+write.csv(HANNITYDF, "HANNITY_gs.csv", row.names = F)
+
+```
+
+## Sources
+
+Articles pertaining to the Brett Kavanaugh Supreme Court confirmation hearing and the 2018-2019 U.S.
+Government shutdown were scraped from the websites of 10 U.S.
+news sources.
+As in Experiment 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
+The sources favored by the highest proportion of consistent liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
+The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
+Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
+All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts, again written with the *papaja* library in *R*, are provided inline with this manuscript [@Aust2017].
+
+## Materials
+
+Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
+We compiled the articles into a dataset [@Wickham2016].
+Using this dataset, we identified word count and average word count per source.
+This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
+This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
+
+The same process was followed for scraping articles related to the partial U.S.
+Government shutdown of 2018-2019.
+The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
+Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
+
+```{r data_clean_kav, eval = F, echo = F}
+#Merge Exp2 text files and code partisan lean
+library(stringr)
+file.names = dir("C:/Users/kayla/Documents/GitHub/Will-Pilot/exp2_data/", pattern = '.csv')
+first = TRUE
+for(i in 1:length(file.names))
+{
+  df = read.csv(file.names[i], stringsAsFactors = FALSE)
+  colnames(df)[1] = "Source"
+  df$Text = gsub('\n', ' ', df$Text)
+  df$Text = gsub('\t', ' ', df$Text)
+  event = str_extract(file.names[i], '_[a-z]+')
+  event = str_replace(event, "_", '')
+  df$Event = rep(event, nrow(df))
+  if(df$Source=='BLAZE'|df$Source=='BREITBART'|df$Source=='FOX'|df$Source=='HANNITY'|df$Source=='RUSH')
+  {df$PartisanLean = rep('Conservative', nrow(df))}
+  if(df$Source=='HUFFPO'|df$Source=='NPR'|df$Source=='NY Times'|df$Source=='POLITICO'|df$Source=='SLATE')
+  {df$PartisanLean = rep('Liberal', nrow(df))}
+  if(first==TRUE)
+  {
+    df_full = df
+    first = FALSE
+  }
+  df_full = rbind(df_full, df)
+}
+
+write.csv(df_full, "exp2_merged data.csv", row.names = FALSE)
+```
 

### 2021-07-01 manuscript/topic_model.Rmd
here's the topic model

---
title: "Topic Model"
author: "Erin M. Buchanan"
date: "7/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(topicmodels)
library(rio)
library(tm)
library(slam)
library(ggplot2)
library(tidyverse)
library(tidytext)
library(dplyr)
```

## Data

```{r}
DF <- import("finaldata_LIWC.csv")
```

## Text Cleaning

```{r}
DF$clean <- removeNumbers(DF$Text)
DF$clean <- removePunctuation(DF$clean)
DF$clean <- removeWords(DF$clean, stopwords(kind = "SMART"))
DF$clean <- tolower(DF$clean)
DF$clean <- gsub("[[:punct:]]", " ", DF$clean)
DF$clean <- gsub("\n", " ", DF$clean)
```

## Topic Model

```{r}
import_corpus <- Corpus(VectorSource(DF$clean))
import_matrix <- DocumentTermMatrix(import_corpus)
import_weight <- tapply(import_matrix$v/row_sums(import_matrix)[import_matrix$i], 
                       import_matrix$j, 
                       mean) *
  log2(nDocs(import_matrix)/col_sums(import_matrix > 0))

import_matrix <- import_matrix[ row_sums(import_matrix) > 0, ]

k <- 10 
SEED <- 58934

LDA_fit <- LDA(import_matrix, k = k, 
              control = list(seed = SEED))
```

## Results

```{r}
terms(LDA_fit,20)

LDA_fit_topics <- tidy(LDA_fit, matrix = "beta")
top_terms <- LDA_fit_topics %>%
   group_by(topic) %>%
   top_n(15, beta) %>%
   ungroup() %>%
   arrange(topic, -beta)

top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  theme_classic() +
  coord_flip()
```

### 2021-08-26 manuscript/Partisan Media Manuscript.Rmd
graphs

@@
 
+Ever increasing attention is being paid to the impacts of partisanship on how people give and receive political information.
+The style and content of political information can be quantified in many ways, and one of those ways is motivation.
+
+In the current study, we explore the motivations of partisan media coverage through the lens of McClelland's classic theory of motivation.
+
 ```{r setup, include = FALSE}
@@
 ####make the table for study 1####
-table1 = matrix(NA, ncol = 12, nrow = 23)
+table1 = matrix(NA, ncol = 12, nrow = 10)
 colnames(table1) = c("DV", "Mconservative", 
@@
 ####make the table for study 2: government shutdown####
-table2 = matrix(NA, ncol = 12, nrow = 23)
+table2 = matrix(NA, ncol = 12, nrow = 10)
 colnames(table2) = c("DV", "Mconservative", 
@@
 ####make the table for study 2: Kavanaugh Hearings####
-table3 = matrix(NA, ncol = 12, nrow = 23)
+table3 = matrix(NA, ncol = 12, nrow = 10)
 colnames(table3) = c("DV", "Mconservative", 
@@
 groups = c(0, 1)
-DVs = c('Analytic','Clout','Authentic','Tone','WPS','Sixltr','anger','social','family','female','male','cogproc','affiliation','achieve','power','reward','risk','focuspast','focuspresent','focusfuture','money','relig','death')
+DVs = c('i','you','shehe','we','they','ipron','affiliation','achieve','power')
 

### 2021-08-26 manuscript/topic_model.Rmd
updated with gamma
graphs

@@
 ```
+
+# Interpretating Topics
+
+- Topic 1: Trump Impeachment
+- Topic 2: Immigration
+- Topic 3: U.S.-China Relations
+- Topic 4: Supreme Court
+- Topic 5: Party Politics
+- Topic 6: Military and Defense
+- Topic 7: U.S-Russia Relations
+- Topic 8: Technology
+- Topic 9: Congress
+- Topic 10: Campaign Scandals
+
+```{r}
+LDA_gamma <- as.data.frame(tidy(LDA_fit, matrix = "gamma"))
+LDA_gamma <- reshape(LDA_gamma, idvar = 'document', timevar = 'topic', direction = 'wide')
+
+DF$document <- row.names(DF)
+LDA_topics <- merge(DF, LDA_gamma, by = 'document')
+```
+
+```{r}
+library(sjPlot)
+setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript/graphs')
+LDA_topics$PartisanLean = as.factor(LDA_topics$PartisanLean)
+# 1 = Conservative, 2 = Liberal (neg coeff = )
+aff1 = glm(affiliation~gamma.1*PartisanLean, data = LDA_topics)
+png('aff1.png')
+plot_model(aff1, type='int')
+dev.off()
+pow1 = glm(power~gamma.1*PartisanLean, data = LDA_topics)
+png('pow1.png')
+plot_model(pow1, type='int')
+dev.off()
+ach1 = glm(achieve~gamma.1*PartisanLean, data = LDA_topics)
+png('ach1.png')
+plot_model(ach1, type='int')
+dev.off()
+
+aff2 = glm(affiliation~gamma.2*PartisanLean, data = LDA_topics)
+png('aff2.png')
+plot_model(aff2, type='int')
+dev.off()
+pow2 = glm(power~gamma.2*PartisanLean, data = LDA_topics)
+png('pow2.png')
+plot_model(pow2, type='int')
+dev.off()
+ach2 = glm(achieve~gamma.2*PartisanLean, data = LDA_topics)
+png('ach2.png')
+plot_model(ach2, type='int')
+dev.off()
+
+aff3 = glm(affiliation~gamma.3*PartisanLean, data = LDA_topics)
+png('aff3.png')
+plot_model(aff3, type='int')
+dev.off()
+pow3 = glm(power~gamma.3*PartisanLean, data = LDA_topics)
+png('pow3.png')
+plot_model(pow3, type='int')
+dev.off()
+ach3 = glm(achieve~gamma.3*PartisanLean, data = LDA_topics)
+png('ach3.png')
+plot_model(ach3, type='int')
+dev.off()
+
+aff4 = glm(affiliation~gamma.4*PartisanLean, data = LDA_topics)
+png('aff4.png')
+plot_model(aff4, type='int')
+dev.off()
+pow4 = glm(power~gamma.4*PartisanLean, data = LDA_topics)
+png('pow4.png')
+plot_model(pow4, type='int')
+dev.off()
+ach4 = glm(achieve~gamma.4*PartisanLean, data = LDA_topics)
+png('ach4.png')
+plot_model(ach4, type='int')
+dev.off()
+
+aff5 = glm(affiliation~gamma.5*PartisanLean, data = LDA_topics)
+png('aff5.png')
+plot_model(aff5, type='int')
+dev.off()
+pow5 = glm(power~gamma.5*PartisanLean, data = LDA_topics)
+png('pow5.png')
+plot_model(pow5, type='int')
+dev.off()
+ach5 = glm(achieve~gamma.5*PartisanLean, data = LDA_topics)
+png('ach5.png')
+plot_model(ach5, type='int')
+dev.off()
+
+aff6 = glm(affiliation~gamma.6*PartisanLean, data = LDA_topics)
+png('aff6.png')
+plot_model(aff6, type='int')
+dev.off()
+pow6 = glm(power~gamma.6*PartisanLean, data = LDA_topics)
+png('pow6.png')
+plot_model(pow6, type='int')
+dev.off()
+ach6 = glm(achieve~gamma.6*PartisanLean, data = LDA_topics)
+png('ach6.png')
+plot_model(ach6, type='int')
+dev.off()
+
+aff7 = glm(affiliation~gamma.7*PartisanLean, data = LDA_topics)
+png('aff7.png')
+plot_model(aff7, type='int')
+dev.off()
+pow7 = glm(power~gamma.7*PartisanLean, data = LDA_topics)
+png('pow7.png')
+plot_model(pow7, type='int')
+dev.off()
+ach7 = glm(achieve~gamma.7*PartisanLean, data = LDA_topics)
+png('ach7.png')
+plot_model(ach7, type='int')
+dev.off()
+
+aff8 = glm(affiliation~gamma.8*PartisanLean, data = LDA_topics)
+png('aff8.png')
+plot_model(aff8, type='int')
+dev.off()
+pow8 = glm(power~gamma.8*PartisanLean, data = LDA_topics)
+png('pow8.png')
+plot_model(pow8, type='int')
+dev.off()
+ach8 = glm(achieve~gamma.8*PartisanLean, data = LDA_topics)
+png('ach8.png')
+plot_model(ach8, type='int')
+dev.off()
+
+aff9 = glm(affiliation~gamma.9*PartisanLean, data = LDA_topics)
+png('aff9.png')
+plot_model(aff9, type='int')
+dev.off()
+pow9 = glm(power~gamma.9*PartisanLean, data = LDA_topics)
+png('pow9.png')
+plot_model(pow9, type='int')
+dev.off()
+ach9 = glm(achieve~gamma.9*PartisanLean, data = LDA_topics)
+png('ach9.png')
+plot_model(ach9, type='int')
+dev.off()
+
+aff10 = glm(affiliation~gamma.10*PartisanLean, data = LDA_topics)
+png('aff10.png')
+plot_model(aff10, type='int')
+dev.off()
+pow10 = glm(power~gamma.10*PartisanLean, data = LDA_topics)
+png('pow10.png')
+plot_model(pow10, type='int')
+dev.off()
+ach10 = glm(achieve~gamma.10*PartisanLean, data = LDA_topics)
+png('ach10.png')
+plot_model(ach10, type='int')
+dev.off()
+```

### 2021-09-30 manuscript/topic_model.Rmd
graphsupdate

--- 2021-07-01 manuscript/topic_model.Rmd
@@
 ```
+
+# Interpretating Topics
+
+- Topic 1: Trump Impeachment
+- Topic 2: Immigration
+- Topic 3: U.S.-China Relations
+- Topic 4: Supreme Court
+- Topic 5: Party Politics
+- Topic 6: Military and Defense
+- Topic 7: U.S-Russia Relations
+- Topic 8: Technology
+- Topic 9: Congress
+- Topic 10: Campaign Scandals
+
+```{r}
+LDA_gamma <- as.data.frame(tidy(LDA_fit, matrix = "gamma"))
+LDA_gamma <- reshape(LDA_gamma, idvar = 'document', timevar = 'topic', direction = 'wide')
+
+DF$document <- row.names(DF)
+LDA_topics <- merge(DF, LDA_gamma, by = 'document')
+```
+
+```{r}
+library(sjPlot)
+setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript/graphs')
+LDA_topics$PartisanLean = as.factor(LDA_topics$PartisanLean)
+# 1 = Conservative, 2 = Liberal (neg coeff = )
+aff1 = glm(affiliation~gamma.1*PartisanLean, data = LDA_topics)
+png('aff1.png')
+plot_model(aff1, type='int')
+dev.off()
+summary(aff1)
+pow1 = glm(power~gamma.1*PartisanLean, data = LDA_topics)
+png('pow1.png')
+plot_model(pow1, type='int')
+dev.off()
+summary(pow1)
+ach1 = glm(achieve~gamma.1*PartisanLean, data = LDA_topics)
+png('ach1.png')
+plot_model(ach1, type='int')
+dev.off()
+summary(ach1)
+
+aff2 = glm(affiliation~gamma.2*PartisanLean, data = LDA_topics)
+png('aff2.png')
+plot_model(aff2, type='int')
+dev.off()
+summary(aff2)
+pow2 = glm(power~gamma.2*PartisanLean, data = LDA_topics)
+png('pow2.png')
+plot_model(pow2, type='int')
+dev.off()
+summary(pow2)
+ach2 = glm(achieve~gamma.2*PartisanLean, data = LDA_topics)
+png('ach2.png')
+plot_model(ach2, type='int')
+dev.off()
+summary(ach2)
+
+aff3 = glm(affiliation~gamma.3*PartisanLean, data = LDA_topics)
+png('aff3.png')
+plot_model(aff3, type='int')
+dev.off()
+summary(aff3)
+pow3 = glm(power~gamma.3*PartisanLean, data = LDA_topics)
+png('pow3.png')
+plot_model(pow3, type='int')
+dev.off()
+summary(pow3)
+ach3 = glm(achieve~gamma.3*PartisanLean, data = LDA_topics)
+png('ach3.png')
+plot_model(ach3, type='int')
+dev.off()
+summary(ach3)
+
+aff4 = glm(affiliation~gamma.4*PartisanLean, data = LDA_topics)
+png('aff4.png')
+plot_model(aff4, type='int')
+dev.off()
+summary(aff4)
+pow4 = glm(power~gamma.4*PartisanLean, data = LDA_topics)
+png('pow4.png')
+plot_model(pow4, type='int')
+dev.off()
+summary(pow4)
+ach4 = glm(achieve~gamma.4*PartisanLean, data = LDA_topics)
+png('ach4.png')
+plot_model(ach4, type='int')
+dev.off()
+summary(ach4)
+
+aff5 = glm(affiliation~gamma.5*PartisanLean, data = LDA_topics)
+png('aff5.png')
+plot_model(aff5, type='int')
+dev.off()
+summary(aff5)
+pow5 = glm(power~gamma.5*PartisanLean, data = LDA_topics)
+png('pow5.png')
+plot_model(pow5, type='int')
+dev.off()
+summary(pow5)
+ach5 = glm(achieve~gamma.5*PartisanLean, data = LDA_topics)
+png('ach5.png')
+plot_model(ach5, type='int')
+dev.off()
+summary(ach5)
+
+aff6 = glm(affiliation~gamma.6*PartisanLean, data = LDA_topics)
+png('aff6.png')
+plot_model(aff6, type='int')
+dev.off()
+summary(aff6)
+pow6 = glm(power~gamma.6*PartisanLean, data = LDA_topics)
+png('pow6.png')
+plot_model(pow6, type='int')
+dev.off()
+summary(pow6)
+ach6 = glm(achieve~gamma.6*PartisanLean, data = LDA_topics)
+png('ach6.png')
+plot_model(ach6, type='int')
+dev.off()
+summary(ach6)
+
+aff7 = glm(affiliation~gamma.7*PartisanLean, data = LDA_topics)
+png('aff7.png')
+plot_model(aff7, type='int')
+dev.off()
+summary(aff7)
+pow7 = glm(power~gamma.7*PartisanLean, data = LDA_topics)
+png('pow7.png')
+plot_model(pow7, type='int')
+dev.off()
+summary(pow7)
+ach7 = glm(achieve~gamma.7*PartisanLean, data = LDA_topics)
+png('ach7.png')
+plot_model(ach7, type='int')
+dev.off()
+summary(ach7)
+
+aff8 = glm(affiliation~gamma.8*PartisanLean, data = LDA_topics)
+png('aff8.png')
+plot_model(aff8, type='int')
+dev.off()
+summary(aff8)
+pow8 = glm(power~gamma.8*PartisanLean, data = LDA_topics)
+png('pow8.png')
+plot_model(pow8, type='int')
+dev.off()
+summary(pow8)
+ach8 = glm(achieve~gamma.8*PartisanLean, data = LDA_topics)
+png('ach8.png')
+plot_model(ach8, type='int')
+dev.off()
+summary(ach8)
+
+aff9 = glm(affiliation~gamma.9*PartisanLean, data = LDA_topics)
+png('aff9.png')
+plot_model(aff9, type='int')
+dev.off()
+summary(aff9)
+pow9 = glm(power~gamma.9*PartisanLean, data = LDA_topics)
+png('pow9.png')
+plot_model(pow9, type='int')
+dev.off()
+summary(pow9)
+ach9 = glm(achieve~gamma.9*PartisanLean, data = LDA_topics)
+png('ach9.png')
+plot_model(ach9, type='int')
+dev.off()
+summary(ach9)
+
+aff10 = glm(affiliation~gamma.10*PartisanLean, data = LDA_topics)
+png('aff10.png')
+plot_model(aff10, type='int')
+dev.off()
+summary(aff10)
+pow10 = glm(power~gamma.10*PartisanLean, data = LDA_topics)
+png('pow10.png')
+plot_model(pow10, type='int')
+dev.off()
+summary(pow10)
+ach10 = glm(achieve~gamma.10*PartisanLean, data = LDA_topics)
+png('ach10.png')
+plot_model(ach10, type='int')
+dev.off()
+summary(ach10)
+```
+
+## Interpretation of Regressions
+
+- Topic 1: Trump Impeachment
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 2: Immigration
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 3: U.S.-China Relations
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 4: Supreme Court
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 5: Party Politics
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 6: Military and Defense
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 7: U.S-Russia Relations
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 8: Technology
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 9: Congress
+  - Achieve:
+  - Power:
+  - Affiliation:
+- Topic 10: Campaign Scandals
+  - Achieve:
+  - Power:
+  - Affiliation:

### 2021-12-13 thesis_version/pilot_manuscript.Rmd
cleaning up

--- 2020-07-29 thesis/pilot_manuscript.Rmd
@@
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, the researchers gathered poltical articles from four sources.
+In Experiment 1, the researchers gathered political articles from four sources.
 We were unable to reveal significant differences in moral or political endorsements, but we solidified the method to be employed in further research.
@@
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
-Goverment Shutdown of 2018-2019.
+Government Shutdown of 2018-2019.
 Once again, no significant differences in moral or political endorsements were found.
@@
 Lastly, "dominance" or "control" describes the extent to which a word makes one feel in or out of control [@Bradley1999].
-The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Mannikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
+The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Manikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
 
@@
 ##import the overalldata 
-overalldata = read.csv("exp1_data/overalldata.csv")
+overalldata = read.csv("../exp1_data/overalldata.csv")
 
@@
 ##pull in the data
-master = read.csv("exp1_data/overalldata.csv", stringsAsFactors = F)
+master = read.csv("../exp1_data/overalldata.csv", stringsAsFactors = F)
 
@@
 
-final = read.csv("exp1_data/finaldata.csv", stringsAsFactors = F)
+final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
 final = na.omit(final) #one weird NA line
@@
 ##open the Warriner data for later
-warriner = read.csv("exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+warriner = read.csv("../exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
 warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
@@
 #read in the harm total words from the mtmm project
-harm_all = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* articles had the lowest reading grade level on average, while *The New York Times* ihad the highest.
+Finally, *Fox News* articles had the lowest reading grade level on average, while *The New York Times* had the highest.
 This result might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
@@
 #read it in
-NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
-BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
-RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+NYtimes_kav = read.csv("../exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+NPR_kav = read.csv("../exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+SLATE_kav = read.csv("../exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+HUFFPO_kav = read.csv("../exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+POLITICO_kav = read.csv("../exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
+FOX_kav = read.csv("../exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
+BREITBART_kav = read.csv("../exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
+RUSH_kav = read.csv("../exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
+BLAZE_kav = read.csv("../exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
+HANNITY_kav = read.csv("../exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
 
@@
 #read it in
-NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
-NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
-SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
-HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
-POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
-FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
-BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
-RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
-BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
-HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
+NYtimes_gs = read.csv("../exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+NPR_gs = read.csv("../exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
+SLATE_gs = read.csv("../exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
+HUFFPO_gs = read.csv("../exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
+POLITICO_gs = read.csv("../exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
+FOX_gs = read.csv("../exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
+BREITBART_gs = read.csv("../exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
+RUSH_gs = read.csv("../exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
+BLAZE_gs = read.csv("../exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
+HANNITY_gs = read.csv("../exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
 
@@
 #read in the harm total words from the mtmm project
-harm_all_kav = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_kav = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all_kav = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all_kav = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all_kav = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all_kav = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 #read in the harm total words from the mtmm project
-harm_all_gs = read.csv("exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_gs = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair_gs, echo = F, include=FALSE}
-fair_all_gs = read.csv("exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all_gs = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
-ingroup_all_gs = read.csv("exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all_gs = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority_gs, echo = F, include=FALSE}
-authority_all_gs = read.csv("exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all_gs = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity_gs, echo = F, include=FALSE}
-purity_all_gs = read.csv("exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all_gs = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 Given part of the researchers' goal with this study was to answer a method question, they must contemplate whether or not the method or the construct of interest (political lean) are the primary contributor to null results.
-Either the method used to detect lean was insufficent for this purpose, or political lean simply does not exist, indicating the presence of a true negative in the results.
+Either the method used to detect lean was insufficient for this purpose, or political lean simply does not exist, indicating the presence of a true negative in the results.
 
@@
 Given this aspect of the news economy, the researchers still believe certain news outlets in the U.S.
-contatin a political slant.
+contain a political slant.
 The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
@@
 @Graham2009 actually performed a process of human error-checking for context when formulating the MFD.
-While this might have helped that team fix mistakes made by the LIWC program (@Pennebaker2007), manual coding of this nature has the potential to introduce an unnacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and beleif systems.
+While this might have helped that team fix mistakes made by the LIWC program (@Pennebaker2007), manual coding of this nature has the potential to introduce an unacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and belief systems.
 Additionally, the numerous ways in which context affects meaning make it difficult to interpret MFD word occurrence outside of a narrow operational definition of "endorsement." In fact, political lean may be communicated through methods other than through the use of particular words.
@@
 Through these divergent strategies, liberal and conservative news organizations might be able to appeal to their fans while exhibiting similar levels of moral endorsement.
-This could represent a further weakness of the Moral Foudnations Dictionary as an instrument, as it is unable to identify these potential strategies for communicating certain points of view.
+This could represent a further weakness of the Moral Foundations Dictionary as an instrument, as it is unable to identify these potential strategies for communicating certain points of view.
 
@@
 For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts.
-According to @Belisle2018, these observations imply President Obama, who empolyed more coordinative frames, utilized language emphasizing unity and similarity between people.
+According to @Belisle2018, these observations imply President Obama, who employed more coordinative frames, utilized language emphasizing unity and similarity between people.
 Donald Trump, on the other hand emphasized differences and divisions between people through his use of distinctive frames [@Belisle2018].
@@
 ```{r appendix_mfd, results = 'asis', echo = FALSE, message = F}
-orig_mfd = read.csv("exp1_data/original_mfd.csv", stringsAsFactors = F, fileEncoding="UTF-8")
+orig_mfd = read.csv("../exp1_data/original_mfd.csv", stringsAsFactors = F, fileEncoding="UTF-8")
 ####build the table here####

### 2021-12-13 SAGE/script for sage.R

@@ -1,478 +1,0 @@
-
-# Web Scraping Code -------------------------------------------------------
-
-#we ran this part daily until the bottom numbers were past 250K words for each one
-
-library(rvest)
-####NY Times####
-#Specifying the url for desired website to be scrapped
-url <- 'https://www.nytimes.com/section/politics'
-
-#Reading the HTML code from the website - headlines
-webpage <- read_html(url)
-headline_data = html_nodes(webpage,'.story-link a, .story-body a')
-
-attr_data = html_attrs(headline_data) 
-attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep("http", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-  
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-  
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.story-content') 
-  
-  ##pull the text
-  text_data = html_text(headline_data)
-  
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-} ##end for loop
-
-####NPR original front page####
-url2 = 'https://www.npr.org/sections/politics/'
-webpage2 = read_html(url2)
-headline_data2 = html_nodes(webpage2,'.title a')
-
-#URLs
-attr_data2 = html_attrs(headline_data2) 
-attr_data2
-
-urlslist2 = unlist(attr_data2)
-urlslist2 = urlslist2[grep("http", urlslist2)]
-urlslist2
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
-colnames(NPRDF) = c("Source", "Url", "Text")
-NPRDF = as.data.frame(NPRDF)
-
-##for loops
-for (i in 1:length(urlslist2)){
-  
-  ##read in the URL
-  webpage2 <- read_html(urlslist2[i])
-  
-  ##pull the specific nodes
[…]

### 2022-01-25 metapsych manuscript/manuscript_metapsych.Rmd
metapsych manuscript draft

--- 2021-12-13 thesis_version/pilot_manuscript.Rmd
@@
 
-In the United States, today's media landscape affords consumers a multitude of options for obtaining political news.
-Since the advent of cable news networks and the World Wide Web in the last decades of the twentieth century, consumers have gained access to an ever-expanding menagerie of news sources, many of which can be called up via a simple click, touch, or swipe.
-Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
-For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant, respectively.
-These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
-Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
-Specifically, the use of differing moral language in political articles might be an indicator of political bias in news media.
-
-Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
-Starting chiefly in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
-Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of "morality." Concerns regarding operationalization remain an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
-
-## Moral Foundations Theory
-
-As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg [@Haidt2007].
-Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance [@Kohlberg1977].
-Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
-Similarly, Kohlberg found people typically start with a "pre-conventional" understanding of morality during infancy in which children understand "right" and "wrong" purely in terms of how they interact with resultant experiences of rewards and punishment.
-Typically, people progress through several steps until they reach a "post-conventional" ethics.
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their "self-chosen ethical principles" [@Kohlberg1977].
-From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality [@Haidt2007].
-This view persisted until it encountered criticism in the early 1980s.
-
-Kohlberg's conception of morality faced major scrutiny from psychologist Carol Gilligan.
-In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women [@Haidt2007].
-Gilligan drew attention to purported differences in the ways men and women are taught to relate to self and others.
-She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-She pushes back against Kohlberg's assumption that moral development replaces "rule of brute force," as enforced by men, with the justice-based "rule of law." According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law [@Gilligan1982].
-Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
-Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring [@Gilligan1982].
-This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring [@Haidt2007].
-While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
+The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].Since then, Kohlberg's theory has been highly criticized with numerous theory and hypotheses being proposed to replace it.
+One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham [@Haidt2007].
+While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related issue, the Moral Foundations Dictionary (MFD) [@Graham2009].@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
+Here we first review evidence and criticisms against this assumption.
+We then provide our own test of the MFD using partisan news articles.
+
+## Moral Foundations Dictionary
 
@@
 
-In their brief overview of the history of moral psychology, @Graham2009 explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
-Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
-Such a system, they argued, did not account for moral concerns outside of the western world [@Graham2009].
-Individually focused concerns can be grouped under an overarching "ethic of autonomy," which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the "ethic of community" (comprising one's duty to their family, tribe, etc.), and the "ethic of divinity" - representing one's duty not to defile their God-given body and soul [@Graham2009].
-In the 2000s, @Haidt2007 took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
-
-Haidt and Graham settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].
-The researchers attempted to locate virtues and morals corresponding to "evolutionary thinking." For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the *fairness/reciprocity* foundation.
-Additionally, evolutionary literature on disgust and its correlation to human behavior regarding food and sex informed the *purity/sanctity* foundation [@Graham2011].
-The researchers identified the five "top candidates" for the foundations of human cultures' morality [@Graham2011].
-
-The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups.
-*harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm.
-*Fairness/reciprocity* represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
-The other three foundations (*ingroup/loyalty*, *authority/respect*, and *purity/sanctity*) are the "binding" foundations, owing to their focus on group-related concerns, rather than those of individuals.
-*Ingroup/loyalty* represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
-*Authority/respect* represents an endorsement of social hierarchies and traditions while denigrating disobedience.
-Finally, *purity/sanctity* represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony [@Haidt2007].
-Liberals tend to endorse the individualizing foundations more than conservatives.
-Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
-It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations [@Graham2009].
-
-Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-@Suhler2011 list several potential weaknesses of MFT that they argue might threaten the theory's validity.
-First, the authors challenge @Haidt2007's claims the moral intuitions represented by MFT are innate and modular.
-@Suhler2011 claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
-Rather, behaviors likely result from interactions between genetics and experience [@Suhler2011].
-According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
-Similarly, @Haidt2007 rely on evidence authored by evolutionary psychologists to make a "strong modularity claim" [@Suhler2011].
-However, as with innateness, there is little neurobiological evidence to support modularity.
-
-@Suhler2011 also criticized the content and taxonomy of the five foundations.
-The authors criticize @Haidt2007's omissions of additional foundations, including *industry* and *modesty*, claiming these concepts are moralized in many societies worldwide.
-Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-For example, @Suhler2011 posit that *ingroup/loyalty* is merely a group-focused version of *harm/care*.
-Work by @Graham2011 might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
-Finally, @Suhler2011 point out that particular concepts related to a foundation, including "anger" in *fairness/reciprocity* and "deception" in *ingroup/loyalty*, could be ascribed to any of the other foundations as well.
-In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five [@Haidt2007; @Suhler2011].
-
-These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
-Such criticisms are especially valid when considered alongside questions about the Moral Foundations Dictionary in particular.
-Nevertheless, there exists compelling evidence supporting the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
-This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary in the next section.
-
-## Moral Foundations Dictionary
-
 In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
@@
 Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-@Graham2009 manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
-The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: "Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus" [@Graham2009].
-This sentence added to the *authority/respect* total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
-The researchers eliminated this sentence from the *authority/respect* raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions [@Graham2009].
-The original Moral Foundations Dictionary can be found in the Appendix.
 
@@
 
-To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurrence of words in a given text from the foundation's respective word list.
-As such, most analyses assume that zero percent occurrence is indicative of no endorsement, while any non-zero percent occurrence indicates endorsement of the foundation.
-This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
-A quick glance at the MFD words for *harm/care* reveals the presence of words that are more closely associated with universally accepted conceptions of *harm* over *care* and vice-versa [@Graham2009].
-For example, the word "cruel" has relatively negative connotations compared to "benefit." For the *harm/care* foundation, it is conceivable that use of the word "cruel" might indicate a greater attentional focus of the idea of *harm* rather than *care*.
-
-For *harm/care*, the definition of the foundation, as well as its name, clearly distinguishes between two somewhat opposite sides of an attentional continuum, with *harm* on the negative end and *care* on the positive side.
-In other words, the entries in the MFD for *harm/care* have somewhat clear positive and negative valences.
-The same pattern can be seen in the MFD entries for the other four foundations.
-*Purity/sanctity* features words that likely have a negative valence to most observers, including "disease" and "trash," along with more positive words, including "right" and "sacred" [@Graham2009].
-These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from *harm/care*: *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*.
-The latter four foundations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of *fairness/reciprocity*.
-
-When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
-How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
-If 2% of a politician's speech features positive words (i.e., "benefit" and "defend") from the MFD *harm/care* list, how can researchers be sure the level and nature of the speaker's "endorsement" of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the *harm/care* list?
-They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the *harm/care* spectrum.
-
-This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The MFQ, which was developed subsequent to the MFD, measures individuals’ endorsements of each of the foundations using a six-point scale [@Graham2011].
-The questionnaire is made up of judgment items and relevance items.
-Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
-An example of such a statement reads: “It can never be right to kill another human being” [@Graham2011].
-Relevance items gauge the respondent's opinion regarding the importance of foundation-related concerns.
-For example, the respondent is directed to rate how important the following situation is to their sense of morals: "whether or not someone did something disgusting." This example measures the relevance of the *purity/sanctity* foundations.
-Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ [@Graham2011].
-
-The Moral Foundations Questionnaire has been validated by multiple researchers.
-Likewise, its five-factor structure has been demonstrated to fit data in multiple countries [@Graham2011; @Davies2014].
-In their article introducing the 30-item MFQ, @Graham2011 conducted an exploratory factor analysis (EFA) and found that a five-factor model fit the data better than a one, two, or three-factor model.
-@Davies2014 conducted a confirmatory factor analysis (CFA) of the MFQ with a sample from New Zealand and likewise found the five-factor model provided the best fit.
-While @Davies2014 concede the US and New Zealand share many similarities as Western nations, which could raise questions regarding the validity of the MFQ in non-Western nations.
-However, there are striking differences between the two countries, including the lack of a two-party political system in New Zealand, that provide grounds for claiming the MFQ generalizes beyond the United States.
-Furthermore, @Graham2011 claim to find a "reasonable" degree of generalizability for the MFQ across participants from many different regions in the world.
-These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by @Suhler2011 should still be taken into account in studies involving the theory.
-
-The aforementioned ambiguity of the Moral Foundations Dictionary as an instrument becomes clearer upon closer examination of the items in the Moral Foundations Questionnaire.
-One item under the *fairness/reciprocity* judgment subscale reads, "Justice is the most important requirement for a society" [@Graham2011].
-The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning "strongly disagree" at 1 to "strongly agree" at 6.
-While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
-When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they "slightly agree" with the statement [@Graham2011].
-This specificity is not present in most analyses involving the MFD and percent occurrence, unless they also take into account the valence of the words used in the text or speech of interest.
-
-## Valence
-
-Borrowing from Osgood's work in the 1950s, @Bradley1999 recognized valence as one of three related dimensions comprising emotion when developing their Affective Norms for English Words (ANEW).
-As mentioned before, "valence," the first dimension, denotes the pleasantness of a given word.
-"Arousal," the second dimension, describes the stimulating nature of a word.
-Lastly, "dominance" or "control" describes the extent to which a word makes one feel in or out of control [@Bradley1999].
-The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Manikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
-
-Participants saw the stimulus word and responded on each scale.
-The valence scale featured a smiling figure at one end (representing pleasantness) and a frowning figure at the other end (for unpleasantness).
-The arousal scale had a "wide-eyed" figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
-Finally, the dominance scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end [@Bradley1999].
-The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words [@Bradley1999].
-ANEW represented an important first step in establishing affective norms for large numbers of English words.
-However, later researchers found the 1,040-word list to be limiting for a language consisting of thousands of words.
-
-@Warriner2013 exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e., "watch" rather than "watched" and "watching").
-The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory [@Warriner2013].
-They argue the list of words included in ANEW is sufficient for small-scale factorial research designs, but the list is "prohibitively small" for larger-scale "megastudies" that are common in psycholinguistic research today [@Warriner2013].
-
-In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by @Kuperman2012 as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media [@New2007].
-This data collection resulted in the final list of 13,915 lemmas.
-Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
-Participants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
-The researchers used a nine-point scale similar to the one used by @Bradley1999 when collecting ratings for ANEW [@Warriner2013].
-
-The researchers noted several points of interest upon observing ratings.
-First, they found that valence and dominance ratings had a negative skew, indicating more words elicited feelings of happiness and control than their respective opposites.
-Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
-This U-shape indicates words with high degrees of positivity and negativity elicited higher arousal [@Warriner2013].
-These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
-
-@Warriner2015 utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in language.
-The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, the Corpus for Contemporary American English (COCA), the British National Corpus (BNC), Touchstone Applied Science Associates, Inc.
-Corpus (TASA), and the corpus used for the Hyperspace Analogue to Language model (HAL), the researchers found that words with positive valence were also used more frequently [@Warriner2015].
-While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the @Warriner2013 list in emotional studies.
-
-In addition to applications in emotion research, the @Warriner2013 norms have been utilized in cognitive research as well.
-One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-@Kuperman2014 sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
-The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks - two cognitive processing tasks wherein a participant has to read aloud or judge a word for its lexicality).
-First, @Kuperman2014 found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
-The researchers also concluded that words causing higher arousal tend to have slower decision times than less-arousing words.
-They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
-They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
-Finally, @Kuperman2014 found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks [@Kuperman2014].
-This research serves as further evidence that the @Warriner2013 list can be used for research inquiries both within and without the field of psycholinguistics.
-
-In the present studies, the researchers used the @Warriner2013 list in order to denote the valence of the words appearing in the news articles scraped from the internet.
-Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
-The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
-Specifically, valences were used to weight the MFD words by their relative degree of positivity or negativity.
-Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
-
-## News Media and Politics
-
-Research into politics, language, and media has illuminated the complex relationships between all three.
-Any politically-oriented discussion of word occurrence as an implication of moral or political position assumes that language and ideology are intrinsically linked.
-Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through language, thus implying a connection between ideology and language.
-She goes on to criticize the notion that language is either the "pre-existing raw material" used to shape ideologies or the "post-hoc vehicle" for their propagation.
-Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies [@Cameron2006].
-Owing to the fact the Moral Foundations Dictionary was developed in order to assess the moral, which includes the ideological, orientation of discourse, its purported ability to assess parts of the structure of language (vocabulary) for ideological lean is of chief interest to the researchers in the present study.
-
-The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S., @Druckman2004 considered political "issues" as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-According to the researchers, "image" priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004].
-The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
-The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
-
-They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
-Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].
-The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g., priming) issues related to energy, defense, and the economy.
-This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
-
-There is a potential caveat regarding the validity of @Druckman2004's findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
-@Pashler2012 point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
-Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
-Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
-@Pashler2012 point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
-Studies investigating perceptual priming have been "directly replicated in hundreds of labs" [@Pashler2012].
-This replication rate does not appear to be the case for social priming, as argued by @Pashler2012.
-
-@Pashler2012 noticed the unusually large effect size values (Cohen's *d*) reported by researchers studying social priming effects.
-The researchers reproduced two studies from @Williams2008 The first study attempted to prime participants by having them plot points on a Cartesian grid.
-The independent variable was priming condition and contained three levels: short, middle, and long distance.
-Those instructed to plot points further apart were hypothesized to express a higher degree of psychological distance regarding their family.
-The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
-@Pashler2012 concluded those two studies from @Williams2008 held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
-
-While these concerns regarding the replication of social priming studies are valid and deserve further investigation, @Druckman2004 does not purport to demonstrate a widespread effect of social priming on the American electorate.
-In other words, this research makes no claim to empirically supported priming effects.
-Rather, @Druckman2004 chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
-These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
-As such, @Druckman2004's research on Nixon serves as an example of language's potential utility in the propagation of desirable political opinions.
-The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
-The idea that even 1970s news media could contain political biases is of particular interest to the current study, which investigates similar phenomena in contemporary news media.
-
-Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014].
-Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival.
-The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].
-
-Therefore, the current study sought to combine both methods related questions and extension/replication of previous moral foundation results found for liberal and conservative sources.
-First, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Second, these weighted percentages were examined for their differences in across liberal and conservative news sources.
+## Critiques of Moral Foundations
+
+Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
+@Suhler2011 criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
+Likewise, @Gray2015 argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
+@Schien2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
+
+Beyond the critiques of the theory itself, many have also provided strong critiques of the Moral Foundations Dictionary (MFD).Conducting two close conceptual replication and six extension studies, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.In a meta-analysis, the theorized differences were only found for authority and purity (e.g.
+conservatives used more authority and purity word).
+Loyalty was contrary to theoretical predictions (e.g.
+used more by liberals), and no differences were found for harm and fairness.Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
+Exploring the political Twitterverse, @Sterling2018 found differences in the MFD to depend on political sophistication.
+For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
+While the MFD has not been extensive used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015, @Frimer2016, @Sagi2014].
+
+The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).These attempts generally fall into two categories: human annotations and semantic representations.
+@Hopp2021 represents the first approach where instead of relying on 'experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
+While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
+@Garten2018 represents the second categories which instead relies on data-driven semantic analysis.
+Using shallow learning models like word2vec, moral foundations are measured using semantic similarity vectors rather than simple word counts.
+
+As a further conceptual replication of @Frimer2020, here we test the liberal-conservative difference proposed by MFT using partisan media content and the Moral Foundations Dictionary.
+We first test differences in a general news corpus compared liberal sources (NPR and New York Times) to conservative sources (Fox News and Breitbart).
+Second, we examined news about specific political events: Brett Kavaugh's Supreme Court nomination and the Government Shutdown in 2018-19.
+Here the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
+To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
+Like @Frimer2020, results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.
 
@@
 
-```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}
+```{r exp1-source-descriptives, echo=F, results = 'asis', echo = FALSE, message = F}
 
@@
 
-The results obtained in Experiment 1 did not confirm the hypothesis.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The strongest effect found was for the *authority/respect* foundation owing to the fact its Cohen's *d* value was greater than the other four foundations.
-However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
-This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
-It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
-
-Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
+The results obtained in Experiment 1 fail to support the differences predicted by Moral Foundations Theory.
+First, differences between liberal and conservative news sources failed to reach statistically significance for any foundations.
+Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
+Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
+Overall, the results lend strong support to the case against the Moral Foundations Dictionary and weakens the case generally for Moral Foundations Theory.
+
+However,one possible limitation of the current data is the general-ness of the corpus.
 The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
-In short, the range of topics covered in Experiment 1 was likely too broad.
-The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
-
-Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-Generally speaking, the researchers believe their methodology to be sound.
-Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
-Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
-The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurrence.
-
-While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
-The researchers identified two such changes that were subsequently employed in Experiment 2.
-First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
-politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court.
-In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
+To address this limitation, two changes that were subsequently employed in Experiment 2.
+First, we elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
+Second, we chose to focus  data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
+Supreme Court and the government shutdown in December 2018 over disagreements about funding a U.S.-Mexico border wall.
+Hence, Experiment 2 is the best test of the Moral Foundations theory and dictionary in the context of partisan news.
 
 # Experiment 2
-
-## Kavanaugh Supreme Court Hearing
-
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@USGovernment2018b].
-Following allegations of sexual assault by high school classmate Dr.
-Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
-
-On September 27, the committee questioned Dr.
-Ford before commencing a second round of questioning for Judge Kavanaugh [@USGovernment2018].
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television [@OConnell2018].
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 [@USGovernment2018a].
-
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals.
-The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-Concerns around abortion might be related either to *harm/care* or *purity/sanctity*.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Likewise, arguments could be made that relate concerns regarding sexual violence to *harm/care* or *fairness/reciprocity*.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
-
-## U.S. Government Shutdown of 2018-2019
-
-The U.S.
-Federal Government partially shut down on December 22, 2018.
-The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress [@Axelrod2019].
-The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
-President Trump demanded $5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget [@Peoples2019].
-Owing to the lack of funding, the government began a partial shutdown, causing "around 800,000" federal employees to be either furloughed or compelled to work without pay [@Axelrod2019].
-
-The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
-President Trump signed the bill, ending the longest government shutdown in U.S.
-history [@Axelrod2019].
-Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole [@Kheel2019].
-Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed [@Peoples2019].
-While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
-
-As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
-Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
-As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns [@Martin2019].
-Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
-Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people [@Martin2019].
-This example potentially ties into the five moral foundations.
-Theological concerns regarding the border wall might invoke *authority/respect* as well as *purity/sanctity*.
-In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
-could also elicit moral concerns related to *ingroup/outgroup*.
-
-Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
-In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
 

### 2022-01-25 metapsych manuscript/manuscript_metapsych_kj.Rmd
metapsych manuscript draft

--- 2022-01-25 metapsych manuscript/manuscript_metapsych.Rmd
@@
     affiliation   : "2"
+  - name          : "Kayla N. Jordan, Ph.D."
+    affiliation   : "2"
 
@@
 abstract: |
-  The media ecosystem has grown, and political opinions have diverged such that there are competing conceptions of objective truth.
-Commentators often point to political biases in news coverage as a catalyst for this political divide.
-The Moral Foundations Dictionary (MFD) facilitates identification of ideological leanings in text through frequency of the occurrence of certain words.
-Through web scraping, the researchers extracted articles from popular news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+  Partisan differences and diviseness have become an increasing hot topic in psychological research.
+Many theories have been proposed to explain these differences and divisions including Moral Foundations Theory.
+The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
+Through web scraping, the researchers extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
 In Experiment 1, the researchers gathered political articles from four sources.
-We were unable to reveal significant differences in moral or political endorsements, but we solidified the method to be employed in further research.
+We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
 In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
@@
 Government Shutdown of 2018-2019.
-Once again, no significant differences in moral or political endorsements were found.
+Once again, no significant differences in moral endorsements were found.
+Together with past work, the results shed doubt on the validity of the MFD as a measure.
 
@@
 For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
-While the MFD has not been extensive used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015, @Frimer2016, @Sagi2014].
+While the MFD has not been extensive used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
 
@@
 While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
-@Garten2018 represents the second categories which instead relies on data-driven semantic analysis.
+@Garten2016 represents the second categories which instead relies on data-driven semantic analysis.
 Using shallow learning models like word2vec, moral foundations are measured using semantic similarity vectors rather than simple word counts.
@@
 
-```{r exp1-source-descriptives, echo=F, results = 'asis', echo = FALSE, message = F}
+```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}
 
@@
 
-The results obtained in Experiment 2 did not confirm either of the hypotheses.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The only significant effect was found for *harm/care* in the Kavanaugh confirmation hearing dataset.
-While the effect was in the hypothesized direction (higher positive endorsement for liberal sources), the effect size was small.
-While there were no significant effects found for the government shutdown topic, a small-to-medium effect size was calculated for the *authority/respect* foundation.
-Once again, the effect was in the hypothesized direction with conservative sources providing higher positive endorsements of the foundation relative to liberal sources.
-
-Both of these effects are consistent with both the research hypotheses as well as previous findings in Moral Foundations Theory scholarship.
-It should be noted these effects were found in isolation, and similar patterns were not found across the other studies.
-These findings undermine any inferences of political bias stemming from the content of news articles.
-The results obtained for Experiment 2 call into question the Moral Foundations Dictionary's efficacy as a tool for establishing differences between political news sources by partisan lean.
+The results obtained in Experiment 2 are slightly more in line with expectations from Moral Foundations Theory, however, in all but one case, the differences were not statistically significant.
+The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given @Graham2009.
+Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the effects much smaller than reported in @Graham2009.
+While not significant, fairness was endorsed more by conservatives in both cases.
+Contradictorily, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
+
+Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by Moral Foundations Theory.
+One issue that Experiment 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
+For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
+The original predictions made by the Moral Foundations are very simplistic and likely much more complex in reality.
 
@@
 
-Within the theoretical framework of Moral Foundations Theory [@Haidt2007], the researchers attempted to devise a method leveraging the Moral Foundations Dictionary [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
-The researchers downloaded news article text from the web, processed the text, matched it with the Moral Foundations Dictionary words, and calculated average valence for words in each article.
-To analyze the data, the researchers constructed multi-level models for each foundation in which weighted percentages were predicted by each source's political lean.
-Individual source was held as a random intercept to control for correlated error.
-This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertaining to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
-Government shutdown from December 2018 to January 2019.
-
-In Experiment 1, the researchers analyzed general political news articles from four prominent U.S.
-news sources: *The New York Times*, *NPR*, *Fox News*, and *Breitbart*.
-They hypothesized *The New York Times* and *NPR* would endorse moral foundations representative of liberal political views and that *Fox News* and *Breitbart* would endorse foundations indicative of conservative views.
-The researchers assigned a political lean (liberal or conservative) to the sources based upon consumer preferences established by @Mitchell2014.
-After collecting the articles through web scraping, processing the article text, calculating percent occurrence of MFD words, and weighting that value by valence, the researchers constructed the MLM.
-The results obtained were not significant in any statistical or practical sense.
+Within the theoretical framework of Moral Foundations Theory [@Haidt2007], we attempted to devise a method leveraging the Moral Foundations Dictionary [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
+In Experiment 1,the results obtained were not significant in any statistical or practical sense.
 There was a small effect found for the *authority/respect* foundation according to Cohen's *d*, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-The researchers viewed these results as an opportunity to alter their method for use in Experiment 2.
-
-In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political leanings in U.S.
-news sources.
-First, the researchers expanded the number of news sources from which articles were collected.
-They added *Slate*, *Politico*, and *Huffington Post* to the list of liberal sources and *The Blaze*, *Rush Limbaugh*, and *Sean Hannity* to the conservative sources.
-Once again, political bias groups were assigned based on @Mitchell2014's findings.
-Second, they elected to collect articles and compile datasets pertaining to two specific topics in U.S.
-news: the Kavanaugh hearing and the government shutdown.
-These topics were chosen due to their relevance to multiple moral foundations.
-Other than those two alterations, the same method (scraping, processing, weighting, and multi-level modelling) was employed for Experiment 2.
-
-For articles pertaining to the Kavanaugh hearing, there was a statistically significant effect for *harm/care*, but the effect size was modest.
-No other statistically or practically significant effects were found for the Kavanaugh topic.
-Likewise, there were no statistically or practically significant effects revealed for the government shutdown topic.
-However, there was a small-to-medium effect size for *authority/respect*.
-The fact these patterns do not appear in any of the other studies undertaken herein decreases the researchers' ability to draw any valuable conclusions regarding the MFD's ability to reveal political bias in American news media.
-
-The results obtained in both experiments, while not confirmatory, provide several avenues for future investigation.
-Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of an effect of political lean on American news writing under the auspices of Moral Foundations Theory.
-This does not, however, rule out the possibility that news media is biased.
-As @Mitchell2014 has demonstrated, self-reported political partisans are drawn to separate sources, but the present research was unable to offer any content-based explanations of this phenomenon.
-Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
-Given part of the researchers' goal with this study was to answer a method question, they must contemplate whether or not the method or the construct of interest (political lean) are the primary contributor to null results.
-Either the method used to detect lean was insufficient for this purpose, or political lean simply does not exist, indicating the presence of a true negative in the results.
-
-The researchers believe these results represent a false negative rather than a true negative.
-That is, we believe political lean exists, but that we have been unable to detect it at a content level.
-The researchers again turn to @Mitchell2014's work in this area: political partisans prefer certain news outlets over others.
-There must be something about the sources' content that facilitates partisans' repeated usage.
-Otherwise, they might not express such loyalty to any one source (or group of sources) over others.
-Given this aspect of the news economy, the researchers still believe certain news outlets in the U.S.
-contain a political slant.
-The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
+In Experiment 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
+Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of Moral Foundations Theory in terms of theorized partisan differences.
 
@@
 
-There remains an aspect of language which this method still cannot address: context.
-Owing to the presence of millions of words in the analyses presented in the current study, the researchers would be unable to check for context and correct endorsement scores accordingly.
-@Graham2009 actually performed a process of human error-checking for context when formulating the MFD.
-While this might have helped that team fix mistakes made by the LIWC program (@Pennebaker2007), manual coding of this nature has the potential to introduce an unacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and belief systems.
-Additionally, the numerous ways in which context affects meaning make it difficult to interpret MFD word occurrence outside of a narrow operational definition of "endorsement." In fact, political lean may be communicated through methods other than through the use of particular words.
-
-One method through which news organizations might appeal to political partisans is through their content strategy rather than their use of MFD words.
-The results in the current study demonstrate a similar pattern of endorsement across both conservative and liberal sources.
-Specifically, the researchers found slightly positive endorsements for all five foundations no matter the political lean of the source.
-While this may simply be an indication of insufficient MFD word occurrence in news articles, it may also demonstrate truly equal endorsement despite political lean.
-While news organizations may endorse all moral foundations, they may also adopt strategies for doing so that appeal to the political partisans consuming their product.
-As an example, a liberal source might endorse *purity/sanctity* through an appeal to reduce waste or pollution (i.e.
-keeping the earth "clean").
-A conservative source, on the other hand, might endorse *purity/sanctity* through an argument in favor of abstinence or religious commitment (i.e.
-keeping a "clean" soul, mind, or body).
-Both publications would register as positive endorsement of *purity/sanctity* despite appropriating the concept for distinct purposes.
-Through these divergent strategies, liberal and conservative news organizations might be able to appeal to their fans while exhibiting similar levels of moral endorsement.
-This could represent a further weakness of the Moral Foundations Dictionary as an instrument, as it is unable to identify these potential strategies for communicating certain points of view.
-
-Thus, the researchers' attention turned to the instrument used to detect differences: the Moral Foundations Dictionary.
+However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
 As mentioned before, MFD is a measure developed from Moral Foundations Theory [@Graham2009].
@@
 
-Alternative instruments could be developed through the Linguistic Inquiry and Word Count program (LIWC) [@Pennebaker2007].
-As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context [@Graham2009].
-This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
-The original authors of the MFD established sound psychometric properties for the tool, implying its validity in several applications.
-For this reason, the researchers elected to utilize the MFD as their primary instrument.
-
-Instruments that improve upon the Moral Foundations Dictionary could theoretically be developed through a LIWC analysis.
-Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from @Warriner2013.
-The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
-@Pennebaker2007 has suggested the program could be applied to analyses of cognitive, social, and emotional states.
-Furthermore, there is some evidence LIWC can be used to detect deception, but the reliability of the program's accuracy in this regard (67%) calls this assertion into question [@Pennebaker2011].
-Despite the promising extent of LIWC's abilities, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
-Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
-
-There is, however, another theoretical framework that could prove useful when applied to the method established in the present research.
-Relational Frame Theory originates in applied behavior analysis, but there exists recent scholarship that demonstrates its potential usefulness in the political realm.
-Relational Frame Theory (RFT) holds that stimuli, including speech and discourse, elicit responses in terms of relationships to other stimuli, even when the stimuli do not otherwise appear to be related [@Blackledge2014].
-For example, an individual's equivalent fear response to a venomous snake as well as a wooded area said to "contain snakes" represents "mutual entailment." That is, the fear response is an effect of both the snake and environment stimuli, which cause the fear response.
-"Combinatorial entailment" can be represented by a fear response elicited by a novel stimulus whose relationship to a well-known stimulus elicits a certain response [@Blackledge2014].
-In the snake example, if another stimulus (Stimulus A), were said to be "worse than" the snake, the relationship between A and the snake would elicit a more severe fear response to Stimulus A.
-RFT utilizes a set of "families" describing the nature of these relationships.
-Such families include (among others) "coordinative," establishing similarities between stimuli, "distinctive," implying fundamental differences between stimuli, and "hierarchical," implying a relation in terms of differing order or rank [@Belisle2018].
-These families can be used to analyze networks of relational frames in discourse.
-
-@Belisle2018 conducted a text analysis (using a computer algorithm) of several speeches made by four recent U.S.
-presidents under Relational Frame Theory.
-These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
-For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts.
-According to @Belisle2018, these observations imply President Obama, who employed more coordinative frames, utilized language emphasizing unity and similarity between people.
-Donald Trump, on the other hand emphasized differences and divisions between people through his use of distinctive frames [@Belisle2018].
-At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
-In any case, this research appears to indicate that RFT might be useful for analyzing political news content similar to the method employed in the current study.
-
-Another apparent strength of RFT is its demonstrated effectiveness in the analysis of political discourse.
-Unlike the development of the Moral Foundations Dictionary, this application of RFT was performed on public facing political discourse that might be more similar to news articles than the Christian sermons upon which the MFD was compiled.
-Additionally, there would likely be greater overlap between the speeches analyzed in @Belisle2018's work and political news, as the media often quotes speeches by the president.
-Furthermore, the types or "families" of relational frames could be used as the individual constructs much like the moral foundations in the present research.
-In order to conform with the method established for this study, their occurrence would need to be scored, probably as a percent.
-This would allow for an intuitive approach to weighting by *z*-scored valence if needed.
-
-While Relational Frame Theory appears to represent a viable option for further research into political news analysis, there are some drawbacks.
-First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
-In other words, RFT represents one method by which to analyze political text by analyzing occurrence of particular frames.
-However, there exists the caveat that the frame families are not known to represent patterns of political ideology at this time.
-One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it is a theory under which endorsement patterns (direction and relationship) could be predicted based upon political affiliation.
-While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
-
-In order to seriously consider RFT as a viable framework for this type of analysis, the researchers would like to be able to draw on further confirmatory evidence of the theory's utility in political discourse analysis.
-Specifically, analyses of more individuals than the four presidents addressed by @Belisle2018 would be needed to further demonstrate RFT's applicability in this field.
-Also, though presidential speeches may be more similar to news articles than sermons, they are still a distinct form of discourse with different goals and audiences than news outlets.
-RFT's reliability across these forms appears to remain untested as of this writing.
-These potential shortcomings are testable and might be overcome through more research.
-As such, RFT's potential as a useful framework for political discourse analysis should not be discounted.
-
-Finally, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
+In critiquing Moral Foundations Theory, @Schien2015 proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
+Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else [@Gray2014, @Schien2015].
+Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
+For example, in the case of abortion, liberals tend to identify the primary harm to the mother leading to a pro-choice position whereas conservative tend to identify the primary harm to the fetus leading to a pro-life position.
+While as of yet, no linguistic measurement of dyadic morality exists; such an approach may be able to better identify the systematic differences between liberals and conservatives.
+
+Turning to atheoretical approaches, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
 Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
@@
 
-The researchers aimed to utilize the Moral Foundations Dictionary and valence in the analysis of political news articles to determine whether or not bias was present.
-In Experiment 1, they tested general political news from four U.S.
-news sources - two liberal and two conservative.
-They were unable to find any significant evidence of political bias in that analysis.
-After adjusting the method to include more sources and specific topics for articles, including the Kavanaugh hearing and the government shutdown, the researchers were once again unable to uncover differences in MFD word use between conservative and liberal news sources.
-The results in the current study seem to demonstrate the MFD's weaknesses in applications to political discourse.
-MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
-In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, through a different theoretical perspective such as Relational Frame Theory, or through alternative strategies involving collecting data and drawing conclusions from which future theories may be derived.
-
-Never before has news media and discourse represented such fertile ground for psychological research.
+Never before has political discourse represented such fertile ground for psychological research.
 The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.

### 2022-03-03 manuscript_version/manuscript_metapsych.Rmd
fixing the manuscript issues

--- 2022-01-25 metapsych manuscript/manuscript_metapsych_kj.Rmd
@@
     address       : "901 S. National Ave, Springfield, MO, 65897"
-    email         : "Padfield94@live.missouristate.edu"
+    email         : "wpadfield@gmail.com"
   - name          : "Erin M. Buchanan, Ph.D."
@@
 
-author_note: |
-  William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
+authornote: |
+  William Padfield completed this project as part of his thesis requirements for a master's degree candidate in Psychology at Missouri State University.
+Submitted to Meta-Psychology.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+The full editorial process of all articles under review at Meta-Psychology can be found following this link: https://tinyurl.com/mp-submissions
 
@@
 The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
-Through web scraping, the researchers extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, the researchers gathered political articles from four sources.
+In Experiment 1, we gathered political articles from four sources.
 We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
-In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Experiment 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
@@
 Once again, no significant differences in moral endorsements were found.
-Together with past work, the results shed doubt on the validity of the MFD as a measure.
+Together with past work, the results shed doubt on the validity of the MFD as a reliable measurement tool.
 
@@
 
-bibliography      : ["will_thesis.bib"] #turn this off right now so it knits
-
-figsintext        : no
+bibliography      : ["metapsych_bib.bib"] #turn this off right now so it knits
+
+floatsintext      : no
 figurelist        : no
@@
 footnotelist      : no
-lineno            : no
-lang              : "english"
-class             : "man"
+linenumbers       : no
 mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
 output            : papaja::apa6_pdf
-replace_ampersands: yes
-csl               : apa6.csl
 ---
@@
 library(MOTE)
+library(quanteda)
+library(quanteda.textstats)
+library(tm)
+library(ngram)
+library(ggplot2)
+library(reshape)
 
@@
 
-The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].Since then, Kohlberg's theory has been highly criticized with numerous theory and hypotheses being proposed to replace it.
+The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].
+Since then, Kohlberg's theory has been highly criticized with numerous theories and hypotheses proposed to replace it.
 One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham [@Haidt2007].
-While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related issue, the Moral Foundations Dictionary (MFD) [@Graham2009].@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
+While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related measurement issue, the Moral Foundations Dictionary (MFD) [@Graham2009].
+@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
 Here we first review evidence and criticisms against this assumption.
@@
 
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007].
-The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
+Haidt and Jesse (2007) formulated MFT as a method by which to capture the entirety of humans' moral domain.
+We argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals.
 In other words, moral psychology ignored the valid moral foundations of conservatives.
-Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
-
-In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
+MFT holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
+
+In order to capture language's role in moral and political reasoning, @Graham2009 formulated the MFD in order to capture moral reasoning and justification as used in speech and text.
 The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
 @Graham2009 created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-
-Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
+Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from we' initial list.
+
+Similar to previous research on MFT, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
 Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers.
@@
 
-Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
+MFT has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
 @Suhler2011 criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
 Likewise, @Gray2015 argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
-@Schien2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
-
-Beyond the critiques of the theory itself, many have also provided strong critiques of the Moral Foundations Dictionary (MFD).Conducting two close conceptual replication and six extension studies, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.In a meta-analysis, the theorized differences were only found for authority and purity (e.g.
-conservatives used more authority and purity word).
-Loyalty was contrary to theoretical predictions (e.g.
-used more by liberals), and no differences were found for harm and fairness.Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
-Exploring the political Twitterverse, @Sterling2018 found differences in the MFD to depend on political sophistication.
+@Schein2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
+
+Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.Conducting two close conceptual replication and six extension studies, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.
+In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
+Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
+Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
+Exploring the political Twitterverse, @Sterling2018 found differences in the MFD depend on political sophistication.
 For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
-While the MFD has not been extensive used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
-
-The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).These attempts generally fall into two categories: human annotations and semantic representations.
+While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
+
+The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).
+These attempts generally fall into two categories: human annotations and semantic representations.
 @Hopp2021 represents the first approach where instead of relying on 'experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
@@
 @Garten2016 represents the second categories which instead relies on data-driven semantic analysis.
-Using shallow learning models like word2vec, moral foundations are measured using semantic similarity vectors rather than simple word counts.
-
-As a further conceptual replication of @Frimer2020, here we test the liberal-conservative difference proposed by MFT using partisan media content and the Moral Foundations Dictionary.
-We first test differences in a general news corpus compared liberal sources (NPR and New York Times) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavaugh's Supreme Court nomination and the Government Shutdown in 2018-19.
-Here the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
+Using shallow neural net models like word2vec [@mikolov_efficient_2013], moral foundations were measured using semantic similarity vectors rather than simple word counts.
+
+As a further conceptual replication of @Frimer2020, we test the liberal-conservative difference proposed by MFT using partisan media content and the MFD.
+We first test differences in a general news corpus compared liberal sources (National Public Radio [NPR] and the New York Times [NYT]) to conservative sources (Fox News and Breitbart).
+Second, we examined news about specific political events: Brett Kavaugh's U.S.
+Supreme Court nomination and the U.S.
+Government Shutdown in 2018-2019.
+In the second experiment, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
 To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
@@
 
-For Experiment 1, the researchers approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
-Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
-Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
+For Experiment 1, we approached the study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
+We hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
+Additionally, we hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
 
@@
 news sources, a process known as web scraping.
-The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
+The sources were *NYT*, *NPR*, *Fox News*, and *Breitbart*.
 They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean.
+We determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
+In general, the *NYT* and *NPR* are preferred by consumers reporting a liberal bias or lean.
 In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean.
-@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
+@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
 
@@
 Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
+While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from the *NYT* and *Breitbart*.
 Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
@@
 
-Concurrent research by @Jordan2019 is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
+Concurrent research by @Jordan2019 assesses the validity of both the MFQ and the MFD through a multi-trait multi-method analysis of the two instruments using multiple samples.
 The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
+We were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
 Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
@@
 final = na.omit(final) #one weird NA line
-
-##load libraries
-library(tm)
-library(ngram)
 
@@
 
-library(quanteda)
-
 final$FK = NA
@@
           escape = F,
-          align = c("l", rep("c", 6))
+          align = c("l", rep("c", 6)), 
+          font_size = 'footnotesize',
+          placement = 'pt'
           )
@@
 
-The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
+We calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
 Statistics calculated included average *z*-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
@@
 Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage [@Kincaid1975].
-For example, a text with a readability score of 11 should be easily read by a high school junior.
+The obtained value is intended to match up with the U.S.
+grade level at which one should be able to comfortably read the passage [@Kincaid1975].
+For example, a text with a readability score of 11 should be easily read by a U.S.
+high school junior.
 
@@
 The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
-*The New York Times* published the greatest number of articles as well as total words.
+*NYT* published the greatest number of articles as well as total words.
 *Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
@@
 Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* articles had the lowest reading grade level on average, while *The New York Times* had the highest.
-This result might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
+Finally, *Fox News* articles had the lowest reading grade level on average, while *NYT* had the highest.
+This result might be attributable to the greater number of tokens in the average *NYT* article compared to *Fox News*.
 The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
@@
 Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
+Based on the weighted percent values for the five foundations, we observed that MFD words seem to make up a small portion of the article text.
 Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
@@
           escape = F,
-          align = c("l", rep("c", 7))
+          align = c("l", rep("c", 7)),
+          font_size = 'footnotesize',
+          placement = 'pt'
           )
@@
 ```{r conference-pic, eval = F, include = F}
-library(ggplot2)
-library(reshape)
-
 cleanup = theme(panel.grid.major = element_blank(), 
@@
 
-The results obtained in Experiment 1 fail to support the differences predicted by Moral Foundations Theory.
-First, differences between liberal and conservative news sources failed to reach statistically significance for any foundations.
+The results obtained in Experiment 1 fail to support the differences predicted by MFT.
+First, differences between liberal and conservative news sources failed to reach statistical or practical (effect size) significance for any foundations.
 Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
 Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
-Overall, the results lend strong support to the case against the Moral Foundations Dictionary and weakens the case generally for Moral Foundations Theory.
-
-However,one possible limitation of the current data is the general-ness of the corpus.
+Overall, the results lend strong support to the case against the MFD and weakens the case generally for MFT.
+
+However, one possible limitation of the current data is the generalness of the corpus.
 The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
@@
 Second, we chose to focus  data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court and the government shutdown in December 2018 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Experiment 2 is the best test of the Moral Foundations theory and dictionary in the context of partisan news.
+Supreme Court and the U.S.
+government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
+Hence, Experiment 2 is the best test of the MFT and the MFD in the context of partisan news.
 
@@
 
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+In contrast to Experiment 1, we approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For Experiment 2, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-Once again, no human participants were needed for this study, so no Institutional Review Board approval was necessary.
+We tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, we analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
+The content will be analyzed for valence and moral alignment under MFT.
 
@@
 
-````{r NPR_kav, eval = F, include = F}
+```{r NPR_kav, eval = F, include = F}
 library(rvest)
@@
 
-````{r Slate_kav, eval = F, include = F}
+```{r Slate_kav, eval = F, include = F}
 library(rvest)
@@
 
-````{r HuffPo_kav, eval = F, include = F}
+```{r HuffPo_kav, eval = F, include = F}
 library(rvest)
@@
 
-````{r Politico_kav, eval = F, include = F}
+```{r Politico_kav, eval = F, include = F}
 library(rvest)
@@
 
-````{r Fox_kav, eval = F, include = F}
+```{r Fox_kav, eval = F, include = F}
 
@@
 
-````{r Breitbart_kav, eval = F, include = F}
+```{r Breitbart_kav, eval = F, include = F}
 library(rvest)
@@
 
-````{r Rush_kav, eval = F, include = F}
+```{r Rush_kav, eval = F, include = F}
 library(rvest)
@@
 
-````{r Blaze_kav, eval = F, include = F}
+```{r Blaze_kav, eval = F, include = F}
 url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
@@
 As in Experiment 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by the highest proportion of consistent liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
+The sources favored by the highest proportion of consistent liberals were the *NYT*, *NPR*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
 The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts, again written with the *papaja* library in *R*, are provided inline with this manuscript [@Aust2017].
 
@@
 
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset [@Wickham2016].
+Using the *rvest* and *RSelenium* libraries, we pulled body text for individual articles from each of the aforementioned 10 news sources and compiled them together [@Wickham2016; @harrison_rselenium_2020].
 Using this dataset, we identified word count and average word count per source.
@@
 The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
+Once again, we elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
 
@@
 
-As in Experiment 1, the text was scanned with *ngram*.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed [@Schmidt2017].
+As in Experiment 1, the text was scanned with *ngram* [@Schmidt2017].
+Again, blank articles, text from the Disqus system, and duplicate articles were removed.
 The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017].
-Words were subsequently matched with their valences from @Warriner2013.
-Depending on the results of @Jordan2019's multi-trait multi-method analysis of the MFD and the Moral Foundations Questionnaire, alternative forms of the Moral Foundations Dictionary with additional words may be imported instead of the original dictionary.
-
-Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@Feinerer2017].
 Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).
 Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurrence in the text.
+We obtained the words' percent occurrence in the text.
 Percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
@@
 
-The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
+We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
 As in Experiment 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
@@
           small = T,
-          align = c("l", rep("c", 6))
+          align = c("l", rep("c", 6)),
+          font_size = 'footnotesize',
+          placement = 'pt'
           )
@@
           small = T, 
-          align = c("l", rep("c", 6))
+          align = c("l", rep("c", 6)),
+          font_size = 'footnotesize',
+          placement = 'pt'
           )
@@
 
-To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
-The researchers used the *nlme* library in *R* [@Pinheiro2017].
+We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Experiment 1.
 Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
@@
 
-The results obtained in Experiment 2 are slightly more in line with expectations from Moral Foundations Theory, however, in all but one case, the differences were not statistically significant.
+The results obtained in Experiment 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
 The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given @Graham2009.
-Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the effects much smaller than reported in @Graham2009.
+Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the practical effects much smaller than reported in @Graham2009.
 While not significant, fairness was endorsed more by conservatives in both cases.
-Contradictorily, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
-
-Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by Moral Foundations Theory.
+In contrast, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
+
+Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
 One issue that Experiment 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
@@
 
-Within the theoretical framework of Moral Foundations Theory [@Haidt2007], we attempted to devise a method leveraging the Moral Foundations Dictionary [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
+Within the theoretical framework of MFT [@Haidt2007], we attempted to devise a method leveraging the MFD [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
 In Experiment 1,the results obtained were not significant in any statistical or practical sense.
@@
 In Experiment 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
-Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of Moral Foundations Theory in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive, the researchers still retain confidence in the overall structure of the methodology established in the current study.
+Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
+
+Despite the fact the results regarding political bias were inconclusive, we still retain confidence in the overall structure of the methodology established in the current study.
 Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
+We implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
 This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
@@
 However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
-As mentioned before, MFD is a measure developed from Moral Foundations Theory [@Graham2009].
+As mentioned before, MFD is a measure developed from MFT [@Graham2009].
 Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
@@
 
-In critiquing Moral Foundations Theory, @Schien2015 proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
-Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else [@Gray2014, @Schien2015].
+In critiquing MFT, @Schein2015 proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
+Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else [@Gray2014, @Schein2015].
 Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
@@
 The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
-Likewise, there are several approaches to analyzing such data, including linear models (like multi-level models) and network-style models such as latent semantic analysis [@Landauer1998].
+Likewise, there are several approaches to analyzing such data, including linear models (like multilevel models) and network-style models such as latent semantic analysis [@Landauer1998].
 Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
@@
 Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
-
-\newpage
-
-# Appendix
-
-```{r appendix_mfd, results = 'asis', echo = FALSE, message = F}
-orig_mfd = read.csv("../exp1_data/original_mfd.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-####build the table here####
-tableprint = matrix(NA, nrow=length(orig_mfd), ncol=5)
-colnames(tableprint) = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity")
-
-#tableprint[ , 1] = unique(final_gs$Source)
-#tableprint[ , 1] = orig_mfd[,1]
-#tableprint[ , 2] = orig_mfd[,2]
-#tableprint[ , 3] = orig_mfd[,3]
-#tableprint[ , 4] = orig_mfd[,4]
-#tableprint[ , 5] = orig_mfd[,5]
-
-tableprint = tableprint[c(1,2,3,4,5)]
-tableprint = orig_mfd
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Original Moral Foundations Dictionary from Graham et al. (2009)",
-          caption = "Moral Foundations Dictionary", 
-          col.names = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity"),
-          format = "latex",
-          escape = F,
-          small = T, 
-          align = c("l", rep("c", 6))
-          )
-```

### 2022-03-03 manuscript_version/manuscript_metapsych.tex
fixing the manuscript issues

--- 2020-08-04 thesis/pilot_manuscript.tex
@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
 \PassOptionsToPackage{hyphens}{url}
 %
-\documentclass[english,,man]{apa6}
+\documentclass[
+  english,
+  man]{apa6}
+\title{Moral Foundations of U.S. Political News Organizations}
+\author{William E. Padfield\textsuperscript{1}, Erin M. Buchanan, Ph.D.\textsuperscript{2}, \& Kayla N. Jordan, Ph.D.\textsuperscript{2}}
+\date{}
+
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
   \IfFileExists{parskip.sty}{%
@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
   pdftitle={Moral Foundations of U.S. Political News Organizations},
-            pdfauthor={William E. Padfield1 \& Erin M. Buchanan, Ph.D.2},
+  pdfauthor={William E. Padfield1, Erin M. Buchanan, Ph.D.2, \& Kayla N. Jordan, Ph.D.2},
+  pdflang={en-EN},
   pdfkeywords={politics, morality, psycholinguistics},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{graphicx}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 \usepackage{csquotes}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+\ifXeTeX
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 \fi
-
-\title{Moral Foundations of U.S. Political News Organizations}
-\author{William E. Padfield\textsuperscript{1} \& Erin M. Buchanan, Ph.D.\textsuperscript{2}}
-\date{}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+
+\authornote{
+
+William Padfield completed this project as part of his thesis requirements for a master's degree candidate in Psychology at Missouri State University.
+Submitted to Meta-Psychology.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+The full editorial process of all articles under review at Meta-Psychology can be found following this link: \url{https://tinyurl.com/mp-submissions}
+
+Correspondence concerning this article should be addressed to William E.
+Padfield, 901 S.
+National Ave, Springfield, MO, 65897.
+E-mail: \href{mailto:wpadfield@gmail.com}{\nolinkurl{wpadfield@gmail.com}}
+
+}
 
@@
 \abstract{
-The media ecosystem has grown, and political opinions have diverged such that there are competing conceptions of objective truth.
-Commentators often point to political biases in news coverage as a catalyst for this political divide.
-The Moral Foundations Dictionary (MFD) facilitates identification of ideological leanings in text through frequency of the occurrence of certain words.
-Through web scraping, the researchers extracted articles from popular news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+Partisan differences and diviseness have become an increasing hot topic in psychological research.
+Many theories have been proposed to explain these differences and divisions including Moral Foundations Theory.
+The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
+Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, the researchers gathered political articles from four sources.
-We were unable to reveal significant differences in moral or political endorsements, but we solidified the method to be employed in further research.
-In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Experiment 1, we gathered political articles from four sources.
+We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
+In Experiment 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
 Government Shutdown of 2018-2019.
-Once again, no significant differences in moral or political endorsements were found.
+Once again, no significant differences in moral endorsements were found.
+Together with past work, the results shed doubt on the validity of the MFD as a reliable measurement tool.
 }
@@
 
-In the United States, today's media landscape affords consumers a multitude of options for obtaining political news.
-Since the advent of cable news networks and the World Wide Web in the last decades of the twentieth century, consumers have gained access to an ever-expanding menagerie of news sources, many of which can be called up via a simple click, touch, or swipe.
-Concurrent with this growth in available news sources, concerns regarding political bias in news reporting have entered public consciousness.
-For example, commentators argue that networks including Fox News Channel and MSNBC communicate political news from a conservative and liberal slant, respectively.
-These purported biases have been a cause for concern given the potential for incomplete or inaccurate news reporting potentially resulting from these biases.
-Given the inherently moral nature of many political arguments and positions, bias in news reporting might manifest as differing moral appeals.
-Specifically, the use of differing moral language in political articles might be an indicator of political bias in news media.
-
-Morality and ethics have been of interest to thinkers, academics, and philosophers since antiquity.
-Starting chiefly in the twentieth century, a scientific approach to humans' understanding of morality emerged under the domain of psychology.
-Theories attempting to explain the development and application of people's moral intuitions built the foundation for the subfield of moral psychology.
-As the field developed, however, considerable debate has taken place regarding operational definitions of \enquote{morality.} Concerns regarding operationalization remain an issue in the field in the twenty-first century as researchers attempt to infer moral and political leanings from text and speech.
-
-\hypertarget{moral-foundations-theory}{%
-\subsection{Moral Foundations Theory}\label{moral-foundations-theory}}
-
-As a discipline, modern moral psychology started in the late 1960s with Lawrence Kohlberg (Haidt \& Graham, 2007).
-Kohlberg's research popularized his theory of the development of moral reasoning.
-This theory establishes the steps of moral reasoning through which humans proceed as their cognitive structures assume higher levels of sophistication and nuance (Kohlberg \& Hersh, 1977).
-Kohlberg borrowed from Jean Piaget's stages of cognitive development in which children progress from the sensorimotor through to the formal operations stage.
-Similarly, Kohlberg found people typically start with a \enquote{pre-conventional} understanding of morality during infancy in which children understand \enquote{right} and \enquote{wrong} purely in terms of how they interact with resultant experiences of rewards and punishment.
-Typically, people progress through several steps until they reach a \enquote{post-conventional} ethics.
-People who have reached the post-conventional stage are said to be able to weigh competing abstractions and reason their way to a conclusion that promotes justice based upon their \enquote{self-chosen ethical principles} (Kohlberg \& Hersh, 1977).
-From Kohlberg's perspective, issues of justice and fairness comprise the foundation of morality (Haidt \& Graham, 2007).
-This view persisted until it encountered criticism in the early 1980s.
-
-Kohlberg's conception of morality faced major scrutiny from psychologist Carol Gilligan.
-In 1982, Gilligan criticized Kohlberg's theory on the grounds that it focused solely on the moral concerns of men, and that it ignored those of women (Haidt \& Graham, 2007).
-Gilligan drew attention to purported differences in the ways men and women are taught to relate to self and others.
-She offered a historic argument contending women have traditionally filled roles related to caring and nurturing.
-She pushes back against Kohlberg's assumption that moral development replaces \enquote{rule of brute force,} as enforced by men, with the justice-based \enquote{rule of law.} According to Gilligan, this assumption implies women are less morally developed, owing to their absence both in masculine displays of violence as well as in enforcement of the law (Gilligan, 1982).
-Gilligan argues for the existence of a distinct, but equal development process that women and girls must undergo in order to develop their moral selves.
-Stark differences in the ways women are traditionally taught to interact with their social world cause them to develop ethical systems based upon their non-aggressive relationships with others.
-Gilligan thus asserted morality was built upon an alternative moral foundation: caring (Gilligan, 1982).
-This debate between competing conceptions of morality did not resolve until Gilligan and Kohlberg conceded the existence of two moral foundations: justice and caring (Haidt \& Graham, 2007).
-While this new direction in moral psychology appeared to represent a more inclusive outlook on the construct, these novel ideas would soon be challenged on the grounds of its apparent western-centric outlook.
-
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain (Haidt \& Graham, 2007).
-The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals (Haidt \& Graham, 2007).
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007).
-
-In their brief overview of the history of moral psychology, Graham, Haidt, and Nosek (2009) explained Shweder, Much, Mahapatra, and Park's objections to moral psychology as it stood in the late 1980s.
-Their criticism centered on the fact moral psychology concerned itself with issues regarding justice and individuals' rights.
-Such a system, they argued, did not account for moral concerns outside of the western world (Graham et al., 2009).
-Individually focused concerns can be grouped under an overarching \enquote{ethic of autonomy,} which was thought to be one of three ethics upon which humans base moral decisions.
-The other two ethics were the \enquote{ethic of community} (comprising one's duty to their family, tribe, etc.), and the \enquote{ethic of divinity} - representing one's duty not to defile their God-given body and soul (Graham et al., 2009).
-In the 2000s, Haidt and Graham (2007) took this line of reasoning further in their assertion that moral psychology favored certain political ideologies over others.
-
-Haidt and Graham settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology (Graham et al., 2011).
-The researchers attempted to locate virtues and morals corresponding to \enquote{evolutionary thinking.} For instance, the researchers cited Mauss' work on reciprocal gift-giving, which informed the establishment of the \emph{fairness/reciprocity} foundation.
-Additionally, evolutionary literature on disgust and its correlation to human behavior regarding food and sex informed the \emph{purity/sanctity} foundation (Graham et al., 2011).
-The researchers identified the five \enquote{top candidates} for the foundations of human cultures' morality (Graham et al., 2011).
-
-The first two foundations (\emph{harm/care} and \emph{fairness/reciprocity}) are termed the \enquote{individualizing foundations,} as they are centered on the concerns of individuals rather than groups.
-\emph{harm/care} represents an endorsement of compassion and kindness, while opposing cruelty and harm.
-\emph{Fairness/reciprocity} represents concerns centered on guaranteeing individual rights as well as justice and equality among all people.
-The other three foundations (\emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}) are the \enquote{binding} foundations, owing to their focus on group-related concerns, rather than those of individuals.
-\emph{Ingroup/loyalty} represents endorsements of patriotism and heroism and discourages nonconformity and dissent.
-\emph{Authority/respect} represents an endorsement of social hierarchies and traditions while denigrating disobedience.
-Finally, \emph{purity/sanctity} represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony (Haidt \& Graham, 2007).
-Liberals tend to endorse the individualizing foundations more than conservatives.
-Conservatives, on the other hand, tend to endorse the binding foundations more than liberals.
-It should be noted, however, conservatives also tend to endorse all five foundations equally, implying they base moral judgments on all foundations (Graham et al., 2009).
-
-Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-Suhler, Churchland, and Joseph (2011) list several potential weaknesses of MFT that they argue might threaten the theory's validity.
-First, the authors challenge Haidt and Graham (2007)'s claims the moral intuitions represented by MFT are innate and modular.
-Suhler et al.
-(2011) claim that advances in biological sciences (embryology and microbiology, specifically) make it more difficult for researchers to claim any one trait is either innate or learned through experience.
-Rather, behaviors likely result from interactions between genetics and experience (Suhler et al., 2011).
-According to the authors, without solid data supporting the innateness of moral foundations, Haidt and Graham have little from which to make such a claim.
-Similarly, Haidt and Graham (2007) rely on evidence authored by evolutionary psychologists to make a \enquote{strong modularity claim} (Suhler et al., 2011).
-However, as with innateness, there is little neurobiological evidence to support modularity.
-
-Suhler et al.
-(2011) also criticized the content and taxonomy of the five foundations.
-The authors criticize Haidt and Graham (2007)'s omissions of additional foundations, including \emph{industry} and \emph{modesty}, claiming these concepts are moralized in many societies worldwide.
-Likewise, the authors question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-For example, Suhler et al.
-(2011) posit that \emph{ingroup/loyalty} is merely a group-focused version of \emph{harm/care}.
-Work by Graham et al.
-(2011) might serve to rebut this criticism, as the researchers found their original five-factor structure seemed to best fit the data when validating the Moral Foundations Questionnaire.
-Finally, Suhler et al.
-(2011) point out that particular concepts related to a foundation, including \enquote{anger} in \emph{fairness/reciprocity} and \enquote{deception} in \emph{ingroup/loyalty}, could be ascribed to any of the other foundations as well.
-In other words, it becomes difficult to recognize a particular concept as indicative of any one foundation when, in theory, they could be applied to all five (Haidt \& Graham, 2007; Suhler et al., 2011).
-
-These criticisms of Moral Foundations Theory are valid and should be taken into consideration when conducting research with instruments derived from MFT.
-Such criticisms are especially valid when considered alongside questions about the Moral Foundations Dictionary in particular.
-Nevertheless, there exists compelling evidence supporting the validity of Moral Foundations Theory, albeit regarding its application solely through the Moral Foundations Questionnaire.
-This evidence is discussed within a brief explanation of the Moral Foundations Questionnaire and its relationship to the Moral Foundations Dictionary in the next section.
+The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development (Kohlberg \& Hersh, 1977).
+Since then, Kohlberg's theory has been highly criticized with numerous theories and hypotheses proposed to replace it.
+One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham (Haidt \& Graham, 2007).
+While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related measurement issue, the Moral Foundations Dictionary (MFD) (Graham, Haidt, \& Nosek, 2009).
+Graham et al.
+(2009) developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
+Here we first review evidence and criticisms against this assumption.
+We then provide our own test of the MFD using partisan news articles.
 
@@
 
+Haidt and Jesse (2007) formulated MFT as a method by which to capture the entirety of humans' moral domain.
+We argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals.
+In other words, moral psychology ignored the valid moral foundations of conservatives.
+MFT holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007).
+
 In order to capture language's role in moral and political reasoning, Graham et al.
-(2009) formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
+(2009) formulated the MFD in order to capture moral reasoning and justification as used in speech and text.
 The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
@@
 (2009) created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count (LIWC; Pennebaker, Booth, \& Frances, 2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-Graham et al.
-(2009) manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons, as word frequency analysis ignores sentence context.
-The researchers offered the following example from a Unitarian sermon as a demonstration of ambiguous statements requiring human verification: \enquote{Don't let some self-interested ecclesiastical or government authority tell you what to believe, but read the Bible with your own eyes and open your heart directly to Jesus} (Graham et al., 2009).
-This sentence added to the \emph{authority/respect} total in LIWC's analysis, but it appears to suggest that one should reject authority in this context.
-The researchers eliminated this sentence from the \emph{authority/respect} raw count on account of this discrepancy between the use of authority-related words and the speaker's clear intentions (Graham et al., 2009).
-The original Moral Foundations Dictionary can be found in the Appendix.
-
-Similar to previous research on Moral Foundations Theory, liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than conservative ministers.
+Then, using the Linguistic Inquiry and Word Count {[}LIWC; Pennebaker, Booth, and Frances (2007){]} computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from we' initial list.
+
+Similar to previous research on MFT, liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than conservative ministers.
 Conversely, conservative ministers used \emph{authority} and \emph{purity} words more often than liberal ministers.
@@
 
-To this point, most text analysis utilizing the Moral Foundations Dictionary operationalizes endorsement of any one of the foundations as percent occurrence of words in a given text from the foundation's respective word list.
-As such, most analyses assume that zero percent occurrence is indicative of no endorsement, while any non-zero percent occurrence indicates endorsement of the foundation.
-This operational definition may not be sufficient in describing the true nature of the writer or speaker's endorsement of one of the sets of moral intuitions.
-A quick glance at the MFD words for \emph{harm/care} reveals the presence of words that are more closely associated with universally accepted conceptions of \emph{harm} over \emph{care} and vice-versa (Graham et al., 2009).
-For example, the word \enquote{cruel} has relatively negative connotations compared to \enquote{benefit.} For the \emph{harm/care} foundation, it is conceivable that use of the word \enquote{cruel} might indicate a greater attentional focus of the idea of \emph{harm} rather than \emph{care}.
-
-For \emph{harm/care}, the definition of the foundation, as well as its name, clearly distinguishes between two somewhat opposite sides of an attentional continuum, with \emph{harm} on the negative end and \emph{care} on the positive side.
-In other words, the entries in the MFD for \emph{harm/care} have somewhat clear positive and negative valences.
-The same pattern can be seen in the MFD entries for the other four foundations.
-\emph{Purity/sanctity} features words that likely have a negative valence to most observers, including \enquote{disease} and \enquote{trash,} along with more positive words, including \enquote{right} and \enquote{sacred} (Graham et al., 2009).
-These dichotomies, however, bring up other questions regarding the definition and names of the other four foundations apart from \emph{harm/care}: \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}.
-The latter four foundations have names that are harder to understand as a valence continuum, as the concepts in the names are more similar, even to the point of being virtually synonymous in the case of \emph{fairness/reciprocity}.
-
-When considering the issue of positive versus negative valence in MFD words, the question of how texts are analyzed vis-a-vis the MFD remains.
-How can raw percentage of MFD word occurrence capture the valence and focus of the writer or speaker?
-If 2\% of a politician's speech features positive words (i.e., \enquote{benefit} and \enquote{defend}) from the MFD \emph{harm/care} list, how can researchers be sure the level and nature of the speaker's \enquote{endorsement} of the foundation equals that of another politician whose speech contained negatively connoted MFD words from the \emph{harm/care} list?
-They would have equal endorsements as far as the numbers are concerned, but the words used and focus given are on opposite sides of the \emph{harm/care} spectrum.
-
-This issue is compounded by the fact the Moral Foundations Questionnaire (MFQ) and its subscales assume endorsement lies on a continuum.
-The MFQ, which was developed subsequent to the MFD, measures individuals' endorsements of each of the foundations using a six-point scale (Graham et al., 2011).
-The questionnaire is made up of judgment items and relevance items.
-Judgment items are phrased such that the respondent signals their agreement or disagreement with straightforward statements.
-An example of such a statement reads: \enquote{It can never be right to kill another human being} (Graham et al., 2011).
-Relevance items gauge the respondent's opinion regarding the importance of foundation-related concerns.
-For example, the respondent is directed to rate how important the following situation is to their sense of morals: \enquote{whether or not someone did something disgusting.} This example measures the relevance of the \emph{purity/sanctity} foundations.
-Each foundation has a judgment and relevance subscale, totaling 10 subscales for the MFQ (Graham et al., 2011).
-
-The Moral Foundations Questionnaire has been validated by multiple researchers.
-Likewise, its five-factor structure has been demonstrated to fit data in multiple countries (Davies, Sibley, \& Liu, 2014; Graham et al., 2011).
-In their article introducing the 30-item MFQ, Graham et al.
-(2011) conducted an exploratory factor analysis (EFA) and found that a five-factor model fit the data better than a one, two, or three-factor model.
-Davies et al.
-(2014) conducted a confirmatory factor analysis (CFA) of the MFQ with a sample from New Zealand and likewise found the five-factor model provided the best fit.
-While Davies et al.
-(2014) concede the US and New Zealand share many similarities as Western nations, which could raise questions regarding the validity of the MFQ in non-Western nations.
-However, there are striking differences between the two countries, including the lack of a two-party political system in New Zealand, that provide grounds for claiming the MFQ generalizes beyond the United States.
-Furthermore, Graham et al.
-(2011) claim to find a \enquote{reasonable} degree of generalizability for the MFQ across participants from many different regions in the world.
-These two bodies of work also provide the best available evidence that the five moral foundations are sufficiently distinct from one another, though broader criticisms of MFT raised by Suhler et al.
-(2011) should still be taken into account in studies involving the theory.
-
-The aforementioned ambiguity of the Moral Foundations Dictionary as an instrument becomes clearer upon closer examination of the items in the Moral Foundations Questionnaire.
-One item under the \emph{fairness/reciprocity} judgment subscale reads, \enquote{Justice is the most important requirement for a society} (Graham et al., 2011).
-The survey respondent must select a number on a scale from 1 to 6 indicating responses spanning \enquote{strongly disagree} at 1 to \enquote{strongly agree} at 6.
-While the scales in the MFQ do not represent true valence as it pertains to individual words, it does allow for a greater degree of specificity in terms of an individual's endorsement of a particular moral foundation.
-When a respondent selects a 4 for the aforementioned MFQ statement, they clearly are indicating they \enquote{slightly agree} with the statement (Graham et al., 2011).
-This specificity is not present in most analyses involving the MFD and percent occurrence, unless they also take into account the valence of the words used in the text or speech of interest.
-
-\hypertarget{valence}{%
-\subsection{Valence}\label{valence}}
-
-Borrowing from Osgood's work in the 1950s, Bradley and Lang (1999) recognized valence as one of three related dimensions comprising emotion when developing their Affective Norms for English Words (ANEW).
-As mentioned before, \enquote{valence,} the first dimension, denotes the pleasantness of a given word.
-\enquote{Arousal,} the second dimension, describes the stimulating nature of a word.
-Lastly, \enquote{dominance} or \enquote{control} describes the extent to which a word makes one feel in or out of control (Bradley \& Lang, 1999).
-The researchers developed ANEW by presenting participants with a list of 100-150 words and asking for them to rate the word on all three dimensions using the Self-Assessment Manikin (SAM), which allows ratings along either a nine-point scale when using traditional paper instruments or a twenty-point scale when using a computerized version.
-
-Participants saw the stimulus word and responded on each scale.
-The valence scale featured a smiling figure at one end (representing pleasantness) and a frowning figure at the other end (for unpleasantness).
-The arousal scale had a \enquote{wide-eyed} figure at one end with a sleepy figure at the other, representing stimulating and unstimulating respectively.
-Finally, the dominance scale featured a large figure, indicating the highest degree of control, at one end and a small figure, indicating a lack of control, at the other end (Bradley \& Lang, 1999).
-The end result of this procedure yielded affective norms along the three dimensions for 1,040 English words (Bradley \& Lang, 1999).
-ANEW represented an important first step in establishing affective norms for large numbers of English words.
-However, later researchers found the 1,040-word list to be limiting for a language consisting of thousands of words.
-
-Warriner, Kuperman, and Brysbaert (2013) exponentially lengthened the list of words with affective norms to 13,915 English lemmas, the base forms of words without inflection (i.e., \enquote{watch} rather than \enquote{watched} and \enquote{watching}).
-The researchers recognized the importance of affective norms in several areas of study, including emotion, language processing, and memory (Warriner et al., 2013).
-They argue the list of words included in ANEW is sufficient for small-scale factorial research designs, but the list is \enquote{prohibitively small} for larger-scale \enquote{megastudies} that are common in psycholinguistic research today (Warriner et al., 2013).
-
-In order to source a large number of lemmas for affective ratings, the researchers drew from several validated sources.
-These include the 30,000 lemmas with age-of-acquisition (average age at which a particular word is learned) ratings gathered by Kuperman, Stadthagen-Gonzalez, and Brysbaert (2012) as well as the content lemmas from the SUBTLEX-US corpus consisting of subtitles from various forms of visual media (New, Brysbaert, Veronis, \& Pallier, 2007).
-This data collection resulted in the final list of 13,915 lemmas.
-Lists of 346-350 words were presented to participants recruited through the Amazon Mechanical Turk subject pool.
-Participants rated the words along one of the three dimensions, unlike the ANEW project in which participants rated each word along all three dimensions at once.
-The researchers used a nine-point scale similar to the one used by Bradley and Lang (1999) when collecting ratings for ANEW (Warriner et al., 2013).
-
-The researchers noted several points of interest upon observing ratings.
-First, they found that valence and dominance ratings had a negative skew, indicating more words elicited feelings of happiness and control than their respective opposites.
-Also, when examining the relationship between valence and arousal ratings, the researchers found a U-shaped relationship.
-This U-shape indicates words with high degrees of positivity and negativity elicited higher arousal (Warriner et al., 2013).
-These observations along with the now-greatly expanded list of affective norms has been applied to several lines of inquiry in psycholinguistics.
-
-Warriner and Kuperman (2015) utilized the new affective norms list in order to investigate the validity of the Pollyanna hypothesis, or the prevalence of a generally optimistic outlook in humans as reflected in language.
-The researchers were able to conclude the existence of a greater number of positive-valence English words in the list of 13,915 lemmas.
-Additionally, after observing token frequency in a number of text corpora, including SUBTLEX-US, the Corpus for Contemporary American English (COCA), the British National Corpus (BNC), Touchstone Applied Science Associates, Inc.~Corpus (TASA), and the corpus used for the Hyperspace Analogue to Language model (HAL), the researchers found that words with positive valence were also used more frequently (Warriner \& Kuperman, 2015).
-While the researchers concede the possibility of an acquiescence bias in ratings as a possible explanation for the observed positivity bias, this investigation represents one application of the Warriner et al.
-(2013) list in emotional studies.
-
-In addition to applications in emotion research, the Warriner et al.
-(2013) norms have been utilized in cognitive research as well.
-One cognition-based study investigates the relationship between emotion and response latencies in word recognition.
-Kuperman, Estes, Brysbaert, and Warriner (2014) sought to use these new norms to fill in the knowledge gaps regarding variance in word recognition.
-The researchers drew several conclusions regarding emotion and word recognition (specifically in naming and lexical decision tasks - two cognitive processing tasks wherein a participant has to read aloud or judge a word for its lexicality).
-First, Kuperman et al.
-(2014) found slower decision-making and reading times in negative-valence words, faster times in neutral words, and even faster times in words with positive valence.
-The researchers also concluded that words causing higher arousal tend to have slower decision times than less-arousing words.
-They found valence had a stronger effect on recognition than arousal (both effects were independent, not interactive).
-They found an interaction between emotion and word frequency such that valence and arousal are more effective on lower frequency words than high frequency words.
-Finally, Kuperman et al.
-(2014) found a greater effect of valence and arousal on response latency for lexical decision tasks than for naming tasks (Kuperman et al., 2014).
-This research serves as further evidence that the Warriner et al.
-(2013) list can be used for research inquiries both within and without the field of psycholinguistics.
-
-In the present studies, the researchers used the Warriner et al.
-(2013) list in order to denote the valence of the words appearing in the news articles scraped from the internet.
-Valence was considered as another independent variable and its relationship with the words comprising the Moral Foundations Dictionary were of chief interest to the researchers.
-The valence was used as a means to determine whether individual words in the MFD represented more positive aspects of their respective foundation or if they denoted a more negative aspect of the foundation.
-Specifically, valences were used to weight the MFD words by their relative degree of positivity or negativity.
-Incorporating word valence into a study involving the MFD is meant to alleviate some of the issues regarding the aforementioned ambiguity regarding the words in the Moral Foundations Dictionary.
-
-\hypertarget{news-media-and-politics}{%
-\subsection{News Media and Politics}\label{news-media-and-politics}}
-
-Research into politics, language, and media has illuminated the complex relationships between all three.
-Any politically-oriented discussion of word occurrence as an implication of moral or political position assumes that language and ideology are intrinsically linked.
-Deborah Cameron (2006) points out the expressive nature of ideological beliefs and how that expression is conveyed through language, thus implying a connection between ideology and language.
-She goes on to criticize the notion that language is either the \enquote{pre-existing raw material} used to shape ideologies or the \enquote{post-hoc vehicle} for their propagation.
-Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies (Cameron, 2006).
-Owing to the fact the Moral Foundations Dictionary was developed in order to assess the moral, which includes the ideological, orientation of discourse, its purported ability to assess parts of the structure of language (vocabulary) for ideological lean is of chief interest to the researchers in the present study.
-
-The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S., Druckman, Jacobs, and Ostermeier (2004) considered political \enquote{issues} as communication that attempts to persuade constituents to vote for the candidates based on their strengths in matters of public policy.
-According to the researchers, \enquote{image} priming describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality (Druckman et al., 2004).
-The researchers investigated political issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others.
-The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon.
-
-They linked the Nixon administration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign.
-Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence (Druckman et al., 2004).
-The researchers also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (e.g., priming) issues related to energy, defense, and the economy.
-This focus implies news media may contribute to Americans' perception of politicians based on where the media places emphasis.
-
-There is a potential caveat regarding the validity of Druckman et al.
-(2004)'s findings: reproductions of several studies purporting to demonstrate social priming effects have failed to replicate the original results.
-Pashler, Coburn, and Harris (2012) point out the distinction between perceptual and social (or goal) priming both in their operational definitions as well as their replicability.
-Perceptual priming often works through the inducement of a certain response from a related prime, as in, for example, semantic priming.
-Social (or goal) priming encompasses phenomena by which people exhibit complex behavioral changes subsequent to exposure to a prime.
-Pashler et al.
-(2012) point out well-known studies investigating social priming, including the use of elderly-related primes to induce slower walking speeds in participants.
-Studies investigating perceptual priming have been \enquote{directly replicated in hundreds of labs} (Pashler et al., 2012).
-This replication rate does not appear to be the case for social priming, as argued by Pashler et al.
-(2012).
-
-Pashler et al.
-(2012) noticed the unusually large effect size values (Cohen's \emph{d}) reported by researchers studying social priming effects.
-The researchers reproduced two studies from Williams and Bargh (2008) The first study attempted to prime participants by having them plot points on a Cartesian grid.
-The independent variable was priming condition and contained three levels: short, middle, and long distance.
-Those instructed to plot points further apart were hypothesized to express a higher degree of psychological distance regarding their family.
-The second study used the same priming conditions, but hypothesized that greater distance between points would prime participants to estimate fewer calories in unhealthy foods than those who were primed with shorter distances between points.
-Pashler et al.
-(2012) concluded those two studies from Williams and Bargh (2008) held little validity while also casting doubt on the prevalence of social priming effects themselves, based on the inability of other researchers to replicate previously reported effects in this area.
-
-While these concerns regarding the replication of social priming studies are valid and deserve further investigation, Druckman et al.
-(2004) does not purport to demonstrate a widespread effect of social priming on the American electorate.
-In other words, this research makes no claim to empirically supported priming effects.
-Rather, Druckman et al.
-(2004) chronicle the efforts on the part of the Nixon Administration to prop up the president's supposed strengths while downplaying his weaknesses.
-These tactics were deployed through the careful use of language in order to achieve the administration's political goals.
-As such, Druckman et al.
-(2004)'s research on Nixon serves as an example of language's potential utility in the propagation of desirable political opinions.
-The researcher's investigation of news media's focus on specific issues during the Carter Administration likewise provide an example of language as a potential conduit for the transfer of politically biased information.
-The idea that even 1970s news media could contain political biases is of particular interest to the current study, which investigates similar phenomena in contemporary news media.
-
-Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress (Clinton \& Enamorado, 2014).
-Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts.
-As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the researchers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival.
-The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election (Clinton \& Enamorado, 2014).
-
-Therefore, the current study sought to combine both methods related questions and extension/replication of previous moral foundation results found for liberal and conservative sources.
-First, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Second, these weighted percentages were examined for their differences in across liberal and conservative news sources.
+\hypertarget{critiques-of-moral-foundations}{%
+\subsection{Critiques of Moral Foundations}\label{critiques-of-moral-foundations}}
+
+MFT has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
+Suhler, Churchland, and Joseph (2011) criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
+Likewise, Gray and Keeney (2015) argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
+Schein and Gray (2015) argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
+
+Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.Conducting two close conceptual replication and six extension studies, Frimer (2020) found that the liberal-conservative differences found in the original study replicated in only 30\% of cases and the effect sizes were over 30 times smaller than reported in Graham et al.
+(2009).
+In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
+Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
+Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
+Exploring the political Twitterverse, Sterling and Jost (2018) found differences in the MFD depend on political sophistication.
+For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
+While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT (Clifford \& Jerit, 2013; Frimer, Tell, \& Haidt, 2015; Sagi \& Dehghani, 2014).
+
+The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).
+These attempts generally fall into two categories: human annotations and semantic representations.
+Hopp, Fisher, Cornell, Huskey, and Weber (2021) represents the first approach where instead of relying on `experts,' a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
+While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
+Garten, Boghrati, Hoover, Johnson, and Dehghani (2016) represents the second categories which instead relies on data-driven semantic analysis.
+Using shallow neural net models like word2vec (Mikolov, Chen, Corrado, \& Dean, 2013), moral foundations were measured using semantic similarity vectors rather than simple word counts.
+
+As a further conceptual replication of Frimer (2020), we test the liberal-conservative difference proposed by MFT using partisan media content and the MFD.
+We first test differences in a general news corpus compared liberal sources (National Public Radio {[}NPR{]} and the New York Times {[}NYT{]}) to conservative sources (Fox News and Breitbart).
+Second, we examined news about specific political events: Brett Kavaugh's U.S.
+Supreme Court nomination and the U.S.
+Government Shutdown in 2018-2019.
+In the second experiment, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
+To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
+Like Frimer (2020), results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.
 
@@
 
-For Experiment 1, the researchers approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources generally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
-Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
-Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
+For Experiment 1, we approached the study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
+We hypothesized the news sources generally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
+Additionally, we hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
 
@@
 news sources, a process known as web scraping.
-The sources were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Fox News}, and \emph{Breitbart}.
+The sources were \emph{NYT}, \emph{NPR}, \emph{Fox News}, and \emph{Breitbart}.
 They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-The researchers determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, \emph{The New York Times} and \emph{NPR} are preferred by consumers reporting a liberal bias or lean.
+We determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
+In general, the \emph{NYT} and \emph{NPR} are preferred by consumers reporting a liberal bias or lean.
 In contrast, \emph{Fox News} and \emph{Breitbart} are believed to have a conservative bias or lean.
 Mitchell et al.
-(2014)'s article presented political ideology as a scale ranging from \enquote{consistently liberal} to \enquote{consistently conservative.} In between these extremes lie more moderate positions, including \enquote{mostly liberal,} \enquote{mixed,} and \enquote{mostly conservative.} Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either \enquote{liberal} and \enquote{conservative} in order to form a basis for comparison.
+(2014)'s article presented political ideology as a scale ranging from ``consistently liberal'' to ``consistently conservative.'' In between these extremes lie more moderate positions, including ``mostly liberal,'' ``mixed,'' and ``mostly conservative.'' Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either ``liberal'' and ``conservative'' in order to form a basis for comparison.
 
@@
 Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not growing at a similar pace as those from \emph{The New York Times} and \emph{Breitbart}.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content \enquote{archive.} The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
+While in the multi-week process of scraping articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not growing at a similar pace as those from the \emph{NYT} and \emph{Breitbart}.
+Upon investigation, we found another, more robust URL for political content from NPR: their politics content ``archive.'' The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
 Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
@@
 The individual words were then reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}).
-The same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
+The same procedure was applied to the MFD words and the words in the Warriner, Kuperman, and Brysbaert (2013) dataset.
 Using the Warriner et al.
@@
 
-Concurrent research by Jordan, Buchanan, and Padfield (2019) is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
+Concurrent research by Jordan, Buchanan, and Padfield (2019) assesses the validity of both the MFQ and the MFD through a multi-trait multi-method analysis of the two instruments using multiple samples.
 The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
+We were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
 Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
@@
 
-\begin{table}[tbp]
+\begin{table}[pt]
 
@@
 \caption{\label{tab:exp1-source-descriptives}Experiment 1 - Descriptive Statistics by Source}
+
+\footnotesize{
 
@@
 \midrule
-NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.29 & 13.81 & 3.93\\
-New York Times & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.33 & 3.30\\
-Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.36 & 120.76 & 18.43 & 8.02\\
-Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.57 & 189.00 & 16.93 & 7.17\\
+NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.28 & 14.00 & 3.93\\
+New York Times & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.42 & 3.36\\
+Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.35 & 120.75 & 18.57 & 7.89\\
+Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.56 & 189.00 & 17.25 & 7.21\\
 \bottomrule
@@
 \end{tabular}
+
+}
 
@@
 
-The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
+We calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
 Statistics calculated included average \emph{z}-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
@@
 Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage (Kincaid et al., 1975).
-For example, a text with a readability score of 11 should be easily read by a high school junior.
+The obtained value is intended to match up with the U.S.
+grade level at which one should be able to comfortably read the passage (Kincaid et al., 1975).
+For example, a text with a readability score of 11 should be easily read by a U.S.
+high school junior.
 
@@
 The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
-\emph{The New York Times} published the greatest number of articles as well as total words.
+\emph{NYT} published the greatest number of articles as well as total words.
 \emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
@@
 Once again the standard deviations call into question any apparent differences between sources.
-Finally, \emph{Fox News} articles had the lowest reading grade level on average, while \emph{The New York Times} had the highest.
-This result might be attributable to the greater number of tokens in the average \emph{New York Times} article compared to \emph{Fox News}.
+Finally, \emph{Fox News} articles had the lowest reading grade level on average, while \emph{NYT} had the highest.
+This result might be attributable to the greater number of tokens in the average \emph{NYT} article compared to \emph{Fox News}.
 The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
@@
 Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
+Based on the weighted percent values for the five foundations, we observed that MFD words seem to make up a small portion of the article text.
 Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
 
-\begin{table}[tbp]
+\begin{table}[pt]
 
@@
 \caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
+
+\footnotesize{
 
@@
 \midrule
-Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .850 & 0.01\\
-Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .715 & 0.02\\
-Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .789 & -0.04\\
-Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.17 & .087 & -0.20\\
-Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.37 & .141 & -0.09\\
+Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .851 & 0.01\\
+Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .713 & 0.02\\
+Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .793 & -0.04\\
+Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.16 & .087 & -0.20\\
+Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.38 & .140 & -0.09\\
 \bottomrule
@@
 
+}
+
 \begin{tablenotes}[para]
@@
 
-The results obtained in Experiment 1 did not confirm the hypothesis.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The strongest effect found was for the \emph{authority/respect} foundation owing to the fact its Cohen's \emph{d} value was greater than the other four foundations.
-However, the effect was in the opposite direction of that which was hypothesized.
-Specifically, the results indicated that liberal leaning sources demonstrated higher positivity regarding that foundation than conservatives.
-This result is contrary not only to the research hypothesis for Experiment 1 but also to previous findings in Moral Foundations Theory research.
-It should be noted, however, the effect size was small and the relationship was not found to be statistically significant.
-
-Upon speculation, the researchers identified one possible reason for why the results were unable to confirm the hypothesis.
-The selection of the broad and amorphous topic of \enquote{political news} may have led to the scraping of large numbers of articles with little to no moral-centric content.
-Rather, many articles may have been, for example, simple reporting on congressional procedures that would leave little room for the use of moral language here, let alone words from the Moral Foundations Dictionary.
-In short, the range of topics covered in Experiment 1 was likely too broad.
-The possibility exists that a tighter focus on one political issue or event, especially one that (on the surface) has a stronger relationship with morality might be more illuminating for research in moral language in news media.
-
-Owing to the exploratory nature of Experiment 1, the researchers were afforded the opportunity to consider changes to the method to be utilized in Experiment 2.
-Generally speaking, the researchers believe their methodology to be sound.
-Web scraping methods and text processing remain viable methods for collecting large amounts of text and subsequently rendering that text in a form suitable for data analysis.
-Experiment 1 also demonstrated a method by which to address inherent problems in the Moral Foundations Dictionary relating to valence.
-The solution provided in Experiment 1 appears to provide insights into the MFD words where none previously existed.
-Finally, calculating weighted percentages and sums for each moral foundation provides an easily interpreted summary of MFD word positivity and occurrence.
-
-While the methodology used in Experiment 1 features many strengths, there are aspects which could be strengthened for future studies.
-The researchers identified two such changes that were subsequently employed in Experiment 2.
-First, the researchers elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, the researchers chose to focus their data collection efforts exclusively on one event in U.S.
-politics: the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court.
-In Experiment 2, the researchers sought to confirm the usefulness and validity of the method as well as test a similar hypothesis as Experiment 1.
+The results obtained in Experiment 1 fail to support the differences predicted by MFT.
+First, differences between liberal and conservative news sources failed to reach statistical or practical (effect size) significance for any foundations.
+Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
+Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
+Overall, the results lend strong support to the case against the MFD and weakens the case generally for MFT.
+
+However, one possible limitation of the current data is the generalness of the corpus.
+The selection of the broad and amorphous topic of ``political news'' may have led to the scraping of large numbers of articles with little to no moral-centric content.
+To address this limitation, two changes that were subsequently employed in Experiment 2.
+First, we elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
+Second, we chose to focus data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
+Supreme Court and the U.S.
+government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
+Hence, Experiment 2 is the best test of the MFT and the MFD in the context of partisan news.
 
@@
 
-\hypertarget{kavanaugh-supreme-court-hearing}{%
-\subsection{Kavanaugh Supreme Court Hearing}\label{kavanaugh-supreme-court-hearing}}
-
-In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice.
-Kavanaugh was previously on the U.S.
-Court of Appeals for the District of Columbia.
-The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 (US Government, 2018a).
-Following allegations of sexual assault by high school classmate Dr.~Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.
-
-On September 27, the committee questioned Dr.~Ford before commencing a second round of questioning for Judge Kavanaugh (US Government, 2018b).
-During the intervening weeks between hearings, two more women came forward with two separate allegations of sexual assault on the part of Kavanaugh.
-According to Nielsen reports, more than 20 million people watched the September 27 proceedings on television (O'Connell, 2018).
-This figure does not take into account viewers who watched online, nor does it account for viewers outside the United States.
-On September 28, the Senate Judiciary Committee voted to send the nomination to the Senate floor.
-Senator Jeff Flake of Arizona, however, lobbied for a week-long FBI investigation on Kavanaugh and the allegations facing him, which the committee, and later the President, approved.
-The investigation concluded with no significant findings.
-The Senate voted 50-48 to approve Kavanaugh's appointment on October 6, 2018 (US Government, 2018c).
-
-The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many dimensions that likely differ depending on one's morals.
-The issue might be exacerbated given the presence of questionable sexual behaviors at the center of many concerns.
-On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime opportunity to bring morality back into interpretation of the Constitution.
-Kavanaugh's confirmation creates a conservative stronghold among the justices on the court.
-Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds.
-Concerns around abortion might be related either to \emph{harm/care} or \emph{purity/sanctity}.
-On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals.
-Likewise, arguments could be made that relate concerns regarding sexual violence to \emph{harm/care} or \emph{fairness/reciprocity}.
-Additionally, the moral duty of the Senate as the upper chamber in the U.S.
-legislature has been scrutinized in public discourse with respect to its handling of the assault allegations vis-a-vis Kavanaugh's confirmation.
-
-\hypertarget{u.s.-government-shutdown-of-2018-2019}{%
-\subsection{U.S. Government Shutdown of 2018-2019}\label{u.s.-government-shutdown-of-2018-2019}}
-
-The U.S.
-Federal Government partially shut down on December 22, 2018.
-The government reopened on January 25, 2019 upon the passage of an appropriations bill by both houses of Congress (Axelrod, 2019).
-The shutdown stemmed from a disagreement between President Donald Trump and Congress over funding for the president's proposed U.S.-Mexico border wall.
-President Trump demanded \$5.7 billion dollars in the new budget to be appropriated for the wall, which Congress did not provide in its budget (Peoples \& Swanson, 2019).
-Owing to the lack of funding, the government began a partial shutdown, causing \enquote{around 800,000} federal employees to be either furloughed or compelled to work without pay (Axelrod, 2019).
-
-The government shutdown ended 35 days later when Congress passed a continuing resolution to fund the government for three weeks while further negotiations regarding the budget would take place.
-President Trump signed the bill, ending the longest government shutdown in U.S.
-history (Axelrod, 2019).
-Many political commentators cite the mounting pressure on Trump and Congress stemming from significant costs both to unpaid American workers and the economy as a whole (Kheel \& Mitchell, 2019).
-Perhaps owing to the financial pressures experienced by thousands of federal employees and their families as a result of a political quarrel, President Trump saw his approval rating fall as the shutdown progressed (Peoples \& Swanson, 2019).
-While the shutdown and its associated burdens were unpopular, the issues discussed concurrent to the shutdown offer the potential for more divergent opinions.
-
-As mentioned before, the shutdown started as a result of an impasse regarding funding for the border wall.
-Since the wall was proposed during the 2016 presidential campaign, the issue has taken on a moral dimension.
-As an example, Shaun Casey, the director of Georgetown University's Berkely Center for Religion, Peace and World Affairs, cites diverging opinions stemming from theological concerns (Martin, 2019).
-Some supporters, citing certain passages from the Bible, believe construction of the wall is part of a divinely ordained process handed down by God.
-Opponents, on the other hand, have cited other parts of the Bible extolling the significance of exiled peoples, especially the Hebrew people (Martin, 2019).
-This example potentially ties into the five moral foundations.
-Theological concerns regarding the border wall might invoke \emph{authority/respect} as well as \emph{purity/sanctity}.
-In addition to these two foundations, the involvement of foreign countries and their citizens' migration into the U.S.
-could also elicit moral concerns related to \emph{ingroup/outgroup}.
-
-Owing to the wealth of moral opinions regarding the border wall and its association with the 2018-2019 government shutdown, the researchers decided to add the government shutdown as a news event to analyze under the auspices of Moral Foundations Theory.
-In addition to articles related to the Kavanaugh confirmation hearing, the researchers scraped articles related to the government shutdown in order to analyze their content for valence and moral alignment.
-
 \hypertarget{method-1}{%
@@
 
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+In contrast to Experiment 1, we approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For Experiment 2, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-Once again, no human participants were needed for this study, so no Institutional Review Board approval was necessary.
+We tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, we analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
+The content will be analyzed for valence and moral alignment under MFT.
 
@@
 (2014).
-The sources favored by the highest proportion of consistent liberals were \emph{The New York Times}, \emph{National Public Radio (NPR)}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
+The sources favored by the highest proportion of consistent liberals were the \emph{NYT}, \emph{NPR}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
 The sources favored by the highest proportion of consistent conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts, again written with the \emph{papaja} library in \emph{R}, are provided inline with this manuscript (Aust \& Barth, 2017).
 
@@
 
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset (Wickham, 2016).
+Using the \emph{rvest} and \emph{RSelenium} libraries, we pulled body text for individual articles from each of the aforementioned 10 news sources and compiled them together (Harrison \& Kim, 2020; Wickham, 2016).
 Using this dataset, we identified word count and average word count per source.
@@
 
-As in Experiment 1, the text was scanned with \emph{ngram}.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed (Schmidt et al., 2017).
+As in Experiment 1, the text was scanned with \emph{ngram} (Schmidt et al., 2017).
+Again, blank articles, text from the Disqus system, and duplicate articles were removed.
 The text was processed and stemmed in order to convert to a usable form for further analysis (Feinerer \& Hornik, 2017).
-Words were subsequently matched with their valences from Warriner et al.
-(2013).
-Depending on the results of Jordan et al.
-(2019)'s multi-trait multi-method analysis of the MFD and the Moral Foundations Questionnaire, alternative forms of the Moral Foundations Dictionary with additional words may be imported instead of the original dictionary.
-
-Using the \emph{tm} and \emph{ngram} packages in \emph{R}, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation (Feinerer \& Hornik, 2017).
 Each individual word was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}).
@@
 (2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurrence in the text.
+We obtained the words' percent occurrence in the text.
 Percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
@@
 
-The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
+We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
 As in Experiment 1, statistics calculated include \emph{z}-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source (Kincaid et al., 1975).
@@
 \midrule
-Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.80 & 1.91\\
-NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.49 & 3.62\\
-New York Times & 0.33 & 0.13 & 653 & 723569 & 1,108.07 & 570.31 & 461.26 & 174.20 & 10.56 & 2.10\\
-Politico & 0.32 & 0.10 & 689 & 1069292 & 1,551.95 & 1,045.47 & 614.66 & 358.68 & 12.09 & 2.60\\
-Slate & 0.29 & 0.12 & 272 & 229896 & 845.21 & 612.22 & 332.42 & 168.17 & 12.35 & 2.47\\
-The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.83 & 1.87\\
-Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 11.04 & 2.17\\
-Fox News & 0.29 & 0.11 & 646 & 1304048 & 2,018.65 & 2,709.77 & 534.47 & 404.21 & 9.70 & 1.87\\
-Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.89 & 2.37\\
-Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1,552.72 & 1,258.51 & 419.00 & 225.80 & 9.42 & 9.26\\
+Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.68 & 1.89\\
+NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.55 & 3.67\\
+New York Times & 0.33 & 0.13 & 653 & 723569 & 1,108.07 & 570.31 & 461.26 & 174.20 & 9.52 & 1.79\\
+Politico & 0.32 & 0.10 & 689 & 1069292 & 1,551.95 & 1,045.47 & 614.66 & 358.68 & 12.10 & 2.66\\
+Slate & 0.29 & 0.12 & 272 & 229896 & 845.21 & 612.22 & 332.42 & 168.17 & 12.30 & 2.48\\
+The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.73 & 1.85\\
+Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 10.87 & 2.12\\
+Fox News & 0.29 & 0.11 & 646 & 1304048 & 2,018.65 & 2,709.77 & 534.47 & 404.21 & 9.71 & 1.86\\
+Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.76 & 2.40\\
+Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1,552.72 & 1,258.51 & 419.00 & 225.80 & 9.17 & 8.86\\
 \bottomrule
@@
 \midrule
-Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.69 & 1.84\\
-NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.19 & 3.15\\
-New York Times & 0.33 & 0.13 & 751 & 831184 & 1,106.77 & 506.92 & 471.80 & 174.88 & 11.28 & 2.19\\
-Politico & 0.29 & 0.10 & 222 & 349499 & 1,574.32 & 875.63 & 638.32 & 313.34 & 11.29 & 1.24\\
-Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.86 & 2.51\\
-The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.69 & 1.85\\
-Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.72 & 2.05\\
-Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2,763.29 & 3,405.44 & 637.30 & 494.00 & 9.37 & 1.94\\
-Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.41 & 4.79\\
-Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1,956.79 & 1,544.14 & 482.79 & 252.79 & 9.76 & 7.61\\
+Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.68 & 1.85\\
+NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.20 & 3.16\\
+New York Times & 0.33 & 0.13 & 752 & 836811 & 1,112.78 & 532.72 & 472.95 & 177.57 & 10.10 & 1.74\\
+Politico & 0.29 & 0.10 & 222 & 349499 & 1,574.32 & 875.63 & 638.32 & 313.34 & 11.31 & 1.26\\
+Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.87 & 2.53\\
+The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.70 & 1.85\\
+Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.71 & 2.05\\
+Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2,763.29 & 3,405.44 & 637.30 & 494.00 & 9.43 & 1.95\\
+Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.36 & 4.81\\
+Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1,956.79 & 1,544.14 & 482.79 & 252.79 & 9.77 & 7.64\\
 \bottomrule
@@
 
-To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
-The researchers used the \emph{nlme} library in \emph{R} (Pinheiro et al., 2017).
+We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Experiment 1.
 Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
@@
 \caption{\label{tab:exp2-tablekav}Kavanaugh Results - Multilevel Model}
+
+\footnotesize{
 
@@
 \caption{\label{tab:exp2-tablegs}Government Shutdown Results - Multilevel Model}
+
+\footnotesize{
 
@@
 Harm/Care & 0.91 & 1.27 & 1.01 & 1.27 & 1.68 & .132 & -0.07\\
-Fairness/Reciprocity & 1.22 & 1.05 & 0.91 & 1.05 & -0.76 & .468 & 0.27\\
-Ingroup/Loyalty & 1.38 & 1.16 & 1.11 & 1.16 & -0.48 & .644 & 0.21\\
-Authority/Respect & 0.87 & 1.24 & 0.36 & 1.24 & -1.38 & .203 & 0.37\\
+Fairness/Reciprocity & 1.22 & 1.05 & 0.91 & 1.05 & -0.76 & .467 & 0.27\\
+Ingroup/Loyalty & 1.38 & 1.16 & 1.11 & 1.16 & -0.48 & .643 & 0.21\\
+Authority/Respect & 0.87 & 1.24 & 0.36 & 1.24 & -1.38 & .204 & 0.37\\
 Purity/Sanctity & 1.29 & 1.13 & 0.99 & 1.13 & 0.03 & .979 & 0.22\\
@@
 
-The results obtained in Experiment 2 did not confirm either of the hypotheses.
-The researchers found little compelling evidence of an effect of partisan lean on MFD endorsement.
-The only significant effect was found for \emph{harm/care} in the Kavanaugh confirmation hearing dataset.
-While the effect was in the hypothesized direction (higher positive endorsement for liberal sources), the effect size was small.
-While there were no significant effects found for the government shutdown topic, a small-to-medium effect size was calculated for the \emph{authority/respect} foundation.
-Once again, the effect was in the hypothesized direction with conservative sources providing higher positive endorsements of the foundation relative to liberal sources.
-
-Both of these effects are consistent with both the research hypotheses as well as previous findings in Moral Foundations Theory scholarship.
-It should be noted these effects were found in isolation, and similar patterns were not found across the other studies.
-These findings undermine any inferences of political bias stemming from the content of news articles.
-The results obtained for Experiment 2 call into question the Moral Foundations Dictionary's efficacy as a tool for establishing differences between political news sources by partisan lean.
+The results obtained in Experiment 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
+The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given Graham et al.
+(2009).
+Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the practical effects much smaller than reported in Graham et al.
+(2009).
+While not significant, fairness was endorsed more by conservatives in both cases.
+In contrast, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
+
+Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
+One issue that Experiment 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in Sterling and Jost (2018).
+For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
+The original predictions made by the Moral Foundations are very simplistic and likely much more complex in reality.
 
@@
 
-Within the theoretical framework of Moral Foundations Theory (Haidt \& Graham, 2007), the researchers attempted to devise a method leveraging the Moral Foundations Dictionary (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
-The researchers downloaded news article text from the web, processed the text, matched it with the Moral Foundations Dictionary words, and calculated average valence for words in each article.
-To analyze the data, the researchers constructed multi-level models for each foundation in which weighted percentages were predicted by each source's political lean.
-Individual source was held as a random intercept to control for correlated error.
-This process was undertaken once in Experiment 1 for general political news and twice in Experiment 2 using articles pertaining to two specific topics in American news: Brett Kavanaugh's confirmation to the Supreme Court and the most recent (as of this writing) partial U.S.
-Government shutdown from December 2018 to January 2019.
-
-In Experiment 1, the researchers analyzed general political news articles from four prominent U.S.
-news sources: \emph{The New York Times}, \emph{NPR}, \emph{Fox News}, and \emph{Breitbart}.
-They hypothesized \emph{The New York Times} and \emph{NPR} would endorse moral foundations representative of liberal political views and that \emph{Fox News} and \emph{Breitbart} would endorse foundations indicative of conservative views.
-The researchers assigned a political lean (liberal or conservative) to the sources based upon consumer preferences established by Mitchell et al.
-(2014).
-After collecting the articles through web scraping, processing the article text, calculating percent occurrence of MFD words, and weighting that value by valence, the researchers constructed the MLM.
-The results obtained were not significant in any statistical or practical sense.
+Within the theoretical framework of MFT (Haidt \& Graham, 2007), we attempted to devise a method leveraging the MFD (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
+In Experiment 1,the results obtained were not significant in any statistical or practical sense.
 There was a small effect found for the \emph{authority/respect} foundation according to Cohen's \emph{d}, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-The researchers viewed these results as an opportunity to alter their method for use in Experiment 2.
-
-In Experiment 2, the researchers adjusted their method in order to increase their potential ability to quantify political leanings in U.S.
-news sources.
-First, the researchers expanded the number of news sources from which articles were collected.
-They added \emph{Slate}, \emph{Politico}, and \emph{Huffington Post} to the list of liberal sources and \emph{The Blaze}, \emph{Rush Limbaugh}, and \emph{Sean Hannity} to the conservative sources.
-Once again, political bias groups were assigned based on Mitchell et al.
-(2014)'s findings.
-Second, they elected to collect articles and compile datasets pertaining to two specific topics in U.S.
-news: the Kavanaugh hearing and the government shutdown.
-These topics were chosen due to their relevance to multiple moral foundations.
-Other than those two alterations, the same method (scraping, processing, weighting, and multi-level modelling) was employed for Experiment 2.
-
-For articles pertaining to the Kavanaugh hearing, there was a statistically significant effect for \emph{harm/care}, but the effect size was modest.
-No other statistically or practically significant effects were found for the Kavanaugh topic.
-Likewise, there were no statistically or practically significant effects revealed for the government shutdown topic.
-However, there was a small-to-medium effect size for \emph{authority/respect}.
-The fact these patterns do not appear in any of the other studies undertaken herein decreases the researchers' ability to draw any valuable conclusions regarding the MFD's ability to reveal political bias in American news media.
-
-The results obtained in both experiments, while not confirmatory, provide several avenues for future investigation.
-Twice confronted with the failure to uncover differences in news media's political content, the researchers were unable to confirm the existence of an effect of political lean on American news writing under the auspices of Moral Foundations Theory.
-This does not, however, rule out the possibility that news media is biased.
-As Mitchell et al.
-(2014) has demonstrated, self-reported political partisans are drawn to separate sources, but the present research was unable to offer any content-based explanations of this phenomenon.
-Even when attenuating the scraping criteria to collect text concerning (what the researchers believed to be) morally resonant topics, the method failed to detect differences in MFD word use by prominent news sources.
-Given part of the researchers' goal with this study was to answer a method question, they must contemplate whether or not the method or the construct of interest (political lean) are the primary contributor to null results.
-Either the method used to detect lean was insufficient for this purpose, or political lean simply does not exist, indicating the presence of a true negative in the results.
-
-The researchers believe these results represent a false negative rather than a true negative.
-That is, we believe political lean exists, but that we have been unable to detect it at a content level.
-The researchers again turn to Mitchell et al.
-(2014)\enquote{s work in this area: political partisans prefer certain news outlets over others.
-There must be something about the sources} content that facilitates partisans' repeated usage.
-Otherwise, they might not express such loyalty to any one source (or group of sources) over others.
-Given this aspect of the news economy, the researchers still believe certain news outlets in the U.S.
-contain a political slant.
-The researchers' focus, therefore, turns toward the limitations of the method, especially the chosen theoretical framework, under which the present research was conducted.
-
-Despite the fact the results regarding political bias were inconclusive, the researchers still retain confidence in the overall structure of the methodology established in the current study.
+In Experiment 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
+Building on Frimer (2020) and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
+
+Despite the fact the results regarding political bias were inconclusive, we still retain confidence in the overall structure of the methodology established in the current study.
 Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
+We implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
 This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
 
-There remains an aspect of language which this method still cannot address: context.
-Owing to the presence of millions of words in the analyses presented in the current study, the researchers would be unable to check for context and correct endorsement scores accordingly.
-Graham et al.
-(2009) actually performed a process of human error-checking for context when formulating the MFD.
-While this might have helped that team fix mistakes made by the LIWC program (Pennebaker et al.
-(2007)), manual coding of this nature has the potential to introduce an unacceptable level of bias in the method, as perceptions of context would be dependent upon raters' interpretations and belief systems.
-Additionally, the numerous ways in which context affects meaning make it difficult to interpret MFD word occurrence outside of a narrow operational definition of \enquote{endorsement.} In fact, political lean may be communicated through methods other than through the use of particular words.
-
-One method through which news organizations might appeal to political partisans is through their content strategy rather than their use of MFD words.
-The results in the current study demonstrate a similar pattern of endorsement across both conservative and liberal sources.
-Specifically, the researchers found slightly positive endorsements for all five foundations no matter the political lean of the source.
-While this may simply be an indication of insufficient MFD word occurrence in news articles, it may also demonstrate truly equal endorsement despite political lean.
-While news organizations may endorse all moral foundations, they may also adopt strategies for doing so that appeal to the political partisans consuming their product.
-As an example, a liberal source might endorse \emph{purity/sanctity} through an appeal to reduce waste or pollution (i.e.~keeping the earth \enquote{clean}).
-A conservative source, on the other hand, might endorse \emph{purity/sanctity} through an argument in favor of abstinence or religious commitment (i.e.~keeping a \enquote{clean} soul, mind, or body).
-Both publications would register as positive endorsement of \emph{purity/sanctity} despite appropriating the concept for distinct purposes.
-Through these divergent strategies, liberal and conservative news organizations might be able to appeal to their fans while exhibiting similar levels of moral endorsement.
-This could represent a further weakness of the Moral Foundations Dictionary as an instrument, as it is unable to identify these potential strategies for communicating certain points of view.
-
-Thus, the researchers' attention turned to the instrument used to detect differences: the Moral Foundations Dictionary.
-As mentioned before, MFD is a measure developed from Moral Foundations Theory (Graham et al., 2009).
+However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
+As mentioned before, MFD is a measure developed from MFT (Graham et al., 2009).
 Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
@@
 
-Alternative instruments could be developed through the Linguistic Inquiry and Word Count program (LIWC) (Pennebaker et al., 2007).
-As stated before, the Moral Foundations Dictionary was established through an analysis of Christian sermons performed mostly with LIWC as well as some human-enforced corrections due to context (Graham et al., 2009).
-This approach was grounded in Moral Foundations Theory, a clear framework within which the authors developed the MFD.
-The original authors of the MFD established sound psychometric properties for the tool, implying its validity in several applications.
-For this reason, the researchers elected to utilize the MFD as their primary instrument.
-
-Instruments that improve upon the Moral Foundations Dictionary could theoretically be developed through a LIWC analysis.
-Researchers could obtain percent occurrence scores for words appearing in certain LIWC categories, which could then be weighted with valence scores from Warriner et al.
-(2013).
-The researchers will consider other applications of the LIWC in future studies aiming to analyze political content.
-Pennebaker et al.
-(2007) has suggested the program could be applied to analyses of cognitive, social, and emotional states.
-Furthermore, there is some evidence LIWC can be used to detect deception, but the reliability of the program's accuracy in this regard (67\%) calls this assertion into question (Pennebaker, 2011).
-Despite the promising extent of LIWC's abilities, without a firm theoretical foundation for such analyses, any such applications of LIWC would face serious questions as to their relevance, validity, and generalizability.
-Nevertheless, LIWC analyses may represent a path to further research into political differences in news media as well as theory formation.
-
-There is, however, another theoretical framework that could prove useful when applied to the method established in the present research.
-Relational Frame Theory originates in applied behavior analysis, but there exists recent scholarship that demonstrates its potential usefulness in the political realm.
-Relational Frame Theory (RFT) holds that stimuli, including speech and discourse, elicit responses in terms of relationships to other stimuli, even when the stimuli do not otherwise appear to be related (Blackledge, 2014).
-For example, an individual's equivalent fear response to a venomous snake as well as a wooded area said to \enquote{contain snakes} represents \enquote{mutual entailment.} That is, the fear response is an effect of both the snake and environment stimuli, which cause the fear response.
-\enquote{Combinatorial entailment} can be represented by a fear response elicited by a novel stimulus whose relationship to a well-known stimulus elicits a certain response (Blackledge, 2014).
-In the snake example, if another stimulus (Stimulus A), were said to be \enquote{worse than} the snake, the relationship between A and the snake would elicit a more severe fear response to Stimulus A.
-RFT utilizes a set of \enquote{families} describing the nature of these relationships.
-Such families include (among others) \enquote{coordinative,} establishing similarities between stimuli, \enquote{distinctive,} implying fundamental differences between stimuli, and \enquote{hierarchical,} implying a relation in terms of differing order or rank (Belisle, Paliliunas, Dixon, \& Tarbox, 2018).
-These families can be used to analyze networks of relational frames in discourse.
-
-Belisle et al.
-(2018) conducted a text analysis (using a computer algorithm) of several speeches made by four recent U.S.
-presidents under Relational Frame Theory.
-These speeches, representing prominent examples of political discourse, were found to differ in their use of relational frames.
-For example, speeches by Donald Trump were found to contain more distinctive frames than other presidents, while Barack Obama utilized more coordinative frames than his counterparts.
-According to Belisle et al.
-(2018), these observations imply President Obama, who employed more coordinative frames, utilized language emphasizing unity and similarity between people.
-Donald Trump, on the other hand emphasized differences and divisions between people through his use of distinctive frames (Belisle et al., 2018).
-At first glance, the differences appear to fall along party lines, though other factors may be involved as well.
-In any case, this research appears to indicate that RFT might be useful for analyzing political news content similar to the method employed in the current study.
-
-Another apparent strength of RFT is its demonstrated effectiveness in the analysis of political discourse.
-Unlike the development of the Moral Foundations Dictionary, this application of RFT was performed on public facing political discourse that might be more similar to news articles than the Christian sermons upon which the MFD was compiled.
-Additionally, there would likely be greater overlap between the speeches analyzed in Belisle et al.
-(2018)'s work and political news, as the media often quotes speeches by the president.
-Furthermore, the types or \enquote{families} of relational frames could be used as the individual constructs much like the moral foundations in the present research.
-In order to conform with the method established for this study, their occurrence would need to be scored, probably as a percent.
-This would allow for an intuitive approach to weighting by \emph{z}-scored valence if needed.
-
-While Relational Frame Theory appears to represent a viable option for further research into political news analysis, there are some drawbacks.
-First, RFT by itself does not purport to elucidate political differences in discourse, and its applications to political research are not yet well established.
-In other words, RFT represents one method by which to analyze political text by analyzing occurrence of particular frames.
-However, there exists the caveat that the frame families are not known to represent patterns of political ideology at this time.
-One of the main strengths of Moral Foundations Theory in the eyes of the researchers was that it is a theory under which endorsement patterns (direction and relationship) could be predicted based upon political affiliation.
-While the results obtained herein may weaken assumptions regarding the MFD's capabilities with political text, Moral Foundations Theory has been repeatedly established as a strong framework for detecting political differences along moral lines.
-
-In order to seriously consider RFT as a viable framework for this type of analysis, the researchers would like to be able to draw on further confirmatory evidence of the theory's utility in political discourse analysis.
-Specifically, analyses of more individuals than the four presidents addressed by Belisle et al.
-(2018) would be needed to further demonstrate RFT's applicability in this field.
-Also, though presidential speeches may be more similar to news articles than sermons, they are still a distinct form of discourse with different goals and audiences than news outlets.
-RFT's reliability across these forms appears to remain untested as of this writing.
-These potential shortcomings are testable and might be overcome through more research.
-As such, RFT's potential as a useful framework for political discourse analysis should not be discounted.
-
-Finally, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
+In critiquing MFT, Schein and Gray (2015) proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
+Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else Schein \& Gray (2015).
+Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
+For example, in the case of abortion, liberals tend to identify the primary harm to the mother leading to a pro-choice position whereas conservative tend to identify the primary harm to the fetus leading to a pro-life position.
+While as of yet, no linguistic measurement of dyadic morality exists; such an approach may be able to better identify the systematic differences between liberals and conservatives.
+
+Turning to atheoretical approaches, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
 Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
 The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
-Likewise, there are several approaches to analyzing such data, including linear models (like multi-level models) and network-style models such as latent semantic analysis (Landauer, 1998).
+Likewise, there are several approaches to analyzing such data, including linear models (like multilevel models) and network-style models such as latent semantic analysis (Landauer, 1998).
 Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
 
-The researchers aimed to utilize the Moral Foundations Dictionary and valence in the analysis of political news articles to determine whether or not bias was present.
-In Experiment 1, they tested general political news from four U.S.
-news sources - two liberal and two conservative.
-They were unable to find any significant evidence of political bias in that analysis.
-After adjusting the method to include more sources and specific topics for articles, including the Kavanaugh hearing and the government shutdown, the researchers were once again unable to uncover differences in MFD word use between conservative and liberal news sources.
-The results in the current study seem to demonstrate the MFD's weaknesses in applications to political discourse.
-MFD words simply might not appear often enough in news articles to register as endorsement for any particular moral foundation over the others.
-In future research, this weakness could be addressed through further alterations to the method, including alternative analyses using computer programs including LIWC, through a different theoretical perspective such as Relational Frame Theory, or through alternative strategies involving collecting data and drawing conclusions from which future theories may be derived.
-
-Never before has news media and discourse represented such fertile ground for psychological research.
+Never before has political discourse represented such fertile ground for psychological research.
 The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
@@
 
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Aust2017}{}%
-Aust, F., \& Barth, M. (2017). papaja: Create APA manuscripts with R Markdown. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-Axelrod2019}{}%
-Axelrod, T.
-(2019).
-Poll: Majority of Americans hold Trump and Republicans responsible for shutdown \textbar{} TheHill.
-Retrieved from \url{https://thehill.com/homenews/campaign/427007-poll-majority-of-americans-hold-trump-and-republicans-responsible-for}
-
-\leavevmode\hypertarget{ref-Belisle2018}{}%
-Belisle, J., Paliliunas, D., Dixon, M.
-R., \& Tarbox, J.
-(2018).
-Feasibility of contextual behavioral speech analyses of US presidents: Inaugural addresses of Bill Clinton, George W.
-Bush, Barack Obama, and Donald Trump, 1993--2017.
-\emph{Journal of Contextual Behavioral Science}, \emph{10}(July), 14--18.
-doi:\href{https://doi.org/10.1016/j.jcbs.2018.07.002}{10.1016/j.jcbs.2018.07.002}
-
-\leavevmode\hypertarget{ref-Blackledge2014}{}%
-Blackledge, J.
-T.
-(2014).
-An introduction to relational frame theory: Basics and applications.
-\emph{The Behavior Analyst Today}, \emph{3}(4), 421--433.
-doi:\href{https://doi.org/10.1037/h0099997}{10.1037/h0099997}
-
-\leavevmode\hypertarget{ref-Bradley1999}{}%
-Bradley, M.
-M., \& Lang, P.
-J.
-(1999).
-\emph{Affective Norms for English Words (ANEW): Instruction manual and affective ratings} (No.
-C-1).
-The Center for Research in Psychophysiology, University of Florida.
-
-\leavevmode\hypertarget{ref-Cameron2006}{}%
-Cameron, D. (2006). Ideology and language. \emph{Journal of Political Ideologies}, \emph{11}(2), 141--152. doi:\href{https://doi.org/10.1080/13569310600687916}{10.1080/13569310600687916}
-
-\leavevmode\hypertarget{ref-Clinton2014}{}%
-Clinton, J.
-D., \& Enamorado, T.
-(2014).
-The national news media's effect on Congress: How Fox News affected elites in Congress.
-\emph{The Journal of Politics}, \emph{76}(4), 928--943.
-doi:\href{https://doi.org/10.1017/S0022381614000425}{10.1017/S0022381614000425}
-
-\leavevmode\hypertarget{ref-Davies2014}{}%
-Davies, C.
-L., Sibley, C.
-G., \& Liu, J.
-H.
-(2014).
-Confirmatory factor analysis of the moral foundations questionnaire independent scale validation in a new zealand sample.
-\emph{Social Psychology}, \emph{45}(6), 431--436.
-doi:\href{https://doi.org/10.1027/1864-9335/a000201}{10.1027/1864-9335/a000201}
-
-\leavevmode\hypertarget{ref-Druckman2004}{}%
-Druckman, J.
-N., Jacobs, L.
-R., \& Ostermeier, E.
-(2004).
-Candidate strategies to prime issues and image.
-\emph{The Journal of Politics}, \emph{66}(4), 1180--1202.
-doi:\href{https://doi.org/10.1111/j.0022-3816.2004.00295.x}{10.1111/j.0022-3816.2004.00295.x}
-
-\leavevmode\hypertarget{ref-Feinerer2017}{}%
-Feinerer, I., \& Hornik, K. (2017). Text mining package. Retrieved from \url{http://tm.r-forge.r-project.org/}
-
-\leavevmode\hypertarget{ref-Gelman2006}{}%
-Gelman, A.
-(2006).
-Multilevel (hierarchical) modeling: What it can and cannot do.
-\emph{Technometrics}, \emph{48}(3), 432--435.
-doi:\href{https://doi.org/10.1198/004017005000000661}{10.1198/004017005000000661}
-
-\leavevmode\hypertarget{ref-Gilligan1982}{}%
-Gilligan, C.
-(1982).
-New maps of development: New visions of maturity.
-\emph{American Journal of Orthopsychiatry}, \emph{52}(2), 199--212.
-doi:\href{https://doi.org/10.1111/j.1939-0025.1982.tb02682.x}{10.1111/j.1939-0025.1982.tb02682.x}
-
-\leavevmode\hypertarget{ref-Graham2009}{}%
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Aust2017}{}}%
+Aust, F., \& Barth, M. (2017). {papaja: Create APA manuscripts with R Markdown.} Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Clifford2013}{}}%
+Clifford, S., \& Jerit, J. (2013). How words do the work of politics: Moral foundations theory and the debate over stem cell research. \emph{The Journal of Politics}, \emph{75}(3), 659--671.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Feinerer2017}{}}%
+Feinerer, I., \& Hornik, K. (2017). {Text mining package}. Retrieved from \url{http://tm.r-forge.r-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Frimer2020}{}}%
+Frimer, J.
+A.
+(2020).
+Do liberals and conservatives use different moral languages?
+Two replications and six extensions of graham, haidt, and nosek's (2009) moral text analysis.
+\emph{Journal of Research in Personality}, \emph{84}, 103906.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Frimer2015}{}}%
+Frimer, J. A., Tell, C. E., \& Haidt, J. (2015). Liberals condemn sacrilege too: The harmless desecration of cerro torre. \emph{Social Psychological and Personality Science}, \emph{6}(8), 878--886.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Garten2016}{}}%
+Garten, J., Boghrati, R., Hoover, J., Johnson, K.
+M., \& Dehghani, M.
+(2016).
+Morality between the lines: Detecting moral sentiment in text.
+In \emph{Proceedings of IJCAI 2016 workshop on computational modeling of attitudes}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gelman2006}{}}%
+Gelman, A. (2006). {Multilevel (hierarchical) modeling: What it can and cannot do}. \emph{Technometrics}, \emph{48}(3), 432--435. \url{https://doi.org/10.1198/004017005000000661}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Graham2009}{}}%
 Graham, J., Haidt, J., \& Nosek, B.
@@
 (2009).
-Liberals and conservatives rely on different sets of moral foundations.
-\emph{Journal of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
-doi:\href{https://doi.org/10.1037/a0015141}{10.1037/a0015141}
-
-\leavevmode\hypertarget{ref-Graham2011}{}%
-Graham, J., Nosek, B.
-A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
-H.
-(2011).
-Mapping the moral domain.
-\emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
-doi:\href{https://doi.org/10.1037/a0021847}{10.1037/a0021847}
-
-\leavevmode\hypertarget{ref-Haidt2007}{}%
+{Liberals and conservatives rely on different sets of moral foundations.} \emph{Journal of Personality and Social Psychology}, \emph{96}(5), 1029--1046.
+\url{https://doi.org/10.1037/a0015141}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gray2015}{}}%
+Gray, K., \& Keeney, J. E. (2015). Disconfirming moral foundations theory on its own terms: Reply to graham (2015). \emph{Social Psychological and Personality Science}, \emph{6}(8), 874--877.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gray2014}{}}%
+Gray, K., Schein, C., \& Ward, A.
+F.
+(2014).
+The myth of harmless wrongs in moral cognition: Automatic dyadic completion from sin to suffering.
+\emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1600.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Haidt2007}{}}%
 Haidt, J., \& Graham, J.
 (2007).
-When morality opposes justice: Conservatives have moral intuitions that Liberals may not recognize.
+{When morality opposes justice: Conservatives have moral intuitions that Liberals may not recognize}.
 \emph{Social Justice Research}, \emph{20}(1), 98--116.
-doi:\href{https://doi.org/10.1007/s11211-007-0034-z}{10.1007/s11211-007-0034-z}
-
-\leavevmode\hypertarget{ref-Jordan2019}{}%
-Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{A validation of the Moral Foundations Questionnaire and Dictionary}. Retrieved from \url{https://osf.io/kt9yf/}
-
-\leavevmode\hypertarget{ref-Kheel2019}{}%
-Kheel, R., \& Mitchell, E.
-(2019).
-Overnight Defense: Trump agrees to reopen government without wall funding \textbar{} Senate approves stopgap spending \textbar{} Dems ask Armed Services chair to block military funding for wall \textbar{} Coast Guard official assures workers they will receive back pay \textbar{} TheHill.
-Retrieved from \url{https://thehill.com/policy/defense/overnights/427045-overnight-defense-trump-agrees-to-reopen-government-without-wall}
-
-\leavevmode\hypertarget{ref-Kincaid1975}{}%
+\url{https://doi.org/10.1007/s11211-007-0034-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-harrison_rselenium_2020}{}}%
+Harrison, J., \& Kim, J. Y. (2020). {RSelenium}: {R} {Bindings} for '{Selenium} {WebDriver}'. Retrieved from \url{https://CRAN.R-project.org/package=RSelenium}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hopp2021}{}}%
+Hopp, F.
+R., Fisher, J.
+T., Cornell, D., Huskey, R., \& Weber, R.
+(2021).
+The extended moral foundations dictionary (eMFD): Development and applications of a crowd-sourced approach to extracting moral intuitions from text.
+\emph{Behavior Research Methods}, \emph{53}(1), 232--246.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Jordan2019}{}}%
+Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{{A validation of the Moral Foundations Questionnaire and Dictionary}}. Retrieved from \url{https://osf.io/kt9yf/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kincaid1975}{}}%
 Kincaid, J.
-P., Fishburne, J., Robert P., R., Richard L., C., \& Brad S.
+P., Fishburne, Jr., Robert P., R., Richard L., C., \& Brad S.
 (1975).
-Derivation of New Readability Formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted Personnel.
-doi:\href{https://doi.org/10.21236/ADA006655}{10.21236/ADA006655}
-
-\leavevmode\hypertarget{ref-Kohlberg1977}{}%
-Kohlberg, L., \& Hersh, R.
-H.
-(1977).
-Moral development: A review of the theory.
-\emph{Theory into Practice}, \emph{16}(2), 53--59.
-doi:\href{https://doi.org/10.1080/00405847709542675}{10.1080/00405847709542675}
-
-\leavevmode\hypertarget{ref-Kuperman2014}{}%
-Kuperman, V., Estes, Z., Brysbaert, M., \& Warriner, A.
-B.
-(2014).
-Emotion and language: Valence and arousal affect word recognition.
-\emph{Journal of Experimental Psychology: General}, \emph{143}(3), 1065--1081.
-doi:\href{https://doi.org/10.1037/a0035669}{10.1037/a0035669}
-
-\leavevmode\hypertarget{ref-Kuperman2012}{}%
-Kuperman, V., Stadthagen-Gonzalez, H., \& Brysbaert, M.
-(2012).
-Age-of-acquisition ratings for 30,000 English words.
-\emph{Behavior Research Methods}, \emph{44}(4), 978--990.
-doi:\href{https://doi.org/10.3758/s13428-012-0210-4}{10.3758/s13428-012-0210-4}
-
-\leavevmode\hypertarget{ref-Landauer1998}{}%
-Landauer, T.
-K.
-(1998).
-Learning and Representing Verbal Meaning.
-\emph{Current Directions in Psychological Science}, \emph{7}(5), 161--164.
-doi:\href{https://doi.org/10.1111/1467-8721.ep10836862}{10.1111/1467-8721.ep10836862}
-
-\leavevmode\hypertarget{ref-Martin2019}{}%
-Martin, M. (2019). The Moral Question Of Trump's Border Wall : NPR. NPR. Retrieved from \url{https://www.npr.org/2019/01/27/689191255/the-morality-question-of-trump-s-border-wall}
-
-\leavevmode\hypertarget{ref-Mitchell2014}{}%
+{Derivation of New Readability Formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted Personnel}.
+\url{https://doi.org/10.21236/ADA006655}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kohlberg1977}{}}%
+Kohlberg, L., \& Hersh, R. H. (1977). {Moral development: A review of the theory}. \emph{Theory Into Practice}, \emph{16}(2), 53--59. \url{https://doi.org/10.1080/00405847709542675}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Landauer1998}{}}%
+Landauer, T. K. (1998). {Learning and Representing Verbal Meaning}. \emph{Current Directions in Psychological Science}, \emph{7}(5), 161--164. \url{https://doi.org/10.1111/1467-8721.ep10836862}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mikolov_efficient_2013}{}}%
+Mikolov, T., Chen, K., Corrado, G., \& Dean, J.
+(2013).
+Efficient {Estimation} of {Word} {Representations} in {Vector} {Space}.
+\emph{arXiv:1301.3781 {[}Cs{]}}.
+Retrieved from \url{http://arxiv.org/abs/1301.3781}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mitchell2014}{}}%
 Mitchell, A., Matsa, K.
@@
 (2014).
-Political polarization \& media habits \textbar{} Pew Research Center.
+{Political polarization {\&} media habits \textbar{} Pew Research Center}.
 Retrieved from \url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
 
-\leavevmode\hypertarget{ref-New2007}{}%
-New, B., Brysbaert, M., Veronis, J., \& Pallier, C.
-(2007).
-The use of film subtitles to estimate word frequencies.
-\emph{Applied Psycholinguistics}, \emph{28}(4), 661--677.
-doi:\href{https://doi.org/10.1017/S014271640707035X}{10.1017/S014271640707035X}
-
-\leavevmode\hypertarget{ref-OConnell2018}{}%
-O'Connell, M.
+\leavevmode\vadjust pre{\hypertarget{ref-Pennebaker2007}{}}%
+Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). {Liwc2007: Linguistic inquiry and word count}. Austin, TX.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pinheiro2017}{}}%
+Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). {nlme: Linear and nonlinear mixed effects models}. Retrieved from \url{https://cran.r-project.org/package=nlme}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sagi2014}{}}%
+Sagi, E., \& Dehghani, M. (2014). Measuring moral rhetoric in text. \emph{Social Science Computer Review}, \emph{32}(2), 132--144.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schein2015}{}}%
+Schein, C., \& Gray, K.
+(2015).
+The unifying moral dyad: Liberals and conservatives share the same harm-based moral template.
+\emph{Personality and Social Psychology Bulletin}, \emph{41}(8), 1147--1163.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2017}{}}%
+Schmidt, M.
+F.
+H., Gonzalez-Cabrera, I., \& Tomasello, M.
+(2017).
+{Children's developing metaethical judgments}.
+\emph{Journal of Experimental Child Psychology}, \emph{164}, 163--177.
+\url{https://doi.org/10.1016/j.jecp.2017.07.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sterling2018}{}}%
+Sterling, J., \& Jost, J.
+T.
 (2018).
-Ford-Kavanaugh Ratings: Hearing Brings 20 Million viewers to cable and broadcast \textbar{} Hollywood Reporter.
-Retrieved from \url{https://www.hollywoodreporter.com/live-feed/ford-kavanaugh-ratings-hearing-brings-20-million-viewers-cable-broadcast-1147785}
-
-\leavevmode\hypertarget{ref-Pashler2012}{}%
-Pashler, H., Coburn, N., \& Harris, C.
-R.
-(2012).
-Priming of Social Distance?
-Failure to Replicate Effects on Social and Food Judgments.
-\emph{PLoS ONE}, \emph{7}(8).
-doi:\href{https://doi.org/10.1371/journal.pone.0042510}{10.1371/journal.pone.0042510}
-
-\leavevmode\hypertarget{ref-Pennebaker2011}{}%
-Pennebaker, J.
-W.
-(2011).
-Using computer analyses to identify language style and aggressive intent: The secret life of function words.
-\emph{Dynamics of Asymmetric Conflict}, \emph{4}(2), 92--102.
-doi:\href{https://doi.org/10.1080/17467586.2011.627932}{10.1080/17467586.2011.627932}
-
-\leavevmode\hypertarget{ref-Pennebaker2007}{}%
-Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). Liwc2007: Linguistic inquiry and word count. Austin, TX.
-
-\leavevmode\hypertarget{ref-Peoples2019}{}%
-Peoples, S., \& Swanson, E. (2019, January). Trump's approval rating sinks in new poll as he gets most blame for shutdown. Chicago.
-
-\leavevmode\hypertarget{ref-Pinheiro2017}{}%
-Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). nlme: Linear and nonlinear mixed effects models. Retrieved from \url{https://cran.r-project.org/package=nlme}
-
-\leavevmode\hypertarget{ref-Schmidt2017}{}%
-Schmidt, M.
-F., Gonzalez-Cabrera, I., \& Tomasello, M.
-(2017).
-Children's developing metaethical judgments.
-\emph{Journal of Experimental Child Psychology}, \emph{164}, 163--177.
-doi:\href{https://doi.org/10.1016/j.jecp.2017.07.008}{10.1016/j.jecp.2017.07.008}
-
-\leavevmode\hypertarget{ref-Suhler2011}{}%
+Moral discourse in the twitterverse: Effects of ideology and political sophistication on language use among US citizens and members of congress.
+\emph{Journal of Language and Politics}, \emph{17}(2), 195--221.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Suhler2011}{}}%
 Suhler, C.
@@
 (2011).
-Can Innate , Modular `` Foundations '' Explain Morality ?
-Challenges for Haidt's Moral Foundations Theory.
+{Can Innate , Modular {`` Foundations ''} Explain Morality ?
+Challenges for Haidt's Moral Foundations Theory}.
 \emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
 
-\leavevmode\hypertarget{ref-USGovernment2018b}{}%
-US Government. (2018a). Congressional Record. \emph{Congressional Record}, \emph{164}(146), 46. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-USGovernment2018}{}%
-US Government. (2018b). Congressional Record. \emph{Congressional Record}, \emph{164}(160), 93. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-USGovernment2018a}{}%
-US Government. (2018c). Congressional Record. \emph{Congressional Record}, \emph{164}(167), 14. doi:\href{https://doi.org/10.1097/00017285-197507000-00018}{10.1097/00017285-197507000-00018}
-
-\leavevmode\hypertarget{ref-Warriner2015}{}%
-Warriner, A.
-B., \& Kuperman, V.
-(2015).
-Affective biases in English are bi-dimensional.
-\emph{Cognition and Emotion}, \emph{29}(7), 1147--1167.
-doi:\href{https://doi.org/10.1080/02699931.2014.968098}{10.1080/02699931.2014.968098}
-
-\leavevmode\hypertarget{ref-Warriner2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Warriner2013}{}}%
 Warriner, A.
@@
 (2013).
-Norms of valence, arousal, and dominance for 13,915 English lemmas.
+{Norms of valence, arousal, and dominance for 13,915 English lemmas}.
 \emph{Behavior Research Methods}, \emph{45}(4), 1191--1207.
-doi:\href{https://doi.org/10.3758/s13428-012-0314-x}{10.3758/s13428-012-0314-x}
-
-\leavevmode\hypertarget{ref-Wickham2016}{}%
-Wickham, H. (2016). Package ` rvest '. Retrieved from \url{https://cran.r-project.org/package=rvest}
-
-\leavevmode\hypertarget{ref-Williams2008}{}%
-Williams, L.
-E., \& Bargh, J.
-A.
-(2008).
-Keeping one's distance.
-\emph{Psychological Science}, \emph{19}(3), 302--308.
-doi:\href{https://doi.org/10.1111/j.1467-9280.2008.02084.x}{10.1111/j.1467-9280.2008.02084.x}
-
-\endgroup
-
-\newpage
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:appendix_mfd}Moral Foundations Dictionary}
-
-\small{
-
-\begin{tabular}{lcccc}
-\toprule
-Harm/Care & Fairness/Reciprocity & Ingroup/Loyalty & Authority/Respect & Purity/Sanctity\\
-\midrule
-abuse & balance & collect & abide & abstain\\
-attack & bias & community & authority & adultery\\
-benefit & constant & deceive & class & church\\
-care & discriminate & desert & command & clean\\
-cruel & equal & family & control & dirt\\
-crush & equate & fellow & defect & disease\\
-damage & even & foreign & defer & disgust\\
-danger & exclude & group & defy & gross\\
-defend & fair & individual & desert & innocent\\
-destroy & favor & member & duty & modest\\
-fight & honest & nation & faith & preserve\\
-guard & impartial & side & father & promiscuous\\
-harm & just & together & honor & pure\\
-hurt & justify & trait & law & right\\
-kill & prefer & unite & lead & ruin\\
-preserve & prejudice &  & legal & sacred\\
-protect & reason &  & mother & sick\\
-ruin & right &  & obey & sin\\
-safe & tolerate &  & oppose & trash\\
-shelter &  &  & order & whole\\
-spurn &  &  & permit & \\
-stomp &  &  & position & \\
-suffer &  &  & preserve & \\
-sympathy &  &  & protest & \\
-violent &  &  & refuse & \\
-war &  &  & respect & \\
- &  &  & revere & \\
- &  &  & serve & \\
- &  &  & tradition & \\
- &  &  & trait & \\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Original Moral Foundations Dictionary from Graham et al. (2009)}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+\url{https://doi.org/10.3758/s13428-012-0314-x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
+Wickham, H. (2016). {Package ` rvest '}. Retrieved from \url{https://cran.r-project.org/package=rvest}
+
+\end{CSLReferences}
 

### 2022-03-03 manuscript_version/manuscript_metapsych.Rmd
update for tables why do they hate me

@@
 library(reshape)
+library(knitr)
 
@@
 
-```{r scraping, eval=FALSE, include=FALSE}
-
-library(rvest)
-####NY Times####
-#Specifying the url for desired website to be scrapped
-url <- 'https://www.nytimes.com/section/politics'
-
-#Reading the HTML code from the website - headlines
-webpage <- read_html(url)
-headline_data = html_nodes(webpage,'.story-link a, .story-body a')
-
-attr_data = html_attrs(headline_data) 
-attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep("http", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.story-content')
-
-  ##pull the text
-  text_data = html_text(headline_data)
-
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-    } ##end for loop
-
-####NPR original front page####
-url2 = 'https://www.npr.org/sections/politics/'
-webpage2 = read_html(url2)
-headline_data2 = html_nodes(webpage2,'.title a')
-
-#URLs
-attr_data2 = html_attrs(headline_data2) 
-attr_data2
-
-urlslist2 = unlist(attr_data2)
-urlslist2 = urlslist2[grep("http", urlslist2)]
-urlslist2
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist2), ncol = 3)
-colnames(NPRDF) = c("Source", "Url", "Text")
-NPRDF = as.data.frame(NPRDF)
-
-##for loops
-for (i in 1:length(urlslist2)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist2[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'#storytext > p')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  NPRDF$Source[i] = "NPR"
-  NPRDF$Url[i] = urlslist2[i]
-  NPRDF$Text[i] = paste(text_data2, collapse = "")
-} ##end for loop
-
-####Fox News####
-url3 = 'http://www.foxnews.com/politics.html'
-url3.1 = 'http://www.foxnews.com/category/politics/executive.html'
-url3.2 = 'http://www.foxnews.com/category/politics/senate.htm.html'
-url3.3 = 'http://www.foxnews.com/category/politics/house-representatives.html'
-url3.4 = 'http://www.foxnews.com/category/politics/judiciary.html'
-url3.5 = 'http://www.foxnews.com/category/politics/foreign-policy.html'
-url3.6 = 'http://www.foxnews.com/category/politics/elections.html'
-webpage3 = read_html(url3)
-webpage3.1 = read_html(url3.1)
-webpage3.2 = read_html(url3.2)
-webpage3.3 = read_html(url3.3)
-webpage3.4 = read_html(url3.4)
-webpage3.5 = read_html(url3.5)
-webpage3.6 = read_html(url3.6)
-
-headline_data3 = html_nodes(webpage3, '.story- a , .article-list .title a')
-headline_data3.1 = html_nodes(webpage3.1, '.story- a , .article-list .title a')
-headline_data3.2 = html_nodes(webpage3.2, '.story- a , .article-list .title a')
-headline_data3.3 = html_nodes(webpage3.3, '.story- a , .article-list .title a')
-headline_data3.4 = html_nodes(webpage3.4, '.story- a , .article-list .title a')
-headline_data3.5 = html_nodes(webpage3.5, '.story- a , .article-list .title a')
-headline_data3.6 = html_nodes(webpage3.6, '.story- a , .article-list .title a')
-
-#headline_data = html_text(headline_data)
-head(headline_data3)
-
-attr_data3 = html_attrs(headline_data3) 
-attr_data3.1 = html_attrs(headline_data3.1) 
-attr_data3.2 = html_attrs(headline_data3.2) 
-attr_data3.3 = html_attrs(headline_data3.3) 
-attr_data3.4 = html_attrs(headline_data3.4) 
-attr_data3.5 = html_attrs(headline_data3.5) 
-attr_data3.6 = html_attrs(headline_data3.6)
-
-attr_data3
-
-urlslist3 = c(unlist(attr_data3), unlist(attr_data3.1), 
-              unlist(attr_data3.2), unlist(attr_data3.3), 
-              unlist(attr_data3.4), unlist(attr_data3.5, attr_data3.6))
-##find all that are href
-urlslist3 = urlslist3[grep("http|.html", urlslist3)]
-##fix the ones without the leading foxnews.com
-urlslist3F = paste("http://www.foxnews.com", urlslist3[grep("^http", urlslist3, invert = T)], sep = "")
-urlslist3N = urlslist3[grep("^http", urlslist3)]
-urlslist3 = c(urlslist3N, urlslist3F)
-urlslist3 = unique(urlslist3)
-urlslist3
-
-##start a data frame
-FoxDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(FoxDF) = c("Source", "Url", "Text")
-FoxDF = as.data.frame(FoxDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage3 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data3 = html_nodes(webpage3,'p+ p , .fn-video+ p , .twitter+ p , .speakable')
-
-  ##pull the text
-  text_data3 = html_text(headline_data3)
-
-  ##save the data
-  FoxDF$Source[i] = "Fox News"
-  FoxDF$Url[i] = urlslist3[i]
-  FoxDF$Text[i] = paste(text_data3, collapse = "")
-} ##end for loop
-
-####Breitbart####
-url4 = 'http://www.breitbart.com/big-government/'
-webpage4 = read_html(url4)
-headline_data4 = html_nodes(webpage4, '.title a , #grid-block-0 span , #BBTrendUL a , #disqus-popularUL a , font')
-#headline_data4 = html_text(headline_data4)
-head(headline_data4)
-
-attr_data4 = html_attrs(headline_data4) 
-attr_data4
-
-urlslist4 = unlist(attr_data4)
-##find all that are href
-urlslist4 = urlslist4[grep("http|/big-government", urlslist4)]
-##fix the ones without the leading bb
-urlslist4F = paste("http://www.breitbart.com", urlslist4[grep("^http", urlslist4, invert = T)], sep = "")
-urlslist4N = urlslist4[grep("^http", urlslist4)]
-urlslist4 = c(urlslist4N, urlslist4F)
-urlslist4 = unique(urlslist4)
-urlslist4
-
-##start a data frame
-BreitbartDF = matrix(NA, nrow = length(urlslist4), ncol = 3)
-colnames(BreitbartDF) = c("Source", "Url", "Text")
-BreitbartDF = as.data.frame(BreitbartDF)
-
-##for loops
-for (i in 1:length(urlslist4)){
-
-  ##read in the URL
-  webpage4 <- read_html(urlslist4[i])
-
-  ##pull the specific nodes
-  headline_data4 = html_nodes(webpage4,'.entry-content p , h2')
-
-  ##pull the text
-  text_data4 = html_text(headline_data4)
-
-  ##save the data
-  BreitbartDF$Source[i] = "Breitbart"
-  BreitbartDF$Url[i] = urlslist4[i]
-  BreitbartDF$Text[i] = paste(text_data4, collapse = "")
-} ##end for loop
-
-####NPR Archive####
-url5 = 'https://www.npr.org/sections/politics/archive'
-webpage5 = read_html(url5)
-headline_data5 = html_nodes(webpage5,'.title a')
-#headline_data = html_text(headline_data)
-#head(headline_data)
-
-#URLs
-attr_data5 = html_attrs(headline_data5) 
-attr_data5
-
-urlslist5 = unlist(attr_data5)
-urlslist5 = urlslist5[grep("http", urlslist5)]
-urlslist5
-
-##start a data frame
-NPRArchiveDF = matrix(NA, nrow = length(urlslist5), ncol = 3)
-colnames(NPRArchiveDF) = c("Source", "Url", "Text")
-NPRArchiveDF = as.data.frame(NPRArchiveDF)
-
-##for loops
-for (i in 1:length(urlslist5)){
-
-  ##read in the URL
-  webpage5 <- read_html(urlslist5[i])
-
-  ##pull the specific nodes
-  headline_data5 = html_nodes(webpage5,'#storytext > p')
-
-  ##pull the text
-  text_data5 = html_text(headline_data5)
-
-  ##save the data
-  NPRArchiveDF$Source[i] = "NPR"
-  NPRArchiveDF$Url[i] = urlslist5[i]
-  NPRArchiveDF$Text[i] = paste(text_data5, collapse = "")
-} ##end for loop
-
-####put together####
-##set your working directory
-setwd("~/OneDrive - Missouri State University/RESEARCH/2 projects/Will-Pilot")
-
-##import the overalldata 
-overalldata = read.csv("../exp1_data/overalldata.csv")
-
-##combine with new data (add the other DF names in here...)
-newdata = rbind(overalldata, NYtimesDF, NPRDF, FoxDF, BreitbartDF, NPRArchiveDF)
-
-#temp NPR updates
-#newdata = newdata[ , -4]
-#newdata = rbind(newdata, NPRArchiveDF)
-
-#change politics archive to NPR, so we can eliminate dupes
-#newdata$Source[newdata$Source == "NPR Politics Archive"] = "NPR"
-#newdata$Source = droplevels(newdata$Source)
-
-##make the newdata unique in case of overlap across days
-newdata = unique(newdata)
-
-##write it back out
-#write.csv(newdata, "overalldata.csv", row.names = F)
-
-##number of articles
-table(newdata$Source)
-
-##number of words
-library(ngram)
-newdata$Text = as.character(newdata$Text)
-for (i in 1:nrow(newdata)) {
-
-  #newdata$writing[i] = preprocess(newdata$Text[i], case="lower", remove.punct=TRUE)
-  newdata$wordcount[i] = string.summary(newdata$Text[i])$words
-
-}
-
-tapply(newdata$wordcount, newdata$Source, mean)
-tapply(newdata$wordcount, newdata$Source, sum)
-
+```{r include = F, eval = F}
+# to see the web scraping and data cleanup for this section see web_scraping.Rmd
+# this code was run previously to create the data for this manuscript
+# note that website changes to places like the NYT means it likely does
+# not run in the same way anymore 
 ```
@@
 At this point, duplicate articles were discarded.
-
-```{r data-cleanup, eval=FALSE, include=FALSE}
-##pull in the data
-master = read.csv("../exp1_data/overalldata.csv", stringsAsFactors = F)
-
-##get rid of the blank stuff
-library(ngram)
-
-for (i in 1:nrow(master)) {
-  master$wordcount[i] = wordcount(master$Text[i])
-}
-
-nozero = subset(master, wordcount > 0)
-tapply(nozero$wordcount, nozero$Source, mean)
-tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones
-nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##figure out the duplicates
-nodis$URLS = duplicated(nodis$Url)
-
-##all data
-final = subset(nodis, URLS == FALSE)
-
-tapply(final$wordcount, final$Source, mean)
-tapply(final$wordcount, final$Source, sum)
-
-write.csv(final, "finaldata.csv")
-
-```
 
@@
 ```{r stem_text, eval=TRUE, include=FALSE}
-
 final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
@@
 
-```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}
-
+```{r exp1_descriptive_calc, echo = F, include = F}
 final$uniquewords = NA
@@
 tableprint = tableprint[c(3, 4, 1, 2) , ]
-
+```
+
+```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
 #change this to match
@@
           escape = F,
-          align = c("l", rep("c", 6)), 
-          font_size = 'footnotesize',
-          placement = 'pt'
+          align = c("l", rep("c", 10)), 
+          font_size = 'footnotesize'
           )
@@
 
-```{r exp1-table, results = 'asis', echo = F}
+```{r exp1_table_calc, include = F, echo = F}
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+tableprint2 = matrix(NA, ncol = 8, nrow = 5)
+colnames(tableprint2) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
 
@@
 #put in the numbers
-tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
+tableprint2[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
                     summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                     harm_d$d)
-tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
+tableprint2[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
                     summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                     fair_d$d)
-tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
+tableprint2[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
                     summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                     ingroup_d$d)
-tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
+tableprint2[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
                     summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                     authority_d$d)
-tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
+tableprint2[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
                     summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
@@
 
-tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
-tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
-
-apa_table(tableprint,
+tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]))
+tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
+```
+
+```{r exp1-table, results = 'asis', echo = F}
+apa_table(as.data.frame(tableprint2),
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
@@
           align = c("l", rep("c", 7)),
-          font_size = 'footnotesize',
-          placement = 'pt'
+          font_size = 'footnotesize'
           )
@@
 
-```{r NYTimes_kav, eval = F, include = F}
-
-library(rvest)
-library(RSelenium)
-
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#page for NYTIMES
-url <- 'https://www.nytimes.com/search?endDate=20181011&query=kavanaugh&sort=best&startDate=20180913'
-
-#navigate to it
-remDr$navigate(url)
-
-#click the button 
-#don't change class name
-#right click --> inspect element 
-webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
-
-#with 752 results at 10 per page we need
-#752 - 10 original = 742 / 10 per click = 75 clicks
-
-for (i in 1:75) { #change this to 75 later
-  webElem$clickElement()
-  Sys.sleep(runif(1, 1, 5))
-}
-
-webpage <-remDr$getPageSource()
-
-#Reading the HTML code from the website - headlines
-webpage2 <- read_html(unlist(webpage))
-
-headline_data = html_nodes(webpage2,'a')
-
-attr_data = html_attrs(headline_data) 
-attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep(".html", urlslist)]
-urlslist = urlslist[grep("/2018", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-#paste NY on front
-urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
-
-  ##pull the text
-  text_data = html_text(headline_data)
-
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-  Sys.sleep(runif(1, 1, 10)) #don't make them angry
-} ##end for loop
-
-write.csv(NYtimesDF, "NYtimes_kav.csv", row.names = F)
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-```
-
-```{r NYTimes_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#page for NYTIMES
-url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'
-
-#navigate to it
-remDr$navigate(url)
-
-#click the button 
-#don't change class name
-#right click --> inspect element 
-webElem <- remDr$findElement(using = 'class name',"css-1t62hi8")
-
-#with 803 results at 10 per page we need
-#803 - 10 original / 10 per click is 80 clicks
-
-for (i in 1:80) {
-  webElem$clickElement()
-  Sys.sleep(runif(1, 1, 5))
-}
-
-webpage <-remDr$getPageSource()
-
-#Reading the HTML code from the website - headlines
-webpage2 <- read_html(unlist(webpage))
-
-headline_data = html_nodes(webpage2,'a')
-
-attr_data = html_attrs(headline_data) 
-#attr_data
-
-urlslist = unlist(attr_data)
-urlslist = urlslist[grep(".html", urlslist)]
-urlslist = urlslist[grep("/201", urlslist)]
-urlslist = unique(urlslist)
-urlslist
-
-#paste NY on front
-urlslist = paste("https://www.nytimes.com", urlslist, sep = "")
-
-##start a data frame
-NYtimesDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(NYtimesDF) = c("Source", "Url", "Text")
-NYtimesDF = as.data.frame(NYtimesDF)
-
-##for loops
-for (i in 1:length(urlslist)){
-
-  ##read in the URL
-  webpage <- read_html(urlslist[i])
-
-  ##pull the specific nodes
-  headline_data = html_nodes(webpage,'.StoryBodyCompanionColumn')
-
-  ##pull the text
-  text_data = html_text(headline_data)
-
-  ##save the data
-  NYtimesDF$Source[i] = "NY Times"
-  NYtimesDF$Url[i] = urlslist[i]
-  NYtimesDF$Text[i] = paste(text_data, collapse = "")
-  Sys.sleep(runif(1, 1, 10)) #don't make them angry
-} ##end for loop
-
-write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
-beep(sound = 5)
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-```
-
-```{r NPR_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-##loop through the page number at the end until done with ~1000 / 20 = 50
-for (i in 1:50) { ##change this to 50
-
-  url = paste0('https://www.npr.org/search?query=kavanaugh&page=', i)
-
-  #navigate to it
-  remDr$navigate(url)
-
-  #scroll on the page
-  webscroll <- remDr$findElement("css", "body")
-  webscroll$sendKeysToElement(list(key = "end"))
-
-  #get the links
-  webElems <- remDr$findElements(using = "css", "[href]")
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-} #close the loop
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-urlslist = unlist(urlslist_final)
-#find all the ones with /2018/
-urlslist2 = urlslist[grep("/2018", urlslist)]
-urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
-urlslist2 = unique(urlslist2)
-temp = strsplit(urlslist2, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#deal with the ones with extra parts
-temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`4` == 2018 & #must be 2018 and 
-                         (temp2$`5` == "09" & as.numeric(temp2$`6`)>=13 | 
-                            temp2$`5` == "10" & as.numeric(temp2$`6`)<=11), #Must be 9 or 10 
-                ])
-
-urlslist3 = urlslist2[as.numeric(rows)]
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(NPRDF) = c("Source", "Url", "Text")
-NPRDF = as.data.frame(NPRDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'#storytext > p')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  NPRDF$Source[i] = "NPR"
-  NPRDF$Url[i] = urlslist3[i]
-  NPRDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-beep(sound = 3)
-
-write.csv(NPRDF, "NPR_kav.csv", row.names = F)
-
-```
-
-```{r NPR_shut, eval = F, include = F}
-
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-##loop through the page number at the end until done with ~3316 / 20 = 166
-for (i in 1:166) {
-
-  url = paste0('https://www.npr.org/search?query=government%20shutodwn&page=', i)
-
-  #navigate to it
-  remDr$navigate(url)
-
-  #scroll on the page
-  webscroll <- remDr$findElement("css", "body")
-  webscroll$sendKeysToElement(list(key = "end"))
-
-  #get the links
-  webElems <- remDr$findElements(using = "css", "[href]")
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-} #close the loop
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-urlslist = unlist(urlslist_final)
-#find all the ones with /2018/
-urlslist2 = urlslist[grep("/201", urlslist)]
-urlslist2 = urlslist2[grep("npr.org", urlslist2)] #get rid of wbur
-urlslist2 = unique(urlslist2)
-temp = strsplit(urlslist2, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#deal with the ones with extra parts
-temp2[temp2$`4` == "sections" , 4:8] = temp2[temp2$`4` == "sections" , 6:10]
-
-#pull only the right dates
-rows = rownames(temp2[ (temp2$`4` == 2018 | temp2$`4` == 2019) & #must be 2018/19 and  
-                         (
-                           (temp2$`5` == "12" & as.numeric(temp2$`6`)>8 & temp2$`4` == 2018) | #after dec 12
-                            (temp2$`5`== "01" & temp2$`4` == 2019) | #all of jan
-                            (temp2$`5` == "02" & as.numeric(temp2$`6`)<8 & temp2$`4` == 2019)
-                           ), #before feb 8
-                ])
-
-urlslist3 = urlslist2[as.numeric(rows)]
-
-##start a data frame
-NPRDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(NPRDF) = c("Source", "Url", "Text")
-NPRDF = as.data.frame(NPRDF)
-
-##for loops
-for (i in 315:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'#storytext > p')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  NPRDF$Source[i] = "NPR"
-  NPRDF$Url[i] = urlslist3[i]
-  NPRDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-beep(sound = 3)
-
-write.csv(NPRDF, "NPR_gs.csv", row.names = F)
-```
-
-```{r Slate_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://slate.com/search?q=kavanaugh&via=homepage_nav_search"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#appear to be 10 pages
-for (i in 1:10){
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
-
-  #don't go too fast for the page to load
-  Sys.sleep(runif(1, 1, 5))
-
-  #click on the page number
-  webClick[[i]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones with /2018/
-urlslist2 = urlslist[grep("/2018/10|/2018/09", urlslist)]
-urlslist2 = unique(urlslist2)
-
-#71 articles seems suspiciously low, so also scraped this page
-#https://slate.com/tag/brett-kavanaugh/
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#337 / 20 = 17 pages
-for (i in 1:17){
-
-  url = paste0("https://slate.com/tag/brett-kavanaugh/", i)
-
-  remDr$navigate(url)
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones with /2018/
-urlslist2.1 = urlslist[grep("/2018/10|/2018/09", urlslist)]
-urlslist2.1 = unique(urlslist2.1)
-
-urlslist3 = unique(c(urlslist2, urlslist2.1))
-
-##start a data frame
-SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(SLATEDF) = c("Source", "Url", "Text")
-SLATEDF = as.data.frame(SLATEDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  SLATEDF$Source[i] = "SLATE"
-  SLATEDF$Url[i] = urlslist3[i]
-  SLATEDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-beep(sound = 3)
-
-write.csv(SLATEDF, "SLATE_kav.csv", row.names = F)
-
-```
-
-```{r SLATE_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://slate.com/search?q=government+shutdown"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#appear to be 10 pages
-for (i in 1:10){
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "css", ".gsc-cursor-page")
-
-  #don't go too fast for the page to load
-  Sys.sleep(runif(1, 1, 5))
-
-  #click on the page number
-  webClick[[i]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones from 12 2018 to 02 2019
-urlslist2 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
-urlslist2 = unique(urlslist2)
-
-#60 something articles seems suspiciously low, so also scraped this page
-#https://slate.com/tag/governtment-shutdown
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#354 / 20 = 18 pages
-for (i in 1:18){
-
-  url = paste0("https://slate.com/tag/government-shutdown/", i)
-
-  remDr$navigate(url)
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #don't go too fast
-  Sys.sleep(runif(1, 1, 5))
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-
-#find all the ones with /2018/
-urlslist2.1 = urlslist[grep("/2018/12|/2019/01|/2019/02", urlslist)]
-urlslist2.1 = unique(urlslist2.1)
-
-urlslist3 = unique(c(urlslist2, urlslist2.1))
-
-##start a data frame
-SLATEDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(SLATEDF) = c("Source", "Url", "Text")
-SLATEDF = as.data.frame(SLATEDF)
-
-##for loops
-for (i in 1:length(urlslist3)){
-
-  ##read in the URL
-  webpage2 <- read_html(urlslist3[i])
-
-  ##pull the specific nodes
-  headline_data2 = html_nodes(webpage2,'.slate-paragraph')
-
-  ##pull the text
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  SLATEDF$Source[i] = "SLATE"
-  SLATEDF$Url[i] = urlslist3[i]
-  SLATEDF$Text[i] = paste(text_data2, collapse = "")
-  Sys.sleep(runif(1, 1, 10))
-} ##end for loop
-
-#beep(sound = 3)
-
-write.csv(SLATEDF, "SLATE_gs.csv", row.names = F)
-```
-
-```{r HuffPo_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=kavanaugh&fr=huffpost_desktop-s"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#943 results with 10 per page 94 clicks
-for (i in 1:94){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "class name", "fz-20")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "class name", "next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 3)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-##start a data frame
-HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HUFFPODF) = c("Source", "Url", "Text")
-HUFFPODF = as.data.frame(HUFFPODF)
-int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
-
-for (i in 937:length(urlslist)){
-
-  #convert the url
-  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
-  temp = gsub("%3a", ":", temp)
-  temp = gsub("%2f", "/", temp)
-
-  webpage = read_html(temp)
-  #figure out the date
-  headline_data = html_nodes(webpage, '.timestamp__date--published')
-  text_data = html_text(headline_data)
-  time = unlist(strsplit(text_data, split = "\n| "))[2]
-  time = as.Date(time, format = "%m/%d/%Y")
-
-  if (time %within% int) {
-    ##pull out the text
-    headline_data2 = html_nodes(webpage,'p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HUFFPODF$Source[i] = "HUFFPO"
-    HUFFPODF$Url[i] = urlslist[i]
-    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 3)
-
-write.csv(HUFFPODF, "HUFFPO_kav.csv", row.names = F)
-```
-
-```{r HuffPo_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://search.huffpost.com/search?utf8=%E2%9C%93&p=government+shutdown&fr=huffpost_desktop"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#942 results with 10 per page 94 clicks
-for (i in 1:94){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "class name", "fz-20")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the button to click on 
-  webClick <- remDr$findElements(using = "class name", "next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 2)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-##start a data frame
-HUFFPODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HUFFPODF) = c("Source", "Url", "Text")
-HUFFPODF = as.data.frame(HUFFPODF)
-int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
-
-for (i in 1:length(urlslist)){
-
-  #convert the url
-  temp = paste("https", unlist(strsplit(unlist(strsplit(urlslist[i], "https"))[3], "/RK=0"))[1], sep = "")
-  temp = gsub("%3a", ":", temp)
-  temp = gsub("%2f", "/", temp)
-
-  webpage = read_html(temp)
-  #figure out the date
-  headline_data = html_nodes(webpage, '.timestamp__date--published')
-  text_data = html_text(headline_data)
-  time = unlist(strsplit(text_data, split = "\n| "))[2]
-  time = as.Date(time, format = "%m/%d/%Y")
-
-  if (time %within% int) {
-    ##pull out the text
-    headline_data2 = html_nodes(webpage,'p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HUFFPODF$Source[i] = "HUFFPO"
-    HUFFPODF$Url[i] = urlslist[i]
-    HUFFPODF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 2)
-
-write.csv(HUFFPODF, "HUFFPO_gs.csv", row.names = F)
-```
-
-```{r Politico_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=kavanaugh&pv=&c=&r=&start=09%2F13%2F2018&start_submit=09%2F13%2F2018&end=10%2F11%2F2018&end_submit=10%2F11%2F2018"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#749 with 20 per page with 37 clicks
-
-for (i in 1:37){
-
-  if (i > 1){
-    #navigate to the next page
-    url = paste0("https://www.politico.com/search/", i, 
-                 "?s=newest&q=kavanaugh&adv=true&start=09/13/2018&end=10/11/2018")
-    remDr$navigate(url)
-  }
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 7)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[grep("/2018/", urlslist)]
-urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
-
-##start a data frame
-POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(POLITICODF) = c("Source", "Url", "Text")
-POLITICODF = as.data.frame(POLITICODF)
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  POLITICODF$Source[i] = "POLITICO"
-  POLITICODF$Url[i] = urlslist[i]
-  POLITICODF$Text[i] = paste(text_data2, collapse = "")
-
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-beep(sound = 7)
-
-write.csv(POLITICODF, "POLITICO_kav.csv", row.names = F)
-#easiest one yet
-```
-
-```{r Politico_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.politico.com/search?adv=true&userInitiated=true&s=newest&q=government+shutdown&pv=&c=&r=&start=12%2F08%2F2018&start_submit=12%2F08%2F2018&end=02%2F08%2F2019&end_submit=02%2F08%2F2019"
-
-remDr$navigate(url)
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#1329 with 20 per page with 66 clicks
-
-for (i in 1:66){
-
-  if (i > 1){
-    #navigate to the next page
-    url = paste0("https://www.politico.com/search/", i, 
-                 "?s=newest&q=government shutdown&adv=true&start=12/08/2018&end=02/08/2019")
-    remDr$navigate(url)
-  }
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "[href]")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 7)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[grep("/2018/", urlslist)]
-urlslist = urlslist[-c(grep("subscriber.", urlslist))] #take out the stuff we can't see
-
-##start a data frame
-POLITICODF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(POLITICODF) = c("Source", "Url", "Text")
-POLITICODF = as.data.frame(POLITICODF)
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  POLITICODF$Source[i] = "POLITICO"
-  POLITICODF$Url[i] = urlslist[i]
-  POLITICODF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(POLITICODF, "POLITICO_gs.csv", row.names = F)
-
-```
-
-```{r Fox_kav, eval = F, include = F}
-
-##start a data frame
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-#loop over the results and go through them
-#1651 with 10 per page with 165 clicks
-
-for (i in 1:165){
-
-    #navigate to the page
-    url = paste0("https://www.foxnews.com/search-results/search?q=kavanaugh&ss=fn&min_date=2018-09-13&max_date=2018-10-11&start=",
-                 (i-1)*10)
-    remDr$navigate(url)
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", ".ng-binding")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("video.", urlslist))] #take out videos
-urlslist = urlslist[-c(grep("/search-results", urlslist))] #take out search result fake links
-
-##start a data frame
-FOXDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(FOXDF) = c("Source", "Url", "Text")
-FOXDF = as.data.frame(FOXDF)
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  FOXDF$Source[i] = "FOX"
-  FOXDF$Url[i] = urlslist[i]
-  FOXDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(FOXDF, "FOX_kav.csv", row.names = F)
-```
-
-```{r Breitbart_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.breitbart.com/tag/brett-kavanaugh/"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-for (i in 1:42){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "h2 a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  if (i > 1)
-    {
-  url = paste0("https://www.breitbart.com/tag/brett-kavanaugh/page/",
-               i+1, "/")
-  remDr$navigate(url)
-  }
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
-                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
-                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(BREITBARTDF) = c("Source", "Url", "Text")
-BREITBARTDF = as.data.frame(BREITBARTDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'h2, p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  BREITBARTDF$Source[i] = "BREITBART"
-  BREITBARTDF$Url[i] = urlslist3[i]
-  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(BREITBARTDF, "BREITBART_kav.csv", row.names = F)
-```
-
-```{r Breitbart_gs, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.breitbart.com/tag/government-shutdown/"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-for (i in 1:16){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "h2 a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  if (i > 1)
-    {
-  url = paste0("https://www.breitbart.com/tag/government-shutdown/page/",
-               i+1, "/")
-  remDr$navigate(url)
-  }
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
-                         (
-                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
-                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
-                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
-                         ), #before feb 8
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-BREITBARTDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(BREITBARTDF) = c("Source", "Url", "Text")
-BREITBARTDF = as.data.frame(BREITBARTDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'h2, p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  BREITBARTDF$Source[i] = "BREITBART"
-  BREITBARTDF$Url[i] = urlslist3[i]
-  BREITBARTDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(BREITBARTDF, "BREITBART_gs.csv", row.names = F)
-```
-
-```{r Rush_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.rushlimbaugh.com/?s=kavanaugh&is_v=1"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-##18 pages
-for (i in 1:18){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
-
-  #click on the page number
-  webClick[[18]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ temp2$`5` == 2018 & #must be 2018 and 
-                         (temp2$`6` == "09" & as.numeric(temp2$`7`)>=13 | 
-                            temp2$`6` == "10" & as.numeric(temp2$`7`)<=11), #Must be 9 or 10 
-                       ])
-
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(RUSHDF) = c("Source", "Url", "Text")
-RUSHDF = as.data.frame(RUSHDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  RUSHDF$Source[i] = "RUSH"
-  RUSHDF$Url[i] = urlslist3[i]
-  RUSHDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(RUSHDF, "RUSH_kav.csv", row.names = F)
-```
-
-```{r Rush_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-#create a blank space to put the links
-urlslist_final = list()
-
-url = "https://www.rushlimbaugh.com/?s=government%20shutdown&is_v=1"
-
-remDr$navigate(url)
-
-#loop over the results and go through them
-##47 pages
-for (i in 1:47){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "css", ".ais-pagination--link")
-
-  #click on the page number
-  webClick[[18]]$clickElement()
-
-  #page reload
-  Sys.sleep(runif(1, 1, 5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-beep(sound = 6)
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("store", urlslist))] #take out store
-urlslist = urlslist[grep("/daily/[0-9]*/[0-9]*/[0-9]*/[a-zA-Z]", urlslist)]
-
-##find the right dates
-temp = strsplit(urlslist, split = "/")
-temp2 = plyr::ldply(temp, rbind)
-temp2 = as.data.frame(apply(temp2, 2, as.character), stringsAsFactors = F)
-
-#pull only the right dates
-rows = rownames(temp2[ (temp2$`5` == 2018 | temp2$`5` == 2019) & #must be 2018/19 and  
-                         (
-                           (temp2$`6` == "12" & as.numeric(temp2$`7`)>8 & temp2$`5` == 2018) | #after dec 12
-                             (temp2$`6`== "01" & temp2$`5` == 2019) | #all of jan
-                             (temp2$`6` == "02" & as.numeric(temp2$`7`)<8 & temp2$`5` == 2019)
-                         ), #before feb 8
-                       ])
-urlslist3 = urlslist[as.numeric(rows)]
-
-##start a data frame
-RUSHDF = matrix(NA, nrow = length(urlslist3), ncol = 3)
-colnames(RUSHDF) = c("Source", "Url", "Text")
-RUSHDF = as.data.frame(RUSHDF)
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data2 = html_nodes(webpage,'p') 
-  text_data2 = html_text(headline_data2)
-
-  ##save the data
-  RUSHDF$Source[i] = "RUSH"
-  RUSHDF$Url[i] = urlslist3[i]
-  RUSHDF$Text[i] = paste(text_data2, collapse = "")
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(RUSHDF, "RUSH_gs.csv", row.names = F)
-
-```
-
-```{r Blaze_kav, eval = F, include = F}
-url9 = 'https://www.theblaze.com/search/?q=kavanaugh'
-webpage9 = read_html(url9)
-headline_data9 = html_nodes(webpage9, '.widget__headline-text')
-
-attr_data9 = html_attrs(headline_data9) 
-attr_data9
-
-urlslist9 = unlist(attr_data9)
-urlslist9 = urlslist9[grep(urlslist9)]
-
-##start a data frame
-BlazeDF = matrix(NA, nrow = length(urlslist9), ncol = 3)
-colnames(BlazeDF) = c("Source", "Url", "Text")
-BlazeDF = as.data.frame(BlazeDF)
-
-##for loops
-for (i in 1:length(urlslist9)){
-
-  ##read in the URL
-  webpage9 <- read_html(urlslist9[i])
-
-  ##pull the specific nodes
-  headline_data9 = html_nodes(webpage9,'p')
-
-  ##pull the text
-  text_data9 = html_text(headline_data9)
-
-  ##save the data
-  BlazeDF$Source[i] = "The Blaze"
-  BlazeDF$Url[i] = urlslist9[i]
-  BlazeDF$Text[i] = paste(text_data9, collapse = "")
-} ##end for loop
-```
-
-```{r Blaze_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.theblaze.com/search/?q=government+shutdown"
-
-remDr$navigate(url)
-
-webClick <- remDr$findElements(using = "css", ".action-btn")
-
-#click next until done
-while (length(webClick) > 0 ) {
-
-  #find the urls for page X
-  webClick <- remDr$findElements(using = "css", ".action-btn")
-
-  webClick[[1]]$clickElement()
-
-  Sys.sleep(runif(1, 1, 5))
-}
-
-#find the urls for page X
-webElems <- remDr$findElements(using = "css", "a")
-
-#add the urls to a list
-urlslist_final = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-##deal with the URLS
-urlslist = urlslist_final
-urlslist = unique(urlslist)
-urlslist = urlslist[-c(grep("video/", urlslist))]
-urlslist = urlslist[grep("/news/", urlslist)]
-urlslist = urlslist[-c(grep("/201[3-7]", urlslist))]
-
-##start a data frame
-BLAZEDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(BLAZEDF) = c("Source", "Url", "Text")
-BLAZEDF = as.data.frame(BLAZEDF)
-int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
-
-for (i in 1:length(urlslist)){
-
-  webpage = read_html(urlslist[i])
-
-  headline_data = html_nodes(webpage, '.post-date')
-  text_data = html_text(headline_data)
-  date = as.Date(text_data, "%B %d, %Y")
-
-  if (date %within% int){
-    headline_data2 = html_nodes(webpage,'h1, h3, p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    BLAZEDF$Source[i] = "BLAZE"
-    BLAZEDF$Url[i] = urlslist[i]
-    BLAZEDF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(BLAZEDF, "BLAZE_gs.csv", row.names = F)
-
-```
-
-```{r Hannity_kav, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.hannity.com/trending/brett-kavanaugh/"
-
-remDr$navigate(url)
-
-urlslist_final = list()
-
-for (i in 1:4){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #move on to the next page
-  url = paste0("https://www.hannity.com/trending/brett-kavanaugh/?pg=", i+1)
-
-  remDr$navigate(url)
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-#also use google search to see if we can find more
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.google.com/search?q=kavanaugh+site%3Ahannity.com&source=lnt&tbs=cdr%3A1%2Ccd_min%3A9%2F13%2F2018%2Ccd_max%3A10%2F11%2F2018&tbm="
-
-remDr$navigate(url)
-
-urlslist_final2 = list()
-
-for (i in 1:3){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "link text", "Next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-urlslist2 = unlist(urlslist_final2)
-urlslist2 = c(urlslist, urlslist2)
-urlslist2 = unique(urlslist2)
-urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
-urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
-urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
-
-##start a data frame
-HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HANNITYDF) = c("Source", "Url", "Text")
-HANNITYDF = as.data.frame(HANNITYDF)
-int <- interval(ymd("2018-09-13"), ymd("2018-10-11"))
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data = html_nodes(webpage, '.author-info')
-  text_data = html_text(headline_data)
-  text_data = strsplit(text_data, " ")[[1]][7]
-  date = as.Date(text_data, "%m.%d.%y")
-
-  if (date %within% int){
-    headline_data2 = html_nodes(webpage,'h1, p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HANNITYDF$Source[i] = "HANNITY"
-    HANNITYDF$Url[i] = urlslist3[i]
-    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(HANNITYDF, "HANNITY_kav.csv", row.names = F)
-```
-
-```{r Hannity_shut, eval = F, include = F}
-library(rvest)
-library(RSelenium)
-library(beepr)
-library(lubridate)
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "http://www.hannity.com/trending/shutdown/"
-
-remDr$navigate(url)
-
-urlslist_final = list()
-
-for (i in 1:4){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #move on to the next page
-  url = paste0("http://www.hannity.com/trending/shutdown/?pg=", i+1)
-
-  remDr$navigate(url)
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-##deal with the URLS
-urlslist = unlist(urlslist_final)
-urlslist = unique(urlslist)
-
-#also use google search to see if we can find more
-
-#open the browser
-rD <- rsDriver(browser=c("chrome"), chromever="73.0.3683.68")
-remDr <- rD[["client"]]
-
-url = "https://www.google.com/search?biw=1366&bih=632&tbs=cdr%3A1%2Ccd_min%3A12%2F8%2F2018%2Ccd_max%3A2%2F8%2F2019&ei=gECaXNe8Aaft_Qb9w7G4BA&q=government+shutdown+site%3Ahannity.com&oq=government+shutdown+site%3Ahannity.com&gs_l=psy-ab.3...0.0..1915...0.0..0.0.0.......0......gws-wiz.aFps0nA33mY"
-
-remDr$navigate(url)
-
-urlslist_final2 = list()
-
-for (i in 1:9){
-
-  #find the urls for page X
-  webElems <- remDr$findElements(using = "css", "a")
-
-  #add the urls to a list
-  urlslist_final2[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
-
-  #find the thing to click on 
-  webClick <- remDr$findElements(using = "link text", "Next")
-
-  #click on the page number
-  webClick[[1]]$clickElement()
-
-  Sys.sleep(runif(1,1,5))
-
-}
-
-remDr$close()
-# stop the selenium server
-rD[["server"]]$stop()
-
-urlslist2 = unlist(urlslist_final2)
-urlslist2 = c(urlslist, urlslist2)
-urlslist2 = unique(urlslist2)
-urlslist3 = urlslist2[grep("/media-room/[a-zA-Z]", urlslist2)]
-urlslist3 = urlslist3[-c(grep("webcache", urlslist3))]
-urlslist3 = urlslist3[-c(grep("radio-show", urlslist3))]
-
-##start a data frame
-HANNITYDF = matrix(NA, nrow = length(urlslist), ncol = 3)
-colnames(HANNITYDF) = c("Source", "Url", "Text")
-HANNITYDF = as.data.frame(HANNITYDF)
-int <- interval(ymd("2018-12-08"), ymd("2019-02-08"))
-
-for (i in 1:length(urlslist3)){
-
-  webpage = read_html(urlslist3[i])
-
-  headline_data = html_nodes(webpage, '.author-info')
-  text_data = html_text(headline_data)
-  text_data = strsplit(text_data, " ")[[1]][7]
-  date = as.Date(text_data, "%m.%d.%y")
-
-  if (date %within% int){
-    headline_data2 = html_nodes(webpage,'h1, p') 
-    text_data2 = html_text(headline_data2)
-
-    ##save the data
-    HANNITYDF$Source[i] = "HANNITY"
-    HANNITYDF$Url[i] = urlslist3[i]
-    HANNITYDF$Text[i] = paste(text_data2, collapse = "")
-  }
-
-  Sys.sleep(runif(1,1,10))
-
-  }
-
-beep(sound = 7)
-
-write.csv(HANNITYDF, "HANNITY_gs.csv", row.names = F)
-
+```{r include = F, echo = F}
+# please see the web_scraping.Rmd to see how we originally collected this data
 ```
@@
 
-```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
+```{r exp2_descriptive_calculate_kav, include = F, echo = F}
 #Kav
@@
 final_kav$valenceavg = NA
-
 for (i in 1:nrow(final_kav)){
@@
   final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
-
-}
-
+}
 # tapply(final_kav$valenceavg, final_kav$Source, mean)
@@
 # tapply(final_kav$wordcount, final_kav$Source, sum)
-
 library(quanteda)
-
 final_kav$FK = NA
-
 for (i in 1:nrow(final_kav)){
@@
 }
-
 # tapply(final_kav$FK, final_kav$Source, mean)
 # tapply(final_kav$FK, final_kav$Source, sd)
-
 #Kav Table
 ####build the table here####
-tableprint = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint[ , 1] = unique(final_kav$Source)
-tableprint[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
+tableprint3 = matrix(NA, nrow=10, ncol=11)
+colnames(tableprint3) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
+#tableprint3[ , 1] = unique(final_kav$Source)
+tableprint3[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
                      "Huffington Post", "NPR", "New York Times", "Politico",
                      "Rush Limbaugh", "Slate")
-tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
-tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
-tableprint[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
-tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
-tableprint[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
-tableprint[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
-tableprint[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
-tableprint[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
-tableprint[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
-tableprint[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
-
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
-
-tableprint = tableprint[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
-
+tableprint3[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
+tableprint3[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
+tableprint3[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
+tableprint3[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
+tableprint3[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
+tableprint3[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
+tableprint3[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
+tableprint3[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
+tableprint3[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
+tableprint3[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
+tableprint3[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint3[ , c(2,3,6,7,8,9,10,11)]))
+tableprint3 = tableprint3[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
+```
+
+```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
 #change this to match
-apa_table(as.data.frame(tableprint),
+apa_table(as.data.frame(tableprint3),
           note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
@@
           escape = F,
-          small = T,
-          align = c("l", rep("c", 6)),
-          font_size = 'footnotesize',
-          placement = 'pt'
+          align = c("l", rep("c", 10)),
+          font_size = 'footnotesize'
           )
@@
 
-```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
+```{r exp2_descriptive_calculate_gs}
 #GS
@@
 ####build the table here####
-tableprint = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint[ , 1] = unique(final_gs$Source)
-tableprint[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
+tableprint4 = matrix(NA, nrow=10, ncol=11)
+colnames(tableprint4) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
+
+#tableprint4[ , 1] = unique(final_gs$Source)
+tableprint4[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
                      "Huffington Post", "NPR", "New York Times", "Politico",
                      "Rush Limbaugh", "Slate")
-tableprint[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
-tableprint[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
-tableprint[ , 4] = tapply(final_gs$valenceavg, final_gs$Source, length)
-tableprint[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
-tableprint[ , 6] = tapply(final_gs$wordcount, final_gs$Source, mean)
-tableprint[ , 7] = tapply(final_gs$wordcount, final_gs$Source, sd)
-tableprint[ , 8] = tapply(final_gs$uniquewords, final_gs$Source, mean)
-tableprint[ , 9] = tapply(final_gs$uniquewords, final_gs$Source, sd)
-tableprint[ , 10] = tapply(final_gs$FK, final_gs$Source, mean)
-tableprint[ , 11] = tapply(final_gs$FK, final_gs$Source, sd)
-
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
-
-tableprint = tableprint[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
-
+tableprint4[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
+tableprint4[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
+tableprint4[ , 4] = tapply(final_gs$valenceavg, final_gs$Source, length)
+tableprint4[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
+tableprint4[ , 6] = tapply(final_gs$wordcount, final_gs$Source, mean)
+tableprint4[ , 7] = tapply(final_gs$wordcount, final_gs$Source, sd)
+tableprint4[ , 8] = tapply(final_gs$uniquewords, final_gs$Source, mean)
+tableprint4[ , 9] = tapply(final_gs$uniquewords, final_gs$Source, sd)
+tableprint4[ , 10] = tapply(final_gs$FK, final_gs$Source, mean)
+tableprint4[ , 11] = tapply(final_gs$FK, final_gs$Source, sd)
+
+tableprint4[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint4[ , c(2,3,6,7,8,9,10,11)]))
+
+tableprint4 = tableprint4[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
+```
+
+```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
 #change this to match
-apa_table(as.data.frame(tableprint),
+apa_table(as.data.frame(tableprint4),
           note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
@@
           escape = F,
-          small = T, 
-          align = c("l", rep("c", 6)),
-          font_size = 'footnotesize',
-          placement = 'pt'
+          align = c("l", rep("c", 10)),
+          font_size = 'footnotesize'
           )
@@
 
-```{r exp2-tablekav, results = 'asis', echo = F}
+```{r exp2_kav_calc, include = F, echo = F}
 #MFD, mean, sd, mean, sd, t, p, d
@@
 tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
-
-apa_table(tableprint_kav,
+```
+
+```{r exp2-tablekav, results = 'asis', echo = F}
+apa_table(as.data.frame(tableprint_kav),
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
@@
 
-```{r exp2-tablegs, results = 'asis', echo = F}
+```{r exp2_gs_calc, include = F, echo = F}
 #MFD, mean, sd, mean, sd, t, p, d
@@
 tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
-
-apa_table(tableprint_gs,
+```
+
+```{r exp2-tablegs, results = 'asis', echo = F}
+apa_table(as.data.frame(tableprint_gs),
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
@@
 Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
+
+\newpage
+
+# References
+
+\begingroup
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2022-03-03 manuscript_version/web_scraping.Rmd
update for tables why do they hate me

--- 2022-01-25 metapsych manuscript/manuscript_metapsych_kj.Rmd
@@
 ---
-title             : "Moral Foundations of U.S. Political News Organizations"
-shorttitle        : "MORAL NEWS"
-
-author: 
-  - name          : "William E. Padfield"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "901 S. National Ave, Springfield, MO, 65897"
-    email         : "Padfield94@live.missouristate.edu"
-  - name          : "Erin M. Buchanan, Ph.D."
-    affiliation   : "2"
-  - name          : "Kayla N. Jordan, Ph.D."
-    affiliation   : "2"
-
-affiliation:
-  - id            : "1"
-    institution   : "Missouri State University"
-  - id            : "2"
-    institution  : "Harrisburg University of Science and Technology"
-
-author_note: |
-  William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.
-
-abstract: |
-  Partisan differences and diviseness have become an increasing hot topic in psychological research.
-Many theories have been proposed to explain these differences and divisions including Moral Foundations Theory.
-The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
-Through web scraping, the researchers extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
-This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, the researchers gathered political articles from four sources.
-We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
-In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
-Supreme Court Justice Brett Kavanaugh and the partial U.S.
-Government Shutdown of 2018-2019.
-Once again, no significant differences in moral endorsements were found.
-Together with past work, the results shed doubt on the validity of the MFD as a measure.
-
-keywords          : "politics, morality, psycholinguistics"
-
-bibliography      : ["will_thesis.bib"] #turn this off right now so it knits
-
-figsintext        : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-lang              : "english"
-class             : "man"
-mask              : no
-output            : papaja::apa6_pdf
-replace_ampersands: yes
-csl               : apa6.csl
+title: "Web Scraping"
+author: "Erin M. Buchanan"
+date: "3/3/2022"
+output: html_document
 ---
 
-```{r load_packages, include = FALSE}
-library(papaja) 
-library(MuMIn)
-library(reshape)
-library(nlme)
-library(ggplot2)
-library(expss)
-library(MOTE)
-
-knitr::opts_chunk$set(cache = TRUE)
-options(tinytex.verbose = TRUE)
-```
-
-The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].Since then, Kohlberg's theory has been highly criticized with numerous theory and hypotheses being proposed to replace it.
-One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham [@Haidt2007].
-While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related issue, the Moral Foundations Dictionary (MFD) [@Graham2009].@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
-Here we first review evidence and criticisms against this assumption.
-We then provide our own test of the MFD using partisan news articles.
-
-## Moral Foundations Dictionary
-
-Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007].
-The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007].
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
-
-In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text.
-The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-@Graham2009 created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.
-
-Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
-Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers.
-However, conservative ministers did not use *ingroup/loyalty* words more than liberals.
-Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].
-
-## Critiques of Moral Foundations
-
-Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-@Suhler2011 criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-Likewise, @Gray2015 argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
-@Schien2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
-
-Beyond the critiques of the theory itself, many have also provided strong critiques of the Moral Foundations Dictionary (MFD).Conducting two close conceptual replication and six extension studies, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.In a meta-analysis, the theorized differences were only found for authority and purity (e.g.
-conservatives used more authority and purity word).
-Loyalty was contrary to theoretical predictions (e.g.
-used more by liberals), and no differences were found for harm and fairness.Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
-Exploring the political Twitterverse, @Sterling2018 found differences in the MFD to depend on political sophistication.
-For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
-While the MFD has not been extensive used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
-
-The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).These attempts generally fall into two categories: human annotations and semantic representations.
-@Hopp2021 represents the first approach where instead of relying on 'experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
-While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
-@Garten2016 represents the second categories which instead relies on data-driven semantic analysis.
-Using shallow learning models like word2vec, moral foundations are measured using semantic similarity vectors rather than simple word counts.
-
-As a further conceptual replication of @Frimer2020, here we test the liberal-conservative difference proposed by MFT using partisan media content and the Moral Foundations Dictionary.
-We first test differences in a general news corpus compared liberal sources (NPR and New York Times) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavaugh's Supreme Court nomination and the Government Shutdown in 2018-19.
-Here the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
-To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Like @Frimer2020, results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.
-
-# Experiment 1
-
-# Method
-
-For Experiment 1, the researchers approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary.
-The researchers hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
-Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
-Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.
-
-## Sources
-
-Political articles were collected from the websites of four notable U.S.
-news sources, a process known as web scraping.
-The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*.
-They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean.
-In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean.
-@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
-
-Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
-For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
-
-Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
-Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
-We later ran a process in order to exclude any duplicate articles.
-*Fox News* presented a similar issue.
-We discovered *Fox News* utilized six URLs in addition to the regular politics page.
-These URLs led to pages containing content pertaining the U.S.
-Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
-Once again, duplicates were subsequently eliminated from any analyses.
-
-## Materials
-
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016].
-Using this dataset, we identified word count and average word count per source.
-This process was completed once daily starting in February 2018 until March 2018.
-Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected in April 2018.
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
+## Libraries
+
+## Experiment 1 Web Scraping Code
 
@@
 
-## Data analysis
-
-Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017].
-This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
-At this point, duplicate articles were discarded.
+## Experiment 1 Data Analysis
 
@@
 
-The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@Feinerer2017].
-The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
-The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
-
-Concurrent research by @Jordan2019 is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples.
-The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
-Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
-
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
-Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurrence were multiplied by their *z*-scored valence.
-Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence.
-Positive values indicate positive valence, and negative values indicate negative valence.
-Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
-
-```{r stem_text, eval=TRUE, include=FALSE}
-
-final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
-final = na.omit(final) #one weird NA line
-
-##load libraries
-library(tm)
-library(ngram)
-
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final)) {
-
-  final$edited[i] = preprocess(final$Text[i], #one value at a time
-           case = "lower", 
-           remove.punct = TRUE,
-           remove.numbers = FALSE, 
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final$stemmed[i] = stemDocument(final$edited[i], language = "english")
-}
-
-```
-
-```{r stem_warriner, include = FALSE}
-##open the Warriner data for later
-warriner = read.csv("../exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
-warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
-
-for(i in 1:nrow(warriner)) {
-  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
-} 
-```
-
-```{r create_datasets_harm, echo = F, include=FALSE}
-#read in the harm total words from the mtmm project
-harm_all = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA" & !is.na(harm_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-harm_final_data = rbind(harm_final_data, temp2)
-}
-
-#pull in the data from Warriner 
-harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
-#fought, safer, spurn
-harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA" & !is.na(fair_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-fair_final_data = rbind(fair_final_data, temp2)
-}
-
-fair_final_data$valence = vlookup(fair_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
-#just plagiar safer
-fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & !is.na(ingroup_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-ingroup_final_data = rbind(ingroup_final_data, temp2)
-}
-
-ingroup_final_data$valence = vlookup(ingroup_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA" & !is.na(authority_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-authority_final_data = rbind(authority_final_data, temp2)
-}
-
-authority_final_data$valence = vlookup(authority_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
-#  abov behind   gase higher  older  taken 
-authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA" & !is.na(purity_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-purity_final_data = rbind(purity_final_data, temp2)
-}
-
-purity_final_data$valence = vlookup(purity_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data$Var1[is.na(purity_final_data$valence) & purity_final_data$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women 
-purity_final_data$valence[purity_final_data$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data$valence[purity_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data$valence[purity_final_data$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r descriptives, echo = F, include = FALSE}
-#summarize the dataset so that you have the total and percent for each foundation 
-# summary(harm_final_data)
-# summary(fair_final_data)
-# summary(ingroup_final_data)
-# summary(authority_final_data)
-# summary(purity_final_data)
-# #report descriptive statistics of the foundations
-# mean(harm_final_data$valence)
-# sd(harm_final_data$valence)
-# mean(fair_final_data$valence)
-# sd(fair_final_data$valence)
-# mean(ingroup_final_data$valence)
-# sd(ingroup_final_data$valence)
-# mean(authority_final_data$valence)
-# sd(authority_final_data$valence)
-# mean(purity_final_data$valence)
-# sd(purity_final_data$valence)
-#note that a big problem is the valence of the words 
-```
-
-```{r analysis_harm, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100
-
-#flatten down to sum by article 
-harm_final_temp = aggregate(harm_final_data$weight, 
-          by = list(harm_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp) = c("URL", "MFDweight")
-
-harm_final_temp$lean[grepl("nytimes.com", harm_final_temp$URL) |
-                       grepl("npr.org", harm_final_temp$URL)] = "Liberal"
-harm_final_temp$lean[grepl("breitbart.com", harm_final_temp$URL) |
-                       grepl("foxnews.com", harm_final_temp$URL)] = "Conservative"
-
-harm_final_temp$Source[grepl("nytimes.com", harm_final_temp$URL)] = "NY Times"
-harm_final_temp$Source[grepl("npr.org", harm_final_temp$URL)] = "NPR"
-harm_final_temp$Source[grepl("foxnews.com", harm_final_temp$URL)] = "Fox"
-harm_final_temp$Source[grepl("breitbart.com", harm_final_temp$URL)] = "Breitbart"
-
-harm_model = lme(MFDweight ~ lean, 
-                 data = harm_final_temp, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model)
-```
-
-```{r analysis_fair, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data$weight = fair_final_data$Freq * fair_final_data$valence / fair_final_data$wordcount * 100
-
-#flatten down to sum by article 
-fair_final_temp = aggregate(fair_final_data$weight, 
-          by = list(fair_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp) = c("URL", "MFDweight")
-
-fair_final_temp$lean[grepl("nytimes.com", fair_final_temp$URL) |
-                       grepl("npr.org", fair_final_temp$URL)] = "Liberal"
-fair_final_temp$lean[grepl("breitbart.com", fair_final_temp$URL) |
-                       grepl("foxnews.com", fair_final_temp$URL)] = "Conservative"
-
-fair_final_temp$Source[grepl("nytimes.com", fair_final_temp$URL)] = "NY Times"
-fair_final_temp$Source[grepl("npr.org", fair_final_temp$URL)] = "NPR"
-fair_final_temp$Source[grepl("foxnews.com", fair_final_temp$URL)] = "Fox"
-fair_final_temp$Source[grepl("breitbart.com", fair_final_temp$URL)] = "Breitbart"
-
-fair_model = lme(MFDweight ~ lean, 
-                 data = fair_final_temp, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model)
-```
-
-```{r analysis_ingroup, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data$weight = ingroup_final_data$Freq * ingroup_final_data$valence / ingroup_final_data$wordcount * 100
-
-#flatten down to sum by article 
-ingroup_final_temp = aggregate(ingroup_final_data$weight, 
-          by = list(ingroup_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp) = c("URL", "MFDweight")
-
-ingroup_final_temp$lean[grepl("nytimes.com", ingroup_final_temp$URL) |
-                       grepl("npr.org", ingroup_final_temp$URL)] = "Liberal"
-ingroup_final_temp$lean[grepl("breitbart.com", ingroup_final_temp$URL) |
-                       grepl("foxnews.com", ingroup_final_temp$URL)] = "Conservative"
-
-ingroup_final_temp$Source[grepl("nytimes.com", ingroup_final_temp$URL)] = "NY Times"
-ingroup_final_temp$Source[grepl("npr.org", ingroup_final_temp$URL)] = "NPR"
-ingroup_final_temp$Source[grepl("foxnews.com", ingroup_final_temp$URL)] = "Fox"
-ingroup_final_temp$Source[grepl("breitbart.com", ingroup_final_temp$URL)] = "Breitbart"
-
-ingroup_model = lme(MFDweight ~ lean, 
-                 data = ingroup_final_temp, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model)
-```
-
-```{r analysis_authority, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data$weight = authority_final_data$Freq * authority_final_data$valence / authority_final_data$wordcount * 100
-
-#flatten down to sum by article 
-authority_final_temp = aggregate(authority_final_data$weight, 
-          by = list(authority_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp) = c("URL", "MFDweight")
-
-authority_final_temp$lean[grepl("nytimes.com", authority_final_temp$URL) |
-                       grepl("npr.org", authority_final_temp$URL)] = "Liberal"
-authority_final_temp$lean[grepl("breitbart.com", authority_final_temp$URL) |
-                       grepl("foxnews.com", authority_final_temp$URL)] = "Conservative"
-
-authority_final_temp$Source[grepl("nytimes.com", authority_final_temp$URL)] = "NY Times"
-authority_final_temp$Source[grepl("npr.org", authority_final_temp$URL)] = "NPR"
-authority_final_temp$Source[grepl("foxnews.com", authority_final_temp$URL)] = "Fox"
-authority_final_temp$Source[grepl("breitbart.com", authority_final_temp$URL)] = "Breitbart"
-
-authority_model = lme(MFDweight ~ lean, 
-                 data = authority_final_temp, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model)
-```
-
-```{r analysis_purity, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data$weight = purity_final_data$Freq * purity_final_data$valence / purity_final_data$wordcount * 100
-
-#flatten down to sum by article 
-purity_final_temp = aggregate(purity_final_data$weight, 
-          by = list(purity_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp) = c("URL", "MFDweight")
-
-purity_final_temp$lean[grepl("nytimes.com", purity_final_temp$URL) |
-                       grepl("npr.org", purity_final_temp$URL)] = "Liberal"
-purity_final_temp$lean[grepl("breitbart.com", purity_final_temp$URL) |
-                       grepl("foxnews.com", purity_final_temp$URL)] = "Conservative"
-
-purity_final_temp$Source[grepl("nytimes.com", purity_final_temp$URL)] = "NY Times"
-purity_final_temp$Source[grepl("npr.org", purity_final_temp$URL)] = "NPR"
-purity_final_temp$Source[grepl("foxnews.com", purity_final_temp$URL)] = "Fox"
-purity_final_temp$Source[grepl("breitbart.com", purity_final_temp$URL)] = "Breitbart"
-
-purity_model = lme(MFDweight ~ lean, 
-                 data = purity_final_temp, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model)
-```
-
-# Results
-
-## Descriptive Statistics
-
-```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}
-
-final$uniquewords = NA
-final$valenceavg = NA
-
-for (i in 1:nrow(final)){
-
-  #add unique
-  final$uniquewords[i] = length(unique(unlist(strsplit(final$stemmed[i], " "))))
-
-  #add valence
-  tempwords = as.data.frame(unlist(strsplit(final$stemmed[i], " ")))
-  colnames(tempwords) = "theword"
-  tempwords$tempval = vlookup(tempwords$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final$valenceavg[i] = mean(tempwords$tempval, na.rm = T)
-
-}
-
-# tapply(final$valenceavg, final$Source, mean)
-# tapply(final$valenceavg, final$Source, sd)
-# tapply(final$wordcount, final$Source, mean)
-# tapply(final$wordcount, final$Source, sd)
-# tapply(final$uniquewords, final$Source, mean)
-# tapply(final$uniquewords, final$Source, sd)
-# tapply(final$Source, final$Source, length)
-# tapply(final$wordcount, final$Source, sum)
-
-library(quanteda)
-
-final$FK = NA
-
-for (i in 1:nrow(final)){
-  final$FK[i] = unlist(textstat_readability(final$Text[i], 
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-# tapply(final$FK, final$Source, mean)
-# tapply(final$FK, final$Source, sd)
-
-####build the table here####
-tableprint = matrix(NA, nrow=4, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint[ , 1] = unique(final$Source)
-tableprint[ , 1] = c("Breitbart", "Fox News", "NPR", "New York Times")
-tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
-tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
-tableprint[ , 4] = tapply(final$valenceavg, final$Source, length)
-tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
-tableprint[ , 6] = tapply(final$wordcount, final$Source, mean)
-tableprint[ , 7] = tapply(final$wordcount, final$Source, sd)
-tableprint[ , 8] = tapply(final$uniquewords, final$Source, mean)
-tableprint[ , 9] = tapply(final$uniquewords, final$Source, sd)
-tableprint[ , 10] = tapply(final$FK, final$Source, mean)
-tableprint[ , 11] = tapply(final$FK, final$Source, sd)
-
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
-
-tableprint = tableprint[c(3, 4, 1, 2) , ]
-
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Experiment 1 - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 6))
-          )
-```
-
-The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included average *z*-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula [@Kincaid1975].
-Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage [@Kincaid1975].
-For example, a text with a readability score of 11 should be easily read by a high school junior.
-
-As seen in Table \@ref(tab:exp1-source-descriptives), the sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
-*The New York Times* published the greatest number of articles as well as total words.
-*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
-Per individual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* articles had the lowest reading grade level on average, while *The New York Times* had the highest.
-This result might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*.
-The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
-Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.
-
-## Inferential Statistics
-
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
-Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp1-table).
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, the researchers observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
-
-```{r exp1-table, results = 'asis', echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
-
-#calculate d
-#harm
-harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
-                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d = d.ind.t(m1 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"]),
-                 n2 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d = d.ind.t(m1 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d = d.ind.t(m1 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"]),
-                 n2 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d = d.ind.t(m1 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"]),
-                 n2 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1, 
-                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
-                    harm_d$d)
-tableprint[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1, 
-                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
-                    fair_d$d)
-tableprint[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1, 
-                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
-                    ingroup_d$d)
-tableprint[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1, 
-                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
-                    authority_d$d)
-tableprint[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1, 
-                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
-                    purity_d$d)
-
-tableprint[ , c(2:6, 8)] = printnum(as.numeric(tableprint[ , c(2:6, 8)]))
-tableprint[ , 7] = printp(as.numeric(tableprint[ , 7]))
-
-apa_table(tableprint,
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Experiment 1 Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7))
-          )
-```
-
-```{r conference-pic, eval = F, include = F}
-library(ggplot2)
-library(reshape)
-
-cleanup = theme(panel.grid.major = element_blank(), 
-                panel.grid.minor = element_blank(), 
-                panel.background = element_blank(), 
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 10))
-
-graphdata = as.data.frame(tableprint)
-graphlong = melt(graphdata[ , c(1,2,4)], 
-                 id = "Foundation")
-graphlong2 = melt(graphdata[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong$sd = graphlong2$value
-graphlong$lower = as.numeric(as.character(graphlong$value)) - 2*as.numeric(as.character(graphlong$sd))
-graphlong$upper = as.numeric(as.character(graphlong$value)) + 2*as.numeric(as.character(graphlong$sd))
-
-graphlong$value = as.numeric(as.character(graphlong$value))
-
-graph_data = ggplot(graphlong, aes(Foundation, value, color = variable)) + 
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), 
-                position = position_dodge(width = 0.90),
-                width = .2) + 
-  cleanup +
-  ylab("Mean Weighted Valence") + 
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-tiff(filename = "exp1_graph.tiff", res = 300, width = 4, 
-     height = 3, units = 'in', compression = "lzw")
-plot(graph_data)
-dev.off()
-
-```
-
-# Discussion
-
-The results obtained in Experiment 1 fail to support the differences predicted by Moral Foundations Theory.
-First, differences between liberal and conservative news sources failed to reach statistically significance for any foundations.
-Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
-Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
-Overall, the results lend strong support to the case against the Moral Foundations Dictionary and weakens the case generally for Moral Foundations Theory.
-
-However,one possible limitation of the current data is the general-ness of the corpus.
-The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-To address this limitation, two changes that were subsequently employed in Experiment 2.
-First, we elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
-Second, we chose to focus  data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court and the government shutdown in December 2018 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Experiment 2 is the best test of the Moral Foundations theory and dictionary in the context of partisan news.
-
-# Experiment 2
-
-# Method
-
-In contrast to Experiment 1, the researchers approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, the researchers hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-The researchers tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, the researchers analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under Moral Foundations Theory.
-Once again, no human participants were needed for this study, so no Institutional Review Board approval was necessary.
+## Experiment 2 Web Scraping Code
 
@@
 ```
-
-## Sources
-
-Articles pertaining to the Brett Kavanaugh Supreme Court confirmation hearing and the 2018-2019 U.S.
-Government shutdown were scraped from the websites of 10 U.S.
-news sources.
-As in Experiment 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by the highest proportion of consistent liberals were *The New York Times*, *National Public Radio (NPR)*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
-The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts, again written with the *papaja* library in *R*, are provided inline with this manuscript [@Aust2017].
-
-## Materials
-
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned 10 news sources (identified using CSS language).
-We compiled the articles into a dataset [@Wickham2016].
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the partial U.S.
-Government shutdown of 2018-2019.
-The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, the researchers elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
-
-```{r data_clean_kav, eval = T, echo = F}
-##combine all kav data into one dataset
-#read it in
-NYtimes_kav = read.csv("../exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-NPR_kav = read.csv("../exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-SLATE_kav = read.csv("../exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("../exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-POLITICO_kav = read.csv("../exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-FOX_kav = read.csv("../exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
-BREITBART_kav = read.csv("../exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
-RUSH_kav = read.csv("../exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-BLAZE_kav = read.csv("../exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
-HANNITY_kav = read.csv("../exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-
-#merge it together
-master_kav = rbind(NYtimes_kav, NPR_kav, SLATE_kav, 
-                        HUFFPO_kav, POLITICO_kav, FOX_kav, 
-                        BREITBART_kav, RUSH_kav, BLAZE_kav, 
-                        HANNITY_kav)
-
-#fix this issue
-master_kav$Text = gsub("\\.", "\\. ", master_kav$Text)
-
-##get rid of the blank stuff
-library(ngram)
-
-for (i in 1:nrow(master_kav)) {
-  master_kav$wordcount[i] = wordcount(master_kav$Text[i])
-}
-
-nozero = subset(master_kav, wordcount > 0)
-nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-# tapply(nozero$wordcount, nozero$Source, mean)
-# tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones - there are none
-#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##all data
-final_kav = nozero
-```
-
-```{r data_clean_gs, eval = T, echo = F}
-##combine all gs data into one dataset
-#read it in
-NYtimes_gs = read.csv("../exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
-NPR_gs = read.csv("../exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
-SLATE_gs = read.csv("../exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
-HUFFPO_gs = read.csv("../exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
-POLITICO_gs = read.csv("../exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
-FOX_gs = read.csv("../exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
-BREITBART_gs = read.csv("../exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
-RUSH_gs = read.csv("../exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
-BLAZE_gs = read.csv("../exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
-HANNITY_gs = read.csv("../exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
-
-#merge it together
-master_gs = rbind(NYtimes_gs, NPR_gs, SLATE_gs, 
-                        HUFFPO_gs, POLITICO_gs, FOX_gs, 
-                        BREITBART_gs, RUSH_gs, BLAZE_gs, 
-                        HANNITY_gs)
-
-#fix this issue
-master_gs$Text = gsub("\\.", "\\. ", master_gs$Text)
-
-for (i in 1:nrow(master_gs)) {
-  master_gs$wordcount[i] = wordcount(master_gs$Text[i])
-}
-
-nozero = subset(master_gs, wordcount > 0)
-nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-
-# tapply(nozero$wordcount, nozero$Source, mean)
-# tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones
-#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##all data
-final_gs = nozero
-```
-
-```{r stem_text_both, eval = T, echo = F}
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final_kav)) {
-
-  final_kav$edited[i] = preprocess(final_kav$Text[i], #one value at a time
-           case = "lower", 
-           remove.punct = TRUE,
-           remove.numbers = FALSE, 
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final_kav$stemmed[i] = stemDocument(final_kav$edited[i], language = "english")
-}
-
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final_gs)) {
-
-  final_gs$edited[i] = preprocess(final_gs$Text[i], #one value at a time
-           case = "lower", 
-           remove.punct = TRUE,
-           remove.numbers = FALSE, 
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final_gs$stemmed[i] = stemDocument(final_gs$edited[i], language = "english")
-}
-
-```
-
-## Data analysis
-
-As in Experiment 1, the text was scanned with *ngram*.
-Again, blank articles, text from the Disqus system, and duplicate articles were removed [@Schmidt2017].
-The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017].
-Words were subsequently matched with their valences from @Warriner2013.
-Depending on the results of @Jordan2019's multi-trait multi-method analysis of the MFD and the Moral Foundations Questionnaire, alternative forms of the Moral Foundations Dictionary with additional words may be imported instead of the original dictionary.
-
-Using the *tm* and *ngram* packages in *R*, the researchers processed the text in order to convert it to lowercase, fix spacing anomalies, and remove punctuation [@Feinerer2017].
-Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).
-Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words in the MFD were assigned their respective valence.
-The researchers obtained the words' percent occurrence in the text.
-Percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
-
-```{r create_datasets_harm_kav, eval = T, echo = F, include = F}
-#read in the harm total words from the mtmm project
-harm_all_kav = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all_kav$words[harm_all_kav$words != "" & harm_all_kav$words != "NA" & !is.na(harm_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-harm_final_data_kav = rbind(harm_final_data_kav, temp2)
-}
-
-#pull in the data from Warriner 
-harm_final_data_kav$valence = vlookup(harm_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-#table(harm_final_data_kav$Var1[is.na(harm_final_data_kav$valence) & harm_final_data_kav$Freq > 0])
-#fought, safer, spurn
-harm_final_data_kav$valence[harm_final_data_kav$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data_kav$valence[harm_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all_kav$words[fair_all_kav$words != "" & fair_all_kav$words != "NA" & !is.na(fair_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-fair_final_data_kav = rbind(fair_final_data_kav, temp2)
-}
-
-fair_final_data_kav$valence = vlookup(fair_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data_kav$Var1[is.na(fair_final_data_kav$valence) & fair_final_data_kav$Freq > 0])
-#just plagiar safer
-fair_final_data_kav$valence[fair_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all_kav$words[ingroup_all_kav$words != "" & ingroup_all_kav$words != "NA" & !is.na(ingroup_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-ingroup_final_data_kav = rbind(ingroup_final_data_kav, temp2)
-}
-
-ingroup_final_data_kav$valence = vlookup(ingroup_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data_kav$Var1[is.na(ingroup_final_data_kav$valence) & ingroup_final_data_kav$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all_kav$words[authority_all_kav$words != "" & authority_all_kav$words != "NA" & !is.na(authority_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-authority_final_data_kav = rbind(authority_final_data_kav, temp2)
-}
-
-authority_final_data_kav$valence = vlookup(authority_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data_kav$Var1[is.na(authority_final_data_kav$valence) & authority_final_data_kav$Freq > 0])
-#  abov behind   gase higher  older  taken 
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all_kav$words[purity_all_kav$words != "" & purity_all_kav$words != "NA" & !is.na(purity_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-purity_final_data_kav = rbind(purity_final_data_kav, temp2)
-}
-
-purity_final_data_kav$valence = vlookup(purity_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data_kav$Var1[is.na(purity_final_data_kav$valence) & purity_final_data_kav$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women 
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r create_datasets_harm_gs, eval = T, echo = F, include = F}
-#read in the harm total words from the mtmm project
-harm_all_gs = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all_gs$words[harm_all_gs$words != "" & harm_all_gs$words != "NA" & !is.na(harm_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-harm_final_data_gs = rbind(harm_final_data_gs, temp2)
-}
-
-#pull in the data from Warriner 
-harm_final_data_gs$valence = vlookup(harm_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-#table(harm_final_data_gs$Var1[is.na(harm_final_data_gs$valence) & harm_final_data_gs$Freq > 0])
-#fought, safer, spurn
-harm_final_data_gs$valence[harm_final_data_gs$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data_gs$valence[harm_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair_gs, echo = F, include=FALSE}
-fair_all_gs = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all_gs$words[fair_all_gs$words != "" & fair_all_gs$words != "NA" & !is.na(fair_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-fair_final_data_gs = rbind(fair_final_data_gs, temp2)
-}
-
-fair_final_data_gs$valence = vlookup(fair_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data_gs$Var1[is.na(fair_final_data_gs$valence) & fair_final_data_gs$Freq > 0])
-#just plagiar safer
-fair_final_data_gs$valence[fair_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
-ingroup_all_gs = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all_gs$words[ingroup_all_gs$words != "" & ingroup_all_gs$words != "NA" & !is.na(ingroup_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-ingroup_final_data_gs = rbind(ingroup_final_data_gs, temp2)
-}
-
-ingroup_final_data_gs$valence = vlookup(ingroup_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data_gs$Var1[is.na(ingroup_final_data_gs$valence) & ingroup_final_data_gs$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority_gs, echo = F, include=FALSE}
-authority_all_gs = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all_gs$words[authority_all_gs$words != "" & authority_all_gs$words != "NA" & !is.na(authority_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-authority_final_data_gs = rbind(authority_final_data_gs, temp2)
-}
-
-authority_final_data_gs$valence = vlookup(authority_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data_gs$Var1[is.na(authority_final_data_gs$valence) & authority_final_data_gs$Freq > 0])
-#  abov behind   gase higher  older  taken 
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity_gs, echo = F, include=FALSE}
-purity_all_gs = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all_gs$words[purity_all_gs$words != "" & purity_all_gs$words != "NA" & !is.na(purity_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-purity_final_data_gs = rbind(purity_final_data_gs, temp2)
-}
-
-purity_final_data_gs$valence = vlookup(purity_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data_gs$Var1[is.na(purity_final_data_gs$valence) & purity_final_data_gs$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women 
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r descriptives_both, echo = F, include = FALSE}
-##summarize the dataset so that you have the total and percent for each foundation
-#kav
-summary(harm_final_data_kav)
-summary(fair_final_data_kav)
-summary(ingroup_final_data_kav)
-summary(authority_final_data_kav)
-summary(purity_final_data_kav)
-#gs
-summary(harm_final_data_gs)
-summary(fair_final_data_gs)
-summary(ingroup_final_data_gs)
-summary(authority_final_data_gs)
-summary(purity_final_data_gs)
-##report descriptive statistics of the foundations
-#kav
-mean(harm_final_data_kav$valence, na.rm = T)
-sd(harm_final_data_kav$valence, na.rm = T)
-mean(fair_final_data_kav$valence, na.rm = T)
-sd(fair_final_data_kav$valence, na.rm = T)
-mean(ingroup_final_data_kav$valence, na.rm = T)
-sd(ingroup_final_data_kav$valence, na.rm = T)
-mean(authority_final_data_kav$valence, na.rm = T)
-sd(authority_final_data_kav$valence, na.rm = T)
-mean(purity_final_data_kav$valence, na.rm = T)
-sd(purity_final_data_kav$valence, na.rm = T)
-#gs
-mean(harm_final_data_gs$valence, na.rm = T)
-sd(harm_final_data_gs$valence, na.rm = T)
-mean(fair_final_data_gs$valence, na.rm = T)
-sd(fair_final_data_gs$valence, na.rm = T)
-mean(ingroup_final_data_gs$valence, na.rm = T)
-sd(ingroup_final_data_gs$valence, na.rm = T)
-mean(authority_final_data_gs$valence, na.rm = T)
-sd(authority_final_data_gs$valence, na.rm = T)
-mean(purity_final_data_gs$valence, na.rm = T)
-sd(purity_final_data_gs$valence, na.rm = T)
-#note that a big problem is the valence of the words 
-```
-
-```{r analysis_harm_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data_kav$weight = harm_final_data_kav$Freq * harm_final_data_kav$valence / harm_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-harm_final_temp_kav = aggregate(harm_final_data_kav$weight, 
-          by = list(harm_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp_kav) = c("URL", "MFDweight")
-
-harm_final_temp_kav$lean[grepl("nytimes.com", harm_final_temp_kav$URL) |
-                       grepl("npr.org", harm_final_temp_kav$URL) |
-                        grepl("slate.com", harm_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", harm_final_temp_kav$URL) |
-                        grepl("politico.com", harm_final_temp_kav$URL)] = "Liberal"
-
-harm_final_temp_kav$lean[grepl("breitbart.com", harm_final_temp_kav$URL) |
-                       grepl("foxnews.com", harm_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", harm_final_temp_kav$URL) |
-                       grepl("theblaze.com", harm_final_temp_kav$URL) |
-                       grepl("hannity.com", harm_final_temp_kav$URL)] = "Conservative"
-
-harm_final_temp_kav$Source[grepl("nytimes.com", harm_final_temp_kav$URL)] = "NY Times"
-harm_final_temp_kav$Source[grepl("npr.org", harm_final_temp_kav$URL)] = "NPR"
-harm_final_temp_kav$Source[grepl("slate.com", harm_final_temp_kav$URL)] = "Slate"
-harm_final_temp_kav$Source[grepl("huffingtonpost.com", harm_final_temp_kav$URL)] = "Huffington Post"
-harm_final_temp_kav$Source[grepl("politico.com", harm_final_temp_kav$URL)] = "Politico"
-harm_final_temp_kav$Source[grepl("foxnews.com", harm_final_temp_kav$URL)] = "Fox"
-harm_final_temp_kav$Source[grepl("breitbart.com", harm_final_temp_kav$URL)] = "Breitbart"
-harm_final_temp_kav$Source[grepl("rushlimbaugh.com", harm_final_temp_kav$URL)] = "Rush Limbaugh"
-harm_final_temp_kav$Source[grepl("theblaze.com", harm_final_temp_kav$URL)] = "The Blaze"
-harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
-harm_model_kav = lme(MFDweight ~ lean, 
-                 data = harm_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model_kav)
-r.squaredGLMM(harm_model_kav)
-```
-
-```{r analysis_fair_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data_kav$weight = fair_final_data_kav$Freq * fair_final_data_kav$valence / fair_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-fair_final_temp_kav = aggregate(fair_final_data_kav$weight, 
-          by = list(fair_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp_kav) = c("URL", "MFDweight")
-
-fair_final_temp_kav$lean[grepl("nytimes.com", fair_final_temp_kav$URL) |
-                       grepl("npr.org", fair_final_temp_kav$URL) |
-                        grepl("slate.com", fair_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", fair_final_temp_kav$URL) |
-                        grepl("politico.com", fair_final_temp_kav$URL)] = "Liberal"
-
-fair_final_temp_kav$lean[grepl("breitbart.com", fair_final_temp_kav$URL) |
-                       grepl("foxnews.com", fair_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", fair_final_temp_kav$URL) |
-                       grepl("theblaze.com", fair_final_temp_kav$URL) |
-                       grepl("hannity.com", fair_final_temp_kav$URL)] = "Conservative"
-
-fair_final_temp_kav$Source[grepl("nytimes.com", fair_final_temp_kav$URL)] = "NY Times"
-fair_final_temp_kav$Source[grepl("npr.org", fair_final_temp_kav$URL)] = "NPR"
-fair_final_temp_kav$Source[grepl("slate.com", fair_final_temp_kav$URL)] = "Slate"
-fair_final_temp_kav$Source[grepl("huffingtonpost.com", fair_final_temp_kav$URL)] = "Huffington Post"
-fair_final_temp_kav$Source[grepl("politico.com", fair_final_temp_kav$URL)] = "Politico"
-fair_final_temp_kav$Source[grepl("foxnews.com", fair_final_temp_kav$URL)] = "Fox"
-fair_final_temp_kav$Source[grepl("breitbart.com", fair_final_temp_kav$URL)] = "Breitbart"
-fair_final_temp_kav$Source[grepl("rushlimbaugh.com", fair_final_temp_kav$URL)] = "Rush Limbaugh"
-fair_final_temp_kav$Source[grepl("theblaze.com", fair_final_temp_kav$URL)] = "The Blaze"
-fair_final_temp_kav$Source[grepl("hannity.com", fair_final_temp_kav$URL)] = "Sean Hannity"
-fair_model_kav = lme(MFDweight ~ lean, 
-                 data = fair_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model_kav)
-```
-
-```{r analysis_ingroup_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data_kav$weight = ingroup_final_data_kav$Freq * ingroup_final_data_kav$valence / ingroup_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-ingroup_final_temp_kav = aggregate(ingroup_final_data_kav$weight, 
-          by = list(ingroup_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp_kav) = c("URL", "MFDweight")
-
-ingroup_final_temp_kav$lean[grepl("nytimes.com", ingroup_final_temp_kav$URL) |
-                       grepl("npr.org", ingroup_final_temp_kav$URL) |
-                        grepl("slate.com", ingroup_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", ingroup_final_temp_kav$URL) |
-                        grepl("politico.com", ingroup_final_temp_kav$URL)] = "Liberal"
-
-ingroup_final_temp_kav$lean[grepl("breitbart.com", ingroup_final_temp_kav$URL) |
-                       grepl("foxnews.com", ingroup_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL) |
-                       grepl("theblaze.com", ingroup_final_temp_kav$URL) |
-                       grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Conservative"
-
-ingroup_final_temp_kav$Source[grepl("nytimes.com", ingroup_final_temp_kav$URL)] = "NY Times"
-ingroup_final_temp_kav$Source[grepl("npr.org", ingroup_final_temp_kav$URL)] = "NPR"
-ingroup_final_temp_kav$Source[grepl("slate.com", ingroup_final_temp_kav$URL)] = "Slate"
-ingroup_final_temp_kav$Source[grepl("huffingtonpost.com", ingroup_final_temp_kav$URL)] = "Huffington Post"
-ingroup_final_temp_kav$Source[grepl("politico.com", ingroup_final_temp_kav$URL)] = "Politico"
-ingroup_final_temp_kav$Source[grepl("foxnews.com", ingroup_final_temp_kav$URL)] = "Fox"
-ingroup_final_temp_kav$Source[grepl("breitbart.com", ingroup_final_temp_kav$URL)] = "Breitbart"
-ingroup_final_temp_kav$Source[grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL)] = "Rush Limbaugh"
-ingroup_final_temp_kav$Source[grepl("theblaze.com", ingroup_final_temp_kav$URL)] = "The Blaze"
-ingroup_final_temp_kav$Source[grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Sean Hannity"
-ingroup_model_kav = lme(MFDweight ~ lean, 
-                 data = ingroup_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model_kav)
-```
-
-```{r analysis_authority_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data_kav$weight = authority_final_data_kav$Freq * authority_final_data_kav$valence / authority_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-authority_final_temp_kav = aggregate(authority_final_data_kav$weight, 
-          by = list(authority_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp_kav) = c("URL", "MFDweight")
-
-authority_final_temp_kav$lean[grepl("nytimes.com", authority_final_temp_kav$URL) |
-                       grepl("npr.org", authority_final_temp_kav$URL) |
-                        grepl("slate.com", authority_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", authority_final_temp_kav$URL) |
-                        grepl("politico.com", authority_final_temp_kav$URL)] = "Liberal"
-
-authority_final_temp_kav$lean[grepl("breitbart.com", authority_final_temp_kav$URL) |
-                       grepl("foxnews.com", authority_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", authority_final_temp_kav$URL) |
-                       grepl("theblaze.com", authority_final_temp_kav$URL) |
-                       grepl("hannity.com", authority_final_temp_kav$URL)] = "Conservative"
-
-authority_final_temp_kav$Source[grepl("nytimes.com", authority_final_temp_kav$URL)] = "NY Times"
-authority_final_temp_kav$Source[grepl("npr.org", authority_final_temp_kav$URL)] = "NPR"
-authority_final_temp_kav$Source[grepl("slate.com", authority_final_temp_kav$URL)] = "Slate"
-authority_final_temp_kav$Source[grepl("huffingtonpost.com", authority_final_temp_kav$URL)] = "Huffington Post"
-authority_final_temp_kav$Source[grepl("politico.com", authority_final_temp_kav$URL)] = "Politico"
-authority_final_temp_kav$Source[grepl("foxnews.com", authority_final_temp_kav$URL)] = "Fox"
-authority_final_temp_kav$Source[grepl("breitbart.com", authority_final_temp_kav$URL)] = "Breitbart"
-authority_final_temp_kav$Source[grepl("rushlimbaugh.com", authority_final_temp_kav$URL)] = "Rush Limbaugh"
-authority_final_temp_kav$Source[grepl("theblaze.com", authority_final_temp_kav$URL)] = "The Blaze"
-authority_final_temp_kav$Source[grepl("hannity.com", authority_final_temp_kav$URL)] = "Sean Hannity"
-authority_model_kav = lme(MFDweight ~ lean, 
-                 data = authority_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model_kav)
-```
-
-```{r analysis_purity_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data_kav$weight = purity_final_data_kav$Freq * purity_final_data_kav$valence / purity_final_data_kav$wordcount * 100
-
-#flatten down to sum by article 
-purity_final_temp_kav = aggregate(purity_final_data_kav$weight, 
-          by = list(purity_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp_kav) = c("URL", "MFDweight")
-
-purity_final_temp_kav$lean[grepl("nytimes.com", purity_final_temp_kav$URL) |
-                       grepl("npr.org", purity_final_temp_kav$URL) |
-                        grepl("slate.com", purity_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", purity_final_temp_kav$URL) |
-                        grepl("politico.com", purity_final_temp_kav$URL)] = "Liberal"
-
-purity_final_temp_kav$lean[grepl("breitbart.com", purity_final_temp_kav$URL) |
-                       grepl("foxnews.com", purity_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", purity_final_temp_kav$URL) |
-                       grepl("theblaze.com", purity_final_temp_kav$URL) |
-                       grepl("hannity.com", purity_final_temp_kav$URL)] = "Conservative"
-
-purity_final_temp_kav$Source[grepl("nytimes.com", purity_final_temp_kav$URL)] = "NY Times"
-purity_final_temp_kav$Source[grepl("npr.org", purity_final_temp_kav$URL)] = "NPR"
-purity_final_temp_kav$Source[grepl("slate.com", purity_final_temp_kav$URL)] = "Slate"
-purity_final_temp_kav$Source[grepl("huffingtonpost.com", purity_final_temp_kav$URL)] = "Huffington Post"
-purity_final_temp_kav$Source[grepl("politico.com", purity_final_temp_kav$URL)] = "Politico"
-purity_final_temp_kav$Source[grepl("foxnews.com", purity_final_temp_kav$URL)] = "Fox"
-purity_final_temp_kav$Source[grepl("breitbart.com", purity_final_temp_kav$URL)] = "Breitbart"
-purity_final_temp_kav$Source[grepl("rushlimbaugh.com", purity_final_temp_kav$URL)] = "Rush Limbaugh"
-purity_final_temp_kav$Source[grepl("theblaze.com", purity_final_temp_kav$URL)] = "The Blaze"
-purity_final_temp_kav$Source[grepl("hannity.com", purity_final_temp_kav$URL)] = "Sean Hannity"
-purity_model_kav = lme(MFDweight ~ lean, 
-                 data = purity_final_temp_kav, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model_kav)
-```
-
-```{r analysis_harm_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data_gs$weight = harm_final_data_gs$Freq * harm_final_data_gs$valence / harm_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-harm_final_temp_gs = aggregate(harm_final_data_gs$weight, 
-          by = list(harm_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp_gs) = c("URL", "MFDweight")
-
-harm_final_temp_gs$lean[grepl("nytimes.com", harm_final_temp_gs$URL) |
-                       grepl("npr.org", harm_final_temp_gs$URL) |
-                        grepl("slate.com", harm_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", harm_final_temp_gs$URL) |
-                        grepl("politico.com", harm_final_temp_gs$URL)] = "Liberal"
-
-harm_final_temp_gs$lean[grepl("breitbart.com", harm_final_temp_gs$URL) |
-                       grepl("foxnews.com", harm_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", harm_final_temp_gs$URL) |
-                       grepl("theblaze.com", harm_final_temp_gs$URL) |
-                       grepl("hannity.com", harm_final_temp_gs$URL)] = "Conservative"
-
-harm_final_temp_gs$Source[grepl("nytimes.com", harm_final_temp_gs$URL)] = "NY Times"
-harm_final_temp_gs$Source[grepl("npr.org", harm_final_temp_gs$URL)] = "NPR"
-harm_final_temp_gs$Source[grepl("slate.com", harm_final_temp_gs$URL)] = "Slate"
-harm_final_temp_gs$Source[grepl("huffingtonpost.com", harm_final_temp_gs$URL)] = "Huffington Post"
-harm_final_temp_gs$Source[grepl("politico.com", harm_final_temp_gs$URL)] = "Politico"
-harm_final_temp_gs$Source[grepl("foxnews.com", harm_final_temp_gs$URL)] = "Fox"
-harm_final_temp_gs$Source[grepl("breitbart.com", harm_final_temp_gs$URL)] = "Breitbart"
-harm_final_temp_gs$Source[grepl("rushlimbaugh.com", harm_final_temp_gs$URL)] = "Rush Limbaugh"
-harm_final_temp_gs$Source[grepl("theblaze.com", harm_final_temp_gs$URL)] = "The Blaze"
-harm_final_temp_gs$Source[grepl("hannity.com", harm_final_temp_gs$URL)] = "Sean Hannity"
-harm_model_gs = lme(MFDweight ~ lean, 
-                 data = harm_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model_gs)
-```
-
-```{r analysis_fair_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data_gs$weight = fair_final_data_gs$Freq * fair_final_data_gs$valence / fair_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-fair_final_temp_gs = aggregate(fair_final_data_gs$weight, 
-          by = list(fair_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp_gs) = c("URL", "MFDweight")
-
-fair_final_temp_gs$lean[grepl("nytimes.com", fair_final_temp_gs$URL) |
-                       grepl("npr.org", fair_final_temp_gs$URL) |
-                        grepl("slate.com", fair_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", fair_final_temp_gs$URL) |
-                        grepl("politico.com", fair_final_temp_gs$URL)] = "Liberal"
-
-fair_final_temp_gs$lean[grepl("breitbart.com", fair_final_temp_gs$URL) |
-                       grepl("foxnews.com", fair_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", fair_final_temp_gs$URL) |
-                       grepl("theblaze.com", fair_final_temp_gs$URL) |
-                       grepl("hannity.com", fair_final_temp_gs$URL)] = "Conservative"
-
-fair_final_temp_gs$Source[grepl("nytimes.com", fair_final_temp_gs$URL)] = "NY Times"
-fair_final_temp_gs$Source[grepl("npr.org", fair_final_temp_gs$URL)] = "NPR"
-fair_final_temp_gs$Source[grepl("slate.com", fair_final_temp_gs$URL)] = "Slate"
-fair_final_temp_gs$Source[grepl("huffingtonpost.com", fair_final_temp_gs$URL)] = "Huffington Post"
-fair_final_temp_gs$Source[grepl("politico.com", fair_final_temp_gs$URL)] = "Politico"
-fair_final_temp_gs$Source[grepl("foxnews.com", fair_final_temp_gs$URL)] = "Fox"
-fair_final_temp_gs$Source[grepl("breitbart.com", fair_final_temp_gs$URL)] = "Breitbart"
-fair_final_temp_gs$Source[grepl("rushlimbaugh.com", fair_final_temp_gs$URL)] = "Rush Limbaugh"
-fair_final_temp_gs$Source[grepl("theblaze.com", fair_final_temp_gs$URL)] = "The Blaze"
-fair_final_temp_gs$Source[grepl("hannity.com", fair_final_temp_gs$URL)] = "Sean Hannity"
-fair_model_gs = lme(MFDweight ~ lean, 
-                 data = fair_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model_gs)
-```
-
-```{r analysis_ingroup_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data_gs$weight = ingroup_final_data_gs$Freq * ingroup_final_data_gs$valence / ingroup_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-ingroup_final_temp_gs = aggregate(ingroup_final_data_gs$weight, 
-          by = list(ingroup_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp_gs) = c("URL", "MFDweight")
-
-ingroup_final_temp_gs$lean[grepl("nytimes.com", ingroup_final_temp_gs$URL) |
-                       grepl("npr.org", ingroup_final_temp_gs$URL) |
-                        grepl("slate.com", ingroup_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", ingroup_final_temp_gs$URL) |
-                        grepl("politico.com", ingroup_final_temp_gs$URL)] = "Liberal"
-
-ingroup_final_temp_gs$lean[grepl("breitbart.com", ingroup_final_temp_gs$URL) |
-                       grepl("foxnews.com", ingroup_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL) |
-                       grepl("theblaze.com", ingroup_final_temp_gs$URL) |
-                       grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Conservative"
-
-ingroup_final_temp_gs$Source[grepl("nytimes.com", ingroup_final_temp_gs$URL)] = "NY Times"
-ingroup_final_temp_gs$Source[grepl("npr.org", ingroup_final_temp_gs$URL)] = "NPR"
-ingroup_final_temp_gs$Source[grepl("slate.com", ingroup_final_temp_gs$URL)] = "Slate"
-ingroup_final_temp_gs$Source[grepl("huffingtonpost.com", ingroup_final_temp_gs$URL)] = "Huffington Post"
-ingroup_final_temp_gs$Source[grepl("politico.com", ingroup_final_temp_gs$URL)] = "Politico"
-ingroup_final_temp_gs$Source[grepl("foxnews.com", ingroup_final_temp_gs$URL)] = "Fox"
-ingroup_final_temp_gs$Source[grepl("breitbart.com", ingroup_final_temp_gs$URL)] = "Breitbart"
-ingroup_final_temp_gs$Source[grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL)] = "Rush Limbaugh"
-ingroup_final_temp_gs$Source[grepl("theblaze.com", ingroup_final_temp_gs$URL)] = "The Blaze"
-ingroup_final_temp_gs$Source[grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Sean Hannity"
-ingroup_model_gs = lme(MFDweight ~ lean, 
-                 data = ingroup_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model_gs)
-```
-
-```{r analysis_authority_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data_gs$weight = authority_final_data_gs$Freq * authority_final_data_gs$valence / authority_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-authority_final_temp_gs = aggregate(authority_final_data_gs$weight, 
-          by = list(authority_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp_gs) = c("URL", "MFDweight")
-
-authority_final_temp_gs$lean[grepl("nytimes.com", authority_final_temp_gs$URL) |
-                       grepl("npr.org", authority_final_temp_gs$URL) |
-                        grepl("slate.com", authority_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", authority_final_temp_gs$URL) |
-                        grepl("politico.com", authority_final_temp_gs$URL)] = "Liberal"
-
-authority_final_temp_gs$lean[grepl("breitbart.com", authority_final_temp_gs$URL) |
-                       grepl("foxnews.com", authority_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", authority_final_temp_gs$URL) |
-                       grepl("theblaze.com", authority_final_temp_gs$URL) |
-                       grepl("hannity.com", authority_final_temp_gs$URL)] = "Conservative"
-
-authority_final_temp_gs$Source[grepl("nytimes.com", authority_final_temp_gs$URL)] = "NY Times"
-authority_final_temp_gs$Source[grepl("npr.org", authority_final_temp_gs$URL)] = "NPR"
-authority_final_temp_gs$Source[grepl("slate.com", authority_final_temp_gs$URL)] = "Slate"
-authority_final_temp_gs$Source[grepl("huffingtonpost.com", authority_final_temp_gs$URL)] = "Huffington Post"
-authority_final_temp_gs$Source[grepl("politico.com", authority_final_temp_gs$URL)] = "Politico"
-authority_final_temp_gs$Source[grepl("foxnews.com", authority_final_temp_gs$URL)] = "Fox"
-authority_final_temp_gs$Source[grepl("breitbart.com", authority_final_temp_gs$URL)] = "Breitbart"
-authority_final_temp_gs$Source[grepl("rushlimbaugh.com", authority_final_temp_gs$URL)] = "Rush Limbaugh"
-authority_final_temp_gs$Source[grepl("theblaze.com", authority_final_temp_gs$URL)] = "The Blaze"
-authority_final_temp_gs$Source[grepl("hannity.com", authority_final_temp_gs$URL)] = "Sean Hannity"
-authority_model_gs = lme(MFDweight ~ lean, 
-                 data = authority_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model_gs)
-```
-
-```{r analysis_purity_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data_gs$weight = purity_final_data_gs$Freq * purity_final_data_gs$valence / purity_final_data_gs$wordcount * 100
-
-#flatten down to sum by article 
-purity_final_temp_gs = aggregate(purity_final_data_gs$weight, 
-          by = list(purity_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp_gs) = c("URL", "MFDweight")
-
-purity_final_temp_gs$lean[grepl("nytimes.com", purity_final_temp_gs$URL) |
-                       grepl("npr.org", purity_final_temp_gs$URL) |
-                        grepl("slate.com", purity_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", purity_final_temp_gs$URL) |
-                        grepl("politico.com", purity_final_temp_gs$URL)] = "Liberal"
-
-purity_final_temp_gs$lean[grepl("breitbart.com", purity_final_temp_gs$URL) |
-                       grepl("foxnews.com", purity_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", purity_final_temp_gs$URL) |
-                       grepl("theblaze.com", purity_final_temp_gs$URL) |
-                       grepl("hannity.com", purity_final_temp_gs$URL)] = "Conservative"
-
-purity_final_temp_gs$Source[grepl("nytimes.com", purity_final_temp_gs$URL)] = "NY Times"
-purity_final_temp_gs$Source[grepl("npr.org", purity_final_temp_gs$URL)] = "NPR"
-purity_final_temp_gs$Source[grepl("slate.com", purity_final_temp_gs$URL)] = "Slate"
-purity_final_temp_gs$Source[grepl("huffingtonpost.com", purity_final_temp_gs$URL)] = "Huffington Post"
-purity_final_temp_gs$Source[grepl("politico.com", purity_final_temp_gs$URL)] = "Politico"
-purity_final_temp_gs$Source[grepl("foxnews.com", purity_final_temp_gs$URL)] = "Fox"
-purity_final_temp_gs$Source[grepl("breitbart.com", purity_final_temp_gs$URL)] = "Breitbart"
-purity_final_temp_gs$Source[grepl("rushlimbaugh.com", purity_final_temp_gs$URL)] = "Rush Limbaugh"
-purity_final_temp_gs$Source[grepl("theblaze.com", purity_final_temp_gs$URL)] = "The Blaze"
-purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
-purity_model_gs = lme(MFDweight ~ lean, 
-                 data = purity_final_temp_gs, 
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model_gs)
-```
-
-# Results
-
-## Descriptive Statistics
-
-The researchers calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Experiment 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
-
-Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
-The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, *Sean Hannity* appears to have published only 27 articles while *Breitbart* published 757 articles on this topic.
-Valence was found to be slightly positive across all sources.
-*Fox News* produced the most total words with the most tokens on average.
-This is likely due to the fact *Fox News* transcribes many of their videos and publishes them in article form.
-*Politico* featured the highest number of types on average.
-*Rush Limbaugh* featured the lowest readability score on average by grade level while *Slate* featured the highest grade-level readability score.
-The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language, as there is likely a lot of overlap between sources' use of language.
-
-Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive statistics for articles about the partial government shutdown.
-Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each source on this topic.
-*Sean Hannity*, *Rush Limbaugh*, and *The Blaze* published fewer than 100 articles while *Fox News* published 1,013 articles.
-*Fox News* again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
-*Politico* had the most types on average.
-For this topic, *Fox News* featured the lowest reading grade level while *Slate* featured the highest reading grade level.
-For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
-
-```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
-#Kav
-final_kav$uniquewords = NA
-final_kav$valenceavg = NA
-
-for (i in 1:nrow(final_kav)){
-
-  #add unique
-  final_kav$uniquewords[i] = length(unique(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-  #add valence
-  tempwords_kav = as.data.frame(unlist(strsplit(final_kav$stemmed[i], " ")))
-  colnames(tempwords_kav) = "theword"
-  tempwords_kav$tempval = vlookup(tempwords_kav$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
-
-}
-
-# tapply(final_kav$valenceavg, final_kav$Source, mean)
-# tapply(final_kav$valenceavg, final_kav$Source, sd)
-# tapply(final_kav$wordcount, final_kav$Source, mean)
-# tapply(final_kav$wordcount, final_kav$Source, sd)
-# tapply(final_kav$uniquewords, final_kav$Source, mean)
-# tapply(final_kav$uniquewords, final_kav$Source, sd)
-# tapply(final_kav$Source, final_kav$Source, length)
-# tapply(final_kav$wordcount, final_kav$Source, sum)
-
-library(quanteda)
-
-final_kav$FK = NA
-
-for (i in 1:nrow(final_kav)){
-  final_kav$FK[i] = unlist(textstat_readability(final_kav$Text[i], 
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-# tapply(final_kav$FK, final_kav$Source, mean)
-# tapply(final_kav$FK, final_kav$Source, sd)
-
-#Kav Table
-####build the table here####
-tableprint = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint[ , 1] = unique(final_kav$Source)
-tableprint[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
-                     "Huffington Post", "NPR", "New York Times", "Politico",
-                     "Rush Limbaugh", "Slate")
-tableprint[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
-tableprint[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
-tableprint[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
-tableprint[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
-tableprint[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
-tableprint[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
-tableprint[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
-tableprint[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
-tableprint[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
-tableprint[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
-
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
-
-tableprint = tableprint[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
-
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Kavanaugh - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          small = T,
-          align = c("l", rep("c", 6))
-          )
-```
-
-```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
-#GS
-final_gs$uniquewords = NA
-final_gs$valenceavg = NA
-
-for (i in 1:nrow(final_gs)){
-
-  #add unique
-  final_gs$uniquewords[i] = length(unique(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-  #add valence
-  tempwords_gs = as.data.frame(unlist(strsplit(final_gs$stemmed[i], " ")))
-  colnames(tempwords_gs) = "theword"
-  tempwords_gs$tempval = vlookup(tempwords_gs$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final_gs$valenceavg[i] = mean(tempwords_gs$tempval, na.rm = T)
-
-}
-
-# tapply(final_gs$valenceavg, final_gs$Source, mean)
-# tapply(final_gs$valenceavg, final_gs$Source, sd)
-# tapply(final_gs$wordcount, final_gs$Source, mean)
-# tapply(final_gs$wordcount, final_gs$Source, sd)
-# tapply(final_gs$uniquewords, final_gs$Source, mean)
-# tapply(final_gs$uniquewords, final_gs$Source, sd)
-# tapply(final_gs$Source, final_gs$Source, length)
-# tapply(final_gs$wordcount, final_gs$Source, sum)
-
-library(quanteda)
-
-final_gs$FK = NA
-
-for (i in 1:nrow(final_gs)){
-  final_gs$FK[i] = unlist(textstat_readability(final_gs$Text[i], 
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-# tapply(final_gs$FK, final_gs$Source, mean)
-# tapply(final_gs$FK, final_gs$Source, sd)
-
-#GS Table
-####build the table here####
-tableprint = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint[ , 1] = unique(final_gs$Source)
-tableprint[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
-                     "Huffington Post", "NPR", "New York Times", "Politico",
-                     "Rush Limbaugh", "Slate")
-tableprint[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
-tableprint[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
-tableprint[ , 4] = tapply(final_gs$valenceavg, final_gs$Source, length)
-tableprint[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
-tableprint[ , 6] = tapply(final_gs$wordcount, final_gs$Source, mean)
-tableprint[ , 7] = tapply(final_gs$wordcount, final_gs$Source, sd)
-tableprint[ , 8] = tapply(final_gs$uniquewords, final_gs$Source, mean)
-tableprint[ , 9] = tapply(final_gs$uniquewords, final_gs$Source, sd)
-tableprint[ , 10] = tapply(final_gs$FK, final_gs$Source, mean)
-tableprint[ , 11] = tapply(final_gs$FK, final_gs$Source, sd)
-
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
-
-tableprint = tableprint[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
-
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Government Shutdown - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          small = T, 
-          align = c("l", rep("c", 6))
-          )
-```
-
-## Inferential Statistics
-
-To analyze if news sources adhered to differences in word use based on their target audience, the researchers utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience.
-The researchers used the *nlme* library in *R* [@Pinheiro2017].
-Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-Two separate MLMs were constructed from datasets compiled for each topic of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a statistically significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
-There were no other significant or practical effects of political lean for any of the other four moral foundations.
-The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp2-tablekav).
-
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations.
-A small-to-medium effect size was observed for *authority/respect*.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
-As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Experiment 1.
-As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
-
-```{r exp2-tablekav, results = 'asis', echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint_kav = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
-
-#calculate d
-#harm
-harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d_kav = d.ind.t(m1 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d_kav = d.ind.t(m1 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d_kav = d.ind.t(m1 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d_kav = d.ind.t(m1 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1, 
-                    summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
-                    harm_d_kav$d)
-tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1, 
-                    summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
-                    fair_d_kav$d)
-tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1, 
-                    summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
-                    ingroup_d_kav$d)
-tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1, 
-                    summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
-                    authority_d_kav$d)
-tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1, 
-                    summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
-                    purity_d_kav$d)
-
-tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]))
-tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
-
-apa_table(tableprint_kav,
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Kavanaugh Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7))
-          )
-```
-
-```{r exp2-tablegs, results = 'asis', echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint_gs = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
-
-#calculate d
-#harm
-harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d_gs = d.ind.t(m1 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d_gs = d.ind.t(m1 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d_gs = d.ind.t(m1 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d_gs = d.ind.t(m1 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T), 
-                 m2 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1, 
-                    summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
-                    harm_d_gs$d)
-tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1, 
-                    summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
-                    fair_d_gs$d)
-tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1, 
-                    summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
-                    ingroup_d_gs$d)
-tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1, 
-                    summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
-                    authority_d_gs$d)
-tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1, 
-                    summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
-                    purity_d_gs$d)
-
-tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]))
-tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
-
-apa_table(tableprint_gs,
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Government Shutdown Results - Multilevel Model", 
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7))
-          )
-```
-
-```{r conference-pic_kav, eval = F, include = F}
-library(ggplot2)
-library(reshape)
-
-cleanup = theme(panel.grid.major = element_blank(), 
-                panel.grid.minor = element_blank(), 
-                panel.background = element_blank(), 
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 10))
-
-graphdata_kav = as.data.frame(tableprint_kav)
-graphlong_kav = melt(graphdata_kav[ , c(1,2,4)], 
-                 id = "Foundation")
-graphlong2_kav = melt(graphdata_kav[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong_kav$sd = graphlong2_kav$value
-graphlong_kav$lower = as.numeric(as.character(graphlong_kav$value)) - 2*as.numeric(as.character(graphlong_kav$sd))
-graphlong_kav$upper = as.numeric(as.character(graphlong_kav$value)) + 2*as.numeric(as.character(graphlong_kav$sd))
-
-graphlong_kav$value = as.numeric(as.character(graphlong_kav$value))
-
-graph_data_kav = ggplot(graphlong_kav, aes(Foundation, value, color = variable)) + 
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), 
-                position = position_dodge(width = 0.90),
-                width = .2) + 
-  cleanup +
-  ylab("Mean Weighted Valence") + 
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-#tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
-#     height = 3, units = 'in', compression = "lzw")
-#plot(graph_data_kav)
-#dev.off()
-```
-
-```{r conference-pic_gs, eval = F, include = F}
-graphdata_gs = as.data.frame(tableprint_gs)
-graphlong_gs = melt(graphdata_gs[ , c(1,2,4)], 
-                 id = "Foundation")
-graphlong2_gs = melt(graphdata_gs[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong_gs$sd = graphlong2_gs$value
-graphlong_gs$lower = as.numeric(as.character(graphlong_gs$value)) - 2*as.numeric(as.character(graphlong_gs$sd))
-graphlong_gs$upper = as.numeric(as.character(graphlong_gs$value)) + 2*as.numeric(as.character(graphlong_gs$sd))
-
-graphlong_gs$value = as.numeric(as.character(graphlong_gs$value))
-
-graph_data_gs = ggplot(graphlong_gs, aes(Foundation, value, color = variable)) + 
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), 
-                position = position_dodge(width = 0.90),
-                width = .2) + 
-  cleanup +
-  ylab("Mean Weighted Valence") + 
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-#tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4, 
-#     height = 3, units = 'in', compression = "lzw")
-#plot(graph_data_gs)
-#dev.off()
-```
-
-# Discussion
-
-The results obtained in Experiment 2 are slightly more in line with expectations from Moral Foundations Theory, however, in all but one case, the differences were not statistically significant.
-The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given @Graham2009.
-Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the effects much smaller than reported in @Graham2009.
-While not significant, fairness was endorsed more by conservatives in both cases.
-Contradictorily, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
-
-Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by Moral Foundations Theory.
-One issue that Experiment 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
-For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
-The original predictions made by the Moral Foundations are very simplistic and likely much more complex in reality.
-
-# Conclusions
-
-Within the theoretical framework of Moral Foundations Theory [@Haidt2007], we attempted to devise a method leveraging the Moral Foundations Dictionary [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
-In Experiment 1,the results obtained were not significant in any statistical or practical sense.
-There was a small effect found for the *authority/respect* foundation according to Cohen's *d*, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-In Experiment 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
-Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of Moral Foundations Theory in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive, the researchers still retain confidence in the overall structure of the methodology established in the current study.
-Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-The researchers implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
-
-However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
-As mentioned before, MFD is a measure developed from Moral Foundations Theory [@Graham2009].
-Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
-Going beyond specific instruments, other theoretical perspectives may be more equipped to explain political differences in discourse.
-Likewise, an atheoretical approach in which large quantities of data are collected from which theories are formulated may be best suited to this area of research.
-
-In critiquing Moral Foundations Theory, @Schien2015 proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
-Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else [@Gray2014, @Schien2015].
-Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
-For example, in the case of abortion, liberals tend to identify the primary harm to the mother leading to a pro-choice position whereas conservative tend to identify the primary harm to the fetus leading to a pro-life position.
-While as of yet, no linguistic measurement of dyadic morality exists; such an approach may be able to better identify the systematic differences between liberals and conservatives.
-
-Turning to atheoretical approaches, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
-Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
-The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
-Likewise, there are several approaches to analyzing such data, including linear models (like multi-level models) and network-style models such as latent semantic analysis [@Landauer1998].
-Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
-
-Never before has political discourse represented such fertile ground for psychological research.
-The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
-Along with this recent increase in the amount of text information, there is now an obligation on the part of researchers to devise proper methods for analyzing that text.
-Solid methodologies must be constructed and periodically improved to keep pace with evolving technologies.
-Likewise, a strong theoretical foundation is paramount to making sense of the current and future media ecosystem.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
-
-\newpage
-
-# Appendix
-
-```{r appendix_mfd, results = 'asis', echo = FALSE, message = F}
-orig_mfd = read.csv("../exp1_data/original_mfd.csv", stringsAsFactors = F, fileEncoding="UTF-8")
-####build the table here####
-tableprint = matrix(NA, nrow=length(orig_mfd), ncol=5)
-colnames(tableprint) = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity")
-
-#tableprint[ , 1] = unique(final_gs$Source)
-#tableprint[ , 1] = orig_mfd[,1]
-#tableprint[ , 2] = orig_mfd[,2]
-#tableprint[ , 3] = orig_mfd[,3]
-#tableprint[ , 4] = orig_mfd[,4]
-#tableprint[ , 5] = orig_mfd[,5]
-
-tableprint = tableprint[c(1,2,3,4,5)]
-tableprint = orig_mfd
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Original Moral Foundations Dictionary from Graham et al. (2009)",
-          caption = "Moral Foundations Dictionary", 
-          col.names = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity"),
-          format = "latex",
-          escape = F,
-          small = T, 
-          align = c("l", rep("c", 6))
-          )
-```

### 2022-03-03 manuscript_version/manuscript_metapsych.Rmd
finally fixed the comma in the tables

@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))
+tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
 
 tableprint = tableprint[c(3, 4, 1, 2) , ]
-```
-
-```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Experiment 1 - Descriptive Statistics by Source", 
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 10)), 
-          font_size = 'footnotesize'
-          )
 ```
@@
 Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.
+
+```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
+#change this to match
+apa_table(as.data.frame(tableprint),
+          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
+          caption = "Experiment 1 - Descriptive Statistics by Source", 
+          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
+          format = "latex",
+          escape = F,
+          align = c("l", rep("c", 10)), 
+          font_size = 'footnotesize',
+          placement = "h"
+          )
+```
 
@@
 
-tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]))
+tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]), big.mark = "")
 tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
@@
           align = c("l", rep("c", 7)),
-          font_size = 'footnotesize'
+          font_size = 'footnotesize',
+          placement = "h"
           )
@@
 
-Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive statistics for articles about the partial government shutdown.
-Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each source on this topic.
-*Sean Hannity*, *Rush Limbaugh*, and *The Blaze* published fewer than 100 articles while *Fox News* published 1,013 articles.
-*Fox News* again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
-*Politico* had the most types on average.
-For this topic, *Fox News* featured the lowest reading grade level while *Slate* featured the highest reading grade level.
-For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
-
 ```{r exp2_descriptive_calculate_kav, include = F, echo = F}
@@
 tableprint3[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
-tableprint3[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint3[ , c(2,3,6,7,8,9,10,11)]))
+tableprint3[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint3[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
 tableprint3 = tableprint3[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
@@
           align = c("l", rep("c", 10)),
-          font_size = 'footnotesize'
+          font_size = 'footnotesize',
+          placement = "h"
           )
 ```
+
+Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive statistics for articles about the partial government shutdown.
+Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
+Once again, there was variation in the number of articles published by each source on this topic.
+*Sean Hannity*, *Rush Limbaugh*, and *The Blaze* published fewer than 100 articles while *Fox News* published 1,013 articles.
+*Fox News* again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
+*Politico* had the most types on average.
+For this topic, *Fox News* featured the lowest reading grade level while *Slate* featured the highest reading grade level.
+For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
 
@@
 
-tableprint4[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint4[ , c(2,3,6,7,8,9,10,11)]))
+tableprint4[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint4[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
 
@@
           align = c("l", rep("c", 10)),
-          font_size = 'footnotesize'
+          font_size = 'footnotesize',
+          placement = "h"
           )
@@
 Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp2-tablekav).
-
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations.
-A small-to-medium effect size was observed for *authority/respect*.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
-As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Experiment 1.
-As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
 
@@
 
-tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]))
+tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]), big.mark = "")
 tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
@@
           align = c("l", rep("c", 7)),
-          font_size = 'footnotesize'
+          font_size = 'footnotesize',
+          placement = "h"
           )
 ```
+
+For news articles about the partial U.S.
+Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations (see Table \@ref(tab:exp2-tablegs)).
+A small-to-medium effect size was observed for *authority/respect*.
+The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
+This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
+As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
+Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
+Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
+
+Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
+A similar pattern was observed for the results in Experiment 1.
+As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
 
@@
 
-tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]))
+tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]), big.mark = "")
 tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))

### 2022-03-03 manuscript_version/manuscript_metapsych.tex
update for tables why do they hate me
finally fixed the comma in the tables

@@
   english,
-  man]{apa6}
+  man,floatsintext]{apa6}
 \title{Moral Foundations of U.S. Political News Organizations}
@@
 \keywords{politics, morality, psycholinguistics}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{csquotes}
@@
 
-\begin{table}[pt]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp1-source-descriptives}Experiment 1 - Descriptive Statistics by Source}
-
-\footnotesize{
-
-\begin{tabular}{lcccccclccc}
-\toprule
-Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
-\midrule
-NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.28 & 14.00 & 3.93\\
-New York Times & 0.30 & 0.13 & 406 & 452579 & 1,114.73 & 511.86 & 454.27 & 154.58 & 16.42 & 3.36\\
-Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.35 & 120.75 & 18.57 & 7.89\\
-Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.56 & 189.00 & 17.25 & 7.21\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 We calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp1-source-descriptives}Experiment 1 - Descriptive Statistics by Source}
+
+\footnotesize{
+
+\begin{tabular}{lcccccccccc}
+\toprule
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+\midrule
+NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.28 & 14.00 & 3.93\\
+New York Times & 0.30 & 0.13 & 406 & 452579 & 1114.73 & 511.86 & 454.27 & 154.58 & 16.42 & 3.36\\
+Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.35 & 120.75 & 18.57 & 7.89\\
+Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.56 & 189.00 & 17.25 & 7.21\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{inferential-statistics}{%
@@
 
-\begin{table}[pt]
+\begin{table}[h]
 
@@
 
-Table \ref{tab:exp2-source-descriptives-gs} displays descriptive statistics for articles about the partial government shutdown.
-Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each source on this topic.
-\emph{Sean Hannity}, \emph{Rush Limbaugh}, and \emph{The Blaze} published fewer than 100 articles while \emph{Fox News} published 1,013 articles.
-\emph{Fox News} again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
-\emph{Politico} had the most types on average.
-For this topic, \emph{Fox News} featured the lowest reading grade level while \emph{Slate} featured the highest reading grade level.
-For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
-
-\begin{table}[pt]
+\begin{table}[h]
 
@@
 
-\small{
+\footnotesize{
 
-\begin{tabular}{lcccccclccc}
+\begin{tabular}{lcccccccccc}
 \toprule
@@
 NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.55 & 3.67\\
-New York Times & 0.33 & 0.13 & 653 & 723569 & 1,108.07 & 570.31 & 461.26 & 174.20 & 9.52 & 1.79\\
-Politico & 0.32 & 0.10 & 689 & 1069292 & 1,551.95 & 1,045.47 & 614.66 & 358.68 & 12.10 & 2.66\\
+New York Times & 0.33 & 0.13 & 653 & 723569 & 1108.07 & 570.31 & 461.26 & 174.20 & 9.52 & 1.79\\
+Politico & 0.32 & 0.10 & 689 & 1069292 & 1551.95 & 1045.47 & 614.66 & 358.68 & 12.10 & 2.66\\
 Slate & 0.29 & 0.12 & 272 & 229896 & 845.21 & 612.22 & 332.42 & 168.17 & 12.30 & 2.48\\
@@
 Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 10.87 & 2.12\\
-Fox News & 0.29 & 0.11 & 646 & 1304048 & 2,018.65 & 2,709.77 & 534.47 & 404.21 & 9.71 & 1.86\\
+Fox News & 0.29 & 0.11 & 646 & 1304048 & 2018.65 & 2709.77 & 534.47 & 404.21 & 9.71 & 1.86\\
 Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.76 & 2.40\\
-Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1,552.72 & 1,258.51 & 419.00 & 225.80 & 9.17 & 8.86\\
+Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1552.72 & 1258.51 & 419.00 & 225.80 & 9.17 & 8.86\\
 \bottomrule
@@
 
-\begin{table}[pt]
+Table \ref{tab:exp2-source-descriptives-gs} displays descriptive statistics for articles about the partial government shutdown.
+Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
+Once again, there was variation in the number of articles published by each source on this topic.
+\emph{Sean Hannity}, \emph{Rush Limbaugh}, and \emph{The Blaze} published fewer than 100 articles while \emph{Fox News} published 1,013 articles.
+\emph{Fox News} again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
+\emph{Politico} had the most types on average.
+For this topic, \emph{Fox News} featured the lowest reading grade level while \emph{Slate} featured the highest reading grade level.
+For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
+
+\begin{table}[h]
 
@@
 NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.20 & 3.16\\
-New York Times & 0.33 & 0.13 & 752 & 836811 & 1,112.78 & 532.72 & 472.95 & 177.57 & 10.10 & 1.74\\
-Politico & 0.29 & 0.10 & 222 & 349499 & 1,574.32 & 875.63 & 638.32 & 313.34 & 11.31 & 1.26\\
+New York Times & 0.33 & 0.13 & 752 & 836811 & 1112.78 & 532.72 & 472.95 & 177.57 & 10.10 & 1.74\\
+Politico & 0.29 & 0.10 & 222 & 349499 & 1574.32 & 875.63 & 638.32 & 313.34 & 11.31 & 1.26\\
 Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.87 & 2.53\\
@@
 Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.71 & 2.05\\
-Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2,763.29 & 3,405.44 & 637.30 & 494.00 & 9.43 & 1.95\\
+Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2763.29 & 3405.44 & 637.30 & 494.00 & 9.43 & 1.95\\
 Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.36 & 4.81\\
-Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1,956.79 & 1,544.14 & 482.79 & 252.79 & 9.77 & 7.64\\
+Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1956.79 & 1544.14 & 482.79 & 252.79 & 9.77 & 7.64\\
 \bottomrule
@@
 
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations.
-A small-to-medium effect size was observed for \emph{authority/respect}.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Experiment 1 in which the largest effect size was observed for \emph{authority/respect}.
-As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Experiment 1.
-As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
-
-\begin{table}[pt]
+\begin{table}[h]
 
@@
 
-\begin{table}[pt]
+For news articles about the partial U.S.
+Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations (see Table \ref{tab:exp2-tablegs}).
+A small-to-medium effect size was observed for \emph{authority/respect}.
+The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
+This effect was similar to Experiment 1 in which the largest effect size was observed for \emph{authority/respect}.
+As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
+Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
+Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
+
+Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
+A similar pattern was observed for the results in Experiment 1.
+As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
+
+\begin{table}[h]
 
@@
 
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+
 \hypertarget{refs}{}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Clifford2013}{}}%
-Clifford, S., \& Jerit, J. (2013). How words do the work of politics: Moral foundations theory and the debate over stem cell research. \emph{The Journal of Politics}, \emph{75}(3), 659--671.
+Clifford, S., \& Jerit, J.
+(2013).
+How words do the work of politics: Moral foundations theory and the debate over stem cell research.
+\emph{The Journal of Politics}, \emph{75}(3), 659--671.
+\url{https://doi.org/10.1017/S0022381613000492}
 
@@
 Do liberals and conservatives use different moral languages?
-Two replications and six extensions of graham, haidt, and nosek's (2009) moral text analysis.
+Two replications and six extensions of {G}raham, {H}aidt, and {N}osek's (2009) moral text analysis.
 \emph{Journal of Research in Personality}, \emph{84}, 103906.
+\url{https://doi.org/10.1016/j.jrp.2019.103906}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Frimer2015}{}}%
-Frimer, J. A., Tell, C. E., \& Haidt, J. (2015). Liberals condemn sacrilege too: The harmless desecration of cerro torre. \emph{Social Psychological and Personality Science}, \emph{6}(8), 878--886.
+Frimer, J.
+A., Tell, C.
+E., \& Haidt, J.
+(2015).
+Liberals condemn sacrilege too: The harmless desecration of {C}erro {T}orre.
+\emph{Social Psychological and Personality Science}, \emph{6}(8), 878--886.
+\url{https://doi.org/10.1177/1948550615597974}
 
@@
 Morality between the lines: Detecting moral sentiment in text.
-In \emph{Proceedings of IJCAI 2016 workshop on computational modeling of attitudes}.
+In \emph{{Proceedings of IJCAI 2016 workshop on Computational Modeling of Attitudes}}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Gray2015}{}}%
-Gray, K., \& Keeney, J. E. (2015). Disconfirming moral foundations theory on its own terms: Reply to graham (2015). \emph{Social Psychological and Personality Science}, \emph{6}(8), 874--877.
+Gray, K., \& Keeney, J.
+E.
+(2015).
+Disconfirming moral foundations theory on its own terms: Reply to {G}raham (2015).
+\emph{Social Psychological and Personality Science}, \emph{6}(8), 874--877.
+\url{https://doi.org/10.1177/1948550615592243}
 
@@
 The myth of harmless wrongs in moral cognition: Automatic dyadic completion from sin to suffering.
-\emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1600.
+\emph{Journal of Experimental Psychology: General}, \emph{143}(4), 1600--1615.
+\url{https://doi.org/10.1037/a0036149}
 
@@
 \emph{Behavior Research Methods}, \emph{53}(1), 232--246.
+\url{https://doi.org/10.3758/s13428-020-01433-0}
 
@@
 (1975).
-{Derivation of New Readability Formulas (Automated Readability Index, Fog Count and Flesch Reading Ease Formula) for Navy Enlisted Personnel}.
+Derivation of new readability formulas (automated readability index, fog count and {F}lesch reading ease formula) for {N}avy enlisted personnel.
 \url{https://doi.org/10.21236/ADA006655}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sagi2014}{}}%
-Sagi, E., \& Dehghani, M. (2014). Measuring moral rhetoric in text. \emph{Social Science Computer Review}, \emph{32}(2), 132--144.
+Sagi, E., \& Dehghani, M. (2014). Measuring moral rhetoric in text. \emph{Social Science Computer Review}, \emph{32}(2), 132--144. \url{https://doi.org/10.1177/0894439313506837}
 
@@
 \emph{Personality and Social Psychology Bulletin}, \emph{41}(8), 1147--1163.
+\url{https://doi.org/10.1177/0146167215591501}
 
@@
 \emph{Journal of Language and Politics}, \emph{17}(2), 195--221.
+\url{https://doi.org/10.1075/jlp.17034.ste}
 
@@
 (2011).
-{Can Innate , Modular {`` Foundations ''} Explain Morality ?
-Challenges for Haidt's Moral Foundations Theory}.
+Can innate , modular "foundations" explain morality?
+Challenges for {H}aidt's {M}oral {F}oundations {T}heory.
 \emph{Journal of Cognitive Neuroscience}, \emph{23}(9), 2103--2116.
+\url{https://doi.org/10.1162/jocn.2011.21637}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-Wickham, H. (2016). {Package ` rvest '}. Retrieved from \url{https://cran.r-project.org/package=rvest}
+Wickham, H. (2016). {Package `rvest'}. Retrieved from \url{https://cran.r-project.org/package=rvest}
 
@@
 
+\endgroup
+
 \end{document}

### 2023-07-06 manuscript_version/revision/manuscript_metapsych_revision.Rmd
Add files via upload

--- 2022-03-03 manuscript_version/manuscript_metapsych.Rmd
@@
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Experiment 1, we gathered political articles from four sources.
+In Study 1, we gathered political articles from four sources.
 We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
-In Experiment 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Study 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
@@
 
-Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.Conducting two close conceptual replication and six extension studies, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.
+Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.
+Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S.
+Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.
 In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
 Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
+Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores.
+Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects.
 Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
@@
 While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
+Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.
 
@@
 We first test differences in a general news corpus compared liberal sources (National Public Radio [NPR] and the New York Times [NYT]) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavaugh's U.S.
+Second, we examined news about specific political events: Brett Kavanaugh's U.S.
 Supreme Court nomination and the U.S.
 Government Shutdown in 2018-2019.
-In the second experiment, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
+In the second study, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
 To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
@@
 
-# Experiment 1
+# Study 1
 
@@
 
-For Experiment 1, we approached the study with the intention to answer a method question.
+For the first natural experiment, we approached the study with the intention to answer a method question.
 That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
@@
 V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Experiment 1 - Descriptive Statistics by Source", 
+          caption = "Study 1 - Descriptive Statistics by Source", 
           col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Experiment 1 Results - Multilevel Model",
+          caption = "Study 1 Results - Multilevel Model",
           col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
@@
 
-The results obtained in Experiment 1 fail to support the differences predicted by MFT.
+The results obtained in Study 1 fail to support the differences predicted by MFT.
 First, differences between liberal and conservative news sources failed to reach statistical or practical (effect size) significance for any foundations.
@@
 The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-To address this limitation, two changes that were subsequently employed in Experiment 2.
-First, we elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
+To address this limitation, two changes that were subsequently employed in Study 2.
+First, we elected to include more news sources for web scraping and analysis in addition to the four used in Study 1.
 Second, we chose to focus  data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
@@
 government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Experiment 2 is the best test of the MFT and the MFD in the context of partisan news.
-
-# Experiment 2
+Hence, Study 2 is the best test of the MFT and the MFD in the context of partisan news.
+
+# Study 2
 
@@
 
-In contrast to Experiment 1, we approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+In contrast to Study 1, we approached Study 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For the second natural experiment, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
@@
 news sources.
-As in Experiment 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
+As in Study 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
 The sources favored by the highest proportion of consistent liberals were the *NYT*, *NPR*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
@@
 
-As in Experiment 1, the text was scanned with *ngram* [@Schmidt2017].
+As in Study 1, the text was scanned with *ngram* [@Schmidt2017].
 Again, blank articles, text from the Disqus system, and duplicate articles were removed.
@@
 We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Experiment 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
+As in Study 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
 
@@
 
-We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Experiment 1.
+We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Study 1.
 Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
@@
 The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*.
-As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
+This effect was similar to Study 1 in which the largest effect size was observed for *authority/respect*.
+As noted before, the effect found in Study 1 was in the opposite direction as what was hypothesized.
 Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
+Owing to a lack of similar effects for either Study 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
 
 Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Experiment 1.
-As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
+A similar pattern was observed for the results in Study 1.
+As in Study 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
 
@@
 
-The results obtained in Experiment 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
+The results obtained in Study 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
 The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given @Graham2009.
@@
 
-Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
-One issue that Experiment 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
+Together with Study 1 and past work, Study 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
+One issue that Study 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
 For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
@@
 Within the theoretical framework of MFT [@Haidt2007], we attempted to devise a method leveraging the MFD [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
-In Experiment 1,the results obtained were not significant in any statistical or practical sense.
+In Study 1,the results obtained were not significant in any statistical or practical sense.
 There was a small effect found for the *authority/respect* foundation according to Cohen's *d*, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-In Experiment 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
+In Study 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
 Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.

### 2023-07-21 manuscript_version/revision/review_response_erin.txt
adding text version in case of merge conflicts

Reviewer 1

This manuscript reports results from a pair of studies examining the validity of the Moral Foundations Dictionary (MFD), specifically by comparing use of terms from the MFD by previously-identified conservative and liberal news sources. The first study compares MFD term usage in two liberal (NPR, NYT) and conservative (Fox News, Breitbart) news sources, finding no significant differences in MFD words used for any of the five moral foundations dimensions between the two types of news sources. A second study, its design based on part on lessons learned from issues with data collection from the first study, did the same with twenty news sources and specifically with coverage of Brett Kavanaugh’s Supreme Court of the United States nomination and confirmation and the 2018-2019 U.S. government shutdown stemming from disputes about a proposed U.S.-Mexico border wall. The second study found a significant (albeit small, effect-wise) difference between liberal and conservative sources only for the harm-care dimension, as the manuscript notes has been found in previous research, but only for the Kavanaugh coverage. Results are interpreted as casting further doubt on the utility of the MFD, and more conceptually the applicability of the MFT dimensions, to explain partisan political differences. I appreciate the level of detail in the description of the studies’ method and analysis, including unexpected issues such as the challenges in scraping some of the first study’s sources. The thorough and highly organized presentation of open materials and the clear explanation of methods including use of specific R packages provides useful guidance to both critical examination of these studies and future research building on them.

The review of research behind the MFT, MFQ, and MFD is parsimonious but thorough, and in my opinion quite reasonable about the shaky conceptual foundations of all three as well as the limited empirical evidence for reliability and validity of the measures. If anything, the review of the literature is forgiving given how often measures like MFT do not even demonstrate adequate inter-item reliability. In any case, the rationale for the study is clearly justified by a fair review of a popular conceptual framework that very much has feet of clay. I also find the justification for the selection of sources to be adequate, and appreciate the authors' basing them in the Mitchell et al. article rather than simply relying on an intuitive assumed rationale for the selection.

RESPONSE:

If there is more systematic justification for why these precise four news sources were chosen over all other options for Study 1, it might be good to share. If there is no such specific justification, though, I don’t think it is a problem that needs addressing further as there is adequate rationale for these two pairs of sources to be—at the very least—fine examples of the two source variable conditions. (Although a critique might be that Breitbart is arguably less mainstream than the other three sources, though that doesn’t seem to invalidate the study’s findings.)

RESPONSE: [Erin]
As described in text, mostly these were chosen due to perceived and self-described political lean. However, we added a sentence about how they also practically worked best:

"At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible."

Given that in many ways the first study ends up being something of a de facto pilot study for the second (which I believe adds substantially to the credibility of the latter as well as the message of the pair as a package here), this is not a major issue as five times as many sources are used in the second study with similar findings. The manuscript seems to imply that these twenty sources represent the top ten sources from each valence of lean in the Mitchel et al., article; if that is so, it may be good to state as much more clearly. If I misunderstood and more arbitrary criteria were used to select each set of ten sources from the Mitchell et al. article’s results, that may need to be clarified as well.

RESPONSE: [Erin]

Again, though, I do not perceive these as concerns even if there is no more specific justification given that these seem appropriate conditions for studies viewed as experiments rather than as some sort of representative source sample. That said, I am reluctant to consider these studies simply experiments per se rather than perhaps as natural experiments. I am not sure I am correct, as I have limited experience with the latter, but I wonder if it might at least be worth suggesting renaming both studies as natural experiments rather than solely as experiments. That said, I defer to the editorial staff, reviewers, and authors themselves regarding whether the manuscript would be more accurate continuing to describe these studies as experiments or if it might be a good idea to call them natural experiments.

RESPONSE: We understand the point of view of this critique and have changed the language accordingly throughout the manuscript.

As a minor point, given that the studies are described as "a further conceptual replication of Frimer (2020)," which seems apt (as well as some of the measures and interpretation thereof are also based on Frimer), it may be useful to describe the findings thereof for the reader at least briefly (even if only in conceptual terms). The study is mentioned parenthetically in a sentence describing previous literature, but a sentence or so more about the specific contribution of Frimer (2020) might aid the reader given it is described as uniquely central to these studies' motivation and design.

RESPONSE: The section in the literature review describing the Frimer study has been expanded like shown below.

“Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD. Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S. Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009. In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words). Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness. Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores. Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects… Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.”

While the manuscript is well-written, there is at least one error I would consider very important, namely at least one misspelling of Brett Kavanaugh's surname. It would, of course, be a good idea to take a very close look for such errors, even if they are not technically germane to the credibility of the studies' design and results. I believe that addressing these issues will result in a useful contribution to the literature about a theoretical framework and measure that seems increasingly in need of some reconsideration—particularly given its popularity.

RESPONSE: The misspelling has been fixed.

Reviewer 2

The present manuscript applies a version of the moral foundations dictionary to news articles. I have to disclose that I am quite strongly predisposed against the validity and generalizability of MFT overall, first because it is extremely US-centric, second because I have seen it fail quite spectacularly in survey applications. I am also quite skeptical of dictionary-based approaches overall. The negative findings of the paper were comfortably confirming my expectations, which might positively bias my review.

I have several major and minor concerns:

(1) I don't exactly understand the purpose of the paper: Is it a validation study of the MFD or an attempted application of MFT to the analysis of media content? This concerns the interpretation of the findings: Do we believe that moral foundations simply did not impact the coverage of the issues, or just that the MFD did not pick up the latent messages because it is a flawed instrument? Would the cited improved methods such as manual coding or modern large language models be more successful? We do not know because the MFD is not systematically compared to alternative approaches. Ironically, the authors mention the multi-trait-multi-method approaches related to MFT, but do not apply them themselves. However, applying on method to one sample, tells us little about the validity of the method *or* the idiosyncrasies of the sample. Therefore, I am unsure what we can learn from the paper.

RESPONSE: [Kayden; should we include the MTMM study?]

(2) The authors extend previous research on the MFD by "augmenting" the word counts with scores from another dictionary (Warriner et al.) I don't have access to the cited papers, especially Frimer's, but if this is an original idea by the authors, it needs *much* more theoretical and methodological justification. Previous applications of the MDF have by design only tapped the salience of the different dimensions in different texts, and it's not obvious to me whether extending this to valence is as straightforward as the present paper suggests. And even if one accepts the premise that context-free ratings of word lemmas by Mturk Workers are useful measures of some kind of word "valence", it's the authors burden of proof that multiplying one set of scores with a completely different set of word scores from another task makes sense. At the very least, I'd expect a quasi-replication study to start out with the traditional application of the MFD, i.e. simple word counts/relative frequencies as outcomes, and then check if and how multiplying them by z-standardized (why btw?) valence scores changes things.

RESPONSE: [Erin]

(3) As a communication scholar, I find the way outlets' leanings are measured by the composition of their readers at least questionable. I know it is a convenient shortcut, but again the question is whether the inferences drawn in the paper are really about the target audience, or the journalists' attitudes and moral predispositions (or the attitudes of the politicians quoted in the news articles). I encourage the authors to more thoroughly consider what kind of theoretical foundation their own arguments (or the cited previous applications of MFT to texts) have. A helpful source could be Benoit, K., Laver, M., & Mikhaylov, S. (2009). Treating words as data with error: Uncertainty in text statements of policy positions. American Journal of Political Science, 53(2), 495-513.

RESPONSE: While we appreciate the complexities of measuring partisan lean of media outlets, we justify the selection and categorization of the news outlets using a Pew Research Center study. Obviously other methods could have been used, but we feel that this is sufficient justification.

“We determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.”

(4) The manuscript can be shortened by removing redundancies between study 1 and 2 descriptions. Also, if the text statistics such as readability are not used as controls or otherwise in the main analysis, why bother with them? While I appreciate the excellent documentation of the scraping, much of this can be moved to a supplement.

RESPONSE: [Erin]

(5) I was really irritated by the use of "Experiment" 1 and 2 in the headings, when no experiments were conducted or at least reported. Please stick to study 1 and 2.

RESPONSE: The wording has been changed.

(6) Reporting the ICC of the Null model with just outlet clustering would be nice and helpful to understand the data.

RESPONSE: [Erin]

(7) Are we sure that linear models are appropriate for the weighted frequency outcomes?

RESPONSE: [Erin]

Reviewer 3

In this article, the authors provide a two-study investigation of the moral leanings of news sources using an approach based on the Moral Foundations Dictionary (MFD). This paper has a number of strengths, and I do believe that we need more work carefully validating dictionary-based approaches to studying moral content (and moral foundations theory) in textual data. I would also like to emphasize that this work is especially impressive being a Master’s thesis. This being said, I also see a number of issues with this manuscript that, in my view, limit the validity of its conclusions. In short, I found myself wondering throughout the methods section(s) as to the extent to which the results observed in this manuscript are due to the analytic decisions that were made rather than due to issues with the MFD (or MFT). This concern is magnified when considering that the authors used a number of rather non-standard techniques compared to extant work. I’ll highlight a few of the most salient issues below: My first concern is the most central to my overall evaluation of the manuscript. I noticed a large number of places where critical methodological details of the analyses conducted in this manuscript were completely left out or glossed over. I appreciate that the authors provided supplemental material containing analysis code, and I’m sure that I could dig through the code and figure out the answers to many of these questions, but it’s critical that methodological choices that are central to the conclusions of the paper be provided in the manuscript itself. A couple of noticeable examples:
•	The details of the valence-weighting procedure applied to the moral foundations words was not clear to me, even after several readings. Was the valence calculated for the moral words themselves, or for the context surrounding the words? How were the z-scores applied (within i.e. within document, within source, overall)? These details are important, because the mean valence of the MFD words varies across different MFD categories, and also because the valence of moral words is almost always contingent on their context (see e.g. Hopp et al., 2021). For example, the sanctity-assigned word “pure” could be be used to refer to “pure water” or to “pure evil.”
•	The details of the MLM’s are also unclear. For example, it seems like political leaning is treated as a categorical variable, but that isn’t mentioned. It’s also unclear how the random intercept for source was created. Again, I could be misunderstanding something, but if source wasn’t nested within political leaning, then creating the random intercept for source would almost certainly wash out any effect that may be attributed to political leaning. I would suggest providing the equations for the models within the text to avoid these sorts of confusions.
RESPONSE: [Erin]

My second concern stems from the first. Given the lack of methodological clarity at several key points in the manuscript, I was somewhat surprised by the forcefulness of the authors’ conclusions. To be clear, I say this as someone who is also quite skeptical of the validity of the MFD (for a more extensive treatment of why, see Hopp et al., 2021). Given that the authors used a customized version of the MFD, I don’t personally see how evidence that the predictions didn’t pan out is evidence that the MFD (much less MFT in general) is less valid.

RESPONSE: [Kayden; should we use the raw scores for comparison?]

This is especially true given that a good deal of the work the authors reference just looks at word counts (not valence-weighted percentages) as indicators of moral-foundations-related differences across sources. As a final note, I would suggest that the authors go through the manuscript with an eye toward including everything that is needed for an interested reader to know the critical methodological details, but also toward removing things that are not germane to the questions that are the authors’ central foci in the manuscript. For example, I would presume that the linguistic complexity analyses could be relegated to supplemental material to make space for more methodological discussion. In sum, although there is much to like about this manuscript, I believe that it needs quite a bit of re-engineering before it’s ready to be published. I would again like to commend the authors on their efforts. I hope that my comments are helpful in continuing to refine this important work.

RESPONSE: [Kayden]

### 2023-07-21 manuscript_version/revision/review_response_erin.txt
updates

@@
 RESPONSE: [Erin]
+We picked the ones based on Mitchell's article that also were practically usable. Therefore, we added this sentence to our second study source section as well:
+
+"These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service."
 
@@
 RESPONSE: [Erin]
+- note if we add the MTMM, this response may be different, so waiting here.
+Also this person seems to think that valence ratings are not useful, so add some notes about how they are very predictive, yada yada.
+
+Critically - also - the MFD was made by just *thinking* about words right? So why is that better than the actual ratings of valence from people?
+
+As noted in text, we z-scored to help with interpretation:
+
+"Valences were z-scored in order to eliminate any ambiguity regarding the direction of the valence. Positive values indicate positive valence, and negative values indicate negative valence."
 
@@
 RESPONSE: [Erin]
+- undecided here maybe something like ...
+Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript.
+Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation.
 
@@
 RESPONSE: [Erin]
+These values have been added to each model table.
 
@@
 RESPONSE: [Erin]
+Each model was checked for assumptions of parametric models. Linearity, normality assumptions were met with some violations of homoscedasticity.
 
@@
 For example, the sanctity-assigned word “pure” could be be used to refer to “pure water” or to “pure evil.”
+
+RESPONSE: [Erin]
+We added an example table of the weighting calculation and rephrased this second completely.
+
+"A complete list of the words for each moral foundation area was created from previous experiments.
+The total number of times each of those words was used in an article was calculated.
+This information was merged with the valence values from the @Warriner2013 dataset.
+A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article.
+The final score was multiplied by 100 to represented a weighted percentage.
+Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article."
+
+Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.
+
 •	The details of the MLM’s are also unclear.
@@
 I would suggest providing the equations for the models within the text to avoid these sorts of confusions.
-RESPONSE: [Erin]
+
+As described in the text:
+
+"Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison."
+
+We would also note that the complete manuscript and code is available on our OSF page: https://osf.io/5kpj7/. We added the equation for the multilevel model directly to the text as well:
+
+"Therefore, the models were calculated by: Weighted Score ~ Political Lean + (~1|Source)."
 

### 2023-07-21 manuscript_version/revision/manuscript_metapsych_revision.Rmd
adding text version in case of merge conflicts
updates

@@
     affiliation   : "2"
-  - name          : "Kayla N. Jordan, Ph.D."
+  - name          : "Kayden N. Jordan, Ph.D."
     affiliation   : "2"
@@
 
-bibliography      : ["metapsych_bib.bib"] #turn this off right now so it knits
+bibliography      : ["../metapsych_bib.bib"] #turn this off right now so it knits
 
@@
 library(knitr)
+library(performance)
+library(dplyr)
 
@@
 
-For the first natural experiment, we approached the study with the intention to answer a method question.
+For the first study, we approached the study with the intention to answer a method question.
 That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
@@
 @Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
+At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible.
 
@@
 
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
-Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurrence were multiplied by their *z*-scored valence.
+A complete list of the words for each moral foundation area was created from previous experiments.
+The total number of times each of those words was used in an article was calculated.
+This information was merged with the valence values from the @Warriner2013 dataset.
+A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article.
+The final score was multiplied by 100 to represented a weighted percentage.
+Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article.
 Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence.
@@
 Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
+See Table \@ref(tab:example-weight) for an example.
 
@@
 harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
+#no spurn available
 ```
@@
 
+harm_icc <- lme(MFDweight ~ 1, 
+                data = harm_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
+
 harm_model = lme(MFDweight ~ lean,
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
+                 random = list(~1|Source)
+                 )
 summary(harm_model)
+
+# check linearity
+random <- rchisq(nrow(harm_final_temp), 7)
+residuals <- scale(residuals(harm_model))
+fitted <- scale(fitted(harm_model))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 
+fair_icc <- lme(MFDweight ~ 1, 
+                data = fair_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
+
 fair_model = lme(MFDweight ~ lean,
@@
 summary(fair_model)
+
+# check linearity
+random <- rchisq(nrow(fair_final_temp), 7)
+residuals <- scale(residuals(fair_model))
+fitted <- scale(fitted(fair_model))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 
+ingroup_icc = lme(MFDweight ~ 1,
+                 data = ingroup_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 ingroup_model = lme(MFDweight ~ lean,
@@
 summary(ingroup_model)
+
+# check linearity
+random <- rchisq(nrow(ingroup_final_temp), 7)
+residuals <- scale(residuals(ingroup_model))
+fitted <- scale(fitted(ingroup_model))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 
+authority_icc = lme(MFDweight ~ 1,
+                 data = authority_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 authority_model = lme(MFDweight ~ lean,
@@
 summary(authority_model)
+
+# check linearity
+random <- rchisq(nrow(authority_final_temp), 7)
+residuals <- scale(residuals(authority_model))
+fitted <- scale(fitted(authority_model))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 
+purity_icc = lme(MFDweight ~ 1,
+                 data = purity_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 purity_model = lme(MFDweight ~ lean,
@@
 summary(purity_model)
+
+# check linearity
+random <- rchisq(nrow(purity_final_temp), 7)
+residuals <- scale(residuals(purity_model))
+fitted <- scale(fitted(purity_model))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
+```
+
+```{r example-weight, results = 'asis', include = FALSE}
+temp_table <- harm_final_data %>% 
+  filter(Freq > 0) %>% 
+  arrange(-Freq) %>% 
+  group_by(Var1) %>% 
+  slice_head() %>% 
+  group_by(URL) %>% 
+  arrange(-Freq) %>% 
+  slice_head() %>% 
+  ungroup() %>% 
+  slice_sample(n = 15, replace = F)
+
+apa_table(temp_table %>% select(-URL), 
+          note = "",
+          caption = "Example of Weighted Coding for Harm Words",
+          col.names = c("Source", "Concept", "Frequency", "Total Words", "Valence", "Weighted Score"),
+          format = "latex",
+          escape = F,
+          align = c("l", "l", rep("c", 4)),
+          font_size = 'footnotesize',
+          placement = "h"
+          )
 ```
@@
 Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
+Therefore, the models were calculated by: Weighted Score ~ Political Lean + (~1|Source).
 
@@
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint2 = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint2) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+tableprint2 = matrix(NA, ncol = 9, nrow = 5)
+colnames(tableprint2) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
 
@@
                     summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
-                    harm_d$d)
+                    harm_d$d, icc(harm_icc)$ICC_unadjusted)
 tableprint2[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1,
                     summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
-                    fair_d$d)
+                    fair_d$d, icc(fair_icc)$ICC_unadjusted)
 tableprint2[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1,
                     summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
-                    ingroup_d$d)
+                    ingroup_d$d, icc(ingroup_icc)$ICC_unadjusted)
 tableprint2[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1,
                     summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
-                    authority_d$d)
+                    authority_d$d, icc(authority_icc)$ICC_unadjusted)
 tableprint2[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1,
                     summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
-                    purity_d$d)
+                    purity_d$d, icc(purity_icc)$ICC_unadjusted)
 
@@
 tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
+tableprint2[ , 9] = printp(as.numeric(tableprint2[ , 7]))
 ```
@@
           caption = "Study 1 Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
           format = "latex",
@@
 In contrast to Study 1, we approached Study 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For the second natural experiment, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+For the second study, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
@@
 The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
+These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
@@
 harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
+
+harm_icc_k <- lme(MFDweight ~ 1,
+                 data = harm_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 harm_model_kav = lme(MFDweight ~ lean,
@@
 r.squaredGLMM(harm_model_kav)
+
+# check linearity
+random <- rchisq(nrow(harm_final_temp_kav), 7)
+residuals <- scale(residuals(harm_model_kav))
+fitted <- scale(fitted(harm_model_kav))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 fair_final_temp_kav$Source[grepl("hannity.com", fair_final_temp_kav$URL)] = "Sean Hannity"
+
+fair_icc_k <- lme(MFDweight ~ 1,
+                 data = fair_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 fair_model_kav = lme(MFDweight ~ lean,
@@
 summary(fair_model_kav)
+
+# check linearity
+random <- rchisq(nrow(fair_final_temp_kav), 7)
+residuals <- scale(residuals(fair_model_kav))
+fitted <- scale(fitted(fair_model_kav))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 ingroup_final_temp_kav$Source[grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Sean Hannity"
+
+ingroup_icc_k <- lme(MFDweight ~ 1,
+                 data = ingroup_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 ingroup_model_kav = lme(MFDweight ~ lean,
@@
 summary(ingroup_model_kav)
+
+# check linearity
+random <- rchisq(nrow(ingroup_final_temp_kav), 7)
+residuals <- scale(residuals(ingroup_model_kav))
+fitted <- scale(fitted(ingroup_model_kav))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 authority_final_temp_kav$Source[grepl("hannity.com", authority_final_temp_kav$URL)] = "Sean Hannity"
+
+authority_icc_k <- lme(MFDweight ~ 1,
+                 data = authority_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 authority_model_kav = lme(MFDweight ~ lean,
@@
 summary(authority_model_kav)
+
+# check linearity
+random <- rchisq(nrow(authority_final_temp_kav), 7)
+residuals <- scale(residuals(authority_model_kav))
+fitted <- scale(fitted(authority_model_kav))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 purity_final_temp_kav$Source[grepl("hannity.com", purity_final_temp_kav$URL)] = "Sean Hannity"
+
+purity_icc_k <- lme(MFDweight ~ 1,
+                 data = purity_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 purity_model_kav = lme(MFDweight ~ lean,
@@
 summary(purity_model_kav)
+
+# check linearity
+random <- rchisq(nrow(purity_final_temp_kav), 7)
+residuals <- scale(residuals(purity_model_kav))
+fitted <- scale(fitted(purity_model_kav))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 harm_final_temp_gs$Source[grepl("hannity.com", harm_final_temp_gs$URL)] = "Sean Hannity"
+
+harm_icc_gs <- lme(MFDweight ~ 1,
+                 data = harm_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 harm_model_gs = lme(MFDweight ~ lean,
@@
 summary(harm_model_gs)
+
+# check linearity
+random <- rchisq(nrow(harm_final_temp_gs), 7)
+residuals <- scale(residuals(harm_model_gs))
+fitted <- scale(fitted(harm_model_gs))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 fair_final_temp_gs$Source[grepl("hannity.com", fair_final_temp_gs$URL)] = "Sean Hannity"
+
+fair_icc_gs <- lme(MFDweight ~ 1,
+                 data = fair_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 fair_model_gs = lme(MFDweight ~ lean,
@@
 summary(fair_model_gs)
+
+# check linearity
+random <- rchisq(nrow(fair_final_temp_gs), 7)
+residuals <- scale(residuals(fair_model_gs))
+fitted <- scale(fitted(fair_model_gs))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 ingroup_final_temp_gs$Source[grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Sean Hannity"
+
+ingroup_icc_gs <- lme(MFDweight ~ 1,
+                 data = ingroup_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 ingroup_model_gs = lme(MFDweight ~ lean,
@@
 summary(ingroup_model_gs)
+
+# check linearity
+random <- rchisq(nrow(ingroup_final_temp_gs), 7)
+residuals <- scale(residuals(ingroup_model_gs))
+fitted <- scale(fitted(ingroup_model_gs))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 authority_final_temp_gs$Source[grepl("hannity.com", authority_final_temp_gs$URL)] = "Sean Hannity"
+
+authority_icc_gs <- lme(MFDweight ~ 1,
+                 data = authority_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 authority_model_gs = lme(MFDweight ~ lean,
@@
 summary(authority_model_gs)
+
+# check linearity
+random <- rchisq(nrow(authority_final_temp_gs), 7)
+residuals <- scale(residuals(authority_model_gs))
+fitted <- scale(fitted(authority_model_gs))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
+
+purity_icc_gs <- lme(MFDweight ~ 1,
+                 data = purity_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 purity_model_gs = lme(MFDweight ~ lean,
@@
 summary(purity_model_gs)
+
+# check linearity
+random <- rchisq(nrow(purity_final_temp_gs), 7)
+residuals <- scale(residuals(purity_model_gs))
+fitted <- scale(fitted(purity_model_gs))
+hist(residuals)
+{qqnorm(residuals); abline(0,1)}
+{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
 ```
@@
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint_kav = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+tableprint_kav = matrix(NA, ncol = 9, nrow = 5)
+colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
 
@@
                     summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
-                    harm_d_kav$d)
+                    harm_d_kav$d, icc(harm_icc_k)$ICC_unadjusted)
 tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1,
                     summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
-                    fair_d_kav$d)
+                    fair_d_kav$d, icc(fair_icc_k)$ICC_unadjusted)
 tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1,
                     summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
-                    ingroup_d_kav$d)
+                    ingroup_d_kav$d, icc(ingroup_icc_k)$ICC_unadjusted)
 tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1,
                     summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
-                    authority_d_kav$d)
+                    authority_d_kav$d, icc(authority_icc_k)$ICC_unadjusted)
 tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1,
                     summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
-                    purity_d_kav$d)
+                    purity_d_kav$d, icc(purity_icc_k)$ICC_unadjusted)
 
@@
 tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
+tableprint_kav[ , 9] = printp(as.numeric(tableprint_kav[ , 9]))
 ```
@@
           caption = "Kavanaugh Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
           format = "latex",
@@
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint_gs = matrix(NA, ncol = 8, nrow = 5)
-colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d")
+tableprint_gs = matrix(NA, ncol = 9, nrow = 5)
+colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
 
@@
                     summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
-                    harm_d_gs$d)
+                    harm_d_gs$d, icc(harm_icc_gs)$ICC_unadjusted)
 tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1,
                     summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
-                    fair_d_gs$d)
+                    fair_d_gs$d, icc(fair_icc_gs)$ICC_unadjusted)
 tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1,
                     summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
-                    ingroup_d_gs$d)
+                    ingroup_d_gs$d, icc(ingroup_icc_gs)$ICC_unadjusted)
 tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1,
                     summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
-                    authority_d_gs$d)
+                    authority_d_gs$d, icc(authority_icc_gs)$ICC_unadjusted)
 tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1,
                     summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
-                    purity_d_gs$d)
+                    purity_d_gs$d, icc(purity_icc_gs)$ICC_unadjusted)
 
@@
 tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
+tableprint_gs[ , 9] = printp(as.numeric(tableprint_gs[ , 9]))
 ```
@@
           caption = "Government Shutdown Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
+          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
           format = "latex",

### 2023-07-21 manuscript_version/revision/review_response_erin.txt
here's the updates

@@
 RESPONSE: [Kayden; should we include the MTMM study?]
+Yes we are going to do that.
 
@@
 RESPONSE: [Erin]
+- look at original thesis for justification for valence
 - note if we add the MTMM, this response may be different, so waiting here.
 Also this person seems to think that valence ratings are not useful, so add some notes about how they are very predictive, yada yada.
+- add information from will's thesis back in there
 
@@
 RESPONSE: [Erin]
+- move readability stats to an appendix
 - undecided here maybe something like ...
@@
 Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.
+[KAYDEN you still decided to use that word LWIC information stuff here]
 

### 2023-07-21 manuscript_version/revision/manuscript_metapsych_revision.Rmd
here's the updates

@@
 
-```{r example-weight, results = 'asis', include = FALSE}
+```{r example-weight, results = 'asis', echo = FALSE}
 temp_table <- harm_final_data %>% 
@@
 apa_table(temp_table %>% select(-URL), 
-          note = "",
+          note = "Concepts were stemmed to match datasets.",
           caption = "Example of Weighted Coding for Harm Words",

### 2023-07-21 manuscript_version/revision/manuscript_metapsych_revision.tex
here's the updates

--- 2022-03-03 manuscript_version/manuscript_metapsych.tex
@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
-\title{Moral Foundations of U.S. Political News Organizations}
-\author{William E. Padfield\textsuperscript{1}, Erin M. Buchanan, Ph.D.\textsuperscript{2}, \& Kayla N. Jordan, Ph.D.\textsuperscript{2}}
-\date{}
-
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Moral Foundations of U.S. Political News Organizations},
-  pdfauthor={William E. Padfield1, Erin M. Buchanan, Ph.D.2, \& Kayla N. Jordan, Ph.D.2},
-  pdflang={en-EN},
-  pdfkeywords={politics, morality, psycholinguistics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 
-% \usepackage{etoolbox}
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+\makeatletter
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 \makeatother
-\shorttitle{MORAL NEWS}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{politics, morality, psycholinguistics}
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Moral Foundations of U.S. Political News Organizations},
+  pdfauthor={William E. Padfield1, Erin M. Buchanan, Ph.D.2, \& Kayden N. Jordan, Ph.D.2},
+  pdflang={en-EN},
+  pdfkeywords={politics, morality, psycholinguistics},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Moral Foundations of U.S. Political News Organizations}
+\author{William E. Padfield\textsuperscript{1}, Erin M. Buchanan, Ph.D.\textsuperscript{2}, \& Kayden N. Jordan, Ph.D.\textsuperscript{2}}
+\date{}
+
+\shorttitle{MORAL NEWS}
 
@@
 
-\abstract{
+\abstract{%
 Partisan differences and diviseness have become an increasing hot topic in psychological research.
@@
 
-Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.Conducting two close conceptual replication and six extension studies, Frimer (2020) found that the liberal-conservative differences found in the original study replicated in only 30\% of cases and the effect sizes were over 30 times smaller than reported in Graham et al.
+Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.
+Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S.
+Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, Frimer (2020) found that the liberal-conservative differences found in the original study replicated in only 30\% of cases and the effect sizes were over 30 times smaller than reported in Graham et al.
 (2009).
@@
 Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
+Additionally, Frimer (2020) tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores.
+Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects.
 Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
@@
 While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT (Clifford \& Jerit, 2013; Frimer, Tell, \& Haidt, 2015; Sagi \& Dehghani, 2014).
+Like Frimer (2020), we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.
 
@@
 These attempts generally fall into two categories: human annotations and semantic representations.
-Hopp, Fisher, Cornell, Huskey, and Weber (2021) represents the first approach where instead of relying on `experts,' a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
+Hopp, Fisher, Cornell, Huskey, and Weber (2021) represents the first approach where instead of relying on `experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
 While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
@@
 We first test differences in a general news corpus compared liberal sources (National Public Radio {[}NPR{]} and the New York Times {[}NYT{]}) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavaugh's U.S.
+Second, we examined news about specific political events: Brett Kavanaugh's U.S.
 Supreme Court nomination and the U.S.
 Government Shutdown in 2018-2019.
-In the second experiment, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
+In the second study, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
 To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
@@
 
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
+\hypertarget{study-1}{%
+\section{Study 1}\label{study-1}}
 
@@
 
-For Experiment 1, we approached the study with the intention to answer a method question.
+For the first study, we approached the study with the intention to answer a method question.
 That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
@@
 (2014)'s article presented political ideology as a scale ranging from ``consistently liberal'' to ``consistently conservative.'' In between these extremes lie more moderate positions, including ``mostly liberal,'' ``mixed,'' and ``mostly conservative.'' Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either ``liberal'' and ``conservative'' in order to form a basis for comparison.
+At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible.
 
@@
 
-The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence.
-Therefore, for each article, the percentage of the number of \emph{harm/care} words occurring in the articles were calculated, and this process was repeated for each of the foundations.
-Words' percent occurrence were multiplied by their \emph{z}-scored valence.
+A complete list of the words for each moral foundation area was created from previous experiments.
+The total number of times each of those words was used in an article was calculated.
+This information was merged with the valence values from the Warriner et al.
+(2013) dataset.
+A weighted score was calculated by multiplying the frequency of occurrence within a document times the \emph{z}-scored valence values and divided by the word count for that article.
+The final score was multiplied by 100 to represented a weighted percentage.
+Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article.
 Valences were \emph{z}-scored in order to eliminate any ambiguity regarding the direction of the valence.
@@
 Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
+See Table \ref{tab:example-weight} for an example.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:example-weight}Example of Weighted Coding for Harm Words}
+
+\footnotesize{
+
+\begin{tabular}{llcccc}
+\toprule
+Source & Concept & Frequency & Total Words & Valence & Weighted Score\\
+\midrule
+Breitbart & abus & 14.00 & 846 & -2.77 & -4.59\\
+Breitbart & cruel & 2.00 & 574 & -1.83 & -0.64\\
+NY Times & unit & 19.00 & 1341 & 0.18 & 0.25\\
+Breitbart & first & 18.00 & 1135 & 1.78 & 2.82\\
+Fox News & comfort & 12.00 & 1053 & 1.71 & 1.95\\
+NPR & attent & 6.00 & 1336 & 1.27 & 0.57\\
+Breitbart & bruis & 3.00 & 290 & -1.43 & -1.48\\
+Breitbart & accid & 3.00 & 196 & -1.97 & -3.02\\
+Breitbart & cut & 11.00 & 1036 & -0.91 & -0.97\\
+Breitbart & child & 8.00 & 622 & 1.68 & 2.16\\
+NPR & injuri & 4.00 & 968 & -2.15 & -0.89\\
+NY Times & drug & 32.00 & 1004 & -0.75 & -2.38\\
+Breitbart & beat & 5.00 & 298 & -0.54 & -0.90\\
+Fox News & weapon & 17.00 & 1175 & -0.87 & -1.26\\
+Breitbart & speci & 3.00 & 390 & 0.15 & 0.12\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} }
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 
-\caption{\label{tab:exp1-source-descriptives}Experiment 1 - Descriptive Statistics by Source}
+\caption{\label{tab:exp1-source-descriptives}Study 1 - Descriptive Statistics by Source}
 
@@
 NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.28 & 14.00 & 3.93\\
-New York Times & 0.30 & 0.13 & 406 & 452579 & 1114.73 & 511.86 & 454.27 & 154.58 & 16.42 & 3.36\\
+New York Times & 0.30 & 0.13 & 406 & 452579 & 1114.73 & 511.86 & 454.27 & 154.58 & 16.44 & 3.36\\
 Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.35 & 120.75 & 18.57 & 7.89\\
@@
 Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
+Therefore, the models were calculated by: Weighted Score \textasciitilde{} Political Lean + (\textasciitilde1\textbar Source).
 
@@
 
-\caption{\label{tab:exp1-table}Experiment 1 Results - Multilevel Model}
+\caption{\label{tab:exp1-table}Study 1 Results - Multilevel Model}
 
@@
 
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccccl}
 \toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
 \midrule
-Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .851 & 0.01\\
-Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .713 & 0.02\\
-Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .793 & -0.04\\
-Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.16 & .087 & -0.20\\
-Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.38 & .140 & -0.09\\
+Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .851 & 0.01 & .851\\
+Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .713 & 0.02 & .713\\
+Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .793 & -0.04 & .793\\
+Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.16 & .087 & -0.20 & .087\\
+Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.38 & .140 & -0.09 & .140\\
 \bottomrule
@@
 The selection of the broad and amorphous topic of ``political news'' may have led to the scraping of large numbers of articles with little to no moral-centric content.
-To address this limitation, two changes that were subsequently employed in Experiment 2.
-First, we elected to include more news sources for web scraping and analysis in addition to the four used in Experiment 1.
+To address this limitation, two changes that were subsequently employed in Study 2.
+First, we elected to include more news sources for web scraping and analysis in addition to the four used in Study 1.
 Second, we chose to focus data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
@@
 government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Experiment 2 is the best test of the MFT and the MFD in the context of partisan news.
+Hence, Study 2 is the best test of the MFT and the MFD in the context of partisan news.
 
-\hypertarget{experiment-2}{%
-\section{Experiment 2}\label{experiment-2}}
+\hypertarget{study-2}{%
+\section{Study 2}\label{study-2}}
 
@@
 
-In contrast to Experiment 1, we approached Experiment 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For Experiment 2, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
+In contrast to Study 1, we approached Study 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
+For the second study, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
 News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
@@
 news sources.
-As in Experiment 1, these sources were selected owing to their favorability among political partisans according to Mitchell et al.
+As in Study 1, these sources were selected owing to their favorability among political partisans according to Mitchell et al.
 (2014).
@@
 The sources favored by the highest proportion of consistent conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
+These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service.
 Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
@@
 
-As in Experiment 1, the text was scanned with \emph{ngram} (Schmidt et al., 2017).
+As in Study 1, the text was scanned with \emph{ngram} (Schmidt et al., 2017).
 Again, blank articles, text from the Disqus system, and duplicate articles were removed.
@@
 We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Experiment 1, statistics calculated include \emph{z}-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source (Kincaid et al., 1975).
+As in Study 1, statistics calculated include \emph{z}-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source (Kincaid et al., 1975).
 
@@
 The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.73 & 1.85\\
-Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.62 & 10.87 & 2.12\\
-Fox News & 0.29 & 0.11 & 646 & 1304048 & 2018.65 & 2709.77 & 534.47 & 404.21 & 9.71 & 1.86\\
+Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.59 & 11.01 & 2.32\\
+Fox News & 0.29 & 0.11 & 646 & 1304048 & 2018.65 & 2709.77 & 534.46 & 404.20 & 9.91 & 1.98\\
 Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.76 & 2.40\\
@@
 Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.71 & 2.05\\
-Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2763.29 & 3405.44 & 637.30 & 494.00 & 9.43 & 1.95\\
+Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2763.29 & 3405.44 & 637.28 & 493.98 & 9.61 & 2.11\\
 Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.36 & 4.81\\
@@
 
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccccl}
 \toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
 \midrule
-Harm/Care & 0.39 & 1.35 & 0.66 & 1.35 & 2.89 & .020 & -0.19\\
-Fairness/Reciprocity & 1.26 & 1.27 & 1.06 & 1.27 & -1.58 & .154 & 0.16\\
-Ingroup/Loyalty & 1.15 & 1.22 & 1.06 & 1.22 & -0.63 & .549 & 0.07\\
-Authority/Respect & 0.85 & 0.99 & 0.75 & 0.99 & -0.93 & .380 & 0.10\\
-Purity/Sanctity & 0.90 & 1.28 & 1.06 & 1.28 & 0.88 & .406 & -0.11\\
+Harm/Care & 0.39 & 1.35 & 0.66 & 1.35 & 2.89 & .020 & -0.19 & .012\\
+Fairness/Reciprocity & 1.26 & 1.27 & 1.06 & 1.27 & -1.58 & .154 & 0.16 & .043\\
+Ingroup/Loyalty & 1.15 & 1.22 & 1.06 & 1.22 & -0.63 & .549 & 0.07 & .031\\
+Authority/Respect & 0.85 & 0.99 & 0.75 & 0.99 & -0.93 & .380 & 0.10 & .021\\
+Purity/Sanctity & 0.90 & 1.28 & 1.06 & 1.28 & 0.88 & .406 & -0.11 & .031\\
 \bottomrule
@@
 The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Experiment 1 in which the largest effect size was observed for \emph{authority/respect}.
-As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized.
+This effect was similar to Study 1 in which the largest effect size was observed for \emph{authority/respect}.
+As noted before, the effect found in Study 1 was in the opposite direction as what was hypothesized.
 Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
+Owing to a lack of similar effects for either Study 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
 
 Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Experiment 1.
-As in Experiment 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
+A similar pattern was observed for the results in Study 1.
+As in Study 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
 
@@
 
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccccl}
 \toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$\\
+Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
 \midrule
-Harm/Care & 0.91 & 1.27 & 1.01 & 1.27 & 1.68 & .132 & -0.07\\
-Fairness/Reciprocity & 1.22 & 1.05 & 0.91 & 1.05 & -0.76 & .467 & 0.27\\
-Ingroup/Loyalty & 1.38 & 1.16 & 1.11 & 1.16 & -0.48 & .643 & 0.21\\
-Authority/Respect & 0.87 & 1.24 & 0.36 & 1.24 & -1.38 & .204 & 0.37\\
-Purity/Sanctity & 1.29 & 1.13 & 0.99 & 1.13 & 0.03 & .979 & 0.22\\
+Harm/Care & 0.91 & 1.27 & 1.01 & 1.27 & 1.68 & .132 & -0.07 & .003\\
+Fairness/Reciprocity & 1.22 & 1.05 & 0.91 & 1.05 & -0.76 & .467 & 0.27 & .044\\
+Ingroup/Loyalty & 1.38 & 1.16 & 1.11 & 1.16 & -0.48 & .643 & 0.21 & .020\\
+Authority/Respect & 0.87 & 1.24 & 0.36 & 1.24 & -1.38 & .204 & 0.37 & .062\\
+Purity/Sanctity & 1.29 & 1.13 & 0.99 & 1.13 & 0.03 & .979 & 0.22 & .043\\
 \bottomrule
@@
 
-The results obtained in Experiment 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
+The results obtained in Study 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
 The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given Graham et al.
@@
 
-Together with Experiment 1 and past work, Experiment 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
-One issue that Experiment 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in Sterling and Jost (2018).
+Together with Study 1 and past work, Study 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
+One issue that Study 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in Sterling and Jost (2018).
 For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
@@
 Within the theoretical framework of MFT (Haidt \& Graham, 2007), we attempted to devise a method leveraging the MFD (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
-In Experiment 1,the results obtained were not significant in any statistical or practical sense.
+In Study 1,the results obtained were not significant in any statistical or practical sense.
 There was a small effect found for the \emph{authority/respect} foundation according to Cohen's \emph{d}, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-In Experiment 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
+In Study 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
 Building on Frimer (2020) and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Aust2017}{}}%
-Aust, F., \& Barth, M. (2017). {papaja: Create APA manuscripts with R Markdown.} Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2017). \emph{{papaja: Create APA manuscripts with R Markdown.}} Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Feinerer2017}{}}%
-Feinerer, I., \& Hornik, K. (2017). {Text mining package}. Retrieved from \url{http://tm.r-forge.r-project.org/}
+Feinerer, I., \& Hornik, K. (2017). \emph{{Text mining package}}. Retrieved from \url{http://tm.r-forge.r-project.org/}
 
@@
 Morality between the lines: Detecting moral sentiment in text.
-In \emph{{Proceedings of IJCAI 2016 workshop on Computational Modeling of Attitudes}}.
+\emph{{Proceedings of IJCAI 2016 workshop on Computational Modeling of Attitudes}}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-harrison_rselenium_2020}{}}%
-Harrison, J., \& Kim, J. Y. (2020). {RSelenium}: {R} {Bindings} for '{Selenium} {WebDriver}'. Retrieved from \url{https://CRAN.R-project.org/package=RSelenium}
+Harrison, J., \& Kim, J. Y. (2020). \emph{{RSelenium}: {R} {Bindings} for '{Selenium} {WebDriver}'}. Retrieved from \url{https://CRAN.R-project.org/package=RSelenium}
 
@@
 (1975).
-Derivation of new readability formulas (automated readability index, fog count and {F}lesch reading ease formula) for {N}avy enlisted personnel.
+\emph{Derivation of new readability formulas (automated readability index, fog count and {F}lesch reading ease formula) for {N}avy enlisted personnel}.
 \url{https://doi.org/10.21236/ADA006655}
@@
 (2014).
-{Political polarization {\&} media habits \textbar{} Pew Research Center}.
+\emph{{Political polarization {\&} media habits \textbar{} Pew Research Center}}.
 Retrieved from \url{http://www.journalism.org/2014/10/21/political-polarization-media-habits/}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Pennebaker2007}{}}%
-Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). {Liwc2007: Linguistic inquiry and word count}. Austin, TX.
+Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). \emph{{Liwc2007: Linguistic inquiry and word count}}. Austin, TX.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pinheiro2017}{}}%
-Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). {nlme: Linear and nonlinear mixed effects models}. Retrieved from \url{https://cran.r-project.org/package=nlme}
+Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). \emph{{nlme: Linear and nonlinear mixed effects models}}. Retrieved from \url{https://cran.r-project.org/package=nlme}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
-Wickham, H. (2016). {Package `rvest'}. Retrieved from \url{https://cran.r-project.org/package=rvest}
+Wickham, H. (2016). \emph{{Package `rvest'}}. Retrieved from \url{https://cran.r-project.org/package=rvest}
 

### 2023-08-16 manuscript_version/revision/MFD MTMM Markdown old.Rmd
old_mtmm_files
all the data and old code for MTMM

---
title             : "A Validation of the Moral Foundations Questionnaire and Dictionary" 
shorttitle        : "VALIDITY OF MFD"

author: 
  - name          : "Kayla N. Jordan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Erin M. Buchanan"
    affiliation   : "2"
  - name          : "William E. Padfield"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Texas - Austin"
  - id            : "2"
    institution   : "Missouri State University"

author_note: |
  Kayla N. Jordan is a Ph.D. candidate at the University of Texas at Austin. Erin M. Buchanan is an Associate Professor of Quantitative Psychology at Missouri State University. William E. Padfield is a masters degree candidate at Missouri State University.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"

bibliography      : ["mtmm_bib.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
knitr::opts_chunk$set(cache = TRUE)

library(papaja)
library(tm)
library(corpus)
library(lavaan)
library(ngram)

##percent missing function
percentmiss = function(x){ sum(is.na(x))/length(x) *100 }
```

Examining the construct and measurement validity of psychometric scales can be difficult, especially for complex constructs such as morality. Given the pervasiveness of language as avenue of moral justification and moral argument, it is important to understand how language is indicative of moral reasoning. Hence, the current study sought to examine the validity of one approach to measuring moral language using the framework of moral foundations theory, in comparison to traditional questionnaire style measurements.

## Moral Foundations Theory

Moral Foundations Theory (MFT) was proposed by @Haidt2004 to explain the differences between political liberals' and conservatives' moral thinking processes. The differences in party processing were explained by variable focus on five moral foundations. The first two of these foundations represents concerns for individuals. The *harm/care* foundation encompasses concerns of promoting compassion and/or denigrating cruelty. The *fairness/reciprocity* foundation covers concerns of ensuring equality and justice. The next three foundations represent concerns for the group. The *ingroup/loyalty* foundation encompasses concerns encouraging patriotism and discouraging dissent. The *authority/respect* foundation represents concerns maintaining tradition and respecting social hierarchies. The *purity/sanctity* foundation encompasses concerns engaging in virtues such as chastity and self-control and abstaining from vices such as lust and gluttony. Throughout this manuscript, we will use *harm*, *fairness*, *ingroup*, *authority*, and *purity* to indicate the foundations and their direction. For example, higher endorsement of the *authority* foundation implies a focus on basing moral judgments on respecting tradition and hierarchy, while lower levels of endorsement imply basing moral judgments less on respecting tradition and hierarchy and more on other concerns.

The endorsement along these moral foundation continuums is related to political orientation. Namely, those of liberal political orientation base moral judgments on the *harm* and *fairness* foundations whereas those of conservative orientation based judgments on all five foundations [@Federico2013; @Graham2009; @Graham2012; @Weber2013]. Furthermore, @Graham2012 found the differences between the two sides of the political spectrum were exaggerated by the opposing party. For example, liberals rated conservatives as more conservative than conservatives rated themselves and vice versa. In addition to political orientation, moral foundations also predicted specific policy preferences and attitudes. @Kertzer2014 found that higher endorsement of the *ingroup*, *authority*, and *purity* foundations predicted support for the Iraq War and a preemptive strike against Iran. However, higher endorsement of *harm* and *fairness* foundations predicted support for the Kyoto protocols. @Koleva2012 examined the relationship between moral foundation endorsement and a wide range of policy attitudes. Greater endorsement of the *harm* foundation predicted opposition to animal testing, the death penalty, and torture, as well as support for gun control. Endorsement of the *ingroup* foundation predicted greater disapproval of flag burning and terrorism, as well as greater support for defense spending. Finally, stronger endorsement of *purity* predicted opposition to abortion, same sex marriage, teaching of evolution, and illegal immigration.

## Moral Foundations Questionnaire

The Moral Foundations Questionnaire (MFQ) was developed in order to measure the extent to which an individual endorses each moral foundation [@Graham2011]. The MFQ is a 30-item scale divided into two subscales: moral relevance and moral judgments. The 15 moral relevance items are equally divided among the five foundations and examine how relevant a condition is to making a moral judgment on a scale of 1 (*not at all relevant*) to 6 (*extremely relevant*). These relevance items include examples such as: "Whether or not someone used violence (*harm*)," "Whether or not someone was denied his or her rights (*fairness*)," "Whether or not someone showed a lack of loyalty (*ingroup*)," "Whether or not an action caused chaos or disorder (*authority*)," and "Whether or not someone did something disgusting (*purity*)." The moral judgments items are also equally divided between the foundations and ask on a six-point scale how much one agrees with each of the statements. These judgment items include: "One of the worst things a person can do is hurt a defenseless animal (*harm*)," "Justice is the most important requirement of a society (*fairness*)," "I am proud of my country's history (*ingroup*)," "Men and women each have different roles to play in society (*authority*)," and "Chastity is an important and valuable virtue (*purity*)."

The internal consistency of this version from @Graham2011 was $\alpha$ = .73 averaged across subscales with a range of $\alpha$ = .65-.84. Across six studies, the MFQ was found to have an average Cronbach's alpha of .63 for *harm*, .64 for *fairness*, .56 for *ingroup*, .59 for *authority*, and .71 for *purity* [@Federico2013; @Graham2009; @Graham2012; @Weber2013]. Test-retest reliability was *r* = .68-.82 using a sample of 123 college students. Confirmatory factor analysis supported a well-fitted five-factor model (*harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity*) over two, individual (*harm* and *fairness*) versus group (*ingroup*, *authority*, and *purity*) foundations, or three, autonomy (*harm*, *fairness*), community (*ingroup*, *authority*), and divinity (*purity*) ethics, foundations factor model. The five-factor structure also fit for non-Western samples, thus, providing evidence of the MFQ generalizability. Convergent validity was supported with correlations on other measures of morality [@Schwartz; @Graham2011].

## Moral Foundations Dictionary

Given the importance of language to political ideology and moral thinking, @Graham2009 developed a moral foundations dictionary (MFD) to examine the use of moral justification in speech and/or writing. A dictionary of roughly 50-60 words was developed for each foundation. Words such as *war* and *peace* should indicate a greater concern with *harm* foundation whereas words such as *homeland* and *terrorism* should indicate a greater concern with the *ingroup* foundation. The other foundation dictionaries include *equal* and *justice* (*fairness*), *honor* and *protest* (*authority*), and *holy* and *sin* (*purity*). To validate the word sets, @Graham2009 examined the frequency of MFD words in liberal and conservative sermons. They found liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers who used *authority* and *purity* words more often. Although conservative ministers were expected to use more *ingroup* words based on political ideology and previous research, an examination of the way liberal ministers used *ingroup* words revealed a tendency for the use of *ingroup* words to glorify rebellion and promote independence (i.e., the opposite direction from *ingroup* definitions). Effect sizes indicated relatively sizable difference between liberal and conservative sermons with Cohen's *d* ranging from 0.56 to 1.27.

@Graham2009's validation focused on the frequency of moral words as a dependent variable for the MFD. In contrast to this approach, @Sagi2013 explored how moral words were used paired with other co-occurring concepts using Latent Semantic Analysis (LSA). They examined three different moral issues in different contexts to piece out specific moral words and their collocates. First, they looked at how moral words were used in relation to the World Trade Center compared to the Empire State Building in the New York Times from 1987-2007. After 9-11, the number of moral words associated with the World Trade Center increased, specifically *harm* words from the MFD. Second, they considered the changes in how moral words were paired with mosque used in blogs as a response to the debate of building a mosque near Ground Zero following 9-11. They found words from the MFD were used more often with mosque during the main debate and then the co-occurrence decreased afterwards. Lastly, they examined moral language tied to the abortion debate in Congress. Republicans used more moral language overall; more specifically, Republicans tended to use more words associated with the *purity* foundation; while Democrats used more words associated with the *fairness* foundation.  
These studies are the first steps at supporting the moral foundations dictionary and questionnaire using the moral foundations framework. This study combined both the dictionary and questionnaire to expand the literature on their usefulness and psychometric properties due to the dearth of studies on both measures. Therefore, the purpose of the current study was to explore the reliability and validity of the MFD and MFQ using the following procedures:

****1) Cronbach's $\alpha$ of both measurement tools, as previous studies have shown mixed reliabilities 2) a multi-method, multi-trait (MTMM) design comparing the MFD and MFQ on one sample, and 3) the predictive validity of the MFD and MFQ to political orientation using Congressional speech records. ****

going to end up editing here after we finish the four pronged approach part.

# Experiment 1

# Method

##Particpants

```{r demos_study1, include = FALSE}
exp1data = read.csv("fixed_association.csv")

##clear out completely columns we don't need
crapcolumns = c(1, 2, 3, 5:14)
finalsample = exp1data[ , -crapcolumns]

##accuracy
summary(finalsample) #Check Q15_1 and Q23 for in-range scores -WP
finalsample$Q23 = factor(finalsample$Q23,
                         levels = 1:3,
                         labels = c("Democrat", "Republican", "Independent"))

#missing 
#by people 
missing_demo1 = apply(finalsample, 1, percentmiss) 
table(missing_demo1)

replacepeople1 = subset(finalsample, missing_demo1 <= 5)  #we are using 5%, yes? 
#by column 
apply(replacepeople1, 2, percentmiss) 
#missing data is on the politics scale which we don't want to replace

finalsample = replacepeople1
summary(finalsample)

party = table(finalsample$Q23)
##be sure to exclude the writing columns columns 2:6 
#I take it I should also remove column 1: ResponseId? 
##outliers
mahal1 = mahalanobis(finalsample[ , -c(1:6,22,23)], 
                    colMeans(finalsample[ , -c(1:6,22,23)], na.rm = TRUE),
                    cov(finalsample[ , -c(1:6,22,23)], use="pairwise.complete.obs"))
#mahal1
cutoff1 = qchisq(1 - .001,ncol(finalsample[ , -c(1:6,22,23)]))
cutoff1
ncol(finalsample[ , -c(1:6,22,23)])
summary(mahal1 < cutoff1) #Hmm what to do w/ NAs?? -WP
noout1 = subset(finalsample, mahal1 < cutoff1)

##assumptions
#correlations for MFQ
correlations1 = cor(noout1[,-c(1:6,22,23)], use="pairwise.complete.obs")
correlations1
symnum(correlations1)

#making the random stuff
random1 = rchisq(nrow(noout1), 7)
fake1 = lm(random1~., data=noout1[ , -c(1:6)])
#normal
standardized1 = rstudent(fake1)
hist(standardized1, breaks=15)

#linear
{qqnorm(standardized1) 
abline(0,1)}
#homog + s
fitvalues1 = scale(fake1$fitted.values)
{plot(fitvalues1, standardized1) 
abline(0,0)
abline(v = 0)}

####create the MFQ subscales####
noout1$harmMFQ = apply(noout1[ , 7:9], 1, sum)
noout1$fairMFQ = apply(noout1[ , 10:12], 1, sum)
noout1$ingroupMFQ = apply(noout1[ , 13:15], 1, sum)
noout1$authorityMFQ = apply(noout1[ , 16:18], 1, sum)
noout1$purityMFQ = apply(noout1[ , 19:21], 1, sum)
```

`r nrow(exp1data)` participants were collected from a large Midwestern university. Participants were given course credit for their introductory psychology course for completing the study. `r nrow(finalsample)` participants had less than five percent missing data and were retained for analyses. Participants were asked to denote their political party, and `r printnum(party["Democrat"]/sum(party)*100,digits = 1)`% indicated they were Democrats, `r printnum(party["Republican"]/sum(party)*100,digits = 1)`% were Republican, and `r printnum(party["Independent"]/sum(party)*100,digits = 1)`% indicated they were Independent.

# Materials and Procedure

A complete example of the survey can be found online at OSF LINK. First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech. Next, the free association task, similar to that used in @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind". The participants were then given three example free association cues, *lost*, *old*, and *article*. For each cue, participants were asked to write all the words that come to mind. To elicit free association to the moral foundation areas, participants were given the following instructions:

"Moral Foundations Theory states that when making moral judgments/decisions, the concerns people have can be divided into five categories. Below are labels of each of these five categories. You will then be asked to list words you think are associated with each of the labels."

Each of the foundation pairs were listed together (i.e., *harm/care*, *fairness/cheating*) with a space for participants to list their free association concepts. After the free association task, participants were then given the 15-items from the moral relevance section of the MFQ as described in the introduction. Last, participants were asked to denote their political orientation from 1 *conservative* to 10 *liberal*, as well as which political party they associated with: Democrat, Republican, and Independent. The survey was delivered through Qualtrics, and participants were recruited through the online participant management system for the university (SONA). Each participant signed an online consent form at the beginning of the study and was given participation credit at the end of the study.

# Results

All data was screening for inaccurate responses, as well as missing data, as described in the participant section. Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise. The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r cutoff1`. These participants were excluded from further analyses, representing `r nrow(noout1)` final participants. The final data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.

The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation. The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`). Participants free association responses were processed using the *tm* library [@CITE] after spell checking. Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*. We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary. Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manuall recode all word forms. Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses. The complete set of word frequencies for each foundation can be found in our supplemental materials.

```{r harm-analysis1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q27 = as.character(noout1$Q27)

##stem the data

for (i in 1:nrow(noout1)) {
  noout1$Q27[i] = paste(unlist(
    text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
}

##create a corpus
harm_corpus = Corpus(VectorSource(noout1$Q27))
harm_TDM = as.matrix(TermDocumentMatrix(harm_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
harm_freq = data.frame(Word = rownames(harm_TDM),
                       Freq = rowSums(harm_TDM),
                       row.names = NULL)
harm_freq$Word = as.character(harm_freq$Word)
harm_freq$percent = harm_freq$Freq/nrow(noout1) *100

write.csv(harm_freq, "exp1_harm_freq.csv", row.names = F)

##subset out to only words with 1% mentions
harm_words = harm_freq$Word[harm_freq$percent >=1]
##turn sideways to add to dataset
harm_TDM = as.data.frame(t(harm_TDM))
harm_TDM = harm_TDM[ , harm_words]

##final dataset for harm
harm_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
                   harm_TDM)

harm_cor = apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})

harmcut = mean(harm_cor) + 2*sd(harm_cor)
harm_words_reduce = names(harm_cor[abs(harm_cor) >= harmcut])
```

```{r fair-analysis1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q29 = as.character(noout1$Q29)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q29[i] = paste(unlist(
    text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
}

##create a corpus
fair_corpus = Corpus(VectorSource(noout1$Q29))
fair_TDM = as.matrix(TermDocumentMatrix(fair_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
fair_freq = data.frame(Word = rownames(fair_TDM),
                       Freq = rowSums(fair_TDM),
                       row.names = NULL)
fair_freq$Word = as.character(fair_freq$Word)
fair_freq$percent = fair_freq$Freq/nrow(noout1) *100

write.csv(fair_freq, "exp1_fair_freq.csv", row.names = F)

##subset out to only words with 1% mentions
fair_words = fair_freq$Word[fair_freq$percent >=1]
##turn sideways to add to dataset
fair_TDM = as.data.frame(t(fair_TDM))
fair_TDM = fair_TDM[ , fair_words]

##final dataset for fair
fair_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
                   fair_TDM)

fair_cor = apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})

faircut = mean(fair_cor) + 2*sd(fair_cor)
fair_words_reduce = names(fair_cor[abs(fair_cor) >= faircut])
```

```{r ingroup-analysis1, include=FALSE}
#q27 through 34 are the writing columns
noout1$Q30 = as.character(noout1$Q30)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q30[i] = paste(unlist(
    text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
}

##create a corpus
ingroup_corpus = Corpus(VectorSource(noout1$Q30))
ingroup_TDM = as.matrix(TermDocumentMatrix(ingroup_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
ingroup_freq = data.frame(Word = rownames(ingroup_TDM),
                       Freq = rowSums(ingroup_TDM),
                       row.names = NULL)
ingroup_freq$Word = as.character(ingroup_freq$Word)
ingroup_freq$percent = ingroup_freq$Freq/nrow(noout1) *100

write.csv(ingroup_freq, "exp1_ingroup_freq.csv", row.names = F)

##subset out to only words with 1% mentions
ingroup_words = ingroup_freq$Word[ingroup_freq$percent >=1]
##turn sideways to add to dataset
ingroup_TDM = as.data.frame(t(ingroup_TDM))
ingroup_TDM = ingroup_TDM[ , ingroup_words]

##final dataset for ingroup
ingroup_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
                   ingroup_TDM)

ingroup_cor = apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})

ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
ingroup_words_reduce = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
```

```{r authority-analysis1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q32 = as.character(noout1$Q32)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q32[i] = paste(unlist(
    text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
}

##create a corpus
authority_corpus = Corpus(VectorSource(noout1$Q32))
authority_TDM = as.matrix(TermDocumentMatrix(authority_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
authority_freq = data.frame(Word = rownames(authority_TDM),
                       Freq = rowSums(authority_TDM),
                       row.names = NULL)
authority_freq$Word = as.character(authority_freq$Word)
authority_freq$percent = authority_freq$Freq/nrow(noout1) *100

write.csv(authority_freq, "exp1_authority_freq.csv", row.names = F)

##subset out to only words with 1% mentions
authority_words = authority_freq$Word[authority_freq$percent >=1]
##turn sideways to add to dataset
authority_TDM = as.data.frame(t(authority_TDM))
authority_TDM = authority_TDM[ , authority_words]

##final dataset for authority
authority_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
                   authority_TDM)

authority_cor = apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})

authoritycut = mean(authority_cor) + 2*sd(authority_cor)
authority_words_reduce = names(authority_cor[abs(authority_cor) >= authoritycut])
```

```{r purity-analysis1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q34 = as.character(noout1$Q34)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q34[i] = paste(unlist(
    text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
}

##create a corpus
purity_corpus = Corpus(VectorSource(noout1$Q34))
purity_TDM = as.matrix(TermDocumentMatrix(purity_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
purity_freq = data.frame(Word = rownames(purity_TDM),
                       Freq = rowSums(purity_TDM),
                       row.names = NULL)
purity_freq$Word = as.character(purity_freq$Word)
purity_freq$percent = purity_freq$Freq/nrow(noout1) *100

write.csv(purity_freq, "exp1_purity_freq.csv", row.names = F)

##subset out to only words with 1% mentions
purity_words = purity_freq$Word[purity_freq$percent >=1]
##turn sideways to add to dataset
purity_TDM = as.data.frame(t(purity_TDM))
purity_TDM = purity_TDM[ , purity_words]

##final dataset for purity
purity_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
                   purity_TDM)

purity_cor = apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})

puritycut = mean(purity_cor) + 2*sd(purity_cor)
purity_words_reduce = names(purity_cor[abs(purity_cor) >= puritycut])
```

This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`. These concepts were included in the full dictionary used for Experiment 3. We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores. Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts. Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation. The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`, ingroup `r length(ingroup_words_reduce)`, authority `r length(authority_words_reduce)`, and purity `r length(purity_words_reduce)`.

# Experiment 2

# Method

## Participants

```{r demos_study2, include=FALSE, warning=FALSE}
sample1 = read.csv("fixed_sample 1.csv", stringsAsFactors = F)
sample2 = read.csv("fixed_sample 2.csv", stringsAsFactors = F)

##merge files together
fullsample = merge(sample1, sample2, all = TRUE)

##merge together the writing samples
#q24, q25, q26, q7 
fullsample$writing = apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
                           1, function(x) toString(na.omit(x)))

##clear out completely columns we don't need
crapcolumns = c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
finalsample = fullsample[ , -crapcolumns]

##accuracy
summary(finalsample[ , 2:40])

finalsample$Q10 = factor(finalsample$Q10,
                         levels = 1:2,
                         labels = c("Man", "Woman"))
finalsample$Q11 = as.numeric(finalsample$Q11)
finalsample$Q12 = factor(finalsample$Q12,
                         levels = 1:7,
                         labels = c("White", "Black", 
                                    "Hispanic", "Asian",
                                    "Native American", 
                                    "Mixed", "Other"))

gender = table(finalsample$Q10)/sum(table(finalsample$Q10))*100
race = table(finalsample$Q12)/sum(table(finalsample$Q12))*100

write.csv(finalsample, 'exp2_finalsample.csv', row.names = FALSE)
newMFD = read.csv('exp2_finalsample_newMFD.csv')
colnames(newMFD)[1:41] = colnames(finalsample)[1:41]
newMFD = newMFD[,c(1,42:55)]
finalsample = merge(finalsample, newMFD, by="ResponseId")

##take out the people with less than 25 words
##use the ngram library to examine the data
##preprocess only works on one string at a time, so going to use a loop go through all the rows (apply won't work because we only want to work on one column)

for (i in 1:nrow(finalsample)) {

  finalsample$writing[i] = preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
  finalsample$wordcount[i] = string.summary(finalsample$writing[i])$words

}

#remove small words people
finalwords = subset(finalsample, wordcount >=25)

##check out missing data
#missing by row
missing = apply(finalwords, 1, percentmiss)
table(missing)
goodrows = subset(finalwords, missing <= 5)

#missing by column
apply(goodrows, 2, percentmiss)

##don't fill in Q10 to the end, be sure to merge these back together
goodcolumns = goodrows[ , -c(32:42)]
badcolumns = goodrows[ , c(32:42)]

#fill in missing data points
library(mice)
tempnomiss = mice(goodcolumns)
nomiss = complete(tempnomiss, 1)
summary(nomiss)
#merge
allcolumns = cbind(nomiss, badcolumns) 
summary(allcolumns)

##outliers
mahal2 = mahalanobis(allcolumns[ , -c(1,46:56)], 
                    colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
                    cov(allcolumns[ , -c(1,46:56)], use="pairwise.complete.obs"))
#mahal2
cutoff2 = qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
cutoff2
ncol(allcolumns[ , -c(1,46:56)])
summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
noout2 = subset(allcolumns, mahal2 < cutoff2)

##assumptions on the questions i.e., not Q10 to the end
#correlations
correlations2 = cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
#correlations2
symnum(correlations2)

#the random stuff
random2 = rchisq(nrow(noout2), 7)
fake2 = lm(random2~., data=noout2[ , -c(1,46:56)])

#normal
standardized2 = rstudent(fake2)
hist(standardized2, breaks=15)

#linear
{qqnorm(standardized2)   
abline(0,1)}

#homog + s
fitvalues2 = scale(fake2$fitted.values)
{plot(fitvalues2, standardized2) 
abline(0,0)
abline(v = 0)}

####create the MFQ subscales####
noout2$harmMFQ = apply(noout2[ , 2:4], 1, sum)
noout2$fairMFQ = apply(noout2[ , 5:7], 1, sum)
noout2$ingroupMFQ = apply(noout2[ , 8:10], 1, sum)
noout2$authorityMFQ = apply(noout2[ , 11:13], 1, sum)
noout2$purityMFQ = apply(noout2[ , 14:16], 1, sum)
```

Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes [@Jordan]. Participants were recruited via an online research system (SONA) and were given course credit for their participation. `r nrow(finalsample)` participants were included in the this study. The study was mostly women (`r printnum(gender["Woman"], digits = 1)`%) and White (`r printnum(race["White"], digits = 1)`%) participants with a mix of minority participants: Black (`r printnum(race["Black"], digits = 1)`%), (`r printnum(race["Hispanic"], digits = 1)`%), (`r printnum(race["Asian"], digits = 1)`%), Native American (`r printnum(race["Native American"], digits = 1)`%), Mixed (`r printnum(race["Mixed"], digits = 1)`%) and Other (`r printnum(race["Other"], digits = 1)`%). The average listed age was `r printnum(mean(finalsample$Q11, na.rm = T))` (*SD* = `r printnum(sd(finalsample$Q11, na.rm = T))`).

##	Materials and Procedure

Data was again collected via Qualtrics. Four fake new stories were presented to participants, which were roughly 400 words each. First, all news stories included a few sentences describing the use of chemical weapons in the Syrian civil war. The news stories were manipulated with political (Republican v. Democrat) and religious (religious v. not) quotes in a 2 x 2 design. News stories can be found in the online materials. Participants also completed the 30-item version of the MFQ as described in the introduction. In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.

After consenting to participate in the study, participants were randomly shown one of the four new articles about Syria's use of chemical weapons. Participants were then asked to write for 5-10 minutes about their reaction to Syria's use of chemical weapons and the needed response from the United States. The second wave of data collection included different writing prompts designed to capture more of the moral foundation areas in their writing. The following writing prompt was used, "Please write about your attitudes on abortion (or same-sex marriage or environmentalism) as well as your reason for this stance." The three prompts were chosen to create a more varied word set by using topics that should elicit words from each moral foundations category by soliciting a moral response. In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants. Participants then completed the MFQ, demographics, and the political orientation scale.

# Results

Participant data was first spell checked and screening for inaccurate responses. Participants who did not write more than fifty words in response to a given prompt were excluded (*n* = `r nrow(finalsample) - nrow(finalwords)`). One missing datapoint was estimated using the *mice* library from *R* [@CITE] for a missing MFQ question, and all other missing data was present in the demographics sections, which were not filled in. The MFQ data were screened for outliers using Mahalanobis distance, and fourteen outliers were found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) = `r printnum(cutoff2)`. These data were excluded leading to a final sample size of `r nrow(noout2)`. Data were screened for assumptions described in Experiment 1 and were found to be satisfactory.

```{r writing_analysis2, include=FALSE}
##stem the data
for (i in 1:nrow(noout2)) {
  noout2$writing2[i] = paste(unlist(
    text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
}

##create a corpus
overall_corpus = Corpus(VectorSource(noout2$writing2))
overall_TDM = as.matrix(TermDocumentMatrix(overall_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
overall_freq = data.frame(Word = rownames(overall_TDM),
                          Freq = rowSums(overall_TDM),
                          row.names = NULL)
overall_freq$Word = as.character(overall_freq$Word)
overall_freq$percent = overall_freq$Freq/nrow(noout2)*100

write.csv(overall_freq, "exp2_freq.csv", row.names = F)

##subset out to only words with 1% mentions
##this goes over 100% but mostly want to subset out things that were only mentioned
##a few times by participants
all_words = overall_freq$Word[overall_freq$percent >=1]

##turn sideways to add to dataset
overall_TDM = as.data.frame(t(overall_TDM))
overall_TDM = overall_TDM[ , all_words]

##final dataset
overall_final = cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
                                  "authorityMFQ", "purityMFQ","ingroupMFQ")],
                   overall_TDM)
```

```{r exp2-mfq-cor, include = FALSE}
##harm
harm_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})

harmcut = mean(harm_cor) + 2*sd(harm_cor)
harm_words_reduce_exp2 = names(harm_cor[abs(harm_cor) >= harmcut])

##fair
fair_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})

faircut = mean(fair_cor) + 2*sd(fair_cor)
fair_words_reduce_exp2 = names(fair_cor[abs(fair_cor) >= faircut])

##purity
purity_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})

puritycut = mean(purity_cor) + 2*sd(purity_cor)
purity_words_reduce_exp2 = names(purity_cor[abs(purity_cor) >= puritycut])

##authority
authority_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})

authoritycut = mean(authority_cor) + 2*sd(authority_cor)
authority_words_reduce_exp2 = names(authority_cor[abs(authority_cor) >= authoritycut])

##ingroup
ingroup_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})

ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
ingroup_words_reduce_exp2 = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])

##print out words list to look at for further analysis
#write.csv(harm_words_reduce_exp2, "words/harm_exp2.csv", row.names = F)
#write.csv(fair_words_reduce_exp2, "words/fair_exp2.csv", row.names = F)
#write.csv(authority_words_reduce_exp2, "words/authority_exp2.csv", row.names = F)
#write.csv(purity_words_reduce_exp2, "words/purity_exp2.csv", row.names = F)
#write.csv(ingroup_words_reduce_exp2, "words/ingroup_exp2.csv", row.names = F)
```

In the first study, only free association responses were collected, but in this study, full writing samples were collected. Therefore, we expected many of the words listed to be part of creating a cohesive discourse, rather than only related to the moral foundation targeted. To find only the most related words, the correlation between word frequency and moral foundation was calculated and words with correlations greater than two standard deviations outside the mean were selected for the dictionary analysis in Experiment 3.  The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation. The average scores were: harm (*M* = `r printnum(mean(noout2$harmMFQ))`, *SD* = `r printnum(sd(noout2$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout2$fairMFQ))`, *SD* = `r printnum(sd(noout2$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout2$ingroupMFQ))`, *SD* = `r printnum(sd(noout2$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout2$authorityMFQ))`, *SD* = `r printnum(sd(noout2$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout2$purityMFQ))`, *SD* = `r printnum(sd(noout2$purityMFQ))`).

```{r compare-ratings, include = FALSE}
authority_erin = read.csv("words/authority_exp2 erin.csv", stringsAsFactors = F)
authority_will = read.csv("words/authority_exp2 will.csv", stringsAsFactors = F)
authority_erin$x[authority_erin$use != authority_will$use]

authority_words_reduce_exp2 = authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]

fair_erin = read.csv("words/fair_exp2 erin.csv", stringsAsFactors = F)
fair_will = read.csv("words/fair_exp2 will.csv", stringsAsFactors = F)
fair_erin$x[fair_erin$use != fair_will$use]
fair_will$use[fair_will$x == "carbon"] = 0
fair_will$use[fair_will$x == "emiss"] = 0
#exclude carbon and emiss due to the prompt

fair_words_reduce_exp2 = fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]

purity_erin = read.csv("words/purity_exp2 erin.csv", stringsAsFactors = F)
purity_will = read.csv("words/purity_exp2 will.csv", stringsAsFactors = F)
purity_erin$x[purity_erin$use != purity_will$use]
purity_will$use[purity_will$x == "befor"] = 1
#before include because of "before sex/ruined/etc."

purity_words_reduce_exp2 = purity_words_reduce_exp2[purity_words_reduce_exp2 %in% purity_will$x[purity_will$use == 1]]

ingroup_erin = read.csv("words/ingroup_exp2 erin.csv", stringsAsFactors = F)
ingroup_will = read.csv("words/ingroup_exp2 will.csv", stringsAsFactors = F)
ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
ingroup_will$use[ingroup_will$x == "mean"] = 1
#mean should be included

ingroup_words_reduce_exp2 = ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]

harm_erin = read.csv("words/harm_exp2 erin.csv", stringsAsFactors = F)
harm_will = read.csv("words/harm_exp2 will.csv", stringsAsFactors = F)
harm_erin$x[harm_erin$use != harm_will$use]
harm_will$use[harm_will$x == "import"] = 1
#import for important

harm_words_reduce_exp2 = harm_words_reduce_exp2[harm_words_reduce_exp2 %in% harm_will$x[harm_will$use == 1]]
```

This set of words was then coded by two of the authors for relevant words with discussion over coding constituting a tiebreaker. For example, for harm words in this study both *also* and *Syria* appeared as correlated words to the harm foundation. The first word does not meet face validity of correlation with the dictionary, and these type of function words or ambiguous verbs (i.e., *get*, *can*) were usually excluded. The second example is likely because of the writing prompt, and therefore, proper nouns were also excluded. The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce_exp2)`, fairness `r length(fair_words_reduce_exp2)`, ingroup `r length(ingroup_words_reduce_exp2)`, authority `r length(authority_words_reduce_exp2)`, and purity `r length(purity_words_reduce_exp2)`.

# Experiment 3

```{r mtmm-setup, include = FALSE}
##original mfd words
original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)

##adding forms/conjugations of words to original_mfd
#harm/care
original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
                             "sympathetic","sympathies","damaged",
                             "damaging","attacked","attacking","attacker",
                             "attacks","attackers", "benefits", "benefitted",
                             "benefitting", "cares", "cared", "caring", "crushes",
                             "crushing", "crushed", "dangerous", "defends", "defending",
                             "defended", "detroys", "destroyed", "destroying",
                             "fights", "fought", "fighting", "guards", "guarded",
                             "guarding", "harms", "harmed", "harming", "hurts",
                             "hurting", "kills", "killed", "killing", "preserves",
                             "preserved", "preserving", "protects", "protected",
                             "protecting", "protection", "ruins", "ruined", "ruining",
                             "safely", "safer", "shelters", "sheltered", "sheltering",
                             "spurns", "spurned", "spurning", "stomps", "stomped",
                             "stomping", "suffers", "suffered", "suffering",
                             "violence", "warring")

#fairness/reciprocity
original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
                             "biases", "discriminates", "discriminated",
                             "discriminating", "discrimination", "equals",
                             "equaled", "equaling", "equates", "equated",
                             "equating", "evens", "evened", "evening",
                             "excludes", "excluded", "excluding", "fairness",
                             "favors", "favored", "favoring", "honesty",
                             "impariality", "justice", "justifies", "justified",
                             "justifying", "prefers", "preferred", "preferring",
                             "prejudices", "prejudiced", "prejudicing", "reasons",
                             "reasoned", "reasoning", "rights", "tolerates",
                             "tolerated", "tolerating", "toleration")

#ingroup/loyalty
original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
                             "communities", "deceives", "deceived", "deceiving",
                             "deception", "deceptions", "deserts", "deserted",
                             "deserting", "desertion", "families", "fellows",
                             "foreigners", "groups", "grouped", "grouping",
                             "indviduals", "indvidualize", "individualized",
                             "individualizing", "members", "nations", "sides",
                             "togetherness", "traits", "unites", "united", "uniting")

#authority/respect
original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
                              "classes", "classed", "classing", "command",
                              "commanded", "commanding", "controls", "controlled",
                              "controlling", "defects", "defected", "defecting",
                              "defers", "deferred", "deferring", "deference",
                              "defies", "defied", "defying", "defiance", "deserts",
                              "deserted", "deserting", "desertion", "duties",
                              "faiths", "fathers", "fathered", "fathering",
                              "honors", "honored", "honoring", "laws", "leads",
                              "leading", "mothers", "mothered", "mothering",
                              "obeys", "obeyed", "obeying", "opposes", "opposed",
                              "opposing", "orders", "ordered", "ordering", "permits",
                              "permitted", "permitting", "positions", "positioned",
                              "positioning", "preserves", "preserved", "preserving",
                              "preservation", "protests", "protested", "protesting",
                              "refuses", "refused", "refusing", "refusal", "respects",
                              "respected", "respecting", "respectful", "reveres",
                              "revered", "revering", "reverence", "serves", "served",
                              "serving", "traditions", "traditional", "traits")

#purity/sanctity
original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
                             "adulteries", "adulterous", "adulterer", "adulterers",
                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
                             "cleanliness", "dirty", "diseases", "diseased", 
                             "disgusts", "disgusted", "disgusting", "grossness",
                             "innocence", "modesty", "preserves", "preserved",
                             "preserving", "preservation", "promiscuity",
                             "promiscuities", "purity", "rights", "ruins", "ruined",
                             "ruining", "sacredness", "sickness", "sicknesses",
                             "sins", "wholeness", "wholesome")

##stem the original mfd
for(i in 1:nrow(original_mfd)) {
  original_mfd$h2[i] = stemDocument(original_mfd$h2[i], language = "english")
  original_mfd$f2[i] = stemDocument(original_mfd$f2[i], language = "english")
  original_mfd$i2[i] = stemDocument(original_mfd$i2[i], language = "english")
  original_mfd$a2[i] = stemDocument(original_mfd$a2[i], language = "english")
  original_mfd$p2[i] = stemDocument(original_mfd$p2[i], language = "english")
}

mtmmdata = noout2[ , c(1:31, 42) ]

####figure out the percents for the exp2 data
for (i in 1:nrow(mtmmdata)) {

  ##figure out the sum for just the original mfd
  mtmmdata$harm_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])

  mtmmdata$purity_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])

  mtmmdata$fair_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])

  mtmmdata$authority_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])

  mtmmdata$ingroup_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])

  ##figure out the sum for all words ever 
  mtmmdata$harm_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])

  mtmmdata$purity_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])

  mtmmdata$fair_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])

  mtmmdata$authority_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])

  mtmmdata$ingroup_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])

  ##figure out the sum for reduced words
  mtmmdata$harm_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])

  mtmmdata$purity_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])

  mtmmdata$fair_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])

  mtmmdata$authority_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])

  mtmmdata$ingroup_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])

}

#create percents instead of frequencies
mtmmdata[ , c(33:47)] = mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100

summary(mtmmdata[ , 33:47])

```

Here I will write about the overall percents and all that jazz for these results. 
Work on the MTMM part

####edit below here however you want

```{r mtmm_orig, include = FALSE}
###Run chunk 8: demos_study2 to update data
###Use noout2 df as dataframe for mtmm
###Columns labeled Harm1/Fairness1/Loyalty1/Authority1/Purity1 are original MFD
###Columns labeled Harm2/Fairness2/Loyalty2/Authority2/Purity2 are revised MFD

##now run some MTMM!
library(semPlot)
library(lavaan)

####mtmm original dictionary####

{model1 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
'}

model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
summary(model1.fit, rsquare=TRUE, standardized=TRUE)
semPaths(model1.fit, whatLabels = "std", layout = "tree")
fitMeasures(model1.fit, fit.measures = "aic")

{model1.2 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig

fair_orig ~~ 1167.145*fair_orig

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
'}

model1.2.fit = cfa(model1.2, data=mtmmdata, std.lv=TRUE)
summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
semPaths(model1.2.fit, whatLabels = "std", layout = "tree")
fitMeasures(model1.2.fit, fit.measures = "aic")

{model2 ='
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig

fair_orig ~~ 1167.145*fair_orig
'}

model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
summary(model2.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model2.fit, fit.measures = "aic")

{model3 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
harmL~~1*fairL
harmL~~1*ingroupL
harmL~~1*authorityL
harmL~~1*purityL
fairL~~1*ingroupL
fairL~~1*authorityL
fairL~~1*purityL
ingroupL~~1*authorityL
ingroupL~~1*purityL
authorityL~~1*purityL

fair_orig ~~ 1167.145*fair_orig
'}

model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
summary(model3.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model3.fit, fit.measures = "aic")

{model4 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
mfq ~~ 0*mfd

fair_orig ~~ 1167.145*fair_orig
'}

model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
summary(model4.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model4.fit, fit.measures = "aic")
```

```{r mtmm_reduce, include = FALSE}

{model1 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
'}

model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
summary(model1.fit, rsquare=TRUE, standardized=TRUE)
semPaths(model1.fit, whatLabels = "std", layout = "tree")
fitMeasures(model1.fit, fit.measures = "aic")

{model2 ='
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
'}

model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
summary(model2.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model2.fit, fit.measures = "aic")

{model3 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
harmL~~1*fairL
harmL~~1*ingroupL
harmL~~1*authorityL
harmL~~1*purityL
fairL~~1*ingroupL
fairL~~1*authorityL
fairL~~1*purityL
ingroupL~~1*authorityL
ingroupL~~1*purityL
authorityL~~1*purityL
'}

model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
summary(model3.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model3.fit, fit.measures = "aic")

{model4 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
mfq ~~ 0*mfd
'}

model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
summary(model4.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model4.fit, fit.measures = "aic")
```

```{r mtmm_all, include = FALSE}

{model1 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_all
fairL =~ Q8_4+Q8_5+Q8_6+fair_all
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
'}

model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
summary(model1.fit, rsquare=TRUE, standardized=TRUE)
semPaths(model1.fit, whatLabels = "std", layout = "tree")
fitMeasures(model1.fit, fit.measures = "aic")

{model2 ='
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
'}

model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
summary(model2.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model2.fit, fit.measures = "aic")

{model3 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_all
fairL =~ Q8_4+Q8_5+Q8_6+fair_all
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
harmL~~1*fairL
harmL~~1*ingroupL
harmL~~1*authorityL
harmL~~1*purityL
fairL~~1*ingroupL
fairL~~1*authorityL
fairL~~1*purityL
ingroupL~~1*authorityL
ingroupL~~1*purityL
authorityL~~1*purityL
'}

model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
summary(model3.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model3.fit, fit.measures = "aic")

{model4 = '
harmL =~ Q8_1+Q8_2+Q8_3+harm_all
fairL =~ Q8_4+Q8_5+Q8_6+fair_all
ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all

##fix the covariances
harmL~~0*mfq
fairL~~0*mfq
ingroupL~~0*mfq
authorityL~~0*mfq
purityL~~0*mfq
harmL~~0*mfd
fairL~~0*mfd
ingroupL~~0*mfd
authorityL~~0*mfd
purityL~~0*mfd
mfq ~~ 0*mfd
'}

model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
summary(model4.fit, rsquare=TRUE, standardized=TRUE)
fitMeasures(model4.fit, fit.measures = "aic")
```

# Experiment 4

```{r read_doc_create_per, include = F, eval = F}
#load the library
library(textreadr)
library(readxl)

#read the list of files in each working folder
folder = here::here()
files2read = c(
  list.files(paste0(folder, "/War Congress Data/House - Conflict"), full.names = T),
  list.files(paste0(folder, "/War Congress Data/House - Kosovo"), full.names = T),
  list.files(paste0(folder, "/War Congress Data/House Hearings - Foreign Affairs"), full.names = T),
  list.files(paste0(folder, "/War Congress Data/Post War Iraq"), full.names = T),
  list.files(paste0(folder, "/War Congress Data/Prez - Conflict"), full.names = T),
  list.files(paste0(folder, "/War Congress Data/Senate - Conflict"), full.names = T),
  list.files(paste0(folder, "/War Congress Data/Senate - Foreign Affairs"), full.names = T)
  )

#create blank list
listofiles = list()

#read them all in
for (i in 1:length(files2read)) {
  listofiles[i] = paste(read_docx(files2read[i]), collapse = " ")
  names(listofiles)[i] = basename(files2read[i])
}

#create a final dataframe of the title + text
docDF = as.data.frame(do.call(rbind, listofiles))
docDF$filename = rownames(docDF)

#merge with other data information
congress_information = read_excel(paste0(folder, 
                                         "/War Congress Data/", 
                                         "List of files.xlsx"))
colnames(congress_information)[1] = "filename"

final_exp4 = merge(congress_information, 
                   docDF,
                   by = "filename",
                   all = T)

#originally wrote this out and imported but it's slow AF
#so save it at the end without all the extra text stuff
##write.csv(final_exp4, "final_exp4.csv", row.names = F)
##final_exp4 = read.csv("final_exp4.csv", stringsAsFactors = F)

##stem the data
for (i in 1:nrow(final_exp4)) {
  final_exp4$writing2[i] = paste(unlist(
    text_tokens(final_exp4$V1[i], stemmer = "en")), collapse = " ")
  final_exp4$wordcount[i] = string.summary(final_exp4$V1[i])$words
}

##create a corpus
overall_corpus = Corpus(VectorSource(final_exp4$writing2))
overall_TDM = as.matrix(TermDocumentMatrix(overall_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))
#convert
overall_exp4 = as.data.frame(t(overall_TDM))
rm(overall_TDM);rm(overall_corpus)

##create sum totals
for (i in 1:nrow(final_exp4)) {

  ##figure out the sum for just the original mfd
  final_exp4$harm_orig[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])

  final_exp4$purity_orig[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])

  final_exp4$fair_orig[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])

  final_exp4$authority_orig[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])

  final_exp4$ingroup_orig[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])

  ##figure out the sum for all words ever 
  final_exp4$harm_all[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])

  final_exp4$purity_all[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])

  final_exp4$fair_all[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])

  final_exp4$authority_all[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])

  final_exp4$ingroup_all[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])

  ##figure out the sum for reduced words
  final_exp4$harm_reduce[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])

  final_exp4$purity_reduce[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])

  final_exp4$fair_reduce[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])

  final_exp4$authority_reduce[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])

  final_exp4$ingroup_reduce[i] = sum(overall_exp4[ i , colnames(overall_exp4) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])

}

#create percents instead of frequencies
final_exp4[ , c(19:33)] = final_exp4[ , c(19:33)] / final_exp4$wordcount * 100

write.csv(final_exp4, "final_exp4.csv", row.names = F)
```

```{r analysis_exp4, include = F}
final_exp4 = read.csv("final_exp4.csv", stringsAsFactors = F)
final_exp4$Party = as.factor(final_exp4$Party)
final_exp4$Venue = as.factor(final_exp4$Venue)
final_exp4$Region = as.factor(final_exp4$Region)

library(ggplot2)
library(reshape)
melted = melt(final_exp4[ , c(13, 19:33)],
              id = "Party")
melted = subset(melted, Party != "I")
melted$Party = droplevels(melted$Party)
melted = na.omit(melted)

cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 15))

ggplot(melted, aes(variable, value, fill = Party)) + 
  stat_summary(fun.y = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2) +
  cleanup + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  NULL

#non-zero
melted2 = subset(melted, value > 0)
ggplot(melted2, aes(variable, value, fill = Party)) + 
  stat_summary(fun.y = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2) +
  cleanup + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  NULL
```

number of zeros in datasets are they different

  Data Cleaning and Descriptives. In sample 1, participants who wrote less than 50 words were deleted (*n* = 69) leaving *n* = 221 participants. The average political orientation was 4.80 (*SD* = 2.21) on a scale of 1 (*conservative*) to 10 (*liberal*). In sample 2, all 160 participants wrote at least 50 words. The mean political orientation was 5.01 (*SD* = 2.33) for sample 2. The data from sample 1 and sample 2 were combined. Before any analyses were conducted, participants who did not use any words from the MFD were deleted; 16 participants were deleted from sample 1 and 25 from sample 2. The final sample size for analysis was *N* = 340 which had a mean political orientation of 4.90 (*SD* = 2.28). MFD scores were computed using NVivo *(CITE)* as both frequency for each foundation and percent coverage for each foundation. Frequency was simply the count of the number of words used from a given foundation dictionary; for example, a participant using the word *war* once and the word *peace* twice would have a frequency score of 3 for the *harm* dictionary. Percent coverage was calculated by taking the frequency and dividing by the word count; for example, given a frequency score of 3 for the *harm* dictionary and a word count of 100, then the percent coverage would be .03 for the *harm* dictionary. MFQ scores for each foundation were calculated by averaging the six items pertaining to each foundation. 
	Reliability. Here we should talk about the reliability of the MFQ for each piece, as well as the reliability of the words for the MFD. I think to do that you might need a thing that has each word as frequency count yes/no or however the LIWC version thing was done. 
	MTMM. BASIC SEM STUFF HERE (also that you used bayes)
Data screening was conducted using SPSS version 22 and AMOS version 22. Participants who were missing data for the MFD, MFQ, or political orientation were deleted from all analyses. Given the distribution of the dictionary variables, participants whose writing sample were less than 2% words from the MFD were deleted resulting in a sample size of 252. Additionally, 7 outliers were deleted.
Widaman's (1985; as cited in @Byrne2009) four-step nested method was used to test the convergent and divergent validity of the MFD and MFQ. The first step is the baseline model (Model 1), which establishes correlation among traits (*harm*, *purity*, *fairness*, *authority*, and *ingroup*) as well as correlation among methods (MFD and MFQ) but no cross correlation of traits and methods. The individual questions from the 30 item version of the MFQ and the total frequency of concepts from each foundation in the MFD were used as measured variables. 
The fit of this first model indicated some misfit, as fit indices were a mix of poor and acceptable, $\chi$ 2 (514) = 977.46, $\chi$ 2/df = 1.90, CFI = .842, RMSEA = .061 [95% CI = .055-.067], SRMR = .0623. In this model, the MFD *harm*, *fairness*, and *ingroup* items significantly loaded onto their trait factors, while *authority* and *purity* did not. All foundations but *authority* loaded significantly on the method traits. All but two of the *ingroup* questions and one *authority* question loaded onto the MFQ trait factors. Several questions of the MFQ did not load significantly onto the methods factors; however, this result was taken as an indicator that traits variance was higher than methods variance. Generally, trait loadings were higher than method loadings for both the MFD and MFQ for *harm* and *fairness* traits. However, the *purity*, *ingroup*, and *authority* foundations did not show this loading pattern. 
ERIN STOPPED HERE CUZ HEADACHE. 
The second step (Model 2) involved eliminating the latent traits from the model. This model was significantly worse than Model 1 indicating the traits are important to the model ($\delta$ $\chi$ 2 = 1141.09, $\delta$ df = 45, $\delta$ CFI = .351). This supports convergent validity for the traits measured by both methods which in this case are the five moral foundations. The third step (Model 3) involved forcing the five traits to be perfectly correlated. This model was significantly worse than Model 1 indicating the usefulness of five unique traits ($\delta$ $\chi$ 2 = 311.09, $\delta$ df = 10, $\delta$ CFI = .097). This supports discriminant validity for the existence of five unique moral foundations. The final step (Model 4) involved allowing the correlations between the traits to be freely estimated and forcing the methods to be uncorrelated. This model was similar to Model 1 indicating the methods both measure the traits but they are both unique methods ($\delta$ $\chi$ 2 = 2.23, $\delta$ df = 1, $\delta$ CFI = .001). This supports discriminant validity for the methods. This set of analyses suggests the MFD is a possibly valid measure of moral foundations but does not measure them well enough to be useful in all applications and may be measuring them differently than the MFQ. 
	Regression predicting Political Orientation. The MFQ has predicted political orientation across many studies [@Federico2013; @Graham2009; @Haidt2009; @Weber2013]. Therefore, in addition to the MTMM analysis, we compared how well the MFD score predicted political orientation compared to how well the MFQ predicted the political orientation. First, total MFQ scores were calculated for each foundation by averaging all six items. Then, a regression analysis was conducted with the five MFQ foundation score predicting political orientation. The overall model was significant, *R2* = .35, *F* (5, 255) = 26.91, *p* < .05. Higher scores on the harm and fairness foundations predicted a more liberal political orientation with harm accounting for 3% of the variance and fairness accounting for 6%. Higher scores on ingroup, authority, and purity predicted a more conservative orientation accounting for 1%, 2%, and 8% on the variance respectively. See *table ?* for regression coefficients. Next, a regression analysis was conducted to determine how well the five MFD scores predicted political orientation. The overall model was not significant, *R2* = .16, *F* (5, 255) = 1.36, *p* = .241. Higher harm scores somewhat predicted more liberal orientation accounting for 1% of the variance in political orientation. Higher purity scores somewhat predicted more conservative orientation accounting for 1% of the variance. See *table ?* for regression coefficients.

## Study 2
  In Study 2, the MFD was applied to real-world data, U.S. Congressional speeches. The purpose of this study was to further test the predictive validity of the MFD. If valid, the MFD should detect political party differences in congressional speeches.

## Method
# Sample
  Speeches were gathered through the Congressional Record available through the U.S. Government Publishing Office. Speeches were gathered from the following venues from 1998-2013: Senate, House of Representatives, Senate Foreign Affairs Committee, and House Foreign Affairs Committee. The topics of the speeches were U.S. foreign policy with the following nations: Iraq, Iran, North Korea, Afghanistan, Kosovo, Libya, Russia, Sudan, and Syria. These speeches often deal with the use of military force and the enforcement of sanctions which should include moral arguments. A total of 5207 Congressional speeches were gathered. These speeches were made by 509 unique speakers. Republicans gave 2268 speeches, and Democrats gave 2939 speeches. 
# Data Processing
  For each speech, the number of words used from each of the five foundation dictionary was calculated. So, each speech had a word frequency count for each foundation. Speeches which did not contain any words from any foundation dictionary were excluded. Across speeches, there were a total of 2,026,243 words. Of these, 7838 (.39%) were *harm* words, 1976 (.10%) were *fairness* words, 2985 (.15%) were *ingroup* words, 4057 (.20%) were *authority* words, and 717 (.04%) were *purity* words.

## Results

democrats should be harm/care, fairness/reciprocity in contrast to the other foundations and more than republicans

republicans should be equal across the foundations, purity/sanctity, authority/respect, ingroup/loyalty more than democrats

potentially think about valence

  Bayesian *t*-tests were used to compare the Democratic and Republican use of MFD words. For *harm* words, the Bayes factor comparing a model of equal use between Democrats and Republicans and a model of greater use by Democrats was .08. In other words, equal use of *harm* words by both parties is more likely. Examining the means revealed that Democrats (*M* = 5.62, *SD* = 8.12), on average, used less than one more *harm* word than Republicans (*M* = 4.87, *SD* = 6.32). For *fairness* words, the Bayes factor was .04; once again, equal use of *fairness* words by both parties is more likely. Essentially no difference exists between the mean use for Democrats (*M* = 2.46, *SD* = 2.74) and Republicans (*M* = 2.66, *SD* = 3.34). For *ingroup*, *authority*, and *purity* words, a model of equal use was tested against a model of greater use by Republicans. A Bayes factor of .10 supported greater probability for the equal use of *ingroup* words with little difference between Republicans (*M* = 2.55, *SD* = 2.83) and Democrats (*M* = 2.48, *SD* = 2.10). A Bayes factor of .04 also supported greater likelihood of the equal use of *authority* words with no substantial difference between Republicans (*M* = 3.06, *SD* = 3.43) and Democrats (*M* = 3.22, *SD* = 3.19). Likewise, a Bayes factor of .09 demonstrated a greater probability for the equal use of *purity* words with little to no difference between Republicans (*M* = 1.52, *SD* = 1.03) and Democrats (*M* = 1.54, *SD* = 1.04). See *figure ?* for all comparisons.

##  Discussion
	The preceding analyses seem to suggest the MFD has limited validity. While the step procedure of the MTMM supports the assumptions that the MFD is measuring the same constructs as the MFQ, the models themselves suggest the MFD measures moral foundations rather poorly. Furthermore, the MFD fails to have the predictive validity found in the MFQ predicting political orientation. Based on the initial work of [@Graham2009], it is possible that the MFD is measuring the moral foundation constructs differently than the MFQ as they did find ingroup words to predict liberal orientation rather than conservative. The problems with the MFD may be due to the use of word frequency. As we found in the current study, the words of the MFD are not used very often which forced us to delete many participants and also left many participants who used only 2 or 3 words from the dictionary. The infrequent use of the MFD words may have caused some mismeasurement of the foundations. The LSA approach taken by @Sagi2013 may be a solution to this problem and may represent a better application of the dictionary. A limitation of the current study was word count for the texts, which could have exacerbated the word frequency problem. The average word count in our study was around 100-200 words; increasing the word count may yield better results in future studies. However, overall it seems that the word frequency method of the MFD is a poor measure of moral foundations theory. Further research is required to either improve the MFD or determine what exactly it is measuring.

### 2023-08-16 manuscript_version/revision/manuscript_metapsych_revision.Rmd
added_study3
basic outline of study 3 for erin to add math

@@
 
+# Study 3
+
+As a final test of the MFD, we had participants write about explicitly moral topics which was then analyzed with the MFD which supplemented using participant score's on the Moral Foundation Questionnaire.
+These changes create the best case scenario for finding the theorized differences
+
+# Participants
+
+Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes (???).
+Participants were recruited via an online research system (SONA) and were given course credit for their participation.
+463 participants were
+included in the this study.
+The study was mostly women (53.9%) and White (76.4%) participants with a mix of minority participants: Black (6.1%), (3.6%), (4.2%), Native American (1.9%), Mixed (2.9%) and Other (4.9%).
+The average listed age was 19.75 (SD =
+200 2.94).
+
+# Materials and Procedure
+
+Data was again collected via Qualtrics. Four fake new stories were presented to participants, which were roughly 400 words each. First, all news stories included a few
+sentences describing the use of chemical weapons in the Syrian civil war.
+The news stories were manipulated with political (Republican v.
+Democrat) and religious (religious v.
+not) quotes in a 2 x 2 design.
+News stories can be found in the online materials.
+Participants also completed the 30-item version of the MFQ as described in the introduction.
+In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.
+
+After consenting to participate in the study, participants were randomly shown one of
+the four new articles about Syria’s use of chemical weapons. Participants were then asked to
+write for 5-10 minutes about their reaction to Syria’s use of chemical weapons and the
+needed response from the United States. The second wave of data collection included
+different writing prompts designed to capture more of the moral foundation areas in their writing. The following writing prompt was used, “Please write about your attitudes on
+abortion (or same-sex marriage or environmentalism) as well as your reason for this stance.”
+The three prompts were chosen to create a more varied word set by using topics that should
+elicit words from each moral foundations category by soliciting a moral response.
+In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants.
+Participants then completed the MFQ, demographics, and the political
+orientation scale.
+
+# Results
+
+# Expanding the MFD
+
+In a separate study of 466 university students, participants completed a free association task where we asked them to list all the words that came to mind from *harm/care*, *fairness/cheating*, *loyalty/XX*, *authority/XX*, *purity/XX*.
+They also completed the 15 item MFQ.
+Responses to the free association task were cleaned and stemmed.
+This lead to a new set of moral foundation words: harm-96, fairness-76, ingroup-86, authority-81, and purity-80.
+These concepts were included in the full dictionary used for Experiment 3.
+
+We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
+Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts.
+Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation.
+The reduced dataset included the following number of words for each foundation: harm 4, fairness 3, ingroup 3, authority 4, and purity 2.
+
+```{r word-association}
+#need the code for the the above stuff
+```
+
+[ERIN, Please do mathy-math here]
+
+# Testing Model Structure
+
+Before testing the theorized differences between liberals and conservatives, we sought to test the validity of the MFD using Multi-Trait, Multi-Method modelling (MTMM) to determine if the MFD is measuring the same latent variables as the MFQ as it should.
+
+```{r mtmm}
+
+```
+
+# Testing Group Differences
+
+```{r mtmm-groupdiffs}
+
+```
+
 # Discussion

### 2023-08-31 manuscript_version/revision/manuscript_metapsych_revision.Rmd
moving the things around

@@
 
+## Study 3.1
+
+this part is the association study information
+
+```{r demos-mtmm-study-3.1, include = FALSE}
+exp1data = read.csv("fixed_association.csv")
+
+##clear out completely columns we don't need
+crapcolumns = c(1, 2, 3, 5:14)
+finalsample = exp1data[ , -crapcolumns]
+
+##accuracy
+summary(finalsample) #Check Q15_1 and Q23 for in-range scores -WP
+finalsample$Q23 = factor(finalsample$Q23,
+                         levels = 1:3,
+                         labels = c("Democrat", "Republican", "Independent"))
+
+#missing 
+#by people 
+missing_demo1 = apply(finalsample, 1, percentmiss) 
+table(missing_demo1)
+
+replacepeople1 = subset(finalsample, missing_demo1 <= 5)  #we are using 5%, yes? 
+#by column 
+apply(replacepeople1, 2, percentmiss) 
+#missing data is on the politics scale which we don't want to replace
+
+finalsample = replacepeople1
+summary(finalsample)
+
+party = table(finalsample$Q23)
+##be sure to exclude the writing columns columns 2:6 
+#I take it I should also remove column 1: ResponseId? 
+##outliers
+mahal1 = mahalanobis(finalsample[ , -c(1:6,22,23)], 
+                    colMeans(finalsample[ , -c(1:6,22,23)], na.rm = TRUE),
+                    cov(finalsample[ , -c(1:6,22,23)], use="pairwise.complete.obs"))
+#mahal1
+cutoff1 = qchisq(1 - .001,ncol(finalsample[ , -c(1:6,22,23)]))
+cutoff1
+ncol(finalsample[ , -c(1:6,22,23)])
+summary(mahal1 < cutoff1) #Hmm what to do w/ NAs?? -WP
+noout1 = subset(finalsample, mahal1 < cutoff1)
+
+##assumptions
+#correlations for MFQ
+correlations1 = cor(noout1[,-c(1:6,22,23)], use="pairwise.complete.obs")
+correlations1
+symnum(correlations1)
+
+#making the random stuff
+random1 = rchisq(nrow(noout1), 7)
+fake1 = lm(random1~., data=noout1[ , -c(1:6)])
+#normal
+standardized1 = rstudent(fake1)
+hist(standardized1, breaks=15)
+
+#linear
+{qqnorm(standardized1) 
+abline(0,1)}
+#homog + s
+fitvalues1 = scale(fake1$fitted.values)
+{plot(fitvalues1, standardized1) 
+abline(0,0)
+abline(v = 0)}
+
+####create the MFQ subscales####
+noout1$harmMFQ = apply(noout1[ , 7:9], 1, sum)
+noout1$fairMFQ = apply(noout1[ , 10:12], 1, sum)
+noout1$ingroupMFQ = apply(noout1[ , 13:15], 1, sum)
+noout1$authorityMFQ = apply(noout1[ , 16:18], 1, sum)
+noout1$purityMFQ = apply(noout1[ , 19:21], 1, sum)
+```
+
+`r nrow(exp1data)` participants were collected from a large Midwestern university.
+Participants were given course credit for their introductory psychology course for completing the study.
+`r nrow(finalsample)` participants had less than five percent missing data and were retained for analyses.
+Participants were asked to denote their political party, and `r printnum(party["Democrat"]/sum(party)*100,digits = 1)`% indicated they were Democrats, `r printnum(party["Republican"]/sum(party)*100,digits = 1)`% were Republican, and `r printnum(party["Independent"]/sum(party)*100,digits = 1)`% indicated they were Independent.
+
+### Materials and Procedure
+
+A complete example of the survey can be found online at OSF LINK.
+First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech.
+Next, the free association task, similar to that used in @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind".
+The participants were then given three example free association cues, *lost*, *old*, and *article*.
+For each cue, participants were asked to write all the words that come to mind.
+To elicit free association to the moral foundation areas, participants were given the following instructions:
+
+"Moral Foundations Theory states that when making moral judgments/decisions, the concerns people have can be divided into five categories.
+Below are labels of each of these five categories.
+You will then be asked to list words you think are associated with each of the labels."
+
+Each of the foundation pairs were listed together (i.e., *harm/care*, *fairness/cheating*) with a space for participants to list their free association concepts.
+After the free association task, participants were then given the 15-items from the moral relevance section of the MFQ as described in the introduction.
+Last, participants were asked to denote their political orientation from 1 *conservative* to 10 *liberal*, as well as which political party they associated with: Democrat, Republican, and Independent.
+The survey was delivered through Qualtrics, and participants were recruited through the online participant management system for the university (SONA).
+Each participant signed an online consent form at the beginning of the study and was given participation credit at the end of the study.
+
+### Results
+
+All data was screening for inaccurate responses, as well as missing data, as described in the participant section.
+Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise.
+The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r cutoff1`.
+These participants were excluded from further analyses, representing `r nrow(noout1)` final participants.
+The final data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.
+
+The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
+The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`).
+Participants free association responses were processed using the *tm* library [@CITE] after spell checking.
+Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*.
+We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary.
+Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manuall recode all word forms.
+Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses.
+The complete set of word frequencies for each foundation can be found in our supplemental materials.
+
+```{r harm-analysis-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1$Q27 = as.character(noout1$Q27)
+
+##stem the data
+
+for (i in 1:nrow(noout1)) {
+  noout1$Q27[i] = paste(unlist(
+    text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+harm_corpus = Corpus(VectorSource(noout1$Q27))
+harm_TDM = as.matrix(TermDocumentMatrix(harm_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+harm_freq = data.frame(Word = rownames(harm_TDM),
+                       Freq = rowSums(harm_TDM),
+                       row.names = NULL)
+harm_freq$Word = as.character(harm_freq$Word)
+harm_freq$percent = harm_freq$Freq/nrow(noout1) *100
+
+write.csv(harm_freq, "exp1_harm_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+harm_words = harm_freq$Word[harm_freq$percent >=1]
+##turn sideways to add to dataset
+harm_TDM = as.data.frame(t(harm_TDM))
+harm_TDM = harm_TDM[ , harm_words]
+
+##final dataset for harm
+harm_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
+                   harm_TDM)
+
+harm_cor = apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})
+
+harmcut = mean(harm_cor) + 2*sd(harm_cor)
+harm_words_reduce = names(harm_cor[abs(harm_cor) >= harmcut])
+```
+
+```{r fair-analysi-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1$Q29 = as.character(noout1$Q29)
+
+##stem the data
+for (i in 1:nrow(noout1)) {
+  noout1$Q29[i] = paste(unlist(
+    text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+fair_corpus = Corpus(VectorSource(noout1$Q29))
+fair_TDM = as.matrix(TermDocumentMatrix(fair_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+fair_freq = data.frame(Word = rownames(fair_TDM),
+                       Freq = rowSums(fair_TDM),
+                       row.names = NULL)
+fair_freq$Word = as.character(fair_freq$Word)
+fair_freq$percent = fair_freq$Freq/nrow(noout1) *100
+
+write.csv(fair_freq, "exp1_fair_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+fair_words = fair_freq$Word[fair_freq$percent >=1]
+##turn sideways to add to dataset
+fair_TDM = as.data.frame(t(fair_TDM))
+fair_TDM = fair_TDM[ , fair_words]
+
+##final dataset for fair
+fair_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
+                   fair_TDM)
+
+fair_cor = apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})
+
+faircut = mean(fair_cor) + 2*sd(fair_cor)
+fair_words_reduce = names(fair_cor[abs(fair_cor) >= faircut])
+```
+
+```{r ingroup-analysis-3.1, include=FALSE}
+#q27 through 34 are the writing columns
+noout1$Q30 = as.character(noout1$Q30)
+
+##stem the data
+for (i in 1:nrow(noout1)) {
+  noout1$Q30[i] = paste(unlist(
+    text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+ingroup_corpus = Corpus(VectorSource(noout1$Q30))
+ingroup_TDM = as.matrix(TermDocumentMatrix(ingroup_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+ingroup_freq = data.frame(Word = rownames(ingroup_TDM),
+                       Freq = rowSums(ingroup_TDM),
+                       row.names = NULL)
+ingroup_freq$Word = as.character(ingroup_freq$Word)
+ingroup_freq$percent = ingroup_freq$Freq/nrow(noout1) *100
+
+write.csv(ingroup_freq, "exp1_ingroup_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+ingroup_words = ingroup_freq$Word[ingroup_freq$percent >=1]
+##turn sideways to add to dataset
+ingroup_TDM = as.data.frame(t(ingroup_TDM))
+ingroup_TDM = ingroup_TDM[ , ingroup_words]
+
+##final dataset for ingroup
+ingroup_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
+                   ingroup_TDM)
+
+ingroup_cor = apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})
+
+ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
+ingroup_words_reduce = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
+```
+
+```{r authority-analysis-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1$Q32 = as.character(noout1$Q32)
+
+##stem the data
+for (i in 1:nrow(noout1)) {
+  noout1$Q32[i] = paste(unlist(
+    text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+authority_corpus = Corpus(VectorSource(noout1$Q32))
+authority_TDM = as.matrix(TermDocumentMatrix(authority_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+authority_freq = data.frame(Word = rownames(authority_TDM),
+                       Freq = rowSums(authority_TDM),
+                       row.names = NULL)
+authority_freq$Word = as.character(authority_freq$Word)
+authority_freq$percent = authority_freq$Freq/nrow(noout1) *100
+
+write.csv(authority_freq, "exp1_authority_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+authority_words = authority_freq$Word[authority_freq$percent >=1]
+##turn sideways to add to dataset
+authority_TDM = as.data.frame(t(authority_TDM))
+authority_TDM = authority_TDM[ , authority_words]
+
+##final dataset for authority
+authority_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
+                   authority_TDM)
+
+authority_cor = apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})
+
+authoritycut = mean(authority_cor) + 2*sd(authority_cor)
+authority_words_reduce = names(authority_cor[abs(authority_cor) >= authoritycut])
+```
+
+```{r purity-analysis-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1$Q34 = as.character(noout1$Q34)
+
+##stem the data
+for (i in 1:nrow(noout1)) {
+  noout1$Q34[i] = paste(unlist(
+    text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+purity_corpus = Corpus(VectorSource(noout1$Q34))
+purity_TDM = as.matrix(TermDocumentMatrix(purity_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+purity_freq = data.frame(Word = rownames(purity_TDM),
+                       Freq = rowSums(purity_TDM),
+                       row.names = NULL)
+purity_freq$Word = as.character(purity_freq$Word)
+purity_freq$percent = purity_freq$Freq/nrow(noout1) *100
+
+write.csv(purity_freq, "exp1_purity_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+purity_words = purity_freq$Word[purity_freq$percent >=1]
+##turn sideways to add to dataset
+purity_TDM = as.data.frame(t(purity_TDM))
+purity_TDM = purity_TDM[ , purity_words]
+
+##final dataset for purity
+purity_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
+                   purity_TDM)
+
+purity_cor = apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})
+
+puritycut = mean(purity_cor) + 2*sd(purity_cor)
+purity_words_reduce = names(purity_cor[abs(purity_cor) >= puritycut])
+```
+
+This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`.
+These concepts were included in the full dictionary used for Experiment 3.
+We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
+Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts.
+Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation.
+The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`, ingroup `r length(ingroup_words_reduce)`, authority `r length(authority_words_reduce)`, and purity `r length(purity_words_reduce)`.
+
+## Study 3.2
+
+this section is about the writing
+
+### Participants
+
+```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
+sample1 = read.csv("fixed_sample 1.csv", stringsAsFactors = F)
+sample2 = read.csv("fixed_sample 2.csv", stringsAsFactors = F)
+
+##merge files together
+fullsample = merge(sample1, sample2, all = TRUE)
+
+##merge together the writing samples
+#q24, q25, q26, q7 
+fullsample$writing = apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
+                           1, function(x) toString(na.omit(x)))
+
+##clear out completely columns we don't need
+crapcolumns = c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
+finalsample = fullsample[ , -crapcolumns]
+
+##accuracy
+summary(finalsample[ , 2:40])
+
+finalsample$Q10 = factor(finalsample$Q10,
+                         levels = 1:2,
+                         labels = c("Man", "Woman"))
+finalsample$Q11 = as.numeric(finalsample$Q11)
+finalsample$Q12 = factor(finalsample$Q12,
+                         levels = 1:7,
+                         labels = c("White", "Black", 
+                                    "Hispanic", "Asian",
+                                    "Native American", 
+                                    "Mixed", "Other"))
+
+gender = table(finalsample$Q10)/sum(table(finalsample$Q10))*100
+race = table(finalsample$Q12)/sum(table(finalsample$Q12))*100
+
+write.csv(finalsample, 'exp2_finalsample.csv', row.names = FALSE)
+newMFD = read.csv('exp2_finalsample_newMFD.csv')
+colnames(newMFD)[1:41] = colnames(finalsample)[1:41]
+newMFD = newMFD[,c(1,42:55)]
+finalsample = merge(finalsample, newMFD, by="ResponseId")
+
+##take out the people with less than 25 words
+##use the ngram library to examine the data
+##preprocess only works on one string at a time, so going to use a loop go through all the rows (apply won't work because we only want to work on one column)
+
+for (i in 1:nrow(finalsample)) {
+
+  finalsample$writing[i] = preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
+  finalsample$wordcount[i] = string.summary(finalsample$writing[i])$words
+
+}
+
+#remove small words people
+finalwords = subset(finalsample, wordcount >=25)
+
+##check out missing data
+#missing by row
+missing = apply(finalwords, 1, percentmiss)
+table(missing)
+goodrows = subset(finalwords, missing <= 5)
+
+#missing by column
+apply(goodrows, 2, percentmiss)
+
+##don't fill in Q10 to the end, be sure to merge these back together
+goodcolumns = goodrows[ , -c(32:42)]
+badcolumns = goodrows[ , c(32:42)]
+
+#fill in missing data points
+library(mice)
+tempnomiss = mice(goodcolumns)
+nomiss = complete(tempnomiss, 1)
+summary(nomiss)
+#merge
+allcolumns = cbind(nomiss, badcolumns) 
+summary(allcolumns)
+
+##outliers
+mahal2 = mahalanobis(allcolumns[ , -c(1,46:56)], 
+                    colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
+                    cov(allcolumns[ , -c(1,46:56)], use="pairwise.complete.obs"))
+#mahal2
+cutoff2 = qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
+cutoff2
+ncol(allcolumns[ , -c(1,46:56)])
+summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
+noout2 = subset(allcolumns, mahal2 < cutoff2)
+
+##assumptions on the questions i.e., not Q10 to the end
+#correlations
+correlations2 = cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
+#correlations2
+symnum(correlations2)
+
+#the random stuff
+random2 = rchisq(nrow(noout2), 7)
+fake2 = lm(random2~., data=noout2[ , -c(1,46:56)])
+
+#normal
+standardized2 = rstudent(fake2)
+hist(standardized2, breaks=15)
+
+#linear
+{qqnorm(standardized2)   
+abline(0,1)}
+
+#homog + s
+fitvalues2 = scale(fake2$fitted.values)
+{plot(fitvalues2, standardized2) 
+abline(0,0)
+abline(v = 0)}
+
+####create the MFQ subscales####
+noout2$harmMFQ = apply(noout2[ , 2:4], 1, sum)
+noout2$fairMFQ = apply(noout2[ , 5:7], 1, sum)
+noout2$ingroupMFQ = apply(noout2[ , 8:10], 1, sum)
+noout2$authorityMFQ = apply(noout2[ , 11:13], 1, sum)
+noout2$purityMFQ = apply(noout2[ , 14:16], 1, sum)
+```
+
+Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes [@Jordan].
+Participants were recruited via an online research system (SONA) and were given course credit for their participation.
+`r nrow(finalsample)` participants were included in the this study.
+The study was mostly women (`r printnum(gender["Woman"], digits = 1)`%) and White (`r printnum(race["White"], digits = 1)`%) participants with a mix of minority participants: Black (`r printnum(race["Black"], digits = 1)`%), (`r printnum(race["Hispanic"], digits = 1)`%), (`r printnum(race["Asian"], digits = 1)`%), Native American (`r printnum(race["Native American"], digits = 1)`%), Mixed (`r printnum(race["Mixed"], digits = 1)`%) and Other (`r printnum(race["Other"], digits = 1)`%).
+The average listed age was `r printnum(mean(finalsample$Q11, na.rm = T))` (*SD* = `r printnum(sd(finalsample$Q11, na.rm = T))`).
+
+###	Materials and Procedure
+
+Data was again collected via Qualtrics.
+Four fake new stories were presented to participants, which were roughly 400 words each.
+First, all news stories included a few sentences describing the use of chemical weapons in the Syrian civil war.
+The news stories were manipulated with political (Republican v.
+Democrat) and religious (religious v.
+not) quotes in a 2 x 2 design.
+News stories can be found in the online materials.
+Participants also completed the 30-item version of the MFQ as described in the introduction.
+In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.
+
+After consenting to participate in the study, participants were randomly shown one of the four new articles about Syria's use of chemical weapons.
+Participants were then asked to write for 5-10 minutes about their reaction to Syria's use of chemical weapons and the needed response from the United States.
+The second wave of data collection included different writing prompts designed to capture more of the moral foundation areas in their writing.
+The following writing prompt was used, "Please write about your attitudes on abortion (or same-sex marriage or environmentalism) as well as your reason for this stance." The three prompts were chosen to create a more varied word set by using topics that should elicit words from each moral foundations category by soliciting a moral response.
+In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants.
+Participants then completed the MFQ, demographics, and the political orientation scale.
+
+### Results
+
+Participant data was first spell checked and screening for inaccurate responses.
+Participants who did not write more than fifty words in response to a given prompt were excluded (*n* = `r nrow(finalsample) - nrow(finalwords)`).
+One missing datapoint was estimated using the *mice* library from *R* [@CITE] for a missing MFQ question, and all other missing data was present in the demographics sections, which were not filled in.
+The MFQ data were screened for outliers using Mahalanobis distance, and fourteen outliers were found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) = `r printnum(cutoff2)`.
+These data were excluded leading to a final sample size of `r nrow(noout2)`.
+Data were screened for assumptions described in Experiment 1 and were found to be satisfactory.
+
+```{r writing-analysis-3.2, include=FALSE}
+##stem the data
+for (i in 1:nrow(noout2)) {
+  noout2$writing2[i] = paste(unlist(
+    text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+overall_corpus = Corpus(VectorSource(noout2$writing2))
+overall_TDM = as.matrix(TermDocumentMatrix(overall_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+overall_freq = data.frame(Word = rownames(overall_TDM),
+                          Freq = rowSums(overall_TDM),
+                          row.names = NULL)
+overall_freq$Word = as.character(overall_freq$Word)
+overall_freq$percent = overall_freq$Freq/nrow(noout2)*100
+
+write.csv(overall_freq, "exp2_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+##this goes over 100% but mostly want to subset out things that were only mentioned
+##a few times by participants
+all_words = overall_freq$Word[overall_freq$percent >=1]
+
+##turn sideways to add to dataset
+overall_TDM = as.data.frame(t(overall_TDM))
+overall_TDM = overall_TDM[ , all_words]
+
+##final dataset
+overall_final = cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
+                                  "authorityMFQ", "purityMFQ","ingroupMFQ")],
+                   overall_TDM)
+```
+
+```{r mfq-cor-3.2, include = FALSE}
+##harm
+harm_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})
+
+harmcut = mean(harm_cor) + 2*sd(harm_cor)
+harm_words_reduce_exp2 = names(harm_cor[abs(harm_cor) >= harmcut])
+
+##fair
+fair_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})
+
+faircut = mean(fair_cor) + 2*sd(fair_cor)
+fair_words_reduce_exp2 = names(fair_cor[abs(fair_cor) >= faircut])
+
+##purity
+purity_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})
+
+puritycut = mean(purity_cor) + 2*sd(purity_cor)
+purity_words_reduce_exp2 = names(purity_cor[abs(purity_cor) >= puritycut])
+
+##authority
+authority_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})
+
+authoritycut = mean(authority_cor) + 2*sd(authority_cor)
+authority_words_reduce_exp2 = names(authority_cor[abs(authority_cor) >= authoritycut])
+
+##ingroup
+ingroup_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})
+
+ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
+ingroup_words_reduce_exp2 = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
+
+##print out words list to look at for further analysis
+#write.csv(harm_words_reduce_exp2, "words/harm_exp2.csv", row.names = F)
+#write.csv(fair_words_reduce_exp2, "words/fair_exp2.csv", row.names = F)
+#write.csv(authority_words_reduce_exp2, "words/authority_exp2.csv", row.names = F)
+#write.csv(purity_words_reduce_exp2, "words/purity_exp2.csv", row.names = F)
+#write.csv(ingroup_words_reduce_exp2, "words/ingroup_exp2.csv", row.names = F)
+```
+
+In the first study, only free association responses were collected, but in this study, full writing samples were collected.
+Therefore, we expected many of the words listed to be part of creating a cohesive discourse, rather than only related to the moral foundation targeted.
+To find only the most related words, the correlation between word frequency and moral foundation was calculated and words with correlations greater than two standard deviations outside the mean were selected for the dictionary analysis in Experiment 3.
+The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
+The average scores were: harm (*M* = `r printnum(mean(noout2$harmMFQ))`, *SD* = `r printnum(sd(noout2$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout2$fairMFQ))`, *SD* = `r printnum(sd(noout2$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout2$ingroupMFQ))`, *SD* = `r printnum(sd(noout2$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout2$authorityMFQ))`, *SD* = `r printnum(sd(noout2$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout2$purityMFQ))`, *SD* = `r printnum(sd(noout2$purityMFQ))`).
+
+```{r compare-ratings-3.2, include = FALSE}
+authority_erin = read.csv("words/authority_exp2 erin.csv", stringsAsFactors = F)
+authority_will = read.csv("words/authority_exp2 will.csv", stringsAsFactors = F)
+authority_erin$x[authority_erin$use != authority_will$use]
+
+authority_words_reduce_exp2 = authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]
+
+fair_erin = read.csv("words/fair_exp2 erin.csv", stringsAsFactors = F)
+fair_will = read.csv("words/fair_exp2 will.csv", stringsAsFactors = F)
+fair_erin$x[fair_erin$use != fair_will$use]
+fair_will$use[fair_will$x == "carbon"] = 0
+fair_will$use[fair_will$x == "emiss"] = 0
+#exclude carbon and emiss due to the prompt
+
+fair_words_reduce_exp2 = fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]
+
+purity_erin = read.csv("words/purity_exp2 erin.csv", stringsAsFactors = F)
+purity_will = read.csv("words/purity_exp2 will.csv", stringsAsFactors = F)
+purity_erin$x[purity_erin$use != purity_will$use]
+purity_will$use[purity_will$x == "befor"] = 1
+#before include because of "before sex/ruined/etc."
+
+purity_words_reduce_exp2 = purity_words_reduce_exp2[purity_words_reduce_exp2 %in% purity_will$x[purity_will$use == 1]]
+
+ingroup_erin = read.csv("words/ingroup_exp2 erin.csv", stringsAsFactors = F)
+ingroup_will = read.csv("words/ingroup_exp2 will.csv", stringsAsFactors = F)
+ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
+ingroup_will$use[ingroup_will$x == "mean"] = 1
+#mean should be included
+
+ingroup_words_reduce_exp2 = ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]
+
+harm_erin = read.csv("words/harm_exp2 erin.csv", stringsAsFactors = F)
+harm_will = read.csv("words/harm_exp2 will.csv", stringsAsFactors = F)
+harm_erin$x[harm_erin$use != harm_will$use]
+harm_will$use[harm_will$x == "import"] = 1
+#import for important
+
+harm_words_reduce_exp2 = harm_words_reduce_exp2[harm_words_reduce_exp2 %in% harm_will$x[harm_will$use == 1]]
+```
+
+This set of words was then coded by two of the authors for relevant words with discussion over coding constituting a tiebreaker.
+For example, for harm words in this study both *also* and *Syria* appeared as correlated words to the harm foundation.
+The first word does not meet face validity of correlation with the dictionary, and these type of function words or ambiguous verbs (i.e., *get*, *can*) were usually excluded.
+The second example is likely because of the writing prompt, and therefore, proper nouns were also excluded.
+The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce_exp2)`, fairness `r length(fair_words_reduce_exp2)`, ingroup `r length(ingroup_words_reduce_exp2)`, authority `r length(authority_words_reduce_exp2)`, and purity `r length(purity_words_reduce_exp2)`.
+
+## Study 3.3
+
+This part is the mtmm
+
+```{r mtmm-setup, include = FALSE}
+##original mfd words
+original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
+
+##adding forms/conjugations of words to original_mfd
+#harm/care
+original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
+                             "sympathetic","sympathies","damaged",
+                             "damaging","attacked","attacking","attacker",
+                             "attacks","attackers", "benefits", "benefitted",
+                             "benefitting", "cares", "cared", "caring", "crushes",
+                             "crushing", "crushed", "dangerous", "defends", "defending",
+                             "defended", "detroys", "destroyed", "destroying",
+                             "fights", "fought", "fighting", "guards", "guarded",
+                             "guarding", "harms", "harmed", "harming", "hurts",
+                             "hurting", "kills", "killed", "killing", "preserves",
+                             "preserved", "preserving", "protects", "protected",
+                             "protecting", "protection", "ruins", "ruined", "ruining",
+                             "safely", "safer", "shelters", "sheltered", "sheltering",
+                             "spurns", "spurned", "spurning", "stomps", "stomped",
+                             "stomping", "suffers", "suffered", "suffering",
+                             "violence", "warring")
+
+#fairness/reciprocity
+original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
+                             "biases", "discriminates", "discriminated",
+                             "discriminating", "discrimination", "equals",
+                             "equaled", "equaling", "equates", "equated",
+                             "equating", "evens", "evened", "evening",
+                             "excludes", "excluded", "excluding", "fairness",
+                             "favors", "favored", "favoring", "honesty",
+                             "impariality", "justice", "justifies", "justified",
+                             "justifying", "prefers", "preferred", "preferring",
+                             "prejudices", "prejudiced", "prejudicing", "reasons",
+                             "reasoned", "reasoning", "rights", "tolerates",
+                             "tolerated", "tolerating", "toleration")
+
+#ingroup/loyalty
+original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
+                             "communities", "deceives", "deceived", "deceiving",
+                             "deception", "deceptions", "deserts", "deserted",
+                             "deserting", "desertion", "families", "fellows",
+                             "foreigners", "groups", "grouped", "grouping",
+                             "indviduals", "indvidualize", "individualized",
+                             "individualizing", "members", "nations", "sides",
+                             "togetherness", "traits", "unites", "united", "uniting")
+
+#authority/respect
+original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
+                              "classes", "classed", "classing", "command",
+                              "commanded", "commanding", "controls", "controlled",
+                              "controlling", "defects", "defected", "defecting",
+                              "defers", "deferred", "deferring", "deference",
+                              "defies", "defied", "defying", "defiance", "deserts",
+                              "deserted", "deserting", "desertion", "duties",
+                              "faiths", "fathers", "fathered", "fathering",
+                              "honors", "honored", "honoring", "laws", "leads",
+                              "leading", "mothers", "mothered", "mothering",
+                              "obeys", "obeyed", "obeying", "opposes", "opposed",
+                              "opposing", "orders", "ordered", "ordering", "permits",
+                              "permitted", "permitting", "positions", "positioned",
+                              "positioning", "preserves", "preserved", "preserving",
+                              "preservation", "protests", "protested", "protesting",
+                              "refuses", "refused", "refusing", "refusal", "respects",
+                              "respected", "respecting", "respectful", "reveres",
+                              "revered", "revering", "reverence", "serves", "served",
+                              "serving", "traditions", "traditional", "traits")
+
+#purity/sanctity
+original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
+                             "adulteries", "adulterous", "adulterer", "adulterers",
+                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
+                             "cleanliness", "dirty", "diseases", "diseased", 
+                             "disgusts", "disgusted", "disgusting", "grossness",
+                             "innocence", "modesty", "preserves", "preserved",
+                             "preserving", "preservation", "promiscuity",
+                             "promiscuities", "purity", "rights", "ruins", "ruined",
+                             "ruining", "sacredness", "sickness", "sicknesses",
+                             "sins", "wholeness", "wholesome")
+
+##stem the original mfd
+for(i in 1:nrow(original_mfd)) {
+  original_mfd$h2[i] = stemDocument(original_mfd$h2[i], language = "english")
+  original_mfd$f2[i] = stemDocument(original_mfd$f2[i], language = "english")
+  original_mfd$i2[i] = stemDocument(original_mfd$i2[i], language = "english")
+  original_mfd$a2[i] = stemDocument(original_mfd$a2[i], language = "english")
+  original_mfd$p2[i] = stemDocument(original_mfd$p2[i], language = "english")
+}
+
+mtmmdata = noout2[ , c(1:31, 42) ]
+
+####figure out the percents for the exp2 data
+for (i in 1:nrow(mtmmdata)) {
+
+  ##figure out the sum for just the original mfd
+  mtmmdata$harm_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])
+
+  mtmmdata$purity_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])
+
+  mtmmdata$fair_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])
+
+  mtmmdata$authority_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])
+
+  mtmmdata$ingroup_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])
+
+  ##figure out the sum for all words ever 
+  mtmmdata$harm_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])
+
+  mtmmdata$purity_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])
+
+  mtmmdata$fair_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])
+
+  mtmmdata$authority_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])
+
+  mtmmdata$ingroup_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])
+
+  ##figure out the sum for reduced words
+  mtmmdata$harm_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])
+
+  mtmmdata$purity_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])
+
+  mtmmdata$fair_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])
+
+  mtmmdata$authority_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])
+
+  mtmmdata$ingroup_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])
+
+}
+
+#create percents instead of frequencies
+mtmmdata[ , c(33:47)] = mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100
+
+summary(mtmmdata[ , 33:47])
+
+```
+
+```{r mtmm_orig, include = FALSE}
+###Run chunk 8: demos_study2 to update data
+###Use noout2 df as dataframe for mtmm
+###Columns labeled Harm1/Fairness1/Loyalty1/Authority1/Purity1 are original MFD
+###Columns labeled Harm2/Fairness2/Loyalty2/Authority2/Purity2 are revised MFD
+
+##now run some MTMM!
+library(semPlot)
+library(lavaan)
+
+####mtmm original dictionary####
+
+{model1 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
+summary(model1.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.fit, fit.measures = "aic")
+
+{model1.2 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+fair_orig ~~ 1167.145*fair_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.2.fit = cfa(model1.2, data=mtmmdata, std.lv=TRUE)
+summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.2.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.2.fit, fit.measures = "aic")
+
+{model2 ='
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+fair_orig ~~ 1167.145*fair_orig
+'}
+
+model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
+summary(model2.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model2.fit, fit.measures = "aic")
+
+{model3 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+harmL~~1*fairL
+harmL~~1*ingroupL
+harmL~~1*authorityL
+harmL~~1*purityL
+fairL~~1*ingroupL
+fairL~~1*authorityL
+fairL~~1*purityL
+ingroupL~~1*authorityL
+ingroupL~~1*purityL
+authorityL~~1*purityL
+
+fair_orig ~~ 1167.145*fair_orig
+'}
+
+model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
+summary(model3.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model3.fit, fit.measures = "aic")
+
+{model4 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+mfq ~~ 0*mfd
+
+fair_orig ~~ 1167.145*fair_orig
+'}
+
+model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
+summary(model4.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model4.fit, fit.measures = "aic")
+```
+
+```{r mtmm_reduce, include = FALSE}
+
+{model1 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
+fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
+purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
+summary(model1.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.fit, fit.measures = "aic")
+
+{model2 ='
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+'}
+
+model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
+summary(model2.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model2.fit, fit.measures = "aic")
+
+{model3 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
+fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
+purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+harmL~~1*fairL
+harmL~~1*ingroupL
+harmL~~1*authorityL
+harmL~~1*purityL
+fairL~~1*ingroupL
+fairL~~1*authorityL
+fairL~~1*purityL
+ingroupL~~1*authorityL
+ingroupL~~1*purityL
+authorityL~~1*purityL
+'}
+
+model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
+summary(model3.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model3.fit, fit.measures = "aic")
+
+{model4 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
+fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
+purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+mfq ~~ 0*mfd
+'}
+
+model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
+summary(model4.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model4.fit, fit.measures = "aic")
+```
+
+```{r mtmm_all, include = FALSE}
+
+{model1 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
+summary(model1.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.fit, fit.measures = "aic")
+
+{model2 ='
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+'}
+
+model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
+summary(model2.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model2.fit, fit.measures = "aic")
+
+{model3 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+harmL~~1*fairL
+harmL~~1*ingroupL
+harmL~~1*authorityL
+harmL~~1*purityL
+fairL~~1*ingroupL
+fairL~~1*authorityL
+fairL~~1*purityL
+ingroupL~~1*authorityL
+ingroupL~~1*purityL
+authorityL~~1*purityL
+'}
+
+model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
+summary(model3.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model3.fit, fit.measures = "aic")
+
+{model4 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+mfq ~~ 0*mfd
+'}
+
+model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
+summary(model4.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model4.fit, fit.measures = "aic")
+```
+
 # Participants

### 2023-09-01 manuscript_version/revision/manuscript_metapsych_revision.Rmd
adding irb for study

@@
 
-bibliography      : ["../metapsych_bib.bib"] #turn this off right now so it knits
+bibliography      : ["./metapsych_bib.bib"] #turn this off right now so it knits
 
@@
 library(dplyr)
+library(rio)
 
@@
 options(tinytex.verbose = TRUE)
+percentmiss <- function(x){sum(is.na(x))/length(x)*100}
 ```
@@
 ```{r stem_text, eval=TRUE, include=FALSE}
-final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
+final = read.csv("./exp1_data/finaldata.csv", stringsAsFactors = F)
 final = na.omit(final) #one weird NA line
@@
 ##open the Warriner data for later
-warriner = read.csv("../exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+warriner = read.csv("./exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
 warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
@@
 #read in the harm total words from the mtmm project
-harm_all = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 #read it in
-NYtimes_kav = read.csv("../exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-NPR_kav = read.csv("../exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-SLATE_kav = read.csv("../exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("../exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-POLITICO_kav = read.csv("../exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-FOX_kav = read.csv("../exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok
-BREITBART_kav = read.csv("../exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
-RUSH_kav = read.csv("../exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-BLAZE_kav = read.csv("../exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HANNITY_kav = read.csv("../exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+NYtimes_kav = read.csv("./exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+NPR_kav = read.csv("./exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+SLATE_kav = read.csv("./exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+HUFFPO_kav = read.csv("./exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+POLITICO_kav = read.csv("./exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+FOX_kav = read.csv("./exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok
+BREITBART_kav = read.csv("./exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
+RUSH_kav = read.csv("./exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+BLAZE_kav = read.csv("./exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+HANNITY_kav = read.csv("./exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
 
@@
 #read it in
-NYtimes_gs = read.csv("../exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
-NPR_gs = read.csv("../exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
-SLATE_gs = read.csv("../exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok
-HUFFPO_gs = read.csv("../exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok
-POLITICO_gs = read.csv("../exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
-FOX_gs = read.csv("../exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok
-BREITBART_gs = read.csv("../exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok
-RUSH_gs = read.csv("../exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
-BLAZE_gs = read.csv("../exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok
-HANNITY_gs = read.csv("../exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
+NYtimes_gs = read.csv("./exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+NPR_gs = read.csv("./exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
+SLATE_gs = read.csv("./exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok
+HUFFPO_gs = read.csv("./exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok
+POLITICO_gs = read.csv("./exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
+FOX_gs = read.csv("./exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok
+BREITBART_gs = read.csv("./exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok
+RUSH_gs = read.csv("./exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
+BLAZE_gs = read.csv("./exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok
+HANNITY_gs = read.csv("./exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
 
@@
 #read in the harm total words from the mtmm project
-harm_all_kav = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_kav = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all_kav = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all_kav = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all_kav = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all_kav = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 #read in the harm total words from the mtmm project
-harm_all_gs = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_gs = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair_gs, echo = F, include=FALSE}
-fair_all_gs = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all_gs = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
-ingroup_all_gs = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all_gs = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority_gs, echo = F, include=FALSE}
-authority_all_gs = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all_gs = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity_gs, echo = F, include=FALSE}
-purity_all_gs = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all_gs = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 
-As a final test of the MFD, we had participants write about explicitly moral topics which was then analyzed with the MFD which supplemented using participant score's on the Moral Foundation Questionnaire.
-These changes create the best case scenario for finding the theorized differences
+Results from Study 1 and 2 indicated that no differences were found in the MFD for Liberal and Conservative sources using the traditional dictionary and valence weighting.
+The MFD was developed in conjunction with the Moral Foundations Questionnaire (MFQ), using the same five latent areas.
+In this set of studies, we examined the MFD and MFQ within the same study.
+The first two sub-studies were used to develop a (potentially) larger dictionary for the MFD and collect data on both scales.
+The last sub-study examined the MFD and MFQ using multi-trait multi-method analysis [CITE WIDAMEN AND BYRNE].
+
+DESCRIBE MTMM
 
@@
 
-this part is the association study information
+In this study, participants were given a word association task elicit additional semantically related word forms for each moral foundation.
+This data was used to expand the MFD for each latent area to determine if these additional words could improve scores and test measurement relation to the MFQ in Study 3.3.
+
+### Participants
 
 ```{r demos-mtmm-study-3.1, include = FALSE}
-exp1data = read.csv("fixed_association.csv")
+exp1data <- import("exp3_data/study3.1_fixed_associations.csv")
 
 ##clear out completely columns we don't need
-crapcolumns = c(1, 2, 3, 5:14)
-finalsample = exp1data[ , -crapcolumns]
+crapcolumns <- c(1, 2, 3, 5:14)
+finalsample <- exp1data[ , -crapcolumns]
 
@@
 summary(finalsample) #Check Q15_1 and Q23 for in-range scores -WP
-finalsample$Q23 = factor(finalsample$Q23,
+finalsample$Q23 <- factor(finalsample$Q23,
                          levels = 1:3,
@@
 #by people 
-missing_demo1 = apply(finalsample, 1, percentmiss) 
+missing_demo1 <- apply(finalsample, 1, percentmiss) 
 table(missing_demo1)
 
-replacepeople1 = subset(finalsample, missing_demo1 <= 5)  #we are using 5%, yes? 
+replacepeople1 <- subset(finalsample, missing_demo1 <= 5)  #we are using 5%, yes? 
 #by column 
@@
 
-finalsample = replacepeople1
+finalsample <- replacepeople1
 summary(finalsample)
 
-party = table(finalsample$Q23)
+party <- table(finalsample$Q23)
 ##be sure to exclude the writing columns columns 2:6 
@@
 ##outliers
-mahal1 = mahalanobis(finalsample[ , -c(1:6,22,23)], 
+mahal1 <- mahalanobis(finalsample[ , -c(1:6,22,23)], 
                     colMeans(finalsample[ , -c(1:6,22,23)], na.rm = TRUE),
@@
 #mahal1
-cutoff1 = qchisq(1 - .001,ncol(finalsample[ , -c(1:6,22,23)]))
+cutoff1 <- qchisq(1 - .001,ncol(finalsample[ , -c(1:6,22,23)]))
 cutoff1
@@
 summary(mahal1 < cutoff1) #Hmm what to do w/ NAs?? -WP
-noout1 = subset(finalsample, mahal1 < cutoff1)
+noout1 <- subset(finalsample, mahal1 < cutoff1)
 
@@
 #correlations for MFQ
-correlations1 = cor(noout1[,-c(1:6,22,23)], use="pairwise.complete.obs")
+correlations1 <- cor(noout1[,-c(1:6,22,23)], use="pairwise.complete.obs")
 correlations1
@@
 #making the random stuff
-random1 = rchisq(nrow(noout1), 7)
-fake1 = lm(random1~., data=noout1[ , -c(1:6)])
+random1 <- rchisq(nrow(noout1), 7)
+fake1 <- lm(random1~., data=noout1[ , -c(1:6)])
 #normal
-standardized1 = rstudent(fake1)
+standardized1 <- rstudent(fake1)
 hist(standardized1, breaks=15)
@@
 #homog + s
-fitvalues1 = scale(fake1$fitted.values)
+fitvalues1 <- scale(fake1$fitted.values)
 {plot(fitvalues1, standardized1) 
@@
 ####create the MFQ subscales####
-noout1$harmMFQ = apply(noout1[ , 7:9], 1, sum)
-noout1$fairMFQ = apply(noout1[ , 10:12], 1, sum)
-noout1$ingroupMFQ = apply(noout1[ , 13:15], 1, sum)
-noout1$authorityMFQ = apply(noout1[ , 16:18], 1, sum)
-noout1$purityMFQ = apply(noout1[ , 19:21], 1, sum)
+noout1$harmMFQ <- apply(noout1[ , 7:9], 1, sum)
+noout1$fairMFQ <- apply(noout1[ , 10:12], 1, sum)
+noout1$ingroupMFQ <- apply(noout1[ , 13:15], 1, sum)
+noout1$authorityMFQ <- apply(noout1[ , 16:18], 1, sum)
+noout1$purityMFQ <- apply(noout1[ , 19:21], 1, sum)
 ```
@@
 
+  Data Cleaning and Descriptives.
+In sample 1, participants who wrote less than 50 words were deleted (*n* = 69) leaving *n* = 221 participants.
+The average political orientation was 4.80 (*SD* = 2.21) on a scale of 1 (*conservative*) to 10 (*liberal*).
+In sample 2, all 160 participants wrote at least 50 words.
+The mean political orientation was 5.01 (*SD* = 2.33) for sample 2.
+The data from sample 1 and sample 2 were combined.
+Before any analyses were conducted, participants who did not use any words from the MFD were deleted; 16 participants were deleted from sample 1 and 25 from sample 2.
+The final sample size for analysis was *N* = 340 which had a mean political orientation of 4.90 (*SD* = 2.28).
+MFD scores were computed using NVivo *(CITE)* as both frequency for each foundation and percent coverage for each foundation.
+Frequency was simply the count of the number of words used from a given foundation dictionary; for example, a participant using the word *war* once and the word *peace* twice would have a frequency score of 3 for the *harm* dictionary.
+Percent coverage was calculated by taking the frequency and dividing by the word count; for example, given a frequency score of 3 for the *harm* dictionary and a word count of 100, then the percent coverage would be .03 for the *harm* dictionary.
+MFQ scores for each foundation were calculated by averaging the six items pertaining to each foundation.
+	Reliability.
+Here we should talk about the reliability of the MFQ for each piece, as well as the reliability of the words for the MFD.
+I think to do that you might need a thing that has each word as frequency count yes/no or however the LIWC version thing was done.
+	MTMM. BASIC SEM STUFF HERE (also that you used bayes)
+Data screening was conducted using SPSS version 22 and AMOS version 22.
+Participants who were missing data for the MFD, MFQ, or political orientation were deleted from all analyses.
+Given the distribution of the dictionary variables, participants whose writing sample were less than 2% words from the MFD were deleted resulting in a sample size of 252.
+Additionally, 7 outliers were deleted.
+Widaman's (1985; as cited in @Byrne2009) four-step nested method was used to test the convergent and divergent validity of the MFD and MFQ.
+The first step is the baseline model (Model 1), which establishes correlation among traits (*harm*, *purity*, *fairness*, *authority*, and *ingroup*) as well as correlation among methods (MFD and MFQ) but no cross correlation of traits and methods.
+The individual questions from the 30 item version of the MFQ and the total frequency of concepts from each foundation in the MFD were used as measured variables.
+The fit of this first model indicated some misfit, as fit indices were a mix of poor and acceptable, $\chi$ 2 (514) = 977.46, $\chi$ 2/df = 1.90, CFI = .842, RMSEA = .061 [95% CI = .055-.067], SRMR = .0623.
+In this model, the MFD *harm*, *fairness*, and *ingroup* items significantly loaded onto their trait factors, while *authority* and *purity* did not.
+All foundations but *authority* loaded significantly on the method traits.
+All but two of the *ingroup* questions and one *authority* question loaded onto the MFQ trait factors.
+Several questions of the MFQ did not load significantly onto the methods factors; however, this result was taken as an indicator that traits variance was higher than methods variance.
+Generally, trait loadings were higher than method loadings for both the MFD and MFQ for *harm* and *fairness* traits.
+However, the *purity*, *ingroup*, and *authority* foundations did not show this loading pattern.
+ERIN STOPPED HERE CUZ HEADACHE. 
+The second step (Model 2) involved eliminating the latent traits from the model.
+This model was significantly worse than Model 1 indicating the traits are important to the model ($\delta$ $\chi$ 2 = 1141.09, $\delta$ df = 45, $\delta$ CFI = .351).
+This supports convergent validity for the traits measured by both methods which in this case are the five moral foundations.
+The third step (Model 3) involved forcing the five traits to be perfectly correlated.
+This model was significantly worse than Model 1 indicating the usefulness of five unique traits ($\delta$ $\chi$ 2 = 311.09, $\delta$ df = 10, $\delta$ CFI = .097).
+This supports discriminant validity for the existence of five unique moral foundations.
+The final step (Model 4) involved allowing the correlations between the traits to be freely estimated and forcing the methods to be uncorrelated.
+This model was similar to Model 1 indicating the methods both measure the traits but they are both unique methods ($\delta$ $\chi$ 2 = 2.23, $\delta$ df = 1, $\delta$ CFI = .001).
+This supports discriminant validity for the methods.
+This set of analyses suggests the MFD is a possibly valid measure of moral foundations but does not measure them well enough to be useful in all applications and may be measuring them differently than the MFQ.
+	Regression predicting Political Orientation.
+The MFQ has predicted political orientation across many studies [@Federico2013; @Graham2009; @Haidt2009; @Weber2013].
+Therefore, in addition to the MTMM analysis, we compared how well the MFD score predicted political orientation compared to how well the MFQ predicted the political orientation.
+First, total MFQ scores were calculated for each foundation by averaging all six items.
+Then, a regression analysis was conducted with the five MFQ foundation score predicting political orientation.
+The overall model was significant, *R2* = .35, *F* (5, 255) = 26.91, *p* < .05.
+Higher scores on the harm and fairness foundations predicted a more liberal political orientation with harm accounting for 3% of the variance and fairness accounting for 6%.
+Higher scores on ingroup, authority, and purity predicted a more conservative orientation accounting for 1%, 2%, and 8% on the variance respectively.
+See *table ?* for regression coefficients.
+Next, a regression analysis was conducted to determine how well the five MFD scores predicted political orientation.
+The overall model was not significant, *R2* = .16, *F* (5, 255) = 1.36, *p* = .241.
+Higher harm scores somewhat predicted more liberal orientation accounting for 1% of the variance in political orientation.
+Higher purity scores somewhat predicted more conservative orientation accounting for 1% of the variance.
+See *table ?* for regression coefficients.
+
 # Participants

### 2023-09-01 manuscript_version/revision/manuscript_metapsych_revision.Rmd
updating with irb

@@
 library(rio)
+library(mice)
+
+# to install this package 
+# tmp <- tempfile()
+# system2("git", c("clone", "--recursive",
+#                  shQuote("https://github.com/leslie-huang/r-corpus.git"), shQuote(tmp)))
+# devtools::install(tmp)
+library(corpus)
 
@@
 
-A complete example of the survey can be found online at OSF LINK.
+A complete example of the survey can be found online at https://osf.io/5uqfn.
 First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech.
-Next, the free association task, similar to that used in @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind".
+Next, the free association task, similar to that used in CITE @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind".
 The participants were then given three example free association cues, *lost*, *old*, and *article*.
@@
 Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise.
-The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r cutoff1`.
+The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012 CITE, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r apa_num(cutoff1)`.
 These participants were excluded from further analyses, representing `r nrow(noout1)` final participants.
-The final data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.
+The final MFQ data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.
 
@@
 The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`).
-Participants free association responses were processed using the *tm* library [@CITE] after spell checking.
+Participants free association responses were processed using the *tm* [CITE] and *corpus* [CITE] libraries after spell checking.
 Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*.
 We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary.
-Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manuall recode all word forms.
+Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manually recode all word forms.
 Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses.
@@
 #q27 through 34 are the writing columns
-noout1$Q27 = as.character(noout1$Q27)
+noout1$Q27 <- as.character(noout1$Q27)
 
 ##stem the data
-
 for (i in 1:nrow(noout1)) {
-  noout1$Q27[i] = paste(unlist(
+  noout1$Q27[i] <- paste(unlist(
     text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
@@
 ##create a corpus
-harm_corpus = Corpus(VectorSource(noout1$Q27))
-harm_TDM = as.matrix(TermDocumentMatrix(harm_corpus,
+harm_corpus <- Corpus(VectorSource(noout1$Q27))
+harm_TDM <- as.matrix(TermDocumentMatrix(harm_corpus,
                               control = list(removePunctuation = TRUE,
@@
 ##view the most frequent words
-harm_freq = data.frame(Word = rownames(harm_TDM),
+harm_freq <- data.frame(Word = rownames(harm_TDM),
                        Freq = rowSums(harm_TDM),
                        row.names = NULL)
-harm_freq$Word = as.character(harm_freq$Word)
-harm_freq$percent = harm_freq$Freq/nrow(noout1) *100
-
-write.csv(harm_freq, "exp1_harm_freq.csv", row.names = F)
+harm_freq$Word <- as.character(harm_freq$Word)
+harm_freq$percent <- harm_freq$Freq/nrow(noout1) *100
+
+write.csv(harm_freq, "exp3_data/study3.1_harm_freq.csv", row.names = F)
 
 ##subset out to only words with 1% mentions
-harm_words = harm_freq$Word[harm_freq$percent >=1]
+harm_words <- harm_freq$Word[harm_freq$percent >=1]
 ##turn sideways to add to dataset
-harm_TDM = as.data.frame(t(harm_TDM))
-harm_TDM = harm_TDM[ , harm_words]
+harm_TDM  <- as.data.frame(t(harm_TDM))
+harm_TDM  <- harm_TDM[ , harm_words]
 
 ##final dataset for harm
-harm_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
+harm_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
                    harm_TDM)
 
-harm_cor = apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})
-
-harmcut = mean(harm_cor) + 2*sd(harm_cor)
-harm_words_reduce = names(harm_cor[abs(harm_cor) >= harmcut])
+harm_cor <- apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})
+
+harmcut <- mean(harm_cor) + 2*sd(harm_cor)
+harm_words_reduce <- names(harm_cor[abs(harm_cor) >= harmcut])
 ```
@@
 for (i in 1:nrow(noout1)) {
-  noout1$Q29[i] = paste(unlist(
+  noout1$Q29[i] <- paste(unlist(
     text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
@@
 ##create a corpus
-fair_corpus = Corpus(VectorSource(noout1$Q29))
-fair_TDM = as.matrix(TermDocumentMatrix(fair_corpus,
+fair_corpus <- Corpus(VectorSource(noout1$Q29))
+fair_TDM <- as.matrix(TermDocumentMatrix(fair_corpus,
                               control = list(removePunctuation = TRUE,
@@
 ##view the most frequent words
-fair_freq = data.frame(Word = rownames(fair_TDM),
+fair_freq <- data.frame(Word = rownames(fair_TDM),
                        Freq = rowSums(fair_TDM),
                        row.names = NULL)
-fair_freq$Word = as.character(fair_freq$Word)
-fair_freq$percent = fair_freq$Freq/nrow(noout1) *100
-
-write.csv(fair_freq, "exp1_fair_freq.csv", row.names = F)
+fair_freq$Word <- as.character(fair_freq$Word)
+fair_freq$percent <- fair_freq$Freq/nrow(noout1) *100
+
+write.csv(fair_freq, "exp3_data/study3.1_fair_freq.csv", row.names = F)
 
 ##subset out to only words with 1% mentions
-fair_words = fair_freq$Word[fair_freq$percent >=1]
+fair_words <- fair_freq$Word[fair_freq$percent >=1]
 ##turn sideways to add to dataset
-fair_TDM = as.data.frame(t(fair_TDM))
-fair_TDM = fair_TDM[ , fair_words]
+fair_TDM <- as.data.frame(t(fair_TDM))
+fair_TDM <- fair_TDM[ , fair_words]
 
 ##final dataset for fair
-fair_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
+fair_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
                    fair_TDM)
 
-fair_cor = apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})
-
-faircut = mean(fair_cor) + 2*sd(fair_cor)
-fair_words_reduce = names(fair_cor[abs(fair_cor) >= faircut])
+fair_cor <- apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})
+
+faircut <- mean(fair_cor) + 2*sd(fair_cor)
+fair_words_reduce <- names(fair_cor[abs(fair_cor) >= faircut])
 ```
@@
 #q27 through 34 are the writing columns
-noout1$Q30 = as.character(noout1$Q30)
+noout1$Q30 <- as.character(noout1$Q30)
 
@@
 for (i in 1:nrow(noout1)) {
-  noout1$Q30[i] = paste(unlist(
+  noout1$Q30[i] <- paste(unlist(
     text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
@@
 ##create a corpus
-ingroup_corpus = Corpus(VectorSource(noout1$Q30))
-ingroup_TDM = as.matrix(TermDocumentMatrix(ingroup_corpus,
+ingroup_corpus <- Corpus(VectorSource(noout1$Q30))
+ingroup_TDM <- as.matrix(TermDocumentMatrix(ingroup_corpus,
                               control = list(removePunctuation = TRUE,
@@
 ##view the most frequent words
-ingroup_freq = data.frame(Word = rownames(ingroup_TDM),
+ingroup_freq <- data.frame(Word = rownames(ingroup_TDM),
                        Freq = rowSums(ingroup_TDM),
                        row.names = NULL)
-ingroup_freq$Word = as.character(ingroup_freq$Word)
-ingroup_freq$percent = ingroup_freq$Freq/nrow(noout1) *100
-
-write.csv(ingroup_freq, "exp1_ingroup_freq.csv", row.names = F)
+ingroup_freq$Word <- as.character(ingroup_freq$Word)
+ingroup_freq$percent <- ingroup_freq$Freq/nrow(noout1) *100
+
+write.csv(ingroup_freq, "exp3_data/study3.1_ingroup_freq.csv", row.names = F)
 
 ##subset out to only words with 1% mentions
-ingroup_words = ingroup_freq$Word[ingroup_freq$percent >=1]
+ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >=1]
 ##turn sideways to add to dataset
-ingroup_TDM = as.data.frame(t(ingroup_TDM))
-ingroup_TDM = ingroup_TDM[ , ingroup_words]
+ingroup_TDM <- as.data.frame(t(ingroup_TDM))
+ingroup_TDM <- ingroup_TDM[ , ingroup_words]
 
 ##final dataset for ingroup
-ingroup_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
+ingroup_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
                    ingroup_TDM)
 
-ingroup_cor = apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})
-
-ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
-ingroup_words_reduce = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
+ingroup_cor <- apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})
+
+ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
+ingroup_words_reduce <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
 ```
@@
 #q27 through 34 are the writing columns
-noout1$Q32 = as.character(noout1$Q32)
+noout1$Q32 <- as.character(noout1$Q32)
 
@@
 for (i in 1:nrow(noout1)) {
-  noout1$Q32[i] = paste(unlist(
+  noout1$Q32[i] <- paste(unlist(
     text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
@@
 ##create a corpus
-authority_corpus = Corpus(VectorSource(noout1$Q32))
-authority_TDM = as.matrix(TermDocumentMatrix(authority_corpus,
+authority_corpus <- Corpus(VectorSource(noout1$Q32))
+authority_TDM <- as.matrix(TermDocumentMatrix(authority_corpus,
                               control = list(removePunctuation = TRUE,
@@
 ##view the most frequent words
-authority_freq = data.frame(Word = rownames(authority_TDM),
+authority_freq <- data.frame(Word = rownames(authority_TDM),
                        Freq = rowSums(authority_TDM),
                        row.names = NULL)
-authority_freq$Word = as.character(authority_freq$Word)
-authority_freq$percent = authority_freq$Freq/nrow(noout1) *100
-
-write.csv(authority_freq, "exp1_authority_freq.csv", row.names = F)
+authority_freq$Word <- as.character(authority_freq$Word)
+authority_freq$percent <- authority_freq$Freq/nrow(noout1) *100
+
+write.csv(authority_freq, "exp3_data/study3.1_authority_freq.csv", row.names = F)
 
 ##subset out to only words with 1% mentions
-authority_words = authority_freq$Word[authority_freq$percent >=1]
+authority_words <- authority_freq$Word[authority_freq$percent >=1]
 ##turn sideways to add to dataset
-authority_TDM = as.data.frame(t(authority_TDM))
-authority_TDM = authority_TDM[ , authority_words]
+authority_TDM <- as.data.frame(t(authority_TDM))
+authority_TDM <- authority_TDM[ , authority_words]
 
 ##final dataset for authority
-authority_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
+authority_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
                    authority_TDM)
 
-authority_cor = apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})
-
-authoritycut = mean(authority_cor) + 2*sd(authority_cor)
-authority_words_reduce = names(authority_cor[abs(authority_cor) >= authoritycut])
+authority_cor <- apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})
+
+authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
+authority_words_reduce <- names(authority_cor[abs(authority_cor) >= authoritycut])
 ```
@@
 #q27 through 34 are the writing columns
-noout1$Q34 = as.character(noout1$Q34)
+noout1$Q34 <- as.character(noout1$Q34)
 
@@
 for (i in 1:nrow(noout1)) {
-  noout1$Q34[i] = paste(unlist(
+  noout1$Q34[i] <- paste(unlist(
     text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
@@
 ##create a corpus
-purity_corpus = Corpus(VectorSource(noout1$Q34))
-purity_TDM = as.matrix(TermDocumentMatrix(purity_corpus,
+purity_corpus <- Corpus(VectorSource(noout1$Q34))
+purity_TDM <- as.matrix(TermDocumentMatrix(purity_corpus,
                               control = list(removePunctuation = TRUE,
@@
 ##view the most frequent words
-purity_freq = data.frame(Word = rownames(purity_TDM),
+purity_freq <- data.frame(Word = rownames(purity_TDM),
                        Freq = rowSums(purity_TDM),
                        row.names = NULL)
-purity_freq$Word = as.character(purity_freq$Word)
-purity_freq$percent = purity_freq$Freq/nrow(noout1) *100
-
-write.csv(purity_freq, "exp1_purity_freq.csv", row.names = F)
+purity_freq$Word <- as.character(purity_freq$Word)
+purity_freq$percent <- purity_freq$Freq/nrow(noout1) *100
+
+write.csv(purity_freq, "exp3_data/study3.1_purity_freq.csv", row.names = F)
 
 ##subset out to only words with 1% mentions
-purity_words = purity_freq$Word[purity_freq$percent >=1]
+purity_words <- purity_freq$Word[purity_freq$percent >=1]
 ##turn sideways to add to dataset
-purity_TDM = as.data.frame(t(purity_TDM))
-purity_TDM = purity_TDM[ , purity_words]
+purity_TDM <- as.data.frame(t(purity_TDM))
+purity_TDM <- purity_TDM[ , purity_words]
 
 ##final dataset for purity
-purity_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
+purity_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
                    purity_TDM)
 
-purity_cor = apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})
-
-puritycut = mean(purity_cor) + 2*sd(purity_cor)
-purity_words_reduce = names(purity_cor[abs(purity_cor) >= puritycut])
+purity_cor <- apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})
+
+puritycut <- mean(purity_cor) + 2*sd(purity_cor)
+purity_words_reduce <- names(purity_cor[abs(purity_cor) >= puritycut])
 ```
@@
 This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`.
-These concepts were included in the full dictionary used for Experiment 3.
+These concepts were included in the full dictionary used for Study 3.3.
 We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
@@
 ```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
-sample1 = read.csv("fixed_sample 1.csv", stringsAsFactors = F)
-sample2 = read.csv("fixed_sample 2.csv", stringsAsFactors = F)
+sample1 <- read.csv("exp3_data/study3.2_fixed_sample 1.csv", stringsAsFactors = F)
+sample2 <- read.csv("exp3_data/study3.2_fixed_sample 2.csv", stringsAsFactors = F)
 
 ##merge files together
-fullsample = merge(sample1, sample2, all = TRUE)
+fullsample <- merge(sample1, sample2, all = TRUE)
 
@@
 #q24, q25, q26, q7 
-fullsample$writing = apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
+fullsample$writing <- apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
                            1, function(x) toString(na.omit(x)))
@@
 ##clear out completely columns we don't need
-crapcolumns = c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
-finalsample = fullsample[ , -crapcolumns]
+crapcolumns <- c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
+finalsample <- fullsample[ , -crapcolumns]
 
@@
 
-finalsample$Q10 = factor(finalsample$Q10,
+finalsample$Q10 <- factor(finalsample$Q10,
                          levels = 1:2,
                          labels = c("Man", "Woman"))
-finalsample$Q11 = as.numeric(finalsample$Q11)
-finalsample$Q12 = factor(finalsample$Q12,
+finalsample$Q11 <- as.numeric(finalsample$Q11)
+finalsample$Q12 <- factor(finalsample$Q12,
                          levels = 1:7,
@@
 
-gender = table(finalsample$Q10)/sum(table(finalsample$Q10))*100
-race = table(finalsample$Q12)/sum(table(finalsample$Q12))*100
-
-write.csv(finalsample, 'exp2_finalsample.csv', row.names = FALSE)
-newMFD = read.csv('exp2_finalsample_newMFD.csv')
-colnames(newMFD)[1:41] = colnames(finalsample)[1:41]
-newMFD = newMFD[,c(1,42:55)]
-finalsample = merge(finalsample, newMFD, by="ResponseId")
+gender <- table(finalsample$Q10)/sum(table(finalsample$Q10))*100
+race <- table(finalsample$Q12)/sum(table(finalsample$Q12))*100
+
+write.csv(finalsample, 'exp3_data/study3.2_finalsample.csv', row.names = FALSE)
+newMFD <- import('exp3_data/study3.2_finalsample_newMFD.csv')
+colnames(newMFD)[1:41] <- colnames(finalsample)[1:41]
+newMFD <- newMFD[,c(1,42:55)]
+finalsample <- merge(finalsample, newMFD, by = "ResponseId")
 
@@
 
-  finalsample$writing[i] = preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
-  finalsample$wordcount[i] = string.summary(finalsample$writing[i])$words
+  finalsample$writing[i] <- preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
+  finalsample$wordcount[i] <- string.summary(finalsample$writing[i])$words
 
@@
 #remove small words people
-finalwords = subset(finalsample, wordcount >=25)
+finalwords <- subset(finalsample, wordcount >=25)
 
@@
 #missing by row
-missing = apply(finalwords, 1, percentmiss)
+missing <- apply(finalwords, 1, percentmiss)
 table(missing)
-goodrows = subset(finalwords, missing <= 5)
+goodrows <- subset(finalwords, missing <= 5)
 
@@
 ##don't fill in Q10 to the end, be sure to merge these back together
-goodcolumns = goodrows[ , -c(32:42)]
-badcolumns = goodrows[ , c(32:42)]
+goodcolumns <- goodrows[ , -c(32:42)]
+badcolumns <- goodrows[ , c(32:42)]
 
 #fill in missing data points
-library(mice)
+
 tempnomiss = mice(goodcolumns)

### 2023-09-02 manuscript_version/revision/manuscript_metapsych_revision.Rmd
cleaning up this folder

@@
 library(mice)
+library(semPlot)
+library(lavaan)
 
@@
 #fill in missing data points
-
-tempnomiss = mice(goodcolumns)
-nomiss = complete(tempnomiss, 1)
+tempnomiss <- mice(goodcolumns)
+nomiss <- complete(tempnomiss, 1)
 summary(nomiss)
 #merge
-allcolumns = cbind(nomiss, badcolumns) 
+allcolumns <- cbind(nomiss, badcolumns) 
 summary(allcolumns)
@@
 ##outliers
-mahal2 = mahalanobis(allcolumns[ , -c(1,46:56)], 
+mahal2 <- mahalanobis(allcolumns[ , -c(1,46:56)], 
                     colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
@@
 #mahal2
-cutoff2 = qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
+cutoff2 <- qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
 cutoff2
@@
 summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
-noout2 = subset(allcolumns, mahal2 < cutoff2)
+noout2 <- subset(allcolumns, mahal2 < cutoff2)
 
@@
 #correlations
-correlations2 = cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
+correlations2 <- cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
 #correlations2
@@
 #the random stuff
-random2 = rchisq(nrow(noout2), 7)
-fake2 = lm(random2~., data=noout2[ , -c(1,46:56)])
+random2 <- rchisq(nrow(noout2), 7)
+fake2 <- lm(random2~., data=noout2[ , -c(1,46:56)])
 
 #normal
-standardized2 = rstudent(fake2)
+standardized2 <- rstudent(fake2)
 hist(standardized2, breaks=15)
@@
 #homog + s
-fitvalues2 = scale(fake2$fitted.values)
+fitvalues2 <- scale(fake2$fitted.values)
 {plot(fitvalues2, standardized2) 
@@
 ####create the MFQ subscales####
-noout2$harmMFQ = apply(noout2[ , 2:4], 1, sum)
-noout2$fairMFQ = apply(noout2[ , 5:7], 1, sum)
-noout2$ingroupMFQ = apply(noout2[ , 8:10], 1, sum)
-noout2$authorityMFQ = apply(noout2[ , 11:13], 1, sum)
-noout2$purityMFQ = apply(noout2[ , 14:16], 1, sum)
-```
-
-Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes [@Jordan].
+noout2$harmMFQ <- apply(noout2[ , 2:4], 1, sum)
+noout2$fairMFQ <- apply(noout2[ , 5:7], 1, sum)
+noout2$ingroupMFQ <- apply(noout2[ , 8:10], 1, sum)
+noout2$authorityMFQ <- apply(noout2[ , 11:13], 1, sum)
+noout2$purityMFQ <- apply(noout2[ , 14:16], 1, sum)
+```
+
+Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes.
 Participants were recruited via an online research system (SONA) and were given course credit for their participation.
@@
 
-Data was again collected via Qualtrics.
+Data was again collected via Qualtrics (https://osf.io/qr3gv).
 Four fake new stories were presented to participants, which were roughly 400 words each.
@@
 News stories can be found in the online materials.
-Participants also completed the 30-item version of the MFQ as described in the introduction.
-In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.
+Participants also completed the 30-item version of the MFQ as described previously.
+In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Study 3.1.
 
@@
 One missing datapoint was estimated using the *mice* library from *R* [@CITE] for a missing MFQ question, and all other missing data was present in the demographics sections, which were not filled in.
-The MFQ data were screened for outliers using Mahalanobis distance, and fourteen outliers were found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) = `r printnum(cutoff2)`.
+The MFQ data were screened for outliers using Mahalanobis distance, and 25 outliers were found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) = `r printnum(cutoff2)`.
 These data were excluded leading to a final sample size of `r nrow(noout2)`.
-Data were screened for assumptions described in Experiment 1 and were found to be satisfactory.
+Data were screened for assumptions described in Study 3.1 and were found to be satisfactory.
 
@@
 for (i in 1:nrow(noout2)) {
-  noout2$writing2[i] = paste(unlist(
+  noout2$writing2[i] <- paste(unlist(
     text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
@@
 ##create a corpus
-overall_corpus = Corpus(VectorSource(noout2$writing2))
-overall_TDM = as.matrix(TermDocumentMatrix(overall_corpus,
+overall_corpus <- Corpus(VectorSource(noout2$writing2))
+overall_TDM <- as.matrix(TermDocumentMatrix(overall_corpus,
                               control = list(removePunctuation = TRUE,
@@
 ##view the most frequent words
-overall_freq = data.frame(Word = rownames(overall_TDM),
+overall_freq <- data.frame(Word = rownames(overall_TDM),
                           Freq = rowSums(overall_TDM),
                           row.names = NULL)
-overall_freq$Word = as.character(overall_freq$Word)
-overall_freq$percent = overall_freq$Freq/nrow(noout2)*100
-
-write.csv(overall_freq, "exp2_freq.csv", row.names = F)
+overall_freq$Word <- as.character(overall_freq$Word)
+overall_freq$percent <- overall_freq$Freq/nrow(noout2)*100
+
+write.csv(overall_freq, "exp3_data/study3.2_freq.csv", row.names = F)
 
@@
 ##a few times by participants
-all_words = overall_freq$Word[overall_freq$percent >=1]
+all_words <- overall_freq$Word[overall_freq$percent >=1]
 
 ##turn sideways to add to dataset
-overall_TDM = as.data.frame(t(overall_TDM))
-overall_TDM = overall_TDM[ , all_words]
+overall_TDM <- as.data.frame(t(overall_TDM))
+overall_TDM <- overall_TDM[ , all_words]
 
 ##final dataset
-overall_final = cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
+overall_final <- cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
                                   "authorityMFQ", "purityMFQ","ingroupMFQ")],
@@
 ##harm
-harm_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})
-
-harmcut = mean(harm_cor) + 2*sd(harm_cor)
-harm_words_reduce_exp2 = names(harm_cor[abs(harm_cor) >= harmcut])
+harm_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})
+
+harmcut <- mean(harm_cor) + 2*sd(harm_cor)
+harm_words_reduce_exp2 <- names(harm_cor[abs(harm_cor) >= harmcut])
 
 ##fair
-fair_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})
-
-faircut = mean(fair_cor) + 2*sd(fair_cor)
-fair_words_reduce_exp2 = names(fair_cor[abs(fair_cor) >= faircut])
+fair_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})
+
+faircut <- mean(fair_cor) + 2*sd(fair_cor)
+fair_words_reduce_exp2 <- names(fair_cor[abs(fair_cor) >= faircut])
 
 ##purity
-purity_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})
-
-puritycut = mean(purity_cor) + 2*sd(purity_cor)
-purity_words_reduce_exp2 = names(purity_cor[abs(purity_cor) >= puritycut])
+purity_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})
+
+puritycut <- mean(purity_cor) + 2*sd(purity_cor)
+purity_words_reduce_exp2 <- names(purity_cor[abs(purity_cor) >= puritycut])
 
 ##authority
-authority_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})
-
-authoritycut = mean(authority_cor) + 2*sd(authority_cor)
-authority_words_reduce_exp2 = names(authority_cor[abs(authority_cor) >= authoritycut])
+authority_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})
+
+authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
+authority_words_reduce_exp2 <- names(authority_cor[abs(authority_cor) >= authoritycut])
 
 ##ingroup
-ingroup_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})
-
-ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
-ingroup_words_reduce_exp2 = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
+ingroup_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})
+
+ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
+ingroup_words_reduce_exp2 <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
 
 ##print out words list to look at for further analysis
-#write.csv(harm_words_reduce_exp2, "words/harm_exp2.csv", row.names = F)
-#write.csv(fair_words_reduce_exp2, "words/fair_exp2.csv", row.names = F)
-#write.csv(authority_words_reduce_exp2, "words/authority_exp2.csv", row.names = F)
-#write.csv(purity_words_reduce_exp2, "words/purity_exp2.csv", row.names = F)
-#write.csv(ingroup_words_reduce_exp2, "words/ingroup_exp2.csv", row.names = F)
+#write.csv(harm_words_reduce_exp2, "exp3_data/words/harm_exp2.csv", row.names = F)
+#write.csv(fair_words_reduce_exp2, "exp3_data/words/fair_exp2.csv", row.names = F)
+#write.csv(authority_words_reduce_exp2, "exp3_data/words/authority_exp2.csv", row.names = F)
+#write.csv(purity_words_reduce_exp2, "exp3_data/words/purity_exp2.csv", row.names = F)
+#write.csv(ingroup_words_reduce_exp2, "exp3_data/words/ingroup_exp2.csv", row.names = F)
 ```
@@
 Therefore, we expected many of the words listed to be part of creating a cohesive discourse, rather than only related to the moral foundation targeted.
-To find only the most related words, the correlation between word frequency and moral foundation was calculated and words with correlations greater than two standard deviations outside the mean were selected for the dictionary analysis in Experiment 3.
+To find only the most related words, the correlation between word frequency and moral foundation was calculated and words with correlations greater than two standard deviations outside the mean were selected for the dictionary analysis in Study 3.3.
 The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
@@
 ```{r compare-ratings-3.2, include = FALSE}
-authority_erin = read.csv("words/authority_exp2 erin.csv", stringsAsFactors = F)
-authority_will = read.csv("words/authority_exp2 will.csv", stringsAsFactors = F)
+authority_erin <- read.csv("exp3_data/words/authority_study3.2 erin.csv", stringsAsFactors = F)
+authority_will <- read.csv("exp3_data/words/authority_study3.2 will.csv", stringsAsFactors = F)
 authority_erin$x[authority_erin$use != authority_will$use]
 
-authority_words_reduce_exp2 = authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]
-
-fair_erin = read.csv("words/fair_exp2 erin.csv", stringsAsFactors = F)
-fair_will = read.csv("words/fair_exp2 will.csv", stringsAsFactors = F)
+authority_words_reduce_exp2 <- authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]
+
+fair_erin <- read.csv("exp3_data/words/fair_study3.2 erin.csv", stringsAsFactors = F)
+fair_will <- read.csv("exp3_data/words/fair_study3.2 will.csv", stringsAsFactors = F)
 fair_erin$x[fair_erin$use != fair_will$use]
-fair_will$use[fair_will$x == "carbon"] = 0
-fair_will$use[fair_will$x == "emiss"] = 0
+fair_will$use[fair_will$x == "carbon"] <- 0
+fair_will$use[fair_will$x == "emiss"] <- 0
 #exclude carbon and emiss due to the prompt
 
-fair_words_reduce_exp2 = fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]
-
-purity_erin = read.csv("words/purity_exp2 erin.csv", stringsAsFactors = F)
-purity_will = read.csv("words/purity_exp2 will.csv", stringsAsFactors = F)
+fair_words_reduce_exp2 <- fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]
+
+purity_erin <- read.csv("exp3_data/words/purity_study3.2 erin.csv", stringsAsFactors = F)
+purity_will <- read.csv("exp3_data/words/purity_study3.2 will.csv", stringsAsFactors = F)
 purity_erin$x[purity_erin$use != purity_will$use]
-purity_will$use[purity_will$x == "befor"] = 1
+purity_will$use[purity_will$x == "befor"] <- 1
 #before include because of "before sex/ruined/etc."
@@
 
-ingroup_erin = read.csv("words/ingroup_exp2 erin.csv", stringsAsFactors = F)
-ingroup_will = read.csv("words/ingroup_exp2 will.csv", stringsAsFactors = F)
+ingroup_erin <- read.csv("exp3_data/words/ingroup_study3.2 erin.csv", stringsAsFactors = F)
+ingroup_will <- read.csv("exp3_data/words/ingroup_study3.2 will.csv", stringsAsFactors = F)
 ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
-ingroup_will$use[ingroup_will$x == "mean"] = 1
+ingroup_will$use[ingroup_will$x == "mean"] <- 1
 #mean should be included
 
-ingroup_words_reduce_exp2 = ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]
-
-harm_erin = read.csv("words/harm_exp2 erin.csv", stringsAsFactors = F)
-harm_will = read.csv("words/harm_exp2 will.csv", stringsAsFactors = F)
+ingroup_words_reduce_exp2 <- ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]
+
+harm_erin <- read.csv("exp3_data/words/harm_study3.2 erin.csv", stringsAsFactors = F)
+harm_will <- read.csv("exp3_data/words/harm_study3.2 will.csv", stringsAsFactors = F)
 harm_erin$x[harm_erin$use != harm_will$use]
-harm_will$use[harm_will$x == "import"] = 1
+harm_will$use[harm_will$x == "import"] <- 1
 #import for important
@@
 ##original mfd words
-original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
+original_mfd <- read.csv("exp3_data/original_mfd.csv", stringsAsFactors = F)
 
@@
 #harm/care
-original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
+original_mfd[c(27:95),1] <- c("abusive","abuser","abused","abusing",
                              "sympathetic","sympathies","damaged",
@@
 #fairness/reciprocity
-original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
+original_mfd[c(20:64),2] <- c("balances", "balanced", "balancing","biased",
                              "biases", "discriminates", "discriminated",
@@
 #ingroup/loyalty
-original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
+original_mfd[c(16:47),3] <- c("collects", "collected", "collecting", "collective",
                              "communities", "deceives", "deceived", "deceiving",
@@
 #authority/respect
-original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
+original_mfd[c(31:112),4] <- c("abides", "abided", "abiding", "authorities",
                               "classes", "classed", "classing", "command",
@@
 #purity/sanctity
-original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
+original_mfd[c(21:60),5] <- c("abstains", "abstained", "abstaining", "abstinence",
                              "adulteries", "adulterous", "adulterer", "adulterers",
@@
 for(i in 1:nrow(original_mfd)) {
-  original_mfd$h2[i] = stemDocument(original_mfd$h2[i], language = "english")
-  original_mfd$f2[i] = stemDocument(original_mfd$f2[i], language = "english")
-  original_mfd$i2[i] = stemDocument(original_mfd$i2[i], language = "english")
-  original_mfd$a2[i] = stemDocument(original_mfd$a2[i], language = "english")
-  original_mfd$p2[i] = stemDocument(original_mfd$p2[i], language = "english")
-}
-
-mtmmdata = noout2[ , c(1:31, 42) ]
+  original_mfd$h2[i] <- stemDocument(original_mfd$h2[i], language = "english")
+  original_mfd$f2[i] <- stemDocument(original_mfd$f2[i], language = "english")
+  original_mfd$i2[i] <- stemDocument(original_mfd$i2[i], language = "english")
+  original_mfd$a2[i] <- stemDocument(original_mfd$a2[i], language = "english")
+  original_mfd$p2[i] <- stemDocument(original_mfd$p2[i], language = "english")
+}
+
+mtmmdata <- noout2[ , c(1:31, 45) ]
 
@@
   ##figure out the sum for just the original mfd
-  mtmmdata$harm_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])
-
-  mtmmdata$purity_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])
-
-  mtmmdata$fair_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])
-
-  mtmmdata$authority_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])
-
-  mtmmdata$ingroup_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])
+  mtmmdata$harm_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])
+
+  mtmmdata$purity_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])
+
+  mtmmdata$fair_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])
+
+  mtmmdata$authority_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])
+
+  mtmmdata$ingroup_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])
 
   ##figure out the sum for all words ever 
-  mtmmdata$harm_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])
-
-  mtmmdata$purity_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])
-
-  mtmmdata$fair_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])
-
-  mtmmdata$authority_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])
-
-  mtmmdata$ingroup_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])
+  mtmmdata$harm_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])
+
+  mtmmdata$purity_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])
+
+  mtmmdata$fair_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])
+
+  mtmmdata$authority_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])
+
+  mtmmdata$ingroup_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])
 
   ##figure out the sum for reduced words
-  mtmmdata$harm_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])
-
-  mtmmdata$purity_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])
-
-  mtmmdata$fair_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])
-
-  mtmmdata$authority_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])
-
-  mtmmdata$ingroup_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])
+  mtmmdata$harm_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])
+
+  mtmmdata$purity_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])
+
+  mtmmdata$fair_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])
+
+  mtmmdata$authority_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])
+
+  mtmmdata$ingroup_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])
 
@@
 #create percents instead of frequencies
-mtmmdata[ , c(33:47)] = mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100
-
+mtmmdata[ , c(33:47)] <- mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100 
 summary(mtmmdata[ , 33:47])
-
 ```
@@
 
-##now run some MTMM!
-library(semPlot)
-library(lavaan)
-
 ####mtmm original dictionary####
 
-{model1 = '
+{model1 <- '
 harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
@@
 
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
+model1.fit <- cfa(model1, data=mtmmdata, std.lv=TRUE)
 summary(model1.fit, rsquare=TRUE, standardized=TRUE)
@@
 
-{model1.2 = '
+{model1.2 <- '
 harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
@@
 
-model1.2.fit = cfa(model1.2, data=mtmmdata, std.lv=TRUE)
+model1.2.fit <- cfa(model1.2, data=mtmmdata, std.lv=TRUE)
 summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
@@
 
-{model2 ='
+{model2 <- '
 mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
@@
 
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
+model2.fit <- cfa(model2, data=mtmmdata, std.lv=TRUE)
 summary(model2.fit, rsquare=TRUE, standardized=TRUE)
@@
 
-{model3 = '
+{model3 <- '
 harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
@@
 
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
+model3.fit <- cfa(model3, data=mtmmdata, std.lv=TRUE)
 summary(model3.fit, rsquare=TRUE, standardized=TRUE)
@@
 
-{model4 = '
+{model4 <- '
 harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
@@
 
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
+model4.fit <- cfa(model4, data=mtmmdata, std.lv=TRUE)
 summary(model4.fit, rsquare=TRUE, standardized=TRUE)

### 2024-01-30 manuscript_version/revision/manuscript_metapsych_revision.Rmd
updating to study 1

@@
 The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
-Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+In Study 1, we explore the MFD-Moral Foundations Questionnaire's measurement overlap using a multi-trait multi-method model.
+These latent trait models were used to inform possible improvement of the MFD.
+Next, we examined two replication extensions of previous work exploring the differences in political articles on moral differences Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
@@
 
-bibliography      : ["./metapsych_bib.bib"] #turn this off right now so it knits
+bibliography      : ["./metapsych_bib.bib"] # add new references
 
@@
 output            : papaja::apa6_pdf
+bibliography: references.bib # delete this 
 ---
@@
 options(tinytex.verbose = TRUE)
-percentmiss <- function(x){sum(is.na(x))/length(x)*100}
-```
-
-The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].
-Since then, Kohlberg's theory has been highly criticized with numerous theories and hypotheses proposed to replace it.
-One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham [@Haidt2007].
-While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related measurement issue, the Moral Foundations Dictionary (MFD) [@Graham2009].
-@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
-Here we first review evidence and criticisms against this assumption.
-We then provide our own test of the MFD using partisan news articles.
-
-## Moral Foundations Dictionary
-
-Haidt and Jesse (2007) formulated MFT as a method by which to capture the entirety of humans' moral domain.
-We argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals.
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-MFT holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
-
-In order to capture language's role in moral and political reasoning, @Graham2009 formulated the MFD in order to capture moral reasoning and justification as used in speech and text.
-The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-@Graham2009 created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from we' initial list.
-
-Similar to previous research on MFT, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
-Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers.
-However, conservative ministers did not use *ingroup/loyalty* words more than liberals.
-Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].
+percentmiss <- function(x){ sum(is.na(x)) / length(x) * 100 }
+```
+
+The field of moral psychology has a long history with modern moral
+psychology beginning in the late 1960s with Lawrence Kohlberg's theory
+of moral development [@Kohlberg1977]. Since then, Kohlberg's theory has
+been highly criticized with numerous theories and hypotheses proposed to
+replace it. One of these theories is Moral Foundations Theory (MFT)
+proposed by Haidt and colleagues [@haidt2004; @Haidt2007]. While the
+theory itself has been widely criticized and debated, the goal of the
+current work is to tackle a related measurement issue, the Moral
+Foundations Dictionary [MFD, @Graham2009]. @Graham2009 developed the
+MFD - a lexicon-based linguistic measure of MFT - arguing that moral
+concerns and the propositions of MFT could be measured and tested with
+the words people use. Here we first review evidence and criticisms
+against this assumption. We then provide our own test of the MFD using
+partisan news articles.
+
+## Moral Foundations Measurement
+
+Haidt and Joseph [-\@haidt2004] and Haidt and Graham [-@Haidt2007]
+formulated MFT as a method by which to capture the entirety of humans'
+moral domain. They argued that older theories of moral psychology were
+focused primarily on issues of justice, fairness, and caring, which are
+individually focused foundations of morality that align with the beliefs
+of political liberals. In other words, moral psychology ignored the
+valid moral foundations of conservatives. MFT holds that people's moral
+domain can be mapped by quantifying their endorsement of five moral
+foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*,
+*authority/respect*, and *purity/sanctity* [@Haidt2007]. Thus, they
+proposed that the addition of these two additional domains could
+adequately capture the broader spectrum of morality.
+
+Measurement of MFT has traditionally focused on two options: 1) the
+Moral Foundations Questionnaire (MFQ) - a typical Likert-type survey
+instrument that measures moral relevance of each foundation to an
+individual and the moral judgment of various scenarios depicting each
+foundation, and 2) the Moral Foundations Dictionary (MFD) which was
+designed to capture language's role in moral reasoning and justification
+as used in speech and text [@Graham2009; @graham2011]. The MFQ is a
+30-item scale with 15 items on the moral relevance and judgment
+scenarios. The 15 moral relevance items are equally divided among the
+five foundations and examine how relevant a condition is to making a
+moral judgment on a scale of 1 (*not at all relevant*) to 6 (*extremely
+relevant*). These relevance items include examples such as: "Whether or
+not someone used violence (*harm*)," "Whether or not someone was denied
+his or her rights (*fairness*)," "Whether or not someone showed a lack
+of loyalty (*ingroup*)," "Whether or not an action caused chaos or
+disorder (*authority*)," and "Whether or not someone did something
+disgusting (*purity*)." The moral judgments items are also equally
+divided between the foundations and ask on a six-point scale how much
+one agrees with each of the statements. These judgment items include:
+"One of the worst things a person can do is hurt a defenseless animal
+(*harm*)," "Justice is the most important requirement of a society
+(*fairness*)," "I am proud of my country's history (*ingroup*)," "Men
+and women each have different roles to play in society (*authority*),"
+and "Chastity is an important and valuable virtue (*purity*)."
+
+The internal consistency of the MFQ from @Graham2011 was $\alpha$ = .73
+averaged across subscales with a range of $\alpha$ = .65-.84. Across six
+studies, the MFQ was found to have an average Cronbach's alpha of .63
+for *harm*, .64 for *fairness*, .56 for *ingroup*, .59 for *authority*,
+and .71 for *purity* [@Federico2013; @Graham2009; @Graham2012;
+@Weber2013]. Test-retest reliability was *r* = .68-.82 using a sample of
+123 college students. Confirmatory factor analysis supported a
+well-fitted five-factor model (*harm/care*, *fairness/reciprocity*,
+*ingroup/loyalty*, *authority/respect*, and *purity/sanctity*) over two,
+individual (*harm* and *fairness*) versus group (*ingroup*, *authority*,
+and *purity*) foundations, or three, autonomy (*harm*, *fairness*),
+community (*ingroup*, *authority*), and divinity (*purity*) ethics,
+foundations factor model. The five-factor structure also fit for
+non-Western samples, thus, providing evidence of the MFQ
+generalizability. Convergent validity was supported with correlations on
+other measures of morality [@Schwartz; @Graham2011].
+
+The MFD is composed of 259 words, with around 50 words assigned to each
+of the five foundations. @Graham2009 created a preliminary list of words
+that they believed would be associated with the five foundations. Words
+such as *war* and *peace* should indicate a greater concern with *harm*
+foundation whereas words such as *homeland* and *terrorism* should
+indicate a greater concern with the *ingroup* foundation. The other
+foundation dictionaries include *equal* and *justice* (*fairness*),
+*honor* and *protest* (*authority*), and *holy* and *sin* (*purity*). To
+validate the word sets, @Graham2009 examined the frequency of MFD words
+in liberal and conservative sermons using the Linguistic Inquiry and
+Word Count [LIWC; @Pennebaker2007] computer program. They found liberal
+ministers used *harm*, *fairness*, and *ingroup* words more often than
+conservative ministers who used *authority* and *purity* words more
+often. Although conservative ministers were expected to use more
+*ingroup* words based on political ideology and previous research, an
+examination of the way liberal ministers used *ingroup* words revealed a
+tendency for the use of *ingroup* words to glorify rebellion and promote
+independence (i.e., the opposite direction from *ingroup* definitions).
+Effect sizes indicated relatively sizable difference between liberal and
+conservative sermons with Cohen's *d* values ranging from 0.56 to 1.27.
+
+In contrast to this approach, @Sagi2013 explored how moral words were
+used paired with other co-occurring concepts using Latent Semantic
+Analysis (LSA). They examined three different moral issues in different
+contexts to piece out specific moral words and their collocates. First,
+they looked at how moral words were used in relation to the World Trade
+Center compared to the Empire State Building in the New York Times from
+1987-2007. After 9-11, the number of moral words associated with the
+World Trade Center increased, specifically *harm* words from the MFD.
+Second, they considered the changes in how moral words were paired with
+mosque used in blogs as a response to the debate of building a mosque
+near Ground Zero following 9-11. They found words from the MFD were used
+more often with mosque during the main debate and then the co-occurrence
+decreased afterwards. Lastly, they examined moral language tied to the
+abortion debate in Congress. Republicans used more moral language
+overall; more specifically, Republicans tended to use more words
+associated with the *purity* foundation; while Democrats used more words
+associated with the *fairness* foundation.
 
@@
 
-MFT has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-@Suhler2011 criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-Likewise, @Gray2015 argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
-@Schein2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
-
-Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.
-Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S.
-Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.
-In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
-Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
-Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores.
-Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects.
-Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
-Exploring the political Twitterverse, @Sterling2018 found differences in the MFD depend on political sophistication.
-For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
-While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
-Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.
-
-The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).
-These attempts generally fall into two categories: human annotations and semantic representations.
-@Hopp2021 represents the first approach where instead of relying on 'experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
-While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
-@Garten2016 represents the second categories which instead relies on data-driven semantic analysis.
-Using shallow neural net models like word2vec [@mikolov_efficient_2013], moral foundations were measured using semantic similarity vectors rather than simple word counts.
-
-As a further conceptual replication of @Frimer2020, we test the liberal-conservative difference proposed by MFT using partisan media content and the MFD.
-We first test differences in a general news corpus compared liberal sources (National Public Radio [NPR] and the New York Times [NYT]) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavanaugh's U.S.
-Supreme Court nomination and the U.S.
-Government Shutdown in 2018-2019.
-In the second study, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
-To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Like @Frimer2020, results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.
+MFT has received criticism on the grounds that its assumptions regarding
+moral intuitions have little empirical basis. @Suhler2011 criticized the
+content and taxonomy of the five foundations and question whether or not
+the foundations are sufficiently distinct as to stand as their own
+foundation. Likewise, @Gray2015 argues that the measurement of the moral
+foundations confounds morality with other constructs (such as weirdness)
+and the moral foundations lack statistical and conceptual distinction.
+@Schein2015 argues that harm-based morality is the most parsimonious and
+logical explanation for MFT findings.
+
+Beyond the critiques of the theory itself, many have also provided
+strong critiques of the measurement using MFD. Conducting two close
+conceptual replication studies using religious sermons and six extension
+studies using U.S. Congressional speeches, party platforms, State of the
+Union addresses, media outlets, and political organization texts,
+@Frimer2020 found that the liberal-conservative differences found in the
+original study replicated in only 30% of cases and the effect sizes were
+over 30 times smaller than reported in @Graham2009. In a meta-analysis,
+the theorized differences were only found for authority and purity
+(e.g., conservatives used more authority and purity words). Loyalty was
+contrary to theoretical predictions (e.g., used more by liberals), and
+no differences were found for harm and fairness. Additionally,
+@Frimer2020 tested the theory under the most forgiving conditions using
+not only the original MFD but also the revised MFD2 as well using log
+transformed scores and raw scores. Even under the best circumstances
+(log transformed MFD2 scores), only two of the foundations showed
+theorized differences but with very small effects. Other studies have
+also found conflicting findings which fail to support the basic
+assertions of MFT. Exploring the political Twitterverse, @Sterling2018
+found differences in the MFD depend on political sophistication. For
+example, harm words were used more by liberals only if they had low
+levels of political sophistication; at high levels of political
+sophistication, conservatives used more harm words. While the MFD has
+not been extensively used (at least in published research), studies
+which have use the MFD to test partisan differences have found mixed
+results in terms of supporting MFT [@Clifford2013; @Frimer2015;
+@Sagi2014]. Like @Frimer2020, we attempt to give the MFD the best chance
+for success by incorporating a weighting method to address the
+skewedness and sparsity of the linguistic data.
+
+The most successful attempts to validate a linguistic measure of moral
+foundations have used more complex methods (compared to the original
+dictionary-based approach). These attempts generally fall into two
+categories: human annotations and semantic representations. @Hopp2021
+represents the first approach where instead of relying on 'experts', a
+large sample of lay people were crowdsourced to manually annotate
+document for content relevant to each foundation. While
+resource-intensive, this method better captures how people may encounter
+and judge moral issues in everyday life leading to a more ecologically
+valid dictionary. @Garten2016 represents the second categories which
+instead relies on data-driven semantic analysis. Using shallow neural
+net models like word2vec [@mikolov_efficient_2013], moral foundations
+were measured using semantic similarity vectors rather than simple word
+counts. Here, we try to augment the simpler approach to add more context
+to see if the MFD liberal-conservative differences can be replicated.
+
+First, we use the MFQ and MFD in a multi-trait multi-method approach to
+determine if the dictionary can be improved and mapped into the
+theoretical MFT traits. This study examined the measurement overlap
+between these two sources, as well as the latent traits after
+controlling for the overlap. Using the results from this study, we
+examined two conceptual replications of @Frimer2020. We test the
+liberal-conservative difference proposed by MFT using partisan media
+content and the MFD. We first test differences in a general news corpus
+compared liberal sources (National Public Radio [NPR] and the New York
+Times [NYT]) to conservative sources (Fox News and Breitbart). Second,
+we examined news about specific political events: Brett Kavanaugh's U.S.
+Supreme Court nomination and the U.S. Government Shutdown in 2018-2019.
+In the second study, the news sources were expanded to cover NYT, NPR,
+Slate, Huffington Post, and Politico on the liberal side and Fox News,
+Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the
+conservative side. To address potential issues of measurement with the
+MFD, the MFD was combined with the information produced in Study 1 and
+weighted by valence to create weighted percentages to better specify
+endorsement. Like @Frimer2020, results were judged based on the
+direction of the liberal-conservative difference compared MFT
+predictions and the size of the effect compared to past studies.
 
@@
 
-For the first study, we approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
-We hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
-Additionally, we hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
+We approached this study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to
+solidify the best method by which to analyze political news text under
+the MFT framework while also alleviating some of the aforementioned
+potential dictionary issues with the MFD. In this set of studies, we
+examined the MFD and MFQ within the same study. The first two
+sub-studies were used to develop a (potentially) larger dictionary for
+the MFD and collect data on both scales. The original dictionary was
+developed conceptually, identifying words that *should* go with each
+moral trait. In Study 1.1 and 1.2, we collect data to expand the
+dictionary. The last sub-study examined the MFD and MFQ using
+multi-trait multi-method (MTMM) analysis using guidelines from
+@byrne2001 and @widaman1985.
+
+MTMM analyses use latent variable modeling to represent the underlying
+structure of a proposed phenomenon, while also accounting for the
+measurement of that phenomenon. As shown in Figure \@ref(fig:fig-mtmm),
+MTMM models are programmed to represent the traits that are measured
+(left hand side circles) and the methods used to measure those traits
+(right hand side circles). The squares in the middle represent the
+actual observed data, which is the MFQ questions and MFD scores. In the
+first model, *correlated traits correlated methods*, the latent
+variables are allowed to correlate on the traits and methods side, but
+not cross correlate from traits to methods. All models are then compared
+to this model to examine fit, convergent, and divergent validity. In the
+second model, *no traits correlated methods*, the trait side of the
+model is deleted and only methods are considered. The model should
+significantly degrade in fit, as the traits should be useful in
+explaining model variance for convergent validity (i.e., you do not want
+a model that suggests all the variances is due to measurement).
+
+In the third model, *perfectly correlated traits freely correlated
+methods*, the traits are added back to the model, but each correlation
+is set to one. The fit is compared to model 1, indicating if divergent
+validity of the traits has occurred. A significant degrade in fit should
+be found to indicate that trait correlations are not perfect. Last,
+model four *correlated traits uncorrelated methods*, the traits are
+allowed to naturally correlate but the methods correlations are set to
+zero. In comparison with model 1, the model should be roughly equal for
+divergent validity. This result would indicate that the methods each
+represent a different component to the measurement of the model, and do
+not represent the same measurement twice.
+
+Given the goal of improved measurement, we compared model 1 of the MTMM
+steps across several dictionaries to determine the best measurement for
+the dictionary. To assess model fit, we used the Root Mean Squared Error
+of Approximation [RMSEA, @steiger1990], the Root Mean Squared Residual
+[RMSR, @jöreskog1971], the Confirmatory Fit Index [CFI, @bentler1990],
+the Tucker-Lewis Index [TLI, @bentler1980]. The RMSEA and RMSR should be
+low for adequate model fit (\< .10) and the CFI and TLI should be high
+for adequate model fit (\> .90). For model comparison, we used a
+$\Delta$ CFI of greater than .01 to indicate a significant degradation
+in fit [@hu1999]. We will additionally use the standardized loadings for
+each of the traits to determine which model has the best measurement of
+moral foundations (\> .30 desired).
+
+For clarity, we programmed the following models:
+
+1.  Model 1 *Correlated Traits Correlated Methods*
+    a.  Original MFD Words
+    b.  Original MFD Words + Study 1.1 + Study 1.2 Words
+    c.  Original MFD Words + Study 1.1 Reduced + Study 1.2 Words
+    d.  Determine if model suggests a feasible structure (fit indices
+        adequate + loadings adequate)
+    e.  Pick the best model to continue (using model comparison)
+2.  Model 2 *No Traits Correlated Methods*
+3.  Model 3 *Perfectly Correlated Traits Correlated Methods*
+4.  Model 4 *Correlated Traits Uncorrelated Methods*
+
+```{r fig-mtmm, fig.cap="Representation of the multi-trait multi-method model for the MFD and MFQ.
+Not all measured variables (squares) are shown for ease of reading.
+The left hand side represents the traits or foundation areas of MFT, while the right hand side represents the two measurement tools for the MFT.
+"}
+knitr::include_graphics("mtmm_mfd.png")
+```
+
+## Study 1.1
+
+In this study, participants were given a word association task elicit
+additional semantically related word forms for each moral foundation.
+This data was used to expand the MFD for each latent area to determine
+if these additional words could improve scores and test measurement
+relation to the MFQ in Study 1.3.
+
+### Participants
+
+```{r demos-mtmm-study-3.1, include = FALSE}
+exp1data <- import("../../study1_data/study1.1_fixed_associations.csv")
+
+# clear out completely columns we don't need
+crapcolumns <- c(1, 2, 3, 5:14)
+study1.1DF <- exp1data[ , -crapcolumns]
+
+# accuracy
+summary(study1.1DF) #Check Q15_1 and Q23 for in-range scores -WP
+study1.1DF$Q23 <- factor(study1.1DF$Q23,
+                         levels = 1:3,
+                         labels = c("Democrat", "Republican", "Independent"))
+
+# missing data 
+missing <- apply(study1.1DF, 1, percentmiss)
+table(missing)
+# a few missing here and there
+# do not want to replace entire MFQ, other missing is political orientation
+# no replacement
+
+# outliers on MFQ only 
+mahal1 <- mahalanobis(study1.1DF[ , -c(1:6,22,23)], 
+                    colMeans(study1.1DF[ , -c(1:6,22,23)], na.rm = TRUE),
+                    cov(study1.1DF[ , -c(1:6,22,23)], use="pairwise.complete.obs"))
+#mahal1
+cutoff1 <- qchisq(1 - .001, ncol(study1.1DF[ , -c(1:6,22,23)]))
+df1 <- ncol(study1.1DF[ , -c(1:6,22,23)])
+summary1 <- summary(mahal1 < cutoff1) # nas will be excluded because they don't have the full scale 
+noout1.1 <- subset(study1.1DF, mahal1 < cutoff1)
+
+# assumptions
+# correlations for MFQ
+correlations1 <- cor(noout1.1[,-c(1:6,22,23)], use="pairwise.complete.obs")
+correlations1
+symnum(correlations1)
+
+# making the random stuff
+random1 <- rchisq(nrow(noout1.1), 7)
+fake1 <- lm(random1 ~ ., data = noout1.1[ , -c(1:6, 22, 23)])
+# normal
+standardized1 <- rstudent(fake1)
+hist(standardized1, breaks=15) # some skew
+
+# linear
+{qqnorm(standardized1) 
+abline(0,1)}
+# fairly linear
+
+# homog + s
+fitvalues1 <- scale(fake1$fitted.values)
+{plot(fitvalues1, standardized1) 
+abline(0,0)
+abline(v = 0)}
+# actually pretty good minus that one outlier
+
+# create subscales 
+noout1.1$harmMFQ <- apply(noout1.1[ , 7:9], 1, sum)
+noout1.1$fairMFQ <- apply(noout1.1[ , 10:12], 1, sum)
+noout1.1$ingroupMFQ <- apply(noout1.1[ , 13:15], 1, sum)
+noout1.1$authorityMFQ <- apply(noout1.1[ , 16:18], 1, sum)
+noout1.1$purityMFQ <- apply(noout1.1[ , 19:21], 1, sum)
+
+party <- table(noout1.1$Q23, useNA = "ifany")
+```
+
+`r nrow(exp1data)` participants were assessed from a large Midwestern
+university. Participants were given course credit for their introductory
+psychology course for completing the study. `r unname(summary1[4])`
+participants had missing data on the MFQ and were excluded from
+analyses. The MFQ data was screened for multivariate outliers with
+Mahalanobis distance as described in @Tabachnick2012, and
+`r unname(summary1[2])` outliers were found using
+$\chi^2_{p < .001}$(`r df1`) = `r apa_num(cutoff1)`. These participants
+were excluded from further analyses, representing `r nrow(noout1.1)`
+final participants. Participants were asked to denote their political
+party, and `r printnum(party["Democrat"]/sum(party)*100,digits = 1)`%
+indicated they were Democrats,
+`r printnum(party["Republican"]/sum(party)*100,digits = 1)`% were
+Republican, and
+`r printnum(party["Independent"]/sum(party)*100,digits = 1)`% indicated
+they were Independent. `r printnum(party[4]/sum(party)*100,digits = 1)`%
+of values were missing for this question.
+
+### Materials and Procedure
+
+A complete example of the survey can be found online at
+<https://osf.io/5uqfn>. First, participants were given a description of
+associative memory as the relation between words that comes about
+through many pairings in writing and speech. Next, the free association
+task, similar to that used in @nelson2004 and @dedeyne2019 was described
+to the participants as listing the "first word that pops into mind". The
+participants were then given three example free association cues,
+*lost*, *old*, and *article*. For each cue, participants were asked to
+write all the words that come to mind. To elicit free association to the
+moral foundation areas, participants were given the following
+instructions:
+
+"Moral Foundations Theory states that when making moral
+judgments/decisions, the concerns people have can be divided into five
+categories. Below are labels of each of these five categories. You will
+then be asked to list words you think are associated with each of the
+labels."
+
+Each of the foundation pairs were listed together (i.e., *harm/care*,
+*fairness/reciprocity,* etc.) with a space for participants to list
+their free association concepts. After the free association task,
+participants were then given the 15-items from the moral relevance
+section of the MFQ as described in the introduction. Last, participants
+were asked to denote their political orientation from 1 *conservative*
+to 10 *liberal*, as well as which political party they associated with:
+Democrat, Republican, and Independent. The survey was delivered through
+Qualtrics, and participants were recruited through the online
+participant management system for the university (SONA). Each
+participant signed an online consent form at the beginning of the study
+and was given participation credit at the end of the study.
+
+### Results
+
+All data was screening for inaccurate responses, as well as missing
+data, as described in the participant section. The final MFQ data was
+screened for assumptions of normality, linearity, and homoscedasticity.
+The MFQ data was slightly skewed but otherwise linear and homoscedastic
+after accounting for skew. No transform was applied. The sum of each
+moral foundation area was calculated in order to determine which words
+were linked to their respective moral foundation. The average scores
+were: harm (*M* = `r printnum(mean(noout1.1$harmMFQ))`, *SD* =
+`r printnum(sd(noout1.1$harmMFQ))`), fairness (*M* =
+`r printnum(mean(noout1.1$fairMFQ))`, *SD* =
+`r printnum(sd(noout1.1$fairMFQ))`), ingroup (*M* =
+`r printnum(mean(noout1.1$ingroupMFQ))`, *SD* =
+`r printnum(sd(noout1.1$ingroupMFQ))`), authority (*M* =
+`r printnum(mean(noout1.1$authorityMFQ))`, *SD* =
+`r printnum(sd(noout1.1$authorityMFQ))`), and purity (*M* =
+`r printnum(mean(noout1.1$purityMFQ))`, *SD* =
+`r printnum(sd(noout1.1$purityMFQ))`). Participants free association
+responses were processed using the *tm* [@feinerer2008] and *corpus*
+[@perry2024] libraries after manual correction of spelling errors. Each
+set of answers was cleaned for punctuation, English stop words (e.g.,
+*the*, *an*, *of*) were removed, and each word was stemmed using the
+English library in *tm*. We did not combine related words in this
+section (i.e., *injure* and *injury*, which have different stems *injur*
+and *injuri*) to allow for maximum coverage of different word forms
+present in the dictionary. Additionally, with the use of automated
+stemmers like that present in the *tm* library, leaving both word forms
+in the dictionary would capture more of the concepts present in future
+analyses with a different corpus without the requirement on the coder to
+manually recode all word forms. Frequency counts of the stemmed words
+were tabulated and only words mentioned with at least one percent
+frequency were used in the subsequent analyses. The complete set of word
+frequencies for each foundation can be found in our supplemental
+materials.
+
+For clarity, the processing pipeline for each separate domain was:
+
+1.  Manual spell checking of free association responses
+2.  Word tokenization and stemming
+3.  Create a term by document matrix
+4.  Remove punctuation and stopwords via the *tm* stopword list
+5.  Calculate percent frequency across documents (all words saved
+    online)
+6.  Remove words with less than 1% mentions across participants
+
+```{r harm-analysis-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1.1$Q27 <- as.character(noout1.1$Q27)
+
+# stem the data
+for (i in 1:nrow(noout1.1)) {
+  noout1.1$Q27[i] <- paste(unlist(
+    text_tokens(noout1.1$Q27[i], stemmer = "en")), collapse = " ")
+}
+
+# create a corpus
+harm_corpus <- Corpus(VectorSource(noout1.1$Q27))
+harm_TDM <- as.matrix(TermDocumentMatrix(harm_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+# calculate the most frequent words
+harm_freq <- data.frame(Word = rownames(harm_TDM),
+                       Freq = rowSums(harm_TDM),
+                       row.names = NULL)
+harm_freq$Word <- as.character(harm_freq$Word)
+harm_freq$percent <- harm_freq$Freq/nrow(noout1.1) *100
+
+write.csv(harm_freq, "../../study1_data/study1.1_harm_freq.csv", row.names = F)
+
+# subset out to only words with 1% mentions
+harm_words <- harm_freq$Word[harm_freq$percent >=1]
+# turn sideways to add to dataset
+harm_TDM  <- as.data.frame(t(harm_TDM))
+harm_TDM  <- harm_TDM[ , harm_words]
+
+# final dataset for harm
+harm_final <- cbind(noout1.1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
+                   harm_TDM)
+
+harm_cor <- apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})
+
+harmcut <- mean(harm_cor) + 2*sd(harm_cor)
+harm_words_reduce <- names(harm_cor[abs(harm_cor) >= harmcut])
+```
+
+```{r fair-analysi-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1.1$Q29 <- as.character(noout1.1$Q29)
+
+# stem the data
+for (i in 1:nrow(noout1.1)) {
+  noout1.1$Q29[i] <- paste(unlist(
+    text_tokens(noout1.1$Q29[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+fair_corpus <- Corpus(VectorSource(noout1.1$Q29))
+fair_TDM <- as.matrix(TermDocumentMatrix(fair_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+fair_freq <- data.frame(Word = rownames(fair_TDM),
+                       Freq = rowSums(fair_TDM),
+                       row.names = NULL)
+fair_freq$Word <- as.character(fair_freq$Word)
+fair_freq$percent <- fair_freq$Freq/nrow(noout1.1) *100
+
+write.csv(fair_freq, "../../study1_data/study1.1_fair_freq.csv", row.names = F)
+
+# subset out to only words with 1% mentions
+fair_words <- fair_freq$Word[fair_freq$percent >=1]
+# turn sideways to add to dataset
+fair_TDM <- as.data.frame(t(fair_TDM))
+fair_TDM <- fair_TDM[ , fair_words]
+
+# final dataset for fair
+fair_final <- cbind(noout1.1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
+                   fair_TDM)
+
+fair_cor <- apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})
+
+faircut <- mean(fair_cor) + 2*sd(fair_cor)
+fair_words_reduce <- names(fair_cor[abs(fair_cor) >= faircut])
+```
+
+```{r ingroup-analysis-3.1, include=FALSE}
+#q27 through 34 are the writing columns
+noout1.1$Q30 <- as.character(noout1.1$Q30)
+
+##stem the data
+for (i in 1:nrow(noout1.1)) {
+  noout1.1$Q30[i] <- paste(unlist(
+    text_tokens(noout1.1$Q30[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+ingroup_corpus <- Corpus(VectorSource(noout1.1$Q30))
+ingroup_TDM <- as.matrix(TermDocumentMatrix(ingroup_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+# view the most frequent words
+ingroup_freq <- data.frame(Word = rownames(ingroup_TDM),
+                       Freq = rowSums(ingroup_TDM),
+                       row.names = NULL)
+ingroup_freq$Word <- as.character(ingroup_freq$Word)
+ingroup_freq$percent <- ingroup_freq$Freq/nrow(noout1.1) *100
+
+write.csv(ingroup_freq, "../../study1_data/study1.1_ingroup_freq.csv", row.names = F)
+
+# subset out to only words with 1% mentions
+ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >=1]
+# turn sideways to add to dataset
+ingroup_TDM <- as.data.frame(t(ingroup_TDM))
+ingroup_TDM <- ingroup_TDM[ , ingroup_words]
+
+# final dataset for ingroup
+ingroup_final <- cbind(noout1.1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
+                   ingroup_TDM)
+
+ingroup_cor <- apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})
+
+ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
+ingroup_words_reduce <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
+```
+
+```{r authority-analysis-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1.1$Q32 <- as.character(noout1.1$Q32)
+
+##stem the data
+for (i in 1:nrow(noout1.1)) {
+  noout1.1$Q32[i] <- paste(unlist(
+    text_tokens(noout1.1$Q32[i], stemmer = "en")), collapse = " ")
+}
+
+# create a corpus
+authority_corpus <- Corpus(VectorSource(noout1.1$Q32))
+authority_TDM <- as.matrix(TermDocumentMatrix(authority_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+# view the most frequent words
+authority_freq <- data.frame(Word = rownames(authority_TDM),
+                       Freq = rowSums(authority_TDM),
+                       row.names = NULL)
+authority_freq$Word <- as.character(authority_freq$Word)
+authority_freq$percent <- authority_freq$Freq/nrow(noout1.1) *100
+
+write.csv(authority_freq, "../../study1_data/study1.1_authority_freq.csv", row.names = F)
+
+# subset out to only words with 1% mentions
+authority_words <- authority_freq$Word[authority_freq$percent >=1]
+# turn sideways to add to dataset
+authority_TDM <- as.data.frame(t(authority_TDM))
+authority_TDM <- authority_TDM[ , authority_words]
+
+# final dataset for authority
+authority_final <- cbind(noout1.1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
+                   authority_TDM)
+
+authority_cor <- apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})
+
+authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
+authority_words_reduce <- names(authority_cor[abs(authority_cor) >= authoritycut])
+```
+
+```{r purity-analysis-3.1, include = FALSE}
+#q27 through 34 are the writing columns
+noout1.1$Q34 <- as.character(noout1.1$Q34)
+
+# stem the data
+for (i in 1:nrow(noout1.1)) {
+  noout1.1$Q34[i] <- paste(unlist(
+    text_tokens(noout1.1$Q34[i], stemmer = "en")), collapse = " ")
+}
+
+# create a corpus
+purity_corpus <- Corpus(VectorSource(noout1.1$Q34))
+purity_TDM <- as.matrix(TermDocumentMatrix(purity_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+# view the most frequent words
+purity_freq <- data.frame(Word = rownames(purity_TDM),
+                       Freq = rowSums(purity_TDM),
+                       row.names = NULL)
+purity_freq$Word <- as.character(purity_freq$Word)
+purity_freq$percent <- purity_freq$Freq/nrow(noout1.1) *100
+
+write.csv(purity_freq, "../../study1_data/study1.1_purity_freq.csv", row.names = F)
+
+# subset out to only words with 1% mentions
+purity_words <- purity_freq$Word[purity_freq$percent >=1]
+# turn sideways to add to dataset
+purity_TDM <- as.data.frame(t(purity_TDM))
+purity_TDM <- purity_TDM[ , purity_words]
+
+##final dataset for purity
+purity_final <- cbind(noout1.1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
+                   purity_TDM)
+
+purity_cor <- apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})
+
+puritycut <- mean(purity_cor) + 2*sd(purity_cor)
+purity_words_reduce <- names(purity_cor[abs(purity_cor) >= puritycut])
+```
+
+This procedure generated a large frequency of words for a new dictionary
+of moral foundations: harm `r length(harm_words)`, fairness
+`r length(fair_words)`, ingroup `r length(ingroup_words)`, authority
+`r length(authority_words)`, and purity `r length(purity_words)`. These
+concepts were included in the full dictionary used for Study 1.3. We
+additionally created a reduced dictionary that included only concepts
+correlated with their respective moral foundations scores. Correlations
+between word frequency and the sum of the MFQ were calculated for each
+foundation and set of concepts. Words were included in the reduced
+dictionary if their correlation was two standard deviations away from
+the mean correlation for that foundation. The reduced dataset included
+the following number of words for each foundation: harm
+`r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`,
+ingroup `r length(ingroup_words_reduce)`, authority
+`r length(authority_words_reduce)`, and purity
+`r length(purity_words_reduce)`.
+
+## Study 1.2
+
+this section is about the writing
+
+### Participants
+
+```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
+sample1 <- read.csv("study1_data/study1.2_fixed_sample 1.csv", stringsAsFactors = F)
+sample2 <- read.csv("study1_data/study1.2_fixed_sample 2.csv", stringsAsFactors = F)
+
+##merge files together
+study1.2DF <- merge(sample1, sample2, all = TRUE)
+
+##merge together the writing samples
+#q24, q25, q26, q7 
+fullsample$writing <- apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
+                           1, function(x) toString(na.omit(x)))
+
+##clear out completely columns we don't need
+crapcolumns <- c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
+finalsample <- fullsample[ , -crapcolumns]
+
+##accuracy
+summary(finalsample[ , 2:40])
+
+finalsample$Q10 <- factor(finalsample$Q10,
+                         levels = 1:2,
+                         labels = c("Man", "Woman"))
+finalsample$Q11 <- as.numeric(finalsample$Q11)
+finalsample$Q12 <- factor(finalsample$Q12,
+                         levels = 1:7,
+                         labels = c("White", "Black", 
+                                    "Hispanic", "Asian",
+                                    "Native American", 
+                                    "Mixed", "Other"))
+
+gender <- table(finalsample$Q10)/sum(table(finalsample$Q10))*100
+race <- table(finalsample$Q12)/sum(table(finalsample$Q12))*100
+
+write.csv(finalsample, 'study1_data/study1.2_finalsample.csv', row.names = FALSE)
+newMFD <- import('study1_data/study1.2_finalsample_newMFD.csv')
+colnames(newMFD)[1:41] <- colnames(finalsample)[1:41]
+newMFD <- newMFD[,c(1,42:55)]
+finalsample <- merge(finalsample, newMFD, by = "ResponseId")
+
+##take out the people with less than 25 words
+##use the ngram library to examine the data
+##preprocess only works on one string at a time, so going to use a loop go through all the rows (apply won't work because we only want to work on one column)
+
+for (i in 1:nrow(finalsample)) {
+
+  finalsample$writing[i] <- preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
+  finalsample$wordcount[i] <- string.summary(finalsample$writing[i])$words
+
+}
+
+#remove small words people
+finalwords <- subset(finalsample, wordcount >=25)
+
+##check out missing data
+#missing by row
+missing <- apply(finalwords, 1, percentmiss)
+table(missing)
+goodrows <- subset(finalwords, missing <= 5)
+
+#missing by column
+apply(goodrows, 2, percentmiss)
+
+##don't fill in Q10 to the end, be sure to merge these back together
+goodcolumns <- goodrows[ , -c(32:42)]
+badcolumns <- goodrows[ , c(32:42)]
+
+#fill in missing data points
+tempnomiss <- mice(goodcolumns)
+nomiss <- complete(tempnomiss, 1)
+summary(nomiss)
+#merge
+allcolumns <- cbind(nomiss, badcolumns) 
+summary(allcolumns)
+
+##outliers
+mahal2 <- mahalanobis(allcolumns[ , -c(1,46:56)], 
+                    colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
+                    cov(allcolumns[ , -c(1,46:56)], use="pairwise.complete.obs"))
+#mahal2
+cutoff2 <- qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
+cutoff2
+ncol(allcolumns[ , -c(1,46:56)])
+summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
+noout2 <- subset(allcolumns, mahal2 < cutoff2)
+
+##assumptions on the questions i.e., not Q10 to the end
+#correlations
+correlations2 <- cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
+#correlations2
+symnum(correlations2)
+
+#the random stuff
+random2 <- rchisq(nrow(noout2), 7)
+fake2 <- lm(random2~., data=noout2[ , -c(1,46:56)])
+
+#normal
+standardized2 <- rstudent(fake2)
+hist(standardized2, breaks=15)
+
+#linear
+{qqnorm(standardized2)   
+abline(0,1)}
+
+#homog + s
+fitvalues2 <- scale(fake2$fitted.values)
+{plot(fitvalues2, standardized2) 
+abline(0,0)
+abline(v = 0)}
+
+####create the MFQ subscales####
+noout2$harmMFQ <- apply(noout2[ , 2:4], 1, sum)
+noout2$fairMFQ <- apply(noout2[ , 5:7], 1, sum)
+noout2$ingroupMFQ <- apply(noout2[ , 8:10], 1, sum)
+noout2$authorityMFQ <- apply(noout2[ , 11:13], 1, sum)
+noout2$purityMFQ <- apply(noout2[ , 14:16], 1, sum)
+```
+
+Participants were recruited in two waves as part of a larger
+investigation on priming political and religious attitudes. Participants
+were recruited via an online research system (SONA) and were given
+course credit for their participation. `r nrow(finalsample)`
+participants were included in the this study. The study was mostly women
+(`r printnum(gender["Woman"], digits = 1)`%) and White
+(`r printnum(race["White"], digits = 1)`%) participants with a mix of
+minority participants: Black (`r printnum(race["Black"], digits = 1)`%),
+(`r printnum(race["Hispanic"], digits = 1)`%),
+(`r printnum(race["Asian"], digits = 1)`%), Native American
+(`r printnum(race["Native American"], digits = 1)`%), Mixed
+(`r printnum(race["Mixed"], digits = 1)`%) and Other
+(`r printnum(race["Other"], digits = 1)`%). The average listed age was
+`r printnum(mean(finalsample$Q11, na.rm = T))` (*SD* =
+`r printnum(sd(finalsample$Q11, na.rm = T))`).
+
+### Materials and Procedure
+
+Data was again collected via Qualtrics (<https://osf.io/qr3gv>). Four
+fake new stories were presented to participants, which were roughly 400
+words each. First, all news stories included a few sentences describing
+the use of chemical weapons in the Syrian civil war. The news stories
+were manipulated with political (Republican v. Democrat) and religious
+(religious v. not) quotes in a 2 x 2 design. News stories can be found
+in the online materials. Participants also completed the 30-item version
+of the MFQ as described previously. In addition to basic demographics
+(gender, age), participant political orientation was assessed with the
+same scale described in Study 3.1.
+
+After consenting to participate in the study, participants were randomly
+shown one of the four new articles about Syria's use of chemical
+weapons. Participants were then asked to write for 5-10 minutes about
+their reaction to Syria's use of chemical weapons and the needed
+response from the United States. The second wave of data collection
+included different writing prompts designed to capture more of the moral
+foundation areas in their writing. The following writing prompt was
+used, "Please write about your attitudes on abortion (or same-sex
+marriage or environmentalism) as well as your reason for this stance."
+The three prompts were chosen to create a more varied word set by using
+topics that should elicit words from each moral foundations category by
+soliciting a moral response. In each wave of data collection (Syria
+prompts, moral prompts) the prompt material was randomized between
+participants. Participants then completed the MFQ, demographics, and the
+political orientation scale.
+
+### Results
+
+Participant data was first spell checked and screening for inaccurate
+responses. Participants who did not write more than fifty words in
+response to a given prompt were excluded (*n* =
+`r nrow(finalsample) - nrow(finalwords)`). One missing datapoint was
+estimated using the *mice* library from *R* [@CITE] for a missing MFQ
+question, and all other missing data was present in the demographics
+sections, which were not filled in. The MFQ data were screened for
+outliers using Mahalanobis distance, and 25 outliers were found at
+$\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) =
+`r printnum(cutoff2)`. These data were excluded leading to a final
+sample size of `r nrow(noout2)`. Data were screened for assumptions
+described in Study 3.1 and were found to be satisfactory.
+
+```{r writing-analysis-3.2, include=FALSE}
+##stem the data
+for (i in 1:nrow(noout2)) {
+  noout2$writing2[i] <- paste(unlist(
+    text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
+}
+
+##create a corpus
+overall_corpus <- Corpus(VectorSource(noout2$writing2))
+overall_TDM <- as.matrix(TermDocumentMatrix(overall_corpus,
+                              control = list(removePunctuation = TRUE,
+                                             stopwords = TRUE)))
+
+##view the most frequent words
+overall_freq <- data.frame(Word = rownames(overall_TDM),
+                          Freq = rowSums(overall_TDM),
+                          row.names = NULL)
+overall_freq$Word <- as.character(overall_freq$Word)
+overall_freq$percent <- overall_freq$Freq/nrow(noout2)*100
+
+write.csv(overall_freq, "study1_data/study1.2_freq.csv", row.names = F)
+
+##subset out to only words with 1% mentions
+##this goes over 100% but mostly want to subset out things that were only mentioned
+##a few times by participants
+all_words <- overall_freq$Word[overall_freq$percent >=1]
+
+##turn sideways to add to dataset
+overall_TDM <- as.data.frame(t(overall_TDM))
+overall_TDM <- overall_TDM[ , all_words]
+
+##final dataset
+overall_final <- cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
+                                  "authorityMFQ", "purityMFQ","ingroupMFQ")],
+                   overall_TDM)
+```
+
+```{r mfq-cor-3.2, include = FALSE}
+##harm
+harm_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})
+
+harmcut <- mean(harm_cor) + 2*sd(harm_cor)
+harm_words_reduce_exp2 <- names(harm_cor[abs(harm_cor) >= harmcut])
+
+##fair
+fair_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})
+
+faircut <- mean(fair_cor) + 2*sd(fair_cor)
+fair_words_reduce_exp2 <- names(fair_cor[abs(fair_cor) >= faircut])
+
+##purity
+purity_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})
+
+puritycut <- mean(purity_cor) + 2*sd(purity_cor)
+purity_words_reduce_exp2 <- names(purity_cor[abs(purity_cor) >= puritycut])
+
+##authority
+authority_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})
+
+authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
+authority_words_reduce_exp2 <- names(authority_cor[abs(authority_cor) >= authoritycut])
+
+##ingroup
+ingroup_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})
+
+ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
+ingroup_words_reduce_exp2 <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
+
+#print out words list to look at for further analysis
+write.csv(harm_words_reduce_exp2, "../study1_data/words/harm_exp2.csv", row.names = F)
+write.csv(fair_words_reduce_exp2, "../study1_data/words/fair_exp2.csv", row.names = F)
+write.csv(authority_words_reduce_exp2, "../study1_data/words/authority_exp2.csv", row.names = F)
+write.csv(purity_words_reduce_exp2, "../study1_data/words/purity_exp2.csv", row.names = F)
+write.csv(ingroup_words_reduce_exp2, "../study1_data/words/ingroup_exp2.csv", row.names = F)
+```
+
+In the first study, only free association responses were collected, but
+in this study, full writing samples were collected. Therefore, we
+expected many of the words listed to be part of creating a cohesive
+discourse, rather than only related to the moral foundation targeted. To
+find only the most related words, the correlation between word frequency
+and moral foundation was calculated and words with correlations greater
+than two standard deviations outside the mean were selected for the
+dictionary analysis in Study 3.3. The sum of each moral foundation area
+was calculated in order to determine which words were linked to their
+respective moral foundation. The average scores were: harm (*M* =
+`r printnum(mean(noout2$harmMFQ))`, *SD* =
+`r printnum(sd(noout2$harmMFQ))`), fairness (*M* =
+`r printnum(mean(noout2$fairMFQ))`, *SD* =
+`r printnum(sd(noout2$fairMFQ))`), ingroup (*M* =
+`r printnum(mean(noout2$ingroupMFQ))`, *SD* =
+`r printnum(sd(noout2$ingroupMFQ))`), authority (*M* =
+`r printnum(mean(noout2$authorityMFQ))`, *SD* =
+`r printnum(sd(noout2$authorityMFQ))`), and purity (*M* =
+`r printnum(mean(noout2$purityMFQ))`, *SD* =
+`r printnum(sd(noout2$purityMFQ))`).
+
+```{r compare-ratings-3.2, include = FALSE}
+authority_erin <- read.csv("study1_data/words/authority_study1.2 erin.csv", stringsAsFactors = F)
+authority_will <- read.csv("study1_data/words/authority_study1.2 will.csv", stringsAsFactors = F)
+authority_erin$x[authority_erin$use != authority_will$use]
+
+authority_words_reduce_exp2 <- authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]
+
+fair_erin <- read.csv("study1_data/words/fair_study1.2 erin.csv", stringsAsFactors = F)
+fair_will <- read.csv("study1_data/words/fair_study1.2 will.csv", stringsAsFactors = F)
+fair_erin$x[fair_erin$use != fair_will$use]
+fair_will$use[fair_will$x == "carbon"] <- 0
+fair_will$use[fair_will$x == "emiss"] <- 0
+#exclude carbon and emiss due to the prompt
+
+fair_words_reduce_exp2 <- fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]
+
+purity_erin <- read.csv("study1_data/words/purity_study1.2 erin.csv", stringsAsFactors = F)
+purity_will <- read.csv("study1_data/words/purity_study1.2 will.csv", stringsAsFactors = F)
+purity_erin$x[purity_erin$use != purity_will$use]
+purity_will$use[purity_will$x == "befor"] <- 1
+#before include because of "before sex/ruined/etc."
+
+purity_words_reduce_exp2 = purity_words_reduce_exp2[purity_words_reduce_exp2 %in% purity_will$x[purity_will$use == 1]]
+
+ingroup_erin <- read.csv("study1_data/words/ingroup_study1.2 erin.csv", stringsAsFactors = F)
+ingroup_will <- read.csv("study1_data/words/ingroup_study1.2 will.csv", stringsAsFactors = F)
+ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
+ingroup_will$use[ingroup_will$x == "mean"] <- 1
+#mean should be included
+
+ingroup_words_reduce_exp2 <- ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]
+
+harm_erin <- read.csv("study1_data/words/harm_study1.2 erin.csv", stringsAsFactors = F)
+harm_will <- read.csv("study1_data/words/harm_study1.2 will.csv", stringsAsFactors = F)
+harm_erin$x[harm_erin$use != harm_will$use]
+harm_will$use[harm_will$x == "import"] <- 1
+# import for important
+
+harm_words_reduce_exp2 = harm_words_reduce_exp2[harm_words_reduce_exp2 %in% harm_will$x[harm_will$use == 1]]
+```
+
+This set of words was then coded by two of the authors for relevant
+words with discussion over coding constituting a tiebreaker. For
+example, for harm words in this study both *also* and *Syria* appeared
+as correlated words to the harm foundation. The first word does not meet
+face validity of correlation with the dictionary, and these type of
+function words or ambiguous verbs (i.e., *get*, *can*) were usually
+excluded. The second example is likely because of the writing prompt,
+and therefore, proper nouns were also excluded. The reduced dataset
+included the following number of words for each foundation: harm
+`r length(harm_words_reduce_exp2)`, fairness
+`r length(fair_words_reduce_exp2)`, ingroup
+`r length(ingroup_words_reduce_exp2)`, authority
+`r length(authority_words_reduce_exp2)`, and purity
+`r length(purity_words_reduce_exp2)`.
+
+## Study 3.3
+
+This part is the mtmm
+
+```{r mtmm-setup, include = FALSE}
+##original mfd words
+original_mfd <- read.csv("study1_data/original_mfd.csv", stringsAsFactors = F)
+
+##adding forms/conjugations of words to original_mfd
+#harm/care
+original_mfd[c(27:95),1] <- c("abusive","abuser","abused","abusing",
+                             "sympathetic","sympathies","damaged",
+                             "damaging","attacked","attacking","attacker",
+                             "attacks","attackers", "benefits", "benefitted",
+                             "benefitting", "cares", "cared", "caring", "crushes",
+                             "crushing", "crushed", "dangerous", "defends", "defending",
+                             "defended", "detroys", "destroyed", "destroying",
+                             "fights", "fought", "fighting", "guards", "guarded",
+                             "guarding", "harms", "harmed", "harming", "hurts",
+                             "hurting", "kills", "killed", "killing", "preserves",
+                             "preserved", "preserving", "protects", "protected",
+                             "protecting", "protection", "ruins", "ruined", "ruining",
+                             "safely", "safer", "shelters", "sheltered", "sheltering",
+                             "spurns", "spurned", "spurning", "stomps", "stomped",
+                             "stomping", "suffers", "suffered", "suffering",
+                             "violence", "warring")
+
+#fairness/reciprocity
+original_mfd[c(20:64),2] <- c("balances", "balanced", "balancing","biased",
+                             "biases", "discriminates", "discriminated",
+                             "discriminating", "discrimination", "equals",
+                             "equaled", "equaling", "equates", "equated",
+                             "equating", "evens", "evened", "evening",
+                             "excludes", "excluded", "excluding", "fairness",
+                             "favors", "favored", "favoring", "honesty",
+                             "impariality", "justice", "justifies", "justified",
+                             "justifying", "prefers", "preferred", "preferring",
+                             "prejudices", "prejudiced", "prejudicing", "reasons",
+                             "reasoned", "reasoning", "rights", "tolerates",
+                             "tolerated", "tolerating", "toleration")
+
+#ingroup/loyalty
+original_mfd[c(16:47),3] <- c("collects", "collected", "collecting", "collective",
+                             "communities", "deceives", "deceived", "deceiving",
+                             "deception", "deceptions", "deserts", "deserted",
+                             "deserting", "desertion", "families", "fellows",
+                             "foreigners", "groups", "grouped", "grouping",
+                             "indviduals", "indvidualize", "individualized",
+                             "individualizing", "members", "nations", "sides",
+                             "togetherness", "traits", "unites", "united", "uniting")
+
+#authority/respect
+original_mfd[c(31:112),4] <- c("abides", "abided", "abiding", "authorities",
+                              "classes", "classed", "classing", "command",
+                              "commanded", "commanding", "controls", "controlled",
+                              "controlling", "defects", "defected", "defecting",
+                              "defers", "deferred", "deferring", "deference",
+                              "defies", "defied", "defying", "defiance", "deserts",
+                              "deserted", "deserting", "desertion", "duties",
+                              "faiths", "fathers", "fathered", "fathering",
+                              "honors", "honored", "honoring", "laws", "leads",
+                              "leading", "mothers", "mothered", "mothering",
+                              "obeys", "obeyed", "obeying", "opposes", "opposed",
+                              "opposing", "orders", "ordered", "ordering", "permits",
+                              "permitted", "permitting", "positions", "positioned",
+                              "positioning", "preserves", "preserved", "preserving",
+                              "preservation", "protests", "protested", "protesting",
+                              "refuses", "refused", "refusing", "refusal", "respects",
+                              "respected", "respecting", "respectful", "reveres",
+                              "revered", "revering", "reverence", "serves", "served",
+                              "serving", "traditions", "traditional", "traits")
+
+#purity/sanctity
+original_mfd[c(21:60),5] <- c("abstains", "abstained", "abstaining", "abstinence",
+                             "adulteries", "adulterous", "adulterer", "adulterers",
+                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
+                             "cleanliness", "dirty", "diseases", "diseased", 
+                             "disgusts", "disgusted", "disgusting", "grossness",
+                             "innocence", "modesty", "preserves", "preserved",
+                             "preserving", "preservation", "promiscuity",
+                             "promiscuities", "purity", "rights", "ruins", "ruined",
+                             "ruining", "sacredness", "sickness", "sicknesses",
+                             "sins", "wholeness", "wholesome")
+
+##stem the original mfd
+for(i in 1:nrow(original_mfd)) {
+  original_mfd$h2[i] <- stemDocument(original_mfd$h2[i], language = "english")
+  original_mfd$f2[i] <- stemDocument(original_mfd$f2[i], language = "english")
+  original_mfd$i2[i] <- stemDocument(original_mfd$i2[i], language = "english")
+  original_mfd$a2[i] <- stemDocument(original_mfd$a2[i], language = "english")
+  original_mfd$p2[i] <- stemDocument(original_mfd$p2[i], language = "english")
+}
+
+mtmmdata <- noout2[ , c(1:31, 45) ]
+
+####figure out the percents for the exp2 data
+for (i in 1:nrow(mtmmdata)) {
+
+  ##figure out the sum for just the original mfd
+  mtmmdata$harm_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])
+
+  mtmmdata$purity_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])
+
+  mtmmdata$fair_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])
+
+  mtmmdata$authority_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])
+
+  mtmmdata$ingroup_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])
+
+  ##figure out the sum for all words ever 
+  mtmmdata$harm_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])
+
+  mtmmdata$purity_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])
+
+  mtmmdata$fair_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])
+
+  mtmmdata$authority_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])
+
+  mtmmdata$ingroup_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])
+
+  ##figure out the sum for reduced words
+  mtmmdata$harm_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])
+
+  mtmmdata$purity_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])
+
+  mtmmdata$fair_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])
+
+  mtmmdata$authority_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])
+
+  mtmmdata$ingroup_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])
+
+}
+
+#create percents instead of frequencies
+mtmmdata[ , c(33:47)] <- mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100 
+summary(mtmmdata[ , 33:47])
+```
+
+```{r mtmm_orig, include = FALSE}
+###Run chunk 8: demos_study2 to update data
+###Use noout2 df as dataframe for mtmm
+###Columns labeled Harm1/Fairness1/Loyalty1/Authority1/Purity1 are original MFD
+###Columns labeled Harm2/Fairness2/Loyalty2/Authority2/Purity2 are revised MFD
+
+####mtmm original dictionary####
+
+{model1 <- '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.fit <- cfa(model1, data=mtmmdata, std.lv=TRUE)
+summary(model1.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.fit, fit.measures = "aic")
+
+{model1.2 <- '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+fair_orig ~~ 1167.145*fair_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.2.fit <- cfa(model1.2, data=mtmmdata, std.lv=TRUE)
+summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.2.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.2.fit, fit.measures = "aic")
+
+{model2 <- '
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+fair_orig ~~ 1167.145*fair_orig
+'}
+
+model2.fit <- cfa(model2, data=mtmmdata, std.lv=TRUE)
+summary(model2.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model2.fit, fit.measures = "aic")
+
+{model3 <- '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+harmL~~1*fairL
+harmL~~1*ingroupL
+harmL~~1*authorityL
+harmL~~1*purityL
+fairL~~1*ingroupL
+fairL~~1*authorityL
+fairL~~1*purityL
+ingroupL~~1*authorityL
+ingroupL~~1*purityL
+authorityL~~1*purityL
+
+fair_orig ~~ 1167.145*fair_orig
+'}
+
+model3.fit <- cfa(model3, data=mtmmdata, std.lv=TRUE)
+summary(model3.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model3.fit, fit.measures = "aic")
+
+{model4 <- '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
+fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
+purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+mfq ~~ 0*mfd
+
+fair_orig ~~ 1167.145*fair_orig
+'}
+
+model4.fit <- cfa(model4, data=mtmmdata, std.lv=TRUE)
+summary(model4.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model4.fit, fit.measures = "aic")
+```
+
+```{r mtmm_reduce, include = FALSE}
+
+{model1 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
+fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
+purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
+summary(model1.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.fit, fit.measures = "aic")
+
+{model2 ='
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+'}
+
+model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
+summary(model2.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model2.fit, fit.measures = "aic")
+
+{model3 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
+fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
+purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+harmL~~1*fairL
+harmL~~1*ingroupL
+harmL~~1*authorityL
+harmL~~1*purityL
+fairL~~1*ingroupL
+fairL~~1*authorityL
+fairL~~1*purityL
+ingroupL~~1*authorityL
+ingroupL~~1*purityL
+authorityL~~1*purityL
+'}
+
+model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
+summary(model3.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model3.fit, fit.measures = "aic")
+
+{model4 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
+fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
+purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+mfq ~~ 0*mfd
+'}
+
+model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
+summary(model4.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model4.fit, fit.measures = "aic")
+```
+
+```{r mtmm_all, include = FALSE}
+
+{model1 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+'}
+
+model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
+summary(model1.fit, rsquare=TRUE, standardized=TRUE)
+semPaths(model1.fit, whatLabels = "std", layout = "tree")
+fitMeasures(model1.fit, fit.measures = "aic")
+
+{model2 ='
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+'}
+
+model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
+summary(model2.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model2.fit, fit.measures = "aic")
+
+{model3 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+harmL~~1*fairL
+harmL~~1*ingroupL
+harmL~~1*authorityL
+harmL~~1*purityL
+fairL~~1*ingroupL
+fairL~~1*authorityL
+fairL~~1*purityL
+ingroupL~~1*authorityL
+ingroupL~~1*purityL
+authorityL~~1*purityL
+'}
+
+model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
+summary(model3.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model3.fit, fit.measures = "aic")
+
+{model4 = '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
+mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
+
+##fix the covariances
+harmL~~0*mfq
+fairL~~0*mfq
+ingroupL~~0*mfq
+authorityL~~0*mfq
+purityL~~0*mfq
+harmL~~0*mfd
+fairL~~0*mfd
+ingroupL~~0*mfd
+authorityL~~0*mfd
+purityL~~0*mfd
+mfq ~~ 0*mfd
+'}
+
+model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
+summary(model4.fit, rsquare=TRUE, standardized=TRUE)
+fitMeasures(model4.fit, fit.measures = "aic")
+```
+
+Data Cleaning and Descriptives. In sample 1, participants who wrote less
+than 50 words were deleted (*n* = 69) leaving *n* = 221 participants.
+The average political orientation was 4.80 (*SD* = 2.21) on a scale of 1
+(*conservative*) to 10 (*liberal*). In sample 2, all 160 participants
+wrote at least 50 words. The mean political orientation was 5.01 (*SD* =
+2.33) for sample 2. The data from sample 1 and sample 2 were combined.
+Before any analyses were conducted, participants who did not use any
+words from the MFD were deleted; 16 participants were deleted from
+sample 1 and 25 from sample 2. The final sample size for analysis was
+*N* = 340 which had a mean political orientation of 4.90 (*SD* = 2.28).
+MFD scores were computed using NVivo *(CITE)* as both frequency for each
+foundation and percent coverage for each foundation. Frequency was
+simply the count of the number of words used from a given foundation
+dictionary; for example, a participant using the word *war* once and the
+word *peace* twice would have a frequency score of 3 for the *harm*
+dictionary. Percent coverage was calculated by taking the frequency and
+dividing by the word count; for example, given a frequency score of 3
+for the *harm* dictionary and a word count of 100, then the percent
+coverage would be .03 for the *harm* dictionary. MFQ scores for each
+foundation were calculated by averaging the six items pertaining to each
+foundation. Reliability. Here we should talk about the reliability of
+the MFQ for each piece, as well as the reliability of the words for the
+MFD. I think to do that you might need a thing that has each word as
+frequency count yes/no or however the LIWC version thing was done. MTMM.
+BASIC SEM STUFF HERE (also that you used bayes) Data screening was
+conducted using SPSS version 22 and AMOS version 22. Participants who
+were missing data for the MFD, MFQ, or political orientation were
+deleted from all analyses. Given the distribution of the dictionary
+variables, participants whose writing sample were less than 2% words
+from the MFD were deleted resulting in a sample size of 252.
+Additionally, 7 outliers were deleted. Widaman's (1985; as cited in
+@Byrne2009) four-step nested method was used to test the convergent and
+divergent validity of the MFD and MFQ. The first step is the baseline
+model (Model 1), which establishes correlation among traits (*harm*,
+*purity*, *fairness*, *authority*, and *ingroup*) as well as correlation
+among methods (MFD and MFQ) but no cross correlation of traits and
+methods. The individual questions from the 30 item version of the MFQ
+and the total frequency of concepts from each foundation in the MFD were
+used as measured variables. The fit of this first model indicated some
+misfit, as fit indices were a mix of poor and acceptable, $\chi$ 2 (514)
+= 977.46, $\chi$ 2/df = 1.90, CFI = .842, RMSEA = .061 [95% CI =
+.055-.067], SRMR = .0623. In this model, the MFD *harm*, *fairness*, and
+*ingroup* items significantly loaded onto their trait factors, while
+*authority* and *purity* did not. All foundations but *authority* loaded
+significantly on the method traits. All but two of the *ingroup*
+questions and one *authority* question loaded onto the MFQ trait
+factors. Several questions of the MFQ did not load significantly onto
+the methods factors; however, this result was taken as an indicator that
+traits variance was higher than methods variance. Generally, trait
+loadings were higher than method loadings for both the MFD and MFQ for
+*harm* and *fairness* traits. However, the *purity*, *ingroup*, and
+*authority* foundations did not show this loading pattern. ERIN STOPPED
+HERE CUZ HEADACHE. The second step (Model 2) involved eliminating the
+latent traits from the model. This model was significantly worse than
+Model 1 indicating the traits are important to the model ($\delta$
+$\chi$ 2 = 1141.09, $\delta$ df = 45, $\delta$ CFI = .351). This
+supports convergent validity for the traits measured by both methods
+which in this case are the five moral foundations. The third step (Model
+3) involved forcing the five traits to be perfectly correlated. This
+model was significantly worse than Model 1 indicating the usefulness of
+five unique traits ($\delta$ $\chi$ 2 = 311.09, $\delta$ df = 10,
+$\delta$ CFI = .097). This supports discriminant validity for the
+existence of five unique moral foundations. The final step (Model 4)
+involved allowing the correlations between the traits to be freely
+estimated and forcing the methods to be uncorrelated. This model was
+similar to Model 1 indicating the methods both measure the traits but
+they are both unique methods ($\delta$ $\chi$ 2 = 2.23, $\delta$ df = 1,
+$\delta$ CFI = .001). This supports discriminant validity for the
+methods. This set of analyses suggests the MFD is a possibly valid
+measure of moral foundations but does not measure them well enough to be
+useful in all applications and may be measuring them differently than
+the MFQ. Regression predicting Political Orientation. The MFQ has
+predicted political orientation across many studies [@Federico2013;
+@Graham2009; @Haidt2009; @Weber2013]. Therefore, in addition to the MTMM
+analysis, we compared how well the MFD score predicted political
+orientation compared to how well the MFQ predicted the political
+orientation. First, total MFQ scores were calculated for each foundation
+by averaging all six items. Then, a regression analysis was conducted
+with the five MFQ foundation score predicting political orientation. The
+overall model was significant, *R2* = .35, *F* (5, 255) = 26.91, *p* \<
+.05. Higher scores on the harm and fairness foundations predicted a more
+liberal political orientation with harm accounting for 3% of the
+variance and fairness accounting for 6%. Higher scores on ingroup,
+authority, and purity predicted a more conservative orientation
+accounting for 1%, 2%, and 8% on the variance respectively. See *table
+?* for regression coefficients. Next, a regression analysis was
+conducted to determine how well the five MFD scores predicted political
+orientation. The overall model was not significant, *R2* = .16, *F* (5,
+255) = 1.36, *p* = .241. Higher harm scores somewhat predicted more
+liberal orientation accounting for 1% of the variance in political
+orientation. Higher purity scores somewhat predicted more conservative
+orientation accounting for 1% of the variance. See *table ?* for
+regression coefficients.
+
+# Participants
+
+Participants were recruited in two waves as part of a larger
+investigation on priming political and religious attitudes (???).
+Participants were recruited via an online research system (SONA) and
+were given course credit for their participation. 463 participants were
+included in the this study. The study was mostly women (53.9%) and White
+(76.4%) participants with a mix of minority participants: Black (6.1%),
+(3.6%), (4.2%), Native American (1.9%), Mixed (2.9%) and Other (4.9%).
+The average listed age was 19.75 (SD = 200 2.94).
+
+# Materials and Procedure
+
+Data was again collected via Qualtrics. Four fake new stories were
+presented to participants, which were roughly 400 words each. First, all
+news stories included a few sentences describing the use of chemical
+weapons in the Syrian civil war. The news stories were manipulated with
+political (Republican v. Democrat) and religious (religious v. not)
+quotes in a 2 x 2 design. News stories can be found in the online
+materials. Participants also completed the 30-item version of the MFQ as
+described in the introduction. In addition to basic demographics
+(gender, age), participant political orientation was assessed with the
+same scale described in Study 1.
+
+After consenting to participate in the study, participants were randomly
+shown one of the four new articles about Syria’s use of chemical
+weapons. Participants were then asked to write for 5-10 minutes about
+their reaction to Syria’s use of chemical weapons and the needed
+response from the United States. The second wave of data collection
+included different writing prompts designed to capture more of the moral
+foundation areas in their writing. The following writing prompt was
+used, “Please write about your attitudes on abortion (or same-sex
+marriage or environmentalism) as well as your reason for this stance.”
+The three prompts were chosen to create a more varied word set by using
+topics that should elicit words from each moral foundations category by
+soliciting a moral response. In each wave of data collection (Syria
+prompts, moral prompts) the prompt material was randomized between
+participants. Participants then completed the MFQ, demographics, and the
+political orientation scale.
+
+# Results
+
+# Expanding the MFD
+
+In a separate study of 466 university students, participants completed a
+free association task where we asked them to list all the words that
+came to mind from *harm/care*, *fairness/reciprocity*, *loyalty/XX*,
+*authority/XX*, *purity/XX*. They also completed the 15 item MFQ.
+Responses to the free association task were cleaned and stemmed. This
+lead to a new set of moral foundation words: harm-96, fairness-76,
+ingroup-86, authority-81, and purity-80. These concepts were included in
+the full dictionary used for Study 3.
+
+We additionally created a reduced dictionary that included only concepts
+correlated with their respective moral foundations scores. Correlations
+between word frequency and the sum of the MFQ were calculated for each
+foundation and set of concepts. Words were included in the reduced
+dictionary if their correlation was two standard deviations away from
+the mean correlation for that foundation. The reduced dataset included
+the following number of words for each foundation: harm 4, fairness 3,
+ingroup 3, authority 4, and purity 2.
+
+```{r word-association}
+#need the code for the the above stuff
+```
+
+[ERIN, Please do mathy-math here]
+
+# Testing Model Structure
+
+Before testing the theorized differences between liberals and
+conservatives, we sought to test the validity of the MFD using
+Multi-Trait, Multi-Method modelling (MTMM) to determine if the MFD is
+measuring the same latent variables as the MFQ as it should.
+
+```{r mtmm}
+
+```
+
+# Testing Group Differences
+
+```{r mtmm-groupdiffs}
+
+```
+
+# Study 2
+
+## Method
+
+We hypothesized the news sources generally perceived as liberal leaning
+(*NPR* and *The New York Times*) would contain MFD words and valences
+indicating endorsements of the individualizing moral foundations
+(*harm/care* and *fairness/reciprocity*). Additionally, we hypothesized
+the two sources generally perceived to be conservative leaning (*Fox
+News* and *Breitbart*) would feature MFD words and valences indicating
+equal endorsement of all five foundations.
 
@@
 Political articles were collected from the websites of four notable U.S.
-news sources, a process known as web scraping.
-The sources were *NYT*, *NPR*, *Fox News*, and *Breitbart*.
-They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-We determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, the *NYT* and *NPR* are preferred by consumers reporting a liberal bias or lean.
-In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean.
-@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
-At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible.
-
-Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
-For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
-
-Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from the *NYT* and *Breitbart*.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
-Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
-We later ran a process in order to exclude any duplicate articles.
-*Fox News* presented a similar issue.
-We discovered *Fox News* utilized six URLs in addition to the regular politics page.
-These URLs led to pages containing content pertaining the U.S.
-Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
-Once again, duplicates were subsequently eliminated from any analyses.
+news sources, a process known as web scraping. The sources were *NYT*,
+*NPR*, *Fox News*, and *Breitbart*. They were selected for their
+widespread recognition and the fact political partisans have strong
+preferences for some sources over others. We determined the political
+lean of each source by referencing @Mitchell2014's article demonstrating
+the self-reported ideological consistency represented by the consumers
+of several news sources. In general, the *NYT* and *NPR* are preferred
+by consumers reporting a liberal bias or lean. In contrast, *Fox News*
+and *Breitbart* are believed to have a conservative bias or lean.
+@Mitchell2014's article presented political ideology as a scale ranging
+from "consistently liberal" to "consistently conservative." In between
+these extremes lie more moderate positions, including "mostly liberal,"
+"mixed," and "mostly conservative." Owing to the lower number of sources
+analyzed herein, we elected to categorize the sources as either
+"liberal" and "conservative" in order to form a basis for comparison. At
+the time of our data collection, these sources were also selected
+because they were open (i.e., no subscription required to access
+articles), and their websites were designed in a way that made
+webscraping possible.
+
+Political articles in particular were identified and subsequently
+scraped by including the specific URL directing to each source's
+political content in the *R* script. For example, rather than scrape
+from nytimes.com, which would return undesired results (non-political
+features, reviews, etc.), we instead included
+nytimes.com/section/politics so that more or less exclusively political
+content was obtained. All code for this manuscript can be found at
+<https://osf.io/5kpj7/>, and the scripts are provided inline with this
+manuscript written with the *papaja* library [@Aust2017].
+
+Identification of the sources' political URLs presented a problem for
+two of the sources owing to complications with how their particular
+sites were structured. While in the multi-week process of scraping
+articles, we noticed word counts for *NPR* and *Fox News* were not
+growing at a similar pace as those from the *NYT* and *Breitbart*. Upon
+investigation, we found another, more robust URL for political content
+from NPR: their politics content "archive." The page structure on NPR's
+website was such that only a limited selection of articles is displayed
+to the user at a given time. Scraping both the archive and the normal
+politics page ensured we were obtaining most (if not all) new articles
+as they were published. We later ran a process in order to exclude any
+duplicate articles. *Fox News* presented a similar issue. We discovered
+*Fox News* utilized six URLs in addition to the regular politics page.
+These URLs led to pages containing content pertaining the U.S. Executive
+Branch, Senate, House of Representatives, Judicial Branch, foreign
+policy, and elections. Once again, duplicates were subsequently
+eliminated from any analyses.
 
@@
 
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016].
-Using this dataset, we identified word count and average word count per source.
-This process was completed once daily starting in February 2018 until March 2018.
-Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected in April 2018.
+Using the *rvest* library in the statistical package *R*, we pulled body
+text for individual articles from each of the aforementioned sources
+(identified using CSS language) and compiled them into a dataset
+[@Wickham2016]. Using this dataset, we identified word count and average
+word count per source. This process was completed once daily starting in
+February 2018 until March 2018. Starting in mid-March 2018, the process
+was completed twice daily - once in the morning and again in the
+evening. Data collection was terminated once 250,000 words per source
+was collected in April 2018.
 
@@
 
-Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017].
-This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
-At this point, duplicate articles were discarded.
-
-The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@Feinerer2017].
-The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
-The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
-
-Concurrent research by @Jordan2019 assesses the validity of both the MFQ and the MFD through a multi-trait multi-method analysis of the two instruments using multiple samples.
-The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-We were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
-Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
-
-A complete list of the words for each moral foundation area was created from previous experiments.
-The total number of times each of those words was used in an article was calculated.
-This information was merged with the valence values from the @Warriner2013 dataset.
-A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article.
-The final score was multiplied by 100 to represented a weighted percentage.
-Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article.
-Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence.
-Positive values indicate positive valence, and negative values indicate negative valence.
-Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
-See Table \@ref(tab:example-weight) for an example.
+Once data collection ended, the text was scanned using the *ngram*
+package in *R* [@Schmidt2017]. This package includes a word count
+function, which was used to remove articles that came through as blank
+text, as well as to eliminate text picked up from the Disqus commenting
+system used by certain websites. At this point, duplicate articles were
+discarded.
+
+The article text was processed using the *tm* and *ngram* packages in
+*R* in order to render the text in lowercase, remove punctuation, and
+fix spacing issues [@Feinerer2017]. The individual words were then
+reduced to their stems (i.e., *abused* was stemmed to *abus*). The same
+procedure was applied to the MFD words and the words in the
+@Warriner2013 dataset. Using the @Warriner2013 dictionary, the words
+making up each of the five foundations in the MFD were matched to their
+respective valence value.
+
+The @Warriner2013 data includes nearly 14,000 English lemmas that have
+been rated for their valence, arousal, and dominance [mirroring
+@bradley1999]. Word emotion ratings have been used to estimate the
+sentiment of a text - a very popular task within classification
+research - by generally averaging the valence scores of the the words
+matched between the text and the available norms [@leveau2012]. Other
+suggestions include the simple summation of word's positive or negative
+valence from a text or respective weighting based on word frequency
+[@hutto2021; @loria2020]. In each of these cases, an overall polarity is
+desired, which is the case here, creating an overall score for each of
+the five MFD domains. Sentiment coding packages often score items from
+-1 to 1 or other values around zero wherein negative scores represent
+negative sentiment, while positive scores represent positive sentiment.
+The @Warriner2013 dataset ranges from 1 (*unhappy*) to 9 (*happy*).
+Thus, to ensure that we anchored their valences around zero, we
+*z*-scored the dataset so that negative scores represented values below
+the average sentiment and positive scores represented values above the
+average sentiment.
+
+Concurrent research by @Jordan2019 assesses the validity of both the MFQ
+and the MFD through a multi-trait multi-method analysis of the two
+instruments using multiple samples. The instruments and foundation areas
+are being analyzed against one another, in order to test reliability, as
+well as against the Congressional Record in order to test predictive
+validity for political orientation. We were able to identify a number of
+potential new words that, if added to the MFD, could comprise a
+dictionary with greater validity, and less likelihood of zero percent
+texts, as this often occurs with the current MFD. Those results have
+informed this analysis, and their updated findings may change the
+underlying dictionary used in this analysis (albeit, we do not expect
+any changes in the results presented below).
+
+A complete list of the words for each moral foundation area was created
+from previous research. The total number of times each of those words
+was used in an article was calculated. This information was merged with
+the valence values from the @Warriner2013 dataset. A weighted score was
+calculated by multiplying the frequency of occurrence within a document
+times the *z*-scored valence values and divided by the word count for
+that article. The final score was multiplied by 100 to represented a
+weighted percentage. Finally, the weighted scores were summed within in
+each article to get a total weighted percentage of the use of moral area
+specific words by article. Valences were *z*-scored in order to
+eliminate any ambiguity regarding the direction of the valence. Positive
+values indicate positive valence, and negative values indicate negative
+valence. Words were categorized in accordance to their MFD affiliation,
+creating a weighted sum for each moral foundation. See Table
+\@ref(tab:example-weight) for an example.
 
 ```{r stem_text, eval=TRUE, include=FALSE}
-final = read.csv("./exp1_data/finaldata.csv", stringsAsFactors = F)
+final = read.csv("./study1_data/finaldata.csv", stringsAsFactors = F)
 final = na.omit(final) #one weird NA line
@@
 ##open the Warriner data for later
-warriner = read.csv("./exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+getwd()
+warriner = read.csv("../../study1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
 warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
@@
 #read in the harm total words from the mtmm project
-harm_all = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all = read.csv("./study1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all = read.csv("./study1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all = read.csv("./study1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all = read.csv("./study1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all = read.csv("./study1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 
-We calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included average *z*-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula [@Kincaid1975].
-Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the U.S.
-grade level at which one should be able to comfortably read the passage [@Kincaid1975].
-For example, a text with a readability score of 11 should be easily read by a U.S.
-high school junior.
-
-As seen in Table \@ref(tab:exp1-source-descriptives), the sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
-*NYT* published the greatest number of articles as well as total words.
-*Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles.
-Per individual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, *Fox News* articles had the lowest reading grade level on average, while *NYT* had the highest.
-This result might be attributable to the greater number of tokens in the average *NYT* article compared to *Fox News*.
-The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
-Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.
+We calculated descriptive statistics for each news source in order to
+understand any and all fundamental linguistic differences in the
+sources' use of English. Statistics calculated included average
+*z*-scored valence of the unique words per article, number of articles
+per source, total number of words per source, average number of tokens
+(words) per article in each source, average number of types (unique
+words) per article in each source, and mean readability level per
+source. Readability statistics were calculated using the Flesch-Kincaid
+Grade Level Readability formula [@Kincaid1975]. Readability is
+calculated using a formula where the total number of syllables, words,
+and sentences in a given passage are determinants of its difficulty. The
+obtained value is intended to match up with the U.S. grade level at
+which one should be able to comfortably read the passage [@Kincaid1975].
+For example, a text with a readability score of 11 should be easily read
+by a U.S. high school junior.
+
+As seen in Table \@ref(tab:exp1-source-descriptives), the sources are
+similar in some aspects yet different in others. Valence appears to be
+slightly positive across all sources. The large standard deviations seem
+to indicate little to no presence of a difference in valence across
+sources. *NYT* published the greatest number of articles as well as
+total words. *Breitbart* featured the lowest number of articles, and
+*NPR* the lowest number of total words from all articles. Per individual
+article, however, *Breitbart* appears to feature the highest average
+number of words as well as unique words. Once again the standard
+deviations call into question any apparent differences between sources.
+Finally, *Fox News* articles had the lowest reading grade level on
+average, while *NYT* had the highest. This result might be attributable
+to the greater number of tokens in the average *NYT* article compared to
+*Fox News*. The standard deviations for readability suggest the presence
+of a diverse array of articles for each source, ranging from low to high
+reading level. Large standard deviations suggest the sources feature a
+lot of overlap between them in their representation of scores.
 
@@
 
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
-Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-Therefore, the models were calculated by: Weighted Score ~ Political Lean + (~1|Source).
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp1-table).
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, we observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
+To analyze if news sources adhered to differences in word use based on
+their target audience, we utilized a multilevel model (MLM) to analyze
+the data. MLM is a regression technique that allows one to control for
+the repeated measurement and nested structured of the data, which
+creates correlated error [@Gelman2006]. Using the *nlme* library in *R*
+[@Pinheiro2017], each foundation's weighted percentage was predicated
+here by the political lean of the news source, using the individual news
+sources as a random intercept to control for the structure of the data.
+Therefore, the models were calculated by: Weighted Score \~ Political
+Lean + (\~1\|Source).
+
+The multilevel model did not indicate the presence of any significant or
+practical effect of political lean for any of the five moral
+foundations. The strongest effect size was observed for the
+*authority/respect* foundation, but the effect was in the opposite
+direction from what was originally hypothesized - liberal sources tended
+to use more *authority/respect* words than did conservative sources.
+Descriptive and test statistics, *p*-values and effect sizes (Cohen's
+*d*) can be found in Table \@ref(tab:exp1-table). To interpret the
+weighted scores, one can examine the mean and standard deviations for
+each. A zero score for the mean, with a non-zero standard deviation,
+would indicate a perfect balance of positive and negative words in each
+category, likely representing a neutral tone when all words are
+considered. Negative percentages would indicate more representation of
+the negative words in the MFD area, while positive percentages indicate
+an endorsement of the positive words in a MFD. Therefore, we suggest
+using the sign of the mean score to determine the directionality of the
+endorsement for the MFD (positive, neutral, negative), and the standard
+deviation to ensure that a zero score is not zero endorsement (i.e., a
+SD of zero indicates no words were used). Based on the weighted percent
+values for the five foundations, we observed that MFD words seem to make
+up a small portion of the article text. Furthermore, the observed
+percentages and means appear to indicate a generally positive
+endorsement of all five foundations across both liberal and conservative
+sources.
 
@@
 
-The results obtained in Study 1 fail to support the differences predicted by MFT.
-First, differences between liberal and conservative news sources failed to reach statistical or practical (effect size) significance for any foundations.
-Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
-Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
-Overall, the results lend strong support to the case against the MFD and weakens the case generally for MFT.
-
-However, one possible limitation of the current data is the generalness of the corpus.
-The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-To address this limitation, two changes that were subsequently employed in Study 2.
-First, we elected to include more news sources for web scraping and analysis in addition to the four used in Study 1.
-Second, we chose to focus  data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court and the U.S.
-government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Study 2 is the best test of the MFT and the MFD in the context of partisan news.
+The results obtained in Study 1 fail to support the differences
+predicted by MFT. First, differences between liberal and conservative
+news sources failed to reach statistical or practical (effect size)
+significance for any foundations. Second, looking purely at the
+direction of the differences, the results run completely contrary to the
+differences expected by MFT. Conservative sources scored higher on
+concern for harm and fairness while liberal sources scored higher on
+concern for loyalty, authority, and purity. Overall, the results lend
+strong support to the case against the MFD and weakens the case
+generally for MFT.
+
+However, one possible limitation of the current data is the generalness
+of the corpus. The selection of the broad and amorphous topic of
+"political news" may have led to the scraping of large numbers of
+articles with little to no moral-centric content. To address this
+limitation, two changes that were subsequently employed in Study 2.
+First, we elected to include more news sources for web scraping and
+analysis in addition to the four used in Study 1. Second, we chose to
+focus data collection efforts on two heavily moralized events in the
+Trump administration: (1) the nomination and confirmation of Justice
+Brett Kavanaugh to the U.S. Supreme Court and the U.S. government
+shutdown in December 2018 through January 2019 over disagreements about
+funding a U.S.-Mexico border wall. Hence, Study 2 is the best test of
+the MFT and the MFD in the context of partisan news.
 
@@
 
-In contrast to Study 1, we approached Study 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For the second study, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-We tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, we analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under MFT.
+In contrast to Study 1, we approached Study 2 with the intention to
+confirm the method employed was valid for the analysis of the scraped
+text as well as for any inferences drawn from the analyses. For the
+second study, we hypothesized that news sources perceived as liberal
+will exhibit positive endorsements of the individualizing moral
+foundations (*harm/care* and *fairness/reciprocity*) in their articles
+reporting on both the Kavanaugh confirmation hearing as well as the
+2018-2019 government shutdown. News sources perceived as conservative
+are hypothesized to positively endorse all five foundations equally in
+their coverage of the Kavanaugh hearing and the government shutdown. We
+tested the hypothesis by analyzing the content scraped from news
+sources' web pages spanning the two weeks before (September 13, 2018)
+and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing,
+owing to its prominence in the news. Likewise, we analyzed content
+spanning two weeks before the start of the government shutdown (December
+8, 2018) to two weeks following the end of the shutdown (February 8,
+2019). The content will be analyzed for valence and moral alignment
+under MFT.
 
@@
 
-Articles pertaining to the Brett Kavanaugh Supreme Court confirmation hearing and the 2018-2019 U.S.
-Government shutdown were scraped from the websites of 10 U.S.
-news sources.
-As in Study 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by the highest proportion of consistent liberals were the *NYT*, *NPR*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
-The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
+Articles pertaining to the Brett Kavanaugh Supreme Court confirmation
+hearing and the 2018-2019 U.S. Government shutdown were scraped from the
+websites of 10 U.S. news sources. As in Study 1, these sources were
+selected owing to their favorability among political partisans according
+to @Mitchell2014. The sources favored by the highest proportion of
+consistent liberals were the *NYT*, *NPR*, *Slate*, *Huffington Post*,
+and *Politico* [@Mitchell2014]. The sources favored by the highest
+proportion of consistent conservatives included *Fox News*, *Breitbart*,
+*The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*. These sources
+were primarily selected due to their political lean but also due to our
+ability to webscrape their contents without a subscription based
+service. Political articles referencing Brett Kavanaugh's nomination
+process were identified and subsequently scraped by including the URL
+for each source's coverage of the nomination in the *R* script.
 
@@
 
-Using the *rvest* and *RSelenium* libraries, we pulled body text for individual articles from each of the aforementioned 10 news sources and compiled them together [@Wickham2016; @harrison_rselenium_2020].
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the partial U.S.
-Government shutdown of 2018-2019.
-The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, we elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
+Using the *rvest* and *RSelenium* libraries, we pulled body text for
+individual articles from each of the aforementioned 10 news sources and
+compiled them together [@Wickham2016; @harrison_rselenium_2020]. Using
+this dataset, we identified word count and average word count per
+source. This process was run for articles pertaining to Kavanaugh's
+nomination that were published between September 13, 2018 and October
+11, 2018 inclusive. This date range was selected in reference to the
+widely-publicized and viewed nomination hearing on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and
+the end date at October 11 (two weeks after the hearing) so that we
+could capture a large amount of data (roughly one month) during which
+Kavanaughnaugh's nomination was at its peak saturation in news coverage.
+
+The same process was followed for scraping articles related to the
+partial U.S. Government shutdown of 2018-2019. The articles scraped were
+published between December 8, 2018 and February 8, 2019 inclusive. Once
+again, we elected to scrape articles published two weeks before and
+after the event in question in order to capitalize on the shutdown's
+saturation in American news media.
 
@@
 
-As in Study 1, the text was scanned with *ngram* [@Schmidt2017].
-Again, blank articles, text from the Disqus system, and duplicate articles were removed.
-The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017].
-Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).
-Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-We obtained the words' percent occurrence in the text.
-Percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
+As in Study 1, the text was scanned with *ngram* [@Schmidt2017]. Again,
+blank articles, text from the Disqus system, and duplicate articles were
+removed. The text was processed and stemmed in order to convert to a
+usable form for further analysis [@Feinerer2017]. Each individual word
+was reduced to its stem (i.e., *diseased* was stemmed to *diseas*). Once
+again, the same procedure was applied to the MFD words and the words in
+the @Warriner2013 dataset. We obtained the words' percent occurrence in
+the text. Percents were multiplied by *z*-scored valence and categorized
+into their proper MFD category.
 
@@
 #read in the harm total words from the mtmm project
-harm_all_kav = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_kav = read.csv("./study1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all_kav = read.csv("./study1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all_kav = read.csv("./study1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all_kav = read.csv("./study1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all_kav = read.csv("./study1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 #read in the harm total words from the mtmm project
-harm_all_gs = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_gs = read.csv("./study1_data/harm_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_fair_gs, echo = F, include=FALSE}
-fair_all_gs = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
+fair_all_gs = read.csv("./study1_data/fair_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
-ingroup_all_gs = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
+ingroup_all_gs = read.csv("./study1_data/ingroup_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_authority_gs, echo = F, include=FALSE}
-authority_all_gs = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
+authority_all_gs = read.csv("./study1_data/authority_words_total.csv", stringsAsFactors = F)
 
@@
 ```{r create_datasets_purity_gs, echo = F, include=FALSE}
-purity_all_gs = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
+purity_all_gs = read.csv("./study1_data/purity_words_total.csv", stringsAsFactors = F)
 
@@
 
-We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Study 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
-
-Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
-The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, *Sean Hannity* appears to have published only 27 articles while *Breitbart* published 757 articles on this topic.
-Valence was found to be slightly positive across all sources.
-*Fox News* produced the most total words with the most tokens on average.
-This is likely due to the fact *Fox News* transcribes many of their videos and publishes them in article form.
-*Politico* featured the highest number of types on average.
-*Rush Limbaugh* featured the lowest readability score on average by grade level while *Slate* featured the highest grade-level readability score.
-The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language, as there is likely a lot of overlap between sources' use of language.
+We calculated descriptive statistics for each news source per topic in
+order to reveal the presence (if any) of linguistic differences in the
+sources' use of language. As in Study 1, statistics calculated include
+*z*-scored valence, number of articles per source, total words per
+source, mean tokens per article in each source, mean types per article
+in each source, and mean readability level (using the Flesch-Kincaid
+Grade Level Readability formula) per source [@Kincaid1975].
+
+Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive
+statistics for sources' writing on the Kavanaughnaugh confirmation
+hearing. The sources were similar in most basic linguistic aspects,
+except for number of articles. For example, *Sean Hannity* appears to
+have published only 27 articles while *Breitbart* published 757 articles
+on this topic. Valence was found to be slightly positive across all
+sources. *Fox News* produced the most total words with the most tokens
+on average. This is likely due to the fact *Fox News* transcribes many
+of their videos and publishes them in article form. *Politico* featured
+the highest number of types on average. *Rush Limbaugh* featured the
+lowest readability score on average by grade level while *Slate*
+featured the highest grade-level readability score. The large standard
+deviations for these statistics, however, preclude conclusions regarding
+differences in the sources' use of language, as there is likely a lot of
+overlap between sources' use of language.
 
@@
 
-Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive statistics for articles about the partial government shutdown.
-Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each source on this topic.
-*Sean Hannity*, *Rush Limbaugh*, and *The Blaze* published fewer than 100 articles while *Fox News* published 1,013 articles.
-*Fox News* again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
-*Politico* had the most types on average.
-For this topic, *Fox News* featured the lowest reading grade level while *Slate* featured the highest reading grade level.
-For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
+Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive
+statistics for articles about the partial government shutdown. Like the
+Kavanaugh hearing, the sources were similar in average valence (slightly
+positive). Once again, there was variation in the number of articles
+published by each source on this topic. *Sean Hannity*, *Rush Limbaugh*,
+and *The Blaze* published fewer than 100 articles while *Fox News*
+published 1,013 articles. *Fox News* again featured the most total words
+and mean tokens, but this is likely due to to the presence of a large
+amount of video transcriptions that the organization published as
+articles. *Politico* had the most types on average. For this topic, *Fox
+News* featured the lowest reading grade level while *Slate* featured the
+highest reading grade level. For each statistic, the excessively high
+standard deviations render any assertions regarding linguistic
+differences inconclusive on a descriptive level due to the
+aforementioned overlap in sources' language use.
 
@@
 
-We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Study 1.
-Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-Two separate MLMs were constructed from datasets compiled for each topic of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a statistically significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
-There were no other significant or practical effects of political lean for any of the other four moral foundations.
-The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp2-tablekav).
+We utilized a multilevel model (MLM) to analyze if news sources
+leveraged different vocabularies based on target audience in the same
+manner as Study 1. Each foundation's weighted percentage was predicted
+by the source's political lean, using the individual source as a random
+intercept to control for the nested data structure. Two separate MLMs
+were constructed from datasets compiled for each topic of interest: the
+Kavanaugh hearing and the partial government shutdown of 2018-2019.
+
+For the Kavanaugh topic, the multilevel model indicated the presence of
+a statistically significant effect for *harm/care*, but the practical
+effect denoted by Cohen's *d* was found to be small. There were no other
+significant or practical effects of political lean for any of the other
+four moral foundations. The effect for *harm/care* was in the
+hypothesized direction with liberal sources tending to use more
+positively *harm/care* words than conservative sources. Descriptive and
+test statistics, *p*-values and effect sizes (Cohen's *d*) can be found
+in Table \@ref(tab:exp2-tablekav).
 
@@
 
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations (see Table \@ref(tab:exp2-tablegs)).
-A small-to-medium effect size was observed for *authority/respect*.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Study 1 in which the largest effect size was observed for *authority/respect*.
-As noted before, the effect found in Study 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Study 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Study 1.
-As in Study 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
+For news articles about the partial U.S. Federal Government Shutdown of
+2018-2019, there were no significant or practical effects of political
+lean for the moral foundations (see Table \@ref(tab:exp2-tablegs)). A
+small-to-medium effect size was observed for *authority/respect*. The
+effect was in the predicted direction as well, as conservative sources
+tended to offer more positive endorsements of the foundation than
+liberal sources. This effect was similar to Study 1 in which the largest
+effect size was observed for *authority/respect*. As noted before, the
+effect found in Study 1 was in the opposite direction as what was
+hypothesized. Thus, it is difficult to draw comparisons between the two
+studies despite the similar pattern for effect size. Owing to a lack of
+similar effects for either Study 1 or the Kavanaugh topic, there is
+doubt as to whether or not a practical or generalized effect exists for
+*authority/respect*.
+
+Based on the weighted percent values for the five foundations applied to
+both topics, MFD words seem to make up little of the article text. A
+similar pattern was observed for the results in Study 1. As in Study 1,
+the percentages and means seem to indicate a generally positive
+endorsement of all five moral foundations across both political
+leanings.
 
@@
 
-# Study 3
-
-Results from Study 1 and 2 indicated that no differences were found in the MFD for Liberal and Conservative sources using the traditional dictionary and valence weighting.
-The MFD was developed in conjunction with the Moral Foundations Questionnaire (MFQ), using the same five latent areas.
-In this set of studies, we examined the MFD and MFQ within the same study.
-The first two sub-studies were used to develop a (potentially) larger dictionary for the MFD and collect data on both scales.
-The last sub-study examined the MFD and MFQ using multi-trait multi-method analysis [CITE WIDAMEN AND BYRNE].
-
-DESCRIBE MTMM
-
-## Study 3.1
-
-In this study, participants were given a word association task elicit additional semantically related word forms for each moral foundation.
-This data was used to expand the MFD for each latent area to determine if these additional words could improve scores and test measurement relation to the MFQ in Study 3.3.
-
-### Participants
-
-```{r demos-mtmm-study-3.1, include = FALSE}
-exp1data <- import("exp3_data/study3.1_fixed_associations.csv")
-
-##clear out completely columns we don't need
-crapcolumns <- c(1, 2, 3, 5:14)
-finalsample <- exp1data[ , -crapcolumns]
-
-##accuracy
-summary(finalsample) #Check Q15_1 and Q23 for in-range scores -WP
-finalsample$Q23 <- factor(finalsample$Q23,
-                         levels = 1:3,
-                         labels = c("Democrat", "Republican", "Independent"))
-
-#missing 
-#by people 
-missing_demo1 <- apply(finalsample, 1, percentmiss) 
-table(missing_demo1)
-
-replacepeople1 <- subset(finalsample, missing_demo1 <= 5)  #we are using 5%, yes? 
-#by column 
-apply(replacepeople1, 2, percentmiss) 
-#missing data is on the politics scale which we don't want to replace
-
-finalsample <- replacepeople1
-summary(finalsample)
-
-party <- table(finalsample$Q23)
-##be sure to exclude the writing columns columns 2:6 
-#I take it I should also remove column 1: ResponseId? 
-##outliers
-mahal1 <- mahalanobis(finalsample[ , -c(1:6,22,23)], 
-                    colMeans(finalsample[ , -c(1:6,22,23)], na.rm = TRUE),
-                    cov(finalsample[ , -c(1:6,22,23)], use="pairwise.complete.obs"))
-#mahal1
-cutoff1 <- qchisq(1 - .001,ncol(finalsample[ , -c(1:6,22,23)]))
-cutoff1
-ncol(finalsample[ , -c(1:6,22,23)])
-summary(mahal1 < cutoff1) #Hmm what to do w/ NAs?? -WP
-noout1 <- subset(finalsample, mahal1 < cutoff1)
-
-##assumptions
-#correlations for MFQ
-correlations1 <- cor(noout1[,-c(1:6,22,23)], use="pairwise.complete.obs")
-correlations1
-symnum(correlations1)
-
-#making the random stuff
-random1 <- rchisq(nrow(noout1), 7)
-fake1 <- lm(random1~., data=noout1[ , -c(1:6)])
-#normal
-standardized1 <- rstudent(fake1)
-hist(standardized1, breaks=15)
-
-#linear
-{qqnorm(standardized1) 
-abline(0,1)}
-#homog + s
-fitvalues1 <- scale(fake1$fitted.values)
-{plot(fitvalues1, standardized1) 
-abline(0,0)
-abline(v = 0)}
-
-####create the MFQ subscales####
-noout1$harmMFQ <- apply(noout1[ , 7:9], 1, sum)
-noout1$fairMFQ <- apply(noout1[ , 10:12], 1, sum)
-noout1$ingroupMFQ <- apply(noout1[ , 13:15], 1, sum)
-noout1$authorityMFQ <- apply(noout1[ , 16:18], 1, sum)
-noout1$purityMFQ <- apply(noout1[ , 19:21], 1, sum)
-```
-
-`r nrow(exp1data)` participants were collected from a large Midwestern university.
-Participants were given course credit for their introductory psychology course for completing the study.
-`r nrow(finalsample)` participants had less than five percent missing data and were retained for analyses.
-Participants were asked to denote their political party, and `r printnum(party["Democrat"]/sum(party)*100,digits = 1)`% indicated they were Democrats, `r printnum(party["Republican"]/sum(party)*100,digits = 1)`% were Republican, and `r printnum(party["Independent"]/sum(party)*100,digits = 1)`% indicated they were Independent.
-
-### Materials and Procedure
-
-A complete example of the survey can be found online at https://osf.io/5uqfn.
-First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech.
-Next, the free association task, similar to that used in CITE @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind".
-The participants were then given three example free association cues, *lost*, *old*, and *article*.
-For each cue, participants were asked to write all the words that come to mind.
-To elicit free association to the moral foundation areas, participants were given the following instructions:
-
-"Moral Foundations Theory states that when making moral judgments/decisions, the concerns people have can be divided into five categories.
-Below are labels of each of these five categories.
-You will then be asked to list words you think are associated with each of the labels."
-
-Each of the foundation pairs were listed together (i.e., *harm/care*, *fairness/cheating*) with a space for participants to list their free association concepts.
-After the free association task, participants were then given the 15-items from the moral relevance section of the MFQ as described in the introduction.
-Last, participants were asked to denote their political orientation from 1 *conservative* to 10 *liberal*, as well as which political party they associated with: Democrat, Republican, and Independent.
-The survey was delivered through Qualtrics, and participants were recruited through the online participant management system for the university (SONA).
-Each participant signed an online consent form at the beginning of the study and was given participation credit at the end of the study.
-
-### Results
-
-All data was screening for inaccurate responses, as well as missing data, as described in the participant section.
-Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise.
-The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012 CITE, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r apa_num(cutoff1)`.
-These participants were excluded from further analyses, representing `r nrow(noout1)` final participants.
-The final MFQ data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.
-
-The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
-The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`).
-Participants free association responses were processed using the *tm* [CITE] and *corpus* [CITE] libraries after spell checking.
-Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*.
-We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary.
-Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manually recode all word forms.
-Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses.
-The complete set of word frequencies for each foundation can be found in our supplemental materials.
-
-```{r harm-analysis-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q27 <- as.character(noout1$Q27)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q27[i] <- paste(unlist(
-    text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-harm_corpus <- Corpus(VectorSource(noout1$Q27))
-harm_TDM <- as.matrix(TermDocumentMatrix(harm_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-harm_freq <- data.frame(Word = rownames(harm_TDM),
-                       Freq = rowSums(harm_TDM),
-                       row.names = NULL)
-harm_freq$Word <- as.character(harm_freq$Word)
-harm_freq$percent <- harm_freq$Freq/nrow(noout1) *100
-
-write.csv(harm_freq, "exp3_data/study3.1_harm_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-harm_words <- harm_freq$Word[harm_freq$percent >=1]
-##turn sideways to add to dataset
-harm_TDM  <- as.data.frame(t(harm_TDM))
-harm_TDM  <- harm_TDM[ , harm_words]
-
-##final dataset for harm
-harm_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
-                   harm_TDM)
-
-harm_cor <- apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})
-
-harmcut <- mean(harm_cor) + 2*sd(harm_cor)
-harm_words_reduce <- names(harm_cor[abs(harm_cor) >= harmcut])
-```
-
-```{r fair-analysi-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q29 = as.character(noout1$Q29)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q29[i] <- paste(unlist(
-    text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-fair_corpus <- Corpus(VectorSource(noout1$Q29))
-fair_TDM <- as.matrix(TermDocumentMatrix(fair_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-fair_freq <- data.frame(Word = rownames(fair_TDM),
-                       Freq = rowSums(fair_TDM),
-                       row.names = NULL)
-fair_freq$Word <- as.character(fair_freq$Word)
-fair_freq$percent <- fair_freq$Freq/nrow(noout1) *100
-
-write.csv(fair_freq, "exp3_data/study3.1_fair_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-fair_words <- fair_freq$Word[fair_freq$percent >=1]
-##turn sideways to add to dataset
-fair_TDM <- as.data.frame(t(fair_TDM))
-fair_TDM <- fair_TDM[ , fair_words]
-
-##final dataset for fair
-fair_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
-                   fair_TDM)
-
-fair_cor <- apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})
-
-faircut <- mean(fair_cor) + 2*sd(fair_cor)
-fair_words_reduce <- names(fair_cor[abs(fair_cor) >= faircut])
-```
-
-```{r ingroup-analysis-3.1, include=FALSE}
-#q27 through 34 are the writing columns
-noout1$Q30 <- as.character(noout1$Q30)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q30[i] <- paste(unlist(
-    text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-ingroup_corpus <- Corpus(VectorSource(noout1$Q30))
-ingroup_TDM <- as.matrix(TermDocumentMatrix(ingroup_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-ingroup_freq <- data.frame(Word = rownames(ingroup_TDM),
-                       Freq = rowSums(ingroup_TDM),
-                       row.names = NULL)
-ingroup_freq$Word <- as.character(ingroup_freq$Word)
-ingroup_freq$percent <- ingroup_freq$Freq/nrow(noout1) *100
-
-write.csv(ingroup_freq, "exp3_data/study3.1_ingroup_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >=1]
-##turn sideways to add to dataset
-ingroup_TDM <- as.data.frame(t(ingroup_TDM))
-ingroup_TDM <- ingroup_TDM[ , ingroup_words]
-
-##final dataset for ingroup
-ingroup_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
-                   ingroup_TDM)
-
-ingroup_cor <- apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})
-
-ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
-ingroup_words_reduce <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
-```
-
-```{r authority-analysis-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q32 <- as.character(noout1$Q32)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q32[i] <- paste(unlist(
-    text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-authority_corpus <- Corpus(VectorSource(noout1$Q32))
-authority_TDM <- as.matrix(TermDocumentMatrix(authority_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-authority_freq <- data.frame(Word = rownames(authority_TDM),
-                       Freq = rowSums(authority_TDM),
-                       row.names = NULL)
-authority_freq$Word <- as.character(authority_freq$Word)
-authority_freq$percent <- authority_freq$Freq/nrow(noout1) *100
-
-write.csv(authority_freq, "exp3_data/study3.1_authority_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-authority_words <- authority_freq$Word[authority_freq$percent >=1]
-##turn sideways to add to dataset
-authority_TDM <- as.data.frame(t(authority_TDM))
-authority_TDM <- authority_TDM[ , authority_words]
-
-##final dataset for authority
-authority_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
-                   authority_TDM)
-
-authority_cor <- apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})
-
-authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
-authority_words_reduce <- names(authority_cor[abs(authority_cor) >= authoritycut])
-```
-
-```{r purity-analysis-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q34 <- as.character(noout1$Q34)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q34[i] <- paste(unlist(
-    text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-purity_corpus <- Corpus(VectorSource(noout1$Q34))
-purity_TDM <- as.matrix(TermDocumentMatrix(purity_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-purity_freq <- data.frame(Word = rownames(purity_TDM),
-                       Freq = rowSums(purity_TDM),
-                       row.names = NULL)
-purity_freq$Word <- as.character(purity_freq$Word)
-purity_freq$percent <- purity_freq$Freq/nrow(noout1) *100
-
-write.csv(purity_freq, "exp3_data/study3.1_purity_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-purity_words <- purity_freq$Word[purity_freq$percent >=1]
-##turn sideways to add to dataset
-purity_TDM <- as.data.frame(t(purity_TDM))
-purity_TDM <- purity_TDM[ , purity_words]
-
-##final dataset for purity
-purity_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
-                   purity_TDM)
-
-purity_cor <- apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})
-
-puritycut <- mean(purity_cor) + 2*sd(purity_cor)
-purity_words_reduce <- names(purity_cor[abs(purity_cor) >= puritycut])
-```
-
-This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`.
-These concepts were included in the full dictionary used for Study 3.3.
-We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
-Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts.
-Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation.
-The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`, ingroup `r length(ingroup_words_reduce)`, authority `r length(authority_words_reduce)`, and purity `r length(purity_words_reduce)`.
-
-## Study 3.2
-
-this section is about the writing
-
-### Participants
-
-```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
-sample1 <- read.csv("exp3_data/study3.2_fixed_sample 1.csv", stringsAsFactors = F)
-sample2 <- read.csv("exp3_data/study3.2_fixed_sample 2.csv", stringsAsFactors = F)
-
-##merge files together
-fullsample <- merge(sample1, sample2, all = TRUE)
-
-##merge together the writing samples
-#q24, q25, q26, q7 
-fullsample$writing <- apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
-                           1, function(x) toString(na.omit(x)))
-
-##clear out completely columns we don't need
-crapcolumns <- c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
-finalsample <- fullsample[ , -crapcolumns]
-
-##accuracy
-summary(finalsample[ , 2:40])
-
-finalsample$Q10 <- factor(finalsample$Q10,
-                         levels = 1:2,
-                         labels = c("Man", "Woman"))
-finalsample$Q11 <- as.numeric(finalsample$Q11)
-finalsample$Q12 <- factor(finalsample$Q12,
-                         levels = 1:7,
-                         labels = c("White", "Black", 
-                                    "Hispanic", "Asian",
-                                    "Native American", 
-                                    "Mixed", "Other"))
-
-gender <- table(finalsample$Q10)/sum(table(finalsample$Q10))*100
-race <- table(finalsample$Q12)/sum(table(finalsample$Q12))*100
-
-write.csv(finalsample, 'exp3_data/study3.2_finalsample.csv', row.names = FALSE)
-newMFD <- import('exp3_data/study3.2_finalsample_newMFD.csv')
-colnames(newMFD)[1:41] <- colnames(finalsample)[1:41]
-newMFD <- newMFD[,c(1,42:55)]
-finalsample <- merge(finalsample, newMFD, by = "ResponseId")
-
-##take out the people with less than 25 words
-##use the ngram library to examine the data
-##preprocess only works on one string at a time, so going to use a loop go through all the rows (apply won't work because we only want to work on one column)
-
-for (i in 1:nrow(finalsample)) {
-
-  finalsample$writing[i] <- preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
-  finalsample$wordcount[i] <- string.summary(finalsample$writing[i])$words
-
-}
-
-#remove small words people
-finalwords <- subset(finalsample, wordcount >=25)
-
-##check out missing data
-#missing by row
-missing <- apply(finalwords, 1, percentmiss)
-table(missing)
-goodrows <- subset(finalwords, missing <= 5)
-
-#missing by column
-apply(goodrows, 2, percentmiss)
-
-##don't fill in Q10 to the end, be sure to merge these back together
-goodcolumns <- goodrows[ , -c(32:42)]
-badcolumns <- goodrows[ , c(32:42)]
-
-#fill in missing data points
-tempnomiss <- mice(goodcolumns)
-nomiss <- complete(tempnomiss, 1)
-summary(nomiss)
-#merge
-allcolumns <- cbind(nomiss, badcolumns) 
-summary(allcolumns)
-
-##outliers
-mahal2 <- mahalanobis(allcolumns[ , -c(1,46:56)], 
-                    colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
-                    cov(allcolumns[ , -c(1,46:56)], use="pairwise.complete.obs"))
-#mahal2
-cutoff2 <- qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
-cutoff2
-ncol(allcolumns[ , -c(1,46:56)])
-summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
-noout2 <- subset(allcolumns, mahal2 < cutoff2)
-
-##assumptions on the questions i.e., not Q10 to the end
-#correlations
-correlations2 <- cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
-#correlations2
-symnum(correlations2)
-
-#the random stuff
-random2 <- rchisq(nrow(noout2), 7)
-fake2 <- lm(random2~., data=noout2[ , -c(1,46:56)])
-
-#normal
-standardized2 <- rstudent(fake2)
-hist(standardized2, breaks=15)
-
-#linear
-{qqnorm(standardized2)   
-abline(0,1)}
-
-#homog + s
-fitvalues2 <- scale(fake2$fitted.values)
-{plot(fitvalues2, standardized2) 
-abline(0,0)
-abline(v = 0)}
-
-####create the MFQ subscales####
-noout2$harmMFQ <- apply(noout2[ , 2:4], 1, sum)
-noout2$fairMFQ <- apply(noout2[ , 5:7], 1, sum)
-noout2$ingroupMFQ <- apply(noout2[ , 8:10], 1, sum)
-noout2$authorityMFQ <- apply(noout2[ , 11:13], 1, sum)
-noout2$purityMFQ <- apply(noout2[ , 14:16], 1, sum)
-```
-
-Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes.
-Participants were recruited via an online research system (SONA) and were given course credit for their participation.
-`r nrow(finalsample)` participants were included in the this study.
-The study was mostly women (`r printnum(gender["Woman"], digits = 1)`%) and White (`r printnum(race["White"], digits = 1)`%) participants with a mix of minority participants: Black (`r printnum(race["Black"], digits = 1)`%), (`r printnum(race["Hispanic"], digits = 1)`%), (`r printnum(race["Asian"], digits = 1)`%), Native American (`r printnum(race["Native American"], digits = 1)`%), Mixed (`r printnum(race["Mixed"], digits = 1)`%) and Other (`r printnum(race["Other"], digits = 1)`%).
-The average listed age was `r printnum(mean(finalsample$Q11, na.rm = T))` (*SD* = `r printnum(sd(finalsample$Q11, na.rm = T))`).
-
-###	Materials and Procedure
-
-Data was again collected via Qualtrics (https://osf.io/qr3gv).
-Four fake new stories were presented to participants, which were roughly 400 words each.
-First, all news stories included a few sentences describing the use of chemical weapons in the Syrian civil war.
-The news stories were manipulated with political (Republican v.
-Democrat) and religious (religious v.
-not) quotes in a 2 x 2 design.
-News stories can be found in the online materials.
-Participants also completed the 30-item version of the MFQ as described previously.
-In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Study 3.1.
-
-After consenting to participate in the study, participants were randomly shown one of the four new articles about Syria's use of chemical weapons.
-Participants were then asked to write for 5-10 minutes about their reaction to Syria's use of chemical weapons and the needed response from the United States.
-The second wave of data collection included different writing prompts designed to capture more of the moral foundation areas in their writing.
-The following writing prompt was used, "Please write about your attitudes on abortion (or same-sex marriage or environmentalism) as well as your reason for this stance." The three prompts were chosen to create a more varied word set by using topics that should elicit words from each moral foundations category by soliciting a moral response.
-In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants.
-Participants then completed the MFQ, demographics, and the political orientation scale.
-
-### Results
-
-Participant data was first spell checked and screening for inaccurate responses.
-Participants who did not write more than fifty words in response to a given prompt were excluded (*n* = `r nrow(finalsample) - nrow(finalwords)`).
-One missing datapoint was estimated using the *mice* library from *R* [@CITE] for a missing MFQ question, and all other missing data was present in the demographics sections, which were not filled in.
-The MFQ data were screened for outliers using Mahalanobis distance, and 25 outliers were found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) = `r printnum(cutoff2)`.
-These data were excluded leading to a final sample size of `r nrow(noout2)`.
-Data were screened for assumptions described in Study 3.1 and were found to be satisfactory.
-
-```{r writing-analysis-3.2, include=FALSE}
-##stem the data
-for (i in 1:nrow(noout2)) {
-  noout2$writing2[i] <- paste(unlist(
-    text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-overall_corpus <- Corpus(VectorSource(noout2$writing2))
-overall_TDM <- as.matrix(TermDocumentMatrix(overall_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-overall_freq <- data.frame(Word = rownames(overall_TDM),
-                          Freq = rowSums(overall_TDM),
-                          row.names = NULL)
-overall_freq$Word <- as.character(overall_freq$Word)
-overall_freq$percent <- overall_freq$Freq/nrow(noout2)*100
-
-write.csv(overall_freq, "exp3_data/study3.2_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-##this goes over 100% but mostly want to subset out things that were only mentioned
-##a few times by participants
-all_words <- overall_freq$Word[overall_freq$percent >=1]
-
-##turn sideways to add to dataset
-overall_TDM <- as.data.frame(t(overall_TDM))
-overall_TDM <- overall_TDM[ , all_words]
-
-##final dataset
-overall_final <- cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
-                                  "authorityMFQ", "purityMFQ","ingroupMFQ")],
-                   overall_TDM)
-```
-
-```{r mfq-cor-3.2, include = FALSE}
-##harm
-harm_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})
-
-harmcut <- mean(harm_cor) + 2*sd(harm_cor)
-harm_words_reduce_exp2 <- names(harm_cor[abs(harm_cor) >= harmcut])
-
-##fair
-fair_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})
-
-faircut <- mean(fair_cor) + 2*sd(fair_cor)
-fair_words_reduce_exp2 <- names(fair_cor[abs(fair_cor) >= faircut])
-
-##purity
-purity_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})
-
-puritycut <- mean(purity_cor) + 2*sd(purity_cor)
-purity_words_reduce_exp2 <- names(purity_cor[abs(purity_cor) >= puritycut])
-
-##authority
-authority_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})
-
-authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
-authority_words_reduce_exp2 <- names(authority_cor[abs(authority_cor) >= authoritycut])
-
-##ingroup
-ingroup_cor <- apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})
-
-ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
-ingroup_words_reduce_exp2 <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
-
-##print out words list to look at for further analysis
-#write.csv(harm_words_reduce_exp2, "exp3_data/words/harm_exp2.csv", row.names = F)
-#write.csv(fair_words_reduce_exp2, "exp3_data/words/fair_exp2.csv", row.names = F)
-#write.csv(authority_words_reduce_exp2, "exp3_data/words/authority_exp2.csv", row.names = F)
-#write.csv(purity_words_reduce_exp2, "exp3_data/words/purity_exp2.csv", row.names = F)
-#write.csv(ingroup_words_reduce_exp2, "exp3_data/words/ingroup_exp2.csv", row.names = F)
-```
-
-In the first study, only free association responses were collected, but in this study, full writing samples were collected.
-Therefore, we expected many of the words listed to be part of creating a cohesive discourse, rather than only related to the moral foundation targeted.
-To find only the most related words, the correlation between word frequency and moral foundation was calculated and words with correlations greater than two standard deviations outside the mean were selected for the dictionary analysis in Study 3.3.
-The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
-The average scores were: harm (*M* = `r printnum(mean(noout2$harmMFQ))`, *SD* = `r printnum(sd(noout2$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout2$fairMFQ))`, *SD* = `r printnum(sd(noout2$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout2$ingroupMFQ))`, *SD* = `r printnum(sd(noout2$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout2$authorityMFQ))`, *SD* = `r printnum(sd(noout2$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout2$purityMFQ))`, *SD* = `r printnum(sd(noout2$purityMFQ))`).
-
-```{r compare-ratings-3.2, include = FALSE}
-authority_erin <- read.csv("exp3_data/words/authority_study3.2 erin.csv", stringsAsFactors = F)
-authority_will <- read.csv("exp3_data/words/authority_study3.2 will.csv", stringsAsFactors = F)
-authority_erin$x[authority_erin$use != authority_will$use]
-
-authority_words_reduce_exp2 <- authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]
-
-fair_erin <- read.csv("exp3_data/words/fair_study3.2 erin.csv", stringsAsFactors = F)
-fair_will <- read.csv("exp3_data/words/fair_study3.2 will.csv", stringsAsFactors = F)
-fair_erin$x[fair_erin$use != fair_will$use]
-fair_will$use[fair_will$x == "carbon"] <- 0
-fair_will$use[fair_will$x == "emiss"] <- 0
-#exclude carbon and emiss due to the prompt
-
-fair_words_reduce_exp2 <- fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]
-
-purity_erin <- read.csv("exp3_data/words/purity_study3.2 erin.csv", stringsAsFactors = F)
-purity_will <- read.csv("exp3_data/words/purity_study3.2 will.csv", stringsAsFactors = F)
-purity_erin$x[purity_erin$use != purity_will$use]
-purity_will$use[purity_will$x == "befor"] <- 1
-#before include because of "before sex/ruined/etc."
-
-purity_words_reduce_exp2 = purity_words_reduce_exp2[purity_words_reduce_exp2 %in% purity_will$x[purity_will$use == 1]]
-
-ingroup_erin <- read.csv("exp3_data/words/ingroup_study3.2 erin.csv", stringsAsFactors = F)
-ingroup_will <- read.csv("exp3_data/words/ingroup_study3.2 will.csv", stringsAsFactors = F)
-ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
-ingroup_will$use[ingroup_will$x == "mean"] <- 1
-#mean should be included
-
-ingroup_words_reduce_exp2 <- ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]
-
-harm_erin <- read.csv("exp3_data/words/harm_study3.2 erin.csv", stringsAsFactors = F)
-harm_will <- read.csv("exp3_data/words/harm_study3.2 will.csv", stringsAsFactors = F)
-harm_erin$x[harm_erin$use != harm_will$use]
-harm_will$use[harm_will$x == "import"] <- 1
-#import for important
-
-harm_words_reduce_exp2 = harm_words_reduce_exp2[harm_words_reduce_exp2 %in% harm_will$x[harm_will$use == 1]]
-```
-
-This set of words was then coded by two of the authors for relevant words with discussion over coding constituting a tiebreaker.
-For example, for harm words in this study both *also* and *Syria* appeared as correlated words to the harm foundation.
-The first word does not meet face validity of correlation with the dictionary, and these type of function words or ambiguous verbs (i.e., *get*, *can*) were usually excluded.
-The second example is likely because of the writing prompt, and therefore, proper nouns were also excluded.
-The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce_exp2)`, fairness `r length(fair_words_reduce_exp2)`, ingroup `r length(ingroup_words_reduce_exp2)`, authority `r length(authority_words_reduce_exp2)`, and purity `r length(purity_words_reduce_exp2)`.
-
-## Study 3.3
-
-This part is the mtmm
-
-```{r mtmm-setup, include = FALSE}
-##original mfd words
-original_mfd <- read.csv("exp3_data/original_mfd.csv", stringsAsFactors = F)
-
-##adding forms/conjugations of words to original_mfd
-#harm/care
-original_mfd[c(27:95),1] <- c("abusive","abuser","abused","abusing",
-                             "sympathetic","sympathies","damaged",
-                             "damaging","attacked","attacking","attacker",
-                             "attacks","attackers", "benefits", "benefitted",
-                             "benefitting", "cares", "cared", "caring", "crushes",
-                             "crushing", "crushed", "dangerous", "defends", "defending",
-                             "defended", "detroys", "destroyed", "destroying",
-                             "fights", "fought", "fighting", "guards", "guarded",
-                             "guarding", "harms", "harmed", "harming", "hurts",
-                             "hurting", "kills", "killed", "killing", "preserves",
-                             "preserved", "preserving", "protects", "protected",
-                             "protecting", "protection", "ruins", "ruined", "ruining",
-                             "safely", "safer", "shelters", "sheltered", "sheltering",
-                             "spurns", "spurned", "spurning", "stomps", "stomped",
-                             "stomping", "suffers", "suffered", "suffering",
-                             "violence", "warring")
-
-#fairness/reciprocity
-original_mfd[c(20:64),2] <- c("balances", "balanced", "balancing","biased",
-                             "biases", "discriminates", "discriminated",
-                             "discriminating", "discrimination", "equals",
-                             "equaled", "equaling", "equates", "equated",
-                             "equating", "evens", "evened", "evening",
-                             "excludes", "excluded", "excluding", "fairness",
-                             "favors", "favored", "favoring", "honesty",
-                             "impariality", "justice", "justifies", "justified",
-                             "justifying", "prefers", "preferred", "preferring",
-                             "prejudices", "prejudiced", "prejudicing", "reasons",
-                             "reasoned", "reasoning", "rights", "tolerates",
-                             "tolerated", "tolerating", "toleration")
-
-#ingroup/loyalty
-original_mfd[c(16:47),3] <- c("collects", "collected", "collecting", "collective",
-                             "communities", "deceives", "deceived", "deceiving",
-                             "deception", "deceptions", "deserts", "deserted",
-                             "deserting", "desertion", "families", "fellows",
-                             "foreigners", "groups", "grouped", "grouping",
-                             "indviduals", "indvidualize", "individualized",
-                             "individualizing", "members", "nations", "sides",
-                             "togetherness", "traits", "unites", "united", "uniting")
-
-#authority/respect
-original_mfd[c(31:112),4] <- c("abides", "abided", "abiding", "authorities",
-                              "classes", "classed", "classing", "command",
-                              "commanded", "commanding", "controls", "controlled",
-                              "controlling", "defects", "defected", "defecting",
-                              "defers", "deferred", "deferring", "deference",
-                              "defies", "defied", "defying", "defiance", "deserts",
-                              "deserted", "deserting", "desertion", "duties",
-                              "faiths", "fathers", "fathered", "fathering",
-                              "honors", "honored", "honoring", "laws", "leads",
-                              "leading", "mothers", "mothered", "mothering",
-                              "obeys", "obeyed", "obeying", "opposes", "opposed",
-                              "opposing", "orders", "ordered", "ordering", "permits",
-                              "permitted", "permitting", "positions", "positioned",
-                              "positioning", "preserves", "preserved", "preserving",
-                              "preservation", "protests", "protested", "protesting",
-                              "refuses", "refused", "refusing", "refusal", "respects",
-                              "respected", "respecting", "respectful", "reveres",
-                              "revered", "revering", "reverence", "serves", "served",
-                              "serving", "traditions", "traditional", "traits")
-
-#purity/sanctity
-original_mfd[c(21:60),5] <- c("abstains", "abstained", "abstaining", "abstinence",
-                             "adulteries", "adulterous", "adulterer", "adulterers",
-                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
-                             "cleanliness", "dirty", "diseases", "diseased", 
-                             "disgusts", "disgusted", "disgusting", "grossness",
-                             "innocence", "modesty", "preserves", "preserved",
-                             "preserving", "preservation", "promiscuity",
-                             "promiscuities", "purity", "rights", "ruins", "ruined",
-                             "ruining", "sacredness", "sickness", "sicknesses",
-                             "sins", "wholeness", "wholesome")
-
-##stem the original mfd
-for(i in 1:nrow(original_mfd)) {
-  original_mfd$h2[i] <- stemDocument(original_mfd$h2[i], language = "english")
-  original_mfd$f2[i] <- stemDocument(original_mfd$f2[i], language = "english")
-  original_mfd$i2[i] <- stemDocument(original_mfd$i2[i], language = "english")
-  original_mfd$a2[i] <- stemDocument(original_mfd$a2[i], language = "english")
-  original_mfd$p2[i] <- stemDocument(original_mfd$p2[i], language = "english")
-}
-
-mtmmdata <- noout2[ , c(1:31, 45) ]
-
-####figure out the percents for the exp2 data
-for (i in 1:nrow(mtmmdata)) {
-
-  ##figure out the sum for just the original mfd
-  mtmmdata$harm_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])
-
-  mtmmdata$purity_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])
-
-  mtmmdata$fair_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])
-
-  mtmmdata$authority_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])
-
-  mtmmdata$ingroup_orig[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])
-
-  ##figure out the sum for all words ever 
-  mtmmdata$harm_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])
-
-  mtmmdata$purity_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])
-
-  mtmmdata$fair_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])
-
-  mtmmdata$authority_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])
-
-  mtmmdata$ingroup_all[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])
-
-  ##figure out the sum for reduced words
-  mtmmdata$harm_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])
-
-  mtmmdata$purity_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])
-
-  mtmmdata$fair_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])
-
-  mtmmdata$authority_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])
-
-  mtmmdata$ingroup_reduce[i] <- sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])
-
-}
-
-#create percents instead of frequencies
-mtmmdata[ , c(33:47)] <- mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100 
-summary(mtmmdata[ , 33:47])
-```
-
-```{r mtmm_orig, include = FALSE}
-###Run chunk 8: demos_study2 to update data
-###Use noout2 df as dataframe for mtmm
-###Columns labeled Harm1/Fairness1/Loyalty1/Authority1/Purity1 are original MFD
-###Columns labeled Harm2/Fairness2/Loyalty2/Authority2/Purity2 are revised MFD
-
-####mtmm original dictionary####
-
-{model1 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit <- cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model1.2 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-fair_orig ~~ 1167.145*fair_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.2.fit <- cfa(model1.2, data=mtmmdata, std.lv=TRUE)
-summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.2.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.2.fit, fit.measures = "aic")
-
-{model2 <- '
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model2.fit <- cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model3.fit <- cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model4.fit <- cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-```{r mtmm_reduce, include = FALSE}
-
-{model1 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-```{r mtmm_all, include = FALSE}
-
-{model1 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-  Data Cleaning and Descriptives.
-In sample 1, participants who wrote less than 50 words were deleted (*n* = 69) leaving *n* = 221 participants.
-The average political orientation was 4.80 (*SD* = 2.21) on a scale of 1 (*conservative*) to 10 (*liberal*).
-In sample 2, all 160 participants wrote at least 50 words.
-The mean political orientation was 5.01 (*SD* = 2.33) for sample 2.
-The data from sample 1 and sample 2 were combined.
-Before any analyses were conducted, participants who did not use any words from the MFD were deleted; 16 participants were deleted from sample 1 and 25 from sample 2.
-The final sample size for analysis was *N* = 340 which had a mean political orientation of 4.90 (*SD* = 2.28).
-MFD scores were computed using NVivo *(CITE)* as both frequency for each foundation and percent coverage for each foundation.
-Frequency was simply the count of the number of words used from a given foundation dictionary; for example, a participant using the word *war* once and the word *peace* twice would have a frequency score of 3 for the *harm* dictionary.
-Percent coverage was calculated by taking the frequency and dividing by the word count; for example, given a frequency score of 3 for the *harm* dictionary and a word count of 100, then the percent coverage would be .03 for the *harm* dictionary.
-MFQ scores for each foundation were calculated by averaging the six items pertaining to each foundation.
-	Reliability.
-Here we should talk about the reliability of the MFQ for each piece, as well as the reliability of the words for the MFD.
-I think to do that you might need a thing that has each word as frequency count yes/no or however the LIWC version thing was done.
-	MTMM. BASIC SEM STUFF HERE (also that you used bayes)
-Data screening was conducted using SPSS version 22 and AMOS version 22.
-Participants who were missing data for the MFD, MFQ, or political orientation were deleted from all analyses.
-Given the distribution of the dictionary variables, participants whose writing sample were less than 2% words from the MFD were deleted resulting in a sample size of 252.
-Additionally, 7 outliers were deleted.
-Widaman's (1985; as cited in @Byrne2009) four-step nested method was used to test the convergent and divergent validity of the MFD and MFQ.
-The first step is the baseline model (Model 1), which establishes correlation among traits (*harm*, *purity*, *fairness*, *authority*, and *ingroup*) as well as correlation among methods (MFD and MFQ) but no cross correlation of traits and methods.
-The individual questions from the 30 item version of the MFQ and the total frequency of concepts from each foundation in the MFD were used as measured variables.
-The fit of this first model indicated some misfit, as fit indices were a mix of poor and acceptable, $\chi$ 2 (514) = 977.46, $\chi$ 2/df = 1.90, CFI = .842, RMSEA = .061 [95% CI = .055-.067], SRMR = .0623.
-In this model, the MFD *harm*, *fairness*, and *ingroup* items significantly loaded onto their trait factors, while *authority* and *purity* did not.
-All foundations but *authority* loaded significantly on the method traits.
-All but two of the *ingroup* questions and one *authority* question loaded onto the MFQ trait factors.
-Several questions of the MFQ did not load significantly onto the methods factors; however, this result was taken as an indicator that traits variance was higher than methods variance.
-Generally, trait loadings were higher than method loadings for both the MFD and MFQ for *harm* and *fairness* traits.
-However, the *purity*, *ingroup*, and *authority* foundations did not show this loading pattern.
-ERIN STOPPED HERE CUZ HEADACHE. 
-The second step (Model 2) involved eliminating the latent traits from the model.
-This model was significantly worse than Model 1 indicating the traits are important to the model ($\delta$ $\chi$ 2 = 1141.09, $\delta$ df = 45, $\delta$ CFI = .351).
-This supports convergent validity for the traits measured by both methods which in this case are the five moral foundations.
-The third step (Model 3) involved forcing the five traits to be perfectly correlated.
-This model was significantly worse than Model 1 indicating the usefulness of five unique traits ($\delta$ $\chi$ 2 = 311.09, $\delta$ df = 10, $\delta$ CFI = .097).
-This supports discriminant validity for the existence of five unique moral foundations.
-The final step (Model 4) involved allowing the correlations between the traits to be freely estimated and forcing the methods to be uncorrelated.
-This model was similar to Model 1 indicating the methods both measure the traits but they are both unique methods ($\delta$ $\chi$ 2 = 2.23, $\delta$ df = 1, $\delta$ CFI = .001).
-This supports discriminant validity for the methods.
-This set of analyses suggests the MFD is a possibly valid measure of moral foundations but does not measure them well enough to be useful in all applications and may be measuring them differently than the MFQ.
-	Regression predicting Political Orientation.
-The MFQ has predicted political orientation across many studies [@Federico2013; @Graham2009; @Haidt2009; @Weber2013].
-Therefore, in addition to the MTMM analysis, we compared how well the MFD score predicted political orientation compared to how well the MFQ predicted the political orientation.
-First, total MFQ scores were calculated for each foundation by averaging all six items.
-Then, a regression analysis was conducted with the five MFQ foundation score predicting political orientation.
-The overall model was significant, *R2* = .35, *F* (5, 255) = 26.91, *p* < .05.
-Higher scores on the harm and fairness foundations predicted a more liberal political orientation with harm accounting for 3% of the variance and fairness accounting for 6%.
-Higher scores on ingroup, authority, and purity predicted a more conservative orientation accounting for 1%, 2%, and 8% on the variance respectively.
-See *table ?* for regression coefficients.
-Next, a regression analysis was conducted to determine how well the five MFD scores predicted political orientation.
-The overall model was not significant, *R2* = .16, *F* (5, 255) = 1.36, *p* = .241.
-Higher harm scores somewhat predicted more liberal orientation accounting for 1% of the variance in political orientation.
-Higher purity scores somewhat predicted more conservative orientation accounting for 1% of the variance.
-See *table ?* for regression coefficients.
-
-# Participants
-
-Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes (???).
-Participants were recruited via an online research system (SONA) and were given course credit for their participation.
-463 participants were
-included in the this study.
-The study was mostly women (53.9%) and White (76.4%) participants with a mix of minority participants: Black (6.1%), (3.6%), (4.2%), Native American (1.9%), Mixed (2.9%) and Other (4.9%).
-The average listed age was 19.75 (SD =
-200 2.94).
-
-# Materials and Procedure
-
-Data was again collected via Qualtrics. Four fake new stories were presented to participants, which were roughly 400 words each. First, all news stories included a few
-sentences describing the use of chemical weapons in the Syrian civil war.
-The news stories were manipulated with political (Republican v.
-Democrat) and religious (religious v.
-not) quotes in a 2 x 2 design.
-News stories can be found in the online materials.
-Participants also completed the 30-item version of the MFQ as described in the introduction.
-In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.
-
-After consenting to participate in the study, participants were randomly shown one of
-the four new articles about Syria’s use of chemical weapons. Participants were then asked to
-write for 5-10 minutes about their reaction to Syria’s use of chemical weapons and the
-needed response from the United States. The second wave of data collection included
-different writing prompts designed to capture more of the moral foundation areas in their writing. The following writing prompt was used, “Please write about your attitudes on
-abortion (or same-sex marriage or environmentalism) as well as your reason for this stance.”
-The three prompts were chosen to create a more varied word set by using topics that should
-elicit words from each moral foundations category by soliciting a moral response.
-In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants.
-Participants then completed the MFQ, demographics, and the political
-orientation scale.
-
-# Results
-
-# Expanding the MFD
-
-In a separate study of 466 university students, participants completed a free association task where we asked them to list all the words that came to mind from *harm/care*, *fairness/cheating*, *loyalty/XX*, *authority/XX*, *purity/XX*.
-They also completed the 15 item MFQ.
-Responses to the free association task were cleaned and stemmed.
-This lead to a new set of moral foundation words: harm-96, fairness-76, ingroup-86, authority-81, and purity-80.
-These concepts were included in the full dictionary used for Experiment 3.
-
-We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
-Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts.
-Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation.
-The reduced dataset included the following number of words for each foundation: harm 4, fairness 3, ingroup 3, authority 4, and purity 2.
-
-```{r word-association}
-#need the code for the the above stuff
-```
-
-[ERIN, Please do mathy-math here]
-
-# Testing Model Structure
-
-Before testing the theorized differences between liberals and conservatives, we sought to test the validity of the MFD using Multi-Trait, Multi-Method modelling (MTMM) to determine if the MFD is measuring the same latent variables as the MFQ as it should.
-
-```{r mtmm}
-
-```
-
-# Testing Group Differences
-
-```{r mtmm-groupdiffs}
-
-```
-
 # Discussion
 
-The results obtained in Study 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
-The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given @Graham2009.
-Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the practical effects much smaller than reported in @Graham2009.
-While not significant, fairness was endorsed more by conservatives in both cases.
-In contrast, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
-
-Together with Study 1 and past work, Study 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
-One issue that Study 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
-For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
-The original predictions made by the Moral Foundations are very simplistic and likely much more complex in reality.
+The results obtained in Study 2 are slightly more in line with
+expectations from MFT, however, in all but one case, the differences
+were not statistically significant. The only statistically significant
+difference was in the harm foundation; liberals did endorse harm more
+than conservatives during the Kavanaugh hearings, but the effect was
+smaller than expected given @Graham2009. Generally for both the
+Kavanaugh hearings and the Government shutdown, the differences were in
+the expected direction (liberals endorsing harm more and conservatives
+endorsing authority and loyalty more), but the differences were not
+statistically significant and the practical effects much smaller than
+reported in @Graham2009. While not significant, fairness was endorsed
+more by conservatives in both cases. In contrast, purity was endorsed
+more by conservatives for the government shutdown, but more by liberals
+for the Kavanaugh hearing though neither difference was statistically
+significant.
+
+Together with Study 1 and past work, Study 2 further calls into question
+the usefulness and efficacy of the Moral Foundations as well as cast
+doubt on the predictions made by MFT. One issue that Study 2 brings up
+is that moral differences between liberals and conservatives may be
+moderated by a number of factors as shown in @Sterling2018. For example,
+here we have liberals concerned with purity for the Kavanaugh hearings
+(a moral bad for liberals and a moral good for conservatives) and
+conservatives concerned with purity during the government shutdown (a
+moral bad for conservatives and a moral good for liberals). The original
+predictions made by the Moral Foundations are very simplistic and likely
+much more complex in reality.
 
@@
 
-Within the theoretical framework of MFT [@Haidt2007], we attempted to devise a method leveraging the MFD [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
-In Study 1,the results obtained were not significant in any statistical or practical sense.
-There was a small effect found for the *authority/respect* foundation according to Cohen's *d*, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-In Study 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
-Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive, we still retain confidence in the overall structure of the methodology established in the current study.
-Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-We implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
-
-However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
-As mentioned before, MFD is a measure developed from MFT [@Graham2009].
-Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
-Going beyond specific instruments, other theoretical perspectives may be more equipped to explain political differences in discourse.
-Likewise, an atheoretical approach in which large quantities of data are collected from which theories are formulated may be best suited to this area of research.
-
-In critiquing MFT, @Schein2015 proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
-Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else [@Gray2014, @Schein2015].
-Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
-For example, in the case of abortion, liberals tend to identify the primary harm to the mother leading to a pro-choice position whereas conservative tend to identify the primary harm to the fetus leading to a pro-life position.
-While as of yet, no linguistic measurement of dyadic morality exists; such an approach may be able to better identify the systematic differences between liberals and conservatives.
-
-Turning to atheoretical approaches, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
-Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
-The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
-Likewise, there are several approaches to analyzing such data, including linear models (like multilevel models) and network-style models such as latent semantic analysis [@Landauer1998].
-Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
-
-Never before has political discourse represented such fertile ground for psychological research.
-The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
-Along with this recent increase in the amount of text information, there is now an obligation on the part of researchers to devise proper methods for analyzing that text.
-Solid methodologies must be constructed and periodically improved to keep pace with evolving technologies.
-Likewise, a strong theoretical foundation is paramount to making sense of the current and future media ecosystem.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
+Within the theoretical framework of MFT [@Haidt2007], we attempted to
+devise a method leveraging the MFD [@Graham2009] in order to quantify
+political bias stemming from content published by several prominent
+American news sources. In Study 1,the results obtained were not
+significant in any statistical or practical sense. There was a small
+effect found for the *authority/respect* foundation according to Cohen's
+*d*, but the effect suggested endorsement for that foundation opposite
+to what was hypothesized. In Study 2, the direction of the differences
+were generally in line with MFT, however, the difference were very small
+and lacks statistically significance. Building on @Frimer2020 and other
+critiques of MFT and the MFD, we show that MFD is not a useful tool for
+measuring moral language while also calling into question the validity
+of MFT in terms of theorized partisan differences.
+
+Despite the fact the results regarding political bias were inconclusive,
+we still retain confidence in the overall structure of the methodology
+established in the current study. Specifically, the procedure for
+scraping text from the web, processing, stemming, and weighting the
+scores with valence seems to represent a solid method for preparing a
+high quantity of text passages for data analysis. We implemented valence
+as an indicator of the directionality of endorsement due to the inherent
+ambiguity of simply calculating MFD word percent occurrence. This method
+served both to augment the face validity of the MFD by incorporating
+valence (thus reducing ambiguity) and to generate a score that is easy
+to understand and analyze.
+
+However, political lean and other important political/moral constructs
+may be communicated through methods other than through the use of
+particular words. As mentioned before, MFD is a measure developed from
+MFT [@Graham2009]. Based upon the results obtained, it might be
+necessary to investigate alternative instruments that could better
+elucidate the differences of interest. Going beyond specific
+instruments, other theoretical perspectives may be more equipped to
+explain political differences in discourse. Likewise, an atheoretical
+approach in which large quantities of data are collected from which
+theories are formulated may be best suited to this area of research.
+
+In critiquing MFT, @Schein2015 proposed an alternative theory explaining
+moral choices and potential partisan differences: Dyadic Theory of
+Morality. Across many studies, researchers find that supposed
+differences in moral foundation can be more easily explained by a
+harm-focused morality where someone/thing is harmed by someone/thing
+else [@Gray2014, @Schein2015]. Rather than liberals and conservatives
+having difference conceptions of morality, dyadic morality argues that
+they simply identify harm differently. For example, in the case of
+abortion, liberals tend to identify the primary harm to the mother
+leading to a pro-choice position whereas conservative tend to identify
+the primary harm to the fetus leading to a pro-life position. While as
+of yet, no linguistic measurement of dyadic morality exists; such an
+approach may be able to better identify the systematic differences
+between liberals and conservatives.
+
+Turning to atheoretical approaches, future studies aiming to uncover
+political lean in discourse may benefit from a bottom-up, data-driven
+approach. Researchers might derive substantive insights into political
+lean through gathering data after which they may formulate theories that
+explain systematic observations obtained from that data. The
+availability of text corpora along with methods for extracting large
+amounts of text from the internet (as was demonstrated in the current
+study) potentially make this a feasible option. Likewise, there are
+several approaches to analyzing such data, including linear models (like
+multilevel models) and network-style models such as latent semantic
+analysis [@Landauer1998]. Owing to the wealth of representative data as
+well as the sophistication of current analytic tools, there is high
+potential for the explanatory power of new theories involving political
+discourse.
+
+Never before has political discourse represented such fertile ground for
+psychological research. The plethora of options for news sources has
+created not only an abundance of choice but also vast quantities of text
+data. Along with this recent increase in the amount of text information,
+there is now an obligation on the part of researchers to devise proper
+methods for analyzing that text. Solid methodologies must be constructed
+and periodically improved to keep pace with evolving technologies.
+Likewise, a strong theoretical foundation is paramount to making sense
+of the current and future media ecosystem. Therefore, it is incumbent
+upon social scientists to continue investigating the information
+consumed by millions of Americans every day so that insights into the
+nature and consequences of political discourse can be more completely
+understood.
 
@@
 
+```{=tex}
 \begingroup
-<div id="refs" custom-style="Bibliography"></div>
+```
+::: {#refs custom-style="Bibliography"}
+:::
+
+```{=tex}
 \endgroup
+```

### 2024-01-30 manuscript_version/revision/revision_letter.Rmd
updating to study 1

---
title          : "Moral Foundations of U.S. Political News Organizations"
authors        : "Padfield, Buchanan, & Jordan"
journal        : "Meta-Psychology"
manuscript-id  : "Manuscript number"
manuscript-src : "headings"

cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
---

Dear Dr. Editor,

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.

In the following we address your and each reviewers' concerns point-by-point.

# Reviewer \#1

:::reviewer
This manuscript reports results from a pair of studies examining the validity of the Moral Foundations Dictionary (MFD), specifically by comparing use of terms from the MFD by previously-identified conservative and liberal news sources. The first study compares MFD term usage in two liberal (NPR, NYT) and conservative (Fox News, Breitbart) news sources, finding no significant differences in MFD words used for any of the five moral foundations dimensions between the two types of news sources. A second study, its design based on part on lessons learned from issues with data collection from the first study, did the same with twenty news sources and specifically with coverage of Brett Kavanaugh’s Supreme Court of the United States nomination and confirmation and the 2018-2019 U.S. government shutdown stemming from disputes about a proposed U.S.-Mexico border wall. The second study found a significant (albeit small, effect-wise) difference between liberal and conservative sources only for the harm-care dimension, as the manuscript notes has been found in previous research, but only for the Kavanaugh coverage. Results are interpreted as casting further doubt on the utility of the MFD, and more conceptually the applicability of the MFT dimensions, to explain partisan political differences. I appreciate the level of detail in the description of the studies’ method and analysis, including unexpected issues such as the challenges in scraping some of the first study’s sources. The thorough and highly organized presentation of open materials and the clear explanation of methods including use of specific R packages provides useful guidance to both critical examination of these studies and future research building on them.

The review of research behind the MFT, MFQ, and MFD is parsimonious but thorough, and in my opinion quite reasonable about the shaky conceptual foundations of all three as well as the limited empirical evidence for reliability and validity of the measures. If anything, the review of the literature is forgiving given how often measures like MFT do not even demonstrate adequate inter-item reliability. In any case, the rationale for the study is clearly justified by a fair review of a popular conceptual framework that very much has feet of clay. I also find the justification for the selection of sources to be adequate, and appreciate the authors' basing them in the Mitchell et al. article rather than simply relying on an intuitive assumed rationale for the selection.
:::

Thank you for your kind words!

:::reviewer
If there is more systematic justification for why these precise four news sources were chosen over all other options for Study 1, it might be good to share. If there is no such specific justification, though, I don’t think it is a problem that needs addressing further as there is adequate rationale for these two pairs of sources to be—at the very least—fine examples of the two source variable conditions. (Although a critique might be that Breitbart is arguably less mainstream than the other three sources, though that doesn’t seem to invalidate the study’s findings.)
:::

As described in text, mostly these were chosen due to perceived and self-described political lean. However, we added a sentence about how they also practically worked best:

"At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible."

:::reviewer
Given that in many ways the first study ends up being something of a de facto pilot study for the second (which I believe adds substantially to the credibility of the latter as well as the message of the pair as a package here), this is not a major issue as five times as many sources are used in the second study with similar findings. The manuscript seems to imply that these twenty sources represent the top ten sources from each valence of lean in the Mitchel et al., article; if that is so, it may be good to state as much more clearly. If I misunderstood and more arbitrary criteria were used to select each set of ten sources from the Mitchell et al. article’s results, that may need to be clarified as well.
:::

We picked the ones based on Mitchell's article that also were practically usable. Therefore, we added this sentence to our second study source section as well:

"These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service."

:::reviewer
Again, though, I do not perceive these as concerns even if there is no more specific justification given that these seem appropriate conditions for studies viewed as experiments rather than as some sort of representative source sample. That said, I am reluctant to consider these studies simply experiments per se rather than perhaps as natural experiments. I am not sure I am correct, as I have limited experience with the latter, but I wonder if it might at least be worth suggesting renaming both studies as natural experiments rather than solely as experiments. That said, I defer to the editorial staff, reviewers, and authors themselves regarding whether the manuscript would be more accurate continuing to describe these studies as experiments or if it might be a good idea to call them natural experiments.
:::

We understand the point of view of this critique and have changed the language accordingly throughout the manuscript.

:::reviewer
As a minor point, given that the studies are described as "a further conceptual replication of Frimer (2020)," which seems apt (as well as some of the measures and interpretation thereof are also based on Frimer), it may be useful to describe the findings thereof for the reader at least briefly (even if only in conceptual terms). The study is mentioned parenthetically in a sentence describing previous literature, but a sentence or so more about the specific contribution of Frimer (2020) might aid the reader given it is described as uniquely central to these studies' motivation and design.
:::

The section in the literature review describing the Frimer study has been expanded like shown below.

“Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD. Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S. Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009. In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words). Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness. Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores. Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects… Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.”

:::reviewer
While the manuscript is well-written, there is at least one error I would consider very important, namely at least one misspelling of Brett Kavanaugh's surname. It would, of course, be a good idea to take a very close look for such errors, even if they are not technically germane to the credibility of the studies' design and results. I believe that addressing these issues will result in a useful contribution to the literature about a theoretical framework and measure that seems increasingly in need of some reconsideration—particularly given its popularity.
:::

The misspelling has been fixed.

# Reviewer \#2

:::reviewer
The present manuscript applies a version of the moral foundations dictionary to news articles. I have to disclose that I am quite strongly predisposed against the validity and generalizability of MFT overall, first because it is extremely US-centric, second because I have seen it fail quite spectacularly in survey applications. I am also quite skeptical of dictionary-based approaches overall. The negative findings of the paper were comfortably confirming my expectations, which might positively bias my review.

I have several major and minor concerns:

(1) I don't exactly understand the purpose of the paper: Is it a validation study of the MFD or an attempted application of MFT to the analysis of media content? This concerns the interpretation of the findings: Do we believe that moral foundations simply did not impact the coverage of the issues, or just that the MFD did not pick up the latent messages because it is a flawed instrument? Would the cited improved methods such as manual coding or modern large language models be more successful? We do not know because the MFD is not systematically compared to alternative approaches. Ironically, the authors mention the multi-trait-multi-method approaches related to MFT, but do not apply them themselves. However, applying on method to one sample, tells us little about the validity of the method *or* the idiosyncrasies of the sample. Therefore, I am unsure what we can learn from the paper.
:::

TO DO ADD THE MTMM STUDY FINALLY

:::reviewer
(2) The authors extend previous research on the MFD by "augmenting" the word counts with scores from another dictionary (Warriner et al.) I don't have access to the cited papers, especially Frimer's, but if this is an original idea by the authors, it needs *much* more theoretical and methodological justification. Previous applications of the MDF have by design only tapped the salience of the different dimensions in different texts, and it's not obvious to me whether extending this to valence is as straightforward as the present paper suggests. And even if one accepts the premise that context-free ratings of word lemmas by Mturk Workers are useful measures of some kind of word "valence", it's the authors burden of proof that multiplying one set of scores with a completely different set of word scores from another task makes sense. At the very least, I'd expect a quasi-replication study to start out with the traditional application of the MFD, i.e. simple word counts/relative frequencies as outcomes, and then check if and how multiplying them by z-standardized (why btw?) valence scores changes things.
:::

TO DO ADD MORE TEXT AND TALK ABOUT THIS STUFF

RESPONSE: [Erin]
- look at original thesis for justification for valence
- note if we add the MTMM, this response may be different, so waiting here. Also this person seems to think that valence ratings are not useful, so add some notes about how they are very predictive, yada yada.
- add information from will's thesis back in there

Critically - also - the MFD was made by just *thinking* about words right? So why is that better than the actual ratings of valence from people?

As noted in text, we z-scored to help with interpretation:

"Valences were z-scored in order to eliminate any ambiguity regarding the direction of the valence. Positive values indicate positive valence, and negative values indicate negative valence."

:::reviewer
(3) As a communication scholar, I find the way outlets' leanings are measured by the composition of their readers at least questionable. I know it is a convenient shortcut, but again the question is whether the inferences drawn in the paper are really about the target audience, or the journalists' attitudes and moral predispositions (or the attitudes of the politicians quoted in the news articles). I encourage the authors to more thoroughly consider what kind of theoretical foundation their own arguments (or the cited previous applications of MFT to texts) have. A helpful source could be Benoit, K., Laver, M., & Mikhaylov, S. (2009). Treating words as data with error: Uncertainty in text statements of policy positions. American Journal of Political Science, 53(2), 495-513.
:::

While we appreciate the complexities of measuring partisan lean of media outlets, we justify the selection and categorization of the news outlets using a Pew Research Center study. Obviously other methods could have been used, but we feel that this is sufficient justification.

“We determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.”

:::reviewer
(4) The manuscript can be shortened by removing redundancies between study 1 and 2 descriptions. Also, if the text statistics such as readability are not used as controls or otherwise in the main analysis, why bother with them? While I appreciate the excellent documentation of the scraping, much of this can be moved to a supplement.
:::

TO DO MAKE THESE CHANGES

RESPONSE: [Erin]
- move readability stats to an appendix
- undecided here maybe something like ...
Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript. Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation.

:::reviewer
(5) I was really irritated by the use of "Experiment" 1 and 2 in the headings, when no experiments were conducted or at least reported. Please stick to study 1 and 2.
:::

The wording has been changed throughout the document.

:::reviewer
(6) Reporting the ICC of the Null model with just outlet clustering would be nice and helpful to understand the data.
:::

These values have been added to each model table.

:::reviewer
(7) Are we sure that linear models are appropriate for the weighted frequency outcomes?
:::

Each model was checked for assumptions of parametric models. Linearity, normality assumptions were met with some violations of homoscedasticity.

# Reviewer \#3

:::reviewer
In this article, the authors provide a two-study investigation of the moral leanings of news sources using an approach based on the Moral Foundations Dictionary (MFD). This paper has a number of strengths, and I do believe that we need more work carefully validating dictionary-based approaches to studying moral content (and moral foundations theory) in textual data. I would also like to emphasize that this work is especially impressive being a Master’s thesis. This being said, I also see a number of issues with this manuscript that, in my view, limit the validity of its conclusions. In short, I found myself wondering throughout the methods section(s) as to the extent to which the results observed in this manuscript are due to the analytic decisions that were made rather than due to issues with the MFD (or MFT). This concern is magnified when considering that the authors used a number of rather non-standard techniques compared to extant work. I’ll highlight a few of the most salient issues below: My first concern is the most central to my overall evaluation of the manuscript. I noticed a large number of places where critical methodological details of the analyses conducted in this manuscript were completely left out or glossed over. I appreciate that the authors provided supplemental material containing analysis code, and I’m sure that I could dig through the code and figure out the answers to many of these questions, but it’s critical that methodological choices that are central to the conclusions of the paper be provided in the manuscript itself. A couple of noticeable examples:

•	The details of the valence-weighting procedure applied to the moral foundations words was not clear to me, even after several readings. Was the valence calculated for the moral words themselves, or for the context surrounding the words? How were the z-scores applied (within i.e. within document, within source, overall)? These details are important, because the mean valence of the MFD words varies across different MFD categories, and also because the valence of moral words is almost always contingent on their context (see e.g. Hopp et al., 2021). For example, the sanctity-assigned word “pure” could be be used to refer to “pure water” or to “pure evil.”
:::

We added an example table of the weighting calculation and rephrased this section completely.

"A complete list of the words for each moral foundation area was created from previous experiments. The total number of times each of those words was used in an article was calculated. This information was merged with the valence values from the @Warriner2013 dataset. A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article. The final score was multiplied by 100 to represented a weighted percentage. Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article."

Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches. In response to the question about analytic choices, we have added information about a MTMM study, as well as the exact same statistics using the raw percentages.

TO DO - DO THIS

:::reviewer
•	The details of the MLM’s are also unclear. For example, it seems like political leaning is treated as a categorical variable, but that isn’t mentioned. It’s also unclear how the random intercept for source was created. Again, I could be misunderstanding something, but if source wasn’t nested within political leaning, then creating the random intercept for source would almost certainly wash out any effect that may be attributed to political leaning. I would suggest providing the equations for the models within the text to avoid these sorts of confusions.
:::

As described in the text:

"Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison."

We would also note that the complete manuscript and code is available on our OSF page: https://osf.io/5kpj7/. We added the equation for the multilevel model directly to the text as well:

"Therefore, the models were calculated by: Weighted Score ~ Political Lean + (~1|Source)."

:::reviewer
My second concern stems from the first. Given the lack of methodological clarity at several key points in the manuscript, I was somewhat surprised by the forcefulness of the authors’ conclusions. To be clear, I say this as someone who is also quite skeptical of the validity of the MFD (for a more extensive treatment of why, see Hopp et al., 2021). Given that the authors used a customized version of the MFD, I don’t personally see how evidence that the predictions didn’t pan out is evidence that the MFD (much less MFT in general) is less valid.
:::

TO DO COMMENT HERE ABOUT THE ORIGINAL SCORING BEING SHIT AS WELL

:::reviewer
This is especially true given that a good deal of the work the authors reference just looks at word counts (not valence-weighted percentages) as indicators of moral-foundations-related differences across sources. As a final note, I would suggest that the authors go through the manuscript with an eye toward including everything that is needed for an interested reader to know the critical methodological details, but also toward removing things that are not germane to the questions that are the authors’ central foci in the manuscript. For example, I would presume that the linguistic complexity analyses could be relegated to supplemental material to make space for more methodological discussion. In sum, although there is much to like about this manuscript, I believe that it needs quite a bit of re-engineering before it’s ready to be published. I would again like to commend the authors on their efforts. I hope that my comments are helpful in continuing to refine this important work.
:::

We have moved information to the supplemental document, as suggested by several reviewers. We additionally add more information about the methodology for clarity.

### 2024-11-30 manuscript_version/revision/appendix.Rmd
rearranging folders and updating the manuscript

--- 2023-09-01 manuscript_version/revision/manuscript_metapsych_revision.Rmd
@@
 ---
-title             : "Moral Foundations of U.S. Political News Organizations"
-shorttitle        : "MORAL NEWS"
-
-author:
-  - name          : "William E. Padfield"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "901 S. National Ave, Springfield, MO, 65897"
-    email         : "wpadfield@gmail.com"
-  - name          : "Erin M. Buchanan, Ph.D."
-    affiliation   : "2"
-  - name          : "Kayden N. Jordan, Ph.D."
-    affiliation   : "2"
-
-affiliation:
-  - id            : "1"
-    institution   : "Missouri State University"
-  - id            : "2"
-    institution  : "Harrisburg University of Science and Technology"
-
-authornote: |
-  William Padfield completed this project as part of his thesis requirements for a master's degree candidate in Psychology at Missouri State University.
-Submitted to Meta-Psychology.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.
-The full editorial process of all articles under review at Meta-Psychology can be found following this link: https://tinyurl.com/mp-submissions
-
-abstract: |
-  Partisan differences and diviseness have become an increasing hot topic in psychological research.
-Many theories have been proposed to explain these differences and divisions including Moral Foundations Theory.
-The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
-Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
-This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Study 1, we gathered political articles from four sources.
-We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
-In Study 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
-Supreme Court Justice Brett Kavanaugh and the partial U.S.
-Government Shutdown of 2018-2019.
-Once again, no significant differences in moral endorsements were found.
-Together with past work, the results shed doubt on the validity of the MFD as a reliable measurement tool.
-
-keywords          : "politics, morality, psycholinguistics"
-
-bibliography      : ["./metapsych_bib.bib"] #turn this off right now so it knits
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
+title: "appendix.Rmd"
 ---
 
-```{r load_packages, include = FALSE}
-library(papaja)
-library(MuMIn)
-library(reshape)
-library(nlme)
-library(ggplot2)
-library(expss)
-library(MOTE)
-library(quanteda)
-library(quanteda.textstats)
-library(tm)
-library(ngram)
-library(ggplot2)
-library(reshape)
-library(knitr)
-library(performance)
-library(dplyr)
-library(rio)
-library(mice)
-
-# to install this package 
-# tmp <- tempfile()
-# system2("git", c("clone", "--recursive",
-#                  shQuote("https://github.com/leslie-huang/r-corpus.git"), shQuote(tmp)))
-# devtools::install(tmp)
-library(corpus)
-
-knitr::opts_chunk$set(cache = TRUE)
-options(tinytex.verbose = TRUE)
-percentmiss <- function(x){sum(is.na(x))/length(x)*100}
-```
-
-The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].
-Since then, Kohlberg's theory has been highly criticized with numerous theories and hypotheses proposed to replace it.
-One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham [@Haidt2007].
-While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related measurement issue, the Moral Foundations Dictionary (MFD) [@Graham2009].
-@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
-Here we first review evidence and criticisms against this assumption.
-We then provide our own test of the MFD using partisan news articles.
-
-## Moral Foundations Dictionary
-
-Haidt and Jesse (2007) formulated MFT as a method by which to capture the entirety of humans' moral domain.
-We argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals.
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-MFT holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].
-
-In order to capture language's role in moral and political reasoning, @Graham2009 formulated the MFD in order to capture moral reasoning and justification as used in speech and text.
-The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-@Graham2009 created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from we' initial list.
-
-Similar to previous research on MFT, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers.
-Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers.
-However, conservative ministers did not use *ingroup/loyalty* words more than liberals.
-Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].
-
-## Critiques of Moral Foundations
-
-MFT has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-@Suhler2011 criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-Likewise, @Gray2015 argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
-@Schein2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
-
-Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.
-Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S.
-Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.
-In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
-Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
-Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores.
-Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects.
-Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
-Exploring the political Twitterverse, @Sterling2018 found differences in the MFD depend on political sophistication.
-For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
-While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].
-Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.
-
-The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).
-These attempts generally fall into two categories: human annotations and semantic representations.
-@Hopp2021 represents the first approach where instead of relying on 'experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
-While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
-@Garten2016 represents the second categories which instead relies on data-driven semantic analysis.
-Using shallow neural net models like word2vec [@mikolov_efficient_2013], moral foundations were measured using semantic similarity vectors rather than simple word counts.
-
-As a further conceptual replication of @Frimer2020, we test the liberal-conservative difference proposed by MFT using partisan media content and the MFD.
-We first test differences in a general news corpus compared liberal sources (National Public Radio [NPR] and the New York Times [NYT]) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavanaugh's U.S.
-Supreme Court nomination and the U.S.
-Government Shutdown in 2018-2019.
-In the second study, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
-To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Like @Frimer2020, results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.
-
-# Study 1
-
-# Method
-
-For the first study, we approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
-We hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*).
-Additionally, we hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations.
-
-## Sources
-
-Political articles were collected from the websites of four notable U.S.
-news sources, a process known as web scraping.
-The sources were *NYT*, *NPR*, *Fox News*, and *Breitbart*.
-They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-We determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, the *NYT* and *NPR* are preferred by consumers reporting a liberal bias or lean.
-In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean.
-@Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.
-At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible.
-
-Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script.
-For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].
-
-Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from the *NYT* and *Breitbart*.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
-Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
-We later ran a process in order to exclude any duplicate articles.
-*Fox News* presented a similar issue.
-We discovered *Fox News* utilized six URLs in addition to the regular politics page.
-These URLs led to pages containing content pertaining the U.S.
-Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
-Once again, duplicates were subsequently eliminated from any analyses.
-
-## Materials
-
-Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016].
-Using this dataset, we identified word count and average word count per source.
-This process was completed once daily starting in February 2018 until March 2018.
-Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected in April 2018.
-
-```{r include = F, eval = F}
-# to see the web scraping and data cleanup for this section see web_scraping.Rmd
-# this code was run previously to create the data for this manuscript
-# note that website changes to places like the NYT means it likely does
-# not run in the same way anymore
-```
-
-## Data analysis
-
-Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017].
-This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
-At this point, duplicate articles were discarded.
-
-The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@Feinerer2017].
-The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*).
-The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
-
-Concurrent research by @Jordan2019 assesses the validity of both the MFQ and the MFD through a multi-trait multi-method analysis of the two instruments using multiple samples.
-The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-We were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
-Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
-
-A complete list of the words for each moral foundation area was created from previous experiments.
-The total number of times each of those words was used in an article was calculated.
-This information was merged with the valence values from the @Warriner2013 dataset.
-A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article.
-The final score was multiplied by 100 to represented a weighted percentage.
-Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article.
-Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence.
-Positive values indicate positive valence, and negative values indicate negative valence.
-Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
-See Table \@ref(tab:example-weight) for an example.
-
-```{r stem_text, eval=TRUE, include=FALSE}
-final = read.csv("./exp1_data/finaldata.csv", stringsAsFactors = F)
-final = na.omit(final) #one weird NA line
-
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final)) {
-
-  final$edited[i] = preprocess(final$Text[i], #one value at a time
-           case = "lower",
-           remove.punct = TRUE,
-           remove.numbers = FALSE,
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final$stemmed[i] = stemDocument(final$edited[i], language = "english")
-}
-
-```
-
-```{r stem_warriner, include = FALSE}
-##open the Warriner data for later
-warriner = read.csv("./exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
-warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
-
-for(i in 1:nrow(warriner)) {
-  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
-}
-```
-
-```{r create_datasets_harm, echo = F, include=FALSE}
-#read in the harm total words from the mtmm project
-harm_all = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA" & !is.na(harm_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-harm_final_data = rbind(harm_final_data, temp2)
-}
-
-#pull in the data from Warriner
-harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
-#fought, safer, spurn
-harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn available
-```
-
-```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA" & !is.na(fair_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-fair_final_data = rbind(fair_final_data, temp2)
-}
-
-fair_final_data$valence = vlookup(fair_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
-#just plagiar safer
-fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & !is.na(ingroup_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-ingroup_final_data = rbind(ingroup_final_data, temp2)
-}
-
-ingroup_final_data$valence = vlookup(ingroup_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA" & !is.na(authority_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-authority_final_data = rbind(authority_final_data, temp2)
-}
-
-authority_final_data$valence = vlookup(authority_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
-#  abov behind   gase higher  older  taken
-authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA" & !is.na(purity_all$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final$Url[i]
-temp2$Source = final$Source[i]
-temp2$wordcount = final$wordcount[i]
-
-#bind with original
-purity_final_data = rbind(purity_final_data, temp2)
-}
-
-purity_final_data$valence = vlookup(purity_final_data$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data$Var1[is.na(purity_final_data$valence) & purity_final_data$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women
-purity_final_data$valence[purity_final_data$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data$valence[purity_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data$valence[purity_final_data$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r descriptives, echo = F, include = FALSE}
-#summarize the dataset so that you have the total and percent for each foundation
-# summary(harm_final_data)
-# summary(fair_final_data)
-# summary(ingroup_final_data)
-# summary(authority_final_data)
-# summary(purity_final_data)
-# #report descriptive statistics of the foundations
-# mean(harm_final_data$valence)
-# sd(harm_final_data$valence)
-# mean(fair_final_data$valence)
-# sd(fair_final_data$valence)
-# mean(ingroup_final_data$valence)
-# sd(ingroup_final_data$valence)
-# mean(authority_final_data$valence)
-# sd(authority_final_data$valence)
-# mean(purity_final_data$valence)
-# sd(purity_final_data$valence)
-#note that a big problem is the valence of the words
-```
-
-```{r analysis_harm, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100
-
-#flatten down to sum by article
-harm_final_temp = aggregate(harm_final_data$weight,
-          by = list(harm_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp) = c("URL", "MFDweight")
-
-harm_final_temp$lean[grepl("nytimes.com", harm_final_temp$URL) |
-                       grepl("npr.org", harm_final_temp$URL)] = "Liberal"
-harm_final_temp$lean[grepl("breitbart.com", harm_final_temp$URL) |
-                       grepl("foxnews.com", harm_final_temp$URL)] = "Conservative"
-
-harm_final_temp$Source[grepl("nytimes.com", harm_final_temp$URL)] = "NY Times"
-harm_final_temp$Source[grepl("npr.org", harm_final_temp$URL)] = "NPR"
-harm_final_temp$Source[grepl("foxnews.com", harm_final_temp$URL)] = "Fox"
-harm_final_temp$Source[grepl("breitbart.com", harm_final_temp$URL)] = "Breitbart"
-
-harm_icc <- lme(MFDweight ~ 1, 
-                data = harm_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source)
-                )
-
-harm_model = lme(MFDweight ~ lean,
-                 data = harm_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source)
-                 )
-summary(harm_model)
-
-# check linearity
-random <- rchisq(nrow(harm_final_temp), 7)
-residuals <- scale(residuals(harm_model))
-fitted <- scale(fitted(harm_model))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_fair, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data$weight = fair_final_data$Freq * fair_final_data$valence / fair_final_data$wordcount * 100
-
-#flatten down to sum by article
-fair_final_temp = aggregate(fair_final_data$weight,
-          by = list(fair_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp) = c("URL", "MFDweight")
-
-fair_final_temp$lean[grepl("nytimes.com", fair_final_temp$URL) |
-                       grepl("npr.org", fair_final_temp$URL)] = "Liberal"
-fair_final_temp$lean[grepl("breitbart.com", fair_final_temp$URL) |
-                       grepl("foxnews.com", fair_final_temp$URL)] = "Conservative"
-
-fair_final_temp$Source[grepl("nytimes.com", fair_final_temp$URL)] = "NY Times"
-fair_final_temp$Source[grepl("npr.org", fair_final_temp$URL)] = "NPR"
-fair_final_temp$Source[grepl("foxnews.com", fair_final_temp$URL)] = "Fox"
-fair_final_temp$Source[grepl("breitbart.com", fair_final_temp$URL)] = "Breitbart"
-
-fair_icc <- lme(MFDweight ~ 1, 
-                data = fair_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source)
-                )
-
-fair_model = lme(MFDweight ~ lean,
-                 data = fair_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model)
-
-# check linearity
-random <- rchisq(nrow(fair_final_temp), 7)
-residuals <- scale(residuals(fair_model))
-fitted <- scale(fitted(fair_model))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_ingroup, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data$weight = ingroup_final_data$Freq * ingroup_final_data$valence / ingroup_final_data$wordcount * 100
-
-#flatten down to sum by article
-ingroup_final_temp = aggregate(ingroup_final_data$weight,
-          by = list(ingroup_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp) = c("URL", "MFDweight")
-
-ingroup_final_temp$lean[grepl("nytimes.com", ingroup_final_temp$URL) |
-                       grepl("npr.org", ingroup_final_temp$URL)] = "Liberal"
-ingroup_final_temp$lean[grepl("breitbart.com", ingroup_final_temp$URL) |
-                       grepl("foxnews.com", ingroup_final_temp$URL)] = "Conservative"
-
-ingroup_final_temp$Source[grepl("nytimes.com", ingroup_final_temp$URL)] = "NY Times"
-ingroup_final_temp$Source[grepl("npr.org", ingroup_final_temp$URL)] = "NPR"
-ingroup_final_temp$Source[grepl("foxnews.com", ingroup_final_temp$URL)] = "Fox"
-ingroup_final_temp$Source[grepl("breitbart.com", ingroup_final_temp$URL)] = "Breitbart"
-
-ingroup_icc = lme(MFDweight ~ 1,
-                 data = ingroup_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-ingroup_model = lme(MFDweight ~ lean,
-                 data = ingroup_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model)
-
-# check linearity
-random <- rchisq(nrow(ingroup_final_temp), 7)
-residuals <- scale(residuals(ingroup_model))
-fitted <- scale(fitted(ingroup_model))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_authority, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data$weight = authority_final_data$Freq * authority_final_data$valence / authority_final_data$wordcount * 100
-
-#flatten down to sum by article
-authority_final_temp = aggregate(authority_final_data$weight,
-          by = list(authority_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp) = c("URL", "MFDweight")
-
-authority_final_temp$lean[grepl("nytimes.com", authority_final_temp$URL) |
-                       grepl("npr.org", authority_final_temp$URL)] = "Liberal"
-authority_final_temp$lean[grepl("breitbart.com", authority_final_temp$URL) |
-                       grepl("foxnews.com", authority_final_temp$URL)] = "Conservative"
-
-authority_final_temp$Source[grepl("nytimes.com", authority_final_temp$URL)] = "NY Times"
-authority_final_temp$Source[grepl("npr.org", authority_final_temp$URL)] = "NPR"
-authority_final_temp$Source[grepl("foxnews.com", authority_final_temp$URL)] = "Fox"
-authority_final_temp$Source[grepl("breitbart.com", authority_final_temp$URL)] = "Breitbart"
-
-authority_icc = lme(MFDweight ~ 1,
-                 data = authority_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-authority_model = lme(MFDweight ~ lean,
-                 data = authority_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model)
-
-# check linearity
-random <- rchisq(nrow(authority_final_temp), 7)
-residuals <- scale(residuals(authority_model))
-fitted <- scale(fitted(authority_model))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_purity, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data$weight = purity_final_data$Freq * purity_final_data$valence / purity_final_data$wordcount * 100
-
-#flatten down to sum by article
-purity_final_temp = aggregate(purity_final_data$weight,
-          by = list(purity_final_data$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp) = c("URL", "MFDweight")
-
-purity_final_temp$lean[grepl("nytimes.com", purity_final_temp$URL) |
-                       grepl("npr.org", purity_final_temp$URL)] = "Liberal"
-purity_final_temp$lean[grepl("breitbart.com", purity_final_temp$URL) |
-                       grepl("foxnews.com", purity_final_temp$URL)] = "Conservative"
-
-purity_final_temp$Source[grepl("nytimes.com", purity_final_temp$URL)] = "NY Times"
-purity_final_temp$Source[grepl("npr.org", purity_final_temp$URL)] = "NPR"
-purity_final_temp$Source[grepl("foxnews.com", purity_final_temp$URL)] = "Fox"
-purity_final_temp$Source[grepl("breitbart.com", purity_final_temp$URL)] = "Breitbart"
-
-purity_icc = lme(MFDweight ~ 1,
-                 data = purity_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-purity_model = lme(MFDweight ~ lean,
-                 data = purity_final_temp,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model)
-
-# check linearity
-random <- rchisq(nrow(purity_final_temp), 7)
-residuals <- scale(residuals(purity_model))
-fitted <- scale(fitted(purity_model))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r example-weight, results = 'asis', echo = FALSE}
-temp_table <- harm_final_data %>% 
-  filter(Freq > 0) %>% 
-  arrange(-Freq) %>% 
-  group_by(Var1) %>% 
-  slice_head() %>% 
-  group_by(URL) %>% 
-  arrange(-Freq) %>% 
-  slice_head() %>% 
-  ungroup() %>% 
-  slice_sample(n = 15, replace = F)
-
-apa_table(temp_table %>% select(-URL), 
-          note = "Concepts were stemmed to match datasets.",
-          caption = "Example of Weighted Coding for Harm Words",
-          col.names = c("Source", "Concept", "Frequency", "Total Words", "Valence", "Weighted Score"),
-          format = "latex",
-          escape = F,
-          align = c("l", "l", rep("c", 4)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-# Results
-
-## Descriptive Statistics
+# Study 2: Descriptive Statistics
 
@@
 ####build the table here####
-tableprint = matrix(NA, nrow=4, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
+tableprint = matrix(NA, nrow = 4, ncol = 11)
+colnames(tableprint) = c("Source", 
+                         "Mean_Valence", "SD_Valence", "Number_of_Articles",
+                         "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types",
+                         "SD_Types", "Mean_Readability", "SD_Readability")
 
@@
 V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Study 1 - Descriptive Statistics by Source",
+          caption = "Study 2 - Descriptive Statistics by Source",
           col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
@@
 
-## Inferential Statistics
-
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error [@Gelman2006].
-Using the *nlme* library in *R* [@Pinheiro2017], each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-Therefore, the models were calculated by: Weighted Score ~ Political Lean + (~1|Source).
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the *authority/respect* foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp1-table).
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, we observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
-
-```{r exp1_table_calc, include = F, echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint2 = matrix(NA, ncol = 9, nrow = 5)
-colnames(tableprint2) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
-
-#calculate d
-#harm
-harm_d = d.ind.t(m1 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
-                 m2 = mean(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Conservative"]),
-                 n2 = length(harm_final_temp$MFDweight[harm_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d = d.ind.t(m1 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
-                 m2 = mean(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Conservative"]),
-                 n2 = length(fair_final_temp$MFDweight[fair_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d = d.ind.t(m1 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
-                 m2 = mean(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp$MFDweight[ingroup_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d = d.ind.t(m1 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
-                 m2 = mean(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Conservative"]),
-                 n2 = length(authority_final_temp$MFDweight[authority_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d = d.ind.t(m1 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
-                 m2 = mean(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Conservative"]),
-                 n2 = length(purity_final_temp$MFDweight[purity_final_temp$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint2[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1,
-                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
-                    harm_d$d, icc(harm_icc)$ICC_unadjusted)
-tableprint2[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1,
-                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
-                    fair_d$d, icc(fair_icc)$ICC_unadjusted)
-tableprint2[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1,
-                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
-                    ingroup_d$d, icc(ingroup_icc)$ICC_unadjusted)
-tableprint2[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1,
-                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
-                    authority_d$d, icc(authority_icc)$ICC_unadjusted)
-tableprint2[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1,
-                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
-                    purity_d$d, icc(purity_icc)$ICC_unadjusted)
-
-tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]), big.mark = "")
-tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
-tableprint2[ , 9] = printp(as.numeric(tableprint2[ , 7]))
-```
-
-```{r exp1-table, results = 'asis', echo = F}
-apa_table(as.data.frame(tableprint2),
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Study 1 Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-```{r conference-pic, eval = F, include = F}
-cleanup = theme(panel.grid.major = element_blank(),
-                panel.grid.minor = element_blank(),
-                panel.background = element_blank(),
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 10))
-
-graphdata = as.data.frame(tableprint)
-graphlong = melt(graphdata[ , c(1,2,4)],
-                 id = "Foundation")
-graphlong2 = melt(graphdata[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong$sd = graphlong2$value
-graphlong$lower = as.numeric(as.character(graphlong$value)) - 2*as.numeric(as.character(graphlong$sd))
-graphlong$upper = as.numeric(as.character(graphlong$value)) + 2*as.numeric(as.character(graphlong$sd))
-
-graphlong$value = as.numeric(as.character(graphlong$value))
-
-graph_data = ggplot(graphlong, aes(Foundation, value, color = variable)) +
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper),
-                position = position_dodge(width = 0.90),
-                width = .2) +
-  cleanup +
-  ylab("Mean Weighted Valence") +
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-tiff(filename = "exp1_graph.tiff", res = 300, width = 4,
-     height = 3, units = 'in', compression = "lzw")
-plot(graph_data)
-dev.off()
-
-```
-
-# Discussion
-
-The results obtained in Study 1 fail to support the differences predicted by MFT.
-First, differences between liberal and conservative news sources failed to reach statistical or practical (effect size) significance for any foundations.
-Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
-Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
-Overall, the results lend strong support to the case against the MFD and weakens the case generally for MFT.
-
-However, one possible limitation of the current data is the generalness of the corpus.
-The selection of the broad and amorphous topic of "political news" may have led to the scraping of large numbers of articles with little to no moral-centric content.
-To address this limitation, two changes that were subsequently employed in Study 2.
-First, we elected to include more news sources for web scraping and analysis in addition to the four used in Study 1.
-Second, we chose to focus  data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court and the U.S.
-government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Study 2 is the best test of the MFT and the MFD in the context of partisan news.
-
-# Study 2
-
-# Method
-
-In contrast to Study 1, we approached Study 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For the second study, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-We tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, we analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under MFT.
-
-```{r include = F, echo = F}
-# please see the web_scraping.Rmd to see how we originally collected this data
-```
-
-## Sources
-
-Articles pertaining to the Brett Kavanaugh Supreme Court confirmation hearing and the 2018-2019 U.S.
-Government shutdown were scraped from the websites of 10 U.S.
-news sources.
-As in Study 1, these sources were selected owing to their favorability among political partisans according to @Mitchell2014.
-The sources favored by the highest proportion of consistent liberals were the *NYT*, *NPR*, *Slate*, *Huffington Post*, and *Politico* [@Mitchell2014].
-The sources favored by the highest proportion of consistent conservatives included *Fox News*, *Breitbart*, *The Rush Limbaugh Show*, *The Blaze*, and *Sean Hannity*.
-These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the *R* script.
-
-## Materials
-
-Using the *rvest* and *RSelenium* libraries, we pulled body text for individual articles from each of the aforementioned 10 news sources and compiled them together [@Wickham2016; @harrison_rselenium_2020].
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the partial U.S.
-Government shutdown of 2018-2019.
-The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, we elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
-
-```{r data_clean_kav, eval = T, echo = F}
-##combine all kav data into one dataset
-#read it in
-NYtimes_kav = read.csv("./exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-NPR_kav = read.csv("./exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-SLATE_kav = read.csv("./exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("./exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-POLITICO_kav = read.csv("./exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-FOX_kav = read.csv("./exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok
-BREITBART_kav = read.csv("./exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
-RUSH_kav = read.csv("./exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-BLAZE_kav = read.csv("./exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HANNITY_kav = read.csv("./exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-
-#merge it together
-master_kav = rbind(NYtimes_kav, NPR_kav, SLATE_kav,
-                        HUFFPO_kav, POLITICO_kav, FOX_kav,
-                        BREITBART_kav, RUSH_kav, BLAZE_kav,
-                        HANNITY_kav)
-
-#fix this issue
-master_kav$Text = gsub("\\.", "\\. ", master_kav$Text)
-
-##get rid of the blank stuff
-library(ngram)
-
-for (i in 1:nrow(master_kav)) {
-  master_kav$wordcount[i] = wordcount(master_kav$Text[i])
-}
-
-nozero = subset(master_kav, wordcount > 0)
-nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-# tapply(nozero$wordcount, nozero$Source, mean)
-# tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones - there are none
-#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##all data
-final_kav = nozero
-```
-
-```{r data_clean_gs, eval = T, echo = F}
-##combine all gs data into one dataset
-#read it in
-NYtimes_gs = read.csv("./exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
-NPR_gs = read.csv("./exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
-SLATE_gs = read.csv("./exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok
-HUFFPO_gs = read.csv("./exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok
-POLITICO_gs = read.csv("./exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
-FOX_gs = read.csv("./exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok
-BREITBART_gs = read.csv("./exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok
-RUSH_gs = read.csv("./exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
-BLAZE_gs = read.csv("./exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok
-HANNITY_gs = read.csv("./exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
-
-#merge it together
-master_gs = rbind(NYtimes_gs, NPR_gs, SLATE_gs,
-                        HUFFPO_gs, POLITICO_gs, FOX_gs,
-                        BREITBART_gs, RUSH_gs, BLAZE_gs,
-                        HANNITY_gs)
-
-#fix this issue
-master_gs$Text = gsub("\\.", "\\. ", master_gs$Text)
-
-for (i in 1:nrow(master_gs)) {
-  master_gs$wordcount[i] = wordcount(master_gs$Text[i])
-}
-
-nozero = subset(master_gs, wordcount > 0)
-nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
-
-# tapply(nozero$wordcount, nozero$Source, mean)
-# tapply(nozero$wordcount, nozero$Source, sum)
-
-##take out the disqus ones
-#nodis = nozero[ -c(grep("disqus", nozero$Url)), ]
-
-##all data
-final_gs = nozero
-```
-
-```{r stem_text_both, eval = T, echo = F}
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final_kav)) {
-
-  final_kav$edited[i] = preprocess(final_kav$Text[i], #one value at a time
-           case = "lower",
-           remove.punct = TRUE,
-           remove.numbers = FALSE,
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final_kav$stemmed[i] = stemDocument(final_kav$edited[i], language = "english")
-}
-
-#process the Text column (write a loop) - save processed text as a separate column
-for(i in 1:nrow(final_gs)) {
-
-  final_gs$edited[i] = preprocess(final_gs$Text[i], #one value at a time
-           case = "lower",
-           remove.punct = TRUE,
-           remove.numbers = FALSE,
-           fix.spacing = TRUE)
-
-##stem the words - do this second in the loop
-  final_gs$stemmed[i] = stemDocument(final_gs$edited[i], language = "english")
-}
-
-```
-
-## Data analysis
-
-As in Study 1, the text was scanned with *ngram* [@Schmidt2017].
-Again, blank articles, text from the Disqus system, and duplicate articles were removed.
-The text was processed and stemmed in order to convert to a usable form for further analysis [@Feinerer2017].
-Each individual word was reduced to its stem (i.e., *diseased* was stemmed to *diseas*).
-Once again, the same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.
-We obtained the words' percent occurrence in the text.
-Percents were multiplied by *z*-scored valence and categorized into their proper MFD category.
-
-```{r create_datasets_harm_kav, eval = T, echo = F, include = F}
-#read in the harm total words from the mtmm project
-harm_all_kav = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all_kav$words[harm_all_kav$words != "" & harm_all_kav$words != "NA" & !is.na(harm_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-harm_final_data_kav = rbind(harm_final_data_kav, temp2)
-}
-
-#pull in the data from Warriner
-harm_final_data_kav$valence = vlookup(harm_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-#table(harm_final_data_kav$Var1[is.na(harm_final_data_kav$valence) & harm_final_data_kav$Freq > 0])
-#fought, safer, spurn
-harm_final_data_kav$valence[harm_final_data_kav$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data_kav$valence[harm_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all_kav$words[fair_all_kav$words != "" & fair_all_kav$words != "NA" & !is.na(fair_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-fair_final_data_kav = rbind(fair_final_data_kav, temp2)
-}
-
-fair_final_data_kav$valence = vlookup(fair_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data_kav$Var1[is.na(fair_final_data_kav$valence) & fair_final_data_kav$Freq > 0])
-#just plagiar safer
-fair_final_data_kav$valence[fair_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all_kav$words[ingroup_all_kav$words != "" & ingroup_all_kav$words != "NA" & !is.na(ingroup_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-ingroup_final_data_kav = rbind(ingroup_final_data_kav, temp2)
-}
-
-ingroup_final_data_kav$valence = vlookup(ingroup_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data_kav$Var1[is.na(ingroup_final_data_kav$valence) & ingroup_final_data_kav$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data_kav$valence[ingroup_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all_kav$words[authority_all_kav$words != "" & authority_all_kav$words != "NA" & !is.na(authority_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-authority_final_data_kav = rbind(authority_final_data_kav, temp2)
-}
-
-authority_final_data_kav$valence = vlookup(authority_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data_kav$Var1[is.na(authority_final_data_kav$valence) & authority_final_data_kav$Freq > 0])
-#  abov behind   gase higher  older  taken
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data_kav$valence[authority_final_data_kav$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data_kav = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_kav)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all_kav$words[purity_all_kav$words != "" & purity_all_kav$words != "NA" & !is.na(purity_all_kav$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_kav$Url[i]
-temp2$Source = final_kav$Source[i]
-temp2$wordcount = final_kav$wordcount[i]
-
-#bind with original
-purity_final_data_kav = rbind(purity_final_data_kav, temp2)
-}
-
-purity_final_data_kav$valence = vlookup(purity_final_data_kav$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data_kav$Var1[is.na(purity_final_data_kav$valence) & purity_final_data_kav$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data_kav$valence[purity_final_data_kav$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r create_datasets_harm_gs, eval = T, echo = F, include = F}
-#read in the harm total words from the mtmm project
-harm_all_gs = read.csv("./exp1_data/harm_words_total.csv", stringsAsFactors = F)
-
-harm_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(harm_all_gs$words[harm_all_gs$words != "" & harm_all_gs$words != "NA" & !is.na(harm_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-harm_final_data_gs = rbind(harm_final_data_gs, temp2)
-}
-
-#pull in the data from Warriner
-harm_final_data_gs$valence = vlookup(harm_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-#table(harm_final_data_gs$Var1[is.na(harm_final_data_gs$valence) & harm_final_data_gs$Freq > 0])
-#fought, safer, spurn
-harm_final_data_gs$valence[harm_final_data_gs$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
-harm_final_data_gs$valence[harm_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
-```
-
-```{r create_datasets_fair_gs, echo = F, include=FALSE}
-fair_all_gs = read.csv("./exp1_data/fair_words_total.csv", stringsAsFactors = F)
-
-fair_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(fair_all_gs$words[fair_all_gs$words != "" & fair_all_gs$words != "NA" & !is.na(fair_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-fair_final_data_gs = rbind(fair_final_data_gs, temp2)
-}
-
-fair_final_data_gs$valence = vlookup(fair_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(fair_final_data_gs$Var1[is.na(fair_final_data_gs$valence) & fair_final_data_gs$Freq > 0])
-#just plagiar safer
-fair_final_data_gs$valence[fair_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#nothing for just or plagiarism
-```
-
-```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
-ingroup_all_gs = read.csv("./exp1_data/ingroup_words_total.csv", stringsAsFactors = F)
-
-ingroup_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(ingroup_all_gs$words[ingroup_all_gs$words != "" & ingroup_all_gs$words != "NA" & !is.na(ingroup_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-ingroup_final_data_gs = rbind(ingroup_final_data_gs, temp2)
-}
-
-ingroup_final_data_gs$valence = vlookup(ingroup_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(ingroup_final_data_gs$Var1[is.na(ingroup_final_data_gs$valence) & ingroup_final_data_gs$Freq > 0])
-#backstabb  benedict      best      fals   indvidu      juda    knight      true
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
-ingroup_final_data_gs$valence[ingroup_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-```
-
-```{r create_datasets_authority_gs, echo = F, include=FALSE}
-authority_all_gs = read.csv("./exp1_data/authority_words_total.csv", stringsAsFactors = F)
-
-authority_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(authority_all_gs$words[authority_all_gs$words != "" & authority_all_gs$words != "NA" & !is.na(authority_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-authority_final_data_gs = rbind(authority_final_data_gs, temp2)
-}
-
-authority_final_data_gs$valence = vlookup(authority_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(authority_final_data_gs$Var1[is.na(authority_final_data_gs$valence) & authority_final_data_gs$Freq > 0])
-#  abov behind   gase higher  older  taken
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
-authority_final_data_gs$valence[authority_final_data_gs$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
-```
-
-```{r create_datasets_purity_gs, echo = F, include=FALSE}
-purity_all_gs = read.csv("./exp1_data/purity_words_total.csv", stringsAsFactors = F)
-
-purity_final_data_gs = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)
-
-for (i in 1:nrow(final_gs)) {
-##first make a table of a response, unlisting everything
-temp = as.data.frame(table(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-#only pull the words in the dataset for each foundation
-temp2 = temp[temp$Var1 %in% unique(purity_all_gs$words[purity_all_gs$words != "" & purity_all_gs$words != "NA" & !is.na(purity_all_gs$words)]), ]
-
-#control here for times when no words
-if (nrow(temp2) == 0){
-  temp2 = data.frame("Var1" = 0, "Freq" = 0)
-}
-
-#add to the dataset
-temp2$URL = final_gs$Url[i]
-temp2$Source = final_gs$Source[i]
-temp2$wordcount = final_gs$wordcount[i]
-
-#bind with original
-purity_final_data_gs = rbind(purity_final_data_gs, temp2)
-}
-
-purity_final_data_gs$valence = vlookup(purity_final_data_gs$Var1, #index in original data
-                                  warriner, #where's the stuff you want to put in
-                                  "V.Mean.Sum", #what column is the stuff you want
-                                  "Word2") #what's the matching index
-
-#figure out stupid words
-table(purity_final_data_gs$Var1[is.na(purity_final_data_gs$valence) & purity_final_data_gs$Freq > 0])
-#befor christian     jesus      mari      none    sacred    someon      true     women
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
-purity_final_data_gs$valence[purity_final_data_gs$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
-```
-
-```{r descriptives_both, echo = F, include = FALSE}
-##summarize the dataset so that you have the total and percent for each foundation
-#kav
-summary(harm_final_data_kav)
-summary(fair_final_data_kav)
-summary(ingroup_final_data_kav)
-summary(authority_final_data_kav)
-summary(purity_final_data_kav)
-#gs
-summary(harm_final_data_gs)
-summary(fair_final_data_gs)
-summary(ingroup_final_data_gs)
-summary(authority_final_data_gs)
-summary(purity_final_data_gs)
-##report descriptive statistics of the foundations
-#kav
-mean(harm_final_data_kav$valence, na.rm = T)
-sd(harm_final_data_kav$valence, na.rm = T)
-mean(fair_final_data_kav$valence, na.rm = T)
-sd(fair_final_data_kav$valence, na.rm = T)
-mean(ingroup_final_data_kav$valence, na.rm = T)
-sd(ingroup_final_data_kav$valence, na.rm = T)
-mean(authority_final_data_kav$valence, na.rm = T)
-sd(authority_final_data_kav$valence, na.rm = T)
-mean(purity_final_data_kav$valence, na.rm = T)
-sd(purity_final_data_kav$valence, na.rm = T)
-#gs
-mean(harm_final_data_gs$valence, na.rm = T)
-sd(harm_final_data_gs$valence, na.rm = T)
-mean(fair_final_data_gs$valence, na.rm = T)
-sd(fair_final_data_gs$valence, na.rm = T)
-mean(ingroup_final_data_gs$valence, na.rm = T)
-sd(ingroup_final_data_gs$valence, na.rm = T)
-mean(authority_final_data_gs$valence, na.rm = T)
-sd(authority_final_data_gs$valence, na.rm = T)
-mean(purity_final_data_gs$valence, na.rm = T)
-sd(purity_final_data_gs$valence, na.rm = T)
-#note that a big problem is the valence of the words
-```
-
-```{r analysis_harm_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data_kav$weight = harm_final_data_kav$Freq * harm_final_data_kav$valence / harm_final_data_kav$wordcount * 100
-
-#flatten down to sum by article
-harm_final_temp_kav = aggregate(harm_final_data_kav$weight,
-          by = list(harm_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp_kav) = c("URL", "MFDweight")
-
-harm_final_temp_kav$lean[grepl("nytimes.com", harm_final_temp_kav$URL) |
-                       grepl("npr.org", harm_final_temp_kav$URL) |
-                        grepl("slate.com", harm_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", harm_final_temp_kav$URL) |
-                        grepl("politico.com", harm_final_temp_kav$URL)] = "Liberal"
-
-harm_final_temp_kav$lean[grepl("breitbart.com", harm_final_temp_kav$URL) |
-                       grepl("foxnews.com", harm_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", harm_final_temp_kav$URL) |
-                       grepl("theblaze.com", harm_final_temp_kav$URL) |
-                       grepl("hannity.com", harm_final_temp_kav$URL)] = "Conservative"
-
-harm_final_temp_kav$Source[grepl("nytimes.com", harm_final_temp_kav$URL)] = "NY Times"
-harm_final_temp_kav$Source[grepl("npr.org", harm_final_temp_kav$URL)] = "NPR"
-harm_final_temp_kav$Source[grepl("slate.com", harm_final_temp_kav$URL)] = "Slate"
-harm_final_temp_kav$Source[grepl("huffingtonpost.com", harm_final_temp_kav$URL)] = "Huffington Post"
-harm_final_temp_kav$Source[grepl("politico.com", harm_final_temp_kav$URL)] = "Politico"
-harm_final_temp_kav$Source[grepl("foxnews.com", harm_final_temp_kav$URL)] = "Fox"
-harm_final_temp_kav$Source[grepl("breitbart.com", harm_final_temp_kav$URL)] = "Breitbart"
-harm_final_temp_kav$Source[grepl("rushlimbaugh.com", harm_final_temp_kav$URL)] = "Rush Limbaugh"
-harm_final_temp_kav$Source[grepl("theblaze.com", harm_final_temp_kav$URL)] = "The Blaze"
-harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
-
-harm_icc_k <- lme(MFDweight ~ 1,
-                 data = harm_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-harm_model_kav = lme(MFDweight ~ lean,
-                 data = harm_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model_kav)
-r.squaredGLMM(harm_model_kav)
-
-# check linearity
-random <- rchisq(nrow(harm_final_temp_kav), 7)
-residuals <- scale(residuals(harm_model_kav))
-fitted <- scale(fitted(harm_model_kav))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_fair_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data_kav$weight = fair_final_data_kav$Freq * fair_final_data_kav$valence / fair_final_data_kav$wordcount * 100
-
-#flatten down to sum by article
-fair_final_temp_kav = aggregate(fair_final_data_kav$weight,
-          by = list(fair_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp_kav) = c("URL", "MFDweight")
-
-fair_final_temp_kav$lean[grepl("nytimes.com", fair_final_temp_kav$URL) |
-                       grepl("npr.org", fair_final_temp_kav$URL) |
-                        grepl("slate.com", fair_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", fair_final_temp_kav$URL) |
-                        grepl("politico.com", fair_final_temp_kav$URL)] = "Liberal"
-
-fair_final_temp_kav$lean[grepl("breitbart.com", fair_final_temp_kav$URL) |
-                       grepl("foxnews.com", fair_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", fair_final_temp_kav$URL) |
-                       grepl("theblaze.com", fair_final_temp_kav$URL) |
-                       grepl("hannity.com", fair_final_temp_kav$URL)] = "Conservative"
-
-fair_final_temp_kav$Source[grepl("nytimes.com", fair_final_temp_kav$URL)] = "NY Times"
-fair_final_temp_kav$Source[grepl("npr.org", fair_final_temp_kav$URL)] = "NPR"
-fair_final_temp_kav$Source[grepl("slate.com", fair_final_temp_kav$URL)] = "Slate"
-fair_final_temp_kav$Source[grepl("huffingtonpost.com", fair_final_temp_kav$URL)] = "Huffington Post"
-fair_final_temp_kav$Source[grepl("politico.com", fair_final_temp_kav$URL)] = "Politico"
-fair_final_temp_kav$Source[grepl("foxnews.com", fair_final_temp_kav$URL)] = "Fox"
-fair_final_temp_kav$Source[grepl("breitbart.com", fair_final_temp_kav$URL)] = "Breitbart"
-fair_final_temp_kav$Source[grepl("rushlimbaugh.com", fair_final_temp_kav$URL)] = "Rush Limbaugh"
-fair_final_temp_kav$Source[grepl("theblaze.com", fair_final_temp_kav$URL)] = "The Blaze"
-fair_final_temp_kav$Source[grepl("hannity.com", fair_final_temp_kav$URL)] = "Sean Hannity"
-
-fair_icc_k <- lme(MFDweight ~ 1,
-                 data = fair_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-fair_model_kav = lme(MFDweight ~ lean,
-                 data = fair_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model_kav)
-
-# check linearity
-random <- rchisq(nrow(fair_final_temp_kav), 7)
-residuals <- scale(residuals(fair_model_kav))
-fitted <- scale(fitted(fair_model_kav))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_ingroup_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data_kav$weight = ingroup_final_data_kav$Freq * ingroup_final_data_kav$valence / ingroup_final_data_kav$wordcount * 100
-
-#flatten down to sum by article
-ingroup_final_temp_kav = aggregate(ingroup_final_data_kav$weight,
-          by = list(ingroup_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp_kav) = c("URL", "MFDweight")
-
-ingroup_final_temp_kav$lean[grepl("nytimes.com", ingroup_final_temp_kav$URL) |
-                       grepl("npr.org", ingroup_final_temp_kav$URL) |
-                        grepl("slate.com", ingroup_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", ingroup_final_temp_kav$URL) |
-                        grepl("politico.com", ingroup_final_temp_kav$URL)] = "Liberal"
-
-ingroup_final_temp_kav$lean[grepl("breitbart.com", ingroup_final_temp_kav$URL) |
-                       grepl("foxnews.com", ingroup_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL) |
-                       grepl("theblaze.com", ingroup_final_temp_kav$URL) |
-                       grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Conservative"
-
-ingroup_final_temp_kav$Source[grepl("nytimes.com", ingroup_final_temp_kav$URL)] = "NY Times"
-ingroup_final_temp_kav$Source[grepl("npr.org", ingroup_final_temp_kav$URL)] = "NPR"
-ingroup_final_temp_kav$Source[grepl("slate.com", ingroup_final_temp_kav$URL)] = "Slate"
-ingroup_final_temp_kav$Source[grepl("huffingtonpost.com", ingroup_final_temp_kav$URL)] = "Huffington Post"
-ingroup_final_temp_kav$Source[grepl("politico.com", ingroup_final_temp_kav$URL)] = "Politico"
-ingroup_final_temp_kav$Source[grepl("foxnews.com", ingroup_final_temp_kav$URL)] = "Fox"
-ingroup_final_temp_kav$Source[grepl("breitbart.com", ingroup_final_temp_kav$URL)] = "Breitbart"
-ingroup_final_temp_kav$Source[grepl("rushlimbaugh.com", ingroup_final_temp_kav$URL)] = "Rush Limbaugh"
-ingroup_final_temp_kav$Source[grepl("theblaze.com", ingroup_final_temp_kav$URL)] = "The Blaze"
-ingroup_final_temp_kav$Source[grepl("hannity.com", ingroup_final_temp_kav$URL)] = "Sean Hannity"
-
-ingroup_icc_k <- lme(MFDweight ~ 1,
-                 data = ingroup_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-ingroup_model_kav = lme(MFDweight ~ lean,
-                 data = ingroup_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model_kav)
-
-# check linearity
-random <- rchisq(nrow(ingroup_final_temp_kav), 7)
-residuals <- scale(residuals(ingroup_model_kav))
-fitted <- scale(fitted(ingroup_model_kav))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_authority_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data_kav$weight = authority_final_data_kav$Freq * authority_final_data_kav$valence / authority_final_data_kav$wordcount * 100
-
-#flatten down to sum by article
-authority_final_temp_kav = aggregate(authority_final_data_kav$weight,
-          by = list(authority_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp_kav) = c("URL", "MFDweight")
-
-authority_final_temp_kav$lean[grepl("nytimes.com", authority_final_temp_kav$URL) |
-                       grepl("npr.org", authority_final_temp_kav$URL) |
-                        grepl("slate.com", authority_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", authority_final_temp_kav$URL) |
-                        grepl("politico.com", authority_final_temp_kav$URL)] = "Liberal"
-
-authority_final_temp_kav$lean[grepl("breitbart.com", authority_final_temp_kav$URL) |
-                       grepl("foxnews.com", authority_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", authority_final_temp_kav$URL) |
-                       grepl("theblaze.com", authority_final_temp_kav$URL) |
-                       grepl("hannity.com", authority_final_temp_kav$URL)] = "Conservative"
-
-authority_final_temp_kav$Source[grepl("nytimes.com", authority_final_temp_kav$URL)] = "NY Times"
-authority_final_temp_kav$Source[grepl("npr.org", authority_final_temp_kav$URL)] = "NPR"
-authority_final_temp_kav$Source[grepl("slate.com", authority_final_temp_kav$URL)] = "Slate"
-authority_final_temp_kav$Source[grepl("huffingtonpost.com", authority_final_temp_kav$URL)] = "Huffington Post"
-authority_final_temp_kav$Source[grepl("politico.com", authority_final_temp_kav$URL)] = "Politico"
-authority_final_temp_kav$Source[grepl("foxnews.com", authority_final_temp_kav$URL)] = "Fox"
-authority_final_temp_kav$Source[grepl("breitbart.com", authority_final_temp_kav$URL)] = "Breitbart"
-authority_final_temp_kav$Source[grepl("rushlimbaugh.com", authority_final_temp_kav$URL)] = "Rush Limbaugh"
-authority_final_temp_kav$Source[grepl("theblaze.com", authority_final_temp_kav$URL)] = "The Blaze"
-authority_final_temp_kav$Source[grepl("hannity.com", authority_final_temp_kav$URL)] = "Sean Hannity"
-
-authority_icc_k <- lme(MFDweight ~ 1,
-                 data = authority_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-authority_model_kav = lme(MFDweight ~ lean,
-                 data = authority_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model_kav)
-
-# check linearity
-random <- rchisq(nrow(authority_final_temp_kav), 7)
-residuals <- scale(residuals(authority_model_kav))
-fitted <- scale(fitted(authority_model_kav))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_purity_kav, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data_kav$weight = purity_final_data_kav$Freq * purity_final_data_kav$valence / purity_final_data_kav$wordcount * 100
-
-#flatten down to sum by article
-purity_final_temp_kav = aggregate(purity_final_data_kav$weight,
-          by = list(purity_final_data_kav$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp_kav) = c("URL", "MFDweight")
-
-purity_final_temp_kav$lean[grepl("nytimes.com", purity_final_temp_kav$URL) |
-                       grepl("npr.org", purity_final_temp_kav$URL) |
-                        grepl("slate.com", purity_final_temp_kav$URL) |
-                        grepl("huffingtonpost.com", purity_final_temp_kav$URL) |
-                        grepl("politico.com", purity_final_temp_kav$URL)] = "Liberal"
-
-purity_final_temp_kav$lean[grepl("breitbart.com", purity_final_temp_kav$URL) |
-                       grepl("foxnews.com", purity_final_temp_kav$URL) |
-                       grepl("rushlimbaugh.com", purity_final_temp_kav$URL) |
-                       grepl("theblaze.com", purity_final_temp_kav$URL) |
-                       grepl("hannity.com", purity_final_temp_kav$URL)] = "Conservative"
-
-purity_final_temp_kav$Source[grepl("nytimes.com", purity_final_temp_kav$URL)] = "NY Times"
-purity_final_temp_kav$Source[grepl("npr.org", purity_final_temp_kav$URL)] = "NPR"
-purity_final_temp_kav$Source[grepl("slate.com", purity_final_temp_kav$URL)] = "Slate"
-purity_final_temp_kav$Source[grepl("huffingtonpost.com", purity_final_temp_kav$URL)] = "Huffington Post"
-purity_final_temp_kav$Source[grepl("politico.com", purity_final_temp_kav$URL)] = "Politico"
-purity_final_temp_kav$Source[grepl("foxnews.com", purity_final_temp_kav$URL)] = "Fox"
-purity_final_temp_kav$Source[grepl("breitbart.com", purity_final_temp_kav$URL)] = "Breitbart"
-purity_final_temp_kav$Source[grepl("rushlimbaugh.com", purity_final_temp_kav$URL)] = "Rush Limbaugh"
-purity_final_temp_kav$Source[grepl("theblaze.com", purity_final_temp_kav$URL)] = "The Blaze"
-purity_final_temp_kav$Source[grepl("hannity.com", purity_final_temp_kav$URL)] = "Sean Hannity"
-
-purity_icc_k <- lme(MFDweight ~ 1,
-                 data = purity_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-purity_model_kav = lme(MFDweight ~ lean,
-                 data = purity_final_temp_kav,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model_kav)
-
-# check linearity
-random <- rchisq(nrow(purity_final_temp_kav), 7)
-residuals <- scale(residuals(purity_model_kav))
-fitted <- scale(fitted(purity_model_kav))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_harm_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-harm_final_data_gs$weight = harm_final_data_gs$Freq * harm_final_data_gs$valence / harm_final_data_gs$wordcount * 100
-
-#flatten down to sum by article
-harm_final_temp_gs = aggregate(harm_final_data_gs$weight,
-          by = list(harm_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(harm_final_temp_gs) = c("URL", "MFDweight")
-
-harm_final_temp_gs$lean[grepl("nytimes.com", harm_final_temp_gs$URL) |
-                       grepl("npr.org", harm_final_temp_gs$URL) |
-                        grepl("slate.com", harm_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", harm_final_temp_gs$URL) |
-                        grepl("politico.com", harm_final_temp_gs$URL)] = "Liberal"
-
-harm_final_temp_gs$lean[grepl("breitbart.com", harm_final_temp_gs$URL) |
-                       grepl("foxnews.com", harm_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", harm_final_temp_gs$URL) |
-                       grepl("theblaze.com", harm_final_temp_gs$URL) |
-                       grepl("hannity.com", harm_final_temp_gs$URL)] = "Conservative"
-
-harm_final_temp_gs$Source[grepl("nytimes.com", harm_final_temp_gs$URL)] = "NY Times"
-harm_final_temp_gs$Source[grepl("npr.org", harm_final_temp_gs$URL)] = "NPR"
-harm_final_temp_gs$Source[grepl("slate.com", harm_final_temp_gs$URL)] = "Slate"
-harm_final_temp_gs$Source[grepl("huffingtonpost.com", harm_final_temp_gs$URL)] = "Huffington Post"
-harm_final_temp_gs$Source[grepl("politico.com", harm_final_temp_gs$URL)] = "Politico"
-harm_final_temp_gs$Source[grepl("foxnews.com", harm_final_temp_gs$URL)] = "Fox"
-harm_final_temp_gs$Source[grepl("breitbart.com", harm_final_temp_gs$URL)] = "Breitbart"
-harm_final_temp_gs$Source[grepl("rushlimbaugh.com", harm_final_temp_gs$URL)] = "Rush Limbaugh"
-harm_final_temp_gs$Source[grepl("theblaze.com", harm_final_temp_gs$URL)] = "The Blaze"
-harm_final_temp_gs$Source[grepl("hannity.com", harm_final_temp_gs$URL)] = "Sean Hannity"
-
-harm_icc_gs <- lme(MFDweight ~ 1,
-                 data = harm_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-harm_model_gs = lme(MFDweight ~ lean,
-                 data = harm_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(harm_model_gs)
-
-# check linearity
-random <- rchisq(nrow(harm_final_temp_gs), 7)
-residuals <- scale(residuals(harm_model_gs))
-fitted <- scale(fitted(harm_model_gs))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_fair_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-fair_final_data_gs$weight = fair_final_data_gs$Freq * fair_final_data_gs$valence / fair_final_data_gs$wordcount * 100
-
-#flatten down to sum by article
-fair_final_temp_gs = aggregate(fair_final_data_gs$weight,
-          by = list(fair_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(fair_final_temp_gs) = c("URL", "MFDweight")
-
-fair_final_temp_gs$lean[grepl("nytimes.com", fair_final_temp_gs$URL) |
-                       grepl("npr.org", fair_final_temp_gs$URL) |
-                        grepl("slate.com", fair_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", fair_final_temp_gs$URL) |
-                        grepl("politico.com", fair_final_temp_gs$URL)] = "Liberal"
-
-fair_final_temp_gs$lean[grepl("breitbart.com", fair_final_temp_gs$URL) |
-                       grepl("foxnews.com", fair_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", fair_final_temp_gs$URL) |
-                       grepl("theblaze.com", fair_final_temp_gs$URL) |
-                       grepl("hannity.com", fair_final_temp_gs$URL)] = "Conservative"
-
-fair_final_temp_gs$Source[grepl("nytimes.com", fair_final_temp_gs$URL)] = "NY Times"
-fair_final_temp_gs$Source[grepl("npr.org", fair_final_temp_gs$URL)] = "NPR"
-fair_final_temp_gs$Source[grepl("slate.com", fair_final_temp_gs$URL)] = "Slate"
-fair_final_temp_gs$Source[grepl("huffingtonpost.com", fair_final_temp_gs$URL)] = "Huffington Post"
-fair_final_temp_gs$Source[grepl("politico.com", fair_final_temp_gs$URL)] = "Politico"
-fair_final_temp_gs$Source[grepl("foxnews.com", fair_final_temp_gs$URL)] = "Fox"
-fair_final_temp_gs$Source[grepl("breitbart.com", fair_final_temp_gs$URL)] = "Breitbart"
-fair_final_temp_gs$Source[grepl("rushlimbaugh.com", fair_final_temp_gs$URL)] = "Rush Limbaugh"
-fair_final_temp_gs$Source[grepl("theblaze.com", fair_final_temp_gs$URL)] = "The Blaze"
-fair_final_temp_gs$Source[grepl("hannity.com", fair_final_temp_gs$URL)] = "Sean Hannity"
-
-fair_icc_gs <- lme(MFDweight ~ 1,
-                 data = fair_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-fair_model_gs = lme(MFDweight ~ lean,
-                 data = fair_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model_gs)
-
-# check linearity
-random <- rchisq(nrow(fair_final_temp_gs), 7)
-residuals <- scale(residuals(fair_model_gs))
-fitted <- scale(fitted(fair_model_gs))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_ingroup_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-ingroup_final_data_gs$weight = ingroup_final_data_gs$Freq * ingroup_final_data_gs$valence / ingroup_final_data_gs$wordcount * 100
-
-#flatten down to sum by article
-ingroup_final_temp_gs = aggregate(ingroup_final_data_gs$weight,
-          by = list(ingroup_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(ingroup_final_temp_gs) = c("URL", "MFDweight")
-
-ingroup_final_temp_gs$lean[grepl("nytimes.com", ingroup_final_temp_gs$URL) |
-                       grepl("npr.org", ingroup_final_temp_gs$URL) |
-                        grepl("slate.com", ingroup_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", ingroup_final_temp_gs$URL) |
-                        grepl("politico.com", ingroup_final_temp_gs$URL)] = "Liberal"
-
-ingroup_final_temp_gs$lean[grepl("breitbart.com", ingroup_final_temp_gs$URL) |
-                       grepl("foxnews.com", ingroup_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL) |
-                       grepl("theblaze.com", ingroup_final_temp_gs$URL) |
-                       grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Conservative"
-
-ingroup_final_temp_gs$Source[grepl("nytimes.com", ingroup_final_temp_gs$URL)] = "NY Times"
-ingroup_final_temp_gs$Source[grepl("npr.org", ingroup_final_temp_gs$URL)] = "NPR"
-ingroup_final_temp_gs$Source[grepl("slate.com", ingroup_final_temp_gs$URL)] = "Slate"
-ingroup_final_temp_gs$Source[grepl("huffingtonpost.com", ingroup_final_temp_gs$URL)] = "Huffington Post"
-ingroup_final_temp_gs$Source[grepl("politico.com", ingroup_final_temp_gs$URL)] = "Politico"
-ingroup_final_temp_gs$Source[grepl("foxnews.com", ingroup_final_temp_gs$URL)] = "Fox"
-ingroup_final_temp_gs$Source[grepl("breitbart.com", ingroup_final_temp_gs$URL)] = "Breitbart"
-ingroup_final_temp_gs$Source[grepl("rushlimbaugh.com", ingroup_final_temp_gs$URL)] = "Rush Limbaugh"
-ingroup_final_temp_gs$Source[grepl("theblaze.com", ingroup_final_temp_gs$URL)] = "The Blaze"
-ingroup_final_temp_gs$Source[grepl("hannity.com", ingroup_final_temp_gs$URL)] = "Sean Hannity"
-
-ingroup_icc_gs <- lme(MFDweight ~ 1,
-                 data = ingroup_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-ingroup_model_gs = lme(MFDweight ~ lean,
-                 data = ingroup_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model_gs)
-
-# check linearity
-random <- rchisq(nrow(ingroup_final_temp_gs), 7)
-residuals <- scale(residuals(ingroup_model_gs))
-fitted <- scale(fitted(ingroup_model_gs))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_authority_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-authority_final_data_gs$weight = authority_final_data_gs$Freq * authority_final_data_gs$valence / authority_final_data_gs$wordcount * 100
-
-#flatten down to sum by article
-authority_final_temp_gs = aggregate(authority_final_data_gs$weight,
-          by = list(authority_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(authority_final_temp_gs) = c("URL", "MFDweight")
-
-authority_final_temp_gs$lean[grepl("nytimes.com", authority_final_temp_gs$URL) |
-                       grepl("npr.org", authority_final_temp_gs$URL) |
-                        grepl("slate.com", authority_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", authority_final_temp_gs$URL) |
-                        grepl("politico.com", authority_final_temp_gs$URL)] = "Liberal"
-
-authority_final_temp_gs$lean[grepl("breitbart.com", authority_final_temp_gs$URL) |
-                       grepl("foxnews.com", authority_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", authority_final_temp_gs$URL) |
-                       grepl("theblaze.com", authority_final_temp_gs$URL) |
-                       grepl("hannity.com", authority_final_temp_gs$URL)] = "Conservative"
-
-authority_final_temp_gs$Source[grepl("nytimes.com", authority_final_temp_gs$URL)] = "NY Times"
-authority_final_temp_gs$Source[grepl("npr.org", authority_final_temp_gs$URL)] = "NPR"
-authority_final_temp_gs$Source[grepl("slate.com", authority_final_temp_gs$URL)] = "Slate"
-authority_final_temp_gs$Source[grepl("huffingtonpost.com", authority_final_temp_gs$URL)] = "Huffington Post"
-authority_final_temp_gs$Source[grepl("politico.com", authority_final_temp_gs$URL)] = "Politico"
-authority_final_temp_gs$Source[grepl("foxnews.com", authority_final_temp_gs$URL)] = "Fox"
-authority_final_temp_gs$Source[grepl("breitbart.com", authority_final_temp_gs$URL)] = "Breitbart"
-authority_final_temp_gs$Source[grepl("rushlimbaugh.com", authority_final_temp_gs$URL)] = "Rush Limbaugh"
-authority_final_temp_gs$Source[grepl("theblaze.com", authority_final_temp_gs$URL)] = "The Blaze"
-authority_final_temp_gs$Source[grepl("hannity.com", authority_final_temp_gs$URL)] = "Sean Hannity"
-
-authority_icc_gs <- lme(MFDweight ~ 1,
-                 data = authority_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-authority_model_gs = lme(MFDweight ~ lean,
-                 data = authority_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model_gs)
-
-# check linearity
-random <- rchisq(nrow(authority_final_temp_gs), 7)
-residuals <- scale(residuals(authority_model_gs))
-fitted <- scale(fitted(authority_model_gs))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-```{r analysis_purity_gs, include = FALSE}
-#final_data clean up
-#multiply by frequency and create percentage
-purity_final_data_gs$weight = purity_final_data_gs$Freq * purity_final_data_gs$valence / purity_final_data_gs$wordcount * 100
-
-#flatten down to sum by article
-purity_final_temp_gs = aggregate(purity_final_data_gs$weight,
-          by = list(purity_final_data_gs$URL),
-          FUN = sum, na.rm = T)
-colnames(purity_final_temp_gs) = c("URL", "MFDweight")
-
-purity_final_temp_gs$lean[grepl("nytimes.com", purity_final_temp_gs$URL) |
-                       grepl("npr.org", purity_final_temp_gs$URL) |
-                        grepl("slate.com", purity_final_temp_gs$URL) |
-                        grepl("huffingtonpost.com", purity_final_temp_gs$URL) |
-                        grepl("politico.com", purity_final_temp_gs$URL)] = "Liberal"
-
-purity_final_temp_gs$lean[grepl("breitbart.com", purity_final_temp_gs$URL) |
-                       grepl("foxnews.com", purity_final_temp_gs$URL) |
-                       grepl("rushlimbaugh.com", purity_final_temp_gs$URL) |
-                       grepl("theblaze.com", purity_final_temp_gs$URL) |
-                       grepl("hannity.com", purity_final_temp_gs$URL)] = "Conservative"
-
-purity_final_temp_gs$Source[grepl("nytimes.com", purity_final_temp_gs$URL)] = "NY Times"
-purity_final_temp_gs$Source[grepl("npr.org", purity_final_temp_gs$URL)] = "NPR"
-purity_final_temp_gs$Source[grepl("slate.com", purity_final_temp_gs$URL)] = "Slate"
-purity_final_temp_gs$Source[grepl("huffingtonpost.com", purity_final_temp_gs$URL)] = "Huffington Post"
-purity_final_temp_gs$Source[grepl("politico.com", purity_final_temp_gs$URL)] = "Politico"
-purity_final_temp_gs$Source[grepl("foxnews.com", purity_final_temp_gs$URL)] = "Fox"
-purity_final_temp_gs$Source[grepl("breitbart.com", purity_final_temp_gs$URL)] = "Breitbart"
-purity_final_temp_gs$Source[grepl("rushlimbaugh.com", purity_final_temp_gs$URL)] = "Rush Limbaugh"
-purity_final_temp_gs$Source[grepl("theblaze.com", purity_final_temp_gs$URL)] = "The Blaze"
-purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
-
-purity_icc_gs <- lme(MFDweight ~ 1,
-                 data = purity_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-
-purity_model_gs = lme(MFDweight ~ lean,
-                 data = purity_final_temp_gs,
-                 method = "ML",
-                 na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model_gs)
-
-# check linearity
-random <- rchisq(nrow(purity_final_temp_gs), 7)
-residuals <- scale(residuals(purity_model_gs))
-fitted <- scale(fitted(purity_model_gs))
-hist(residuals)
-{qqnorm(residuals); abline(0,1)}
-{plot(fitted, residuals); abline(h = 0); abline(v = 0)}
-```
-
-# Results
-
-## Descriptive Statistics
-
-We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Study 1, statistics calculated include *z*-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source [@Kincaid1975].
-
-Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
-The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, *Sean Hannity* appears to have published only 27 articles while *Breitbart* published 757 articles on this topic.
-Valence was found to be slightly positive across all sources.
-*Fox News* produced the most total words with the most tokens on average.
-This is likely due to the fact *Fox News* transcribes many of their videos and publishes them in article form.
-*Politico* featured the highest number of types on average.
-*Rush Limbaugh* featured the lowest readability score on average by grade level while *Slate* featured the highest grade-level readability score.
-The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language, as there is likely a lot of overlap between sources' use of language.
+# Study 3: Descriptive Statistics
+
+We calculated descriptive statistics for each news source per topic in
+order to reveal the presence (if any) of linguistic differences in the
+sources' use of language. As in Study 1, statistics calculated include
+*z*-scored valence, number of articles per source, total words per
+source, mean tokens per article in each source, mean types per article
+in each source, and mean readability level (using the Flesch-Kincaid
+Grade Level Readability formula) per source [@Kincaid1975].
+
+Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive
+statistics for sources' writing on the Kavanaughnaugh confirmation
+hearing. The sources were similar in most basic linguistic aspects,
+except for number of articles. For example, *Sean Hannity* appears to
+have published only 27 articles while *Breitbart* published 757 articles
+on this topic. Valence was found to be slightly positive across all
+sources. *Fox News* produced the most total words with the most tokens
+on average. This is likely due to the fact *Fox News* transcribes many
+of their videos and publishes them in article form. *Politico* featured
+the highest number of types on average. *Rush Limbaugh* featured the
+lowest readability score on average by grade level while *Slate*
+featured the highest grade-level readability score. The large standard
+deviations for these statistics, however, preclude conclusions regarding
+differences in the sources' use of language, as there is likely a lot of
+overlap between sources' use of language.
 
@@
 ####build the table here####
-tableprint3 = matrix(NA, nrow=10, ncol=11)
+tableprint3 = matrix(NA, nrow = 10, ncol = 11)
 colnames(tableprint3) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
@@
 ####build the table here####
-tableprint4 = matrix(NA, nrow=10, ncol=11)
+tableprint4 = matrix(NA, nrow = 10, ncol = 11)
 colnames(tableprint4) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
@@
 ```
-
-## Inferential Statistics
-
-We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Study 1.
-Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-Two separate MLMs were constructed from datasets compiled for each topic of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a statistically significant effect for *harm/care*, but the practical effect denoted by Cohen's *d* was found to be small.
-There were no other significant or practical effects of political lean for any of the other four moral foundations.
-The effect for *harm/care* was in the hypothesized direction with liberal sources tending to use more positively *harm/care* words than conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's *d*) can be found in Table \@ref(tab:exp2-tablekav).
-
-```{r exp2_kav_calc, include = F, echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint_kav = matrix(NA, ncol = 9, nrow = 5)
-colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
-
-#calculate d
-#harm
-harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d_kav = d.ind.t(m1 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 m2 = mean(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(fair_final_temp_kav$MFDweight[fair_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d_kav = d.ind.t(m1 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 m2 = mean(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp_kav$MFDweight[ingroup_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d_kav = d.ind.t(m1 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 m2 = mean(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(authority_final_temp_kav$MFDweight[authority_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d_kav = d.ind.t(m1 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 m2 = mean(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Conservative"]),
-                 n2 = length(purity_final_temp_kav$MFDweight[purity_final_temp_kav$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1,
-                    summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
-                    harm_d_kav$d, icc(harm_icc_k)$ICC_unadjusted)
-tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1,
-                    summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
-                    fair_d_kav$d, icc(fair_icc_k)$ICC_unadjusted)
-tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1,
-                    summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
-                    ingroup_d_kav$d, icc(ingroup_icc_k)$ICC_unadjusted)
-tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1,
-                    summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
-                    authority_d_kav$d, icc(authority_icc_k)$ICC_unadjusted)
-tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1,
-                    summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
-                    purity_d_kav$d, icc(purity_icc_k)$ICC_unadjusted)
-
-tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]), big.mark = "")
-tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
-tableprint_kav[ , 9] = printp(as.numeric(tableprint_kav[ , 9]))
-```
-
-```{r exp2-tablekav, results = 'asis', echo = F}
-apa_table(as.data.frame(tableprint_kav),
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Kavanaugh Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations (see Table \@ref(tab:exp2-tablegs)).
-A small-to-medium effect size was observed for *authority/respect*.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Study 1 in which the largest effect size was observed for *authority/respect*.
-As noted before, the effect found in Study 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Study 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Study 1.
-As in Study 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
-
-```{r exp2_gs_calc, include = F, echo = F}
-#MFD, mean, sd, mean, sd, t, p, d
-tableprint_gs = matrix(NA, ncol = 9, nrow = 5)
-colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
-
-#calculate d
-#harm
-harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#fair
-fair_d_gs = d.ind.t(m1 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 m2 = mean(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(fair_final_temp_gs$MFDweight[fair_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#ingroup
-ingroup_d_gs = d.ind.t(m1 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 m2 = mean(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(ingroup_final_temp_gs$MFDweight[ingroup_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#authority
-authority_d_gs = d.ind.t(m1 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 m2 = mean(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(authority_final_temp_gs$MFDweight[authority_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#purity
-purity_d_gs = d.ind.t(m1 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 m2 = mean(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 sd1 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
-                 sd2 = sd(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
-                 n1 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Conservative"]),
-                 n2 = length(purity_final_temp_gs$MFDweight[purity_final_temp_gs$lean == "Liberal"]),
-                 a = .05)
-
-#put in the numbers
-tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1,
-                    summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
-                    harm_d_gs$d, icc(harm_icc_gs)$ICC_unadjusted)
-tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1,
-                    summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
-                    fair_d_gs$d, icc(fair_icc_gs)$ICC_unadjusted)
-tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1,
-                    summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
-                    ingroup_d_gs$d, icc(ingroup_icc_gs)$ICC_unadjusted)
-tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1,
-                    summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
-                    authority_d_gs$d, icc(authority_icc_gs)$ICC_unadjusted)
-tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1,
-                    summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
-                    purity_d_gs$d, icc(purity_icc_gs)$ICC_unadjusted)
-
-tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]), big.mark = "")
-tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
-tableprint_gs[ , 9] = printp(as.numeric(tableprint_gs[ , 9]))
-```
-
-```{r exp2-tablegs, results = 'asis', echo = F}
-apa_table(as.data.frame(tableprint_gs),
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Government Shutdown Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 7)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-```{r conference-pic_kav, eval = F, include = F}
-library(ggplot2)
-library(reshape)
-
-cleanup = theme(panel.grid.major = element_blank(),
-                panel.grid.minor = element_blank(),
-                panel.background = element_blank(),
-                axis.line.x = element_line(color = "black"),
-                axis.line.y = element_line(color = "black"),
-                legend.key = element_rect(fill = "white"),
-                text = element_text(size = 10))
-
-graphdata_kav = as.data.frame(tableprint_kav)
-graphlong_kav = melt(graphdata_kav[ , c(1,2,4)],
-                 id = "Foundation")
-graphlong2_kav = melt(graphdata_kav[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong_kav$sd = graphlong2_kav$value
-graphlong_kav$lower = as.numeric(as.character(graphlong_kav$value)) - 2*as.numeric(as.character(graphlong_kav$sd))
-graphlong_kav$upper = as.numeric(as.character(graphlong_kav$value)) + 2*as.numeric(as.character(graphlong_kav$sd))
-
-graphlong_kav$value = as.numeric(as.character(graphlong_kav$value))
-
-graph_data_kav = ggplot(graphlong_kav, aes(Foundation, value, color = variable)) +
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper),
-                position = position_dodge(width = 0.90),
-                width = .2) +
-  cleanup +
-  ylab("Mean Weighted Valence") +
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-#tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4,
-#     height = 3, units = 'in', compression = "lzw")
-#plot(graph_data_kav)
-#dev.off()
-```
-
-```{r conference-pic_gs, eval = F, include = F}
-graphdata_gs = as.data.frame(tableprint_gs)
-graphlong_gs = melt(graphdata_gs[ , c(1,2,4)],
-                 id = "Foundation")
-graphlong2_gs = melt(graphdata_gs[ , c(1, 3,5)],
-                  id = "Foundation",
-                  measured = c("SD_C", "SD_L"))
-graphlong_gs$sd = graphlong2_gs$value
-graphlong_gs$lower = as.numeric(as.character(graphlong_gs$value)) - 2*as.numeric(as.character(graphlong_gs$sd))
-graphlong_gs$upper = as.numeric(as.character(graphlong_gs$value)) + 2*as.numeric(as.character(graphlong_gs$sd))
-
-graphlong_gs$value = as.numeric(as.character(graphlong_gs$value))
-
-graph_data_gs = ggplot(graphlong_gs, aes(Foundation, value, color = variable)) +
-  geom_point(position = position_dodge(width = 0.90)) +
-  geom_errorbar(aes(ymin = lower, ymax = upper),
-                position = position_dodge(width = 0.90),
-                width = .2) +
-  cleanup +
-  ylab("Mean Weighted Valence") +
-  scale_color_manual(values = c("red", "blue"),
-                       labels = c("Conservative", "Liberal"),
-                       name = "Party") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
-  geom_hline(yintercept = 0, linetype = 1, color = "black")
-
-#tiff(filename = "exp2_graph_gs.tiff", res = 300, width = 4,
-#     height = 3, units = 'in', compression = "lzw")
-#plot(graph_data_gs)
-#dev.off()
-```
-
-# Study 3
-
-Results from Study 1 and 2 indicated that no differences were found in the MFD for Liberal and Conservative sources using the traditional dictionary and valence weighting.
-The MFD was developed in conjunction with the Moral Foundations Questionnaire (MFQ), using the same five latent areas.
-In this set of studies, we examined the MFD and MFQ within the same study.
-The first two sub-studies were used to develop a (potentially) larger dictionary for the MFD and collect data on both scales.
-The last sub-study examined the MFD and MFQ using multi-trait multi-method analysis [CITE WIDAMEN AND BYRNE].
-
-DESCRIBE MTMM
-
-## Study 3.1
-
-In this study, participants were given a word association task elicit additional semantically related word forms for each moral foundation.
-This data was used to expand the MFD for each latent area to determine if these additional words could improve scores and test measurement relation to the MFQ in Study 3.3.
-
-### Participants
-
-```{r demos-mtmm-study-3.1, include = FALSE}
-exp1data <- import("exp3_data/study3.1_fixed_associations.csv")
-
-##clear out completely columns we don't need
-crapcolumns <- c(1, 2, 3, 5:14)
-finalsample <- exp1data[ , -crapcolumns]
-
-##accuracy
-summary(finalsample) #Check Q15_1 and Q23 for in-range scores -WP
-finalsample$Q23 <- factor(finalsample$Q23,
-                         levels = 1:3,
-                         labels = c("Democrat", "Republican", "Independent"))
-
-#missing 
-#by people 
-missing_demo1 <- apply(finalsample, 1, percentmiss) 
-table(missing_demo1)
-
-replacepeople1 <- subset(finalsample, missing_demo1 <= 5)  #we are using 5%, yes? 
-#by column 
-apply(replacepeople1, 2, percentmiss) 
-#missing data is on the politics scale which we don't want to replace
-
-finalsample <- replacepeople1
-summary(finalsample)
-
-party <- table(finalsample$Q23)
-##be sure to exclude the writing columns columns 2:6 
-#I take it I should also remove column 1: ResponseId? 
-##outliers
-mahal1 <- mahalanobis(finalsample[ , -c(1:6,22,23)], 
-                    colMeans(finalsample[ , -c(1:6,22,23)], na.rm = TRUE),
-                    cov(finalsample[ , -c(1:6,22,23)], use="pairwise.complete.obs"))
-#mahal1
-cutoff1 <- qchisq(1 - .001,ncol(finalsample[ , -c(1:6,22,23)]))
-cutoff1
-ncol(finalsample[ , -c(1:6,22,23)])
-summary(mahal1 < cutoff1) #Hmm what to do w/ NAs?? -WP
-noout1 <- subset(finalsample, mahal1 < cutoff1)
-
-##assumptions
-#correlations for MFQ
-correlations1 <- cor(noout1[,-c(1:6,22,23)], use="pairwise.complete.obs")
-correlations1
-symnum(correlations1)
-
-#making the random stuff
-random1 <- rchisq(nrow(noout1), 7)
-fake1 <- lm(random1~., data=noout1[ , -c(1:6)])
-#normal
-standardized1 <- rstudent(fake1)
-hist(standardized1, breaks=15)
-
-#linear
-{qqnorm(standardized1) 
-abline(0,1)}
-#homog + s
-fitvalues1 <- scale(fake1$fitted.values)
-{plot(fitvalues1, standardized1) 
-abline(0,0)
-abline(v = 0)}
-
-####create the MFQ subscales####
-noout1$harmMFQ <- apply(noout1[ , 7:9], 1, sum)
-noout1$fairMFQ <- apply(noout1[ , 10:12], 1, sum)
-noout1$ingroupMFQ <- apply(noout1[ , 13:15], 1, sum)
-noout1$authorityMFQ <- apply(noout1[ , 16:18], 1, sum)
-noout1$purityMFQ <- apply(noout1[ , 19:21], 1, sum)
-```
-
-`r nrow(exp1data)` participants were collected from a large Midwestern university.
-Participants were given course credit for their introductory psychology course for completing the study.
-`r nrow(finalsample)` participants had less than five percent missing data and were retained for analyses.
-Participants were asked to denote their political party, and `r printnum(party["Democrat"]/sum(party)*100,digits = 1)`% indicated they were Democrats, `r printnum(party["Republican"]/sum(party)*100,digits = 1)`% were Republican, and `r printnum(party["Independent"]/sum(party)*100,digits = 1)`% indicated they were Independent.
-
-### Materials and Procedure
-
-A complete example of the survey can be found online at https://osf.io/5uqfn.
-First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech.
-Next, the free association task, similar to that used in CITE @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind".
-The participants were then given three example free association cues, *lost*, *old*, and *article*.
-For each cue, participants were asked to write all the words that come to mind.
-To elicit free association to the moral foundation areas, participants were given the following instructions:
-
-"Moral Foundations Theory states that when making moral judgments/decisions, the concerns people have can be divided into five categories.
-Below are labels of each of these five categories.
-You will then be asked to list words you think are associated with each of the labels."
-
-Each of the foundation pairs were listed together (i.e., *harm/care*, *fairness/cheating*) with a space for participants to list their free association concepts.
-After the free association task, participants were then given the 15-items from the moral relevance section of the MFQ as described in the introduction.
-Last, participants were asked to denote their political orientation from 1 *conservative* to 10 *liberal*, as well as which political party they associated with: Democrat, Republican, and Independent.
-The survey was delivered through Qualtrics, and participants were recruited through the online participant management system for the university (SONA).
-Each participant signed an online consent form at the beginning of the study and was given participation credit at the end of the study.
-
-### Results
-
-All data was screening for inaccurate responses, as well as missing data, as described in the participant section.
-Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise.
-The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012 CITE, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r apa_num(cutoff1)`.
-These participants were excluded from further analyses, representing `r nrow(noout1)` final participants.
-The final MFQ data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.
-
-The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
-The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`).
-Participants free association responses were processed using the *tm* [CITE] and *corpus* [CITE] libraries after spell checking.
-Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*.
-We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary.
-Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manually recode all word forms.
-Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses.
-The complete set of word frequencies for each foundation can be found in our supplemental materials.
-
-```{r harm-analysis-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q27 <- as.character(noout1$Q27)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q27[i] <- paste(unlist(
-    text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-harm_corpus <- Corpus(VectorSource(noout1$Q27))
-harm_TDM <- as.matrix(TermDocumentMatrix(harm_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-harm_freq <- data.frame(Word = rownames(harm_TDM),
-                       Freq = rowSums(harm_TDM),
-                       row.names = NULL)
-harm_freq$Word <- as.character(harm_freq$Word)
-harm_freq$percent <- harm_freq$Freq/nrow(noout1) *100
-
-write.csv(harm_freq, "exp3_data/study3.1_harm_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-harm_words <- harm_freq$Word[harm_freq$percent >=1]
-##turn sideways to add to dataset
-harm_TDM  <- as.data.frame(t(harm_TDM))
-harm_TDM  <- harm_TDM[ , harm_words]
-
-##final dataset for harm
-harm_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
-                   harm_TDM)
-
-harm_cor <- apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})
-
-harmcut <- mean(harm_cor) + 2*sd(harm_cor)
-harm_words_reduce <- names(harm_cor[abs(harm_cor) >= harmcut])
-```
-
-```{r fair-analysi-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q29 = as.character(noout1$Q29)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q29[i] <- paste(unlist(
-    text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-fair_corpus <- Corpus(VectorSource(noout1$Q29))
-fair_TDM <- as.matrix(TermDocumentMatrix(fair_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-fair_freq <- data.frame(Word = rownames(fair_TDM),
-                       Freq = rowSums(fair_TDM),
-                       row.names = NULL)
-fair_freq$Word <- as.character(fair_freq$Word)
-fair_freq$percent <- fair_freq$Freq/nrow(noout1) *100
-
-write.csv(fair_freq, "exp3_data/study3.1_fair_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-fair_words <- fair_freq$Word[fair_freq$percent >=1]
-##turn sideways to add to dataset
-fair_TDM <- as.data.frame(t(fair_TDM))
-fair_TDM <- fair_TDM[ , fair_words]
-
-##final dataset for fair
-fair_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
-                   fair_TDM)
-
-fair_cor <- apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})
-
-faircut <- mean(fair_cor) + 2*sd(fair_cor)
-fair_words_reduce <- names(fair_cor[abs(fair_cor) >= faircut])
-```
-
-```{r ingroup-analysis-3.1, include=FALSE}
-#q27 through 34 are the writing columns
-noout1$Q30 <- as.character(noout1$Q30)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q30[i] <- paste(unlist(
-    text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-ingroup_corpus <- Corpus(VectorSource(noout1$Q30))
-ingroup_TDM <- as.matrix(TermDocumentMatrix(ingroup_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-ingroup_freq <- data.frame(Word = rownames(ingroup_TDM),
-                       Freq = rowSums(ingroup_TDM),
-                       row.names = NULL)
-ingroup_freq$Word <- as.character(ingroup_freq$Word)
-ingroup_freq$percent <- ingroup_freq$Freq/nrow(noout1) *100
-
-write.csv(ingroup_freq, "exp3_data/study3.1_ingroup_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >=1]
-##turn sideways to add to dataset
-ingroup_TDM <- as.data.frame(t(ingroup_TDM))
-ingroup_TDM <- ingroup_TDM[ , ingroup_words]
-
-##final dataset for ingroup
-ingroup_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
-                   ingroup_TDM)
-
-ingroup_cor <- apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})
-
-ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
-ingroup_words_reduce <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
-```
-
-```{r authority-analysis-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q32 <- as.character(noout1$Q32)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q32[i] <- paste(unlist(
-    text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-authority_corpus <- Corpus(VectorSource(noout1$Q32))
-authority_TDM <- as.matrix(TermDocumentMatrix(authority_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-authority_freq <- data.frame(Word = rownames(authority_TDM),
-                       Freq = rowSums(authority_TDM),
-                       row.names = NULL)
-authority_freq$Word <- as.character(authority_freq$Word)
-authority_freq$percent <- authority_freq$Freq/nrow(noout1) *100
-
-write.csv(authority_freq, "exp3_data/study3.1_authority_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-authority_words <- authority_freq$Word[authority_freq$percent >=1]
-##turn sideways to add to dataset
-authority_TDM <- as.data.frame(t(authority_TDM))
-authority_TDM <- authority_TDM[ , authority_words]
-
-##final dataset for authority
-authority_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
-                   authority_TDM)
-
-authority_cor <- apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})
-
-authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
-authority_words_reduce <- names(authority_cor[abs(authority_cor) >= authoritycut])
-```
-
-```{r purity-analysis-3.1, include = FALSE}
-#q27 through 34 are the writing columns
-noout1$Q34 <- as.character(noout1$Q34)
-
-##stem the data
-for (i in 1:nrow(noout1)) {
-  noout1$Q34[i] <- paste(unlist(
-    text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-purity_corpus <- Corpus(VectorSource(noout1$Q34))
-purity_TDM <- as.matrix(TermDocumentMatrix(purity_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-purity_freq <- data.frame(Word = rownames(purity_TDM),
-                       Freq = rowSums(purity_TDM),
-                       row.names = NULL)
-purity_freq$Word <- as.character(purity_freq$Word)
-purity_freq$percent <- purity_freq$Freq/nrow(noout1) *100
-
-write.csv(purity_freq, "exp3_data/study3.1_purity_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-purity_words <- purity_freq$Word[purity_freq$percent >=1]
-##turn sideways to add to dataset
-purity_TDM <- as.data.frame(t(purity_TDM))
-purity_TDM <- purity_TDM[ , purity_words]
-
-##final dataset for purity
-purity_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
-                   purity_TDM)
-
-purity_cor <- apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})
-
-puritycut <- mean(purity_cor) + 2*sd(purity_cor)
-purity_words_reduce <- names(purity_cor[abs(purity_cor) >= puritycut])
-```
-
-This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`.
-These concepts were included in the full dictionary used for Study 3.3.
-We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
-Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts.
-Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation.
-The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`, ingroup `r length(ingroup_words_reduce)`, authority `r length(authority_words_reduce)`, and purity `r length(purity_words_reduce)`.
-
-## Study 3.2
-
-this section is about the writing
-
-### Participants
-
-```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
-sample1 <- read.csv("exp3_data/study3.2_fixed_sample 1.csv", stringsAsFactors = F)
-sample2 <- read.csv("exp3_data/study3.2_fixed_sample 2.csv", stringsAsFactors = F)
-
-##merge files together
-fullsample <- merge(sample1, sample2, all = TRUE)
-
-##merge together the writing samples
-#q24, q25, q26, q7 
-fullsample$writing <- apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
-                           1, function(x) toString(na.omit(x)))
-
-##clear out completely columns we don't need
-crapcolumns <- c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
-finalsample <- fullsample[ , -crapcolumns]
-
-##accuracy
-summary(finalsample[ , 2:40])
-
-finalsample$Q10 <- factor(finalsample$Q10,
-                         levels = 1:2,
-                         labels = c("Man", "Woman"))
-finalsample$Q11 <- as.numeric(finalsample$Q11)
-finalsample$Q12 <- factor(finalsample$Q12,
-                         levels = 1:7,
-                         labels = c("White", "Black", 
-                                    "Hispanic", "Asian",
-                                    "Native American", 
-                                    "Mixed", "Other"))
-
-gender <- table(finalsample$Q10)/sum(table(finalsample$Q10))*100
-race <- table(finalsample$Q12)/sum(table(finalsample$Q12))*100
-
-write.csv(finalsample, 'exp3_data/study3.2_finalsample.csv', row.names = FALSE)
-newMFD <- import('exp3_data/study3.2_finalsample_newMFD.csv')
-colnames(newMFD)[1:41] <- colnames(finalsample)[1:41]
-newMFD <- newMFD[,c(1,42:55)]
-finalsample <- merge(finalsample, newMFD, by = "ResponseId")
-
-##take out the people with less than 25 words
-##use the ngram library to examine the data
-##preprocess only works on one string at a time, so going to use a loop go through all the rows (apply won't work because we only want to work on one column)
-
-for (i in 1:nrow(finalsample)) {
-
-  finalsample$writing[i] <- preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
-  finalsample$wordcount[i] <- string.summary(finalsample$writing[i])$words
-
-}
-
-#remove small words people
-finalwords <- subset(finalsample, wordcount >=25)
-
-##check out missing data
-#missing by row
-missing <- apply(finalwords, 1, percentmiss)
-table(missing)
-goodrows <- subset(finalwords, missing <= 5)
-
-#missing by column
-apply(goodrows, 2, percentmiss)
-
-##don't fill in Q10 to the end, be sure to merge these back together
-goodcolumns <- goodrows[ , -c(32:42)]
-badcolumns <- goodrows[ , c(32:42)]
-
-#fill in missing data points
-
-tempnomiss = mice(goodcolumns)
-nomiss = complete(tempnomiss, 1)
-summary(nomiss)
-#merge
-allcolumns = cbind(nomiss, badcolumns) 
-summary(allcolumns)
-
-##outliers
-mahal2 = mahalanobis(allcolumns[ , -c(1,46:56)], 
-                    colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
-                    cov(allcolumns[ , -c(1,46:56)], use="pairwise.complete.obs"))
-#mahal2
-cutoff2 = qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
-cutoff2
-ncol(allcolumns[ , -c(1,46:56)])
-summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
-noout2 = subset(allcolumns, mahal2 < cutoff2)
-
-##assumptions on the questions i.e., not Q10 to the end
-#correlations
-correlations2 = cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
-#correlations2
-symnum(correlations2)
-
-#the random stuff
-random2 = rchisq(nrow(noout2), 7)
-fake2 = lm(random2~., data=noout2[ , -c(1,46:56)])
-
-#normal
-standardized2 = rstudent(fake2)
-hist(standardized2, breaks=15)
-
-#linear
-{qqnorm(standardized2)   
-abline(0,1)}
-
-#homog + s
-fitvalues2 = scale(fake2$fitted.values)
-{plot(fitvalues2, standardized2) 
-abline(0,0)
-abline(v = 0)}
-
-####create the MFQ subscales####
-noout2$harmMFQ = apply(noout2[ , 2:4], 1, sum)
-noout2$fairMFQ = apply(noout2[ , 5:7], 1, sum)
-noout2$ingroupMFQ = apply(noout2[ , 8:10], 1, sum)
-noout2$authorityMFQ = apply(noout2[ , 11:13], 1, sum)
-noout2$purityMFQ = apply(noout2[ , 14:16], 1, sum)
-```
-
-Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes [@Jordan].
-Participants were recruited via an online research system (SONA) and were given course credit for their participation.
-`r nrow(finalsample)` participants were included in the this study.
-The study was mostly women (`r printnum(gender["Woman"], digits = 1)`%) and White (`r printnum(race["White"], digits = 1)`%) participants with a mix of minority participants: Black (`r printnum(race["Black"], digits = 1)`%), (`r printnum(race["Hispanic"], digits = 1)`%), (`r printnum(race["Asian"], digits = 1)`%), Native American (`r printnum(race["Native American"], digits = 1)`%), Mixed (`r printnum(race["Mixed"], digits = 1)`%) and Other (`r printnum(race["Other"], digits = 1)`%).
-The average listed age was `r printnum(mean(finalsample$Q11, na.rm = T))` (*SD* = `r printnum(sd(finalsample$Q11, na.rm = T))`).
-
-###	Materials and Procedure
-
-Data was again collected via Qualtrics.
-Four fake new stories were presented to participants, which were roughly 400 words each.
-First, all news stories included a few sentences describing the use of chemical weapons in the Syrian civil war.
-The news stories were manipulated with political (Republican v.
-Democrat) and religious (religious v.
-not) quotes in a 2 x 2 design.
-News stories can be found in the online materials.
-Participants also completed the 30-item version of the MFQ as described in the introduction.
-In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.
-
-After consenting to participate in the study, participants were randomly shown one of the four new articles about Syria's use of chemical weapons.
-Participants were then asked to write for 5-10 minutes about their reaction to Syria's use of chemical weapons and the needed response from the United States.
-The second wave of data collection included different writing prompts designed to capture more of the moral foundation areas in their writing.
-The following writing prompt was used, "Please write about your attitudes on abortion (or same-sex marriage or environmentalism) as well as your reason for this stance." The three prompts were chosen to create a more varied word set by using topics that should elicit words from each moral foundations category by soliciting a moral response.
-In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants.
-Participants then completed the MFQ, demographics, and the political orientation scale.
-
-### Results
-
-Participant data was first spell checked and screening for inaccurate responses.
-Participants who did not write more than fifty words in response to a given prompt were excluded (*n* = `r nrow(finalsample) - nrow(finalwords)`).
-One missing datapoint was estimated using the *mice* library from *R* [@CITE] for a missing MFQ question, and all other missing data was present in the demographics sections, which were not filled in.
-The MFQ data were screened for outliers using Mahalanobis distance, and fourteen outliers were found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) = `r printnum(cutoff2)`.
-These data were excluded leading to a final sample size of `r nrow(noout2)`.
-Data were screened for assumptions described in Experiment 1 and were found to be satisfactory.
-
-```{r writing-analysis-3.2, include=FALSE}
-##stem the data
-for (i in 1:nrow(noout2)) {
-  noout2$writing2[i] = paste(unlist(
-    text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
-}
-
-##create a corpus
-overall_corpus = Corpus(VectorSource(noout2$writing2))
-overall_TDM = as.matrix(TermDocumentMatrix(overall_corpus,
-                              control = list(removePunctuation = TRUE,
-                                             stopwords = TRUE)))
-
-##view the most frequent words
-overall_freq = data.frame(Word = rownames(overall_TDM),
-                          Freq = rowSums(overall_TDM),
-                          row.names = NULL)
-overall_freq$Word = as.character(overall_freq$Word)
-overall_freq$percent = overall_freq$Freq/nrow(noout2)*100
-
-write.csv(overall_freq, "exp2_freq.csv", row.names = F)
-
-##subset out to only words with 1% mentions
-##this goes over 100% but mostly want to subset out things that were only mentioned
-##a few times by participants
-all_words = overall_freq$Word[overall_freq$percent >=1]
-
-##turn sideways to add to dataset
-overall_TDM = as.data.frame(t(overall_TDM))
-overall_TDM = overall_TDM[ , all_words]
-
-##final dataset
-overall_final = cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
-                                  "authorityMFQ", "purityMFQ","ingroupMFQ")],
-                   overall_TDM)
-```
-
-```{r mfq-cor-3.2, include = FALSE}
-##harm
-harm_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$harmMFQ)})
-
-harmcut = mean(harm_cor) + 2*sd(harm_cor)
-harm_words_reduce_exp2 = names(harm_cor[abs(harm_cor) >= harmcut])
-
-##fair
-fair_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$fairMFQ)})
-
-faircut = mean(fair_cor) + 2*sd(fair_cor)
-fair_words_reduce_exp2 = names(fair_cor[abs(fair_cor) >= faircut])
-
-##purity
-purity_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$purityMFQ)})
-
-puritycut = mean(purity_cor) + 2*sd(purity_cor)
-purity_words_reduce_exp2 = names(purity_cor[abs(purity_cor) >= puritycut])
-
-##authority
-authority_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$authorityMFQ)})
-
-authoritycut = mean(authority_cor) + 2*sd(authority_cor)
-authority_words_reduce_exp2 = names(authority_cor[abs(authority_cor) >= authoritycut])
-
-##ingroup
-ingroup_cor = apply(overall_final[ , 7:ncol(overall_final)], 2, function (x) { cor(x, overall_final$ingroupMFQ)})
-
-ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
-ingroup_words_reduce_exp2 = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
-
-##print out words list to look at for further analysis
-#write.csv(harm_words_reduce_exp2, "words/harm_exp2.csv", row.names = F)
-#write.csv(fair_words_reduce_exp2, "words/fair_exp2.csv", row.names = F)
-#write.csv(authority_words_reduce_exp2, "words/authority_exp2.csv", row.names = F)
-#write.csv(purity_words_reduce_exp2, "words/purity_exp2.csv", row.names = F)
-#write.csv(ingroup_words_reduce_exp2, "words/ingroup_exp2.csv", row.names = F)
-```
-
-In the first study, only free association responses were collected, but in this study, full writing samples were collected.
-Therefore, we expected many of the words listed to be part of creating a cohesive discourse, rather than only related to the moral foundation targeted.
-To find only the most related words, the correlation between word frequency and moral foundation was calculated and words with correlations greater than two standard deviations outside the mean were selected for the dictionary analysis in Experiment 3.
-The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation.
-The average scores were: harm (*M* = `r printnum(mean(noout2$harmMFQ))`, *SD* = `r printnum(sd(noout2$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout2$fairMFQ))`, *SD* = `r printnum(sd(noout2$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout2$ingroupMFQ))`, *SD* = `r printnum(sd(noout2$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout2$authorityMFQ))`, *SD* = `r printnum(sd(noout2$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout2$purityMFQ))`, *SD* = `r printnum(sd(noout2$purityMFQ))`).
-
-```{r compare-ratings-3.2, include = FALSE}
-authority_erin = read.csv("words/authority_exp2 erin.csv", stringsAsFactors = F)
-authority_will = read.csv("words/authority_exp2 will.csv", stringsAsFactors = F)
-authority_erin$x[authority_erin$use != authority_will$use]
-
-authority_words_reduce_exp2 = authority_words_reduce_exp2[authority_words_reduce_exp2 %in% authority_will$x[authority_will$use == 1]]
-
-fair_erin = read.csv("words/fair_exp2 erin.csv", stringsAsFactors = F)
-fair_will = read.csv("words/fair_exp2 will.csv", stringsAsFactors = F)
-fair_erin$x[fair_erin$use != fair_will$use]
-fair_will$use[fair_will$x == "carbon"] = 0
-fair_will$use[fair_will$x == "emiss"] = 0
-#exclude carbon and emiss due to the prompt
-
-fair_words_reduce_exp2 = fair_words_reduce_exp2[fair_words_reduce_exp2 %in% fair_will$x[fair_will$use == 1]]
-
-purity_erin = read.csv("words/purity_exp2 erin.csv", stringsAsFactors = F)
-purity_will = read.csv("words/purity_exp2 will.csv", stringsAsFactors = F)
-purity_erin$x[purity_erin$use != purity_will$use]
-purity_will$use[purity_will$x == "befor"] = 1
-#before include because of "before sex/ruined/etc."
-
-purity_words_reduce_exp2 = purity_words_reduce_exp2[purity_words_reduce_exp2 %in% purity_will$x[purity_will$use == 1]]
-
-ingroup_erin = read.csv("words/ingroup_exp2 erin.csv", stringsAsFactors = F)
-ingroup_will = read.csv("words/ingroup_exp2 will.csv", stringsAsFactors = F)
-ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
-ingroup_will$use[ingroup_will$x == "mean"] = 1
-#mean should be included
-
-ingroup_words_reduce_exp2 = ingroup_words_reduce_exp2[ingroup_words_reduce_exp2 %in% ingroup_will$x[ingroup_will$use == 1]]
-
-harm_erin = read.csv("words/harm_exp2 erin.csv", stringsAsFactors = F)
-harm_will = read.csv("words/harm_exp2 will.csv", stringsAsFactors = F)
-harm_erin$x[harm_erin$use != harm_will$use]
-harm_will$use[harm_will$x == "import"] = 1
-#import for important
-
-harm_words_reduce_exp2 = harm_words_reduce_exp2[harm_words_reduce_exp2 %in% harm_will$x[harm_will$use == 1]]
-```
-
-This set of words was then coded by two of the authors for relevant words with discussion over coding constituting a tiebreaker.
-For example, for harm words in this study both *also* and *Syria* appeared as correlated words to the harm foundation.
-The first word does not meet face validity of correlation with the dictionary, and these type of function words or ambiguous verbs (i.e., *get*, *can*) were usually excluded.
-The second example is likely because of the writing prompt, and therefore, proper nouns were also excluded.
-The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce_exp2)`, fairness `r length(fair_words_reduce_exp2)`, ingroup `r length(ingroup_words_reduce_exp2)`, authority `r length(authority_words_reduce_exp2)`, and purity `r length(purity_words_reduce_exp2)`.
-
-## Study 3.3
-
-This part is the mtmm
-
-```{r mtmm-setup, include = FALSE}
-##original mfd words
-original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)
-
-##adding forms/conjugations of words to original_mfd
-#harm/care
-original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
-                             "sympathetic","sympathies","damaged",
-                             "damaging","attacked","attacking","attacker",
-                             "attacks","attackers", "benefits", "benefitted",
-                             "benefitting", "cares", "cared", "caring", "crushes",
-                             "crushing", "crushed", "dangerous", "defends", "defending",
-                             "defended", "detroys", "destroyed", "destroying",
-                             "fights", "fought", "fighting", "guards", "guarded",
-                             "guarding", "harms", "harmed", "harming", "hurts",
-                             "hurting", "kills", "killed", "killing", "preserves",
-                             "preserved", "preserving", "protects", "protected",
-                             "protecting", "protection", "ruins", "ruined", "ruining",
-                             "safely", "safer", "shelters", "sheltered", "sheltering",
-                             "spurns", "spurned", "spurning", "stomps", "stomped",
-                             "stomping", "suffers", "suffered", "suffering",
-                             "violence", "warring")
-
-#fairness/reciprocity
-original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
-                             "biases", "discriminates", "discriminated",
-                             "discriminating", "discrimination", "equals",
-                             "equaled", "equaling", "equates", "equated",
-                             "equating", "evens", "evened", "evening",
-                             "excludes", "excluded", "excluding", "fairness",
-                             "favors", "favored", "favoring", "honesty",
-                             "impariality", "justice", "justifies", "justified",
-                             "justifying", "prefers", "preferred", "preferring",
-                             "prejudices", "prejudiced", "prejudicing", "reasons",
-                             "reasoned", "reasoning", "rights", "tolerates",
-                             "tolerated", "tolerating", "toleration")
-
-#ingroup/loyalty
-original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
-                             "communities", "deceives", "deceived", "deceiving",
-                             "deception", "deceptions", "deserts", "deserted",
-                             "deserting", "desertion", "families", "fellows",
-                             "foreigners", "groups", "grouped", "grouping",
-                             "indviduals", "indvidualize", "individualized",
-                             "individualizing", "members", "nations", "sides",
-                             "togetherness", "traits", "unites", "united", "uniting")
-
-#authority/respect
-original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
-                              "classes", "classed", "classing", "command",
-                              "commanded", "commanding", "controls", "controlled",
-                              "controlling", "defects", "defected", "defecting",
-                              "defers", "deferred", "deferring", "deference",
-                              "defies", "defied", "defying", "defiance", "deserts",
-                              "deserted", "deserting", "desertion", "duties",
-                              "faiths", "fathers", "fathered", "fathering",
-                              "honors", "honored", "honoring", "laws", "leads",
-                              "leading", "mothers", "mothered", "mothering",
-                              "obeys", "obeyed", "obeying", "opposes", "opposed",
-                              "opposing", "orders", "ordered", "ordering", "permits",
-                              "permitted", "permitting", "positions", "positioned",
-                              "positioning", "preserves", "preserved", "preserving",
-                              "preservation", "protests", "protested", "protesting",
-                              "refuses", "refused", "refusing", "refusal", "respects",
-                              "respected", "respecting", "respectful", "reveres",
-                              "revered", "revering", "reverence", "serves", "served",
-                              "serving", "traditions", "traditional", "traits")
-
-#purity/sanctity
-original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
-                             "adulteries", "adulterous", "adulterer", "adulterers",
-                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
-                             "cleanliness", "dirty", "diseases", "diseased", 
-                             "disgusts", "disgusted", "disgusting", "grossness",
-                             "innocence", "modesty", "preserves", "preserved",
-                             "preserving", "preservation", "promiscuity",
-                             "promiscuities", "purity", "rights", "ruins", "ruined",
-                             "ruining", "sacredness", "sickness", "sicknesses",
-                             "sins", "wholeness", "wholesome")
-
-##stem the original mfd
-for(i in 1:nrow(original_mfd)) {
-  original_mfd$h2[i] = stemDocument(original_mfd$h2[i], language = "english")
-  original_mfd$f2[i] = stemDocument(original_mfd$f2[i], language = "english")
-  original_mfd$i2[i] = stemDocument(original_mfd$i2[i], language = "english")
-  original_mfd$a2[i] = stemDocument(original_mfd$a2[i], language = "english")
-  original_mfd$p2[i] = stemDocument(original_mfd$p2[i], language = "english")
-}
-
-mtmmdata = noout2[ , c(1:31, 42) ]
-
-####figure out the percents for the exp2 data
-for (i in 1:nrow(mtmmdata)) {
-
-  ##figure out the sum for just the original mfd
-  mtmmdata$harm_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"])])
-
-  mtmmdata$purity_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"])])
-
-  mtmmdata$fair_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"])])
-
-  mtmmdata$authority_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"])])
-
-  mtmmdata$ingroup_orig[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"])])
-
-  ##figure out the sum for all words ever 
-  mtmmdata$harm_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words, harm_words_reduce_exp2))])
-
-  mtmmdata$purity_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words, purity_words_reduce_exp2))])
-
-  mtmmdata$fair_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words, fair_words_reduce_exp2))])
-
-  mtmmdata$authority_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words, authority_words_reduce_exp2))])
-
-  mtmmdata$ingroup_all[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words, ingroup_words_reduce_exp2))])
-
-  ##figure out the sum for reduced words
-  mtmmdata$harm_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$h2[original_mfd$h2 != "" & original_mfd$h2 != "NA"], harm_words_reduce, harm_words_reduce_exp2))])
-
-  mtmmdata$purity_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$p2[original_mfd$p2 != "" & original_mfd$p2 != "NA"], purity_words_reduce, purity_words_reduce_exp2))])
-
-  mtmmdata$fair_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$f2[original_mfd$f2 != "" & original_mfd$f2 != "NA"], fair_words_reduce, fair_words_reduce_exp2))])
-
-  mtmmdata$authority_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$a2[original_mfd$a2 != "" & original_mfd$a2 != "NA"], authority_words_reduce, authority_words_reduce_exp2))])
-
-  mtmmdata$ingroup_reduce[i] = sum(overall_final[ i , colnames(overall_final) %in% unique(c(original_mfd$i2[original_mfd$i2 != "" & original_mfd$i2 != "NA"], ingroup_words_reduce, ingroup_words_reduce_exp2))])
-
-}
-
-#create percents instead of frequencies
-mtmmdata[ , c(33:47)] = mtmmdata[ , c(33:47)] / mtmmdata$wordcount * 100
-
-summary(mtmmdata[ , 33:47])
-
-```
-
-```{r mtmm_orig, include = FALSE}
-###Run chunk 8: demos_study2 to update data
-###Use noout2 df as dataframe for mtmm
-###Columns labeled Harm1/Fairness1/Loyalty1/Authority1/Purity1 are original MFD
-###Columns labeled Harm2/Fairness2/Loyalty2/Authority2/Purity2 are revised MFD
-
-##now run some MTMM!
-library(semPlot)
-library(lavaan)
-
-####mtmm original dictionary####
-
-{model1 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model1.2 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-fair_orig ~~ 1167.145*fair_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.2.fit = cfa(model1.2, data=mtmmdata, std.lv=TRUE)
-summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.2.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.2.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-```{r mtmm_reduce, include = FALSE}
-
-{model1 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-```{r mtmm_all, include = FALSE}
-
-{model1 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-  Data Cleaning and Descriptives.
-In sample 1, participants who wrote less than 50 words were deleted (*n* = 69) leaving *n* = 221 participants.
-The average political orientation was 4.80 (*SD* = 2.21) on a scale of 1 (*conservative*) to 10 (*liberal*).
-In sample 2, all 160 participants wrote at least 50 words.
-The mean political orientation was 5.01 (*SD* = 2.33) for sample 2.
-The data from sample 1 and sample 2 were combined.
-Before any analyses were conducted, participants who did not use any words from the MFD were deleted; 16 participants were deleted from sample 1 and 25 from sample 2.
-The final sample size for analysis was *N* = 340 which had a mean political orientation of 4.90 (*SD* = 2.28).
-MFD scores were computed using NVivo *(CITE)* as both frequency for each foundation and percent coverage for each foundation.
-Frequency was simply the count of the number of words used from a given foundation dictionary; for example, a participant using the word *war* once and the word *peace* twice would have a frequency score of 3 for the *harm* dictionary.
-Percent coverage was calculated by taking the frequency and dividing by the word count; for example, given a frequency score of 3 for the *harm* dictionary and a word count of 100, then the percent coverage would be .03 for the *harm* dictionary.
-MFQ scores for each foundation were calculated by averaging the six items pertaining to each foundation.
-	Reliability.
-Here we should talk about the reliability of the MFQ for each piece, as well as the reliability of the words for the MFD.
-I think to do that you might need a thing that has each word as frequency count yes/no or however the LIWC version thing was done.
-	MTMM. BASIC SEM STUFF HERE (also that you used bayes)
-Data screening was conducted using SPSS version 22 and AMOS version 22.
-Participants who were missing data for the MFD, MFQ, or political orientation were deleted from all analyses.
-Given the distribution of the dictionary variables, participants whose writing sample were less than 2% words from the MFD were deleted resulting in a sample size of 252.
-Additionally, 7 outliers were deleted.
-Widaman's (1985; as cited in @Byrne2009) four-step nested method was used to test the convergent and divergent validity of the MFD and MFQ.
-The first step is the baseline model (Model 1), which establishes correlation among traits (*harm*, *purity*, *fairness*, *authority*, and *ingroup*) as well as correlation among methods (MFD and MFQ) but no cross correlation of traits and methods.
-The individual questions from the 30 item version of the MFQ and the total frequency of concepts from each foundation in the MFD were used as measured variables.
-The fit of this first model indicated some misfit, as fit indices were a mix of poor and acceptable, $\chi$ 2 (514) = 977.46, $\chi$ 2/df = 1.90, CFI = .842, RMSEA = .061 [95% CI = .055-.067], SRMR = .0623.
-In this model, the MFD *harm*, *fairness*, and *ingroup* items significantly loaded onto their trait factors, while *authority* and *purity* did not.
-All foundations but *authority* loaded significantly on the method traits.
-All but two of the *ingroup* questions and one *authority* question loaded onto the MFQ trait factors.
-Several questions of the MFQ did not load significantly onto the methods factors; however, this result was taken as an indicator that traits variance was higher than methods variance.
-Generally, trait loadings were higher than method loadings for both the MFD and MFQ for *harm* and *fairness* traits.
-However, the *purity*, *ingroup*, and *authority* foundations did not show this loading pattern.
-ERIN STOPPED HERE CUZ HEADACHE. 
-The second step (Model 2) involved eliminating the latent traits from the model.
-This model was significantly worse than Model 1 indicating the traits are important to the model ($\delta$ $\chi$ 2 = 1141.09, $\delta$ df = 45, $\delta$ CFI = .351).
-This supports convergent validity for the traits measured by both methods which in this case are the five moral foundations.
-The third step (Model 3) involved forcing the five traits to be perfectly correlated.
-This model was significantly worse than Model 1 indicating the usefulness of five unique traits ($\delta$ $\chi$ 2 = 311.09, $\delta$ df = 10, $\delta$ CFI = .097).
-This supports discriminant validity for the existence of five unique moral foundations.
-The final step (Model 4) involved allowing the correlations between the traits to be freely estimated and forcing the methods to be uncorrelated.
-This model was similar to Model 1 indicating the methods both measure the traits but they are both unique methods ($\delta$ $\chi$ 2 = 2.23, $\delta$ df = 1, $\delta$ CFI = .001).
-This supports discriminant validity for the methods.
-This set of analyses suggests the MFD is a possibly valid measure of moral foundations but does not measure them well enough to be useful in all applications and may be measuring them differently than the MFQ.
-	Regression predicting Political Orientation.
-The MFQ has predicted political orientation across many studies [@Federico2013; @Graham2009; @Haidt2009; @Weber2013].
-Therefore, in addition to the MTMM analysis, we compared how well the MFD score predicted political orientation compared to how well the MFQ predicted the political orientation.
-First, total MFQ scores were calculated for each foundation by averaging all six items.
-Then, a regression analysis was conducted with the five MFQ foundation score predicting political orientation.
-The overall model was significant, *R2* = .35, *F* (5, 255) = 26.91, *p* < .05.
-Higher scores on the harm and fairness foundations predicted a more liberal political orientation with harm accounting for 3% of the variance and fairness accounting for 6%.
-Higher scores on ingroup, authority, and purity predicted a more conservative orientation accounting for 1%, 2%, and 8% on the variance respectively.
-See *table ?* for regression coefficients.
-Next, a regression analysis was conducted to determine how well the five MFD scores predicted political orientation.
-The overall model was not significant, *R2* = .16, *F* (5, 255) = 1.36, *p* = .241.
-Higher harm scores somewhat predicted more liberal orientation accounting for 1% of the variance in political orientation.
-Higher purity scores somewhat predicted more conservative orientation accounting for 1% of the variance.
-See *table ?* for regression coefficients.
-
-# Participants
-
-Participants were recruited in two waves as part of a larger investigation on priming political and religious attitudes (???).
-Participants were recruited via an online research system (SONA) and were given course credit for their participation.
-463 participants were
-included in the this study.
-The study was mostly women (53.9%) and White (76.4%) participants with a mix of minority participants: Black (6.1%), (3.6%), (4.2%), Native American (1.9%), Mixed (2.9%) and Other (4.9%).
-The average listed age was 19.75 (SD =
-200 2.94).
-
-# Materials and Procedure
-
-Data was again collected via Qualtrics. Four fake new stories were presented to participants, which were roughly 400 words each. First, all news stories included a few
-sentences describing the use of chemical weapons in the Syrian civil war.
-The news stories were manipulated with political (Republican v.
-Democrat) and religious (religious v.
-not) quotes in a 2 x 2 design.
-News stories can be found in the online materials.
-Participants also completed the 30-item version of the MFQ as described in the introduction.
-In addition to basic demographics (gender, age), participant political orientation was assessed with the same scale described in Experiment 1.
-
-After consenting to participate in the study, participants were randomly shown one of
-the four new articles about Syria’s use of chemical weapons. Participants were then asked to
-write for 5-10 minutes about their reaction to Syria’s use of chemical weapons and the
-needed response from the United States. The second wave of data collection included
-different writing prompts designed to capture more of the moral foundation areas in their writing. The following writing prompt was used, “Please write about your attitudes on
-abortion (or same-sex marriage or environmentalism) as well as your reason for this stance.”
-The three prompts were chosen to create a more varied word set by using topics that should
-elicit words from each moral foundations category by soliciting a moral response.
-In each wave of data collection (Syria prompts, moral prompts) the prompt material was randomized between participants.
-Participants then completed the MFQ, demographics, and the political
-orientation scale.
-
-# Results
-
-# Expanding the MFD
-
-In a separate study of 466 university students, participants completed a free association task where we asked them to list all the words that came to mind from *harm/care*, *fairness/cheating*, *loyalty/XX*, *authority/XX*, *purity/XX*.
-They also completed the 15 item MFQ.
-Responses to the free association task were cleaned and stemmed.
-This lead to a new set of moral foundation words: harm-96, fairness-76, ingroup-86, authority-81, and purity-80.
-These concepts were included in the full dictionary used for Experiment 3.
-
-We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores.
-Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts.
-Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation.
-The reduced dataset included the following number of words for each foundation: harm 4, fairness 3, ingroup 3, authority 4, and purity 2.
-
-```{r word-association}
-#need the code for the the above stuff
-```
-
-[ERIN, Please do mathy-math here]
-
-# Testing Model Structure
-
-Before testing the theorized differences between liberals and conservatives, we sought to test the validity of the MFD using Multi-Trait, Multi-Method modelling (MTMM) to determine if the MFD is measuring the same latent variables as the MFQ as it should.
-
-```{r mtmm}
-
-```
-
-# Testing Group Differences
-
-```{r mtmm-groupdiffs}
-
-```
-
-# Discussion
-
-The results obtained in Study 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
-The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given @Graham2009.
-Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the practical effects much smaller than reported in @Graham2009.
-While not significant, fairness was endorsed more by conservatives in both cases.
-In contrast, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
-
-Together with Study 1 and past work, Study 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
-One issue that Study 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in @Sterling2018.
-For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
-The original predictions made by the Moral Foundations are very simplistic and likely much more complex in reality.
-
-# Conclusions
-
-Within the theoretical framework of MFT [@Haidt2007], we attempted to devise a method leveraging the MFD [@Graham2009] in order to quantify political bias stemming from content published by several prominent American news sources.
-In Study 1,the results obtained were not significant in any statistical or practical sense.
-There was a small effect found for the *authority/respect* foundation according to Cohen's *d*, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-In Study 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
-Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive, we still retain confidence in the overall structure of the methodology established in the current study.
-Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-We implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
-
-However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
-As mentioned before, MFD is a measure developed from MFT [@Graham2009].
-Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
-Going beyond specific instruments, other theoretical perspectives may be more equipped to explain political differences in discourse.
-Likewise, an atheoretical approach in which large quantities of data are collected from which theories are formulated may be best suited to this area of research.
-
-In critiquing MFT, @Schein2015 proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
-Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else [@Gray2014, @Schein2015].
-Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
-For example, in the case of abortion, liberals tend to identify the primary harm to the mother leading to a pro-choice position whereas conservative tend to identify the primary harm to the fetus leading to a pro-life position.
-While as of yet, no linguistic measurement of dyadic morality exists; such an approach may be able to better identify the systematic differences between liberals and conservatives.
-
-Turning to atheoretical approaches, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
-Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
-The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
-Likewise, there are several approaches to analyzing such data, including linear models (like multilevel models) and network-style models such as latent semantic analysis [@Landauer1998].
-Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
-
-Never before has political discourse represented such fertile ground for psychological research.
-The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
-Along with this recent increase in the amount of text information, there is now an obligation on the part of researchers to devise proper methods for analyzing that text.
-Solid methodologies must be constructed and periodically improved to keep pace with evolving technologies.
-Likewise, a strong theoretical foundation is paramount to making sense of the current and future media ecosystem.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
-
-\newpage
-
-# References
-
-\begingroup
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2024-11-30 manuscript_version/revision/manuscript_metapsych_revision.Rmd
rearranging folders and updating the manuscript

@@
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Study 1, we gathered political articles from four sources.
+In Study 2, we gathered political articles from four sources.
 We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
-In Study 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Study 3, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
@@
 
-bibliography      : ["./metapsych_bib.bib"] # add new references
+# bibliography      : ["./metapsych_bib.bib"] # add new references
 
@@
 output            : papaja::apa6_pdf
-bibliography: references.bib # delete this 
+bibliography: references.bib 
+appendix          :
+  - "appendix.Rmd"
 ---
@@
 library(lavaan)
+library(broom)
+library(tidyr)
 
@@
 generalizability. Convergent validity was supported with correlations on
-other measures of morality [@Schwartz; @Graham2011].
+other measures of morality [@Graham2011].
 
@@
 
-In contrast to this approach, @Sagi2013 explored how moral words were
+In contrast to this approach, @Sagi2014 explored how moral words were
 used paired with other co-occurring concepts using Latent Semantic
@@
 
-# Method
-
 We approached this study with the intention to answer a method question.
@@
 
-MTMM analyses use latent variable modeling to represent the underlying
-structure of a proposed phenomenon, while also accounting for the
-measurement of that phenomenon. As shown in Figure \@ref(fig:fig-mtmm),
-MTMM models are programmed to represent the traits that are measured
-(left hand side circles) and the methods used to measure those traits
-(right hand side circles). The squares in the middle represent the
-actual observed data, which is the MFQ questions and MFD scores. In the
-first model, *correlated traits correlated methods*, the latent
-variables are allowed to correlate on the traits and methods side, but
-not cross correlate from traits to methods. All models are then compared
-to this model to examine fit, convergent, and divergent validity. In the
-second model, *no traits correlated methods*, the trait side of the
-model is deleted and only methods are considered. The model should
-significantly degrade in fit, as the traits should be useful in
-explaining model variance for convergent validity (i.e., you do not want
-a model that suggests all the variances is due to measurement).
-
-In the third model, *perfectly correlated traits freely correlated
-methods*, the traits are added back to the model, but each correlation
-is set to one. The fit is compared to model 1, indicating if divergent
-validity of the traits has occurred. A significant degrade in fit should
-be found to indicate that trait correlations are not perfect. Last,
-model four *correlated traits uncorrelated methods*, the traits are
-allowed to naturally correlate but the methods correlations are set to
-zero. In comparison with model 1, the model should be roughly equal for
-divergent validity. This result would indicate that the methods each
-represent a different component to the measurement of the model, and do
-not represent the same measurement twice.
-
-Given the goal of improved measurement, we compared model 1 of the MTMM
-steps across several dictionaries to determine the best measurement for
-the dictionary. To assess model fit, we used the Root Mean Squared Error
-of Approximation [RMSEA, @steiger1990], the Root Mean Squared Residual
-[RMSR, @jöreskog1971], the Confirmatory Fit Index [CFI, @bentler1990],
-the Tucker-Lewis Index [TLI, @bentler1980]. The RMSEA and RMSR should be
-low for adequate model fit (\< .10) and the CFI and TLI should be high
-for adequate model fit (\> .90). For model comparison, we used a
-$\Delta$ CFI of greater than .01 to indicate a significant degradation
-in fit [@hu1999]. We will additionally use the standardized loadings for
-each of the traits to determine which model has the best measurement of
-moral foundations (\> .30 desired).
-
-For clarity, we programmed the following models:
-
-1.  Model 1 *Correlated Traits Correlated Methods*
-    a.  Original MFD Words
-    b.  Original MFD Words + Study 1.1 + Study 1.2 Words
-    c.  Original MFD Words + Study 1.1 Reduced + Study 1.2 Words
-    d.  Determine if model suggests a feasible structure (fit indices
-        adequate + loadings adequate)
-    e.  Pick the best model to continue (using model comparison)
-2.  Model 2 *No Traits Correlated Methods*
-3.  Model 3 *Perfectly Correlated Traits Correlated Methods*
-4.  Model 4 *Correlated Traits Uncorrelated Methods*
-
-```{r fig-mtmm, fig.cap="Representation of the multi-trait multi-method model for the MFD and MFQ.
-Not all measured variables (squares) are shown for ease of reading.
-The left hand side represents the traits or foundation areas of MFT, while the right hand side represents the two measurement tools for the MFT.
-"}
-knitr::include_graphics("mtmm_mfd.png")
-```
-
 ## Study 1.1
@@
 
-```{r demos-mtmm-study-3.1, include = FALSE}
+```{r demos-mtmm-study-1.1, include = FALSE}
 exp1data <- import("../../study1_data/study1.1_fixed_associations.csv")
@@
 # outliers on MFQ only 
-mahal1 <- mahalanobis(study1.1DF[ , -c(1:6,22,23)], 
+mahal1.1 <- mahalanobis(study1.1DF[ , -c(1:6,22,23)], 
                     colMeans(study1.1DF[ , -c(1:6,22,23)], na.rm = TRUE),
-                    cov(study1.1DF[ , -c(1:6,22,23)], use="pairwise.complete.obs"))
-#mahal1
-cutoff1 <- qchisq(1 - .001, ncol(study1.1DF[ , -c(1:6,22,23)]))
-df1 <- ncol(study1.1DF[ , -c(1:6,22,23)])
-summary1 <- summary(mahal1 < cutoff1) # nas will be excluded because they don't have the full scale 
-noout1.1 <- subset(study1.1DF, mahal1 < cutoff1)
+                    cov(study1.1DF[ , -c(1:6,22,23)], use = "pairwise.complete.obs"))
+#mahal1.1
+cutoff1.1 <- qchisq(1 - .001, ncol(study1.1DF[ , -c(1:6,22,23)]))
+df1.1 <- ncol(study1.1DF[ , -c(1:6,22,23)])
+summary1.1 <- summary(mahal1.1 < cutoff1.1) # nas will be excluded because they don't have the full scale 
+noout1.1 <- subset(study1.1DF, mahal1.1 < cutoff1.1)
 
@@
 # correlations for MFQ
-correlations1 <- cor(noout1.1[,-c(1:6,22,23)], use="pairwise.complete.obs")
-correlations1
-symnum(correlations1)
+correlations1.1 <- cor(noout1.1[,-c(1:6,22,23)], use = "pairwise.complete.obs")
+correlations1.1
+symnum(correlations1.1)
 
 # making the random stuff
-random1 <- rchisq(nrow(noout1.1), 7)
-fake1 <- lm(random1 ~ ., data = noout1.1[ , -c(1:6, 22, 23)])
+random1.1 <- rchisq(nrow(noout1.1), 7)
+fake1.1 <- lm(random1.1 ~ ., data = noout1.1[ , -c(1:6, 22, 23)])
 # normal
-standardized1 <- rstudent(fake1)
-hist(standardized1, breaks=15) # some skew
+standardized1.1 <- rstudent(fake1.1)
+hist(standardized1.1, breaks = 15) # some skew
 
 # linear
-{qqnorm(standardized1) 
+{qqnorm(standardized1.1) 
 abline(0,1)}
@@
 # homog + s
-fitvalues1 <- scale(fake1$fitted.values)
-{plot(fitvalues1, standardized1) 
+fitvalues1.1 <- scale(fake1.1$fitted.values)
+{plot(fitvalues1.1, standardized1.1) 
 abline(0,0)
@@
 university. Participants were given course credit for their introductory
-psychology course for completing the study. `r unname(summary1[4])`
+psychology course for completing the study. `r unname(summary1.1[4])`
 participants had missing data on the MFQ and were excluded from
@@
 Mahalanobis distance as described in @Tabachnick2012, and
-`r unname(summary1[2])` outliers were found using
-$\chi^2_{p < .001}$(`r df1`) = `r apa_num(cutoff1)`. These participants
+`r unname(summary1.1[2])` outliers were found using
+$\chi^2_{p < .001}$(`r df1.1`) = `r apa_num(cutoff1.1)`. These participants
 were excluded from further analyses, representing `r nrow(noout1.1)`
@@
 A complete example of the survey can be found online at
-<https://osf.io/5uqfn>. First, participants were given a description of
+<https://osf.io/6mv2g>. First, participants were given a description of
 associative memory as the relation between words that comes about
@@
 
-1.  Manual spell checking of free association responses
-2.  Word tokenization and stemming
-3.  Create a term by document matrix
-4.  Remove punctuation and stopwords via the *tm* stopword list
-5.  Calculate percent frequency across documents (all words saved
-    online)
-6.  Remove words with less than 1% mentions across participants
-
-```{r harm-analysis-3.1, include = FALSE}
+1.  Manual spell checking of free association responses.
+2.  Word tokenization and stemming.
+3.  Create a term by document matrix.
+4.  Remove punctuation and stopwords via the *tm* stopword list.
+5.  Calculate percent frequency across documents.
+6.  Remove words with less than 1% mentions across participants.
+
+```{r harm-analysis-1.1, include = FALSE}
 #q27 through 34 are the writing columns
@@
 # subset out to only words with 1% mentions
-harm_words <- harm_freq$Word[harm_freq$percent >=1]
+harm_words <- harm_freq$Word[harm_freq$percent >= 1]
 # turn sideways to add to dataset
@@
 
-```{r fair-analysi-3.1, include = FALSE}
+```{r fair-analysi-1.1, include = FALSE}
 #q27 through 34 are the writing columns
@@
 # subset out to only words with 1% mentions
-fair_words <- fair_freq$Word[fair_freq$percent >=1]
+fair_words <- fair_freq$Word[fair_freq$percent >= 1]
 # turn sideways to add to dataset
@@
 
-```{r ingroup-analysis-3.1, include=FALSE}
+```{r ingroup-analysis-1.1, include = FALSE}
 #q27 through 34 are the writing columns
@@
 # subset out to only words with 1% mentions
-ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >=1]
+ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >= 1]
 # turn sideways to add to dataset
@@
 
-```{r authority-analysis-3.1, include = FALSE}
+```{r authority-analysis-1.1, include = FALSE}
 #q27 through 34 are the writing columns
@@
 # subset out to only words with 1% mentions
-authority_words <- authority_freq$Word[authority_freq$percent >=1]
+authority_words <- authority_freq$Word[authority_freq$percent >= 1]
 # turn sideways to add to dataset
@@
 
-```{r purity-analysis-3.1, include = FALSE}
+```{r purity-analysis-1.1, include = FALSE}
 #q27 through 34 are the writing columns
@@
 # subset out to only words with 1% mentions
-purity_words <- purity_freq$Word[purity_freq$percent >=1]
+purity_words <- purity_freq$Word[purity_freq$percent >= 1]
 # turn sideways to add to dataset
@@
 
-this section is about the writing
+In this study, participants were asked to write about chemical warfare
+(wave 1), abortion, same-sex marriage, and environmentalism (wave 2).
+These prompts were designed to elicit writing about moral concepts that
+would relate to the moral foundations areas for expansion of the
+dictionary.
 
@@
 
-```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
-sample1 <- read.csv("study1_data/study1.2_fixed_sample 1.csv", stringsAsFactors = F)
-sample2 <- read.csv("study1_data/study1.2_fixed_sample 2.csv", stringsAsFactors = F)
+```{r demos-mtmm-study-1.2, include = FALSE, warning = FALSE}
+sample1 <- read.csv("../../study1_data/study1.2_fixed_sample 1.csv", stringsAsFactors = F)
+sample2 <- read.csv("../../study1_data/study1.2_fixed_sample 2.csv", stringsAsFactors = F)
 
@@
 #q24, q25, q26, q7 
-fullsample$writing <- apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
+study1.2DF$writing <- apply(study1.2DF[, c("Q24", "Q25", "Q26", "Q7")], 
                            1, function(x) toString(na.omit(x)))
@@
 crapcolumns <- c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
-finalsample <- fullsample[ , -crapcolumns]
+study1.2DF <- study1.2DF[ , -crapcolumns]
 
 ##accuracy
-summary(finalsample[ , 2:40])
-
-finalsample$Q10 <- factor(finalsample$Q10,
+summary(study1.2DF[ , 2:40])
+
+study1.2DF$Q10 <- factor(study1.2DF$Q10,
                          levels = 1:2,
                          labels = c("Man", "Woman"))
-finalsample$Q11 <- as.numeric(finalsample$Q11)
-finalsample$Q12 <- factor(finalsample$Q12,
+study1.2DF$Q11 <- as.numeric(study1.2DF$Q11)
+study1.2DF$Q12 <- factor(study1.2DF$Q12,
                          levels = 1:7,
@@
 
-gender <- table(finalsample$Q10)/sum(table(finalsample$Q10))*100
-race <- table(finalsample$Q12)/sum(table(finalsample$Q12))*100
-
-write.csv(finalsample, 'study1_data/study1.2_finalsample.csv', row.names = FALSE)
-newMFD <- import('study1_data/study1.2_finalsample_newMFD.csv')
-colnames(newMFD)[1:41] <- colnames(finalsample)[1:41]
+gender <- table(study1.2DF$Q10)/sum(table(study1.2DF$Q10))*100
+race <- table(study1.2DF$Q12)/sum(table(study1.2DF$Q12))*100
+
+write.csv(study1.2DF, '../../study1_data/study1.2_finalsample.csv', row.names = FALSE)
+newMFD <- import('../../study1_data/study1.2_finalsample_newMFD.csv')
+colnames(newMFD)[1:41] <- colnames(study1.2DF)[1:41]
 newMFD <- newMFD[,c(1,42:55)]
-finalsample <- merge(finalsample, newMFD, by = "ResponseId")
+study1.2DF <- merge(study1.2DF, newMFD, by = "ResponseId")
 
@@
 
-for (i in 1:nrow(finalsample)) {
-
-  finalsample$writing[i] <- preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
-  finalsample$wordcount[i] <- string.summary(finalsample$writing[i])$words
+for (i in 1:nrow(study1.2DF)) {
+
+  study1.2DF$writing[i] <- preprocess(study1.2DF$writing[i], case = "lower", remove.punct = TRUE)
+  study1.2DF$wordcount[i] <- string.summary(study1.2DF$writing[i])$words
 
@@
 #remove small words people
-finalwords <- subset(finalsample, wordcount >=25)
+finalwords <- subset(study1.2DF, wordcount >= 25)
 
@@
 ##outliers
-mahal2 <- mahalanobis(allcolumns[ , -c(1,46:56)], 
+mahal1.2 <- mahalanobis(allcolumns[ , -c(1,46:56)], 
                     colMeans(allcolumns[ , -c(1,46:56)], na.rm = TRUE),
-                    cov(allcolumns[ , -c(1,46:56)], use="pairwise.complete.obs"))
-#mahal2
-cutoff2 <- qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
-cutoff2
+                    cov(allcolumns[ , -c(1,46:56)], use = "pairwise.complete.obs"))
+#mahal1.2
+cutoff1.2 <- qchisq(1 - .001,ncol(allcolumns[ , -c(1,46:56)]))
+cutoff1.2
 ncol(allcolumns[ , -c(1,46:56)])
-summary(mahal2 < cutoff2) #Hmm what to do w/ NAs?? 
-noout2 <- subset(allcolumns, mahal2 < cutoff2)
+summary(mahal1.2 < cutoff1.2) #Hmm what to do w/ NAs?? 
+noout1.2 <- subset(allcolumns, mahal1.2 < cutoff1.2)
 
@@
 #correlations
-correlations2 <- cor(noout2[,-c(1,46:56)], use="pairwise.complete.obs")
-#correlations2
-symnum(correlations2)
+correlations1.2 <- cor(noout1.2[,-c(1,46:56)], use = "pairwise.complete.obs")
+#correlations1.2
+symnum(correlations1.2)
 
 #the random stuff
-random2 <- rchisq(nrow(noout2), 7)
-fake2 <- lm(random2~., data=noout2[ , -c(1,46:56)])
+random1.2 <- rchisq(nrow(noout1.2), 7)
+fake1.2 <- lm(random1.2 ~ ., data = noout1.2[ , -c(1,46:56)])
 
 #normal
-standardized2 <- rstudent(fake2)
-hist(standardized2, breaks=15)
+standardized1.2 <- rstudent(fake1.2)
+hist(standardized1.2, breaks = 15)
 
 #linear
-{qqnorm(standardized2)   
+{qqnorm(standardized1.2)   
 abline(0,1)}
@@
 #homog + s
-fitvalues2 <- scale(fake2$fitted.values)
-{plot(fitvalues2, standardized2) 
+fitvalues1.2 <- scale(fake1.2$fitted.values)
+{plot(fitvalues1.2, standardized1.2) 
 abline(0,0)
@@
 ####create the MFQ subscales####
-noout2$harmMFQ <- apply(noout2[ , 2:4], 1, sum)
-noout2$fairMFQ <- apply(noout2[ , 5:7], 1, sum)
-noout2$ingroupMFQ <- apply(noout2[ , 8:10], 1, sum)
-noout2$authorityMFQ <- apply(noout2[ , 11:13], 1, sum)
-noout2$purityMFQ <- apply(noout2[ , 14:16], 1, sum)
+noout1.2$harmMFQ <- apply(noout1.2[ , 2:4], 1, sum)
+noout1.2$fairMFQ <- apply(noout1.2[ , 5:7], 1, sum)
+noout1.2$ingroupMFQ <- apply(noout1.2[ , 8:10], 1, sum)
+noout1.2$authorityMFQ <- apply(noout1.2[ , 11:13], 1, sum)
+noout1.2$purityMFQ <- apply(noout1.2[ , 14:16], 1, sum)
 ```
@@
 were recruited via an online research system (SONA) and were given
-course credit for their participation. `r nrow(finalsample)`
+course credit for their participation. `r nrow(study1.2DF)`
 participants were included in the this study. The study was mostly women
@@
 (`r printnum(race["Other"], digits = 1)`%). The average listed age was
-`r printnum(mean(finalsample$Q11, na.rm = T))` (*SD* =
-`r printnum(sd(finalsample$Q11, na.rm = T))`).
+`r printnum(mean(study1.2DF$Q11, na.rm = T))` (*SD*  = 
+`r printnum(sd(study1.2DF$Q11, na.rm = T))`).
 
@@
 
-Data was again collected via Qualtrics (<https://osf.io/qr3gv>). Four
-fake new stories were presented to participants, which were roughly 400
-words each. First, all news stories included a few sentences describing
-the use of chemical weapons in the Syrian civil war. The news stories
-were manipulated with political (Republican v. Democrat) and religious
-(religious v. not) quotes in a 2 x 2 design. News stories can be found
-in the online materials. Participants also completed the 30-item version
-of the MFQ as described previously. In addition to basic demographics
-(gender, age), participant political orientation was assessed with the
-same scale described in Study 3.1.
-
-After consenting to participate in the study, participants were randomly
-shown one of the four new articles about Syria's use of chemical
-weapons. Participants were then asked to write for 5-10 minutes about
-their reaction to Syria's use of chemical weapons and the needed
-response from the United States. The second wave of data collection
-included different writing prompts designed to capture more of the moral
-foundation areas in their writing. The following writing prompt was
-used, "Please write about your attitudes on abortion (or same-sex
-marriage or environmentalism) as well as your reason for this stance."
-The three prompts were chosen to create a more varied word set by using
-topics that should elicit words from each moral foundations category by
-soliciting a moral response. In each wave of data collection (Syria
-prompts, moral prompts) the prompt material was randomized between
-participants. Participants then completed the MFQ, demographics, and the
-political orientation scale.
+#### Wave 1
+
+Data was again collected via Qualtrics. Four fake new stories
+were presented to participants, which were roughly 400 words each.
+First, all news stories included a few sentences describing the use of
+chemical weapons in the Syrian civil war. The news stories were
+manipulated with political (Republican v. Democrat) and religious
+(religious v. not) quotes in a 2 x 2 between-subjects design. News
+stories can be found in the online materials. After consenting to
+participate in the study, participants were randomly shown one of the
+four new articles about Syria's use of chemical weapons. Participants
+were then asked to write for 5-10 minutes about their reaction to
+Syria's use of chemical weapons and the needed response from the United
+States. Participants also completed the 30-item version of the MFQ as
+described previously. In addition to basic demographics (gender, age),
+participant political orientation was assessed with the same scale
+described in Study 1.1.
+
+#### Wave 2
+
+The second wave of data collection included different writing prompts
+designed to capture more of the moral foundation areas in their writing.
+The following writing prompt(s) were used, "Please write about your
+attitudes on abortion (or same-sex marriage or environmentalism) as well
+as your reason for this stance." The three prompts were chosen to create
+a more varied word set by using topics that should elicit words from
+each moral foundations category by soliciting a moral response. The
+writing prompts were randomized within participant, and each participant
+completed all three prompts. Participants then completed the MFQ,
+demographics, and the political orientation scale.
 
@@
 response to a given prompt were excluded (*n*  = 
-`r nrow(finalsample) - nrow(finalwords)`). One missing datapoint was
-estimated using the *mice* library from *R* [@CITE] for a missing MFQ
-question, and all other missing data was present in the demographics
-sections, which were not filled in. The MFQ data were screened for
-outliers using Mahalanobis distance, and 25 outliers were found at
-$\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`) =
-`r printnum(cutoff2)`. These data were excluded leading to a final
-sample size of `r nrow(noout2)`. Data were screened for assumptions
-described in Study 3.1 and were found to be satisfactory.
-
-```{r writing-analysis-3.2, include=FALSE}
+`r nrow(study1.2DF) - nrow(finalwords)`). One missing datapoint was
+estimated using the *mice* library from *R* for a missing MFQ question
+[@buuren2011], and all other missing data was present in the
+demographics sections, which were not filled in. The MFQ data were
+screened for outliers using Mahalanobis distance, and `r nrow(finalwords) - nrow(noout1.2)` outliers were
+found at $\chi^2_{p<.001}$(`r ncol(allcolumns[ , -c(1,32:42)])`)  = 
+`r printnum(cutoff1.2)`. These data were excluded leading to a final
+sample size of `r nrow(noout1.2)`. Data were screened for assumptions
+described in Study 1.1 and were found to be satisfactory.
+
+```{r writing-analysis-1.2, include = FALSE}
 ##stem the data
-for (i in 1:nrow(noout2)) {
-  noout2$writing2[i] <- paste(unlist(
-    text_tokens(noout2$writing[i], stemmer = "en")), collapse = " ")
+for (i in 1:nrow(noout1.2)) {
+  noout1.2$writing2[i] <- paste(unlist(
+    text_tokens(noout1.2$writing[i], stemmer = "en")), collapse = " ")
 }
@@
 ##create a corpus
-overall_corpus <- Corpus(VectorSource(noout2$writing2))
+overall_corpus <- Corpus(VectorSource(noout1.2$writing2))
 overall_TDM <- as.matrix(TermDocumentMatrix(overall_corpus,
@@
 overall_freq$Word <- as.character(overall_freq$Word)
-overall_freq$percent <- overall_freq$Freq/nrow(noout2)*100
-
-write.csv(overall_freq, "study1_data/study1.2_freq.csv", row.names = F)
+overall_freq$percent <- overall_freq$Freq/nrow(noout1.2)*100
+
+write.csv(overall_freq, "../../study1_data/study1.2_freq.csv", row.names = F)
 
@@
 ##a few times by participants
-all_words <- overall_freq$Word[overall_freq$percent >=1]
+all_words <- overall_freq$Word[overall_freq$percent >= 1]
 
@@
 ##final dataset
-overall_final <- cbind(noout2[ , c("ResponseId", "harmMFQ", "fairMFQ",
+overall_final <- cbind(noout1.2[ , c("ResponseId", "harmMFQ", "fairMFQ",
                                   "authorityMFQ", "purityMFQ","ingroupMFQ")],
@@
 
-```{r mfq-cor-3.2, include = FALSE}
+```{r mfq-cor-1.2, include = FALSE}
 ##harm
@@
 #print out words list to look at for further analysis
-write.csv(harm_words_reduce_exp2, "../study1_data/words/harm_exp2.csv", row.names = F)
-write.csv(fair_words_reduce_exp2, "../study1_data/words/fair_exp2.csv", row.names = F)
-write.csv(authority_words_reduce_exp2, "../study1_data/words/authority_exp2.csv", row.names = F)
-write.csv(purity_words_reduce_exp2, "../study1_data/words/purity_exp2.csv", row.names = F)
-write.csv(ingroup_words_reduce_exp2, "../study1_data/words/ingroup_exp2.csv", row.names = F)
+write.csv(harm_words_reduce_exp2, "../../study1_data/words/harm_exp2.csv", row.names = F)
+write.csv(fair_words_reduce_exp2, "../../study1_data/words/fair_exp2.csv", row.names = F)
+write.csv(authority_words_reduce_exp2, "../../study1_data/words/authority_exp2.csv", row.names = F)
+write.csv(purity_words_reduce_exp2, "../../study1_data/words/purity_exp2.csv", row.names = F)
+write.csv(ingroup_words_reduce_exp2, "../../study1_data/words/ingroup_exp2.csv", row.names = F)
 ```
@@
 find only the most related words, the correlation between word frequency
-and moral foundation was calculated and words with correlations greater
+and MFQ subscore was calculated, and words with correlations greater
 than two standard deviations outside the mean were selected for the
-dictionary analysis in Study 3.3. The sum of each moral foundation area
-was calculated in order to determine which words were linked to their
-respective moral foundation. The average scores were: harm (*M* =
-`r printnum(mean(noout2$harmMFQ))`, *SD* =
-`r printnum(sd(noout2$harmMFQ))`), fairness (*M* =
-`r printnum(mean(noout2$fairMFQ))`, *SD* =
-`r printnum(sd(noout2$fairMFQ))`), ingroup (*M* =
-`r printnum(mean(noout2$ingroupMFQ))`, *SD* =
-`r printnum(sd(noout2$ingroupMFQ))`), authority (*M* =
-`r printnum(mean(noout2$authorityMFQ))`, *SD* =
-`r printnum(sd(noout2$authorityMFQ))`), and purity (*M* =
-`r printnum(mean(noout2$purityMFQ))`, *SD* =
-`r printnum(sd(noout2$purityMFQ))`).
-
-```{r compare-ratings-3.2, include = FALSE}
-authority_erin <- read.csv("study1_data/words/authority_study1.2 erin.csv", stringsAsFactors = F)
-authority_will <- read.csv("study1_data/words/authority_study1.2 will.csv", stringsAsFactors = F)
+dictionary analysis in Study 1.3. The sum of each MFQ subscore
+was calculated for the correlation analysis. The average scores were: harm (*M*  = 
+`r printnum(mean(noout1.2$harmMFQ))`, *SD*  = 
+`r printnum(sd(noout1.2$harmMFQ))`), fairness (*M*  = 
+`r printnum(mean(noout1.2$fairMFQ))`, *SD*  = 
+`r printnum(sd(noout1.2$fairMFQ))`), ingroup (*M*  = 
+`r printnum(mean(noout1.2$ingroupMFQ))`, *SD*  = 
+`r printnum(sd(noout1.2$ingroupMFQ))`), authority (*M*  = 
+`r printnum(mean(noout1.2$authorityMFQ))`, *SD*  = 
+`r printnum(sd(noout1.2$authorityMFQ))`), and purity (*M*  = 
+`r printnum(mean(noout1.2$purityMFQ))`, *SD*  = 
+`r printnum(sd(noout1.2$purityMFQ))`).
+
+```{r compare-ratings-1.2, include = FALSE}
+authority_erin <- read.csv("../../study1_data/words/authority_study1.2 erin.csv", stringsAsFactors = F)
+authority_will <- read.csv("../../study1_data/words/authority_study1.2 will.csv", stringsAsFactors = F)
 authority_erin$x[authority_erin$use != authority_will$use]
@@
 
-fair_erin <- read.csv("study1_data/words/fair_study1.2 erin.csv", stringsAsFactors = F)
-fair_will <- read.csv("study1_data/words/fair_study1.2 will.csv", stringsAsFactors = F)
+fair_erin <- read.csv("../../study1_data/words/fair_study1.2 erin.csv", stringsAsFactors = F)
+fair_will <- read.csv("../../study1_data/words/fair_study1.2 will.csv", stringsAsFactors = F)
 fair_erin$x[fair_erin$use != fair_will$use]
@@
 
-purity_erin <- read.csv("study1_data/words/purity_study1.2 erin.csv", stringsAsFactors = F)
-purity_will <- read.csv("study1_data/words/purity_study1.2 will.csv", stringsAsFactors = F)
+purity_erin <- read.csv("../../study1_data/words/purity_study1.2 erin.csv", stringsAsFactors = F)
+purity_will <- read.csv("../../study1_data/words/purity_study1.2 will.csv", stringsAsFactors = F)
 purity_erin$x[purity_erin$use != purity_will$use]
@@
 
-ingroup_erin <- read.csv("study1_data/words/ingroup_study1.2 erin.csv", stringsAsFactors = F)
-ingroup_will <- read.csv("study1_data/words/ingroup_study1.2 will.csv", stringsAsFactors = F)
+ingroup_erin <- read.csv("../../study1_data/words/ingroup_study1.2 erin.csv", stringsAsFactors = F)
+ingroup_will <- read.csv("../../study1_data/words/ingroup_study1.2 will.csv", stringsAsFactors = F)
 ingroup_erin$x[ingroup_erin$use != ingroup_will$use]
@@
 
-harm_erin <- read.csv("study1_data/words/harm_study1.2 erin.csv", stringsAsFactors = F)
-harm_will <- read.csv("study1_data/words/harm_study1.2 will.csv", stringsAsFactors = F)
+harm_erin <- read.csv("../../study1_data/words/harm_study1.2 erin.csv", stringsAsFactors = F)
+harm_will <- read.csv("../../study1_data/words/harm_study1.2 will.csv", stringsAsFactors = F)
 harm_erin$x[harm_erin$use != harm_will$use]
@@
 
-This set of words was then coded by two of the authors for relevant
-words with discussion over coding constituting a tiebreaker. For
+The correlated set of words was then coded by two of the authors (EB, WP) for relevancy to the MFQ subscore and all disagreements were discussed to determine final inclusion. For
 example, for harm words in this study both *also* and *Syria* appeared
@@
 
-## Study 3.3
-
-This part is the mtmm
+## Study 1.3
+
+MTMM analyses use latent variable modeling to represent the underlying
+structure of a proposed phenomenon, while also accounting for the
+measurement of that phenomenon. As shown in Figure \@ref(fig:fig-mtmm),
+MTMM models are programmed to represent the traits that are measured
+(left hand side circles) and the methods used to measure those traits
+(right hand side circles). The squares in the middle represent the
+actual observed data, which is the MFQ questions and MFD scores. In the
+first model, *correlated traits correlated methods*, the latent
+variables are allowed to correlate on the traits and methods side, but
+not cross correlate from traits to methods. All models are then compared
+to this model to examine fit, convergent, and divergent validity. In the
+second model, *no traits correlated methods*, the trait side of the
+model is deleted and only methods are considered. The model should
+significantly degrade in fit, as the traits should be useful in
+explaining model variance for convergent validity (i.e., you do not want
+a model that suggests all the variances is due to measurement).
+
+In the third model, *perfectly correlated traits freely correlated methods*, the traits are added back to the model, but each correlation
+is set to one. The fit is compared to model 1, indicating if divergent
+validity of the traits has occurred. A significant degrade in fit should
+be found to indicate that trait correlations are not perfect. Last,
+model four *correlated traits uncorrelated methods*, the traits are
+allowed to naturally correlate but the methods correlations are set to
+zero. In comparison with model 1, the model should be roughly equal for
+divergent validity. This result would indicate that the methods each
+represent a different component to the measurement of the model, and do
+not represent the same measurement twice.
+
+Given the goal of improved measurement, we compared model 1 of the MTMM
+steps across several dictionaries to determine the best measurement for
+the dictionary. To assess model fit, we used the Root Mean Squared Error
+of Approximation [RMSEA, @steiger1990], the Root Mean Squared Residual
+[RMSR, @jöreskog1971], the Confirmatory Fit Index [CFI, @bentler1990],
+the Tucker-Lewis Index [TLI, @bentler1980]. The RMSEA and RMSR should be
+low for adequate model fit (\< .10) and the CFI and TLI should be high
+for adequate model fit (\> .90). For model comparison, we used a
+$\Delta$ CFI of greater than .01 to indicate a significant degradation
+in fit [@hu1999]. We will additionally use the standardized loadings for
+each of the traits to determine which model has the best measurement of
+moral foundations (\> .30 desired).
+
+```{r fig-mtmm, fig.cap = "Representation of the multi-trait multi-method model for the MFD and MFQ.
+Not all measured variables (squares) are shown for ease of reading.
+The left hand side represents the traits or foundation areas of MFT, while the right hand side represents the two measurement tools for the MFT.
+"}
+knitr::include_graphics("mtmm_mfd.png")
+```
+
+### Method
+
+#### MFD Dictionaries
+
+We created three versions of the MFD for separate MTMM analyses.
+The first dataset *original MFD* was comprised of the original concepts from the MFD.
+We added all versions of the original words (i.e., abuse --> abusive, abuser, abused) to ensure all forms of the words were captured within the stemming procedure.
+These words where then stemmed using the same procedures as the data processing described for the overall study to match the data processing completed on the participant prompt responses in Study 1.2.
+The *complete MFD* dataset included the original MFD concepts, all concepts listed from Study 1.1, and concepts from Study 1.2.
+The *reduced MFD* dataset included all concepts from the original MFD, correlated concepts from Study 1.2, and concepts from Study 1.2 (only correlated concepts were selected in Study 1.2).
+The percent of concepts within each moral found area was calculated on the writing prompts from Study 1.2.
+The percent values were calculated on the processed data excluding all stop words.
+These values are represented as the MFD squares in Figure \@ref(fig:fig-mtmm).
+
+#### MFQ Subscore
+
+The MFQ individual questions for each participant were used from Study 1.2.
+These values are represented as the MFQ Qs squares in Figure \@ref(fig:fig-mtmm).
+The final number of participants included in this model was `r nrow(noout1.2)`.
+
+#### Models
+
+For clarity, we programmed the following models:
+
+1.  Model 1 *Correlated Traits Correlated Methods*
+    a.  *Original* Original MFD Words
+    b.  *Complete* Original MFD Words + Study 1.1 + Study 1.2 Words
+    c.  *Reduced* Original MFD Words + Study 1.1 Reduced + Study 1.2 Words
+    d.  Determine if model suggests a feasible structure (fit indices
+        adequate + loadings adequate)
+    e.  Pick the best model to continue (using model comparison)
+2.  Model 2 *No Traits Correlated Methods*
+3.  Model 3 *Perfectly Correlated Traits Correlated Methods*
+4.  Model 4 *Correlated Traits Uncorrelated Methods*
 
@@
 ##original mfd words
-original_mfd <- read.csv("study1_data/original_mfd.csv", stringsAsFactors = F)
+original_mfd <- read.csv("../../study1_data/original_mfd.csv", stringsAsFactors = F)
 
@@
 
-mtmmdata <- noout2[ , c(1:31, 45) ]
+mtmmdata <- noout1.2[ , c(1:31, 45) ]
 
@@
 
-```{r mtmm_orig, include = FALSE}
-###Run chunk 8: demos_study2 to update data
-###Use noout2 df as dataframe for mtmm
-###Columns labeled Harm1/Fairness1/Loyalty1/Authority1/Purity1 are original MFD
-###Columns labeled Harm2/Fairness2/Loyalty2/Authority2/Purity2 are revised MFD
-
-####mtmm original dictionary####
-
+### Results
+
+```{r tab-mtmm, results = 'asis'}
+# table of the percents for each with the means from the studies 
+mtmmdata <- mtmmdata %>% 
+  mutate(harm_total = Q8_1+Q8_2+Q8_3,
+         fair_total = Q8_4+Q8_5+Q8_6, 
+         ingroup_total = Q8_7+Q8_8+Q8_9,
+         authority_total = Q8_10+Q8_11+Q8_12,
+         purity_total = Q8_13+Q8_14+Q8_15)
+
+mtmmdata.summary <- mtmmdata %>% 
+  summarize(
+    m_harm_mfq = mean(harm_total),
+    m_fair_mfq = mean(fair_total),
+    m_ingroup_mfq = mean(ingroup_total),
+    m_authority_mfq = mean(authority_total),
+    m_purity_mfq = mean(purity_total),
+    sd_harm_mfq = sd(harm_total),
+    sd_fair_mfq = sd(fair_total),
+    sd_ingroup_mfq = sd(ingroup_total),
+    sd_authority_mfq = sd(authority_total),
+    sd_purity_mfq = sd(purity_total),
+
+    m_harm_orig = mean(harm_orig),
+    m_fair_orig = mean(fair_orig),
+    m_ingroup_orig = mean(ingroup_orig),
+    m_authority_orig = mean(authority_orig),
+    m_purity_orig = mean(purity_orig),
+    sd_harm_orig = sd(harm_orig),
+    sd_fair_orig = sd(fair_orig),
+    sd_ingroup_orig = sd(ingroup_orig),
+    sd_authority_orig = sd(authority_orig),
+    sd_purity_orig = sd(purity_orig),
+
+    m_harm_all = mean(harm_all),
+    m_fair_all = mean(fair_all),
+    m_ingroup_all = mean(ingroup_all),
+    m_authority_all = mean(authority_all),
+    m_purity_all = mean(purity_all),
+    sd_harm_all = sd(harm_all),
+    sd_fair_all = sd(fair_all),
+    sd_ingroup_all = sd(ingroup_all),
+    sd_authority_all = sd(authority_all),
+    sd_purity_all = sd(purity_all),
+
+    m_harm_reduce = mean(harm_reduce),
+    m_fair_reduce = mean(fair_reduce),
+    m_ingroup_reduce = mean(ingroup_reduce),
+    m_authority_reduce = mean(authority_reduce),
+    m_purity_reduce = mean(purity_reduce),
+    sd_harm_reduce = sd(harm_reduce),
+    sd_fair_reduce = sd(fair_reduce),
+    sd_ingroup_reduce = sd(ingroup_reduce),
+    sd_authority_reduce = sd(authority_reduce),
+    sd_purity_reduce = sd(purity_reduce)
+  ) %>% 
+  pivot_longer(
+    cols = everything(),                      # Pivot all columns
+    names_to = c("Statistic", "Foundation_Area", "Dataset"),         # Split names into `type` and `variable`
+    names_sep = "_",                          # Split names on the underscore "_"
+    values_to = "value"                       # Values go into the `value` column
+  ) %>%
+  pivot_wider(
+    names_from = Statistic,                        # Pivot the `type` column (m, sd)
+    values_from = value                       # Populate `M` and `SD` columns
+  ) %>% 
+  mutate(Foundation_Area = factor(Foundation_Area, 
+                                  levels = names(table(Foundation_Area)), 
+                                  labels = c("Authority",
+                                             "Fair", 
+                                             "Harm", 
+                                             "Ingroup",
+                                             "Purity")),
+         Dataset = factor(Dataset,
+                          levels = names(table(Dataset)),
+                          labels = c("Complete", "MFQ", "Original", 
+                                     "Reduced")),
+         Dataset = factor(Dataset, levels = c("MFQ", 
+                                              "Original",
+                                              "Complete",
+                                              "Reduced"))) %>% 
+  arrange(Foundation_Area, Dataset)
+
+apa_table(mtmmdata.summary, 
+          note = "Mean percents for dictionaries, mean total subscores for the MFQ.",
+          caption = "Mean Percent Scores and MFQ Scores for Foundation Areas",
+          col.names = c("Foundation Area", "Dictionary/MFQ", "M", "SD"),
+          format = "latex",
+          escape = F,
+          align = c("l", "l", "c", "c"),
+          font_size = 'footnotesize',
+          placement = "h"
+          )
+```
+
+Table \@ref(tab:tab-mtmm) indicates the average percents found for each dictionary within each moral foundation area.
+The original MFD shows the lowest percentage of moral words for each foundation area, while the complete and reduced dataset show increases in the percent of text that would be considered moral words.
+
+#### Model 1
+
+```{r mtmm-model1, include = FALSE}
 {model1 <- '
@@
 authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+purityL =~ Q8_13+Q8_14+Q8_15+purity_orig 
 mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
@@
 
-model1.fit <- cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model1.2 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
+model1.fit <- cfa(model1, data = mtmmdata, std.lv = TRUE)
+model1.orig.results <- broom::tidy(model1.fit) 
+model1.orig.fit.results <- broom::glance(model1.fit)
+
+write.csv(model1.orig.results, "mtmm_results/original_model1.csv", row.names = F)
+
+{model1 <- '
+harmL =~ Q8_1+Q8_2+Q8_3+harm_all
+fairL =~ Q8_4+Q8_5+Q8_6+fair_all
+ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
+authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
+purityL =~ Q8_13+Q8_14+Q8_15+purity_all 
 mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-fair_orig ~~ 1167.145*fair_orig
+mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
 
@@
 
-model1.2.fit <- cfa(model1.2, data=mtmmdata, std.lv=TRUE)
-summary(model1.2.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.2.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.2.fit, fit.measures = "aic")
-
-{model2 <- '
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model2.fit <- cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model3.fit <- cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 <- '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_orig
-fairL =~ Q8_4+Q8_5+Q8_6+fair_orig
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_orig
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_orig
-purityL=~ Q8_13+Q8_14+Q8_15+purity_orig 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_orig+fair_orig+ingroup_orig+authority_orig+purity_orig
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-
-fair_orig ~~ 1167.145*fair_orig
-'}
-
-model4.fit <- cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-```{r mtmm_reduce, include = FALSE}
-
-{model1 = '
+model1.fit <- cfa(model1, data = mtmmdata, std.lv = TRUE)
+model1.all.results <- broom::tidy(model1.fit) 
+model1.all.fit.results <- broom::glance(model1.fit)
+
+write.csv(model1.all.results, "mtmm_results/all_model1.csv", row.names = F)
+
+{model1 <- '
 harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
@@
 authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
+purityL =~ Q8_13+Q8_14+Q8_15+purity_reduce 
 mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
@@
 
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_reduce
-fairL =~ Q8_4+Q8_5+Q8_6+fair_reduce
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_reduce
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_reduce
-purityL=~ Q8_13+Q8_14+Q8_15+purity_reduce 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_reduce+fair_reduce+ingroup_reduce+authority_reduce+purity_reduce
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-```{r mtmm_all, include = FALSE}
-
-{model1 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-'}
-
-model1.fit = cfa(model1, data=mtmmdata, std.lv=TRUE)
-summary(model1.fit, rsquare=TRUE, standardized=TRUE)
-semPaths(model1.fit, whatLabels = "std", layout = "tree")
-fitMeasures(model1.fit, fit.measures = "aic")
-
-{model2 ='
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-'}
-
-model2.fit = cfa(model2, data=mtmmdata, std.lv=TRUE)
-summary(model2.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model2.fit, fit.measures = "aic")
-
-{model3 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-harmL~~1*fairL
-harmL~~1*ingroupL
-harmL~~1*authorityL
-harmL~~1*purityL
-fairL~~1*ingroupL
-fairL~~1*authorityL
-fairL~~1*purityL
-ingroupL~~1*authorityL
-ingroupL~~1*purityL
-authorityL~~1*purityL
-'}
-
-model3.fit = cfa(model3, data=mtmmdata, std.lv=TRUE)
-summary(model3.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model3.fit, fit.measures = "aic")
-
-{model4 = '
-harmL =~ Q8_1+Q8_2+Q8_3+harm_all
-fairL =~ Q8_4+Q8_5+Q8_6+fair_all
-ingroupL =~ Q8_7+Q8_8+Q8_9+ingroup_all
-authorityL =~ Q8_10+Q8_11+Q8_12+authority_all
-purityL=~ Q8_13+Q8_14+Q8_15+purity_all 
-mfq =~ Q8_1+Q8_2+Q8_3+Q8_4+Q8_5+Q8_6+Q8_7+Q8_8+Q8_9+Q8_10+Q8_11+Q8_12+Q8_13+Q8_14+Q8_15
-mfd =~ harm_all+fair_all+ingroup_all+authority_all+purity_all
-
-##fix the covariances
-harmL~~0*mfq
-fairL~~0*mfq
-ingroupL~~0*mfq
-authorityL~~0*mfq
-purityL~~0*mfq
-harmL~~0*mfd
-fairL~~0*mfd
-ingroupL~~0*mfd
-authorityL~~0*mfd
-purityL~~0*mfd
-mfq ~~ 0*mfd
-'}
-
-model4.fit = cfa(model4, data=mtmmdata, std.lv=TRUE)
-summary(model4.fit, rsquare=TRUE, standardized=TRUE)
-fitMeasures(model4.fit, fit.measures = "aic")
-```
-
-Data Cleaning and Descriptives. In sample 1, participants who wrote less
-than 50 words were deleted (*n* = 69) leaving *n* = 221 participants.
-The average political orientation was 4.80 (*SD* = 2.21) on a scale of 1
-(*conservative*) to 10 (*liberal*). In sample 2, all 160 participants
-wrote at least 50 words. The mean political orientation was 5.01 (*SD* =
-2.33) for sample 2. The data from sample 1 and sample 2 were combined.
-Before any analyses were conducted, participants who did not use any
-words from the MFD were deleted; 16 participants were deleted from
-sample 1 and 25 from sample 2. The final sample size for analysis was
-*N* = 340 which had a mean political orientation of 4.90 (*SD* = 2.28).
-MFD scores were computed using NVivo *(CITE)* as both frequency for each
-foundation and percent coverage for each foundation. Frequency was
-simply the count of the number of words used from a given foundation
-dictionary; for example, a participant using the word *war* once and the
-word *peace* twice would have a frequency score of 3 for the *harm*
-dictionary. Percent coverage was calculated by taking the frequency and
-dividing by the word count; for example, given a frequency score of 3
-for the *harm* dictionary and a word count of 100, then the percent
-coverage would be .03 for the *harm* dictionary. MFQ scores for each
-foundation were calculated by averaging the six items pertaining to each
-foundation. Reliability. Here we should talk about the reliability of
-the MFQ for each piece, as well as the reliability of the words for the
-MFD. I think to do that you might need a thing that has each word as
-frequency count yes/no or however the LIWC version thing was done. MTMM.
-BASIC SEM STUFF HERE (also that you used bayes) Data screening was
-conducted using SPSS version 22 and AMOS version 22. Participants who
-were missing data for the MFD, MFQ, or political orientation were
-deleted from all analyses. Given the distribution of the dictionary
-variables, participants whose writing sample were less than 2% words
-from the MFD were deleted resulting in a sample size of 252.
-Additionally, 7 outliers were deleted. Widaman's (1985; as cited in
-@Byrne2009) four-step nested method was used to test the convergent and
-divergent validity of the MFD and MFQ. The first step is the baseline
-model (Model 1), which establishes correlation among traits (*harm*,
-*purity*, *fairness*, *authority*, and *ingroup*) as well as correlation
-among methods (MFD and MFQ) but no cross correlation of traits and
-methods. The individual questions from the 30 item version of the MFQ
-and the total frequency of concepts from each foundation in the MFD were
-used as measured variables. The fit of this first model indicated some
-misfit, as fit indices were a mix of poor and acceptable, $\chi$ 2 (514)
-= 977.46, $\chi$ 2/df = 1.90, CFI = .842, RMSEA = .061 [95% CI =
-.055-.067], SRMR = .0623. In this model, the MFD *harm*, *fairness*, and
-*ingroup* items significantly loaded onto their trait factors, while
-*authority* and *purity* did not. All foundations but *authority* loaded
-significantly on the method traits. All but two of the *ingroup*
-questions and one *authority* question loaded onto the MFQ trait
-factors. Several questions of the MFQ did not load significantly onto
-the methods factors; however, this result was taken as an indicator that
-traits variance was higher than methods variance. Generally, trait
-loadings were higher than method loadings for both the MFD and MFQ for
-*harm* and *fairness* traits. However, the *purity*, *ingroup*, and
-*authority* foundations did not show this loading pattern. ERIN STOPPED
-HERE CUZ HEADACHE. The second step (Model 2) involved eliminating the
-latent traits from the model. This model was significantly worse than
-Model 1 indicating the traits are important to the model ($\delta$
-$\chi$ 2 = 1141.09, $\delta$ df = 45, $\delta$ CFI = .351). This
-supports convergent validity for the traits measured by both methods
-which in this case are the five moral foundations. The third step (Model
-3) involved forcing the five traits to be perfectly correlated. This
-model was significantly worse than Model 1 indicating the usefulness of
-five unique traits ($\delta$ $\chi$ 2 = 311.09, $\delta$ df = 10,
-$\delta$ CFI = .097). This supports discriminant validity for the
-existence of five unique moral foundations. The final step (Model 4)
-involved allowing the correlations between the traits to be freely
-estimated and forcing the methods to be uncorrelated. This model was
-similar to Model 1 indicating the methods both measure the traits but
-they are both unique methods ($\delta$ $\chi$ 2 = 2.23, $\delta$ df = 1,
-$\delta$ CFI = .001). This supports discriminant validity for the
-methods. This set of analyses suggests the MFD is a possibly valid
-measure of moral foundations but does not measure them well enough to be
-useful in all applications and may be measuring them differently than
-the MFQ. Regression predicting Political Orientation. The MFQ has
-predicted political orientation across many studies [@Federico2013;
-@Graham2009; @Haidt2009; @Weber2013]. Therefore, in addition to the MTMM
-analysis, we compared how well the MFD score predicted political
-orientation compared to how well the MFQ predicted the political
-orientation. First, total MFQ scores were calculated for each foundation
-by averaging all six items. Then, a regression analysis was conducted
-with the five MFQ foundation score predicting political orientation. The
-overall model was significant, *R2* = .35, *F* (5, 255) = 26.91, *p* \<
-.05. Higher scores on the harm and fairness foundations predicted a more
-liberal political orientation with harm accounting for 3% of the
-variance and fairness accounting for 6%. Higher scores on ingroup,
-authority, and purity predicted a more conservative orientation
-accounting for 1%, 2%, and 8% on the variance respectively. See *table
-?* for regression coefficients. Next, a regression analysis was
-conducted to determine how well the five MFD scores predicted political
-orientation. The overall model was not significant, *R2* = .16, *F* (5,
-255) = 1.36, *p* = .241. Higher harm scores somewhat predicted more
-liberal orientation accounting for 1% of the variance in political
-orientation. Higher purity scores somewhat predicted more conservative
-orientation accounting for 1% of the variance. See *table ?* for
-regression coefficients.
-
-# Participants
-
-Participants were recruited in two waves as part of a larger
-investigation on priming political and religious attitudes (???).
-Participants were recruited via an online research system (SONA) and
-were given course credit for their participation. 463 participants were
-included in the this study. The study was mostly women (53.9%) and White
-(76.4%) participants with a mix of minority participants: Black (6.1%),
-(3.6%), (4.2%), Native American (1.9%), Mixed (2.9%) and Other (4.9%).
-The average listed age was 19.75 (SD = 200 2.94).
-
-# Materials and Procedure
-
-Data was again collected via Qualtrics. Four fake new stories were
-presented to participants, which were roughly 400 words each. First, all
-news stories included a few sentences describing the use of chemical
-weapons in the Syrian civil war. The news stories were manipulated with
-political (Republican v. Democrat) and religious (religious v. not)
-quotes in a 2 x 2 design. News stories can be found in the online
-materials. Participants also completed the 30-item version of the MFQ as
-described in the introduction. In addition to basic demographics
-(gender, age), participant political orientation was assessed with the
-same scale described in Study 1.
-
-After consenting to participate in the study, participants were randomly
-shown one of the four new articles about Syria’s use of chemical
-weapons. Participants were then asked to write for 5-10 minutes about
-their reaction to Syria’s use of chemical weapons and the needed
-response from the United States. The second wave of data collection
-included different writing prompts designed to capture more of the moral
-foundation areas in their writing. The following writing prompt was
-used, “Please write about your attitudes on abortion (or same-sex
-marriage or environmentalism) as well as your reason for this stance.”
-The three prompts were chosen to create a more varied word set by using
-topics that should elicit words from each moral foundations category by
-soliciting a moral response. In each wave of data collection (Syria
-prompts, moral prompts) the prompt material was randomized between
-participants. Participants then completed the MFQ, demographics, and the
-political orientation scale.
-
-# Results
-
-# Expanding the MFD
-
-In a separate study of 466 university students, participants completed a
-free association task where we asked them to list all the words that
-came to mind from *harm/care*, *fairness/reciprocity*, *loyalty/XX*,
-*authority/XX*, *purity/XX*. They also completed the 15 item MFQ.
-Responses to the free association task were cleaned and stemmed. This
-lead to a new set of moral foundation words: harm-96, fairness-76,
-ingroup-86, authority-81, and purity-80. These concepts were included in
-the full dictionary used for Study 3.
-
-We additionally created a reduced dictionary that included only concepts
-correlated with their respective moral foundations scores. Correlations
-between word frequency and the sum of the MFQ were calculated for each
-foundation and set of concepts. Words were included in the reduced
-dictionary if their correlation was two standard deviations away from
-the mean correlation for that foundation. The reduced dataset included
-the following number of words for each foundation: harm 4, fairness 3,
-ingroup 3, authority 4, and purity 2.
-
-```{r word-association}
-#need the code for the the above stuff
-```
-
-[ERIN, Please do mathy-math here]
-
-# Testing Model Structure
-
-Before testing the theorized differences between liberals and
-conservatives, we sought to test the validity of the MFD using
-Multi-Trait, Multi-Method modelling (MTMM) to determine if the MFD is
-measuring the same latent variables as the MFQ as it should.
-
-```{r mtmm}
-
-```
-
-# Testing Group Differences
-
-```{r mtmm-groupdiffs}
-
-```
+model1.fit <- cfa(model1, data = mtmmdata, std.lv = TRUE)
+model1.reduce.results <- broom::tidy(model1.fit) 
+model1.reduce.fit.results <- broom::glance(model1.fit)
+
+write.csv(model1.reduce.results, "mtmm_results/reduce_model1.csv", row.names = F)
+```
+
+Fit indices from the MTMM Model 1 step are shown in Table \@ref(tab:mtmm-model1-table).
+The complete parameter estimates from these models are saved online for full inspection due to their length.
+The fit indices from these models indicate that all models showed good fit.
+The original and complete MFD models showed equal fit ($\Delta$ CFA <= .01), and both models were better than the reduced MFD model.
+We then inspected the loadings to determine the adequacy of the loadings for the MFQ and MFD.
+These results are shown in Table \@ref(tab:mtmm-model1-table2).
+All but one question for the MFQ load adequately (>.30) on each of their moral foundation areas.
+None of the MFD areas load onto their moral foundation area, as all loadings are close to zero (and non-significant, see online).
+The excellent model fit was likely due to the structure of the MFQ, as the MFD results do not show relation to their foundation area.
+We did not run further models, as the goal was to show that Model 1 was the best model with appropriate loadings for foundations.
+
+```{r mtmm-model1-table, results = 'asis'}
+apa_table(
+  bind_rows(
+  model1.orig.fit.results, model1.all.fit.results, model1.reduce.fit.results
+) %>% 
+  mutate(Model = c("Original", "Complete", "Reduced")) %>% 
+  select(Model, chisq, npar, rmsea, srmr, cfi, tli, AIC)
+  , 
+          caption = "MTMM Fit Indices for Model 1 MTMM",
+          col.names = c("Model", "Chi-Sq", "df", "RMSEA", "SRMR", "CFI", "TLI", "AIC"),
+          format = "latex",
+          escape = F,
+          align = c("l", "l", "c", "c"),
+          font_size = 'footnotesize',
+          placement = "h"
+          )
+```
+
+```{r mtmm-model1-table2, results = 'asis'}
+est.table <-   bind_rows(
+  model1.orig.results %>% 
+    mutate(Model = "Original") %>% 
+    filter(op == "=~"), 
+  model1.all.results %>% 
+    mutate(Model = "All") %>% 
+    filter(op == "=~"), 
+  model1.reduce.results %>% 
+    mutate(Model = "Reduce") %>% 
+    filter(op == "=~")
+) %>% 
+  mutate(term = gsub("_orig|_all|_reduce", "", term)) %>% 
+  select(term, std.all, Model) %>% 
+  pivot_wider(
+    data = .,
+    id_cols = c(term), 
+    names_from = Model,
+    values_from = std.all
+    ) %>% 
+  slice_head(n = 20) %>% 
+  mutate(Latent = rep(c("Harm", "Fair", "Ingroup", "Authority", "Purity"), each = 4),
+         Measured = rep(c("1", "2", "3", "MFD"), times = 5)) %>% 
+  select(Latent, Measured, Original:Reduce)
+
+apa_table(est.table, 
+          note = "Estimates are completely standardized loadings from the model.",
+          caption = "MTMM Fit Estimates for Model 1 Loadings",
+          col.names = c("Latent Variable", "Measured Variable", 
+                        "Original", "All", "Reduced"),
+          format = "latex",
+          escape = F,
+          align = c("l", "l", "c", "c"),
+          font_size = 'footnotesize',
+          placement = "h"
+          )
+```
+
+## Discussion
+
+Study 1 was designed to investigate if the original MFD could be improved with additional concepts.
+As shown in Table \@ref(tab:tab-mtmm), the original MFD is often heavily skewed toward zero with very low percentages of moral words used in text.
+These results were found even when writing about concepts that should theoretically active moral values.
+The suggested improvements did increase percentages of included words; however, the results from the MTMM indicate that the MFD does not appear to relate to the MFQ moral foundations.
+In a separate set of studies, we examined if the original MFD proposed results for liberal and conservative values could be found within new sources [@Sagi2014].
+Further, we examined if the MFD could be improved with markers of valence (i.e., positive, negative), rather than just inclusion of more words.
 
@@
 (*harm/care* and *fairness/reciprocity*). Additionally, we hypothesized
-the two sources generally perceived to be conservative leaning (*Fox
-News* and *Breitbart*) would feature MFD words and valences indicating
+the two sources generally perceived to be conservative leaning (*Fox News* 
+and *Breitbart*) would feature MFD words and valences indicating
 equal endorsement of all five foundations.
 
-## Sources
+### Sources
 
@@
 
-## Materials
+### Materials
 
@@
 
-## Data analysis
+### Data analysis
 
@@
 
-Concurrent research by @Jordan2019 assesses the validity of both the MFQ
-and the MFD through a multi-trait multi-method analysis of the two
-instruments using multiple samples. The instruments and foundation areas
-are being analyzed against one another, in order to test reliability, as
-well as against the Congressional Record in order to test predictive
-validity for political orientation. We were able to identify a number of
-potential new words that, if added to the MFD, could comprise a
-dictionary with greater validity, and less likelihood of zero percent
-texts, as this often occurs with the current MFD. Those results have
-informed this analysis, and their updated findings may change the
-underlying dictionary used in this analysis (albeit, we do not expect
-any changes in the results presented below).
-
-A complete list of the words for each moral foundation area was created
-from previous research. The total number of times each of those words
+Given the results from Study 1.3, we used the original MFD to calculate 
+the number of words included for each moral foundation area. We could 
+also suggest using the larger complete dataset, given that the CFI indicated 
+similar models, and we note here that the pattern of results do not change 
+if that dictionary is used instead. The total number of times each of those words
 was used in an article was calculated. This information was merged with
@@
 
-```{r stem_text, eval=TRUE, include=FALSE}
-final = read.csv("./study1_data/finaldata.csv", stringsAsFactors = F)
+```{r stem_text, eval = TRUE, include = FALSE}
+final = read.csv("../../study2_data/finaldata.csv", stringsAsFactors = F)
 final = na.omit(final) #one weird NA line
@@
 ##open the Warriner data for later
-getwd()
-warriner = read.csv("../../study1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
+warriner = read.csv("../../study2_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
 warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)
@@
 
-```{r create_datasets_harm, echo = F, include=FALSE}
+```{r create_datasets_harm, echo = F, include = FALSE}
 #read in the harm total words from the mtmm project
-harm_all = read.csv("./study1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all = read.csv("../../study2_data/harm_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_fair, include=FALSE}
-fair_all = read.csv("./study1_data/fair_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_fair, include = FALSE}
+fair_all = read.csv("../../study2_data/fair_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_ingroup, include=FALSE}
-ingroup_all = read.csv("./study1_data/ingroup_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_ingroup, include = FALSE}
+ingroup_all = read.csv("../../study2_data/ingroup_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_authority, include=FALSE}
-authority_all = read.csv("./study1_data/authority_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_authority, include = FALSE}
+authority_all = read.csv("../../study2_data/authority_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_purity, include=FALSE}
-purity_all = read.csv("./study1_data/purity_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_purity, include = FALSE}
+purity_all = read.csv("../../study2_data/purity_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
+harm_final_temp <- harm_final_temp %>% 
+  left_join(
+    harm_final_data %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
+
 harm_final_temp$lean[grepl("nytimes.com", harm_final_temp$URL) |
@@
 
+harm_icc_p <- lme(percent ~ 1, 
+                data = harm_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
+
 harm_model = lme(MFDweight ~ lean,
@@
                  )
-summary(harm_model)
+
+harm_model_p = lme(percent ~ lean,
+                 data = harm_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                 )
 
@@
 
+fair_final_temp <- fair_final_temp %>% 
+  left_join(
+    fair_final_data %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
+
 fair_final_temp$lean[grepl("nytimes.com", fair_final_temp$URL) |
@@
 
+fair_icc_p <- lme(percent ~ 1, 
+                data = fair_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
+
 fair_model = lme(MFDweight ~ lean,
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
-summary(fair_model)
+                 random = list(~1|Source)
+                 )
+
+fair_model_p = lme(percent ~ lean,
+                 data = fair_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                 )
 
@@
 
+ingroup_final_temp <- ingroup_final_temp %>% 
+  left_join(
+    ingroup_final_data %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
+
 ingroup_final_temp$lean[grepl("nytimes.com", ingroup_final_temp$URL) |
@@
 
-ingroup_icc = lme(MFDweight ~ 1,
+ingroup_icc <- lme(MFDweight ~ 1, 
                 data = ingroup_final_temp,
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
+                 random = list(~1|Source)
+                )
+
+ingroup_icc_p <- lme(percent ~ 1, 
+                data = ingroup_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
 
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
-summary(ingroup_model)
+                 random = list(~1|Source)
+                 )
+
+ingroup_model_p = lme(percent ~ lean,
+                 data = ingroup_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                 )
 
@@
 
+authority_final_temp <- authority_final_temp %>% 
+  left_join(
+    authority_final_data %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
+
 authority_final_temp$lean[grepl("nytimes.com", authority_final_temp$URL) |
@@
 
-authority_icc = lme(MFDweight ~ 1,
+authority_icc <- lme(MFDweight ~ 1, 
                 data = authority_final_temp,
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
+                 random = list(~1|Source)
+                )
+
+authority_icc_p <- lme(percent ~ 1, 
+                data = authority_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
 
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
-summary(authority_model)
+                 random = list(~1|Source)
+                 )
+
+authority_model_p = lme(percent ~ lean,
+                 data = authority_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                 )
 
@@
 
+purity_final_temp <- purity_final_temp %>% 
+  left_join(
+    purity_final_data %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
+
 purity_final_temp$lean[grepl("nytimes.com", purity_final_temp$URL) |
@@
 
-purity_icc = lme(MFDweight ~ 1,
+purity_icc <- lme(MFDweight ~ 1, 
                 data = purity_final_temp,
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
+                 random = list(~1|Source)
+                )
+
+purity_icc_p <- lme(percent ~ 1, 
+                data = purity_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                )
 
@@
                  na.action = "na.omit",
-                 random = list(~1|Source))
-summary(purity_model)
+                 random = list(~1|Source)
+                 )
+
+purity_model_p = lme(percent ~ lean,
+                 data = purity_final_temp,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source)
+                 )
 
@@
 
-# Results
-
-## Descriptive Statistics
-
-```{r exp1_descriptive_calc, echo = F, include = F}
-final$uniquewords = NA
-final$valenceavg = NA
-
-for (i in 1:nrow(final)){
-
-  #add unique
-  final$uniquewords[i] = length(unique(unlist(strsplit(final$stemmed[i], " "))))
-
-  #add valence
-  tempwords = as.data.frame(unlist(strsplit(final$stemmed[i], " ")))
-  colnames(tempwords) = "theword"
-  tempwords$tempval = vlookup(tempwords$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final$valenceavg[i] = mean(tempwords$tempval, na.rm = T)
-
-}
-
-# tapply(final$valenceavg, final$Source, mean)
-# tapply(final$valenceavg, final$Source, sd)
-# tapply(final$wordcount, final$Source, mean)
-# tapply(final$wordcount, final$Source, sd)
-# tapply(final$uniquewords, final$Source, mean)
-# tapply(final$uniquewords, final$Source, sd)
-# tapply(final$Source, final$Source, length)
-# tapply(final$wordcount, final$Source, sum)
-
-final$FK = NA
-
-for (i in 1:nrow(final)){
-  final$FK[i] = unlist(textstat_readability(final$Text[i],
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-# tapply(final$FK, final$Source, mean)
-# tapply(final$FK, final$Source, sd)
-
-####build the table here####
-tableprint = matrix(NA, nrow=4, ncol=11)
-colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint[ , 1] = unique(final$Source)
-tableprint[ , 1] = c("Breitbart", "Fox News", "NPR", "New York Times")
-tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
-tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
-tableprint[ , 4] = tapply(final$valenceavg, final$Source, length)
-tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
-tableprint[ , 6] = tapply(final$wordcount, final$Source, mean)
-tableprint[ , 7] = tapply(final$wordcount, final$Source, sd)
-tableprint[ , 8] = tapply(final$uniquewords, final$Source, mean)
-tableprint[ , 9] = tapply(final$uniquewords, final$Source, sd)
-tableprint[ , 10] = tapply(final$FK, final$Source, mean)
-tableprint[ , 11] = tapply(final$FK, final$Source, sd)
-
-tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
-
-tableprint = tableprint[c(3, 4, 1, 2) , ]
-```
-
-We calculated descriptive statistics for each news source in order to
-understand any and all fundamental linguistic differences in the
-sources' use of English. Statistics calculated included average
-*z*-scored valence of the unique words per article, number of articles
-per source, total number of words per source, average number of tokens
-(words) per article in each source, average number of types (unique
-words) per article in each source, and mean readability level per
-source. Readability statistics were calculated using the Flesch-Kincaid
-Grade Level Readability formula [@Kincaid1975]. Readability is
-calculated using a formula where the total number of syllables, words,
-and sentences in a given passage are determinants of its difficulty. The
-obtained value is intended to match up with the U.S. grade level at
-which one should be able to comfortably read the passage [@Kincaid1975].
-For example, a text with a readability score of 11 should be easily read
-by a U.S. high school junior.
-
-As seen in Table \@ref(tab:exp1-source-descriptives), the sources are
-similar in some aspects yet different in others. Valence appears to be
-slightly positive across all sources. The large standard deviations seem
-to indicate little to no presence of a difference in valence across
-sources. *NYT* published the greatest number of articles as well as
-total words. *Breitbart* featured the lowest number of articles, and
-*NPR* the lowest number of total words from all articles. Per individual
-article, however, *Breitbart* appears to feature the highest average
-number of words as well as unique words. Once again the standard
-deviations call into question any apparent differences between sources.
-Finally, *Fox News* articles had the lowest reading grade level on
-average, while *NYT* had the highest. This result might be attributable
-to the greater number of tokens in the average *NYT* article compared to
-*Fox News*. The standard deviations for readability suggest the presence
-of a diverse array of articles for each source, ranging from low to high
-reading level. Large standard deviations suggest the sources feature a
-lot of overlap between them in their representation of scores.
-
-```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
-#change this to match
-apa_table(as.data.frame(tableprint),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Study 1 - Descriptive Statistics by Source",
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 10)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-## Inferential Statistics
+## Results
 
@@
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint2 = matrix(NA, ncol = 9, nrow = 5)
-colnames(tableprint2) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
+tableprint2 = matrix(NA, ncol = 10, nrow = 10)
+colnames(tableprint2) = c("Model",
+  "Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
 
@@
 
+harm_d_p = d.ind.t(m1 = mean(harm_final_temp$percent[harm_final_temp$lean == "Conservative"], na.rm = T),
+                 m2 = mean(harm_final_temp$percent[harm_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(harm_final_temp$percent[harm_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(harm_final_temp$percent[harm_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(harm_final_temp$percent[harm_final_temp$lean == "Conservative"]),
+                 n2 = length(harm_final_temp$percent[harm_final_temp$lean == "Liberal"]),
+                 a = .05)
+
 #fair
@@
 
+fair_d_p = d.ind.t(m1 = mean(fair_final_temp$percent[fair_final_temp$lean == "Conservative"], na.rm = T),
+                 m2 = mean(fair_final_temp$percent[fair_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(fair_final_temp$percent[fair_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(fair_final_temp$percent[fair_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(fair_final_temp$percent[fair_final_temp$lean == "Conservative"]),
+                 n2 = length(fair_final_temp$percent[fair_final_temp$lean == "Liberal"]),
+                 a = .05)
+
 #ingroup
@@
 
+ingroup_d_p = d.ind.t(m1 = mean(ingroup_final_temp$percent[ingroup_final_temp$lean == "Conservative"], na.rm = T),
+                 m2 = mean(ingroup_final_temp$percent[ingroup_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(ingroup_final_temp$percent[ingroup_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(ingroup_final_temp$percent[ingroup_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(ingroup_final_temp$percent[ingroup_final_temp$lean == "Conservative"]),
+                 n2 = length(ingroup_final_temp$percent[ingroup_final_temp$lean == "Liberal"]),
+                 a = .05)
+
 #authority
@@
 
+authority_d_p = d.ind.t(m1 = mean(authority_final_temp$percent[authority_final_temp$lean == "Conservative"], na.rm = T),
+                 m2 = mean(authority_final_temp$percent[authority_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(authority_final_temp$percent[authority_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(authority_final_temp$percent[authority_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(authority_final_temp$percent[authority_final_temp$lean == "Conservative"]),
+                 n2 = length(authority_final_temp$percent[authority_final_temp$lean == "Liberal"]),
+                 a = .05)
+
 #purity
@@
 
+purity_d_p = d.ind.t(m1 = mean(purity_final_temp$percent[purity_final_temp$lean == "Conservative"], na.rm = T),
+                 m2 = mean(purity_final_temp$percent[purity_final_temp$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(purity_final_temp$percent[purity_final_temp$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(purity_final_temp$percent[purity_final_temp$lean == "Liberal"], na.rm = T),
+                 n1 = length(purity_final_temp$percent[purity_final_temp$lean == "Conservative"]),
+                 n2 = length(purity_final_temp$percent[purity_final_temp$lean == "Liberal"]),
+                 a = .05)
+
 #put in the numbers
-tableprint2[1, ] = c("Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1,
+tableprint2[1, ] = c("Valence", "Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1,
                     summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
-                    harm_d$d, icc(harm_icc)$ICC_unadjusted)
-tableprint2[2, ] = c("Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1,
+                    harm_d$d, icc(harm_icc, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[2, ] = c("Valence", "Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1,
                     summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
-                    fair_d$d, icc(fair_icc)$ICC_unadjusted)
-tableprint2[3, ] = c("Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1,
+                    fair_d$d, icc(fair_icc, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[3, ] = c("Valence", "Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1,
                     summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
-                    ingroup_d$d, icc(ingroup_icc)$ICC_unadjusted)
-tableprint2[4, ] = c("Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1,
+                    ingroup_d$d, icc(ingroup_icc, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[4, ] = c("Valence", "Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1,
                     summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
-                    authority_d$d, icc(authority_icc)$ICC_unadjusted)
-tableprint2[5, ] = c("Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1,
+                    authority_d$d, icc(authority_icc, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[5, ] = c("Valence", "Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1,
                     summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
-                    purity_d$d, icc(purity_icc)$ICC_unadjusted)
-
-tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]), big.mark = "")
-tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
-tableprint2[ , 9] = printp(as.numeric(tableprint2[ , 7]))
+                    purity_d$d, icc(purity_icc, tolerance = 1e-10)$ICC_unadjusted)
+
+tableprint2[6, ] = c("Original", "Harm/Care", harm_d_p$M1, harm_d_p$sd1, harm_d_p$M2, harm_d_p$sd1,
+                    summary(harm_model_p)$tTable[2,4], summary(harm_model_p)$tTable[2,5],
+                    harm_d_p$d, icc(harm_icc_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[7, ] = c("Original", "Fairness/Reciprocity", fair_d_p$M1, fair_d_p$sd1, fair_d_p$M2, fair_d_p$sd1,
+                    summary(fair_model_p)$tTable[2,4], summary(fair_model_p)$tTable[2,5],
+                    fair_d_p$d, icc(fair_icc_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[8, ] = c("Original", "Ingroup/Loyalty", ingroup_d_p$M1, ingroup_d_p$sd1, ingroup_d_p$M2, ingroup_d_p$sd1,
+                    summary(ingroup_model_p)$tTable[2,4], summary(ingroup_model_p)$tTable[2,5],
+                    ingroup_d_p$d, icc(ingroup_icc_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[9, ] = c("Original", "Authority/Respect", authority_d_p$M1, authority_d_p$sd1, authority_d_p$M2, authority_d_p$sd1,
+                    summary(authority_model_p)$tTable[2,4], summary(authority_model_p)$tTable[2,5],
+                    authority_d_p$d, icc(authority_icc_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint2[10, ] = c("Original", "Purity/Sanctity", purity_d_p$M1, purity_d_p$sd1, purity_d_p$M2, purity_d_p$sd1,
+                    summary(purity_model_p)$tTable[2,4], summary(purity_model_p)$tTable[2,5],
+                    purity_d_p$d, icc(purity_icc_p, tolerance = 1e-10)$ICC_unadjusted)
+
+tableprint2[ , c(3:7,9)] = printnum(as.numeric(tableprint2[ , c(3:7,9)]), big.mark = "")
+tableprint2[ , 8] = printp(as.numeric(tableprint2[ , 8]))
+tableprint2[ , 10] = printp(as.numeric(tableprint2[ , 10]))
 ```
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Study 1 Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
+          caption = "Study 2 Results - Multilevel Model",
+          col.names = c("Model", 
+            "Foundation", "$M_C$", "$SD_C$", "$M_L$", 
+            "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
           format = "latex",
@@
 
-# Discussion
-
-The results obtained in Study 1 fail to support the differences
+## Discussion
+
+The results obtained in Study 2 fail to support the differences
 predicted by MFT. First, differences between liberal and conservative
@@
 articles with little to no moral-centric content. To address this
-limitation, two changes that were subsequently employed in Study 2.
+limitation, two changes that were subsequently employed in Study 3.
 First, we elected to include more news sources for web scraping and
-analysis in addition to the four used in Study 1. Second, we chose to
+analysis in addition to the four used in Study 2. Second, we chose to
 focus data collection efforts on two heavily moralized events in the
@@
 shutdown in December 2018 through January 2019 over disagreements about
-funding a U.S.-Mexico border wall. Hence, Study 2 is the best test of
+funding a U.S.-Mexico border wall. Hence, Study 3 is the best test of
 the MFT and the MFD in the context of partisan news.
 
-# Study 2
-
-# Method
-
-In contrast to Study 1, we approached Study 2 with the intention to
+# Study 3
+
+## Method
+
+In contrast to Study 2, we approached Study 3 with the intention to
 confirm the method employed was valid for the analysis of the scraped
@@
 
-## Sources
+### Sources
 
@@
 hearing and the 2018-2019 U.S. Government shutdown were scraped from the
-websites of 10 U.S. news sources. As in Study 1, these sources were
+websites of 10 U.S. news sources. As in Study 2, these sources were
 selected owing to their favorability among political partisans according
@@
 #read it in
-NYtimes_kav = read.csv("./exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-NPR_kav = read.csv("./exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-SLATE_kav = read.csv("./exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HUFFPO_kav = read.csv("./exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-POLITICO_kav = read.csv("./exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-FOX_kav = read.csv("./exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok
-BREITBART_kav = read.csv("./exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
-RUSH_kav = read.csv("./exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-BLAZE_kav = read.csv("./exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
-HANNITY_kav = read.csv("./exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
+NYtimes_kav = read.csv("../../study3_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+NPR_kav = read.csv("../../study3_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+SLATE_kav = read.csv("../../study3_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+HUFFPO_kav = read.csv("../../study3_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+POLITICO_kav = read.csv("../../study3_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+FOX_kav = read.csv("../../study3_data/FOX_kav.csv", stringsAsFactors = F) #ok
+BREITBART_kav = read.csv("../../study3_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
+RUSH_kav = read.csv("../../study3_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+BLAZE_kav = read.csv("../../study3_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+HANNITY_kav = read.csv("../../study3_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
 
@@
 #fix this issue
+master_kav$Text <- iconv(master_kav$Text, from = "", to = "UTF-8", sub = "byte")
 master_kav$Text = gsub("\\.", "\\. ", master_kav$Text)
@@
 #read it in
-NYtimes_gs = read.csv("./exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
-NPR_gs = read.csv("./exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
-SLATE_gs = read.csv("./exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok
-HUFFPO_gs = read.csv("./exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok
-POLITICO_gs = read.csv("./exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
-FOX_gs = read.csv("./exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok
-BREITBART_gs = read.csv("./exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok
-RUSH_gs = read.csv("./exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
-BLAZE_gs = read.csv("./exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok
-HANNITY_gs = read.csv("./exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
+NYtimes_gs = read.csv("../../study3_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
+NPR_gs = read.csv("../../study3_data/NPR_gs.csv", stringsAsFactors = F) #ok
+SLATE_gs = read.csv("../../study3_data/SLATE_gs.csv", stringsAsFactors = F) #ok
+HUFFPO_gs = read.csv("../../study3_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok
+POLITICO_gs = read.csv("../../study3_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
+FOX_gs = read.csv("../../study3_data/FOX_gs.csv", stringsAsFactors = F) #ok
+BREITBART_gs = read.csv("../../study3_data/BREITBART_gs.csv", stringsAsFactors = F) #ok
+RUSH_gs = read.csv("../../study3_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok
+BLAZE_gs = read.csv("../../study3_data/BLAZE_gs.csv", stringsAsFactors = F) #ok
+HANNITY_gs = read.csv("../../study3_data/HANNITY_gs.csv", stringsAsFactors = F) #ok
 
@@
 #fix this issue
+master_gs$Text <- iconv(master_gs$Text, from = "", to = "UTF-8", sub = "byte")
 master_gs$Text = gsub("\\.", "\\. ", master_gs$Text)
@@
 
-## Data analysis
-
-As in Study 1, the text was scanned with *ngram* [@Schmidt2017]. Again,
+### Data analysis
+
+As in Study 1 and 2, the text was scanned with *ngram* [@Schmidt2017]. Again,
 blank articles, text from the Disqus system, and duplicate articles were
@@
 #read in the harm total words from the mtmm project
-harm_all_kav = read.csv("./study1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_kav = read.csv("../../study2_data/harm_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_fair_kav, include=FALSE}
-fair_all_kav = read.csv("./study1_data/fair_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_fair_kav, include = FALSE}
+fair_all_kav = read.csv("../../study2_data/fair_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_ingroup_kav, include=FALSE}
-ingroup_all_kav = read.csv("./study1_data/ingroup_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_ingroup_kav, include = FALSE}
+ingroup_all_kav = read.csv("../../study2_data/ingroup_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_authority_kav, include=FALSE}
-authority_all_kav = read.csv("./study1_data/authority_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_authority_kav, include = FALSE}
+authority_all_kav = read.csv("../../study2_data/authority_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_purity_kav, include=FALSE}
-purity_all_kav = read.csv("./study1_data/purity_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_purity_kav, include = FALSE}
+purity_all_kav = read.csv("../../study2_data/purity_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 #read in the harm total words from the mtmm project
-harm_all_gs = read.csv("./study1_data/harm_words_total.csv", stringsAsFactors = F)
+harm_all_gs = read.csv("../../study2_data/harm_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_fair_gs, echo = F, include=FALSE}
-fair_all_gs = read.csv("./study1_data/fair_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_fair_gs, echo = F, include = FALSE}
+fair_all_gs = read.csv("../../study2_data/fair_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_ingroup_gs, echo = F, include=FALSE}
-ingroup_all_gs = read.csv("./study1_data/ingroup_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_ingroup_gs, echo = F, include = FALSE}
+ingroup_all_gs = read.csv("../../study2_data/ingroup_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_authority_gs, echo = F, include=FALSE}
-authority_all_gs = read.csv("./study1_data/authority_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_authority_gs, echo = F, include = FALSE}
+authority_all_gs = read.csv("../../study2_data/authority_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
-```{r create_datasets_purity_gs, echo = F, include=FALSE}
-purity_all_gs = read.csv("./study1_data/purity_words_total.csv", stringsAsFactors = F)
+```{r create_datasets_purity_gs, echo = F, include = FALSE}
+purity_all_gs = read.csv("../../study2_data/purity_words_total.csv", stringsAsFactors = F) %>% 
+  filter(dataset == "orig")
 
@@
 
+harm_final_temp_kav <- harm_final_temp_kav %>% 
+  left_join(
+    harm_final_data_kav %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
+
 harm_final_temp_kav$lean[grepl("nytimes.com", harm_final_temp_kav$URL) |
@@
 
+harm_icc_k_p <- lme(percent ~ 1,
+                 data = harm_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 harm_model_kav = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(harm_model_kav)
-r.squaredGLMM(harm_model_kav)
+
+harm_model_kav_p = lme(percent ~ lean,
+                 data = harm_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(fair_final_temp_kav) = c("URL", "MFDweight")
+
+fair_final_temp_kav <- fair_final_temp_kav %>% 
+  left_join(
+    fair_final_data_kav %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+fair_icc_k_p <- lme(percent ~ 1,
+                 data = fair_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 fair_model_kav = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(fair_model_kav)
+
+fair_model_kav_p = lme(percent ~ lean,
+                 data = fair_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(ingroup_final_temp_kav) = c("URL", "MFDweight")
+
+ingroup_final_temp_kav <- ingroup_final_temp_kav %>% 
+  left_join(
+    ingroup_final_data_kav %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+ingroup_icc_k_p <- lme(percent ~ 1,
+                 data = ingroup_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 ingroup_model_kav = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(ingroup_model_kav)
+
+ingroup_model_kav_p = lme(percent ~ lean,
+                 data = ingroup_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(authority_final_temp_kav) = c("URL", "MFDweight")
+
+authority_final_temp_kav <- authority_final_temp_kav %>% 
+  left_join(
+    authority_final_data_kav %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+authority_icc_k_p <- lme(percent ~ 1,
+                 data = authority_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 authority_model_kav = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(authority_model_kav)
+
+authority_model_kav_p = lme(percent ~ lean,
+                 data = authority_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(purity_final_temp_kav) = c("URL", "MFDweight")
+
+purity_final_temp_kav <- purity_final_temp_kav %>% 
+  left_join(
+    purity_final_data_kav %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+purity_icc_k_p <- lme(percent ~ 1,
+                 data = purity_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 purity_model_kav = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(purity_model_kav)
+
+purity_model_kav_p = lme(percent ~ lean,
+                 data = purity_final_temp_kav,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(harm_final_temp_gs) = c("URL", "MFDweight")
+
+harm_final_temp_gs <- harm_final_temp_gs %>% 
+  left_join(
+    harm_final_data_gs %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+harm_icc_gs_p <- lme(percent ~ 1,
+                 data = harm_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 harm_model_gs = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(harm_model_gs)
+
+harm_model_gs_p = lme(percent ~ lean,
+                 data = harm_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(fair_final_temp_gs) = c("URL", "MFDweight")
+
+fair_final_temp_gs <- fair_final_temp_gs %>% 
+  left_join(
+    fair_final_data_gs %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+fair_icc_gs_p <- lme(percent ~ 1,
+                 data = fair_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 fair_model_gs = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(fair_model_gs)
+
+fair_model_gs_p = lme(percent ~ lean,
+                 data = fair_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(ingroup_final_temp_gs) = c("URL", "MFDweight")
+
+ingroup_final_temp_gs <- ingroup_final_temp_gs %>% 
+  left_join(
+    ingroup_final_data_gs %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+ingroup_icc_gs_p <- lme(percent ~ 1,
+                 data = ingroup_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 ingroup_model_gs = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(ingroup_model_gs)
+
+ingroup_model_gs_p = lme(percent ~ lean,
+                 data = ingroup_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(authority_final_temp_gs) = c("URL", "MFDweight")
+
+authority_final_temp_gs <- authority_final_temp_gs %>% 
+  left_join(
+    authority_final_data_gs %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+authority_icc_gs_p <- lme(percent ~ 1,
+                 data = authority_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 authority_model_gs = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(authority_model_gs)
+
+authority_model_gs_p = lme(percent ~ lean,
+                 data = authority_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 colnames(purity_final_temp_gs) = c("URL", "MFDweight")
+
+purity_final_temp_gs <- purity_final_temp_gs %>% 
+  left_join(
+    purity_final_data_gs %>% 
+  group_by(URL) %>% 
+  summarize(percent = sum(Freq)/unique(wordcount)*100), 
+  by = "URL"
+  )
 
@@
 
+purity_icc_gs_p <- lme(percent ~ 1,
+                 data = purity_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
+
 purity_model_gs = lme(MFDweight ~ lean,
@@
                  random = list(~1|Source))
-summary(purity_model_gs)
+
+purity_model_gs_p = lme(percent ~ lean,
+                 data = purity_final_temp_gs,
+                 method = "ML",
+                 na.action = "na.omit",
+                 random = list(~1|Source))
 
@@
 
-# Results
-
-## Descriptive Statistics
-
-We calculated descriptive statistics for each news source per topic in
-order to reveal the presence (if any) of linguistic differences in the
-sources' use of language. As in Study 1, statistics calculated include
-*z*-scored valence, number of articles per source, total words per
-source, mean tokens per article in each source, mean types per article
-in each source, and mean readability level (using the Flesch-Kincaid
-Grade Level Readability formula) per source [@Kincaid1975].
-
-Table \@ref(tab:exp2-source-descriptives-kav) displays the descriptive
-statistics for sources' writing on the Kavanaughnaugh confirmation
-hearing. The sources were similar in most basic linguistic aspects,
-except for number of articles. For example, *Sean Hannity* appears to
-have published only 27 articles while *Breitbart* published 757 articles
-on this topic. Valence was found to be slightly positive across all
-sources. *Fox News* produced the most total words with the most tokens
-on average. This is likely due to the fact *Fox News* transcribes many
-of their videos and publishes them in article form. *Politico* featured
-the highest number of types on average. *Rush Limbaugh* featured the
-lowest readability score on average by grade level while *Slate*
-featured the highest grade-level readability score. The large standard
-deviations for these statistics, however, preclude conclusions regarding
-differences in the sources' use of language, as there is likely a lot of
-overlap between sources' use of language.
-
-```{r exp2_descriptive_calculate_kav, include = F, echo = F}
-#Kav
-final_kav$uniquewords = NA
-final_kav$valenceavg = NA
-for (i in 1:nrow(final_kav)){
-
-  #add unique
-  final_kav$uniquewords[i] = length(unique(unlist(strsplit(final_kav$stemmed[i], " "))))
-
-  #add valence
-  tempwords_kav = as.data.frame(unlist(strsplit(final_kav$stemmed[i], " ")))
-  colnames(tempwords_kav) = "theword"
-  tempwords_kav$tempval = vlookup(tempwords_kav$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
-}
-# tapply(final_kav$valenceavg, final_kav$Source, mean)
-# tapply(final_kav$valenceavg, final_kav$Source, sd)
-# tapply(final_kav$wordcount, final_kav$Source, mean)
-# tapply(final_kav$wordcount, final_kav$Source, sd)
-# tapply(final_kav$uniquewords, final_kav$Source, mean)
-# tapply(final_kav$uniquewords, final_kav$Source, sd)
-# tapply(final_kav$Source, final_kav$Source, length)
-# tapply(final_kav$wordcount, final_kav$Source, sum)
-library(quanteda)
-final_kav$FK = NA
-for (i in 1:nrow(final_kav)){
-  final_kav$FK[i] = unlist(textstat_readability(final_kav$Text[i],
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-# tapply(final_kav$FK, final_kav$Source, mean)
-# tapply(final_kav$FK, final_kav$Source, sd)
-#Kav Table
-####build the table here####
-tableprint3 = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint3) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-#tableprint3[ , 1] = unique(final_kav$Source)
-tableprint3[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity",
-                     "Huffington Post", "NPR", "New York Times", "Politico",
-                     "Rush Limbaugh", "Slate")
-tableprint3[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
-tableprint3[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
-tableprint3[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
-tableprint3[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
-tableprint3[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
-tableprint3[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
-tableprint3[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
-tableprint3[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
-tableprint3[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
-tableprint3[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
-tableprint3[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint3[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
-tableprint3 = tableprint3[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
-```
-
-```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
-#change this to match
-apa_table(as.data.frame(tableprint3),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Kavanaugh - Descriptive Statistics by Source",
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 10)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-Table \@ref(tab:exp2-source-descriptives-gs) displays descriptive
-statistics for articles about the partial government shutdown. Like the
-Kavanaugh hearing, the sources were similar in average valence (slightly
-positive). Once again, there was variation in the number of articles
-published by each source on this topic. *Sean Hannity*, *Rush Limbaugh*,
-and *The Blaze* published fewer than 100 articles while *Fox News*
-published 1,013 articles. *Fox News* again featured the most total words
-and mean tokens, but this is likely due to to the presence of a large
-amount of video transcriptions that the organization published as
-articles. *Politico* had the most types on average. For this topic, *Fox
-News* featured the lowest reading grade level while *Slate* featured the
-highest reading grade level. For each statistic, the excessively high
-standard deviations render any assertions regarding linguistic
-differences inconclusive on a descriptive level due to the
-aforementioned overlap in sources' language use.
-
-```{r exp2_descriptive_calculate_gs}
-#GS
-final_gs$uniquewords = NA
-final_gs$valenceavg = NA
-
-for (i in 1:nrow(final_gs)){
-
-  #add unique
-  final_gs$uniquewords[i] = length(unique(unlist(strsplit(final_gs$stemmed[i], " "))))
-
-  #add valence
-  tempwords_gs = as.data.frame(unlist(strsplit(final_gs$stemmed[i], " ")))
-  colnames(tempwords_gs) = "theword"
-  tempwords_gs$tempval = vlookup(tempwords_gs$theword, #index in original data
-                    warriner, #where's the stuff you want to put in
-                    "V.Mean.Sum", #what column is the stuff you want
-                    "Word2") #what's the matching index
-
-  final_gs$valenceavg[i] = mean(tempwords_gs$tempval, na.rm = T)
-
-}
-
-# tapply(final_gs$valenceavg, final_gs$Source, mean)
-# tapply(final_gs$valenceavg, final_gs$Source, sd)
-# tapply(final_gs$wordcount, final_gs$Source, mean)
-# tapply(final_gs$wordcount, final_gs$Source, sd)
-# tapply(final_gs$uniquewords, final_gs$Source, mean)
-# tapply(final_gs$uniquewords, final_gs$Source, sd)
-# tapply(final_gs$Source, final_gs$Source, length)
-# tapply(final_gs$wordcount, final_gs$Source, sum)
-
-library(quanteda)
-
-final_gs$FK = NA
-
-for (i in 1:nrow(final_gs)){
-  final_gs$FK[i] = unlist(textstat_readability(final_gs$Text[i],
-                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
-}
-
-# tapply(final_gs$FK, final_gs$Source, mean)
-# tapply(final_gs$FK, final_gs$Source, sd)
-
-#GS Table
-####build the table here####
-tableprint4 = matrix(NA, nrow=10, ncol=11)
-colnames(tableprint4) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
-
-#tableprint4[ , 1] = unique(final_gs$Source)
-tableprint4[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity",
-                     "Huffington Post", "NPR", "New York Times", "Politico",
-                     "Rush Limbaugh", "Slate")
-tableprint4[ , 2] = tapply(final_gs$valenceavg, final_gs$Source, mean)
-tableprint4[ , 3] = tapply(final_gs$valenceavg, final_gs$Source, sd)
-tableprint4[ , 4] = tapply(final_gs$valenceavg, final_gs$Source, length)
-tableprint4[ , 5] = tapply(final_gs$wordcount, final_gs$Source, sum)
-tableprint4[ , 6] = tapply(final_gs$wordcount, final_gs$Source, mean)
-tableprint4[ , 7] = tapply(final_gs$wordcount, final_gs$Source, sd)
-tableprint4[ , 8] = tapply(final_gs$uniquewords, final_gs$Source, mean)
-tableprint4[ , 9] = tapply(final_gs$uniquewords, final_gs$Source, sd)
-tableprint4[ , 10] = tapply(final_gs$FK, final_gs$Source, mean)
-tableprint4[ , 11] = tapply(final_gs$FK, final_gs$Source, sd)
-
-tableprint4[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint4[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
-
-tableprint4 = tableprint4[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
-```
-
-```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
-#change this to match
-apa_table(as.data.frame(tableprint4),
-          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
-          caption = "Government Shutdown - Descriptive Statistics by Source",
-          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
-          format = "latex",
-          escape = F,
-          align = c("l", rep("c", 10)),
-          font_size = 'footnotesize',
-          placement = "h"
-          )
-```
-
-## Inferential Statistics
+## Results
 
@@
 leveraged different vocabularies based on target audience in the same
-manner as Study 1. Each foundation's weighted percentage was predicted
+manner as Study 2. Each foundation's weighted percentage was predicted
 by the source's political lean, using the individual source as a random
@@
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint_kav = matrix(NA, ncol = 9, nrow = 5)
-colnames(tableprint_kav) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
+tableprint_kav = matrix(NA, ncol = 10, nrow = 10)
+colnames(tableprint_kav) = c("Model", 
+  "Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
 
@@
 
+harm_d_kav_p = d.ind.t(m1 = mean(harm_final_temp_kav$percent[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 m2 = mean(harm_final_temp_kav$percent[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(harm_final_temp_kav$percent[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(harm_final_temp_kav$percent[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(harm_final_temp_kav$percent[harm_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(harm_final_temp_kav$percent[harm_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
 #fair
@@
 
+fair_d_kav_p = d.ind.t(m1 = mean(fair_final_temp_kav$percent[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 m2 = mean(fair_final_temp_kav$percent[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(fair_final_temp_kav$percent[fair_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(fair_final_temp_kav$percent[fair_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(fair_final_temp_kav$percent[fair_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(fair_final_temp_kav$percent[fair_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
 #ingroup
@@
 
+ingroup_d_kav_p = d.ind.t(m1 = mean(ingroup_final_temp_kav$percent[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 m2 = mean(ingroup_final_temp_kav$percent[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(ingroup_final_temp_kav$percent[ingroup_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(ingroup_final_temp_kav$percent[ingroup_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(ingroup_final_temp_kav$percent[ingroup_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(ingroup_final_temp_kav$percent[ingroup_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
 #authority
@@
 
+authority_d_kav_p = d.ind.t(m1 = mean(authority_final_temp_kav$percent[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 m2 = mean(authority_final_temp_kav$percent[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(authority_final_temp_kav$percent[authority_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(authority_final_temp_kav$percent[authority_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(authority_final_temp_kav$percent[authority_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(authority_final_temp_kav$percent[authority_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
 #purity
@@
 
+purity_d_kav_p = d.ind.t(m1 = mean(purity_final_temp_kav$percent[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 m2 = mean(purity_final_temp_kav$percent[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(purity_final_temp_kav$percent[purity_final_temp_kav$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(purity_final_temp_kav$percent[purity_final_temp_kav$lean == "Liberal"], na.rm = T),
+                 n1 = length(purity_final_temp_kav$percent[purity_final_temp_kav$lean == "Conservative"]),
+                 n2 = length(purity_final_temp_kav$percent[purity_final_temp_kav$lean == "Liberal"]),
+                 a = .05)
+
 #put in the numbers
-tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1,
+tableprint_kav[1, ] = c("Valence", "Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1,
                     summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
-                    harm_d_kav$d, icc(harm_icc_k)$ICC_unadjusted)
-tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1,
+                    harm_d_kav$d, icc(harm_icc_k, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[2, ] = c("Valence", "Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1,
                     summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
-                    fair_d_kav$d, icc(fair_icc_k)$ICC_unadjusted)
-tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1,
+                    fair_d_kav$d, icc(fair_icc_k, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[3, ] = c("Valence", "Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1,
                     summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
-                    ingroup_d_kav$d, icc(ingroup_icc_k)$ICC_unadjusted)
-tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1,
+                    ingroup_d_kav$d, icc(ingroup_icc_k, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[4, ] = c("Valence", "Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1,
                     summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
-                    authority_d_kav$d, icc(authority_icc_k)$ICC_unadjusted)
-tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1,
+                    authority_d_kav$d, icc(authority_icc_k, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[5, ] = c("Valence", "Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1,
                     summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
-                    purity_d_kav$d, icc(purity_icc_k)$ICC_unadjusted)
-
-tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]), big.mark = "")
-tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
-tableprint_kav[ , 9] = printp(as.numeric(tableprint_kav[ , 9]))
+                    purity_d_kav$d, icc(purity_icc_k, tolerance = 1e-10)$ICC_unadjusted)
+
+tableprint_kav[6, ] = c("Original", "Harm/Care", harm_d_kav_p$M1, harm_d_kav_p$sd1, harm_d_kav_p$M2, harm_d_kav_p$sd1,
+                    summary(harm_model_kav_p)$tTable[2,4], summary(harm_model_kav_p)$tTable[2,5],
+                    harm_d_kav_p$d, icc(harm_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[7, ] = c("Original", "Fairness/Reciprocity", fair_d_kav_p$M1, fair_d_kav_p$sd1, fair_d_kav_p$M2, fair_d_kav_p$sd1,
+                    summary(fair_model_kav_p)$tTable[2,4], summary(fair_model_kav_p)$tTable[2,5],
+                    fair_d_kav_p$d, icc(fair_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[8, ] = c("Original", "Ingroup/Loyalty", ingroup_d_kav_p$M1, ingroup_d_kav_p$sd1, ingroup_d_kav_p$M2, ingroup_d_kav_p$sd1,
+                    summary(ingroup_model_kav_p)$tTable[2,4], summary(ingroup_model_kav_p)$tTable[2,5],
+                    ingroup_d_kav_p$d, icc(ingroup_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[9, ] = c("Original", "Authority/Respect", authority_d_kav_p$M1, authority_d_kav_p$sd1, authority_d_kav_p$M2, authority_d_kav_p$sd1,
+                    summary(authority_model_kav_p)$tTable[2,4], summary(authority_model_kav_p)$tTable[2,5],
+                    authority_d_kav_p$d, icc(authority_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_kav[10, ] = c("Original", "Purity/Sanctity", purity_d_kav_p$M1, purity_d_kav_p$sd1, purity_d_kav_p$M2, purity_d_kav_p$sd1,
+                    summary(purity_model_kav_p)$tTable[2,4], summary(purity_model_kav_p)$tTable[2,5],
+                    purity_d_kav_p$d, icc(purity_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
+
+tableprint_kav[ , c(3:7, 9)] = printnum(as.numeric(tableprint_kav[ ,  c(3:7, 9)]), big.mark = "")
+tableprint_kav[ , 8] = printp(as.numeric(tableprint_kav[ , 8]))
+tableprint_kav[ , 10] = printp(as.numeric(tableprint_kav[ , 10]))
 ```
@@
           caption = "Kavanaugh Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
+          col.names = c("Model",
+            "Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
           format = "latex",
           escape = F,
-          align = c("l", rep("c", 7)),
+          align = c("l", "l", rep("c", 7)),
           font_size = 'footnotesize',
@@
 tended to offer more positive endorsements of the foundation than
-liberal sources. This effect was similar to Study 1 in which the largest
+liberal sources. This effect was similar to Study 2 in which the largest
 effect size was observed for *authority/respect*. As noted before, the
-effect found in Study 1 was in the opposite direction as what was
+effect found in Study 2 was in the opposite direction as what was
 hypothesized. Thus, it is difficult to draw comparisons between the two
 studies despite the similar pattern for effect size. Owing to a lack of
-similar effects for either Study 1 or the Kavanaugh topic, there is
+similar effects for either Study 2 or the Kavanaugh topic, there is
 doubt as to whether or not a practical or generalized effect exists for
@@
 both topics, MFD words seem to make up little of the article text. A
-similar pattern was observed for the results in Study 1. As in Study 1,
+similar pattern was observed for the results in Study 2. As in Study 2,
 the percentages and means seem to indicate a generally positive
@@
 #MFD, mean, sd, mean, sd, t, p, d
-tableprint_gs = matrix(NA, ncol = 9, nrow = 5)
-colnames(tableprint_gs) = c("Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
+tableprint_gs = matrix(NA, ncol = 10, nrow = 10)
+colnames(tableprint_gs) = c("Model",
+  "Foundation", "M_C", "SD_C", "M_L", "SD_L", "t", "p", "d", "ICC")
 
@@
 
+harm_d_gs_p = d.ind.t(m1 = mean(harm_final_temp_gs$percent[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 m2 = mean(harm_final_temp_gs$percent[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(harm_final_temp_gs$percent[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(harm_final_temp_gs$percent[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(harm_final_temp_gs$percent[harm_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(harm_final_temp_gs$percent[harm_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
 #fair
@@
 
+fair_d_gs_p = d.ind.t(m1 = mean(fair_final_temp_gs$percent[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 m2 = mean(fair_final_temp_gs$percent[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(fair_final_temp_gs$percent[fair_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(fair_final_temp_gs$percent[fair_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(fair_final_temp_gs$percent[fair_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(fair_final_temp_gs$percent[fair_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
 #ingroup
@@
 
+ingroup_d_gs_p = d.ind.t(m1 = mean(ingroup_final_temp_gs$percent[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 m2 = mean(ingroup_final_temp_gs$percent[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(ingroup_final_temp_gs$percent[ingroup_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(ingroup_final_temp_gs$percent[ingroup_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(ingroup_final_temp_gs$percent[ingroup_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(ingroup_final_temp_gs$percent[ingroup_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
 #authority
@@
 
+authority_d_gs_p = d.ind.t(m1 = mean(authority_final_temp_gs$percent[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 m2 = mean(authority_final_temp_gs$percent[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(authority_final_temp_gs$percent[authority_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(authority_final_temp_gs$percent[authority_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(authority_final_temp_gs$percent[authority_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(authority_final_temp_gs$percent[authority_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
 #purity
@@
 
+purity_d_gs_p = d.ind.t(m1 = mean(purity_final_temp_gs$percent[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 m2 = mean(purity_final_temp_gs$percent[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 sd1 = sd(purity_final_temp_gs$percent[purity_final_temp_gs$lean == "Conservative"], na.rm = T),
+                 sd2 = sd(purity_final_temp_gs$percent[purity_final_temp_gs$lean == "Liberal"], na.rm = T),
+                 n1 = length(purity_final_temp_gs$percent[purity_final_temp_gs$lean == "Conservative"]),
+                 n2 = length(purity_final_temp_gs$percent[purity_final_temp_gs$lean == "Liberal"]),
+                 a = .05)
+
 #put in the numbers
-tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1,
+tableprint_gs[1, ] = c("Valence", "Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1,
                     summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
-                    harm_d_gs$d, icc(harm_icc_gs)$ICC_unadjusted)
-tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1,
+                    harm_d_gs$d, icc(harm_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_gs[2, ] = c("Valence", "Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1,
                     summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
-                    fair_d_gs$d, icc(fair_icc_gs)$ICC_unadjusted)
-tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1,
+                    fair_d_gs$d, icc(fair_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_gs[3, ] = c("Valence", "Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1,
                     summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
                     ingroup_d_gs$d, icc(ingroup_icc_gs)$ICC_unadjusted)
-tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1,
+tableprint_gs[4, ] = c("Valence", "Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1,
                     summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
-                    authority_d_gs$d, icc(authority_icc_gs)$ICC_unadjusted)
-tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1,
+                    authority_d_gs$d, icc(authority_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_gs[5, ] = c("Valence", "Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1,
                     summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
-                    purity_d_gs$d, icc(purity_icc_gs)$ICC_unadjusted)
-
-tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]), big.mark = "")
-tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
-tableprint_gs[ , 9] = printp(as.numeric(tableprint_gs[ , 9]))
+                    purity_d_gs$d, icc(purity_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
+
+tableprint_gs[6, ] = c("Original", "Harm/Care", harm_d_gs_p$M1, harm_d_gs_p$sd1, harm_d_gs_p$M2, harm_d_gs_p$sd1,
+                    summary(harm_model_gs_p)$tTable[2,4], summary(harm_model_gs_p)$tTable[2,5],
+                    harm_d_gs_p$d, icc(harm_icc_gs_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_gs[7, ] = c("Original", "Fairness/Reciprocity", fair_d_gs_p$M1, fair_d_gs_p$sd1, fair_d_gs_p$M2, fair_d_gs_p$sd1,
+                    summary(fair_model_gs_p)$tTable[2,4], summary(fair_model_gs_p)$tTable[2,5],
+                    fair_d_gs_p$d, icc(fair_icc_gs_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_gs[8, ] = c("Original", "Ingroup/Loyalty", ingroup_d_gs_p$M1, ingroup_d_gs_p$sd1, ingroup_d_gs_p$M2, ingroup_d_gs_p$sd1,
+                    summary(ingroup_model_gs_p)$tTable[2,4], summary(ingroup_model_gs_p)$tTable[2,5],
+                    ingroup_d_gs_p$d, icc(ingroup_icc_gs_p)$ICC_unadjusted)
+tableprint_gs[9, ] = c("Original", "Authority/Respect", authority_d_gs_p$M1, authority_d_gs_p$sd1, authority_d_gs_p$M2, authority_d_gs_p$sd1,
+                    summary(authority_model_gs_p)$tTable[2,4], summary(authority_model_gs_p)$tTable[2,5],
+                    authority_d_gs_p$d, icc(authority_icc_gs_p, tolerance = 1e-10)$ICC_unadjusted)
+tableprint_gs[10, ] = c("Original", "Purity/Sanctity", purity_d_gs_p$M1, purity_d_gs_p$sd1, purity_d_gs_p$M2, purity_d_gs_p$sd1,
+                    summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
+                    purity_d_gs$d, icc(purity_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
+
+tableprint_gs[ , c(3:7, 9)] = printnum(as.numeric(tableprint_gs[ , c(3:7, 9)]), big.mark = "")
+tableprint_gs[ , 8] = printp(as.numeric(tableprint_gs[ , 8]))
+tableprint_gs[ , 10] = printp(as.numeric(tableprint_gs[ , 10]))
 ```
@@
           caption = "Government Shutdown Results - Multilevel Model",
-          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
+          col.names = c("Model", 
+            "Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
           format = "latex",
           escape = F,
-          align = c("l", rep("c", 7)),
+          align = c("l", "l", rep("c", 7)),
           font_size = 'footnotesize',
@@
 
-# Discussion
-
-The results obtained in Study 2 are slightly more in line with
+## Discussion
+
+The results obtained in Study 3 are slightly more in line with
 expectations from MFT, however, in all but one case, the differences
@@
 
-Together with Study 1 and past work, Study 2 further calls into question
+Together with Study 2 and past work, Study 3 further calls into question
 the usefulness and efficacy of the Moral Foundations as well as cast
-doubt on the predictions made by MFT. One issue that Study 2 brings up
+doubt on the predictions made by MFT. One issue that Study 3 brings up
 is that moral differences between liberals and conservatives may be
@@
 
-Within the theoretical framework of MFT [@Haidt2007], we attempted to
-devise a method leveraging the MFD [@Graham2009] in order to quantify
+Within the theoretical framework of MFT [@Haidt2007], we attempted to improve the MFD [@Graham2009] and demonstrate its relation with other reliable measurements of moral foundations, the MFQ.
+In Study 1, we examined potential new concepts to add to the MFD by collecting word associations and moral related texts from participants.
+Several dictionary improvements were suggested, but the results of a multi-trait multi-method analysis indicate that the MFD does not relate to the moral foundations found in the MFD.
+Therefore, we did not find support for the use of the MFD in relation to the MFT using a convergent and divergent validity technique.
+
+In Study 2 and 3, we attempted to
+devise a method leveraging the MFD in order to quantify
 political bias stemming from content published by several prominent
-American news sources. In Study 1,the results obtained were not
+American news sources. In Study 2, the results obtained were not
 significant in any statistical or practical sense. There was a small
@@
 *d*, but the effect suggested endorsement for that foundation opposite
-to what was hypothesized. In Study 2, the direction of the differences
+to what was hypothesized. In Study 3, the direction of the differences
 were generally in line with MFT, however, the difference were very small
@@
 
-```{=tex}
-\begingroup
-```
-::: {#refs custom-style="Bibliography"}
+::: {#refs}
 :::
 
-```{=tex}
-\endgroup
-```
+\newpage
+
+# (APPENDIX) Appendix {.unnumbered}
+
+```{r child = "appendix.Rmd"}
+```

### 2024-11-30 manuscript_version/revision/manuscript_metapsych_revision.tex
rearranging folders and updating the manuscript

@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \def\languageshorthands#1{}
+\ifLuaTeX
+  \usepackage[english]{selnolig} % disable illegal ligatures
+\fi
 % Manuscript styling
@@
   {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
     {}{\InnerPatchFailed}%
@@
 {}{\PatchFailed}
+\makeatother
 \keywords{politics, morality, psycholinguistics}
 \usepackage{csquotes}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
-Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+In Study 1, we explore the MFD-Moral Foundations Questionnaire's measurement overlap using a multi-trait multi-method model.
+These latent trait models were used to inform possible improvement of the MFD.
+Next, we examined two replication extensions of previous work exploring the differences in political articles on moral differences Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
-In Study 1, we gathered political articles from four sources.
+In Study 2, we gathered political articles from four sources.
 We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
-In Study 2, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
+In Study 3, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
 Supreme Court Justice Brett Kavanaugh and the partial U.S.
@@
 
-The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development (Kohlberg \& Hersh, 1977).
-Since then, Kohlberg's theory has been highly criticized with numerous theories and hypotheses proposed to replace it.
-One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham (Haidt \& Graham, 2007).
-While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related measurement issue, the Moral Foundations Dictionary (MFD) (Graham, Haidt, \& Nosek, 2009).
-Graham et al.
-(2009) developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use.
-Here we first review evidence and criticisms against this assumption.
-We then provide our own test of the MFD using partisan news articles.
-
-\hypertarget{moral-foundations-dictionary}{%
-\subsection{Moral Foundations Dictionary}\label{moral-foundations-dictionary}}
-
-Haidt and Jesse (2007) formulated MFT as a method by which to capture the entirety of humans' moral domain.
-We argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals.
-In other words, moral psychology ignored the valid moral foundations of conservatives.
-MFT holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007).
-
-In order to capture language's role in moral and political reasoning, Graham et al.
-(2009) formulated the MFD in order to capture moral reasoning and justification as used in speech and text.
-The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations.
-Graham et al.
-(2009) created a preliminary list of words that they believed would be associated with the five foundations.
-Then, using the Linguistic Inquiry and Word Count {[}LIWC; Pennebaker, Booth, and Frances (2007){]} computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from we' initial list.
-
-Similar to previous research on MFT, liberal ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than conservative ministers.
-Conversely, conservative ministers used \emph{authority} and \emph{purity} words more often than liberal ministers.
-However, conservative ministers did not use \emph{ingroup/loyalty} words more than liberals.
-Rather, liberal ministers used words pertaining to \emph{ingroup/loyalty}, but in contexts that promote rebellion and independence - causes \emph{opposite} to positive endorsements of that foundation (Graham et al., 2009).
-
-\hypertarget{critiques-of-moral-foundations}{%
-\subsection{Critiques of Moral Foundations}\label{critiques-of-moral-foundations}}
-
-MFT has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis.
-Suhler, Churchland, and Joseph (2011) criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation.
-Likewise, Gray and Keeney (2015) argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction.
-Schein and Gray (2015) argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.
-
-Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.
-Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S.
-Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, Frimer (2020) found that the liberal-conservative differences found in the original study replicated in only 30\% of cases and the effect sizes were over 30 times smaller than reported in Graham et al.
-(2009).
-In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
-Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
-Additionally, Frimer (2020) tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores.
-Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects.
-Other studies have also found conflicting findings which fail to support the basic assertions of MFT.
-Exploring the political Twitterverse, Sterling and Jost (2018) found differences in the MFD depend on political sophistication.
-For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words.
-While the MFD has not been extensively used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT (Clifford \& Jerit, 2013; Frimer, Tell, \& Haidt, 2015; Sagi \& Dehghani, 2014).
-Like Frimer (2020), we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.
-
-The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).
-These attempts generally fall into two categories: human annotations and semantic representations.
-Hopp, Fisher, Cornell, Huskey, and Weber (2021) represents the first approach where instead of relying on `experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation.
-While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary.
-Garten, Boghrati, Hoover, Johnson, and Dehghani (2016) represents the second categories which instead relies on data-driven semantic analysis.
-Using shallow neural net models like word2vec (Mikolov, Chen, Corrado, \& Dean, 2013), moral foundations were measured using semantic similarity vectors rather than simple word counts.
-
-As a further conceptual replication of Frimer (2020), we test the liberal-conservative difference proposed by MFT using partisan media content and the MFD.
-We first test differences in a general news corpus compared liberal sources (National Public Radio {[}NPR{]} and the New York Times {[}NYT{]}) to conservative sources (Fox News and Breitbart).
-Second, we examined news about specific political events: Brett Kavanaugh's U.S.
-Supreme Court nomination and the U.S.
-Government Shutdown in 2018-2019.
-In the second study, the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side.
-To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement.
-Like Frimer (2020), results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.
-
-\hypertarget{study-1}{%
-\section{Study 1}\label{study-1}}
-
-\hypertarget{method}{%
-\section{Method}\label{method}}
-
-For the first study, we approached the study with the intention to answer a method question.
-That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the MFT framework while also alleviating some of the aforementioned valence problem observed in the MFD.
-We hypothesized the news sources generally perceived as liberal leaning (\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}).
-Additionally, we hypothesized the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences indicating equal endorsement of all five foundations.
-
-\hypertarget{sources}{%
-\subsection{Sources}\label{sources}}
+The field of moral psychology has a long history with modern moral
+psychology beginning in the late 1960s with Lawrence Kohlberg's theory
+of moral development (Kohlberg \& Hersh, 1977). Since then, Kohlberg's theory has
+been highly criticized with numerous theories and hypotheses proposed to
+replace it. One of these theories is Moral Foundations Theory (MFT)
+proposed by Haidt and colleagues (Haidt \& Graham, 2007; Haidt \& Joseph, 2004). While the
+theory itself has been widely criticized and debated, the goal of the
+current work is to tackle a related measurement issue, the Moral
+Foundations Dictionary (MFD, Graham, Haidt, \& Nosek, 2009). Graham et al. (2009) developed the
+MFD - a lexicon-based linguistic measure of MFT - arguing that moral
+concerns and the propositions of MFT could be measured and tested with
+the words people use. Here we first review evidence and criticisms
+against this assumption. We then provide our own test of the MFD using
+partisan news articles.
+
+\subsection{Moral Foundations Measurement}\label{moral-foundations-measurement}
+
+Haidt and Joseph {[}-@haidt2004{]} and Haidt and Graham (2007)
+formulated MFT as a method by which to capture the entirety of humans'
+moral domain. They argued that older theories of moral psychology were
+focused primarily on issues of justice, fairness, and caring, which are
+individually focused foundations of morality that align with the beliefs
+of political liberals. In other words, moral psychology ignored the
+valid moral foundations of conservatives. MFT holds that people's moral
+domain can be mapped by quantifying their endorsement of five moral
+foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty},
+\emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007). Thus, they
+proposed that the addition of these two additional domains could
+adequately capture the broader spectrum of morality.
+
+Measurement of MFT has traditionally focused on two options: 1) the
+Moral Foundations Questionnaire (MFQ) - a typical Likert-type survey
+instrument that measures moral relevance of each foundation to an
+individual and the moral judgment of various scenarios depicting each
+foundation, and 2) the Moral Foundations Dictionary (MFD) which was
+designed to capture language's role in moral reasoning and justification
+as used in speech and text (Graham et al., 2009, 2011a). The MFQ is a
+30-item scale with 15 items on the moral relevance and judgment
+scenarios. The 15 moral relevance items are equally divided among the
+five foundations and examine how relevant a condition is to making a
+moral judgment on a scale of 1 (\emph{not at all relevant}) to 6 (\emph{extremely
+relevant}). These relevance items include examples such as: ``Whether or
+not someone used violence (\emph{harm}),'' ``Whether or not someone was denied
+his or her rights (\emph{fairness}),'' ``Whether or not someone showed a lack
+of loyalty (\emph{ingroup}),'' ``Whether or not an action caused chaos or
+disorder (\emph{authority}),'' and ``Whether or not someone did something
+disgusting (\emph{purity}).'' The moral judgments items are also equally
+divided between the foundations and ask on a six-point scale how much
+one agrees with each of the statements. These judgment items include:
+``One of the worst things a person can do is hurt a defenseless animal
+(\emph{harm}),'' ``Justice is the most important requirement of a society
+(\emph{fairness}),'' ``I am proud of my country's history (\emph{ingroup}),'' ``Men
+and women each have different roles to play in society (\emph{authority}),''
+and ``Chastity is an important and valuable virtue (\emph{purity}).''
+
+The internal consistency of the MFQ from Graham et al. (2011b) was \(\alpha\) = .73
+averaged across subscales with a range of \(\alpha\) = .65-.84. Across six
+studies, the MFQ was found to have an average Cronbach's alpha of .63
+for \emph{harm}, .64 for \emph{fairness}, .56 for \emph{ingroup}, .59 for \emph{authority},
+and .71 for \emph{purity} (Federico, Weber, Ergun, \& Hunt, 2013; Graham et al., 2009; Graham, Nosek, \& Haidt, 2012; Weber \& Federico, 2013).
+Test-retest reliability was \emph{r} = .68-.82 using a sample of
+123 college students. Confirmatory factor analysis supported a
+well-fitted five-factor model (\emph{harm/care}, \emph{fairness/reciprocity},
+\emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}) over two,
+individual (\emph{harm} and \emph{fairness}) versus group (\emph{ingroup}, \emph{authority},
+and \emph{purity}) foundations, or three, autonomy (\emph{harm}, \emph{fairness}),
+community (\emph{ingroup}, \emph{authority}), and divinity (\emph{purity}) ethics,
+foundations factor model. The five-factor structure also fit for
+non-Western samples, thus, providing evidence of the MFQ
+generalizability. Convergent validity was supported with correlations on
+other measures of morality (Graham et al., 2011b).
+
+The MFD is composed of 259 words, with around 50 words assigned to each
+of the five foundations. Graham et al. (2009) created a preliminary list of words
+that they believed would be associated with the five foundations. Words
+such as \emph{war} and \emph{peace} should indicate a greater concern with \emph{harm}
+foundation whereas words such as \emph{homeland} and \emph{terrorism} should
+indicate a greater concern with the \emph{ingroup} foundation. The other
+foundation dictionaries include \emph{equal} and \emph{justice} (\emph{fairness}),
+\emph{honor} and \emph{protest} (\emph{authority}), and \emph{holy} and \emph{sin} (\emph{purity}). To
+validate the word sets, Graham et al. (2009) examined the frequency of MFD words
+in liberal and conservative sermons using the Linguistic Inquiry and
+Word Count {[}LIWC; Pennebaker, Booth, and Frances (2007){]} computer program. They found liberal
+ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than
+conservative ministers who used \emph{authority} and \emph{purity} words more
+often. Although conservative ministers were expected to use more
+\emph{ingroup} words based on political ideology and previous research, an
+examination of the way liberal ministers used \emph{ingroup} words revealed a
+tendency for the use of \emph{ingroup} words to glorify rebellion and promote
+independence (i.e., the opposite direction from \emph{ingroup} definitions).
+Effect sizes indicated relatively sizable difference between liberal and
+conservative sermons with Cohen's \emph{d} values ranging from 0.56 to 1.27.
+
+In contrast to this approach, Sagi and Dehghani (2014) explored how moral words were
+used paired with other co-occurring concepts using Latent Semantic
+Analysis (LSA). They examined three different moral issues in different
+contexts to piece out specific moral words and their collocates. First,
+they looked at how moral words were used in relation to the World Trade
+Center compared to the Empire State Building in the New York Times from
+1987-2007. After 9-11, the number of moral words associated with the
+World Trade Center increased, specifically \emph{harm} words from the MFD.
+Second, they considered the changes in how moral words were paired with
+mosque used in blogs as a response to the debate of building a mosque
+near Ground Zero following 9-11. They found words from the MFD were used
+more often with mosque during the main debate and then the co-occurrence
+decreased afterwards. Lastly, they examined moral language tied to the
+abortion debate in Congress. Republicans used more moral language
+overall; more specifically, Republicans tended to use more words
+associated with the \emph{purity} foundation; while Democrats used more words
+associated with the \emph{fairness} foundation.
+
+\subsection{Critiques of Moral Foundations}\label{critiques-of-moral-foundations}
+
+MFT has received criticism on the grounds that its assumptions regarding
+moral intuitions have little empirical basis. Suhler, Churchland, and Joseph (2011) criticized the
+content and taxonomy of the five foundations and question whether or not
+the foundations are sufficiently distinct as to stand as their own
+foundation. Likewise, Gray and Keeney (2015) argues that the measurement of the moral
+foundations confounds morality with other constructs (such as weirdness)
+and the moral foundations lack statistical and conceptual distinction.
+Schein and Gray (2015) argues that harm-based morality is the most parsimonious and
+logical explanation for MFT findings.
+
+Beyond the critiques of the theory itself, many have also provided
+strong critiques of the measurement using MFD. Conducting two close
+conceptual replication studies using religious sermons and six extension
+studies using U.S. Congressional speeches, party platforms, State of the
+Union addresses, media outlets, and political organization texts,
+Frimer (2020) found that the liberal-conservative differences found in the
+original study replicated in only 30\% of cases and the effect sizes were
+over 30 times smaller than reported in Graham et al. (2009). In a meta-analysis,
+the theorized differences were only found for authority and purity
+(e.g., conservatives used more authority and purity words). Loyalty was
+contrary to theoretical predictions (e.g., used more by liberals), and
+no differences were found for harm and fairness. Additionally,
+Frimer (2020) tested the theory under the most forgiving conditions using
+not only the original MFD but also the revised MFD2 as well using log
+transformed scores and raw scores. Even under the best circumstances
+(log transformed MFD2 scores), only two of the foundations showed
+theorized differences but with very small effects. Other studies have
+also found conflicting findings which fail to support the basic
+assertions of MFT. Exploring the political Twitterverse, Sterling and Jost (2018)
+found differences in the MFD depend on political sophistication. For
+example, harm words were used more by liberals only if they had low
+levels of political sophistication; at high levels of political
+sophistication, conservatives used more harm words. While the MFD has
+not been extensively used (at least in published research), studies
+which have use the MFD to test partisan differences have found mixed
+results in terms of supporting MFT (Clifford \& Jerit, 2013; Frimer, Tell, \& Haidt, 2015; Sagi \& Dehghani, 2014). Like Frimer (2020), we attempt to give the MFD the best chance
+for success by incorporating a weighting method to address the
+skewedness and sparsity of the linguistic data.
+
+The most successful attempts to validate a linguistic measure of moral
+foundations have used more complex methods (compared to the original
+dictionary-based approach). These attempts generally fall into two
+categories: human annotations and semantic representations. Hopp, Fisher, Cornell, Huskey, and Weber (2021)
+represents the first approach where instead of relying on `experts', a
+large sample of lay people were crowdsourced to manually annotate
+document for content relevant to each foundation. While
+resource-intensive, this method better captures how people may encounter
+and judge moral issues in everyday life leading to a more ecologically
+valid dictionary. Garten, Boghrati, Hoover, Johnson, and Dehghani (2016) represents the second categories which
+instead relies on data-driven semantic analysis. Using shallow neural
+net models like word2vec (Mikolov, Chen, Corrado, \& Dean, 2013), moral foundations
+were measured using semantic similarity vectors rather than simple word
+counts. Here, we try to augment the simpler approach to add more context
+to see if the MFD liberal-conservative differences can be replicated.
+
+First, we use the MFQ and MFD in a multi-trait multi-method approach to
+determine if the dictionary can be improved and mapped into the
+theoretical MFT traits. This study examined the measurement overlap
+between these two sources, as well as the latent traits after
+controlling for the overlap. Using the results from this study, we
+examined two conceptual replications of Frimer (2020). We test the
+liberal-conservative difference proposed by MFT using partisan media
+content and the MFD. We first test differences in a general news corpus
+compared liberal sources (National Public Radio {[}NPR{]} and the New York
+Times {[}NYT{]}) to conservative sources (Fox News and Breitbart). Second,
+we examined news about specific political events: Brett Kavanaugh's U.S.
+Supreme Court nomination and the U.S. Government Shutdown in 2018-2019.
+In the second study, the news sources were expanded to cover NYT, NPR,
+Slate, Huffington Post, and Politico on the liberal side and Fox News,
+Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the
+conservative side. To address potential issues of measurement with the
+MFD, the MFD was combined with the information produced in Study 1 and
+weighted by valence to create weighted percentages to better specify
+endorsement. Like Frimer (2020), results were judged based on the
+direction of the liberal-conservative difference compared MFT
+predictions and the size of the effect compared to past studies.
+
+\section{Study 1}\label{study-1}
+
+We approached this study with the intention to answer a method question.
+That is, this portion of the current research was conducted in order to
+solidify the best method by which to analyze political news text under
+the MFT framework while also alleviating some of the aforementioned
+potential dictionary issues with the MFD. In this set of studies, we
+examined the MFD and MFQ within the same study. The first two
+sub-studies were used to develop a (potentially) larger dictionary for
+the MFD and collect data on both scales. The original dictionary was
+developed conceptually, identifying words that \emph{should} go with each
+moral trait. In Study 1.1 and 1.2, we collect data to expand the
+dictionary. The last sub-study examined the MFD and MFQ using
+multi-trait multi-method (MTMM) analysis using guidelines from
+Byrne (2001) and Widaman (1985).
+
+\subsection{Study 1.1}\label{study-1.1}
+
+In this study, participants were given a word association task elicit
+additional semantically related word forms for each moral foundation.
+This data was used to expand the MFD for each latent area to determine
+if these additional words could improve scores and test measurement
+relation to the MFQ in Study 1.3.
+
+\subsubsection{Participants}\label{participants}
+
+466 participants were assessed from a large Midwestern
+university. Participants were given course credit for their introductory
+psychology course for completing the study. 14
+participants had missing data on the MFQ and were excluded from
+analyses. The MFQ data was screened for multivariate outliers with
+Mahalanobis distance as described in Tabachnick and Fidell (2012), and
+15 outliers were found using
+\(\chi^2_{p < .001}\)(15) = 37.70. These participants
+were excluded from further analyses, representing 437
+final participants. Participants were asked to denote their political
+party, and 25.9\%
+indicated they were Democrats,
+42.8\% were
+Republican, and
+31.1\% indicated
+they were Independent. 0.2\%
+of values were missing for this question.
+
+\subsubsection{Materials and Procedure}\label{materials-and-procedure}
+
+A complete example of the survey can be found online at
+\url{https://osf.io/6mv2g}. First, participants were given a description of
+associative memory as the relation between words that comes about
+through many pairings in writing and speech. Next, the free association
+task, similar to that used in Nelson, McEvoy, and Schreiber (2004) and De Deyne, Navarro, Perfors, Brysbaert, and Storms (2019) was described
+to the participants as listing the ``first word that pops into mind''. The
+participants were then given three example free association cues,
+\emph{lost}, \emph{old}, and \emph{article}. For each cue, participants were asked to
+write all the words that come to mind. To elicit free association to the
+moral foundation areas, participants were given the following
+instructions:
+
+``Moral Foundations Theory states that when making moral
+judgments/decisions, the concerns people have can be divided into five
+categories. Below are labels of each of these five categories. You will
+then be asked to list words you think are associated with each of the
+labels.''
+
+Each of the foundation pairs were listed together (i.e., \emph{harm/care},
+\emph{fairness/reciprocity,} etc.) with a space for participants to list
+their free association concepts. After the free association task,
+participants were then given the 15-items from the moral relevance
+section of the MFQ as described in the introduction. Last, participants
+were asked to denote their political orientation from 1 \emph{conservative}
+to 10 \emph{liberal}, as well as which political party they associated with:
+Democrat, Republican, and Independent. The survey was delivered through
+Qualtrics, and participants were recruited through the online
+participant management system for the university (SONA). Each
+participant signed an online consent form at the beginning of the study
+and was given participation credit at the end of the study.
+
+\subsubsection{Results}\label{results}
+
+All data was screening for inaccurate responses, as well as missing
+data, as described in the participant section. The final MFQ data was
+screened for assumptions of normality, linearity, and homoscedasticity.
+The MFQ data was slightly skewed but otherwise linear and homoscedastic
+after accounting for skew. No transform was applied. The sum of each
+moral foundation area was calculated in order to determine which words
+were linked to their respective moral foundation. The average scores
+were: harm (\emph{M} = 14.18, \emph{SD} =
+2.44), fairness (\emph{M} =
+14.30, \emph{SD} =
+2.59), ingroup (\emph{M} =
+12.74, \emph{SD} =
+2.92), authority (\emph{M} =
+12.05, \emph{SD} =
+3.01), and purity (\emph{M} =
+11.57, \emph{SD} =
+3.36). Participants free association
+responses were processed using the \emph{tm} (Feinerer, Hornik, \& Meyer, 2008) and \emph{corpus}
+(Perry, 2024) libraries after manual correction of spelling errors. Each
+set of answers was cleaned for punctuation, English stop words (e.g.,
+\emph{the}, \emph{an}, \emph{of}) were removed, and each word was stemmed using the
+English library in \emph{tm}. We did not combine related words in this
+section (i.e., \emph{injure} and \emph{injury}, which have different stems \emph{injur}
+and \emph{injuri}) to allow for maximum coverage of different word forms
+present in the dictionary. Additionally, with the use of automated
+stemmers like that present in the \emph{tm} library, leaving both word forms
+in the dictionary would capture more of the concepts present in future
+analyses with a different corpus without the requirement on the coder to
+manually recode all word forms. Frequency counts of the stemmed words
+were tabulated and only words mentioned with at least one percent
+frequency were used in the subsequent analyses. The complete set of word
+frequencies for each foundation can be found in our supplemental
+materials.
+
+For clarity, the processing pipeline for each separate domain was:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Manual spell checking of free association responses.
+\item
+  Word tokenization and stemming.
+\item
+  Create a term by document matrix.
+\item
+  Remove punctuation and stopwords via the \emph{tm} stopword list.
+\item
+  Calculate percent frequency across documents.
+\item
+  Remove words with less than 1\% mentions across participants.
+\end{enumerate}
+
+This procedure generated a large frequency of words for a new dictionary
+of moral foundations: harm 96, fairness
+77, ingroup 87, authority
+84, and purity 81. These
+concepts were included in the full dictionary used for Study 1.3. We
+additionally created a reduced dictionary that included only concepts
+correlated with their respective moral foundations scores. Correlations
+between word frequency and the sum of the MFQ were calculated for each
+foundation and set of concepts. Words were included in the reduced
+dictionary if their correlation was two standard deviations away from
+the mean correlation for that foundation. The reduced dataset included
+the following number of words for each foundation: harm
+4, fairness 3,
+ingroup 2, authority
+4, and purity
+1.
+
+\subsection{Study 1.2}\label{study-1.2}
+
+In this study, participants were asked to write about chemical warfare
+(wave 1), abortion, same-sex marriage, and environmentalism (wave 2).
+These prompts were designed to elicit writing about moral concepts that
+would relate to the moral foundations areas for expansion of the
+dictionary.
+
+\subsubsection{Participants}\label{participants-1}
+
+Participants were recruited in two waves as part of a larger
+investigation on priming political and religious attitudes. Participants
+were recruited via an online research system (SONA) and were given
+course credit for their participation. 463
+participants were included in the this study. The study was mostly women
+(53.9\%) and White
+(76.4\%) participants with a mix of
+minority participants: Black (6.1\%),
+(3.6\%),
+(4.2\%), Native American
+(1.9\%), Mixed
+(2.9\%) and Other
+(4.9\%). The average listed age was
+19.75 (\emph{SD} =
+2.94).
+
+\subsubsection{Materials and Procedure}\label{materials-and-procedure-1}
+
+\paragraph{Wave 1}\label{wave-1}
+
+Data was again collected via Qualtrics. Four fake new stories
+were presented to participants, which were roughly 400 words each.
+First, all news stories included a few sentences describing the use of
+chemical weapons in the Syrian civil war. The news stories were
+manipulated with political (Republican v. Democrat) and religious
+(religious v. not) quotes in a 2 x 2 between-subjects design. News
+stories can be found in the online materials. After consenting to
+participate in the study, participants were randomly shown one of the
+four new articles about Syria's use of chemical weapons. Participants
+were then asked to write for 5-10 minutes about their reaction to
+Syria's use of chemical weapons and the needed response from the United
+States. Participants also completed the 30-item version of the MFQ as
+described previously. In addition to basic demographics (gender, age),
+participant political orientation was assessed with the same scale
+described in Study 1.1.
+
+\paragraph{Wave 2}\label{wave-2}
+
+The second wave of data collection included different writing prompts
+designed to capture more of the moral foundation areas in their writing.
+The following writing prompt(s) were used, ``Please write about your
+attitudes on abortion (or same-sex marriage or environmentalism) as well
+as your reason for this stance.'' The three prompts were chosen to create
+a more varied word set by using topics that should elicit words from
+each moral foundations category by soliciting a moral response. The
+writing prompts were randomized within participant, and each participant
+completed all three prompts. Participants then completed the MFQ,
+demographics, and the political orientation scale.
+
+\subsubsection{Results}\label{results-1}
+
+Participant data was first spell checked and screening for inaccurate
+responses. Participants who did not write more than fifty words in
+response to a given prompt were excluded (\emph{n} =
+51). One missing datapoint was
+estimated using the \emph{mice} library from \emph{R} for a missing MFQ question
+(Buuren \& Groothuis-Oudshoorn, 2011), and all other missing data was present in the
+demographics sections, which were not filled in. The MFQ data were
+screened for outliers using Mahalanobis distance, and 25 outliers were
+found at \(\chi^2_{p<.001}\)(44) =
+78.75. These data were excluded leading to a final
+sample size of 387. Data were screened for assumptions
+described in Study 1.1 and were found to be satisfactory.
+
+In the first study, only free association responses were collected, but
+in this study, full writing samples were collected. Therefore, we
+expected many of the words listed to be part of creating a cohesive
+discourse, rather than only related to the moral foundation targeted. To
+find only the most related words, the correlation between word frequency
+and MFQ subscore was calculated, and words with correlations greater
+than two standard deviations outside the mean were selected for the
+dictionary analysis in Study 1.3. The sum of each MFQ subscore
+was calculated for the correlation analysis. The average scores were: harm (\emph{M} =
+13.85, \emph{SD} =
+2.79), fairness (\emph{M} =
+14.12, \emph{SD} =
+2.78), ingroup (\emph{M} =
+11.96, \emph{SD} =
+3.24), authority (\emph{M} =
+11.52, \emph{SD} =
+3.06), and purity (\emph{M} =
+11.69, \emph{SD} =
+3.61).
+
+The correlated set of words was then coded by two of the authors (EB, WP) for relevancy to the MFQ subscore and all disagreements were discussed to determine final inclusion. For
+example, for harm words in this study both \emph{also} and \emph{Syria} appeared
+as correlated words to the harm foundation. The first word does not meet
+face validity of correlation with the dictionary, and these type of
+function words or ambiguous verbs (i.e., \emph{get}, \emph{can}) were usually
+excluded. The second example is likely because of the writing prompt,
+and therefore, proper nouns were also excluded. The reduced dataset
+included the following number of words for each foundation: harm
+11, fairness
+11, ingroup
+12, authority
+17, and purity
+29.
+
+\subsection{Study 1.3}\label{study-1.3}
+
+MTMM analyses use latent variable modeling to represent the underlying
+structure of a proposed phenomenon, while also accounting for the
+measurement of that phenomenon. As shown in Figure \ref{fig:fig-mtmm},
+MTMM models are programmed to represent the traits that are measured
+(left hand side circles) and the methods used to measure those traits
+(right hand side circles). The squares in the middle represent the
+actual observed data, which is the MFQ questions and MFD scores. In the
+first model, \emph{correlated traits correlated methods}, the latent
+variables are allowed to correlate on the traits and methods side, but
+not cross correlate from traits to methods. All models are then compared
+to this model to examine fit, convergent, and divergent validity. In the
+second model, \emph{no traits correlated methods}, the trait side of the
+model is deleted and only methods are considered. The model should
+significantly degrade in fit, as the traits should be useful in
+explaining model variance for convergent validity (i.e., you do not want
+a model that suggests all the variances is due to measurement).
+
+In the third model, \emph{perfectly correlated traits freely correlated methods}, the traits are added back to the model, but each correlation
+is set to one. The fit is compared to model 1, indicating if divergent
+validity of the traits has occurred. A significant degrade in fit should
+be found to indicate that trait correlations are not perfect. Last,
+model four \emph{correlated traits uncorrelated methods}, the traits are
+allowed to naturally correlate but the methods correlations are set to
+zero. In comparison with model 1, the model should be roughly equal for
+divergent validity. This result would indicate that the methods each
+represent a different component to the measurement of the model, and do
+not represent the same measurement twice.
+
+Given the goal of improved measurement, we compared model 1 of the MTMM
+steps across several dictionaries to determine the best measurement for
+the dictionary. To assess model fit, we used the Root Mean Squared Error
+of Approximation (RMSEA, Steiger, 1990), the Root Mean Squared Residual
+(RMSR, Jöreskog, 1971), the Confirmatory Fit Index (CFI, Bentler, 1990),
+the Tucker-Lewis Index (TLI, Bentler \& Bonett, 1980). The RMSEA and RMSR should be
+low for adequate model fit (\textless{} .10) and the CFI and TLI should be high
+for adequate model fit (\textgreater{} .90). For model comparison, we used a
+\(\Delta\) CFI of greater than .01 to indicate a significant degradation
+in fit (Hu \& Bentler, 1999). We will additionally use the standardized loadings for
+each of the traits to determine which model has the best measurement of
+moral foundations (\textgreater{} .30 desired).
+
+\begin{figure}
+\includegraphics[width=6.3in]{mtmm_mfd} \caption{Representation of the multi-trait multi-method model for the MFD and MFQ.
+Not all measured variables (squares) are shown for ease of reading.
+The left hand side represents the traits or foundation areas of MFT, while the right hand side represents the two measurement tools for the MFT.
+}\label{fig:fig-mtmm}
+\end{figure}
+
+\subsubsection{Method}\label{method}
+
+\paragraph{MFD Dictionaries}\label{mfd-dictionaries}
+
+We created three versions of the MFD for separate MTMM analyses.
+The first dataset \emph{original MFD} was comprised of the original concepts from the MFD.
+We added all versions of the original words (i.e., abuse --\textgreater{} abusive, abuser, abused) to ensure all forms of the words were captured within the stemming procedure.
+These words where then stemmed using the same procedures as the data processing described for the overall study to match the data processing completed on the participant prompt responses in Study 1.2.
+The \emph{complete MFD} dataset included the original MFD concepts, all concepts listed from Study 1.1, and concepts from Study 1.2.
+The \emph{reduced MFD} dataset included all concepts from the original MFD, correlated concepts from Study 1.2, and concepts from Study 1.2 (only correlated concepts were selected in Study 1.2).
+The percent of concepts within each moral found area was calculated on the writing prompts from Study 1.2.
+The percent values were calculated on the processed data excluding all stop words.
+These values are represented as the MFD squares in Figure \ref{fig:fig-mtmm}.
+
+\paragraph{MFQ Subscore}\label{mfq-subscore}
+
+The MFQ individual questions for each participant were used from Study 1.2.
+These values are represented as the MFQ Qs squares in Figure \ref{fig:fig-mtmm}.
+The final number of participants included in this model was 387.
+
+\paragraph{Models}\label{models}
+
+For clarity, we programmed the following models:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Model 1 \emph{Correlated Traits Correlated Methods}
+
+  \begin{enumerate}
+  \def\labelenumii{\alph{enumii}.}
+  \tightlist
+  \item
+    \emph{Original} Original MFD Words
+  \item
+    \emph{Complete} Original MFD Words + Study 1.1 + Study 1.2 Words
+  \item
+    \emph{Reduced} Original MFD Words + Study 1.1 Reduced + Study 1.2 Words
+  \item
+    Determine if model suggests a feasible structure (fit indices
+    adequate + loadings adequate)
+  \item
+    Pick the best model to continue (using model comparison)
+  \end{enumerate}
+\item
+  Model 2 \emph{No Traits Correlated Methods}
+\item
+  Model 3 \emph{Perfectly Correlated Traits Correlated Methods}
+\item
+  Model 4 \emph{Correlated Traits Uncorrelated Methods}
+\end{enumerate}
+
+\subsubsection{Results}\label{results-2}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tab-mtmm}Mean Percent Scores and MFQ Scores for Foundation Areas}
+
+\footnotesize{
+
+\begin{tabular}{llcc}
+\toprule
+Foundation Area & Dictionary/MFQ & M & SD\\
+\midrule
+Authority & MFQ & 11.52 & 3.06\\
+Authority & Original & 0.37 & 0.62\\
+Authority & Complete & 3.88 & 2.12\\
+Authority & Reduced & 0.98 & 1.06\\
+Fair & MFQ & 14.12 & 2.78\\
+Fair & Original & 1.05 & 0.95\\
+Fair & Complete & 4.94 & 2.37\\
+Fair & Reduced & 3.16 & 1.85\\
+Harm & MFQ & 13.85 & 2.79\\
+Harm & Original & 1.13 & 1.21\\
+Harm & Complete & 7.17 & 3.05\\
+Harm & Reduced & 3.97 & 2.24\\
+Ingroup & MFQ & 11.96 & 3.24\\
+Ingroup & Original & 0.97 & 1.40\\
+Ingroup & Complete & 5.12 & 2.63\\
+Ingroup & Reduced & 1.69 & 1.67\\
+Purity & MFQ & 11.69 & 3.61\\
+Purity & Original & 0.73 & 0.82\\
+Purity & Complete & 3.92 & 2.20\\
+Purity & Reduced & 1.94 & 1.46\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Mean percents for dictionaries, mean total subscores for the MFQ.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Table \ref{tab:tab-mtmm} indicates the average percents found for each dictionary within each moral foundation area.
+The original MFD shows the lowest percentage of moral words for each foundation area, while the complete and reduced dataset show increases in the percent of text that would be considered moral words.
+
+\paragraph{Model 1}\label{model-1}
+
+Fit indices from the MTMM Model 1 step are shown in Table \ref{tab:mtmm-model1-table}.
+The complete parameter estimates from these models are saved online for full inspection due to their length.
+The fit indices from these models indicate that all models showed good fit.
+The original and complete MFD models showed equal fit (\(\Delta\) CFA \textless= .01), and both models were better than the reduced MFD model.
+We then inspected the loadings to determine the adequacy of the loadings for the MFQ and MFD.
+These results are shown in Table \ref{tab:mtmm-model1-table2}.
+All but one question for the MFQ load adequately (\textgreater.30) on each of their moral foundation areas.
+None of the MFD areas load onto their moral foundation area, as all loadings are close to zero (and non-significant, see online).
+The excellent model fit was likely due to the structure of the MFQ, as the MFD results do not show relation to their foundation area.
+We did not run further models, as the goal was to show that Model 1 was the best model with appropriate loadings for foundations.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:mtmm-model1-table}MTMM Fit Indices for Model 1 MTMM}
+
+\footnotesize{
+
+\begin{tabular}{llccllcc}
+\toprule
+Model & Chi-Sq & df & RMSEA & SRMR & CFI & TLI & AIC\\
+\midrule
+Original & 204.40 & 71.00 & 0.03 & 0.04 & 0.98 & 0.97 & 21,575.55\\
+Complete & 239.09 & 71.00 & 0.04 & 0.04 & 0.97 & 0.96 & 24,868.17\\
+Reduced & 283.10 & 71.00 & 0.05 & 0.05 & 0.95 & 0.94 & 23,380.58\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:mtmm-model1-table2}MTMM Fit Estimates for Model 1 Loadings}
+
+\footnotesize{
+
+\begin{tabular}{llccl}
+\toprule
+Latent Variable & Measured Variable & Original & All & Reduced\\
+\midrule
+Harm & 1 & 0.61 & 0.61 & 0.61\\
+Harm & 2 & 0.70 & 0.69 & 0.69\\
+Harm & 3 & 0.38 & 0.37 & 0.36\\
+Harm & MFD & -0.05 & -0.03 & -0.05\\
+Fair & 1 & 0.76 & 0.76 & 0.77\\
+Fair & 2 & 0.52 & 0.50 & 0.50\\
+Fair & 3 & 0.23 & 0.22 & 0.22\\
+Fair & MFD & -0.01 & 0.10 & 0.05\\
+Ingroup & 1 & 0.63 & 0.63 & 0.63\\
+Ingroup & 2 & 0.73 & 0.72 & 0.73\\
+Ingroup & 3 & 0.82 & 0.81 & 0.81\\
+Ingroup & MFD & -0.10 & 0.03 & 0.05\\
+Authority & 1 & 0.81 & 0.80 & 0.81\\
+Authority & 2 & 0.72 & 0.72 & 0.72\\
+Authority & 3 & 0.42 & 0.41 & 0.41\\
+Authority & MFD & 0.06 & 0.00 & -0.04\\
+Purity & 1 & 0.71 & 0.71 & 0.71\\
+Purity & 2 & 0.67 & 0.67 & 0.67\\
+Purity & 3 & 0.64 & 0.64 & 0.64\\
+Purity & MFD & 0.06 & -0.05 & -0.11\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Estimates are completely standardized loadings from the model.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\subsection{Discussion}\label{discussion}
+
+Study 1 was designed to investigate if the original MFD could be improved with additional concepts.
+As shown in Table \ref{tab:tab-mtmm}, the original MFD is often heavily skewed toward zero with very low percentages of moral words used in text.
+These results were found even when writing about concepts that should theoretically active moral values.
+The suggested improvements did increase percentages of included words; however, the results from the MTMM indicate that the MFD does not appear to relate to the MFQ moral foundations.
+In a separate set of studies, we examined if the original MFD proposed results for liberal and conservative values could be found within new sources (Sagi \& Dehghani, 2014).
+Further, we examined if the MFD could be improved with markers of valence (i.e., positive, negative), rather than just inclusion of more words.
+
+\section{Study 2}\label{study-2}
+
+\subsection{Method}\label{method-1}
+
+We hypothesized the news sources generally perceived as liberal leaning
+(\emph{NPR} and \emph{The New York Times}) would contain MFD words and valences
+indicating endorsements of the individualizing moral foundations
+(\emph{harm/care} and \emph{fairness/reciprocity}). Additionally, we hypothesized
+the two sources generally perceived to be conservative leaning (\emph{Fox News}
+and \emph{Breitbart}) would feature MFD words and valences indicating
+equal endorsement of all five foundations.
+
+\subsubsection{Sources}\label{sources}
 
 Political articles were collected from the websites of four notable U.S.
-news sources, a process known as web scraping.
-The sources were \emph{NYT}, \emph{NPR}, \emph{Fox News}, and \emph{Breitbart}.
-They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others.
-We determined the political lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating the self-reported ideological consistency represented by the consumers of several news sources.
-In general, the \emph{NYT} and \emph{NPR} are preferred by consumers reporting a liberal bias or lean.
-In contrast, \emph{Fox News} and \emph{Breitbart} are believed to have a conservative bias or lean.
-Mitchell et al.
-(2014)'s article presented political ideology as a scale ranging from ``consistently liberal'' to ``consistently conservative.'' In between these extremes lie more moderate positions, including ``mostly liberal,'' ``mixed,'' and ``mostly conservative.'' Owing to the lower number of sources analyzed herein, we elected to categorize the sources as either ``liberal'' and ``conservative'' in order to form a basis for comparison.
-At the time of our data collection, these sources were also selected because they were open (i.e., no subscription required to access articles), and their websites were designed in a way that made webscraping possible.
-
-Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the \emph{R} script.
-For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained.
-All code for this manuscript can be found at \url{https://osf.io/5kpj7/}, and the scripts are provided inline with this manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
-
-Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured.
-While in the multi-week process of scraping articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not growing at a similar pace as those from the \emph{NYT} and \emph{Breitbart}.
-Upon investigation, we found another, more robust URL for political content from NPR: their politics content ``archive.'' The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time.
-Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published.
-We later ran a process in order to exclude any duplicate articles.
-\emph{Fox News} presented a similar issue.
-We discovered \emph{Fox News} utilized six URLs in addition to the regular politics page.
-These URLs led to pages containing content pertaining the U.S.
-Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections.
-Once again, duplicates were subsequently eliminated from any analyses.
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset (Wickham, 2016).
-Using this dataset, we identified word count and average word count per source.
-This process was completed once daily starting in February 2018 until March 2018.
-Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening.
-Data collection was terminated once 250,000 words per source was collected in April 2018.
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-Once data collection ended, the text was scanned using the \emph{ngram} package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017).
-This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites.
-At this point, duplicate articles were discarded.
-
-The article text was processed using the \emph{tm} and \emph{ngram} packages in \emph{R} in order to render the text in lowercase, remove punctuation, and fix spacing issues (Feinerer \& Hornik, 2017).
-The individual words were then reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}).
-The same procedure was applied to the MFD words and the words in the Warriner, Kuperman, and Brysbaert (2013) dataset.
-Using the Warriner et al.
-(2013) dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.
-
-Concurrent research by Jordan, Buchanan, and Padfield (2019) assesses the validity of both the MFQ and the MFD through a multi-trait multi-method analysis of the two instruments using multiple samples.
-The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation.
-We were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD.
-Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).
-
-A complete list of the words for each moral foundation area was created from previous experiments.
-The total number of times each of those words was used in an article was calculated.
-This information was merged with the valence values from the Warriner et al.
-(2013) dataset.
-A weighted score was calculated by multiplying the frequency of occurrence within a document times the \emph{z}-scored valence values and divided by the word count for that article.
-The final score was multiplied by 100 to represented a weighted percentage.
-Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article.
-Valences were \emph{z}-scored in order to eliminate any ambiguity regarding the direction of the valence.
-Positive values indicate positive valence, and negative values indicate negative valence.
-Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.
-See Table \ref{tab:example-weight} for an example.
+news sources, a process known as web scraping. The sources were \emph{NYT},
+\emph{NPR}, \emph{Fox News}, and \emph{Breitbart}. They were selected for their
+widespread recognition and the fact political partisans have strong
+preferences for some sources over others. We determined the political
+lean of each source by referencing Mitchell, Matsa, Gottfried, and Kiley (2014)'s article demonstrating
+the self-reported ideological consistency represented by the consumers
+of several news sources. In general, the \emph{NYT} and \emph{NPR} are preferred
+by consumers reporting a liberal bias or lean. In contrast, \emph{Fox News}
+and \emph{Breitbart} are believed to have a conservative bias or lean.
+Mitchell et al. (2014)'s article presented political ideology as a scale ranging
+from ``consistently liberal'' to ``consistently conservative.'' In between
+these extremes lie more moderate positions, including ``mostly liberal,''
+``mixed,'' and ``mostly conservative.'' Owing to the lower number of sources
+analyzed herein, we elected to categorize the sources as either
+``liberal'' and ``conservative'' in order to form a basis for comparison. At
+the time of our data collection, these sources were also selected
+because they were open (i.e., no subscription required to access
+articles), and their websites were designed in a way that made
+webscraping possible.
+
+Political articles in particular were identified and subsequently
+scraped by including the specific URL directing to each source's
+political content in the \emph{R} script. For example, rather than scrape
+from nytimes.com, which would return undesired results (non-political
+features, reviews, etc.), we instead included
+nytimes.com/section/politics so that more or less exclusively political
+content was obtained. All code for this manuscript can be found at
+\url{https://osf.io/5kpj7/}, and the scripts are provided inline with this
+manuscript written with the \emph{papaja} library (Aust \& Barth, 2017).
+
+Identification of the sources' political URLs presented a problem for
+two of the sources owing to complications with how their particular
+sites were structured. While in the multi-week process of scraping
+articles, we noticed word counts for \emph{NPR} and \emph{Fox News} were not
+growing at a similar pace as those from the \emph{NYT} and \emph{Breitbart}. Upon
+investigation, we found another, more robust URL for political content
+from NPR: their politics content ``archive.'' The page structure on NPR's
+website was such that only a limited selection of articles is displayed
+to the user at a given time. Scraping both the archive and the normal
+politics page ensured we were obtaining most (if not all) new articles
+as they were published. We later ran a process in order to exclude any
+duplicate articles. \emph{Fox News} presented a similar issue. We discovered
+\emph{Fox News} utilized six URLs in addition to the regular politics page.
+These URLs led to pages containing content pertaining the U.S. Executive
+Branch, Senate, House of Representatives, Judicial Branch, foreign
+policy, and elections. Once again, duplicates were subsequently
+eliminated from any analyses.
+
+\subsubsection{Materials}\label{materials}
+
+Using the \emph{rvest} library in the statistical package \emph{R}, we pulled body
+text for individual articles from each of the aforementioned sources
+(identified using CSS language) and compiled them into a dataset
+(Wickham, 2016). Using this dataset, we identified word count and average
+word count per source. This process was completed once daily starting in
+February 2018 until March 2018. Starting in mid-March 2018, the process
+was completed twice daily - once in the morning and again in the
+evening. Data collection was terminated once 250,000 words per source
+was collected in April 2018.
+
+\subsubsection{Data analysis}\label{data-analysis}
+
+Once data collection ended, the text was scanned using the \emph{ngram}
+package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017). This package includes a word count
+function, which was used to remove articles that came through as blank
+text, as well as to eliminate text picked up from the Disqus commenting
+system used by certain websites. At this point, duplicate articles were
+discarded.
+
+The article text was processed using the \emph{tm} and \emph{ngram} packages in
+\emph{R} in order to render the text in lowercase, remove punctuation, and
+fix spacing issues (Feinerer \& Hornik, 2017). The individual words were then
+reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}). The same
+procedure was applied to the MFD words and the words in the
+Warriner, Kuperman, and Brysbaert (2013) dataset. Using the Warriner et al. (2013) dictionary, the words
+making up each of the five foundations in the MFD were matched to their
+respective valence value.
+
+The Warriner et al. (2013) data includes nearly 14,000 English lemmas that have
+been rated for their valence, arousal, and dominance (mirroring Bradley \& Lang, 1999). Word emotion ratings have been used to estimate the
+sentiment of a text - a very popular task within classification
+research - by generally averaging the valence scores of the the words
+matched between the text and the available norms (Leveau, Jhean-Larose, Denhière, \& Nguyen, 2012). Other
+suggestions include the simple summation of word's positive or negative
+valence from a text or respective weighting based on word frequency
+(Hutto, 2021; Loria, 2020). In each of these cases, an overall polarity is
+desired, which is the case here, creating an overall score for each of
+the five MFD domains. Sentiment coding packages often score items from
+-1 to 1 or other values around zero wherein negative scores represent
+negative sentiment, while positive scores represent positive sentiment.
+The Warriner et al. (2013) dataset ranges from 1 (\emph{unhappy}) to 9 (\emph{happy}).
+Thus, to ensure that we anchored their valences around zero, we
+\emph{z}-scored the dataset so that negative scores represented values below
+the average sentiment and positive scores represented values above the
+average sentiment.
+
+Given the results from Study 1.3, we used the original MFD to calculate
+the number of words included for each moral foundation area. We could
+also suggest using the larger complete dataset, given that the CFI indicated
+similar models, and we note here that the pattern of results do not change
+if that dictionary is used instead. The total number of times each of those words
+was used in an article was calculated. This information was merged with
+the valence values from the Warriner et al. (2013) dataset. A weighted score was
+calculated by multiplying the frequency of occurrence within a document
+times the \emph{z}-scored valence values and divided by the word count for
+that article. The final score was multiplied by 100 to represented a
+weighted percentage. Finally, the weighted scores were summed within in
+each article to get a total weighted percentage of the use of moral area
+specific words by article. Valences were \emph{z}-scored in order to
+eliminate any ambiguity regarding the direction of the valence. Positive
+values indicate positive valence, and negative values indicate negative
+valence. Words were categorized in accordance to their MFD affiliation,
+creating a weighted sum for each moral foundation. See Table
+\ref{tab:example-weight} for an example.
 
@@
 \midrule
-Breitbart & abus & 14.00 & 846 & -2.77 & -4.59\\
+Breitbart & defend & 4.00 & 341 & 0.97 & 1.14\\
+NPR & protect & 11.00 & 1550 & 1.39 & 0.98\\
+NPR & fight & 7.00 & 10740 & -1.20 & -0.08\\
+NPR & violenc & 11.00 & 1419 & -1.85 & -1.43\\
+Breitbart & safe & 4.00 & 1108 & 2.07 & 0.75\\
+Breitbart & sympathet & 1.00 & 1632 & 1.26 & 0.08\\
+Breitbart & benefit & 6.00 & 1774 & 1.42 & 0.48\\
+NY Times & care & 19.00 & 4422 & 2.02 & 0.87\\
+NY Times & harm & 4.00 & 1100 & -2.47 & -0.90\\
+Breitbart & damag & 4.00 & 1624 & -1.63 & -0.40\\
+Breitbart & preserv & 2.00 & 254 & 1.27 & 1.00\\
+NY Times & destroy & 5.00 & 1494 & -1.88 & -0.63\\
+NY Times & spurn & 1.00 & 1508 & NA & NA\\
 Breitbart & cruel & 2.00 & 574 & -1.83 & -0.64\\
-NY Times & unit & 19.00 & 1341 & 0.18 & 0.25\\
-Breitbart & first & 18.00 & 1135 & 1.78 & 2.82\\
-Fox News & comfort & 12.00 & 1053 & 1.71 & 1.95\\
-NPR & attent & 6.00 & 1336 & 1.27 & 0.57\\
-Breitbart & bruis & 3.00 & 290 & -1.43 & -1.48\\
-Breitbart & accid & 3.00 & 196 & -1.97 & -3.02\\
-Breitbart & cut & 11.00 & 1036 & -0.91 & -0.97\\
-Breitbart & child & 8.00 & 622 & 1.68 & 2.16\\
-NPR & injuri & 4.00 & 968 & -2.15 & -0.89\\
-NY Times & drug & 32.00 & 1004 & -0.75 & -2.38\\
-Breitbart & beat & 5.00 & 298 & -0.54 & -0.90\\
-Fox News & weapon & 17.00 & 1175 & -0.87 & -1.26\\
-Breitbart & speci & 3.00 & 390 & 0.15 & 0.12\\
+Breitbart & violent & 6.00 & 1211 & -2.20 & -1.09\\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} }
+\normalsize{\textit{Note.} Concepts were stemmed to match datasets.}
 \end{tablenotes}
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{descriptive-statistics}{%
-\subsection{Descriptive Statistics}\label{descriptive-statistics}}
-
-We calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English.
-Statistics calculated included average \emph{z}-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source.
-Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula (Kincaid, Fishburne, Robert P., Richard L., \& Brad S., 1975).
-Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty.
-The obtained value is intended to match up with the U.S.
-grade level at which one should be able to comfortably read the passage (Kincaid et al., 1975).
-For example, a text with a readability score of 11 should be easily read by a U.S.
-high school junior.
-
-As seen in Table \ref{tab:exp1-source-descriptives}, the sources are similar in some aspects yet different in others.
-Valence appears to be slightly positive across all sources.
-The large standard deviations seem to indicate little to no presence of a difference in valence across sources.
-\emph{NYT} published the greatest number of articles as well as total words.
-\emph{Breitbart} featured the lowest number of articles, and \emph{NPR} the lowest number of total words from all articles.
-Per individual article, however, \emph{Breitbart} appears to feature the highest average number of words as well as unique words.
-Once again the standard deviations call into question any apparent differences between sources.
-Finally, \emph{Fox News} articles had the lowest reading grade level on average, while \emph{NYT} had the highest.
-This result might be attributable to the greater number of tokens in the average \emph{NYT} article compared to \emph{Fox News}.
-The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level.
-Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.
+\subsection{Results}\label{results-3}
+
+To analyze if news sources adhered to differences in word use based on
+their target audience, we utilized a multilevel model (MLM) to analyze
+the data. MLM is a regression technique that allows one to control for
+the repeated measurement and nested structured of the data, which
+creates correlated error (Gelman, 2006). Using the \emph{nlme} library in \emph{R}
+(Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated
+here by the political lean of the news source, using the individual news
+sources as a random intercept to control for the structure of the data.
+Therefore, the models were calculated by: Weighted Score \textasciitilde{} Political
+Lean + (\textasciitilde1\textbar Source).
+
+The multilevel model did not indicate the presence of any significant or
+practical effect of political lean for any of the five moral
+foundations. The strongest effect size was observed for the
+\emph{authority/respect} foundation, but the effect was in the opposite
+direction from what was originally hypothesized - liberal sources tended
+to use more \emph{authority/respect} words than did conservative sources.
+Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's
+\emph{d}) can be found in Table \ref{tab:exp1-table}. To interpret the
+weighted scores, one can examine the mean and standard deviations for
+each. A zero score for the mean, with a non-zero standard deviation,
+would indicate a perfect balance of positive and negative words in each
+category, likely representing a neutral tone when all words are
+considered. Negative percentages would indicate more representation of
+the negative words in the MFD area, while positive percentages indicate
+an endorsement of the positive words in a MFD. Therefore, we suggest
+using the sign of the mean score to determine the directionality of the
+endorsement for the MFD (positive, neutral, negative), and the standard
+deviation to ensure that a zero score is not zero endorsement (i.e., a
+SD of zero indicates no words were used). Based on the weighted percent
+values for the five foundations, we observed that MFD words seem to make
+up a small portion of the article text. Furthermore, the observed
+percentages and means appear to indicate a generally positive
+endorsement of all five foundations across both liberal and conservative
+sources.
 
@@
 
-\caption{\label{tab:exp1-source-descriptives}Study 1 - Descriptive Statistics by Source}
+\caption{\label{tab:exp1-table}Study 2 Results - Multilevel Model}
 
@@
 
-\begin{tabular}{lcccccccccc}
+\begin{tabular}{lccccccclc}
 \toprule
-Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
 \midrule
-NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.28 & 14.00 & 3.93\\
-New York Times & 0.30 & 0.13 & 406 & 452579 & 1114.73 & 511.86 & 454.27 & 154.58 & 16.44 & 3.36\\
-Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.35 & 120.75 & 18.57 & 7.89\\
-Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.56 & 189.00 & 17.25 & 7.21\\
+Valence & Harm/Care & -0.49 & 1.26 & -0.44 & 1.26 & 0.50 & .668 & -0.04 & .001\\
+Valence & Fairness/Reciprocity & 0.47 & 0.64 & 0.44 & 0.64 & -1.23 & .344 & 0.05 & < .001\\
+Valence & Ingroup/Loyalty & 0.39 & 0.49 & 0.38 & 0.49 & -0.58 & .620 & 0.02 & < .001\\
+Valence & Authority/Respect & 0.09 & 0.49 & 0.07 & 0.49 & -1.25 & .338 & 0.05 & < .001\\
+Valence & Purity/Sanctity & 0.19 & 0.53 & 0.13 & 0.53 & -2.77 & .109 & 0.10 & .001\\
+Original & Harm/Care & 0.55 & 0.60 & 0.50 & 0.60 & -1.84 & .207 & 0.07 & < .001\\
+Original & Fairness/Reciprocity & 0.46 & 0.49 & 0.41 & 0.49 & -2.57 & .124 & 0.10 & .003\\
+Original & Ingroup/Loyalty & 0.63 & 0.64 & 0.68 & 0.64 & 1.83 & .208 & -0.07 & .002\\
+Original & Authority/Respect & 0.67 & 0.70 & 0.60 & 0.70 & -2.28 & .150 & 0.09 & < .001\\
+Original & Purity/Sanctity & 0.17 & 0.32 & 0.11 & 0.32 & -3.78 & .064 & 0.20 & .009\\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
 \end{tablenotes}
@@
 
-\hypertarget{inferential-statistics}{%
-\subsection{Inferential Statistics}\label{inferential-statistics}}
-
-To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data.
-MLM is a regression technique that allows one to control for the repeated measurement and nested structured of the data, which creates correlated error (Gelman, 2006).
-Using the \emph{nlme} library in \emph{R} (Pinheiro, Bates, Debroy, Sarkar, \& Team, 2017), each foundation's weighted percentage was predicated here by the political lean of the news source, using the individual news sources as a random intercept to control for the structure of the data.
-Therefore, the models were calculated by: Weighted Score \textasciitilde{} Political Lean + (\textasciitilde1\textbar Source).
-
-The multilevel model did not indicate the presence of any significant or practical effect of political lean for any of the five moral foundations.
-The strongest effect size was observed for the \emph{authority/respect} foundation, but the effect was in the opposite direction from what was originally hypothesized - liberal sources tended to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp1-table}.
-To interpret the weighted scores, one can examine the mean and standard deviations for each.
-A zero score for the mean, with a non-zero standard deviation, would indicate a perfect balance of positive and negative words in each category, likely representing a neutral tone when all words are considered.
-Negative percentages would indicate more representation of the negative words in the MFD area, while positive percentages indicate an endorsement of the positive words in a MFD.
-Therefore, we suggest using the sign of the mean score to determine the directionality of the endorsement for the MFD (positive, neutral, negative), and the standard deviation to ensure that a zero score is not zero endorsement (i.e., a SD of zero indicates no words were used).
-Based on the weighted percent values for the five foundations, we observed that MFD words seem to make up a small portion of the article text.
-Furthermore, the observed percentages and means appear to indicate a generally positive endorsement of all five foundations across both liberal and conservative sources.
+\subsection{Discussion}\label{discussion-1}
+
+The results obtained in Study 2 fail to support the differences
+predicted by MFT. First, differences between liberal and conservative
+news sources failed to reach statistical or practical (effect size)
+significance for any foundations. Second, looking purely at the
+direction of the differences, the results run completely contrary to the
+differences expected by MFT. Conservative sources scored higher on
+concern for harm and fairness while liberal sources scored higher on
+concern for loyalty, authority, and purity. Overall, the results lend
+strong support to the case against the MFD and weakens the case
+generally for MFT.
+
+However, one possible limitation of the current data is the generalness
+of the corpus. The selection of the broad and amorphous topic of
+``political news'' may have led to the scraping of large numbers of
+articles with little to no moral-centric content. To address this
+limitation, two changes that were subsequently employed in Study 3.
+First, we elected to include more news sources for web scraping and
+analysis in addition to the four used in Study 2. Second, we chose to
+focus data collection efforts on two heavily moralized events in the
+Trump administration: (1) the nomination and confirmation of Justice
+Brett Kavanaugh to the U.S. Supreme Court and the U.S. government
+shutdown in December 2018 through January 2019 over disagreements about
+funding a U.S.-Mexico border wall. Hence, Study 3 is the best test of
+the MFT and the MFD in the context of partisan news.
+
+\section{Study 3}\label{study-3}
+
+\subsection{Method}\label{method-2}
+
+In contrast to Study 2, we approached Study 3 with the intention to
+confirm the method employed was valid for the analysis of the scraped
+text as well as for any inferences drawn from the analyses. For the
+second study, we hypothesized that news sources perceived as liberal
+will exhibit positive endorsements of the individualizing moral
+foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles
+reporting on both the Kavanaugh confirmation hearing as well as the
+2018-2019 government shutdown. News sources perceived as conservative
+are hypothesized to positively endorse all five foundations equally in
+their coverage of the Kavanaugh hearing and the government shutdown. We
+tested the hypothesis by analyzing the content scraped from news
+sources' web pages spanning the two weeks before (September 13, 2018)
+and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing,
+owing to its prominence in the news. Likewise, we analyzed content
+spanning two weeks before the start of the government shutdown (December
+8, 2018) to two weeks following the end of the shutdown (February 8,
+2019). The content will be analyzed for valence and moral alignment
+under MFT.
+
+\subsubsection{Sources}\label{sources-1}
+
+Articles pertaining to the Brett Kavanaugh Supreme Court confirmation
+hearing and the 2018-2019 U.S. Government shutdown were scraped from the
+websites of 10 U.S. news sources. As in Study 2, these sources were
+selected owing to their favorability among political partisans according
+to Mitchell et al. (2014). The sources favored by the highest proportion of
+consistent liberals were the \emph{NYT}, \emph{NPR}, \emph{Slate}, \emph{Huffington Post},
+and \emph{Politico} (Mitchell et al., 2014). The sources favored by the highest
+proportion of consistent conservatives included \emph{Fox News}, \emph{Breitbart},
+\emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}. These sources
+were primarily selected due to their political lean but also due to our
+ability to webscrape their contents without a subscription based
+service. Political articles referencing Brett Kavanaugh's nomination
+process were identified and subsequently scraped by including the URL
+for each source's coverage of the nomination in the \emph{R} script.
+
+\subsubsection{Materials}\label{materials-1}
+
+Using the \emph{rvest} and \emph{RSelenium} libraries, we pulled body text for
+individual articles from each of the aforementioned 10 news sources and
+compiled them together (Harrison \& Kim, 2020; Wickham, 2016). Using
+this dataset, we identified word count and average word count per
+source. This process was run for articles pertaining to Kavanaugh's
+nomination that were published between September 13, 2018 and October
+11, 2018 inclusive. This date range was selected in reference to the
+widely-publicized and viewed nomination hearing on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and
+the end date at October 11 (two weeks after the hearing) so that we
+could capture a large amount of data (roughly one month) during which
+Kavanaughnaugh's nomination was at its peak saturation in news coverage.
+
+The same process was followed for scraping articles related to the
+partial U.S. Government shutdown of 2018-2019. The articles scraped were
+published between December 8, 2018 and February 8, 2019 inclusive. Once
+again, we elected to scrape articles published two weeks before and
+after the event in question in order to capitalize on the shutdown's
+saturation in American news media.
+
+\subsubsection{Data analysis}\label{data-analysis-1}
+
+As in Study 1 and 2, the text was scanned with \emph{ngram} (Schmidt et al., 2017). Again,
+blank articles, text from the Disqus system, and duplicate articles were
+removed. The text was processed and stemmed in order to convert to a
+usable form for further analysis (Feinerer \& Hornik, 2017). Each individual word
+was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}). Once
+again, the same procedure was applied to the MFD words and the words in
+the Warriner et al. (2013) dataset. We obtained the words' percent occurrence in
+the text. Percents were multiplied by \emph{z}-scored valence and categorized
+into their proper MFD category.
+
+\subsection{Results}\label{results-4}
+
+We utilized a multilevel model (MLM) to analyze if news sources
+leveraged different vocabularies based on target audience in the same
+manner as Study 2. Each foundation's weighted percentage was predicted
+by the source's political lean, using the individual source as a random
+intercept to control for the nested data structure. Two separate MLMs
+were constructed from datasets compiled for each topic of interest: the
+Kavanaugh hearing and the partial government shutdown of 2018-2019.
+
+For the Kavanaugh topic, the multilevel model indicated the presence of
+a statistically significant effect for \emph{harm/care}, but the practical
+effect denoted by Cohen's \emph{d} was found to be small. There were no other
+significant or practical effects of political lean for any of the other
+four moral foundations. The effect for \emph{harm/care} was in the
+hypothesized direction with liberal sources tending to use more
+positively \emph{harm/care} words than conservative sources. Descriptive and
+test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found
+in Table \ref{tab:exp2-tablekav}.
 
@@
 
-\caption{\label{tab:exp1-table}Study 1 Results - Multilevel Model}
+\caption{\label{tab:exp2-tablekav}Kavanaugh Results - Multilevel Model}
 
@@
 
-\begin{tabular}{lcccccccl}
+\begin{tabular}{llcccccccl}
 \toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
+Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
 \midrule
-Harm/Care & 0.50 & 2.21 & 0.49 & 2.21 & -0.21 & .851 & 0.01 & .851\\
-Fairness/Reciprocity & 1.13 & 1.38 & 1.11 & 1.38 & -0.42 & .713 & 0.02 & .713\\
-Ingroup/Loyalty & 1.28 & 1.63 & 1.34 & 1.63 & 0.30 & .793 & -0.04 & .793\\
-Authority/Respect & 0.72 & 1.62 & 1.06 & 1.62 & 3.16 & .087 & -0.20 & .087\\
-Purity/Sanctity & 1.11 & 1.48 & 1.27 & 1.48 & 2.38 & .140 & -0.09 & .140\\
+Valence & Harm/Care & -0.35 & 0.69 & -0.32 & 0.69 & 0.58 & .575 & -0.04 & .013\\
+Valence & Fairness/Reciprocity & 0.91 & 0.74 & 0.60 & 0.74 & -2.68 & .028 & 0.42 & .095\\
+Valence & Ingroup/Loyalty & 0.24 & 0.31 & 0.25 & 0.31 & 0.31 & .764 & -0.03 & .004\\
+Valence & Authority/Respect & 0.04 & 0.32 & 0.06 & 0.32 & 1.08 & .313 & -0.06 & .003\\
+Valence & Purity/Sanctity & 0.36 & 0.51 & 0.16 & 0.51 & -1.75 & .118 & 0.47 & .133\\
+Original & Harm/Care & 0.33 & 0.36 & 0.35 & 0.36 & 0.60 & .567 & -0.04 & .010\\
+Original & Fairness/Reciprocity & 0.77 & 0.57 & 0.54 & 0.57 & -2.84 & .022 & 0.40 & .142\\
+Original & Ingroup/Loyalty & 0.34 & 0.37 & 0.37 & 0.37 & 0.35 & .733 & -0.06 & .010\\
+Original & Authority/Respect & 0.43 & 0.49 & 0.46 & 0.49 & 1.20 & .266 & -0.04 & .004\\
+Original & Purity/Sanctity & 0.28 & 0.31 & 0.15 & 0.31 & -2.44 & .040 & 0.49 & .126\\
 \bottomrule
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The results obtained in Study 1 fail to support the differences predicted by MFT.
-First, differences between liberal and conservative news sources failed to reach statistical or practical (effect size) significance for any foundations.
-Second, looking purely at the direction of the differences, the results run completely contrary to the differences expected by MFT.
-Conservative sources scored higher on concern for harm and fairness while liberal sources scored higher on concern for loyalty, authority, and purity.
-Overall, the results lend strong support to the case against the MFD and weakens the case generally for MFT.
-
-However, one possible limitation of the current data is the generalness of the corpus.
-The selection of the broad and amorphous topic of ``political news'' may have led to the scraping of large numbers of articles with little to no moral-centric content.
-To address this limitation, two changes that were subsequently employed in Study 2.
-First, we elected to include more news sources for web scraping and analysis in addition to the four used in Study 1.
-Second, we chose to focus data collection efforts on two heavily moralized events in the Trump administration: (1) the nomination and confirmation of Justice Brett Kavanaugh to the U.S.
-Supreme Court and the U.S.
-government shutdown in December 2018 through January 2019 over disagreements about funding a U.S.-Mexico border wall.
-Hence, Study 2 is the best test of the MFT and the MFD in the context of partisan news.
-
-\hypertarget{study-2}{%
-\section{Study 2}\label{study-2}}
-
-\hypertarget{method-1}{%
-\section{Method}\label{method-1}}
-
-In contrast to Study 1, we approached Study 2 with the intention to confirm the method employed was valid for the analysis of the scraped text as well as for any inferences drawn from the analyses.
-For the second study, we hypothesized that news sources perceived as liberal will exhibit positive endorsements of the individualizing moral foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles reporting on both the Kavanaugh confirmation hearing as well as the 2018-2019 government shutdown.
-News sources perceived as conservative are hypothesized to positively endorse all five foundations equally in their coverage of the Kavanaugh hearing and the government shutdown.
-We tested the hypothesis by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
-Likewise, we analyzed content spanning two weeks before the start of the government shutdown (December 8, 2018) to two weeks following the end of the shutdown (February 8, 2019).
-The content will be analyzed for valence and moral alignment under MFT.
-
-\hypertarget{sources-1}{%
-\subsection{Sources}\label{sources-1}}
-
-Articles pertaining to the Brett Kavanaugh Supreme Court confirmation hearing and the 2018-2019 U.S.
-Government shutdown were scraped from the websites of 10 U.S.
-news sources.
-As in Study 1, these sources were selected owing to their favorability among political partisans according to Mitchell et al.
-(2014).
-The sources favored by the highest proportion of consistent liberals were the \emph{NYT}, \emph{NPR}, \emph{Slate}, \emph{Huffington Post}, and \emph{Politico} (Mitchell et al., 2014).
-The sources favored by the highest proportion of consistent conservatives included \emph{Fox News}, \emph{Breitbart}, \emph{The Rush Limbaugh Show}, \emph{The Blaze}, and \emph{Sean Hannity}.
-These sources were primarily selected due to their political lean but also due to our ability to webscrape their contents without a subscription based service.
-Political articles referencing Brett Kavanaugh's nomination process were identified and subsequently scraped by including the URL for each source's coverage of the nomination in the \emph{R} script.
-
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
-
-Using the \emph{rvest} and \emph{RSelenium} libraries, we pulled body text for individual articles from each of the aforementioned 10 news sources and compiled them together (Harrison \& Kim, 2020; Wickham, 2016).
-Using this dataset, we identified word count and average word count per source.
-This process was run for articles pertaining to Kavanaugh's nomination that were published between September 13, 2018 and October 11, 2018 inclusive.
-This date range was selected in reference to the widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we could capture a large amount of data (roughly one month) during which Kavanaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the partial U.S.
-Government shutdown of 2018-2019.
-The articles scraped were published between December 8, 2018 and February 8, 2019 inclusive.
-Once again, we elected to scrape articles published two weeks before and after the event in question in order to capitalize on the shutdown's saturation in American news media.
-
-\hypertarget{data-analysis-1}{%
-\subsection{Data analysis}\label{data-analysis-1}}
-
-As in Study 1, the text was scanned with \emph{ngram} (Schmidt et al., 2017).
-Again, blank articles, text from the Disqus system, and duplicate articles were removed.
-The text was processed and stemmed in order to convert to a usable form for further analysis (Feinerer \& Hornik, 2017).
-Each individual word was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}).
-Once again, the same procedure was applied to the MFD words and the words in the Warriner et al.
-(2013) dataset.
-We obtained the words' percent occurrence in the text.
-Percents were multiplied by \emph{z}-scored valence and categorized into their proper MFD category.
-
-\hypertarget{results-1}{%
-\section{Results}\label{results-1}}
-
-\hypertarget{descriptive-statistics-1}{%
-\subsection{Descriptive Statistics}\label{descriptive-statistics-1}}
-
-We calculated descriptive statistics for each news source per topic in order to reveal the presence (if any) of linguistic differences in the sources' use of language.
-As in Study 1, statistics calculated include \emph{z}-scored valence, number of articles per source, total words per source, mean tokens per article in each source, mean types per article in each source, and mean readability level (using the Flesch-Kincaid Grade Level Readability formula) per source (Kincaid et al., 1975).
-
-Table \ref{tab:exp2-source-descriptives-kav} displays the descriptive statistics for sources' writing on the Kavanaugh confirmation hearing.
-The sources were similar in most basic linguistic aspects, except for number of articles.
-For example, \emph{Sean Hannity} appears to have published only 27 articles while \emph{Breitbart} published 757 articles on this topic.
-Valence was found to be slightly positive across all sources.
-\emph{Fox News} produced the most total words with the most tokens on average.
-This is likely due to the fact \emph{Fox News} transcribes many of their videos and publishes them in article form.
-\emph{Politico} featured the highest number of types on average.
-\emph{Rush Limbaugh} featured the lowest readability score on average by grade level while \emph{Slate} featured the highest grade-level readability score.
-The large standard deviations for these statistics, however, preclude conclusions regarding differences in the sources' use of language, as there is likely a lot of overlap between sources' use of language.
+For news articles about the partial U.S. Federal Government Shutdown of
+2018-2019, there were no significant or practical effects of political
+lean for the moral foundations (see Table \ref{tab:exp2-tablegs}). A
+small-to-medium effect size was observed for \emph{authority/respect}. The
+effect was in the predicted direction as well, as conservative sources
+tended to offer more positive endorsements of the foundation than
+liberal sources. This effect was similar to Study 2 in which the largest
+effect size was observed for \emph{authority/respect}. As noted before, the
+effect found in Study 2 was in the opposite direction as what was
+hypothesized. Thus, it is difficult to draw comparisons between the two
+studies despite the similar pattern for effect size. Owing to a lack of
+similar effects for either Study 2 or the Kavanaugh topic, there is
+doubt as to whether or not a practical or generalized effect exists for
+\emph{authority/respect}.
+
+Based on the weighted percent values for the five foundations applied to
+both topics, MFD words seem to make up little of the article text. A
+similar pattern was observed for the results in Study 2. As in Study 2,
+the percentages and means seem to indicate a generally positive
+endorsement of all five moral foundations across both political
+leanings.
 
@@
 
-\caption{\label{tab:exp2-source-descriptives-kav}Kavanaugh - Descriptive Statistics by Source}
+\caption{\label{tab:exp2-tablegs}Government Shutdown Results - Multilevel Model}
 
@@
 
-\begin{tabular}{lcccccccccc}
+\begin{tabular}{llcccccccl}
 \toprule
-Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
 \midrule
-Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.68 & 1.89\\
-NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.55 & 3.67\\
-New York Times & 0.33 & 0.13 & 653 & 723569 & 1108.07 & 570.31 & 461.26 & 174.20 & 9.52 & 1.79\\
-Politico & 0.32 & 0.10 & 689 & 1069292 & 1551.95 & 1045.47 & 614.66 & 358.68 & 12.10 & 2.66\\
-Slate & 0.29 & 0.12 & 272 & 229896 & 845.21 & 612.22 & 332.42 & 168.17 & 12.30 & 2.48\\
-The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.73 & 1.85\\
-Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.59 & 11.01 & 2.32\\
-Fox News & 0.29 & 0.11 & 646 & 1304048 & 2018.65 & 2709.77 & 534.46 & 404.20 & 9.91 & 1.98\\
-Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.76 & 2.40\\
-Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1552.72 & 1258.51 & 419.00 & 225.80 & 9.17 & 8.86\\
+Valence & Harm/Care & -0.13 & 0.70 & -0.15 & 0.70 & -0.55 & .594 & 0.03 & .008\\
+Valence & Fairness/Reciprocity & 0.79 & 0.57 & 0.40 & 0.57 & -1.57 & .154 & 0.74 & .139\\
+Valence & Ingroup/Loyalty & 0.35 & 0.39 & 0.37 & 0.39 & 0.53 & .611 & -0.05 & .012\\
+Valence & Authority/Respect & 0.03 & 0.33 & 0.03 & 0.33 & 0.67 & .524 & -0.01 & .004\\
+Valence & Purity/Sanctity & 0.48 & 0.49 & 0.08 & 0.49 & -1.38 & .206 & 0.85 & .155\\
+Original & Harm/Care & 0.34 & 0.38 & 0.36 & 0.38 & 1.24 & .251 & -0.04 & < .001\\
+Original & Fairness/Reciprocity & 0.68 & 0.44 & 0.38 & 0.44 & -2.35 & .047 & 0.75 & .148\\
+Original & Ingroup/Loyalty & 0.51 & 0.50 & 0.54 & 0.50 & 0.23 & .825 & -0.06 & .015\\
+Original & Authority/Respect & 0.42 & 0.44 & 0.43 & 0.44 & 0.58 & .578 & -0.02 & .002\\
+Original & Purity/Sanctity & 0.34 & 0.30 & 0.13 & 0.30 & -1.38 & .206 & 0.85 & .155\\
 \bottomrule
@@
 
-Table \ref{tab:exp2-source-descriptives-gs} displays descriptive statistics for articles about the partial government shutdown.
-Like the Kavanaugh hearing, the sources were similar in average valence (slightly positive).
-Once again, there was variation in the number of articles published by each source on this topic.
-\emph{Sean Hannity}, \emph{Rush Limbaugh}, and \emph{The Blaze} published fewer than 100 articles while \emph{Fox News} published 1,013 articles.
-\emph{Fox News} again featured the most total words and mean tokens, but this is likely due to to the presence of a large amount of video transcriptions that the organization published as articles.
-\emph{Politico} had the most types on average.
-For this topic, \emph{Fox News} featured the lowest reading grade level while \emph{Slate} featured the highest reading grade level.
-For each statistic, the excessively high standard deviations render any assertions regarding linguistic differences inconclusive on a descriptive level due to the aforementioned overlap in sources' language use.
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-source-descriptives-gs}Government Shutdown - Descriptive Statistics by Source}
-
-\footnotesize{
-
-\begin{tabular}{lcccccccccc}
-\toprule
-Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
-\midrule
-Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.68 & 1.85\\
-NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.20 & 3.16\\
-New York Times & 0.33 & 0.13 & 752 & 836811 & 1112.78 & 532.72 & 472.95 & 177.57 & 10.10 & 1.74\\
-Politico & 0.29 & 0.10 & 222 & 349499 & 1574.32 & 875.63 & 638.32 & 313.34 & 11.31 & 1.26\\
-Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.87 & 2.53\\
-The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.70 & 1.85\\
-Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.71 & 2.05\\
-Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2763.29 & 3405.44 & 637.28 & 493.98 & 9.61 & 2.11\\
-Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.36 & 4.81\\
-Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1956.79 & 1544.14 & 482.79 & 252.79 & 9.77 & 7.64\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
-V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{inferential-statistics-1}{%
-\subsection{Inferential Statistics}\label{inferential-statistics-1}}
-
-We utilized a multilevel model (MLM) to analyze if news sources leveraged different vocabularies based on target audience in the same manner as Study 1.
-Each foundation's weighted percentage was predicted by the source's political lean, using the individual source as a random intercept to control for the nested data structure.
-Two separate MLMs were constructed from datasets compiled for each topic of interest: the Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of a statistically significant effect for \emph{harm/care}, but the practical effect denoted by Cohen's \emph{d} was found to be small.
-There were no other significant or practical effects of political lean for any of the other four moral foundations.
-The effect for \emph{harm/care} was in the hypothesized direction with liberal sources tending to use more positively \emph{harm/care} words than conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found in Table \ref{tab:exp2-tablekav}.
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-tablekav}Kavanaugh Results - Multilevel Model}
-
-\footnotesize{
-
-\begin{tabular}{lcccccccl}
-\toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
-\midrule
-Harm/Care & 0.39 & 1.35 & 0.66 & 1.35 & 2.89 & .020 & -0.19 & .012\\
-Fairness/Reciprocity & 1.26 & 1.27 & 1.06 & 1.27 & -1.58 & .154 & 0.16 & .043\\
-Ingroup/Loyalty & 1.15 & 1.22 & 1.06 & 1.22 & -0.63 & .549 & 0.07 & .031\\
-Authority/Respect & 0.85 & 0.99 & 0.75 & 0.99 & -0.93 & .380 & 0.10 & .021\\
-Purity/Sanctity & 0.90 & 1.28 & 1.06 & 1.28 & 0.88 & .406 & -0.11 & .031\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-For news articles about the partial U.S.
-Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations (see Table \ref{tab:exp2-tablegs}).
-A small-to-medium effect size was observed for \emph{authority/respect}.
-The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources.
-This effect was similar to Study 1 in which the largest effect size was observed for \emph{authority/respect}.
-As noted before, the effect found in Study 1 was in the opposite direction as what was hypothesized.
-Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size.
-Owing to a lack of similar effects for either Study 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for \emph{authority/respect}.
-
-Based on the weighted percent values for the five foundations applied to both topics, MFD words seem to make up little of the article text.
-A similar pattern was observed for the results in Study 1.
-As in Study 1, the percentages and means seem to indicate a generally positive endorsement of all five moral foundations across both political leanings.
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:exp2-tablegs}Government Shutdown Results - Multilevel Model}
-
-\footnotesize{
-
-\begin{tabular}{lcccccccl}
-\toprule
-Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
-\midrule
-Harm/Care & 0.91 & 1.27 & 1.01 & 1.27 & 1.68 & .132 & -0.07 & .003\\
-Fairness/Reciprocity & 1.22 & 1.05 & 0.91 & 1.05 & -0.76 & .467 & 0.27 & .044\\
-Ingroup/Loyalty & 1.38 & 1.16 & 1.11 & 1.16 & -0.48 & .643 & 0.21 & .020\\
-Authority/Respect & 0.87 & 1.24 & 0.36 & 1.24 & -1.38 & .204 & 0.37 & .062\\
-Purity/Sanctity & 1.29 & 1.13 & 0.99 & 1.13 & 0.03 & .979 & 0.22 & .043\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
-
-The results obtained in Study 2 are slightly more in line with expectations from MFT, however, in all but one case, the differences were not statistically significant.
-The only statistically significant difference was in the harm foundation; liberals did endorse harm more than conservatives during the Kavanaugh hearings, but the effect was smaller than expected given Graham et al.
-(2009).
-Generally for both the Kavanaugh hearings and the Government shutdown, the differences were in the expected direction (liberals endorsing harm more and conservatives endorsing authority and loyalty more), but the differences were not statistically significant and the practical effects much smaller than reported in Graham et al.
-(2009).
-While not significant, fairness was endorsed more by conservatives in both cases.
-In contrast, purity was endorsed more by conservatives for the government shutdown, but more by liberals for the Kavanaugh hearing though neither difference was statistically significant.
-
-Together with Study 1 and past work, Study 2 further calls into question the usefulness and efficacy of the Moral Foundations as well as cast doubt on the predictions made by MFT.
-One issue that Study 2 brings up is that moral differences between liberals and conservatives may be moderated by a number of factors as shown in Sterling and Jost (2018).
-For example, here we have liberals concerned with purity for the Kavanaugh hearings (a moral bad for liberals and a moral good for conservatives) and conservatives concerned with purity during the government shutdown (a moral bad for conservatives and a moral good for liberals).
-The original predictions made by the Moral Foundations are very simplistic and likely much more complex in reality.
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-Within the theoretical framework of MFT (Haidt \& Graham, 2007), we attempted to devise a method leveraging the MFD (Graham et al., 2009) in order to quantify political bias stemming from content published by several prominent American news sources.
-In Study 1,the results obtained were not significant in any statistical or practical sense.
-There was a small effect found for the \emph{authority/respect} foundation according to Cohen's \emph{d}, but the effect suggested endorsement for that foundation opposite to what was hypothesized.
-In Study 2, the direction of the differences were generally in line with MFT, however, the difference were very small and lacks statistically significance.
-Building on Frimer (2020) and other critiques of MFT and the MFD, we show that MFD is not a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive, we still retain confidence in the overall structure of the methodology established in the current study.
-Specifically, the procedure for scraping text from the web, processing, stemming, and weighting the scores with valence seems to represent a solid method for preparing a high quantity of text passages for data analysis.
-We implemented valence as an indicator of the directionality of endorsement due to the inherent ambiguity of simply calculating MFD word percent occurrence.
-This method served both to augment the face validity of the MFD by incorporating valence (thus reducing ambiguity) and to generate a score that is easy to understand and analyze.
-
-However, political lean and other important political/moral constructs may be communicated through methods other than through the use of particular words.
-As mentioned before, MFD is a measure developed from MFT (Graham et al., 2009).
-Based upon the results obtained, it might be necessary to investigate alternative instruments that could better elucidate the differences of interest.
-Going beyond specific instruments, other theoretical perspectives may be more equipped to explain political differences in discourse.
-Likewise, an atheoretical approach in which large quantities of data are collected from which theories are formulated may be best suited to this area of research.
-
-In critiquing MFT, Schein and Gray (2015) proposed an alternative theory explaining moral choices and potential partisan differences: Dyadic Theory of Morality.
-Across many studies, researchers find that supposed differences in moral foundation can be more easily explained by a harm-focused morality where someone/thing is harmed by someone/thing else Schein \& Gray (2015).
-Rather than liberals and conservatives having difference conceptions of morality, dyadic morality argues that they simply identify harm differently.
-For example, in the case of abortion, liberals tend to identify the primary harm to the mother leading to a pro-choice position whereas conservative tend to identify the primary harm to the fetus leading to a pro-life position.
-While as of yet, no linguistic measurement of dyadic morality exists; such an approach may be able to better identify the systematic differences between liberals and conservatives.
-
-Turning to atheoretical approaches, future studies aiming to uncover political lean in discourse may benefit from a bottom-up, data-driven approach.
-Researchers might derive substantive insights into political lean through gathering data after which they may formulate theories that explain systematic observations obtained from that data.
-The availability of text corpora along with methods for extracting large amounts of text from the internet (as was demonstrated in the current study) potentially make this a feasible option.
-Likewise, there are several approaches to analyzing such data, including linear models (like multilevel models) and network-style models such as latent semantic analysis (Landauer, 1998).
-Owing to the wealth of representative data as well as the sophistication of current analytic tools, there is high potential for the explanatory power of new theories involving political discourse.
-
-Never before has political discourse represented such fertile ground for psychological research.
-The plethora of options for news sources has created not only an abundance of choice but also vast quantities of text data.
-Along with this recent increase in the amount of text information, there is now an obligation on the part of researchers to devise proper methods for analyzing that text.
-Solid methodologies must be constructed and periodically improved to keep pace with evolving technologies.
-Likewise, a strong theoretical foundation is paramount to making sense of the current and future media ecosystem.
-Therefore, it is incumbent upon social scientists to continue investigating the information consumed by millions of Americans every day so that insights into the nature and consequences of political discourse can be more completely understood.
+\subsection{Discussion}\label{discussion-2}
+
+The results obtained in Study 3 are slightly more in line with
+expectations from MFT, however, in all but one case, the differences
+were not statistically significant. The only statistically significant
+difference was in the harm foundation; liberals did endorse harm more
+than conservatives during the Kavanaugh hearings, but the effect was
+smaller than expected given Graham et al. (2009). Generally for both the
+Kavanaugh hearings and the Government shutdown, the differences were in
+the expected direction (liberals endorsing harm more and conservatives
+endorsing authority and loyalty more), but the differences were not
+statistically significant and the practical effects much smaller than
+reported in Graham et al. (2009). While not significant, fairness was endorsed
+more by conservatives in both cases. In contrast, purity was endorsed
+more by conservatives for the government shutdown, but more by liberals
+for the Kavanaugh hearing though neither difference was statistically
+significant.
+
+Together with Study 2 and past work, Study 3 further calls into question
+the usefulness and efficacy of the Moral Foundations as well as cast
+doubt on the predictions made by MFT. One issue that Study 3 brings up
+is that moral differences between liberals and conservatives may be
+moderated by a number of factors as shown in Sterling and Jost (2018). For example,
+here we have liberals concerned with purity for the Kavanaugh hearings
+(a moral bad for liberals and a moral good for conservatives) and
+conservatives concerned with purity during the government shutdown (a
+moral bad for conservatives and a moral good for liberals). The original
+predictions made by the Moral Foundations are very simplistic and likely
+much more complex in reality.
+
+\section{Conclusions}\label{conclusions}
+
+Within the theoretical framework of MFT (Haidt \& Graham, 2007), we attempted to improve the MFD (Graham et al., 2009) and demonstrate its relation with other reliable measurements of moral foundations, the MFQ.
+In Study 1, we examined potential new concepts to add to the MFD by collecting word associations and moral related texts from participants.
+Several dictionary improvements were suggested, but the results of a multi-trait multi-method analysis indicate that the MFD does not relate to the moral foundations found in the MFD.
+Therefore, we did not find support for the use of the MFD in relation to the MFT using a convergent and divergent validity technique.
+
+In Study 2 and 3, we attempted to
+devise a method leveraging the MFD in order to quantify
+political bias stemming from content published by several prominent
+American news sources. In Study 2, the results obtained were not
+significant in any statistical or practical sense. There was a small
+effect found for the \emph{authority/respect} foundation according to Cohen's
+\emph{d}, but the effect suggested endorsement for that foundation opposite
+to what was hypothesized. In Study 3, the direction of the differences
+were generally in line with MFT, however, the difference were very small
+and lacks statistically significance. Building on Frimer (2020) and other
+critiques of MFT and the MFD, we show that MFD is not a useful tool for
+measuring moral language while also calling into question the validity
+of MFT in terms of theorized partisan differences.
+
+Despite the fact the results regarding political bias were inconclusive,
+we still retain confidence in the overall structure of the methodology
+established in the current study. Specifically, the procedure for
+scraping text from the web, processing, stemming, and weighting the
+scores with valence seems to represent a solid method for preparing a
+high quantity of text passages for data analysis. We implemented valence
+as an indicator of the directionality of endorsement due to the inherent
+ambiguity of simply calculating MFD word percent occurrence. This method
+served both to augment the face validity of the MFD by incorporating
+valence (thus reducing ambiguity) and to generate a score that is easy
+to understand and analyze.
+
+However, political lean and other important political/moral constructs
+may be communicated through methods other than through the use of
+particular words. As mentioned before, MFD is a measure developed from
+MFT (Graham et al., 2009). Based upon the results obtained, it might be
+necessary to investigate alternative instruments that could better
+elucidate the differences of interest. Going beyond specific
+instruments, other theoretical perspectives may be more equipped to
+explain political differences in discourse. Likewise, an atheoretical
+approach in which large quantities of data are collected from which
+theories are formulated may be best suited to this area of research.
+
+In critiquing MFT, Schein and Gray (2015) proposed an alternative theory explaining
+moral choices and potential partisan differences: Dyadic Theory of
+Morality. Across many studies, researchers find that supposed
+differences in moral foundation can be more easily explained by a
+harm-focused morality where someone/thing is harmed by someone/thing
+else Schein \& Gray (2015). Rather than liberals and conservatives
+having difference conceptions of morality, dyadic morality argues that
+they simply identify harm differently. For example, in the case of
+abortion, liberals tend to identify the primary harm to the mother
+leading to a pro-choice position whereas conservative tend to identify
+the primary harm to the fetus leading to a pro-life position. While as
+of yet, no linguistic measurement of dyadic morality exists; such an
+approach may be able to better identify the systematic differences
+between liberals and conservatives.
+
+Turning to atheoretical approaches, future studies aiming to uncover
+political lean in discourse may benefit from a bottom-up, data-driven
+approach. Researchers might derive substantive insights into political
+lean through gathering data after which they may formulate theories that
+explain systematic observations obtained from that data. The
+availability of text corpora along with methods for extracting large
+amounts of text from the internet (as was demonstrated in the current
+study) potentially make this a feasible option. Likewise, there are
+several approaches to analyzing such data, including linear models (like
+multilevel models) and network-style models such as latent semantic
+analysis (Landauer, 1998). Owing to the wealth of representative data as
+well as the sophistication of current analytic tools, there is high
+potential for the explanatory power of new theories involving political
+discourse.
+
+Never before has political discourse represented such fertile ground for
+psychological research. The plethora of options for news sources has
+created not only an abundance of choice but also vast quantities of text
+data. Along with this recent increase in the amount of text information,
+there is now an obligation on the part of researchers to devise proper
+methods for analyzing that text. Solid methodologies must be constructed
+and periodically improved to keep pace with evolving technologies.
+Likewise, a strong theoretical foundation is paramount to making sense
+of the current and future media ecosystem. Therefore, it is incumbent
+upon social scientists to continue investigating the information
+consumed by millions of Americans every day so that insights into the
+nature and consequences of political discourse can be more completely
+understood.
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-
-\hypertarget{refs}{}
+\section{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Aust2017}{}}%
+\bibitem[\citeproctext]{ref-Aust2017}
 Aust, F., \& Barth, M. (2017). \emph{{papaja: Create APA manuscripts with R Markdown.}} Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Clifford2013}{}}%
+\bibitem[\citeproctext]{ref-bentler1990}
+Bentler, P. M. (1990). Comparative fit indexes in structural models. \emph{Psychological Bulletin}, \emph{107}(2), 238--246. \url{https://doi.org/10.1037/0033-2909.107.2.238}
+
+\bibitem[\citeproctext]{ref-bentler1980}
+Bentler, P.
+M., \& Bonett, D.
+G.
+(1980).
+Significance tests and goodness of fit in the analysis of covariance structures.
+\emph{Psychological Bulletin}, \emph{88}(3), 588--606.
+\url{https://doi.org/10.1037/0033-2909.88.3.588}
+
+\bibitem[\citeproctext]{ref-bradley1999}
+Bradley, M. M., \& Lang, P. J. (1999). \emph{Affective Norms for English Words (ANEW): Instruction Manual and Affective Ratings}. The Center for Research in Psychophysiology.
+
+\bibitem[\citeproctext]{ref-buuren2011}
+Buuren, S.
+V., \& Groothuis-Oudshoorn, K.
+(2011).
+{\textbf{mice}} : Multivariate Imputation by Chained Equations in {\emph{R}}.
+\emph{Journal of Statistical Software}, \emph{45}(3).
+\url{https://doi.org/10.18637/jss.v045.i03}
+
+\bibitem[\citeproctext]{ref-byrne2001}
+Byrne, B.
+M.
+(2001).
+Structural Equation Modeling With AMOS, EQS, and LISREL: Comparative Approaches to Testing for the Factorial Validity of a Measuring Instrument.
+\emph{International Journal of Testing}, \emph{1}(1), 55--86.
+\url{https://doi.org/10.1207/S15327574IJT0101_4}
+
+\bibitem[\citeproctext]{ref-Clifford2013}
 Clifford, S., \& Jerit, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Feinerer2017}{}}%
+\bibitem[\citeproctext]{ref-dedeyne2019}
+De Deyne, S., Navarro, D.
+J., Perfors, A., Brysbaert, M., \& Storms, G.
+(2019).
+The {``}Small World of Words{''} English word association norms for over 12,000 cue words.
+\emph{Behavior Research Methods}, \emph{51}(3), 987--1006.
+\url{https://doi.org/10.3758/s13428-018-1115-7}
+
+\bibitem[\citeproctext]{ref-Federico2013}
+Federico, C.
+M., Weber, C.
+R., Ergun, D., \& Hunt, C.
+(2013).
+{Mapping the Connections between Politics and Morality: The Multiple Sociopolitical Orientations Involved in Moral Intuition}.
+\emph{Political Psychology}, \emph{34}(4), 589--610.
+\url{https://doi.org/10.1111/pops.12006}
+
+\bibitem[\citeproctext]{ref-Feinerer2017}
 Feinerer, I., \& Hornik, K. (2017). \emph{{Text mining package}}. Retrieved from \url{http://tm.r-forge.r-project.org/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Frimer2020}{}}%
+\bibitem[\citeproctext]{ref-feinerer2008}
+Feinerer, I., Hornik, K., \& Meyer, D. (2008). Text Mining Infrastructure in {\emph{R}}. \emph{Journal of Statistical Software}, \emph{25}(5). \url{https://doi.org/10.18637/jss.v025.i05}
+
+\bibitem[\citeproctext]{ref-Frimer2020}
 Frimer, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Frimer2015}{}}%
+\bibitem[\citeproctext]{ref-Frimer2015}
 Frimer, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Garten2016}{}}%
+\bibitem[\citeproctext]{ref-Garten2016}
 Garten, J., Boghrati, R., Hoover, J., Johnson, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gelman2006}{}}%
+\bibitem[\citeproctext]{ref-Gelman2006}
 Gelman, A. (2006). {Multilevel (hierarchical) modeling: What it can and cannot do}. \emph{Technometrics}, \emph{48}(3), 432--435. \url{https://doi.org/10.1198/004017005000000661}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Graham2009}{}}%
+\bibitem[\citeproctext]{ref-Graham2009}
 Graham, J., Haidt, J., \& Nosek, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gray2015}{}}%
+\bibitem[\citeproctext]{ref-Graham2012}
+Graham, J., Nosek, B.
+A., \& Haidt, J.
+(2012).
+{The Moral Stereotypes of Liberals and Conservatives: Exaggeration of Differences across the Political Spectrum}.
+\emph{PLoS ONE}, \emph{7}(12), e50092.
+\url{https://doi.org/10.1371/journal.pone.0050092}
+
+\bibitem[\citeproctext]{ref-graham2011}
+Graham, J., Nosek, B.
+A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
+H.
+(2011a).
+Mapping the moral domain.
+\emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
+\url{https://doi.org/10.1037/a0021847}
+
+\bibitem[\citeproctext]{ref-Graham2011}
+Graham, J., Nosek, B.
+A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
+H.
+(2011b).
+{Mapping the moral domain.} \emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
+\url{https://doi.org/10.1037/a0021847}
+
+\bibitem[\citeproctext]{ref-Gray2015}
 Gray, K., \& Keeney, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gray2014}{}}%
+\bibitem[\citeproctext]{ref-Gray2014}
 Gray, K., Schein, C., \& Ward, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Haidt2007}{}}%
+\bibitem[\citeproctext]{ref-Haidt2007}
 Haidt, J., \& Graham, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-harrison_rselenium_2020}{}}%
+\bibitem[\citeproctext]{ref-haidt2004}
+Haidt, J., \& Joseph, C.
+(2004).
+Intuitive ethics: How innately prepared intuitions generate culturally variable virtues.
+\emph{Daedalus}, \emph{133}(4), 55--66.
+Retrieved from \url{https://www.jstor.org/stable/20027945}
+
+\bibitem[\citeproctext]{ref-harrison_rselenium_2020}
 Harrison, J., \& Kim, J. Y. (2020). \emph{{RSelenium}: {R} {Bindings} for '{Selenium} {WebDriver}'}. Retrieved from \url{https://CRAN.R-project.org/package=RSelenium}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hopp2021}{}}%
+\bibitem[\citeproctext]{ref-Hopp2021}
 Hopp, F.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jordan2019}{}}%
-Jordan, K. N., Buchanan, E. M., \& Padfield, W. E. (2019). \emph{{A validation of the Moral Foundations Questionnaire and Dictionary}}. Retrieved from \url{https://osf.io/kt9yf/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kincaid1975}{}}%
+\bibitem[\citeproctext]{ref-hu1999}
+Hu, L., \& Bentler, P.
+M.
+(1999).
+Cutoff criteria for fit indexes in covariance structure analysis: Conventional criteria versus new alternatives.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{6}(1), 1--55.
+\url{https://doi.org/10.1080/10705519909540118}
+
+\bibitem[\citeproctext]{ref-hutto2021}
+Hutto, C. (2021). \emph{Welcome to VaderSentiment{'}s documentation! {\textemdash} VaderSentiment 3.3.1 documentation}. Retrieved from \url{https://vadersentiment.readthedocs.io/en/latest/}
+
+\bibitem[\citeproctext]{ref-juxf6reskog1971}
+Jöreskog, K. G. (1971). Simultaneous factor analysis in several populations. \emph{Psychometrika}, \emph{36}(4), 409--426. \url{https://doi.org/10.1007/BF02291366}
+
+\bibitem[\citeproctext]{ref-Kincaid1975}
 Kincaid, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kohlberg1977}{}}%
+\bibitem[\citeproctext]{ref-Kohlberg1977}
 Kohlberg, L., \& Hersh, R. H. (1977). {Moral development: A review of the theory}. \emph{Theory Into Practice}, \emph{16}(2), 53--59. \url{https://doi.org/10.1080/00405847709542675}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Landauer1998}{}}%
+\bibitem[\citeproctext]{ref-Landauer1998}
 Landauer, T. K. (1998). {Learning and Representing Verbal Meaning}. \emph{Current Directions in Psychological Science}, \emph{7}(5), 161--164. \url{https://doi.org/10.1111/1467-8721.ep10836862}
 
-\leavevmode\vadjust pre{\hypertarget{ref-mikolov_efficient_2013}{}}%
+\bibitem[\citeproctext]{ref-leveau2012}
+Leveau, N., Jhean-Larose, S., Denhière, G., \& Nguyen, B.-L.
+(2012).
+Validating an interlingual metanorm for emotional analysis of texts.
+\emph{Behavior Research Methods}, \emph{44}(4), 1007--1014.
+\url{https://doi.org/10.3758/s13428-012-0208-y}
+
+\bibitem[\citeproctext]{ref-loria2020}
+Loria, S. (2020). \emph{Tutorial: Quickstart {\textemdash} TextBlob 0.16.0 documentation}. Retrieved from \url{https://textblob.readthedocs.io/en/dev/quickstart.html}
+
+\bibitem[\citeproctext]{ref-mikolov_efficient_2013}
 Mikolov, T., Chen, K., Corrado, G., \& Dean, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mitchell2014}{}}%
+\bibitem[\citeproctext]{ref-Mitchell2014}
 Mitchell, A., Matsa, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pennebaker2007}{}}%
+\bibitem[\citeproctext]{ref-nelson2004}
+Nelson, D.
+L., McEvoy, C.
+L., \& Schreiber, T.
+A.
+(2004).
+The University of South Florida free association, rhyme, and word fragment norms.
+\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{36}(3), 402--407.
+\url{https://doi.org/10.3758/BF03195588}
+
+\bibitem[\citeproctext]{ref-Pennebaker2007}
 Pennebaker, J. W., Booth, R. J., \& Frances, M. E. (2007). \emph{{Liwc2007: Linguistic inquiry and word count}}. Austin, TX.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Pinheiro2017}{}}%
+\bibitem[\citeproctext]{ref-perry2024}
+Perry, P. O. (2024). \emph{Corpus: Text corpus analysis}. Retrieved from \url{https://leslie-huang.github.io/r-corpus/}
+
+\bibitem[\citeproctext]{ref-Pinheiro2017}
 Pinheiro, J., Bates, D., Debroy, S., Sarkar, D., \& Team, R. C. (2017). \emph{{nlme: Linear and nonlinear mixed effects models}}. Retrieved from \url{https://cran.r-project.org/package=nlme}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sagi2014}{}}%
+\bibitem[\citeproctext]{ref-Sagi2014}
 Sagi, E., \& Dehghani, M. (2014). Measuring moral rhetoric in text. \emph{Social Science Computer Review}, \emph{32}(2), 132--144. \url{https://doi.org/10.1177/0894439313506837}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schein2015}{}}%
+\bibitem[\citeproctext]{ref-Schein2015}
 Schein, C., \& Gray, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schmidt2017}{}}%
+\bibitem[\citeproctext]{ref-Schmidt2017}
 Schmidt, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sterling2018}{}}%
+\bibitem[\citeproctext]{ref-steiger1990}
+Steiger, J.
+H.
+(1990).
+Structural model evaluation and modification: An interval estimation approach.
+\emph{Multivariate Behavioral Research}, \emph{25}(2), 173--180.
+\url{https://doi.org/10.1207/s15327906mbr2502_4}
+
+\bibitem[\citeproctext]{ref-Sterling2018}
 Sterling, J., \& Jost, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Suhler2011}{}}%
+\bibitem[\citeproctext]{ref-Suhler2011}
 Suhler, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Warriner2013}{}}%
+\bibitem[\citeproctext]{ref-Tabachnick2012}
+Tabachnick, B. G., \& Fidell, L. S. (2012). \emph{\href{https://www.ncbi.nlm.nih.gov/pubmed/1577}{{Using multivariate statistics}}} (Sixth). Boston, MA: Pearson.
+
+\bibitem[\citeproctext]{ref-Warriner2013}
 Warriner, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2016}{}}%
+\bibitem[\citeproctext]{ref-Weber2013}
+Weber, C.
+R., \& Federico, C.
+M.
+(2013).
+{Moral Foundations and Heterogeneity in Ideological Preferences}.
+\emph{Political Psychology}, \emph{34}(1), 107--126.
+\url{https://doi.org/10.1111/j.1467-9221.2012.00922.x}
+
+\bibitem[\citeproctext]{ref-Wickham2016}
 Wickham, H. (2016). \emph{{Package `rvest'}}. Retrieved from \url{https://cran.r-project.org/package=rvest}
 
+\bibitem[\citeproctext]{ref-widaman1985}
+Widaman, K.
+F.
+(1985).
+Hierarchically Nested Covariance Structure Models for Multitrait-Multimethod Data.
+\emph{Applied Psychological Measurement}, \emph{9}(1), 1--26.
+\url{https://doi.org/10.1177/014662168500900101}
+
 \end{CSLReferences}
 
-\endgroup
+\newpage
+
+\appendix
+
+\section{Study 2: Descriptive Statistics}\label{study-2-descriptive-statistics}
+
+We calculated descriptive statistics for each news source in order to
+understand any and all fundamental linguistic differences in the
+sources' use of English. Statistics calculated included average
+\emph{z}-scored valence of the unique words per article, number of articles
+per source, total number of words per source, average number of tokens
+(words) per article in each source, average number of types (unique
+words) per article in each source, and mean readability level per
+source. Readability statistics were calculated using the Flesch-Kincaid
+Grade Level Readability formula (Kincaid, Fishburne, Robert P., Richard L., \& Brad S., 1975). Readability is
+calculated using a formula where the total number of syllables, words,
+and sentences in a given passage are determinants of its difficulty. The
+obtained value is intended to match up with the U.S. grade level at
+which one should be able to comfortably read the passage (Kincaid et al., 1975).
+For example, a text with a readability score of 11 should be easily read
+by a U.S. high school junior.
+
+As seen in Table \ref{tab:exp1-source-descriptives}, the sources are
+similar in some aspects yet different in others. Valence appears to be
+slightly positive across all sources. The large standard deviations seem
+to indicate little to no presence of a difference in valence across
+sources. \emph{NYT} published the greatest number of articles as well as
+total words. \emph{Breitbart} featured the lowest number of articles, and
+\emph{NPR} the lowest number of total words from all articles. Per individual
+article, however, \emph{Breitbart} appears to feature the highest average
+number of words as well as unique words. Once again the standard
+deviations call into question any apparent differences between sources.
+Finally, \emph{Fox News} articles had the lowest reading grade level on
+average, while \emph{NYT} had the highest. This result might be attributable
+to the greater number of tokens in the average \emph{NYT} article compared to
+\emph{Fox News}. The standard deviations for readability suggest the presence
+of a diverse array of articles for each source, ranging from low to high
+reading level. Large standard deviations suggest the sources feature a
+lot of overlap between them in their representation of scores.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp1-source-descriptives}Study 2 - Descriptive Statistics by Source}
+
+\footnotesize{
+
+\begin{tabular}{lcccccccccc}
+\toprule
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+\midrule
+NPR & 0.28 & 0.23 & 695 & 302977 & 435.94 & 642.63 & 191.96 & 192.28 & 14.00 & 3.93\\
+New York Times & 0.30 & 0.13 & 406 & 452579 & 1114.73 & 511.86 & 454.27 & 154.58 & 16.44 & 3.36\\
+Breitbart & 0.29 & 0.18 & 1437 & 722022 & 502.45 & 347.90 & 243.35 & 120.75 & 18.56 & 7.90\\
+Fox News & 0.29 & 0.17 & 503 & 296779 & 590.02 & 528.60 & 283.56 & 189.00 & 17.25 & 7.21\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\section{Study 3: Descriptive Statistics}\label{study-3-descriptive-statistics}
+
+We calculated descriptive statistics for each news source per topic in
+order to reveal the presence (if any) of linguistic differences in the
+sources' use of language. As in Study 1, statistics calculated include
+\emph{z}-scored valence, number of articles per source, total words per
+source, mean tokens per article in each source, mean types per article
+in each source, and mean readability level (using the Flesch-Kincaid
+Grade Level Readability formula) per source (Kincaid et al., 1975).
+
+Table \ref{tab:exp2-source-descriptives-kav} displays the descriptive
+statistics for sources' writing on the Kavanaughnaugh confirmation
+hearing. The sources were similar in most basic linguistic aspects,
+except for number of articles. For example, \emph{Sean Hannity} appears to
+have published only 27 articles while \emph{Breitbart} published 757 articles
+on this topic. Valence was found to be slightly positive across all
+sources. \emph{Fox News} produced the most total words with the most tokens
+on average. This is likely due to the fact \emph{Fox News} transcribes many
+of their videos and publishes them in article form. \emph{Politico} featured
+the highest number of types on average. \emph{Rush Limbaugh} featured the
+lowest readability score on average by grade level while \emph{Slate}
+featured the highest grade-level readability score. The large standard
+deviations for these statistics, however, preclude conclusions regarding
+differences in the sources' use of language, as there is likely a lot of
+overlap between sources' use of language.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp2-source-descriptives-kav}Kavanaugh - Descriptive Statistics by Source}
+
+\footnotesize{
+
+\begin{tabular}{lcccccccccc}
+\toprule
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+\midrule
+Huffington Post & 0.27 & 0.12 & 552 & 359046 & 650.45 & 462.21 & 283.07 & 129.23 & 10.68 & 1.89\\
+NPR & 0.22 & 0.25 & 366 & 108605 & 296.73 & 499.10 & 128.12 & 172.51 & 12.55 & 3.67\\
+New York Times & 0.33 & 0.13 & 653 & 723569 & 1108.07 & 570.31 & 461.26 & 174.20 & 9.50 & 1.79\\
+Politico & 0.32 & 0.10 & 689 & 1069292 & 1551.95 & 1045.47 & 614.66 & 358.68 & 12.09 & 2.66\\
+Slate & 0.29 & 0.12 & 272 & 229896 & 845.21 & 612.22 & 332.42 & 168.17 & 12.29 & 2.48\\
+The Blaze & 0.25 & 0.13 & 277 & 128097 & 462.44 & 149.66 & 210.52 & 53.14 & 10.73 & 1.85\\
+Breitbart & 0.30 & 0.13 & 757 & 375848 & 496.50 & 609.91 & 230.03 & 153.59 & 11.00 & 2.32\\
+Fox News & 0.29 & 0.11 & 646 & 1304048 & 2018.65 & 2709.77 & 534.46 & 404.20 & 9.91 & 1.98\\
+Sean Hannity & 0.31 & 0.11 & 27 & 5926 & 219.48 & 145.98 & 121.04 & 57.26 & 11.76 & 2.40\\
+Rush Limbaugh & 0.38 & 0.13 & 172 & 267067 & 1552.72 & 1258.51 & 419.00 & 225.80 & 9.17 & 8.86\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Table \ref{tab:exp2-source-descriptives-gs} displays descriptive
+statistics for articles about the partial government shutdown. Like the
+Kavanaugh hearing, the sources were similar in average valence (slightly
+positive). Once again, there was variation in the number of articles
+published by each source on this topic. \emph{Sean Hannity}, \emph{Rush Limbaugh},
+and \emph{The Blaze} published fewer than 100 articles while \emph{Fox News}
+published 1,013 articles. \emph{Fox News} again featured the most total words
+and mean tokens, but this is likely due to to the presence of a large
+amount of video transcriptions that the organization published as
+articles. \emph{Politico} had the most types on average. For this topic, \emph{Fox
+News} featured the lowest reading grade level while \emph{Slate} featured the
+highest reading grade level. For each statistic, the excessively high
+standard deviations render any assertions regarding linguistic
+differences inconclusive on a descriptive level due to the
+aforementioned overlap in sources' language use.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp2-source-descriptives-gs}Government Shutdown - Descriptive Statistics by Source}
+
+\footnotesize{
+
+\begin{tabular}{lcccccccccc}
+\toprule
+Source & $M_V$ & $SD_V$ & $N_{Article}$ & $N_{Words}$ & $M_T$ & $SD_T$ & $M_{Ty}$ & $SD_{Ty}$ & $M_{FK}$ & $SD_{FK}$\\
+\midrule
+Huffington Post & 0.30 & 0.13 & 432 & 242220 & 560.69 & 425.52 & 258.27 & 130.54 & 10.67 & 1.85\\
+NPR & 0.23 & 0.22 & 434 & 151114 & 348.19 & 457.34 & 155.53 & 171.30 & 11.20 & 3.16\\
+New York Times & 0.33 & 0.13 & 752 & 836811 & 1112.78 & 532.72 & 472.95 & 177.57 & 10.09 & 1.74\\
+Politico & 0.29 & 0.10 & 222 & 349499 & 1574.32 & 875.63 & 638.32 & 313.34 & 11.30 & 1.26\\
+Slate & 0.30 & 0.12 & 117 & 85254 & 728.67 & 464.34 & 301.71 & 138.74 & 11.86 & 2.54\\
+The Blaze & 0.26 & 0.13 & 98 & 38983 & 397.79 & 102.10 & 185.66 & 41.93 & 10.70 & 1.85\\
+Breitbart & 0.34 & 0.15 & 309 & 102886 & 332.96 & 238.70 & 168.31 & 81.59 & 10.70 & 2.04\\
+Fox News & 0.35 & 0.13 & 1013 & 2799217 & 2763.29 & 3405.44 & 637.28 & 493.98 & 9.61 & 2.11\\
+Sean Hannity & 0.29 & 0.14 & 63 & 10311 & 163.67 & 33.59 & 95.13 & 16.59 & 13.36 & 4.81\\
+Rush Limbaugh & 0.37 & 0.12 & 78 & 152630 & 1956.79 & 1544.14 & 482.79 & 252.79 & 9.77 & 7.64\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.
+V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2024-11-30 manuscript_version/revision/revision_letter.Rmd
rearranging folders and updating the manuscript

@@
 
-thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
+Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
 
@@
 
-TO DO ADD THE MTMM STUDY FINALLY
+The cited manuscript from our original paper was another manuscript the team was working on.
+We decided to merge those results with this manuscript for stronger evidence about the issues with the MFD.
+We have rewritten sections to clarify, using the theoretical information proposed by the MFT and other publications, we examined if those results could be found: within several different types of sources and with potential improvements to the MFD.
+Study 1 now includes our MTMM results.
 
@@
 
-TO DO ADD MORE TEXT AND TALK ABOUT THIS STUFF
+In our revisions, we have now tested several ideas: 1) if we add more words can we see how the MFD is related to the MFQ (which has good validity evidence)?
+2) if that doesn't work, can we augment scores with valence to improve the results?
+The original MFD was created by simply thinking about words that should relate to the moral foundation areas, and we expand by suggesting new terms through free association and written texts focusing on moral areas.
+While some frequencies correlate with MFQ results, the relation to the MFQ does not appear to hold with MTMM results.
 
-RESPONSE: [Erin]
-- look at original thesis for justification for valence
-- note if we add the MTMM, this response may be different, so waiting here.
-Also this person seems to think that valence ratings are not useful, so add some notes about how they are very predictive, yada yada.
-- add information from will's thesis back in there
-
-Critically - also - the MFD was made by just *thinking* about words right? So why is that better than the actual ratings of valence from people?
-
-As noted in text, we z-scored to help with interpretation:
-
-"Valences were z-scored in order to eliminate any ambiguity regarding the direction of the valence. Positive values indicate positive valence, and negative values indicate negative valence."
+We examined valence to improve MFD scoring by adding context to the words included.
+Within one foundation, concepts are both positive and negative.
+We examined if adding that information would improve the ability to find expected differences.
+We added citations for justification for valence ratings, as this is very popular technique for sentiment analysis.
+As noted in text, we z-scored to help with interpretation, as the dataset ranges from 1 to 9, but -1 to 1 is easier to interpret (i.e., greater than zero is positive, less than zero is negative).
+For comparison, we also provide the results of the traditional scoring, which is to simply calculate the percent of the words within a text.
 
@@
 
-TO DO MAKE THESE CHANGES
-
-RESPONSE: [Erin]
-- move readability stats to an appendix
-- undecided here maybe something like ...
 Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript.
 Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation.
+We have streamlined in method sections when it was repetitive refering back to previous studies.
 
@@
 
-We added an example table of the weighting calculation and rephrased this section completely.
+We added an example table of the weighting calculation and rephrased this section completely for clarity.
 
@@
 Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.
-In response to the question about analytic choices, we have added information about a MTMM study, as well as the exact same statistics using the raw percentages.
 
-TO DO - DO THIS
+In response to the question about analytic choices, we have added information about a MTMM study (study 1), as well as the exact same statistics using the mean percentages for comparison (study 2-3).
+The results remain the same.
 
@@
 
-TO DO COMMENT HERE ABOUT THE ORIGINAL SCORING BEING SHIT AS WELL
+We added comparisons to the original scoring to demonstrate the results remain the same (study 2 and 3).
 

### 2024-11-30 manuscript_version/revision/manuscript_metapsych_revision.Rmd
finalizing the revision letter and manuscript

@@
 Many theories have been proposed to explain these differences and divisions including Moral Foundations Theory.
-The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences.
-In Study 1, we explore the MFD-Moral Foundations Questionnaire's measurement overlap using a multi-trait multi-method model.
-These latent trait models were used to inform possible improvement of the MFD.
-Next, we examined two replication extensions of previous work exploring the differences in political articles on moral differences Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
+The current research seeks determine if a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD) can unveil these theoretical partisan differences.
+In Study 1, we explored the MFD-Moral Foundations Questionnaire's measurement overlap using a multi-trait multi-method model and determined if current predictive shortcomings of the MFD can be improved with additional linguistic content.
+Next, we examined two replication extensions of previous work assessing the differences in political articles on moral differences using the MFD.
+Through web scraping, we extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences.
 This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology.
 In Study 2, we gathered political articles from four sources.
-We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research.
 In Study 3, we expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S.
@@
 Government Shutdown of 2018-2019.
-Once again, no significant differences in moral endorsements were found.
-Together with past work, the results shed doubt on the validity of the MFD as a reliable measurement tool.
+Results from all studies indicate that the MFD may not consistently show exptected partisan differences, shedding doubt on the usefulness of the MFD.
 
@@
 the words people use. Here we first review evidence and criticisms
-against this assumption. We then provide our own test of the MFD using
-partisan news articles.
+against this assumption. We then provide our own test of the MFD using a statistical validity assessment and partisan news articles.
 
@@
 
-Haidt and Joseph [-\@haidt2004] and Haidt and Graham [-@Haidt2007]
+Haidt and Joseph [-@haidt2004] and Haidt and Graham [-@Haidt2007]
 formulated MFT as a method by which to capture the entirety of humans'
@@
 domain can be mapped by quantifying their endorsement of five moral
-foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*,
-*authority/respect*, and *purity/sanctity* [@Haidt2007]. Thus, they
+foundations: harm/care, fairness/reciprocity, ingroup/loyalty,
+authority/respect, and purity/sanctity [@Haidt2007]. Thus, they
 proposed that the addition of these two additional domains could
-adequately capture the broader spectrum of morality.
+adequately capture the broader spectrum of morality. Throughout the rest of the article, we will use the first word from each of these continuums to denote the foundation area.
 
@@
 designed to capture language's role in moral reasoning and justification
-as used in speech and text [@Graham2009; @graham2011]. The MFQ is a
+as used in speech and text [@Graham2009; @Graham2011]. The MFQ is a
 30-item scale with 15 items on the moral relevance and judgment
@@
 relevant*). These relevance items include examples such as: "Whether or
-not someone used violence (*harm*)," "Whether or not someone was denied
-his or her rights (*fairness*)," "Whether or not someone showed a lack
-of loyalty (*ingroup*)," "Whether or not an action caused chaos or
-disorder (*authority*)," and "Whether or not someone did something
-disgusting (*purity*)." The moral judgments items are also equally
+not someone used violence (harm)," "Whether or not someone was denied
+his or her rights (fairness)," "Whether or not someone showed a lack
+of loyalty (ingroup)," "Whether or not an action caused chaos or
+disorder (authority)," and "Whether or not someone did something
+disgusting (purity)." The moral judgments items are also equally
 divided between the foundations and ask on a six-point scale how much
@@
 "One of the worst things a person can do is hurt a defenseless animal
-(*harm*)," "Justice is the most important requirement of a society
-(*fairness*)," "I am proud of my country's history (*ingroup*)," "Men
-and women each have different roles to play in society (*authority*),"
-and "Chastity is an important and valuable virtue (*purity*)."
+(harm)," "Justice is the most important requirement of a society
+(fairness)," "I am proud of my country's history (ingroup)," "Men
+and women each have different roles to play in society (authority),"
+and "Chastity is an important and valuable virtue (purity)."
 
@@
 studies, the MFQ was found to have an average Cronbach's alpha of .63
-for *harm*, .64 for *fairness*, .56 for *ingroup*, .59 for *authority*,
-and .71 for *purity* [@Federico2013; @Graham2009; @Graham2012;
+for harm, .64 for fairness, .56 for ingroup, .59 for authority,
+and .71 for purity [@Federico2013; @Graham2009; @Graham2012;
 @Weber2013]. Test-retest reliability was *r* = .68-.82 using a sample of
 123 college students. Confirmatory factor analysis supported a
-well-fitted five-factor model (*harm/care*, *fairness/reciprocity*,
-*ingroup/loyalty*, *authority/respect*, and *purity/sanctity*) over two,
-individual (*harm* and *fairness*) versus group (*ingroup*, *authority*,
-and *purity*) foundations, or three, autonomy (*harm*, *fairness*),
-community (*ingroup*, *authority*), and divinity (*purity*) ethics,
+well-fitted five-factor model (harm, fairness,
+ingroup, authority, and purity) over two,
+individual (harm and fairness) versus group (ingroup, authority,
+and purity) foundations, or three, autonomy (harm, fairness),
+community (ingroup, authority), and divinity (purity) ethics,
 foundations factor model. The five-factor structure also fit for
@@
 that they believed would be associated with the five foundations. Words
-such as *war* and *peace* should indicate a greater concern with *harm*
+such as *war* and *peace* should indicate a greater concern with harm
 foundation whereas words such as *homeland* and *terrorism* should
-indicate a greater concern with the *ingroup* foundation. The other
-foundation dictionaries include *equal* and *justice* (*fairness*),
-*honor* and *protest* (*authority*), and *holy* and *sin* (*purity*). To
+indicate a greater concern with the ingroup foundation. The other
+foundation dictionaries include *equal* and *justice* (fairness),
+*honor* and *protest* (authority), and *holy* and *sin* (purity). To
 validate the word sets, @Graham2009 examined the frequency of MFD words
 in liberal and conservative sermons using the Linguistic Inquiry and
-Word Count [LIWC; @Pennebaker2007] computer program. They found liberal
-ministers used *harm*, *fairness*, and *ingroup* words more often than
-conservative ministers who used *authority* and *purity* words more
+Word Count [LIWC, @Pennebaker2007] computer program. They found liberal
+ministers used harm, fairness, and ingroup words more often than
+conservative ministers who used authority and purity words more
 often. Although conservative ministers were expected to use more
-*ingroup* words based on political ideology and previous research, an
-examination of the way liberal ministers used *ingroup* words revealed a
-tendency for the use of *ingroup* words to glorify rebellion and promote
-independence (i.e., the opposite direction from *ingroup* definitions).
+ingroup words based on political ideology and previous research, an
+examination of the way liberal ministers used ingroup words revealed a
+tendency for the use of ingroup words to glorify rebellion and promote
+independence (i.e., the opposite direction from ingroup definitions).
 Effect sizes indicated relatively sizable difference between liberal and
-conservative sermons with Cohen's *d* values ranging from 0.56 to 1.27.
+conservative sermons with Cohen's $d_s$ values ranging from 0.56 to 1.27.
 
@@
 1987-2007. After 9-11, the number of moral words associated with the
-World Trade Center increased, specifically *harm* words from the MFD.
+World Trade Center increased, specifically harm words from the MFD.
 Second, they considered the changes in how moral words were paired with
@@
 overall; more specifically, Republicans tended to use more words
-associated with the *purity* foundation; while Democrats used more words
-associated with the *fairness* foundation.
+associated with the purity foundation; while Democrats used more words
+associated with the fairness foundation.
 
@@
 the foundations are sufficiently distinct as to stand as their own
-foundation. Likewise, @Gray2015 argues that the measurement of the moral
+foundation. Likewise, @Gray2015 argued that the measurement of the moral
 foundations confounds morality with other constructs (such as weirdness)
-and the moral foundations lack statistical and conceptual distinction.
-@Schein2015 argues that harm-based morality is the most parsimonious and
+and that the moral foundations lack statistical and conceptual distinction.
+@Schein2015 argued that harm-based morality is the most parsimonious and
 logical explanation for MFT findings.
@@
 (log transformed MFD2 scores), only two of the foundations showed
-theorized differences but with very small effects. Other studies have
+theorized differences but with very small effects.
+
+Other studies have
 also found conflicting findings which fail to support the basic
@@
 @Sagi2014]. Like @Frimer2020, we attempt to give the MFD the best chance
-for success by incorporating a weighting method to address the
+for success by both increasing linguistic content and incorporating a weighting method to address the
 skewedness and sparsity of the linguistic data.
@@
 categories: human annotations and semantic representations. @Hopp2021
-represents the first approach where instead of relying on 'experts', a
+assessed the first approach where instead of relying on 'experts', a
 large sample of lay people were crowdsourced to manually annotate
@@
 and judge moral issues in everyday life leading to a more ecologically
-valid dictionary. @Garten2016 represents the second categories which
+valid dictionary. @Garten2016 examined the second category which
 instead relies on data-driven semantic analysis. Using shallow neural
@@
 between these two sources, as well as the latent traits after
-controlling for the overlap. Using the results from this study, we
+controlling for method-related measurement. Using the results from this study, we
 examined two conceptual replications of @Frimer2020. We test the
@@
 
-Each of the foundation pairs were listed together (i.e., *harm/care*,
-*fairness/reciprocity,* etc.) with a space for participants to list
+Each of the foundation pairs were listed together (i.e., harm,
+fairness, etc.) with a space for participants to list
 their free association concepts. After the free association task,
@@
 
-Participant data was first spell checked and screening for inaccurate
-responses. Participants who did not write more than fifty words in
+Participants who did not write more than fifty words in
 response to a given prompt were excluded (*n*  = 
@@
 ##adding forms/conjugations of words to original_mfd
-#harm/care
+#Harm
 original_mfd[c(27:95),1] <- c("abusive","abuser","abused","abusing",
@@
 
-#fairness/reciprocity
+#Fairness
 original_mfd[c(20:64),2] <- c("balances", "balanced", "balancing","biased",
@@
 
-#ingroup/loyalty
+#Ingroup
 original_mfd[c(16:47),3] <- c("collects", "collected", "collecting", "collective",
@@
 
-#authority/respect
+#Authority
 original_mfd[c(31:112),4] <- c("abides", "abided", "abiding", "authorities",
@@
 
-#purity/sanctity
+#Purity
 original_mfd[c(21:60),5] <- c("abstains", "abstained", "abstaining", "abstinence",
@@
           font_size = 'footnotesize',
-          placement = "h"
+          placement = "ht"
           )
@@
 The fit indices from these models indicate that all models showed good fit.
-The original and complete MFD models showed equal fit ($\Delta$ CFA <= .01), and both models were better than the reduced MFD model.
+The original and complete MFD models showed equal fit ($\Delta$ CFI <= .01), and both models were better than the reduced MFD model.
 We then inspected the loadings to determine the adequacy of the loadings for the MFQ and MFD.
 These results are shown in Table \@ref(tab:mtmm-model1-table2).
-All but one question for the MFQ load adequately (>.30) on each of their moral foundation areas.
+All but one question for the MFQ load adequately (>.30; *denied rights*) on each of their moral foundation areas.
 None of the MFD areas load onto their moral foundation area, as all loadings are close to zero (and non-significant, see online).
@@
          Measured = rep(c("1", "2", "3", "MFD"), times = 5)) %>% 
-  select(Latent, Measured, Original:Reduce)
+  select(Latent, Measured, Original:Reduce) %>% 
+  mutate(Measured = c(
+    "Emotional Suffering", 
+    "Cared for Weak",
+    "Cruel",
+    "MFD", 
+    "Treated Differently", 
+    "Acted Unfairly", 
+    "Denied Rights",
+    "MFD", 
+    "Love for Country",
+    "Betray Group",
+    "Lack of Loyalty",
+    "MFD",
+    "Lack of Respect",
+    "Conformed to Tradition",
+    "Chaos or Disorder",
+    "MFD",
+    "Purity and Decency",
+    "Disgusting",
+    "Acted God",
+    "MFD"
+  ))
 
@@
           note = "Estimates are completely standardized loadings from the model.",
-          caption = "MTMM Fit Estimates for Model 1 Loadings",
+          caption = "MTMM Parameter Estimates for Model 1 Loadings",
           col.names = c("Latent Variable", "Measured Variable", 
@@
 indicating endorsements of the individualizing moral foundations
-(*harm/care* and *fairness/reciprocity*). Additionally, we hypothesized
-the two sources generally perceived to be conservative leaning (*Fox News* 
-and *Breitbart*) would feature MFD words and valences indicating
-equal endorsement of all five foundations.
+(harm and fairness), and thus, higher foundation scores in this area than conservative sources [@Sagi2014].
+Additionally, we hypothesized that the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences with higher scores in the authority and purity areas.
+Given the previously mixed results of ingroup, we do not make a directional prediction [@Frimer2020].
 
@@
 investigation, we found another, more robust URL for political content
-from NPR: their politics content "archive." The page structure on NPR's
+from NPR: their politics content archive. The page structure on NPR's
 website was such that only a limited selection of articles is displayed
@@
 
-### Data analysis
-
-Once data collection ended, the text was scanned using the *ngram*
-package in *R* [@Schmidt2017]. This package includes a word count
-function, which was used to remove articles that came through as blank
-text, as well as to eliminate text picked up from the Disqus commenting
-system used by certain websites. At this point, duplicate articles were
-discarded.
-
-The article text was processed using the *tm* and *ngram* packages in
-*R* in order to render the text in lowercase, remove punctuation, and
-fix spacing issues [@Feinerer2017]. The individual words were then
-reduced to their stems (i.e., *abused* was stemmed to *abus*). The same
-procedure was applied to the MFD words and the words in the
-@Warriner2013 dataset. Using the @Warriner2013 dictionary, the words
-making up each of the five foundations in the MFD were matched to their
-respective valence value.
-
+### Data Analysis
+
+Once data collection ended, the text sources and @Warriner2013 dataset were processed as described in Study 1.
+The words making up each of the five foundations in the MFD were matched to their respective valence value.
 The @Warriner2013 data includes nearly 14,000 English lemmas that have
@@
 also suggest using the larger complete dataset, given that the CFI indicated 
-similar models, and we note here that the pattern of results do not change 
-if that dictionary is used instead. The total number of times each of those words
+similar models. The total number of times each of those words
 was used in an article was calculated. This information was merged with
@@
 apa_table(temp_table %>% select(-URL), 
-          note = "Concepts were stemmed to match datasets.",
+          note = "Concepts were stemmed to match datasets. The frequency was divided by the total numbers and then multiply by valence and 100 to create percent weighted scores.",
           caption = "Example of Weighted Coding for Harm Words",
@@
 ## Results
+
+Descriptive and test statistics, *p*-values and effect sizes (Cohen's
+$d_s$) can be found in Table \@ref(tab:exp1-table). To interpret the
+weighted scores, one can examine the mean and standard deviations for
+each. A zero score for the mean, with a non-zero standard deviation,
+would indicate a perfect balance of positive and negative words in each
+category, likely representing a neutral sentiment when all words are
+considered. Negative percentages would indicate more representation of
+the negative words in the MFD area, while positive percentages indicate
+an endorsement of the positive words in a MFD. Therefore, we suggest
+using the sign of the mean score to determine the directionality of the
+endorsement for the MFD (positive, neutral, negative), and the standard
+deviation to ensure that a zero score is not zero endorsement (i.e., a
+SD of zero indicates no words were used).
 
@@
 sources as a random intercept to control for the structure of the data.
-Therefore, the models were calculated by: Weighted Score \~ Political
-Lean + (\~1\|Source).
-
-The multilevel model did not indicate the presence of any significant or
-practical effect of political lean for any of the five moral
-foundations. The strongest effect size was observed for the
-*authority/respect* foundation, but the effect was in the opposite
-direction from what was originally hypothesized - liberal sources tended
-to use more *authority/respect* words than did conservative sources.
-Descriptive and test statistics, *p*-values and effect sizes (Cohen's
-*d*) can be found in Table \@ref(tab:exp1-table). To interpret the
-weighted scores, one can examine the mean and standard deviations for
-each. A zero score for the mean, with a non-zero standard deviation,
-would indicate a perfect balance of positive and negative words in each
-category, likely representing a neutral tone when all words are
-considered. Negative percentages would indicate more representation of
-the negative words in the MFD area, while positive percentages indicate
-an endorsement of the positive words in a MFD. Therefore, we suggest
-using the sign of the mean score to determine the directionality of the
-endorsement for the MFD (positive, neutral, negative), and the standard
-deviation to ensure that a zero score is not zero endorsement (i.e., a
-SD of zero indicates no words were used). Based on the weighted percent
-values for the five foundations, we observed that MFD words seem to make
-up a small portion of the article text. Furthermore, the observed
-percentages and means appear to indicate a generally positive
-endorsement of all five foundations across both liberal and conservative
-sources.
+Therefore, the models were calculated by: `Weighted Score (or Original Percent Score) ~ Political
+Lean + (~1|Source)`.
+Both the valence weighted scores and original MFD scores were used as dependent variables to compare results across different scorings of the MFD.
+The multilevel model did not indicate the presence of any significant effects for political lean for any of the five moral
+foundations.
+The effect sizes ($d_s$) appear to show a similar pattern of results, but given that most are close to zero, it is difficult to know if these two scoring systems showed similar results or these results were simply null effects.
+The original scoring shows a small effect size for purity (considering that previous effect sizes reported were .50+, we considered .20 small) in the expected direction.
 
@@
 #put in the numbers
-tableprint2[1, ] = c("Valence", "Harm/Care", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1,
+tableprint2[1, ] = c("Valence", "Harm", harm_d$M1, harm_d$sd1, harm_d$M2, harm_d$sd1,
                     summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                     harm_d$d, icc(harm_icc, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[2, ] = c("Valence", "Fairness/Reciprocity", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1,
+tableprint2[2, ] = c("Valence", "Fairness", fair_d$M1, fair_d$sd1, fair_d$M2, fair_d$sd1,
                     summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                     fair_d$d, icc(fair_icc, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[3, ] = c("Valence", "Ingroup/Loyalty", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1,
+tableprint2[3, ] = c("Valence", "Ingroup", ingroup_d$M1, ingroup_d$sd1, ingroup_d$M2, ingroup_d$sd1,
                     summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                     ingroup_d$d, icc(ingroup_icc, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[4, ] = c("Valence", "Authority/Respect", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1,
+tableprint2[4, ] = c("Valence", "Authority", authority_d$M1, authority_d$sd1, authority_d$M2, authority_d$sd1,
                     summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                     authority_d$d, icc(authority_icc, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[5, ] = c("Valence", "Purity/Sanctity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1,
+tableprint2[5, ] = c("Valence", "Purity", purity_d$M1, purity_d$sd1, purity_d$M2, purity_d$sd1,
                     summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
@@
 
-tableprint2[6, ] = c("Original", "Harm/Care", harm_d_p$M1, harm_d_p$sd1, harm_d_p$M2, harm_d_p$sd1,
+tableprint2[6, ] = c("Original", "Harm", harm_d_p$M1, harm_d_p$sd1, harm_d_p$M2, harm_d_p$sd1,
                     summary(harm_model_p)$tTable[2,4], summary(harm_model_p)$tTable[2,5],
                     harm_d_p$d, icc(harm_icc_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[7, ] = c("Original", "Fairness/Reciprocity", fair_d_p$M1, fair_d_p$sd1, fair_d_p$M2, fair_d_p$sd1,
+tableprint2[7, ] = c("Original", "Fairness", fair_d_p$M1, fair_d_p$sd1, fair_d_p$M2, fair_d_p$sd1,
                     summary(fair_model_p)$tTable[2,4], summary(fair_model_p)$tTable[2,5],
                     fair_d_p$d, icc(fair_icc_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[8, ] = c("Original", "Ingroup/Loyalty", ingroup_d_p$M1, ingroup_d_p$sd1, ingroup_d_p$M2, ingroup_d_p$sd1,
+tableprint2[8, ] = c("Original", "Ingroup", ingroup_d_p$M1, ingroup_d_p$sd1, ingroup_d_p$M2, ingroup_d_p$sd1,
                     summary(ingroup_model_p)$tTable[2,4], summary(ingroup_model_p)$tTable[2,5],
                     ingroup_d_p$d, icc(ingroup_icc_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[9, ] = c("Original", "Authority/Respect", authority_d_p$M1, authority_d_p$sd1, authority_d_p$M2, authority_d_p$sd1,
+tableprint2[9, ] = c("Original", "Authority", authority_d_p$M1, authority_d_p$sd1, authority_d_p$M2, authority_d_p$sd1,
                     summary(authority_model_p)$tTable[2,4], summary(authority_model_p)$tTable[2,5],
                     authority_d_p$d, icc(authority_icc_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint2[10, ] = c("Original", "Purity/Sanctity", purity_d_p$M1, purity_d_p$sd1, purity_d_p$M2, purity_d_p$sd1,
+tableprint2[10, ] = c("Original", "Purity", purity_d_p$M1, purity_d_p$sd1, purity_d_p$M2, purity_d_p$sd1,
                     summary(purity_model_p)$tTable[2,4], summary(purity_model_p)$tTable[2,5],
@@
           note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
-          caption = "Study 2 Results - Multilevel Model",
+          caption = "News Source Results - Multilevel Model",
           col.names = c("Model", 
             "Foundation", "$M_C$", "$SD_C$", "$M_L$", 
-            "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
+            "$SD_L$", "$t$", "$p$", "$d_s$", "ICC"),
           format = "latex",
@@
 
-The results obtained in Study 2 fail to support the differences
+The results obtained in Study 2 fail to support most of the predicted differences
 predicted by MFT. First, differences between liberal and conservative
 news sources failed to reach statistical or practical (effect size)
-significance for any foundations. Second, looking purely at the
-direction of the differences, the results run completely contrary to the
-differences expected by MFT. Conservative sources scored higher on
-concern for harm and fairness while liberal sources scored higher on
-concern for loyalty, authority, and purity. Overall, the results lend
-strong support to the case against the MFD and weakens the case
-generally for MFT.
-
-However, one possible limitation of the current data is the generalness
+significance for nearly all foundations.
+One effect was in the predicted direction, with higher endorsement for purity words in the conservative sources.
+One possible limitation of the current data is the generalness
 of the corpus. The selection of the broad and amorphous topic of
@@
 shutdown in December 2018 through January 2019 over disagreements about
-funding a U.S.-Mexico border wall. Hence, Study 3 is the best test of
+funding a U.S.-Mexico border wall. Hence, Study 3 was an improved test of
 the MFT and the MFD in the context of partisan news.
@@
 
-In contrast to Study 2, we approached Study 3 with the intention to
-confirm the method employed was valid for the analysis of the scraped
-text as well as for any inferences drawn from the analyses. For the
-second study, we hypothesized that news sources perceived as liberal
-will exhibit positive endorsements of the individualizing moral
-foundations (*harm/care* and *fairness/reciprocity*) in their articles
-reporting on both the Kavanaugh confirmation hearing as well as the
-2018-2019 government shutdown. News sources perceived as conservative
-are hypothesized to positively endorse all five foundations equally in
-their coverage of the Kavanaugh hearing and the government shutdown. We
-tested the hypothesis by analyzing the content scraped from news
-sources' web pages spanning the two weeks before (September 13, 2018)
-and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing,
-owing to its prominence in the news. Likewise, we analyzed content
+We tested the same hypotheses as described in Study 2 by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, we analyzed content
 spanning two weeks before the start of the government shutdown (December
 8, 2018) to two weeks following the end of the shutdown (February 8,
-2019). The content will be analyzed for valence and moral alignment
-under MFT.
+2019).
 
@@
 ability to webscrape their contents without a subscription based
-service. Political articles referencing Brett Kavanaugh's nomination
-process were identified and subsequently scraped by including the URL
-for each source's coverage of the nomination in the *R* script.
+service.
 
@@
 individual articles from each of the aforementioned 10 news sources and
-compiled them together [@Wickham2016; @harrison_rselenium_2020]. Using
-this dataset, we identified word count and average word count per
-source. This process was run for articles pertaining to Kavanaugh's
-nomination that were published between September 13, 2018 and October
-11, 2018 inclusive. This date range was selected in reference to the
-widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and
-the end date at October 11 (two weeks after the hearing) so that we
+compiled them together [@Wickham2016; @harrison_rselenium_2020].
+Kavanaugh's widely-publicized and viewed nomination hearing was on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we
 could capture a large amount of data (roughly one month) during which
-Kavanaughnaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the
+Kavanaugh's nomination was at its peak saturation in news coverage. The same process was followed for scraping articles related to the
 partial U.S. Government shutdown of 2018-2019. The articles scraped were
@@
 
-As in Study 1 and 2, the text was scanned with *ngram* [@Schmidt2017]. Again,
-blank articles, text from the Disqus system, and duplicate articles were
-removed. The text was processed and stemmed in order to convert to a
-usable form for further analysis [@Feinerer2017]. Each individual word
-was reduced to its stem (i.e., *diseased* was stemmed to *diseas*). Once
-again, the same procedure was applied to the MFD words and the words in
-the @Warriner2013 dataset. We obtained the words' percent occurrence in
-the text. Percents were multiplied by *z*-scored valence and categorized
-into their proper MFD category.
+The data analysis used the same procedure as Study 1 for preparing the text, and the same weighting procedure described in Study 2 for creating valence scores.
 
@@
 harm_final_data_kav$valence[harm_final_data_kav$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
+#no spurn available
 ```
@@
 harm_final_data_gs$valence[harm_final_data_gs$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
-#no spurn avaliable
+#no spurn available
 ```
@@
 
-We utilized a multilevel model (MLM) to analyze if news sources
-leveraged different vocabularies based on target audience in the same
-manner as Study 2. Each foundation's weighted percentage was predicted
-by the source's political lean, using the individual source as a random
-intercept to control for the nested data structure. Two separate MLMs
-were constructed from datasets compiled for each topic of interest: the
-Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of
-a statistically significant effect for *harm/care*, but the practical
-effect denoted by Cohen's *d* was found to be small. There were no other
-significant or practical effects of political lean for any of the other
-four moral foundations. The effect for *harm/care* was in the
-hypothesized direction with liberal sources tending to use more
-positively *harm/care* words than conservative sources. Descriptive and
-test statistics, *p*-values and effect sizes (Cohen's *d*) can be found
-in Table \@ref(tab:exp2-tablekav).
+The same multilevel models were used to calculate the differences in news sources political lean across foundation areas using either valence weighted scoring or original MFD scoring (see Study 2 for model code).
+
+The pattern of results is nearly identical when examining $d_s$ scores for standardization, as the scorings are set on different scales (see Table \@ref(tab:exp2-tablekav)).
+A few significant results were found: 1) higher fairness scores for conservatives $d_s$ ~ .40s (both), 2) higher purity scores for conservatives $d_s$ ~ .47s (original score significant, weighted scores non-significant, but effect sizes were nearly identical).
+In general, the variance is a bit larger for the weighted scores, which may lead to the differences in traditional significance interpretations, and we advise examining effect sizes for interpretation.
+The rest of the effects were nearly zero.
 
@@
 #put in the numbers
-tableprint_kav[1, ] = c("Valence", "Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1,
+tableprint_kav[1, ] = c("Valence", "Harm", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1,
                     summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
                     harm_d_kav$d, icc(harm_icc_k, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[2, ] = c("Valence", "Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1,
+tableprint_kav[2, ] = c("Valence", "Fairness", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1,
                     summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
                     fair_d_kav$d, icc(fair_icc_k, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[3, ] = c("Valence", "Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1,
+tableprint_kav[3, ] = c("Valence", "Ingroup", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1,
                     summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
                     ingroup_d_kav$d, icc(ingroup_icc_k, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[4, ] = c("Valence", "Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1,
+tableprint_kav[4, ] = c("Valence", "Authority", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1,
                     summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
                     authority_d_kav$d, icc(authority_icc_k, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[5, ] = c("Valence", "Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1,
+tableprint_kav[5, ] = c("Valence", "Purity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1,
                     summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
@@
 
-tableprint_kav[6, ] = c("Original", "Harm/Care", harm_d_kav_p$M1, harm_d_kav_p$sd1, harm_d_kav_p$M2, harm_d_kav_p$sd1,
+tableprint_kav[6, ] = c("Original", "Harm", harm_d_kav_p$M1, harm_d_kav_p$sd1, harm_d_kav_p$M2, harm_d_kav_p$sd1,
                     summary(harm_model_kav_p)$tTable[2,4], summary(harm_model_kav_p)$tTable[2,5],
                     harm_d_kav_p$d, icc(harm_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[7, ] = c("Original", "Fairness/Reciprocity", fair_d_kav_p$M1, fair_d_kav_p$sd1, fair_d_kav_p$M2, fair_d_kav_p$sd1,
+tableprint_kav[7, ] = c("Original", "Fairness", fair_d_kav_p$M1, fair_d_kav_p$sd1, fair_d_kav_p$M2, fair_d_kav_p$sd1,
                     summary(fair_model_kav_p)$tTable[2,4], summary(fair_model_kav_p)$tTable[2,5],
                     fair_d_kav_p$d, icc(fair_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[8, ] = c("Original", "Ingroup/Loyalty", ingroup_d_kav_p$M1, ingroup_d_kav_p$sd1, ingroup_d_kav_p$M2, ingroup_d_kav_p$sd1,
+tableprint_kav[8, ] = c("Original", "Ingroup", ingroup_d_kav_p$M1, ingroup_d_kav_p$sd1, ingroup_d_kav_p$M2, ingroup_d_kav_p$sd1,
                     summary(ingroup_model_kav_p)$tTable[2,4], summary(ingroup_model_kav_p)$tTable[2,5],
                     ingroup_d_kav_p$d, icc(ingroup_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[9, ] = c("Original", "Authority/Respect", authority_d_kav_p$M1, authority_d_kav_p$sd1, authority_d_kav_p$M2, authority_d_kav_p$sd1,
+tableprint_kav[9, ] = c("Original", "Authority", authority_d_kav_p$M1, authority_d_kav_p$sd1, authority_d_kav_p$M2, authority_d_kav_p$sd1,
                     summary(authority_model_kav_p)$tTable[2,4], summary(authority_model_kav_p)$tTable[2,5],
                     authority_d_kav_p$d, icc(authority_icc_k_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_kav[10, ] = c("Original", "Purity/Sanctity", purity_d_kav_p$M1, purity_d_kav_p$sd1, purity_d_kav_p$M2, purity_d_kav_p$sd1,
+tableprint_kav[10, ] = c("Original", "Purity", purity_d_kav_p$M1, purity_d_kav_p$sd1, purity_d_kav_p$M2, purity_d_kav_p$sd1,
                     summary(purity_model_kav_p)$tTable[2,4], summary(purity_model_kav_p)$tTable[2,5],
@@
 apa_table(as.data.frame(tableprint_kav),
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
+          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively.",
           caption = "Kavanaugh Results - Multilevel Model",
           col.names = c("Model",
-            "Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
+            "Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d_s$", "ICC"),
           format = "latex",
@@
           font_size = 'footnotesize',
-          placement = "h"
+          placement = "ht"
           ) 
@@
 For news articles about the partial U.S. Federal Government Shutdown of
-2018-2019, there were no significant or practical effects of political
-lean for the moral foundations (see Table \@ref(tab:exp2-tablegs)). A
-small-to-medium effect size was observed for *authority/respect*. The
-effect was in the predicted direction as well, as conservative sources
-tended to offer more positive endorsements of the foundation than
-liberal sources. This effect was similar to Study 2 in which the largest
-effect size was observed for *authority/respect*. As noted before, the
-effect found in Study 2 was in the opposite direction as what was
-hypothesized. Thus, it is difficult to draw comparisons between the two
-studies despite the similar pattern for effect size. Owing to a lack of
-similar effects for either Study 2 or the Kavanaugh topic, there is
-doubt as to whether or not a practical or generalized effect exists for
-*authority/respect*.
-
-Based on the weighted percent values for the five foundations applied to
-both topics, MFD words seem to make up little of the article text. A
-similar pattern was observed for the results in Study 2. As in Study 2,
-the percentages and means seem to indicate a generally positive
-endorsement of all five moral foundations across both political
-leanings.
+2018-2019, only one significant effect was found (see Table \@ref(tab:exp2-tablegs)).
+The original scoring for fairness indicated that conservatives endorsed more fairness related words $d_s$ = 0.75.
+The valence weighted scoring showed the same effect size $d_s$ = 0.74, but was non-significant in traditional null hypothesis testing interpretations.
+Both effects would be considered large and in line with previous findings, *except* in the opposition direction of predicted results.
+The same large effects can be found for the purity foundation $d_s$ = 0.85 (both), in the expected direction that conservative sources endorsed more purity words than liberal sources.
 
@@
 #put in the numbers
-tableprint_gs[1, ] = c("Valence", "Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1,
+tableprint_gs[1, ] = c("Valence", "Harm", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1,
                     summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
                     harm_d_gs$d, icc(harm_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_gs[2, ] = c("Valence", "Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1,
+tableprint_gs[2, ] = c("Valence", "Fairness", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1,
                     summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
                     fair_d_gs$d, icc(fair_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_gs[3, ] = c("Valence", "Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1,
+tableprint_gs[3, ] = c("Valence", "Ingroup", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1,
                     summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
                     ingroup_d_gs$d, icc(ingroup_icc_gs)$ICC_unadjusted)
-tableprint_gs[4, ] = c("Valence", "Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1,
+tableprint_gs[4, ] = c("Valence", "Authority", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1,
                     summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
                     authority_d_gs$d, icc(authority_icc_gs, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_gs[5, ] = c("Valence", "Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1,
+tableprint_gs[5, ] = c("Valence", "Purity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1,
                     summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
@@
 
-tableprint_gs[6, ] = c("Original", "Harm/Care", harm_d_gs_p$M1, harm_d_gs_p$sd1, harm_d_gs_p$M2, harm_d_gs_p$sd1,
+tableprint_gs[6, ] = c("Original", "Harm", harm_d_gs_p$M1, harm_d_gs_p$sd1, harm_d_gs_p$M2, harm_d_gs_p$sd1,
                     summary(harm_model_gs_p)$tTable[2,4], summary(harm_model_gs_p)$tTable[2,5],
                     harm_d_gs_p$d, icc(harm_icc_gs_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_gs[7, ] = c("Original", "Fairness/Reciprocity", fair_d_gs_p$M1, fair_d_gs_p$sd1, fair_d_gs_p$M2, fair_d_gs_p$sd1,
+tableprint_gs[7, ] = c("Original", "Fairness", fair_d_gs_p$M1, fair_d_gs_p$sd1, fair_d_gs_p$M2, fair_d_gs_p$sd1,
                     summary(fair_model_gs_p)$tTable[2,4], summary(fair_model_gs_p)$tTable[2,5],
                     fair_d_gs_p$d, icc(fair_icc_gs_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_gs[8, ] = c("Original", "Ingroup/Loyalty", ingroup_d_gs_p$M1, ingroup_d_gs_p$sd1, ingroup_d_gs_p$M2, ingroup_d_gs_p$sd1,
+tableprint_gs[8, ] = c("Original", "Ingroup", ingroup_d_gs_p$M1, ingroup_d_gs_p$sd1, ingroup_d_gs_p$M2, ingroup_d_gs_p$sd1,
                     summary(ingroup_model_gs_p)$tTable[2,4], summary(ingroup_model_gs_p)$tTable[2,5],
                     ingroup_d_gs_p$d, icc(ingroup_icc_gs_p)$ICC_unadjusted)
-tableprint_gs[9, ] = c("Original", "Authority/Respect", authority_d_gs_p$M1, authority_d_gs_p$sd1, authority_d_gs_p$M2, authority_d_gs_p$sd1,
+tableprint_gs[9, ] = c("Original", "Authority", authority_d_gs_p$M1, authority_d_gs_p$sd1, authority_d_gs_p$M2, authority_d_gs_p$sd1,
                     summary(authority_model_gs_p)$tTable[2,4], summary(authority_model_gs_p)$tTable[2,5],
                     authority_d_gs_p$d, icc(authority_icc_gs_p, tolerance = 1e-10)$ICC_unadjusted)
-tableprint_gs[10, ] = c("Original", "Purity/Sanctity", purity_d_gs_p$M1, purity_d_gs_p$sd1, purity_d_gs_p$M2, purity_d_gs_p$sd1,
+tableprint_gs[10, ] = c("Original", "Purity", purity_d_gs_p$M1, purity_d_gs_p$sd1, purity_d_gs_p$M2, purity_d_gs_p$sd1,
                     summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
@@
 apa_table(as.data.frame(tableprint_gs),
-          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
+          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively.",
           caption = "Government Shutdown Results - Multilevel Model",
           col.names = c("Model", 
-            "Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$", "ICC"),
+            "Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d_s$", "ICC"),
           format = "latex",
@@
 
-The results obtained in Study 3 are slightly more in line with
-expectations from MFT, however, in all but one case, the differences
-were not statistically significant. The only statistically significant
-difference was in the harm foundation; liberals did endorse harm more
-than conservatives during the Kavanaugh hearings, but the effect was
-smaller than expected given @Graham2009. Generally for both the
-Kavanaugh hearings and the Government shutdown, the differences were in
-the expected direction (liberals endorsing harm more and conservatives
-endorsing authority and loyalty more), but the differences were not
-statistically significant and the practical effects much smaller than
-reported in @Graham2009. While not significant, fairness was endorsed
-more by conservatives in both cases. In contrast, purity was endorsed
-more by conservatives for the government shutdown, but more by liberals
-for the Kavanaugh hearing though neither difference was statistically
-significant.
-
-Together with Study 2 and past work, Study 3 further calls into question
-the usefulness and efficacy of the Moral Foundations as well as cast
-doubt on the predictions made by MFT. One issue that Study 3 brings up
-is that moral differences between liberals and conservatives may be
-moderated by a number of factors as shown in @Sterling2018. For example,
-here we have liberals concerned with purity for the Kavanaugh hearings
-(a moral bad for liberals and a moral good for conservatives) and
-conservatives concerned with purity during the government shutdown (a
-moral bad for conservatives and a moral good for liberals). The original
-predictions made by the Moral Foundations are very simplistic and likely
-much more complex in reality.
+The results obtained in Study 3 portrayed that focused news sources may provide a bit more evidence for the MFD to assess MFT's predictions, at least for purity.
+This result showed a large effect, and depending on the scoring, sometimes the traditional significance matching results from @Graham2009.
+The results for fairness were in the opposite direction of expectations, given the MFT and previous studies, where we found that conservatives endorsed more fairness words than liberal sources.
+Study 2 and 3's results indicated that the effect sizes will likely be similar for either the traditional percent or weighted scoring, as they are nearly identical in each study.
+We suggest using the simpler percent scoring, which can be calculated with both programming software *R* and point and click software LIWC [@Pennebaker2007].
 
@@
 Several dictionary improvements were suggested, but the results of a multi-trait multi-method analysis indicate that the MFD does not relate to the moral foundations found in the MFD.
-Therefore, we did not find support for the use of the MFD in relation to the MFT using a convergent and divergent validity technique.
+Therefore, we did not find support for the use of the MFD in relation to the MFQ using a convergent and divergent validity technique.
 
 In Study 2 and 3, we attempted to
-devise a method leveraging the MFD in order to quantify
-political bias stemming from content published by several prominent
-American news sources. In Study 2, the results obtained were not
-significant in any statistical or practical sense. There was a small
-effect found for the *authority/respect* foundation according to Cohen's
-*d*, but the effect suggested endorsement for that foundation opposite
-to what was hypothesized. In Study 3, the direction of the differences
-were generally in line with MFT, however, the difference were very small
-and lacks statistically significance. Building on @Frimer2020 and other
-critiques of MFT and the MFD, we show that MFD is not a useful tool for
-measuring moral language while also calling into question the validity
-of MFT in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive,
-we still retain confidence in the overall structure of the methodology
-established in the current study. Specifically, the procedure for
-scraping text from the web, processing, stemming, and weighting the
-scores with valence seems to represent a solid method for preparing a
-high quantity of text passages for data analysis. We implemented valence
-as an indicator of the directionality of endorsement due to the inherent
-ambiguity of simply calculating MFD word percent occurrence. This method
-served both to augment the face validity of the MFD by incorporating
-valence (thus reducing ambiguity) and to generate a score that is easy
-to understand and analyze.
-
-However, political lean and other important political/moral constructs
+devise a method leveraging the MFD and valence weighting in order to replicate previous effects on political bias stemming from content published by several prominent American news sources.
+In Study 2, we only discovered a small effect for purity, while all other results obtained were not
+significant in any statistical or practical sense.
+This result was replicated in Study 3 with a larger effect size, along with differences found in fairness, albeit in the opposite direction than predicted.
+Building on @Frimer2020 and other critiques of MFT and the MFD, we show that MFD may not yet be a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
+
+The results from different proposed scoring methods remained consistent with the original percent scoring method.
+This scoring may provide insight into the sentiment of the texts.
+For example, the harm foundation is considered a continuum ranging from harm to care.
+The results from Study 2 and 3 indicate that the MFD likely measures more harm than care across the continuum in our sources.
+In general, given that the weighted valence scoring requires more sophisticated programming skills to implement, we suggest using the original scoring of the MFD with all results taken together.
+
+Political lean and other important political/moral constructs
 may be communicated through methods other than through the use of
@@
 
-In critiquing MFT, @Schein2015 proposed an alternative theory explaining
+In critiquing the MFT, @Schein2015 proposed an alternative theory explaining
 moral choices and potential partisan differences: Dyadic Theory of
@@
 harm-focused morality where someone/thing is harmed by someone/thing
-else [@Gray2014, @Schein2015]. Rather than liberals and conservatives
+else [@Gray2014; @Schein2015]. Rather than liberals and conservatives
 having difference conceptions of morality, dyadic morality argues that

### 2024-11-30 manuscript_version/revision/manuscript_metapsych_revision.tex
finalizing the revision letter and manuscript

@@
 Government Shutdown of 2018-2019.
-Once again, no significant differences in moral endorsements were found.
-Together with past work, the results shed doubt on the validity of the MFD as a reliable measurement tool.
+Results from all studies indicate that the MFD may not consistently show exptected partisan differences, shedding doubt on the usefulness of the MFD.
 }
@@
 
-Haidt and Joseph {[}-@haidt2004{]} and Haidt and Graham (2007)
+Haidt and Joseph (2004) and Haidt and Graham (2007)
 formulated MFT as a method by which to capture the entirety of humans'
@@
 domain can be mapped by quantifying their endorsement of five moral
-foundations: \emph{harm/care}, \emph{fairness/reciprocity}, \emph{ingroup/loyalty},
-\emph{authority/respect}, and \emph{purity/sanctity} (Haidt \& Graham, 2007). Thus, they
+foundations: harm/care, fairness/reciprocity, ingroup/loyalty,
+authority/respect, and purity/sanctity (Haidt \& Graham, 2007). Thus, they
 proposed that the addition of these two additional domains could
-adequately capture the broader spectrum of morality.
+adequately capture the broader spectrum of morality. Throughout the rest of the article, we will use the first word from each of these continuums to denote the foundation area.
 
@@
 designed to capture language's role in moral reasoning and justification
-as used in speech and text (Graham et al., 2009, 2011a). The MFQ is a
+as used in speech and text (Graham et al., 2009, 2011). The MFQ is a
 30-item scale with 15 items on the moral relevance and judgment
@@
 relevant}). These relevance items include examples such as: ``Whether or
-not someone used violence (\emph{harm}),'' ``Whether or not someone was denied
-his or her rights (\emph{fairness}),'' ``Whether or not someone showed a lack
-of loyalty (\emph{ingroup}),'' ``Whether or not an action caused chaos or
-disorder (\emph{authority}),'' and ``Whether or not someone did something
-disgusting (\emph{purity}).'' The moral judgments items are also equally
+not someone used violence (harm),'' ``Whether or not someone was denied
+his or her rights (fairness),'' ``Whether or not someone showed a lack
+of loyalty (ingroup),'' ``Whether or not an action caused chaos or
+disorder (authority),'' and ``Whether or not someone did something
+disgusting (purity).'' The moral judgments items are also equally
 divided between the foundations and ask on a six-point scale how much
@@
 ``One of the worst things a person can do is hurt a defenseless animal
-(\emph{harm}),'' ``Justice is the most important requirement of a society
-(\emph{fairness}),'' ``I am proud of my country's history (\emph{ingroup}),'' ``Men
-and women each have different roles to play in society (\emph{authority}),''
-and ``Chastity is an important and valuable virtue (\emph{purity}).''
-
-The internal consistency of the MFQ from Graham et al. (2011b) was \(\alpha\) = .73
+(harm),'' ``Justice is the most important requirement of a society
+(fairness),'' ``I am proud of my country's history (ingroup),'' ``Men
+and women each have different roles to play in society (authority),''
+and ``Chastity is an important and valuable virtue (purity).''
+
+The internal consistency of the MFQ from Graham et al. (2011) was \(\alpha\) = .73
 averaged across subscales with a range of \(\alpha\) = .65-.84. Across six
 studies, the MFQ was found to have an average Cronbach's alpha of .63
-for \emph{harm}, .64 for \emph{fairness}, .56 for \emph{ingroup}, .59 for \emph{authority},
-and .71 for \emph{purity} (Federico, Weber, Ergun, \& Hunt, 2013; Graham et al., 2009; Graham, Nosek, \& Haidt, 2012; Weber \& Federico, 2013).
+for harm, .64 for fairness, .56 for ingroup, .59 for authority,
+and .71 for purity (Federico, Weber, Ergun, \& Hunt, 2013; Graham et al., 2009; Graham, Nosek, \& Haidt, 2012; Weber \& Federico, 2013).
 Test-retest reliability was \emph{r} = .68-.82 using a sample of
 123 college students. Confirmatory factor analysis supported a
-well-fitted five-factor model (\emph{harm/care}, \emph{fairness/reciprocity},
-\emph{ingroup/loyalty}, \emph{authority/respect}, and \emph{purity/sanctity}) over two,
-individual (\emph{harm} and \emph{fairness}) versus group (\emph{ingroup}, \emph{authority},
-and \emph{purity}) foundations, or three, autonomy (\emph{harm}, \emph{fairness}),
-community (\emph{ingroup}, \emph{authority}), and divinity (\emph{purity}) ethics,
+well-fitted five-factor model (harm, fairness,
+ingroup, authority, and purity) over two,
+individual (harm and fairness) versus group (ingroup, authority,
+and purity) foundations, or three, autonomy (harm, fairness),
+community (ingroup, authority), and divinity (purity) ethics,
 foundations factor model. The five-factor structure also fit for
@@
 generalizability. Convergent validity was supported with correlations on
-other measures of morality (Graham et al., 2011b).
+other measures of morality (Graham et al., 2011).
 
@@
 that they believed would be associated with the five foundations. Words
-such as \emph{war} and \emph{peace} should indicate a greater concern with \emph{harm}
+such as \emph{war} and \emph{peace} should indicate a greater concern with harm
 foundation whereas words such as \emph{homeland} and \emph{terrorism} should
-indicate a greater concern with the \emph{ingroup} foundation. The other
-foundation dictionaries include \emph{equal} and \emph{justice} (\emph{fairness}),
-\emph{honor} and \emph{protest} (\emph{authority}), and \emph{holy} and \emph{sin} (\emph{purity}). To
+indicate a greater concern with the ingroup foundation. The other
+foundation dictionaries include \emph{equal} and \emph{justice} (fairness),
+\emph{honor} and \emph{protest} (authority), and \emph{holy} and \emph{sin} (purity). To
 validate the word sets, Graham et al. (2009) examined the frequency of MFD words
 in liberal and conservative sermons using the Linguistic Inquiry and
-Word Count {[}LIWC; Pennebaker, Booth, and Frances (2007){]} computer program. They found liberal
-ministers used \emph{harm}, \emph{fairness}, and \emph{ingroup} words more often than
-conservative ministers who used \emph{authority} and \emph{purity} words more
+Word Count (LIWC, Pennebaker, Booth, \& Frances, 2007) computer program. They found liberal
+ministers used harm, fairness, and ingroup words more often than
+conservative ministers who used authority and purity words more
 often. Although conservative ministers were expected to use more
-\emph{ingroup} words based on political ideology and previous research, an
-examination of the way liberal ministers used \emph{ingroup} words revealed a
-tendency for the use of \emph{ingroup} words to glorify rebellion and promote
-independence (i.e., the opposite direction from \emph{ingroup} definitions).
+ingroup words based on political ideology and previous research, an
+examination of the way liberal ministers used ingroup words revealed a
+tendency for the use of ingroup words to glorify rebellion and promote
+independence (i.e., the opposite direction from ingroup definitions).
 Effect sizes indicated relatively sizable difference between liberal and
-conservative sermons with Cohen's \emph{d} values ranging from 0.56 to 1.27.
+conservative sermons with Cohen's \(d_s\) values ranging from 0.56 to 1.27.
 
@@
 1987-2007. After 9-11, the number of moral words associated with the
-World Trade Center increased, specifically \emph{harm} words from the MFD.
+World Trade Center increased, specifically harm words from the MFD.
 Second, they considered the changes in how moral words were paired with
@@
 overall; more specifically, Republicans tended to use more words
-associated with the \emph{purity} foundation; while Democrats used more words
-associated with the \emph{fairness} foundation.
+associated with the purity foundation; while Democrats used more words
+associated with the fairness foundation.
 
@@
 the foundations are sufficiently distinct as to stand as their own
-foundation. Likewise, Gray and Keeney (2015) argues that the measurement of the moral
+foundation. Likewise, Gray and Keeney (2015) argued that the measurement of the moral
 foundations confounds morality with other constructs (such as weirdness)
-and the moral foundations lack statistical and conceptual distinction.
-Schein and Gray (2015) argues that harm-based morality is the most parsimonious and
+and that the moral foundations lack statistical and conceptual distinction.
+Schein and Gray (2015) argued that harm-based morality is the most parsimonious and
 logical explanation for MFT findings.
@@
 results in terms of supporting MFT (Clifford \& Jerit, 2013; Frimer, Tell, \& Haidt, 2015; Sagi \& Dehghani, 2014). Like Frimer (2020), we attempt to give the MFD the best chance
-for success by incorporating a weighting method to address the
+for success by both increasing linguistic content and incorporating a weighting method to address the
 skewedness and sparsity of the linguistic data.
@@
 categories: human annotations and semantic representations. Hopp, Fisher, Cornell, Huskey, and Weber (2021)
-represents the first approach where instead of relying on `experts', a
+assessed the first approach where instead of relying on `experts', a
 large sample of lay people were crowdsourced to manually annotate
@@
 and judge moral issues in everyday life leading to a more ecologically
-valid dictionary. Garten, Boghrati, Hoover, Johnson, and Dehghani (2016) represents the second categories which
+valid dictionary. Garten, Boghrati, Hoover, Johnson, and Dehghani (2016) examined the second category which
 instead relies on data-driven semantic analysis. Using shallow neural
@@
 between these two sources, as well as the latent traits after
-controlling for the overlap. Using the results from this study, we
+controlling for method-related measurement. Using the results from this study, we
 examined two conceptual replications of Frimer (2020). We test the
@@
 
-Each of the foundation pairs were listed together (i.e., \emph{harm/care},
-\emph{fairness/reciprocity,} etc.) with a space for participants to list
+Each of the foundation pairs were listed together (i.e., harm,
+fairness, etc.) with a space for participants to list
 their free association concepts. After the free association task,
@@
 
-Participant data was first spell checked and screening for inaccurate
-responses. Participants who did not write more than fifty words in
+Participants who did not write more than fifty words in
 response to a given prompt were excluded (\emph{n} =
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 
@@
 The fit indices from these models indicate that all models showed good fit.
-The original and complete MFD models showed equal fit (\(\Delta\) CFA \textless= .01), and both models were better than the reduced MFD model.
+The original and complete MFD models showed equal fit (\(\Delta\) CFI \textless= .01), and both models were better than the reduced MFD model.
 We then inspected the loadings to determine the adequacy of the loadings for the MFQ and MFD.
 These results are shown in Table \ref{tab:mtmm-model1-table2}.
-All but one question for the MFQ load adequately (\textgreater.30) on each of their moral foundation areas.
+All but one question for the MFQ load adequately (\textgreater.30; \emph{denied rights}) on each of their moral foundation areas.
 None of the MFD areas load onto their moral foundation area, as all loadings are close to zero (and non-significant, see online).
@@
 
-\caption{\label{tab:mtmm-model1-table2}MTMM Fit Estimates for Model 1 Loadings}
+\caption{\label{tab:mtmm-model1-table2}MTMM Parameter Estimates for Model 1 Loadings}
 
@@
 \midrule
-Harm & 1 & 0.61 & 0.61 & 0.61\\
-Harm & 2 & 0.70 & 0.69 & 0.69\\
-Harm & 3 & 0.38 & 0.37 & 0.36\\
+Harm & Emotional Suffering & 0.61 & 0.61 & 0.61\\
+Harm & Cared for Weak & 0.70 & 0.69 & 0.69\\
+Harm & Cruel & 0.38 & 0.37 & 0.36\\
 Harm & MFD & -0.05 & -0.03 & -0.05\\
-Fair & 1 & 0.76 & 0.76 & 0.77\\
-Fair & 2 & 0.52 & 0.50 & 0.50\\
-Fair & 3 & 0.23 & 0.22 & 0.22\\
+Fair & Treated Differently & 0.76 & 0.76 & 0.77\\
+Fair & Acted Unfairly & 0.52 & 0.50 & 0.50\\
+Fair & Denied Rights & 0.23 & 0.22 & 0.22\\
 Fair & MFD & -0.01 & 0.10 & 0.05\\
-Ingroup & 1 & 0.63 & 0.63 & 0.63\\
-Ingroup & 2 & 0.73 & 0.72 & 0.73\\
-Ingroup & 3 & 0.82 & 0.81 & 0.81\\
+Ingroup & Love for Country & 0.63 & 0.63 & 0.63\\
+Ingroup & Betray Group & 0.73 & 0.72 & 0.73\\
+Ingroup & Lack of Loyalty & 0.82 & 0.81 & 0.81\\
 Ingroup & MFD & -0.10 & 0.03 & 0.05\\
-Authority & 1 & 0.81 & 0.80 & 0.81\\
-Authority & 2 & 0.72 & 0.72 & 0.72\\
-Authority & 3 & 0.42 & 0.41 & 0.41\\
+Authority & Lack of Respect & 0.81 & 0.80 & 0.81\\
+Authority & Conformed to Tradition & 0.72 & 0.72 & 0.72\\
+Authority & Chaos or Disorder & 0.42 & 0.41 & 0.41\\
 Authority & MFD & 0.06 & 0.00 & -0.04\\
-Purity & 1 & 0.71 & 0.71 & 0.71\\
-Purity & 2 & 0.67 & 0.67 & 0.67\\
-Purity & 3 & 0.64 & 0.64 & 0.64\\
+Purity & Purity and Decency & 0.71 & 0.71 & 0.71\\
+Purity & Disgusting & 0.67 & 0.67 & 0.67\\
+Purity & Acted God & 0.64 & 0.64 & 0.64\\
 Purity & MFD & 0.06 & -0.05 & -0.11\\
@@
 indicating endorsements of the individualizing moral foundations
-(\emph{harm/care} and \emph{fairness/reciprocity}). Additionally, we hypothesized
-the two sources generally perceived to be conservative leaning (\emph{Fox News}
-and \emph{Breitbart}) would feature MFD words and valences indicating
-equal endorsement of all five foundations.
+(harm and fairness), and thus, higher foundation scores in this area than conservative sources (Sagi \& Dehghani, 2014).
+Additionally, we hypothesized that the two sources generally perceived to be conservative leaning (\emph{Fox News} and \emph{Breitbart}) would feature MFD words and valences with higher scores in the authority and purity areas.
+Given the previously mixed results of ingroup, we do not make a directional prediction (Frimer, 2020).
 
@@
 investigation, we found another, more robust URL for political content
-from NPR: their politics content ``archive.'' The page structure on NPR's
+from NPR: their politics content archive. The page structure on NPR's
 website was such that only a limited selection of articles is displayed
@@
 
-\subsubsection{Data analysis}\label{data-analysis}
-
-Once data collection ended, the text was scanned using the \emph{ngram}
-package in \emph{R} (Schmidt, Gonzalez-Cabrera, \& Tomasello, 2017). This package includes a word count
-function, which was used to remove articles that came through as blank
-text, as well as to eliminate text picked up from the Disqus commenting
-system used by certain websites. At this point, duplicate articles were
-discarded.
-
-The article text was processed using the \emph{tm} and \emph{ngram} packages in
-\emph{R} in order to render the text in lowercase, remove punctuation, and
-fix spacing issues (Feinerer \& Hornik, 2017). The individual words were then
-reduced to their stems (i.e., \emph{abused} was stemmed to \emph{abus}). The same
-procedure was applied to the MFD words and the words in the
-Warriner, Kuperman, and Brysbaert (2013) dataset. Using the Warriner et al. (2013) dictionary, the words
-making up each of the five foundations in the MFD were matched to their
-respective valence value.
-
-The Warriner et al. (2013) data includes nearly 14,000 English lemmas that have
+\subsubsection{Data Analysis}\label{data-analysis}
+
+Once data collection ended, the text sources and Warriner, Kuperman, and Brysbaert (2013) dataset were processed as described in Study 1.
+The words making up each of the five foundations in the MFD were matched to their respective valence value.
+The Warriner et al.
+(2013) data includes nearly 14,000 English lemmas that have
 been rated for their valence, arousal, and dominance (mirroring Bradley \& Lang, 1999). Word emotion ratings have been used to estimate the
@@
 also suggest using the larger complete dataset, given that the CFI indicated
-similar models, and we note here that the pattern of results do not change
-if that dictionary is used instead. The total number of times each of those words
+similar models. The total number of times each of those words
 was used in an article was calculated. This information was merged with
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Concepts were stemmed to match datasets.}
+\normalsize{\textit{Note.} Concepts were stemmed to match datasets. The frequency was divided by the total numbers and then multiply by valence and 100 to create percent weighted scores.}
 \end{tablenotes}
@@
 \subsection{Results}\label{results-3}
+
+Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's
+\(d_s\)) can be found in Table \ref{tab:exp1-table}. To interpret the
+weighted scores, one can examine the mean and standard deviations for
+each. A zero score for the mean, with a non-zero standard deviation,
+would indicate a perfect balance of positive and negative words in each
+category, likely representing a neutral sentiment when all words are
+considered. Negative percentages would indicate more representation of
+the negative words in the MFD area, while positive percentages indicate
+an endorsement of the positive words in a MFD. Therefore, we suggest
+using the sign of the mean score to determine the directionality of the
+endorsement for the MFD (positive, neutral, negative), and the standard
+deviation to ensure that a zero score is not zero endorsement (i.e., a
+SD of zero indicates no words were used).
 
@@
 sources as a random intercept to control for the structure of the data.
-Therefore, the models were calculated by: Weighted Score \textasciitilde{} Political
-Lean + (\textasciitilde1\textbar Source).
-
-The multilevel model did not indicate the presence of any significant or
-practical effect of political lean for any of the five moral
-foundations. The strongest effect size was observed for the
-\emph{authority/respect} foundation, but the effect was in the opposite
-direction from what was originally hypothesized - liberal sources tended
-to use more \emph{authority/respect} words than did conservative sources.
-Descriptive and test statistics, \emph{p}-values and effect sizes (Cohen's
-\emph{d}) can be found in Table \ref{tab:exp1-table}. To interpret the
-weighted scores, one can examine the mean and standard deviations for
-each. A zero score for the mean, with a non-zero standard deviation,
-would indicate a perfect balance of positive and negative words in each
-category, likely representing a neutral tone when all words are
-considered. Negative percentages would indicate more representation of
-the negative words in the MFD area, while positive percentages indicate
-an endorsement of the positive words in a MFD. Therefore, we suggest
-using the sign of the mean score to determine the directionality of the
-endorsement for the MFD (positive, neutral, negative), and the standard
-deviation to ensure that a zero score is not zero endorsement (i.e., a
-SD of zero indicates no words were used). Based on the weighted percent
-values for the five foundations, we observed that MFD words seem to make
-up a small portion of the article text. Furthermore, the observed
-percentages and means appear to indicate a generally positive
-endorsement of all five foundations across both liberal and conservative
-sources.
-
-\begin{table}[h]
+Therefore, the models were calculated by: \texttt{Weighted\ Score\ (or\ Original\ Percent\ Score)\ \textasciitilde{}\ Political\ Lean\ +\ (\textasciitilde{}1\textbar{}Source)}.
+Both the valence weighted scores and original MFD scores were used as dependent variables to compare results across different scorings of the MFD.
+The multilevel model did not indicate the presence of any significant effects for political lean for any of the five moral
+foundations.
+The effect sizes (\(d_s\)) appear to show a similar pattern of results, but given that most are close to zero, it is difficult to know if these two scoring systems showed similar results or these results were simply null effects.
+The original scoring shows a small effect size for purity (considering that previous effect sizes reported were .50+, we considered .20 small) in the expected direction.
+
+\begin{table}[ht]
 
@@
 
-\caption{\label{tab:exp1-table}Study 2 Results - Multilevel Model}
+\caption{\label{tab:exp1-table}News Source Results - Multilevel Model}
 
@@
 \toprule
-Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
+Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d_s$ & ICC\\
 \midrule
-Valence & Harm/Care & -0.49 & 1.26 & -0.44 & 1.26 & 0.50 & .668 & -0.04 & .001\\
-Valence & Fairness/Reciprocity & 0.47 & 0.64 & 0.44 & 0.64 & -1.23 & .344 & 0.05 & < .001\\
-Valence & Ingroup/Loyalty & 0.39 & 0.49 & 0.38 & 0.49 & -0.58 & .620 & 0.02 & < .001\\
-Valence & Authority/Respect & 0.09 & 0.49 & 0.07 & 0.49 & -1.25 & .338 & 0.05 & < .001\\
-Valence & Purity/Sanctity & 0.19 & 0.53 & 0.13 & 0.53 & -2.77 & .109 & 0.10 & .001\\
-Original & Harm/Care & 0.55 & 0.60 & 0.50 & 0.60 & -1.84 & .207 & 0.07 & < .001\\
-Original & Fairness/Reciprocity & 0.46 & 0.49 & 0.41 & 0.49 & -2.57 & .124 & 0.10 & .003\\
-Original & Ingroup/Loyalty & 0.63 & 0.64 & 0.68 & 0.64 & 1.83 & .208 & -0.07 & .002\\
-Original & Authority/Respect & 0.67 & 0.70 & 0.60 & 0.70 & -2.28 & .150 & 0.09 & < .001\\
-Original & Purity/Sanctity & 0.17 & 0.32 & 0.11 & 0.32 & -3.78 & .064 & 0.20 & .009\\
+Valence & Harm & -0.49 & 1.26 & -0.44 & 1.26 & 0.50 & .668 & -0.04 & .001\\
+Valence & Fairness & 0.47 & 0.64 & 0.44 & 0.64 & -1.23 & .344 & 0.05 & < .001\\
+Valence & Ingroup & 0.39 & 0.49 & 0.38 & 0.49 & -0.58 & .620 & 0.02 & < .001\\
+Valence & Authority & 0.09 & 0.49 & 0.07 & 0.49 & -1.25 & .338 & 0.05 & < .001\\
+Valence & Purity & 0.19 & 0.53 & 0.13 & 0.53 & -2.77 & .109 & 0.10 & .001\\
+Original & Harm & 0.55 & 0.60 & 0.50 & 0.60 & -1.84 & .207 & 0.07 & < .001\\
+Original & Fairness & 0.46 & 0.49 & 0.41 & 0.49 & -2.57 & .124 & 0.10 & .003\\
+Original & Ingroup & 0.63 & 0.64 & 0.68 & 0.64 & 1.83 & .208 & -0.07 & .002\\
+Original & Authority & 0.67 & 0.70 & 0.60 & 0.70 & -2.28 & .150 & 0.09 & < .001\\
+Original & Purity & 0.17 & 0.32 & 0.11 & 0.32 & -3.78 & .064 & 0.20 & .009\\
 \bottomrule
@@
 
-In contrast to Study 2, we approached Study 3 with the intention to
-confirm the method employed was valid for the analysis of the scraped
-text as well as for any inferences drawn from the analyses. For the
-second study, we hypothesized that news sources perceived as liberal
-will exhibit positive endorsements of the individualizing moral
-foundations (\emph{harm/care} and \emph{fairness/reciprocity}) in their articles
-reporting on both the Kavanaugh confirmation hearing as well as the
-2018-2019 government shutdown. News sources perceived as conservative
-are hypothesized to positively endorse all five foundations equally in
-their coverage of the Kavanaugh hearing and the government shutdown. We
-tested the hypothesis by analyzing the content scraped from news
-sources' web pages spanning the two weeks before (September 13, 2018)
-and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing,
-owing to its prominence in the news. Likewise, we analyzed content
+We tested the same hypotheses as described in Study 2 by analyzing the content scraped from news sources' web pages spanning the two weeks before (September 13, 2018) and two weeks after (October 11, 2018) Kavanaugh's confirmation hearing, owing to its prominence in the news.
+Likewise, we analyzed content
 spanning two weeks before the start of the government shutdown (December
 8, 2018) to two weeks following the end of the shutdown (February 8,
-2019). The content will be analyzed for valence and moral alignment
-under MFT.
+2019).
 
@@
 ability to webscrape their contents without a subscription based
-service. Political articles referencing Brett Kavanaugh's nomination
-process were identified and subsequently scraped by including the URL
-for each source's coverage of the nomination in the \emph{R} script.
+service.
 
@@
 individual articles from each of the aforementioned 10 news sources and
-compiled them together (Harrison \& Kim, 2020; Wickham, 2016). Using
-this dataset, we identified word count and average word count per
-source. This process was run for articles pertaining to Kavanaugh's
-nomination that were published between September 13, 2018 and October
-11, 2018 inclusive. This date range was selected in reference to the
-widely-publicized and viewed nomination hearing on September 27, 2018.
-We set the start date at September 13 (two weeks before the hearing) and
-the end date at October 11 (two weeks after the hearing) so that we
+compiled them together (Harrison \& Kim, 2020; Wickham, 2016).
+Kavanaugh's widely-publicized and viewed nomination hearing was on September 27, 2018.
+We set the start date at September 13 (two weeks before the hearing) and the end date at October 11 (two weeks after the hearing) so that we
 could capture a large amount of data (roughly one month) during which
-Kavanaughnaugh's nomination was at its peak saturation in news coverage.
-
-The same process was followed for scraping articles related to the
+Kavanaugh's nomination was at its peak saturation in news coverage. The same process was followed for scraping articles related to the
 partial U.S. Government shutdown of 2018-2019. The articles scraped were
@@
 
-As in Study 1 and 2, the text was scanned with \emph{ngram} (Schmidt et al., 2017). Again,
-blank articles, text from the Disqus system, and duplicate articles were
-removed. The text was processed and stemmed in order to convert to a
-usable form for further analysis (Feinerer \& Hornik, 2017). Each individual word
-was reduced to its stem (i.e., \emph{diseased} was stemmed to \emph{diseas}). Once
-again, the same procedure was applied to the MFD words and the words in
-the Warriner et al. (2013) dataset. We obtained the words' percent occurrence in
-the text. Percents were multiplied by \emph{z}-scored valence and categorized
-into their proper MFD category.
+The data analysis used the same procedure as Study 1 for preparing the text, and the same weighting procedure described in Study 2 for creating valence scores.
 
@@
 
-We utilized a multilevel model (MLM) to analyze if news sources
-leveraged different vocabularies based on target audience in the same
-manner as Study 2. Each foundation's weighted percentage was predicted
-by the source's political lean, using the individual source as a random
-intercept to control for the nested data structure. Two separate MLMs
-were constructed from datasets compiled for each topic of interest: the
-Kavanaugh hearing and the partial government shutdown of 2018-2019.
-
-For the Kavanaugh topic, the multilevel model indicated the presence of
-a statistically significant effect for \emph{harm/care}, but the practical
-effect denoted by Cohen's \emph{d} was found to be small. There were no other
-significant or practical effects of political lean for any of the other
-four moral foundations. The effect for \emph{harm/care} was in the
-hypothesized direction with liberal sources tending to use more
-positively \emph{harm/care} words than conservative sources. Descriptive and
-test statistics, \emph{p}-values and effect sizes (Cohen's \emph{d}) can be found
-in Table \ref{tab:exp2-tablekav}.
-
-\begin{table}[h]
+The same multilevel models were used to calculate the differences in news sources political lean across foundation areas using either valence weighted scoring or original MFD scoring (see Study 2 for model code).
+
+The pattern of results is nearly identical when examining \(d_s\) scores for standardization, as the scorings are set on different scales (see Table \ref{tab:exp2-tablekav}).
+A few significant results were found: 1) higher fairness scores for conservatives \(d_s\) \textasciitilde{} .40s (both), 2) higher purity scores for conservatives \(d_s\) \textasciitilde{} .47s (original score significant, weighted scores non-significant, but effect sizes were nearly identical).
+In general, the variance is a bit larger for the weighted scores, which may lead to the differences in traditional significance interpretations, and we advise examining effect sizes for interpretation.
+The rest of the effects were nearly zero.
+
+\begin{table}[ht]
 
@@
 \toprule
-Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
+Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d_s$ & ICC\\
 \midrule
-Valence & Harm/Care & -0.35 & 0.69 & -0.32 & 0.69 & 0.58 & .575 & -0.04 & .013\\
-Valence & Fairness/Reciprocity & 0.91 & 0.74 & 0.60 & 0.74 & -2.68 & .028 & 0.42 & .095\\
-Valence & Ingroup/Loyalty & 0.24 & 0.31 & 0.25 & 0.31 & 0.31 & .764 & -0.03 & .004\\
-Valence & Authority/Respect & 0.04 & 0.32 & 0.06 & 0.32 & 1.08 & .313 & -0.06 & .003\\
-Valence & Purity/Sanctity & 0.36 & 0.51 & 0.16 & 0.51 & -1.75 & .118 & 0.47 & .133\\
-Original & Harm/Care & 0.33 & 0.36 & 0.35 & 0.36 & 0.60 & .567 & -0.04 & .010\\
-Original & Fairness/Reciprocity & 0.77 & 0.57 & 0.54 & 0.57 & -2.84 & .022 & 0.40 & .142\\
-Original & Ingroup/Loyalty & 0.34 & 0.37 & 0.37 & 0.37 & 0.35 & .733 & -0.06 & .010\\
-Original & Authority/Respect & 0.43 & 0.49 & 0.46 & 0.49 & 1.20 & .266 & -0.04 & .004\\
-Original & Purity/Sanctity & 0.28 & 0.31 & 0.15 & 0.31 & -2.44 & .040 & 0.49 & .126\\
+Valence & Harm & -0.35 & 0.69 & -0.32 & 0.69 & 0.58 & .575 & -0.04 & .013\\
+Valence & Fairness & 0.91 & 0.74 & 0.60 & 0.74 & -2.68 & .028 & 0.42 & .095\\
+Valence & Ingroup & 0.24 & 0.31 & 0.25 & 0.31 & 0.31 & .764 & -0.03 & .004\\
+Valence & Authority & 0.04 & 0.32 & 0.06 & 0.32 & 1.08 & .313 & -0.06 & .003\\
+Valence & Purity & 0.36 & 0.51 & 0.16 & 0.51 & -1.75 & .118 & 0.47 & .133\\
+Original & Harm & 0.33 & 0.36 & 0.35 & 0.36 & 0.60 & .567 & -0.04 & .010\\
+Original & Fairness & 0.77 & 0.57 & 0.54 & 0.57 & -2.84 & .022 & 0.40 & .142\\
+Original & Ingroup & 0.34 & 0.37 & 0.37 & 0.37 & 0.35 & .733 & -0.06 & .010\\
+Original & Authority & 0.43 & 0.49 & 0.46 & 0.49 & 1.20 & .266 & -0.04 & .004\\
+Original & Purity & 0.28 & 0.31 & 0.15 & 0.31 & -2.44 & .040 & 0.49 & .126\\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively}
+\normalsize{\textit{Note.} For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively.}
 \end{tablenotes}
@@
 For news articles about the partial U.S. Federal Government Shutdown of
-2018-2019, there were no significant or practical effects of political
-lean for the moral foundations (see Table \ref{tab:exp2-tablegs}). A
-small-to-medium effect size was observed for \emph{authority/respect}. The
-effect was in the predicted direction as well, as conservative sources
-tended to offer more positive endorsements of the foundation than
-liberal sources. This effect was similar to Study 2 in which the largest
-effect size was observed for \emph{authority/respect}. As noted before, the
-effect found in Study 2 was in the opposite direction as what was
-hypothesized. Thus, it is difficult to draw comparisons between the two
-studies despite the similar pattern for effect size. Owing to a lack of
-similar effects for either Study 2 or the Kavanaugh topic, there is
-doubt as to whether or not a practical or generalized effect exists for
-\emph{authority/respect}.
-
-Based on the weighted percent values for the five foundations applied to
-both topics, MFD words seem to make up little of the article text. A
-similar pattern was observed for the results in Study 2. As in Study 2,
-the percentages and means seem to indicate a generally positive
-endorsement of all five moral foundations across both political
-leanings.
-
-\begin{table}[h]
+2018-2019, only one significant effect was found (see Table \ref{tab:exp2-tablegs}).
+The original scoring for fairness indicated that conservatives endorsed more fairness related words \(d_s\) = 0.75.
+The valence weighted scoring showed the same effect size \(d_s\) = 0.74, but was non-significant in traditional null hypothesis testing interpretations.
+Both effects would be considered large and in line with previous findings, \emph{except} in the opposition direction of predicted results.
+The same large effects can be found for the purity foundation \(d_s\) = 0.85 (both), in the expected direction that conservative sources endorsed more purity words than liberal sources.
+
+\begin{table}[ht]
 
@@
 \toprule
-Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d$ & ICC\\
+Model & Foundation & $M_C$ & $SD_C$ & $M_L$ & $SD_L$ & $t$ & $p$ & $d_s$ & ICC\\
 \midrule
-Valence & Harm/Care & -0.13 & 0.70 & -0.15 & 0.70 & -0.55 & .594 & 0.03 & .008\\
-Valence & Fairness/Reciprocity & 0.79 & 0.57 & 0.40 & 0.57 & -1.57 & .154 & 0.74 & .139\\
-Valence & Ingroup/Loyalty & 0.35 & 0.39 & 0.37 & 0.39 & 0.53 & .611 & -0.05 & .012\\
-Valence & Authority/Respect & 0.03 & 0.33 & 0.03 & 0.33 & 0.67 & .524 & -0.01 & .004\\
-Valence & Purity/Sanctity & 0.48 & 0.49 & 0.08 & 0.49 & -1.38 & .206 & 0.85 & .155\\
-Original & Harm/Care & 0.34 & 0.38 & 0.36 & 0.38 & 1.24 & .251 & -0.04 & < .001\\
-Original & Fairness/Reciprocity & 0.68 & 0.44 & 0.38 & 0.44 & -2.35 & .047 & 0.75 & .148\\
-Original & Ingroup/Loyalty & 0.51 & 0.50 & 0.54 & 0.50 & 0.23 & .825 & -0.06 & .015\\
-Original & Authority/Respect & 0.42 & 0.44 & 0.43 & 0.44 & 0.58 & .578 & -0.02 & .002\\
-Original & Purity/Sanctity & 0.34 & 0.30 & 0.13 & 0.30 & -1.38 & .206 & 0.85 & .155\\
+Valence & Harm & -0.13 & 0.70 & -0.15 & 0.70 & -0.55 & .594 & 0.03 & .008\\
+Valence & Fairness & 0.79 & 0.57 & 0.40 & 0.57 & -1.57 & .154 & 0.74 & .139\\
+Valence & Ingroup & 0.35 & 0.39 & 0.37 & 0.39 & 0.53 & .611 & -0.05 & .012\\
+Valence & Authority & 0.03 & 0.33 & 0.03 & 0.33 & 0.67 & .524 & -0.01 & .004\\
+Valence & Purity & 0.48 & 0.49 & 0.08 & 0.49 & -1.38 & .206 & 0.85 & .155\\
+Original & Harm & 0.34 & 0.38 & 0.36 & 0.38 & 1.24 & .251 & -0.04 & < .001\\
+Original & Fairness & 0.68 & 0.44 & 0.38 & 0.44 & -2.35 & .047 & 0.75 & .148\\
+Original & Ingroup & 0.51 & 0.50 & 0.54 & 0.50 & 0.23 & .825 & -0.06 & .015\\
+Original & Authority & 0.42 & 0.44 & 0.43 & 0.44 & 0.58 & .578 & -0.02 & .002\\
+Original & Purity & 0.34 & 0.30 & 0.13 & 0.30 & -1.38 & .206 & 0.85 & .155\\
 \bottomrule
@@
 
-The results obtained in Study 3 are slightly more in line with
-expectations from MFT, however, in all but one case, the differences
-were not statistically significant. The only statistically significant
-difference was in the harm foundation; liberals did endorse harm more
-than conservatives during the Kavanaugh hearings, but the effect was
-smaller than expected given Graham et al. (2009). Generally for both the
-Kavanaugh hearings and the Government shutdown, the differences were in
-the expected direction (liberals endorsing harm more and conservatives
-endorsing authority and loyalty more), but the differences were not
-statistically significant and the practical effects much smaller than
-reported in Graham et al. (2009). While not significant, fairness was endorsed
-more by conservatives in both cases. In contrast, purity was endorsed
-more by conservatives for the government shutdown, but more by liberals
-for the Kavanaugh hearing though neither difference was statistically
-significant.
-
-Together with Study 2 and past work, Study 3 further calls into question
-the usefulness and efficacy of the Moral Foundations as well as cast
-doubt on the predictions made by MFT. One issue that Study 3 brings up
-is that moral differences between liberals and conservatives may be
-moderated by a number of factors as shown in Sterling and Jost (2018). For example,
-here we have liberals concerned with purity for the Kavanaugh hearings
-(a moral bad for liberals and a moral good for conservatives) and
-conservatives concerned with purity during the government shutdown (a
-moral bad for conservatives and a moral good for liberals). The original
-predictions made by the Moral Foundations are very simplistic and likely
-much more complex in reality.
+The results obtained in Study 3 portrayed that focused news sources may provide a bit more evidence for the MFD to assess MFT's predictions, at least for purity.
+This result showed a large effect, and depending on the scoring, sometimes the traditional significance matching results from Graham et al.
+(2009).
+The results for fairness were in the opposite direction of expectations, given the MFT and previous studies, where we found that conservatives endorsed more fairness words than liberal sources.
+Study 2 and 3's results indicated that the effect sizes will likely be similar for either the traditional percent or weighted scoring, as they are nearly identical in each study.
+We suggest using the simpler percent scoring, which can be calculated with both programming software \emph{R} and point and click software LIWC (Pennebaker et al., 2007).
 
@@
 Several dictionary improvements were suggested, but the results of a multi-trait multi-method analysis indicate that the MFD does not relate to the moral foundations found in the MFD.
-Therefore, we did not find support for the use of the MFD in relation to the MFT using a convergent and divergent validity technique.
+Therefore, we did not find support for the use of the MFD in relation to the MFQ using a convergent and divergent validity technique.
 
 In Study 2 and 3, we attempted to
-devise a method leveraging the MFD in order to quantify
-political bias stemming from content published by several prominent
-American news sources. In Study 2, the results obtained were not
-significant in any statistical or practical sense. There was a small
-effect found for the \emph{authority/respect} foundation according to Cohen's
-\emph{d}, but the effect suggested endorsement for that foundation opposite
-to what was hypothesized. In Study 3, the direction of the differences
-were generally in line with MFT, however, the difference were very small
-and lacks statistically significance. Building on Frimer (2020) and other
-critiques of MFT and the MFD, we show that MFD is not a useful tool for
-measuring moral language while also calling into question the validity
-of MFT in terms of theorized partisan differences.
-
-Despite the fact the results regarding political bias were inconclusive,
-we still retain confidence in the overall structure of the methodology
-established in the current study. Specifically, the procedure for
-scraping text from the web, processing, stemming, and weighting the
-scores with valence seems to represent a solid method for preparing a
-high quantity of text passages for data analysis. We implemented valence
-as an indicator of the directionality of endorsement due to the inherent
-ambiguity of simply calculating MFD word percent occurrence. This method
-served both to augment the face validity of the MFD by incorporating
-valence (thus reducing ambiguity) and to generate a score that is easy
-to understand and analyze.
-
-However, political lean and other important political/moral constructs
+devise a method leveraging the MFD and valence weighting in order to replicate previous effects on political bias stemming from content published by several prominent American news sources.
+In Study 2, we only discovered a small effect for purity, while all other results obtained were not
+significant in any statistical or practical sense.
+This result was replicated in Study 3 with a larger effect size, along with differences found in fairness, albeit in the opposite direction than predicted.
+Building on Frimer (2020) and other critiques of MFT and the MFD, we show that MFD may not yet be a useful tool for measuring moral language while also calling into question the validity of MFT in terms of theorized partisan differences.
+
+The results from different proposed scoring methods remained consistent with the original percent scoring method.
+This scoring may provide insight into the sentiment of the texts.
+For example, the harm foundation is considered a continuum ranging from harm to care.
+The results from Study 2 and 3 indicate that the MFD likely measures more harm than care across the continuum in our sources.
+In general, given that the weighted valence scoring requires more sophisticated programming skills to implement, we suggest using the original scoring of the MFD with all results taken together.
+
+Political lean and other important political/moral constructs
 may be communicated through methods other than through the use of
@@
 
-In critiquing MFT, Schein and Gray (2015) proposed an alternative theory explaining
+In critiquing the MFT, Schein and Gray (2015) proposed an alternative theory explaining
 moral choices and potential partisan differences: Dyadic Theory of
@@
 harm-focused morality where someone/thing is harmed by someone/thing
-else Schein \& Gray (2015). Rather than liberals and conservatives
+else (Gray, Schein, \& Ward, 2014; Schein \& Gray, 2015). Rather than liberals and conservatives
 having difference conceptions of morality, dyadic morality argues that
@@
 
-\bibitem[\citeproctext]{ref-Feinerer2017}
-Feinerer, I., \& Hornik, K. (2017). \emph{{Text mining package}}. Retrieved from \url{http://tm.r-forge.r-project.org/}
-
 \bibitem[\citeproctext]{ref-feinerer2008}
@@
 
-\bibitem[\citeproctext]{ref-graham2011}
-Graham, J., Nosek, B.
-A., Haidt, J., Iyer, R., Koleva, S., \& Ditto, P.
-H.
-(2011a).
-Mapping the moral domain.
-\emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
-\url{https://doi.org/10.1037/a0021847}
-
 \bibitem[\citeproctext]{ref-Graham2011}
@@
 H.
-(2011b).
+(2011).
 {Mapping the moral domain.} \emph{Journal of Personality and Social Psychology}, \emph{101}(2), 366--385.
@@
 \url{https://doi.org/10.1177/0146167215591501}
-
-\bibitem[\citeproctext]{ref-Schmidt2017}
-Schmidt, M.
-F.
-H., Gonzalez-Cabrera, I., \& Tomasello, M.
-(2017).
-{Children's developing metaethical judgments}.
-\emph{Journal of Experimental Child Psychology}, \emph{164}, 163--177.
-\url{https://doi.org/10.1016/j.jecp.2017.07.008}
 

### 2024-11-30 manuscript_version/revision/revision_letter.Rmd
finalizing the revision letter and manuscript

@@
 Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
+Because we made a large number of changes to the document as requested, we do not copy all the changes here, but note a few specific areas.
+We believe the manuscript is much improved and thank the reviewers for their thoughtful commments.
 
@@
 
-The section in the literature review describing the Frimer study has been expanded like shown below.
-
-“Beyond the critiques of the theory itself, many have also provided strong critiques of the measurement using MFD.
-Conducting two close conceptual replication studies using religious sermons and six extension studies using U.S.
-Congressional speeches, party platforms, State of the Union addresses, media outlets, and political organization texts, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.
-In a meta-analysis, the theorized differences were only found for authority and purity (e.g., conservatives used more authority and purity words).
-Loyalty was contrary to theoretical predictions (e.g., used more by liberals), and no differences were found for harm and fairness.
-Additionally, @Frimer2020 tested the theory under the most forgiving conditions using not only the original MFD but also the revised MFD2 as well using log transformed scores as well as raw scores.
-Even under the best circumstances (log transformed MFD2 scores), only 2 of the foundations showed theorized differences but with very small effects… Like @Frimer2020, we attempt to give the MFD the best chance for success by incorporating a weighting method to address the skewedness and sparsity of the linguistic data.”
+The section in the literature review describing the Frimer study has been expanded to fully describe the study.
 
@@
 
-Given no page limits for the manuscript, we have opted to include this detail for transparency and openness purposes within the manuscript.
-Linguistic analysis heavily relies on the pre-processing steps taken on the data, and informing readers on these actions can help contextualize interpretation.
 We have streamlined in method sections when it was repetitive refering back to previous studies.
+We did keep places in which analyses were different or otherwise it was necessary for clarity (given the other reviewers comments).
 
@@
 We added an example table of the weighting calculation and rephrased this section completely for clarity.
-
-"A complete list of the words for each moral foundation area was created from previous experiments.
-The total number of times each of those words was used in an article was calculated.
-This information was merged with the valence values from the @Warriner2013 dataset.
-A weighted score was calculated by multiplying the frequency of occurrence within a document times the *z*-scored valence values and divided by the word count for that article.
-The final score was multiplied by 100 to represented a weighted percentage.
-Finally, the weighted scores were summed within in each article to get a total weighted percentage of the use of moral area specific words by article."
-
 Unfortunately, as with many linguistic analyses that focus on individual words (as with the MFD), context is lost using these approaches.
@@
 In response to the question about analytic choices, we have added information about a MTMM study (study 1), as well as the exact same statistics using the mean percentages for comparison (study 2-3).
-The results remain the same.
+We believe these additions will allow for comparison of different approaches versus the normal approach and the validity evidence for the MFD.
 

### 2024-11-30 manuscript_version/revision/revision_letter.Rmd
fixing a few typos in the response letter

@@
 
-Dear Dr. Editor,
+Dear Dr. Elson,
 
@@
 Because we made a large number of changes to the document as requested, we do not copy all the changes here, but note a few specific areas.
-We believe the manuscript is much improved and thank the reviewers for their thoughtful commments.
+We believe the manuscript is much improved and thank the reviewers for their thoughtful comments.
 
 In the following we address your and each reviewers' concerns point-by-point.
+
+Preprint: https://osf.io/rmj73/
+
+OSF: https://osf.io/5kpj7/, https://osf.io/rmj73/
 
@@
 
-We have streamlined in method sections when it was repetitive refering back to previous studies.
+We have streamlined in method sections when it was repetitive referring back to previous studies.
 We did keep places in which analyses were different or otherwise it was necessary for clarity (given the other reviewers comments).
